### 2017-12-20 Probabilistic forecasts in hierarchical time series.tex
Add files via upload

\documentclass[a4paper, 11pt]{article}
\usepackage[a4paper, inner=3cm, outer=3cm, top=2cm, bottom=3cm]{geometry}
\usepackage{amsmath, amssymb, fixmath, qtree, bm, calrsfs, enumitem,multirow, caption, textcmds,siunitx,adjustbox, mathrsfs, float, amstext}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usepackage[natbib=true,backend=bibtex,style=authoryear-comp,dashed=false,maxbibnames=99,firstinits=true,maxcitenames=3,url=true,doi=false,isbn=false]{biblatex}
\usepackage[pdftex,colorlinks=true]{hyperref}
\hypersetup{citecolor=blue,linkcolor=blue,urlcolor=blue}
\DeclareNameAlias{sortname}{last-first}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type

\bibliography{References_paper1}
\begin{document}

\title{Probabilistic Forecasts in Hierarchical Time Series}
\maketitle

\section{Introduction.}
\begin{itemize}
	\item Introduction to hierarchical time series including a literature review in the context of point forecasts. 
	\item Importance of probabilistic forecasts in time series.
	\item Lack of attention in the context of probabilistic forecasts in hierarchical literature.

\end{itemize}

\section{Notations}
We first introduce notations where possible we follow \citet{Wickramasuriya2017}. Suppose $\mathbold{y}_t \in \bm{\mathbb{R}}^n$ comprising all observations of the whole hierarchy at time $t$ and $\mathbold{b}_t \in \bm{\mathbb{R}}^m$ comprising only the bottom level observations at  time $t$. Then due to the aggregation nature of the hierarchy we have,

\begin{equation}
\mathbold{y}_t = \mathbold{Sb}_t,
\end{equation}
where $\mathbold{S}$ is a $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold. Since this linear subspace is equivalent to the column space of $\bm{S}$, we denote it as $\mathscr{C}(\bm{S})$. Further the null space of $\bm{S}$ which is orthogonal to this linear subspace is denoted by $\mathscr{N}(\bm{S})$. 
To understand the notations clearly, consider the hierarchy given in Figure 1.\\

\begin{figure}
	\begin{center}
		\leaf{AA} \leaf{AB} \leaf{AC}
		\branch{3}{A}
		\leaf{BA} \leaf{BB}
		\branch{2}{B}
		\branch{2}{Tot}
		\qobitree
	\end{center}
	\caption{Two level hierarchical diagram}
\end{figure}
\noindent
In any hierarchy, the most aggregated level is termed as level 0, the second most aggregated level is termed as level 1 and so on. This example consists of two levels. At a particular time $t$, let $y_{T,t}$ denote the observation at level 0; $y_{A,t}, y_{B,t} $ denote observations at level 1; and $y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}$ denote observations at level 2. Then $\mathbold{y}_t = [y_{T,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}]^T$, \\$\mathbold{b}_t = [y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}]^T$, $m=7$, n=11$, $ and $$ \mathbold{S} = \begin{pmatrix} 1& 1 &1 &1 &1 \\ 1 &1 &1 & 0 &0 \\   0&0 &0 & 1 & 1 \\ & & I_5 &  & \end{pmatrix}, $$ where $I_5$ is a $5$-dimension identity matrix. \\

\section{Coherent forecasts}

The main purpose of this section is to provide formal definitions for coherent forecasts. We start with redefining the coherent point forecasts using the properties of vector spaces which is then followed by the definition of coherent probabilistic forecasts. 
\\

\noindent
\textbf{Definition 3.1: Coherent Point Forecasts}\\
\noindent
Suppose $\bm{\breve{y}}_{t+h} \in \mathbb{R}^n$ consists point forecasts of each series in the hierarchy at time $t+h$.  $\bm{\breve{y}}_{t+h}$ is said to be \textit{Coherent} if it lies in a $m$-dimensional subspace of $\bm{\mathbb{R}}^n$ which is spanned by the columns of $\bm{S}$. \\

\noindent
\textbf{Definition 3.2: Coherent Probabilistic Forecasts}\\
\noindent
Let $(\bm{\mathbb{R}}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability measure space where $\mathscr{F}^m$ is a sigma algebra on $\bm{\mathbb{R}}^m$. $\breve{\nu}(.)$ on $(\mathscr{C}(\bm{S}), \mathscr{F}_{\bm{S}})$ is said to be coherent probability measure iff $$\breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall \quad \bm{A} \in \mathscr{F}^m,$$ where $\bm{S}(\bm{A})$ denotes the image of subset $\bm{A}$ under $\bm{S}$.

\usetikzlibrary{arrows,positioning,shapes,fit,calc}

\begin{figure}[H]
	\begin{center}
		\begin{tikzpicture}[
		>=stealth,
		bullet/.style={
			fill=black,
			circle,
			minimum width=1.5cm,
			inner sep=0pt
		},
		projection/.style={
			->,
			thick,
			label,
			shorten <=2pt,
			shorten >=2pt
		},
		every fit/.style={
			ellipse,
			draw,
			inner sep=0pt
		}
		]

		\node at (2,3) {$\bm{S}$};

		\node at (0,5) {$\bm{\mathbb{R}}^m$(domain of $\bm{S}$)};
		\node at (4,5) {$\bm{\mathbb{R}}^n$(codomain of $\bm{S}$)};
		\node at (4,1.0) {$\mathscr{C}(\bm{S})$};
		%\node[bullet,label=below:$f(x)$] at (4,2.5){};

		\draw (0,2.5) ellipse (1.02cm and 2.2cm);
		\draw (4,2.5) ellipse (1.02cm and 2.2cm);
		\draw (4,2.5) ellipse (0.51cm and 1.1cm);

		\draw[projection, label=below:$f$] (0.3,2.5) -- (3.8,2.5) ;

		\end{tikzpicture}
		\newline
	\end{center}
	\caption{Any set $\bm{A} \in \bm{\mathbb{R}}$ will be mapped to the $\mathscr{C}(\bm{S})$ through the mapping $\bm{S}$}
\end{figure}
\noindent
Definition 3.2 implies the probability measure on $\mathscr{C}(\bm{S})$ is equivalent to the probability measure on $(\bm{\mathbb{R}}^m, \bm{\mathscr{F}}^m)$. Hence, there is no density anywhere outside the linear subspace spanned by the columns of $\bm{S}$. That is, a \textit{Coherent probability density forecast} is any density $\bm{f}(\bm{\breve{y}}_{t+h})$ such that $\bm{f}(\bm{\breve{y}}_{t+h})=0$ for all $\bm{\breve{y}}_{t+h}$ in the null space of $\bm{S}$. Following example will help to understand these definitions more clearly.\\

\noindent
\textbf{Example 1}\\
\noindent
Consider a simple hierarchy with two bottom level series A and B that add up to the top level series T. Suppose the forecasts at time $t+h$ of these series are given by $\mathbold{\breve{y}}_{t+h} = [\breve{y}_{T,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$ and $\mathbold{\breve{y}}_{t+h} \in \bm{\mathbb{R}}^3$. Due to the aggregation constraint of the hierarchy we have $\breve{y}_{T,t+h}=\breve{y}_{A,t+h}+\breve{y}_{B,t+h}$. This implies, even though  $\mathbold{\breve{y}}_{t+h}$ is in $\bm{\mathbb{R}}^3$, the points actually lie in a two dimensional subspace within that $\bm{\mathbb{R}}^3$ space. This subspace is equivalent to $\mathscr{C}(\bm{S})$ for this simple hierarchy. Therefore, for any $\mathbold{\breve{y}}_{t+h} \in \mathscr{N}(\bm{S})$ have a zero probability. I.e. $f(\mathbold{\breve{y}}_{t+h})=0$ for any $\mathbold{\breve{y}}_{t+h} \in \mathscr{N}(\bm{S})$.\\

\noindent
By the definition of coherent forecasts, it is clear that there are only $m$ number of linear independent series in the whole hierarchy. We refer to these as $m$ dimensional \textit{basis set of series} since these series generates a \textit{basis} that spans the $\mathscr{C}(\bm{S})$. Other $n-m$ series of the hierarchy can be linearly determined by these basis set of series. This implies that any coherent density is a degenerate density. We can think of the $m$ bottom level series of a given hierarchy as a basis set of series. Then the columns of $\bm{S}$ is a basis that generates through the bottom level series. This basis spans the linear subspace where the degenerate density lives on.\\

\noindent
However bottom level series are not the only set of basis series and we can find many other basis set of series which generates basis that spans the same $\mathscr{C}(\bm{S})$ for a given hierarchy. If we go back to the hierarchy in example 1, instead of two bottom level series $(\bm{A,B})$ we can take $(\bm{T,A})$ as the basis set of series and the basis that generates through $(\bm{T,A})$ will be $\{\begin{pmatrix}
1&0&1 \end{pmatrix}^T, \begin{pmatrix}
0&1&-1 \end{pmatrix}^T\}$. Another possible basis would be the singular value decomposition of $\bm{S}$.\\

\noindent
An important thing to notice here is all of these basis spans the same linear subspace equivalent to the $\mathscr{C}(\bm{S})$. Therefore the definition $(3.2)$ is not unique and one can redefine the coherent probabilistic forecasts with respect to any basis. However we stick to the definition $(3.2)$ and consider the basis defined by the columns of $\bm{S}$ that generates through the bottom levels of the hierarchy in what follows.\\

\noindent
It is also worth to mention that the definition $(3.1)$ and $(3.2)$ facilitate extension to the forecast reconciliation which we talk about in the next section. In contrast to our definition, \citet{BenTaieb2017} defines the coherent probabilistic forecasts in terms of convolution. According to their definition, if the forecasts are coherent, then the convolution of forecast distributions of disaggregate series is same as the forecast distribution of the corresponding aggregate series. This is the only study that copes with probabilistic forecasts in hierarchical literature thus far.

\section{Forecast reconciliation}
\noindent
Bottom-up, top-down and middle-out methods are the most traditional forecasting methods that were used to produce coherent point forecasts in early studies on hierarchical literature. In bottom-up approach, forecasts of the lowest level are first generated and they are simply aggregated to forecast the upper levels of the hierarchy \citep{Dunn1976}. 
In contrast, the top-down approach involves forecasting the most aggregated series first and then disaggregating these forecasts down the hierarchy based on the proportions of observed data \citep{Gross1990}. A compromise between these two approaches is the middle-out method which entails forecasting each series of a selected middle level in the hierarchy and then forecasting upper levels by the bottom-up method and lower levels by the top-down method.\\

\noindent
These three approaches use only a part of the information available when producing coherent forecasts. This might result inaccurate forecasts. For example, if the bottom level series are highly volatile or too noisy and hence challenging to forecast, then the resulting forecasts from bottom-up approach would be inaccurate.\\

\noindent
As an alternative to these conventional methods, \citet{Hyndman2011} propose to use information from all the levels of the hierarchy and reconcile them to obtain coherent point forecasts. In this approach, independent forecasts of all series are initially obtained. It is very unlikely that these forecasts are coherent. Then, these forecasts are optimally combined through a regression model to obtain coherent forecasts. This study has given arise to the concept of point forecast reconciliation in hierarchical time series. In general, any forecasting method that use a set of incoherent forecasts and revise them to obtain coherent forecasts is referred to as forecast reconciliation method. For example, Minimum Trace reconciliation \citep{Wickramasuriya2017}, GTOP \citep{VanErven2015a}. It is important to notice that bottom-up, top-down and middle-out methods are not reconciliation methods since they only use forecasts from a part of the levels in the hierarchy when producing coherent forecasts. \\

\subsection{Point forecast reconciliation}

Even though the point forecast reconciliation has a well established literature, we would like to redefine this using concepts in linear algebra as a groundwork for the probabilistic forecast reconciliation. \\

\noindent
\textbf{Definition 4.1}\\
\noindent
Let $\bm{g}:\bm{\mathbb{R}}^n \rightarrow \bm{\mathbb{R}}^m $ and $\hat{\bm{y}}_{t+h} \in \bm{\mathbb{R}}^n$ be any set of incoherent forecasts at time $t+h$. Then $\tilde{\bm{b}}_{t+h}$ is said to be reconciled bottom level forecasts if 
\begin{equation}
\tilde{\bm{b}}_{t+h}=\bm{g}(\hat{\bm{y}}_{t+h}),
\end{equation}
\noindent
where $\bm{g}(\hat{\bm{y}}_{t+h})$ is the image of $\hat{\bm{y}}_{t+h}$ under $\bm{g}$ on $\bm{\mathbb{R}}^m$. The reconciled forecasts for the whole hierarchy is then given by $\tilde{\bm{y}}_{t+h}=\bm{S}(\tilde{\bm{b}}_{t+h})$ such that $\tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})$, where $\bm{S}(\tilde{\bm{b}}_{t+h})$ is the image of $\tilde{\bm{y}}_{t+h}$ under $\bm{S}$ on the $\mathscr{C}(\bm{S}) < \bm{\mathbb{R}}^n$.\\

\noindent
In the following content we explain more on how this definition can be used in practice to reconcile point forecasts in hierarchical time series. Let $\bm{R} \in \bm{\mathbb{R}}^{n \times n-m}$ consists the columns that spans $\mathscr{N}(\bm{S})$ which is orthogonal to $\mathscr{C}(\bm{S})$. $\mathscr{N}(\bm{S})$ is also equivalent to the $\mathscr{C}(\bm{R})$. Note that $\bm{R}$ is also not unique and one example is a matrix whose columns represent the aggregation constraints for the hierarchy. Then for the hierarchy in example 1, $$ \mathbold{S} = \begin{pmatrix} 1& 1 \\ 1 & 0 \\ 0&1 \end{pmatrix} \quad \text{and} \quad \mathbold{R} = \begin{pmatrix}  1 \\ -1 \\ -1 \end{pmatrix}.$$ 
\noindent
Further let $\{\bm{s}_1,...,\bm{s}_m\}$ and $\{\bm{r}_1,...,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively. Then $\bm{B}=\{\bm{s}_1,...,\bm{s}_m, \bm{r}_1,...,\bm{r}_{n-m}\}$ is a basis for $\bm{\mathbb{R}}^n$. Now, using the insights of definition 4.1, we can follow the below steps to reconcile the point forecasts.\\

\noindent
\textbf{Step 1: Obtaining reconciled bottom level point forecasts}\\

\noindent
For a given incoherent set of point forecasts $\hat{\bm{y}}_{t+h} \in \bm{\mathbb{R}}^n$, first we find the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$. Let $\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T$ denote these coordinates. Note that $\tilde{\bm{b}}_{t+h}$ is a basis set of series which is really the reconciled bottom level series that generates $\{\bm{s}_1,...,\bm{s}_m\}$ and $\tilde{\bm{t}}_{t+h}$ is another basis set of series that generates $\{\bm{r}_1,...,\bm{r}_{n-m}\}$. Then from basic properties of linear algebra it follows that,

\begin{flalign}\label{4.1}
\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T = \hat{\bm{y}}_{t+h},
\end{flalign}
\begin{flalign}\label{4.2}
\hat{\bm{y}}_{t+h} = \bm{S}\tilde{\bm{b}}_{t+h} +  \bm{R}\tilde{\bm{t}}_{t+h},
\end{flalign}
\noindent
and
\begin{flalign}\label{4.3}
\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T  = \begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\hat{\bm{y}}_{t+h}.
\end{flalign}

\noindent
In order to find $(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1}$, let $\bm{S}_{\bot}$ and $\bm{R}_{\bot}$ be the orthogonal complements of $\bm{S}$ and $\bm{R}$ 
respectively. Then $(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1}$ is given by,

\begin{flalign}
\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
(\bm{R}_\bot \bm{S})^{-1}\bm{R}_\bot\\ \cdots \\ (\bm{S}_\bot \bm{R})^{-1}\bm{S}_\bot
\end{pmatrix}.
\end{flalign}

\noindent
Thus we have, 
\begin{flalign} \label{4.4}
\begin{pmatrix}
\tilde{\bm{b}}_{t+h}\\ \cdots \\ \tilde{\bm{t}}_{t+h}
\end{pmatrix} = \begin{pmatrix}
(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot\\ \cdots \\ (\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot
\end{pmatrix}\hat{\bm{y}}_{t+h}.
\end{flalign}

\noindent
From (\ref{4.4}) it follows that, 
\begin{flalign}
\tilde{\bm{b}}_{t+h}=(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot \hat{\bm{y}}_{t+h} 
\end{flalign}
\\

\noindent
\textbf{Step 2: Obtaining reconciled point forecasts for the whole hierarchy}\\

\noindent
This step directly followed by the definition for coherent forecasts. That is, to obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \bm{\mathbb{R}}^n$ to the $\mathscr{C}(\bm{S})$ through $\bm{S}$. Thus we have, 
\begin{flalign}
\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})<\bm{\mathbb{R}}^n
\end{flalign}

\noindent
Finding a suitable $\bm{R}_\bot$ with respect to a certain loss function will results optimally reconciled point forecasts of the hierarchy. Notice that, if the mapping $\bm{g}$ in definition 4.1 is considered to be linear we have,
\begin{flalign}
\bm{g}=(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot.
\end{flalign}
\noindent
In previous studies on hierarchical point forecasting, $\bm{g}$ is also considered as a $m \times n$ matrix $\bm{P}$ and thus $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$. 
In other words, $\bm{g}$ linearly projects incoherent point forecasts onto the $\mathscr{C}(\bm{S})$. Further in our context, we need to find $\bm{R}_\bot$ such that $\bm{R}^T_\bot \bm{S}$ is invertible. i.e, $(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot \bm{S}=\bm{I}$. This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}.

\noindent
In their study, \citet{Hyndman2011} proposed to choose,
\begin{flalign*}
\tilde{\bm{b}}^{OLS}_{t+h}=(\bm{S}^T \bm{S})^{-1}\bm{S}^T \hat{\bm{y}}_{t+h},
\end{flalign*}
\noindent
where in this context, $\bm{R}^T_\bot = \bm{S}^T$. Thus the reconciled point forecasts for the entire hierarchy is given by, 
\begin{flalign}
\tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}^T \bm{S})^{-1}\bm{S}^T \hat{\bm{y}}_{t+h}.
\end{flalign}
\noindent
They referred this to as OLS solution and the loss function they considered is equivalent to the euclidean norm between $\hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h}$, i.e. $<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>$.\\

\noindent
According to a recent study by \citet{Wickramasuriya2017}, choosing $\bm{R}^T_\bot = \bm{S}^T\hat{\bm{W}}^{-1}_{T+h}$ will minimize the trace of mean squared reconciled forecasts errors under the property of unbiasedness. $\hat{\bm{W}}^{-1}_{T+h}$ is the variance of the incoherent forecast errors. This will result, 
\begin{flalign*}
\tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}^T\hat{\bm{W}}^{-1}_{T+h} \bm{S})^{-1}\bm{S}^T\hat{\bm{W}}^{-1}_{T+h} \hat{\bm{y}}_{t+h},
\end{flalign*}
and thus,
\begin{flalign}
\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}^T \hat{\bm{W}}^{-1}_{T+h}\bm{S})^{-1}\bm{S}^T\hat{\bm{W}}^{-1}_{T+h} \hat{\bm{y}}_{t+h}.
\end{flalign}

\noindent
They referred this to as MinT solution. It is also worth to notice that the loss function they considered is equivalent to the Mahalanobis distance between $\hat{\bm{y}}_{T+h}$ and $\tilde{\bm{y}}_{T+h}$. i.e. $<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>_{\hat{\bm{W}}}$.

\subsection{Probabilistic forecast reconciliation}

In terms of probabilistic forecasts, the reconciliation implies finding the probability measure of the coherent forecasts using the information of incoherent probabilistic forecast measure. A more formal definition is given below. \\

\noindent
\textbf{Definition 4.2}\\
\noindent
Suppose $(\bm{\mathbb{R}}^n, \mathscr{F}^n, \hat{\nu})$ be an incoherent probability measure space and $(\bm{\mathbb{R}}^m, \mathscr{F}^m, \nu^m)$ be a probability measure space defined on $\bm{\mathbb{R}}^m$. Let $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m $. Then the probability measure on reconciled bottom levels is such that, 
\begin{flalign}
\nu^m(\bm{A}) = \hat{\nu}(\bm{g}^{-1}(\bm{A})), \quad \forall \quad \bm{A} \in \mathscr{F}^m.
\end{flalign}
\noindent
Further the reconciled probability measure of the whole hierarchy is given by, 
\begin{flalign}
\tilde{\nu}(\bm{S}(\bm{A})) = \hat{\nu}(\bm{g}^{-1}(\bm{A})), \quad \forall \quad \bm{A} \in \mathscr{F}^m,
\end{flalign}
\noindent
where, $\bm{S}:\mathbb{R}^m \rightarrow \mathbb{R}^n$ and $\tilde{\nu}(.)$ is the probability measure on the measure space $(\mathscr{C}(\bm{S}), \mathscr{F}_S)$.\\

\noindent
Since the above definition seems not to be straight forward in reconciling incoherent forecasts, the following content explains how this can be used in practice to obtain reconciled probabilistic forecasts for hierarchical time series. \\

\noindent
Recall that $\hat{\bm{y}}_{t+h}$ is a set of incoherent point forecasts and the coordinates of that with respect to the basis $\bm{B}$ is given by (\ref{4.1}). Suppose $\hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ is the probability density of $\hat{\bm{y}}_{t+h}$. Our goal is to reconcile $\hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ such that the density lives on the $\mathscr{C}(\bm{S})$. In order to obtain this reconciled density, we need to project $\hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ onto the $\mathscr{C}(\bm{S})$ along the direction of $\mathscr{C}(\bm{R})$. \\

\noindent
Let the density of coordinates of $\hat{\bm{y}}_{t+h}$ with respect to basis $\bm{B}$ is denoted by $\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})$. Then it follows from  (\ref{4.3}) and the facts on density of transformed variables,

\begin{flalign}\label{4.5}
\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad det(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array}),
\end{flalign}
\noindent
where $det(.)$ denote the determinant of a matrix. Now that we have the density of $\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T $, the marginal density of $(\tilde{\bm{b}}_{t+h})$ can be obtained by integrating (\ref{4.5}) over the range of $\tilde{\bm{t}}_{t+h}$. This will result the reconciled density of the bottom level series $(\tilde{\bm{b}}_{t+h})$. i.e.,
\begin{flalign}
\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\int_{lim(\tilde{\bm{t}}_{t+h})}\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad det(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})\quad d\tilde{\bm{t}}_{t+h}.
\end{flalign}

\noindent
Finally to get the reconciled density of the whole hierarchy, we simply follow the definition $(3.2)$ and have, 
\begin{flalign}
\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\bm{S}\circ \tilde{\bm{f}}(\tilde{\bm{b}}_{t+h}).
\end{flalign}

\noindent
This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the $\mathscr{C}(\bm{S})<\bm{\mathbb{R}}^n$

\section{Evaluation of hierarchical probabilistic forecasts}

The necessary final step in hierarchical forecasting is to make sure that our forecast distributions are accurate enough to predict the uncertain future. In general, forecasters prefer to maximize the sharpness of the predictive distribution subject to the calibration \citep{Gneiting2014}. Therefore the probabilistic forecasts should be evaluated with respect to these two properties.\\

\noindent
Calibration refers to the statistical compatibility between probabilistic forecasts and realizations. In other words, random draws from a perfectly calibrated predictive distribution should be equivalent to the realizations. The uniformity in Probability Integral Transformation (PIT) of predictive densities evaluated at realizations implies well calibrated probabilistic forecasts. Therefore, assessing the uniformity in PIT of predictive densities, by inspecting their histograms and correlograms can be used as a simple tool for evaluating the calibration of probabilistic forecasts.  \\

\noindent
On the other hand, sharpness refers to the spread or the concentration of prediction distributions and it is a property of forecasts only. The more concentrated the predictive distributions, the sharper the forecasts are \citep{Gneiting2008}. The sharpness of density forecasts can be assessed in terms of the prediction intervals. Sharper density forecasts will have shorter prediction intervals. However, independently assessing the calibration and sharpness will not help to properly evaluate the probabilistic forecasts. Therefore to assess these properties simultaneously, we use scoring rules. \\

\noindent
Scoring rules are summary measures obtained based on the relationship between predictive distribution and the realizations. In some studies, researchers take the scoring rules to be positively oriented which they would wish to maximize \citep{Gneiting2007}. However, scoring rules were also defined to be negatively oriented which forecasters wish to minimize \citep{Gneiting2014}. We consider these negatively oriented scoring rules to evaluate probabilistic forecasts in hierarchical time series. \\

\noindent
Let $\bm{Y}$ be a $n$-dimensional random vector from the predictive distribution $\mathbold{F}$ and $\mathbold{y}$ be $n$-dimension vector of realizations. Scoring rule is a numerical value $S(\mathbold{Y,y})$ assign to each pair $(\mathbold{Y,y})$. Suppose the true distribution of $\mathbold{y}$ is given by $\mathbold{G}$. Then the proper scoring rule is defined as,
\begin{equation}\label{eq:(3.1.)}
S(\mathbold{G,G}) \le S(\mathbold{Y,G}),
\end{equation}
\noindent
where $S(\mathbold{Y,G})=E_{\mathbold{G}}[S(\mathbold{Y,y})]$ is the expected score under the true distribution $\mathbold{G}$ \citep{Gneiting2008, Gneiting2014}. \\

\noindent
Let $\bm{\tilde{Y}}_{T+h}$ and $\bm{\tilde{Y}}'_{T+h}$ be two independent random vectors from the coherent forecast distribution $\tilde{\bm{F}}$ with the density function $\tilde{\bm{f}}(.)$ at time $t+h$ and $\bm{y}_{T+h}$ is the vector of realizations. Further $\tilde{Y}_{T+h,i}$ and $\tilde{Y}_{T+h,j}$ are $i^{\text{th}}$ and $j^{\text{th}}$ components of the vector $\tilde{\bm{Y}}_{T+h}$. Then the following table summarizes few existing proper scoring rules.

\begin{center}
	\captionof{table}{\textit{Scoring rules to evaluate multivariate forecast densities }}

	\resizebox{\linewidth}{!}{

		\begin{tabular}{ L | L | L}
			\hline
			\hline
			\textbf{Scoring rule} & \textbf{Expression} & \textbf{Reference}\\
			\\
			\hline
			\hline \\
			\text{Log score} & LS(\tilde{\bm{F}},\bm{y}_{T+h}) = -log {\tilde{\bm{f}}(\bm{y}_{T+h})} & \text{\citet{Gneiting2007}} \\
			\\ 
			\hline \\
			\text{Energy score} & eS(\bm{\tilde{Y}_{T+h},y_{T+h}}) = E_{\tilde{\bm{F}}}||\tilde{\bm{Y}}_{T+h}-\bm{y}_{T+h}||^\alpha - \frac{1}{2}E_{\tilde{\bm{F}}}||\tilde{\bm{Y}}_{T+h}-\tilde{\bm{Y}}'_{T+h}||^\alpha, \alpha \in (0,2] & \text{\citet{Gneiting2008}} \\
			\\
			\hline
			\text{Variogram score} & VS(\tilde{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - E_{\tilde{\bm{F}}}|\tilde{Y}_{T+h,i}-\tilde{Y}_{T+h,j}|^p\right)^2 & \text{\citet{SCHEUERER2015}} \\
			\hline
		\end{tabular}

		}
\end{center}

\noindent
Log scores can be used to evaluate the hierarchical probabilistic forecasts if it is reasonable to assume a parametric forecast density for the hierarchy. However the \qq{degenerecy} of the coherent forecast densities would be problematic when using log scores. We will discuss more about this in the next sub section.\\

\noindent
In the energy score, for $\alpha=2$, it can be easily shown that
\begin{equation} \label{eq:(5.1)}
eS(\bm{\tilde{Y}_{T+h},y_{T+h}}) = ||\bm{y}_{T+h}-\tilde{\bm{\mu}}_{T+h}||^2,
\end{equation}

\noindent
where $\tilde{\bm{\mu}}_{T+h} =E_{\bm{F}}(\tilde{\bm{Y}}_{T+h}) $. Therefore in the limiting case, the energy score only measures the accuracy of the forecast mean, but not the entire distribution. Further \citet{Pinson2013a} argued that the Energy score given in table 1 has a very low discrimination ability for incorrectly specified covariances, even though it discriminates the misspecified means well. \\

\noindent
The variogram score given in Table $1$ is for order $p$ where, $w_{ij}$ are non-negative weights. \citet{SCHEUERER2015} have shown that the variogram score has a high discrimination ability of misspecified means, variance and correlation structure than the Energy score. Further they suggested the variogram score with $p=0.5$ is more powerful.\\

\noindent
For a possible finite sample of size $B$ from the multivariate forecast density $\tilde{\bm{F}}$, the variogram score is defined as,

\begin{flalign}
VS(\tilde{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - \frac{1}{m} \displaystyle\sum_{k=1}^{B} |\tilde{Y}^k_{T+h,i}-\tilde{Y}^k_{T+h,j}|^p\right)^2.
\end{flalign}

%For example, assume you have a Gaussian coherent predictive density $\bm{\tilde{f}}_{T+h}$. Then the log score is given by,

%\begin{equation} 
%LS(\bm{\tilde{f}_{T+h},y_{T+h}}) = -\log \left(\frac{1}{(2\pi)^{\frac{m}{2}}|\bm{\tilde{\Sigma}}_{T+h}|^{\frac{1}{2}}}\exp\left[-\frac{1}{2}(\bm{y}_{T+h}-\bm{\tilde{\mu}}_{T+h})^T %\bm{\tilde{\Sigma}_{T+h}}^{-1}(\bm{y}_{T+h}-\bm{\tilde{\mu}}_{T+h})\right]\right),
%\end{equation}

%\noindent
%where $\bm{\tilde{\mu}}_{T+h}$ and $\bm{\tilde{\Sigma}}_{T+h}$ are the coherent mean and variance-covariance matrix of the predictive Gaussian density and both lies in the linear %subspace spanned by $\mathscr{C}(\bm{S})$. Then $\bm{\tilde{\Sigma}}_{T+h}$ is always a singular matrix and hence the determinant will be zero. Therefore the density function of %degenerate Gaussian distribution is undefined. However, we could use the pseudo determinant, i.e. product of positive eigenvalues and the pseudo inverse to calculate the log score %to compare the predictive ability of coherent forecast densities.

\subsection{Evaluating coherent forecast densities}

As it was mentioned in the previous section, any coherent hierarchical forecast density is a degenerate density. To the best of our knowledge, there is no proper multivariate scoring rule that has been introduced in literature to evaluate densities with degeneracy. Further it can be easily seen that some of the existing scoring rules breakdown under the degeneracy. For example take the log score in the univariate case. Suppose the true density is degenerate at $x=0$, i.e. $f(x)=\mathbb{1}\{x=0\}$.  Now consider two predictive densities $p_1(x)$ and $p_2(x)$. Let $p_1(x)$ is equivalent to the true density, i.e. $p_1(x)=\mathbb{1}\{x=0\}$ and $p_2(x) =^d N(0,\sigma^2)$ with $\sigma^2 < (2\pi)^{-1}$. The expected log score of $p_1$ is:
$$S(f,f) = S(p_1,f) -ln[p_1(x=0)]=0,$$
\noindent
and that of $p_2$ is:
$$S(p_2,f) = -ln[p_2(x=0)]<0.$$ 
\noindent
Therefore $S(f,f) > S(p_2,f)$ and hence there exist at least one forecast density which breaks the condition (\ref{eq:(3.1.)}) for proper scoring rule. This implies log score cannot be used to evaluate the degenerate densities.  \\

\noindent
This suggest that it is necessary to have a rule of thumb to use these scoring rules in order to evaluate coherent forecast densities. First we should notice that, even though the coherent distribution of the entire hierarchy is degenerate, the density of the basis set of series is non-degenerate since these series are linearly independent. Further, if we can correctly specify the forecast distribution of these basis set of series, then we have almost obtained the correct forecast distribution of the whole hierarchy. Therefore, we propose to evaluate the predictive ability of only the basis set of series of the coherent forecast density by using any of the above discussed multivariate scoring rules. This will also avoid the impact of degeneracy for the scoring rules. \\

\noindent
For example, since the bottom level series is a set of basis series for a given hierarchy, we can evaluate the predictive ability of the bottom level series of the coherent forecast distribution instead of evaluating the whole distribution. Further if our purpose is to compare two coherent forecast densities, we can compare the forecast ability of only the bottom level forecast densities.

\subsection{Comparison of coherent and incoherent forecast densities}

It is also important to assess how the coherent or reconciled forecast densities improve the predictive ability compared to the incoherent forecasts. Clearly we cannot use multivariate scoring rules, even for the basis set of series, since the coherent and incoherent forecast densities lie in two different matrix spaces.\\

\noindent
However you could compare individual margins of the forecast density of the hierarchy using univariate proper scoring rules. Most widely used Continuous Ranked Probability Score (CRPS) for evaluating univariate forecast densities would be helpful for this. \\

\begin{equation} \label{eq:(3.6)}
CRPS(\tilde{F}_i,y_{T+h,i}) = E_{\tilde{F}_i}|\tilde{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}E_{\tilde{F}_i}|\tilde{Y}_{T+h,i}-\tilde{Y}'_{T+h,i}|,
\end{equation}

\noindent
where $\tilde{Y}_{T+h,i}$ and $\tilde{Y}'_{T+h,i}$ are two independent copies from the $i^{\text{th}}$ reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy and $y_{T+h,i}$ is the $i^{\text{th}}$ realization from the true marginal distribution $G_i$.

\subsection{Simulation study}

\section{Conclusions.}

\newpage
\printbibliography
\end{document}

### 2018-01-02 Probabilistic forecasts in hierarchical time series.tex
Add files via upload

@@
 i.e.,
-\begin{flalign}
+\begin{flalign}\label{4.6}
 \tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\int_{lim(\tilde{\bm{t}}_{t+h})}\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad det(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})\quad d\tilde{\bm{t}}_{t+h}.
@@
 \noindent
-This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the $\mathscr{C}(\bm{S})<\bm{\mathbb{R}}^n$
+This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the $\mathscr{C}(\bm{S})<\bm{\mathbb{R}}^n$\\
+
+\noindent
+\textbf{Example 2}\\
+
+\noindent  
+Suppose $\hat{\bm{Y}}_{t+h} \sim \mathscr{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h}) \leftrightarrow^d \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$. Then from (\ref{4.5}) it follows,
+
+\begin{flalign*}
+\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad \Big|\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array}\Big| = \frac{\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) }{\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|}.
+\end{flalign*}
+\noindent
+By substituting the Gaussian distribution function to $\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})$ we get,
+
+\begin{flalign*}
+\bm{f_B}(.)&=\frac{\exp\left\{-\frac{1}{2}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})^T \bm{\hat{\Sigma}_{t+h}}^{-1}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
+&= \frac{\exp\left\{-\frac{1}{2}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\bm{\hat{\mu}}_{t+h}\Big)^T \bm{\hat{\Sigma}_{t+h}}^{-1}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
+\end{flalign*}
+
+\begin{flalign*}
+\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|}
+\exp \Big\{&-\frac{1}{2}\Big(\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big)^T\\
+&\Big[\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^T\Big]^{-1}\\ 
+&\Big(\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.
+\end{flalign*}
+\noindent
+Recall that, $\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
+(\bm{R}_\bot \bm{S})^{-1}\bm{R}_\bot\\ \cdots \\ (\bm{S}_\bot \bm{R})^{-1}\bm{S}_\bot
+\end{pmatrix} = \begin{pmatrix}
+\bm{P}\\\bm{Q}
+\end{pmatrix},$(say). Then,
+
+\begin{flalign*}
+\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix} \Big|}
+\exp \Big\{&-\frac{1}{2}\Big[\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\mu}}_{t+h}\Big]^T\Big[\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}^T\Big]^{-1}\\
+&\Big[\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\mu}}_{t+h}\Big] \Big\},
+\end{flalign*}
+
+\begin{flalign*}
+\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}^T\Big|^{\frac{1}{2}}}
+\exp \Big\{&-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix}^T \Big[\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}^T\Big]^{-1}\\
+& \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix} \Big\}.
+\end{flalign*}
+\noindent
+Since, $\Big[\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}^T\Big] = \begin{pmatrix}
+\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T\\
+\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T
+\end{pmatrix}$ we have,
+
+\begin{flalign*}
+\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\begin{pmatrix}
+	\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T\\
+	\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T
+	\end{pmatrix}\Big|^{\frac{1}{2}}}
+\exp \Big\{&-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix}^T\\ 
+&\Big[\begin{pmatrix}
+\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T\\
+\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T
+\end{pmatrix}\Big]^{-1} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix} \Big\}.
+\end{flalign*}
+\noindent
+$\bm{f_B}(.)$ gives the joint distribution of $\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T $, which is a multivariate Gaussian distribution.
+Then from (\ref{4.6}) and the properties of marginalization of multivariate Gaussian distribution it follows,
+
+\begin{flalign}
+\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T\Big|^{\frac{1}{2}}}
+\exp \Big\{-\frac{1}{2} (\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h})^T (\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T)^{-1}(\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}) \Big\}
+\end{flalign}
 

### 2018-01-06 Probabilistic forecasts in hierarchical time series.tex
Add files via upload

@@
 This implies that any coherent density is a degenerate density.
-We can think of the $m$ bottom level series of a given hierarchy as a basis set of series.
-Then the columns of $\bm{S}$ is a basis that generates through the bottom level series.
+The $m$ number of bottom level series of a given hierarchy can be considered as a basis set of series.
+Then the columns of $\bm{S}$ is a basis that generates through these bottom level series.
 This basis spans the linear subspace where the degenerate density lives on.\\
@@
 where $\bm{g}(\hat{\bm{y}}_{t+h})$ is the image of $\hat{\bm{y}}_{t+h}$ under $\bm{g}$ on $\bm{\mathbb{R}}^m$.
-The reconciled forecasts for the whole hierarchy is then given by $\tilde{\bm{y}}_{t+h}=\bm{S}(\tilde{\bm{b}}_{t+h})$ such that $\tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})$, where $\bm{S}(\tilde{\bm{b}}_{t+h})$ is the image of $\tilde{\bm{y}}_{t+h}$ under $\bm{S}$ on the $\mathscr{C}(\bm{S}) < \bm{\mathbb{R}}^n$.\\
+The reconciled forecasts for the whole hierarchy is then given by $\tilde{\bm{y}}_{t+h}=\bm{S}(\tilde{\bm{b}}_{t+h})$ such that $\tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})$, where $\bm{S}(\tilde{\bm{b}}_{t+h})$ is the image of $\tilde{\bm{b}}_{t+h}$ under $\bm{S}$ on the $\mathscr{C}(\bm{S}) < \bm{\mathbb{R}}^n$.\\
 
@@
 \begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
-(\bm{R}_\bot \bm{S})^{-1}\bm{R}_\bot\\ \cdots \\ (\bm{S}_\bot \bm{R})^{-1}\bm{S}_\bot
+(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot\\ \cdots \\ (\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot
 \end{pmatrix}.
@@
 \noindent
-This step directly followed by the definition for coherent forecasts.
+This step directly follows by the definition for coherent forecasts.
 That is, to obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \bm{\mathbb{R}}^n$ to the $\mathscr{C}(\bm{S})$ through $\bm{S}$.
@@
 \begin{flalign}
-\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})<\bm{\mathbb{R}}^n
+\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})<\bm{\mathbb{R}}^n.
 \end{flalign}
@@
 \noindent
-Finding a suitable $\bm{R}_\bot$ with respect to a certain loss function will results optimally reconciled point forecasts of the hierarchy.
+Finding a suitable $\bm{R}_\bot$ with respect to a certain loss function will result optimally reconciled point forecasts of the hierarchy.
 Notice that, if the mapping $\bm{g}$ in definition 4.1 is considered to be linear we have,
@@
 \noindent
-In previous studies on hierarchical point forecasting, $\bm{g}$ is also considered as a $m \times n$ matrix $\bm{P}$ and thus $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$. 
+In previous studies on hierarchical point forecasting, $\bm{g}$ is considered as a $m \times n$ matrix $\bm{P}$ and thus $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$. 
 In other words, $\bm{g}$ linearly projects incoherent point forecasts onto the $\mathscr{C}(\bm{S})$.
@@
 \noindent
-Recall that $\hat{\bm{y}}_{t+h}$ is a set of incoherent point forecasts and the coordinates of that with respect to the basis $\bm{B}$ is given by (\ref{4.1}).
-Suppose $\hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ is the probability density of $\hat{\bm{y}}_{t+h}$.
-Our goal is to reconcile $\hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ such that the density lives on the $\mathscr{C}(\bm{S})$.
+Recall that $\hat{\bm{y}}_{t+h}$ is a set of incoherent point forecasts and the coordinates of that with respect to the basis $\bm{B}$ is given by (\ref{4.3}).
+Suppose $\hat{\bm{f}}(.)$ is the probability density of $\hat{\bm{y}}_{t+h}$.
+Our goal is to reconcile $\hat{\bm{f}}(.)$ such that the density lives on the $\mathscr{C}(\bm{S})$.
 In order to obtain this reconciled density, we need to project $\hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ onto the $\mathscr{C}(\bm{S})$ along the direction of $\mathscr{C}(\bm{R})$.
@@
 \noindent
-Let the density of coordinates of $\hat{\bm{y}}_{t+h}$ with respect to basis $\bm{B}$ is denoted by $\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})$.
-Then it follows from  (\ref{4.3}) and the facts on density of transformed variables,
+Let the density of coordinates of $\hat{\bm{y}}_{t+h}$ with respect to basis $\bm{B}$ is denoted by $\bm{f_B}(.)$. Then it follows from  (\ref{4.3}) and the facts on density of transformed variables,
 
 \begin{flalign}\label{4.5}
-\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad det(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array}),
+\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad \Big|\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array}\Big|,
 \end{flalign}
 \noindent
-where $det(.)$ denote the determinant of a matrix.
+where $|.|$ denote the determinant of a matrix.
 Now that we have the density of $\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T $, the marginal density of $(\tilde{\bm{b}}_{t+h})$ can be obtained by integrating (\ref{4.5}) over the range of $\tilde{\bm{t}}_{t+h}$.
@@
 \begin{flalign}\label{4.6}
-\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\int_{lim(\tilde{\bm{t}}_{t+h})}\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad det(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})\quad d\tilde{\bm{t}}_{t+h}.
+\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\int_{lim(\tilde{\bm{t}}_{t+h})}\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad \Big|\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array}\Big| \quad d\tilde{\bm{t}}_{t+h}.
 \end{flalign}
@@
 Finally to get the reconciled density of the whole hierarchy, we simply follow the definition $(3.2)$ and have, 
-\begin{flalign}
+\begin{flalign}\label{4.7}
 \tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\bm{S}\circ \tilde{\bm{f}}(\tilde{\bm{b}}_{t+h}).
@@
 \noindent
-By substituting the Gaussian distribution function to $\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})$ we get,
+By substituting the Gaussian distribution function to $\bm{f_B}(.)$ we get,
 
@@
 Recall that, $\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
-(\bm{R}_\bot \bm{S})^{-1}\bm{R}_\bot\\ \cdots \\ (\bm{S}_\bot \bm{R})^{-1}\bm{S}_\bot
+(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot\\ \cdots \\ (\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot
 \end{pmatrix} = \begin{pmatrix}
@@
 
-\begin{flalign}
+\begin{flalign}\label{ex:2.1}
 \tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T\Big|^{\frac{1}{2}}}
@@
 \end{flalign}
+
+\noindent
+(\ref{ex:2.1} ) implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\hat{\bm{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T)$ where $\bm{P} = (\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$.
+Then from (\ref{4.7}) it follows that
+
+\begin{flalign}
+\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
+\end{flalign}
+\noindent
+That is the reconciled Gaussian forecast distribution of the whole hierarchy is $\mathscr{N}(\bm{SP}\hat{\bm{\mu}}_{t+h}, \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T\bm{S}^T)$.
 

### 2018-01-09 Probabilistic forecasts in hierarchical time series.tex
Add files via upload

@@
 \noindent
-This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the $\mathscr{C}(\bm{S})<\bm{\mathbb{R}}^n$\\
+This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the $\mathscr{C}(\bm{S})<\bm{\mathbb{R}}^n$.
+Following example illustrates how this method can be used to reconcile an incoherent Gaussian forecast distribution.\\
 
@@
 \noindent
-Recall that, $\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
+Recall that, $$\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
 (\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot\\ \cdots \\ (\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot
@@
 \bm{P}\\\bm{Q}
-\end{pmatrix},$(say). Then,
+\end{pmatrix},$$ where, $\bm{P}=(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$ and $\bm{Q}=(\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot$. Then,
 
@@
 Then from (\ref{4.6}) and the properties of marginalization of multivariate Gaussian distribution it follows,
-
 \begin{flalign}\label{ex:2.1}
 \tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T\Big|^{\frac{1}{2}}}
-\exp \Big\{-\frac{1}{2} (\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h})^T (\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T)^{-1}(\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}) \Big\}
+\exp \Big\{-\frac{1}{2} (\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h})^T (\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T)^{-1}(\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}) \Big\}.
 \end{flalign}
@@
 \noindent
-(\ref{ex:2.1} ) implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\hat{\bm{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T)$ where $\bm{P} = (\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$.
-Then from (\ref{4.7}) it follows that
-
+(\ref{ex:2.1}) implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\hat{\bm{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T)$ where $\bm{P} = (\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$.
+Then from (\ref{4.7}) it follows that,
 \begin{flalign}
@@
 \noindent
-That is the reconciled Gaussian forecast distribution of the whole hierarchy is $\mathscr{N}(\bm{SP}\hat{\bm{\mu}}_{t+h}, \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T\bm{S}^T)$.
+Therefore, the reconciled Gaussian forecast distribution of the whole hierarchy is $\mathscr{N}(\bm{SP}\hat{\bm{\mu}}_{t+h}, \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T\bm{S}^T)$.
 
@@
 In other words, random draws from a perfectly calibrated predictive distribution should be equivalent to the realizations.
-The uniformity in Probability Integral Transformation (PIT) of predictive densities evaluated at realizations implies well calibrated probabilistic forecasts.
-Therefore, assessing the uniformity in PIT of predictive densities, by inspecting their histograms and correlograms can be used as a simple tool for evaluating the calibration of probabilistic forecasts.
-\\
-
-\noindent
 On the other hand, sharpness refers to the spread or the concentration of prediction distributions and it is a property of forecasts only.
 The more concentrated the predictive distributions, the sharper the forecasts are \citep{Gneiting2008}.
-The sharpness of density forecasts can be assessed in terms of the prediction intervals.
-Sharper density forecasts will have shorter prediction intervals.
 However, independently assessing the calibration and sharpness will not help to properly evaluate the probabilistic forecasts.
@@
 \noindent
-Let $\bm{Y}$ be a $n$-dimensional random vector from the predictive distribution $\mathbold{F}$ and $\mathbold{y}$ be $n$-dimension vector of realizations.
-Scoring rule is a numerical value $S(\mathbold{Y,y})$ assign to each pair $(\mathbold{Y,y})$.
-Suppose the true distribution of $\mathbold{y}$ is given by $\mathbold{G}$.
-Then the proper scoring rule is defined as,
+Let $\bm{{\breve{Y}}}$ and $\bm{Y}$ be a $n$-dimensional random vectors from the predictive distribution $\mathbold{F}$ and the true distribution $\mathbold{G}$.
+Further let $\mathbold{y}$ be a $n$-dimensional realization.
+Then the scoring rule is a numerical value $S(\mathbold{{\breve{Y}},y})$ assign to each pair $(\mathbold{{\breve{Y}},y})$ and the proper scoring rule is defined as,
 \begin{equation}\label{eq:(3.1.)}
-S(\mathbold{G,G}) \le S(\mathbold{Y,G}),
+E_{\mathbold{G}}[S(\mathbold{Y,y})] \le E_{\mathbold{G}}[S(\mathbold{{\breve{Y}},y})],
 \end{equation}
 \noindent
-where $S(\mathbold{Y,G})=E_{\mathbold{G}}[S(\mathbold{Y,y})]$ is the expected score under the true distribution $\mathbold{G}$ \citep{Gneiting2008, Gneiting2014}. \\
+where $E_{\mathbold{G}}[S(\mathbold{Y,y})]$ is the expected score under the true distribution $\mathbold{G}$ \citep{Gneiting2008, Gneiting2014}. \\
 
 \noindent
-Let $\bm{\tilde{Y}}_{T+h}$ and $\bm{\tilde{Y}}'_{T+h}$ be two independent random vectors from the coherent forecast distribution $\tilde{\bm{F}}$ with the density function $\tilde{\bm{f}}(.)$ at time $t+h$ and $\bm{y}_{T+h}$ is the vector of realizations.
-Further $\tilde{Y}_{T+h,i}$ and $\tilde{Y}_{T+h,j}$ are $i^{\text{th}}$ and $j^{\text{th}}$ components of the vector $\tilde{\bm{Y}}_{T+h}$.
-Then the following table summarizes few existing proper scoring rules.
+Following table summarizes few existing proper scoring rules.
 
@@
 
+	\small
 	\resizebox{\linewidth}{!}{
@@
 			\hline \\
-			\text{Log score} & LS(\tilde{\bm{F}},\bm{y}_{T+h}) = -log {\tilde{\bm{f}}(\bm{y}_{T+h})} & \text{\citet{Gneiting2007}} \\
+			\text{Log score} & LS(\breve{\bm{F}},\bm{y}_{T+h}) = -log {\breve{\bm{f}}(\bm{y}_{T+h})} & \text{\citet{Gneiting2007}} \\
 			\\ 
 			\hline \\
-			\text{Energy score} & eS(\bm{\tilde{Y}_{T+h},y_{T+h}}) = E_{\tilde{\bm{F}}}||\tilde{\bm{Y}}_{T+h}-\bm{y}_{T+h}||^\alpha - \frac{1}{2}E_{\tilde{\bm{F}}}||\tilde{\bm{Y}}_{T+h}-\tilde{\bm{Y}}'_{T+h}||^\alpha, \alpha \in (0,2] & \text{\citet{Gneiting2008}} \\
+			\text{Energy score} & eS(\bm{\breve{Y}_{T+h},y_{T+h}}) = E_{\breve{\bm{F}}}||\breve{\bm{Y}}_{T+h}-\bm{y}_{T+h}||^\alpha - \frac{1}{2}E_{\breve{\bm{F}}}||\breve{\bm{Y}}_{T+h}-\breve{\bm{Y}}'_{T+h}||^\alpha, \alpha \in (0,2] & \text{\citet{Gneiting2008}} \\
 			\\
 			\hline
-			\text{Variogram score} & VS(\tilde{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - E_{\tilde{\bm{F}}}|\tilde{Y}_{T+h,i}-\tilde{Y}_{T+h,j}|^p\right)^2 & \text{\citet{SCHEUERER2015}} \\
+			\text{Variogram score} & VS(\breve{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - E_{\breve{\bm{F}}}|\breve{Y}_{T+h,i}-\breve{Y}_{T+h,j}|^p\right)^2 & \text{\citet{SCHEUERER2015}} \\
 			\hline
@@
 \end{center}
+\textit{NOTE: $\bm{\breve{Y}}_{T+h}$ and $\bm{\breve{Y}}'_{T+h}$ be two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with the density function $\breve{\bm{f}}(.)$ at time $t+h$ and $\bm{y}_{T+h}$ is the vector of realizations.
+Further $\breve{Y}_{T+h,i}$ and $\breve{Y}_{T+h,j}$ are $i^{\text{th}}$ and $j^{\text{th}}$ components of the vector $\breve{\bm{Y}}_{T+h}$.
+Further the variogram score given is for order $p$ where, $w_{ij}$ are non-negative weights.}\\
 
 \noindent
-Log scores can be used to evaluate the hierarchical probabilistic forecasts if it is reasonable to assume a parametric forecast density for the hierarchy.
-However the \qq{degenerecy} of the coherent forecast densities would be problematic when using log scores.
+Even though the log score can be used evaluate simulated forecast densities with large samples \citep{Jordan2017}, it is more convenient to use if it is reasonable to assume a parametric forecast density for the hierarchy.
+However, the \qq{degenerecy} of coherent forecast densities would be problematic when using log scores.
 We will discuss more about this in the next sub section.\\
@@
 \begin{equation} \label{eq:(5.1)}
-eS(\bm{\tilde{Y}_{T+h},y_{T+h}}) = ||\bm{y}_{T+h}-\tilde{\bm{\mu}}_{T+h}||^2,
+eS(\bm{\breve{Y}_{T+h},y_{T+h}}) = ||\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}||^2,
 \end{equation}
@@
 \noindent
-where $\tilde{\bm{\mu}}_{T+h} =E_{\bm{F}}(\tilde{\bm{Y}}_{T+h}) $.
+where $\breve{\bm{\mu}}_{T+h} =E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $.
 Therefore in the limiting case, the energy score only measures the accuracy of the forecast mean, but not the entire distribution.
@@
 \noindent
-The variogram score given in Table $1$ is for order $p$ where, $w_{ij}$ are non-negative weights.
-\citet{SCHEUERER2015} have shown that the variogram score has a high discrimination ability of misspecified means, variance and correlation structure than the Energy score.
+However, \citet{SCHEUERER2015} have shown that the variogram score has a high discrimination ability of misspecified means, variance and correlation structure than the Energy score.
 Further they suggested the variogram score with $p=0.5$ is more powerful.\\
-
 \noindent
-For a possible finite sample of size $B$ from the multivariate forecast density $\tilde{\bm{F}}$, the variogram score is defined as,
+For a possible finite sample of size $B$ from the multivariate forecast density $\breve{\bm{F}}$, the variogram score is defined as,
 
 \begin{flalign}
-VS(\tilde{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - \frac{1}{m} \displaystyle\sum_{k=1}^{B} |\tilde{Y}^k_{T+h,i}-\tilde{Y}^k_{T+h,j}|^p\right)^2.
+VS(\breve{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - \frac{1}{m} \displaystyle\sum_{k=1}^{B} |\breve{Y}^k_{T+h,i}-\breve{Y}^k_{T+h,j}|^p\right)^2.
 \end{flalign}
@@
 As it was mentioned in the previous section, any coherent hierarchical forecast density is a degenerate density.
-To the best of our knowledge, there is no proper multivariate scoring rule that has been introduced in literature to evaluate densities with degeneracy.
+To the best of our knowledge, there is no proper multivariate scoring rule in literature to evaluate degenerate densities.
 Further it can be easily seen that some of the existing scoring rules breakdown under the degeneracy.
@@
 The expected log score of $p_1$ is:
-$$S(f,f) = S(p_1,f) -ln[p_1(x=0)]=0,$$
+$$E_f[S(f,f)] = E_f[S(p_1,f)] = -ln[p_1(x=0)]=0,$$
 \noindent
 and that of $p_2$ is:
-$$S(p_2,f) = -ln[p_2(x=0)]<0.$$ 
+$$E_f[S(p_2,f)] = -ln[p_2(x=0)]<0.$$ 
 \noindent
@@
 \noindent
-However you could compare individual margins of the forecast density of the hierarchy using univariate proper scoring rules.
+However we could compare individual margins of the forecast density of the hierarchy using univariate proper scoring rules.
 Most widely used Continuous Ranked Probability Score (CRPS) for evaluating univariate forecast densities would be helpful for this.
@@
 \begin{equation} \label{eq:(3.6)}
-CRPS(\tilde{F}_i,y_{T+h,i}) = E_{\tilde{F}_i}|\tilde{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}E_{\tilde{F}_i}|\tilde{Y}_{T+h,i}-\tilde{Y}'_{T+h,i}|,
+CRPS(\breve{F}_i,y_{T+h,i}) = E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}'_{T+h,i}|,
 \end{equation}
@@
 \noindent
-where $\tilde{Y}_{T+h,i}$ and $\tilde{Y}'_{T+h,i}$ are two independent copies from the $i^{\text{th}}$ reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy and $y_{T+h,i}$ is the $i^{\text{th}}$ realization from the true marginal distribution $G_i$.
+where $\breve{Y}_{T+h,i}$ and $\breve{Y}'_{T+h,i}$ are two independent copies from the $i^{\text{th}}$ reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy and $y_{T+h,i}$ is the $i^{\text{th}}$ realization from the true marginal distribution $G_i$.
 

### 2018-01-18 Probabilistic forecasts in hierarchical time series.tex
Add files via upload

@@
 	\begin{center}
-		\leaf{AA} \leaf{AB} \leaf{AC}
-		\branch{3}{A}
+		\leaf{AA} \leaf{AB} 
+		\branch{2}{A}
 		\leaf{BA} \leaf{BB}
@@
 At a particular time $t$, let $y_{T,t}$ denote the observation at level 0; $y_{A,t}, y_{B,t} $ denote observations at level 1; and $y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}$ denote observations at level 2.
-Then $\mathbold{y}_t = [y_{T,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}]^T$, \\$\mathbold{b}_t = [y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}]^T$, $m=7$, n=11$, $ and $$ \mathbold{S} = \begin{pmatrix} 1& 1 &1 &1 &1 \\ 1 &1 &1 & 0 &0 \\   0&0 &0 & 1 & 1 \\ & & I_5 &  & \end{pmatrix}, $$ where $I_5$ is a $5$-dimension identity matrix.
+Then $\mathbold{y}_t = [y_{T,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}]^T$, \\$\mathbold{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]^T$, $m=4$, $n=7$, and $$ \mathbold{S} = \begin{pmatrix} 1& 1 &1 &1  \\ 1 &1 & 0 &0 \\   0&0  & 1 & 1 \\ & & I_4 &   \end{pmatrix}, $$ where $I_4$ is a $4$-dimension identity matrix.
 \\
@@
 
-\subsection{Simulation study}
+\section{Simulation study}
+Main purpose of this simulation study to establish the importance of reconciliation in probabilistic hierarchical forecasting.
+We narrow down the simulation setting for the Gaussian framework in this context.
+Suppose all the historical data in the hierarchy follows a multivariate Gaussian distribution, i.e.
+$\bm{y}_T \sim \mathscr{N}(\bm{\mu}_T, \bm{\Sigma}_T)$ where both $\bm{\mu}_T$ and $\bm{\Sigma}_T$ lives in $\mathscr{C}(\bm{S})$ by the nature of the hierarchical time series.
+We are interested in estimating the predictive Gaussian distribution of $\bm{Y}_{T+h}| \bm{\mathcal{I}}_T$ where $\bm{\mathcal{I}}_T= \{\bm{y}_1,\bm{y}_2,....,\bm{y}_T\}$, which should also lives in $\mathscr{C}(\bm{S})$.
+\\
+
+\noindent
+Suppose we independently fit the models for each series in the hierarchy and obtained the point and variance forecasts denoted by $\hat{\bm{\mu}}_{T+h}$ and $\hat{\bm{\Sigma}}_{T+h}$ respectively.
+Note that the variance forecast can be obtained through the in-sample errors.
+General convention on Gaussian density estimation is to take the point and variance forecasts as the estimates of mean and variance of the respective predictive distribution \citep{Hall2007}.
+Thus the incoherent predictive distribution is given by  $\hat{\bm{Y}}_{T+h}| \bm{\mathcal{I}}_T \sim \mathscr{N}(\hat{\bm{y}}_{T+h}, \hat{\bm{\Sigma}}_{T+h})$.
+We call this distribution is incoherent since it is very unlikely the point and variance forecasts from the independently fitted models to be coherent.
+Then it directly follows from example 2 that the reconciled Gaussian predictive distribution is given by, $\tilde{\bm{Y}}_{T+h}| \bm{\mathcal{I}}_T \sim \mathscr{N}(\bm{SP}\hat{\bm{y}}_{T+h}, \bm{SP}\hat{\bm{\Sigma}}_{T+h}\bm{P}^T\bm{S}^T)$ where $\bm{P} = (\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$.\\
+
+\noindent
+\textbf{Result 1}: Choosing $\bm{R}^T_\bot = \bm{S}^T\hat{\bm{\Sigma}}_{T+h}^{-1}$ will ensure at least the mean of the predictive Gaussian distribution is optimally reconciled with respect to the energy score.\\
+
+\noindent
+Result 1 can be easily shown as follows.
+From (\ref{eq:(5.1)}) the energy score at the upper limit of $\alpha$ is given by, $||\bm{y}_{T+h}-\bm{SP}\hat{\bm{y}}_{T+h}||^2$.
+Then the expectation of energy score with respect to the true distribution is equivalent to the trace of mean squared forecast error, i.e.
+$$E_{\bm{G}}[eS(\bm{\tilde{Y}_{T+h},y_{T+h}})]= Tr\{E_{\bm{y}_{T+h}}[(\bm{y}_{T+h}-\bm{SP}\hat{\bm{y}}_{T+h})(\bm{y}_{T+h}-\bm{SP}\hat{\bm{y}}_{T+h})^T|\mathcal{I}_{T}]\}.$$
+\noindent
+From Theorem 1 of \citet{Wickramasuriya2017} it immediately follows that $\bm{P} = (\bm{S}^T\bm\hat{\bm{\Sigma}}_{T+h}^{-1}\bm{S})^{-1}\bm{S}^T\bm\hat{\bm{\Sigma}}_{T+h}^{-1}$ minimizes the expected energy score constrained on the unbiasedness of reconciled forecasts.
+Thus we have $\bm{R}^T_\bot = \bm{S}^T\hat{\bm{\Sigma}}_{T+h}^{-1}$.
+\\
+
+\noindent
+It should be noted that $\hat{\bm{\Sigma}}_{T+h}$ can be estimated in different methods which yields different estimation of $\bm{R}^T_\bot$. Following table summarizes these methods.
+
+\begin{center}
+	\captionof{table}{\textit{Summarizing different estimates of $\bm{R}^T_\bot$} }
+
+	\resizebox{\linewidth}{!}{
+		\small
+		\small
+		\begin{tabular}{c c c }
+			\hline\hline\\
+			\textbf{Method}& \textbf{Estimate of $\hat{\bm{\Sigma}}_{T+h}$} & \textbf{Estimate of $\bm{R}^T_\bot$} \\  
+			\hline \hline\\
+			OLS & $\bm{I}$ & $\bm{S}^T$\\
+			\hline\\
+
+			MinT(Sample) & 	$\hat{\bm{\Sigma}}_{T+1}$ & $\bm{S}^T\hat{\bm{\Sigma}}_{T+1}^{-1}$\\
+			& (1-step ahead insample variance covariance matrix) &\\
+			\hline\\
+
+			MinT(Shrink) & $\hat{\mathbold{\Sigma}}_{T+1}^{shr} = \tau\text{Diag}(\hat{\mathbold{\Sigma}}_{T+1}) + (1-\tau)\hat{\mathbold{\Sigma}}_{T+1}$ & $\bm{S}^T(\hat{\bm{\Sigma}}_{T+1}^{shr})^{-1}$\\
+			\hline\\
+
+			MinT(WLS) & $\hat{\mathbold{\Sigma}}_{T+1}^{wls} = \text{Diag}(\hat{\mathbold{\Sigma}}_{T+1}^{shr})$ & 	$\bm{S}^T(\hat{\bm{\Sigma}}_{T+1}^{wls})^{-1}$\\
+			\hline
+			\hline
+
+		\end{tabular}
+	}
+\end{center}
+\textit{Note: $\hat{\mathbold{\Sigma}}_{T+1}^{shr}$ is a shrinkage estimator proposed by \citet{Schafer2005} and also used by \citet{Wickramasuriya2017}, where $\tau = \frac{\sum_{i \ne j}\hat{Var}(\hat{r}_{ij})}{\sum_{i \ne j}\hat{r}_{ij}^2}$, $\hat{r}_{ij}$ is the $ij$-th element of sample correlation matrix.
+Further Diag($\bm{A}$) denote the diagonal matrix of $\bm{A}$}.\\
+
+\noindent
+It is worth mentioning that all these forecasting methods were well established in the context of point forecast reconciliation \citep{Hyndman2011, Wickramasuriya2017, Hyndman2016}.
+However our attempt is to emphasis the use of these reconciliation methods in the context of probabilistic forecasts.
+\\
+
+\noindent
+\textbf{Simulation setup}\\
+
+\noindent
+We consider the hierarchy given in figure (1) for this simulation study.
+This hierarchy consists two aggregation levels with four bottom level series.
+Each bottom level series will be generated first and add them up to obtain the data for respective upper level series.
+Hierarchical time series in practice contain much noisier series in the bottom level than in aggregate series.
+In order to simulate this feature in the hierarchy, we refer to \citet{Wickramasuriya2017} and the data generating process will be given as follows.
+\\
+
+\noindent
+Suppose $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from $ARIMA(p,d,q)$ processes where, $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability and the contemporaneous errors $\{\epsilon_{AA,t},\epsilon_{AB,t},\epsilon_{BA,t},\epsilon_{BB,t}\} \sim \mathcal{N}(\bm{0}, \bm{\Sigma})$.
+Further, the parameters for $AR$ and $MA$ components will be randomly and uniformly generated from $[0.3,0.5]$ and $[0.3,0.7]$ respectively.
+Then the bottom level series $\{y_{AA,t},y_{AB,t},y_{BA,t},y_{BB,t}\}$ will be obtained as:
+$$y_{AA,t} = w_{AA,t} + u_t - 0.5v_t,$$
+$$y_{AB,t} = w_{AB,t} - u_t - 0.5v_t,$$
+$$y_{BA,t} = w_{BA,t} + u_t + 0.5v_t,$$
+$$y_{BB,t} = w_{BB,t} - u_t + 0.5v_t,$$ 
+\noindent
+where $u_t \sim N(0,\sigma^2_u)$ and $v_t \sim N(0,\sigma^2_v)$.
+
+\noindent
+To obtain the aggregate series at level 1, we add their respective bottom level series such as: 
+$$y_{A,t} = w_{AA,t} + w_{AB,t} - v_t,$$
+$$y_{B,t} = w_{BA,t} + w_{BB,t} + v_t,$$
+\noindent
+and the total series will be obtained as: 
+$$y_{Tot,t} = w_{AA,t} + w_{AB,t} + w_{BA,t} + w_{BB,t}.$$
+\noindent
+To get less noisier aggregate series than disaggregate series, we choose $\bm{\Sigma}, \sigma^2_u$ and $\sigma^2_v$ such that,
+
+$$Var(\epsilon_{AA,t}+\epsilon_{AB,t}+\epsilon_{BA,t}+\epsilon_{BB,t}) \le Var(\epsilon_{AA,t}+\epsilon_{AB,t}-v_t) \le Var(\epsilon_{AA,t}+u_t-0.5v_t),$$
+$$\bm{l}_1\bm{\Sigma} \bm{l}_1^T \le \bm{l}_2\bm{\Sigma} \bm{l}_2^T + \sigma^2_v \le  \bm{l}_3\bm{\Sigma} \bm{l}_3^T + \sigma^2_u + \frac{1}{4}\sigma^2_v,$$
+\noindent
+where $\bm{l}_1 = \begin{pmatrix} 1&1&1&1 \end{pmatrix}, \bm{l}_2 = \begin{pmatrix} 1&1&0&0 \end{pmatrix}$ and $\bm{l}_3 = \begin{pmatrix} 1&0&0&0 \end{pmatrix}$.
+\noindent 
+This follows, 
+$$\bm{l}_1\bm{\Sigma} \bm{l}_1^T - \bm{l}_2\bm{\Sigma} \bm{l}_2^T \le \sigma^2_v \le \frac{4}{3}(\sigma^2_u + \bm{l}_3\bm{\Sigma} \bm{l}_3^T - \bm{l}_2\bm{\Sigma} \bm{l}_2^T).$$
+\noindent
+Thus we choose, 
+$\mathbold{\Sigma} =  \begin{pmatrix} 5.0 & 3.1 & 0.6 & 0.4\\
+3.1 & 4.0 & 0.9 & 1.4\\
+0.6 & 0.9 & 2.0 & 1.8\\
+0.4 & 1.4 & 1.8 & 3.0\\
+\end{pmatrix}, \quad \sigma^2_u = 19$ and $\sigma^2_u = 18$ in our simulation setting. \\
+
+\noindent
+As such we generate data for the hierarchy with sample size $T=501$.
+Then univariate $ARIMA$ models were fitted for each series independently using the first 500 observations and obtain 1-step ahead base (incoherent) forecasts.
+We use \textit{forecast} package in \textbf{R}-software \citet{hyndman2017forecasting} for model fitting and forecasting.
+Further, different estimates of $\hat{\Sigma}_{T+1}$ and the corresponding $\bm{R}^T_\bot$ were obtained as summarized in Table 2.
+This process was then replicated using $1000$ different data sets from the same data generating process.
+\\
+
+\noindent
+To assess the predictive performance of different forecasting methods, we use scoring rules as discussed in section 5.
+In addition to that we use Skill score \citep{Gneiting2007} for any comparison.
+For a given forecasting method, evaluated by a particular scoring rule $S(.)$ , the skill score will be calculated as follows,
+\begin{flalign}
+Ss[S_B(.)] = \frac{S_B(\mathbold{{\breve{Y}},y}) - S_B(\mathbold{{{Y}},y})^{ref}}{S_B(\mathbold{{{Y}},y})^{ref}}\times 100\%,
+\end{flalign} 
+\noindent
+where $S_B(.)$ is average score over $B$ samples and $S_B(\mathbold{{{Y}},y})^{ref}$ is the average score of the reference forecasting methods.
+Thus $Ss[S_B(.)]$ gives the percentage improvement of the preferred forecasting method relative to the reference method.
+\\
+
+\noindent
+As it was mentioned before we wish to establish the importance of reconciliation methods from this simulation study.
+In particular we compare different reconciliation methods over the conventional bottom-up method and the importance of coherent forecasts over incoherent forecasts.
+For the former comparison we use bottom level probabilistic forecasts and calculated the energy score, log score, variogram score (presented in Table 3) and the skill score is calculated with reference to bottom up method (presented in Table 4).
+For the latter comparison we calculate the CRPS for each aggregate series (presented in Table 5) and the skill score is calculated with reference to the incoherent forecasts.\\
+
+\pagebreak
+\noindent
+\textbf{Comparison of reconciled forecasts using bottom level series}
+
+\begin{center}
+	\captionof{table}{\textit{Comparison of reconciled forecasts using bottom level series} }
+
+	\resizebox{\linewidth}{!}{
+		\small
+		\scriptsize
+		\begin{tabular}{@{}l S[table-format=2.2] S[table-format=2.2]  S[table-format=2.2] @{}}
+
+			\hline
+			\hline
+
+			\text{Forecasting method} &  \text{Energy score} & \text{Log score} & \text{Variogram score} \\ 
+			\hline
+			\hline
+
+			MinT(Shrink) & 7.58  & 11.34  &  2.96  \\
+
+			MinT(Sample) & 7.60  & 11.34  & 2.97   \\
+
+			MinT(WLS) & 7.93  & 12.62  & 3.16   \\
+
+			OLS & 7.81  & 11.53  & 3.06   \\
+
+			Bottom up &  8.29 & 12.10  & 3.05   \\
+
+			\hline
+			\hline
+
+		\end{tabular}
+	}
+\end{center}
+
+\small
+\begin{center}
+	\captionof{table}{\textit{Comparison of reconciliation methods against Bottom up method} }
+
+	\resizebox{\linewidth}{!}{
+		\scriptsize
+		\begin{tabular}{@{}l S[table-format=2.2] S[table-format=2.2]  S[table-format=2.2] @{}}
+
+			\hline
+			\hline
+
+			\text{Forecasting method} &  \text{Energy score} & \text{Log score} & \text{Variogram score} \\ 
+			\hline
+			\hline
+
+			MinT(Shrink) & 8.56  & 6.28  & 2.95  \\
+
+			MinT(Sample)  & 8.32  & 6.28  & 2.62  \\
+
+			MinT(WLS)  & 4.34  & -4.30  & -3.61  \\
+
+			OLS  & 5.79  & 4.71  & -0.33  \\
+
+			\hline
+			\hline
+
+		\end{tabular}
+	}
+\end{center}
+\textit{Note: Each entry represent the percentage skill score with respect to the bottom up forecasts}\\\\
+
+\noindent
+\textbf{Comparison of unreconciled vs. reconciled forecasts for the aggregate series}
+
+\begin{center}
+	\captionof{table}{\textit{Comparison of unreconciled vs. reconciled forecasts for the aggregate series}}
+
+	\small
+	\resizebox{\linewidth}{!}{
+		\scriptsize
+		\begin{tabular}{@{}l S[table-format=1.2] S[table-format=1.2]  S[table-format=1.2] S[table-format=1.2] S[table-format=1.2]  S[table-format=1.2] @{}}
+
+			\hline
+			\hline
+
+			\multirow{2}{*}{\text{Forecasting method}} & \multicolumn{2}{ c }{\text{Total}} & \multicolumn{2}{c}{\text{Series - A}} & \multicolumn{2}{c}{\text{Series - B}} \\ \cline{2-7} & \text{CRPS} &  \text{LogS} &   \text{CRPS} &   \text{LogS} &   \text{CRPS} &   \text{LogS} \\
+			\hline
+			\hline
+			Unreconciled & 5.57 & 3.99 & 12.68 & 4.87 & 10.35 & 4.66 \\
+
+			MinT(Shrink) & 5.44 & 3.97 & 10.04 & 4.64 & 8.92 & 4.52 \\
+
+			MinT(Sample) & 5.44 & 3.97 & 10.07 & 4.64 & 8.95 & 4.52 \\
+
+			MinT(WLS) & 4.26 & 3.70 & 5.45 & 3.94 & 5.06 & 3.86 \\
+
+			OLS & 6.50 & 4.18 & 10.91 & 4.72 & 9.29 & 4.56 \\
+
+			Bottom up  & 19.95 & 5.33 & 15.21 & 5.05 & 12.40 & 4.84 \\
+
+			\hline
+			\hline
+
+		\end{tabular}
+	}
+\end{center}
+
+\pagebreak
+\begin{center}
+	\captionof{table}{\textit{Comparison of unreconciled vs. reconciled forecasts for the aggregate series using Skill score}}
+
+	\resizebox{\linewidth}{!}{
+	\scriptsize	
+		\begin{tabular}{@{}l S[table-format=1.2] S[table-format=1.2]  S[table-format=1.2] S[table-format=1.2] S[table-format=1.2]  S[table-format=1.2] @{}}
+
+			\hline
+			\hline
+
+			\multirow{2}{*}{\text{Forecasting method}} & \multicolumn{2}{ c }{\text{Total}} & \multicolumn{2}{c}{\text{Series - A}} & \multicolumn{2}{c}{\text{Series - B}} \\ \cline{2-7} & \text{CRPS} &  \text{LogS} &   \text{CRPS} &   \text{LogS} &   \text{CRPS} &   \text{LogS} \\
+			\hline
+			\hline
+
+			MinT(Shrink) & 2.33 & 0.50 & 20.82 & 4.72 & 13.82 & 3.00 \\
+
+			MinT(Sample)  & 2.33 & 0.50 & 20.58 & 4.72 & 13.53 & 3.00 \\
+
+			MinT(WLS)  & 23.52 & 7.27 & 57.02 & 19.10 & 51.11 & 17.17 \\
+
+			OLS  & -16.70 & -4.76 & 13.96 & 3.08 & 10.24 & 2.15 \\
+
+			Bottom up   & -258.17 & -33.58 & -19.95 & -3.70 & -19.81 & -3.86 \\
+
+			\hline
+			\hline
+
+		\end{tabular}
+	}
+\end{center}
 

### 2018-02-01 Probabilistic forecasts in hierarchical time series.tex
Draft 1

--- 2018-01-09 Probabilistic forecasts in hierarchical time series.tex
@@
 \newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type
+\def\mathbi#1{\textit{ #1}}
+\def\mathB#1{\textbf{ #1}}
 
@@
 \section{Introduction.}
-\begin{itemize}
-	\item Introduction to hierarchical time series including a literature review in the context of point forecasts. 
-	\item Importance of probabilistic forecasts in time series.
-	\item Lack of attention in the context of probabilistic forecasts in hierarchical literature.
+Many research applications often involve a large collection of multiple time series some of which are aggregates of others.
+These collection of time series are called hierarchical time series.
+For example, electricity demand of a country can be disaggregated along a geographical hierarchy.
+One would be interested in forecasting electricity demand of the whole country along with the demand of states, cities and households.
+This is referred to as hierarchical forecasting.
+An important aspect of hierarchical forecasting is to have coherent forecasts across the hierarchy; that is, forecasts at lower levels should add up to their respective upper levels of aggregation.\\
 
-\end{itemize}
+\noindent
+There is a rich literature on producing coherent point forecasts in hierarchical time series.
+The traditional approaches involve bottom-up, top-down and middle-out methods.
+In the bottom-up approach, forecasts of the lowest level are first generated and they are simply aggregated to forecast upper levels of the hierarchy \citep{Dunn1976}.
+In contrast, the top-down approach involves forecasting the most aggregated series first and then disaggregating these forecasts down the hierarchy based on the proportions of observed data \citep{Gross1990}.
+Many studies in the literature have broadly discussed the relative advantages and disadvantages of bottom-up and top-down methods and situations in which they would provide reliable forecasts \citep{Schwarzkopf1988,Kahn1998, Lapide1998,Fliedner2001}.
+A compromise between these two approaches is the middle-out method which entails forecasting each series of a selected middle level in the hierarchy and then forecasting upper levels by the bottom-up method and lower levels by the top-down method.
+Apparently, these three approaches use only a part of the information available when producing coherent forecasts.
+This might result inaccurate forecasts.
+For example, if the bottom level series are highly volatile or too noisy and hence challenging to forecast, then the resulting forecasts from bottom-up approach would be inaccurate.\\
+
+\noindent
+As an alternative to these conventional methods, \citet{Hyndman2011} propose to use information from all the levels of the hierarchy and reconcile them to obtain coherent point forecasts.
+In this approach, independent forecasts of all series are initially obtained.
+It is very unlikely that these forecasts are coherent.
+Then, these forecasts are optimally combined through a regression model to obtain coherent forecasts.
+This study has given arise to the concept of point forecast reconciliation in hierarchical time series.
+In general, any forecasting method that use a set of incoherent forecasts and revise them to obtain coherent forecasts is referred to as forecast reconciliation method.
+Thus it is important to notice that bottom-up, top-down and middle-out methods are not reconciliation methods since they use only a part of information from the hierarchy to produce coherent forecasts.
+\\
+
+\noindent
+In a recent study on point forecast reconciliation, \citet{Wickramasuriya2017} propose to minimize the trace of mean squared coherent forecasts errors to optimally reconcile a set of unbiased, incoherent forecasts.
+Assuring the resulting reconciled forecasts are unbiased, they found an unique analytical solution to the proposed minimization problem.
+They referred this to as MinT approach.
+This solution was further improved to be computationally feasible for high dimensional hierarchies.
+\\
+
+\noindent
+In recent forecasting literature, its being the rationality to provide the associated uncertainty about the future, in addition to the point forecasts.
+This is referred to as probabilistic forecasts \citep{Gneiting2014}.
+For example, \citet{McSharry2005} produced probabilistic forecasts in application to electricity demand, \citet{BenTaieb2017} in application to smart meter data, \citet{Pinson2009} in application to wind power generation, \citet{Gel2004}, \citet{Gneiting2005a} and \citet{Gneiting2005} in application to prediction of weather quantities.
+\\
+
+\noindent      
+Although there is a thorough literature on producing coherent point forecasts of hierarchical time series, a very limited attention has been given in the context on probabilistic forecasts.
+Recently \citet{BenTaieb2017} proposed an algorithm to produce coherent probabilistic forecasts with the application to UK electricity smart meter data.
+This is the only study that copes with the probabilistic forecasts in hierarchical time series thus far.
+In their approach, a sample from the mean reconciled predictive distribution of the bottom level will be first generated.
+This sample will be then aggregated to obtain the coherent probabilistic forecasts of the respective upper levels of the hierarchy.
+Hence this method is a bottom-up based approach.
+They further use MinT approach for the mean reconciliation of the bottom level predictive distribution and a copula based approach to model the dependency structure of the hierarchy, when producing the sample of bottom level probabilistic forecasts.\\
+
+\noindent
+Our contribution in this paper is to provide a proper theoretical background for the probabilistic hierarchical forecasts.
+First we redefine the coherency of point forecasts and the reconciliation of a set of incoherent point forecasts by using the concepts on vector spaces and measure theory.
+This will leads us to provide a proper definition for probabilistic forecast reconciliation.
+Due to the aggregation structure in hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate.
+We discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation and also in the evaluation of their predictive performances.
+Further we provide theoretical results on probabilistic forecast reconciliation in the Gaussian framework.
+\\
+
+\noindent
+Rest of the paper is structured as follows.
+We start with introducing the notations in section 2.
+In section 3 we provide our definitions for coherency which is followed by the definitions for forecast reconciliation in section 4.
+Section 5 discuss about the methods that can be used for evaluation of probabilistic hierarchical forecasts.
+Section 6 consists the theoretical results followed by the simulation study on probabilistic forecast reconciliation in Gaussian framework and we enclose with the remarkable conclusions in section 7.
 
@@
 Further the null space of $\bm{S}$ which is orthogonal to this linear subspace is denoted by $\mathscr{N}(\bm{S})$.
-To understand the notations clearly, consider the hierarchy given in Figure 1.\\
-
-\begin{figure}
+To understand the notations clearly, consider the hierarchy given in Figure 1.
+\begin{figure}[H]
 	\begin{center}
-		\leaf{AA} \leaf{AB} \leaf{AC}
-		\branch{3}{A}
+		\leaf{AA} \leaf{AB} 
+		\branch{2}{A}
 		\leaf{BA} \leaf{BB}
@@
 This example consists of two levels.
-At a particular time $t$, let $y_{T,t}$ denote the observation at level 0; $y_{A,t}, y_{B,t} $ denote observations at level 1; and $y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}$ denote observations at level 2.
-Then $\mathbold{y}_t = [y_{T,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}]^T$, \\$\mathbold{b}_t = [y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}]^T$, $m=7$, n=11$, $ and $$ \mathbold{S} = \begin{pmatrix} 1& 1 &1 &1 &1 \\ 1 &1 &1 & 0 &0 \\   0&0 &0 & 1 & 1 \\ & & I_5 &  & \end{pmatrix}, $$ where $I_5$ is a $5$-dimension identity matrix.
+At a particular time $t$, let $y_{Tot,t}$ denote the observation at level 0; $y_{A,t}, y_{B,t} $ denote observations at level 1; and $y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}$ denote observations at level 2.
+Then $\mathbold{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}]^T$, \\$\mathbold{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]^T$, $m=4$, $n=7$, and $$ \mathbold{S} = \begin{pmatrix} 1& 1 &1 &1  \\ 1 &1 & 0 &0 \\   0&0  & 1 & 1 \\ & & I_4 &   \end{pmatrix}, $$ where $I_4$ is a $4$-dimension identity matrix.
 \\
@@
 	\end{center}
-	\caption{Any set $\bm{A} \in \bm{\mathbb{R}}$ will be mapped to the $\mathscr{C}(\bm{S})$ through the mapping $\bm{S}$}
+	\caption{Any set $\bm{A} \in \bm{\mathbb{R}}^m$ will be mapped to the $\mathscr{C}(\bm{S})$ through the mapping $\bm{S}$}
 \end{figure}
@@
 This implies that any coherent density is a degenerate density.
-The $m$ number of bottom level series of a given hierarchy can be considered as a basis set of series.
+In particular, the $m$ number of bottom level series of a given hierarchy can be considered as a basis set of series.
 Then the columns of $\bm{S}$ is a basis that generates through these bottom level series.
@@
 According to their definition, if the forecasts are coherent, then the convolution of forecast distributions of disaggregate series is same as the forecast distribution of the corresponding aggregate series.
-This is the only study that copes with probabilistic forecasts in hierarchical literature thus far.
 
 \section{Forecast reconciliation}
-\noindent
-Bottom-up, top-down and middle-out methods are the most traditional forecasting methods that were used to produce coherent point forecasts in early studies on hierarchical literature.
-In bottom-up approach, forecasts of the lowest level are first generated and they are simply aggregated to forecast the upper levels of the hierarchy \citep{Dunn1976}.
-In contrast, the top-down approach involves forecasting the most aggregated series first and then disaggregating these forecasts down the hierarchy based on the proportions of observed data \citep{Gross1990}.
-A compromise between these two approaches is the middle-out method which entails forecasting each series of a selected middle level in the hierarchy and then forecasting upper levels by the bottom-up method and lower levels by the top-down method.\\
 
-\noindent
-These three approaches use only a part of the information available when producing coherent forecasts.
-This might result inaccurate forecasts.
-For example, if the bottom level series are highly volatile or too noisy and hence challenging to forecast, then the resulting forecasts from bottom-up approach would be inaccurate.\\
-
-\noindent
-As an alternative to these conventional methods, \citet{Hyndman2011} propose to use information from all the levels of the hierarchy and reconcile them to obtain coherent point forecasts.
-In this approach, independent forecasts of all series are initially obtained.
-It is very unlikely that these forecasts are coherent.
-Then, these forecasts are optimally combined through a regression model to obtain coherent forecasts.
-This study has given arise to the concept of point forecast reconciliation in hierarchical time series.
-In general, any forecasting method that use a set of incoherent forecasts and revise them to obtain coherent forecasts is referred to as forecast reconciliation method.
-For example, Minimum Trace reconciliation \citep{Wickramasuriya2017}, GTOP \citep{VanErven2015a}.
-It is important to notice that bottom-up, top-down and middle-out methods are not reconciliation methods since they only use forecasts from a part of the levels in the hierarchy when producing coherent forecasts.
-\\
+Previous studies on point forecast literature has shown that the reconciliation provides better coherent forecasts than the conventional bottom-up and top-down methods (\cite{Hyndman2011}; \cite{VanErven2015a}; \cite{Wickramasuriya2017}).
+However this was not well established in the context of probabilistic forecasts.
+Nevertheless, there is no proper definition for the probabilistic forecast reconciliation in the published literature.
+Thus in this section we focus on defining the probabilistic forecast reconciliation and discuss how that definition can be used in practice.
 
@@
 
-Even though the point forecast reconciliation has a well established literature, we would like to redefine this using concepts in linear algebra as a groundwork for the probabilistic forecast reconciliation.
-\\
+Initially we redefine point forecast reconciliation using the concepts in linear algebra as a groundwork for the probabilistic forecast reconciliation. \\
 
@@
 This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}.
+\\
 
@@
 \noindent
-According to a recent study by \citet{Wickramasuriya2017}, choosing $\bm{R}^T_\bot = \bm{S}^T\hat{\bm{W}}^{-1}_{T+h}$ will minimize the trace of mean squared reconciled forecasts errors under the property of unbiasedness.
-$\hat{\bm{W}}^{-1}_{T+h}$ is the variance of the incoherent forecast errors.
+According to a recent study by \citet{Wickramasuriya2017}, choosing $\bm{R}^T_\bot = \bm{S}^T\bm{W}^{-1}_{h}$ will minimize the trace of mean squared reconciled forecasts errors under the property of unbiasedness where, $\bm{W}^{-1}_{h}$ is the variance of the incoherent forecast errors.
 This will result,
 \begin{flalign*}
-\tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}^T\hat{\bm{W}}^{-1}_{T+h} \bm{S})^{-1}\bm{S}^T\hat{\bm{W}}^{-1}_{T+h} \hat{\bm{y}}_{t+h},
+\tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}^T\bm{W}^{-1}_{h} \bm{S})^{-1}\bm{S}^T\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h},
 \end{flalign*}
@@
 \begin{flalign}
-\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}^T \hat{\bm{W}}^{-1}_{T+h}\bm{S})^{-1}\bm{S}^T\hat{\bm{W}}^{-1}_{T+h} \hat{\bm{y}}_{t+h}.
+\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}^T \bm{W}^{-1}_{h}\bm{S})^{-1}\bm{S}^T\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h}.
 \end{flalign}
@@
 i.e.
-$<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>_{\hat{\bm{W}}}$.
+$<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>_{\bm{W}_h}$.
 
@@
 \noindent  
-Suppose $\hat{\bm{Y}}_{t+h} \sim \mathscr{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h}) \leftrightarrow^d \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$. Then from (\ref{4.5}) it follows,
+Suppose $\mathscr{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h})\leftrightarrow^d \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ is an incoherent forecast distribution at time $t+h$.
+Then from (\ref{4.5}) it follows,
 
@@
 \bm{f_B}(.)&=\frac{\exp\left\{-\frac{1}{2}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})^T \bm{\hat{\Sigma}_{t+h}}^{-1}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
-&= \frac{\exp\left\{-\frac{1}{2}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\bm{\hat{\mu}}_{t+h}\Big)^T \bm{\hat{\Sigma}_{t+h}}^{-1}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
+&= \frac{\exp\left\{-\frac{1}{2}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)^T \bm{\hat{\Sigma}_{t+h}}^{-1}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
 \end{flalign*}
@@
 \bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|}
-\exp \Big\{&-\frac{1}{2}\Big(\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big)^T\\
+\exp \Big\{&-\frac{1}{2}\Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big)^T\\
 &\Big[\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^T\Big]^{-1}\\ 
-&\Big(\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.
+&\Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.
 \end{flalign*}
@@
 \exp \Big\{&-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix}^T\\ 
-&\Big[\begin{pmatrix}
+&\begin{pmatrix}
 \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T\\
 \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T
-\end{pmatrix}\Big]^{-1} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix} \Big\}.
+\end{pmatrix}^{-1}\\
+&\begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix} \Big\}.
 \end{flalign*}
@@
 \noindent
-(\ref{ex:2.1}) implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\hat{\bm{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T)$ where $\bm{P} = (\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$.
+(\ref{ex:2.1}) implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T)$ where $\bm{P} = (\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$.
 Then from (\ref{4.7}) it follows that,
@@
 \noindent
-Therefore, the reconciled Gaussian forecast distribution of the whole hierarchy is $\mathscr{N}(\bm{SP}\hat{\bm{\mu}}_{t+h}, \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T\bm{S}^T)$.
+Therefore, the reconciled Gaussian forecast distribution of the whole hierarchy is\\
+$\mathscr{N}(\bm{SP}\bm{\hat{\mu}}_{t+h}, \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T\bm{S}^T)$.
 
@@
 \end{center}
-\textit{NOTE: $\bm{\breve{Y}}_{T+h}$ and $\bm{\breve{Y}}'_{T+h}$ be two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with the density function $\breve{\bm{f}}(.)$ at time $t+h$ and $\bm{y}_{T+h}$ is the vector of realizations.
+\textit{NOTE: $\bm{\breve{Y}}_{T+h}$ and $\bm{\breve{Y}}'_{T+h}$ be two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with the density function $\breve{\bm{f}}(.)$ at time $T+h$ and $\bm{y}_{T+h}$ is the vector of realizations.
 Further $\breve{Y}_{T+h,i}$ and $\breve{Y}_{T+h,j}$ are $i^{\text{th}}$ and $j^{\text{th}}$ components of the vector $\breve{\bm{Y}}_{T+h}$.
@@
 \\
-
 \begin{equation} \label{eq:(3.6)}
@@
 where $\breve{Y}_{T+h,i}$ and $\breve{Y}'_{T+h,i}$ are two independent copies from the $i^{\text{th}}$ reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy and $y_{T+h,i}$ is the $i^{\text{th}}$ realization from the true marginal distribution $G_i$.
+We can also use univariate log scores for which we could assume a parametric forecast distribution.
 
-\subsection{Simulation study}
+\section{Probabilistic forecast reconciliation in the Gaussian framework}
+
+Main purpose of this section is to establish the importance of reconciliation in probabilistic hierarchical forecasting.
+We narrow down the simulation setting for the Gaussian framework in this work.
+That is, suppose all the historical data in the hierarchy follows a multivariate Gaussian distribution, i.e.
+$\bm{y}_T \sim \mathscr{N}(\bm{\mu}_T, \bm{\Sigma}_T)$ where both $\bm{\mu}_T$ and $\bm{\Sigma}_T$ lives in $\mathscr{C}(\bm{S})$ by nature of the hierarchical time series.
+We are interested in estimating the predictive Gaussian distribution of $\bm{Y}_{T+h}| \bm{\mathcal{I}}_T$ where $\bm{\mathcal{I}}_T= \{\bm{y}_1,\bm{y}_2,....,\bm{y}_T\}$, which should also lives in $\mathscr{C}(\bm{S})$.
+\\
+
+\noindent
+Suppose we independently fit the models for each series in the hierarchy.
+Let $\hat{Y}_{T+h,i}$ gives the point forecast of $i^{\text{th}}$ series at time $T+h$ conditional on the past observations $\{y_{1,i},...,y_{T,i}\}$ which minimizes the mean squared forecast error of $Y_{T+h,i}|\{y_{1,i},...,y_{T,i}\}$, where $i=1,...,n$.
+Then we have, $$\hat{Y}_{T+h,i} = E[Y_{T+h,i}|y_{1,i},...,y_{T,i}]$$
+
+\noindent
+Let $\hat{\bm{Y}}_{T+h}=(\hat{Y}_{T+h,1},...,\hat{Y}_{T+h,n})'$. Then, $$\hat{\bm{\mu}}_{T+h}=E[\bm{Y}_{T+h}|\bm{\mathcal{I}}_T] = \hat{\bm{Y}}_{T+h}.$$
+
+\noindent
+Further we have, 
+\begin{flalign*}
+Var(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) = & E[(\bm{Y}_{T+h} - E[\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T])(\bm{Y}_{T+h} - E[\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T])T]\\
+& = E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})T|\bm{\mathcal{I}}_T]\\
+& = \bm{W}_{T+h}
+\end{flalign*}
+
+\noindent
+Then the conditional forecast distribution at time $T+h$ will be multivariate Gaussian distribution with mean $\hat{\bm{Y}}_{T+h}$ and variance $\bm{W}_{T+h}$. 
+Since the point forecasts were obtained individually, it is very unlikely that the mean and variance lies in the coherent subspace.
+Therefore it gives the incoherent conditional forecast distribution which we denote as,
+\begin{flalign}\label{eq:(6.1)}
+\widehat{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathscr{N}(\hat{\bm{Y}}_{T+h}, \bm{W}_{T+h})
+\end{flalign}
+
+\noindent
+Since our primary objective is to find the coherent forecast density of the hierarchy, we need to reconciled \ref{eq:(6.1)}.
+Recalling from example 2, the reconciled Gaussian predictive distribution is then given by,
+\begin{flalign}\label{eq:(6.1)}
+\widetilde{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathscr{N}(\bm{SP}\hat{\bm{Y}}_{T+h}, \bm{SP}\bm{W}_{T+h}\bm{P}^T\bm{S}^T)
+\end{flalign}  
+\noindent
+where, $\bm{P} = (\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$.\\
+
+\noindent
+\textbf{Result 1}: Choosing $\bm{R}^T_\bot = \bm{S}^T\bm{W}_{T+h}^{-1}$ will ensure at least the mean of the predictive Gaussian distribution is optimally reconciled with respect to the energy score.\\
+
+\noindent
+Result 1 can be easily shown as follows.
+From (\ref{eq:(5.1)}) the energy score at the upper limit of $\alpha$ is given by, $||\bm{y}_{T+h}-\bm{SP}\hat{\bm{y}}_{T+h}||^2$.
+Then the expectation of energy score with respect to the true distribution is equivalent to the trace of mean squared forecast error, i.e.
+$$E_{\bm{G}}[eS(\bm{\tilde{Y}_{T+h},y_{T+h}})]= Tr\{E_{\bm{y}_{T+h}}[(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})^T|\mathcal{I}_{T}]\}.$$
+\noindent
+From Theorem 1 of \citet{Wickramasuriya2017} it immediately follows that $\bm{P} = (\bm{S}^T\bm{W}_{T+h}^{-1}\bm{S})^{-1}\bm{S}^T\bm{W}_{T+h}^{-1}$ minimizes the expected energy score constrained on the unbiasedness of reconciled forecasts.
+Thus we have $\bm{R}^T_\bot = \bm{S}^T\bm{W}_{T+h}^{-1}$.
+\\
+
+\noindent
+It should be noted that $\bm{W}_{T+h}$ can be estimated in different methods which yields different estimation of $\bm{R}^T_\bot$. Following table summarizes these methods.
+
+\begin{center}
+	\captionof{table}{\textit{Summarizing different estimates of $\bm{R}^T_\bot$} }
+
+	\resizebox{\linewidth}{!}{
+		\small
+		\small
+		\begin{tabular}{c c c }
+			\hline\hline\\
+			\textbf{Method}& \textbf{Estimate of $\bm{W}_{h}$} & \textbf{Estimate of $\bm{R}^T_\bot$} \\  
+			\hline \hline\\
+			OLS & $\bm{I}$ & $\bm{S}^T$\\
+			\hline\\
+
+			MinT(Sample) & 	$\bm{W}_{T+1}$ & $\bm{S}^T\bm{W}_{T+1}^{-1}$\\
+			& (1-step ahead insample variance covariance matrix) &\\
+			\hline\\
+
+			MinT(Shrink) & $\mathbold{W}_{T+1}^{shr} = \tau\text{Diag}(\mathbold{W}_{T+1}) + (1-\tau)\mathbold{W}_{T+1}$ & $\bm{S}^T(\bm{W}_{T+1}^{shr})^{-1}$\\
+			\hline\\
+
+			MinT(WLS) & $\mathbold{W}_{T+1}^{wls} = \text{Diag}(\mathbold{W}_{T+1}^{shr})$ & 	$\bm{S}^T(\bm{W}_{T+1}^{wls})^{-1}$\\
+			\hline
+			\hline
+
+		\end{tabular}
+	}
+\end{center}
+\textit{Note: $\mathbold{W}_{T+1}^{shr}$ is a shrinkage estimator proposed by \citet{Schafer2005} and also used by \citet{Wickramasuriya2017}, where $\tau = \frac{\sum_{i \ne j}\hat{Var}(\hat{r}_{ij})}{\sum_{i \ne j}\hat{r}_{ij}^2}$, $\hat{r}_{ij}$ is the $ij$-th element of sample correlation matrix.
+Further Diag($\bm{A}$) denote the diagonal matrix of $\bm{A}$}.\\
+
+\noindent
+It is worth mentioning that all these forecasting methods were well established in the context of point forecast reconciliation \citep{Hyndman2011, Wickramasuriya2017, Hyndman2016}.
+However our attempt is to emphasis the use of these reconciliation methods in the context of probabilistic forecasts at least in the Gaussian framework.
+\\
+
+\noindent
+\textbf{Simulation setup}\\
+
+\noindent
+We consider the hierarchy given in figure (1) for this simulation study.
+This hierarchy consists two aggregation levels with four bottom level series.
+Each bottom level series will be generated first and add them up to obtain the data for respective upper level series.
+Hierarchical time series in practice contain much noisier series in the bottom level than in aggregate series.
+In order to simulate this feature in the hierarchy, we refer to \citet{Wickramasuriya2017} and the data generating process will be given as follows.
+\\
+
+\noindent
+Suppose $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from $ARIMA(p,d,q)$ processes where, $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability.
+Further, the contemporaneous errors $\{\epsilon_{AA,t},\epsilon_{AB,t},\epsilon_{BA,t},\epsilon_{BB,t}\} \sim \mathcal{N}(\bm{0}, \bm{\Sigma})$.
+The parameters for $AR$ and $MA$ components will be randomly and uniformly generated from $[0.3,0.5]$ and $[0.3,0.7]$ respectively.
+Then the bottom level series $\{y_{AA,t},y_{AB,t},y_{BA,t},y_{BB,t}\}$ will be obtained as:
+$$y_{AA,t} = w_{AA,t} + u_t - 0.5v_t,$$
+$$y_{AB,t} = w_{AB,t} - u_t - 0.5v_t,$$
+$$y_{BA,t} = w_{BA,t} + u_t + 0.5v_t,$$
+$$y_{BB,t} = w_{BB,t} - u_t + 0.5v_t,$$ 
+\noindent
+where $u_t \sim N(0,\sigma^2_u)$ and $v_t \sim N(0,\sigma^2_v)$.
+
+\noindent
+To obtain the aggregate series at level 1, we add their respective bottom level series such as: 
+$$y_{A,t} = w_{AA,t} + w_{AB,t} - v_t,$$
+$$y_{B,t} = w_{BA,t} + w_{BB,t} + v_t,$$
+\noindent
+and the total series will be obtained as: 
+$$y_{Tot,t} = w_{AA,t} + w_{AB,t} + w_{BA,t} + w_{BB,t}.$$
+\noindent
+To get less noisier aggregate series than disaggregate series, we choose $\bm{\Sigma}, \sigma^2_u$ and $\sigma^2_v$ such that,
+
+$$Var(\epsilon_{AA,t}+\epsilon_{AB,t}+\epsilon_{BA,t}+\epsilon_{BB,t}) \le Var(\epsilon_{AA,t}+\epsilon_{AB,t}-v_t) \le Var(\epsilon_{AA,t}+u_t-0.5v_t),$$
+$$\bm{l}_1\bm{\Sigma} \bm{l}_1^T \le \bm{l}_2\bm{\Sigma} \bm{l}_2^T + \sigma^2_v \le  \bm{l}_3\bm{\Sigma} \bm{l}_3^T + \sigma^2_u + \frac{1}{4}\sigma^2_v,$$
+\noindent
+where $\bm{l}_1 = \begin{pmatrix} 1&1&1&1 \end{pmatrix}, \bm{l}_2 = \begin{pmatrix} 1&1&0&0 \end{pmatrix}$ and $\bm{l}_3 = \begin{pmatrix} 1&0&0&0 \end{pmatrix}$.
+\noindent 
+This follows, 
+$$\bm{l}_1\bm{\Sigma} \bm{l}_1^T - \bm{l}_2\bm{\Sigma} \bm{l}_2^T \le \sigma^2_v \le \frac{4}{3}(\sigma^2_u + \bm{l}_3\bm{\Sigma} \bm{l}_3^T - \bm{l}_2\bm{\Sigma} \bm{l}_2^T).$$
+\noindent
+Thus we choose, 
+$\mathbold{\Sigma} =  \begin{pmatrix} 5.0 & 3.1 & 0.6 & 0.4\\
+3.1 & 4.0 & 0.9 & 1.4\\
+0.6 & 0.9 & 2.0 & 1.8\\
+0.4 & 1.4 & 1.8 & 3.0\\
+\end{pmatrix}, \quad \sigma^2_u = 19$ and $\sigma^2_u = 18$ in our simulation setting. \\
+
+\noindent
+As such we generate data for the hierarchy with sample size $T=501$.
+Then univariate $ARIMA$ models were fitted for each series independently using the first 500 observations and obtain 1-step ahead base (incoherent) forecasts.
+We use \textit{forecast} package in \textbf{R}-software \citet{hyndman2017forecasting} for model fitting and forecasting.
+Further, different estimates of $\bm{W}_{T+1}$ and the corresponding $\bm{R}^T_\bot$ were obtained as summarized in Table 2.
+This process was then replicated using $1000$ different data sets from the same data generating process.
+\\
+
+\noindent
+To assess the predictive performance of different forecasting methods, we use scoring rules as discussed in section 5.
+In addition to that we use Skill score \citep{Gneiting2007} for any comparison.
+For a given forecasting method, evaluated by a particular scoring rule $S(.)$ , the skill score will be calculated as follows,
+\begin{flalign}
+Ss[S_B(.)] = \frac{S_B(\mathbold{{{Y}},y})^{ref} - S_B(\mathbold{{\breve{Y}},y})}{S_B(\mathbold{{{Y}},y})^{ref}}\times 100\%,
+\end{flalign} 
+\noindent
+where $S_B(.)$ is average score over $B$ samples and $S_B(\mathbold{{{Y}},y})^{ref}$ is the average score of the reference forecasting methods.
+Thus $Ss[S_B(.)]$ gives the percentage improvement of the preferred forecasting method relative to the reference method.
+Any negative value of $Ss[S_B(.)]$ indicate that the method we compared is poor than the reference method, whereas any positive value indicates that method is superior to the reference method.\\
+
+\noindent
+As it was mentioned before we wish to establish the importance of reconciliation methods from this simulation study.
+In particular we compare different reconciliation methods over the conventional bottom-up method and also evaluate the predictive ability of coherent forecasts over incoherent forecasts.
+For the former comparison we use bottom level probabilistic forecasts and calculate the percentage skill score based on energy score, log score and variogram score for each reconciliation method with reference to the bottom up method (presented in Table 3).
+For the latter comparison we use percentage skill score based on CRPS and univariate log score for coherent probabilistic forecasts of each individual series with reference to incoherent forecasts (presented in Table 5).\\
+
+\noindent
+It is clearly evident from the results in table 3 that the multivariate reconciled forecasts for the bottom level series from MinT(Shrink), MinT(Sample) and OLS methods outperform the bottom up forecasts.
+Further it turns out that probabilistic forecasts from MinT(Sample) has the best predictive ability.
+MinT(Shrink) also performing fairly well compared to the other methods.
+\\
+
+\noindent
+When it comes to the comparison of incoherent versus coherent probabilistic forecasts using the individual series in the hierarchy, MinT(WLS) seems to produce probabilistic forecasts with the best predictive ability.
+Nonetheless, MinT(Shrink), MinT(Sample) and OLS (OLS except for total level) produce coherent forecasts with improved predictive ability compared to incoherent forecasts.
+Further it can be noticed that bottom-up method produce worst forecasts.
+
+\pagebreak
+\begin{center}
+	\captionof{table}{\textit{Comparison of reconciliation methods against Bottom up method} }
+
+	\resizebox{\linewidth}{!}{
+		\small
+		\begin{tabular}{@{}l S[table-format=2.2] S[table-format=2.2]  S[table-format=2.2] @{}}
+
+			\hline
+			\hline
+
+			{Forecasting method} &  {Energy score} & {Log score} & {Variogram score} \\ 
+			\hline
+			\hline
+
+			MinT(Shrink) & 10.13 & 6.74 & 4.71  \\
+
+			MinT(Sample) & $\mathB{10.25}$ & $\bm{6.83}$ & $\bm{5.00}$ \\
+
+			MinT(WLS) & 5.06 & -4.85 & -2.06  \\
+
+			OLS & 6.36 & 4.52 & 0.59  \\
+
+			\hline
+
+			\textit{Bottom up} & $\mathbi{8.49}$ & $\mathbi{12.16}$ & $\mathbi{3.40}$    \\
+
+			\hline
+			\hline
+
+		\end{tabular}
+	}
+\end{center}
+\textit{Note: "Bottom up" row represent the average score for the bottom up method.
+Each entry above this row represent the percentage skill score with reference to the bottom up forecasting method.
+A positive(negative) entry shows the percentage increase(decrease) of score for different reconciliation methods with relative to the bottom up method}.\\\\
+
+\begin{center}
+	\captionof{table}{\textit{Comparison of incoherent vs. coherent forecasts for the aggregate series using Skill score}}
+
+	\resizebox{\linewidth}{!}{
+	\scriptsize	
+		\begin{tabular}{@{}l S[table-format=1.2] S[table-format=1.2]  S[table-format=1.2] S[table-format=1.2] S[table-format=1.2]  S[table-format=1.2] S[table-format=1.2] S[table-format=1.2]  S[table-format=1.2] S[table-format=1.2] S[table-format=1.2]  S[table-format=1.2] S[table-format=1.2] S[table-format=1.2] @{}}
+
+		\hline
+		\hline
+
+		\multirow{2}{*}{\text{Forecasting method}} & \multicolumn{2}{ c }{\text{Total}} & \multicolumn{2}{c}{\text{Series - A}} & \multicolumn{2}{c}{\text{Series - B}} & \multicolumn{2}{c}{\text{Series - AA}} & \multicolumn{2}{c}{\text{Series - AB}}& \multicolumn{2}{c}{\text{Series - BA}} & \multicolumn{2}{c}{\text{Series - BB}} \\ \cline{2-15} & \text{CRPS} &  \text{LogS} &   \text{CRPS} &   \text{LogS} &   \text{CRPS} &   \text{LogS} & \text{CRPS} &  \text{LogS}& \text{CRPS} &  \text{LogS}& \text{CRPS} &  \text{LogS}& \text{CRPS} &  \text{LogS} \\
+		\hline
+		\hline
+
+		MinT(Shrink)  & 1.99 & 0.50 & 19.82 & 4.33 &	14.18 &	3.21 & 16.09 & 3.40 & 18.88 & 4.08 & 11.59 & 2.88 &	14.68 &	3.04 \\
+
+		MinT(Sample) & 2.17 & 0.50 & 19.58 & 4.33 &	13.89 &	3.21 & 16.54 & 3.40 & 19.45 & 4.29 & 11.97 & 2.88 &	14.98 &	3.26 \\
+
+		MinT(WLS)  & $\bm{22.83}$ & $\bm{7.04}$ &	$\bm{56.35}$ &	$\bm{18.76}$ &	$\bm{51.44}$ &	$\bm{17.34}$ &	$\bm{37.84}$ &	$\bm{10.43}$ &	$\bm{36.13}$ &	$\bm{10.09}$ &	$\bm{30.17}$ & $\bm{9.73}$ & $\bm{37.35}$ & $\bm{10.65}$ \\
+
+		OLS  & -17.39 &	-4.77 &	13.27 &	2.89 & 10.63 & 2.36 & 9.41 & 1.70 &	10.1 & 1.93 & 7.44 & 1.33 &	9.21 & 1.74	\\
+
+		Bottom up & -259.78 & -33.67 & -20.22 &	-3.92 &	-19.92 & -3.85 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
+
+		\hline
+
+		\textit{Incoherent} & $\mathbi{5.52}$ & $\mathbi{3.98}$	& $\mathbi{12.51}$  & $\mathbi{4.85}$ & $\mathbi{10.44}$ & $\mathbi{4.67}$ & $\mathbi{10.94}$ &	$\mathbi{4.70}$ & $\mathbi{10.49}$ & $\mathbi{4.66}$ & $\mathbi{9.14}$ & $\mathbi{9.14}$ & $\mathbi{9.88}$ & $\mathbi{ 4.60}$ \\
+
+		\hline
+		\hline
+
+	\end{tabular}
+	}
+\end{center}
+\textit{Note: "Incoherent" row represent the average score for incoherent forecasts.
+Each entry above this row represent the percentage skill score with reference to the incoherent forecasts.
+A positive(negative) entry shows the percentage increase(decrease) of score for different forecasting methods with relative to incoherent forecasts}.\\\\
 
 \section{Conclusions.}
+
+Although the problem of hierarchical point forecasts is well studied in literature, there is a lack of attention in the context of probabilistic forecasts.
+Thus we attempted to fill this gap in literature by providing substantial theoretical background to the problem.
+We initially provided rigorous definitions for the coherent point and probabilistic forecasts using the principles of measure theory.
+Due to the aggregation nature of hierarchy, the probability density is a degenerate density.
+Thus the forecast distribution that we opt to find should also lies in a lower dimensional subspace of $\bm{\mathbb{R}}^{n}$.\\
+
+\noindent
+As it was well established that the reconciliation outperform other conventional point forecasting methods in hierarchical literature, we proposed to use reconciliation in probabilistic forecasting as well to obtain coherent degenerate densities.
+We provided distinct definition for density forecast reconciliation and how it can be used to reconcile incoherent densities in practice.\\
+
+\noindent
+Assuming a multivariate Gaussian distribution for the hierarchy, we showed how to obtain reconciled Gaussian forecast densities, utilizing available information in the hierarchy.
+The simulation study further showed that the MinT reconciliation method \citep{Wickramasuriya2017} is useful in producing improved coherent probabilistic forecasts at least in the Gaussian framework.
 

### 2018-02-17 Probabilistic forecasts in hierarchical time series.tex
Add files via upload

@@
 Many research applications often involve a large collection of multiple time series some of which are aggregates of others.
-These collection of time series are called hierarchical time series.
+These collections of time series are called hierarchical time series.
 For example, electricity demand of a country can be disaggregated along a geographical hierarchy.
-One would be interested in forecasting electricity demand of the whole country along with the demand of states, cities and households.
+One would be interested in forecasting electricity demand of the whole country along with the demand of states, cities, and households.
 This is referred to as hierarchical forecasting.
@@
 Apparently, these three approaches use only a part of the information available when producing coherent forecasts.
-This might result inaccurate forecasts.
+This might result in inaccurate forecasts.
 For example, if the bottom level series are highly volatile or too noisy and hence challenging to forecast, then the resulting forecasts from bottom-up approach would be inaccurate.\\
@@
 Then, these forecasts are optimally combined through a regression model to obtain coherent forecasts.
-This study has given arise to the concept of point forecast reconciliation in hierarchical time series.
-In general, any forecasting method that use a set of incoherent forecasts and revise them to obtain coherent forecasts is referred to as forecast reconciliation method.
-Thus it is important to notice that bottom-up, top-down and middle-out methods are not reconciliation methods since they use only a part of information from the hierarchy to produce coherent forecasts.
+This study has given a rise to the concept of point forecast reconciliation in hierarchical time series.
+In general, any forecasting method that uses a set of incoherent forecasts and revises them to obtain coherent forecasts is referred to as forecast reconciliation method.
+Thus it is important to notice that bottom-up, top-down and middle-out methods are not reconciliation methods since they use only a part of the information from the hierarchy to produce coherent forecasts.
 \\
@@
 In a recent study on point forecast reconciliation, \citet{Wickramasuriya2017} propose to minimize the trace of mean squared coherent forecasts errors to optimally reconcile a set of unbiased, incoherent forecasts.
-Assuring the resulting reconciled forecasts are unbiased, they found an unique analytical solution to the proposed minimization problem.
+Assuring the resulting reconciled forecasts are unbiased, they found a unique analytical solution to the proposed minimization problem.
 They referred this to as MinT approach.
@@
 \noindent
-In recent forecasting literature, its being the rationality to provide the associated uncertainty about the future, in addition to the point forecasts.
+In recent forecasting literature, it is being the rationality to provide the associated uncertainty about the future, in addition to the point forecasts.
 This is referred to as probabilistic forecasts \citep{Gneiting2014}.
@@
 \noindent      
-Although there is a thorough literature on producing coherent point forecasts of hierarchical time series, a very limited attention has been given in the context on probabilistic forecasts.
+Although there is a thorough literature on producing coherent point forecasts of hierarchical time series, a very limited attention has been given in the context of probabilistic forecasts.
 Recently \citet{BenTaieb2017} proposed an algorithm to produce coherent probabilistic forecasts with the application to UK electricity smart meter data.
@@
 Our contribution in this paper is to provide a proper theoretical background for the probabilistic hierarchical forecasts.
-First we redefine the coherency of point forecasts and the reconciliation of a set of incoherent point forecasts by using the concepts on vector spaces and measure theory.
+First, we redefine the coherency of point forecasts and the reconciliation of a set of incoherent point forecasts by using the concepts on vector spaces and measure theory.
 This will leads us to provide a proper definition for probabilistic forecast reconciliation.
-Due to the aggregation structure in hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate.
+Due to the aggregation structure in the hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate.
 We discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation and also in the evaluation of their predictive performances.
-Further we provide theoretical results on probabilistic forecast reconciliation in the Gaussian framework.
+Further, we provide theoretical results on probabilistic forecast reconciliation in the Gaussian framework.
 \\
@@
 In section 3 we provide our definitions for coherency which is followed by the definitions for forecast reconciliation in section 4.
-Section 5 discuss about the methods that can be used for evaluation of probabilistic hierarchical forecasts.
-Section 6 consists the theoretical results followed by the simulation study on probabilistic forecast reconciliation in Gaussian framework and we enclose with the remarkable conclusions in section 7.
+Section 5 discusses the methods that can be used for evaluation of probabilistic hierarchical forecasts.
+Section 6 consists the theoretical results followed by the simulation study on probabilistic forecast reconciliation in the Gaussian framework and we enclose with the remarkable conclusions in section 7.
 
 \section{Notations}
-We first introduce notations where possible we follow \citet{Wickramasuriya2017}.
+We first introduce notations where possible following \citet{Wickramasuriya2017}.
 Suppose $\mathbold{y}_t \in \bm{\mathbb{R}}^n$ comprising all observations of the whole hierarchy at time $t$ and $\mathbold{b}_t \in \bm{\mathbb{R}}^m$ comprising only the bottom level observations at  time $t$.
@@
 This example consists of two levels.
-At a particular time $t$, let $y_{Tot,t}$ denote the observation at level 0; $y_{A,t}, y_{B,t} $ denote observations at level 1; and $y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}$ denote observations at level 2.
-Then $\mathbold{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}]^T$, \\$\mathbold{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]^T$, $m=4$, $n=7$, and $$ \mathbold{S} = \begin{pmatrix} 1& 1 &1 &1  \\ 1 &1 & 0 &0 \\   0&0  & 1 & 1 \\ & & I_4 &   \end{pmatrix}, $$ where $I_4$ is a $4$-dimension identity matrix.
+At a particular time $t$, let $y_{Tot,t}$ denote the observation at level 0; $y_{A,t}, y_{B,t} $ denote observations at level 1; and $y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}$ denote observations at level 2.
+Then $\mathbold{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, \\$\mathbold{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and $$ \mathbold{S} = \begin{pmatrix} 1& 1 &1 &1  \\ 1 &1 & 0 &0 \\   0&0  & 1 & 1 \\ & & I_4 &   \end{pmatrix}, $$ where $I_4$ is a $4$-dimension identity matrix.
 \\
@@
 Let $(\bm{\mathbb{R}}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability measure space where $\mathscr{F}^m$ is a sigma algebra on $\bm{\mathbb{R}}^m$.
-$\breve{\nu}(.)$ on $(\mathscr{C}(\bm{S}), \mathscr{F}_{\bm{S}})$ is said to be coherent probability measure iff $$\breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall \quad \bm{A} \in \mathscr{F}^m,$$ where $\bm{S}(\bm{A})$ denotes the image of subset $\bm{A}$ under $\bm{S}$.
+$\breve{\nu}(.)$ on the measurable space $(\mathscr{C}(\bm{S}), \mathscr{F}_{\bm{S}})$ is said to be coherent probability measure iff $$\breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall \quad \bm{A} \in \mathscr{F}^m,$$ where $\bm{S}(\bm{A})$ denotes the image of subset $\bm{A}$ under $\bm{S}$.
 
@@
 Definition 3.2 implies the probability measure on $\mathscr{C}(\bm{S})$ is equivalent to the probability measure on $(\bm{\mathbb{R}}^m, \bm{\mathscr{F}}^m)$.
-Hence, there is no density anywhere outside the linear subspace spanned by the columns of $\bm{S}$.
-That is, a \textit{Coherent probability density forecast} is any density $\bm{f}(\bm{\breve{y}}_{t+h})$ such that $\bm{f}(\bm{\breve{y}}_{t+h})=0$ for all $\bm{\breve{y}}_{t+h}$ in the null space of $\bm{S}$.
+Hence, there is no density anywhere outside the linear subspace spanned by the columns of $\bm{S}$ in $\bm{\mathbb{R}}^n$.
+That is, a \textit{Coherent probability density forecast} is any density $\bm{f}(\bm{\breve{y}}_{t+h})$ such that $\bm{f}(\bm{\breve{y}}_{t+h})=0$ for all $\bm{\breve{y}}_{t+h} \in \mathscr{N}(\bm{S})$.
 Following example will help to understand these definitions more clearly.\\
@@
 \noindent
-\textbf{Example 1}\\
+\textbf{Example 1}:\\
+
 \noindent
-Consider a simple hierarchy with two bottom level series A and B that add up to the top level series T.
-Suppose the forecasts at time $t+h$ of these series are given by $\mathbold{\breve{y}}_{t+h} = [\breve{y}_{T,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$ and $\mathbold{\breve{y}}_{t+h} \in \bm{\mathbb{R}}^3$.
-Due to the aggregation constraint of the hierarchy we have $\breve{y}_{T,t+h}=\breve{y}_{A,t+h}+\breve{y}_{B,t+h}$.
+Consider a simple hierarchy with two bottom level series $A$ and $B$ that add up to the top level series $Tot$.
+Suppose the forecasts at time $t+h$ of these series are given by $\mathbold{\breve{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$ and $\mathbold{\breve{y}}_{t+h} \in \bm{\mathbb{R}}^3$.
+Due to the aggregation constraint of the hierarchy we have $\breve{y}_{Tot,t+h}=\breve{y}_{A,t+h}+\breve{y}_{B,t+h}$.
 This implies, even though  $\mathbold{\breve{y}}_{t+h}$ is in $\bm{\mathbb{R}}^3$, the points actually lie in a two dimensional subspace within that $\bm{\mathbb{R}}^3$ space.
@@
 In particular, the $m$ number of bottom level series of a given hierarchy can be considered as a basis set of series.
-Then the columns of $\bm{S}$ is a basis that generates through these bottom level series.
+Then the set of columns of $\bm{S}$ is a basis that generates through these bottom level series.
 This basis spans the linear subspace where the degenerate density lives on.\\
@@
 However bottom level series are not the only set of basis series and we can find many other basis set of series which generates basis that spans the same $\mathscr{C}(\bm{S})$ for a given hierarchy.
-If we go back to the hierarchy in example 1, instead of two bottom level series $(\bm{A,B})$ we can take $(\bm{T,A})$ as the basis set of series and the basis that generates through $(\bm{T,A})$ will be $\{\begin{pmatrix}
-1&0&1 \end{pmatrix}^T, \begin{pmatrix}
-0&1&-1 \end{pmatrix}^T\}$. Another possible basis would be the singular value decomposition of $\bm{S}$.\\
+If we go back to the hierarchy in example 1, instead of two bottom level series $(\bm{A,B})$ we can take $(\bm{Tot,A})$ as the basis set of series and the basis that generates through $(\bm{Tot,A})$ will be $\{\begin{pmatrix}
+1&0&1 \end{pmatrix}', \begin{pmatrix}
+0&1&-1 \end{pmatrix}'\}$. Another possible basis would be the singular value decomposition of $\bm{S}$.\\
 
@@
 Therefore the definition $(3.2)$ is not unique and one can redefine the coherent probabilistic forecasts with respect to any basis.
-However we stick to the definition $(3.2)$ and consider the basis defined by the columns of $\bm{S}$ that generates through the bottom levels of the hierarchy in what follows.\\
+However, we stick to the definition $(3.2)$ and consider the basis defined by the columns of $\bm{S}$ that generates through the bottom levels of the hierarchy in what follows.\\
 
@@
 
-Previous studies on point forecast literature has shown that the reconciliation provides better coherent forecasts than the conventional bottom-up and top-down methods (\cite{Hyndman2011}; \cite{VanErven2015a}; \cite{Wickramasuriya2017}).
-However this was not well established in the context of probabilistic forecasts.
+Previous studies on point forecast literature have shown that the reconciliation provides better coherent forecasts than the conventional bottom-up and top-down methods (\cite{Hyndman2011}; \cite{VanErven2015a}; \cite{Wickramasuriya2017}).
+However, this was not well established in the context of probabilistic forecasts.
 Nevertheless, there is no proper definition for the probabilistic forecast reconciliation in the published literature.
-Thus in this section we focus on defining the probabilistic forecast reconciliation and discuss how that definition can be used in practice.
+Thus in this section, we focus on defining the probabilistic forecast reconciliation and discuss how that definition can be used in practice.
 
@@
 In the following content we explain more on how this definition can be used in practice to reconcile point forecasts in hierarchical time series.
-Let $\bm{R} \in \bm{\mathbb{R}}^{n \times n-m}$ consists the columns that spans $\mathscr{N}(\bm{S})$ which is orthogonal to $\mathscr{C}(\bm{S})$.
+Let $\bm{R} \in \bm{\mathbb{R}}^{n \times (n-m)}$ consists the columns that spans $\mathscr{N}(\bm{S})$ which is orthogonal to $\mathscr{C}(\bm{S})$.
 $\mathscr{N}(\bm{S})$ is also equivalent to the $\mathscr{C}(\bm{R})$.
@@
 Then $\bm{B}=\{\bm{s}_1,...,\bm{s}_m, \bm{r}_1,...,\bm{r}_{n-m}\}$ is a basis for $\bm{\mathbb{R}}^n$.
-Now, using the insights of definition 4.1, we can follow the below steps to reconcile the point forecasts.\\
+Now, using the insights of definition 4.1, we can use the following steps to reconcile the point forecasts.\\
 
@@
 For a given incoherent set of point forecasts $\hat{\bm{y}}_{t+h} \in \bm{\mathbb{R}}^n$, first we find the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$.
-Let $\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T$ denote these coordinates.
+Let $\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}'$ denote these coordinates.
 Note that $\tilde{\bm{b}}_{t+h}$ is a basis set of series which is really the reconciled bottom level series that generates $\{\bm{s}_1,...,\bm{s}_m\}$ and $\tilde{\bm{t}}_{t+h}$ is another basis set of series that generates $\{\bm{r}_1,...,\bm{r}_{n-m}\}$.
@@
 \begin{flalign}\label{4.1}
-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T = \hat{\bm{y}}_{t+h},
+\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}' = \hat{\bm{y}}_{t+h},
 \end{flalign}
@@
 \begin{flalign}\label{4.3}
-\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T  = \begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\hat{\bm{y}}_{t+h}.
+\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}'  = \begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\hat{\bm{y}}_{t+h}.
 \end{flalign}
@@
 \begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
-(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot\\ \cdots \\ (\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot
+(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot\\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
 \end{pmatrix}.
@@
 \end{pmatrix} = \begin{pmatrix}
-(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot\\ \cdots \\ (\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot
+(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot\\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
 \end{pmatrix}\hat{\bm{y}}_{t+h}.
@@
 \begin{flalign}
-\tilde{\bm{b}}_{t+h}=(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot \hat{\bm{y}}_{t+h} 
+\tilde{\bm{b}}_{t+h}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h} 
 \end{flalign}
@@
 \begin{flalign}
-\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})<\bm{\mathbb{R}}^n.
+\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})<\bm{\mathbb{R}}^n.
 \end{flalign}
@@
 \begin{flalign}
-\bm{g}=(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot.
+\bm{g}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot.
 \end{flalign}
@@
 In other words, $\bm{g}$ linearly projects incoherent point forecasts onto the $\mathscr{C}(\bm{S})$.
-Further in our context, we need to find $\bm{R}_\bot$ such that $\bm{R}^T_\bot \bm{S}$ is invertible.
-i.e, $(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot \bm{S}=\bm{I}$.
+Further in our context, we need to find $\bm{R}_\bot$ such that $\bm{R}'_\bot \bm{S}$ is invertible.
+i.e, $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \bm{S}=\bm{I}$.
 This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}.
@@
 \begin{flalign*}
-\tilde{\bm{b}}^{OLS}_{t+h}=(\bm{S}^T \bm{S})^{-1}\bm{S}^T \hat{\bm{y}}_{t+h},
+\tilde{\bm{b}}^{OLS}_{t+h}=(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h},
 \end{flalign*}
 \noindent
-where in this context, $\bm{R}^T_\bot = \bm{S}^T$. Thus the reconciled point forecasts for the entire hierarchy is given by, 
+where in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy is given by, 
 \begin{flalign}
-\tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}^T \bm{S})^{-1}\bm{S}^T \hat{\bm{y}}_{t+h}.
+\tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h}.
 \end{flalign}
@@
 \noindent
-According to a recent study by \citet{Wickramasuriya2017}, choosing $\bm{R}^T_\bot = \bm{S}^T\bm{W}^{-1}_{h}$ will minimize the trace of mean squared reconciled forecasts errors under the property of unbiasedness where, $\bm{W}^{-1}_{h}$ is the variance of the incoherent forecast errors.
+According to a recent study by \citet{Wickramasuriya2017}, choosing $\bm{R}'_\bot = \bm{S}'\bm{W}^{-1}_{h}$ will minimize the trace of mean squared reconciled forecast errors under the property of unbiasedness where, $\bm{W}^{-1}_{h}$ is the variance of the incoherent forecast errors.
 This will result,
 \begin{flalign*}
-\tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}^T\bm{W}^{-1}_{h} \bm{S})^{-1}\bm{S}^T\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h},
+\tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}'\bm{W}^{-1}_{h} \bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h},
 \end{flalign*}
@@
 \begin{flalign}
-\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}^T \bm{W}^{-1}_{h}\bm{S})^{-1}\bm{S}^T\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h}.
+\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}' \bm{W}^{-1}_{h}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h}.
 \end{flalign}
@@
 \noindent
-Since the above definition seems not to be straight forward in reconciling incoherent forecasts, the following content explains how this can be used in practice to obtain reconciled probabilistic forecasts for hierarchical time series.
+Since the above definition seems not to be straightforward in reconciling incoherent forecasts, the following content explains how this can be used in practice to obtain reconciled probabilistic forecasts for hierarchical time series.
 \\
@@
 where $|.|$ denote the determinant of a matrix.
-Now that we have the density of $\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T $, the marginal density of $(\tilde{\bm{b}}_{t+h})$ can be obtained by integrating (\ref{4.5}) over the range of $\tilde{\bm{t}}_{t+h}$.
-This will result the reconciled density of the bottom level series $(\tilde{\bm{b}}_{t+h})$.
+Now that we have the density of $\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}' $, the marginal density of $\tilde{\bm{b}}_{t+h}$ can be obtained by integrating (\ref{4.5}) over the range of $\tilde{\bm{t}}_{t+h}$.
+This will result the reconciled density of the bottom level series $\tilde{\bm{b}}_{t+h}$.
 i.e.,
@@
 \noindent
-Finally to get the reconciled density of the whole hierarchy, we simply follow the definition $(3.2)$ and have, 
+Finally to get the reconciled density of the whole hierarchy, we simply follow the definition $3.2$ and have, 
 \begin{flalign}\label{4.7}
@@
 \noindent  
-Suppose $\mathscr{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h})\leftrightarrow^d \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ is an incoherent forecast distribution at time $t+h$.
+Suppose $\mathscr{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h}) \overset{d}{\leftrightarrow} \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ is an incoherent forecast distribution at time $t+h$.
 Then from (\ref{4.5}) it follows,
@@
 \begin{flalign*}
-\bm{f_B}(.)&=\frac{\exp\left\{-\frac{1}{2}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})^T \bm{\hat{\Sigma}_{t+h}}^{-1}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
-&= \frac{\exp\left\{-\frac{1}{2}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)^T \bm{\hat{\Sigma}_{t+h}}^{-1}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
+\bm{f_B}(.)&=\frac{\exp\left\{-\frac{1}{2}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})' \bm{\hat{\Sigma}_{t+h}}^{-1}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
+&= \frac{\exp\left\{-\frac{1}{2}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)' \bm{\hat{\Sigma}_{t+h}}^{-1}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
 \end{flalign*}
@@
 \bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|}
-\exp \Big\{&-\frac{1}{2}\Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big)^T\\
-&\Big[\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^T\Big]^{-1}\\ 
+\exp \Big\{&-\frac{1}{2}\Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big)'\\
+&\Big[\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}'\Big]^{-1}\\ 
 &\Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.
@@
 Recall that, $$\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
-(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot\\ \cdots \\ (\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot
+(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot\\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
 \end{pmatrix} = \begin{pmatrix}
 \bm{P}\\\bm{Q}
-\end{pmatrix},$$ where, $\bm{P}=(\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$ and $\bm{Q}=(\bm{S}^T_\bot \bm{R})^{-1}\bm{S}^T_\bot$. Then,
+\end{pmatrix},$$ where, $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ and $\bm{Q}=(\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot$. Then,
 
@@
 \bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix} \Big|}
-\exp \Big\{&-\frac{1}{2}\Big[\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\mu}}_{t+h}\Big]^T\Big[\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}^T\Big]^{-1}\\
+\exp \Big\{&-\frac{1}{2}\Big[\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\mu}}_{t+h}\Big]'\Big[\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}'\Big]^{-1}\\
 &\Big[\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\mu}}_{t+h}\Big] \Big\},
@@
 \begin{flalign*}
-\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}^T\Big|^{\frac{1}{2}}}
-\exp \Big\{&-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix}^T \Big[\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}^T\Big]^{-1}\\
+\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}'\Big|^{\frac{1}{2}}}
+\exp \Big\{&-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix}' \Big[\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}'\Big]^{-1}\\
 & \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix} \Big\}.
@@
 \noindent
-Since, $\Big[\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}^T\Big] = \begin{pmatrix}
-\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T\\
-\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T
+Since, $\Big[\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}'\Big] = \begin{pmatrix}
+\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'\\
+\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'
 \end{pmatrix}$ we have,
@@
 \bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\begin{pmatrix}
-	\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T\\
-	\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T
+	\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'\\
+	\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'
 	\end{pmatrix}\Big|^{\frac{1}{2}}}
-\exp \Big\{&-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix}^T\\ 
+\exp \Big\{&-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix}'\\ 
 &\begin{pmatrix}
-\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T\\
-\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}^T
+\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'\\
+\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'
 \end{pmatrix}^{-1}\\
@@
 \noindent
-$\bm{f_B}(.)$ gives the joint distribution of $\begin{pmatrix}\tilde{\bm{b}}^T_{t+h} & \vdots& \tilde{\bm{t}}^T_{t+h}\end{pmatrix}^T $, which is a multivariate Gaussian distribution.
+$\bm{f_B}(.)$ gives the joint distribution of $\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}' $, which is a multivariate Gaussian distribution.
 Then from (\ref{4.6}) and the properties of marginalization of multivariate Gaussian distribution it follows,
 \begin{flalign}\label{ex:2.1}
-\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T\Big|^{\frac{1}{2}}}
-\exp \Big\{-\frac{1}{2} (\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h})^T (\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}^T)^{-1}(\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}) \Big\}.
+\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}'\Big|^{\frac{1}{2}}}
+\exp \Big\{-\frac{1}{2} (\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h})' (\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}')^{-1}(\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}) \Big\}.
 \end{flalign}
@@
 \noindent
-(\ref{ex:2.1}) implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T)$ where $\bm{P} = (\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$.
+(\ref{ex:2.1}) implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$ where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
 Then from (\ref{4.7}) it follows that,
@@
 Therefore, the reconciled Gaussian forecast distribution of the whole hierarchy is\\
-$\mathscr{N}(\bm{SP}\bm{\hat{\mu}}_{t+h}, \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}^T\bm{S}^T)$.
+$\mathscr{N}(\bm{SP}\bm{\hat{\mu}}_{t+h}, \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}')$.
 
@@
 			\hline \\
-			\text{Energy score} & eS(\bm{\breve{Y}_{T+h},y_{T+h}}) = E_{\breve{\bm{F}}}||\breve{\bm{Y}}_{T+h}-\bm{y}_{T+h}||^\alpha - \frac{1}{2}E_{\breve{\bm{F}}}||\breve{\bm{Y}}_{T+h}-\breve{\bm{Y}}'_{T+h}||^\alpha, \alpha \in (0,2] & \text{\citet{Gneiting2008}} \\
+			\text{Energy score} & eS(\bm{\breve{Y}_{T+h},y_{T+h}}) = E_{\breve{\bm{F}}}||\breve{\bm{Y}}_{T+h}-\bm{y}_{T+h}||^\alpha - \frac{1}{2}E_{\breve{\bm{F}}}||\breve{\bm{Y}}_{T+h}-\breve{\bm{Y}}^*_{T+h}||^\alpha, \alpha \in (0,2] & \text{\citet{Gneiting2008}} \\
 			\\
@@
 \end{center}
-\textit{NOTE: $\bm{\breve{Y}}_{T+h}$ and $\bm{\breve{Y}}'_{T+h}$ be two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with the density function $\breve{\bm{f}}(.)$ at time $T+h$ and $\bm{y}_{T+h}$ is the vector of realizations.
+\textit{NOTE: $\bm{\breve{Y}}_{T+h}$ and $\bm{\breve{Y}}^*_{T+h}$ be two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with the density function $\breve{\bm{f}}(.)$ at time $T+h$ and $\bm{y}_{T+h}$ is the vector of realizations.
 Further $\breve{Y}_{T+h,i}$ and $\breve{Y}_{T+h,j}$ are $i^{\text{th}}$ and $j^{\text{th}}$ components of the vector $\breve{\bm{Y}}_{T+h}$.
-Further the variogram score given is for order $p$ where, $w_{ij}$ are non-negative weights.}\\
+Further the variogram score is given for order $p$ where, $w_{ij}$ are non-negative weights.}\\
 
@@
 However, the \qq{degenerecy} of coherent forecast densities would be problematic when using log scores.
-We will discuss more about this in the next sub section.\\
+We will discuss more on this in the next subsection.\\
 
@@
 \noindent
-This suggest that it is necessary to have a rule of thumb to use these scoring rules in order to evaluate coherent forecast densities.
+Thus it is necessary to have a rule of thumb to use these scoring rules in order to evaluate coherent forecast densities.
 First we should notice that, even though the coherent distribution of the entire hierarchy is degenerate, the density of the basis set of series is non-degenerate since these series are linearly independent.
@@
 For example, since the bottom level series is a set of basis series for a given hierarchy, we can evaluate the predictive ability of the bottom level series of the coherent forecast distribution instead of evaluating the whole distribution.
-Further if our purpose is to compare two coherent forecast densities, we can compare the forecast ability of only the bottom level forecast densities.
+Further, if our purpose is to compare two coherent forecast densities, we can compare the forecast ability of only the bottom level forecast densities.
 
@@
 It is also important to assess how the coherent or reconciled forecast densities improve the predictive ability compared to the incoherent forecasts.
-Clearly we cannot use multivariate scoring rules, even for the basis set of series, since the coherent and incoherent forecast densities lie in two different matrix spaces.\\
+Clearly, we cannot use multivariate scoring rules, even for the basis set of series, since the coherent and incoherent forecast densities lie in two different matrix spaces.\\
 
@@
 However we could compare individual margins of the forecast density of the hierarchy using univariate proper scoring rules.
-Most widely used Continuous Ranked Probability Score (CRPS) for evaluating univariate forecast densities would be helpful for this.
+Most widely used Continuous Ranked Probability Score (CRPS) would be helpful for this.
 \\
 \begin{equation} \label{eq:(3.6)}
-CRPS(\breve{F}_i,y_{T+h,i}) = E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}'_{T+h,i}|,
+CRPS(\breve{F}_i,y_{T+h,i}) = E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|,
 \end{equation}
@@
 \noindent
-where $\breve{Y}_{T+h,i}$ and $\breve{Y}'_{T+h,i}$ are two independent copies from the $i^{\text{th}}$ reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy and $y_{T+h,i}$ is the $i^{\text{th}}$ realization from the true marginal distribution $G_i$.
+where $\breve{Y}_{T+h,i}$ and $\breve{Y}^*_{T+h,i}$ are two independent copies from the $i^{\text{th}}$ reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy and $y_{T+h,i}$ is the $i^{\text{th}}$ realization from the true marginal distribution $G_i$.
 We can also use univariate log scores for which we could assume a parametric forecast distribution.
@@
 \noindent
-Suppose we independently fit the models for each series in the hierarchy.
-Let $\hat{Y}_{T+h,i}$ gives the point forecast of $i^{\text{th}}$ series at time $T+h$ conditional on the past observations $\{y_{1,i},...,y_{T,i}\}$ which minimizes the mean squared forecast error of $Y_{T+h,i}|\{y_{1,i},...,y_{T,i}\}$, where $i=1,...,n$.
-Then we have, $$\hat{Y}_{T+h,i} = E[Y_{T+h,i}|y_{1,i},...,y_{T,i}]$$
+Considering the individual series in the hierarchy, it is well known that the optimal point forecasts with respect to the minimal mean square error is given by the $E[Y_{T+h,i}|y_{1,i},...,y_{T,i}],$ $i=1,..,n$.
+Suppose we independently fit time series models for each series in the hierarchy.
+Then the point forecasts from the estimated models, denoted by $\hat{Y}_{T+h,i}$ is unbiased and consistent estimator of $E[Y_{T+h,i}|y_{1,i},...,y_{T,i}]$, given that the parameter estimates of the fitted models are unbiased and asymptotically consistent.
+\\
 
 \noindent
-Let $\hat{\bm{Y}}_{T+h}=(\hat{Y}_{T+h,1},...,\hat{Y}_{T+h,n})'$. Then, $$\hat{\bm{\mu}}_{T+h}=E[\bm{Y}_{T+h}|\bm{\mathcal{I}}_T] = \hat{\bm{Y}}_{T+h}.$$
+For example, suppose the data from $i^\text{th}$ series follows a $ARMA(p,q)$ model. i.e.,
+$$Y_{t,i}=\alpha_1Y_{t-1,i}+...+\alpha_pY_{t-p,i}+\epsilon_t + \beta_1\epsilon_{t-1,i}+...+\beta_q\epsilon_{t-q,i},$$ where $\epsilon_t \sim iid \mathcal{N}(0, \sigma_i^2)$. Then, 
+$$E[Y_{T+h,i}|y_{1,i},...,y_{T,i}] = \alpha_1Y_{T+h-1,i}+...+\alpha_pY_{T+h-p,i}+ \beta_1\epsilon_{T+h-1,i}+...+\beta_q\epsilon_{T+h-q,i}.$$
 
 \noindent
-Further we have, 
+Since $\bm{\alpha} = (\alpha_1,...,\alpha_p)'$ and $\bm{\beta} = (\beta_1,...,\beta_q)'$ are unknown in practice and thus estimated using the maximum likelihood method.
+Let $\bm{\hat{\alpha}}$ and $\bm{\hat{\beta}}$ denote the maximum likelihood estimates of $\bm{\alpha}$ and $\bm{\beta}$ respectively.
+\citet{Yao2006} showed that $\bm{\hat{\alpha}}$ and $\bm{\hat{\beta}}$ are asymptotically consistent estimators.
+Thus the point forecasts from this estimated model $Y_{T+h,i}$, will also be a consistent estimator for $E[Y_{T+h,i}|y_{1,i},...,y_{T,i}]$.
+i.e.,
+\begin{flalign} \label{eq:(6.01)}
+Y_{T+h,i} \overset{p}{\to} E[Y_{T+h,i}|y_{1,i},...,y_{T,i}] \quad \text{as} \quad T \to \infty.
+\end{flalign}
+
+\noindent
+Let $\hat{\bm{Y}}_{T+h}=(\hat{Y}_{T+h,1},...,\hat{Y}_{T+h,n})'$ and (\ref{eq:(6.01)}) holds for all $i=1,...,n$. Then from Slutsky's theorem it follows that, 
+\begin{flalign}\label{eq:(6.02)}
+\hat{\bm{Y}}_{T+h} \overset{p}{\to} E[\bm{Y}_{T+h}|\bm{\mathcal{I}}_T] \quad \text{as} \quad T \to \infty.
+\end{flalign}
+
+\noindent
+Further let the forecast error due to $\hat{\bm{Y}}_{T+h}$ is given by, 
 \begin{flalign*}
-Var(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) = & E[(\bm{Y}_{T+h} - E[\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T])(\bm{Y}_{T+h} - E[\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T])T]\\
-& = E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})T|\bm{\mathcal{I}}_T]\\
-& = \bm{W}_{T+h}
+\hat{\bm{e}}_{T+h} = \bm{Y}_{T+h}-\hat{\bm{Y}}_{T+h}, \quad \hat{\bm{e}} \sim \bm{\mathcal{N}}(0, \bm{W}_{T+h}).
+\end{flalign*}
+\noindent
+Now consider the variance of $\hat{\bm{e}}_{T+h}$,
+
+\begin{flalign*}
+E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = &  E[(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)- \hat{\bm{Y}}_{T+h})\\ &(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T],\\
+= & E[(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T]\\ \quad & + E[E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
+\quad &+  E[(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
+\quad &+ E[E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T]
 \end{flalign*}
@@
 \noindent
-Then the conditional forecast distribution at time $T+h$ will be multivariate Gaussian distribution with mean $\hat{\bm{Y}}_{T+h}$ and variance $\bm{W}_{T+h}$. 
-Since the point forecasts were obtained individually, it is very unlikely that the mean and variance lies in the coherent subspace.
-Therefore it gives the incoherent conditional forecast distribution which we denote as,
-\begin{flalign}\label{eq:(6.1)}
+From (\ref{eq:(6.02)}) it immediately follows that,
+
+\begin{flalign*}
+&E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] \overset{p}{\to} E[(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T],
+\end{flalign*} 
+\begin{flalign}
+\bm{W}_{T+h} \overset{p}{\to} Var(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) \quad \text{as} \quad T \to \infty.
+\end{flalign}
+\noindent
+It should be noted that, even though $\hat{\bm{Y}}_{T+h}$ and $\bm{W}_{T+h}$ are asymptotically consistent estimators for $E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ and $Var(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ respectively, they are not coherent since they doesn't lie in the coherent subspace.
+Thus the Gaussian forecast distribution with mean $\hat{\bm{Y}}_{T+h}$ and variance $\bm{W}_{T+h}$ will be incoherent and we denote it by,
+\begin{flalign}\label{eq:(6.03)}
 \widehat{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathscr{N}(\hat{\bm{Y}}_{T+h}, \bm{W}_{T+h})
@@
 \noindent
-Since our primary objective is to find the coherent forecast density of the hierarchy, we need to reconciled \ref{eq:(6.1)}.
+Since our primary objective is to find the coherent forecast density of the hierarchy, we need to reconciled (\ref{eq:(6.03)}).
 Recalling from example 2, the reconciled Gaussian predictive distribution is then given by,
-\begin{flalign}\label{eq:(6.1)}
-\widetilde{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathscr{N}(\bm{SP}\hat{\bm{Y}}_{T+h}, \bm{SP}\bm{W}_{T+h}\bm{P}^T\bm{S}^T)
+\begin{flalign}\label{eq:(6.04)}
+\widetilde{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathscr{N}(\bm{SP}\hat{\bm{Y}}_{T+h}, \bm{SP}\bm{W}_{T+h}\bm{P}'\bm{S}')
 \end{flalign}  
 \noindent
-where, $\bm{P} = (\bm{R}^T_\bot \bm{S})^{-1}\bm{R}^T_\bot$.\\
+where, $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.\\
 
+\pagebreak
 \noindent
-\textbf{Result 1}: Choosing $\bm{R}^T_\bot = \bm{S}^T\bm{W}_{T+h}^{-1}$ will ensure at least the mean of the predictive Gaussian distribution is optimally reconciled with respect to the energy score.\\
+\textbf{Result 1}: Choosing $\bm{R}'_\bot = \bm{S}'\bm{W}_{T+h}^{-1}$ will ensure at least the mean of the predictive Gaussian distribution is optimally reconciled with respect to the energy score.\\
 
@@
 Then the expectation of energy score with respect to the true distribution is equivalent to the trace of mean squared forecast error, i.e.
-$$E_{\bm{G}}[eS(\bm{\tilde{Y}_{T+h},y_{T+h}})]= Tr\{E_{\bm{y}_{T+h}}[(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})^T|\mathcal{I}_{T}]\}.$$
+$$E_{\bm{G}}[eS(\bm{\tilde{Y}_{T+h},y_{T+h}})]= Tr\{E_{\bm{y}_{T+h}}[(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})'|\mathcal{I}_{T}]\}.$$
 \noindent
-From Theorem 1 of \citet{Wickramasuriya2017} it immediately follows that $\bm{P} = (\bm{S}^T\bm{W}_{T+h}^{-1}\bm{S})^{-1}\bm{S}^T\bm{W}_{T+h}^{-1}$ minimizes the expected energy score constrained on the unbiasedness of reconciled forecasts.
-Thus we have $\bm{R}^T_\bot = \bm{S}^T\bm{W}_{T+h}^{-1}$.
+From Theorem 1 of \citet{Wickramasuriya2017} it immediately follows that $\bm{P} = (\bm{S}'\bm{W}_{T+h}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}_{T+h}^{-1}$ minimizes the expected energy score constrained on the unbiasedness of reconciled forecasts.
+Thus we have $\bm{R}'_\bot = \bm{S}'\bm{W}_{T+h}^{-1}$.
 \\
@@
 \noindent
-It should be noted that $\bm{W}_{T+h}$ can be estimated in different methods which yields different estimation of $\bm{R}^T_\bot$. Following table summarizes these methods.
+It should be noted that $\bm{W}_{T+h}$ can be estimated in different methods which yields different estimation of $\bm{R}'_\bot$. Following table summarizes these methods.
 
 \begin{center}
-	\captionof{table}{\textit{Summarizing different estimates of $\bm{R}^T_\bot$} }
+	\captionof{table}{\textit{Summarizing different estimates of $\bm{R}'_\bot$} }
 
@@
 			\hline\hline\\
-			\textbf{Method}& \textbf{Estimate of $\bm{W}_{h}$} & \textbf{Estimate of $\bm{R}^T_\bot$} \\  
+			\textbf{Method}& \textbf{Estimate of $\bm{W}_{h}$} & \textbf{Estimate of $\bm{R}'_\bot$} \\  
 			\hline \hline\\
-			OLS & $\bm{I}$ & $\bm{S}^T$\\
+			OLS & $\bm{I}$ & $\bm{S}'$\\
 			\hline\\
 
-			MinT(Sample) & 	$\bm{W}_{T+1}$ & $\bm{S}^T\bm{W}_{T+1}^{-1}$\\
+			MinT(Sample) & 	$\bm{\hat{W}}_{T+1}^{sam}$ & $\bm{S}'(\bm{\hat{W}}_{T+1}^{sam})^{-1}$\\
 			& (1-step ahead insample variance covariance matrix) &\\
@@
 
-			MinT(Shrink) & $\mathbold{W}_{T+1}^{shr} = \tau\text{Diag}(\mathbold{W}_{T+1}) + (1-\tau)\mathbold{W}_{T+1}$ & $\bm{S}^T(\bm{W}_{T+1}^{shr})^{-1}$\\
+			MinT(Shrink) & $\mathbold{\hat{W}}_{T+1}^{shr} = \tau\text{Diag}(\mathbold{\hat{W}}_{T+1}^{sam}) + (1-\tau)\mathbold{\hat{W}}_{T+1}^{sam}$ & $\bm{S}'(\bm{\hat{W}}_{T+1}^{shr})^{-1}$\\
 			\hline\\
 
-			MinT(WLS) & $\mathbold{W}_{T+1}^{wls} = \text{Diag}(\mathbold{W}_{T+1}^{shr})$ & 	$\bm{S}^T(\bm{W}_{T+1}^{wls})^{-1}$\\
+			MinT(WLS) & $\mathbold{\hat{W}}_{T+1}^{wls} = \text{Diag}(\mathbold{\hat{W}}_{T+1}^{shr})$ & 	$\bm{S}'(\bm{\hat{W}}_{T+1}^{wls})^{-1}$\\
 			\hline
@@
 \end{center}
-\textit{Note: $\mathbold{W}_{T+1}^{shr}$ is a shrinkage estimator proposed by \citet{Schafer2005} and also used by \citet{Wickramasuriya2017}, where $\tau = \frac{\sum_{i \ne j}\hat{Var}(\hat{r}_{ij})}{\sum_{i \ne j}\hat{r}_{ij}^2}$, $\hat{r}_{ij}$ is the $ij$-th element of sample correlation matrix.
+\textit{Note: For $n<T$, $\bm{\hat{W}}_{T+1}^{sam}$ is an unbiased and consistent estimator for $\bm{W}_{T+1}$.
+$\mathbold{\hat{W}}_{T+1}^{shr}$ is a shrinkage estimator which is much suitable for large dimensions.
+$\mathbold{\hat{W}}_{T+1}^{shr}$ was proposed by \citet{Schafer2005} and also used by \citet{Wickramasuriya2017}, where $\tau = \frac{\sum_{i \ne j}\hat{Var}(\hat{r}_{ij})}{\sum_{i \ne j}\hat{r}_{ij}^2}$, $\hat{r}_{ij}$ is the $ij$-th element of sample correlation matrix.
 Further Diag($\bm{A}$) denote the diagonal matrix of $\bm{A}$}.\\
@@
 This hierarchy consists two aggregation levels with four bottom level series.
-Each bottom level series will be generated first and add them up to obtain the data for respective upper level series.
+Each bottom-level series will be generated first and add them up to obtain the data for respective upper-level series.
 Hierarchical time series in practice contain much noisier series in the bottom level than in aggregate series.
@@
 $$Var(\epsilon_{AA,t}+\epsilon_{AB,t}+\epsilon_{BA,t}+\epsilon_{BB,t}) \le Var(\epsilon_{AA,t}+\epsilon_{AB,t}-v_t) \le Var(\epsilon_{AA,t}+u_t-0.5v_t),$$
-$$\bm{l}_1\bm{\Sigma} \bm{l}_1^T \le \bm{l}_2\bm{\Sigma} \bm{l}_2^T + \sigma^2_v \le  \bm{l}_3\bm{\Sigma} \bm{l}_3^T + \sigma^2_u + \frac{1}{4}\sigma^2_v,$$
+$$\bm{l}_1\bm{\Sigma} \bm{l}_1' \le \bm{l}_2\bm{\Sigma} \bm{l}_2' + \sigma^2_v \le  \bm{l}_3\bm{\Sigma} \bm{l}_3' + \sigma^2_u + \frac{1}{4}\sigma^2_v,$$
 \noindent
@@
 This follows, 
-$$\bm{l}_1\bm{\Sigma} \bm{l}_1^T - \bm{l}_2\bm{\Sigma} \bm{l}_2^T \le \sigma^2_v \le \frac{4}{3}(\sigma^2_u + \bm{l}_3\bm{\Sigma} \bm{l}_3^T - \bm{l}_2\bm{\Sigma} \bm{l}_2^T).$$
+$$\bm{l}_1\bm{\Sigma} \bm{l}_1' - \bm{l}_2\bm{\Sigma} \bm{l}_2' \le \sigma^2_v \le \frac{4}{3}(\sigma^2_u + \bm{l}_3\bm{\Sigma} \bm{l}_3' - \bm{l}_2\bm{\Sigma} \bm{l}_2').$$
 \noindent
@@
 We use \textit{forecast} package in \textbf{R}-software \citet{hyndman2017forecasting} for model fitting and forecasting.
-Further, different estimates of $\bm{W}_{T+1}$ and the corresponding $\bm{R}^T_\bot$ were obtained as summarized in Table 2.
+Further, different estimates of $\bm{W}_{T+1}$ and the corresponding $\bm{R}'_\bot$ were obtained as summarized in Table 2.
 This process was then replicated using $1000$ different data sets from the same data generating process.
@@
 As it was mentioned before we wish to establish the importance of reconciliation methods from this simulation study.
-In particular we compare different reconciliation methods over the conventional bottom-up method and also evaluate the predictive ability of coherent forecasts over incoherent forecasts.
-For the former comparison we use bottom level probabilistic forecasts and calculate the percentage skill score based on energy score, log score and variogram score for each reconciliation method with reference to the bottom up method (presented in Table 3).
-For the latter comparison we use percentage skill score based on CRPS and univariate log score for coherent probabilistic forecasts of each individual series with reference to incoherent forecasts (presented in Table 5).\\
+In particular, we compare different reconciliation methods over the conventional bottom-up method and also evaluate the predictive ability of coherent forecasts over incoherent forecasts.
+For the former comparison, we use bottom level probabilistic forecasts and calculate the percentage skill score based on energy score, log score and variogram score for each reconciliation method with reference to the bottom up method (presented in Table 3).
+For the latter comparison, we use percentage skill score based on CRPS and univariate log score for coherent probabilistic forecasts of each individual series with reference to incoherent forecasts (presented in Table 4 and 5).\\
 
 \noindent
-It is clearly evident from the results in table 3 that the multivariate reconciled forecasts for the bottom level series from MinT(Shrink), MinT(Sample) and OLS methods outperform the bottom up forecasts.
-Further it turns out that probabilistic forecasts from MinT(Sample) has the best predictive ability.
-MinT(Shrink) also performing fairly well compared to the other methods.
-\\
+It is clearly evident from the results in table 3 that the multivariate reconciled forecasts for the bottom level series from MinT(Shrink) and MinT(Sample) outperform the bottom-up forecasts.
+Further, these two methods produce probabilistic forecasts with best predictive ability in comparison to incoherent forecasts (from table 4 and 5).
+Moreover, it turns out that OLS and bottom-up methods produce the worst forecasts.
 
-\noindent
-When it comes to the comparison of incoherent versus coherent probabilistic forecasts using the individual series in the hierarchy, MinT(WLS) seems to produce probabilistic forecasts with the best predictive ability.
-Nonetheless, MinT(Shrink), MinT(Sample) and OLS (OLS except for total level) produce coherent forecasts with improved predictive ability compared to incoherent forecasts.
-Further it can be noticed that bottom-up method produce worst forecasts.
-
-\pagebreak
 \begin{center}
-	\captionof{table}{\textit{Comparison of reconciliation methods against Bottom up method} }
+	\captionof{table}{\textit{Comparison of incoherent forecasts using bottom level series} }
 
@@
 		\small
-		\begin{tabular}{@{}l S[table-format=2.2] S[table-format=2.2]  S[table-format=2.2] @{}}
+		\scriptsize
+		\begin{tabular}{@{}l S[table-format=2.2] S[table-format=2.2]  S[table-format=2.2] S[table-format=2.2] S[table-format=2.2]  S[table-format=2.2] @{}}
 
@@
 
-			{Forecasting method} &  {Energy score} & {Log score} & {Variogram score} \\ 
+			\multirow{2}{*}{\text{Forecasting method}} & \multicolumn{2}{ c }{\text{Energy score}} & \multicolumn{2}{c}{\text{Log score}} & \multicolumn{2}{c}{\text{Variogram score}} \\ 
+			\cline{2-7} & \text{Mean score} &  \text{Skill score (\%)} &   \text{Mean score} &   \text{Skill score (\%)} &   \text{Mean score} &   \text{Skill score (\%)}\\
 			\hline
@@
 
-			MinT(Shrink) & 10.13 & 6.74 & 4.71  \\
+			MinT(Shrink) & 7.47	& 10.11 & 11.34 & 6.44 & 3.05 &	4.69  \\
 
-			MinT(Sample) & $\mathB{10.25}$ & $\bm{6.83}$ & $\bm{5.00}$ \\
+			MinT(Sample) & 7.47 & 10.11 & 11.33 & 6.52 & 3.05 &	4.69  \\
 
-			MinT(WLS) & 5.06 & -4.85 & -2.06  \\
+			MinT(WLS) & 7.91 &	4.81 & 12.64 & -4.29 & 3.23 & -0.94  \\
 
-			OLS & 6.36 & 4.52 & 0.59  \\
+			OLS & 10.14 & -22.02 & 135.13 &	-1014.93 & 4.6 & -43.75  \\
 
-			\hline
-
-			\textit{Bottom up} & $\mathbi{8.49}$ & $\mathbi{12.16}$ & $\mathbi{3.40}$    \\
+			Bottom up & 8.31 &	& 12.12 & &	3.2	 \\
 
@@
 \end{center}
-\textit{Note: "Bottom up" row represent the average score for the bottom up method.
-Each entry above this row represent the percentage skill score with reference to the bottom up forecasting method.
-A positive(negative) entry shows the percentage increase(decrease) of score for different reconciliation methods with relative to the bottom up method}.\\\\
+\textit{Note: Each entry corresponds to the column "Skill score ($\%$)" under the given scoring rule represent the percentage skill score with reference to the bottom up forecasting method.
+A positive(negative) entry in these columns shows the percentage increase(decrease) of score for different reconciliation methods with relative to the bottom up method}.\\\\
 
+\pagebreak
 \begin{center}
@@
 	\scriptsize	
-		\begin{tabular}{@{}l S[table-format=1.2] S[table-format=1.2]  S[table-format=1.2] S[table-format=1.2] S[table-format=1.2]  S[table-format=1.2] S[table-format=1.2] S[table-format=1.2]  S[table-format=1.2] S[table-format=1.2] S[table-format=1.2]  S[table-format=1.2] S[table-format=1.2] S[table-format=1.2] @{}}
+		\begin{tabular}{@{}l S[table-format=5.5] S[table-format=5.5]  S[table-format=5.5] S[table-format=5.5] S[table-format=5.5]  S[table-format=5.5]  @{}}
 
@@
 
-		\multirow{2}{*}{\text{Forecasting method}} & \multicolumn{2}{ c }{\text{Total}} & \multicolumn{2}{c}{\text{Series - A}} & \multicolumn{2}{c}{\text{Series - B}} & \multicolumn{2}{c}{\text{Series - AA}} & \multicolumn{2}{c}{\text{Series - AB}}& \multicolumn{2}{c}{\text{Series - BA}} & \multicolumn{2}{c}{\text{Series - BB}} \\ \cline{2-15} & \text{CRPS} &  \text{LogS} &   \text{CRPS} &   \text{LogS} &   \text{CRPS} &   \text{LogS} & \text{CRPS} &  \text{LogS}& \text{CRPS} &  \text{LogS}& \text{CRPS} &  \text{LogS}& \text{CRPS} &  \text{LogS} \\
+		\multirow{2}{*}{\text{Forecasting method}} & \multicolumn{2}{ c }{\text{Total}} & \multicolumn{2}{c}{\text{Series - A}} & \multicolumn{2}{c}{\text{Series - B}} \\ 
+		\cline{2-7} &  CRPS &  LogS &   CRPS &   LogS &   CRPS &   LogS \\ 
 		\hline
@@
 
-		MinT(Shrink)  & 1.99 & 0.50 & 19.82 & 4.33 &	14.18 &	3.21 & 16.09 & 3.40 & 18.88 & 4.08 & 11.59 & 2.88 &	14.68 &	3.04 \\
+		MinT(Shrink) & 1.12 & 0.34 & 10.07 & 2.93 &	5.41 & 1.52 \\
 
-		MinT(Sample) & 2.17 & 0.50 & 19.58 & 4.33 &	13.89 &	3.21 & 16.54 & 3.40 & 19.45 & 4.29 & 11.97 & 2.88 &	14.98 &	3.26 \\
+		MinT(Sample) & 1.12 & 0.34 & 10.07 & 2.93 &	5.41 & 1.52	\\
 
-		MinT(WLS)  & $\bm{22.83}$ & $\bm{7.04}$ &	$\bm{56.35}$ &	$\bm{18.76}$ &	$\bm{51.44}$ &	$\bm{17.34}$ &	$\bm{37.84}$ &	$\bm{10.43}$ &	$\bm{36.13}$ &	$\bm{10.09}$ &	$\bm{30.17}$ & $\bm{9.73}$ & $\bm{37.35}$ & $\bm{10.65}$ \\
+		MinT(WLS) & -2.61 &	-2.02 &	5.28 & -4.40 & 2.70 & -4.24 \\
 
-		OLS  & -17.39 &	-4.77 &	13.27 &	2.89 & 10.63 & 2.36 & 9.41 & 1.70 &	10.1 & 1.93 & 7.44 & 1.33 &	9.21 & 1.74	\\
+		OLS & -38.06 & -698.99 & -24.70 & -1368.33 & -24.86 & -1159.09 \\
 
-		Bottom up & -259.78 & -33.67 & -20.22 &	-3.92 &	-19.92 & -3.85 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 & 0.00 \\
+		Bottom up & -89.55 & -21.83 & -8.87 & -2.35 & -9.46 & -2.73	 \\
 
@@
 
-		\textit{Incoherent} & $\mathbi{5.52}$ & $\mathbi{3.98}$	& $\mathbi{12.51}$  & $\mathbi{4.85}$ & $\mathbi{10.44}$ & $\mathbi{4.67}$ & $\mathbi{10.94}$ &	$\mathbi{4.70}$ & $\mathbi{10.49}$ & $\mathbi{4.66}$ & $\mathbi{9.14}$ & $\mathbi{9.14}$ & $\mathbi{9.88}$ & $\mathbi{ 4.60}$ \\
+		\textit{Incoherent} & $\mathbi{2.68}$ & $\mathbi{2.97}$	& $\mathbi{4.17}$  & $\mathbi{3.41}$ & $\mathbi{3.70}$ & $\mathbi{3.30}$ \\
 
@@
 Each entry above this row represent the percentage skill score with reference to the incoherent forecasts.
-A positive(negative) entry shows the percentage increase(decrease) of score for different forecasting methods with relative to incoherent forecasts}.\\\\
+A positive(negative) entry shows the percentage increase(decrease) of score for different forecasting methods with relative to incoherent forecasts}.\\
+
+\begin{center}
+	\captionof{table}{\textit{Comparison of incoherent vs. coherent forecasts for the individual bottom level series using Skill score}}
+
+	\resizebox{\linewidth}{!}{
+		\scriptsize	
+		\begin{tabular}{@{}l S[table-format=4.4] S[table-format=4.4]  S[table-format=4.4] S[table-format=4.4] S[table-format=4.4]  S[table-format=4.4] S[table-format=4.4] S[table-format=4.4] @{}}
+
+			\hline
+			\hline
+
+			\multirow{2}{*}{\text{Forecasting method}} & \multicolumn{2}{c}{\text{Series - AA}} & \multicolumn{2}{c}{\text{Series - AB}}& \multicolumn{2}{c}{\text{Series - BA}} & \multicolumn{2}{c}{\text{Series - BB}} \\
+			\cline{2-9} & CRPS &  LogS & CRPS &  LogS & CRPS &  LogS & CRPS & LogS \\ 
+			\hline
+			\hline
+
+			MinT(Shrink) & 8.71 & 2.71 & 10.57 & 3.04 &	5.95 & 1.86 & 7.91 & 2.46 \\
+
+			MinT(Sample) & 8.71 & 2.71 & 10.57 & 3.04 &	5.95 & 1.86 & 8.19 & 2.46 \\
+
+			MinT(WLS) & 5.54 & 0.30 & 5.96 & 0.30 &	2.43 & -0.62 & 5.08 & 0.62  \\
+
+			OLS  & -22.43 &	-931.63 & -22.49 & -886.32 & -26.01 & -834.67 &	-23.45 & -812.92 \\
+
+			\hline
+
+			\textit{Incoherent} & $\mathbi{3.79}$ & $\mathbi{3.32}$	& $\mathbi{3.69}$  & $\mathbi{3.29}$ & $\mathbi{3.46}$ & $\mathbi{3.23}$ & $\mathbi{3.54}$ &	$\mathbi{3.25}$  \\
+
+			\hline
+			\hline
+
+		\end{tabular}
+	}
+\end{center}
 
@@
 
-Although the problem of hierarchical point forecasts is well studied in literature, there is a lack of attention in the context of probabilistic forecasts.
-Thus we attempted to fill this gap in literature by providing substantial theoretical background to the problem.
+Although the problem of hierarchical point forecasts is well studied in the literature, there is a lack of attention in the context of probabilistic forecasts.
+Thus we attempted to fill this gap in the literature by providing substantial theoretical background to the problem.
 We initially provided rigorous definitions for the coherent point and probabilistic forecasts using the principles of measure theory.
 Due to the aggregation nature of hierarchy, the probability density is a degenerate density.
-Thus the forecast distribution that we opt to find should also lies in a lower dimensional subspace of $\bm{\mathbb{R}}^{n}$.\\
+Thus the forecast distribution that we opt to find should also lie in a lower dimensional subspace of $\bm{\mathbb{R}}^{n}$.\\
 
 \noindent
-As it was well established that the reconciliation outperform other conventional point forecasting methods in hierarchical literature, we proposed to use reconciliation in probabilistic forecasting as well to obtain coherent degenerate densities.
-We provided distinct definition for density forecast reconciliation and how it can be used to reconcile incoherent densities in practice.\\
+As it was well established that the reconciliation outperforms other conventional point forecasting methods in the hierarchical literature, we proposed to use reconciliation in probabilistic forecasting as well to obtain coherent degenerate densities.
+We provided a distinct definition for density forecast reconciliation and how it can be used to reconcile incoherent densities in practice.\\
 
@@
 Assuming a multivariate Gaussian distribution for the hierarchy, we showed how to obtain reconciled Gaussian forecast densities, utilizing available information in the hierarchy.
-The simulation study further showed that the MinT reconciliation method \citep{Wickramasuriya2017} is useful in producing improved coherent probabilistic forecasts at least in the Gaussian framework.
+An extensive Monte Carlo simulation study further showed that the MinT reconciliation method \citep{Wickramasuriya2017} is useful in producing improved coherent probabilistic forecasts at least in the Gaussian framework.
 

### 2018-02-18 Probabilistic forecasts in hierarchical time series.tex
Converted to Monash wp style and fixed lots of latex issues

@@
 \documentclass[a4paper, 11pt]{article}
-\usepackage[a4paper, inner=3cm, outer=3cm, top=2cm, bottom=3cm]{geometry}
-\usepackage{amsmath, amssymb, fixmath, qtree, bm, calrsfs, enumitem,multirow, caption, textcmds,siunitx,adjustbox, mathrsfs, float, amstext}
+\usepackage{monashwp}
+\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx, mathrsfs, float, booktabs}
 \usepackage[bb=boondox]{mathalfa}
 \usepackage{tikz}
-\usepackage[natbib=true,backend=bibtex,style=authoryear-comp,dashed=false,maxbibnames=99,firstinits=true,maxcitenames=3,url=true,doi=false,isbn=false]{biblatex}
-\usepackage[pdftex,colorlinks=true]{hyperref}
+\usetikzlibrary{arrows,positioning,shapes,fit,calc}
 \hypersetup{citecolor=blue,linkcolor=blue,urlcolor=blue}
@@
 \def\mathB#1{\textbf{ #1}}
+\def\E{\text{E}}
+\mathtoolsset{showonlyrefs=true}
+
+\newtheorem{definition}{Definition}[section]
 
 \bibliography{References_paper1}
+
+\title{Probabilistic Forecasts in Hierarchical~Time~Series}
+\author{Puwasala Gamakumara\\ Anastasios Panagiotelis\\ George Athanasopoulos\\ Rob J Hyndman}
+
+\addresses{\textbf{Puwasala Gamakumara}\\
+  Department of Econometrics and Business Statistics,\\
+  Monash University,\\ VIC 3800, Australia.\\
+  Email: Puwasala.Gamakumara@monash.edu \\[1cm]
+  \textbf{Anastasios Panagiotelis}\\
+  Department of Econometrics and Business Statistics,\\
+  Monash University,\\ VIC 3800, Australia.\\
+  Email: Anastasios.Panagiotelis@monash.edu\\[1cm]
+  \textbf{George Athanasopoulos}\\
+  Department of Econometrics and Business Statistics,\\
+  Monash University,\\ VIC 3800, Australia.\\
+  Email: George.Athanasopoulos@monash.edu\\[1cm]
+  \textbf{Rob J Hyndman}\\
+  Department of Econometrics and Business Statistics,\\
+  Monash University,\\ VIC 3800, Australia.\\
+  Email: Rob.Hyndman@monash.edu}
+
+\lfoot{\sf Gamakumara, Panagiotelis, Athanasopoulos \& Hyndman: \today}
+
 \begin{document}
 
-\title{Probabilistic Forecasts in Hierarchical Time Series}
 \maketitle
 
-\section{Introduction.}
+\begin{abstract}
+  TBC
+\end{abstract}
+
+\section{Introduction}
+
 Many research applications often involve a large collection of multiple time series some of which are aggregates of others.
@@
 This is referred to as hierarchical forecasting.
-An important aspect of hierarchical forecasting is to have coherent forecasts across the hierarchy; that is, forecasts at lower levels should add up to their respective upper levels of aggregation.\\
+An important aspect of hierarchical forecasting is to have coherent forecasts across the hierarchy; that is, forecasts at lower levels should add up to their respective upper levels of aggregation.
 
-\noindent
 There is a rich literature on producing coherent point forecasts in hierarchical time series.
@@
 This might result in inaccurate forecasts.
-For example, if the bottom level series are highly volatile or too noisy and hence challenging to forecast, then the resulting forecasts from bottom-up approach would be inaccurate.\\
+For example, if the bottom level series are highly volatile or too noisy and hence challenging to forecast, then the resulting forecasts from bottom-up approach would be inaccurate.
 
-\noindent
 As an alternative to these conventional methods, \citet{Hyndman2011} propose to use information from all the levels of the hierarchy and reconcile them to obtain coherent point forecasts.
@@
 Thus it is important to notice that bottom-up, top-down and middle-out methods are not reconciliation methods since they use only a part of the information from the hierarchy to produce coherent forecasts.
-\\
 
-\noindent
 In a recent study on point forecast reconciliation, \citet{Wickramasuriya2017} propose to minimize the trace of mean squared coherent forecasts errors to optimally reconcile a set of unbiased, incoherent forecasts.
@@
 This solution was further improved to be computationally feasible for high dimensional hierarchies.
-\\
 
-\noindent
 In recent forecasting literature, it is being the rationality to provide the associated uncertainty about the future, in addition to the point forecasts.
@@
 For example, \citet{McSharry2005} produced probabilistic forecasts in application to electricity demand, \citet{BenTaieb2017} in application to smart meter data, \citet{Pinson2009} in application to wind power generation, \citet{Gel2004}, \citet{Gneiting2005a} and \citet{Gneiting2005} in application to prediction of weather quantities.
-\\
 
-\noindent      
 Although there is a thorough literature on producing coherent point forecasts of hierarchical time series, a very limited attention has been given in the context of probabilistic forecasts.
@@
 Hence this method is a bottom-up based approach.
-They further use MinT approach for the mean reconciliation of the bottom level predictive distribution and a copula based approach to model the dependency structure of the hierarchy, when producing the sample of bottom level probabilistic forecasts.\\
+They further use MinT approach for the mean reconciliation of the bottom level predictive distribution and a copula based approach to model the dependency structure of the hierarchy, when producing the sample of bottom level probabilistic forecasts.
 
-\noindent
 Our contribution in this paper is to provide a proper theoretical background for the probabilistic hierarchical forecasts.
@@
 Further, we provide theoretical results on probabilistic forecast reconciliation in the Gaussian framework.
-\\
 
-\noindent
 Rest of the paper is structured as follows.
@@
 \section{Notations}
+
 We first introduce notations where possible following \citet{Wickramasuriya2017}.
-Suppose $\mathbold{y}_t \in \bm{\mathbb{R}}^n$ comprising all observations of the whole hierarchy at time $t$ and $\mathbold{b}_t \in \bm{\mathbb{R}}^m$ comprising only the bottom level observations at  time $t$.
+Suppose $\bm{y}_t \in \mathbb{R}^n$ comprising all observations of the whole hierarchy at time $t$ and $\bm{b}_t \in \mathbb{R}^m$ comprising only the bottom level observations at  time $t$.
 Then due to the aggregation nature of the hierarchy we have,
-
 \begin{equation}
-\mathbold{y}_t = \mathbold{Sb}_t,
+  \bm{y}_t = \bm{Sb}_t,
 \end{equation}
-where $\mathbold{S}$ is a $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold.
+where $\bm{S}$ is a $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold.
 Since this linear subspace is equivalent to the column space of $\bm{S}$, we denote it as $\mathscr{C}(\bm{S})$.
 Further the null space of $\bm{S}$ which is orthogonal to this linear subspace is denoted by $\mathscr{N}(\bm{S})$.
+
 To understand the notations clearly, consider the hierarchy given in Figure 1.
@@
 \end{figure}
-\noindent
+
 In any hierarchy, the most aggregated level is termed as level 0, the second most aggregated level is termed as level 1 and so on.
@@
 At a particular time $t$, let $y_{Tot,t}$ denote the observation at level 0; $y_{A,t}, y_{B,t} $ denote observations at level 1; and $y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}$ denote observations at level 2.
-Then $\mathbold{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, \\$\mathbold{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and $$ \mathbold{S} = \begin{pmatrix} 1& 1 &1 &1  \\ 1 &1 & 0 &0 \\   0&0  & 1 & 1 \\ & & I_4 &   \end{pmatrix}, $$ where $I_4$ is a $4$-dimension identity matrix.
-\\
+Then
+$\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, \\
+$\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and
+$$
+  \bm{S} =
+  \begin{pmatrix}
+    1& 1 &1 &1  \\ 1 &1 & 0 &0 \\   0&0  & 1 & 1 \\ & & I_4 &
+  \end{pmatrix},
+$$
+where $I_4$ is a $4$-dimension identity matrix.
 
@@
 We start with redefining the coherent point forecasts using the properties of vector spaces which is then followed by the definition of coherent probabilistic forecasts.
-\\
 
-\noindent
-\textbf{Definition 3.1: Coherent Point Forecasts}\\
-\noindent
-Suppose $\bm{\breve{y}}_{t+h} \in \mathbb{R}^n$ consists point forecasts of each series in the hierarchy at time $t+h$.
-$\bm{\breve{y}}_{t+h}$ is said to be \textit{Coherent} if it lies in a $m$-dimensional subspace of $\bm{\mathbb{R}}^n$ which is spanned by the columns of $\bm{S}$.
-\\
+\begin{definition}[Coherent Point Forecasts]
+Suppose $\breve{\bm{y}}_{t+h} \in \mathbb{R}^n$ consists point forecasts of each series in the hierarchy at time $t+h$.
+$\breve{\bm{y}}_{t+h}$ is said to be \textit{Coherent} if it lies in a $m$-dimensional subspace of $\mathbb{R}^n$ which is spanned by the columns of $\bm{S}$.
+\end{definition}
 
-\noindent
-\textbf{Definition 3.2: Coherent Probabilistic Forecasts}\\
-\noindent
-Let $(\bm{\mathbb{R}}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability measure space where $\mathscr{F}^m$ is a sigma algebra on $\bm{\mathbb{R}}^m$.
+\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
+Let $(\mathbb{R}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability measure space where $\mathscr{F}^m$ is a sigma algebra on $\mathbb{R}^m$.
 $\breve{\nu}(.)$ on the measurable space $(\mathscr{C}(\bm{S}), \mathscr{F}_{\bm{S}})$ is said to be coherent probability measure iff $$\breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall \quad \bm{A} \in \mathscr{F}^m,$$ where $\bm{S}(\bm{A})$ denotes the image of subset $\bm{A}$ under $\bm{S}$.
-
-\usetikzlibrary{arrows,positioning,shapes,fit,calc}
+\end{definition}
 
@@
 
-		\node at (0,5) {$\bm{\mathbb{R}}^m$(domain of $\bm{S}$)};
-		\node at (4,5) {$\bm{\mathbb{R}}^n$(codomain of $\bm{S}$)};
+      \node at (0,5) {$\mathbb{R}^m$(domain of $\bm{S}$)};
+      \node at (4,5) {$\mathbb{R}^n$(codomain of $\bm{S}$)};
       \node at (4,1.0) {$\mathscr{C}(\bm{S})$};
@@
   \end{center}
-	\caption{Any set $\bm{A} \in \bm{\mathbb{R}}^m$ will be mapped to the $\mathscr{C}(\bm{S})$ through the mapping $\bm{S}$}
+  \caption{Any set $\bm{A} \in \mathbb{R}^m$ will be mapped to the $\mathscr{C}(\bm{S})$ through the mapping $\bm{S}$}
 \end{figure}
-\noindent
-Definition 3.2 implies the probability measure on $\mathscr{C}(\bm{S})$ is equivalent to the probability measure on $(\bm{\mathbb{R}}^m, \bm{\mathscr{F}}^m)$.
-Hence, there is no density anywhere outside the linear subspace spanned by the columns of $\bm{S}$ in $\bm{\mathbb{R}}^n$.
-That is, a \textit{Coherent probability density forecast} is any density $\bm{f}(\bm{\breve{y}}_{t+h})$ such that $\bm{f}(\bm{\breve{y}}_{t+h})=0$ for all $\bm{\breve{y}}_{t+h} \in \mathscr{N}(\bm{S})$.
-Following example will help to understand these definitions more clearly.\\
 
-\noindent
-\textbf{Example 1}:\\
+Definition \ref{def:cohprob} implies the probability measure on $\mathscr{C}(\bm{S})$ is equivalent to the probability measure on $(\mathbb{R}^m, \bm{\mathscr{F}}^m)$.
+Hence, there is no density anywhere outside the linear subspace spanned by the columns of $\bm{S}$ in $\mathbb{R}^n$.
+That is, a \textit{Coherent probability density forecast} is any density $\bm{f}(\breve{\bm{y}}_{t+h})$ such that $\bm{f}(\breve{\bm{y}}_{t+h})=0$ for all $\breve{\bm{y}}_{t+h} \in \mathscr{N}(\bm{S})$.
+Following example will help to understand these definitions more clearly.
 
-\noindent
+\subsubsection*{Example 1}
+
 Consider a simple hierarchy with two bottom level series $A$ and $B$ that add up to the top level series $Tot$.
-Suppose the forecasts at time $t+h$ of these series are given by $\mathbold{\breve{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$ and $\mathbold{\breve{y}}_{t+h} \in \bm{\mathbb{R}}^3$.
+Suppose the forecasts at time $t+h$ of these series are given by $\breve{\bm{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$ and $\breve{\bm{y}}_{t+h} \in \mathbb{R}^3$.
 Due to the aggregation constraint of the hierarchy we have $\breve{y}_{Tot,t+h}=\breve{y}_{A,t+h}+\breve{y}_{B,t+h}$.
-This implies, even though  $\mathbold{\breve{y}}_{t+h}$ is in $\bm{\mathbb{R}}^3$, the points actually lie in a two dimensional subspace within that $\bm{\mathbb{R}}^3$ space.
+This implies, even though  $\breve{\bm{y}}_{t+h}$ is in $\mathbb{R}^3$, the points actually lie in a two dimensional subspace within that $\mathbb{R}^3$ space.
 This subspace is equivalent to $\mathscr{C}(\bm{S})$ for this simple hierarchy.
-Therefore, for any $\mathbold{\breve{y}}_{t+h} \in \mathscr{N}(\bm{S})$ have a zero probability.
+Therefore, for any $\breve{\bm{y}}_{t+h} \in \mathscr{N}(\bm{S})$ have a zero probability.
 I.e.
-$f(\mathbold{\breve{y}}_{t+h})=0$ for any $\mathbold{\breve{y}}_{t+h} \in \mathscr{N}(\bm{S})$.\\
+$f(\breve{\bm{y}}_{t+h})=0$ for any $\breve{\bm{y}}_{t+h} \in \mathscr{N}(\bm{S})$.
 
-\noindent
 By the definition of coherent forecasts, it is clear that there are only $m$ number of linear independent series in the whole hierarchy.
@@
 Then the set of columns of $\bm{S}$ is a basis that generates through these bottom level series.
-This basis spans the linear subspace where the degenerate density lives on.\\
+This basis spans the linear subspace where the degenerate density lives on.
 
-\noindent
 However bottom level series are not the only set of basis series and we can find many other basis set of series which generates basis that spans the same $\mathscr{C}(\bm{S})$ for a given hierarchy.
-If we go back to the hierarchy in example 1, instead of two bottom level series $(\bm{A,B})$ we can take $(\bm{Tot,A})$ as the basis set of series and the basis that generates through $(\bm{Tot,A})$ will be $\{\begin{pmatrix}
-1&0&1 \end{pmatrix}', \begin{pmatrix}
-0&1&-1 \end{pmatrix}'\}$. Another possible basis would be the singular value decomposition of $\bm{S}$.\\
+If we go back to the hierarchy in example 1, instead of two bottom level series $(\bm{A,B})$ we can take $(\bm{Tot,A})$ as the basis set of series and the basis that generates through $(\bm{Tot,A})$ will be
+$\{
+  \begin{pmatrix} 1&0&1 \end{pmatrix}',
+  \begin{pmatrix} 0&1&-1 \end{pmatrix}'\}$.
+Another possible basis would be the singular value decomposition of $\bm{S}$.
 
-\noindent
 An important thing to notice here is all of these basis spans the same linear subspace equivalent to the $\mathscr{C}(\bm{S})$.
 Therefore the definition $(3.2)$ is not unique and one can redefine the coherent probabilistic forecasts with respect to any basis.
-However, we stick to the definition $(3.2)$ and consider the basis defined by the columns of $\bm{S}$ that generates through the bottom levels of the hierarchy in what follows.\\
+However, we stick to the definition $(3.2)$ and consider the basis defined by the columns of $\bm{S}$ that generates through the bottom levels of the hierarchy in what follows.
 
-\noindent
 It is also worth to mention that the definition $(3.1)$ and $(3.2)$ facilitate extension to the forecast reconciliation which we talk about in the next section.
@@
 
-Initially we redefine point forecast reconciliation using the concepts in linear algebra as a groundwork for the probabilistic forecast reconciliation. \\
+Initially we redefine point forecast reconciliation using the concepts in linear algebra as a groundwork for the probabilistic forecast reconciliation.
 
-\noindent
-\textbf{Definition 4.1}\\
-\noindent
-Let $\bm{g}:\bm{\mathbb{R}}^n \rightarrow \bm{\mathbb{R}}^m $ and $\hat{\bm{y}}_{t+h} \in \bm{\mathbb{R}}^n$ be any set of incoherent forecasts at time $t+h$.
+\begin{definition}
+Let $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m $ and $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$ be any set of incoherent forecasts at time $t+h$.
 Then $\tilde{\bm{b}}_{t+h}$ is said to be reconciled bottom level forecasts if
@@
 \end{equation}
-\noindent
-where $\bm{g}(\hat{\bm{y}}_{t+h})$ is the image of $\hat{\bm{y}}_{t+h}$ under $\bm{g}$ on $\bm{\mathbb{R}}^m$.
-The reconciled forecasts for the whole hierarchy is then given by $\tilde{\bm{y}}_{t+h}=\bm{S}(\tilde{\bm{b}}_{t+h})$ such that $\tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})$, where $\bm{S}(\tilde{\bm{b}}_{t+h})$ is the image of $\tilde{\bm{b}}_{t+h}$ under $\bm{S}$ on the $\mathscr{C}(\bm{S}) < \bm{\mathbb{R}}^n$.\\
+where $\bm{g}(\hat{\bm{y}}_{t+h})$ is the image of $\hat{\bm{y}}_{t+h}$ under $\bm{g}$ on $\mathbb{R}^m$.
+The reconciled forecasts for the whole hierarchy is then given by $\tilde{\bm{y}}_{t+h}=\bm{S}(\tilde{\bm{b}}_{t+h})$ such that $\tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})$, where $\bm{S}(\tilde{\bm{b}}_{t+h})$ is the image of $\tilde{\bm{b}}_{t+h}$ under $\bm{S}$ on the $\mathscr{C}(\bm{S}) < \mathbb{R}^n$.
+\end{definition}
 
-\noindent
 In the following content we explain more on how this definition can be used in practice to reconcile point forecasts in hierarchical time series.
-Let $\bm{R} \in \bm{\mathbb{R}}^{n \times (n-m)}$ consists the columns that spans $\mathscr{N}(\bm{S})$ which is orthogonal to $\mathscr{C}(\bm{S})$.
+Let $\bm{R} \in \mathbb{R}^{n \times (n-m)}$ consists the columns that spans $\mathscr{N}(\bm{S})$ which is orthogonal to $\mathscr{C}(\bm{S})$.
 $\mathscr{N}(\bm{S})$ is also equivalent to the $\mathscr{C}(\bm{R})$.
 Note that $\bm{R}$ is also not unique and one example is a matrix whose columns represent the aggregation constraints for the hierarchy.
-Then for the hierarchy in example 1, $$ \mathbold{S} = \begin{pmatrix} 1& 1 \\ 1 & 0 \\ 0&1 \end{pmatrix} \quad \text{and} \quad \mathbold{R} = \begin{pmatrix}  1 \\ -1 \\ -1 \end{pmatrix}.$$
-\noindent
-Further let $\{\bm{s}_1,...,\bm{s}_m\}$ and $\{\bm{r}_1,...,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively.
-Then $\bm{B}=\{\bm{s}_1,...,\bm{s}_m, \bm{r}_1,...,\bm{r}_{n-m}\}$ is a basis for $\bm{\mathbb{R}}^n$.
-Now, using the insights of definition 4.1, we can use the following steps to reconcile the point forecasts.\\
+Then for the hierarchy in example 1,
+$$
+  \bm{S} =
+  \begin{pmatrix}
+    1& 1 \\ 1 & 0 \\ 0&1
+  \end{pmatrix}
+  \quad \text{and} \quad
+  \bm{R} =
+  \begin{pmatrix}
+    1 \\ -1 \\ -1
+  \end{pmatrix}.
+$$
+Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively.
+Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$.
+Now, using the insights of definition 4.1, we can use the following steps to reconcile the point forecasts.
 
-\noindent
-\textbf{Step 1: Obtaining reconciled bottom level point forecasts}\\
+\subsubsection*{Step 1: Obtaining reconciled bottom level point forecasts}
 
-\noindent
-For a given incoherent set of point forecasts $\hat{\bm{y}}_{t+h} \in \bm{\mathbb{R}}^n$, first we find the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$.
+For a given incoherent set of point forecasts $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$, first we find the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$.
 Let $\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}'$ denote these coordinates.
-Note that $\tilde{\bm{b}}_{t+h}$ is a basis set of series which is really the reconciled bottom level series that generates $\{\bm{s}_1,...,\bm{s}_m\}$ and $\tilde{\bm{t}}_{t+h}$ is another basis set of series that generates $\{\bm{r}_1,...,\bm{r}_{n-m}\}$.
+Note that $\tilde{\bm{b}}_{t+h}$ is a basis set of series which is really the reconciled bottom level series that generates $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\tilde{\bm{t}}_{t+h}$ is another basis set of series that generates $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$.
 Then from basic properties of linear algebra it follows that,
-
 \begin{flalign}\label{4.1}
-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}' = \hat{\bm{y}}_{t+h},
+  \begin{pmatrix}
+    \bm{S} & \vdots& \bm{R}
+  \end{pmatrix}
+  \begin{pmatrix}
+    \tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}
+  \end{pmatrix}'
+  = \hat{\bm{y}}_{t+h},
 \end{flalign}
@@
 \end{flalign}
-\noindent
 and
 \begin{flalign}\label{4.3}
-\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}'  = \begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\hat{\bm{y}}_{t+h}.
+  \begin{pmatrix}
+    \tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}
+   \end{pmatrix}' =
+   \begin{pmatrix}
+     \bm{S} & \vdots& \bm{R}
+   \end{pmatrix}^{-1}
+   \hat{\bm{y}}_{t+h}.
 \end{flalign}
 
-\noindent
 In order to find $(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1}$, let $\bm{S}_{\bot}$ and $\bm{R}_{\bot}$ be the orthogonal complements of $\bm{S}$ and $\bm{R}$
 respectively. Then $(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1}$ is given by,
-
 \begin{flalign}
   \begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
-(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot\\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
+    (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
   \end{pmatrix}.
 \end{flalign}
-
-\noindent
 Thus we have,
@@
   \begin{pmatrix}
-\tilde{\bm{b}}_{t+h}\\ \cdots \\ \tilde{\bm{t}}_{t+h}
+    \tilde{\bm{b}}_{t+h} \\ \cdots \\ \tilde{\bm{t}}_{t+h}
   \end{pmatrix} = \begin{pmatrix}
-(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot\\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
+    (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
   \end{pmatrix}\hat{\bm{y}}_{t+h}.
@@
 
-\noindent
-From (\ref{4.4}) it follows that, 
+From \eqref{4.4} it follows that,
 \begin{flalign}
@@
 \end{flalign}
-\\
 
-\noindent
-\textbf{Step 2: Obtaining reconciled point forecasts for the whole hierarchy}\\
+\subsubsection*{Step 2: Obtaining reconciled point forecasts for the whole hierarchy}
 
-\noindent
 This step directly follows by the definition for coherent forecasts.
-That is, to obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \bm{\mathbb{R}}^n$ to the $\mathscr{C}(\bm{S})$ through $\bm{S}$.
+That is, to obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \mathbb{R}^n$ to the $\mathscr{C}(\bm{S})$ through $\bm{S}$.
 Thus we have,
 \begin{flalign}
-\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})<\bm{\mathbb{R}}^n.
+  \tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})<\mathbb{R}^n.
 \end{flalign}
 
-\noindent
 Finding a suitable $\bm{R}_\bot$ with respect to a certain loss function will result optimally reconciled point forecasts of the hierarchy.
@@
 \end{flalign}
-\noindent
+
 In previous studies on hierarchical point forecasting, $\bm{g}$ is considered as a $m \times n$ matrix $\bm{P}$ and thus $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$.
@@
 This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}.
-\\
 
-\noindent
 In their study, \citet{Hyndman2011} proposed to choose,
@@
 \end{flalign*}
-\noindent
 where in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy is given by,
@@
 \end{flalign}
-\noindent
 They referred this to as OLS solution and the loss function they considered is equivalent to the euclidean norm between $\hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h}$, i.e.
-$<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>$.\\
+$<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>$.
 
-\noindent
 According to a recent study by \citet{Wickramasuriya2017}, choosing $\bm{R}'_\bot = \bm{S}'\bm{W}^{-1}_{h}$ will minimize the trace of mean squared reconciled forecast errors under the property of unbiasedness where, $\bm{W}^{-1}_{h}$ is the variance of the incoherent forecast errors.
@@
 
-\noindent
 They referred this to as MinT solution.
@@
 A more formal definition is given below.
-\\
 
-\noindent
-\textbf{Definition 4.2}\\
-\noindent
-Suppose $(\bm{\mathbb{R}}^n, \mathscr{F}^n, \hat{\nu})$ be an incoherent probability measure space and $(\bm{\mathbb{R}}^m, \mathscr{F}^m, \nu^m)$ be a probability measure space defined on $\bm{\mathbb{R}}^m$.
+\begin{definition}
+Suppose $(\mathbb{R}^n, \mathscr{F}^n, \hat{\nu})$ be an incoherent probability measure space and $(\mathbb{R}^m, \mathscr{F}^m, \nu^m)$ be a probability measure space defined on $\mathbb{R}^m$.
 Let $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m $.
@@
 \end{flalign}
-\noindent
+
 Further the reconciled probability measure of the whole hierarchy is given by,
@@
 \end{flalign}
-\noindent
-where, $\bm{S}:\mathbb{R}^m \rightarrow \mathbb{R}^n$ and $\tilde{\nu}(.)$ is the probability measure on the measure space $(\mathscr{C}(\bm{S}), \mathscr{F}_S)$.\\
+where $\bm{S}:\mathbb{R}^m \rightarrow \mathbb{R}^n$ and $\tilde{\nu}(.)$ is the probability measure on the measure space $(\mathscr{C}(\bm{S}), \mathscr{F}_S)$.
+\end{definition}
 
-\noindent
 Since the above definition seems not to be straightforward in reconciling incoherent forecasts, the following content explains how this can be used in practice to obtain reconciled probabilistic forecasts for hierarchical time series.
-\\
 
-\noindent
-Recall that $\hat{\bm{y}}_{t+h}$ is a set of incoherent point forecasts and the coordinates of that with respect to the basis $\bm{B}$ is given by (\ref{4.3}).
+Recall that $\hat{\bm{y}}_{t+h}$ is a set of incoherent point forecasts and the coordinates of that with respect to the basis $\bm{B}$ is given by \eqref{4.3}.
 Suppose $\hat{\bm{f}}(.)$ is the probability density of $\hat{\bm{y}}_{t+h}$.
@@
 In order to obtain this reconciled density, we need to project $\hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ onto the $\mathscr{C}(\bm{S})$ along the direction of $\mathscr{C}(\bm{R})$.
-\\
 
-\noindent
-Let the density of coordinates of $\hat{\bm{y}}_{t+h}$ with respect to basis $\bm{B}$ is denoted by $\bm{f_B}(.)$. Then it follows from  (\ref{4.3}) and the facts on density of transformed variables,
-
+Let the density of coordinates of $\hat{\bm{y}}_{t+h}$ with respect to basis $\bm{B}$ is denoted by $\bm{f_B}(.)$. Then it follows from  \eqref{4.3} and the facts on density of transformed variables,
 \begin{flalign}\label{4.5}
@@
 \end{flalign}
-\noindent
 where $|.|$ denote the determinant of a matrix.
-Now that we have the density of $\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}' $, the marginal density of $\tilde{\bm{b}}_{t+h}$ can be obtained by integrating (\ref{4.5}) over the range of $\tilde{\bm{t}}_{t+h}$.
+Now that we have the density of $\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}' $, the marginal density of $\tilde{\bm{b}}_{t+h}$ can be obtained by integrating \eqref{4.5} over the range of $\tilde{\bm{t}}_{t+h}$.
 This will result the reconciled density of the bottom level series $\tilde{\bm{b}}_{t+h}$.
@@
 
-\noindent
 Finally to get the reconciled density of the whole hierarchy, we simply follow the definition $3.2$ and have,
@@
 \end{flalign}
+This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the $\mathscr{C}(\bm{S})<\mathbb{R}^n$.
+Following example illustrates how this method can be used to reconcile an incoherent Gaussian forecast distribution.
 
-\noindent
-This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the $\mathscr{C}(\bm{S})<\bm{\mathbb{R}}^n$.
-Following example illustrates how this method can be used to reconcile an incoherent Gaussian forecast distribution.\\
+\subsubsection*{Example 2}
 
-\noindent
-\textbf{Example 2}\\
-
-\noindent  
 Suppose $\mathscr{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h}) \overset{d}{\leftrightarrow} \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ is an incoherent forecast distribution at time $t+h$.
-Then from (\ref{4.5}) it follows,
-
+Then from \eqref{4.5} it follows,
 \begin{flalign*}
@@
 \end{flalign*}
-\noindent
 By substituting the Gaussian distribution function to $\bm{f_B}(.)$ we get,
-
 \begin{flalign*}
   \bm{f_B}(.)&=\frac{\exp\left\{-\frac{1}{2}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})' \bm{\hat{\Sigma}_{t+h}}^{-1}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
-&= \frac{\exp\left\{-\frac{1}{2}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)' \bm{\hat{\Sigma}_{t+h}}^{-1}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
+  &= \frac{\exp\left\{-\frac{1}{2}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)' \bm{\hat{\Sigma}_{t+h}}^{-1}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},
 \end{flalign*}
-
 \begin{flalign*}
@@
 \end{flalign*}
-\noindent
 Recall that, $$\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
-(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot\\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
+    (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
   \end{pmatrix} = \begin{pmatrix}
-\bm{P}\\\bm{Q}
+    \bm{P} \\\bm{Q}
   \end{pmatrix},$$ where, $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ and $\bm{Q}=(\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot$. Then,
-
 \begin{flalign*}
@@
 \end{flalign*}
-
 \begin{flalign*}
@@
 \end{flalign*}
-\noindent
 Since, $\Big[\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}'\Big] = \begin{pmatrix}
-\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'\\
+    \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}' \\
     \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'
   \end{pmatrix}$ we have,
-
 \begin{flalign*}
   \bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\begin{pmatrix}
-	\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'\\
+    \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}' \\
     \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'
@@
   &\begin{pmatrix}
-\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'\\
+    \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}' \\
     \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'
@@
 \end{flalign*}
-\noindent
 $\bm{f_B}(.)$ gives the joint distribution of $\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}' $, which is a multivariate Gaussian distribution.
-Then from (\ref{4.6}) and the properties of marginalization of multivariate Gaussian distribution it follows,
+Then from \eqref{4.6} and the properties of marginalization of multivariate Gaussian distribution it follows,
 \begin{flalign}\label{ex:2.1}
@@
 
-\noindent
-(\ref{ex:2.1}) implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$ where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
-Then from (\ref{4.7}) it follows that,
+Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$ where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
+Then from \eqref{4.7} it follows that,
 \begin{flalign}
@@
 \end{flalign}
-\noindent
 Therefore, the reconciled Gaussian forecast distribution of the whole hierarchy is\\
@@
 In general, forecasters prefer to maximize the sharpness of the predictive distribution subject to the calibration \citep{Gneiting2014}.
-Therefore the probabilistic forecasts should be evaluated with respect to these two properties.\\
+Therefore the probabilistic forecasts should be evaluated with respect to these two properties.
 
-\noindent
 Calibration refers to the statistical compatibility between probabilistic forecasts and realizations.
@@
 Therefore to assess these properties simultaneously, we use scoring rules.
-\\
 
-\noindent
 Scoring rules are summary measures obtained based on the relationship between predictive distribution and the realizations.
@@
 We consider these negatively oriented scoring rules to evaluate probabilistic forecasts in hierarchical time series.
-\\
 
-\noindent
-Let $\bm{{\breve{Y}}}$ and $\bm{Y}$ be a $n$-dimensional random vectors from the predictive distribution $\mathbold{F}$ and the true distribution $\mathbold{G}$.
-Further let $\mathbold{y}$ be a $n$-dimensional realization.
-Then the scoring rule is a numerical value $S(\mathbold{{\breve{Y}},y})$ assign to each pair $(\mathbold{{\breve{Y}},y})$ and the proper scoring rule is defined as,
+Let $\bm{{\breve{Y}}}$ and $\bm{Y}$ be a $n$-dimensional random vectors from the predictive distribution $\bm{F}$ and the true distribution $\bm{G}$.
+Further let $\bm{y}$ be a $n$-dimensional realization.
+Then the scoring rule is a numerical value $S(\bm{{\breve{Y}},y})$ assign to each pair $(\bm{{\breve{Y}},y})$ and the proper scoring rule is defined as,
 \begin{equation}\label{eq:(3.1.)}
-E_{\mathbold{G}}[S(\mathbold{Y,y})] \le E_{\mathbold{G}}[S(\mathbold{{\breve{Y}},y})],
+  E_{\bm{G}}[S(\bm{Y,y})] \le E_{\bm{G}}[S(\bm{{\breve{Y}},y})],
 \end{equation}
-\noindent
-where $E_{\mathbold{G}}[S(\mathbold{Y,y})]$ is the expected score under the true distribution $\mathbold{G}$ \citep{Gneiting2008, Gneiting2014}. \\
+where $E_{\bm{G}}[S(\bm{Y,y})]$ is the expected score under the true distribution $\bm{G}$ \citep{Gneiting2008, Gneiting2014}.
 
-\noindent
 Following table summarizes few existing proper scoring rules.
 
-\begin{center}
-	\captionof{table}{\textit{Scoring rules to evaluate multivariate forecast densities }}
+\begin{table}
+  \caption{Scoring rules to evaluate multivariate forecast densities.
+$\breve{\bm{y}}_{T+h}$ and $\breve{\bm{y}}^*_{T+h}$ be two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with the density function $\breve{\bm{f}}(.)$ at time $T+h$ and $\bm{y}_{T+h}$ is the vector of realizations.
+Further $\breve{Y}_{T+h,i}$ and $\breve{Y}_{T+h,j}$ are $i$th and $j$th components of the vector $\breve{\bm{Y}}_{T+h}$.
+Further the variogram score is given for order $p$ where, $w_{ij}$ are non-negative weights.}
+  \centering\small\setstretch{1.3}
+    \begin{tabular}{@{}lp{8.1cm}l@{}}
+      \toprule
+      \textbf{Scoring rule}  & \textbf{Expression} & \textbf{Reference}           \\
+      \midrule
+      \text{Log score}       &
+        $\text{LS}(\breve{\bm{F}},\bm{y}_{T+h}) = -\log {\breve{\bm{f}}(\bm{y}_{T+h})}$ &
+        \citet{Gneiting2007}  \\\\[-0.2cm]
+      \text{Energy score}    &
+        $\text{eS}(\bm{\breve{Y}}_{T+h},\bm{y}_{T+h}) =
+          \E_{\breve{\bm{F}}}
+            \|\breve{\bm{Y}}_{T+h}-\bm{y}_{T+h}\|^\alpha -$ \par\hfill
+            $\frac{1}{2}\E_{\breve{\bm{F}}}\|\breve{\bm{Y}}_{T+h}-\breve{\bm{Y}}^*_{T+h}\|^\alpha$, \,\, $\alpha \in (0,2]$ &
+        \citet{Gneiting2008}  \\\\[-0.2cm]
+      \text{Variogram score} &
+        $\text{VS}(\breve{\bm{F}}, \bm{y}_{T+h}) =
+          \sum\limits_{i=1}^{n}
+          \sum\limits_{j=1}^{n}
+          w_{ij}\Big(|y_{T+h,i} - y_{T+h,j}|^p -$ \par\hfill
+          $\E_{\breve{\bm{F}}}|\breve{Y}_{T+h,i}-\breve{Y}_{T+h,j}|^p\Big)^2$     &
+        \citet{SCHEUERER2015} \\
+      \bottomrule
+    \end{tabular}
+\end{table}
 
-	\small
-	\resizebox{\linewidth}{!}{
-
-		\begin{tabular}{ L | L | L}
-			\hline
-			\hline
-			\textbf{Scoring rule} & \textbf{Expression} & \textbf{Reference}\\
-			\\
-			\hline
-			\hline \\
-			\text{Log score} & LS(\breve{\bm{F}},\bm{y}_{T+h}) = -log {\breve{\bm{f}}(\bm{y}_{T+h})} & \text{\citet{Gneiting2007}} \\
-			\\ 
-			\hline \\
-			\text{Energy score} & eS(\bm{\breve{Y}_{T+h},y_{T+h}}) = E_{\breve{\bm{F}}}||\breve{\bm{Y}}_{T+h}-\bm{y}_{T+h}||^\alpha - \frac{1}{2}E_{\breve{\bm{F}}}||\breve{\bm{Y}}_{T+h}-\breve{\bm{Y}}^*_{T+h}||^\alpha, \alpha \in (0,2] & \text{\citet{Gneiting2008}} \\
-			\\
-			\hline
-			\text{Variogram score} & VS(\breve{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - E_{\breve{\bm{F}}}|\breve{Y}_{T+h,i}-\breve{Y}_{T+h,j}|^p\right)^2 & \text{\citet{SCHEUERER2015}} \\
-			\hline
-		\end{tabular}
-
-		}
-\end{center}
-\textit{NOTE: $\bm{\breve{Y}}_{T+h}$ and $\bm{\breve{Y}}^*_{T+h}$ be two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with the density function $\breve{\bm{f}}(.)$ at time $T+h$ and $\bm{y}_{T+h}$ is the vector of realizations.
-Further $\breve{Y}_{T+h,i}$ and $\breve{Y}_{T+h,j}$ are $i^{\text{th}}$ and $j^{\text{th}}$ components of the vector $\breve{\bm{Y}}_{T+h}$.
-Further the variogram score is given for order $p$ where, $w_{ij}$ are non-negative weights.}\\
-
-\noindent
 Even though the log score can be used evaluate simulated forecast densities with large samples \citep{Jordan2017}, it is more convenient to use if it is reasonable to assume a parametric forecast density for the hierarchy.
 However, the \qq{degenerecy} of coherent forecast densities would be problematic when using log scores.
-We will discuss more on this in the next subsection.\\
+We will discuss more on this in the next subsection.
 
-\noindent
 In the energy score, for $\alpha=2$, it can be easily shown that
 \begin{equation} \label{eq:(5.1)}
-eS(\bm{\breve{Y}_{T+h},y_{T+h}}) = ||\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}||^2,
+  eS(\bm{\breve{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
 \end{equation}
-
-\noindent
 where $\breve{\bm{\mu}}_{T+h} =E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $.
@@
 Further \citet{Pinson2013a} argued that the Energy score given in table 1 has a very low discrimination ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
-\\
 
-\noindent
 However, \citet{SCHEUERER2015} have shown that the variogram score has a high discrimination ability of misspecified means, variance and correlation structure than the Energy score.
-Further they suggested the variogram score with $p=0.5$ is more powerful.\\
-\noindent
+Further they suggested the variogram score with $p=0.5$ is more powerful.
+
 For a possible finite sample of size $B$ from the multivariate forecast density $\breve{\bm{F}}$, the variogram score is defined as,
-
 \begin{flalign}
@@
 
-%\noindent
+%
 %where $\bm{\tilde{\mu}}_{T+h}$ and $\bm{\tilde{\Sigma}}_{T+h}$ are the coherent mean and variance-covariance matrix of the predictive Gaussian density and both lies in the linear %subspace spanned by $\mathscr{C}(\bm{S})$.
@@
 The expected log score of $p_1$ is:
-$$E_f[S(f,f)] = E_f[S(p_1,f)] = -ln[p_1(x=0)]=0,$$
-\noindent
+$$
+  E_f[S(f,f)] = E_f[S(p_1,f)] = -ln[p_1(x=0)]=0,
+$$
 and that of $p_2$ is:
-$$E_f[S(p_2,f)] = -ln[p_2(x=0)]<0.$$ 
-\noindent
-Therefore $S(f,f) > S(p_2,f)$ and hence there exist at least one forecast density which breaks the condition (\ref{eq:(3.1.)}) for proper scoring rule.
+$$
+  E_f[S(p_2,f)] = -ln[p_2(x=0)]<0.
+$$
+Therefore $S(f,f) > S(p_2,f)$ and hence there exist at least one forecast density which breaks the condition \eqref{eq:(3.1.)} for proper scoring rule.
 This implies log score cannot be used to evaluate the degenerate densities.
-\\
 
-\noindent
 Thus it is necessary to have a rule of thumb to use these scoring rules in order to evaluate coherent forecast densities.
@@
 This will also avoid the impact of degeneracy for the scoring rules.
-\\
 
-\noindent
 For example, since the bottom level series is a set of basis series for a given hierarchy, we can evaluate the predictive ability of the bottom level series of the coherent forecast distribution instead of evaluating the whole distribution.
@@
 It is also important to assess how the coherent or reconciled forecast densities improve the predictive ability compared to the incoherent forecasts.
-Clearly, we cannot use multivariate scoring rules, even for the basis set of series, since the coherent and incoherent forecast densities lie in two different matrix spaces.\\
+Clearly, we cannot use multivariate scoring rules, even for the basis set of series, since the coherent and incoherent forecast densities lie in two different matrix spaces.
 
-\noindent
 However we could compare individual margins of the forecast density of the hierarchy using univariate proper scoring rules.
 Most widely used Continuous Ranked Probability Score (CRPS) would be helpful for this.
-\\
 \begin{equation} \label{eq:(3.6)}
-CRPS(\breve{F}_i,y_{T+h,i}) = E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|,
+  \text{CRPS}(\breve{F}_i,y_{T+h,i}) = E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|,
 \end{equation}
-
-\noindent
-where $\breve{Y}_{T+h,i}$ and $\breve{Y}^*_{T+h,i}$ are two independent copies from the $i^{\text{th}}$ reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy and $y_{T+h,i}$ is the $i^{\text{th}}$ realization from the true marginal distribution $G_i$.
+where $\breve{Y}_{T+h,i}$ and $\breve{Y}^*_{T+h,i}$ are two independent copies from the $i$th reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy and $y_{T+h,i}$ is the $i$th realization from the true marginal distribution $G_i$.
 We can also use univariate log scores for which we could assume a parametric forecast distribution.
@@
 $\bm{y}_T \sim \mathscr{N}(\bm{\mu}_T, \bm{\Sigma}_T)$ where both $\bm{\mu}_T$ and $\bm{\Sigma}_T$ lives in $\mathscr{C}(\bm{S})$ by nature of the hierarchical time series.
-We are interested in estimating the predictive Gaussian distribution of $\bm{Y}_{T+h}| \bm{\mathcal{I}}_T$ where $\bm{\mathcal{I}}_T= \{\bm{y}_1,\bm{y}_2,....,\bm{y}_T\}$, which should also lives in $\mathscr{C}(\bm{S})$.
-\\
+We are interested in estimating the predictive Gaussian distribution of $\bm{Y}_{T+h}| \bm{\mathcal{I}}_T$ where $\bm{\mathcal{I}}_T= \{\bm{y}_1,\bm{y}_2,\dots.,\bm{y}_T\}$, which should also lives in $\mathscr{C}(\bm{S})$.
 
-\noindent
-Considering the individual series in the hierarchy, it is well known that the optimal point forecasts with respect to the minimal mean square error is given by the $E[Y_{T+h,i}|y_{1,i},...,y_{T,i}],$ $i=1,..,n$.
+Considering the individual series in the hierarchy, it is well known that the optimal point forecasts with respect to the minimal mean square error is given by the $\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}],$ $i=1,\dots,n$.
 Suppose we independently fit time series models for each series in the hierarchy.
-Then the point forecasts from the estimated models, denoted by $\hat{Y}_{T+h,i}$ is unbiased and consistent estimator of $E[Y_{T+h,i}|y_{1,i},...,y_{T,i}]$, given that the parameter estimates of the fitted models are unbiased and asymptotically consistent.
-\\
+Then the point forecasts from the estimated models, denoted by $\hat{Y}_{T+h,i}$ is unbiased and consistent estimator of $\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}]$, given that the parameter estimates of the fitted models are unbiased and asymptotically consistent.
 
-\noindent
-For example, suppose the data from $i^\text{th}$ series follows a $ARMA(p,q)$ model. i.e.,
-$$Y_{t,i}=\alpha_1Y_{t-1,i}+...+\alpha_pY_{t-p,i}+\epsilon_t + \beta_1\epsilon_{t-1,i}+...+\beta_q\epsilon_{t-q,i},$$ where $\epsilon_t \sim iid \mathcal{N}(0, \sigma_i^2)$. Then, 
-$$E[Y_{T+h,i}|y_{1,i},...,y_{T,i}] = \alpha_1Y_{T+h-1,i}+...+\alpha_pY_{T+h-p,i}+ \beta_1\epsilon_{T+h-1,i}+...+\beta_q\epsilon_{T+h-q,i}.$$
+For example, suppose the data from $i$th series follows a ARMA$(p,q)$ model. i.e.,
+$$
+  Y_{t,i}=\alpha_1Y_{t-1,i}+\dots+\alpha_pY_{t-p,i}+\epsilon_t + \beta_1\epsilon_{t-1,i}+\dots+\beta_q\epsilon_{t-q,i},
+$$
+where $\epsilon_t \sim \mathcal{NID}(0, \sigma_i^2)$. Then,
+$$
+  \E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}] = \alpha_1Y_{T+h-1,i}+\dots+\alpha_pY_{T+h-p,i}+ \beta_1\epsilon_{T+h-1,i}+\dots+\beta_q\epsilon_{T+h-q,i}.
+$$
 
-\noindent
-Since $\bm{\alpha} = (\alpha_1,...,\alpha_p)'$ and $\bm{\beta} = (\beta_1,...,\beta_q)'$ are unknown in practice and thus estimated using the maximum likelihood method.
+Since $\bm{\alpha} = (\alpha_1,\dots,\alpha_p)'$ and $\bm{\beta} = (\beta_1,\dots,\beta_q)'$ are unknown in practice and thus estimated using the maximum likelihood method.
 Let $\bm{\hat{\alpha}}$ and $\bm{\hat{\beta}}$ denote the maximum likelihood estimates of $\bm{\alpha}$ and $\bm{\beta}$ respectively.
 \citet{Yao2006} showed that $\bm{\hat{\alpha}}$ and $\bm{\hat{\beta}}$ are asymptotically consistent estimators.
-Thus the point forecasts from this estimated model $Y_{T+h,i}$, will also be a consistent estimator for $E[Y_{T+h,i}|y_{1,i},...,y_{T,i}]$.
+Thus the point forecasts from this estimated model $Y_{T+h,i}$, will also be a consistent estimator for $\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}]$.
 i.e.,
 \begin{flalign} \label{eq:(6.01)}
-Y_{T+h,i} \overset{p}{\to} E[Y_{T+h,i}|y_{1,i},...,y_{T,i}] \quad \text{as} \quad T \to \infty.
+  Y_{T+h,i} \overset{p}{\to} \E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}] \quad \text{as} \quad T \to \infty.
 \end{flalign}
 
-\noindent
-Let $\hat{\bm{Y}}_{T+h}=(\hat{Y}_{T+h,1},...,\hat{Y}_{T+h,n})'$ and (\ref{eq:(6.01)}) holds for all $i=1,...,n$. Then from Slutsky's theorem it follows that, 
+Let $\hat{\bm{Y}}_{T+h}=(\hat{Y}_{T+h,1},\dots,\hat{Y}_{T+h,n})'$ and \eqref{eq:(6.01)} holds for all $i=1,\dots,n$. Then from Slutsky's theorem it follows that,
 \begin{flalign}\label{eq:(6.02)}
-\hat{\bm{Y}}_{T+h} \overset{p}{\to} E[\bm{Y}_{T+h}|\bm{\mathcal{I}}_T] \quad \text{as} \quad T \to \infty.
+  \hat{\bm{Y}}_{T+h} \overset{p}{\to} \E[\bm{Y}_{T+h}|\bm{\mathcal{I}}_T] \quad \text{as} \quad T \to \infty.
 \end{flalign}
-
-\noindent
 Further let the forecast error due to $\hat{\bm{Y}}_{T+h}$ is given by,
@@
 \end{flalign*}
-\noindent
+
 Now consider the variance of $\hat{\bm{e}}_{T+h}$,
-
 \begin{flalign*}
-E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = &  E[(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)- \hat{\bm{Y}}_{T+h})\\ &(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T],\\
-= & E[(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T]\\ \quad & + E[E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
-\quad &+  E[(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
-\quad &+ E[E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T]
+  \E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = &  \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)- \hat{\bm{Y}}_{T+h})\\
+  &(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T],\\
+  = & \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T]\\ \quad & + \E[\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
+  \quad &+  \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
+  \quad &+ \E[\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T]
 \end{flalign*}
 
-\noindent
-From (\ref{eq:(6.02)}) it immediately follows that,
-
+From \eqref{eq:(6.02)} it immediately follows that,
 \begin{flalign*}
-&E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] \overset{p}{\to} E[(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T],
+  &\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] \overset{p}{\to} \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T],
 \end{flalign*}
@@
 \end{flalign}
-\noindent
-It should be noted that, even though $\hat{\bm{Y}}_{T+h}$ and $\bm{W}_{T+h}$ are asymptotically consistent estimators for $E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ and $Var(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ respectively, they are not coherent since they doesn't lie in the coherent subspace.
+
+It should be noted that, even though $\hat{\bm{Y}}_{T+h}$ and $\bm{W}_{T+h}$ are asymptotically consistent estimators for $\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ and $Var(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ respectively, they are not coherent since they doesn't lie in the coherent subspace.
 Thus the Gaussian forecast distribution with mean $\hat{\bm{Y}}_{T+h}$ and variance $\bm{W}_{T+h}$ will be incoherent and we denote it by,
@@
 
-\noindent
-Since our primary objective is to find the coherent forecast density of the hierarchy, we need to reconciled (\ref{eq:(6.03)}).
+Since our primary objective is to find the coherent forecast density of the hierarchy, we need to reconciled \eqref{eq:(6.03)}.
 Recalling from example 2, the reconciled Gaussian predictive distribution is then given by,
@@
 \end{flalign}
-\noindent
-where, $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.\\
+where, $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
 
-\pagebreak
-\noindent
-\textbf{Result 1}: Choosing $\bm{R}'_\bot = \bm{S}'\bm{W}_{T+h}^{-1}$ will ensure at least the mean of the predictive Gaussian distribution is optimally reconciled with respect to the energy score.\\
+\textbf{Result 1}: Choosing $\bm{R}'_\bot = \bm{S}'\bm{W}_{T+h}^{-1}$ will ensure at least the mean of the predictive Gaussian distribution is optimally reconciled with respect to the energy score.
 
-\noindent
 Result 1 can be easily shown as follows.
-From (\ref{eq:(5.1)}) the energy score at the upper limit of $\alpha$ is given by, $||\bm{y}_{T+h}-\bm{SP}\hat{\bm{y}}_{T+h}||^2$.
+From \eqref{eq:(5.1)} the energy score at the upper limit of $\alpha$ is given by, $\|\bm{y}_{T+h}-\bm{SP}\hat{\bm{y}}_{T+h}\|^2$.
 Then the expectation of energy score with respect to the true distribution is equivalent to the trace of mean squared forecast error, i.e.
 $$E_{\bm{G}}[eS(\bm{\tilde{Y}_{T+h},y_{T+h}})]= Tr\{E_{\bm{y}_{T+h}}[(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})'|\mathcal{I}_{T}]\}.$$
-\noindent
+
 From Theorem 1 of \citet{Wickramasuriya2017} it immediately follows that $\bm{P} = (\bm{S}'\bm{W}_{T+h}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}_{T+h}^{-1}$ minimizes the expected energy score constrained on the unbiasedness of reconciled forecasts.
 Thus we have $\bm{R}'_\bot = \bm{S}'\bm{W}_{T+h}^{-1}$.
-\\
 
-\noindent
 It should be noted that $\bm{W}_{T+h}$ can be estimated in different methods which yields different estimation of $\bm{R}'_\bot$. Following table summarizes these methods.
 
-\begin{center}
-	\captionof{table}{\textit{Summarizing different estimates of $\bm{R}'_\bot$} }
+\begin{table}
+  \caption{Summarizing different estimates of $\bm{R}'_\bot$.
+For $n<T$, $\bm{\hat{W}}_{T+1}^{sam}$ is an unbiased and consistent estimator for $\bm{W}_{T+1}$.
+$\bm{\hat{W}}_{T+1}^{shr}$ is a shrinkage estimator which is much suitable for large dimensions.
+$\bm{\hat{W}}_{T+1}^{shr}$ was proposed by \citet{Schafer2005} and also used by \citet{Wickramasuriya2017}, where $\tau = \frac{\sum_{i \ne j}\hat{Var}(\hat{r}_{ij})}{\sum_{i \ne j}\hat{r}_{ij}^2}$, $\hat{r}_{ij}$ is the $ij$th element of sample correlation matrix.
+Further Diag($\bm{A}$) denote the diagonal matrix of $\bm{A}$}
+  \centering\setstretch{1.5}
+    \begin{tabular}{lll}
+      \toprule
+      \textbf{Method} & \textbf{Estimate of $\bm{W}_{h}$} & \textbf{Estimate of $\bm{R}'_\bot$}      \\
+      \midrule
+      OLS             &
+        $\bm{I}$  &
+        $\bm{S}'$  \\
+      MinT(Sample)    &
+        $\bm{\hat{W}}_{T+1}^{sam}$ &
+        $\bm{S}'(\bm{\hat{W}}_{T+1}^{sam})^{-1}$ \\
+      MinT(Shrink)    &
+        $\bm{\hat{W}}_{T+1}^{shr} = \tau\text{Diag}(\bm{\hat{W}}_{T+1}^{sam}) + (1-\tau)\bm{\hat{W}}_{T+1}^{sam}$ &
+        $\bm{S}'(\bm{\hat{W}}_{T+1}^{shr})^{-1}$ \\
+      MinT(WLS)       &
+        $\bm{\hat{W}}_{T+1}^{wls} = \text{Diag}(\bm{\hat{W}}_{T+1}^{shr})$ &
+        $\bm{S}'(\bm{\hat{W}}_{T+1}^{wls})^{-1}$ \\
+      \bottomrule
+    \end{tabular}
+\end{table}
 
-	\resizebox{\linewidth}{!}{
-		\small
-		\small
-		\begin{tabular}{c c c }
-			\hline\hline\\
-			\textbf{Method}& \textbf{Estimate of $\bm{W}_{h}$} & \textbf{Estimate of $\bm{R}'_\bot$} \\  
-			\hline \hline\\
-			OLS & $\bm{I}$ & $\bm{S}'$\\
-			\hline\\
-
-			MinT(Sample) & 	$\bm{\hat{W}}_{T+1}^{sam}$ & $\bm{S}'(\bm{\hat{W}}_{T+1}^{sam})^{-1}$\\
-			& (1-step ahead insample variance covariance matrix) &\\
-			\hline\\
-
-			MinT(Shrink) & $\mathbold{\hat{W}}_{T+1}^{shr} = \tau\text{Diag}(\mathbold{\hat{W}}_{T+1}^{sam}) + (1-\tau)\mathbold{\hat{W}}_{T+1}^{sam}$ & $\bm{S}'(\bm{\hat{W}}_{T+1}^{shr})^{-1}$\\
-			\hline\\
-
-			MinT(WLS) & $\mathbold{\hat{W}}_{T+1}^{wls} = \text{Diag}(\mathbold{\hat{W}}_{T+1}^{shr})$ & 	$\bm{S}'(\bm{\hat{W}}_{T+1}^{wls})^{-1}$\\
-			\hline
-			\hline
-
-		\end{tabular}
-	}
-\end{center}
-\textit{Note: For $n<T$, $\bm{\hat{W}}_{T+1}^{sam}$ is an unbiased and consistent estimator for $\bm{W}_{T+1}$.
-$\mathbold{\hat{W}}_{T+1}^{shr}$ is a shrinkage estimator which is much suitable for large dimensions.
-$\mathbold{\hat{W}}_{T+1}^{shr}$ was proposed by \citet{Schafer2005} and also used by \citet{Wickramasuriya2017}, where $\tau = \frac{\sum_{i \ne j}\hat{Var}(\hat{r}_{ij})}{\sum_{i \ne j}\hat{r}_{ij}^2}$, $\hat{r}_{ij}$ is the $ij$-th element of sample correlation matrix.
-Further Diag($\bm{A}$) denote the diagonal matrix of $\bm{A}$}.\\
-
-\noindent
 It is worth mentioning that all these forecasting methods were well established in the context of point forecast reconciliation \citep{Hyndman2011, Wickramasuriya2017, Hyndman2016}.
 However our attempt is to emphasis the use of these reconciliation methods in the context of probabilistic forecasts at least in the Gaussian framework.
-\\
 
-\noindent
-\textbf{Simulation setup}\\
+\subsubsection*{Simulation setup}
 
-\noindent
 We consider the hierarchy given in figure (1) for this simulation study.
@@
 In order to simulate this feature in the hierarchy, we refer to \citet{Wickramasuriya2017} and the data generating process will be given as follows.
-\\
 
-\noindent
 Suppose $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from $ARIMA(p,d,q)$ processes where, $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability.
@@
 $$y_{BB,t} = w_{BB,t} - u_t + 0.5v_t,$$
-\noindent
 where $u_t \sim N(0,\sigma^2_u)$ and $v_t \sim N(0,\sigma^2_v)$.
 
-\noindent
 To obtain the aggregate series at level 1, we add their respective bottom level series such as:
@@
 $$y_{B,t} = w_{BA,t} + w_{BB,t} + v_t,$$
-\noindent
 and the total series will be obtained as:
 $$y_{Tot,t} = w_{AA,t} + w_{AB,t} + w_{BA,t} + w_{BB,t}.$$
-\noindent
+
 To get less noisier aggregate series than disaggregate series, we choose $\bm{\Sigma}, \sigma^2_u$ and $\sigma^2_v$ such that,
+$$
+  Var(\epsilon_{AA,t}+\epsilon_{AB,t}+\epsilon_{BA,t}+\epsilon_{BB,t}) \le Var(\epsilon_{AA,t}+\epsilon_{AB,t}-v_t) \le Var(\epsilon_{AA,t}+u_t-0.5v_t),
+$$
+$$
+  \bm{l}_1\bm{\Sigma} \bm{l}_1' \le \bm{l}_2\bm{\Sigma} \bm{l}_2' + \sigma^2_v \le  \bm{l}_3\bm{\Sigma} \bm{l}_3' + \sigma^2_u + \frac{1}{4}\sigma^2_v,
+$$
+where $\bm{l}_1 = \begin{pmatrix} 1&1&1&1 \end{pmatrix}, \bm{l}_2 = \begin{pmatrix} 1&1&0&0 \end{pmatrix}$ and $\bm{l}_3 = \begin{pmatrix} 1&0&0&0 \end{pmatrix}$.
 
-$$Var(\epsilon_{AA,t}+\epsilon_{AB,t}+\epsilon_{BA,t}+\epsilon_{BB,t}) \le Var(\epsilon_{AA,t}+\epsilon_{AB,t}-v_t) \le Var(\epsilon_{AA,t}+u_t-0.5v_t),$$
-$$\bm{l}_1\bm{\Sigma} \bm{l}_1' \le \bm{l}_2\bm{\Sigma} \bm{l}_2' + \sigma^2_v \le  \bm{l}_3\bm{\Sigma} \bm{l}_3' + \sigma^2_u + \frac{1}{4}\sigma^2_v,$$
-\noindent
-where $\bm{l}_1 = \begin{pmatrix} 1&1&1&1 \end{pmatrix}, \bm{l}_2 = \begin{pmatrix} 1&1&0&0 \end{pmatrix}$ and $\bm{l}_3 = \begin{pmatrix} 1&0&0&0 \end{pmatrix}$.
-\noindent 
 This follows,
 $$\bm{l}_1\bm{\Sigma} \bm{l}_1' - \bm{l}_2\bm{\Sigma} \bm{l}_2' \le \sigma^2_v \le \frac{4}{3}(\sigma^2_u + \bm{l}_3\bm{\Sigma} \bm{l}_3' - \bm{l}_2\bm{\Sigma} \bm{l}_2').$$
-\noindent
 Thus we choose,
-$\mathbold{\Sigma} =  \begin{pmatrix} 5.0 & 3.1 & 0.6 & 0.4\\
-3.1 & 4.0 & 0.9 & 1.4\\
-0.6 & 0.9 & 2.0 & 1.8\\
-0.4 & 1.4 & 1.8 & 3.0\\
-\end{pmatrix}, \quad \sigma^2_u = 19$ and $\sigma^2_u = 18$ in our simulation setting. \\
+$\bm{\Sigma} =
+  \begin{pmatrix}
+    5.0 & 3.1 & 0.6 & 0.4 \\
+    3.1 & 4.0 & 0.9 & 1.4 \\
+    0.6 & 0.9 & 2.0 & 1.8 \\
+    0.4 & 1.4 & 1.8 & 3.0 \\
+  \end{pmatrix}$,
+$\sigma^2_u = 19$ and $\sigma^2_u = 18$ in our simulation setting.
 
-\noindent
 As such we generate data for the hierarchy with sample size $T=501$.
@@
 This process was then replicated using $1000$ different data sets from the same data generating process.
-\\
 
-\noindent
 To assess the predictive performance of different forecasting methods, we use scoring rules as discussed in section 5.
@@
 \begin{flalign}
-Ss[S_B(.)] = \frac{S_B(\mathbold{{{Y}},y})^{ref} - S_B(\mathbold{{\breve{Y}},y})}{S_B(\mathbold{{{Y}},y})^{ref}}\times 100\%,
+  Ss[S_B(.)] = \frac{S_B(\bm{{{Y}},y})^{ref} - S_B(\bm{{\breve{Y}},y})}{S_B(\bm{{{Y}},y})^{ref}}\times 100\%,
 \end{flalign}
-\noindent
-where $S_B(.)$ is average score over $B$ samples and $S_B(\mathbold{{{Y}},y})^{ref}$ is the average score of the reference forecasting methods.
+where $S_B(.)$ is average score over $B$ samples and $S_B(\bm{{{Y}},y})^{ref}$ is the average score of the reference forecasting methods.
 Thus $Ss[S_B(.)]$ gives the percentage improvement of the preferred forecasting method relative to the reference method.
-Any negative value of $Ss[S_B(.)]$ indicate that the method we compared is poor than the reference method, whereas any positive value indicates that method is superior to the reference method.\\
+Any negative value of $Ss[S_B(.)]$ indicate that the method we compared is poor than the reference method, whereas any positive value indicates that method is superior to the reference method.
 
-\noindent
 As it was mentioned before we wish to establish the importance of reconciliation methods from this simulation study.
@@
 For the former comparison, we use bottom level probabilistic forecasts and calculate the percentage skill score based on energy score, log score and variogram score for each reconciliation method with reference to the bottom up method (presented in Table 3).
-For the latter comparison, we use percentage skill score based on CRPS and univariate log score for coherent probabilistic forecasts of each individual series with reference to incoherent forecasts (presented in Table 4 and 5).\\
+For the latter comparison, we use percentage skill score based on CRPS and univariate log score for coherent probabilistic forecasts of each individual series with reference to incoherent forecasts (presented in Table 4 and 5).
 
-\noindent
 It is clearly evident from the results in table 3 that the multivariate reconciled forecasts for the bottom level series from MinT(Shrink) and MinT(Sample) outperform the bottom-up forecasts.
@@
 
-\begin{center}
-	\captionof{table}{\textit{Comparison of incoherent forecasts using bottom level series} }
+\begin{table}
+  \caption{Comparison of incoherent forecasts using bottom level series.
+The ``Skill score'' columns give the percentage skill score with reference to the bottom up forecasting method.
+A positive entry in these columns shows the percentage increase of score for different reconciliation methods with relative to the bottom up method.}
+  \centering\small
+  \begin{tabular}{@{}lSSSSSS@{}}
+    \toprule
+    Forecasting &
+    \multicolumn{2}{c}{\text{Energy score}} &
+    \multicolumn{2}{c}{\text{Log score}} &
+    \multicolumn{2}{c}{\text{Variogram score}} \\
+    \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(l){6-7}
+    method &
+    \text{Mean score} & \text{Skill score} &
+    \text{Mean score} & \text{Skill score} &
+    \text{Mean score} & \text{Skill score}\\
+    \midrule
+    MinT(Shrink) &  7.47 &  10.11 &  11.34 &     6.44 & 3.05 &   4.69 \\
+    MinT(Sample) &  7.47 &  10.11 &  11.33 &     6.52 & 3.05 &   4.69 \\
+    MinT(WLS)    &  7.91 &   4.81 &  12.64 &    -4.29 & 3.23 &  -0.94 \\
+    OLS          & 10.14 & -22.02 & 135.13 & -1014.93 & 4.60 & -43.75 \\
+    Bottom up    &  8.31 &        &  12.12 &          & 3.20 &        \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
-	\resizebox{\linewidth}{!}{
-		\small
-		\scriptsize
-		\begin{tabular}{@{}l S[table-format=2.2] S[table-format=2.2]  S[table-format=2.2] S[table-format=2.2] S[table-format=2.2]  S[table-format=2.2] @{}}
+\begin{table}
+  \caption{Comparison of incoherent vs.
+coherent forecasts for the aggregate series using Skill score.
+"Incoherent" row represent the average score for incoherent forecasts.
+Each entry above this row represent the percentage skill score with reference to the incoherent forecasts.
+A positive(negative) entry shows the percentage increase(decrease) of score for different forecasting methods with relative to incoherent forecasts.}
+  \centering\small
+  \begin{tabular}{@{}lSSSSSS@{}}
+    \toprule
+    Forecasting &
+      \multicolumn{2}{c}{\text{Total}} &
+      \multicolumn{2}{c}{\text{Series - A}} &
+      \multicolumn{2}{c}{\text{Series - B}} \\
+    \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(l){6-7}
+    method      &  CRPS   & LogS    & CRPS   & LogS     & CRPS   & LogS     \\
+    \midrule
+    MinT(Shrink) & 1.12   & 0.34    & 10.07  & 2.93     & 5.41   & 1.52     \\
+    MinT(Sample) & 1.12   & 0.34    & 10.07  & 2.93     & 5.41   & 1.52     \\
+    MinT(WLS)    & -2.61  & -2.02   & 5.28   & -4.40    & 2.70   & -4.24    \\
+    OLS          & -38.06 & -698.99 & -24.70 & -1368.33 & -24.86 & -1159.09 \\
+    Bottom up    & -89.55 & -21.83  & -8.87  & -2.35    & -9.46  & -2.73    \\
+    \midrule
+    \textit{Incoherent} & $\mathbi{2.68}$ & $\mathbi{2.97}$ & $\mathbi{4.17}$ & $\mathbi{3.41}$ & $\mathbi{3.70}$ & $\mathbi{3.30}$ \\
+    \bottomrule
+  \end{tabular}
+\end{table}
 
-			\hline
-			\hline
+\begin{table}
+  \caption{Comparison of incoherent vs. coherent forecasts for the individual bottom level series using Skill score.}
+  \centering\tabcolsep=0.08cm\small
+    \begin{tabular}{@{}lSSSSSSSS@{}}
+      \toprule
+      Forecasting &
+        \multicolumn{2}{c}{\text{Series - AA}} &
+        \multicolumn{2}{c}{\text{Series - AB}} &
+        \multicolumn{2}{c}{\text{Series - BA}} &
+        \multicolumn{2}{c}{\text{Series - BB}} \\
+      \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(l){8-9}
+      method       & CRPS   & LogS    & CRPS   & LogS    & CRPS   & LogS    & CRPS   & LogS \\
+      \midrule
+      MinT(Shrink) & 8.71   & 2.71    & 10.57  & 3.04    & 5.95   & 1.86    & 7.91   & 2.46 \\
+      MinT(Sample) & 8.71   & 2.71    & 10.57  & 3.04    & 5.95   & 1.86    & 8.19   & 2.46 \\
+      MinT(WLS)    & 5.54   & 0.30    & 5.96   & 0.30    & 2.43   & -0.62   & 5.08   & 0.62 \\
+      OLS          & -22.43 & -931.63 & -22.49 & -886.32 & -26.01 & -834.67 & -23.45 & -812.92 \\
+      \midrule
+      \textit{Incoherent} & $\mathbi{3.79}$ & $\mathbi{3.32}$ & $\mathbi{3.69}$ & $\mathbi{3.29}$ & $\mathbi{3.46}$ & $\mathbi{3.23}$ & $\mathbi{3.54}$ & $\mathbi{3.25}$ \\
+      \bottomrule
+    \end{tabular}
+\end{table}
 
-			\multirow{2}{*}{\text{Forecasting method}} & \multicolumn{2}{ c }{\text{Energy score}} & \multicolumn{2}{c}{\text{Log score}} & \multicolumn{2}{c}{\text{Variogram score}} \\ 
-			\cline{2-7} & \text{Mean score} &  \text{Skill score (\%)} &   \text{Mean score} &   \text{Skill score (\%)} &   \text{Mean score} &   \text{Skill score (\%)}\\
-			\hline
-			\hline
-
-			MinT(Shrink) & 7.47	& 10.11 & 11.34 & 6.44 & 3.05 &	4.69  \\
-
-			MinT(Sample) & 7.47 & 10.11 & 11.33 & 6.52 & 3.05 &	4.69  \\
-
-			MinT(WLS) & 7.91 &	4.81 & 12.64 & -4.29 & 3.23 & -0.94  \\
-
-			OLS & 10.14 & -22.02 & 135.13 &	-1014.93 & 4.6 & -43.75  \\
-
-			Bottom up & 8.31 &	& 12.12 & &	3.2	 \\
-
-			\hline
-			\hline
-
-		\end{tabular}
-	}
-\end{center}
-\textit{Note: Each entry corresponds to the column "Skill score ($\%$)" under the given scoring rule represent the percentage skill score with reference to the bottom up forecasting method.
-A positive(negative) entry in these columns shows the percentage increase(decrease) of score for different reconciliation methods with relative to the bottom up method}.\\\\
-
-\pagebreak
-\begin{center}
-	\captionof{table}{\textit{Comparison of incoherent vs. coherent forecasts for the aggregate series using Skill score}}
-
-	\resizebox{\linewidth}{!}{
-	\scriptsize	
-		\begin{tabular}{@{}l S[table-format=5.5] S[table-format=5.5]  S[table-format=5.5] S[table-format=5.5] S[table-format=5.5]  S[table-format=5.5]  @{}}
-
-		\hline
-		\hline
-
-		\multirow{2}{*}{\text{Forecasting method}} & \multicolumn{2}{ c }{\text{Total}} & \multicolumn{2}{c}{\text{Series - A}} & \multicolumn{2}{c}{\text{Series - B}} \\ 
-		\cline{2-7} &  CRPS &  LogS &   CRPS &   LogS &   CRPS &   LogS \\ 
-		\hline
-		\hline
-
-		MinT(Shrink) & 1.12 & 0.34 & 10.07 & 2.93 &	5.41 & 1.52 \\
-
-		MinT(Sample) & 1.12 & 0.34 & 10.07 & 2.93 &	5.41 & 1.52	\\
-
-		MinT(WLS) & -2.61 &	-2.02 &	5.28 & -4.40 & 2.70 & -4.24 \\
-
-		OLS & -38.06 & -698.99 & -24.70 & -1368.33 & -24.86 & -1159.09 \\
-
-		Bottom up & -89.55 & -21.83 & -8.87 & -2.35 & -9.46 & -2.73	 \\
-
-		\hline
-
-		\textit{Incoherent} & $\mathbi{2.68}$ & $\mathbi{2.97}$	& $\mathbi{4.17}$  & $\mathbi{3.41}$ & $\mathbi{3.70}$ & $\mathbi{3.30}$ \\
-
-		\hline
-		\hline
-
-	\end{tabular}
-	}
-\end{center}
-\textit{Note: "Incoherent" row represent the average score for incoherent forecasts.
-Each entry above this row represent the percentage skill score with reference to the incoherent forecasts.
-A positive(negative) entry shows the percentage increase(decrease) of score for different forecasting methods with relative to incoherent forecasts}.\\
-
-\begin{center}
-	\captionof{table}{\textit{Comparison of incoherent vs. coherent forecasts for the individual bottom level series using Skill score}}
-
-	\resizebox{\linewidth}{!}{
-		\scriptsize	
-		\begin{tabular}{@{}l S[table-format=4.4] S[table-format=4.4]  S[table-format=4.4] S[table-format=4.4] S[table-format=4.4]  S[table-format=4.4] S[table-format=4.4] S[table-format=4.4] @{}}
-
-			\hline
-			\hline
-
-			\multirow{2}{*}{\text{Forecasting method}} & \multicolumn{2}{c}{\text{Series - AA}} & \multicolumn{2}{c}{\text{Series - AB}}& \multicolumn{2}{c}{\text{Series - BA}} & \multicolumn{2}{c}{\text{Series - BB}} \\
-			\cline{2-9} & CRPS &  LogS & CRPS &  LogS & CRPS &  LogS & CRPS & LogS \\ 
-			\hline
-			\hline
-
-			MinT(Shrink) & 8.71 & 2.71 & 10.57 & 3.04 &	5.95 & 1.86 & 7.91 & 2.46 \\
-
-			MinT(Sample) & 8.71 & 2.71 & 10.57 & 3.04 &	5.95 & 1.86 & 8.19 & 2.46 \\
-
-			MinT(WLS) & 5.54 & 0.30 & 5.96 & 0.30 &	2.43 & -0.62 & 5.08 & 0.62  \\
-
-			OLS  & -22.43 &	-931.63 & -22.49 & -886.32 & -26.01 & -834.67 &	-23.45 & -812.92 \\
-
-			\hline
-
-			\textit{Incoherent} & $\mathbi{3.79}$ & $\mathbi{3.32}$	& $\mathbi{3.69}$  & $\mathbi{3.29}$ & $\mathbi{3.46}$ & $\mathbi{3.23}$ & $\mathbi{3.54}$ &	$\mathbi{3.25}$  \\
-
-			\hline
-			\hline
-
-		\end{tabular}
-	}
-\end{center}
-
-\section{Conclusions.}
+\section{Conclusions}
 
@@
 Due to the aggregation nature of hierarchy, the probability density is a degenerate density.
-Thus the forecast distribution that we opt to find should also lie in a lower dimensional subspace of $\bm{\mathbb{R}}^{n}$.\\
+Thus the forecast distribution that we opt to find should also lie in a lower dimensional subspace of $\mathbb{R}^{n}$.
 
-\noindent
 As it was well established that the reconciliation outperforms other conventional point forecasting methods in the hierarchical literature, we proposed to use reconciliation in probabilistic forecasting as well to obtain coherent degenerate densities.
-We provided a distinct definition for density forecast reconciliation and how it can be used to reconcile incoherent densities in practice.\\
+We provided a distinct definition for density forecast reconciliation and how it can be used to reconcile incoherent densities in practice.
 
-\noindent
 Assuming a multivariate Gaussian distribution for the hierarchy, we showed how to obtain reconciled Gaussian forecast densities, utilizing available information in the hierarchy.

### 2018-02-18 ProbabilisticCoherence.tex
Renamed files to avoid spaces

--- 2018-02-18 Probabilistic forecasts in hierarchical time series.tex
@@
 
-\section{Introduction}
+\section{Introduction}\label{sec:intro}
 
@@
 Rest of the paper is structured as follows.
-We start with introducing the notations in section 2.
-In section 3 we provide our definitions for coherency which is followed by the definitions for forecast reconciliation in section 4.
-Section 5 discusses the methods that can be used for evaluation of probabilistic hierarchical forecasts.
-Section 6 consists the theoretical results followed by the simulation study on probabilistic forecast reconciliation in the Gaussian framework and we enclose with the remarkable conclusions in section 7.
+We start with introducing the notations in Section \ref{sec:notation}.
+In Section \ref{sec:definitions} we provide our definitions for coherency which is followed by the definitions for forecast reconciliation in Section \ref{sec:reconciliation}.
+Section \ref{sec:evaluation} discusses the methods that can be used for evaluation of probabilistic hierarchical forecasts.
+Section \ref{sec:gaussian} consists the theoretical results followed by the simulation study on probabilistic forecast reconciliation in the Gaussian framework and we enclose with the remarkable conclusions in Section \ref{sec:conclusions}.
 
-\section{Notations}
+\section{Notations}\label{sec:notation}
 
@@
 Then
-$\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, \\
+$\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$,
 $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and
@@
 
-\section{Coherent forecasts}
+\section{Coherent forecasts}\label{sec:definitions}
 
@@
 Let $(\mathbb{R}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability measure space where $\mathscr{F}^m$ is a sigma algebra on $\mathbb{R}^m$.
-$\breve{\nu}(.)$ on the measurable space $(\mathscr{C}(\bm{S}), \mathscr{F}_{\bm{S}})$ is said to be coherent probability measure iff $$\breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall \quad \bm{A} \in \mathscr{F}^m,$$ where $\bm{S}(\bm{A})$ denotes the image of subset $\bm{A}$ under $\bm{S}$.
+$\breve{\nu}(.)$ on the measurable space $(\mathscr{C}(\bm{S}), \mathscr{F}_{\bm{S}})$ is said to be coherent probability measure iff
+$$
+  \breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall \quad \bm{A} \in \mathscr{F}^m,
+$$
+where $\bm{S}(\bm{A})$ denotes the image of subset $\bm{A}$ under $\bm{S}$.
 \end{definition}
@@
 
-\section{Forecast reconciliation}
+\section{Forecast reconciliation}\label{sec:reconciliation}
 
@@
 Then from basic properties of linear algebra it follows that,
-\begin{flalign}\label{4.1}
+\[
   \begin{pmatrix}
@@
   = \hat{\bm{y}}_{t+h},
-\end{flalign}
-\begin{flalign}\label{4.2}
+\]
+\[
   \hat{\bm{y}}_{t+h} = \bm{S}\tilde{\bm{b}}_{t+h} +  \bm{R}\tilde{\bm{t}}_{t+h},
-\end{flalign}
+\]
 and
-\begin{flalign}\label{4.3}
+\begin{equation}\label{4.3}
   \begin{pmatrix}
@@
    \hat{\bm{y}}_{t+h}.
-\end{flalign}
+\end{equation}
 
-In order to find $(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1}$, let $\bm{S}_{\bot}$ and $\bm{R}_{\bot}$ be the orthogonal complements of $\bm{S}$ and $\bm{R}$
-respectively. Then $(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1}$ is given by,
-\begin{flalign}
+In order to find $\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}$, let $\bm{S}_{\bot}$ and $\bm{R}_{\bot}$ be the orthogonal complements of $\bm{S}$ and $\bm{R}$
+respectively. Then $\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}$ is given by,
+\begin{equation}
   \begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
@@
   \end{pmatrix}.
-\end{flalign}
+\end{equation}
 Thus we have,
-\begin{flalign} \label{4.4}
+\begin{equation} \label{4.4}
   \begin{pmatrix}
@@
   \end{pmatrix}\hat{\bm{y}}_{t+h}.
-\end{flalign}
+\end{equation}
 
 From \eqref{4.4} it follows that,
-\begin{flalign}
+\begin{equation}
   \tilde{\bm{b}}_{t+h}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}
-\end{flalign}
+\end{equation}
 
@@
 Thus we have,
-\begin{flalign}
+\begin{equation}
   \tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})<\mathbb{R}^n.
-\end{flalign}
+\end{equation}
 
@@
 Notice that, if the mapping $\bm{g}$ in definition 4.1 is considered to be linear we have,
-\begin{flalign}
+\begin{equation}
   \bm{g}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot.
-\end{flalign}
+\end{equation}
 
@@
 In their study, \citet{Hyndman2011} proposed to choose,
-\begin{flalign*}
+\begin{equation*}
   \tilde{\bm{b}}^{OLS}_{t+h}=(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h},
-\end{flalign*}
+\end{equation*}
 where in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy is given by,
-\begin{flalign}
+\begin{equation}
   \tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h}.
-\end{flalign}
+\end{equation}
 They referred this to as OLS solution and the loss function they considered is equivalent to the euclidean norm between $\hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h}$, i.e.
@@
 This will result,
-\begin{flalign*}
+\begin{equation*}
   \tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}'\bm{W}^{-1}_{h} \bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h},
-\end{flalign*}
+\end{equation*}
 and thus,
-\begin{flalign}
+\begin{equation}
   \tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}' \bm{W}^{-1}_{h}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h}.
-\end{flalign}
+\end{equation}
 
@@
 Then the probability measure on reconciled bottom levels is such that,
-\begin{flalign}
+\begin{equation}
   \nu^m(\bm{A}) = \hat{\nu}(\bm{g}^{-1}(\bm{A})), \quad \forall \quad \bm{A} \in \mathscr{F}^m.
-\end{flalign}
+\end{equation}
 
 Further the reconciled probability measure of the whole hierarchy is given by,
-\begin{flalign}
+\begin{equation}
   \tilde{\nu}(\bm{S}(\bm{A})) = \hat{\nu}(\bm{g}^{-1}(\bm{A})), \quad \forall \quad \bm{A} \in \mathscr{F}^m,
-\end{flalign}
+\end{equation}
 where $\bm{S}:\mathbb{R}^m \rightarrow \mathbb{R}^n$ and $\tilde{\nu}(.)$ is the probability measure on the measure space $(\mathscr{C}(\bm{S}), \mathscr{F}_S)$.
@@
 Let the density of coordinates of $\hat{\bm{y}}_{t+h}$ with respect to basis $\bm{B}$ is denoted by $\bm{f_B}(.)$. Then it follows from  \eqref{4.3} and the facts on density of transformed variables,
-\begin{flalign}\label{4.5}
+\begin{equation}\label{4.5}
   \bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad \Big|\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array}\Big|,
-\end{flalign}
+\end{equation}
 where $|.|$ denote the determinant of a matrix.
@@
 i.e.,
-\begin{flalign}\label{4.6}
+\begin{equation}\label{4.6}
   \tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\int_{lim(\tilde{\bm{t}}_{t+h})}\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad \Big|\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array}\Big| \quad d\tilde{\bm{t}}_{t+h}.
-\end{flalign}
+\end{equation}
 
 Finally to get the reconciled density of the whole hierarchy, we simply follow the definition $3.2$ and have,
-\begin{flalign}\label{4.7}
+\begin{equation}\label{4.7}
   \tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\bm{S}\circ \tilde{\bm{f}}(\tilde{\bm{b}}_{t+h}).
-\end{flalign}
+\end{equation}
 This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the $\mathscr{C}(\bm{S})<\mathbb{R}^n$.
@@
 Then from \eqref{4.5} it follows,
-\begin{flalign*}
+\begin{equation*}
   \bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad \Big|\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array}\Big| = \frac{\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) }{\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|}.
-\end{flalign*}
+\end{equation*}
 By substituting the Gaussian distribution function to $\bm{f_B}(.)$ we get,
-\begin{flalign*}
-  \bm{f_B}(.)&=\frac{\exp\left\{-\frac{1}{2}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})' \bm{\hat{\Sigma}_{t+h}}^{-1}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
-  &= \frac{\exp\left\{-\frac{1}{2}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)' \bm{\hat{\Sigma}_{t+h}}^{-1}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},
-\end{flalign*}
-\begin{flalign*}
-  \bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|}
-  \exp \Big\{&-\frac{1}{2}\Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big)'\\
-  &\Big[\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}'\Big]^{-1}\\
-  &\Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.
-\end{flalign*}
-Recall that, $$\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
-    (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
-  \end{pmatrix} = \begin{pmatrix}
+\begin{align*}
+  \bm{f_B}(.)
+  & =
+    \frac{\exp\left\{-\frac{1}{2}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})' \bm{\hat{\Sigma}_{t+h}}^{-1}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
+  & =
+    \frac{\exp\left\{-\frac{1}{2}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)' \bm{\hat{\Sigma}_{t+h}}^{-1}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
+  & =
+    \frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|}
+  \exp \Big\{-\frac{1}{2}\Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big)'\\
+  & \hspace*{1cm} \Big[\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}'\Big]^{-1}
+  \ Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.
+\end{align*}
+Recall that,
+$$
+  \begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} =
+  \begin{pmatrix}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot \end{pmatrix} =
+  \begin{pmatrix}
     \bm{P} \\\bm{Q}
-  \end{pmatrix},$$ where, $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ and $\bm{Q}=(\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot$. Then,
-\begin{flalign*}
+  \end{pmatrix},
+$$
+where, $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ and $\bm{Q}=(\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot$. Then,
+\begin{align*}
   \bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix} \Big|}
@@
   &\Big[\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\mu}}_{t+h}\Big] \Big\},
-\end{flalign*}
-\begin{flalign*}
+\end{align*}
+\begin{align*}
   \bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}'\Big|^{\frac{1}{2}}}
@@
   & \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix} \Big\}.
-\end{flalign*}
+\end{align*}
 Since, $\Big[\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}'\Big] = \begin{pmatrix}
@@
   \end{pmatrix}$ we have,
-\begin{flalign*}
+\begin{align*}
   \bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\begin{pmatrix}
@@
   &\begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix} \Big\}.
-\end{flalign*}
+\end{align*}
 $\bm{f_B}(.)$ gives the joint distribution of $\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}' $, which is a multivariate Gaussian distribution.
 Then from \eqref{4.6} and the properties of marginalization of multivariate Gaussian distribution it follows,
-\begin{flalign}\label{ex:2.1}
+\begin{equation}\label{ex:2.1}
   \tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}'\Big|^{\frac{1}{2}}}
   \exp \Big\{-\frac{1}{2} (\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h})' (\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}')^{-1}(\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}) \Big\}.
-\end{flalign}
+\end{equation}
 
@@
 Then from \eqref{4.7} it follows that,
-\begin{flalign}
+\begin{equation}
   \tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
-\end{flalign}
+\end{equation}
 Therefore, the reconciled Gaussian forecast distribution of the whole hierarchy is\\
@@
 
-\section{Evaluation of hierarchical probabilistic forecasts}
+\section{Evaluation of hierarchical probabilistic forecasts}\label{sec:evaluation}
 
@@
 
-Let $\bm{{\breve{Y}}}$ and $\bm{Y}$ be a $n$-dimensional random vectors from the predictive distribution $\bm{F}$ and the true distribution $\bm{G}$.
+Let $\bm{\breve{Y}}$ and $\bm{Y}$ be a $n$-dimensional random vectors from the predictive distribution $\bm{F}$ and the true distribution $\bm{G}$.
 Further let $\bm{y}$ be a $n$-dimensional realization.
-Then the scoring rule is a numerical value $S(\bm{{\breve{Y}},y})$ assign to each pair $(\bm{{\breve{Y}},y})$ and the proper scoring rule is defined as,
+Then the scoring rule is a numerical value $S(\bm{\breve{Y}},\bm{y})$ assign to each pair $(\bm{\breve{Y}},\bm{y})$ and the proper scoring rule is defined as,
 \begin{equation}\label{eq:(3.1.)}
-  E_{\bm{G}}[S(\bm{Y,y})] \le E_{\bm{G}}[S(\bm{{\breve{Y}},y})],
+  \E_{\bm{G}}[S(\bm{Y},\bm{y})] \le \E_{\bm{G}}[S(\bm{\breve{Y}},\bm{y})],
 \end{equation}
-where $E_{\bm{G}}[S(\bm{Y,y})]$ is the expected score under the true distribution $\bm{G}$ \citep{Gneiting2008, Gneiting2014}.
+where $\E_{\bm{G}}[S(\bm{Y,y})]$ is the expected score under the true distribution $\bm{G}$ \citep{Gneiting2008, Gneiting2014}.
 
-Following table summarizes few existing proper scoring rules.
+Table \ref{table:scoringrules} summarizes few existing proper scoring rules.
 
-\begin{table}
+\begin{table}[!b]
   \caption{Scoring rules to evaluate multivariate forecast densities.
@@
 Further $\breve{Y}_{T+h,i}$ and $\breve{Y}_{T+h,j}$ are $i$th and $j$th components of the vector $\breve{\bm{Y}}_{T+h}$.
-Further the variogram score is given for order $p$ where, $w_{ij}$ are non-negative weights.}
+Further the variogram score is given for order $p$ where, $w_{ij}$ are non-negative weights.}\label{table:scoringrules}
   \centering\small\setstretch{1.3}
@@
 \begin{equation} \label{eq:(5.1)}
-  eS(\bm{\breve{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
+  \text{eS}(\bm{\breve{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
 \end{equation}
-where $\breve{\bm{\mu}}_{T+h} =E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $.
+where $\breve{\bm{\mu}}_{T+h} =\E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $.
 Therefore in the limiting case, the energy score only measures the accuracy of the forecast mean, but not the entire distribution.
-Further \citet{Pinson2013a} argued that the Energy score given in table 1 has a very low discrimination ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
+Further \citet{Pinson2013a} argued that the Energy score given in Table \ref{table:scoringrules} has a very low discrimination ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
 
@@
 For a possible finite sample of size $B$ from the multivariate forecast density $\breve{\bm{F}}$, the variogram score is defined as,
-\begin{flalign}
-  VS(\breve{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - \frac{1}{m} \displaystyle\sum_{k=1}^{B} |\breve{Y}^k_{T+h,i}-\breve{Y}^k_{T+h,j}|^p\right)^2.
-\end{flalign}
+\begin{equation}
+  \text{VS}(\breve{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - \frac{1}{m} \displaystyle\sum_{k=1}^{B} |\breve{Y}^k_{T+h,i}-\breve{Y}^k_{T+h,j}|^p\right)^2.
+\end{equation}
 
@@
 $$
-  E_f[S(f,f)] = E_f[S(p_1,f)] = -ln[p_1(x=0)]=0,
+  \E_f[S(f,f)] = \E_f[S(p_1,f)] = -\log[p_1(x=0)]=0,
 $$
@@
 $$
-  E_f[S(p_2,f)] = -ln[p_2(x=0)]<0.
+  \E_f[S(p_2,f)] = -\log[p_2(x=0)]<0.
 $$
@@
 \begin{equation} \label{eq:(3.6)}
-  \text{CRPS}(\breve{F}_i,y_{T+h,i}) = E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|,
+  \text{CRPS}(\breve{F}_i,y_{T+h,i}) = \E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}\E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|,
 \end{equation}
@@
 
-\section{Probabilistic forecast reconciliation in the Gaussian framework}
+\section{Probabilistic forecast reconciliation in the Gaussian framework}\label{sec:gaussian}
 
@@
 i.e.,
-\begin{flalign} \label{eq:(6.01)}
+\begin{equation} \label{eq:(6.01)}
   Y_{T+h,i} \overset{p}{\to} \E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}] \quad \text{as} \quad T \to \infty.
-\end{flalign}
+\end{equation}
 
 Let $\hat{\bm{Y}}_{T+h}=(\hat{Y}_{T+h,1},\dots,\hat{Y}_{T+h,n})'$ and \eqref{eq:(6.01)} holds for all $i=1,\dots,n$. Then from Slutsky's theorem it follows that,
-\begin{flalign}\label{eq:(6.02)}
+\begin{equation}\label{eq:(6.02)}
   \hat{\bm{Y}}_{T+h} \overset{p}{\to} \E[\bm{Y}_{T+h}|\bm{\mathcal{I}}_T] \quad \text{as} \quad T \to \infty.
-\end{flalign}
+\end{equation}
 Further let the forecast error due to $\hat{\bm{Y}}_{T+h}$ is given by,
-\begin{flalign*}
+\begin{equation*}
   \hat{\bm{e}}_{T+h} = \bm{Y}_{T+h}-\hat{\bm{Y}}_{T+h}, \quad \hat{\bm{e}} \sim \bm{\mathcal{N}}(0, \bm{W}_{T+h}).
-\end{flalign*}
+\end{equation*}
 
 Now consider the variance of $\hat{\bm{e}}_{T+h}$,
-\begin{flalign*}
-  \E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = &  \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)- \hat{\bm{Y}}_{T+h})\\
-  &(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T],\\
-  = & \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T]\\ \quad & + \E[\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
-  \quad &+  \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
-  \quad &+ \E[\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T]
-\end{flalign*}
+\begin{align*}
+  \E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = &
+    \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)- \hat{\bm{Y}}_{T+h})\\
+  & \quad
+    (\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T],\\
+  = &
+    \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T]\\
+   & \quad
+    + \E[\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
+   & \quad
+    +  \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
+   &  \quad
+    + \E[\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T]
+\end{align*}
 
 From \eqref{eq:(6.02)} it immediately follows that,
-\begin{flalign*}
+\begin{align*}
   &\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] \overset{p}{\to} \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T],
-\end{flalign*}
-\begin{flalign}
-  \bm{W}_{T+h} \overset{p}{\to} Var(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) \quad \text{as} \quad T \to \infty.
-\end{flalign}
+\end{align*}
+\begin{equation}
+  \bm{W}_{T+h} \overset{p}{\to} \text{Var}(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) \quad \text{as} \quad T \to \infty.
+\end{equation}
 
-It should be noted that, even though $\hat{\bm{Y}}_{T+h}$ and $\bm{W}_{T+h}$ are asymptotically consistent estimators for $\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ and $Var(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ respectively, they are not coherent since they doesn't lie in the coherent subspace.
+It should be noted that, even though $\hat{\bm{Y}}_{T+h}$ and $\bm{W}_{T+h}$ are asymptotically consistent estimators for $\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ and $\text{Var}(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ respectively, they are not coherent since they doesn't lie in the coherent subspace.
 Thus the Gaussian forecast distribution with mean $\hat{\bm{Y}}_{T+h}$ and variance $\bm{W}_{T+h}$ will be incoherent and we denote it by,
-\begin{flalign}\label{eq:(6.03)}
+\begin{equation}\label{eq:(6.03)}
   \widehat{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathscr{N}(\hat{\bm{Y}}_{T+h}, \bm{W}_{T+h})
-\end{flalign}
+\end{equation}
 
@@
 Recalling from example 2, the reconciled Gaussian predictive distribution is then given by,
-\begin{flalign}\label{eq:(6.04)}
+\begin{equation}\label{eq:(6.04)}
   \widetilde{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathscr{N}(\bm{SP}\hat{\bm{Y}}_{T+h}, \bm{SP}\bm{W}_{T+h}\bm{P}'\bm{S}')
-\end{flalign}
+\end{equation}
 where, $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
@@
 Then the expectation of energy score with respect to the true distribution is equivalent to the trace of mean squared forecast error, i.e.
-$$E_{\bm{G}}[eS(\bm{\tilde{Y}_{T+h},y_{T+h}})]= Tr\{E_{\bm{y}_{T+h}}[(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})'|\mathcal{I}_{T}]\}.$$
+$$
+  \E_{\bm{G}}[eS(\bm{\tilde{Y}_{T+h},y_{T+h}})]= \text{Tr}\{\E_{\bm{y}_{T+h}}[(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})'|\mathcal{I}_{T}]\}.
+$$
 
@@
 
-It should be noted that $\bm{W}_{T+h}$ can be estimated in different methods which yields different estimation of $\bm{R}'_\bot$. Following table summarizes these methods.
+It should be noted that $\bm{W}_{T+h}$ can be estimated in different methods which yields different estimation of $\bm{R}'_\bot$. Table \ref{table:2} summarizes these methods.
 
@@
 $\bm{\hat{W}}_{T+1}^{shr}$ is a shrinkage estimator which is much suitable for large dimensions.
-$\bm{\hat{W}}_{T+1}^{shr}$ was proposed by \citet{Schafer2005} and also used by \citet{Wickramasuriya2017}, where $\tau = \frac{\sum_{i \ne j}\hat{Var}(\hat{r}_{ij})}{\sum_{i \ne j}\hat{r}_{ij}^2}$, $\hat{r}_{ij}$ is the $ij$th element of sample correlation matrix.
-Further Diag($\bm{A}$) denote the diagonal matrix of $\bm{A}$}
+$\bm{\hat{W}}_{T+1}^{shr}$ was proposed by \citet{Schafer2005} and also used by \citet{Wickramasuriya2017}, where $\tau = \frac{\sum_{i \ne j}\hat{\text{Var}}(\hat{r}_{ij})}{\sum_{i \ne j}\hat{r}_{ij}^2}$, $\hat{r}_{ij}$ is the $ij$th element of sample correlation matrix.
+Further Diag($\bm{A}$) denote the diagonal matrix of $\bm{A}$}\label{table:2}
   \centering\setstretch{1.5}
@@
 Then the bottom level series $\{y_{AA,t},y_{AB,t},y_{BA,t},y_{BB,t}\}$ will be obtained as:
-$$y_{AA,t} = w_{AA,t} + u_t - 0.5v_t,$$
-$$y_{AB,t} = w_{AB,t} - u_t - 0.5v_t,$$
-$$y_{BA,t} = w_{BA,t} + u_t + 0.5v_t,$$
-$$y_{BB,t} = w_{BB,t} - u_t + 0.5v_t,$$
+\begin{align*}
+y_{AA,t} &= w_{AA,t} + u_t - 0.5v_t,\\
+y_{AB,t} &= w_{AB,t} - u_t - 0.5v_t,\\
+y_{BA,t} &= w_{BA,t} + u_t + 0.5v_t,\\
+y_{BB,t} &= w_{BB,t} - u_t + 0.5v_t,
+\end{align*}
 where $u_t \sim N(0,\sigma^2_u)$ and $v_t \sim N(0,\sigma^2_v)$.
@@
 To obtain the aggregate series at level 1, we add their respective bottom level series such as:
-$$y_{A,t} = w_{AA,t} + w_{AB,t} - v_t,$$
-$$y_{B,t} = w_{BA,t} + w_{BB,t} + v_t,$$
+\begin{align*}
+y_{A,t} &= w_{AA,t} + w_{AB,t} - v_t,\\
+y_{B,t} &= w_{BA,t} + w_{BB,t} + v_t,
+\end{align*}
 and the total series will be obtained as:
@@
 $$
-  Var(\epsilon_{AA,t}+\epsilon_{AB,t}+\epsilon_{BA,t}+\epsilon_{BB,t}) \le Var(\epsilon_{AA,t}+\epsilon_{AB,t}-v_t) \le Var(\epsilon_{AA,t}+u_t-0.5v_t),
+  \text{Var}(\epsilon_{AA,t}+\epsilon_{AB,t}+\epsilon_{BA,t}+\epsilon_{BB,t}) \le \text{Var}(\epsilon_{AA,t}+\epsilon_{AB,t}-v_t) \le \text{Var}(\epsilon_{AA,t}+u_t-0.5v_t),
 $$
@@
 We use \textit{forecast} package in \textbf{R}-software \citet{hyndman2017forecasting} for model fitting and forecasting.
-Further, different estimates of $\bm{W}_{T+1}$ and the corresponding $\bm{R}'_\bot$ were obtained as summarized in Table 2.
+Further, different estimates of $\bm{W}_{T+1}$ and the corresponding $\bm{R}'_\bot$ were obtained as summarized in Table \ref{table:2}.
 This process was then replicated using $1000$ different data sets from the same data generating process.
 
-To assess the predictive performance of different forecasting methods, we use scoring rules as discussed in section 5.
+To assess the predictive performance of different forecasting methods, we use scoring rules as discussed in Section \ref{sec:evaluation}.
 In addition to that we use Skill score \citep{Gneiting2007} for any comparison.
 For a given forecasting method, evaluated by a particular scoring rule $S(.)$ , the skill score will be calculated as follows,
-\begin{flalign}
-  Ss[S_B(.)] = \frac{S_B(\bm{{{Y}},y})^{ref} - S_B(\bm{{\breve{Y}},y})}{S_B(\bm{{{Y}},y})^{ref}}\times 100\%,
-\end{flalign}
-where $S_B(.)$ is average score over $B$ samples and $S_B(\bm{{{Y}},y})^{ref}$ is the average score of the reference forecasting methods.
+\begin{equation}
+  Ss[S_B(.)] = \frac{S_B(\bm{Y},\bm{y})^{\text{ref}} - S_B(\bm{\breve{Y}},\bm{y})}{S_B(\bm{Y},\bm{y})^{\text{ref}}}\times 100\%,
+\end{equation}
+where $S_B(.)$ is average score over $B$ samples and $S_B(\bm{Y},\bm{y})^{\text{ref}}$ is the average score of the reference forecasting methods.
 Thus $Ss[S_B(.)]$ gives the percentage improvement of the preferred forecasting method relative to the reference method.
@@
 In particular, we compare different reconciliation methods over the conventional bottom-up method and also evaluate the predictive ability of coherent forecasts over incoherent forecasts.
-For the former comparison, we use bottom level probabilistic forecasts and calculate the percentage skill score based on energy score, log score and variogram score for each reconciliation method with reference to the bottom up method (presented in Table 3).
-For the latter comparison, we use percentage skill score based on CRPS and univariate log score for coherent probabilistic forecasts of each individual series with reference to incoherent forecasts (presented in Table 4 and 5).
+For the former comparison, we use bottom level probabilistic forecasts and calculate the percentage skill score based on energy score, log score and variogram score for each reconciliation method with reference to the bottom up method (presented in Table \ref{table:3}).
+For the latter comparison, we use percentage skill score based on CRPS and univariate log score for coherent probabilistic forecasts of each individual series with reference to incoherent forecasts (presented in Tables \ref{table:4} and \ref{table:5}).
 
-It is clearly evident from the results in table 3 that the multivariate reconciled forecasts for the bottom level series from MinT(Shrink) and MinT(Sample) outperform the bottom-up forecasts.
-Further, these two methods produce probabilistic forecasts with best predictive ability in comparison to incoherent forecasts (from table 4 and 5).
+It is clearly evident from the results in Table \ref{table:3} that the multivariate reconciled forecasts for the bottom level series from MinT(Shrink) and MinT(Sample) outperform the bottom-up forecasts.
+Further, these two methods produce probabilistic forecasts with best predictive ability in comparison to incoherent forecasts (from Tables \ref{table:4} and \ref{table:5}).
 Moreover, it turns out that OLS and bottom-up methods produce the worst forecasts.
@@
 The ``Skill score'' columns give the percentage skill score with reference to the bottom up forecasting method.
-A positive entry in these columns shows the percentage increase of score for different reconciliation methods with relative to the bottom up method.}
+A positive entry in these columns shows the percentage increase of score for different reconciliation methods with relative to the bottom up method.}\label{table:3}
   \centering\small
@@
 \begin{table}
-  \caption{Comparison of incoherent vs.
-coherent forecasts for the aggregate series using Skill score.
+  \caption{Comparison of incoherent vs coherent forecasts for the aggregate series using Skill score.
 "Incoherent" row represent the average score for incoherent forecasts.
 Each entry above this row represent the percentage skill score with reference to the incoherent forecasts.
-A positive(negative) entry shows the percentage increase(decrease) of score for different forecasting methods with relative to incoherent forecasts.}
+A positive(negative) entry shows the percentage increase(decrease) of score for different forecasting methods with relative to incoherent forecasts.}\label{table:4}
   \centering\small
@@
 \begin{table}
-  \caption{Comparison of incoherent vs. coherent forecasts for the individual bottom level series using Skill score.}
+  \caption{Comparison of incoherent vs coherent forecasts for the individual bottom level series using Skill score.}\label{table:5}
   \centering\tabcolsep=0.08cm\small
@@
 
-\section{Conclusions}
+\section{Conclusions}\label{sec:conclusions}
 

### 2018-03-03 ProbabilisticCoherence.tex
Did some changes according to Tas's comments

@@
 
-Many research applications often involve a large collection of multiple time series some of which are aggregates of others.
-These collections of time series are called hierarchical time series.
+	Many research applications often involve a large collection of time series some of which are aggregates of others.
+These are called hierarchical time series.
 For example, electricity demand of a country can be disaggregated along a geographical hierarchy.
@@
 In the bottom-up approach, forecasts of the lowest level are first generated and they are simply aggregated to forecast upper levels of the hierarchy \citep{Dunn1976}.
-In contrast, the top-down approach involves forecasting the most aggregated series first and then disaggregating these forecasts down the hierarchy based on the proportions of observed data \citep{Gross1990}.
+	In contrast, the top-down approach involves forecasting the most aggregated series first and then disaggregating these forecasts down the hierarchy based on the proportions learn from observed data \citep{Gross1990}.
 	Many studies in the literature have broadly discussed the relative advantages and disadvantages of bottom-up and top-down methods and situations in which they would provide reliable forecasts \citep{Schwarzkopf1988,Kahn1998, Lapide1998,Fliedner2001}.
 	A compromise between these two approaches is the middle-out method which entails forecasting each series of a selected middle level in the hierarchy and then forecasting upper levels by the bottom-up method and lower levels by the top-down method.
-Apparently, these three approaches use only a part of the information available when producing coherent forecasts.
+It is apparent that, these three approaches use only a part of the information available when producing coherent forecasts.
 This might result in inaccurate forecasts.
@@
 
-As an alternative to these conventional methods, \citet{Hyndman2011} propose to use information from all the levels of the hierarchy and reconcile them to obtain coherent point forecasts.
-In this approach, independent forecasts of all series are initially obtained.
+	As an alternative to these conventional methods, \citet{Hyndman2011} propose to utilize the information from all levels of the hierarchy to obtain coherent point forecasts.
+This is a two stage process.
+In the first stage, the forecasts of all series are independently obtained by fitting univariate models for individual series in the hierarchy.
 It is very unlikely that these forecasts are coherent.
-Then, these forecasts are optimally combined through a regression model to obtain coherent forecasts.
-This study has given a rise to the concept of point forecast reconciliation in hierarchical time series.
-In general, any forecasting method that uses a set of incoherent forecasts and revises them to obtain coherent forecasts is referred to as forecast reconciliation method.
-Thus it is important to notice that bottom-up, top-down and middle-out methods are not reconciliation methods since they use only a part of the information from the hierarchy to produce coherent forecasts.
+Thus in the second stage, these forecasts are optimally combined through a regression model to obtain coherent forecasts.
+This second step is referred to as reconciliation since it uses a set of incoherent forecasts and revise them to make it coherent.
+Thus it has given arise to the concept of point forecast reconciliation in hierarchical time series.
+This study was further improved by \citet{Wickramasuriya2017} to obtain optimally reconciled point forecasts by minimizing the mean squared coherent forecast errors.
 
-In a recent study on point forecast reconciliation, \citet{Wickramasuriya2017} propose to minimize the trace of mean squared coherent forecasts errors to optimally reconcile a set of unbiased, incoherent forecasts.
-Assuring the resulting reconciled forecasts are unbiased, they found a unique analytical solution to the proposed minimization problem.
-They referred this to as MinT approach.
-This solution was further improved to be computationally feasible for high dimensional hierarchies.
+	It is also important to notice that the traditional bottom-up, top-down and middle-out forecasting methods are not reconciliation methods since they use only a part of the information from the hierarchy to produce coherent forecasts.
 
-In recent forecasting literature, it is being the rationality to provide the associated uncertainty about the future, in addition to the point forecasts.
-This is referred to as probabilistic forecasts \citep{Gneiting2014}.
+	Providing the associated uncertainty around the point forecasts has been of great interest in recent forecasting literature.
+This is also referred to as probabilistic forecasts \citep{Gneiting2014}.
 For example, \citet{McSharry2005} produced probabilistic forecasts in application to electricity demand, \citet{BenTaieb2017} in application to smart meter data, \citet{Pinson2009} in application to wind power generation, \citet{Gel2004}, \citet{Gneiting2005a} and \citet{Gneiting2005} in application to prediction of weather quantities.
@@
 This is the only study that copes with the probabilistic forecasts in hierarchical time series thus far.
-In their approach, a sample from the mean reconciled predictive distribution of the bottom level will be first generated.
+In their approach, a sample from the bottom level predictive distribution will be first generated.
 This sample will be then aggregated to obtain the coherent probabilistic forecasts of the respective upper levels of the hierarchy.
 Hence this method is a bottom-up based approach.
-They further use MinT approach for the mean reconciliation of the bottom level predictive distribution and a copula based approach to model the dependency structure of the hierarchy, when producing the sample of bottom level probabilistic forecasts.
+They propose to use MinT approach for the mean reconciliation of the bottom level predictive distribution and a copula based approach to model the dependency structure of the hierarchy, when generating the sample from bottom level probabilistic forecasts.
 
-Our contribution in this paper is to provide a proper theoretical background for the probabilistic hierarchical forecasts.
-First, we redefine the coherency of point forecasts and the reconciliation of a set of incoherent point forecasts by using the concepts on vector spaces and measure theory.
-This will leads us to provide a proper definition for probabilistic forecast reconciliation.
-Due to the aggregation structure in the hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate.
+	Our contribution in this paper is to provide a proper theoretical background for the probabilistic forecasts reconciliation in hierarchical time series.
+First, we provide an alternative definition for coherency of point forecasts and the reconciliation of a set of incoherent point forecasts by using the concepts on vector spaces and measure theory.
+Based on these, we provide a rigorous definition for probabilistic forecast reconciliation and how we can reconcile the incoherent forecast densities in practice.
+Further, due to the aggregation structure of the hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate.
 We discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation and also in the evaluation of their predictive performances.
-Further, we provide theoretical results on probabilistic forecast reconciliation in the Gaussian framework.
+In addition to that, we provide theoretical results on probabilistic forecast reconciliation in the Gaussian framework which is followed by a simulation study to show the importance of reconciliation in the probabilistic framework.
 
 	Rest of the paper is structured as follows.
-We start with introducing the notations in Section \ref{sec:notation}.
-In Section \ref{sec:definitions} we provide our definitions for coherency which is followed by the definitions for forecast reconciliation in Section \ref{sec:reconciliation}.
-Section \ref{sec:evaluation} discusses the methods that can be used for evaluation of probabilistic hierarchical forecasts.
-Section \ref{sec:gaussian} consists the theoretical results followed by the simulation study on probabilistic forecast reconciliation in the Gaussian framework and we enclose with the remarkable conclusions in Section \ref{sec:conclusions}.
+We start with introducing the notations in section 2.
+In section 3 we provide our definitions for coherency which is followed by the definitions for forecast reconciliation in section 4.
+Section 5 discusses the methods that can be used for evaluation of probabilistic hierarchical forecasts.
+Section 6 consists the theoretical results followed by the simulation study on probabilistic forecast reconciliation in the Gaussian framework and we enclose with the remarkable conclusions in section 7.
 
@@
 
-We first introduce notations where possible following \citet{Wickramasuriya2017}.
-Suppose $\bm{y}_t \in \mathbb{R}^n$ comprising all observations of the whole hierarchy at time $t$ and $\bm{b}_t \in \mathbb{R}^m$ comprising only the bottom level observations at  time $t$.
+	We first introduce notations which mostly follow \citet{Wickramasuriya2017}.
+Suppose $\mathbold{y}_t \in \bm{\mathbb{R}}^n$ comprising all observations of the whole hierarchy at time $t$ and $\mathbold{b}_t \in \bm{\mathbb{R}}^m$ comprising only the bottom level observations at  time $t$.
 Then due to the aggregation nature of the hierarchy we have,
+
 	\begin{equation}
-  \bm{y}_t = \bm{Sb}_t,
+	\mathbold{y}_t = \mathbold{Sb}_t,
 	\end{equation}
-where $\bm{S}$ is a $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold.
-Since this linear subspace is equivalent to the column space of $\bm{S}$, we denote it as $\mathscr{C}(\bm{S})$.
-Further the null space of $\bm{S}$ which is orthogonal to this linear subspace is denoted by $\mathscr{N}(\bm{S})$.
+	where $\mathbold{S}$ is a $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold.
 
+	\noindent 
 	To understand the notations clearly, consider the hierarchy given in Figure 1.
@@
 	\end{figure}
-
+	\noindent
 	In any hierarchy, the most aggregated level is termed as level 0, the second most aggregated level is termed as level 1 and so on.
@@
 At a particular time $t$, let $y_{Tot,t}$ denote the observation at level 0; $y_{A,t}, y_{B,t} $ denote observations at level 1; and $y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}$ denote observations at level 2.
-Then
-$\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$,
-$\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and
-$$
-  \bm{S} =
-  \begin{pmatrix}
-    1& 1 &1 &1  \\ 1 &1 & 0 &0 \\   0&0  & 1 & 1 \\ & & I_4 &
-  \end{pmatrix},
-$$
-where $I_4$ is a $4$-dimension identity matrix.
+Then $\mathbold{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, \\$\mathbold{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and $$ \mathbold{S} = \begin{pmatrix} 1& 1 &1 &1  \\ 1 &1 & 0 &0 \\   0&0  & 1 & 1 \\ & & I_4 &   \end{pmatrix}, $$ where $I_4$ is a $4$-dimension identity matrix.
 
@@
 	The main purpose of this section is to provide formal definitions for coherent forecasts.
-We start with redefining the coherent point forecasts using the properties of vector spaces which is then followed by the definition of coherent probabilistic forecasts.
+We first give an alternative definition for coherent point forecasts using the properties of vector spaces which is then followed by the definition of coherent probabilistic forecasts.
 
-\begin{definition}[Coherent Point Forecasts]
-Suppose $\breve{\bm{y}}_{t+h} \in \mathbb{R}^n$ consists point forecasts of each series in the hierarchy at time $t+h$.
-$\breve{\bm{y}}_{t+h}$ is said to be \textit{Coherent} if it lies in a $m$-dimensional subspace of $\mathbb{R}^n$ which is spanned by the columns of $\bm{S}$.
+	\begin{definition}[Coherent subspace]
+		Let $\bm{\mathbb{C}}^m$ is a $m$-dimensional subspace of $\bm{\mathbb{R}}^n$, $\bm{\mathbb{C}}^m < \bm{\mathbb{R}}^n$.
+$\bm{\mathbb{C}}^m$ is said to be a coherent space, if it is spanned by the columns of $\bm{S}$.
+	\end{definition}
+
+	It is worth to notice that the coherent space $\bm{\mathbb{C}}^m$ is equivalent to the column space of $\bm{S}$ which we denote by $\mathscr{C}(\bm{S})$.
+Further the space orthogonal to $\bm{\mathbb{C}}^m$ is denoted by $\bm{\mathbb{N}}^{n-m}$ and it is equivalent to the null space of $\bm{S}$.
+
+	\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
+		Suppose $\bm{\breve{y}}_{t+h} \in \mathbb{R}^n$ consists point forecasts of each series in the hierarchy at time $t+h$.
+$\bm{\breve{y}}_{t+h}$ is said to be \textit{Coherent} if $\bm{\breve{y}}_{t+h} \in \bm{\mathbb{C}}$.
 	\end{definition}
@@
 	\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
-Let $(\mathbb{R}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability measure space where $\mathscr{F}^m$ is a sigma algebra on $\mathbb{R}^m$.
-$\breve{\nu}(.)$ on the measurable space $(\mathscr{C}(\bm{S}), \mathscr{F}_{\bm{S}})$ is said to be coherent probability measure iff
-$$
-  \breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall \quad \bm{A} \in \mathscr{F}^m,
-$$
+		Let $(\bm{\mathbb{R}}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability triple where $\mathscr{F}^m$ is sigma algebra on $\bm{\mathbb{R}}^m$.
+Then, $(\bm{\mathbb{C}}, \mathscr{F}_{\bm{S}}, \breve{\nu})$ is said to be coherent probability measure space iff,
+		$$\breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall \quad \bm{A} \in \mathscr{F}^m,$$ 
 		where $\bm{S}(\bm{A})$ denotes the image of subset $\bm{A}$ under $\bm{S}$. 
@@
 			\node at (4,5) {$\mathbb{R}^n$(codomain of $\bm{S}$)};
-      \node at (4,1.0) {$\mathscr{C}(\bm{S})$};
+			\node at (4,1.0) {$\bm{\mathbb{C}}^m$};
 			%\node[bullet,label=below:$f(x)$] at (4,2.5){};
@@
 		\end{center}
-  \caption{Any set $\bm{A} \in \mathbb{R}^m$ will be mapped to the $\mathscr{C}(\bm{S})$ through the mapping $\bm{S}$}
+		\caption{Any set $\bm{A} \in \mathbb{R}^m$ will be mapped to the $\bm{\mathbb{C}}^m$ through the mapping $\bm{S}$}
 	\end{figure}
 
-Definition \ref{def:cohprob} implies the probability measure on $\mathscr{C}(\bm{S})$ is equivalent to the probability measure on $(\mathbb{R}^m, \bm{\mathscr{F}}^m)$.
-Hence, there is no density anywhere outside the linear subspace spanned by the columns of $\bm{S}$ in $\mathbb{R}^n$.
-That is, a \textit{Coherent probability density forecast} is any density $\bm{f}(\breve{\bm{y}}_{t+h})$ such that $\bm{f}(\breve{\bm{y}}_{t+h})=0$ for all $\breve{\bm{y}}_{t+h} \in \mathscr{N}(\bm{S})$.
+	Definition (\ref{def:cohprob}) implies the probability measure on $\bm{\mathbb{C}}^m$ is equivalent to the probability measure on $(\bm{\mathbb{R}}^m, \bm{\mathscr{F}}^m)$.
+Hence, there is no density anywhere outside the linear subspace $\bm{\mathbb{C}}^m$.
+That is, a \textit{Coherent probability density forecast} is any density $\bm{f}(\bm{\breve{y}}_{t+h})$ such that $\bm{f}(\bm{\breve{y}}_{t+h})=0$ for all $\bm{\breve{y}}_{t+h} \in \bm{\mathbb{N}}^{n-m}$.
 Following example will help to understand these definitions more clearly.
@@
 	Consider a simple hierarchy with two bottom level series $A$ and $B$ that add up to the top level series $Tot$.
-Suppose the forecasts at time $t+h$ of these series are given by $\breve{\bm{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$ and $\breve{\bm{y}}_{t+h} \in \mathbb{R}^3$.
+Suppose the forecasts at time $t+h$ of these series are given by $\mathbold{\breve{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$ and $\mathbold{\breve{y}}_{t+h} \in \bm{\mathbb{R}}^3$.
 Due to the aggregation constraint of the hierarchy we have $\breve{y}_{Tot,t+h}=\breve{y}_{A,t+h}+\breve{y}_{B,t+h}$.
-This implies, even though  $\breve{\bm{y}}_{t+h}$ is in $\mathbb{R}^3$, the points actually lie in a two dimensional subspace within that $\mathbb{R}^3$ space.
-This subspace is equivalent to $\mathscr{C}(\bm{S})$ for this simple hierarchy.
-Therefore, for any $\breve{\bm{y}}_{t+h} \in \mathscr{N}(\bm{S})$ have a zero probability.
+This implies, even though  $\mathbold{\breve{y}}_{t+h}$ is in $\bm{\mathbb{R}}^3$, the points actually lie in $\bm{\mathbb{C}}^2$, which is a two dimensional subspace within that $\bm{\mathbb{R}}^3$ space.
+Therefore, for any $\mathbold{\breve{y}}_{t+h} \in \bm{\mathbb{N}}$ have a zero probability.
 I.e.
-$f(\breve{\bm{y}}_{t+h})=0$ for any $\breve{\bm{y}}_{t+h} \in \mathscr{N}(\bm{S})$.
+$f(\mathbold{\breve{y}}_{t+h})=0$ for any $\mathbold{\breve{y}}_{t+h} \in \bm{\mathbb{N}}$.
 
-By the definition of coherent forecasts, it is clear that there are only $m$ number of linear independent series in the whole hierarchy.
-We refer to these as $m$ dimensional \textit{basis set of series} since these series generates a \textit{basis} that spans the $\mathscr{C}(\bm{S})$.
-Other $n-m$ series of the hierarchy can be linearly determined by these basis set of series.
-This implies that any coherent density is a degenerate density.
-In particular, the $m$ number of bottom level series of a given hierarchy can be considered as a basis set of series.
-Then the set of columns of $\bm{S}$ is a basis that generates through these bottom level series.
-This basis spans the linear subspace where the degenerate density lives on.
+	For a particular coherent subspace $\bm{\mathbb{C}}^m$, there exist several distinct basis vectors.
+For example, in the smallest hierarchy considered above, $\left\{\begin{pmatrix} 1&1&0 \end{pmatrix}', \begin{pmatrix} 1&0&1 \end{pmatrix}'\right\}$, $\left\{\begin{pmatrix} 1&0&1 \end{pmatrix}',\\ \begin{pmatrix}
+	0&1&-1 \end{pmatrix}'\right\}$ and the singular value decomposition of these two are some alternative basis vectors that spans the same $\bm{\mathbb{C}}^m$.
+Given a basis for $\bm{\mathbb{C}}^m$, every series of the hierarchy can be linearly determined as a linear combination of that basis vectors.
+We referred to the coefficients of these linear combinations as the \textit{basis series}.
+It is apparent that these basis series are $m$ dimensional and linearly independent in a given hierarchy.
+For example, in the smallest hierarchy, $(\bm{A,B})$ and $(\bm{Tot,A})$ are the basis series corresponds to the basis vectors $\left\{\begin{pmatrix} 1&1&0 \end{pmatrix}', \begin{pmatrix} 1&0&1 \end{pmatrix}'\right\}$ and $\left\{\begin{pmatrix} 1&0&1 \end{pmatrix}', \begin{pmatrix}
+	0&1&-1 \end{pmatrix}'\right\}$ respectively. Thus it is clear that the set of bottom level series is a basis series that corresponds to the column vectors of $\bm{S}$.
 
-However bottom level series are not the only set of basis series and we can find many other basis set of series which generates basis that spans the same $\mathscr{C}(\bm{S})$ for a given hierarchy.
-If we go back to the hierarchy in example 1, instead of two bottom level series $(\bm{A,B})$ we can take $(\bm{Tot,A})$ as the basis set of series and the basis that generates through $(\bm{Tot,A})$ will be
-$\{
-  \begin{pmatrix} 1&0&1 \end{pmatrix}',
-  \begin{pmatrix} 0&1&-1 \end{pmatrix}'\}$.
-Another possible basis would be the singular value decomposition of $\bm{S}$.
+	An important thing to notice here is, since the basis are not unique for a give coherent subspace, the definition (\ref{def:cohprob}) is not unique and one can redefine the coherent probabilistic forecasts with respect to any basis.
+However, we stick to the definition (\ref{def:cohprob}) and consider the basis defined by the columns of $\bm{S}$ in what follows.
 
-An important thing to notice here is all of these basis spans the same linear subspace equivalent to the $\mathscr{C}(\bm{S})$.
-Therefore the definition $(3.2)$ is not unique and one can redefine the coherent probabilistic forecasts with respect to any basis.
-However, we stick to the definition $(3.2)$ and consider the basis defined by the columns of $\bm{S}$ that generates through the bottom levels of the hierarchy in what follows.
-
-It is also worth to mention that the definition $(3.1)$ and $(3.2)$ facilitate extension to the forecast reconciliation which we talk about in the next section.
+	It is also worth to mention that the definition (\ref{def:cohpoint}) and (\ref{def:cohprob}) facilitate extension to the forecast reconciliation which we talk about in the next section.
 In contrast to our definition, \citet{BenTaieb2017} defines the coherent probabilistic forecasts in terms of convolution.
@@
 	Previous studies on point forecast literature have shown that the reconciliation provides better coherent forecasts than the conventional bottom-up and top-down methods (\cite{Hyndman2011}; \cite{VanErven2015a}; \cite{Wickramasuriya2017}).
-However, this was not well established in the context of probabilistic forecasts.
-Nevertheless, there is no proper definition for the probabilistic forecast reconciliation in the published literature.
-Thus in this section, we focus on defining the probabilistic forecast reconciliation and discuss how that definition can be used in practice.
+However, not extended in the context of probabilistic forecasts in published literature.
+Thus our main focus is to rigorously define the probabilistic forecast reconciliation and discuss how that definition can be used in practice.
 
@@
 
-Initially we redefine point forecast reconciliation using the concepts in linear algebra as a groundwork for the probabilistic forecast reconciliation.
+	Initially we define point forecast reconciliation as a groundwork to the probabilistic forecast reconciliation.
 
-\begin{definition}
-Let $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m $ and $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$ be any set of incoherent forecasts at time $t+h$.
+	\begin{definition}\label{def:reconpoint}
+		Let $\bm{g}:\bm{\mathbb{R}}^n \rightarrow \bm{\mathbb{R}}^m $ and $\hat{\bm{y}}_{t+h} \in \bm{\mathbb{R}}^n$ be any set of incoherent forecasts at time $t+h$.
 Then $\tilde{\bm{b}}_{t+h}$ is said to be reconciled bottom level forecasts if
@@
 		\end{equation}
-where $\bm{g}(\hat{\bm{y}}_{t+h})$ is the image of $\hat{\bm{y}}_{t+h}$ under $\bm{g}$ on $\mathbb{R}^m$.
-The reconciled forecasts for the whole hierarchy is then given by $\tilde{\bm{y}}_{t+h}=\bm{S}(\tilde{\bm{b}}_{t+h})$ such that $\tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})$, where $\bm{S}(\tilde{\bm{b}}_{t+h})$ is the image of $\tilde{\bm{b}}_{t+h}$ under $\bm{S}$ on the $\mathscr{C}(\bm{S}) < \mathbb{R}^n$.
+		where $\bm{g}(\hat{\bm{y}}_{t+h})$ is the image of $\hat{\bm{y}}_{t+h}$ under $\bm{g}$ on $\bm{\mathbb{R}}^m$.
+The reconciled forecasts for the whole hierarchy is then given by $\tilde{\bm{y}}_{t+h}=\bm{S} \circ \bm{g}(\hat{\bm{y}}_{t+h})$ such that $\tilde{\bm{y}}_{t+h} \in \bm{\mathbb{C}}^m$, where $\bm{S}\circ \bm{g}(.)$ is a projection of $\bm{g}(.)$ onto the $\bm{\mathbb{C}}^m$.
 	\end{definition}
 
-In the following content we explain more on how this definition can be used in practice to reconcile point forecasts in hierarchical time series.
-Let $\bm{R} \in \mathbb{R}^{n \times (n-m)}$ consists the columns that spans $\mathscr{N}(\bm{S})$ which is orthogonal to $\mathscr{C}(\bm{S})$.
-$\mathscr{N}(\bm{S})$ is also equivalent to the $\mathscr{C}(\bm{R})$.
-Note that $\bm{R}$ is also not unique and one example is a matrix whose columns represent the aggregation constraints for the hierarchy.
+	Importance of definition (\ref{def:reconpoint}) is that it facilitates for both linear and non-linear reconciliation.
+In other words, if $\bm{g}$ is a non-linear function, then the reconciliation of $\hat{\bm{y}}_{t+h}$ will be non-linear.
+On the other hand, if $\bm{g}$ is a linear function, then $\bm{S}\circ \bm{g}(.)$ will linearly projects incoherent point forecasts onto $\bm{\mathbb{C}}^m$.
+Latter was the main focus in previous studies in hierarchical point forecasting, where $\bm{g}$ is considered as a $m \times n$ matrix $\bm{P}$ and thus $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$.
+
+	In the following content we provide an alternative explanation for linear reconciliation based on definition (\ref{def:reconpoint}).
+Let $\bm{R} \in \bm{\mathbb{R}}^{n \times (n-m)}$ consists the columns that spans $\bm{\mathbb{N}}^{n-m}$ which is orthogonal to $\bm{\mathbb{C}}^m$.
+Note that $\bm{R}$ is also not unique and one example is a matrix whose columns represent the aggregation constraints for a given hierarchy.
 Then for the hierarchy in example 1,
 	$$ 
-  \bm{S} =
+	\mathbold{S} = 
 	\begin{pmatrix} 
@@
 	\quad \text{and} \quad 
-  \bm{R} =
+	\mathbold{R} = 
 	\begin{pmatrix}  
@@
 	$$ 
-Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively.
-Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$.
-Now, using the insights of definition 4.1, we can use the following steps to reconcile the point forecasts.
+	\noindent
+	Further let $\{\bm{s}_1,...,\bm{s}_m\}$ and $\{\bm{r}_1,...,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively.
+Then $\bm{B}=\{\bm{s}_1,...,\bm{s}_m, \bm{r}_1,...,\bm{r}_{n-m}\}$ is a basis for $\bm{\mathbb{R}}^n$.
+Now, using the insights of definition (\ref{def:reconpoint}), we can use the following steps to reconcile the point forecasts.
 
@@
 
-For a given incoherent set of point forecasts $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$, first we find the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$.
+	For a given incoherent set of point forecasts $\hat{\bm{y}}_{t+h} \in \bm{\mathbb{R}}^n$, first we find the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$.
 Let $\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}'$ denote these coordinates.
-Note that $\tilde{\bm{b}}_{t+h}$ is a basis set of series which is really the reconciled bottom level series that generates $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\tilde{\bm{t}}_{t+h}$ is another basis set of series that generates $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$.
+Note that $\tilde{\bm{b}}_{t+h}$ is a basis series which is really the reconciled bottom level series that corresponds to the coefficients of linear combination of the basis $\{\bm{s}_1,...,\bm{s}_m\}$.
+Similarly, $\tilde{\bm{t}}_{t+h}$ is another basis series corresponds to the coefficients of linear combination of the basis $\{\bm{r}_1,...,\bm{r}_{n-m}\}$.
 Then from basic properties of linear algebra it follows that,
+
 	\[
@@
 	This step directly follows by the definition for coherent forecasts.
-That is, to obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \mathbb{R}^n$ to the $\mathscr{C}(\bm{S})$ through $\bm{S}$.
+That is, to obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \bm{\mathbb{R}}^n$ to the $\bm{\mathbb{C}}^m$ through $\bm{S}$.
 Thus we have,
 	\begin{equation}
-  \tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})<\mathbb{R}^n.
+	\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \bm{\mathbb{C}}^m<\bm{\mathbb{R}}^n.
 	\end{equation}
@@
 	Finding a suitable $\bm{R}_\bot$ with respect to a certain loss function will result optimally reconciled point forecasts of the hierarchy.
-Notice that, if the mapping $\bm{g}$ in definition 4.1 is considered to be linear we have,
-\begin{equation}
-  \bm{g}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot.
-\end{equation}
+Notice that, if $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$, then the definition for linear reconciliation of point forecasts in previous studies coincides with our explanation.
 
-In previous studies on hierarchical point forecasting, $\bm{g}$ is considered as a $m \times n$ matrix $\bm{P}$ and thus $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$.
-In other words, $\bm{g}$ linearly projects incoherent point forecasts onto the $\mathscr{C}(\bm{S})$.
 	Further in our context, we need to find $\bm{R}_\bot$ such that $\bm{R}'_\bot \bm{S}$ is invertible.
@@
 
-\begin{definition}
-Suppose $(\mathbb{R}^n, \mathscr{F}^n, \hat{\nu})$ be an incoherent probability measure space and $(\mathbb{R}^m, \mathscr{F}^m, \nu^m)$ be a probability measure space defined on $\mathbb{R}^m$.
+	\begin{definition} \label{def:reconprob}
+		Suppose $(\mathbb{R}^n, \mathscr{F}^n, \hat{\nu})$ be an incoherent probability triple and $(\mathbb{R}^m, \mathscr{F}^m, \nu^m)$ be a probability triple defined on $\mathbb{R}^m$.
 Let $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m $.
@@
 		\end{equation}
-where $\bm{S}:\mathbb{R}^m \rightarrow \mathbb{R}^n$ and $\tilde{\nu}(.)$ is the probability measure on the measure space $(\mathscr{C}(\bm{S}), \mathscr{F}_S)$.
+		where $\bm{S}:\mathbb{R}^m \rightarrow \mathbb{C}^m$ and $\tilde{\nu}(.)$ is the probability measure on the measure space $(\mathbb{C}^m, \mathscr{F}_S)$.
 	\end{definition}
@@
 Suppose $\hat{\bm{f}}(.)$ is the probability density of $\hat{\bm{y}}_{t+h}$.
-Our goal is to reconcile $\hat{\bm{f}}(.)$ such that the density lives on the $\mathscr{C}(\bm{S})$.
-In order to obtain this reconciled density, we need to project $\hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ onto the $\mathscr{C}(\bm{S})$ along the direction of $\mathscr{C}(\bm{R})$.
+Our goal is to reconcile $\hat{\bm{f}}(.)$ such that the density lives on the $\mathbb{C}^m$.
+In order to obtain this reconciled density, we need to project $\hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ onto the $\mathbb{C}^m$ along the direction of $\mathbb{N}^{n-m}$.
 
@@
 
-Finally to get the reconciled density of the whole hierarchy, we simply follow the definition $3.2$ and have,
+	Finally to get the reconciled density of the whole hierarchy, we simply follow the definition (\ref{def:cohprob}) and have,
 	\begin{equation}\label{4.7}
@@
 	\end{equation}
-This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the $\mathscr{C}(\bm{S})<\mathbb{R}^n$.
+	This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the $\mathbb{C}^m<\mathbb{R}^n$.
 Following example illustrates how this method can be used to reconcile an incoherent Gaussian forecast distribution.
@@
 	& \hspace*{1cm} \Big[\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}'\Big]^{-1}
-  \ Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.
+	\Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.
 	\end{align*}
@@
 	\begin{equation}
-  \text{VS}(\breve{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - \frac{1}{m} \displaystyle\sum_{k=1}^{B} |\breve{Y}^k_{T+h,i}-\breve{Y}^k_{T+h,j}|^p\right)^2.
+	\text{VS}(\breve{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - \frac{1}{B} \displaystyle\sum_{k=1}^{B} |\breve{Y}^k_{T+h,i}-\breve{Y}^k_{T+h,j}|^p\right)^2.
 	\end{equation}
@@
 	%
-%where $\bm{\tilde{\mu}}_{T+h}$ and $\bm{\tilde{\Sigma}}_{T+h}$ are the coherent mean and variance-covariance matrix of the predictive Gaussian density and both lies in the linear %subspace spanned by $\mathscr{C}(\bm{S})$.
+	%where $\bm{\tilde{\mu}}_{T+h}$ and $\bm{\tilde{\Sigma}}_{T+h}$ are the coherent mean and variance-covariance matrix of the predictive Gaussian density and both lies in the linear %subspace spanned by $\mathbb{C}^m$.
 Then $\bm{\tilde{\Sigma}}_{T+h}$ is always a singular matrix and hence the determinant will be zero.
@@
 That is, suppose all the historical data in the hierarchy follows a multivariate Gaussian distribution, i.e.
-$\bm{y}_T \sim \mathscr{N}(\bm{\mu}_T, \bm{\Sigma}_T)$ where both $\bm{\mu}_T$ and $\bm{\Sigma}_T$ lives in $\mathscr{C}(\bm{S})$ by nature of the hierarchical time series.
-We are interested in estimating the predictive Gaussian distribution of $\bm{Y}_{T+h}| \bm{\mathcal{I}}_T$ where $\bm{\mathcal{I}}_T= \{\bm{y}_1,\bm{y}_2,\dots.,\bm{y}_T\}$, which should also lives in $\mathscr{C}(\bm{S})$.
+$\bm{y}_T \sim \mathscr{N}(\bm{\mu}_T, \bm{\Sigma}_T)$ where both $\bm{\mu}_T$ and $\bm{\Sigma}_T$ lives in $\mathbb{C}^m$ by nature of the hierarchical time series.
+We are interested in estimating the predictive Gaussian distribution of $\bm{Y}_{T+h}| \bm{\mathcal{I}}_T$ where $\bm{\mathcal{I}}_T= \{\bm{y}_1,\bm{y}_2,\dots.,\bm{y}_T\}$, which should also lives in $\mathbb{C}^m$.
 
@@
 \citet{Yao2006} showed that $\bm{\hat{\alpha}}$ and $\bm{\hat{\beta}}$ are asymptotically consistent estimators.
-Thus the point forecasts from this estimated model $Y_{T+h,i}$, will also be a consistent estimator for $\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}]$.
+Thus the point forecasts from this estimated model, $\hat{Y}_{T+h,i}$, will also be a consistent estimator for $\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}]$.
 i.e.,
 	\begin{equation} \label{eq:(6.01)}
-  Y_{T+h,i} \overset{p}{\to} \E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}] \quad \text{as} \quad T \to \infty.
+	\hat{Y}_{T+h,i} \overset{p}{\to} \E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}] \quad \text{as} \quad T \to \infty.
 	\end{equation}
@@
 	\begin{equation*}
-  \hat{\bm{e}}_{T+h} = \bm{Y}_{T+h}-\hat{\bm{Y}}_{T+h}, \quad \hat{\bm{e}} \sim \bm{\mathcal{N}}(0, \bm{W}_{T+h}).
+	\hat{\bm{e}}_{T+h} = \bm{Y}_{T+h}-\hat{\bm{Y}}_{T+h},
 	\end{equation*}
@@
 	\begin{equation}
-  \bm{W}_{T+h} \overset{p}{\to} \text{Var}(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) \quad \text{as} \quad T \to \infty.
+	\bm{W}_{T+h} \overset{p}{\to} \text{Var}(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) \quad \text{as} \quad T \to \infty,
 	\end{equation}
+	where, $\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = \bm{W}_{T+h}$.
 
@@
 
-As it was well established that the reconciliation outperforms other conventional point forecasting methods in the hierarchical literature, we proposed to use reconciliation in probabilistic forecasting as well to obtain coherent degenerate densities.
+	As it was well established that the reconciliation outperforms other conventional point forecasting methods in the hierarchical literature, we proposed to use reconciliation in probabilistic framework to obtain coherent degenerate densities.
 We provided a distinct definition for density forecast reconciliation and how it can be used to reconcile incoherent densities in practice.

### 2018-03-06 ProbabilisticCoherence.tex
Revised intro

@@
 
-	Many research applications often involve a large collection of time series some of which are aggregates of others.
+Many research applications involve a large collection of time series, some of which are aggregates of others.
 These are called hierarchical time series.
-For example, electricity demand of a country can be disaggregated along a geographical hierarchy.
-One would be interested in forecasting electricity demand of the whole country along with the demand of states, cities, and households.
-This is referred to as hierarchical forecasting.
-An important aspect of hierarchical forecasting is to have coherent forecasts across the hierarchy; that is, forecasts at lower levels should add up to their respective upper levels of aggregation.
+For example, electricity demand of a country can be disaggregated along a geographical hierarchy: the electricity demand of the whole country can be divided into the demand of states, cities, and households.
 
-	There is a rich literature on producing coherent point forecasts in hierarchical time series.
-The traditional approaches involve bottom-up, top-down and middle-out methods.
+When forecasting such time series, it is important to have ``coherent'' forecasts across the hierarchy: aggregates of the forecasts at lower levels should be equal to the forecasts at the upper levels of aggregation.
+In other words, sums of forecasts should be equal to the forecasts of the sums.
+
+The traditional approaches to produce coherent point forecasts are the bottom-up, top-down and middle-out methods.
 In the bottom-up approach, forecasts of the lowest level are first generated and they are simply aggregated to forecast upper levels of the hierarchy \citep{Dunn1976}.
-	In contrast, the top-down approach involves forecasting the most aggregated series first and then disaggregating these forecasts down the hierarchy based on the proportions learn from observed data \citep{Gross1990}.
-	Many studies in the literature have broadly discussed the relative advantages and disadvantages of bottom-up and top-down methods and situations in which they would provide reliable forecasts \citep{Schwarzkopf1988,Kahn1998, Lapide1998,Fliedner2001}.
+In contrast, the top-down approach involves forecasting the most aggregated series first and then disaggregating these forecasts down the hierarchy based on the corresponding proportions of observed data \citep{Gross1990}.
+Many studies have discussed the relative advantages and disadvantages of bottom-up and top-down methods, and situations in which each would provide reliable forecasts \citep{Schwarzkopf1988,Kahn1998, Lapide1998,Fliedner2001}.
 A compromise between these two approaches is the middle-out method which entails forecasting each series of a selected middle level in the hierarchy and then forecasting upper levels by the bottom-up method and lower levels by the top-down method.
-It is apparent that, these three approaches use only a part of the information available when producing coherent forecasts.
+
+It is apparent that these three approaches use only part of the information available when producing coherent forecasts.
 This might result in inaccurate forecasts.
-For example, if the bottom level series are highly volatile or too noisy and hence challenging to forecast, then the resulting forecasts from bottom-up approach would be inaccurate.
+For example, if the bottom level series are highly volatile or noisy, and hence challenging to forecast, then the resulting forecasts from the bottom-up approach are likely to be inaccurate.
 
-	As an alternative to these conventional methods, \citet{Hyndman2011} propose to utilize the information from all levels of the hierarchy to obtain coherent point forecasts.
-This is a two stage process.
+As an alternative to these traditional methods, \citet{Hyndman2011} proposed to utilize the information from all levels of the hierarchy to obtain coherent point forecasts in  a two stage process.
 In the first stage, the forecasts of all series are independently obtained by fitting univariate models for individual series in the hierarchy.
@@
 Thus in the second stage, these forecasts are optimally combined through a regression model to obtain coherent forecasts.
-This second step is referred to as reconciliation since it uses a set of incoherent forecasts and revise them to make it coherent.
-Thus it has given arise to the concept of point forecast reconciliation in hierarchical time series.
-This study was further improved by \citet{Wickramasuriya2017} to obtain optimally reconciled point forecasts by minimizing the mean squared coherent forecast errors.
+This second step is referred to as ``reconciliation'' since it takes a set of incoherent forecasts and revises them to be coherent.
+The approach was further improved by \citet{Wickramasuriya2017} who proposed the ``MinT'' algorithm to obtain optimally reconciled point forecasts by minimizing the mean squared coherent forecast errors.
 
-	It is also important to notice that the traditional bottom-up, top-down and middle-out forecasting methods are not reconciliation methods since they use only a part of the information from the hierarchy to produce coherent forecasts.
+Traditional bottom-up, top-down and middle-out forecasting methods are not strictly reconciliation methods since they use only a part of the information from the hierarchy to produce coherent forecasts.
 
-	Providing the associated uncertainty around the point forecasts has been of great interest in recent forecasting literature.
-This is also referred to as probabilistic forecasts \citep{Gneiting2014}.
-For example, \citet{McSharry2005} produced probabilistic forecasts in application to electricity demand, \citet{BenTaieb2017} in application to smart meter data, \citet{Pinson2009} in application to wind power generation, \citet{Gel2004}, \citet{Gneiting2005a} and \citet{Gneiting2005} in application to prediction of weather quantities.
+Point forecasts are limited because they provide no indication of forecast uncertainty.
+Providing prediction intervals helps, but a richer description of forecast uncertainty is obtained by estimating the entire forecast distribution.
+These are often called ``probabilistic forecasts'' \citep{Gneiting2014}.
+For example, \citet{McSharry2005} produced probabilistic forecasts for electricity demand, \citet{BenTaieb2017} for smart meter data, \citet{Pinson2009} for wind power generation, and \citet{Gel2004}, \citet{Gneiting2005a} and \citet{Gneiting2005} for various weather variables.
 
-	Although there is a thorough literature on producing coherent point forecasts of hierarchical time series, a very limited attention has been given in the context of probabilistic forecasts.
-Recently \citet{BenTaieb2017} proposed an algorithm to produce coherent probabilistic forecasts with the application to UK electricity smart meter data.
-This is the only study that copes with the probabilistic forecasts in hierarchical time series thus far.
-In their approach, a sample from the bottom level predictive distribution will be first generated.
-This sample will be then aggregated to obtain the coherent probabilistic forecasts of the respective upper levels of the hierarchy.
-Hence this method is a bottom-up based approach.
-They propose to use MinT approach for the mean reconciliation of the bottom level predictive distribution and a copula based approach to model the dependency structure of the hierarchy, when generating the sample from bottom level probabilistic forecasts.
+Although there is a rich and growing literature on producing coherent point forecasts of hierarchical time series, little  attention has been given to coherent probabilistic forecasts.
+The only relevant paper we are aware of is \citet{BenTaieb2017}, who recently proposed an algorithm to produce coherent probabilistic forecasts and applied it to UK electricity smart meter data.
+In their approach, a sample from the bottom level predictive distribution is first generated, and then aggregated to obtain coherent probabilistic forecasts of the upper levels of the hierarchy.
+Hence this method is a bottom-up approach.
+They propose to first use the MinT algorithm to reconcile the means of the bottom level forecast distributions, and then a copula-based approach is employed to model the dependency structure of the hierarchy.
+The resulting multi-dimensional distribution is used to generating empirical forecast distributions for all bottom-level series.
+Thus, while \citet{BenTaieb2017} provide coherent probabilistic forecasts, they do no forecast reconciliation of the distributions.
+In that sense, their approach is analogous to bottom-up point forecasting rather than forecast reconciliation.
 
-	Our contribution in this paper is to provide a proper theoretical background for the probabilistic forecasts reconciliation in hierarchical time series.
-First, we provide an alternative definition for coherency of point forecasts and the reconciliation of a set of incoherent point forecasts by using the concepts on vector spaces and measure theory.
-Based on these, we provide a rigorous definition for probabilistic forecast reconciliation and how we can reconcile the incoherent forecast densities in practice.
+After introducing our notation in Section \ref{sec:notation}, we define what is meant by probabilistic forecast reconciliation for hierarchical time series in Section \ref{sec:definitions}.
+First, we provide a new definition for coherency of point forecasts, and the reconciliation of a set of incoherent point forecasts, using  concepts related to vector spaces and measure theory.
+Based on these, we provide a rigorous definition for probabilistic forecast reconciliation, and how we can reconcile the incoherent forecast densities in practice.
+
 Further, due to the aggregation structure of the hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate.
-We discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation and also in the evaluation of their predictive performances.
-In addition to that, we provide theoretical results on probabilistic forecast reconciliation in the Gaussian framework which is followed by a simulation study to show the importance of reconciliation in the probabilistic framework.
+In Section \ref{sec:reconciliation}, we discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation, and in Section \ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts.
 
-	Rest of the paper is structured as follows.
-We start with introducing the notations in section 2.
-In section 3 we provide our definitions for coherency which is followed by the definitions for forecast reconciliation in section 4.
-Section 5 discusses the methods that can be used for evaluation of probabilistic hierarchical forecasts.
-Section 6 consists the theoretical results followed by the simulation study on probabilistic forecast reconciliation in the Gaussian framework and we enclose with the remarkable conclusions in section 7.
+Some theoretical results on probabilistic forecast reconciliation in the Gaussian framework are given in Section \ref{sec:gaussian}, including a simulation study to show the importance of reconciliation in the probabilistic framework.
 
-	\section{Notations}\label{sec:notation}
+We conclude with some thoughts on extensions and limitations in Section \ref{sec:conclusions}.
 
-	We first introduce notations which mostly follow \citet{Wickramasuriya2017}.
-Suppose $\mathbold{y}_t \in \bm{\mathbb{R}}^n$ comprising all observations of the whole hierarchy at time $t$ and $\mathbold{b}_t \in \bm{\mathbb{R}}^m$ comprising only the bottom level observations at  time $t$.
+\section{Notation}\label{sec:notation}
+
+Our notation largely follows that introduced in \citet{Wickramasuriya2017}.
+Suppose $\bm{y}_t \in \bm{\mathbb{R}}^n$ comprises all observations of the hierarchy at time $t$ and $\bm{b}_t \in \bm{\mathbb{R}}^m$ comprises only the bottom level observations at time $t$.
 Then due to the aggregation nature of the hierarchy we have,
-
 \begin{equation}
-	\mathbold{y}_t = \mathbold{Sb}_t,
+  \bm{y}_t = \bm{Sb}_t,
 \end{equation}
-	where $\mathbold{S}$ is a $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold.
+where $\bm{S}$ is a $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold.
 
@@
 At a particular time $t$, let $y_{Tot,t}$ denote the observation at level 0; $y_{A,t}, y_{B,t} $ denote observations at level 1; and $y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}$ denote observations at level 2.
-Then $\mathbold{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, \\$\mathbold{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and $$ \mathbold{S} = \begin{pmatrix} 1& 1 &1 &1  \\ 1 &1 & 0 &0 \\   0&0  & 1 & 1 \\ & & I_4 &   \end{pmatrix}, $$ where $I_4$ is a $4$-dimension identity matrix.
+Then $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, \\$\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and $$ \bm{S} = \begin{pmatrix} 1& 1 &1 &1  \\ 1 &1 & 0 &0 \\   0&0  & 1 & 1 \\ & & I_4 &   \end{pmatrix}, $$ where $I_4$ is a $4$-dimension identity matrix.
 
@@
 Consider a simple hierarchy with two bottom level series $A$ and $B$ that add up to the top level series $Tot$.
-Suppose the forecasts at time $t+h$ of these series are given by $\mathbold{\breve{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$ and $\mathbold{\breve{y}}_{t+h} \in \bm{\mathbb{R}}^3$.
+Suppose the forecasts at time $t+h$ of these series are given by $\bm{\breve{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$ and $\bm{\breve{y}}_{t+h} \in \bm{\mathbb{R}}^3$.
 Due to the aggregation constraint of the hierarchy we have $\breve{y}_{Tot,t+h}=\breve{y}_{A,t+h}+\breve{y}_{B,t+h}$.
-This implies, even though  $\mathbold{\breve{y}}_{t+h}$ is in $\bm{\mathbb{R}}^3$, the points actually lie in $\bm{\mathbb{C}}^2$, which is a two dimensional subspace within that $\bm{\mathbb{R}}^3$ space.
-Therefore, for any $\mathbold{\breve{y}}_{t+h} \in \bm{\mathbb{N}}$ have a zero probability.
+This implies, even though  $\bm{\breve{y}}_{t+h}$ is in $\bm{\mathbb{R}}^3$, the points actually lie in $\bm{\mathbb{C}}^2$, which is a two dimensional subspace within that $\bm{\mathbb{R}}^3$ space.
+Therefore, for any $\bm{\breve{y}}_{t+h} \in \bm{\mathbb{N}}$ have a zero probability.
 I.e.
-$f(\mathbold{\breve{y}}_{t+h})=0$ for any $\mathbold{\breve{y}}_{t+h} \in \bm{\mathbb{N}}$.
+$f(\bm{\breve{y}}_{t+h})=0$ for any $\bm{\breve{y}}_{t+h} \in \bm{\mathbb{N}}$.
 
@@
 $$ 
-	\mathbold{S} = 
+\bm{S} = 
 \begin{pmatrix} 
@@
 \quad \text{and} \quad 
-	\mathbold{R} = 
+\bm{R} = 
 \begin{pmatrix}  

### 2018-03-06 ProbabilisticCoherence.tex
Updated sections 2 and 3

@@
 Our notation largely follows that introduced in \citet{Wickramasuriya2017}.
-Suppose $\bm{y}_t \in \bm{\mathbb{R}}^n$ comprises all observations of the hierarchy at time $t$ and $\bm{b}_t \in \bm{\mathbb{R}}^m$ comprises only the bottom level observations at time $t$.
-Then due to the aggregation nature of the hierarchy we have,
+Suppose $\bm{y}_t \in \mathbb{R}^n$ comprises all observations of the hierarchy at time $t$ and $\bm{b}_t \in \mathbb{R}^m$ comprises only the bottom level observations at time $t$.
+Then due to the aggregation nature of the hierarchy we have
 \begin{equation}
@@
 \end{equation}
-where $\bm{S}$ is a $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold.
+where $\bm{S}$ is an $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold.
 
-\noindent 
-To understand the notations clearly, consider the hierarchy given in Figure 1.
+In any hierarchy, the most aggregated level is labelled level 0, the second most aggregated level is labelled level 1 and so on.
+
+Consider the hierarchy given in Figure \ref{fig1}.
+
 \begin{figure}[H]
@@
   \end{center}
-	\caption{Two level hierarchical diagram}
+  \caption{Two level hierarchical diagram}\label{fig1}
 \end{figure}
-\noindent
-In any hierarchy, the most aggregated level is termed as level 0, the second most aggregated level is termed as level 1 and so on.
+
 This example consists of two levels.
-At a particular time $t$, let $y_{Tot,t}$ denote the observation at level 0; $y_{A,t}, y_{B,t} $ denote observations at level 1; and $y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}$ denote observations at level 2.
-Then $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, \\$\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and $$ \bm{S} = \begin{pmatrix} 1& 1 &1 &1  \\ 1 &1 & 0 &0 \\   0&0  & 1 & 1 \\ & & I_4 &   \end{pmatrix}, $$ where $I_4$ is a $4$-dimension identity matrix.
+At a particular time $t$, let $y_{Tot,t}$ denote the observation at level~0; $y_{A,t}, y_{B,t} $ denote observations at level~1; and $y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}$ denote observations at level~2.
+Then $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and
+$$ 
+  \bm{S} = \begin{pmatrix} 
+               1& 1 &1 &1  \\ 
+               1 &1 & 0 &0 \\   
+               0&0  & 1 & 1 \\ 
+               & \multicolumn{2}{c}{I_4} &   
+           \end{pmatrix}, 
+$$ 
+where $I_4$ is a $4$-dimension identity matrix.
 
@@
 
-The main purpose of this section is to provide formal definitions for coherent forecasts.
-We first give an alternative definition for coherent point forecasts using the properties of vector spaces which is then followed by the definition of coherent probabilistic forecasts.
+While coherent point forecasts have been discussed many times previously, the definitions of coherence previously given are vague and are not easily extended to the situation of probabilistic forecasting.
+
+We first give a new definition for coherent point forecasts using the properties of vector spaces, and then provide a definition of coherent probabilistic forecasts.
 
 \begin{definition}[Coherent subspace]
-	Let $\bm{\mathbb{C}}^m$ is a $m$-dimensional subspace of $\bm{\mathbb{R}}^n$, $\bm{\mathbb{C}}^m < \bm{\mathbb{R}}^n$.
-$\bm{\mathbb{C}}^m$ is said to be a coherent space, if it is spanned by the columns of $\bm{S}$.
+Suppose an $n$-dimensional time series $\bm{y}_t \in \mathbb{R}^n$ is subject to the linear aggregation constraint $\bm{y}_t = \bm{S}\bm{b}_t$ where $\bm{b}_t \in \mathbb{R}^m$ and $\bm{S}$ is an $n \times m$ constant matrix.
+Let $\mathbb{C}^m$ be an $m$-dimensional subspace of $\mathbb{R}^n$, where $\mathbb{C}^m < \mathbb{R}^n$.
+Then $\mathbb{C}^m$ is said to be a coherent space if it is spanned by the columns of $\bm{S}$.
 \end{definition}
 
-It is worth to notice that the coherent space $\bm{\mathbb{C}}^m$ is equivalent to the column space of $\bm{S}$ which we denote by $\mathscr{C}(\bm{S})$.
-Further the space orthogonal to $\bm{\mathbb{C}}^m$ is denoted by $\bm{\mathbb{N}}^{n-m}$ and it is equivalent to the null space of $\bm{S}$.
+Notice that the coherent space $\mathbb{C}^m$ is equivalent to the column space of $\bm{S}$, which we denote by $\mathscr{C}(\bm{S})$.
+Further, the space orthogonal to $\mathbb{C}^m$ is equivalent to the null space of $\bm{S}$, which we denote by $\bm{\mathbb{N}}^{n-m}$.
 
 \begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
-	Suppose $\bm{\breve{y}}_{t+h} \in \mathbb{R}^n$ consists point forecasts of each series in the hierarchy at time $t+h$.
-$\bm{\breve{y}}_{t+h}$ is said to be \textit{Coherent} if $\bm{\breve{y}}_{t+h} \in \bm{\mathbb{C}}$.
+	Suppose $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ denotes point forecasts of each series in the hierarchy at time $t+h$.
+Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathbb{C}$.
 \end{definition}
@@
 \begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
-	Let $(\bm{\mathbb{R}}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability triple where $\mathscr{F}^m$ is sigma algebra on $\bm{\mathbb{R}}^m$.
-Then, $(\bm{\mathbb{C}}, \mathscr{F}_{\bm{S}}, \breve{\nu})$ is said to be coherent probability measure space iff,
-	$$\breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall \quad \bm{A} \in \mathscr{F}^m,$$ 
+	Let $(\mathbb{R}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability triple where $\mathscr{F}^m$ is a $\sigma$-algebra on $\mathbb{R}^m$.
+Then, $(\mathbb{C}, \mathscr{F}_{\bm{S}}, \breve{\nu})$ is said to be a coherent probability measure space iff
+	$$
+      \breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall  \bm{A} \in \mathscr{F}^m,
+    $$ 
 	where $\bm{S}(\bm{A})$ denotes the image of subset $\bm{A}$ under $\bm{S}$. 
 \end{definition}
+
+We illustrate Definition \ref{def:cohprob} in Figure \ref{fig2}, showing $\bm{S}$ mapping any set $\bm{A}\in\mathbb{R}^m$ to the coherent space.
 
@@
 		\node at (4,5) {$\mathbb{R}^n$(codomain of $\bm{S}$)};
-		\node at (4,1.0) {$\bm{\mathbb{C}}^m$};
+		\node at (4,1.0) {$\mathbb{C}^m$};
 		%\node[bullet,label=below:$f(x)$] at (4,2.5){};
@@
 	\end{center}
-	\caption{Any set $\bm{A} \in \mathbb{R}^m$ will be mapped to the $\bm{\mathbb{C}}^m$ through the mapping $\bm{S}$}
+	\caption{Any set $\bm{A} \in \mathbb{R}^m$ will be mapped to $\mathbb{C}^m$ through the mapping $\bm{S}$}\label{fig2}
 \end{figure}
 
-Definition (\ref{def:cohprob}) implies the probability measure on $\bm{\mathbb{C}}^m$ is equivalent to the probability measure on $(\bm{\mathbb{R}}^m, \bm{\mathscr{F}}^m)$.
-Hence, there is no density anywhere outside the linear subspace $\bm{\mathbb{C}}^m$.
-That is, a \textit{Coherent probability density forecast} is any density $\bm{f}(\bm{\breve{y}}_{t+h})$ such that $\bm{f}(\bm{\breve{y}}_{t+h})=0$ for all $\bm{\breve{y}}_{t+h} \in \bm{\mathbb{N}}^{n-m}$.
-Following example will help to understand these definitions more clearly.
+Definition \ref{def:cohprob} implies the probability measure on $\mathbb{C}^m$ is equivalent to the probability measure on $(\mathbb{R}^m, \bm{\mathscr{F}}^m)$.
+Hence, there is no density anywhere outside the linear subspace $\mathbb{C}^m$.
+That is, a \textit{coherent probability density forecast} is any density $\bm{f}(\breve{\bm{y}}_{t+h})$ such that $\bm{f}(\breve{\bm{y}}_{t+h})=0$ for all $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}^{n-m}$.
 
-\subsubsection*{Example 1}
+The following example will help to understand these definitions more clearly.
 
 Consider a simple hierarchy with two bottom level series $A$ and $B$ that add up to the top level series $Tot$.
-Suppose the forecasts at time $t+h$ of these series are given by $\bm{\breve{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$ and $\bm{\breve{y}}_{t+h} \in \bm{\mathbb{R}}^3$.
+Suppose the forecasts of these series at time $t+h$ are given by $\breve{\bm{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$.
 Due to the aggregation constraint of the hierarchy we have $\breve{y}_{Tot,t+h}=\breve{y}_{A,t+h}+\breve{y}_{B,t+h}$.
-This implies, even though  $\bm{\breve{y}}_{t+h}$ is in $\bm{\mathbb{R}}^3$, the points actually lie in $\bm{\mathbb{C}}^2$, which is a two dimensional subspace within that $\bm{\mathbb{R}}^3$ space.
-Therefore, for any $\bm{\breve{y}}_{t+h} \in \bm{\mathbb{N}}$ have a zero probability.
-I.e.
-$f(\bm{\breve{y}}_{t+h})=0$ for any $\bm{\breve{y}}_{t+h} \in \bm{\mathbb{N}}$.
+This implies that, even though  $\breve{\bm{y}}_{t+h} \in \mathbb{R}^3$, the points actually lie in $\mathbb{C}^2$, which is a two dimensional subspace within that $\mathbb{R}^3$ space.
+Therefore, any $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}$ is impossible, so that $f(\breve{\bm{y}}_{t+h})=0$ for any $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}$.
 
-For a particular coherent subspace $\bm{\mathbb{C}}^m$, there exist several distinct basis vectors.
-For example, in the smallest hierarchy considered above, $\left\{\begin{pmatrix} 1&1&0 \end{pmatrix}', \begin{pmatrix} 1&0&1 \end{pmatrix}'\right\}$, $\left\{\begin{pmatrix} 1&0&1 \end{pmatrix}',\\ \begin{pmatrix}
-0&1&-1 \end{pmatrix}'\right\}$ and the singular value decomposition of these two are some alternative basis vectors that spans the same $\bm{\mathbb{C}}^m$.
-Given a basis for $\bm{\mathbb{C}}^m$, every series of the hierarchy can be linearly determined as a linear combination of that basis vectors.
-We referred to the coefficients of these linear combinations as the \textit{basis series}.
-It is apparent that these basis series are $m$ dimensional and linearly independent in a given hierarchy.
-For example, in the smallest hierarchy, $(\bm{A,B})$ and $(\bm{Tot,A})$ are the basis series corresponds to the basis vectors $\left\{\begin{pmatrix} 1&1&0 \end{pmatrix}', \begin{pmatrix} 1&0&1 \end{pmatrix}'\right\}$ and $\left\{\begin{pmatrix} 1&0&1 \end{pmatrix}', \begin{pmatrix}
-0&1&-1 \end{pmatrix}'\right\}$ respectively. Thus it is clear that the set of bottom level series is a basis series that corresponds to the column vectors of $\bm{S}$.
+For a particular coherent subspace $\mathbb{C}^m$, there exist several distinct basis vectors. For example, in the small hierarchy considered above, 
+ $\{(1 ~1 ~0)', (1 ~0 ~1)'\}$, 
+ $\{(1 ~ 0 ~ 1)',(0~1~-\!\!1)'\}$ 
+and the singular value decomposition of these two are some alternative basis vectors that span the same $\mathbb{C}^m$.
+Given a basis for $\mathbb{C}^m$, every series of the hierarchy can be linearly determined as a linear combination of those basis vectors.
+We refer to the coefficients of these linear combinations as the \textit{basis series}.
+It is apparent that these basis series are $m$-dimensional and linearly independent in a given hierarchy.
+For example, in the smallest hierarchy, $(A,B)$ and $(Tot,A)$ are the basis series corresponding to the basis vectors
+ $\{(1 ~1 ~0)', (1 ~0 ~1)'\}$, 
+ $\{(1 ~ 0 ~ 1)',(0~1~-\!\!1)'\}$
+respectively. Thus it is clear that the set of bottom level series is a basis series that corresponds to the column vectors of $\bm{S}$.
 
-An important thing to notice here is, since the basis are not unique for a give coherent subspace, the definition (\ref{def:cohprob}) is not unique and one can redefine the coherent probabilistic forecasts with respect to any basis.
-However, we stick to the definition (\ref{def:cohprob}) and consider the basis defined by the columns of $\bm{S}$ in what follows.
+Because the basis is not unique for a given coherent subspace, Definition \ref{def:cohprob} is not unique, and one can redefine the coherent probabilistic forecasts with respect to any basis.
+However, we stick to Definition \ref{def:cohprob} and consider the basis defined by the columns of $\bm{S}$ in what follows.
 
-It is also worth to mention that the definition (\ref{def:cohpoint}) and (\ref{def:cohprob}) facilitate extension to the forecast reconciliation which we talk about in the next section.
-In contrast to our definition, \citet{BenTaieb2017} defines the coherent probabilistic forecasts in terms of convolution.
-According to their definition, if the forecasts are coherent, then the convolution of forecast distributions of disaggregate series is same as the forecast distribution of the corresponding aggregate series.
+Definitions \ref{def:cohpoint} and \ref{def:cohprob} facilitate extension to probabilistic forecast reconciliation which we discuss in the next section.
+In contrast to our definition, \citet{BenTaieb2017} define coherent probabilistic forecasts in terms of convolutions.
+According to their definition, if the forecasts are coherent, then the convolution of forecast distributions of disaggregate series is identical to the forecast distribution of the corresponding aggregate series.
+While this is consistent with our definition, it is not easy to extend their definition to deal with probabilistic reconciliation.
 
@@
 
-Previous studies on point forecast literature have shown that the reconciliation provides better coherent forecasts than the conventional bottom-up and top-down methods (\cite{Hyndman2011}; \cite{VanErven2015a}; \cite{Wickramasuriya2017}).
-However, not extended in the context of probabilistic forecasts in published literature.
-Thus our main focus is to rigorously define the probabilistic forecast reconciliation and discuss how that definition can be used in practice.
+Previous studies on coherent point forecasting have shown that reconciliation provides better coherent forecasts than the conventional bottom-up and top-down methods \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017}.
+However, this idea has not been explored in the context of probabilistic forecasting.
+Consequently, we Thus our main focus is to rigorously define the probabilistic forecast reconciliation and discuss how that definition can be used in practice.
 
@@
 \begin{definition}\label{def:reconpoint}
-	Let $\bm{g}:\bm{\mathbb{R}}^n \rightarrow \bm{\mathbb{R}}^m $ and $\hat{\bm{y}}_{t+h} \in \bm{\mathbb{R}}^n$ be any set of incoherent forecasts at time $t+h$.
+	Let $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m $ and $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$ be any set of incoherent forecasts at time $t+h$.
 Then $\tilde{\bm{b}}_{t+h}$ is said to be reconciled bottom level forecasts if
@@
 	\end{equation}
-	where $\bm{g}(\hat{\bm{y}}_{t+h})$ is the image of $\hat{\bm{y}}_{t+h}$ under $\bm{g}$ on $\bm{\mathbb{R}}^m$.
-The reconciled forecasts for the whole hierarchy is then given by $\tilde{\bm{y}}_{t+h}=\bm{S} \circ \bm{g}(\hat{\bm{y}}_{t+h})$ such that $\tilde{\bm{y}}_{t+h} \in \bm{\mathbb{C}}^m$, where $\bm{S}\circ \bm{g}(.)$ is a projection of $\bm{g}(.)$ onto the $\bm{\mathbb{C}}^m$.
+	where $\bm{g}(\hat{\bm{y}}_{t+h})$ is the image of $\hat{\bm{y}}_{t+h}$ under $\bm{g}$ on $\mathbb{R}^m$.
+The reconciled forecasts for the whole hierarchy is then given by $\tilde{\bm{y}}_{t+h}=\bm{S} \circ \bm{g}(\hat{\bm{y}}_{t+h})$ such that $\tilde{\bm{y}}_{t+h} \in \mathbb{C}^m$, where $\bm{S}\circ \bm{g}(.)$ is a projection of $\bm{g}(.)$ onto the $\mathbb{C}^m$.
 \end{definition}
@@
 In other words, if $\bm{g}$ is a non-linear function, then the reconciliation of $\hat{\bm{y}}_{t+h}$ will be non-linear.
-On the other hand, if $\bm{g}$ is a linear function, then $\bm{S}\circ \bm{g}(.)$ will linearly projects incoherent point forecasts onto $\bm{\mathbb{C}}^m$.
+On the other hand, if $\bm{g}$ is a linear function, then $\bm{S}\circ \bm{g}(.)$ will linearly projects incoherent point forecasts onto $\mathbb{C}^m$.
 Latter was the main focus in previous studies in hierarchical point forecasting, where $\bm{g}$ is considered as a $m \times n$ matrix $\bm{P}$ and thus $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$.
@@
 In the following content we provide an alternative explanation for linear reconciliation based on definition (\ref{def:reconpoint}).
-Let $\bm{R} \in \bm{\mathbb{R}}^{n \times (n-m)}$ consists the columns that spans $\bm{\mathbb{N}}^{n-m}$ which is orthogonal to $\bm{\mathbb{C}}^m$.
+Let $\bm{R} \in \mathbb{R}^{n \times (n-m)}$ consists the columns that spans $\bm{\mathbb{N}}^{n-m}$ which is orthogonal to $\mathbb{C}^m$.
 Note that $\bm{R}$ is also not unique and one example is a matrix whose columns represent the aggregation constraints for a given hierarchy.
@@
 $$
-\noindent
+
 Further let $\{\bm{s}_1,...,\bm{s}_m\}$ and $\{\bm{r}_1,...,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively.
-Then $\bm{B}=\{\bm{s}_1,...,\bm{s}_m, \bm{r}_1,...,\bm{r}_{n-m}\}$ is a basis for $\bm{\mathbb{R}}^n$.
+Then $\bm{B}=\{\bm{s}_1,...,\bm{s}_m, \bm{r}_1,...,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$.
 Now, using the insights of definition (\ref{def:reconpoint}), we can use the following steps to reconcile the point forecasts.
@@
 
-For a given incoherent set of point forecasts $\hat{\bm{y}}_{t+h} \in \bm{\mathbb{R}}^n$, first we find the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$.
+For a given incoherent set of point forecasts $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$, first we find the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$.
 Let $\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}'$ denote these coordinates.
@@
 This step directly follows by the definition for coherent forecasts.
-That is, to obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \bm{\mathbb{R}}^n$ to the $\bm{\mathbb{C}}^m$ through $\bm{S}$.
+That is, to obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \mathbb{R}^n$ to the $\mathbb{C}^m$ through $\bm{S}$.
 Thus we have,
 \begin{equation}
-\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \bm{\mathbb{C}}^m<\bm{\mathbb{R}}^n.
+\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \mathbb{C}^m<\mathbb{R}^n.
 \end{equation}
@@
 
-Let $\bm{\breve{Y}}$ and $\bm{Y}$ be a $n$-dimensional random vectors from the predictive distribution $\bm{F}$ and the true distribution $\bm{G}$.
+Let $\breve{\bm{Y}}$ and $\bm{Y}$ be a $n$-dimensional random vectors from the predictive distribution $\bm{F}$ and the true distribution $\bm{G}$.
 Further let $\bm{y}$ be a $n$-dimensional realization.
-Then the scoring rule is a numerical value $S(\bm{\breve{Y}},\bm{y})$ assign to each pair $(\bm{\breve{Y}},\bm{y})$ and the proper scoring rule is defined as,
+Then the scoring rule is a numerical value $S(\breve{\bm{Y}},\bm{y})$ assign to each pair $(\breve{\bm{Y}},\bm{y})$ and the proper scoring rule is defined as,
 \begin{equation}\label{eq:(3.1.)}
-\E_{\bm{G}}[S(\bm{Y},\bm{y})] \le \E_{\bm{G}}[S(\bm{\breve{Y}},\bm{y})],
+\E_{\bm{G}}[S(\bm{Y},\bm{y})] \le \E_{\bm{G}}[S(\breve{\bm{Y}},\bm{y})],
 \end{equation}
@@
 		\text{Energy score}    &
-		$\text{eS}(\bm{\breve{Y}}_{T+h},\bm{y}_{T+h}) =
+		$\text{eS}(\breve{\bm{Y}}_{T+h},\bm{y}_{T+h}) =
 		\E_{\breve{\bm{F}}}
@@
 \begin{equation} \label{eq:(5.1)}
-\text{eS}(\bm{\breve{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
+\text{eS}(\breve{\bm{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
 \end{equation}
@@
 \begin{equation}
-Ss[S_B(.)] = \frac{S_B(\bm{Y},\bm{y})^{\text{ref}} - S_B(\bm{\breve{Y}},\bm{y})}{S_B(\bm{Y},\bm{y})^{\text{ref}}}\times 100\%,
+Ss[S_B(.)] = \frac{S_B(\bm{Y},\bm{y})^{\text{ref}} - S_B(\breve{\bm{Y}},\bm{y})}{S_B(\bm{Y},\bm{y})^{\text{ref}}}\times 100\%,
 \end{equation}

### 2018-03-06 ProbabilisticCoherence.tex
Started on section 4

@@
 Traditional bottom-up, top-down and middle-out forecasting methods are not strictly reconciliation methods since they use only a part of the information from the hierarchy to produce coherent forecasts.
+
+Previous studies on coherent point forecasting have shown that reconciliation provides better coherent forecasts than the traditional bottom-up and top-down methods \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017}.
+However, this idea has not been explored in the context of probabilistic forecasting.
 
@@
 
-Previous studies on coherent point forecasting have shown that reconciliation provides better coherent forecasts than the conventional bottom-up and top-down methods \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017}.
-However, this idea has not been explored in the context of probabilistic forecasting.
-Consequently, we Thus our main focus is to rigorously define the probabilistic forecast reconciliation and discuss how that definition can be used in practice.
+Initially we define point forecast reconciliation, before extending the idea to the probabilistic setting.
 
@@
 
-Initially we define point forecast reconciliation as a groundwork to the probabilistic forecast reconciliation.
-
 \begin{definition}\label{def:reconpoint}
-	Let $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m $ and $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$ be any set of incoherent forecasts at time $t+h$.
-Then $\tilde{\bm{b}}_{t+h}$ is said to be reconciled bottom level forecasts if
+  Let $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$ be any set of incoherent forecasts at time $t+h$, and let 
   \begin{equation}
-	\tilde{\bm{b}}_{t+h}=\bm{g}(\hat{\bm{y}}_{t+h}),
+    \tilde{\bm{y}}_{t+h}=\bm{S} \circ \bm{g}(\hat{\bm{y}}_{t+h}),
   \end{equation} 
-	where $\bm{g}(\hat{\bm{y}}_{t+h})$ is the image of $\hat{\bm{y}}_{t+h}$ under $\bm{g}$ on $\mathbb{R}^m$.
-The reconciled forecasts for the whole hierarchy is then given by $\tilde{\bm{y}}_{t+h}=\bm{S} \circ \bm{g}(\hat{\bm{y}}_{t+h})$ such that $\tilde{\bm{y}}_{t+h} \in \mathbb{C}^m$, where $\bm{S}\circ \bm{g}(.)$ is a projection of $\bm{g}(.)$ onto the $\mathbb{C}^m$.
+  where $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m$.
+Then $\tilde{\bm{y}}_{t+h}$ is said to be ``reconciled'' if  $\tilde{\bm{y}}_{t+h} \in \mathbb{C}^m$, where $\bm{S}\circ \bm{g}(.)$ is a projection of $\bm{g}(.)$ onto $\mathbb{C}^m$.
 \end{definition}
 
-Importance of definition (\ref{def:reconpoint}) is that it facilitates for both linear and non-linear reconciliation.
+The importance of Definition \ref{def:reconpoint} is that it allows for both linear and non-linear reconciliation.
 In other words, if $\bm{g}$ is a non-linear function, then the reconciliation of $\hat{\bm{y}}_{t+h}$ will be non-linear.

### 2018-03-07 ProbabilisticCoherence.tex
Updated section 4

@@
 \mathtoolsset{showonlyrefs=true}
+
+\def\PQ{\begin{pmatrix}\bm{P}\\[-0.2cm]\bm{Q}\end{pmatrix}}
+\def\bt{\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\[-0.2cm]\tilde{\bm{t}}_{t+h}\end{pmatrix}}
 
@@
   \end{equation} 
-  where $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m$.
-Then $\tilde{\bm{y}}_{t+h}$ is said to be ``reconciled'' if  $\tilde{\bm{y}}_{t+h} \in \mathbb{C}^m$, where $\bm{S}\circ \bm{g}(.)$ is a projection of $\bm{g}(.)$ onto $\mathbb{C}^m$.
+  where $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m$ and $\bm{S}\circ \bm{g}(\cdot)$ is a projection of $\bm{g}(\cdot)$ onto $\mathbb{C}^m$.
+Then $\tilde{\bm{y}}_{t+h}$ is said to be ``reconciled'' if  $\tilde{\bm{y}}_{t+h} \in \mathbb{C}^m$.
 \end{definition}
 
-The importance of Definition \ref{def:reconpoint} is that it allows for both linear and non-linear reconciliation.
-In other words, if $\bm{g}$ is a non-linear function, then the reconciliation of $\hat{\bm{y}}_{t+h}$ will be non-linear.
-On the other hand, if $\bm{g}$ is a linear function, then $\bm{S}\circ \bm{g}(.)$ will linearly projects incoherent point forecasts onto $\mathbb{C}^m$.
-Latter was the main focus in previous studies in hierarchical point forecasting, where $\bm{g}$ is considered as a $m \times n$ matrix $\bm{P}$ and thus $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$.
+Definition \ref{def:reconpoint} allows for both linear and non-linear reconciliation.
+In other words, if $\bm{g}$ is a non-linear function, then the reconciliation of $\hat{\bm{y}}_{t+h}$ will be non-linear, while if $\bm{g}$ is a linear function, then $\bm{S}\circ \bm{g}(\cdot)$ will linearly project incoherent point forecasts onto $\mathbb{C}^m$.
+Previous studies in hierarchical point forecasting have only focussed on the linear case, $\bm{g}(\bm{y}) = \bm{P}\bm{y}$, where $\bm{P}$ is an $m \times n$ matrix, and so $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$.
 
-In the following content we provide an alternative explanation for linear reconciliation based on definition (\ref{def:reconpoint}).
-Let $\bm{R} \in \mathbb{R}^{n \times (n-m)}$ consists the columns that spans $\bm{\mathbb{N}}^{n-m}$ which is orthogonal to $\mathbb{C}^m$.
-Note that $\bm{R}$ is also not unique and one example is a matrix whose columns represent the aggregation constraints for a given hierarchy.
-Then for the hierarchy in example 1,
+Using Definition \ref{def:reconpoint}, we can now explain previous results for linear forecast reconciliation.
+Let $\bm{R} \in \mathbb{R}^{n \times (n-m)}$ comprise the columns that span $\bm{\mathbb{N}}^{n-m}$, which is orthogonal to $\mathbb{C}^m$.
+Note that $\bm{R}$ is not unique; one example is a matrix whose columns represent the aggregation constraints for a given hierarchy.
+For the hierarchy in example 1,
 $$ 
@@
 
-Further let $\{\bm{s}_1,...,\bm{s}_m\}$ and $\{\bm{r}_1,...,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively.
-Then $\bm{B}=\{\bm{s}_1,...,\bm{s}_m, \bm{r}_1,...,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$.
-Now, using the insights of definition (\ref{def:reconpoint}), we can use the following steps to reconcile the point forecasts.
+Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively.
+Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$.
+Now, using the insights of Definition \ref{def:reconpoint}, we can use the following steps to reconcile the point forecasts.
 
@@
 For a given incoherent set of point forecasts $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$, first we find the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$.
-Let $\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}'$ denote these coordinates.
-Note that $\tilde{\bm{b}}_{t+h}$ is a basis series which is really the reconciled bottom level series that corresponds to the coefficients of linear combination of the basis $\{\bm{s}_1,...,\bm{s}_m\}$.
-Similarly, $\tilde{\bm{t}}_{t+h}$ is another basis series corresponds to the coefficients of linear combination of the basis $\{\bm{r}_1,...,\bm{r}_{n-m}\}$.
+Let $(\tilde{\bm{b}}'_{t+h} , \tilde{\bm{t}}'_{t+h})'$ denote these coordinates.
+Note that $\tilde{\bm{b}}_{t+h}$ is a basis series which is equivalent to the reconciled bottom level series, and which corresponds to the linear combination coefficients of the basis $\{\bm{s}_1,\dots,\bm{s}_m\}$.
+Similarly, $\tilde{\bm{t}}_{t+h}$ is another basis series corresponding to the linear combination coefficients of the basis $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$.
 Then from basic properties of linear algebra it follows that,
-
 \[
-\begin{pmatrix}
-\bm{S} & \vdots& \bm{R}
-\end{pmatrix}
-\begin{pmatrix}
-\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}
-\end{pmatrix}'
+(\bm{S} ~ \vdots~ \bm{R})
+(\tilde{\bm{b}}'_{t+h},~ \tilde{\bm{t}}'_{t+h})'
 = \hat{\bm{y}}_{t+h},
@@
 \begin{equation}\label{4.3}
-\begin{pmatrix}
-\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}
-\end{pmatrix}' =
-\begin{pmatrix}
-\bm{S} & \vdots& \bm{R}
-\end{pmatrix}^{-1}
+(\tilde{\bm{b}}'_{t+h}, ~ \tilde{\bm{t}}'_{t+h})' =
+(\bm{S} ~ \vdots~ \bm{R})^{-1}
 \hat{\bm{y}}_{t+h}.
@@
 
-In order to find $\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}$, let $\bm{S}_{\bot}$ and $\bm{R}_{\bot}$ be the orthogonal complements of $\bm{S}$ and $\bm{R}$
-respectively. Then $\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}$ is given by,
+In order to find $(\bm{S} ~ \vdots~ \bm{R})^{-1}$, let $\bm{S}_{\bot}$ and $\bm{R}_{\bot}$ be the orthogonal complements of $\bm{S}$ and $\bm{R}$
+respectively. Then $(\bm{S} ~ \vdots~ \bm{R})^{-1}$ is given by,
 \begin{equation}
-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} = \begin{pmatrix}
+(\bm{S} ~ \vdots~ \bm{R})^{-1} = \begin{pmatrix}
 (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
@@
 
-This step directly follows by the definition for coherent forecasts.
-That is, to obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \mathbb{R}^n$ to the $\mathbb{C}^m$ through $\bm{S}$.
+This step directly follows from the definition for coherent forecasts.
+To obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \mathbb{R}^n$ to the $\mathbb{C}^m$ through $\bm{S}$.
 Thus we have,
 \begin{equation}
-\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \mathbb{C}^m<\mathbb{R}^n.
+\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \qquad \tilde{\bm{y}}_{t+h} \in \mathbb{C}^m<\mathbb{R}^n.
 \end{equation}
 
-Finding a suitable $\bm{R}_\bot$ with respect to a certain loss function will result optimally reconciled point forecasts of the hierarchy.
-Notice that, if $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$, then the definition for linear reconciliation of point forecasts in previous studies coincides with our explanation.
+Finding a suitable $\bm{R}_\bot$ with respect to a certain loss function will lead to optimally reconciled point forecasts of the hierarchy.
+If $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$, then the definition for linear reconciliation of point forecasts in previous studies coincides with our explanation.
 
-Further in our context, we need to find $\bm{R}_\bot$ such that $\bm{R}'_\bot \bm{S}$ is invertible.
-i.e, $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \bm{S}=\bm{I}$.
+In our context, we need to find $\bm{R}_\bot$ such that $\bm{R}'_\bot \bm{S}$ is invertible; i.e, $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \bm{S}=\bm{I}$.
 This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}.
 
-In their study, \citet{Hyndman2011} proposed to choose,
+\citet{Hyndman2011} proposed to choose
 \begin{equation*}
@@
 \end{equation*}
-where in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy is given by,
+where in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy are given by,
 \begin{equation}
@@
 \end{equation}
-They referred this to as OLS solution and the loss function they considered is equivalent to the euclidean norm between $\hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h}$, i.e.
+They referred this to as the OLS solution and the loss function they considered is equivalent to the Euclidean norm between $\hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h}$; i.e.
 $<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>$.
 
-According to a recent study by \citet{Wickramasuriya2017}, choosing $\bm{R}'_\bot = \bm{S}'\bm{W}^{-1}_{h}$ will minimize the trace of mean squared reconciled forecast errors under the property of unbiasedness where, $\bm{W}^{-1}_{h}$ is the variance of the incoherent forecast errors.
-This will result,
+According to a recent study by \citet{Wickramasuriya2017}, selecting $\bm{R}'_\bot = \bm{S}'\bm{W}^{-1}_{h}$ will minimize the trace of mean squared reconciled forecast errors under the property of unbiasedness, where $\bm{W}^{-1}_{h}$ is the variance of the incoherent forecast errors.
+This will result in
 \begin{equation*}
@@
 
-They referred this to as MinT solution.
-It is also worth to notice that the loss function they considered is equivalent to the Mahalanobis distance between $\hat{\bm{y}}_{T+h}$ and $\tilde{\bm{y}}_{T+h}$.
+They referred this to as the MinT solution.
+The loss function they considered is equivalent to the Mahalanobis distance between $\hat{\bm{y}}_{T+h}$ and $\tilde{\bm{y}}_{T+h}$.
 i.e.
@@
 
-In terms of probabilistic forecasts, the reconciliation implies finding the probability measure of the coherent forecasts using the information of incoherent probabilistic forecast measure.
+For probabilistic forecasts, reconciliation implies finding the probability measure of the coherent forecasts using the information from an incoherent probabilistic forecast measure.
 A more formal definition is given below.
@@
 \begin{definition} \label{def:reconprob}
-  Suppose $(\mathbb{R}^n, \mathscr{F}^n, \hat{\nu})$ be an incoherent probability triple and $(\mathbb{R}^m, \mathscr{F}^m, \nu^m)$ be a probability triple defined on $\mathbb{R}^m$.
+  Suppose $(\mathbb{R}^n, \mathscr{F}^n, \hat{\nu})$ is an incoherent probability triple and $(\mathbb{R}^m, \mathscr{F}^m, \nu^m)$ is a probability triple defined on $\mathbb{R}^m$.
 Let $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m $.
-Then the probability measure on reconciled bottom levels is such that,
+Then the probability measure on the reconciled bottom levels is such that
   \begin{equation}
@@
   \end{equation}
-
-  Further the reconciled probability measure of the whole hierarchy is given by,
+  Further the probability measure of the whole reconciled hierarchy is given by
   \begin{equation}
-  \tilde{\nu}(\bm{S}(\bm{A})) = \hat{\nu}(\bm{g}^{-1}(\bm{A})), \quad \forall \quad \bm{A} \in \mathscr{F}^m,
+  \tilde{\nu}(\bm{S}(\bm{A})) = \hat{\nu}(\bm{g}^{-1}(\bm{A})) \qquad \forall \bm{A} \in \mathscr{F}^m,
   \end{equation}
-  where $\bm{S}:\mathbb{R}^m \rightarrow \mathbb{C}^m$ and $\tilde{\nu}(.)$ is the probability measure on the measure space $(\mathbb{C}^m, \mathscr{F}_S)$.
+  where $\bm{S}:\mathbb{R}^m \rightarrow \mathbb{C}^m$ and $\tilde{\nu}(\cdot)$ is the probability measure on the measure space $(\mathbb{C}^m, \mathscr{F}_S)$.
 \end{definition}
 
-Since the above definition seems not to be straightforward in reconciling incoherent forecasts, the following content explains how this can be used in practice to obtain reconciled probabilistic forecasts for hierarchical time series.
+We now discuss how this definition can be used in practice to obtain reconciled probabilistic forecasts for hierarchical time series.
 
-Recall that $\hat{\bm{y}}_{t+h}$ is a set of incoherent point forecasts and the coordinates of that with respect to the basis $\bm{B}$ is given by \eqref{4.3}.
-Suppose $\hat{\bm{f}}(.)$ is the probability density of $\hat{\bm{y}}_{t+h}$.
-Our goal is to reconcile $\hat{\bm{f}}(.)$ such that the density lives on the $\mathbb{C}^m$.
-In order to obtain this reconciled density, we need to project $\hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ onto the $\mathbb{C}^m$ along the direction of $\mathbb{N}^{n-m}$.
+Recall that $\hat{\bm{y}}_{t+h}$ is a set of incoherent point forecasts and the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$ are given by \eqref{4.3}.
+Suppose $\hat{\bm{f}}(\cdot)$ is the probability density of $\hat{\bm{y}}_{t+h}$.
+Our goal is to reconcile $\hat{\bm{f}}(\cdot)$ such that the density lives on $\mathbb{C}^m$.
+In order to obtain this reconciled density, we need to project $\hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ onto $\mathbb{C}^m$ along the direction of $\mathbb{N}^{n-m}$.
 
-Let the density of coordinates of $\hat{\bm{y}}_{t+h}$ with respect to basis $\bm{B}$ is denoted by $\bm{f_B}(.)$. Then it follows from  \eqref{4.3} and the facts on density of transformed variables,
+Let the density of $\hat{\bm{y}}_{t+h}$ with respect to basis $\bm{B}$ be denoted by $\bm{f_B}(\cdot)$.
+Then it follows from  \eqref{4.3}, and standard results for densities of transformed variables, that
 \begin{equation}\label{4.5}
-\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad \Big|\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array}\Big|,
+\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \,\Big|\bm{S} ~ \vdots~ \bm{R}\Big|,
 \end{equation}
-where $|.|$ denote the determinant of a matrix.
-Now that we have the density of $\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}' $, the marginal density of $\tilde{\bm{b}}_{t+h}$ can be obtained by integrating \eqref{4.5} over the range of $\tilde{\bm{t}}_{t+h}$.
-This will result the reconciled density of the bottom level series $\tilde{\bm{b}}_{t+h}$.
-i.e.,
+where $|\cdot|$ denotes the determinant of a matrix.
+Now that we have the density of $(\tilde{\bm{b}}'_{t+h} , \tilde{\bm{t}}'_{t+h})'$, the marginal density of $\tilde{\bm{b}}_{t+h}$ can be obtained by integrating \eqref{4.5} over the range of $\tilde{\bm{t}}_{t+h}$.
+This will result in the reconciled density of the bottom level series $\tilde{\bm{b}}_{t+h}$,
 \begin{equation}\label{4.6}
-\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\int_{lim(\tilde{\bm{t}}_{t+h})}\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad \Big|\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array}\Big| \quad d\tilde{\bm{t}}_{t+h}.
+\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\int_{\lim(\tilde{\bm{t}}_{t+h})}\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h})\,  \Big|\bm{S} ~ \vdots~ \bm{R}\Big| \, d\tilde{\bm{t}}_{t+h}.
 \end{equation}
 
-Finally to get the reconciled density of the whole hierarchy, we simply follow the definition (\ref{def:cohprob}) and have,
+Finally to get the reconciled density of the whole hierarchy, we simply follow Definition \ref{def:cohprob} to obtain
 \begin{equation}\label{4.7}
@@
 \end{equation}
-This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the $\mathbb{C}^m<\mathbb{R}^n$.
-Following example illustrates how this method can be used to reconcile an incoherent Gaussian forecast distribution.
+This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the space $\mathbb{C}^m<\mathbb{R}^n$.
+The following example illustrates how this method can be used to reconcile an incoherent Gaussian forecast distribution.
 
@@
 Suppose $\mathscr{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h}) \overset{d}{\leftrightarrow} \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ is an incoherent forecast distribution at time $t+h$.
-Then from \eqref{4.5} it follows,
+Then from \eqref{4.5} it follows that
 \begin{equation*}
-\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \quad \Big|\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array}\Big| = \frac{\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) }{\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|}.
+\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \, \Big|\bm{S} ~ \vdots~ \bm{R}\Big| = \frac{\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) }{\Big|(\bm{S} ~ \vdots~ \bm{R})^{-1}\Big|}.
 \end{equation*}
-By substituting the Gaussian distribution function to $\bm{f_B}(.)$ we get,
+By substituting the Gaussian distribution function for $\bm{f_B}(\cdot)$ we get
 \begin{align*}
-\bm{f_B}(.)
+\bm{f_B}(\cdot)
 & =
-\frac{\exp\left\{-\frac{1}{2}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})' \bm{\hat{\Sigma}_{t+h}}^{-1}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
+\frac{\exp\left\{-\frac{1}{2}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})' \bm{\hat{\Sigma}_{t+h}}^{-1}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\bm{S} ~ \vdots~ \bm{R})^{-1}\Big|},\\
 & =
-\frac{\exp\left\{-\frac{1}{2}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)' \bm{\hat{\Sigma}_{t+h}}^{-1}\Big(\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|},\\
+\frac{\exp\left\{-\frac{1}{2}\Big((\bm{S} ~ \vdots~ \bm{R})\bt-\bm{\hat{\mu}}_{t+h}\Big)' \bm{\hat{\Sigma}_{t+h}}^{-1}\Big((\bm{S} ~ \vdots~ \bm{R})\bt-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\bm{S} ~ \vdots~ \bm{R})^{-1}\Big|},\\
 & =
-\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\begin{array}{ccc}\bm{S} & \vdots& \bm{R}\end{array})^{-1} \Big|}
-\exp \Big\{-\frac{1}{2}\Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big)'\\
-& \hspace*{1cm} \Big[\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}'\Big]^{-1}
-\Big(\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.
+\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\bm{S} ~ \vdots~ \bm{R})^{-1} \Big|}
+\exp \Big\{-\frac{1}{2}\Big(\bt-(\bm{S} ~ \vdots~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\Big)'\\
+& \hspace*{6cm} \Big[(\bm{S} ~ \vdots~ \bm{R})\bm{\hat{\Sigma}_{t+h}}(\bm{S} ~ \vdots~ \bm{R})'\Big]^{-1}
+\Big(\bt-(\bm{S} ~ \vdots~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.
 \end{align*}
-Recall that,
+Recall that
 $$
-\begin{pmatrix}\bm{S} & \vdots& \bm{R}\end{pmatrix}^{-1} =
+(\bm{S} ~ \vdots~ \bm{R})^{-1} =
 \begin{pmatrix}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot \end{pmatrix} =
@@
 $$
-where, $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ and $\bm{Q}=(\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot$. Then,
+where $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ and $\bm{Q}=(\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot$. Then
 \begin{align*}
-\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix} \Big|}
-\exp \Big\{&-\frac{1}{2}\Big[\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\mu}}_{t+h}\Big]'\Big[\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}'\Big]^{-1}\\
-&\Big[\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\ \tilde{\bm{t}}_{t+h}\end{pmatrix}-\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\mu}}_{t+h}\Big] \Big\},
+\bm{f_B}(\cdot)& =\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|\PQ \Big|}
+\exp \Big\{-\frac{1}{2}\Big[\bt-\PQ\bm{\hat{\mu}}_{t+h}\Big]'\\[-0.5cm]
+& \hspace*{7cm}
+\Big[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big]^{-1}\Big[\bt-\PQ\bm{\hat{\mu}}_{t+h}\Big] \Big\},\\[0.5cm]
+ & =\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big|^{\frac{1}{2}}}
+\exp \Big\{-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h} \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix}' &\\[-0.5cm]
+& \hspace*{7cm}
+ \Big[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big]^{-1}\begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix} \Big\}.
 \end{align*}
-\begin{align*}
-\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}'\Big|^{\frac{1}{2}}}
-\exp \Big\{&-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix}' \Big[\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}'\Big]^{-1}\\
-& \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix} \Big\}.
-\end{align*}
-Since, $\Big[\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}\bm{\hat{\Sigma}_{t+h}}\begin{pmatrix}\bm{P}\\\bm{Q}\end{pmatrix}'\Big] = \begin{pmatrix}
+Since $\Big[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big] = \begin{pmatrix}
 \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}' \\
 \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'
-\end{pmatrix}$ we have,
+\end{pmatrix}$ we have
 \begin{align*}
-\bm{f_B}(.)=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\begin{pmatrix}
+\bm{f_B}(\cdot)&=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\begin{pmatrix}
   \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}' \\
@@
   \end{pmatrix}\Big|^{\frac{1}{2}}}
-\exp \Big\{&-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix}'\\
-&\begin{pmatrix}
+\exp \Big\{-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix}'\\
+&\hspace*{7cm}\begin{pmatrix}
 \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}' \\
 \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'
-\end{pmatrix}^{-1}\\
-&\begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix} \Big\}.
+\end{pmatrix}^{-1}
+\begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix} \Big\}.
 \end{align*}
-$\bm{f_B}(.)$ gives the joint distribution of $\begin{pmatrix}\tilde{\bm{b}}'_{t+h} & \vdots& \tilde{\bm{t}}'_{t+h}\end{pmatrix}' $, which is a multivariate Gaussian distribution.
-Then from \eqref{4.6} and the properties of marginalization of multivariate Gaussian distribution it follows,
+This is the joint multivariate Gaussian distribution of $(\tilde{\bm{b}}'_{t+h} ~ \vdots~ \tilde{\bm{t}}'_{t+h})'$.
+Then from \eqref{4.6} and the properties of the multivariate Gaussian distribution, it follows that
 \begin{equation}\label{ex:2.1}
@@
 Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$ where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
-Then from \eqref{4.7} it follows that,
+Then from \eqref{4.7} it follows that
 \begin{equation}
@@
 Therefore, the reconciled Gaussian forecast distribution of the whole hierarchy is\\
-$\mathscr{N}(\bm{SP}\bm{\hat{\mu}}_{t+h}, \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}')$.
+$\mathscr{N}(\bm{SP}\bm{\hat{\mu}}_{t+h},~ \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}')$.
 
@@
   \caption{Scoring rules to evaluate multivariate forecast densities.
-$\breve{\bm{y}}_{T+h}$ and $\breve{\bm{y}}^*_{T+h}$ be two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with the density function $\breve{\bm{f}}(.)$ at time $T+h$ and $\bm{y}_{T+h}$ is the vector of realizations.
+$\breve{\bm{y}}_{T+h}$ and $\breve{\bm{y}}^*_{T+h}$ be two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with the density function $\breve{\bm{f}}(\cdot)$ at time $T+h$ and $\bm{y}_{T+h}$ is the vector of realizations.
 Further $\breve{Y}_{T+h,i}$ and $\breve{Y}_{T+h,j}$ are $i$th and $j$th components of the vector $\breve{\bm{Y}}_{T+h}$.
@@
 In addition to that we use Skill score \citep{Gneiting2007} for any comparison.
-For a given forecasting method, evaluated by a particular scoring rule $S(.)$ , the skill score will be calculated as follows,
+For a given forecasting method, evaluated by a particular scoring rule $S(\cdot)$ , the skill score will be calculated as follows,
 \begin{equation}
-Ss[S_B(.)] = \frac{S_B(\bm{Y},\bm{y})^{\text{ref}} - S_B(\breve{\bm{Y}},\bm{y})}{S_B(\bm{Y},\bm{y})^{\text{ref}}}\times 100\%,
+Ss[S_B(\cdot)] = \frac{S_B(\bm{Y},\bm{y})^{\text{ref}} - S_B(\breve{\bm{Y}},\bm{y})}{S_B(\bm{Y},\bm{y})^{\text{ref}}}\times 100\%,
 \end{equation}
-where $S_B(.)$ is average score over $B$ samples and $S_B(\bm{Y},\bm{y})^{\text{ref}}$ is the average score of the reference forecasting methods.
-Thus $Ss[S_B(.)]$ gives the percentage improvement of the preferred forecasting method relative to the reference method.
-Any negative value of $Ss[S_B(.)]$ indicate that the method we compared is poor than the reference method, whereas any positive value indicates that method is superior to the reference method.
+where $S_B(\cdot)$ is average score over $B$ samples and $S_B(\bm{Y},\bm{y})^{\text{ref}}$ is the average score of the reference forecasting methods.
+Thus $Ss[S_B(\cdot)]$ gives the percentage improvement of the preferred forecasting method relative to the reference method.
+Any negative value of $Ss[S_B(\cdot)]$ indicate that the method we compared is poor than the reference method, whereas any positive value indicates that method is superior to the reference method.
 

### 2018-03-21 ProbabilisticCoherence.tex
Updated section 5

@@
 \usepackage{monashwp}
-\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx, mathrsfs, float, booktabs}
+\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx}
+\usepackage{mathrsfs, float, booktabs,todonotes}
 \usepackage[bb=boondox]{mathalfa}
@@
 The only relevant paper we are aware of is \citet{BenTaieb2017}, who recently proposed an algorithm to produce coherent probabilistic forecasts and applied it to UK electricity smart meter data.
-In their approach, a sample from the bottom level predictive distribution is first generated, and then aggregated to obtain coherent probabilistic forecasts of the upper levels of the hierarchy.
+In their approach, a sample from the bottom level forecast distribution is first generated, and then aggregated to obtain coherent probabilistic forecasts of the upper levels of the hierarchy.
 Hence this method is a bottom-up approach.
@@
 \begin{definition}[Coherent subspace]
-Suppose an $n$-dimensional time series $\bm{y}_t \in \mathbb{R}^n$ is subject to the linear aggregation constraint $\bm{y}_t = \bm{S}\bm{b}_t$ where $\bm{b}_t \in \mathbb{R}^m$ and $\bm{S}$ is an $n \times m$ constant matrix.
+Suppose an $n$-dimensional time series $\bm{y}_t \in \mathbb{R}^n$ is subject to the linear aggregation constraint $\bm{y}_t = \bm{S}\bm{b}_t$, where $\bm{b}_t \in \mathbb{R}^m$ and $\bm{S}$ is an $n \times m$ constant matrix.
 Let $\mathbb{C}^m$ be an $m$-dimensional subspace of $\mathbb{R}^n$, where $\mathbb{C}^m < \mathbb{R}^n$.
@@
 \begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
-  Let $(\mathbb{R}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability triple where $\mathscr{F}^m$ is a $\sigma$-algebra on $\mathbb{R}^m$.
+  Let $(\mathbb{R}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability triple, where $\mathscr{F}^m$ is a $\sigma$-algebra on $\mathbb{R}^m$.
 Then, $(\mathbb{C}, \mathscr{F}_{\bm{S}}, \breve{\nu})$ is said to be a coherent probability measure space iff
@@
 \end{equation*}
-where in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy are given by,
+where, in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy are given by,
 \begin{equation}
@@
 
-Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$ where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
+Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
 Then from \eqref{4.7} it follows that
@@
 
-The necessary final step in hierarchical forecasting is to make sure that our forecast distributions are accurate enough to predict the uncertain future.
-In general, forecasters prefer to maximize the sharpness of the predictive distribution subject to the calibration \citep{Gneiting2014}.
+The necessary final step in hierarchical forecasting is to make sure that our forecast distributions are accurately predicting the uncertain future.
+In general, forecasters prefer to maximize the sharpness of the forecast distribution subject to the calibration \citep{Gneiting2014}.
 Therefore the probabilistic forecasts should be evaluated with respect to these two properties.
@@
 Calibration refers to the statistical compatibility between probabilistic forecasts and realizations.
-In other words, random draws from a perfectly calibrated predictive distribution should be equivalent to the realizations.
-On the other hand, sharpness refers to the spread or the concentration of prediction distributions and it is a property of forecasts only.
-The more concentrated the predictive distributions, the sharper the forecasts are \citep{Gneiting2008}.
+In other words, random draws from a perfectly calibrated forecast distribution should be equivalent in distribution to the realizations.
+On the other hand, sharpness refers to the spread or the concentration of the prediction distributions and it is a property of the forecasts only.
+The more concentrated the forecast distributions, the sharper the forecasts \citep{Gneiting2008}.
 However, independently assessing the calibration and sharpness will not help to properly evaluate the probabilistic forecasts.
-Therefore to assess these properties simultaneously, we use scoring rules.
+Therefore we need to assess these properties simultaneously using scoring rules.
 
-Scoring rules are summary measures obtained based on the relationship between predictive distribution and the realizations.
-In some studies, researchers take the scoring rules to be positively oriented which they would wish to maximize \citep{Gneiting2007}.
-However, scoring rules were also defined to be negatively oriented which forecasters wish to minimize \citep{Gneiting2014}.
-We consider these negatively oriented scoring rules to evaluate probabilistic forecasts in hierarchical time series.
+Scoring rules are summary measures obtained based on the relationship between the forecast distributions and the realizations.
+In some studies, researchers take the scoring rules to be positively oriented, in which case the scores should be maximized \citep{Gneiting2007}.
+However, scoring rules have also been defined to be negatively oriented, and then the scores should be minimized \citep{Gneiting2014}.
+We consider negatively oriented scoring rules to evaluate probabilistic forecasts in hierarchical time series.
 
-Let $\breve{\bm{Y}}$ and $\bm{Y}$ be a $n$-dimensional random vectors from the predictive distribution $\bm{F}$ and the true distribution $\bm{G}$.
-Further let $\bm{y}$ be a $n$-dimensional realization.
-Then the scoring rule is a numerical value $S(\breve{\bm{Y}},\bm{y})$ assign to each pair $(\breve{\bm{Y}},\bm{y})$ and the proper scoring rule is defined as,
+Let $\breve{\bm{Y}}$ and $\bm{Y}$ be $n$-dimensional random vectors from the forecast distribution $\bm{F}$ and the true distribution $\bm{G}$, respectively.
+Further let $\bm{y}$ be an $n$-dimensional realization from $\bm{G}$.
+Then a scoring rule is a numerical value $S(\breve{\bm{Y}},\bm{y})$ assigned to each pair $(\breve{\bm{Y}},\bm{y})$.
+It is a ``proper'' scoring rule if
 \begin{equation}\label{eq:(3.1.)}
@@
 
-Table \ref{table:scoringrules} summarizes few existing proper scoring rules.
+Table \ref{table:scoringrules} summarizes a few existing proper scoring rules.
 
-\begin{table}[!b]
+\begin{table}[!bh]
   \caption{Scoring rules to evaluate multivariate forecast densities.
-$\breve{\bm{y}}_{T+h}$ and $\breve{\bm{y}}^*_{T+h}$ be two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with the density function $\breve{\bm{f}}(\cdot)$ at time $T+h$ and $\bm{y}_{T+h}$ is the vector of realizations.
-Further $\breve{Y}_{T+h,i}$ and $\breve{Y}_{T+h,j}$ are $i$th and $j$th components of the vector $\breve{\bm{Y}}_{T+h}$.
-Further the variogram score is given for order $p$ where, $w_{ij}$ are non-negative weights.}\label{table:scoringrules}
+Here, $\breve{\bm{y}}_{T+h}$ and $\breve{\bm{y}}^*_{T+h}$ are two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with density function $\breve{\bm{f}}(\cdot)$ at time $T+h$, and $\bm{y}_{T+h}$ is the vector of realizations.
+Further, $\breve{Y}_{T+h,i}$ and $\breve{Y}_{T+h,j}$ are the $i$th and $j$th components of the vector $\breve{\bm{Y}}_{T+h}$.
+The variogram score is given for order $p$, where $w_{ij}$ denote non-negative weights.}\label{table:scoringrules}
   \centering\small\setstretch{1.3}
@@
 
-Even though the log score can be used evaluate simulated forecast densities with large samples \citep{Jordan2017}, it is more convenient to use if it is reasonable to assume a parametric forecast density for the hierarchy.
-However, the \qq{degenerecy} of coherent forecast densities would be problematic when using log scores.
-We will discuss more on this in the next subsection.
+Even though the log score can be used to evaluate simulated forecast densities with large samples \citep{Jordan2017}, it is more convenient to use if we can assume a parametric forecast density for the hierarchy.
+However, the degeneracy of coherent forecast densities is problematic when using log scores.
+We will discuss this further in the next subsection.
 
-In the energy score, for $\alpha=2$, it can be easily shown that
+For the energy score with $\alpha=2$, it can be easily shown that
 \begin{equation} \label{eq:(5.1)}
@@
 where $\breve{\bm{\mu}}_{T+h} =\E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $.
-Therefore in the limiting case, the energy score only measures the accuracy of the forecast mean, but not the entire distribution.
-Further \citet{Pinson2013a} argued that the Energy score given in Table \ref{table:scoringrules} has a very low discrimination ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
+Therefore, in the limiting case, the energy score only measures the accuracy of the forecast mean, and not the entire distribution.
+Similarly, \citet{Pinson2013a} argued that the energy score given in Table \ref{table:scoringrules} has a very low discrimination ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
 
-However, \citet{SCHEUERER2015} have shown that the variogram score has a high discrimination ability of misspecified means, variance and correlation structure than the Energy score.
-Further they suggested the variogram score with $p=0.5$ is more powerful.
-
-For a possible finite sample of size $B$ from the multivariate forecast density $\breve{\bm{F}}$, the variogram score is defined as,
+In contrast, \citet{SCHEUERER2015} have shown that the variogram score has a higher discrimination ability of misspecified means, variances and correlation structures than the energy score.
+For a finite sample of size $B$ from the multivariate forecast density $\breve{\bm{F}}$, the empirical variogram score is defined as
 \begin{equation}
@@
 \end{equation}
+\citet{SCHEUERER2015} recommend using $p=0.5$.
 
@@
 
-As it was mentioned in the previous section, any coherent hierarchical forecast density is a degenerate density.
-To the best of our knowledge, there is no proper multivariate scoring rule in literature to evaluate degenerate densities.
-Further it can be easily seen that some of the existing scoring rules breakdown under the degeneracy.
-For example take the log score in the univariate case.
+Any coherent hierarchical forecast density is a degenerate density.
+To the best of our knowledge, there is no proper multivariate scoring rule available to evaluate degenerate densities.
+Further, it can easily be seen that some of the existing scoring rules breakdown under degeneracy.
+
+For example, consider the log score in the univariate case.
 Suppose the true density is degenerate at $x=0$, i.e.
 $f(x)=\mathbb{1}\{x=0\}$.
-Now consider two predictive densities $p_1(x)$ and $p_2(x)$.
-Let $p_1(x)$ is equivalent to the true density, i.e.
-$p_1(x)=\mathbb{1}\{x=0\}$ and $p_2(x) =^d N(0,\sigma^2)$ with $\sigma^2 < (2\pi)^{-1}$.
-The expected log score of $p_1$ is:
+\todo{I think you need Dirac delta functions here.}  Now consider two predictive densities $p_1(x)$ and $p_2(x)$.
+Let $p_1(x)$ be equivalent to the true density, i.e.
+$p_1(x)=\mathbb{1}\{x=0\}$, and let $p_2(x) \sim N(0,\sigma^2)$ with $\sigma^2 < (2\pi)^{-1}$.
+The expected log score of $p_1$ is
 $$
@@
 $$
-and that of $p_2$ is:
+while that of $p_2$ is
 $$
@@
 $$
-Therefore $S(f,f) > S(p_2,f)$ and hence there exist at least one forecast density which breaks the condition \eqref{eq:(3.1.)} for proper scoring rule.
-This implies log score cannot be used to evaluate the degenerate densities.
+Therefore $S(f,f) > S(p_2,f)$, and there exists at least one forecast density which breaks the condition \eqref{eq:(3.1.)} for a proper scoring rule.
+This implies that the log score cannot be used to evaluate the degenerate densities.
 
-Thus it is necessary to have a rule of thumb to use these scoring rules in order to evaluate coherent forecast densities.
-First we should notice that, even though the coherent distribution of the entire hierarchy is degenerate, the density of the basis set of series is non-degenerate since these series are linearly independent.
-Further, if we can correctly specify the forecast distribution of these basis set of series, then we have almost obtained the correct forecast distribution of the whole hierarchy.
-Therefore, we propose to evaluate the predictive ability of only the basis set of series of the coherent forecast density by using any of the above discussed multivariate scoring rules.
-This will also avoid the impact of degeneracy for the scoring rules.
+However, even though the coherent distribution of the entire hierarchy is degenerate, the density of the basis set of series is non-degenerate since these series are linearly independent.
+Further, if we can correctly specify the forecast distribution of the basis set of series, then we have almost obtained the correct forecast distribution of the whole hierarchy.
+Therefore, we propose to evaluate the forecast distributions using only the basis set of series.
+Then we can use any of the multivariate scoring rules discussed above without incurring problems due to degeneracy.
 
-For example, since the bottom level series is a set of basis series for a given hierarchy, we can evaluate the predictive ability of the bottom level series of the coherent forecast distribution instead of evaluating the whole distribution.
-Further, if our purpose is to compare two coherent forecast densities, we can compare the forecast ability of only the bottom level forecast densities.
+For example, since the bottom level series forms a set of basis series for a given hierarchy, we can evaluate the coherent forecast distribution using only the bottom level series instead of evaluating the whole distribution.
+In particular, if our purpose is to compare two coherent forecast densities, we can compare them using only the bottom level forecast densities.
 
@@
 It is also important to assess how the coherent or reconciled forecast densities improve the predictive ability compared to the incoherent forecasts.
-Clearly, we cannot use multivariate scoring rules, even for the basis set of series, since the coherent and incoherent forecast densities lie in two different matrix spaces.
+Clearly, we cannot use multivariate scoring rules, even for the basis set of series, since the coherent and incoherent forecast densities lie in two different metric spaces.
 
-However we could compare individual margins of the forecast density of the hierarchy using univariate proper scoring rules.
-Most widely used Continuous Ranked Probability Score (CRPS) would be helpful for this.
+However we could compare the individual margins of the forecast density of the hierarchy using univariate proper scoring rules.
+The widely used Continuous Ranked Probability Score (CRPS) could then be used.
+This is defined as
 \begin{equation} \label{eq:(3.6)}
@@
 \end{equation}
-where $\breve{Y}_{T+h,i}$ and $\breve{Y}^*_{T+h,i}$ are two independent copies from the $i$th reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy and $y_{T+h,i}$ is the $i$th realization from the true marginal distribution $G_i$.
-We can also use univariate log scores for which we could assume a parametric forecast distribution.
+where $\breve{Y}_{T+h,i}$ and $\breve{Y}^*_{T+h,i}$ are two independent copies from the $i$th reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy, and $y_{T+h,i}$ is the $i$th realization from the true marginal distribution $G_i$.
+We could also use univariate log scores, for which we could assume a parametric forecast distribution.
 
@@
 That is, suppose all the historical data in the hierarchy follows a multivariate Gaussian distribution, i.e.
-$\bm{y}_T \sim \mathscr{N}(\bm{\mu}_T, \bm{\Sigma}_T)$ where both $\bm{\mu}_T$ and $\bm{\Sigma}_T$ lives in $\mathbb{C}^m$ by nature of the hierarchical time series.
-We are interested in estimating the predictive Gaussian distribution of $\bm{Y}_{T+h}| \bm{\mathcal{I}}_T$ where $\bm{\mathcal{I}}_T= \{\bm{y}_1,\bm{y}_2,\dots.,\bm{y}_T\}$, which should also lives in $\mathbb{C}^m$.
+$\bm{y}_T \sim \mathscr{N}(\bm{\mu}_T, \bm{\Sigma}_T)$, where both $\bm{\mu}_T$ and $\bm{\Sigma}_T$ lives in $\mathbb{C}^m$ by nature of the hierarchical time series.
+We are interested in estimating the predictive Gaussian distribution of $\bm{Y}_{T+h}| \bm{\mathcal{I}}_T$, where $\bm{\mathcal{I}}_T= \{\bm{y}_1,\bm{y}_2,\dots.,\bm{y}_T\}$, which should also live in $\mathbb{C}^m$.
 
@@
 \end{equation}
-where, $\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = \bm{W}_{T+h}$.
+where $\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = \bm{W}_{T+h}$.
 
@@
 Since our primary objective is to find the coherent forecast density of the hierarchy, we need to reconciled \eqref{eq:(6.03)}.
-Recalling from example 2, the reconciled Gaussian predictive distribution is then given by,
+Recalling from example 2, the reconciled Gaussian forecast distribution is then given by,
 \begin{equation}\label{eq:(6.04)}
-\widetilde{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathscr{N}(\bm{SP}\hat{\bm{Y}}_{T+h}, \bm{SP}\bm{W}_{T+h}\bm{P}'\bm{S}')
+\widetilde{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathscr{N}(\bm{SP}\hat{\bm{Y}}_{T+h}, \bm{SP}\bm{W}_{T+h}\bm{P}'\bm{S}'),
 \end{equation}
-where, $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
+where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
 
@@
 
-Suppose $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from $ARIMA(p,d,q)$ processes where, $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability.
+Suppose $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from $ARIMA(p,d,q)$ processes, where $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability.
 Further, the contemporaneous errors $\{\epsilon_{AA,t},\epsilon_{AB,t},\epsilon_{BA,t},\epsilon_{BB,t}\} \sim \mathcal{N}(\bm{0}, \bm{\Sigma})$.

### 2018-03-21 ProbabilisticCoherence.tex
Updated section 6

@@
 This might result in inaccurate forecasts.
-For example, if the bottom level series are highly volatile or noisy, and hence challenging to forecast, then the resulting forecasts from the bottom-up approach are likely to be inaccurate.
+For example, if the bottom-level series are highly volatile or noisy, and hence challenging to forecast, then the resulting forecasts from the bottom-up approach are likely to be inaccurate.
 
@@
 The only relevant paper we are aware of is \citet{BenTaieb2017}, who recently proposed an algorithm to produce coherent probabilistic forecasts and applied it to UK electricity smart meter data.
-In their approach, a sample from the bottom level forecast distribution is first generated, and then aggregated to obtain coherent probabilistic forecasts of the upper levels of the hierarchy.
+In their approach, a sample from the bottom-level forecast distribution is first generated, and then aggregated to obtain coherent probabilistic forecasts of the upper levels of the hierarchy.
 Hence this method is a bottom-up approach.
-They propose to first use the MinT algorithm to reconcile the means of the bottom level forecast distributions, and then a copula-based approach is employed to model the dependency structure of the hierarchy.
+They propose to first use the MinT algorithm to reconcile the means of the bottom-level forecast distributions, and then a copula-based approach is employed to model the dependency structure of the hierarchy.
 The resulting multi-dimensional distribution is used to generating empirical forecast distributions for all bottom-level series.
@@
 
-After introducing our notation in Section \ref{sec:notation}, we define what is meant by probabilistic forecast reconciliation for hierarchical time series in Section \ref{sec:definitions}.
+After introducing our notation in Section~\ref{sec:notation}, we define what is meant by probabilistic forecast reconciliation for hierarchical time series in Section~\ref{sec:definitions}.
 First, we provide a new definition for coherency of point forecasts, and the reconciliation of a set of incoherent point forecasts, using  concepts related to vector spaces and measure theory.
@@
 Further, due to the aggregation structure of the hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate.
-In Section \ref{sec:reconciliation}, we discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation, and in Section \ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts.
+In Section~\ref{sec:reconciliation}, we discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation, and in Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts.
 
-Some theoretical results on probabilistic forecast reconciliation in the Gaussian framework are given in Section \ref{sec:gaussian}, including a simulation study to show the importance of reconciliation in the probabilistic framework.
+Some theoretical results on probabilistic forecast reconciliation in the Gaussian framework are given in Section~\ref{sec:gaussian}, including a simulation study to show the importance of reconciliation in the probabilistic framework.
 
-We conclude with some thoughts on extensions and limitations in Section \ref{sec:conclusions}.
+We conclude with some thoughts on extensions and limitations in Section~\ref{sec:conclusions}.
 
@@
 Our notation largely follows that introduced in \citet{Wickramasuriya2017}.
-Suppose $\bm{y}_t \in \mathbb{R}^n$ comprises all observations of the hierarchy at time $t$ and $\bm{b}_t \in \mathbb{R}^m$ comprises only the bottom level observations at time $t$.
+Suppose $\bm{y}_t \in \mathbb{R}^n$ comprises all observations of the hierarchy at time $t$ and $\bm{b}_t \in \mathbb{R}^m$ comprises only the bottom-level observations at time $t$.
 Then due to the aggregation nature of the hierarchy we have
@@
 
-Consider the hierarchy given in Figure \ref{fig1}.
+Consider the hierarchy given in Figure~\ref{fig1}.
 
@@
   \end{center}
-  \caption{Two level hierarchical diagram}\label{fig1}
+  \caption{Two level hierarchical diagram.}\label{fig1}
 \end{figure}
@@
 
-We illustrate Definition \ref{def:cohprob} in Figure \ref{fig2}, showing $\bm{S}$ mapping any set $\bm{A}\in\mathbb{R}^m$ to the coherent space.
+We illustrate Definition~\ref{def:cohprob} in Figure~\ref{fig2}, showing $\bm{S}$ mapping any set $\bm{A}\in\mathbb{R}^m$ to the coherent space.
 
@@
   \end{center}
-  \caption{Any set $\bm{A} \in \mathbb{R}^m$ will be mapped to $\mathbb{C}^m$ through the mapping $\bm{S}$}\label{fig2}
+  \caption{Any set $\bm{A} \in \mathbb{R}^m$ will be mapped to $\mathbb{C}^m$ through the mapping $\bm{S}$.}\label{fig2}
 \end{figure}
 
-Definition \ref{def:cohprob} implies the probability measure on $\mathbb{C}^m$ is equivalent to the probability measure on $(\mathbb{R}^m, \bm{\mathscr{F}}^m)$.
+Definition~\ref{def:cohprob} implies the probability measure on $\mathbb{C}^m$ is equivalent to the probability measure on $(\mathbb{R}^m, \bm{\mathscr{F}}^m)$.
 Hence, there is no density anywhere outside the linear subspace $\mathbb{C}^m$.
@@
 
-Consider a simple hierarchy with two bottom level series $A$ and $B$ that add up to the top level series $Tot$.
+Consider a simple hierarchy with two bottom-level series $A$ and $B$ that add up to the top level series $Tot$.
 Suppose the forecasts of these series at time $t+h$ are given by $\breve{\bm{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$.
@@
  $\{(1 ~ 0 ~ 1)',(0~1~-\!\!1)'\}$
-respectively. Thus it is clear that the set of bottom level series is a basis series that corresponds to the column vectors of $\bm{S}$.
+respectively. Thus it is clear that the set of bottom-level series is a basis series that corresponds to the column vectors of $\bm{S}$.
 
-Because the basis is not unique for a given coherent subspace, Definition \ref{def:cohprob} is not unique, and one can redefine the coherent probabilistic forecasts with respect to any basis.
-However, we stick to Definition \ref{def:cohprob} and consider the basis defined by the columns of $\bm{S}$ in what follows.
+Because the basis is not unique for a given coherent subspace, Definition~\ref{def:cohprob} is not unique, and one can redefine the coherent probabilistic forecasts with respect to any basis.
+However, we stick to Definition~\ref{def:cohprob} and consider the basis defined by the columns of $\bm{S}$ in what follows.
 
-Definitions \ref{def:cohpoint} and \ref{def:cohprob} facilitate extension to probabilistic forecast reconciliation which we discuss in the next section.
+Definitions~\ref{def:cohpoint} and~\ref{def:cohprob} facilitate extension to probabilistic forecast reconciliation which we discuss in the next section.
 In contrast to our definition, \citet{BenTaieb2017} define coherent probabilistic forecasts in terms of convolutions.
@@
 
-Definition \ref{def:reconpoint} allows for both linear and non-linear reconciliation.
+Definition~\ref{def:reconpoint} allows for both linear and non-linear reconciliation.
 In other words, if $\bm{g}$ is a non-linear function, then the reconciliation of $\hat{\bm{y}}_{t+h}$ will be non-linear, while if $\bm{g}$ is a linear function, then $\bm{S}\circ \bm{g}(\cdot)$ will linearly project incoherent point forecasts onto $\mathbb{C}^m$.
@@
 
-Using Definition \ref{def:reconpoint}, we can now explain previous results for linear forecast reconciliation.
+Using Definition~\ref{def:reconpoint}, we can now explain previous results for linear forecast reconciliation.
 Let $\bm{R} \in \mathbb{R}^{n \times (n-m)}$ comprise the columns that span $\bm{\mathbb{N}}^{n-m}$, which is orthogonal to $\mathbb{C}^m$.
@@
 Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$.
-Now, using the insights of Definition \ref{def:reconpoint}, we can use the following steps to reconcile the point forecasts.
+Now, using the insights of Definition~\ref{def:reconpoint}, we can use the following steps to reconcile the point forecasts.
 
-\subsubsection*{Step 1: Obtaining reconciled bottom level point forecasts}
+\subsubsection*{Step 1: Obtaining reconciled bottom-level point forecasts}
 
@@
 Let $(\tilde{\bm{b}}'_{t+h} , \tilde{\bm{t}}'_{t+h})'$ denote these coordinates.
-Note that $\tilde{\bm{b}}_{t+h}$ is a basis series which is equivalent to the reconciled bottom level series, and which corresponds to the linear combination coefficients of the basis $\{\bm{s}_1,\dots,\bm{s}_m\}$.
+Note that $\tilde{\bm{b}}_{t+h}$ is a basis series which is equivalent to the reconciled bottom-level series, and which corresponds to the linear combination coefficients of the basis $\{\bm{s}_1,\dots,\bm{s}_m\}$.
 Similarly, $\tilde{\bm{t}}_{t+h}$ is another basis series corresponding to the linear combination coefficients of the basis $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$.
-Then from basic properties of linear algebra it follows that,
+Then from basic properties of linear algebra it follows that
 \[
@@
 In order to find $(\bm{S} ~ \vdots~ \bm{R})^{-1}$, let $\bm{S}_{\bot}$ and $\bm{R}_{\bot}$ be the orthogonal complements of $\bm{S}$ and $\bm{R}$
-respectively. Then $(\bm{S} ~ \vdots~ \bm{R})^{-1}$ is given by,
+respectively. Then $(\bm{S} ~ \vdots~ \bm{R})^{-1}$ is given by
 \begin{equation}
@@
 
-From \eqref{4.4} it follows that,
+From \eqref{4.4} it follows that
 \begin{equation}
@@
 \citet{Hyndman2011} proposed to choose
-\begin{equation*}
+\begin{equation}
 \tilde{\bm{b}}^{OLS}_{t+h}=(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h},
-\end{equation*}
-where, in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy are given by,
+\end{equation}
+where, in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy are given by
 \begin{equation}
@@
 This will result in
-\begin{equation*}
+\begin{equation}
 \tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}'\bm{W}^{-1}_{h} \bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h},
-\end{equation*}
+\end{equation}
 and thus,
@@
 Now that we have the density of $(\tilde{\bm{b}}'_{t+h} , \tilde{\bm{t}}'_{t+h})'$, the marginal density of $\tilde{\bm{b}}_{t+h}$ can be obtained by integrating \eqref{4.5} over the range of $\tilde{\bm{t}}_{t+h}$.
-This will result in the reconciled density of the bottom level series $\tilde{\bm{b}}_{t+h}$,
+This will result in the reconciled density of the bottom-level series $\tilde{\bm{b}}_{t+h}$,
 \begin{equation}\label{4.6}
@@
 
-Finally to get the reconciled density of the whole hierarchy, we simply follow Definition \ref{def:cohprob} to obtain
+Finally to get the reconciled density of the whole hierarchy, we simply follow Definition~\ref{def:cohprob} to obtain
 \begin{equation}\label{4.7}
@@
 
-Suppose $\mathscr{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h}) \overset{d}{\leftrightarrow} \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ is an incoherent forecast distribution at time $t+h$.
+Suppose $\mathcal{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h}) \overset{d}{\leftrightarrow} \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ is an incoherent forecast distribution at time $t+h$.
 Then from \eqref{4.5} it follows that
-\begin{equation*}
+\begin{equation}
 \bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \, \Big|\bm{S} ~ \vdots~ \bm{R}\Big| = \frac{\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) }{\Big|(\bm{S} ~ \vdots~ \bm{R})^{-1}\Big|}.
-\end{equation*}
+\end{equation}
 By substituting the Gaussian distribution function for $\bm{f_B}(\cdot)$ we get
@@
 
-Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathscr{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
+Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
 Then from \eqref{4.7} it follows that
-\begin{equation}
+\begin{equation}\label{eq:gaussianreconciled}
 \tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
@@
 Therefore, the reconciled Gaussian forecast distribution of the whole hierarchy is\\
-$\mathscr{N}(\bm{SP}\bm{\hat{\mu}}_{t+h},~ \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}')$.
+$\mathcal{N}(\bm{SP}\bm{\hat{\mu}}_{t+h},~ \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}')$.
 
@@
 
-Table \ref{table:scoringrules} summarizes a few existing proper scoring rules.
+Table~\ref{table:scoringrules} summarizes a few existing proper scoring rules.
 
@@
     \text{Energy score}    &
-    $\text{eS}(\breve{\bm{Y}}_{T+h},\bm{y}_{T+h}) =
+    $\text{ES}(\breve{\bm{Y}}_{T+h},\bm{y}_{T+h}) =
     \E_{\breve{\bm{F}}}
@@
 \begin{equation} \label{eq:(5.1)}
-\text{eS}(\breve{\bm{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
+\text{ES}(\breve{\bm{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
 \end{equation}
@@
 Therefore, in the limiting case, the energy score only measures the accuracy of the forecast mean, and not the entire distribution.
-Similarly, \citet{Pinson2013a} argued that the energy score given in Table \ref{table:scoringrules} has a very low discrimination ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
+Similarly, \citet{Pinson2013a} argued that the energy score given in Table~\ref{table:scoringrules} has a very low discrimination ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
 
@@
 
-%For example, assume you have a Gaussian coherent predictive density $\bm{\tilde{f}}_{T+h}$. Then the log score is given by,
+%For example, assume you have a Gaussian coherent predictive density $\bm{\tilde{f}}_{T+h}$. Then the log score is given by
 
@@
 Let $p_1(x)$ be equivalent to the true density, i.e.
-$p_1(x)=\mathbb{1}\{x=0\}$, and let $p_2(x) \sim N(0,\sigma^2)$ with $\sigma^2 < (2\pi)^{-1}$.
+$p_1(x)=\mathbb{1}\{x=0\}$, and let $p_2(x) \sim \mathcal{N}(0,\sigma^2)$ with $\sigma^2 < (2\pi)^{-1}$.
 The expected log score of $p_1$ is
@@
 
-For example, since the bottom level series forms a set of basis series for a given hierarchy, we can evaluate the coherent forecast distribution using only the bottom level series instead of evaluating the whole distribution.
-In particular, if our purpose is to compare two coherent forecast densities, we can compare them using only the bottom level forecast densities.
+For example, since the bottom-level series forms a set of basis series for a given hierarchy, we can evaluate the coherent forecast distribution using only the bottom-level series instead of evaluating the whole distribution.
+In particular, if our purpose is to compare two coherent forecast densities, we can compare them using only the bottom-level forecast densities.
 
@@
 
-Main purpose of this section is to establish the importance of reconciliation in probabilistic hierarchical forecasting.
-We narrow down the simulation setting for the Gaussian framework in this work.
-That is, suppose all the historical data in the hierarchy follows a multivariate Gaussian distribution, i.e.
-$\bm{y}_T \sim \mathscr{N}(\bm{\mu}_T, \bm{\Sigma}_T)$, where both $\bm{\mu}_T$ and $\bm{\Sigma}_T$ lives in $\mathbb{C}^m$ by nature of the hierarchical time series.
+An important special case for probabilistic forecasting arises when we can assume a multivariate Gaussian distribution.
+That is, suppose all the historical data in the hierarchy follows a multivariate Gaussian distribution, $\bm{y}_T \sim \mathcal{N}(\bm{\mu}_T, \bm{\Sigma}_T)$, where both $\bm{\mu}_T$ and $\bm{\Sigma}_T$ live in $\mathbb{C}^m$ by nature of the hierarchical structure of the data.
 We are interested in estimating the predictive Gaussian distribution of $\bm{Y}_{T+h}| \bm{\mathcal{I}}_T$, where $\bm{\mathcal{I}}_T= \{\bm{y}_1,\bm{y}_2,\dots.,\bm{y}_T\}$, which should also live in $\mathbb{C}^m$.
 
-Considering the individual series in the hierarchy, it is well known that the optimal point forecasts with respect to the minimal mean square error is given by the $\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}],$ $i=1,\dots,n$.
+It is well known that the optimal point forecasts with respect to the minimal mean square error are given by the conditional expectations, $\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}],$ $i=1,\dots,n$.
 Suppose we independently fit time series models for each series in the hierarchy.
-Then the point forecasts from the estimated models, denoted by $\hat{Y}_{T+h,i}$ is unbiased and consistent estimator of $\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}]$, given that the parameter estimates of the fitted models are unbiased and asymptotically consistent.
+Then the point forecasts, $\hat{Y}_{T+h,i}$, from the estimated models are unbiased and consistent estimators of $\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}]$, assuming the parameter estimates of the fitted models are unbiased and asymptotically consistent.
+\todo{Only for linear models?}
 
@@
 $$
-Y_{t,i}=\alpha_1Y_{t-1,i}+\dots+\alpha_pY_{t-p,i}+\epsilon_t + \beta_1\epsilon_{t-1,i}+\dots+\beta_q\epsilon_{t-q,i},
+Y_{t,i}=\alpha_1Y_{t-1,i}+\dots+\alpha_pY_{t-p,i}+\varepsilon_t + \beta_1\varepsilon_{t-1,i}+\dots+\beta_q\varepsilon_{t-q,i},
 $$
-where $\epsilon_t \sim \mathcal{NID}(0, \sigma_i^2)$. Then,
+where $\varepsilon_t \sim \mathcal{NID}(0, \sigma_i^2)$. Then,
 $$
-\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}] = \alpha_1Y_{T+h-1,i}+\dots+\alpha_pY_{T+h-p,i}+ \beta_1\epsilon_{T+h-1,i}+\dots+\beta_q\epsilon_{T+h-q,i}.
+\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}] = \alpha_1Y_{T+h-1,i}+\dots+\alpha_pY_{T+h-p,i}+ \beta_1\varepsilon_{T+h-1,i}+\dots+\beta_q\varepsilon_{T+h-q,i}.
 $$
@@
 
-Let $\hat{\bm{Y}}_{T+h}=(\hat{Y}_{T+h,1},\dots,\hat{Y}_{T+h,n})'$ and \eqref{eq:(6.01)} holds for all $i=1,\dots,n$. Then from Slutsky's theorem it follows that,
+Let $\hat{\bm{Y}}_{T+h}=(\hat{Y}_{T+h,1},\dots,\hat{Y}_{T+h,n})'$ and suppose \eqref{eq:(6.01)} holds for $i=1,\dots,n$. Then from Slutsky's theorem it follows that
 \begin{equation}\label{eq:(6.02)}
@@
 \end{equation}
-Further let the forecast error due to $\hat{\bm{Y}}_{T+h}$ is given by,
-\begin{equation*}
+Further, let the forecast error due to $\hat{\bm{Y}}_{T+h}$ be given by
+\begin{equation}
 \hat{\bm{e}}_{T+h} = \bm{Y}_{T+h}-\hat{\bm{Y}}_{T+h},
-\end{equation*}
-
-Now consider the variance of $\hat{\bm{e}}_{T+h}$,
+\end{equation}
+and consider the variance of $\hat{\bm{e}}_{T+h}$,
 \begin{align*}
@@
 &  \quad
-+ \E[\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T]
++ \E[\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T].
 \end{align*}
 
-From \eqref{eq:(6.02)} it immediately follows that,
+From \eqref{eq:(6.02)} it immediately follows that
 \begin{align*}
-&\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] \overset{p}{\to} \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T],
+&\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] \overset{p}{\to} \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T].
 \end{align*}
+That is,
 \begin{equation}
@@
 
-It should be noted that, even though $\hat{\bm{Y}}_{T+h}$ and $\bm{W}_{T+h}$ are asymptotically consistent estimators for $\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ and $\text{Var}(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ respectively, they are not coherent since they doesn't lie in the coherent subspace.
-Thus the Gaussian forecast distribution with mean $\hat{\bm{Y}}_{T+h}$ and variance $\bm{W}_{T+h}$ will be incoherent and we denote it by,
+Even though $\hat{\bm{Y}}_{T+h}$ and $\bm{W}_{T+h}$ are asymptotically consistent estimators for $\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ and $\text{Var}(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ respectively, they are not coherent since they do not lie in the coherent subspace.
+Thus the Gaussian forecast distribution with mean $\hat{\bm{Y}}_{T+h}$ and variance $\bm{W}_{T+h}$ will be incoherent, and we denote it by
 \begin{equation}\label{eq:(6.03)}
-\widehat{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathscr{N}(\hat{\bm{Y}}_{T+h}, \bm{W}_{T+h})
+\widehat{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathcal{N}(\hat{\bm{Y}}_{T+h}, \bm{W}_{T+h})
 \end{equation}
 
-Since our primary objective is to find the coherent forecast density of the hierarchy, we need to reconciled \eqref{eq:(6.03)}.
-Recalling from example 2, the reconciled Gaussian forecast distribution is then given by,
+Since our primary objective is to find the coherent forecast density of the hierarchy, we need to reconcile \eqref{eq:(6.03)}.
+Using \eqref{eq:gaussianreconciled}, the reconciled Gaussian forecast distribution is then given by
 \begin{equation}\label{eq:(6.04)}
-\widetilde{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathscr{N}(\bm{SP}\hat{\bm{Y}}_{T+h}, \bm{SP}\bm{W}_{T+h}\bm{P}'\bm{S}'),
+\widetilde{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathcal{N}(\bm{SP}\hat{\bm{Y}}_{T+h}, \bm{SP}\bm{W}_{T+h}\bm{P}'\bm{S}'),
 \end{equation}
@@
 
-\textbf{Result 1}: Choosing $\bm{R}'_\bot = \bm{S}'\bm{W}_{T+h}^{-1}$ will ensure at least the mean of the predictive Gaussian distribution is optimally reconciled with respect to the energy score.
+\textbf{Result 1}: Choosing $\bm{R}'_\bot = \bm{S}'\bm{W}_{T+h}^{-1}$ will ensure that at least the mean of the predictive Gaussian distribution is optimally reconciled with respect to the energy score.
 
 Result 1 can be easily shown as follows.
-From \eqref{eq:(5.1)} the energy score at the upper limit of $\alpha$ is given by, $\|\bm{y}_{T+h}-\bm{SP}\hat{\bm{y}}_{T+h}\|^2$.
-Then the expectation of energy score with respect to the true distribution is equivalent to the trace of mean squared forecast error, i.e.
+From \eqref{eq:(5.1)}, the energy score at the upper limit of $\alpha=2$ is given by $\|\bm{y}_{T+h}-\bm{SP}\hat{\bm{y}}_{T+h}\|^2$.
+Then the expectation of the energy score with respect to the true distribution is equivalent to the trace of mean squared forecast error; i.e.,
 $$
@@
 
-From Theorem 1 of \citet{Wickramasuriya2017} it immediately follows that $\bm{P} = (\bm{S}'\bm{W}_{T+h}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}_{T+h}^{-1}$ minimizes the expected energy score constrained on the unbiasedness of reconciled forecasts.
+From Theorem 1 of \citet{Wickramasuriya2017} it immediately follows that $\bm{P} = (\bm{S}'\bm{W}_{T+h}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}_{T+h}^{-1}$ minimizes the expected energy score, if we constrain the reconciled forecasts to be unbiased.
 Thus we have $\bm{R}'_\bot = \bm{S}'\bm{W}_{T+h}^{-1}$.
 
-It should be noted that $\bm{W}_{T+h}$ can be estimated in different methods which yields different estimation of $\bm{R}'_\bot$. Table \ref{table:2} summarizes these methods.
+It should be noted that $\bm{W}_{T+h}$ can be estimated in different ways, which yields different estimates of $\bm{R}'_\bot$. Table~\ref{table:2} summarizes some of these methods.
 
 \begin{table}
-  \caption{Summarizing different estimates of $\bm{R}'_\bot$.
+  \caption{Several possible estimates of $\bm{R}'_\bot$.
 For $n<T$, $\bm{\hat{W}}_{T+1}^{sam}$ is an unbiased and consistent estimator for $\bm{W}_{T+1}$.
-$\bm{\hat{W}}_{T+1}^{shr}$ is a shrinkage estimator which is much suitable for large dimensions.
-$\bm{\hat{W}}_{T+1}^{shr}$ was proposed by \citet{Schafer2005} and also used by \citet{Wickramasuriya2017}, where $\tau = \frac{\sum_{i \ne j}\hat{\text{Var}}(\hat{r}_{ij})}{\sum_{i \ne j}\hat{r}_{ij}^2}$, $\hat{r}_{ij}$ is the $ij$th element of sample correlation matrix.
-Further Diag($\bm{A}$) denote the diagonal matrix of $\bm{A}$}\label{table:2}
+$\bm{\hat{W}}_{T+1}^{shr}$ is a shrinkage estimator which is more suitable for large dimensions.
+$\bm{\hat{W}}_{T+1}^{shr}$ was proposed by \citet{Schafer2005} and also used by \citet{Wickramasuriya2017}, where Diag($\bm{A}$) denotes the diagonal matrix of $\bm{A}$, $\tau = \frac{\sum_{i \ne j}\hat{\text{Var}}(\hat{r}_{ij})}{\sum_{i \ne j}\hat{r}_{ij}^2}$, and $\hat{r}_{ij}$ is the $ij$th element of the sample correlation matrix.}\label{table:2}
   \centering\setstretch{1.5}
@@
 
-It is worth mentioning that all these forecasting methods were well established in the context of point forecast reconciliation \citep{Hyndman2011, Wickramasuriya2017, Hyndman2016}.
-However our attempt is to emphasis the use of these reconciliation methods in the context of probabilistic forecasts at least in the Gaussian framework.
+All of these forecasting methods are well-established in the context of point forecast reconciliation \citep{Hyndman2011, Hyndman2016,Wickramasuriya2017}.
+Here, we are showing how these reconciliation methods can be used in the context of probabilistic forecast reconciliation, at least in the Gaussian framework.
 
-\subsubsection*{Simulation setup}
+\subsubsection*{Simulations}
 
-We consider the hierarchy given in figure (1) for this simulation study.
-This hierarchy consists two aggregation levels with four bottom level series.
-Each bottom-level series will be generated first and add them up to obtain the data for respective upper-level series.
-Hierarchical time series in practice contain much noisier series in the bottom level than in aggregate series.
-In order to simulate this feature in the hierarchy, we refer to \citet{Wickramasuriya2017} and the data generating process will be given as follows.
+We consider the hierarchy given in Figure~\ref{fig1}, comprising two aggregation levels with four bottom-level series.
+Each bottom-level series will be generated first, and then summed to obtain the data for the upper-level series.
+In practice, hierarchical time series tend to contain much noisier series at lower levels of aggregation.
+In order to replicate this feature in our simulations, we follow the data generating process proposed by \citet{Wickramasuriya2017}.
 
-Suppose $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from $ARIMA(p,d,q)$ processes, where $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability.
-Further, the contemporaneous errors $\{\epsilon_{AA,t},\epsilon_{AB,t},\epsilon_{BA,t},\epsilon_{BB,t}\} \sim \mathcal{N}(\bm{0}, \bm{\Sigma})$.
-The parameters for $AR$ and $MA$ components will be randomly and uniformly generated from $[0.3,0.5]$ and $[0.3,0.7]$ respectively.
-Then the bottom level series $\{y_{AA,t},y_{AB,t},y_{BA,t},y_{BB,t}\}$ will be obtained as:
+Suppose $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from ARIMA$(p,d,q)$ processes, where $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability.
+Further, the contemporaneous errors $\{\varepsilon_{AA,t},\varepsilon_{AB,t},\varepsilon_{BA,t},\varepsilon_{BB,t}\} \sim \mathcal{N}(\bm{0}, \bm{\Sigma})$.
+The parameters for the AR and MA components will be randomly and uniformly generated from $[0.3,0.5]$ and $[0.3,0.7]$ respectively.
+Then the bottom-level series $\{y_{AA,t},y_{AB,t},y_{BA,t},y_{BB,t}\}$ will be obtained as:
 \begin{align*}
@@
 \end{align*}
-where $u_t \sim N(0,\sigma^2_u)$ and $v_t \sim N(0,\sigma^2_v)$.
-
-To obtain the aggregate series at level 1, we add their respective bottom level series such as:
+where $u_t \sim \mathcal{N}(0,\sigma^2_u)$ and $v_t \sim \mathcal{N}(0,\sigma^2_v)$.
+To obtain the aggregate series at level 1, we add the bottom-level series:
 \begin{align*}
@@
 \end{align*}
-and the total series will be obtained as:
+and the total series is obtained using
 $$y_{Tot,t} = w_{AA,t} + w_{AB,t} + w_{BA,t} + w_{BB,t}.$$
 
-To get less noisier aggregate series than disaggregate series, we choose $\bm{\Sigma}, \sigma^2_u$ and $\sigma^2_v$ such that,
+To ensure noisier disaggregate series than aggregate series, we choose $\bm{\Sigma}, \sigma^2_u$ and $\sigma^2_v$ such that
 $$
-\text{Var}(\epsilon_{AA,t}+\epsilon_{AB,t}+\epsilon_{BA,t}+\epsilon_{BB,t}) \le \text{Var}(\epsilon_{AA,t}+\epsilon_{AB,t}-v_t) \le \text{Var}(\epsilon_{AA,t}+u_t-0.5v_t),
+\text{Var}(\varepsilon_{AA,t}+\varepsilon_{AB,t}+\varepsilon_{BA,t}+\varepsilon_{BB,t}) \le \text{Var}(\varepsilon_{AA,t}+\varepsilon_{AB,t}-v_t) \le \text{Var}(\varepsilon_{AA,t}+u_t-0.5v_t).
 $$
+Therefore
 $$
@@
 $$
-where $\bm{l}_1 = \begin{pmatrix} 1&1&1&1 \end{pmatrix}, \bm{l}_2 = \begin{pmatrix} 1&1&0&0 \end{pmatrix}$ and $\bm{l}_3 = \begin{pmatrix} 1&0&0&0 \end{pmatrix}$.
-
-This follows,
+where $\bm{l}_1 = (1,1,1,1)'$, $\bm{l}_2 = (1,1,0,0)'$ and $\bm{l}_3 = (1,0,0,0)'$, and hence
 $$\bm{l}_1\bm{\Sigma} \bm{l}_1' - \bm{l}_2\bm{\Sigma} \bm{l}_2' \le \sigma^2_v \le \frac{4}{3}(\sigma^2_u + \bm{l}_3\bm{\Sigma} \bm{l}_3' - \bm{l}_2\bm{\Sigma} \bm{l}_2').$$
-Thus we choose,
+To satisfy these constraints, we choose
 $\bm{\Sigma} =
@@
 
-As such we generate data for the hierarchy with sample size $T=501$.
-Then univariate $ARIMA$ models were fitted for each series independently using the first 500 observations and obtain 1-step ahead base (incoherent) forecasts.
-We use \textit{forecast} package in \textbf{R}-software \citet{hyndman2017forecasting} for model fitting and forecasting.
-Further, different estimates of $\bm{W}_{T+1}$ and the corresponding $\bm{R}'_\bot$ were obtained as summarized in Table \ref{table:2}.
-This process was then replicated using $1000$ different data sets from the same data generating process.
+We generate data for the hierarchy with sample size $T=501$.
+Univariate ARIMA models were fitted for each series independently using the first 500 observations, and 1-step ahead base (incoherent) forecasts were calculated.
+We use the \textit{forecast} package \citep{hyndman2017forecasting} in R \citep{Rcore} for model fitting and forecasting.
+The different estimates of $\bm{W}_{T+1}$ and the corresponding $\bm{R}'_\bot$ from Table~\ref{table:2} were obtained.
+This process was replicated using $1000$ different data sets from the same data generating processes.
 
-To assess the predictive performance of different forecasting methods, we use scoring rules as discussed in Section \ref{sec:evaluation}.
-In addition to that we use Skill score \citep{Gneiting2007} for any comparison.
-For a given forecasting method, evaluated by a particular scoring rule $S(\cdot)$ , the skill score will be calculated as follows,
+To assess the predictive performance of different forecasting methods, we use scoring rules as discussed in Section~\ref{sec:evaluation}.
+To faciliate comparisons, we report skill scores \citep{Gneiting2007}.
+For a given forecasting method, evaluated by a particular scoring rule $S(\cdot)$, the skill score is calculated as
 \begin{equation}
@@
 \end{equation}
-where $S_B(\cdot)$ is average score over $B$ samples and $S_B(\bm{Y},\bm{y})^{\text{ref}}$ is the average score of the reference forecasting methods.
+where $S_B(\cdot)$ is the average score over $B$ samples and $S_B(\bm{Y},\bm{y})^{\text{ref}}$ is the average score for the reference forecasting method.
 Thus $Ss[S_B(\cdot)]$ gives the percentage improvement of the preferred forecasting method relative to the reference method.
-Any negative value of $Ss[S_B(\cdot)]$ indicate that the method we compared is poor than the reference method, whereas any positive value indicates that method is superior to the reference method.
+Any negative value of $Ss[S_B(\cdot)]$ indicates that the method we compared is worse than the reference method, whereas any positive value indicates that method is superior to the reference method.
 
-As it was mentioned before we wish to establish the importance of reconciliation methods from this simulation study.
-In particular, we compare different reconciliation methods over the conventional bottom-up method and also evaluate the predictive ability of coherent forecasts over incoherent forecasts.
-For the former comparison, we use bottom level probabilistic forecasts and calculate the percentage skill score based on energy score, log score and variogram score for each reconciliation method with reference to the bottom up method (presented in Table \ref{table:3}).
-For the latter comparison, we use percentage skill score based on CRPS and univariate log score for coherent probabilistic forecasts of each individual series with reference to incoherent forecasts (presented in Tables \ref{table:4} and \ref{table:5}).
+In Table~\ref{table:3}, we compare different reconciliation methods over the conventional bottom-up method.
+We use bottom-level probabilistic forecasts and calculate the percentage skill score based on energy score, log score and variogram score for each reconciliation method with reference to the bottom-up method.
 
-It is clearly evident from the results in Table \ref{table:3} that the multivariate reconciled forecasts for the bottom level series from MinT(Shrink) and MinT(Sample) outperform the bottom-up forecasts.
-Further, these two methods produce probabilistic forecasts with best predictive ability in comparison to incoherent forecasts (from Tables \ref{table:4} and \ref{table:5}).
+We also evaluate the predictive ability of coherent forecasts over incoherent forecasts in Tables~\ref{table:4} and~\ref{table:5}.
+Here we use percentage skill score based on CRPS and univariate log score for coherent probabilistic forecasts of each individual series with reference to incoherent forecasts.
+
+It is clearly evident from the results in Table~\ref{table:3} that the multivariate reconciled forecasts for the bottom-level series from MinT(Shrink) and MinT(Sample) out-perform the bottom-up forecasts.
+Further, these two methods produce probabilistic forecasts with the best predictive ability in comparison to incoherent forecasts (from Tables~\ref{table:4} and~\ref{table:5}).
 Moreover, it turns out that OLS and bottom-up methods produce the worst forecasts.
@@
 \begin{table}
-  \caption{Comparison of incoherent forecasts using bottom level series.
-The ``Skill score'' columns give the percentage skill score with reference to the bottom up forecasting method.
-A positive entry in these columns shows the percentage increase of score for different reconciliation methods with relative to the bottom up method.}\label{table:3}
+  \caption{Comparison of incoherent forecasts using bottom-level series.
+The ``Skill score'' columns give the percentage skill score with reference to the bottom-up forecasting method.
+Entries in these columns show the percentage increase of score for different reconciliation methods relative to the bottom-up method.}\label{table:3}
   \centering\small
@@
     OLS          & 10.14 & -22.02 & 135.13 & -1014.93 & 4.60 & -43.75 \\
-    Bottom up    &  8.31 &        &  12.12 &          & 3.20 &        \\
+    Bottom-up    &  8.31 &        &  12.12 &          & 3.20 &        \\
     \bottomrule
@@
 \begin{table}
-  \caption{Comparison of incoherent vs coherent forecasts for the aggregate series using Skill score.
-"Incoherent" row represent the average score for incoherent forecasts.
-Each entry above this row represent the percentage skill score with reference to the incoherent forecasts.
-A positive(negative) entry shows the percentage increase(decrease) of score for different forecasting methods with relative to incoherent forecasts.}\label{table:4}
+  \caption{Comparison of incoherent vs coherent forecasts for the aggregate series using Skill scores.
+The ``Incoherent'' row shows the average scores for incoherent forecasts.
+Each entry above this row represents the percentage skill score with reference to the incoherent forecasts.
+Entries show the percentage increase in score for different forecasting methods relative to the incoherent forecasts.}\label{table:4}
   \centering\small
@@
     OLS          & -38.06 & -698.99 & -24.70 & -1368.33 & -24.86 & -1159.09 \\
-    Bottom up    & -89.55 & -21.83  & -8.87  & -2.35    & -9.46  & -2.73    \\
+    Bottom-up    & -89.55 & -21.83  & -8.87  & -2.35    & -9.46  & -2.73    \\
     \midrule
@@
 \begin{table}
-  \caption{Comparison of incoherent vs coherent forecasts for the individual bottom level series using Skill score.}\label{table:5}
+  \caption{Comparison of incoherent vs coherent forecasts for the individual bottom-level series using Skill scores.}\label{table:5}
   \centering\tabcolsep=0.08cm\small

### 2018-03-31 ProbabilisticCoherence.tex
Rewrote section 2, removed discussion of levels, changed title to hierarchical time series

@@
 
-\section{Notation}\label{sec:notation}
+\section{Hierarchical Time Series}\label{sec:notation}
 
-Our notation largely follows that introduced in \citet{Wickramasuriya2017}.
-Suppose $\bm{y}_t \in \mathbb{R}^n$ comprises all observations of the hierarchy at time $t$ and $\bm{b}_t \in \mathbb{R}^m$ comprises only the bottom-level observations at time $t$.
-Then due to the aggregation nature of the hierarchy we have
-\begin{equation}
-  \bm{y}_t = \bm{Sb}_t,
-\end{equation}
-where $\bm{S}$ is an $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold.
-
-In any hierarchy, the most aggregated level is labelled level 0, the second most aggregated level is labelled level 1 and so on.
-
-Consider the hierarchy given in Figure~\ref{fig1}.
+In the section, and throughout the paper, we will try to follow notational conventions used in \citet{Wickramasuriya2017} as much as possible.
+A hierarchical time series is a collection of $n$ variables where some variables are aggregates of other variables.
+For example in the hierarchy depicted in Figure~\ref{fig1} below, the variable labelled $Tot$ is the sum of the series $A$
+and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.
+The bottom level series are defined as those $m$ variables that cannot be formed as aggregates of other variables, in the example in Figure~\ref{fig1} these are the series $AA$, $AB$, $BA$ and $BB$.
 
@@
 
-This example consists of two levels.
-At a particular time $t$, let $y_{Tot,t}$ denote the observation at level~0; $y_{A,t}, y_{B,t} $ denote observations at level~1; and $y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}$ denote observations at level~2.
-Then $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and
+We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprised of observations of all variables in the hierarchy at time $t$,  and $\bm{b}_t \in \mathbb{R}^m$ is a vector comprised of observations of all bottom-level series at time $t$.
+The hierarchical structure of the data imply the following
+\begin{equation}
+  \bm{y}_t = \bm{Sb}_t,
+\end{equation}
+where $\bm{S}$ is an $n \times m$ constant matrix encoding the aggregation constraints.
+For example for the hierarchy in Figure~\ref{fig1}, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and
 $$ 
@@
                0&0  & 1 & 1 \\ 
-               & \multicolumn{2}{c}{I_4} &   
+               & \multicolumn{2}{c}{\bm{I}_4} &   
            \end{pmatrix}, 
 $$
+
 where $I_4$ is a $4$-dimension identity matrix.

### 2018-03-31 ProbabilisticCoherence.tex
Cleaned Definition 3.1 using mathfrak for spaces since C looks like  complex numbers and N like natural

@@
 \usetikzlibrary{arrows,positioning,shapes,fit,calc}
+\usepackage{amsfonts}
 \hypersetup{citecolor=blue,linkcolor=blue,urlcolor=blue}
@@
 
-While coherent point forecasts have been discussed many times previously, the definitions of coherence previously given are vague and are not easily extended to the situation of probabilistic forecasting.
+It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect aggregation constraints.
+We follow other authors in describing this property as {\em coherence}.
+%While coherent point forecasts have been discussed many times previously, the definitions of coherence previously given are vague and are not easily extended to the situation of probabilistic forecasting.
 
-We first give a new definition for coherent point forecasts using the properties of vector spaces, and then provide a definition of coherent probabilistic forecasts.
+We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem thus facilitating the development of the reconciliation techniques of section~\ref{sec:reconciliation}.
 
 \begin{definition}[Coherent subspace]
-Suppose an $n$-dimensional time series $\bm{y}_t \in \mathbb{R}^n$ is subject to the linear aggregation constraint $\bm{y}_t = \bm{S}\bm{b}_t$, where $\bm{b}_t \in \mathbb{R}^m$ and $\bm{S}$ is an $n \times m$ constant matrix.
-Let $\mathbb{C}^m$ be an $m$-dimensional subspace of $\mathbb{R}^n$, where $\mathbb{C}^m < \mathbb{R}^n$.
-Then $\mathbb{C}^m$ is said to be a coherent space if it is spanned by the columns of $\bm{S}$.
+Let an $n$-dimensional time series $\bm{y}_t \in \mathbb{R}^n$ be subject to the linear aggregation constraint $\bm{y}_t = \bm{S}\bm{b}_t$, where $\bm{b}_t \in \mathbb{R}^m$ and $\bm{S}$ is an $n \times m$ constant matrix.
+The $m$-dimensional subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e.
+$\mathfrak{s}=\mbox{span}(\bm{S})$, is defined as the {\em coherent space}.
 \end{definition}
 
-Notice that the coherent space $\mathbb{C}^m$ is equivalent to the column space of $\bm{S}$, which we denote by $\mathscr{C}(\bm{S})$.
-Further, the space orthogonal to $\mathbb{C}^m$ is equivalent to the null space of $\bm{S}$, which we denote by $\bm{\mathbb{N}}^{n-m}$.
+We will also denote the $n\times(n-m)$ orthogonal complement of $\bm{S}$ as $\bm{S}_{\perp}$, where $\mathfrak{s}=\mbox{span}\left(\bm{S}_{\perp}\right)$ is the nullspace of $\bm{S}$
 

### 2018-03-31 ProbabilisticCoherence.tex
Cleaned up definitions of coherence, moved figure, comment out discussion about densities

@@
 
-We will also denote the $n\times(n-m)$ orthogonal complement of $\bm{S}$ as $\bm{S}_{\perp}$, where $\mathfrak{s}=\mbox{span}\left(\bm{S}_{\perp}\right)$ is the nullspace of $\bm{S}$
-
-\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
-  Suppose $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ denotes point forecasts of each series in the hierarchy at time $t+h$.
-Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathbb{C}$.
-\end{definition}
-
-\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
-  Let $(\mathbb{R}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability triple, where $\mathscr{F}^m$ is a $\sigma$-algebra on $\mathbb{R}^m$.
-Then, $(\mathbb{C}, \mathscr{F}_{\bm{S}}, \breve{\nu})$ is said to be a coherent probability measure space iff
-  $$
-      \breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall  \bm{A} \in \mathscr{F}^m,
-    $$ 
-  where $\bm{S}(\bm{A})$ denotes the image of subset $\bm{A}$ under $\bm{S}$. 
-\end{definition}
-
-We illustrate Definition~\ref{def:cohprob} in Figure~\ref{fig2}, showing $\bm{S}$ mapping any set $\bm{A}\in\mathbb{R}^m$ to the coherent space.
+We also denote the $n\times(n-m)$ orthogonal complement of $\bm{S}$ as $\bm{S}_{\perp}$, where $\mathfrak{s}=\mbox{span}\left(\bm{S}_{\perp}\right)$ is the nullspace of $\bm{S}$.
+We also note that when $\bm{S}$ is understood as a linear mapping $\bm{S}:\mathbb{R}^m\rightarrow\mathbb{R}^n$ whose image given by the coherent space $\mathfrak{s}$.
+This is depicted in Figure~\ref{fig2}.
 
@@
     \node at (4,5) {$\mathbb{R}^n$(codomain of $\bm{S}$)};
-    \node at (4,1.0) {$\mathbb{C}^m$};
+    \node at (4,1.0) {$\mathfrak{s}$};
     %\node[bullet,label=below:$f(x)$] at (4,2.5){};
@@
   \end{center}
-  \caption{Any set $\bm{A} \in \mathbb{R}^m$ will be mapped to $\mathbb{C}^m$ through the mapping $\bm{S}$.}\label{fig2}
+  \caption{The domain, codomain and image of the mapping $\bm{S}$.}\label{fig2}
 \end{figure}
 
-Definition~\ref{def:cohprob} implies the probability measure on $\mathbb{C}^m$ is equivalent to the probability measure on $(\mathbb{R}^m, \bm{\mathscr{F}}^m)$.
+\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
+  Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a point forecast of the values of all series in the hierarchy at time $t+h$,  made using information up to and including time $t$.
+Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathfrak{s}$.
+\end{definition}
+
+\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
+  Let $(\mathbb{R}^m, \bm{\mathscr{F}}, \nu)$ be a probability triple, where $\mathscr{F}$ is the usual $\sigma$-algebra on $\mathbb{R}^m$.
+Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_{\mathfrak{s}}$.
+Here $\mathscr{F}_{\mathfrak{s}}$ is formed as collection of sets $\bm{S}(\bm{A})$, where $\bm{S}(\bm{A})$ denotes the image of the set $\bm{A}\in \mathscr{F}$ under the mapping $\bm{S}$.
+Then $\breve{\nu}$ is said to be a \emph{coherent probability measure} iff
+  $$
+      \breve{\nu}(\bm{S}(\bm{A})) = \nu(\bm{A}) \quad \forall  \bm{A} \in \mathscr{F},
+    $$  
+\end{definition}
+
+%Definition~\ref{def:cohprob} implies the probability measure on $\mathbb{C}^m$ is equivalent to the probability measure on $(\mathbb{R}^m, \bm{\mathscr{F}}^m)$.
 Hence, there is no density anywhere outside the linear subspace $\mathbb{C}^m$.
@@
 
-The following example will help to understand these definitions more clearly.
+%The following example will help to understand these definitions more clearly.
 
-Consider a simple hierarchy with two bottom-level series $A$ and $B$ that add up to the top level series $Tot$.
+%Consider a simple hierarchy with two bottom-level series $A$ and $B$ that add up to the top level series $Tot$.
 Suppose the forecasts of these series at time $t+h$ are given by $\breve{\bm{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$.

### 2018-04-01 ProbabilisticCoherence.tex
Cleaned up definition of basis series and comparison to Ben Taieb Taylor Hyndman definition of coherence

@@
 
-For a particular coherent subspace $\mathbb{C}^m$, there exist several distinct basis vectors. For example, in the small hierarchy considered above, 
- $\{(1 ~1 ~0)', (1 ~0 ~1)'\}$, 
- $\{(1 ~ 0 ~ 1)',(0~1~-\!\!1)'\}$ 
-and the singular value decomposition of these two are some alternative basis vectors that span the same $\mathbb{C}^m$.
-Given a basis for $\mathbb{C}^m$, every series of the hierarchy can be linearly determined as a linear combination of those basis vectors.
-We refer to the coefficients of these linear combinations as the \textit{basis series}.
-It is apparent that these basis series are $m$-dimensional and linearly independent in a given hierarchy.
-For example, in the smallest hierarchy, $(A,B)$ and $(Tot,A)$ are the basis series corresponding to the basis vectors
- $\{(1 ~1 ~0)', (1 ~0 ~1)'\}$, 
- $\{(1 ~ 0 ~ 1)',(0~1~-\!\!1)'\}$
-respectively. Thus it is clear that the set of bottom-level series is a basis series that corresponds to the column vectors of $\bm{S}$.
+These definitions of the coherent space $\mathfrak{s}$ and coherent point and probabilistic forecasts are defined in terms of the mapping $\bm{S}$ and may give the impression that the bottom level series play an important role in the definition.
+However, alternative definitions could be formed using any set of basis vectors that spans $\mathfrak{s}$.
+For example, consider the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$.
+In this case the matrix $\bm{S}$ has columns  $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$ and the mapping $\bm{S}$ transforms $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy.
+However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy.
+In general, since there are an infinite number linear bases for $\mathfrak{s}$ the definitions above could be made in terms of any series and not just the bottom level series.
+In general we will call the series (or linear combinations thereof) used in the definitions of coherence as \textit{basis series}.
+Unless stated otherwise, we will always consider the bottom level series to be the basis series, since this facilitates comparison with existing approaches in the literature.
 
-Because the basis is not unique for a given coherent subspace, Definition~\ref{def:cohprob} is not unique, and one can redefine the coherent probabilistic forecasts with respect to any basis.
+%Because the basis is not unique for a given coherent subspace, Definition~\ref{def:cohprob} is not unique, and one can redefine the coherent probabilistic forecasts with respect to any basis.
 However, we stick to Definition~\ref{def:cohprob} and consider the basis defined by the columns of $\bm{S}$ in what follows.
 
-Definitions~\ref{def:cohpoint} and~\ref{def:cohprob} facilitate extension to probabilistic forecast reconciliation which we discuss in the next section.
-In contrast to our definition, \citet{BenTaieb2017} define coherent probabilistic forecasts in terms of convolutions.
-According to their definition, if the forecasts are coherent, then the convolution of forecast distributions of disaggregate series is identical to the forecast distribution of the corresponding aggregate series.
-While this is consistent with our definition, it is not easy to extend their definition to deal with probabilistic reconciliation.
+%Definitions~\ref{def:cohpoint} and~\ref{def:cohprob} facilitate extension to probabilistic forecast reconciliation which we discuss in the next section. 
+To  the best of our knowledge, the only other definition of coherent probabilistic forecasts is given by \citet{BenTaieb2017} who define coherent probabilistic forecasts in terms of convolutions.
+According to their definition, probabilistic forecasts are coherent when a convolution of forecast distributions of disaggregate series is identical to the forecast distribution of the corresponding aggregate series.
+Their definition is consistent with our definition, our reason for providing a different definition is that the geometric understanding of coherence will facilitate our definitions of probabilistic forecast reconciliation to which we now turn our attention.
 

### 2018-04-02 ProbabilisticCoherence.tex
Point reconciliation defined in terms of linear maps - non-linear mappings will come in their own section

@@
   \begin{equation}
-    \tilde{\bm{y}}_{t+h}=\bm{S} \circ \bm{g}(\hat{\bm{y}}_{t+h}),
+    \tilde{\bm{y}}_{t+h}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h},
   \end{equation} 
-  where $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m$ and $\bm{S}\circ \bm{g}(\cdot)$ is a projection of $\bm{g}(\cdot)$ onto $\mathbb{C}^m$.
-Then $\tilde{\bm{y}}_{t+h}$ is said to be ``reconciled'' if  $\tilde{\bm{y}}_{t+h} \in \mathbb{C}^m$.
+  where $\bm{G}$ is an $m\times n$ matrix. We say $\tilde{\bm{y}}_{t+h}$ is ``reconciled'' with respect to the mapping $\bm{G}$.
 \end{definition}
 
-Definition~\ref{def:reconpoint} allows for both linear and non-linear reconciliation.
-In other words, if $\bm{g}$ is a non-linear function, then the reconciliation of $\hat{\bm{y}}_{t+h}$ will be non-linear, while if $\bm{g}$ is a linear function, then $\bm{S}\circ \bm{g}(\cdot)$ will linearly project incoherent point forecasts onto $\mathbb{C}^m$.
-Previous studies in hierarchical point forecasting have only focussed on the linear case, $\bm{g}(\bm{y}) = \bm{P}\bm{y}$, where $\bm{P}$ is an $m \times n$ matrix, and so $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$.
+In definition~\ref{def:reconpoint} we assume $\bm{G}$ to be a linear mapping, which implies that  $\bm{S}\bm{G}$ is a projection matrix from $\mathbb{R}^n$ onto $\mathfrak{s}$.
+This is consistent with previous studies where the notation $\bm{P}$ is often used in place of $\bm{G}$.
+In principle ${\bm G}$ can be a non-linear mapping $\bm{G}:\mathbb{R}^n \rightarrow \mathbb{R}^m$ a possibility we consider in Section~\ref{nonlinear} [TO BE ADDED LATER].
 

### 2018-04-02 ProbabilisticCoherence.tex
Changed  discussion of R matrix

@@
 
-We also denote the $n\times(n-m)$ orthogonal complement of $\bm{S}$ as $\bm{S}_{\perp}$, where $\mathfrak{s}=\mbox{span}\left(\bm{S}_{\perp}\right)$ is the nullspace of $\bm{S}$.
+We also denote the $n\times(n-m)$ orthogonal complement of $\bm{S}$ as $\bm{S}_{\perp}$, where $\mathfrak{s}_\perp=\mbox{span}\left(\bm{S}_{\perp}\right)$ is the nullspace of $\bm{S}$.
 We also note that when $\bm{S}$ is understood as a linear mapping $\bm{S}:\mathbb{R}^m\rightarrow\mathbb{R}^n$ whose image given by the coherent space $\mathfrak{s}$.
@@
 
-Using Definition~\ref{def:reconpoint}, we can now explain previous results for linear forecast reconciliation.
-Let $\bm{R} \in \mathbb{R}^{n \times (n-m)}$ comprise the columns that span $\bm{\mathbb{N}}^{n-m}$, which is orthogonal to $\mathbb{C}^m$.
-Note that $\bm{R}$ is not unique; one example is a matrix whose columns represent the aggregation constraints for a given hierarchy.
-For the hierarchy in example 1,
-$$ 
-\bm{S} = 
-\begin{pmatrix} 
-1& 1 \\ 1 & 0 \\ 0&1 
-\end{pmatrix} 
-\quad \text{and} \quad 
-\bm{R} = 
-\begin{pmatrix}  
-1 \\ -1 \\ -1 
-\end{pmatrix}.
-$$
-
-Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively.
+Definition~\ref{def:reconpoint}, in fact defines an entire family of forecast reconciliation methods including many methods currently extant in the literature.
+To provide a geometric interpretation, we introduce an $\mathbb{R}^{n \times (n-m)}$ matrix $\bm{R}$ whose columns span the null space $\mathfrak{s}_{\perp}$.
+The columns of $\bm{R}$ can be thought of as `directions' along which incoherent point forecasts are projected onto the coherent space.
+A straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$ is the vector $(1,-1,-1)$.
+This vector is orthogonal to the columns of $\bm{S}$ in the usual sense of Euclidean geometry.
+%$$ 
+%\bm{S} = 
+%\begin{pmatrix} 
+%1& 1 \\ 1 & 0 \\ 0&1 
+%\end{pmatrix} 
+%\quad \text{and} \quad 
+%\bm{R} = 
+%\begin{pmatrix}  
+%1 \\ -1 \\ -1 
+%\end{pmatrix}.
+%$$ 
+%
+%Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively.
 Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$.

### 2018-04-02 ProbabilisticCoherence.tex
Discussion around point reconciliation definition cleaned up. Discussion about SPS=S added

@@
 This is consistent with previous studies where the notation $\bm{P}$ is often used in place of $\bm{G}$.
-In principle ${\bm G}$ can be a non-linear mapping $\bm{G}:\mathbb{R}^n \rightarrow \mathbb{R}^m$ a possibility we consider in Section~\ref{nonlinear} [TO BE ADDED LATER].
+In principle ${\bm G}$ can be a non-linear mapping $\bm{G}:\mathbb{R}^n \rightarrow \mathbb{R}^m$ a possibility we consider in Section~\ref{nonlinear} {\color{red}[AP: I WILL ADD THIS LATER]}.
 
-Definition~\ref{def:reconpoint}, in fact defines an entire family of forecast reconciliation methods including many methods currently extant in the literature.
-To provide a geometric interpretation, we introduce an $\mathbb{R}^{n \times (n-m)}$ matrix $\bm{R}$ whose columns span the null space $\mathfrak{s}_{\perp}$.
-The columns of $\bm{R}$ can be thought of as `directions' along which incoherent point forecasts are projected onto the coherent space.
-A straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$ is the vector $(1,-1,-1)$.
-This vector is orthogonal to the columns of $\bm{S}$ in the usual sense of Euclidean geometry.
+Definition~\ref{def:reconpoint}, actually defines an entire family of forecast reconciliation methods including many methods currently extant in the literature.
+To provide a geometric interpretation, we introduce an $n \times (n-m)$ matrix $\bm{R}$ whose columns span the null space $\mathfrak{s}_{\perp}$.
+The matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
+However, since $\bm{R}$ is not unique, the columns of any given $\bm{R}$ matrix can also be thought of as `directions' along which incoherent point forecasts are projected onto the coherent space.
+For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$ is the vector $(1,-1,-1)$, which is orthogonal to the columns of $\bm{S}$ in the usual sense of Euclidean geometry.
 %$$ 
@@
 
-\subsubsection*{Step 1: Obtaining reconciled bottom-level point forecasts}
+%\subsubsection*{Step 1: Change of basis}
 
-For a given incoherent set of point forecasts $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$, first we find the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$.
-Let $(\tilde{\bm{b}}'_{t+h} , \tilde{\bm{t}}'_{t+h})'$ denote these coordinates.
-Note that $\tilde{\bm{b}}_{t+h}$ is a basis series which is equivalent to the reconciled bottom-level series, and which corresponds to the linear combination coefficients of the basis $\{\bm{s}_1,\dots,\bm{s}_m\}$.
-Similarly, $\tilde{\bm{t}}_{t+h}$ is another basis series corresponding to the linear combination coefficients of the basis $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$.
-Then from basic properties of linear algebra it follows that
+To illustrate further note that the columns of $\bm{S}$ and $\bm{R}$ provide a basis for $\mathbb{R}^n$.
+As such any vector of incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$, can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$.
+Let $\tilde{\bm{b}}'_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$, respectively.
+The process of reconciliation involves setting $\tilde{\bm{b}}_{t+h|t}$ to be the values of the reconciled bottom-level series and setting $\tilde{\bm{a}}_{t+h}=\bm{0}$ to ensure coherence.
+From properties of linear algebra it follows that
+%\[
+%(\bm{S} ~ \vdots~ \bm{R})
+%(\tilde{\bm{b}}'_{t+h},~ \tilde{\bm{t}}'_{t+h})'
+%= \hat{\bm{y}}_{t+h},
+%\]
 \[
-(\bm{S} ~ \vdots~ \bm{R})
-(\tilde{\bm{b}}'_{t+h},~ \tilde{\bm{t}}'_{t+h})'
-= \hat{\bm{y}}_{t+h},
+\hat{\bm{y}}_{t+h|t} = (\bm{S} ~ \vdots~ \bm{R})
+(\tilde{\bm{b}}'_{t+h|t},~ \tilde{\bm{a}}'_{t+h|t})'= \bm{S}\tilde{\bm{b}}_{t+h|t} +  \bm{R}\tilde{\bm{a}}_{t+h|t},
 \]
+while setting $\tilde{\bm{a}}_{t+h|t}=\bm{0}$ gives the reconciled point forecast
 \[
-\hat{\bm{y}}_{t+h} = \bm{S}\tilde{\bm{b}}_{t+h} +  \bm{R}\tilde{\bm{t}}_{t+h},
+\tilde{\bm{y}}_{t+h|t} = \bm{S}\tilde{\bm{b}}_{t+h|t}
 \]
-and
-\begin{equation}\label{4.3}
-(\tilde{\bm{b}}'_{t+h}, ~ \tilde{\bm{t}}'_{t+h})' =
-(\bm{S} ~ \vdots~ \bm{R})^{-1}
-\hat{\bm{y}}_{t+h}.
-\end{equation}
 
-In order to find $(\bm{S} ~ \vdots~ \bm{R})^{-1}$, let $\bm{S}_{\bot}$ and $\bm{R}_{\bot}$ be the orthogonal complements of $\bm{S}$ and $\bm{R}$
-respectively. Then $(\bm{S} ~ \vdots~ \bm{R})^{-1}$ is given by
+%\begin{equation}\label{4.3}
+%(\tilde{\bm{b}}'_{t+h}, ~ \tilde{\bm{t}}'_{t+h})' =
+%(\bm{S} ~ \vdots~ \bm{R})^{-1}
+%\hat{\bm{y}}_{t+h}.
+%\end{equation}
+
+In order to find $\tilde{\bm{b}}'_{t+h|t}$ we require the inverse $(\bm{S} ~ \vdots~ \bm{R})^{-1}$ which is given by
 \begin{equation}
@@
 (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
-\end{pmatrix}.
+\end{pmatrix}\,,
 \end{equation}
-Thus we have,
-\begin{equation} \label{4.4}
-\begin{pmatrix}
-\tilde{\bm{b}}_{t+h} \\ \cdots \\ \tilde{\bm{t}}_{t+h}
-\end{pmatrix} = \begin{pmatrix}
-(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
-\end{pmatrix}\hat{\bm{y}}_{t+h}.
-\end{equation}
+where $\bm{S}_{\bot}$ and $\bm{R}_{\bot}$ be the orthogonal complements of $\bm{S}$ and $\bm{R}$
+respectively.
+Thus it follows that $\tilde{\bm{b}}_{t+h}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$.
+Here $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ is equivalent to $\bm{G}$ in Definition~\ref{def:reconpoint}.
 
-From \eqref{4.4} it follows that
-\begin{equation}
-\tilde{\bm{b}}_{t+h}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}
-\end{equation}
+%\begin{equation} \label{4.4}
+%\begin{pmatrix}
+%\tilde{\bm{b}}_{t+h} \\ \cdots \\ \tilde{\bm{t}}_{t+h}
+%\end{pmatrix} = \begin{pmatrix}
+%(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
+%\end{pmatrix}\hat{\bm{y}}_{t+h}.
+%\end{equation}
+%From \eqref{4.4} it follows that
+%\begin{equation}
+%\tilde{\bm{b}}_{t+h}=(\bm{R}'_\bot %\bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}
+%\end{equation}
 
-\subsubsection*{Step 2: Obtaining reconciled point forecasts for the whole hierarchy}
-
-This step directly follows from the definition for coherent forecasts.
+%\subsubsection*{Step 2: Obtaining reconciled point forecasts for the whole hierarchy}
+%
+%This step directly follows from the definition for coherent forecasts.
 To obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \mathbb{R}^n$ to the $\mathbb{C}^m$ through $\bm{S}$.
 Thus we have,
-\begin{equation}
-\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \qquad \tilde{\bm{y}}_{t+h} \in \mathbb{C}^m<\mathbb{R}^n.
-\end{equation}
+%\begin{equation}
+%\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \qquad \tilde{\bm{y}}_{t+h} \in \mathbb{C}^m<\mathbb{R}^n.
+%\end{equation}
 
 Finding a suitable $\bm{R}_\bot$ with respect to a certain loss function will lead to optimally reconciled point forecasts of the hierarchy.
-If $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$, then the definition for linear reconciliation of point forecasts in previous studies coincides with our explanation.
-
+%If $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$, then the definition for linear reconciliation of point forecasts in previous studies coincides with our explanation.
 In our context, we need to find $\bm{R}_\bot$ such that $\bm{R}'_\bot \bm{S}$ is invertible; i.e, $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \bm{S}=\bm{I}$.
-This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}.
+This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}{\color{red}[AP:NONE OF THIS MAKES SENSE TO ME.
+$R_{\perp}'S$ WILL BE INVERTIBLE AS LONG AS NONE OF THE COLUMNS OF R SIT ON THE COLUMN SPACE OF S.
+AS LONG AS R IS STICKING INTO THE NULL SPACE OF S, THEN SPS=S ALWAYS SINCE SP IS JUST A PROJECTION THAT PUTS VECTORS ON THE COLUMN SPACE OF S.
+SINCE THE COLUMNS OF S ARE ALREADY ON THE COLUMN SPACE OF S, THEN MULTIPLYING SP SIMPLY DOES NOTHING TO THEM.
+THE CONNECTION TO UNBIASEDNESS IS STILL NOT CLEAR TO ME.]}.
 

### 2018-04-02 ProbabilisticCoherence.tex
Definition of probabilistic reconciliation cleaned up

@@
 \begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
-  Let $(\mathbb{R}^m, \bm{\mathscr{F}}, \nu)$ be a probability triple, where $\mathscr{F}$ is the usual $\sigma$-algebra on $\mathbb{R}^m$.
-Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_{\mathfrak{s}}$.
-Here $\mathscr{F}_{\mathfrak{s}}$ is formed as collection of sets $\bm{S}(\bm{A})$, where $\bm{S}(\bm{A})$ denotes the image of the set $\bm{A}\in \mathscr{F}$ under the mapping $\bm{S}$.
+  Let $(\mathbb{R}^m, \mathscr{F}^{\mathbb{R}^m}, \nu)$ be a probability triple, where $\mathscr{F}^{\mathbb{R}^m}$ is the usual $\sigma$-algebra on $\mathbb{R}^m$.
+Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}^{\mathfrak{s}}$.
+Here $\mathscr{F}_{\mathfrak{s}}$ is formed as collection of sets $s(A)$, where $s(A)$ denotes the image of the set $A\in \mathscr{F}$ under the mapping $s(.)$ and the mapping $s:\mathbb{R}^m\rightarrow\mathbb{R}^n$ denotes premultiplication by the matrix $\bm{S}$.
 Then $\breve{\nu}$ is said to be a \emph{coherent probability measure} iff
   $$
-      \breve{\nu}(\bm{S}(\bm{A})) = \nu(\bm{A}) \quad \forall  \bm{A} \in \mathscr{F},
+      \breve{\nu}(s(A)) = \nu(A) \quad \forall  A \in \mathscr{F}^{\mathbb{R}^m},
     $$  
@@
   \end{equation} 
-  where $\bm{G}$ is an $m\times n$ matrix. We say $\tilde{\bm{y}}_{t+h}$ is ``reconciled'' with respect to the mapping $\bm{G}$.
+  where $\bm{G}$ is an $m\times n$ matrix.
+We say $\tilde{\bm{y}}_{t+h}$ is ``reconciled'' with respect to the mapping $g(.)$, where $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ is defined as premultiplication be $\bm{G}$.
 \end{definition}
 
-In definition~\ref{def:reconpoint} we assume $\bm{G}$ to be a linear mapping, which implies that  $\bm{S}\bm{G}$ is a projection matrix from $\mathbb{R}^n$ onto $\mathfrak{s}$.
-This is consistent with previous studies where the notation $\bm{P}$ is often used in place of $\bm{G}$.
-In principle ${\bm G}$ can be a non-linear mapping $\bm{G}:\mathbb{R}^n \rightarrow \mathbb{R}^m$ a possibility we consider in Section~\ref{nonlinear} {\color{red}[AP: I WILL ADD THIS LATER]}.
+In definition~\ref{def:reconpoint}  $\bm{S}\bm{G}$ is a projection matrix that maps $\mathbb{R}^n$ onto $\mathfrak{s}$.
+We note that a similar characterisation of reconciliation has been used in previous studies but where the notation $\bm{P}$ is used in place of $\bm{G}$.
+In principle $g(.)$ can also be a non-linear mapping, a possibility we consider in Section~\ref{nonlinear} {\color{red}[AP: I WILL ADD THIS LATER]}.
 
@@
 
-For probabilistic forecasts, reconciliation implies finding the probability measure of the coherent forecasts using the information from an incoherent probabilistic forecast measure.
+We now extend the methodology of point forecast reconciliation to probabilistic forecasts
+
+%For probabilistic forecasts, reconciliation implies finding the probability measure of the coherent forecasts using the information from an incoherent probabilistic forecast measure.
 A more formal definition is given below.
@@
 \begin{definition} \label{def:reconprob}
-  Suppose $(\mathbb{R}^n, \mathscr{F}^n, \hat{\nu})$ is an incoherent probability triple and $(\mathbb{R}^m, \mathscr{F}^m, \nu^m)$ is a probability triple defined on $\mathbb{R}^m$.
-Let $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m $.
-Then the probability measure on the reconciled bottom levels is such that
+  Let $(\mathbb{R}^n, \mathscr{F}^{\mathbb{R}^n}, \hat{\nu})$ be an incoherent probability triple   defined on $\mathbb{R}^n$ associated with $\bm{y}_{t+h}$ conditional on all information up to time $t$.
+Let $(\mathbb{R}^m, \mathscr{F}^{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$.
+Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear mapping.
+Let $\nu$ have the following property:
   \begin{equation}
-  \nu^m(\bm{A}) = \hat{\nu}(\bm{g}^{-1}(\bm{A})), \quad \forall \quad \bm{A} \in \mathscr{F}^m.
+  \nu(A) = \hat{\nu}(g^{-1}(A)), \quad \forall \quad A \in \mathscr{F}^{\mathbb{R}^m}\,,
   \end{equation}
-  Further the probability measure of the whole reconciled hierarchy is given by
+  where $g^{-1}(A)$ denotes the pre-image of the measurable set $A$, that is the set of all points in $\mathbb{R}^n$ that map to a point in $A$ under the mapping $g(.)$ or $g^{-1}(A):=\left\{\bm{y}\in \mathbb{R}^n:\bm{Gy}\in A \right\}$.
+We define $\tilde{\nu}$ as the reconciled probability measure of $\hat{\nu}$ with respect to the mapping $g(.)$ if the following holds
   \begin{equation}
-  \tilde{\nu}(\bm{S}(\bm{A})) = \hat{\nu}(\bm{g}^{-1}(\bm{A})) \qquad \forall \bm{A} \in \mathscr{F}^m,
+  \tilde{\nu}(s(A)) = \nu(A)= \hat{\nu}(\bm{g}^{-1}(A)) \qquad \forall A \in \mathscr{F}^{\mathbb{R}^m},
   \end{equation}
-  where $\bm{S}:\mathbb{R}^m \rightarrow \mathbb{C}^m$ and $\tilde{\nu}(\cdot)$ is the probability measure on the measure space $(\mathbb{C}^m, \mathscr{F}_S)$.
+  where $\tilde{\nu}(\cdot)$ is the probability measure on the measure space $(\mathfrak{s}, \mathscr{F}_\mathfrak{s})$.
 \end{definition}

### 2018-04-02 ProbabilisticCoherence.tex
Changes throughout sections 2,3 and 4 to make things more consistent

@@
 \end{equation}
-where $\bm{S}$ is an $n \times m$ constant matrix encoding the aggregation constraints.
+where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints.
 For example for the hierarchy in Figure~\ref{fig1}, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and
@@
 
-where $I_4$ is a $4$-dimension identity matrix.
+where $\bm{I}_4$ is a $4\times 4$ identity matrix.
 
@@
 It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect aggregation constraints.
-We follow other authors in describing this property as {\em coherence}.
+We follow other authors in using the nomenclature{\em coherence} to describe this property.
 %While coherent point forecasts have been discussed many times previously, the definitions of coherence previously given are vague and are not easily extended to the situation of probabilistic forecasting.
 
-We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem thus facilitating the development of the reconciliation techniques of section~\ref{sec:reconciliation}.
+We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem thus facilitating the development of the probabilistic forecast reconciliation in section~\ref{sec:reconciliation}.
 
-\begin{definition}[Coherent subspace]
+\begin{definition}[Coherent subspace]\label{def:cohspace}
 Let an $n$-dimensional time series $\bm{y}_t \in \mathbb{R}^n$ be subject to the linear aggregation constraint $\bm{y}_t = \bm{S}\bm{b}_t$, where $\bm{b}_t \in \mathbb{R}^m$ and $\bm{S}$ is an $n \times m$ constant matrix.
@@
 We also denote the $n\times(n-m)$ orthogonal complement of $\bm{S}$ as $\bm{S}_{\perp}$, where $\mathfrak{s}_\perp=\mbox{span}\left(\bm{S}_{\perp}\right)$ is the nullspace of $\bm{S}$.
-We also note that when $\bm{S}$ is understood as a linear mapping $\bm{S}:\mathbb{R}^m\rightarrow\mathbb{R}^n$ whose image given by the coherent space $\mathfrak{s}$.
-This is depicted in Figure~\ref{fig2}.
+Also at times is  will be useful to think of pre-multiplication by $\bm{S}$ as a linear mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$ in which case we use the notation $s(.)$.
+Although the codomain of $s(.)$ is $\mathbb{R}^n$ its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.
 
@@
 
-    \node at (2,3) {$\bm{S}$};
+    \node at (2,3) {$s$};
 
-    \node at (0,5) {$\mathbb{R}^m$(domain of $\bm{S}$)};
-    \node at (4,5) {$\mathbb{R}^n$(codomain of $\bm{S}$)};
-    \node at (4,1.0) {$\mathfrak{s}$};
+    \node at (0,5) {$\mathbb{R}^m$(domain of $s$)};
+    \node at (4,5) {$\mathbb{R}^n$(codomain of $s$)};
+    \node at (4.5,1.0) {$\mathfrak{s}$(image of $s$)};
     %\node[bullet,label=below:$f(x)$] at (4,2.5){};
@@
   \end{center}
-  \caption{The domain, codomain and image of the mapping $\bm{S}$.}\label{fig2}
+  \caption{The domain, codomain and image of the mapping $s$.}\label{fig2}
 \end{figure}
@@
 Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}^{\mathfrak{s}}$.
-Here $\mathscr{F}_{\mathfrak{s}}$ is formed as collection of sets $s(A)$, where $s(A)$ denotes the image of the set $A\in \mathscr{F}$ under the mapping $s(.)$ and the mapping $s:\mathbb{R}^m\rightarrow\mathbb{R}^n$ denotes premultiplication by the matrix $\bm{S}$.
-Then $\breve{\nu}$ is said to be a \emph{coherent probability measure} iff
+Here $\mathscr{F}^{\mathfrak{s}}$ is formed as collection of sets $s(A)$, where $s(A)$ denotes the image of the set $A\in \mathscr{F}^{\mathbb{R}^m}$ under the mapping $s(.)$.
+Let the measure $\breve{\nu}$ have the property
   $$
@@
     $$  
+  A probabilistic forecast is coherent if uncertainty in $\bm{y_{t+h}}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}^{\mathfrak{s}},\breve{\nu})$.
 \end{definition}
@@
 
-These definitions of the coherent space $\mathfrak{s}$ and coherent point and probabilistic forecasts are defined in terms of the mapping $\bm{S}$ and may give the impression that the bottom level series play an important role in the definition.
+These definitions of the coherent space $\mathfrak{s}$ and coherent point and probabilistic forecasts are defined in terms of the mapping $s(.)$ and may give the impression that the bottom level series play an important role in the definition.
 However, alternative definitions could be formed using any set of basis vectors that spans $\mathfrak{s}$.
@@
 In general we will call the series (or linear combinations thereof) used in the definitions of coherence as \textit{basis series}.
-Unless stated otherwise, we will always consider the bottom level series to be the basis series, since this facilitates comparison with existing approaches in the literature.
+Unless stated otherwise, we will always consider the basis series to be the bottom level series as in Definition~\ref{def:cohpoint} and Defintion~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.
 
@@
 According to their definition, probabilistic forecasts are coherent when a convolution of forecast distributions of disaggregate series is identical to the forecast distribution of the corresponding aggregate series.
-Their definition is consistent with our definition, our reason for providing a different definition is that the geometric understanding of coherence will facilitate our definitions of probabilistic forecast reconciliation to which we now turn our attention.
+Their definition is consistent with our definition, our reason for providing a different definition is that the geometric understanding of coherence will facilitate our definitions of point and probabilistic forecast reconciliation to which we now turn our attention.
 
@@
 
+  Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent forecasts at time $t+h$ using information up to and including time $t$.
+Let $\bm{G}$ be an $m\times n$ matrix and $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping corresponding to pre-multiplication by $\bm{G}$.
   \begin{definition}\label{def:reconpoint}
-  Let $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$ be any set of incoherent forecasts at time $t+h$, and let 
+  The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $g(.)$ iff
   \begin{equation}
-    \tilde{\bm{y}}_{t+h}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h},
+    \tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}\,.
   \end{equation}
-  where $\bm{G}$ is an $m\times n$ matrix.
-We say $\tilde{\bm{y}}_{t+h}$ is ``reconciled'' with respect to the mapping $g(.)$, where $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ is defined as premultiplication be $\bm{G}$.
+
 \end{definition}
@@
 We note that a similar characterisation of reconciliation has been used in previous studies but where the notation $\bm{P}$ is used in place of $\bm{G}$.
-In principle $g(.)$ can also be a non-linear mapping, a possibility we consider in Section~\ref{nonlinear} {\color{red}[AP: I WILL ADD THIS LATER]}.
+In principle the definition can be generalised where $g(.)$ is a non-linear mapping, a possibility we consider in Section~\ref{nonlinear} {\color{red}[AP: I WILL ADD THIS LATER]}.
 
@@
 To illustrate further note that the columns of $\bm{S}$ and $\bm{R}$ provide a basis for $\mathbb{R}^n$.
-As such any vector of incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$, can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$.
+As such any incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$, can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$.
 Let $\tilde{\bm{b}}'_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$, respectively.
@@
 \[
-\hat{\bm{y}}_{t+h|t} = (\bm{S} ~ \vdots~ \bm{R})
-(\tilde{\bm{b}}'_{t+h|t},~ \tilde{\bm{a}}'_{t+h|t})'= \bm{S}\tilde{\bm{b}}_{t+h|t} +  \bm{R}\tilde{\bm{a}}_{t+h|t},
+\hat{\bm{y}}_{t+h|t} = (\bm{S} ~ \bm{R})
+\begin{pmatrix}
+\tilde{\bm{b}}_{t+h|t}\\ \tilde{\bm{a}}_{t+h|t}
+\end{pmatrix}= \bm{S}\tilde{\bm{b}}_{t+h|t} +  \bm{R}\tilde{\bm{a}}_{t+h|t},
 \]
@@
 
-In order to find $\tilde{\bm{b}}'_{t+h|t}$ we require the inverse $(\bm{S} ~ \vdots~ \bm{R})^{-1}$ which is given by
+In order to find $\tilde{\bm{b}}_{t+h|t}$ we require the inverse $(\bm{S} ~ \bm{R})^{-1}$ which is given by
 \begin{equation}
-(\bm{S} ~ \vdots~ \bm{R})^{-1} = \begin{pmatrix}
-(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
+(\bm{S} ~  \bm{R})^{-1} = \begin{pmatrix}
+(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
 \end{pmatrix}\,,
@@
 
+  Let $(\mathbb{R}^n, \mathscr{F}^{\mathbb{R}^n}, \hat{\nu})$ be an incoherent probability triple that characterises forecast uncertainty in for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.
+Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear mapping.
+Let $(\mathbb{R}^m, \mathscr{F}^{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$ where $\nu$ has the following property:
+  \begin{equation}
+  \nu(A) = \hat{\nu}(g^{-1}(A)), \quad \forall \quad A \in \mathscr{F}^{\mathbb{R}^m}\,.
+  \end{equation}
+  Here $g^{-1}(A)$ denotes the pre-image of the measurable set $A$, that is $g^{-1}(A):=\left\{\bm{y}\in \mathbb{R}^n:\bm{Gy}\in A \right\}$.
+In words, the preimage $g^{-1}(A)$ is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $A$.
   \begin{definition} \label{def:reconprob}
-  Let $(\mathbb{R}^n, \mathscr{F}^{\mathbb{R}^n}, \hat{\nu})$ be an incoherent probability triple   defined on $\mathbb{R}^n$ associated with $\bm{y}_{t+h}$ conditional on all information up to time $t$.
-Let $(\mathbb{R}^m, \mathscr{F}^{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$.
-Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear mapping.
-Let $\nu$ have the following property:
-  \begin{equation}
-  \nu(A) = \hat{\nu}(g^{-1}(A)), \quad \forall \quad A \in \mathscr{F}^{\mathbb{R}^m}\,,
-  \end{equation}
-  where $g^{-1}(A)$ denotes the pre-image of the measurable set $A$, that is the set of all points in $\mathbb{R}^n$ that map to a point in $A$ under the mapping $g(.)$ or $g^{-1}(A):=\left\{\bm{y}\in \mathbb{R}^n:\bm{Gy}\in A \right\}$.
   We define $\tilde{\nu}$ as the reconciled probability measure of $\hat{\nu}$ with respect to the mapping $g(.)$ if the following holds
   \begin{equation}
-  \tilde{\nu}(s(A)) = \nu(A)= \hat{\nu}(\bm{g}^{-1}(A)) \qquad \forall A \in \mathscr{F}^{\mathbb{R}^m},
+  \tilde{\nu}(s(A)) = \nu(A)= \hat{\nu}(g^{-1}(A)) \qquad \forall A \in \mathscr{F}^{\mathbb{R}^m},
   \end{equation}
-  where $\tilde{\nu}(\cdot)$ is the probability measure on the measure space $(\mathfrak{s}, \mathscr{F}_\mathfrak{s})$.
+  where $\tilde{\nu}(\cdot)$ is a probability measure on the $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_\mathfrak{s}$.
 \end{definition}

### 2018-04-04 ProbabilisticCoherence.tex
Correction made to earlier changes about R as restriction matrix, further cleaning up of definition of probabilisitic forecast reconciliation

@@
 To provide a geometric interpretation, we introduce an $n \times (n-m)$ matrix $\bm{R}$ whose columns span the null space $\mathfrak{s}_{\perp}$.
-The matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
-However, since $\bm{R}$ is not unique, the columns of any given $\bm{R}$ matrix can also be thought of as `directions' along which incoherent point forecasts are projected onto the coherent space.
 For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$ is the vector $(1,-1,-1)$, which is orthogonal to the columns of $\bm{S}$ in the usual sense of Euclidean geometry.
+In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
+In general, the columns of any given $\bm{R}$ matrix can also be thought of as `directions' along which incoherent point forecasts are projected onto the coherent space, and these directions need not be orthogonal to $\mathfrak{s}$.
 %$$ 
@@
 
-  Let $(\mathbb{R}^n, \mathscr{F}^{\mathbb{R}^n}, \hat{\nu})$ be an incoherent probability triple that characterises forecast uncertainty in for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.
+  Let $(\mathbb{R}^n, \mathscr{F}^{\mathbb{R}^n}, \hat{\nu})$ be an probability triple, that is not necessarily coherent and that characterises forecast uncertainty for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.
 Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear mapping.
@@
   \end{equation}
-  Here $g^{-1}(A)$ denotes the pre-image of the measurable set $A$, that is $g^{-1}(A):=\left\{\bm{y}\in \mathbb{R}^n:\bm{Gy}\in A \right\}$.
-In words, the preimage $g^{-1}(A)$ is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $A$.
+  Here $g^{-1}(A):=\left\{\bm{y}\in \mathbb{R}^n:g(\bm{y})\in A \right\}$ is the pre-image of $A$, that is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $A$.
   \begin{definition} \label{def:reconprob}
-  We define $\tilde{\nu}$ as the reconciled probability measure of $\hat{\nu}$ with respect to the mapping $g(.)$ if the following holds
+  We define the reconciled probability measure of $\hat{\nu}$ with respect to the mapping $g(.)$ as a probability measure $\tilde{\nu}$ on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_\mathfrak{s}$ where the following holds
   \begin{equation}
-  \tilde{\nu}(s(A)) = \nu(A)= \hat{\nu}(g^{-1}(A)) \qquad \forall A \in \mathscr{F}^{\mathbb{R}^m},
+  \tilde{\nu}(s(A)) = \nu(A)= \hat{\nu}(g^{-1}(A)) \qquad \forall A \in \mathscr{F}^{\mathbb{R}^m}\,.
   \end{equation}
-  where $\tilde{\nu}(\cdot)$ is a probability measure on the $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_\mathfrak{s}$.
 \end{definition}
@@
 We now discuss how this definition can be used in practice to obtain reconciled probabilistic forecasts for hierarchical time series.
+Recall that the case of forecast reconciliation could be broken down into three steps.
+In the first via a change of basis $\hat{\bm{y}_{t+h|t}}$ is transformed into coordinates $\tilde{\bm{b}_{t+h|t}}$ and $\tilde{\bm{a}_{t+h|t}}$.
+In the second, $\tilde{\bm{a}_{t+h|t}}$ is discarded and $\tilde{\bm{b}_{t+h|t}}$ are kept as the bottom level reconciled forecasts.
+In the third reconciled forecasts for the entire hierarchy are recovered via $\tilde{\bm{y}_{t+h|t}}=\bm{S}\tilde{\bm{b}_{t+h|t}}$.
+We now outline these three steps for probabilistic forecasts and demonstrate how they correspond to Definition~\ref{def:reconprob}.
 

### 2018-04-04 ProbabilisticCoherence.tex
More discussion around probabilistic forecast reconciliation (which still needs work).  Also notation changes

@@
   \begin{equation}
-  \nu(A) = \hat{\nu}(g^{-1}(A)), \quad \forall \quad A \in \mathscr{F}^{\mathbb{R}^m}\,.
+  \nu(B) = \hat{\nu}(g^{-1}(B)), \quad \forall \quad B \in \mathscr{F}^{\mathbb{R}^m}\,.
   \end{equation}
-  Here $g^{-1}(A):=\left\{\bm{y}\in \mathbb{R}^n:g(\bm{y})\in A \right\}$ is the pre-image of $A$, that is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $A$.
+  Here $g^{-1}(B):=\left\{\bm{y}\in \mathbb{R}^n:g(\bm{y})\in B \right\}$ is the pre-image of $B$, that is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $B$.
   \begin{definition} \label{def:reconprob}
@@
   \begin{equation}
-  \tilde{\nu}(s(A)) = \nu(A)= \hat{\nu}(g^{-1}(A)) \qquad \forall A \in \mathscr{F}^{\mathbb{R}^m}\,.
+  \tilde{\nu}(s(B)) = \nu(B)= \hat{\nu}(g^{-1}(B)) \qquad \forall B \in \mathscr{F}^{\mathbb{R}^m}\,.
   \end{equation}
@@
 Recall that the case of forecast reconciliation could be broken down into three steps.
-In the first via a change of basis $\hat{\bm{y}_{t+h|t}}$ is transformed into coordinates $\tilde{\bm{b}_{t+h|t}}$ and $\tilde{\bm{a}_{t+h|t}}$.
-In the second, $\tilde{\bm{a}_{t+h|t}}$ is discarded and $\tilde{\bm{b}_{t+h|t}}$ are kept as the bottom level reconciled forecasts.
-In the third reconciled forecasts for the entire hierarchy are recovered via $\tilde{\bm{y}_{t+h|t}}=\bm{S}\tilde{\bm{b}_{t+h|t}}$.
+In the first via a change of basis $\hat{\bm{y}}_{t+h|t}$ is transformed into coordinates $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$.
+In the second, $\tilde{\bm{a}}_{t+h|t}$ is discarded and $\tilde{\bm{b}}_{t+h|t}$ are kept as the bottom level reconciled forecasts.
+In the third, reconciled forecasts for the entire hierarchy are recovered via $\tilde{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}$.
 We now outline these three steps for probabilistic forecasts and demonstrate how they correspond to Definition~\ref{def:reconprob}.
 
-Recall that $\hat{\bm{y}}_{t+h}$ is a set of incoherent point forecasts and the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$ are given by \eqref{4.3}.
+To clarify, we note that while $\hat{\nu}$ is a probability measure for an $n$-vector $\hat{\bm{y}}$,  probability statements in terms of a different coordinate system can be made via an appropriate change of basis.
+Letting $f(.)$ be generic notation for a probability density functions and following the notation from our definition of point forecast reconciliation where $\hat{\bm{y}}=\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}$ we obtain
+
+\begin{equation}
+f(\hat{\bm{y}})=f(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}})|\left(\bm{S}~\bm{R}\right)|
+\end{equation}
+
+The expression $\hat{\nu}(g^{-1}(B))$ is in Definition~\ref{def:reconprob} is equivalent to the probability statement $\mbox{Pr}(\hat{\bm{y}}\in g^{-1}(B))$.
+After the change of basis this is equivalent to $\mbox{Pr}(\tilde{\bm{b}}\in (B))$ which implies
+
+\begin{align}
+\mbox{Pr}(\hat{\bm{y}}\in g^{-1}(B))&=\int_{g^{-1}(B)}f(\hat{\bm{y}})d\hat{\bm{y}}\\
+&=\int_{B}\int f(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}})|\left(\bm{S}~\bm{R}\right)|d\tilde{\bm{a}}d\tilde{\bm{b}}
+\end{align}
+
+After integration out over $\tilde{\bm{a}}$, a step analogous to setting $\bm{a}=0$ for point forecasting we obtain a expressions that gives the probability the bottom level (reconciled) series lie in the region $B$, which corresponds to $\nu(B)$ in Definition~\ref{def:reconprob}.
+To make a valid probability statement about the entire hierarchy we simply use the bottom level probabilistic forecasts together with Definition~\ref{def:cohprob}.
+
+%Recall that $\hat{\bm{y}}_{t+h}$ is a set of incoherent point forecasts and the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$ are given by \eqref{4.3}.
 Suppose $\hat{\bm{f}}(\cdot)$ is the probability density of $\hat{\bm{y}}_{t+h}$.
@@
 
-Let the density of $\hat{\bm{y}}_{t+h}$ with respect to basis $\bm{B}$ be denoted by $\bm{f_B}(\cdot)$.
+%Let the density of $\hat{\bm{y}}_{t+h}$ with respect to basis $\bm{B}$ be denoted by $\bm{f_B}(\cdot)$.
 Then it follows from  \eqref{4.3}, and standard results for densities of transformed variables, that
-\begin{equation}\label{4.5}
-\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \,\Big|\bm{S} ~ \vdots~ \bm{R}\Big|,
-\end{equation}
-where $|\cdot|$ denotes the determinant of a matrix.
+%\begin{equation}\label{4.5}
+%\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \,\Big|\bm{S} ~ \vdots~ \bm{R}\Big|,
+%\end{equation}
+%where $|\cdot|$ denotes the determinant of a matrix.
 Now that we have the density of $(\tilde{\bm{b}}'_{t+h} , \tilde{\bm{t}}'_{t+h})'$, the marginal density of $\tilde{\bm{b}}_{t+h}$ can be obtained by integrating \eqref{4.5} over the range of $\tilde{\bm{t}}_{t+h}$.
 This will result in the reconciled density of the bottom-level series $\tilde{\bm{b}}_{t+h}$,
-\begin{equation}\label{4.6}
-\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\int_{\lim(\tilde{\bm{t}}_{t+h})}\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h})\,  \Big|\bm{S} ~ \vdots~ \bm{R}\Big| \, d\tilde{\bm{t}}_{t+h}.
-\end{equation}
-
-Finally to get the reconciled density of the whole hierarchy, we simply follow Definition~\ref{def:cohprob} to obtain
-\begin{equation}\label{4.7}
-\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\bm{S}\circ \tilde{\bm{f}}(\tilde{\bm{b}}_{t+h}).
-\end{equation}
-This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the space $\mathbb{C}^m<\mathbb{R}^n$.
+%\begin{equation}\label{4.6}
+%\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\int_{\lim(\tilde{\bm{t}}_{t+h})}\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h})\,  \Big|\bm{S} ~ \vdots~ \bm{R}\Big| \, d\tilde{\bm{t}}_{t+h}.
+%\end{equation}
+%
+%Finally to get the reconciled density of the whole hierarchy, we simply follow Definition~\ref{def:cohprob} to obtain
+%\begin{equation}\label{4.7}
+%\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\bm{S}\circ \tilde{\bm{f}}(\tilde{\bm{b}}_{t+h}).
+%\end{equation}
+%This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the space $\mathbb{C}^m<\mathbb{R}^n$.
 The following example illustrates how this method can be used to reconcile an incoherent Gaussian forecast distribution.
 
-\subsubsection*{Example 2}
+\subsubsection*{Example: Gaussian Distributions}
 

### 2018-04-04 ProbabilisticCoherence.tex
Notation A changed to B in defintion of probablistic forecast coherence

@@
 Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}^{\mathfrak{s}}$.
-Here $\mathscr{F}^{\mathfrak{s}}$ is formed as collection of sets $s(A)$, where $s(A)$ denotes the image of the set $A\in \mathscr{F}^{\mathbb{R}^m}$ under the mapping $s(.)$.
+Here $\mathscr{F}^{\mathfrak{s}}$ is formed as collection of sets $s(B)$, where $s(B)$ denotes the image of the set $B\in \mathscr{F}^{\mathbb{R}^m}$ under the mapping $s(.)$.
 Let the measure $\breve{\nu}$ have the property
   $$
-      \breve{\nu}(s(A)) = \nu(A) \quad \forall  A \in \mathscr{F}^{\mathbb{R}^m},
+      \breve{\nu}(s(B)) = \nu(B) \quad \forall  B \in \mathscr{F}^{\mathbb{R}^m},
     $$  

### 2018-04-17 ProbabilisticCoherence.tex
Changes to Gaussian example, drop subscripts, notational changes, work on qf separately

@@
 
-\def\PQ{\begin{pmatrix}\bm{P}\\[-0.2cm]\bm{Q}\end{pmatrix}}
-\def\bt{\begin{pmatrix}\tilde{\bm{b}}_{t+h}\\[-0.2cm]\tilde{\bm{t}}_{t+h}\end{pmatrix}}
+\def\PQ{\begin{pmatrix}\bm{G}\\[-0.2cm]\bm{H}\end{pmatrix}}
+\def\bt{\begin{pmatrix}\tilde{\bm{b}}\\[-0.2cm]\tilde{\bm{a}}\end{pmatrix}}
 
@@
 
-Suppose $\mathcal{N}(\hat{\bm{\mu}}_{t+h}, \hat{\bm{\Sigma}}_{t+h}) \overset{d}{\leftrightarrow} \hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ is an incoherent forecast distribution at time $t+h$.
-Then from \eqref{4.5} it follows that
+Suppose an unreconciled probabilistic forecast is Gaussian with mean $\hat{\bm \mu}$ and variance-covariance matrix $\hat{\bm \Sigma}$.
+The subscripts $t+h|t$ are surpresed for brevity.
+The unreconciled density
+
 \begin{equation}
-\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \, \Big|\bm{S} ~ \vdots~ \bm{R}\Big| = \frac{\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) }{\Big|(\bm{S} ~ \vdots~ \bm{R})^{-1}\Big|}.
+  f(\hat{\bm{y}})=(2\pi)^{-n/2}|\hat{\bm{\Sigma}}|^{-1/2}\exp\left\{-\frac{1}{2}\left[(\hat{\bm y}-\hat{\bm \mu})'\hat{\bm{\Sigma}}^{-1}(\hat{\bm y}-\hat{\bm \mu})\right]\right\}
 \end{equation}
-By substituting the Gaussian distribution function for $\bm{f_B}(\cdot)$ we get
+
+After a change in basis
+
+\begin{equation}
+f(\tilde{\bm b},\tilde{\bm a})=(2\pi)^{-\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{-\frac{1}{2}}\Big|(\bm{S} ~ \vdots~ \bm{R})\Big|\exp\left\{-\frac{1}{2}q\right\}\,,
+\end{equation}
+where
+\begin{equation}
+q=(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\bm{\hat{\mu}})' \bm{\hat{\Sigma}}^{-1}(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\bm{\hat{\mu}})
+\end{equation}
+
+The quadratic form $q$ can be rearranged as
 \begin{align*}
-\bm{f_B}(\cdot)
+q& = 
+\Big((\bm{S} ~ \vdots~ \bm{R})\bt-\bm{\hat{\mu}}\Big)' \bm{\hat{\Sigma}}^{-1}\Big((\bm{S} ~ \vdots~ \bm{R})\bt-\bm{\hat{\mu}}\Big),\\
 & =
-\frac{\exp\left\{-\frac{1}{2}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})' \bm{\hat{\Sigma}_{t+h}}^{-1}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}-\bm{\hat{\mu}}_{t+h})\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\bm{S} ~ \vdots~ \bm{R})^{-1}\Big|},\\
-& =
-\frac{\exp\left\{-\frac{1}{2}\Big((\bm{S} ~ \vdots~ \bm{R})\bt-\bm{\hat{\mu}}_{t+h}\Big)' \bm{\hat{\Sigma}_{t+h}}^{-1}\Big((\bm{S} ~ \vdots~ \bm{R})\bt-\bm{\hat{\mu}}_{t+h}\Big)\right\}}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\bm{S} ~ \vdots~ \bm{R})^{-1}\Big|},\\
-& =
-\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|(\bm{S} ~ \vdots~ \bm{R})^{-1} \Big|}
-\exp \Big\{-\frac{1}{2}\Big(\bt-(\bm{S} ~ \vdots~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\Big)'\\
-& \hspace*{6cm} \Big[(\bm{S} ~ \vdots~ \bm{R})\bm{\hat{\Sigma}_{t+h}}(\bm{S} ~ \vdots~ \bm{R})'\Big]^{-1}
-\Big(\bt-(\bm{S} ~ \vdots~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\Big) \Big\}.
+\Big(\bt-(\bm{S} ~ \vdots~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\Big)' \Big[(\bm{S} ~ \vdots~ \bm{R})\bm{\hat{\Sigma}_{t+h}}(\bm{S} ~ \vdots~ \bm{R})'\Big]^{-1}
+\Big(\bt-(\bm{S} ~ \vdots~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\Big)\,.
 \end{align*}
+
 Recall that
@@
 \begin{pmatrix}
-\bm{P} \\\bm{Q}
+\bm{G} \\\bm{H}
 \end{pmatrix},
 $$
-where $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ and $\bm{Q}=(\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot$. Then
+where $\bm{G}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ and $\bm{H}=(\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot$. Then $q$ can be simplified further as
 \begin{align*}
-\bm{f_B}(\cdot)& =\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|\PQ \Big|}
-\exp \Big\{-\frac{1}{2}\Big[\bt-\PQ\bm{\hat{\mu}}_{t+h}\Big]'\\[-0.5cm]
-& \hspace*{7cm}
-\Big[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big]^{-1}\Big[\bt-\PQ\bm{\hat{\mu}}_{t+h}\Big] \Big\},\\[0.5cm]
- & =\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big|^{\frac{1}{2}}}
-\exp \Big\{-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h} \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix}' &\\[-0.5cm]
-& \hspace*{7cm}
- \Big[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big]^{-1}\begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix} \Big\}.
+q& =%\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|\PQ \Big|}
+%\exp \Big\{-\frac{1}{2}
+\Big[\bt-\PQ\bm{\hat{\mu}}_{t+h}\Big]'%\\[-0.5cm]
+\Big[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big]^{-1}\Big[\bt-\PQ\bm{\hat{\mu}}_{t+h}\Big] %\Big\},
+\\[0.5cm]
+ & =%\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big|^{\frac{1}{2}}}
+%\exp \Big\{-\frac{1}{2} 
+\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}\\ \tilde{\bm{a}}- \bm{H}\bm{\hat{\mu}}\end{pmatrix}' %&\\[-0.5cm]
+%& \hspace*{7cm}
+ \Big[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big]^{-1}\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}\\ \tilde{\bm{a}}- \bm{H}\bm{\hat{\mu}}\end{pmatrix} %\Big\}.
 \end{align*}

### 2018-04-17 ProbabilisticCoherence.tex
Gaussian Example Complete, although some cleaning up of brackets/braces/parenthesis still needed

@@
 \end{align*}
-Since $\Big[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big] = \begin{pmatrix}
-\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}' \\
-\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'
-\end{pmatrix}$ we have
+%Since $\Big[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big] = \begin{pmatrix}
+%\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}' 
+%\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'
+%\end{pmatrix}$ we have
+
+Similar manipulations on determinant of the covariance matrix lead to the following expression for the density
+
 \begin{align*}
-\bm{f_B}(\cdot)&=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\begin{pmatrix}
-  \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}' \\
-  \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'
-  \end{pmatrix}\Big|^{\frac{1}{2}}}
-\exp \Big\{-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix}'\\
-&\hspace*{7cm}\begin{pmatrix}
-\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}' \\
-\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'
+f(\tilde{\bm{b}},\tilde{\bm{a}})&
+=(2\pi)^{-\frac{n}{2}}\Big|
+\begin{pmatrix}
+  \bm{G}\bm{\hat{\Sigma}}\bm{G}' & \bm{G}\bm{\hat{\Sigma}}\bm{H}' \\
+  \bm{H}\bm{\hat{\Sigma}}\bm{G}' & \bm{H}\bm{\hat{\Sigma}}\bm{H}'
+\end{pmatrix}
+\Big|^{-\frac{1}{2}}
+\exp \Big\{-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}\\ \tilde{\bm{a}}- \bm{H}\bm{\hat{\mu}}\end{pmatrix}'\\
+&\hspace*{7cm}
+\begin{pmatrix}
+\bm{G}\bm{\hat{\Sigma}}\bm{G}' & \bm{G}\bm{\hat{\Sigma}}\bm{H}' \\
+\bm{H}\bm{\hat{\Sigma}}\bm{G}' & \bm{H}\bm{\hat{\Sigma}}\bm{H}'
 \end{pmatrix}^{-1}
-\begin{pmatrix}\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}\\ \tilde{\bm{t}}_{t+h}- \bm{Q}\bm{\hat{\mu}}_{t+h}\end{pmatrix} \Big\}.
+\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}\\ \tilde{\bm{a}}- \bm{H}\bm{\hat{\mu}}\end{pmatrix} \Big\}.
 \end{align*}
-This is the joint multivariate Gaussian distribution of $(\tilde{\bm{b}}'_{t+h} ~ \vdots~ \tilde{\bm{t}}'_{t+h})'$.
-Then from \eqref{4.6} and the properties of the multivariate Gaussian distribution, it follows that
+Marginalising out $\tilde{\bm{a}}$, it follows leads to the following bottom level reconciled forecasts. 
 \begin{equation}\label{ex:2.1}
-\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}'\Big|^{\frac{1}{2}}}
-\exp \Big\{-\frac{1}{2} (\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h})' (\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}')^{-1}(\tilde{\bm{b}}_{t+h} - \bm{P}\bm{\hat{\mu}}_{t+h}) \Big\}.
+f(\tilde{\bm{b}})=(2\pi)^{-\frac{m}{2}}\Big|\bm{G}\bm{\hat{\Sigma}}\bm{G}'\Big|^{\frac{1}{2}}
+\exp \Big\{-\frac{1}{2} (\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}})' (\bm{G}\bm{\hat{\Sigma}}\bm{G}')^{-1}(\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}) \Big\}.
 \end{equation}
 
-Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
+%Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
 Then from \eqref{4.7} it follows that
-\begin{equation}\label{eq:gaussianreconciled}
-\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
-\end{equation}
-Therefore, the reconciled Gaussian forecast distribution of the whole hierarchy is\\
-$\mathcal{N}(\bm{SP}\bm{\hat{\mu}}_{t+h},~ \bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}')$.
+%\begin{equation}\label{eq:gaussianreconciled}
+%\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
+%\end{equation}
+Which implies that the reconciled probabilistic forecast for the bottom level series is $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$.
+The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean  $\bm{SG}\bm{\hat{\mu}}$ and rank deficient covariance matrix $\bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}'$.
 

### 2018-04-18 ProbabilisticCoherence.tex
Ellitpical theorem statement - proof to follow

@@
 \usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx}
-\usepackage{mathrsfs, float, booktabs,todonotes}
+\usepackage{mathrsfs, float, booktabs,todonotes,amsthm}
 \usepackage[bb=boondox]{mathalfa}
@@
 
+\theoremstyle{theo}
+\newtheorem{theo}{Theorem}[section]
+
+\theoremstyle{definition}
 \newtheorem{definition}{Definition}[section]
@@
 The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean  $\bm{SG}\bm{\hat{\mu}}$ and rank deficient covariance matrix $\bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}'$.
+\subsection{Elliptical Distributions}
+We now show that if the mapping $g(.)$ in definition $\ref{def:reconpoint}$ is extended to allow for a translation by ${\bm d}$, i.e.
+$g({\bm y})={\bm G}{\bm y}+{\bm d}$, then the true predictive distribution can be recovered for elliptical distributions.
+\begin{theo}[Reconciliation for Elliptical Distributions]
+	Let an unreconciled probabilistic forecast come from the elliptical class with location parameter $\hat{\bm \mu}$ and scale matrix $\hat{\bm \Sigma}$.
+Let the true predictive distribution of ${\bm y}_{t+h|t}$ also belong to the elliptical class with location parameter ${\bm \mu}$ and scale matrix ${\bm \Sigma}$.
+Then the affine reconciliation mapping $g({\bm y})={\bm G}{\bm y}+{\bm d}$ with $\bm{G}={\bm\Omega}^{1/2}{\bm\Sigma}^{-1/2}$ where $\bm\Omega$ is the bottom level true variance covariance matrix and ${\bm d}={\bm SG}\left({\bm \mu}-\hat{\bm \mu}\right)$ recovers the true predictive density.
+\end{theo}
+\begin{proof}
+  It follows from the closure of elliptical densities under affine transformations and marginalisation.  NEED TO WRITE UP!
+\end{proof}
 

### 2018-04-18 ProbabilisticCoherence.tex
Added proof for elliptical case.  Need to add discussion

@@
 Let the true predictive distribution of ${\bm y}_{t+h|t}$ also belong to the elliptical class with location parameter ${\bm \mu}$ and scale matrix ${\bm \Sigma}$.
-Then the affine reconciliation mapping $g({\bm y})={\bm G}{\bm y}+{\bm d}$ with $\bm{G}={\bm\Omega}^{1/2}{\bm\Sigma}^{-1/2}$ where $\bm\Omega$ is the bottom level true variance covariance matrix and ${\bm d}={\bm SG}\left({\bm \mu}-\hat{\bm \mu}\right)$ recovers the true predictive density.
+Then the affine reconciliation mapping $g({\bm y})={\bm G}{\bm y}+{\bm d}$ with $\bm{G}={\bm\Omega}^{1/2}{\bm\Sigma}^{-1/2}$ where $\bm\Omega$ is the bottom level true variance covariance matrix and ${\bm d}={\bm S}{\bm G}\left({\bm \mu}-\hat{\bm \mu}\right)$ recovers the true predictive density.
 \end{theo}
 \begin{proof}
-  It follows from the closure of elliptical densities under affine transformations and marginalisation.  NEED TO WRITE UP!
+   Since elliptical distributions are closed under affine transformations, and are closed under marginalisation, reconciliation of an elliptical distribution yields an elliptical distribution (although the unreconciled and unreconciled distributions may be different members of the class of elliptical distributions).
+The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}{\bm \Sigma}{\bm G}'{\bm S}'$ while the location matrix is given by $\bm{S}\bm{G}\hat{\bm \mu}+{\bm d}$.
+For the choice of ${\bf G}$ given above, the reconciled scale matrix is
+   \begin{align*}
+   \tilde{\bm \Sigma}=&{\bm S}{\bm\Omega}^{1/2}{\bm\Sigma}^{-1/2}{\bm \Sigma}{\bm\Sigma}^{-1/2}{\bm\Omega}^{1/2}{\bm S}'\\
+   =&{\bm S}{\bm \Omega}{\bm S}'\\
+   =&{\bm \Sigma}
+   \end{align*}
+   For the choices of ${\bf G}$ and ${\bf d}$ given above, the reconciled location matrix is 
+   \begin{align*}
+   \tilde{\bm \mu}=&{\bm S}{\bm G}\hat{\bm \mu}+{\bm S}{\bm G}\left({\bm \mu}-\hat{\bm \mu}\right)\\
+   =&{\bm S}{\bm G}\hat{\bm \mu}-{\bm S}{\bm G}\hat{\bm \mu}+{\bm S}{\bm G}{\bm \mu}\\
+   =&{\bm S}{\bm G}{\bm \mu}\\
+   =&{\bm \mu}\\
+   \end{align*}
+   The final equality above holds since ${\bm S}{\bm G}$ projects any vector onto the coherent subspace, however since ${\bm \mu}$ is the mean of the true data generating process, it must already lie on the coherent subspace.
 \end{proof}	
-
+It should be noted that these choices of ${\bm G}$ and ${\bm d}$ depend on the true location and scale of the predictive distribution and are thus infeasible in practice.
+However, these expressions do provide some insight on why some choices for ${\bm G}$ in the point forecast reconciliation literature may also work well for probablistic forecasts.
+For example, for the MinT solution ...
 \section{Evaluation of hierarchical probabilistic forecasts}\label{sec:evaluation}

### 2018-04-19 ProbabilisticCoherence.tex
Some comments on MinT v infeasible optimal
Finished up until section 4 excluding pictures

--- 2018-04-17 ProbabilisticCoherence.tex
@@
 In our context, we need to find $\bm{R}_\bot$ such that $\bm{R}'_\bot \bm{S}$ is invertible; i.e, $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \bm{S}=\bm{I}$.
-This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}{\color{red}[AP:NONE OF THIS MAKES SENSE TO ME.
-$R_{\perp}'S$ WILL BE INVERTIBLE AS LONG AS NONE OF THE COLUMNS OF R SIT ON THE COLUMN SPACE OF S.
-AS LONG AS R IS STICKING INTO THE NULL SPACE OF S, THEN SPS=S ALWAYS SINCE SP IS JUST A PROJECTION THAT PUTS VECTORS ON THE COLUMN SPACE OF S.
-SINCE THE COLUMNS OF S ARE ALREADY ON THE COLUMN SPACE OF S, THEN MULTIPLYING SP SIMPLY DOES NOTHING TO THEM.
-THE CONNECTION TO UNBIASEDNESS IS STILL NOT CLEAR TO ME.]}.
+This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}
 
@@
 The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean  $\bm{SG}\bm{\hat{\mu}}$ and rank deficient covariance matrix $\bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}'$.
+\subsection{Elliptical Distributions}
+We now show that if the mapping $g(.)$ in definition $\ref{def:reconpoint}$ is extended to allow for a translation by ${\bm d}$, i.e.
+$g({\bm y})={\bm G}{\bm y}+{\bm d}$, then the true predictive distribution can be recovered for elliptical distributions.
+Here, for any square matrix ${\bm C}$, ${\bm C}^{1/2}$ and ${\bm C}^{-1/2}$ are defined to satisfy ${\bm C}^{1/2}\left({\bm C}^{1/2}\right)'={\bm C}$ and ${\bm C}^{-1/2}\left({\bm C}^{-1/2}\right)'={\bm C}^{-1}$, for example ${\bm C}^{1/2}$ may be obtained via the Cholesky or eigenvalue decompositions.
+\begin{theo}[Reconciliation for Elliptical Distributions]
+	Let an unreconciled probabilistic forecast come from the elliptical class with location parameter $\hat{\bm \mu}$ and scale matrix $\hat{\bm \Sigma}$.
+Let the true predictive distribution of ${\bm y}_{t+h|t}$ also belong to the elliptical class with location parameter ${\bm \mu}$ and scale matrix ${\bm \Sigma}$.
+Then the affine reconciliation mapping $g({\bm y})={\bm G}{\bm y}+{\bm d}$ with $\bm{G}={\bm\Omega}^{1/2}{\bm\Sigma}^{-1/2}$ and ${\bm d}={\bm S}{\bm G}\left({\bm \mu}-\hat{\bm \mu}\right)$ recovers the true predictive density, where $\bm\Omega$ is the true variance covariance matrix of the predictive distribution for the bottom level.
+\end{theo}
+\begin{proof}
+   Since elliptical distributions are closed under affine transformations, and are closed under marginalisation, reconciliation of an elliptical distribution yields an elliptical distribution (although the unreconciled and unreconciled distributions may be different members of the class of elliptical distributions).
+The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}{\bm \Sigma}{\bm G}'{\bm S}'$ while the location matrix is given by $\bm{S}\bm{G}\hat{\bm \mu}+{\bm d}$.
+For the choice of ${\bf G}$ given above, the reconciled scale matrix is
+   \begin{align*}
+   \tilde{\bm \Sigma}_{opt}=&{\bm S}{\bm\Omega}^{1/2}{\bm\Sigma}^{-1/2}{\bm \Sigma}{\bm\Sigma}^{-1/2}{\bm\Omega}^{1/2}{\bm S}'\\
+   =&{\bm S}{\bm \Omega}{\bm S}'\\
+   =&{\bm \Sigma}
+   \end{align*}
+   For the choices of ${\bf G}_{opt}$ and ${\bf d}_{opt}$ given above, the reconciled location matrix is 
+   \begin{align*}
+   \tilde{\bm \mu}_{opt}=&{\bm S}{\bm G}_{opt}\hat{\bm \mu}+{\bm S}{\bm G}_{opt}\left({\bm \mu}-\hat{\bm \mu}\right)\\
+   =&{\bm S}{\bm G}_{opt}\hat{\bm \mu}-{\bm S}{\bm G}_{opt}\hat{\bm \mu}+{\bm S}{\bm G}_{opt}{\bm \mu}\\
+   =&{\bm S}{\bm G}_{opt}{\bm \mu}\\
+   =&{\bm \mu}\\
+   \end{align*}
+   The final equality above holds since ${\bm S}{\bm G}$ projects any vector onto the coherent subspace, however since ${\bm \mu}$ is the mean of the true data generating process, it must already lie on the coherent subspace.
+\end{proof}	
+It should be noted that these choices of ${\bm G}$ and ${\bm d}$ depend on the true location and scale of the predictive distribution and are thus infeasible in practice.
+However, these expressions do provide some insight on why some choices for ${\bm G}$ in the point forecast reconciliation literature may also work well for probablistic forecasts.
+To illustrate, first rearrange the equation for the optimal value of  $\bm{G}_{opt}={\bm\Omega}^{1/2}\hat{\bm\Sigma}^{-1/2}$ as ${\bm\Omega}^{1/2}=\bm{G}_{opt}\hat{\bm\Sigma}^{1/2}$.
+Using an arbitrary ${\bm G}$ provides an approximation for ${\bm\Omega}^{1/2}$.
+This approximation is equivalent to the way bottom level estimates are produced in point forecast reconciliation, however it is carried out columnwise on  $\hat{\bm\Sigma}^{1/2}$.
+Meanwhile the value for $\tilde{\bm \mu}_{opt}$ includes a projection of $\hat{\bm \mu}$ onto $\mathfrak{s}$, and while it is infeasible to obtain the translation ${\bm d}$, it is worthwhile noting that this measures the distance between the reconciled mean and true mean.
 

### 2018-04-20 ProbabilisticCoherence.tex
Clean up sections 2 to section 4

@@
 In the section, and throughout the paper, we will try to follow notational conventions used in \citet{Wickramasuriya2017} as much as possible.
-A hierarchical time series is a collection of $n$ variables where some variables are aggregates of other variables.
+A {\em hierarchical time series} is a collection of $n$ variables where some variables are aggregates of other variables.
 For example in the hierarchy depicted in Figure~\ref{fig1} below, the variable labelled $Tot$ is the sum of the series $A$
 and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.
-The bottom level series are defined as those $m$ variables that cannot be formed as aggregates of other variables, in the example in Figure~\ref{fig1} these are the series $AA$, $AB$, $BA$ and $BB$.
+The {\em bottom level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables, in the example in Figure~\ref{fig1} these are the series $AA$, $AB$, $BA$ and $BB$.
 
@@
 We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprised of observations of all variables in the hierarchy at time $t$,  and $\bm{b}_t \in \mathbb{R}^m$ is a vector comprised of observations of all bottom-level series at time $t$.
-The hierarchical structure of the data imply the following
+The hierarchical structure of the data imply the following holds for all $t$
 \begin{equation}
@@
 where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints.
-For example for the hierarchy in Figure~\ref{fig1}, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and
+For the hierarchy in Figure~\ref{fig1}, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and
 $$ 
@@
 It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect aggregation constraints.
-We follow other authors in using the nomenclature{\em coherence} to describe this property.
+We follow other authors in using the nomenclature {\em coherence} to describe this property.
 %While coherent point forecasts have been discussed many times previously, the definitions of coherence previously given are vague and are not easily extended to the situation of probabilistic forecasting.
@@
 Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}^{\mathfrak{s}}$.
-Here $\mathscr{F}^{\mathfrak{s}}$ is formed as collection of sets $s(B)$, where $s(B)$ denotes the image of the set $B\in \mathscr{F}^{\mathbb{R}^m}$ under the mapping $s(.)$.
+Here $\mathscr{F}^{\mathfrak{s}}$ is formed as collection of sets $s(\mathcal{B})$, where $s(\mathcal{B})$ denotes the image of the set $\mathcal{B}\in \mathscr{F}^{\mathbb{R}^m}$ under the mapping $s(.)$.
 Let the measure $\breve{\nu}$ have the property
   $$
-      \breve{\nu}(s(B)) = \nu(B) \quad \forall  B \in \mathscr{F}^{\mathbb{R}^m},
-    $$  
-  A probabilistic forecast is coherent if uncertainty in $\bm{y_{t+h}}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}^{\mathfrak{s}},\breve{\nu})$.
+      \breve{\nu}(s(\mathcal{B})) = \nu(\mathcal{B}) \quad \forall  \mathcal{B} \in \mathscr{F}^{\mathbb{R}^m},
+    $$  
+  A probabilistic forecast is coherent if uncertainty in $\bm{y_{t+h|h}}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}^{\mathfrak{s}},\breve{\nu})$.
 \end{definition}
@@
 For example, consider the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$.
-In this case the matrix $\bm{S}$ has columns  $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$ and the mapping $\bm{S}$ transforms $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy.
-However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy.
-In general, since there are an infinite number linear bases for $\mathfrak{s}$ the definitions above could be made in terms of any series and not just the bottom level series.
-In general we will call the series (or linear combinations thereof) used in the definitions of coherence as \textit{basis series}.
-Unless stated otherwise, we will always consider the basis series to be the bottom level series as in Definition~\ref{def:cohpoint} and Defintion~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.
+In this case the matrix $\bm{S}$ has columns  $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$ and premultiplying by $\bm{S}$ transforms arbitrary values of $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy.
+However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy.
+The definitions above could be made in terms of any series and not just the bottom level series.
+In general, we call the series (or linear combinations thereof) used in the definitions of coherence as \textit{basis series}.
+Unless stated otherwise, we will always assume that the basis series are the bottom level series as in Definition~\ref{def:cohpoint} and Defintion~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.
 
@@
 
-  Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent forecasts at time $t+h$ using information up to and including time $t$.
+  Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ using information up to and including time $t$.
 Let $\bm{G}$ be an $m\times n$ matrix and $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping corresponding to pre-multiplication by $\bm{G}$.
@@
 
-Definition~\ref{def:reconpoint}, actually defines an entire family of forecast reconciliation methods including many methods currently extant in the literature.
+Definition~\ref{def:reconpoint}, defines an entire family of forecast reconciliation methods including many methods currently extant in the literature.
 To provide a geometric interpretation, we introduce an $n \times (n-m)$ matrix $\bm{R}$ whose columns span the null space $\mathfrak{s}_{\perp}$.
-For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$ is the vector $(1,-1,-1)$, which is orthogonal to the columns of $\bm{S}$ in the usual sense of Euclidean geometry.
+For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
 In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
@@
 As such any incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$, can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$.
-Let $\tilde{\bm{b}}'_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$, respectively.
+Let $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$, respectively.
 The process of reconciliation involves setting $\tilde{\bm{b}}_{t+h|t}$ to be the values of the reconciled bottom-level series and setting $\tilde{\bm{a}}_{t+h}=\bm{0}$ to ensure coherence.
@@
 
-Finding a suitable $\bm{R}_\bot$ with respect to a certain loss function will lead to optimally reconciled point forecasts of the hierarchy.
+Finding a suitable $\bm{R}$ with respect to a certain loss function will lead to optimally reconciled point forecasts of the hierarchy.
 %If $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$, then the definition for linear reconciliation of point forecasts in previous studies coincides with our explanation.
-In our context, we need to find $\bm{R}_\bot$ such that $\bm{R}'_\bot \bm{S}$ is invertible; i.e, $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \bm{S}=\bm{I}$.
+In our context, we need to find $\bm{R}$ such that $\bm{R}'_\bot \bm{S}$ is invertible; i.e, $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \bm{S}=\bm{I}$.
 This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}
@@
   \begin{equation}
-  \nu(B) = \hat{\nu}(g^{-1}(B)), \quad \forall \quad B \in \mathscr{F}^{\mathbb{R}^m}\,.
-  \end{equation}
-  Here $g^{-1}(B):=\left\{\bm{y}\in \mathbb{R}^n:g(\bm{y})\in B \right\}$ is the pre-image of $B$, that is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $B$.
+  \nu(\mathcal{B}) = \hat{\nu}(g^{-1}(\mathcal{B})), \quad \forall \mathcal{B} \in \mathscr{F}^{\mathbb{R}^m}\,.
+  \end{equation}
+  Here $g^{-1}(\mathcal{B}):=\left\{\breve{\bm{y}}\in \mathbb{R}^n:g(\breve{\bm{y}})\in \mathcal{B} \right\}$ is the pre-image of $\mathcal{B}$, that is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $\mathcal{B}$.
   \begin{definition} \label{def:reconprob}
@@
   \begin{equation}
-  \tilde{\nu}(s(B)) = \nu(B)= \hat{\nu}(g^{-1}(B)) \qquad \forall B \in \mathscr{F}^{\mathbb{R}^m}\,.
+  \tilde{\nu}(s(\mathcal{B})) = \nu(\mathcal{B})= \hat{\nu}(g^{-1}(\mathcal{B})) \qquad \forall \mathcal{B} \in \mathscr{F}^{\mathbb{R}^m}\,.
   \end{equation}
@@
 Recall that the case of forecast reconciliation could be broken down into three steps.
-In the first via a change of basis $\hat{\bm{y}}_{t+h|t}$ is transformed into coordinates $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$.
+In the first, $\hat{\bm{y}}_{t+h|t}$ is transformed into coordinates $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ via a change of basis.
 In the second, $\tilde{\bm{a}}_{t+h|t}$ is discarded and $\tilde{\bm{b}}_{t+h|t}$ are kept as the bottom level reconciled forecasts.
@@
 
-To clarify, we note that while $\hat{\nu}$ is a probability measure for an $n$-vector $\hat{\bm{y}}$,  probability statements in terms of a different coordinate system can be made via an appropriate change of basis.
-Letting $f(.)$ be generic notation for a probability density functions and following the notation from our definition of point forecast reconciliation where $\hat{\bm{y}}=\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}$ we obtain
-
-\begin{equation}
-f(\hat{\bm{y}})=f(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}})|\left(\bm{S}~\bm{R}\right)|
-\end{equation}
-
-The expression $\hat{\nu}(g^{-1}(B))$ is in Definition~\ref{def:reconprob} is equivalent to the probability statement $\mbox{Pr}(\hat{\bm{y}}\in g^{-1}(B))$.
-After the change of basis this is equivalent to $\mbox{Pr}(\tilde{\bm{b}}\in (B))$ which implies
+While $\hat{\nu}$ is a probability measure for an $n$-vector $\hat{\bm{y}}_{t+h|t}$,  probability statements in terms of a different coordinate system can be made via an appropriate change of basis.
+Letting $f(.)$ be generic notation for a probability density functions and following the notation from our definition of point forecast reconciliation where $\hat{\bm{y}}=\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t}$ we obtain
+
+\begin{equation}
+f(\hat{\bm{y}}_{t+h|t})=f(\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t})|\left(\bm{S}~\bm{R}\right)|
+\end{equation}
+
+The expression $\hat{\nu}(g^{-1}(\mathcal{B}))$ in Definition~\ref{def:reconprob} is equivalent to the probability statement $\mbox{Pr}(\hat{\bm{y}}_{t+h|t}\in g^{-1}(\mathcal{B}))$.
+After the change of basis this is equivalent to $\mbox{Pr}(\tilde{\bm{b}}\in \mathcal{B})$ which implies
 
 \begin{align}
-\mbox{Pr}(\hat{\bm{y}}\in g^{-1}(B))&=\int_{g^{-1}(B)}f(\hat{\bm{y}})d\hat{\bm{y}}\\
-&=\int_{B}\int f(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}})|\left(\bm{S}~\bm{R}\right)|d\tilde{\bm{a}}d\tilde{\bm{b}}
+\mbox{Pr}(\hat{\bm{y}}_{t+h|t}\in g^{-1}(\mathcal{B}))&=\int\limits_{g^{-1}(\mathcal{B})}f(\hat{\bm{y}}_{t+h|t})d\hat{\bm{y}}_{t+h|t}\\
+&=\int\limits_{\mathcal{B}}\int f(\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t})|\left(\bm{S}~\bm{R}\right)|d\tilde{\bm{a}}_{t+h|t}d\tilde{\bm{b}}_{t+h|t}
 \end{align}
 
-After integration out over $\tilde{\bm{a}}$, a step analogous to setting $\bm{a}=0$ for point forecasting we obtain a expressions that gives the probability the bottom level (reconciled) series lie in the region $B$, which corresponds to $\nu(B)$ in Definition~\ref{def:reconprob}.
+After integrating out over $\tilde{\bm{a}}_{t+h|t}$, a step analogous to setting $\tilde{\bm{a}}_{t+h|t}=0$ for point forecasting, we obtain an expressions that gives the probability the reconciled bottom level series lies in the region $\mathcal{B}$.
+This corresponds to $\nu(\mathcal{B})$ in Definition~\ref{def:reconprob}.
 To make a valid probability statement about the entire hierarchy we simply use the bottom level probabilistic forecasts together with Definition~\ref{def:cohprob}.
@@
 Suppose an unreconciled probabilistic forecast is Gaussian with mean $\hat{\bm \mu}$ and variance-covariance matrix $\hat{\bm \Sigma}$.
-The subscripts $t+h|t$ are surpresed for brevity.
+The subscripts $t+h|t$ are suppressed for brevity.
 The unreconciled density
@@
 \begin{equation}
-f(\tilde{\bm b},\tilde{\bm a})=(2\pi)^{-\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{-\frac{1}{2}}\Big|(\bm{S} ~ \vdots~ \bm{R})\Big|\exp\left\{-\frac{1}{2}q\right\}\,,
+f(\tilde{\bm b},\tilde{\bm a})=(2\pi)^{-\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{-\frac{1}{2}}\Big|(\bm{S} ~  \bm{R})\Big|\exp\left\{-\frac{1}{2}q\right\}\,,
 \end{equation}
@@
 q& = 
-\Big((\bm{S} ~ \vdots~ \bm{R})\bt-\bm{\hat{\mu}}\Big)' \bm{\hat{\Sigma}}^{-1}\Big((\bm{S} ~ \vdots~ \bm{R})\bt-\bm{\hat{\mu}}\Big),\\
+\left((\bm{S} ~  \bm{R})\bt-\bm{\hat{\mu}}\right)' \bm{\hat{\Sigma}}^{-1}\left((\bm{S} ~ \bm{R})\bt-\bm{\hat{\mu}}\right),\\
 & =
-\Big(\bt-(\bm{S} ~ \vdots~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\Big)' \Big[(\bm{S} ~ \vdots~ \bm{R})\bm{\hat{\Sigma}_{t+h}}(\bm{S} ~ \vdots~ \bm{R})'\Big]^{-1}
-\Big(\bt-(\bm{S} ~ \vdots~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\Big)\,.
+\left(\bt-(\bm{S} ~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\right)' \Big[(\bm{S}  \bm{R})\bm{\hat{\Sigma}_{t+h}}(\bm{S} ~ \bm{R})'\Big]^{-1}
+\left(\bt-(\bm{S} ~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\right)\,.
 \end{align*}
@@
 $$
-(\bm{S} ~ \vdots~ \bm{R})^{-1} =
-\begin{pmatrix}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot \end{pmatrix} =
+(\bm{S} ~ \bm{R})^{-1} =
+\begin{pmatrix}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot  \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot \end{pmatrix} :=
 \begin{pmatrix}
 \bm{G} \\\bm{H}
-\end{pmatrix},
-$$
-where $\bm{G}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ and $\bm{H}=(\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot$. Then $q$ can be simplified further as
+\end{pmatrix}\,.
+$$
+Then $q$ can be rearranged further as
 \begin{align*}
@@
 %\exp \Big\{-\frac{1}{2}
-\Big[\bt-\PQ\bm{\hat{\mu}}_{t+h}\Big]'%\\[-0.5cm]
-\Big[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big]^{-1}\Big[\bt-\PQ\bm{\hat{\mu}}_{t+h}\Big] %\Big\},
+\left[\bt-\PQ\bm{\hat{\mu}}_{t+h}\right]'%\\[-0.5cm]
+\left[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\right]^{-1}\left[\bt-\PQ\bm{\hat{\mu}}_{t+h}\right] %\Big\},
 \\[0.5cm]
@@
 %& \hspace*{7cm}
- \Big[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big]^{-1}\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}\\ \tilde{\bm{a}}- \bm{H}\bm{\hat{\mu}}\end{pmatrix} %\Big\}.
+ \left[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\right]^{-1}\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}\\ \tilde{\bm{a}}- \bm{H}\bm{\hat{\mu}}\end{pmatrix} %\Big\}.
 \end{align*}
@@
 f(\tilde{\bm{b}},\tilde{\bm{a}})&
-=(2\pi)^{-\frac{n}{2}}\Big|
+=(2\pi)^{-\frac{n}{2}}\left|
 \begin{pmatrix}
@@
 \end{pmatrix}
-\Big|^{-\frac{1}{2}}
-\exp \Big\{-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}\\ \tilde{\bm{a}}- \bm{H}\bm{\hat{\mu}}\end{pmatrix}'\\
+\right|^{-\frac{1}{2}}
+\exp \left\{-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}\\ \tilde{\bm{a}}- \bm{H}\bm{\hat{\mu}}\end{pmatrix}'\right.\\
 &\hspace*{7cm}
-\begin{pmatrix}
+\left.\begin{pmatrix}
 \bm{G}\bm{\hat{\Sigma}}\bm{G}' & \bm{G}\bm{\hat{\Sigma}}\bm{H}' \\
@@
 \end{pmatrix}^{-1}
-\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}\\ \tilde{\bm{a}}- \bm{H}\bm{\hat{\mu}}\end{pmatrix} \Big\}.
+\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}\\ \tilde{\bm{a}}- \bm{H}\bm{\hat{\mu}}\end{pmatrix} \right\}.
 \end{align*}
-Marginalising out $\tilde{\bm{a}}$, it follows leads to the following bottom level reconciled forecasts. 
+Marginalising out $\tilde{\bm{a}}$, leads to the following bottom level reconciled forecasts. 
 \begin{equation}\label{ex:2.1}
@@
 %\end{equation}
-Which implies that the reconciled probabilistic forecast for the bottom level series is $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$.
-The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean  $\bm{SG}\bm{\hat{\mu}}$ and rank deficient covariance matrix $\bm{SP}\hat{\bm{\Sigma}}_{t+h}\bm{P}'\bm{S}'$.
+Which implies that the reconciled probabilistic forecast for the bottom level series is $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{G}\bm{\hat{\mu}}_{t+h}, \bm{G}\hat{\bm{\Sigma}}_{t+h}\bm{G}')$.
+The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean  $\bm{SG}\bm{\hat{\mu}}$ and rank deficient covariance matrix $\bm{SG}\hat{\bm{\Sigma}}_{t+h}\bm{G}'\bm{S}'$.
 \subsection{Elliptical Distributions}
@@
 Let the true predictive distribution of ${\bm y}_{t+h|t}$ also belong to the elliptical class with location parameter ${\bm \mu}$ and scale matrix ${\bm \Sigma}$.
-Then the affine reconciliation mapping $g({\bm y})={\bm G}{\bm y}+{\bm d}$ with $\bm{G}={\bm\Omega}^{1/2}{\bm\Sigma}^{-1/2}$ and ${\bm d}={\bm S}{\bm G}\left({\bm \mu}-\hat{\bm \mu}\right)$ recovers the true predictive density, where $\bm\Omega$ is the true variance covariance matrix of the predictive distribution for the bottom level.
+Then the affine reconciliation mapping $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ with $\bm{G}_{opt}={\bm\Omega}^{1/2}{\bm\Sigma}^{-1/2}$ and ${\bm d}_{opt}={\bm S}{\bm G}_{opt}\left({\bm \mu}-\hat{\bm \mu}\right)$ recovers the true predictive density, where $\bm\Omega$ is the true variance covariance matrix of the predictive distribution for the bottom level.
 \end{theo}
@@
    Since elliptical distributions are closed under affine transformations, and are closed under marginalisation, reconciliation of an elliptical distribution yields an elliptical distribution (although the unreconciled and unreconciled distributions may be different members of the class of elliptical distributions).
-The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}{\bm \Sigma}{\bm G}'{\bm S}'$ while the location matrix is given by $\bm{S}\bm{G}\hat{\bm \mu}+{\bm d}$.
-For the choice of ${\bf G}$ given above, the reconciled scale matrix is
+The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}_{opt}{\bm \Sigma}{\bm G}_{opt}'{\bm S}'$ while the location matrix is given by $\bm{S}\bm{G}_{opt}\hat{\bm \mu}+{\bm d}_{opt}$.
+The reconciled scale matrix is
    \begin{align*}
@@
    \end{align*}
-   The final equality above holds since ${\bm S}{\bm G}$ projects any vector onto the coherent subspace, however since ${\bm \mu}$ is the mean of the true data generating process, it must already lie on the coherent subspace.
+   The final equality above holds since ${\bm S}{\bm G}_{opt}$ projects any vector onto the coherent subspace, however since ${\bm \mu}$ is the mean of the true data generating process, it must already lie on the coherent subspace and ${\bm S}{\bm G}_{opt}{\bm \mu}={\bm \mu}$.
 \end{proof}	
-It should be noted that these choices of ${\bm G}$ and ${\bm d}$ depend on the true location and scale of the predictive distribution and are thus infeasible in practice.
-However, these expressions do provide some insight on why some choices for ${\bm G}$ in the point forecast reconciliation literature may also work well for probablistic forecasts.
+It should be noted that ${\bm G}_{opt}$ and ${\bm d}_{opt}$ depend on the true location and scale of the predictive distribution and are thus infeasible in practice.
+However, these expressions do provide some insight on why some choices for ${\bm G}$ in the point forecast reconciliation literature may also work well for probabilistic forecasts.
 To illustrate, first rearrange the equation for the optimal value of  $\bm{G}_{opt}={\bm\Omega}^{1/2}\hat{\bm\Sigma}^{-1/2}$ as ${\bm\Omega}^{1/2}=\bm{G}_{opt}\hat{\bm\Sigma}^{1/2}$.
-Using an arbitrary ${\bm G}$ provides an approximation for ${\bm\Omega}^{1/2}$.
-This approximation is equivalent to the way bottom level estimates are produced in point forecast reconciliation, however it is carried out columnwise on  $\hat{\bm\Sigma}^{1/2}$.
-Meanwhile the value for $\tilde{\bm \mu}_{opt}$ includes a projection of $\hat{\bm \mu}$ onto $\mathfrak{s}$, and while it is infeasible to obtain the translation ${\bm d}$, it is worthwhile noting that this measures the distance between the reconciled mean and true mean.
+For arbitrary ${\bm G}\hat{\bm\Sigma}^{1/2}$ is an approximation for ${\bm\Omega}^{1/2}$.
+This approximation has similarities with the way bottom level estimates are produced for point forecast reconciliation.
+Rather than mapping a vector of point forecasts to reconcilied bottom level forecasts, the columns of  $\hat{\bm\Sigma}^{1/2}$ are mapped to an approximation of the columns of ${\bm\Omega}^{1/2}$.
+The value for $\tilde{\bm \mu}_{opt}$ includes a projection of $\hat{\bm \mu}$ onto $\mathfrak{s}$.
+While it is infeasible to obtain the translation ${\bm d}$, it is worthwhile noting that this measures the difference between the reconciled mean and true mean.
 

### 2018-04-20 ProbabilisticCoherence.tex
Discussion of point reconciliation made more concise and includes bottom up

@@
 
+Point reconciliation methods will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of ${\bm R}$.
+For example \cite{Hyndman2011} consider $\tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h}$ which minimises the Euclidean distance between $\hat{\bm y}$ and $\tilde{\bm y}$.
+\cite{Wickramasuriya2017} consider $\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}' \bm{W}^{-1}_{h}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h}$, where ${\bm W}$ is an estimate of the variance covariance matrix of the unreconciled errors.
+This
+minimises the Mahalonobis distance between $\hat{\bm y}$ and $\tilde{\bm y}$.
+Bottom up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom level series.
+As such bottom up methods are at should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.
+
 %\begin{equation} \label{4.4}
@@
 
-Finding a suitable $\bm{R}$ with respect to a certain loss function will lead to optimally reconciled point forecasts of the hierarchy.
+%Finding a suitable $\bm{R}$ with respect to a certain loss function will lead to optimally reconciled point forecasts of the hierarchy.
 %If $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$, then the definition for linear reconciliation of point forecasts in previous studies coincides with our explanation.
-In our context, we need to find $\bm{R}$ such that $\bm{R}'_\bot \bm{S}$ is invertible; i.e, $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \bm{S}=\bm{I}$.
+
+%In our context, we need to find $\bm{R}$ such that $\bm{R}'_\bot \bm{S}$ is invertible; i.e, $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \bm{S}=\bm{I}$.
 This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}
 
-\citet{Hyndman2011} proposed to choose
-\begin{equation}
-\tilde{\bm{b}}^{OLS}_{t+h}=(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h},
-\end{equation}
-where, in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy are given by
-\begin{equation}
-\tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h}.
-\end{equation}
-They referred this to as the OLS solution and the loss function they considered is equivalent to the Euclidean norm between $\hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h}$; i.e.
+%\citet{Hyndman2011} proposed to choose
+%\begin{equation}
+%\tilde{\bm{b}}^{OLS}_{t+h}=(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h},
+%\end{equation}
+%where, in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy are given by
+%\begin{equation}
+%\tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h}.
+%\end{equation}
+%They referred this to as the OLS solution and the loss function they considered is equivalent to the Euclidean norm between $\hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h}$; i.e.
 $<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>$.
-
-According to a recent study by \citet{Wickramasuriya2017}, selecting $\bm{R}'_\bot = \bm{S}'\bm{W}^{-1}_{h}$ will minimize the trace of mean squared reconciled forecast errors under the property of unbiasedness, where $\bm{W}^{-1}_{h}$ is the variance of the incoherent forecast errors.
+%
+%According to a recent study by \citet{Wickramasuriya2017}, selecting $\bm{R}'_\bot = \bm{S}'\bm{W}^{-1}_{h}$ will minimize the trace of mean squared reconciled forecast errors under the property of unbiasedness, where $\bm{W}^{-1}_{h}$ is the variance of the incoherent forecast errors.
 This will result in
-\begin{equation}
-\tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}'\bm{W}^{-1}_{h} \bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h},
-\end{equation}
-and thus,
-\begin{equation}
-\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}' \bm{W}^{-1}_{h}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h}.
-\end{equation}
-
-They referred this to as the MinT solution.
+%\begin{equation}
+%\tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}'\bm{W}^{-1}_{h} \bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h},
+%\end{equation}
+%and thus,
+%\begin{equation}
+%\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}' \bm{W}^{-1}_{h}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h}.
+%\end{equation}
+%
+%They referred this to as the MinT solution.
 The loss function they considered is equivalent to the Mahalanobis distance between $\hat{\bm{y}}_{T+h}$ and $\tilde{\bm{y}}_{T+h}$.

### 2018-04-20 Figs/probforerec_schematic.tex
files for creating schematic plot - run r script to get tikz picture

% Created by tikzDevice version 0.11 on 2018-04-20 18:17:41
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,361.35);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (480.69,312.15);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 88.68, 49.37) --
	( 88.68,302.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 91.62) --
	(505.89, 91.62);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 88.68, 91.62) -- (417.71,165.55);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (404.42,153.31) --
	(417.71,165.55) --
	(400.46,170.93);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (423.71,163.26) {{\Large ${\bm S}$}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (276.70,122.13) {{\huge $\mathfrak{s}$}};

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 88.68, 91.62) -- (182.69,260.61);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (182.98,242.54) --
	(182.69,260.61) --
	(167.19,251.33);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (182.69,266.61) {{\Large ${\bm R}$}};

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 88.68, 49.37) --
	(229.69,302.86);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (182.69, 49.37) --
	(323.70,302.86);
\definecolor{drawColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 1.6pt,line join=round,line cap=round] (115.54, 97.65) --
	(222.98,121.79);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (229.69, 68.00) {{\huge $\color{red}{s(\mathcal{B})}$}};
\definecolor{drawColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.69, 70.49) -- (169.26,109.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.30,108.78) --
	(169.26,109.72) --
	(177.47, 93.63);
\definecolor{fillColor}{RGB}{0,0,255}

\path[fill=fillColor,fill opacity=0.10] ( 65.18,  7.12) --
	(159.19,  7.12) --
	(347.20,345.10) --
	(253.19,345.10) --
	cycle;
\definecolor{drawColor}{RGB}{0,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (370.70,215.86) {{\huge $\color{blue}{g^{-1}(\mathcal{B}})$}};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (370.70,218.36) -- (229.69,176.11);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.09,189.26) --
	(229.69,176.11) --
	(247.27,171.95);
\end{scope}
\end{tikzpicture}

### 2018-04-20 Figs/probforerec_schematic.r

@@ -1,0 +1,36 @@
+##A script to create a plot that is a schematic describing probabilistic forecast reconciliation.
+
+library(latex2exp)
+library(tikzDevice)
+options(tikzLatexPackages=c(getOption("tikzLatexPackages"),"\\usepackage{amsfonts}","\\usepackage{bm}"),
+        tikzFooter = "\\caption{a caption}")
+tikz('probforerec_schematic.tex',height=5)
+plot.new()
+plot.window(xlim = c(-0.25,4),ylim = c(-0.5,5))
+lines(c(0,0),c(-1,5))
+lines(c(-1,5),c(0,0))
+#lines(c(-1,3.5),c(-0.5,1.75),lwd=2)
+arrows(0,0,3.5,1.75,lwd=3)
+text(3.5,1.75,"{\\Large ${\\bm S}$}",pos=4)
+text(2,1,"{\\huge $\\mathfrak{s}$}",pos=1)
+#lines(c(-0.25,1),c(-1,4),lwd=2)
+arrows(0,0,1,4,lwd=3)
+text(1,4,"{\\Large ${\\bm R}$}",pos=3)
+
+lines(c(0,1.5),c(-1,5),lty=2)
+
+lines(c(1,2.5),c(-1,5),lty=2)
+
+lines(c(2/7,10/7),c(1/7,5/7),lwd=4,col='red')
+text(1.5,-0.5,"{\\huge $\\color{red}{s(\\mathcal{B})}$}")
+arrows(1.5,-0.5,6/7,3/7,col='red')
+
+cord.x<-c(-0.25, 0.75, 2.75, 1.75)
+cord.y<-c(-2, -2, 6, 6)
+
+polygon(cord.x,cord.y,col=adjustcolor('blue',alpha=0.1),border = NA)
+
+text(3,3,"{\\huge $\\color{blue}{g^{-1}(\\mathcal{B}})$}",col='blue')
+arrows(3,3,1.5,2,col='blue')
+
+dev.off()

### 2018-04-20 ProbabilisticCoherence.tex
Probabilistic forecast reconcliation schematic plot included with explanation

@@
 \end{definition}
+
+This definition extends the notion of forecast reconciliation to the probabilistic setting.
+Under point reconciliation methods, the reconciled point forecast is equal to the unreconciled point forecast after the latter is passed through two linear mappings.
+Similarly, probabilistic forecast reconciliation assigns the same probability to two sets where the points in one set are obtained by passing all points in the other set through two linear mappings.
+This is depicted schematically in Figure~\ref{fig:pfr_sch}.
+
+\begin{figure}
+	\input{Figs/probforerec_schematic.tex}
+	\caption{Summary of probabilistic forecast reconciliation.
+The probability that ${\bm y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that ${\bm y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast.
+Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:pfr_sch}
+\end{figure}
 

### 2018-04-20 Figs/pointforerec_schematic.tex
Additional figure for point reconciliation added

--- 2018-04-20 Figs/probforerec_schematic.tex
@@
-% Created by tikzDevice version 0.11 on 2018-04-20 18:17:41
+% Created by tikzDevice version 0.11 on 2018-04-20 18:57:37
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (276.70,122.13) {{\huge $\mathfrak{s}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (276.70,112.53) {{\huge $\mathfrak{s}$}};
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 88.68, 49.37) --
-	(229.69,302.86);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (108.22,  0.00) --
+	(276.70,302.86);
+\definecolor{drawColor}{RGB}{0,0,255}
+\definecolor{fillColor}{RGB}{0,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (182.69, 49.37) --
-	(323.70,302.86);
-\definecolor{drawColor}{RGB}{255,0,0}
-
-\path[draw=drawColor,line width= 1.6pt,line join=round,line cap=round] (115.54, 97.65) --
-	(222.98,121.79);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (229.69,218.36) circle (  3.00);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (229.69, 68.00) {{\huge $\color{red}{s(\mathcal{B})}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (229.69,236.36) {{\huge $\color{blue}{\hat{\bm{y}}}$}};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (212.19,173.82) {{\huge ${\color{blue} s\circ g}$}};
 \definecolor{drawColor}{RGB}{255,0,0}
+\definecolor{fillColor}{RGB}{255,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.69, 70.49) -- (169.26,109.72);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.26,109.72) circle (  3.00);
+\definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (187.30,108.78) --
-	(169.26,109.72) --
-	(177.47, 93.63);
-\definecolor{fillColor}{RGB}{0,0,255}
-
-\path[fill=fillColor,fill opacity=0.10] ( 65.18,  7.12) --
-	(159.19,  7.12) --
-	(347.20,345.10) --
-	(253.19,345.10) --
-	cycle;
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (169.26, 85.99) {{\huge $\color{red}{\tilde{\bm{y}}}$}};
 \definecolor{drawColor}{RGB}{0,0,255}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (370.70,215.86) {{\huge $\color{blue}{g^{-1}(\mathcal{B}})$}};
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.69,218.36) -- (169.26,109.72);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (370.70,218.36) -- (229.69,176.11);
-
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (242.09,189.26) --
-	(229.69,176.11) --
-	(247.27,171.95);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.97,127.79) --
+	(169.26,109.72) --
+	(184.76,119.01);
 \end{scope}

### 2018-04-20 Figs/schematics.r

@@ -1,0 +1,69 @@
+##A script to create a plot that is a schematic describing forecast reconciliation.
+
+library(latex2exp)
+library(tikzDevice)
+options(tikzLatexPackages=c(getOption("tikzLatexPackages"),"\\usepackage{amsfonts}","\\usepackage{bm}"),
+        tikzFooter = "\\caption{a caption}")
+
+
+
+##Point forecast reconciliation.
+
+tikz('pointforerec_schematic.tex',height=5)
+plot.new()
+plot.window(xlim = c(-0.25,4),ylim = c(-0.5,5))
+lines(c(0,0),c(-1,5))
+lines(c(-1,5),c(0,0))
+#lines(c(-1,3.5),c(-0.5,1.75),lwd=2)
+arrows(0,0,3.5,1.75,lwd=3)
+text(3.5,1.75,"{\\Large ${\\bm S}$}",pos=4)
+text(2,1,"{\\huge $\\mathfrak{s}$}",pos=1,offset = 1.3)
+#lines(c(-0.25,1),c(-1,4),lwd=2)
+arrows(0,0,1,4,lwd=3)
+text(1,4,"{\\Large ${\\bm R}$}",pos=3)
+
+lines(c(0,2),c(-3,5),lty=2)
+points(1.5,3,pch=20,cex=2,col='blue')
+text(1.5,3,"{\\huge $\\color{blue}{\\hat{\\bm{y}}}$}",pos = 3,offset = 1.5)
+
+text(1.25,2,"{\\huge ${\\color{blue} s\\circ g}$}",pos=4)
+
+points(6/7,3/7,pch=20,cex=2,col='red')
+text(6/7,3/7,"{\\huge $\\color{red}{\\tilde{\\bm{y}}}$}",pos=1,offset = 1.5)
+
+arrows(1.5,3,6/7,3/7,col='blue')
+
+dev.off()
+
+
+
+tikz('probforerec_schematic.tex',height=5)
+plot.new()
+plot.window(xlim = c(-0.25,4),ylim = c(-0.5,5))
+lines(c(0,0),c(-1,5))
+lines(c(-1,5),c(0,0))
+#lines(c(-1,3.5),c(-0.5,1.75),lwd=2)
+arrows(0,0,3.5,1.75,lwd=3)
+text(3.5,1.75,"{\\Large ${\\bm S}$}",pos=4)
[…]

### 2018-04-20 ProbabilisticCoherence.tex
cleanup

@@
 In general, the columns of any given $\bm{R}$ matrix can also be thought of as `directions' along which incoherent point forecasts are projected onto the coherent space, and these directions need not be orthogonal to $\mathfrak{s}$.
+A schematic of this geometric interpretation is provided in Figure~\ref{fig:pointfr_sch}.
 %$$ 
@@
 %\subsubsection*{Step 1: Change of basis}
+
+\begin{figure}
+	\input{Figs/pointforerec_schematic.tex}
+	\caption{Summary of probabilistic point reconciliation.
+The mapping $G(.)$ projects the unreconciled forecast $\hat{\bm y}$ onto   Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:pointfr_sch}
+\end{figure}
 
@@
 Similarly, probabilistic forecast reconciliation assigns the same probability to two sets where the points in one set are obtained by passing all points in the other set through two linear mappings.
-This is depicted schematically in Figure~\ref{fig:pfr_sch}.
+This is depicted schematically in Figure~\ref{fig:probfr_sch}.
 
@@
 The probability that ${\bm y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that ${\bm y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast.
-Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:pfr_sch}
+Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:probfr_sch}
 \end{figure}

### 2018-04-23 ProbabilisticCoherence.tex
Sketch of section 5 started - more to do

@@
 
-The necessary final step in hierarchical forecasting is to make sure that our forecast distributions are accurately predicting the uncertain future.
-In general, forecasters prefer to maximize the sharpness of the forecast distribution subject to the calibration \citep{Gneiting2014}.
+The necessary final step in hierarchical forecasting is to make sure that our forecast distributions are accurate.
+In general, forecasters prefer to maximize the sharpness of the forecast distribution subject to calibration \citep{Gneiting2014}.
 Therefore the probabilistic forecasts should be evaluated with respect to these two properties.
@@
 In other words, random draws from a perfectly calibrated forecast distribution should be equivalent in distribution to the realizations.
-On the other hand, sharpness refers to the spread or the concentration of the prediction distributions and it is a property of the forecasts only.
+On the other hand, sharpness refers to the spread or the concentration of the predictive distributions and it is a property of the forecasts only.
 The more concentrated the forecast distributions, the sharper the forecasts \citep{Gneiting2008}.
@@
 However, scoring rules have also been defined to be negatively oriented, and then the scores should be minimized \citep{Gneiting2014}.
-We consider negatively oriented scoring rules to evaluate probabilistic forecasts in hierarchical time series.
-
-Let $\breve{\bm{Y}}$ and $\bm{Y}$ be $n$-dimensional random vectors from the forecast distribution $\bm{F}$ and the true distribution $\bm{G}$, respectively.
-Further let $\bm{y}$ be an $n$-dimensional realization from $\bm{G}$.
-Then a scoring rule is a numerical value $S(\breve{\bm{Y}},\bm{y})$ assigned to each pair $(\breve{\bm{Y}},\bm{y})$.
+We follow the latter convention here.
+
+Let $\bm{P}$ be a forecast distribution and let $\bm{Q}$ be the true data generating process respectively.
+Further let $\omega$ be a realization from $\bm{Q}$.
+Then a scoring rule is a function that maps $P,\omega$ to $\mathbb{R}$.
 It is a ``proper'' scoring rule if
 \begin{equation}\label{eq:(3.1.)}
-\E_{\bm{G}}[S(\bm{Y},\bm{y})] \le \E_{\bm{G}}[S(\breve{\bm{Y}},\bm{y})],
-\end{equation}
-where $\E_{\bm{G}}[S(\bm{Y,y})]$ is the expected score under the true distribution $\bm{G}$ \citep{Gneiting2008, Gneiting2014}.
+\E_{\bm{Q}}[S(P,\omega)] \le \E_{\bm{Q}}[S(Q,\omega)],
+\end{equation}
+where $\E_{\bm{Q}}[S(\bm{P,\omega})]$ is the expected score under the true distribution $\bm{Q}$ \citep{Gneiting2008, Gneiting2014}.
+When this inequality is strict, the scoring rule is said to be strictly proper.
+
+\subsection{Univariate Scoring rules}
+
+\todo{In here discuss how scoring rules can be applied to each margin and simply added up.
+This allows us to compare unreconciled and reconciled forecasts.
+It has been done in Ben Taieb Taylor Hyndman and Jeon Panagiotelis Petropoulos}
+
+\subsection{Multivariate Scoring rules}
+
+\todo{Discuss log score, energy (inc. non-Euclidean?) score and variogram score in general}
 
@@
 
+\subsubsection{Comparing Unreconciled Forecasts to Reconciled Forecasts}
+
+\todo{Summary: Log score should not be used.
+Energy score - still trying to prove that reconciled dominates unreconciled, will show "half" proof if necessart.
+Variogram score - it might be possible to show reconciled dominate unreconciled, I will have a look.}
+
 Even though the log score can be used to evaluate simulated forecast densities with large samples \citep{Jordan2017}, it is more convenient to use if we can assume a parametric forecast density for the hierarchy.
@@
 
-\subsection{Evaluating coherent forecast densities}
+\subsubsection{Comparing Reconciled Forecasts to one another}
 

### 2018-04-27 ProbabilisticCoherence.tex
Added discussion of univariate scores

@@
 
+In the context of probabilistic forecast reconciliation there could be two motivations for using scoring rules.
+The first is to compare unreconciled densities to reconciled densities.
+Although reconciliation is a valuable goal in and of itself since it can be important in aligning decision making across, for example, different units of an enterprise, in the point forecasting literature, forecast reconciliation has also been shown to improve forecast performance \todo{Some References}.
+It will be worthwhile to see whether the same holds in the probabilistic forecasting case \todo{mention energy score proof - if we get it}.
+The second motivation for using scoring rules is to compare two or more sets of reconciled probabilistic forecasts.
+The objective here is to evaluate which reconciliation mapping $g(.)$ works best in practice.
+
 \subsection{Univariate Scoring rules}
 
-\todo{In here discuss how scoring rules can be applied to each margin and simply added up.
-This allows us to compare unreconciled and reconciled forecasts.
-It has been done in Ben Taieb Taylor Hyndman and Jeon Panagiotelis Petropoulos}
+One way to evaluate probabilistic forecasts is via the application of univariate scoring rules to each variable in a hierarchy.
+A summary can be taken of the expected scores across each margin for example a mean or median.
+In the simulations of section~\ref{sec:gaussian} we consider two scoring rules.
+The log score is given by the log of the marginal density of each variable.
+The cumulative rank probability score generalises mean square error and is given by
+\begin{align} \label{eq:CRPS}
+\text{CRPS}(\breve{F}_i,y_{T+h,i}) &=\int \left(F_i(\breve{y}_i)-\mathbb{1}(y_i<y_{T+h,i})\right)dy_i\\ &=\E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}\E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|\,,
+\end{align}
+where the expectations in the second line can be approximated by Monte Carlo.
+
+Although univariate scoring ruled have been used in the limited literature on probabilistic forecasting for hierarchies \cite{BenTaieb2017} and Jeon et al \todo{Jeon Panagiotelis and Petropoulos reference} to date, there are a number of shortcomings to this approach.
+Crucially, evaluating univariate scores on the margins do not account for the dependence in the hierarchy.
 
@@
 This is defined as
-\begin{equation} \label{eq:(3.6)}
-\text{CRPS}(\breve{F}_i,y_{T+h,i}) = \E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}\E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|,
-\end{equation}
+%\begin{equation} \label{eq:(3.6)}
+%\text{CRPS}(\breve{F}_i,y_{T+h,i}) = \E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}\E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|,
+%\end{equation}
 where $\breve{Y}_{T+h,i}$ and $\breve{Y}^*_{T+h,i}$ are two independent copies from the $i$th reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy, and $y_{T+h,i}$ is the $i$th realization from the true marginal distribution $G_i$.

### 2018-04-27 ProbabilisticCoherence.tex
Slight restructure of 5, write up of univariate and multivariate scores in general

@@
 
-\todo{Discuss log score, energy (inc. non-Euclidean?) score and variogram score in general}
-
-Table~\ref{table:scoringrules} summarizes a few existing proper scoring rules.
+While the a number of alternative proper scoring rules are available for univariate forecasts, the multivariate case is somewhat more limited.
+Here we focus on three cases, the log score, the energy score and the variogram score.
+These are summarised in table~\ref{table:scoringrules} summarizes a few existing proper scoring rules.
 
@@
 
-\subsubsection{Comparing Unreconciled Forecasts to Reconciled Forecasts}
-
-\todo{Summary: Log score should not be used.
-Energy score - still trying to prove that reconciled dominates unreconciled, will show "half" proof if necessart.
-Variogram score - it might be possible to show reconciled dominate unreconciled, I will have a look.}
-
-Even though the log score can be used to evaluate simulated forecast densities with large samples \citep{Jordan2017}, it is more convenient to use if we can assume a parametric forecast density for the hierarchy.
-However, the degeneracy of coherent forecast densities is problematic when using log scores.
+The log score can be approximated using a sample of values from the probabilistic forecast density \citep{Jordan2017} however it is more commonly used when a parametric form for the density is available for the probabilistic forecast.
+So far, we have only defined probabilistic forecasts in terms of probability measures.
+Although densities can be obtained for both reconciled and unreconciled forecasts, the degeneracy of reconciled forecasts is problematic when using log scores.
 We will discuss this further in the next subsection.
 
-For the energy score with $\alpha=2$, it can be easily shown that
+The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the representation in Table~\ref{table:scoringrules} in terms of expectations leads itself to easy computation when samples from the probabilistic forecast are available.
+An interesting case is where $\alpha=2$, where it can be easily shown that
 \begin{equation} \label{eq:(5.1)}
@@
 where $\breve{\bm{\mu}}_{T+h} =\E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $.
-Therefore, in the limiting case, the energy score only measures the accuracy of the forecast mean, and not the entire distribution.
-Similarly, \citet{Pinson2013a} argued that the energy score given in Table~\ref{table:scoringrules} has a very low discrimination ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
+In this limiting case, the energy score only measures the accuracy of the forecast mean, and not the entire distribution and the energy score is proper, but not strictly proper.
+\citet{Pinson2013a} also argues that the energy score has very low discriminative ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
 
@@
 
-\subsubsection{Comparing Reconciled Forecasts to one another}
-
-Any coherent hierarchical forecast density is a degenerate density.
-To the best of our knowledge, there is no proper multivariate scoring rule available to evaluate degenerate densities.
-Further, it can easily be seen that some of the existing scoring rules breakdown under degeneracy.
+\subsubsection{Comparing Unreconciled Forecasts to Reconciled Forecasts}
 
@@
 This implies that the log score cannot be used to evaluate the degenerate densities.
+
+To be discussed: Energy score - still trying to prove that reconciled dominates unreconciled, will show "half" proof if necessary.
+Variogram score - it might be possible to show reconciled dominate unreconciled, I will have a look.
+
+\subsubsection{Comparing Reconciled Forecasts to one another}
+
+Any coherent hierarchical forecast density is a degenerate density.
+To the best of our knowledge, there is no proper multivariate scoring rule available to evaluate degenerate densities.
+Further, it can easily be seen that some of the existing scoring rules breakdown under degeneracy.
 

### 2018-04-27 ProbabilisticCoherence.tex
Rewritten discussion of why log score breaks down

@@
 
-For example, consider the log score in the univariate case.
-Suppose the true density is degenerate at $x=0$, i.e.
-$f(x)=\mathbb{1}\{x=0\}$.
-\todo{I think you need Dirac delta functions here.}  Now consider two predictive densities $p_1(x)$ and $p_2(x)$.
-Let $p_1(x)$ be equivalent to the true density, i.e.
-$p_1(x)=\mathbb{1}\{x=0\}$, and let $p_2(x) \sim \mathcal{N}(0,\sigma^2)$ with $\sigma^2 < (2\pi)^{-1}$.
-The expected log score of $p_1$ is
-$$
-\E_f[S(f,f)] = \E_f[S(p_1,f)] = -\log[p_1(x=0)]=0,
-$$
-while that of $p_2$ is
-$$
-\E_f[S(p_2,f)] = -\log[p_2(x=0)]<0.
-$$
-Therefore $S(f,f) > S(p_2,f)$, and there exists at least one forecast density which breaks the condition \eqref{eq:(3.1.)} for a proper scoring rule.
-This implies that the log score cannot be used to evaluate the degenerate densities.
+For both reconciled and unreconciled densities it is possible to obtain a density from the probability measures defined in \ref{sec:definitions}.
+As such it may seem sensible to compare unreconciled densities to reconciled densities on the basis of log score.
+However more careful consideration shows that using the log score may fail in the case of multivariate distributions with a degeneracy.
+
+Consider a rotated version of hierarchical time series $\bm{z}_t={\bm U}{\bm y}_t$ so that the first $m$ elements of $\bm{z}_t$ denoted $\bm{z}^(1)_t$ are unconstrained, while the remaining $n-m$ elements denoted $\bm{z}^(2)_t$ equal $0$ when the aggregation constraints hold.
+An example of the $n\times n$ ${\bm U}$ could be the left singular values of the matrix ${\bm S}$.
+For a non-degenerate probability measure on $\mathbb{R}^n$, the density is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^n$.
+For a coherent probability measure the density after rotation is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^m$.
+
+Consider the case where the true density is $f_1(\bm{z}^{(1)}_t)\mathbb{1}\left({\bm{z}^{(2)}_t}\right)$ , the reconciled density is identical to the true density and the unreconciled density is given by $f_1(\bm{z}^{(1)}_t)f_2(\bm{z}^{(2)}_t)$, where $f_2$ is highly concentrated around $0$ but still a proper density, for example a Gaussian with variance $\sigma^2{\bm I}$ with $\sigma^2 < (2\pi)^{-1}$.
+The log score of the reconciled density is
+$$
+S\left(\tilde{f},\bm{z}^{(1)}_t\right) = -\log f_1\left(\bm{z}^{(1)}_t\right),
+$$
+while that of the unreconciled density is
+\begin{align}
+S\left(\hat{f},\bm{z}^{(1)}_t\right) &= -\log f_1(\bm{z}^{(1)}_t)-f_2(\bm{z}^{(1)}_t)\\
+&= -\log f_1(\bm{z}^{(1)}_t)+\frac{n-m}{2}\log(2\pi\sigma^2)\\
+&\leq-\log f_1(\bm{z}^{(1)}_t).
+\end{align}
+
+After taking expectations $ES(f,f) > ES(\hat{f},f)$, violating the condition \eqref{eq:(3.1.)} for a proper scoring rule.
+A similar issue also arises when discrete random variables are modelled as if they were continuous, an issue discussed in Section 4.1, page 366 of \cite{Gneiting2007}.
+This implies that the log score should not be used to evaluate multivariate densities with degeneracies and should be avoided when comparing reconciled and unreconciled probabilistic forecasts.
 

### 2018-04-27 ProbabilisticCoherence.tex
Redundant subsection commented out

@@
 
-\subsection{Comparison of coherent and incoherent forecast densities}
-
-It is also important to assess how the coherent or reconciled forecast densities improve the predictive ability compared to the incoherent forecasts.
+%\subsection{Comparison of coherent and incoherent forecast densities}
+%
+%It is also important to assess how the coherent or reconciled forecast densities improve the predictive ability compared to the incoherent forecasts.
 Clearly, we cannot use multivariate scoring rules, even for the basis set of series, since the coherent and incoherent forecast densities lie in two different metric spaces.
-
-However we could compare the individual margins of the forecast density of the hierarchy using univariate proper scoring rules.
+%
+%However we could compare the individual margins of the forecast density of the hierarchy using univariate proper scoring rules.
 The widely used Continuous Ranked Probability Score (CRPS) could then be used.
 This is defined as
-%\begin{equation} \label{eq:(3.6)}
-%\text{CRPS}(\breve{F}_i,y_{T+h,i}) = \E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}\E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|,
-%\end{equation}
-where $\breve{Y}_{T+h,i}$ and $\breve{Y}^*_{T+h,i}$ are two independent copies from the $i$th reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy, and $y_{T+h,i}$ is the $i$th realization from the true marginal distribution $G_i$.
+%%\begin{equation} \label{eq:(3.6)}
+%%\text{CRPS}(\breve{F}_i,y_{T+h,i}) = \E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}\E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|,
+%%\end{equation}
+%where $\breve{Y}_{T+h,i}$ and $\breve{Y}^*_{T+h,i}$ are two independent copies from the $i$th reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy, and $y_{T+h,i}$ is the $i$th realization from the true marginal distribution $G_i$.
 We could also use univariate log scores, for which we could assume a parametric forecast distribution.

### 2018-04-27 ProbabilisticCoherence.tex
Reorganisation of section 5.2.2 and some open questions posed

@@
 
+\todo{Stuff below still open}
+
 To be discussed: Energy score - still trying to prove that reconciled dominates unreconciled, will show "half" proof if necessary.
@@
 
-Any coherent hierarchical forecast density is a degenerate density.
-To the best of our knowledge, there is no proper multivariate scoring rule available to evaluate degenerate densities.
-Further, it can easily be seen that some of the existing scoring rules breakdown under degeneracy.
-
-However, even though the coherent distribution of the entire hierarchy is degenerate, the density of the basis set of series is non-degenerate since these series are linearly independent.
-Further, if we can correctly specify the forecast distribution of the basis set of series, then we have almost obtained the correct forecast distribution of the whole hierarchy.
-Therefore, we propose to evaluate the forecast distributions using only the basis set of series.
+A characteristic of coherent probabilistic forecasts is that they can be completely characterised in terms of basis series.
+If probabilistic forecasts of the basis series are accurate, then forecasts for the whole hierarchy are also accurate.
+Therefore, we propose that two different sets of reconciled forecasts can be compared to one another using only the basis set of series.
 Then we can use any of the multivariate scoring rules discussed above without incurring problems due to degeneracy.
-
 For example, since the bottom-level series forms a set of basis series for a given hierarchy, we can evaluate the coherent forecast distribution using only the bottom-level series instead of evaluating the whole distribution.
-In particular, if our purpose is to compare two coherent forecast densities, we can compare them using only the bottom-level forecast densities.
+\todo{Two questions below}
+
+\begin{itemize}
+	\item Can we prove that if reconciled forecast A is better than forecast B in terms of the bottom level then it will also be better for the whole series.
+This is kind of obvious for log score, but may not be for energy score and variogram score
+	\item Does the basis we use matter.
+We know that energy score is invariant to orthogonal rotations but ${\bm S}$ is not (semi) orthogonal.
+On the other hand, I don't think variogram is invariant to rotations as all unless $p=2$.
+\end{itemize}
 

### 2018-06-05 Presentation/Figs/orth_pointforerec_schematic.tex
Added Presentation

\begin{tikzpicture}[x=0.7pt,y=0.7pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,505.89);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (263.88,456.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.84,106.94) --
	( 68.84,387.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 22.07,153.71) --
	(289.08,153.71);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 68.84,153.71) -- (232.54,235.56);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (222.59,220.48) --
	(232.54,235.56) --
	(214.51,236.64);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (238.54,233.26) {{\large ${\bm S}$}};
\definecolor{drawColor}{RGB}{0,0,255}
\definecolor{fillColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.00,294.02) circle (  3.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (139.00,312.02) {{\large $\color{blue}{\hat{\bm{y}}}$}};
\definecolor{drawColor}{RGB}{255,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.09,209.84) circle (  3.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (181.09,186.10) {{\large $\color{red}{\tilde{\bm{y}}}$}};
\definecolor{drawColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.00,294.02) -- (181.09,209.84);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.02,219.79) --
	(181.09,209.84) --
	(182.18,227.87);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.93,173.75) circle (  3.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (108.93,150.02) {{\large $\color{black}{{\bm{y}}}$}};
\end{scope}
\end{tikzpicture}

### 2018-06-05 Presentation/Figs/probforerec_schematic.tex
Added Presentation

--- 2018-04-20 Figs/probforerec_schematic.tex
@@
-% Created by tikzDevice version 0.11 on 2018-04-20 18:17:41
+% Created by tikzDevice version 0.11 on 2018-04-24 21:50:28
 % !TEX encoding = UTF-8 Unicode
-\begin{tikzpicture}[x=1pt,y=1pt]
+\begin{tikzpicture}[x=0.6pt,y=0.6pt]
 \definecolor{fillColor}{RGB}{255,255,255}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (229.69, 68.00) {{\huge $\color{red}{s(\mathcal{B})}$}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (244.09, 68.20) {{\huge $\color{red}{s(\mathcal{B})}$}};
 \definecolor{drawColor}{RGB}{255,0,0}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (370.70,215.86) {{\huge $\color{blue}{g^{-1}(\mathcal{B}})$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (370.70,232.76) {{\huge $\color{blue}{g^{-1}(\mathcal{B}})$}};
 

### 2018-06-05 Presentation/ProbForeRec.tex
Added Presentation

\documentclass{beamer}
\usetheme{Warsaw}
\usepackage{amsmath,amsthm, bm, tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\title{Probabilistic Forecast Reconciliation}
\date{June 20, 2018}
\author[GPAH]{Puwasala Gamakumara, Anastasios Panagiotelis, George Athanasopoulos and Rob Hyndman}
\begin{document}
  \begin{frame}
    \maketitle
  \end{frame}
  \section{Concepts}
  \begin{frame}{Hierarchical and Grouped Time Series}
  	\begin{itemize}
  	  \item Collections of Time Series often characterised by aggregation constraints
  	  \begin{itemize}
  	    \item Cross-Sectionally
  		\item Temporally
  	  \end{itemize}
      \item {\bf Coherent} forecasts respect such constraints. 
      \item Independently produced forecasts are generally incoherent.
  \end{itemize}
  picture of hierarchy  
\end{frame}  
  \begin{frame}{Forecast Reconciliation}
  	\begin{itemize}
  	  \item Forecast reconciliation involves
  	  \begin{enumerate}
  	  	\item Producing incoherent {\bf base} forecasts for all series in an $n\times 1$ vector $\hat{\bm y}$
        \item Adjusting base forecasts to obtain {\bf reconciled} forecasts in an $n\times 1$ vector $\tilde{\bm y}$
  	  \end{enumerate} 
      \item Why do we care?
        \begin{enumerate}
        	\item Aligned decision making.
        	\item Improved forecast accuracy
        \end{enumerate}
  	\end{itemize}
  \end{frame}
  \begin{frame}{Reconciliation in two steps}
  	\begin{itemize}
  		\item Many reconciliation methods involve two steps
  		\begin{enumerate}
  			\item Pre-multiply $\hat{\bm y}$ by a $m\times n$ matrix $\bm G$ to obtain {\bf bottom} level series ${\bm b}={\bm G}{\hat{\bm y}}$ 
  			\item Pre-multiply ${\bm b}$ by a $n\times m$ matrix $\bm S$ to obtain ${\tilde{\bm y}}$, i.e. $\tilde{\bm y}={\bm S}{{\bm b}}$
  		\end{enumerate}
  	    \item The matrix ${\bm S}$ defines the aggregation constraints, e.g.
  	    \begin{equation*}
  	    {\bm S}=\begin{pmatrix} 1 &1 \\1 &0 \\0 &1 \\
  	    \end{pmatrix}
  	    \end{equation*}
  	    \item Choices of ${\bm G}$ defines reconciliation method, e.g. OLS: ${\bm G}=\left(\bm{S}'\bm{S}\right)^{-1}{\bm S'}$ and Bottom Up: ${\bm G}=\left(\bm{0}_{m\times n-m}~\bm{I}_{m\times m}\right)$ 
    \end{itemize}
  \end{frame}
  \begin{frame}{Geometry}
  	\vspace{-2.3cm}
  	\centering
  	\input{Figs/orth_pointforerec_schematic}
  \end{frame}
  \section{Probabilistic Reconciliation}
  \begin{frame}{Coherent Subspace}
  	\begin{definition} 
  		The {\bf coherent subspace} is the linear subspace spanned by the columns of ${\bm S}$, i.e. $\mathfrak{s}=\mbox{sp}({\bm S})$
  	\end{definition}
    This definition is not unique, it could be defined as the span of: 
    \begin{equation*}
    {\bm S}^*=\begin{pmatrix}1&0\\0&1\\1&-1\end{pmatrix}
    \end{equation*}
  \end{frame}
  \begin{frame}{Coherent Probabilistic Forecast}
    Let $(\mathbb{R}^m,\mathcal{F}_{\mathbb{R}^m},\nu)$ and $(\mathfrak{s},\mathcal{F}_{\mathfrak{s}},\nu_\mathfrak{s})$ be probability triples on $m$-dimensional space and the coherent subspace respectively.
    \begin{definition}
      The probability measure $\nu_{\mathfrak{s}}$ is coherent if
      \begin{equation*}
      \nu(\mathcal{B})=\nu_{\mathfrak{s}}(s(\mathcal{B}))\quad\forall\mathcal{B}\in \mathcal{F}_{\mathcal{R}_m}
      \end{equation*} 
    \end{definition}
    where $s(\mathcal{B})$ is the image of $\mathcal{B}$ under premultiplication by ${\bm S}$
  \end{frame}
  \begin{frame}{Reconciled Probabilistic Forecast}
  	Let $g:\mathbb{R}^n\rightarrow\mathbb{R}^m$ be a linear map.  Then 
  	\begin{definition}
  	The probability triple $\left(\mathfrak{s},\mathcal{F}_{\mathfrak{s}},\tilde{\nu}\right)$ is the reconciles the probability triple $\left(\mathbb{R}^n,\mathcal{F}_{\mathbb{R}^n},\hat{\nu}\right)$ with with respect to $g$ iff
  	\begin{equation*}
  	\tilde{\nu}(s(\mathcal{B}))=\nu(\mathcal{B})=\hat{\nu}(g^{-1}(\mathcal{B}))\quad\forall \mathcal{B}\in\mathbb{R}^n
  	\end{equation*}
  	\end{definition}
    where $g^{-1}$ is the pre-image of $g$.
  \end{frame}
  \begin{frame}{Geometry}
  	\centering
  	\input{Figs/probforerec_schematic}
  \end{frame}
  \begin{frame}{Analytically}
  	If we have an unreconciled density the reconciled density can be obtained by linear transformations and marginalisation.
  	\begin{align*}
  	\mbox{Pr}(\tilde{\bm{b}}\in s(\mathcal{B}))&=\mbox{Pr}(\hat{\bm{y}}\in g^{-1}(\mathcal{B}))\\
  	&=\int\limits_{g^{-1}(\mathcal{B})}f(\hat{\bm{y}})d\hat{\bm{y}}\\
  	&=\int\limits_{\mathcal{B}}\int f(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}})|\left(\bm{S}~\bm{R}\right)|d\tilde{\bm{a}}d\tilde{\bm{b}}
  	\end{align*}
  \end{frame}
  \begin{frame}{Elliptical distributions}
  	Let the unreconciled density be elliptical with location  $\hat{\bm{\mu}}$ and scale $\hat{\bm{\Sigma}}$ and let the true predictive density be elliptical with location  ${\bm{\mu}}$ and scale ${\bm{S}}{\bm{\Omega}}{\bm{S}}'$.
  	\begin{theorem}
  		The true predictive distribution can be recovered via linear reconciliation.  The optimal (but infeasible) mapping is $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ where $\bm{G}_{opt}={\bm\Omega}^{1/2}{\bm\hat{\Sigma}}^{-1/2}$ and ${\bm d}_{opt}={\bm S}{\bm G}_{opt}\left({\bm \mu}-\hat{\bm \mu}\right)$.
  	\end{theorem}
    This follows from the closure property of elliptical distributions under affine transformations and marginalisation.
  \end{frame}
  \begin{frame}{With a sample}
  	\begin{itemize}
  		\item Often densities are unavailable but we can simulate a sample from the predictive distribution.
  		\item Suppose $\bm{\hat{y}}^{[1]},\ldots,\bm{\hat{y}}^{[J]}$ is a sample from the unreconciled probabilistic forecast.
  		\item Then setting $\tilde{\bm y}^{[j]}=s\circ g(\hat{\bm y}^{[j]})=\bm{S}\bm{G}\hat{\bm y}^{[j]}$ produces a sample from the reconciled distribution with respect to $g$.
  	\end{itemize}
  \end{frame}
  \section{Scoring}
  \begin{frame}{Univariate v Multivariate Scores}
    Scoring rules can be used to evaluate probabilistic forecasts
    \begin{itemize}
    	\item Univariate
    	\begin{itemize}
    		\item Log Score
    		\item Continuous Rank Probability Score
    	\end{itemize}
    	\item Multivariate
        \begin{itemize}
	      \item Log Score
	      \item Energy Score
        \end{itemize}
    \end{itemize}
    These may be computed using densities or a sample.
  \end{frame}
  \begin{frame}{Approaches}
  	\begin{enumerate}
  		\item Use a summary of all univariate scores.
  		\item Make comparisons on the joint distribution of bottom level series only.
        \item Make comparisons using the full joint distribution
  \end{enumerate}
  There are pitfalls to the third approach.
  \end{frame}
  \begin{frame}{Reconciled v Unreconciled}
	When comparing reconciled and unreconciled probabilistic forecasts on the basis of log score
	\begin{theorem}
		Let $f(\bm{y})$ be the true predictive density (on $\mathfrak{s}$) and $LS$ be the (negatively-oriented) log score.  Then there exists an unreconciled density  $\hat{f}(\bm{y})$ on $\mathbb{R}^n$ such that
		\begin{equation*}
		E_{\bm y}\left[S(\hat{f},\bm{y})\right]<E_{\bm y}\left[S(f,\bm{y})\right]
		\end{equation*}
	\end{theorem}
    The log score is not proper {\bf in this context}.
  \end{frame}
  \begin{frame}{Reconciled v Reconciled}
	\begin{itemize}
		\item For two reconciled probabilistic forecasts log score can be used.
		\item Comparisons can be made on the basis of bottom level series (or any basis series).
		\item By the definition of coherence $\log (f({\bm b}))=\log (f({\bm S}{\bm b}){\bm J})$
		\item The Jacobian does not affect the ordering of log score.
	\end{itemize}
  \end{frame}
  \begin{frame}{Energy  score}
  	\begin{itemize}
  		\item More care must be taken using the energy score.
  		\item Energy score is invariant to orthogonal transformation but not affine transformations.
  		\item Since ${\bm S}$ is not a rotation the ranking of different methods based on the full hierarchy may differ from the ranking based on bottom level series only.
  	\end{itemize}
  \end{frame}
   \begin{frame}{Simulations}
   	\begin{itemize}
   		\item If you want to see tables with numbers look at the paper.
   		\item The main takeaway messages are:
   		    \begin{itemize}
   		    	\item Reconiliation is better than no reconciliation.
   		    	\item Bottom up does not do well.
   		    	\item MinT (an oblique projection) does well.
   		    \end{itemize} 
   	\end{itemize}
   \end{frame}
   \begin{frame}{Looking ahead}
     \begin{itemize}
     	\item The optimal feasible reconciliation method remains an open question even for elliptical distributions.
     	\begin{itemize}
     		\item It is likely to depend on the specific score used.
     	\end{itemize}
        \item Are non-linear reconciliation methods worthwhile?
        \item How should probabilistic reconciliation work for non-elliptical distributions.
        \item Further development of multivariate scoring rules.
     \end{itemize}	
   \end{frame}
\end{document}

### 2018-06-05 Presentation/ProbForeRec.tex
changes to presentation

@@
 \usetheme{Warsaw}
-\usepackage{amsmath,amsthm, bm, tikz}
+\usepackage{amsmath,amsthm, bm, tikz,qtree}
 \usetikzlibrary{arrows,positioning,shapes,fit,calc}
@@
   \end{itemize}
-  picture of hierarchy  
+\begin{figure}
+	\begin{center}
+		\leaf{AA} \leaf{AB} 
+		\branch{2}{A}
+		\leaf{BA} \leaf{BB}
+		\branch{2}{B}
+		\branch{2}{Tot}
+		\qobitree
+	\end{center}
+\end{figure}
 \end{frame}  
@@
   	    \begin{equation*}
-  	    {\bm S}=\begin{pmatrix} 1 &1 \\1 &0 \\0 &1 \\
+  	    {\bm S}=\begin{pmatrix} 1 &1 &1 &1 \\1 &1 &0 &0 \\0 &0 &1 &1 \\ &{\bm I_{4\times 4}}
   	    \end{pmatrix}
@@
   \end{frame}
+  \begin{frame}{Geometry: Oblique Projection}
+  	\vspace{-0.9cm}
+  	\centering
+  	\input{Figs/pointforerec_schematic}
+  \end{frame}
   \section{Probabilistic Reconciliation}
@@
   	\end{definition}
-    This definition is not unique, it could be defined as the span of: 
-    \begin{equation*}
-    {\bm S}^*=\begin{pmatrix}1&0\\0&1\\1&-1\end{pmatrix}
-    \end{equation*}
+    Instead of using bottom-level series a different combination of $m$ {\bf basis series} could be used (e.g.
+top and $m-1$ bottom).
+Although ${\bm S}$ would be different $\mathfrak{s}$ would be the same.
   \end{frame}
   \begin{frame}{Coherent Probabilistic Forecast}
-    Let $(\mathbb{R}^m,\mathcal{F}_{\mathbb{R}^m},\nu)$ and $(\mathfrak{s},\mathcal{F}_{\mathfrak{s}},\nu_\mathfrak{s})$ be probability triples on $m$-dimensional space and the coherent subspace respectively.
+    Let $(\mathbb{R}^m,\mathcal{F}_{\mathbb{R}^m},\nu)$ and $(\mathfrak{s},\mathcal{F}_{\mathfrak{s}},\mu)$ be probability triples on $m$-dimensional space and the coherent subspace respectively.
     \begin{definition}
@@
       \begin{equation*}
-      \nu(\mathcal{B})=\nu_{\mathfrak{s}}(s(\mathcal{B}))\quad\forall\mathcal{B}\in \mathcal{F}_{\mathcal{R}_m}
+      \nu(\mathcal{B})=\mu(s(\mathcal{B}))\quad\forall\mathcal{B}\in \mathcal{F}_{\mathcal{R}_m}
       \end{equation*} 
@@
   	\begin{equation*}
-  	\tilde{\nu}(s(\mathcal{B}))=\nu(\mathcal{B})=\hat{\nu}(g^{-1}(\mathcal{B}))\quad\forall \mathcal{B}\in\mathbb{R}^n
+  	\tilde{\nu}(s(\mathcal{B}))=\nu(\mathcal{B})=\hat{\nu}(g^{-1}(\mathcal{B}))\quad\forall \mathcal{B}\in\mathcal{F}_{\mathcal{R}_m}
   	\end{equation*}
@@
    		    \begin{itemize}
-   		    	\item Reconiliation is better than no reconciliation.
+   		    	\item Reconciliation is better than no reconciliation.
    		    	\item Bottom up does not do well.

### 2018-06-12 Presentation/ProbForeRec.tex
Fixed typos

@@
   	    \end{equation*}
-  	    \item Choices of ${\bm G}$ defines reconciliation method, e.g.
+  	    \item Choice of ${\bm G}$ defines reconciliation method, e.g.
 OLS: ${\bm G}=\left(\bm{S}'\bm{S}\right)^{-1}{\bm S'}$ and Bottom Up: ${\bm G}=\left(\bm{0}_{m\times n-m}~\bm{I}_{m\times m}\right)$
@@
     \begin{definition}
-      The probability measure $\nu_{\mathfrak{s}}$ is coherent if
+      The probability measure $\nu$ is coherent if
       \begin{equation*}
-      \nu(\mathcal{B})=\mu(s(\mathcal{B}))\quad\forall\mathcal{B}\in \mathcal{F}_{\mathcal{R}_m}
+      \nu(\mathcal{B})=\mu(s(\mathcal{B}))\quad\forall\mathcal{B}\in \mathcal{F}_{\mathbb{R}_m}
       \end{equation*} 
@@
   	\begin{equation*}
-  	\tilde{\nu}(s(\mathcal{B}))=\nu(\mathcal{B})=\hat{\nu}(g^{-1}(\mathcal{B}))\quad\forall \mathcal{B}\in\mathcal{F}_{\mathcal{R}_m}
+  	\tilde{\nu}(s(\mathcal{B}))=\nu(\mathcal{B})=\hat{\nu}(g^{-1}(\mathcal{B}))\quad\forall \mathcal{B}\in\mathcal{F}_{\mathbb{R}_m}
   	\end{equation*}
@@
   	\begin{align*}
-  	\mbox{Pr}(\tilde{\bm{b}}\in s(\mathcal{B}))&=\mbox{Pr}(\hat{\bm{y}}\in g^{-1}(\mathcal{B}))\\
+  	\mbox{Pr}(\tilde{\bm{b}}\in \mathcal{B})&=\mbox{Pr}(\hat{\bm{y}}\in g^{-1}(\mathcal{B}))\\
   	&=\int\limits_{g^{-1}(\mathcal{B})}f(\hat{\bm{y}})d\hat{\bm{y}}\\
@@
   		The true predictive distribution can be recovered via linear reconciliation.
-The optimal (but infeasible) mapping is $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ where $\bm{G}_{opt}={\bm\Omega}^{1/2}{\bm\hat{\Sigma}}^{-1/2}$ and ${\bm d}_{opt}={\bm S}{\bm G}_{opt}\left({\bm \mu}-\hat{\bm \mu}\right)$.
+The optimal (but infeasible) mapping is $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ where $\bm{G}_{opt}={\bm\Omega}^{1/2}{\hat{\bm{\Sigma}}}^{-1/2}$ and ${\bm d}_{opt}={\bm S}{\bm G}_{opt}\left({\bm \mu}-\hat{\bm \mu}\right)$.
   	\end{theorem}
@@
    	\begin{itemize}
-   		\item If you want to see tables with numbers look at the paper.
+   		\item If you want to see tables with numbers see the paper.
    		\item The main takeaway messages are:
@@
    		    	\item Bottom up does not do well.
-   		    	\item MinT (an oblique projection) does well.
+   		    	\item OLS (an orthogonal projection) does poorly.
+   		    	\item MinT (an oblique projection) does best.
    		    \end{itemize} 
@@
    \end{frame}
+    \begin{frame}{The paper}
+    	\begin{itemize}
+    		\item A paper will be available soon (end of July).
+    		\item Google {\em EBS Monash Working Paper}.
+    		\item Or email me :)
+    	\end{itemize}
+    \end{frame}
 \end{document}

### 2018-06-12 Presentation/ProbForeRec.tex
fixed minor errors

@@
   	\begin{itemize}
-  	  \item Collections of Time Series often characterised by aggregation constraints
+  	  \item Collections of time series often characterised by aggregation constraints
   	  \begin{itemize}
@@
   	  	\item Producing incoherent {\bf base} forecasts for all series in an $n\times 1$ vector $\hat{\bm y}$
-        \item Adjusting base forecasts to obtain {\bf reconciled} forecasts in an $n\times 1$ vector $\tilde{\bm y}$
+        \item Adjusting base forecasts to obtain coherent {\bf reconciled} forecasts in an $n\times 1$ vector $\tilde{\bm y}$
   	  \end{enumerate} 
@@
   	\begin{definition}
-  	The probability triple $\left(\mathfrak{s},\mathcal{F}_{\mathfrak{s}},\tilde{\nu}\right)$ is the reconciles the probability triple $\left(\mathbb{R}^n,\mathcal{F}_{\mathbb{R}^n},\hat{\nu}\right)$ with with respect to $g$ iff
+  	The probability triple $\left(\mathfrak{s},\mathcal{F}_{\mathfrak{s}},\tilde{\nu}\right)$ reconciles the probability triple $\left(\mathbb{R}^n,\mathcal{F}_{\mathbb{R}^n},\hat{\nu}\right)$ with with respect to $g$ iff
   	\begin{equation*}
@@
 		\begin{equation*}
-		E_{\bm y}\left[S(\hat{f},\bm{y})\right]<E_{\bm y}\left[S(f,\bm{y})\right]
+		E_{\bm y}\left[LS(\hat{f},\bm{y})\right]<E_{\bm y}\left[LS(f,\bm{y})\right]
 		\end{equation*}

### 2018-06-19 Presentation/ProbForeRec.tex
fixed mistake in dopt and two other minor changes

@@
   	\begin{itemize}
-  	  \item Collections of time series often characterised by aggregation constraints
+  	  \item Collections of time series are often characterised by aggregation constraints
   	  \begin{itemize}
@@
   		The true predictive distribution can be recovered via linear reconciliation.
-The optimal (but infeasible) mapping is $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ where $\bm{G}_{opt}={\bm\Omega}^{1/2}{\hat{\bm{\Sigma}}}^{-1/2}$ and ${\bm d}_{opt}={\bm S}{\bm G}_{opt}\left({\bm \mu}-\hat{\bm \mu}\right)$.
+The optimal (but infeasible) mapping is $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ where $\bm{G}_{opt}={\bm\Omega}^{1/2}{\hat{\bm{\Sigma}}}^{-1/2}$ and ${\bm d}_{opt}={\bm G}_{opt}\left({\bm \mu}-\hat{\bm \mu}\right)$.
   	\end{theorem}
@@
   	\begin{itemize}
-  		\item More care must be taken using the energy score.
+  		\item Using bottom level series only is a bad idea for energy score.
   		\item Energy score is invariant to orthogonal transformation but not affine transformations.

### 2018-06-26 ProbabilisticCoherence.tex
Written up discussion of comparing coherent v coherent

--- 2018-04-27 ProbabilisticCoherence.tex
@@
 
-To be discussed: Energy score - still trying to prove that reconciled dominates unreconciled, will show "half" proof if necessary.
-Variogram score - it might be possible to show reconciled dominate unreconciled, I will have a look.
-
 \subsubsection{Comparing Reconciled Forecasts to one another}
 
-Any coherent hierarchical forecast density is a degenerate density.
-To the best of our knowledge, there is no proper multivariate scoring rule available to evaluate degenerate densities.
-Further, it can easily be seen that some of the existing scoring rules breakdown under degeneracy.
-
-However, even though the coherent distribution of the entire hierarchy is degenerate, the density of the basis set of series is non-degenerate since these series are linearly independent.
-Further, if we can correctly specify the forecast distribution of the basis set of series, then we have almost obtained the correct forecast distribution of the whole hierarchy.
-Therefore, we propose to evaluate the forecast distributions using only the basis set of series.
-Then we can use any of the multivariate scoring rules discussed above without incurring problems due to degeneracy.
-
-For example, since the bottom-level series forms a set of basis series for a given hierarchy, we can evaluate the coherent forecast distribution using only the bottom-level series instead of evaluating the whole distribution.
-In particular, if our purpose is to compare two coherent forecast densities, we can compare them using only the bottom-level forecast densities.
+Coherent probabilistic forecasts can be completely characterised in terms of basis series; if a probabilistic forecast is  available for the basis series then a probabilistic forecast can be recovered for  the  entire hierarchy via Definition~\ref{def:cohprob}.
+This may suggest that it is adequate to merely compare two coherent forecasts to  one  another using  the basis series only.
+We now show how this is  dependent on the specific scoring rule used.
+
+For the log score, suppose the coherent probabilistic forecast has density $f(\bm{b})$.
+The density for the full hierarchy is given by $f(\bm{y})=f(\bm{Sb})=f(\bm{b})J$ where $J=\prod_{j=1}^{m}\lambda_j^{-1}$ is the inverse of a pseudo-determinant of the non-square  matrix $X$ and $\lambda_j$ are the non-zero singular values of ${\bm S}$.
+Therefore for any coherent density the log score of the full hierarchy differs from the log score for the bottom level series by the term $log(J)$.
+This term depends  only on the structure of the  hierarchy and is fixed across different forecasting methods.
+Therefore if one method achieves a lower expected log score than an alternative method  when assessed using the bottom level series, the same ordering is preserved when an assessment is made on the basis of the full hierarchy.
+
+The same property does not hold for all scores in general.
+For example, energy score can be expressed in terms of an expectations of norms.
+In general, since norms are invariant under orthogonal rotations the energy score is also invariant under orthogonal transformations \citep{Szekely2013,Gneiting2007}.
+In the context of two coherent forecasts the same is true of a semi-orthogonal transformation from a lower dimensional basis series to the full hierarchy.
+However,  when ${\bm S}$ is  the usual summing matrix, it is not semi-orthogonal.
+As such the energy score computed on the bottom level series will differ from the energy score computed using the full hierarchy and the ordering of different reconciliation methods may change depending on the basis series used.
+In this case we recommend computing energy score using the full hierarchy.
+Although the discussion here is related to energy score, the same logic holds for other scores that are not invariant to orthogonal rotations, for example the variogram score.
+
+The properties of mutlivariate scoring rules in the context of evaluating reconciled probabilistic forecasts in Table~\ref{tab:prop}.
+
+\begin{table}
+	\centering
+	\begin{tabular}{rll}
+	& Coherent v Incoherent &Coherent v Coherent\\
+	\hline
+	Log Score & Not proper & Ordering preserved if compared using\\ &&bottom level only\\
+	Energy/ & Proper & Full hierarchy should be used\\
+	Variogram Score & &\\
+	\hline
+    \end{tabular}
+	\caption{Summary of properties of scoring rules in the context of reconciled probabilistic forecasts.}
+	\label{tab:prop}
+
+\end{table}
 

### 2018-06-27 ProbabilisticCoherence.tex
Material removed  from Section 6 which is now purely about simulation

@@
 
-\section{Probabilistic forecast reconciliation in the Gaussian framework}\label{sec:gaussian}
-
-An important special case for probabilistic forecasting arises when we can assume a multivariate Gaussian distribution.
+\section{Simulation Study}\label{sec:gaussian}
+
+%An important special case for probabilistic forecasting arises when we can assume a multivariate Gaussian distribution.
 That is, suppose all the historical data in the hierarchy follows a multivariate Gaussian distribution, $\bm{y}_T \sim \mathcal{N}(\bm{\mu}_T, \bm{\Sigma}_T)$, where both $\bm{\mu}_T$ and $\bm{\Sigma}_T$ live in $\mathbb{C}^m$ by nature of the hierarchical structure of the data.
 We are interested in estimating the predictive Gaussian distribution of $\bm{Y}_{T+h}| \bm{\mathcal{I}}_T$, where $\bm{\mathcal{I}}_T= \{\bm{y}_1,\bm{y}_2,\dots.,\bm{y}_T\}$, which should also live in $\mathbb{C}^m$.
-
-It is well known that the optimal point forecasts with respect to the minimal mean square error are given by the conditional expectations, $\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}],$ $i=1,\dots,n$.
+%
+%It is well known that the optimal point forecasts with respect to the minimal mean square error are given by the conditional expectations, $\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}],$ $i=1,\dots,n$.
 Suppose we independently fit time series models for each series in the hierarchy.
@@
 \todo{Only for linear models?}
-
-For example, suppose the data from $i$th series follows a ARMA$(p,q)$ model. i.e.,
-$$
-Y_{t,i}=\alpha_1Y_{t-1,i}+\dots+\alpha_pY_{t-p,i}+\varepsilon_t + \beta_1\varepsilon_{t-1,i}+\dots+\beta_q\varepsilon_{t-q,i},
-$$
-where $\varepsilon_t \sim \mathcal{NID}(0, \sigma_i^2)$. Then,
-$$
-\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}] = \alpha_1Y_{T+h-1,i}+\dots+\alpha_pY_{T+h-p,i}+ \beta_1\varepsilon_{T+h-1,i}+\dots+\beta_q\varepsilon_{T+h-q,i}.
-$$
-
-Since $\bm{\alpha} = (\alpha_1,\dots,\alpha_p)'$ and $\bm{\beta} = (\beta_1,\dots,\beta_q)'$ are unknown in practice and thus estimated using the maximum likelihood method.
+%
+%For example, suppose the data from $i$th series follows a ARMA$(p,q)$ model. i.e.,
+%$$
+%Y_{t,i}=\alpha_1Y_{t-1,i}+\dots+\alpha_pY_{t-p,i}+\varepsilon_t + \beta_1\varepsilon_{t-1,i}+\dots+\beta_q\varepsilon_{t-q,i},
+%$$
+%where $\varepsilon_t \sim \mathcal{NID}(0, \sigma_i^2)$. Then,
+%$$
+%\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}] = \alpha_1Y_{T+h-1,i}+\dots+\alpha_pY_{T+h-p,i}+ \beta_1\varepsilon_{T+h-1,i}+\dots+\beta_q\varepsilon_{T+h-q,i}.
+%$$
+%
+%Since $\bm{\alpha} = (\alpha_1,\dots,\alpha_p)'$ and $\bm{\beta} = (\beta_1,\dots,\beta_q)'$ are unknown in practice and thus estimated using the maximum likelihood method.
 Let $\bm{\hat{\alpha}}$ and $\bm{\hat{\beta}}$ denote the maximum likelihood estimates of $\bm{\alpha}$ and $\bm{\beta}$ respectively.
@@
 i.e.,
-\begin{equation} \label{eq:(6.01)}
-\hat{Y}_{T+h,i} \overset{p}{\to} \E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}] \quad \text{as} \quad T \to \infty.
-\end{equation}
-
-Let $\hat{\bm{Y}}_{T+h}=(\hat{Y}_{T+h,1},\dots,\hat{Y}_{T+h,n})'$ and suppose \eqref{eq:(6.01)} holds for $i=1,\dots,n$. Then from Slutsky's theorem it follows that
-\begin{equation}\label{eq:(6.02)}
-\hat{\bm{Y}}_{T+h} \overset{p}{\to} \E[\bm{Y}_{T+h}|\bm{\mathcal{I}}_T] \quad \text{as} \quad T \to \infty.
-\end{equation}
-Further, let the forecast error due to $\hat{\bm{Y}}_{T+h}$ be given by
-\begin{equation}
-\hat{\bm{e}}_{T+h} = \bm{Y}_{T+h}-\hat{\bm{Y}}_{T+h},
-\end{equation}
-and consider the variance of $\hat{\bm{e}}_{T+h}$,
-\begin{align*}
-\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = &
-\E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)- \hat{\bm{Y}}_{T+h})\\
-& \quad
-(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T],\\
-= &
-\E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T]\\
-& \quad
-+ \E[\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
-& \quad
-+  \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
-&  \quad
-+ \E[\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T].
-\end{align*}
-
-From \eqref{eq:(6.02)} it immediately follows that
-\begin{align*}
-&\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] \overset{p}{\to} \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T].
-\end{align*}
-That is,
-\begin{equation}
-\bm{W}_{T+h} \overset{p}{\to} \text{Var}(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) \quad \text{as} \quad T \to \infty,
-\end{equation}
-where $\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = \bm{W}_{T+h}$.
-
-Even though $\hat{\bm{Y}}_{T+h}$ and $\bm{W}_{T+h}$ are asymptotically consistent estimators for $\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ and $\text{Var}(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ respectively, they are not coherent since they do not lie in the coherent subspace.
+%\begin{equation} \label{eq:(6.01)}
+%\hat{Y}_{T+h,i} \overset{p}{\to} \E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}] \quad \text{as} \quad T \to \infty.
+%\end{equation}
+%
+%Let $\hat{\bm{Y}}_{T+h}=(\hat{Y}_{T+h,1},\dots,\hat{Y}_{T+h,n})'$ and suppose \eqref{eq:(6.01)} holds for $i=1,\dots,n$. Then from Slutsky's theorem it follows that
+%\begin{equation}\label{eq:(6.02)}
+%\hat{\bm{Y}}_{T+h} \overset{p}{\to} \E[\bm{Y}_{T+h}|\bm{\mathcal{I}}_T] \quad \text{as} \quad T \to \infty.
+%\end{equation}
+%Further, let the forecast error due to $\hat{\bm{Y}}_{T+h}$ be given by
+%\begin{equation}
+%\hat{\bm{e}}_{T+h} = \bm{Y}_{T+h}-\hat{\bm{Y}}_{T+h},
+%\end{equation}
+%and consider the variance of $\hat{\bm{e}}_{T+h}$,
+%\begin{align*}
+%\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = &
+%\E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)- \hat{\bm{Y}}_{T+h})\\
+%& \quad
+%(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T],\\
+%= &
+%\E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T]\\
+%& \quad
+%+ \E[\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
+%& \quad
+%+  \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
+%&  \quad
+%+ \E[\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T].
+%\end{align*}
+%
+%From \eqref{eq:(6.02)} it immediately follows that
+%\begin{align*}
+%&\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] \overset{p}{\to} \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T].
+%\end{align*}
+%That is,
+%\begin{equation}
+%\bm{W}_{T+h} \overset{p}{\to} \text{Var}(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) \quad \text{as} \quad T \to \infty,
+%\end{equation}
+%where $\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = \bm{W}_{T+h}$.
+%
+%Even though $\hat{\bm{Y}}_{T+h}$ and $\bm{W}_{T+h}$ are asymptotically consistent estimators for $\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ and $\text{Var}(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ respectively, they are not coherent since they do not lie in the coherent subspace.
 Thus the Gaussian forecast distribution with mean $\hat{\bm{Y}}_{T+h}$ and variance $\bm{W}_{T+h}$ will be incoherent, and we denote it by
-\begin{equation}\label{eq:(6.03)}
-\widehat{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathcal{N}(\hat{\bm{Y}}_{T+h}, \bm{W}_{T+h})
-\end{equation}
-
-Since our primary objective is to find the coherent forecast density of the hierarchy, we need to reconcile \eqref{eq:(6.03)}.
+%\begin{equation}\label{eq:(6.03)}
+%\widehat{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathcal{N}(\hat{\bm{Y}}_{T+h}, \bm{W}_{T+h})
+%\end{equation}
+%
+%Since our primary objective is to find the coherent forecast density of the hierarchy, we need to reconcile \eqref{eq:(6.03)}.
 Using \eqref{eq:gaussianreconciled}, the reconciled Gaussian forecast distribution is then given by
-\begin{equation}\label{eq:(6.04)}
-\widetilde{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathcal{N}(\bm{SP}\hat{\bm{Y}}_{T+h}, \bm{SP}\bm{W}_{T+h}\bm{P}'\bm{S}'),
-\end{equation}
-where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
-
-\textbf{Result 1}: Choosing $\bm{R}'_\bot = \bm{S}'\bm{W}_{T+h}^{-1}$ will ensure that at least the mean of the predictive Gaussian distribution is optimally reconciled with respect to the energy score.
-
-Result 1 can be easily shown as follows.
+%\begin{equation}\label{eq:(6.04)}
+%\widetilde{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathcal{N}(\bm{SP}\hat{\bm{Y}}_{T+h}, \bm{SP}\bm{W}_{T+h}\bm{P}'\bm{S}'),
+%\end{equation}
+%where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
+%
+%\textbf{Result 1}: Choosing $\bm{R}'_\bot = \bm{S}'\bm{W}_{T+h}^{-1}$ will ensure that at least the mean of the predictive Gaussian distribution is optimally reconciled with respect to the energy score.
+%
+%Result 1 can be easily shown as follows.
 From \eqref{eq:(5.1)}, the energy score at the upper limit of $\alpha=2$ is given by $\|\bm{y}_{T+h}-\bm{SP}\hat{\bm{y}}_{T+h}\|^2$.
 Then the expectation of the energy score with respect to the true distribution is equivalent to the trace of mean squared forecast error; i.e.,
-$$
-\E_{\bm{G}}[eS(\bm{\tilde{Y}_{T+h},y_{T+h}})]= \text{Tr}\{\E_{\bm{y}_{T+h}}[(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})'|\mathcal{I}_{T}]\}.
-$$
-
-From Theorem 1 of \citet{Wickramasuriya2017} it immediately follows that $\bm{P} = (\bm{S}'\bm{W}_{T+h}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}_{T+h}^{-1}$ minimizes the expected energy score, if we constrain the reconciled forecasts to be unbiased.
+%$$
+%\E_{\bm{G}}[eS(\bm{\tilde{Y}_{T+h},y_{T+h}})]= \text{Tr}\{\E_{\bm{y}_{T+h}}[(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})'|\mathcal{I}_{T}]\}.
+%$$
+%
+%From Theorem 1 of \citet{Wickramasuriya2017} it immediately follows that $\bm{P} = (\bm{S}'\bm{W}_{T+h}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}_{T+h}^{-1}$ minimizes the expected energy score, if we constrain the reconciled forecasts to be unbiased.
 Thus we have $\bm{R}'_\bot = \bm{S}'\bm{W}_{T+h}^{-1}$.
-
-It should be noted that $\bm{W}_{T+h}$ can be estimated in different ways, which yields different estimates of $\bm{R}'_\bot$. Table~\ref{table:2} summarizes some of these methods.
-
+%
+%It should be noted that $\bm{W}_{T+h}$ can be estimated in different ways, which yields different estimates of $\bm{R}'_\bot$. Table~\ref{table:2} summarizes some of these methods.
+%
 \begin{table}
@@
 
-\subsubsection*{Simulations}
-
-We consider the hierarchy given in Figure~\ref{fig1}, comprising two aggregation levels with four bottom-level series.
+We now turn our attention to comparing different reconciliation methods in a simulation study where the data is conditionally Gaussian.
+We choose the Gaussian due to its analytical tractability which allows for evaluation on the basis of all scoring rules (including the log score).
+The non-Gaussian case lies beyond the scope of this simulation study, but can be handled by a bootstrapping approach proposed in separate work.
+
+For  the data generating process, we consider the hierarchy given in Figure~\ref{fig1}, comprising two aggregation levels with four bottom-level series.
 Each bottom-level series will be generated first, and then summed to obtain the data for the upper-level series.
@@
 To assess the predictive performance of different forecasting methods, we use scoring rules as discussed in Section~\ref{sec:evaluation}.
-To faciliate comparisons, we report skill scores \citep{Gneiting2007}.
+To facilitate comparisons, we report skill scores \citep{Gneiting2007}.
 For a given forecasting method, evaluated by a particular scoring rule $S(\cdot)$, the skill score is calculated as
@@
 
-In Table~\ref{table:3}, we compare different reconciliation methods over the conventional bottom-up method.
-We use bottom-level probabilistic forecasts and calculate the percentage skill score based on energy score, log score and variogram score for each reconciliation method with reference to the bottom-up method.
+Table~\ref{table:3}, summarised the different reconciliation methods over the conventional bottom-up method.
+The so-called OLS method uses an orthogonal projection, while  the remaining methods consider oblique projections where ${\bm G}=\left({\bm S}'{\bm W}^{-1}{\bm S}\right)^{-1}{\bm S}'{\bm W}^{-1}$.
+In each case we calculate the percentage skill score based on energy score, log score and variogram score for each reconciliation method with reference to the bottom-up method.
 

### 2018-06-27 ProbabilisticCoherence.tex
Everything up to 4.3 rewritten to take into account that projections are a special case of G only

@@
 It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect aggregation constraints.
-We follow other authors in using the nomenclature {\em coherence} to describe this property.
+We follow other authors \cite{Wickramasuriya2017}\todo{FPP?} in using the nomenclature {\em coherence} to describe this property.
 %While coherent point forecasts have been discussed many times previously, the definitions of coherence previously given are vague and are not easily extended to the situation of probabilistic forecasting.
@@
 
+Recall that $\bm{y}_t \in \mathbb{R}^n$ is a $n$-dimensional time series subject to the linear aggregation constraint $\bm{y}_t = \bm{S}\bm{b}_t$, where $\bm{b}_t \in \mathbb{R}^m$ and $\bm{S}$ is an $n \times m$ constant matrix.
+
 \begin{definition}[Coherent subspace]\label{def:cohspace}
-Let an $n$-dimensional time series $\bm{y}_t \in \mathbb{R}^n$ be subject to the linear aggregation constraint $\bm{y}_t = \bm{S}\bm{b}_t$, where $\bm{b}_t \in \mathbb{R}^m$ and $\bm{S}$ is an $n \times m$ constant matrix.
-The $m$-dimensional subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e.
-$\mathfrak{s}=\mbox{span}(\bm{S})$, is defined as the {\em coherent space}.
+ The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e. $\mathfrak{s}=\mbox{span}(\bm{S})$, is defined as the {\em coherent space}. 
 \end{definition}
 
-We also denote the $n\times(n-m)$ orthogonal complement of $\bm{S}$ as $\bm{S}_{\perp}$, where $\mathfrak{s}_\perp=\mbox{span}\left(\bm{S}_{\perp}\right)$ is the nullspace of $\bm{S}$.
 Also at times is  will be useful to think of pre-multiplication by $\bm{S}$ as a linear mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$ in which case we use the notation $s(.)$.
@@
 
+Let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple, where $\mathscr{F}_{\mathbb{R}^m}$ is the usual $\sigma$-algebra on $\mathbb{R}^m$.
+Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_{\mathfrak{s}}$.
+Here $\mathscr{F}_{\mathfrak{s}}$ is formed as collection of sets $s(\mathcal{B})$, where $s(\mathcal{B})$ denotes the image of the set $\mathcal{B}\in \mathscr{F}_{\mathbb{R}^m}$ under the mapping $s(.)$.
+
 \begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
-  Let $(\mathbb{R}^m, \mathscr{F}^{\mathbb{R}^m}, \nu)$ be a probability triple, where $\mathscr{F}^{\mathbb{R}^m}$ is the usual $\sigma$-algebra on $\mathbb{R}^m$.
-Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}^{\mathfrak{s}}$.
-Here $\mathscr{F}^{\mathfrak{s}}$ is formed as collection of sets $s(\mathcal{B})$, where $s(\mathcal{B})$ denotes the image of the set $\mathcal{B}\in \mathscr{F}^{\mathbb{R}^m}$ under the mapping $s(.)$.
-Let the measure $\breve{\nu}$ have the property
-  $$
-      \breve{\nu}(s(\mathcal{B})) = \nu(\mathcal{B}) \quad \forall  \mathcal{B} \in \mathscr{F}^{\mathbb{R}^m},
-    $$  
-  A probabilistic forecast is coherent if uncertainty in $\bm{y_{t+h|h}}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}^{\mathfrak{s}},\breve{\nu})$.
+  The measure $\breve{\nu}$ is coherent if it has the property
+  $$
+      \breve{\nu}(s(\mathcal{B})) = \nu(\mathcal{B}) \quad \forall  \mathcal{B} \in \mathscr{F}_{\mathbb{R}^m},
+    $$    
 \end{definition}
+A probabilistic forecast for time $t+h$ is coherent if uncertainty in $\bm{y_{t+h|h}}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.
 
@@
 The definitions above could be made in terms of any series and not just the bottom level series.
-In general, we call the series (or linear combinations thereof) used in the definitions of coherence as \textit{basis series}.
+In general, we call the series (or linear combinations thereof) used in the definitions of coherence \textit{basis series}.
 Unless stated otherwise, we will always assume that the basis series are the bottom level series as in Definition~\ref{def:cohpoint} and Defintion~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.
@@
   Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ using information up to and including time $t$.
-Let $\bm{G}$ be an $m\times n$ matrix and $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping corresponding to pre-multiplication by $\bm{G}$.
+Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively and $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})={\bm G}{\bm y}+{\bm d}$.
   \begin{definition}\label{def:reconpoint}
@@
   \begin{equation}
-    \tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}\,.
+    \tilde{\bm{y}}_{t+h|t}=\bm{S}\left(\bm{G}\hat{\bm{y}}_{t+h|t}+{\bm d}\right)\,.
   \end{equation}
@@
 
-In definition~\ref{def:reconpoint}  $\bm{S}\bm{G}$ is a projection matrix that maps $\mathbb{R}^n$ onto $\mathfrak{s}$.
-We note that a similar characterisation of reconciliation has been used in previous studies but where the notation $\bm{P}$ is used in place of $\bm{G}$.
-In principle the definition can be generalised where $g(.)$ is a non-linear mapping, a possibility we consider in Section~\ref{nonlinear} {\color{red}[AP: I WILL ADD THIS LATER]}.
-
-Definition~\ref{def:reconpoint}, defines an entire family of forecast reconciliation methods including many methods currently extant in the literature.
-To provide a geometric interpretation, we introduce an $n \times (n-m)$ matrix $\bm{R}$ whose columns span the null space $\mathfrak{s}_{\perp}$.
+Many choices of $g(.)$ currently extant in the literature including the OLS, WLS and MinT methods are such that $s\circ g$ is a projection.
+To define these more generally and provide geometric intuition, we introduce an $n \times (n-m)$ matrix $\bm{R}$ whose columns span the null space of $\mathfrak{s}_{\perp}$.
 For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
@@
 In general, the columns of any given $\bm{R}$ matrix can also be thought of as `directions' along which incoherent point forecasts are projected onto the coherent space, and these directions need not be orthogonal to $\mathfrak{s}$.
-A schematic of this geometric interpretation is provided in Figure~\ref{fig:pointfr_sch}.
+Projections are special cases of Definition~\ref{def:reconpoint} where ${\bm d=0}$ and ${\bm G}$ has the form $\left({\bm R}_\perp'{S}\right)^{-1}{\bm R}_\perp'$ where ${\bm R}_\perp$ is the $n\times m$ orthogonal complement of ${\bm R}$.
+In the example provided, ${\bm R}_\perp'={\bm S}$ and reconciliation corresponds to the so called `OLS' method \cite{Hyndman2011}.
+A schematic providing a geometric interpretation is given in Figure~\ref{fig:pointfr_sch}.
+
 %$$ 
@@
 As such any incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$, can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$.
-Let $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$, respectively.
+Let $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$ respectively after a change of basis.
 The process of reconciliation involves setting $\tilde{\bm{b}}_{t+h|t}$ to be the values of the reconciled bottom-level series and setting $\tilde{\bm{a}}_{t+h}=\bm{0}$ to ensure coherence.
@@
 \end{equation}
-where $\bm{S}_{\bot}$ and $\bm{R}_{\bot}$ be the orthogonal complements of $\bm{S}$ and $\bm{R}$
-respectively.
+where $\bm{S}_{\bot}$ is the orthogonal complements of $\bm{S}$.
 Thus it follows that $\tilde{\bm{b}}_{t+h}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$.
-Here $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ is equivalent to $\bm{G}$ in Definition~\ref{def:reconpoint}.
-
-Point reconciliation methods will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of ${\bm R}$.
+Here $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ corresponds to $\bm{G}$ as defined previously.
+
+Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of ${\bm R}$.
 For example \cite{Hyndman2011} consider $\tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h}$ which minimises the Euclidean distance between $\hat{\bm y}$ and $\tilde{\bm y}$.
@@
 Bottom up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom level series.
-As such bottom up methods are at should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.
+As such, bottom up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.\todo{mention reducing distance to truth?}.
 
@@
 
-  Let $(\mathbb{R}^n, \mathscr{F}^{\mathbb{R}^n}, \hat{\nu})$ be an probability triple, that is not necessarily coherent and that characterises forecast uncertainty for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.
+  Let $(\mathbb{R}^n, \mathscr{F}^{\mathbb{R}^n}, \hat{\nu})$ be an probability triple, that is incoherent and that characterises forecast uncertainty for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.
+This may be obtained from the first stage of the forecasting process e.g.
+by modelling and forecasting each series individually.
 Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear mapping.
-Let $(\mathbb{R}^m, \mathscr{F}^{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$ where $\nu$ has the following property:
-  \begin{equation}
-  \nu(\mathcal{B}) = \hat{\nu}(g^{-1}(\mathcal{B})), \quad \forall \mathcal{B} \in \mathscr{F}^{\mathbb{R}^m}\,.
-  \end{equation}
-  Here $g^{-1}(\mathcal{B}):=\left\{\breve{\bm{y}}\in \mathbb{R}^n:g(\breve{\bm{y}})\in \mathcal{B} \right\}$ is the pre-image of $\mathcal{B}$, that is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $\mathcal{B}$.
+Let $(\mathbb{R}^m, \mathscr{F}^{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$.
   \begin{definition} \label{def:reconprob}
@@
   \begin{equation}
-  \tilde{\nu}(s(\mathcal{B})) = \nu(\mathcal{B})= \hat{\nu}(g^{-1}(\mathcal{B})) \qquad \forall \mathcal{B} \in \mathscr{F}^{\mathbb{R}^m}\,.
-  \end{equation}
+  \tilde{\nu}(s(\mathcal{B})) = \nu(\mathcal{B})= \hat{\nu}(g^{-1}(\mathcal{B})) \qquad \forall \mathcal{B} \in \mathscr{F}^{\mathbb{R}^m}\,,
+  \end{equation}
+  where $g^{-1}(\mathcal{B}):=\left\{\breve{\bm{y}}\in \mathbb{R}^n:g(\breve{\bm{y}})\in \mathcal{B} \right\}$ is the pre-image of $\mathcal{B}$, that is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $\mathcal{B}$.
 \end{definition}
@@
 Similarly, probabilistic forecast reconciliation assigns the same probability to two sets where the points in one set are obtained by passing all points in the other set through two linear mappings.
-This is depicted schematically in Figure~\ref{fig:probfr_sch}.
+This is depicted schematically when $s\circ g$ is a projection in Figure~\ref{fig:probfr_sch}.
 
@@
 	\caption{Summary of probabilistic forecast reconciliation.
-The probability that ${\bm y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that ${\bm y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast.
+The probability that ${\bm y}_{t+h|t}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that ${\bm y}_{t+h|t}$ lies in the shaded blue area under the unreconciled probabilistic forecast.
 Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:probfr_sch}
@@
 
-We now discuss how this definition can be used in practice to obtain reconciled probabilistic forecasts for hierarchical time series.
-Recall that the case of forecast reconciliation could be broken down into three steps.
+Recall that when $s\circ g$ is a projection, the case of point forecast reconciliation could be broken down into three steps.
 In the first, $\hat{\bm{y}}_{t+h|t}$ is transformed into coordinates $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ via a change of basis.
@@
 In the third, reconciled forecasts for the entire hierarchy are recovered via $\tilde{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}$.
-We now outline these three steps for probabilistic forecasts and demonstrate how they correspond to Definition~\ref{def:reconprob}.
+We now outline the analogues to these three steps for probabilistic forecasts when predictive densities are available.
 
 While $\hat{\nu}$ is a probability measure for an $n$-vector $\hat{\bm{y}}_{t+h|t}$,  probability statements in terms of a different coordinate system can be made via an appropriate change of basis.
-Letting $f(.)$ be generic notation for a probability density functions and following the notation from our definition of point forecast reconciliation where $\hat{\bm{y}}=\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t}$ we obtain
+Letting $f(.)$ be generic notation for a probability density functions and following the notation from our definition of point forecast reconciliation where $\hat{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t}$ we obtain
 
@@
 
-After integrating out over $\tilde{\bm{a}}_{t+h|t}$, a step analogous to setting $\tilde{\bm{a}}_{t+h|t}=0$ for point forecasting, we obtain an expressions that gives the probability the reconciled bottom level series lies in the region $\mathcal{B}$.
+After integrating out over $\tilde{\bm{a}}_{t+h|t}$, a step analogous to setting $\tilde{\bm{a}}_{t+h|t}=0$ for point forecasting, we obtain an expression that gives the probability the reconciled bottom level series lies in the region $\mathcal{B}$.
 This corresponds to $\nu(\mathcal{B})$ in Definition~\ref{def:reconprob}.

### 2018-06-27 ProbabilisticCoherence.tex
Minor changes to section 5

@@
 
-Let $\bm{P}$ be a forecast distribution and let $\bm{Q}$ be the true data generating process respectively.
-Further let $\omega$ be a realization from $\bm{Q}$.
-Then a scoring rule is a function that maps $P,\omega$ to $\mathbb{R}$.
+Let $P$ be a forecast distribution and let $Q$ be the true data generating process respectively.
+Furthermore let $\omega$ be a realization from $Q$.
+Then a scoring rule is a function $S(P,\omega)$ that maps $P,\omega$ to $\mathbb{R}$.
 It is a ``proper'' scoring rule if
@@
 \end{equation}
-where $\E_{\bm{Q}}[S(\bm{P,\omega})]$ is the expected score under the true distribution $\bm{Q}$ \citep{Gneiting2008, Gneiting2014}.
-When this inequality is strict, the scoring rule is said to be strictly proper.
+where $\E_{Q}[S(P,\omega)]$ is the expected score under the true distribution $Q$ \citep{Gneiting2008, Gneiting2014}.  When this inequality is strict, the scoring rule is said to be strictly proper.
 
@@
 Although reconciliation is a valuable goal in and of itself since it can be important in aligning decision making across, for example, different units of an enterprise, in the point forecasting literature, forecast reconciliation has also been shown to improve forecast performance \todo{Some References}.
-It will be worthwhile to see whether the same holds in the probabilistic forecasting case \todo{mention energy score proof - if we get it}.
-The second motivation for using scoring rules is to compare two or more sets of reconciled probabilistic forecasts.
+It will be worthwhile to see whether the same holds in the probabilistic forecasting case.
+The second motivation for using scoring rules is to compare two or more sets of reconciled probabilistic forecasts to one another.
 The objective here is to evaluate which reconciliation mapping $g(.)$ works best in practice.
@@
 \begin{align} \label{eq:CRPS}
-\text{CRPS}(\breve{F}_i,y_{T+h,i}) &=\int \left(F_i(\breve{y}_i)-\mathbb{1}(y_i<y_{T+h,i})\right)dy_i\\ &=\E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}\E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|\,,
+\text{CRPS}(\breve{F}_i,y_{T+h,i}) &=\int \left(\breve{F}_i(\breve{y}_i)-\mathbb{1}(y_i<y_{T+h,i})\right)dy_i\\ &=\E_{\breve{Y}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}\E_{\breve{Y}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|\,,
 \end{align}
-where the expectations in the second line can be approximated by Monte Carlo.
-
-Although univariate scoring ruled have been used in the limited literature on probabilistic forecasting for hierarchies \cite{BenTaieb2017} and Jeon et al \todo{Jeon Panagiotelis and Petropoulos reference} to date, there are a number of shortcomings to this approach.
-Crucially, evaluating univariate scores on the margins do not account for the dependence in the hierarchy.
+where $\breve{Y}_i$ and $\breve{Y}^*_{T+h,i}$ are independent copies of a random variable with distribution $\breve{F}_i$ and the latter is the predictive distribution for the $i^{th}$ margin of a forecast for time $t+h$ made at time $t$.
+The expectations in the second line can be approximated by Monte Carlo when a sample from the predictive distribution is available.
+
+An advantage to this approach is that it allows the forecaster to evaluate the levels and individual series of the hierarchy where the gains to reconciliation are greatest.
+For this reason this approach has been used in the limited literature on probabilistic forecasting for hierarchies \cite{BenTaieb2017} and Jeon et al \todo{Jeon Panagiotelis and Petropoulos reference} to date.
+A major shortcomings to this approach however is that, evaluating univariate scores on the margins do not account for the dependence in the hierarchy.
 
@@
 While the a number of alternative proper scoring rules are available for univariate forecasts, the multivariate case is somewhat more limited.
-Here we focus on three cases, the log score, the energy score and the variogram score.
-These are summarised in table~\ref{table:scoringrules} summarizes a few existing proper scoring rules.
+Here we focus on three scoring rules: the log score, the energy score and the variogram score.
+These are summarized in table~\ref{table:scoringrules}.
 
@@
 The log score can be approximated using a sample of values from the probabilistic forecast density \citep{Jordan2017} however it is more commonly used when a parametric form for the density is available for the probabilistic forecast.
-So far, we have only defined probabilistic forecasts in terms of probability measures.
+So far, we have mainly defined probabilistic forecasts in terms of probability measures.
 Although densities can be obtained for both reconciled and unreconciled forecasts, the degeneracy of reconciled forecasts is problematic when using log scores.
@@
 
-Consider a rotated version of hierarchical time series $\bm{z}_t={\bm U}{\bm y}_t$ so that the first $m$ elements of $\bm{z}_t$ denoted $\bm{z}^(1)_t$ are unconstrained, while the remaining $n-m$ elements denoted $\bm{z}^(2)_t$ equal $0$ when the aggregation constraints hold.
-An example of the $n\times n$ ${\bm U}$ could be the left singular values of the matrix ${\bm S}$.
+Consider a rotated version of hierarchical time series $\bm{z}_t={\bm U}{\bm y}_t$ so that the first $m$ elements of $\bm{z}_t$ denoted $\bm{z}^{(1)}_t$ are unconstrained, while the remaining $n-m$ elements denoted $\bm{z}^{(2)}_t$ equal $0$ when the aggregation constraints hold.
+An example of the $n\times n$ ${\bm U}$ could be the matrix of left singular vectors of ${\bm S}$.
 For a non-degenerate probability measure on $\mathbb{R}^n$, the density is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^n$.
-For a coherent probability measure the density after rotation is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^m$.
-
-Consider the case where the true density is $f_1(\bm{z}^{(1)}_t)\mathbb{1}\left({\bm{z}^{(2)}_t}\right)$ , the reconciled density is identical to the true density and the unreconciled density is given by $f_1(\bm{z}^{(1)}_t)f_2(\bm{z}^{(2)}_t)$, where $f_2$ is highly concentrated around $0$ but still a proper density, for example a Gaussian with variance $\sigma^2{\bm I}$ with $\sigma^2 < (2\pi)^{-1}$.
-The log score of the reconciled density is
+%For a coherent probability measure the density after rotation is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^m$.
+
+Consider the case where the true density is $f_1(\bm{z}^{(1)}_t)\mathbb{1}\left({\bm{z}^{(2)}_t}\right)$, and is compared to an incoherent density is given by $f_1(\bm{z}^{(1)}_t)f_2(\bm{z}^{(2)}_t)$, where $f_2$ is highly concentrated around $0$ but still a proper density.
+For example $f_2$ may be Gaussian with variance $\sigma^2{\bm I}$ with $\sigma^2 < (2\pi)^{-1}$.
+The log score under the true DGP is
 $$
@@
 &= -\log f_1(\bm{z}^{(1)}_t)+\frac{n-m}{2}\log(2\pi\sigma^2)\\
-&\leq-\log f_1(\bm{z}^{(1)}_t).
+&<-\log f_1(\bm{z}^{(1)}_t).
 \end{align}
@@
 For the log score, suppose the coherent probabilistic forecast has density $f(\bm{b})$.
-The density for the full hierarchy is given by $f(\bm{y})=f(\bm{Sb})=f(\bm{b})J$ where $J=\prod_{j=1}^{m}\lambda_j^{-1}$ is the inverse of a pseudo-determinant of the non-square  matrix $X$ and $\lambda_j$ are the non-zero singular values of ${\bm S}$.
+The density for the full hierarchy is given by $f(\bm{y})=f(\bm{Sb})=f(\bm{b})J^{-1}$ where $J=\prod_{j=1}^{m}\lambda_j$ is a pseudo-determinant of the non-square  matrix ${\bm S}$ and $\lambda_j$ are the non-zero singular values of ${\bm S}$.
 Therefore for any coherent density the log score of the full hierarchy differs from the log score for the bottom level series by the term $log(J)$.
-This term depends  only on the structure of the  hierarchy and is fixed across different forecasting methods.
-Therefore if one method achieves a lower expected log score than an alternative method  when assessed using the bottom level series, the same ordering is preserved when an assessment is made on the basis of the full hierarchy.
+This term depends  only on the structure of the  hierarchy and is fixed across different reconciliation methods.
+Therefore if one method achieves a lower expected log score compared to an alternative method  when assessed using the bottom level series, the same ordering is preserved when an assessment is made on the basis of the full hierarchy.
 
 The same property does not hold for all scores in general.
-For example, energy score can be expressed in terms of an expectations of norms.
+For example, energy score can be expressed in terms of expectations of norms.
 In general, since norms are invariant under orthogonal rotations the energy score is also invariant under orthogonal transformations \citep{Szekely2013,Gneiting2007}.
@@
 In this case we recommend computing energy score using the full hierarchy.
-Although the discussion here is related to energy score, the same logic holds for other scores that are not invariant to orthogonal rotations, for example the variogram score.
-
-The properties of mutlivariate scoring rules in the context of evaluating reconciled probabilistic forecasts in Table~\ref{tab:prop}.
+Although the discussion here is related to energy score, the same logic holds for other multivariate scores that are not invariant to orthogonal rotations, for example the variogram score.
+
+The properties of multivariate scoring rules in the context of evaluating reconciled probabilistic forecasts in Table~\ref{tab:prop}.
 

### 2018-06-27 ProbabilisticCoherence.tex
Section 6 rewritten - tables still need to be updates

@@
 
-All of these forecasting methods are well-established in the context of point forecast reconciliation \citep{Hyndman2011, Hyndman2016,Wickramasuriya2017}.
+%All of these forecasting methods are well-established in the context of point forecast reconciliation \citep{Hyndman2011, Hyndman2016,Wickramasuriya2017}.
 Here, we are showing how these reconciliation methods can be used in the context of probabilistic forecast reconciliation, at least in the Gaussian framework.
@@
 We now turn our attention to comparing different reconciliation methods in a simulation study where the data is conditionally Gaussian.
-We choose the Gaussian due to its analytical tractability which allows for evaluation on the basis of all scoring rules (including the log score).
+We choose the Gaussian case due to its analytical tractability which allows for evaluation on the basis of all scoring rules (including the log score).
 The non-Gaussian case lies beyond the scope of this simulation study, but can be handled by a bootstrapping approach proposed in separate work.
@@
 
-Suppose $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from ARIMA$(p,d,q)$ processes, where $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability.
-Further, the contemporaneous errors $\{\varepsilon_{AA,t},\varepsilon_{AB,t},\varepsilon_{BA,t},\varepsilon_{BB,t}\} \sim \mathcal{N}(\bm{0}, \bm{\Sigma})$.
-The parameters for the AR and MA components will be randomly and uniformly generated from $[0.3,0.5]$ and $[0.3,0.7]$ respectively.
-Then the bottom-level series $\{y_{AA,t},y_{AB,t},y_{BA,t},y_{BB,t}\}$ will be obtained as:
+First $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from ARIMA$(p,d,q)$ processes, where $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability.
+The errors driving these ARIMA processes denoted $\varepsilon$ are jointly normal $\{\varepsilon_{AA,t},\varepsilon_{AB,t},\varepsilon_{BA,t},\varepsilon_{BB,t}\} \overset{iid}{\sim} \mathcal{N}(\bm{0}, \bm{\Sigma})~\forall t$.
+The parameters for the AR and MA components are randomly and uniformly generated from $[0.3,0.5]$ and $[0.3,0.7]$ respectively.
+Then the bottom-level series $\{y_{AA,t},y_{AB,t},y_{BA,t},y_{BB,t}\}$ are given by:
 \begin{align*}
@@
 where $u_t \sim \mathcal{N}(0,\sigma^2_u)$ and $v_t \sim \mathcal{N}(0,\sigma^2_v)$.
-To obtain the aggregate series at level 1, we add the bottom-level series:
+The aggregate series at in the middle level level, are given by:
 \begin{align*}
@@
 \end{align*}
-and the total series is obtained using
+and the total series is given by
 $$y_{Tot,t} = w_{AA,t} + w_{AB,t} + w_{BA,t} + w_{BB,t}.$$
@@
 $$
-\text{Var}(\varepsilon_{AA,t}+\varepsilon_{AB,t}+\varepsilon_{BA,t}+\varepsilon_{BB,t}) \le \text{Var}(\varepsilon_{AA,t}+\varepsilon_{AB,t}-v_t) \le \text{Var}(\varepsilon_{AA,t}+u_t-0.5v_t).
+\text{Var}(\varepsilon_{AA,t}+\varepsilon_{AB,t}+\varepsilon_{BA,t}+\varepsilon_{BB,t}) \le \text{Var}(\varepsilon_{AA,t}+\varepsilon_{AB,t}-v_t) \le \text{Var}(\varepsilon_{AA,t}+u_t-0.5v_t)\,,
 $$
-Therefore
-$$
-\bm{l}_1\bm{\Sigma} \bm{l}_1' \le \bm{l}_2\bm{\Sigma} \bm{l}_2' + \sigma^2_v \le  \bm{l}_3\bm{\Sigma} \bm{l}_3' + \sigma^2_u + \frac{1}{4}\sigma^2_v,
-$$
-where $\bm{l}_1 = (1,1,1,1)'$, $\bm{l}_2 = (1,1,0,0)'$ and $\bm{l}_3 = (1,0,0,0)'$, and hence
-$$\bm{l}_1\bm{\Sigma} \bm{l}_1' - \bm{l}_2\bm{\Sigma} \bm{l}_2' \le \sigma^2_v \le \frac{4}{3}(\sigma^2_u + \bm{l}_3\bm{\Sigma} \bm{l}_3' - \bm{l}_2\bm{\Sigma} \bm{l}_2').$$
-To satisfy these constraints, we choose
+and similar inequalities hold when $\varepsilon_{AA,t}$ is replaced by $\varepsilon_{AB,t}$, $\varepsilon_{BA,t}$ and $\varepsilon_{BB,t}$ in the second and third terms.
+%Therefore
+%$$
+%\bm{l}_1\bm{\Sigma} \bm{l}_1' \le \bm{l}_2\bm{\Sigma} \bm{l}_2' + \sigma^2_v \le  \bm{l}_3\bm{\Sigma} \bm{l}_3' + \sigma^2_u + \frac{1}{4}\sigma^2_v,
+%$$
+%where $\bm{l}_1 = (1,1,1,1)'$, $\bm{l}_2 = (1,1,0,0)'$ and $\bm{l}_3 = (1,0,0,0)'$, and hence
+%$$\bm{l}_1\bm{\Sigma} \bm{l}_1' - \bm{l}_2\bm{\Sigma} \bm{l}_2' \le \sigma^2_v \le \frac{4}{3}(\sigma^2_u + \bm{l}_3\bm{\Sigma} \bm{l}_3' - \bm{l}_2\bm{\Sigma} \bm{l}_2').$$
+The values of $\bm{\Sigma}$, $\sigma^2_u$ and $\sigma^2_v$, that we use and which satisfy these constraints are:
 $\bm{\Sigma} =
@@
 
-We generate data for the hierarchy with sample size $T=501$.
-Univariate ARIMA models were fitted for each series independently using the first 500 observations, and 1-step ahead base (incoherent) forecasts were calculated.
-We use the \textit{forecast} package \citep{hyndman2017forecasting} in R \citep{Rcore} for model fitting and forecasting.
-The different estimates of $\bm{W}_{T+1}$ and the corresponding $\bm{R}'_\bot$ from Table~\ref{table:2} were obtained.
-This process was replicated using $1000$ different data sets from the same data generating processes.
+We generate data a sample size of $T=501$.
+Univariate ARIMA models are selected for each series using the \textit{auto.arima} function in the \textit{forecast} package \citep{hyndman2017forecasting} in R \citep{Rcore}.
+The same package was used to fit each series independently using the first 500 observations, and evaluate 1-step ahead base (incoherent) probabilstic forecasts.
+These were then reconciled using different projections summarzied in Table~\ref{table:2}.
+This process was replicated using $1000$ different data sets from the same data generating processes.\todo{Are the DGPs the same in all cases?}
 
@@
 To facilitate comparisons, we report skill scores \citep{Gneiting2007}.
-For a given forecasting method, evaluated by a particular scoring rule $S(\cdot)$, the skill score is calculated as
-\begin{equation}
-Ss[S_B(\cdot)] = \frac{S_B(\bm{Y},\bm{y})^{\text{ref}} - S_B(\breve{\bm{Y}},\bm{y})}{S_B(\bm{Y},\bm{y})^{\text{ref}}}\times 100\%,
-\end{equation}
-where $S_B(\cdot)$ is the average score over $B$ samples and $S_B(\bm{Y},\bm{y})^{\text{ref}}$ is the average score for the reference forecasting method.
-Thus $Ss[S_B(\cdot)]$ gives the percentage improvement of the preferred forecasting method relative to the reference method.
-Any negative value of $Ss[S_B(\cdot)]$ indicates that the method we compared is worse than the reference method, whereas any positive value indicates that method is superior to the reference method.
-
-Table~\ref{table:3}, summarised the different reconciliation methods over the conventional bottom-up method.
-The so-called OLS method uses an orthogonal projection, while  the remaining methods consider oblique projections where ${\bm G}=\left({\bm S}'{\bm W}^{-1}{\bm S}\right)^{-1}{\bm S}'{\bm W}^{-1}$.
-In each case we calculate the percentage skill score based on energy score, log score and variogram score for each reconciliation method with reference to the bottom-up method.
-
-We also evaluate the predictive ability of coherent forecasts over incoherent forecasts in Tables~\ref{table:4} and~\ref{table:5}.
-Here we use percentage skill score based on CRPS and univariate log score for coherent probabilistic forecasts of each individual series with reference to incoherent forecasts.
-
-It is clearly evident from the results in Table~\ref{table:3} that the multivariate reconciled forecasts for the bottom-level series from MinT(Shrink) and MinT(Sample) out-perform the bottom-up forecasts.
-Further, these two methods produce probabilistic forecasts with the best predictive ability in comparison to incoherent forecasts (from Tables~\ref{table:4} and~\ref{table:5}).
-Moreover, it turns out that OLS and bottom-up methods produce the worst forecasts.
+For a given forecasting method, evaluated by a particular scoring rule $S(\cdot)$, the skill score %is calculated as
+%\begin{equation}
+%Ss[S_B(\cdot)] = \frac{S_B(\bm{Y},\bm{y})^{\text{ref}} - S_B(\breve{\bm{Y}},\bm{y})}{S_B(\bm{Y},\bm{y})^{\text{ref}}}\times 100\%,
+%\end{equation}
+%where $S_B(\cdot)$ is the average score over $B$ samples and $S_B(\bm{Y},\bm{y})^{\text{ref}}$ is the average score for the reference forecasting method. Thus $Ss[S_B(\cdot)]$ 
+gives the percentage improvement of the preferred forecasting method relative to a reference method.
+A negative valued skill score indicates that a method is worse than the reference method, whereas any positive value indicates that method is superior to the reference method.
+
+Table~\ref{table:3} summarizes the forecasting performance of unreconciled, bottom-up, OLS, WLS and two MinT reconciliation methods using log score, energy score and variogram score.
+In all cases skill scores are calculated with the bottom-up method as reference.
+All log scores are evaluated on the basis of bottom level series only, however these only differ from the log scores for the full hierarchy by a fixed constant.
+The cell for log score of unreconciled forecasts is left blank since the log score is not proper in this context.
+Overall, the MinT methods provide the best performance irrespective of the scoring rule, and all methods that reconcile using information at all levels of the forecast improve upon unreconciled forecasts.
+Bottom up forecasts perform even worse than unreconciled forecasts.
+
+Tables~\ref{table:4} and~\ref{table:5} break down the forecasting performance of different reconciliation methods by considering univariate scores on each individual margin.
+The log score and CRPS are considered while skill scores are computed with the unreconciled forecast as a reference.
+When broken down in this fashion, the methods based on MinT perform best for all series and always outperform bottom up and unreconciled forecasts.
+The same cannot be said for OLS which performs worse than bottom up and incoherent forecasts on every individual series\todo{Puzzling it does so bad, but outperforms unreconciled on joint evaluation}.
 

### 2018-06-28 ProbabilisticCoherence.tex
Changes to Section 4.3 - still incomplete

@@
 \subsection{Elliptical Distributions}
-We now show that if the mapping $g(.)$ in definition $\ref{def:reconpoint}$ is extended to allow for a translation by ${\bm d}$, i.e.
-$g({\bm y})={\bm G}{\bm y}+{\bm d}$, then the true predictive distribution can be recovered for elliptical distributions.
+We now show that the true predictive distribution can be recovered for elliptical distributions via linear reconciliation.
 Here, for any square matrix ${\bm C}$, ${\bm C}^{1/2}$ and ${\bm C}^{-1/2}$ are defined to satisfy ${\bm C}^{1/2}\left({\bm C}^{1/2}\right)'={\bm C}$ and ${\bm C}^{-1/2}\left({\bm C}^{-1/2}\right)'={\bm C}^{-1}$, for example ${\bm C}^{1/2}$ may be obtained via the Cholesky or eigenvalue decompositions.
@@
 Let the true predictive distribution of ${\bm y}_{t+h|t}$ also belong to the elliptical class with location parameter ${\bm \mu}$ and scale matrix ${\bm \Sigma}$.
-Then the affine reconciliation mapping $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ with $\bm{G}_{opt}={\bm\Omega}^{1/2}{\bm\Sigma}^{-1/2}$ and ${\bm d}_{opt}={\bm S}{\bm G}_{opt}\left({\bm \mu}-\hat{\bm \mu}\right)$ recovers the true predictive density, where $\bm\Omega$ is the true variance covariance matrix of the predictive distribution for the bottom level.
+Then the affine reconciliation mapping $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ with $\bm{G}_{opt}={\bm A}{\bm\Sigma}^{-1/2}$ and ${\bm d}_{opt}={\bm \mu}-{\bm S}{\bm G}_{opt}\hat{\bm \mu}$ recovers the true predictive density where ${\bm A}$ is any $m\times n$ matrix such that ${\bm A}{\bm A}'={\bm \Omega}$ and ${\bm \Omega}$ is the true variance covariance matrix of the predictive distribution for the bottom level.
 \end{theo}
@@
    \begin{align*}
-   \tilde{\bm \Sigma}_{opt}=&{\bm S}{\bm\Omega}^{1/2}{\bm\Sigma}^{-1/2}{\bm \Sigma}{\bm\Sigma}^{-1/2}{\bm\Omega}^{1/2}{\bm S}'\\
+   \tilde{\bm \Sigma}_{opt}=&{\bm S}{\bm A}{\bm\Sigma}^{-1/2}{\bm \Sigma}\left({\bm\Sigma}^{-1/2}\right)'{\bm A}'{\bm S}'\\
    =&{\bm S}{\bm \Omega}{\bm S}'\\
@@
    \end{align*}
-   For the choices of ${\bf G}_{opt}$ and ${\bf d}_{opt}$ given above, the reconciled location matrix is 
+   For the choices of ${\bf G}_{opt}$ and ${\bf d}_{opt}$ given above, the reconciled location vector is 
    \begin{align*}
-   \tilde{\bm \mu}_{opt}=&{\bm S}{\bm G}_{opt}\hat{\bm \mu}+{\bm S}{\bm G}_{opt}\left({\bm \mu}-\hat{\bm \mu}\right)\\
-   =&{\bm S}{\bm G}_{opt}\hat{\bm \mu}-{\bm S}{\bm G}_{opt}\hat{\bm \mu}+{\bm S}{\bm G}_{opt}{\bm \mu}\\
-   =&{\bm S}{\bm G}_{opt}{\bm \mu}\\
+   \tilde{\bm \mu}_{opt}=&{\bm S}{\bm G}_{opt}\hat{\bm \mu}+{\bm \mu}-{\bm S}{\bm G}_{opt}\hat{\bm \mu}\\
    =&{\bm \mu}\\
    \end{align*}
-   The final equality above holds since ${\bm S}{\bm G}_{opt}$ projects any vector onto the coherent subspace, however since ${\bm \mu}$ is the mean of the true data generating process, it must already lie on the coherent subspace and ${\bm S}{\bm G}_{opt}{\bm \mu}={\bm \mu}$.
 \end{proof}	
-It should be noted that ${\bm G}_{opt}$ and ${\bm d}_{opt}$ depend on the true location and scale of the predictive distribution and are thus infeasible in practice.
-However, these expressions do provide some insight on why some choices for ${\bm G}$ in the point forecast reconciliation literature may also work well for probabilistic forecasts.
+A number of insights can be drawn from this theorem.
+First, although a linear mapping $g(.)$ can be used to recover the true density in the elliptical case, the same does not hold in general.
+Second, $g(.)$ is not, in general, a projection matrix.
+Third, ${\bm G}_{opt}$ and ${\bm d}_{opt}$ depend on the true location and scale of the predictive distribution and are thus infeasible in practice.
+
+\todo{Some discussion about why projections are good}.
+
+%However, these expressions do provide some insight on why some choices for ${\bm G}$ in the point forecast reconciliation literature may also work well for probabilistic forecasts.
 To illustrate, first rearrange the equation for the optimal value of  $\bm{G}_{opt}={\bm\Omega}^{1/2}\hat{\bm\Sigma}^{-1/2}$ as ${\bm\Omega}^{1/2}=\bm{G}_{opt}\hat{\bm\Sigma}^{1/2}$.

### 2018-06-29 ProbabilisticCoherence.tex
New tables of results (with seed saved)

@@
 \begin{table}
-  \caption{Comparison of incoherent forecasts using bottom-level series.
-The ``Skill score'' columns give the percentage skill score with reference to the bottom-up forecasting method.
-Entries in these columns show the percentage increase of score for different reconciliation methods relative to the bottom-up method.}\label{table:3}
+	\caption{Comparison of coherent forecasts.
+``Energy score'' and ``Variogram score'' columns give scores based on the joint forecast distribution of whole hierarchy.
+``Log score'' column gives the log scores of the joint forecast distribution of bottom level.
+``Skill score'' columns give the percentage skill score with reference to the bottom-up method.
+Entries in these columns show the percentage increase of score for different reconciliation methods relative to the bottom-up method.
+}\label{table:3}
+
 	\centering\small
@@
 		\multicolumn{2}{c}{\text{Energy score}} &
-    \multicolumn{2}{c}{\text{Log score}} &
-    \multicolumn{2}{c}{\text{Variogram score}} \\
+		\multicolumn{2}{c}{\text{Variogram score}} &
+		\multicolumn{2}{c}{\text{Log score}} \\
 		\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(l){6-7}
 		method &
-    \text{Mean score} & \text{Skill score} &
-    \text{Mean score} & \text{Skill score} &
-    \text{Mean score} & \text{Skill score}\\
+		\text{Mean score} & \text{Skill score \%} &
+		\text{Mean score} & \text{Skill score \%} &
+		\text{Mean score} & \text{Skill score \%}\\
 		\midrule
-    MinT(Shrink) &  7.47 &  10.11 &  11.34 &     6.44 & 3.05 &   4.69 \\
-    MinT(Sample) &  7.47 &  10.11 &  11.33 &     6.52 & 3.05 &   4.69 \\
-    MinT(WLS)    &  7.91 &   4.81 &  12.64 &    -4.29 & 3.23 &  -0.94 \\
-    OLS          & 10.14 & -22.02 & 135.13 & -1014.93 & 4.60 & -43.75 \\
-    Bottom-up    &  8.31 &        &  12.12 &          & 3.20 &        \\
+		MinT(Shrink) &  10.03 & 18.79  & 8.44  & 8.46 & 11.30 &  6.22 \\
+		MinT(Sample) &  10.01 & 18.95  & 8.41  & 8.79 & 11.29 &  6.31 \\
+		MinT(WLS)    &  10.53 & 14.74  & 9.02  & 2.17 & 12.61 & -4.65 \\
+		OLS          &  10.53 & 14.74  & 8.86  & 3.09 & 11.54 &  4.23\\
+		Bottom-up    &  12.35 &    	   & 9.22  &      & 12.05 &  \\
+		Incoherent	 &  11.12 &   	   & 9.53  &      &       &  \\
 		\bottomrule
@@
 \begin{table}
-  \caption{Comparison of incoherent vs coherent forecasts for the aggregate series using Skill scores.
+	\caption{Comparison of incoherent vs coherent forecasts based on the univariate forecast distribution of aggregate series.
 The ``Incoherent'' row shows the average scores for incoherent forecasts.
 Each entry above this row represents the percentage skill score with reference to the incoherent forecasts.
-Entries show the percentage increase in score for different forecasting methods relative to the incoherent forecasts.}\label{table:4}
+These entries show the percentage increase in score for different forecasting methods relative to the incoherent forecasts.}\label{table:4}
 	\centering\small
@@
 		\midrule
-    MinT(Shrink) & 1.12   & 0.34    & 10.07  & 2.93     & 5.41   & 1.52     \\
-    MinT(Sample) & 1.12   & 0.34    & 10.07  & 2.93     & 5.41   & 1.52     \\
-    MinT(WLS)    & -2.61  & -2.02   & 5.28   & -4.40    & 2.70   & -4.24    \\
-    OLS          & -38.06 & -698.99 & -24.70 & -1368.33 & -24.86 & -1159.09 \\
-    Bottom-up    & -89.55 & -21.83  & -8.87  & -2.35    & -9.46  & -2.73    \\
+		MinT(Shrink) &   0.74  &   0.00   & 10.49   &  3.24  &  9.16  &  2.73    \\
+		MinT(Sample) &   0.74  &   0.00   & 10.49   &  3.24  &  9.16  &  2.73    \\
+		MinT(WLS)    &  -2.96  &  -2.36   &  6.10   & -4.12  &  5.66  & -3.03    \\
+		OLS          &  -9.26  &  -3.36   &  7.07   &  2.06  &  7.01  &  1.82    \\
+		Bottom-up    & -91.48  & -22.22   & -8.05   & -2.06  & -6.20  & -1.82    \\
 		\midrule
-    \textit{Incoherent} & $\mathbi{2.68}$ & $\mathbi{2.97}$ & $\mathbi{4.17}$ & $\mathbi{3.41}$ & $\mathbi{3.70}$ & $\mathbi{3.30}$ \\
+		\textit{Incoherent} & $\mathbi{2.70}$ & $\mathbi{2.97}$ & $\mathbi{4.10}$ & $\mathbi{3.40}$ & $\mathbi{3.71}$ & $\mathbi{3.30}$ \\
 		\bottomrule
@@
 \begin{table}
-  \caption{Comparison of incoherent vs coherent forecasts for the individual bottom-level series using Skill scores.}\label{table:5}
+	\caption{Comparison of incoherent vs coherent forecasts based univariate forecast distribution of bottom-level series.
+The ``Incoherent'' row shows the average scores for incoherent forecasts.}\label{table:5}
 	\centering\tabcolsep=0.08cm\small
@@
 		\midrule
-    MinT(Shrink) & 8.71   & 2.71    & 10.57  & 3.04    & 5.95   & 1.86    & 7.91   & 2.46 \\
-    MinT(Sample) & 8.71   & 2.71    & 10.57  & 3.04    & 5.95   & 1.86    & 8.19   & 2.46 \\
-    MinT(WLS)    & 5.54   & 0.30    & 5.96   & 0.30    & 2.43   & -0.62   & 5.08   & 0.62 \\
-    OLS          & -22.43 & -931.63 & -22.49 & -886.32 & -26.01 & -834.67 & -23.45 & -812.92 \\
+		MinT(Shrink) &  7.61  &  2.43  &  10.82  &  3.02  &  5.93  &  1.86  &  7.76  & 2.47  \\
+		MinT(Sample) &  7.88  &  2.43  &  11.08  &  3.02  &  6.20  &  1.86  &  8.05  & 2.47  \\
+		MinT(WLS)    &  3.53  &  0.00  &   6.33  &  0.60  &  2.43  & -0.62  &  4.89  & 0.62  \\
+		OLS          &  2.99  &  0.91  &   5.28  &  1.51  &  2.90  &  0.62  &  4.31  & 1.23  \\
 		\midrule
-    \textit{Incoherent} & $\mathbi{3.79}$ & $\mathbi{3.32}$ & $\mathbi{3.69}$ & $\mathbi{3.29}$ & $\mathbi{3.46}$ & $\mathbi{3.23}$ & $\mathbi{3.54}$ & $\mathbi{3.25}$ \\
+		\textit{Incoherent} & $\mathbi{3.68}$ & $\mathbi{3.29}$ & $\mathbi{3.79}$ & $\mathbi{3.31}$ & $\mathbi{3.45}$ & $\mathbi{3.22}$ & $\mathbi{3.48}$ & $\mathbi{3.24}$ \\
 		\bottomrule

### 2018-06-30 ProbabilisticCoherence.tex
Added new theorems for point forecasting case

@@
 
-Many choices of $g(.)$ currently extant in the literature including the OLS, WLS and MinT methods are such that $s\circ g$ is a projection.
-To define these more generally and provide geometric intuition, we introduce an $n \times (n-m)$ matrix $\bm{R}$ whose columns span the null space of $\mathfrak{s}_{\perp}$.
+Many choices of $g(.)$ currently extant in the literature including the so called OLS \cite{Hyndman2011}, WLS \todo{First WLS  reference?} and MinT\cite{Wickramasuriya2017} methods are special cases where $s\circ g$ is a projection and are summarised in Table~\ref{table:2}.
+These can be defined so that ${\bm G}=\left({\bm R'_{\perp}}{\bm S}\right)^{-1}{\bm S}'$ and ${\bm d}={\bm 0}$.
+Here, ${\bm R_{\perp}}$ is a $n\times m$ orthogonal complement to the an $n \times (n-m)$ matrix $\bm{R}$ where the columns of the latter span the null space of $\mathfrak{s}_{\perp}$.
 For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
 In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
-In general, the columns of any given $\bm{R}$ matrix can also be thought of as `directions' along which incoherent point forecasts are projected onto the coherent space, and these directions need not be orthogonal to $\mathfrak{s}$.
-Projections are special cases of Definition~\ref{def:reconpoint} where ${\bm d=0}$ and ${\bm G}$ has the form $\left({\bm R}_\perp'{S}\right)^{-1}{\bm R}_\perp'$ where ${\bm R}_\perp$ is the $n\times m$ orthogonal complement of ${\bm R}$.
-In the example provided, ${\bm R}_\perp'={\bm S}$ and reconciliation corresponds to the so called `OLS' method \cite{Hyndman2011}.
-A schematic providing a geometric interpretation is given in Figure~\ref{fig:pointfr_sch}.
+For the example provided, ${\bm R}_\perp'={\bm S}$ and reconciliation corresponds to the so called `OLS' method \cite{Hyndman2011}.
+For the case where ${\bm R}_\perp'\neq{\bm S}$, for example WLS and MinT, there are two possible interpretations.
+One is that these are oblique projections in Euclidean space where the columns of $\bm{R}$ are `directions' along which incoherent point forecasts are projected onto the coherent space $\mathfrak{s}$.
+Alternatively, since ${\bm R}_\perp'$ is usually written in the form ${\bm S}'{\bm W}^{-1}$, these projections can be thought of as orthogonal projections after applying the transformation ${\bm W^{-1/2}}$.
+A schematic providing a geometric interpretation of point reconciliation is given in Figure~\ref{fig:pointfr_sch}.
+
+\begin{table}
+	\caption{Several possible estimates of $\bm{R}'_\bot$.
+For $n<T$, $\bm{\hat{W}}_{T+1}^{sam}$ is an unbiased and consistent estimator for $\bm{W}_{T+1}$.
+$\bm{\hat{W}}_{T+1}^{shr}$ is a shrinkage estimator which is more suitable for large dimensions.
+$\bm{\hat{W}}_{T+1}^{shr}$ was proposed by \citet{Schafer2005} and also used by \citet{Wickramasuriya2017}, where Diag($\bm{A}$) denotes the diagonal matrix of $\bm{A}$, $\tau = \frac{\sum_{i \ne j}\hat{\text{Var}}(\hat{r}_{ij})}{\sum_{i \ne j}\hat{r}_{ij}^2}$, and $\hat{r}_{ij}$ is the $ij$th element of the sample correlation matrix.}\label{table:2}
+	\centering\setstretch{1.5}
+	\begin{tabular}{lll}
+		\toprule
+		\textbf{Method} & \textbf{Estimate of $\bm{W}_{h}$} & \textbf{Estimate of $\bm{R}'_\bot$}      \\
+		\midrule
+		OLS             &
+		$\bm{I}$  &
+		$\bm{S}'$  \\
+		MinT(Sample)    &
+		$\bm{\hat{W}}_{T+1}^{sam}$ &
+		$\bm{S}'(\bm{\hat{W}}_{T+1}^{sam})^{-1}$ \\
+		MinT(Shrink)    &
+		$\bm{\hat{W}}_{T+1}^{shr} = \tau\text{Diag}(\bm{\hat{W}}_{T+1}^{sam}) + (1-\tau)\bm{\hat{W}}_{T+1}^{sam}$ &
+		$\bm{S}'(\bm{\hat{W}}_{T+1}^{shr})^{-1}$ \\
+		WLS       &
+		$\bm{\hat{W}}_{T+1}^{wls} = \text{Diag}(\bm{\hat{W}}_{T+1}^{shr})$ &
+		$\bm{S}'(\bm{\hat{W}}_{T+1}^{wls})^{-1}$ \\
+		\bottomrule
+	\end{tabular}
+\end{table}
 
@@
 
+Before generalising the concept of point reconciliation to probabilistic forecasts we state two theorems that motivate the use of projections for point forecast reconciliation.
+First, let ${\bm \mu}_{t+h|t}:=E({\bm y}_{t+h}|{\bm y}_{1},\dots,{\bm y}_{t})$ and assume $\hat{\bm y}_{t+h|t}$ is an unbiased prediction, that is $E_{1:t}\left(\hat{\bm y}_{t+h|t}\right)=\mu_{t+h|t}$ where the subscript $1:t$ denotes an expectation taken over the training sample.
+
+\begin{theo}[Unbiasedness preserving property]
+  The reconciled point forecast will also be an unbiased prediction as long as $s\circ g$ is a projection 
+\end{theo}
+\begin{proof}
+	The expected value of the reconciled forecast is given by
+	\begin{align*}
+	E_{1:t}\left(\tilde{\bm y}_{t+h|t}\right)&=E_{1:t}\left({\bm S}{\bm G}\hat{\bm y}_{t+h|t}\right)\\
+	&={\bm S}{\bm G}E_{1:t}\left(\hat{\bm y}_{t+h|t}\right)\\
+    &={\bm S}{\bm G}{\bm \mu}_{t+h|t}\\
+	\end{align*}
+	Since the aggregation constraints hold for the true data generating process ${\bm \mu}_{t+h|t}$ must lie in $\mathfrak{s}$.
+If ${\bm S}{\bm G}$ is a projection then it is equivalent to the identity map for all vectors that lie in its range.
+Therefore ${\bm S}{\bm G}{\bm \mu}_{t+h|t}={\bm \mu}_{t+h|t}$ when ${\bm S}{\bm G}$ is a projection matrix.
+\end{proof}
+We note the same result does not hold for general ${\bm G}$ even though the range of $s\circ g$ is $\mathfrak{s}$.
+Now let ${\bm y}_{t+h}$ be the realisation of the data generating process at time $t+h$ and let $||{\bm v}||_2$ be the L2 norm of vector ${\bm v}$.
+The following theorem shows that reconciliation never increases, and in most cases reduces the sum of squared errors of point forecasts.
+
+\begin{theo}[Distance reducing property]
+	If $\tilde{\bm y}_{t+h|t}={\bm S}{\bm G}\hat{\bm y}_{t+h|t}$ where ${\bm G}$ is such that ${\bm S}{\bm G}$ is an orthogonal projection then the following inequality holds
+	  \begin{equation}
+	    ||(\tilde{\bm y}_{t+h|t}-{\bm y}_{t+h})||^2_2\le||(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||^2_2
+	  \end{equation}
+\end{theo}
+\begin{proof}
+	Since the aggregation constraints must hold for all realisations, ${\bm y}_{t+h}\in\frak{s}$ and ${\bm y}_{t+h}={\bm S}{\bm G}{\bm y}_{t+h}$ whenever ${\bm S}{\bm G}$ is a projection.  Therefore 
+	\begin{align}
+	||(\tilde{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2&=||({\bm S}{\bm G}\hat{\bm y}_{t+h|t}-{\bm S}{\bm G}{\bm y}_{t+h})||_2\\
+	&=||{\bm S}{\bm G}(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2\\
+	\end{align}
+	The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators\todo{Find reference or prove}, therefore
+	 \begin{equation*}
+	 ||{\bm S}{\bm G}(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2\le
+	 ||(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2
+	 \end{equation*}
+\end{proof}
+The inequality is strict whenever $\hat{\bm y}_{t+h|t}\notin\mathfrak{s}$.
+
 \subsection{Probabilistic forecast reconciliation}
@@
 
-  Let $(\mathbb{R}^n, \mathscr{F}^{\mathbb{R}^n}, \hat{\nu})$ be an probability triple, that is incoherent and that characterises forecast uncertainty for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.
+  Let $(\mathbb{R}^n, \mathscr{F}_{\mathbb{R}^n}, \hat{\nu})$ be an probability triple, that is incoherent and that characterises forecast uncertainty for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.
 This may be obtained from the first stage of the forecasting process e.g.
@@
 Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear mapping.
-Let $(\mathbb{R}^m, \mathscr{F}^{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$.
+Let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$.
   \begin{definition} \label{def:reconprob}
@@
   \begin{equation}
-  \tilde{\nu}(s(\mathcal{B})) = \nu(\mathcal{B})= \hat{\nu}(g^{-1}(\mathcal{B})) \qquad \forall \mathcal{B} \in \mathscr{F}^{\mathbb{R}^m}\,,
+  \tilde{\nu}(s(\mathcal{B})) = \nu(\mathcal{B})= \hat{\nu}(g^{-1}(\mathcal{B})) \qquad \forall \mathcal{B} \in \mathscr{F}_{\mathbb{R}^m}\,,
   \end{equation}
@@
 & =
-\left(\bt-(\bm{S} ~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\right)' \Big[(\bm{S}  \bm{R})\bm{\hat{\Sigma}_{t+h}}(\bm{S} ~ \bm{R})'\Big]^{-1}
+\left(\bt-(\bm{S} ~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\right)' \Big[(\bm{S}  \bm{R})^{-1}\bm{\hat{\Sigma}_{t+h}}\left((\bm{S} ~ \bm{R})^{-1}\right)'\Big]^{-1}
 \left(\bt-(\bm{S} ~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\right)\,.
@@
 As such it may seem sensible to compare unreconciled densities to reconciled densities on the basis of log score.
-However more careful consideration shows that using the log score may fail in the case of multivariate distributions with a degeneracy.
-
+The following theorem shows that using the log score may fail in the case of multivariate distributions with a degeneracy.
+
+\begin{theo}[Impropriety of log score]
+	When the true data generating process is a coherent measure, then the log score is improper with respect to the class of incoherent measures.
+\end{theo}
+\begin{proof}
 Consider a rotated version of hierarchical time series $\bm{z}_t={\bm U}{\bm y}_t$ so that the first $m$ elements of $\bm{z}_t$ denoted $\bm{z}^{(1)}_t$ are unconstrained, while the remaining $n-m$ elements denoted $\bm{z}^{(2)}_t$ equal $0$ when the aggregation constraints hold.
@@
 After taking expectations $ES(f,f) > ES(\hat{f},f)$, violating the condition \eqref{eq:(3.1.)} for a proper scoring rule.  
+\end{proof}
+
 A similar issue also arises when discrete random variables are modelled as if they were continuous, an issue discussed in Section 4.1, page 366 of \cite{Gneiting2007}.
@@
 %
-\begin{table}
-  \caption{Several possible estimates of $\bm{R}'_\bot$.
-For $n<T$, $\bm{\hat{W}}_{T+1}^{sam}$ is an unbiased and consistent estimator for $\bm{W}_{T+1}$.
-$\bm{\hat{W}}_{T+1}^{shr}$ is a shrinkage estimator which is more suitable for large dimensions.
-$\bm{\hat{W}}_{T+1}^{shr}$ was proposed by \citet{Schafer2005} and also used by \citet{Wickramasuriya2017}, where Diag($\bm{A}$) denotes the diagonal matrix of $\bm{A}$, $\tau = \frac{\sum_{i \ne j}\hat{\text{Var}}(\hat{r}_{ij})}{\sum_{i \ne j}\hat{r}_{ij}^2}$, and $\hat{r}_{ij}$ is the $ij$th element of the sample correlation matrix.}\label{table:2}
-  \centering\setstretch{1.5}
-  \begin{tabular}{lll}
-    \toprule
-    \textbf{Method} & \textbf{Estimate of $\bm{W}_{h}$} & \textbf{Estimate of $\bm{R}'_\bot$}      \\
-    \midrule
-    OLS             &
-    $\bm{I}$  &
-    $\bm{S}'$  \\
-    MinT(Sample)    &
-    $\bm{\hat{W}}_{T+1}^{sam}$ &
-    $\bm{S}'(\bm{\hat{W}}_{T+1}^{sam})^{-1}$ \\
-    MinT(Shrink)    &
-    $\bm{\hat{W}}_{T+1}^{shr} = \tau\text{Diag}(\bm{\hat{W}}_{T+1}^{sam}) + (1-\tau)\bm{\hat{W}}_{T+1}^{sam}$ &
-    $\bm{S}'(\bm{\hat{W}}_{T+1}^{shr})^{-1}$ \\
-    MinT(WLS)       &
-    $\bm{\hat{W}}_{T+1}^{wls} = \text{Diag}(\bm{\hat{W}}_{T+1}^{shr})$ &
-    $\bm{S}'(\bm{\hat{W}}_{T+1}^{wls})^{-1}$ \\
-    \bottomrule
-  \end{tabular}
-\end{table}
 

### 2018-07-01 ProbabilisticCoherence.tex
Discussion of why MinT works added

@@
 Second, $g(.)$ is not, in general, a projection matrix.
-Third, ${\bm G}_{opt}$ and ${\bm d}_{opt}$ depend on the true location and scale of the predictive distribution and are thus infeasible in practice.
-
-\todo{Some discussion about why projections are good}.
+The conditions for which a the true predictive density can be recovered by reconciliation are given below.
+
+\begin{theo}[True predictive via projection]
+	Assume that the true predictive distribution is elliptical with location ${\bm mu}$ and scale ${\bm Sigma}$.
+Consider reconciliation via a projection $g({\bm y})=({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}{\bm y}$
+	The true predictive distribution can be recovered via reconciliation of an elliptical distribution with location $\hat{\bm \mu}$ $\hat{\bm \Sigma}$ and scale when the following conditions hold.
+	\begin{align}
+	sp(\hat{\bm\mu}-{\bm \mu})&\subset sp(\bm{R})\\
+    sp(\bm{\Sigma}^{1/2}-{\bm \Sigma}^{1/2})&\subset sp({\bm R})\\
+	\end{align}
+\end{theo}
+\begin{proof}
+	The reconciled location vector will be given by
+	\begin{align*}
+		\tilde{\bm \mu}&={\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}\hat{\bm \mu}\\
+		&={\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}\left(\hat{\bm \mu}+{\bm \mu}-{\bm \mu}\right)\\
+		&={\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}{\bm \mu}+{\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}\left(\hat{\bm \mu}-{\bm \mu}\right)\\
+	\end{align*}
+  Since ${\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}$ is a projection onto $\mathfrak{s}$ and ${\bm \mu}\in\mathfrak{s}$ the first term simplified to ${\bm \mu}$.
+If ${\bm \mu}-\hat{\bm \mu}$ lies in the span of ${\bm R}$ then multiplication by ${\bm R}'_{\perp}$ reduced the second term to ${\bm 0}$.
+By a similar argument it can be shown that $\tilde{\bm \Sigma}^{1/2}={\bm \Sigma}^{1/2}$.
+The closure property of elliptical distributions under affine transformations ensures that the full true predictive distribution can be recovered.
+\end{proof}  
+Although these conditions will rarely hold in practice and only apply to a limited class of distributions they do provide some insight into selecting a projection for reconciliation.
+If the value of $\hat{\bm \mu}$ were equi-probable in all directions then a projection orthogonal to $\mathfrak{s}$ would be a sensible choice for ${\bm R}$ since it would in some sense represent a `median' direction for ${\bm \mu}-\hat{\bm \mu}$.
+However, the one step ahead in-sample errors are usually correlated suggesting that $\hat{\bm \mu}$ is more likely to fall in some directions than others.
+As such an orthogonal projection after transformation by the inverse of the one step ahead in-sample errors may be more intuitively appealing.
+This is exactly what the MinT projection estimates, and as simulations will show in Section~\ref{sec:gaussian}, this projection leads to the best empirical results.
 

### 2018-07-02 ProbabilisticCoherence.tex
Sketch intro and conclusion added

@@
 \section{Introduction}\label{sec:intro}
+Sketch narrative to tell
+\begin{itemize}
+	\item Coherence is important in point forecasting to
+	\begin{itemize}
+		\item Align decisions
+		\item Improve forecasts
+	\end{itemize}
+	\item We propose a geometric interpretation via linear transformations including special case of projections.
+	\item These nest existing methods but the interpretation has advantages 
+	\begin{itemize}
+		\item Prove that projections preserve unbiasedness.  Previously assumed in special cases.
+		\item Prove reconciliation (using projection) always improves sum of squared errors (or a scaled/transformed version thereof).
+		\item Most importantly generalises to probabilistic forecasting.
+	\end{itemize}
+    \item For elliptical distributions, true predictive can be recovered via linear reconciliation and in special cases, via projection.
+    \item Discuss evaluation of forecasts
+    \begin{itemize}
+    	\item Log score improper when coherent v incoherent
+    	\item Energy score cn be used instead
+    	\item Discuss scores for coherent v coherent.
+    \end{itemize}
+    \item Finally evidence MinT is best from simulation
+\end{itemize}
 
@@
 
+Points to discuss
+\begin{itemize}
+	\item Optimal reconciliation likely to depend on
+	\begin{itemize}
+		\item Properties of base probabilstic forecast
+		\item Scoring rule
+	\end{itemize}
+    \item Case where no parametric form available
+    \item Cases where $g$ and maybe even $s$ are non linear
+\end{itemize}
+
 Although the problem of hierarchical point forecasts is well studied in the literature, there is a lack of attention in the context of probabilistic forecasts.

### 2018-07-03 ProbabilisticCoherence.tex
Introduction written

--- 2018-07-01 ProbabilisticCoherence.tex
@@
 
-\section{Introduction}\label{sec:intro}
-
-Many research applications involve a large collection of time series, some of which are aggregates of others.
-These are called hierarchical time series.
-For example, electricity demand of a country can be disaggregated along a geographical hierarchy: the electricity demand of the whole country can be divided into the demand of states, cities, and households.
-
-When forecasting such time series, it is important to have ``coherent'' forecasts across the hierarchy: aggregates of the forecasts at lower levels should be equal to the forecasts at the upper levels of aggregation.
-In other words, sums of forecasts should be equal to the forecasts of the sums.
-
-The traditional approaches to produce coherent point forecasts are the bottom-up, top-down and middle-out methods.
-In the bottom-up approach, forecasts of the lowest level are first generated and they are simply aggregated to forecast upper levels of the hierarchy \citep{Dunn1976}.
+%
+%\section{Introduction}\label{sec:intro}
+%Sketch narrative to tell
+%\begin{itemize}
+%	\item Coherence is important in point forecasting to
+%	\begin{itemize}
+%		\item Align decisions
+%		\item Improve forecasts
+%	\end{itemize}
+%	\item We propose a geometric interpretation via linear transformations including special case of projections.
+%	\item These nest existing methods but the interpretation has advantages 
+%	\begin{itemize}
+%		\item Prove that projections preserve unbiasedness.  Previously assumed in special cases.
+%		\item Prove reconciliation (using projection) always improves sum of squared errors (or a scaled/transformed version thereof).
+%		\item Most importantly generalises to probabilistic forecasting.
+%	\end{itemize}
+%    \item For elliptical distributions, true predictive can be recovered via linear reconciliation and in special cases, via projection.
+%    \item Discuss evaluation of forecasts
+%    \begin{itemize}
+%    	\item Log score improper when coherent v incoherent
+%    	\item Energy score cn be used instead
+%    	\item Discuss scores for coherent v coherent.
+%    \end{itemize}
+%    \item Finally evidence MinT is best from simulation
+%\end{itemize}
+
+Large collections of time series often follow some aggregation structure.
+For example, the electricity demand of a country can be disaggregated according to a geographical hierarchy of states, cities, and individual households or according to temporal hierarchy of yearly, quarterly and monthly demand.
+In these so-called hierarchical time series, forecasts are often required for all individual series.
+To ensure aligned decision making it is important for forecasts at the most disaggregated - or bottom-level - to add up to forecasts at more aggregated - or higher - levels.
+This property is referred to as ``coherence''.
+
+Traditional approaches to ensure coherent point forecasts produce forecasts at a single level.
+For instance in the bottom-up \citep{Dunn1976} approach, forecasts are produced at the most disaggregated level and then summed to recover top level-series.
+Alternatively, in the top-down approach \citep{Gross1990} a top-level forecast is produced and bottom level forecasts are recovered as  historical or forecasted proportions of the top-level forecast,while the middle-out approach is a hybrid between these two.
+
+In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular.
+These methods produce first stage, or  so called `base' forecasts independently for each series.
+Since base are rarely coherent in practice,  they are subsequently adjusted  or `reconciled' to ensure coherence.
+To  date reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling least squares estimators.
+These include Ordinary Least Squares {OLS} \cite{Hyndman2011}, Weighted Least Squares {WLS} \todo{citation?} and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017}, more commonly referred to as MinT since it minimises the trace of  the squared error matrix.
+These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and in some sense hedge against the risk of model misspecification error in a single level.
+
+A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \cite[see][and references therein]{Gneiting2014}.
+Indeed to the best of our knowledge, the as yet unpublished work of \cite{BenTaieb2017} is the only paper to deal with the issue of coherent probabilistic forecasts, and although the means of the predictive distributions are reconciled, the overall distributions are constructed in a bottom up fashion.
+In contrast, the main objective of our paper is to generalise point forecast reconciliation to probabilistic forecast reconciliation.
+
+To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we  first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections.
+In addition to being highly intuitive, this allows us to establish a number of theoretical results.
+We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts while the second shows that reconciled forecasts dominate unreconciled forecasts since projections are bounded operators.
+We provide definitions of coherence and forecast reconciliation in the probabilistic setting and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation.
+We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class.
+We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly esitimated in practice, our  theoretical results lead to a heuristic argument in favour of MinT reconciliation.
+
+We also cover the issue of forecast evaluation of probabilistic forecasts via scoring rules.
+In particular we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.
+As such we recommend the use of the energy score and variogram score for comparing reconciled to unreconciled forecasts.
+Two or more reconciled forecasts can be compared using log score,energy score and  variogram score, although we show that comparisons should be  made on the full hierarchy for the latter two scores.
+
+The remainder of the papers is  structured as follows.
+In Section~\ref{sec:notation}, hierarchical time series are discussed in general and notation is  defined.
+In section \ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.
+Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results.
+In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian},  Section~\ref{sec:conclusions} concludes.
+
+%In the bottom-up approach, forecasts of the lowest level are first generated and they are simply aggregated to forecast upper levels of the hierarchy \citep{Dunn1976}.
 In contrast, the top-down approach involves forecasting the most aggregated series first and then disaggregating these forecasts down the hierarchy based on the corresponding proportions of observed data \citep{Gross1990}.
@@
 
-It is apparent that these three approaches use only part of the information available when producing coherent forecasts.
+%It is apparent that these three approaches use only part of the information available when producing coherent forecasts.
 This might result in inaccurate forecasts.
@@
 
-As an alternative to these traditional methods, \citet{Hyndman2011} proposed to utilize the information from all levels of the hierarchy to obtain coherent point forecasts in  a two stage process.
+%As an alternative to these traditional methods, \citet{Hyndman2011} proposed to utilize the information from all levels of the hierarchy to obtain coherent point forecasts in  a two stage process.
 In the first stage, the forecasts of all series are independently obtained by fitting univariate models for individual series in the hierarchy.
@@
 
-Traditional bottom-up, top-down and middle-out forecasting methods are not strictly reconciliation methods since they use only a part of the information from the hierarchy to produce coherent forecasts.
-
-Previous studies on coherent point forecasting have shown that reconciliation provides better coherent forecasts than the traditional bottom-up and top-down methods \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017}.
+%Traditional bottom-up, top-down and middle-out forecasting methods are not strictly reconciliation methods since they use only a part of the information from the hierarchy to produce coherent forecasts.
+
+%Previous studies on coherent point forecasting have shown that reconciliation provides better coherent forecasts than the traditional bottom-up and top-down methods \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017}.
 However, this idea has not been explored in the context of probabilistic forecasting.
 
-Point forecasts are limited because they provide no indication of forecast uncertainty.
+%Point forecasts are limited because they provide no indication of forecast uncertainty.
 Providing prediction intervals helps, but a richer description of forecast uncertainty is obtained by estimating the entire forecast distribution.
@@
 
-Although there is a rich and growing literature on producing coherent point forecasts of hierarchical time series, little  attention has been given to coherent probabilistic forecasts.
+%Although there is a rich and growing literature on producing coherent point forecasts of hierarchical time series, little  attention has been given to coherent probabilistic forecasts.
 The only relevant paper we are aware of is \citet{BenTaieb2017}, who recently proposed an algorithm to produce coherent probabilistic forecasts and applied it to UK electricity smart meter data.
@@
 In that sense, their approach is analogous to bottom-up point forecasting rather than forecast reconciliation.
-
-After introducing our notation in Section~\ref{sec:notation}, we define what is meant by probabilistic forecast reconciliation for hierarchical time series in Section~\ref{sec:definitions}.
+%
+%After introducing our notation in Section~\ref{sec:notation}, we define what is meant by probabilistic forecast reconciliation for hierarchical time series in Section~\ref{sec:definitions}.
 First, we provide a new definition for coherency of point forecasts, and the reconciliation of a set of incoherent point forecasts, using  concepts related to vector spaces and measure theory.
 Based on these, we provide a rigorous definition for probabilistic forecast reconciliation, and how we can reconcile the incoherent forecast densities in practice.
-
-Further, due to the aggregation structure of the hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate.
+%
+%Further, due to the aggregation structure of the hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate.
 In Section~\ref{sec:reconciliation}, we discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation, and in Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts.
-
-Some theoretical results on probabilistic forecast reconciliation in the Gaussian framework are given in Section~\ref{sec:gaussian}, including a simulation study to show the importance of reconciliation in the probabilistic framework.
-
-We conclude with some thoughts on extensions and limitations in Section~\ref{sec:conclusions}.
+%
+%Some theoretical results on probabilistic forecast reconciliation in the Gaussian framework are given in Section~\ref{sec:gaussian}, including a simulation study to show the importance of reconciliation in the probabilistic framework.
+%
+%We conclude with some thoughts on extensions and limitations in Section~\ref{sec:conclusions}.
 

### 2018-07-04 ProbabilisticCoherence.tex
Conclusion written

@@
 
-Points to discuss
-\begin{itemize}
-	\item Optimal reconciliation likely to depend on
-	\begin{itemize}
-		\item Properties of base probabilstic forecast
-		\item Scoring rule
-	\end{itemize}
-    \item Case where no parametric form available
-    \item Cases where $g$ and maybe even $s$ are non linear
-\end{itemize}
-
-Although the problem of hierarchical point forecasts is well studied in the literature, there is a lack of attention in the context of probabilistic forecasts.
+%Although the problem of hierarchical point forecasts is well studied in the literature, there is a lack of attention in the context of probabilistic forecasts.
 Thus we attempted to fill this gap in the literature by providing substantial theoretical background to the problem.
-We initially provided rigorous definitions for the coherent point and probabilistic forecasts using the principles of measure theory.
-Due to the aggregation nature of hierarchy, the probability density is a degenerate density.
+
+By redefining coherent forecasts and forecast reconciliation in geometric terms we have established two new theoretical results that support the use of projections for point forecast reconciliation, and crucially have extended these concepts to probabilistic forecasting.
+We show that for elliptical distributions, the true predictive density can be recovered by linear reconciliation and establish conditions for which this linear mapping is a projection.
+Although this optimal projection cannot feasibly be obtained in practice, a projection similar to the MinT procedure provides a good approximation in practice.
+This is supported by the results of a simulation study.
+Finally, we also discuss strategies for evaluating probabilistic forecasts for hierarchical time series establishing a key results regarding the impropriety of the log score with respect to incoherent forecasts.
+
+In many ways this paper sets up a substantial future research agenda.
+For example, having defined what amounts to an entire class of reconciliation methods for probabilistic forecasts it will be worthwhile investigating which specific projections are optimal.
+This is likely to depend on the specific scoring rule employed as well as the properties of base forecasts.
+Another avenue worth investigation is to consider whether it is possible to recover the true predictive distribution for non-elliptical distributions possible via a non-linear mapping $g(.)$.
+
+%Due to the aggregation nature of hierarchy, the probability density is a degenerate density.
 Thus the forecast distribution that we opt to find should also lie in a lower dimensional subspace of $\mathbb{R}^{n}$.
 
-As it was well established that the reconciliation outperforms other conventional point forecasting methods in the hierarchical literature, we proposed to use reconciliation in probabilistic framework to obtain coherent degenerate densities.
+%As it was well established that the reconciliation outperforms other conventional point forecasting methods in the hierarchical literature, we proposed to use reconciliation in probabilistic framework to obtain coherent degenerate densities.
 We provided a distinct definition for density forecast reconciliation and how it can be used to reconcile incoherent densities in practice.
 
-Assuming a multivariate Gaussian distribution for the hierarchy, we showed how to obtain reconciled Gaussian forecast densities, utilizing available information in the hierarchy.
+%Assuming a multivariate Gaussian distribution for the hierarchy, we showed how to obtain reconciled Gaussian forecast densities, utilizing available information in the hierarchy.
 An extensive Monte Carlo simulation study further showed that the MinT reconciliation method \citep{Wickramasuriya2017} is useful in producing improved coherent probabilistic forecasts at least in the Gaussian framework.

### 2018-07-04 ProbabilisticCoherence.tex
Abstract added

@@
 \begin{abstract}
-  TBC
+  The process by which forecasts are adjusted to ensure coherence to aggregation constraints that hold for real data - known as forecast reconiliation - is extended from the point forecasts to probabilistic forecasts.
+This is achieved by redefining many concepts from the existing literature in terms of linear mappings in general, and projections more specifically.
+New theorems establish that linear reconciliation can recover the true predictive distribution in the elliptical case as well as general conditions for when this can be achieved via projection.
+A geometric interpretation is also used to prove two new theoretical results for point forecasting; that  reconciliation via projection a) preserves unbiasedness and b) dominates unreconciled forecasts in a mean squared error sense.
+Strategies for forecast evaluation based on scoring rules are discussed and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive disstribution coheres with aggregation constraints.
+Finally evidence from simulation study show that reconciliation based on an oblique projection, derived from the MinT method of \cite{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
 \end{abstract}
@@
 %
-%\section{Introduction}\label{sec:intro}
+\section{Introduction}\label{sec:intro}
 %Sketch narrative to tell

### 2018-07-05 ProbabilisticCoherence.tex
Cleaned up abstract

@@
 \begin{abstract}
-  The process by which forecasts are adjusted to ensure coherence to aggregation constraints that hold for real data - known as forecast reconiliation - is extended from the point forecasts to probabilistic forecasts.
-This is achieved by redefining many concepts from the existing literature in terms of linear mappings in general, and projections more specifically.
-New theorems establish that linear reconciliation can recover the true predictive distribution in the elliptical case as well as general conditions for when this can be achieved via projection.
+  Adjusting forecasts to ensure coherence with aggregation constraints that hold for real data - a process known as forecast reconiliation - is extended from point forecasts to probabilistic forecasts.
+This is achieved by redefining forecast reconciliation in terms of linear mappings in general, and projections more specifically.
+New theorems establish that the true predictive distribution can be recovered in the elliptical case by a linear mapping and general conditions are derived for when this linear mapping is a projection.
 A geometric interpretation is also used to prove two new theoretical results for point forecasting; that  reconciliation via projection a) preserves unbiasedness and b) dominates unreconciled forecasts in a mean squared error sense.

### 2018-07-05 ProbabilisticCoherence.tex
Cleaned up intro

@@
 Large collections of time series often follow some aggregation structure.
-For example, the electricity demand of a country can be disaggregated according to a geographical hierarchy of states, cities, and individual households or according to temporal hierarchy of yearly, quarterly and monthly demand.
+For example, the electricity demand of a country can be disaggregated according to a geographical hierarchy of states, cities, and individual households or by a temporal hierarchy of yearly, quarterly and monthly demand.
 In these so-called hierarchical time series, forecasts are often required for all individual series.
@@
 This property is referred to as ``coherence''.
-
-Traditional approaches to ensure coherent point forecasts produce forecasts at a single level.
-For instance in the bottom-up \citep{Dunn1976} approach, forecasts are produced at the most disaggregated level and then summed to recover top level-series.
-Alternatively, in the top-down approach \citep{Gross1990} a top-level forecast is produced and bottom level forecasts are recovered as  historical or forecasted proportions of the top-level forecast,while the middle-out approach is a hybrid between these two.
-
-In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular.
-These methods produce first stage, or  so called `base' forecasts independently for each series.
-Since base are rarely coherent in practice,  they are subsequently adjusted  or `reconciled' to ensure coherence.
-To  date reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling least squares estimators.
-These include Ordinary Least Squares {OLS} \cite{Hyndman2011}, Weighted Least Squares {WLS} \todo{citation?} and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017}, more commonly referred to as MinT since it minimises the trace of  the squared error matrix.
-These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and in some sense hedge against the risk of model misspecification error in a single level.
-
-A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \cite[see][and references therein]{Gneiting2014}.
-Indeed to the best of our knowledge, the as yet unpublished work of \cite{BenTaieb2017} is the only paper to deal with the issue of coherent probabilistic forecasts, and although the means of the predictive distributions are reconciled, the overall distributions are constructed in a bottom up fashion.
-In contrast, the main objective of our paper is to generalise point forecast reconciliation to probabilistic forecast reconciliation.
-
-To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we  first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections.
-In addition to being highly intuitive, this allows us to establish a number of theoretical results.
-We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts while the second shows that reconciled forecasts dominate unreconciled forecasts since projections are bounded operators.
-We provide definitions of coherence and forecast reconciliation in the probabilistic setting and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation.
-We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class.
-We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly esitimated in practice, our  theoretical results lead to a heuristic argument in favour of MinT reconciliation.
-
-We also cover the issue of forecast evaluation of probabilistic forecasts via scoring rules.
-In particular we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.
-As such we recommend the use of the energy score and variogram score for comparing reconciled to unreconciled forecasts.
-Two or more reconciled forecasts can be compared using log score,energy score and  variogram score, although we show that comparisons should be  made on the full hierarchy for the latter two scores.
-
-The remainder of the papers is  structured as follows.
-In Section~\ref{sec:notation}, hierarchical time series are discussed in general and notation is  defined.
-In section \ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.
-Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results.
-In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian},  Section~\ref{sec:conclusions} concludes.
-
-%In the bottom-up approach, forecasts of the lowest level are first generated and they are simply aggregated to forecast upper levels of the hierarchy \citep{Dunn1976}.
-In contrast, the top-down approach involves forecasting the most aggregated series first and then disaggregating these forecasts down the hierarchy based on the corresponding proportions of observed data \citep{Gross1990}.
-Many studies have discussed the relative advantages and disadvantages of bottom-up and top-down methods, and situations in which each would provide reliable forecasts \citep{Schwarzkopf1988,Kahn1998, Lapide1998,Fliedner2001}.
-A compromise between these two approaches is the middle-out method which entails forecasting each series of a selected middle level in the hierarchy and then forecasting upper levels by the bottom-up method and lower levels by the top-down method.
-
-%It is apparent that these three approaches use only part of the information available when producing coherent forecasts.
-This might result in inaccurate forecasts.
-For example, if the bottom-level series are highly volatile or noisy, and hence challenging to forecast, then the resulting forecasts from the bottom-up approach are likely to be inaccurate.
-
-%As an alternative to these traditional methods, \citet{Hyndman2011} proposed to utilize the information from all levels of the hierarchy to obtain coherent point forecasts in  a two stage process.
-In the first stage, the forecasts of all series are independently obtained by fitting univariate models for individual series in the hierarchy.
-It is very unlikely that these forecasts are coherent.
-Thus in the second stage, these forecasts are optimally combined through a regression model to obtain coherent forecasts.
-This second step is referred to as ``reconciliation'' since it takes a set of incoherent forecasts and revises them to be coherent.
-The approach was further improved by \citet{Wickramasuriya2017} who proposed the ``MinT'' algorithm to obtain optimally reconciled point forecasts by minimizing the mean squared coherent forecast errors.
-
-%Traditional bottom-up, top-down and middle-out forecasting methods are not strictly reconciliation methods since they use only a part of the information from the hierarchy to produce coherent forecasts.
-
-%Previous studies on coherent point forecasting have shown that reconciliation provides better coherent forecasts than the traditional bottom-up and top-down methods \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017}.
-However, this idea has not been explored in the context of probabilistic forecasting.
-
-%Point forecasts are limited because they provide no indication of forecast uncertainty.
-Providing prediction intervals helps, but a richer description of forecast uncertainty is obtained by estimating the entire forecast distribution.
-These are often called ``probabilistic forecasts'' \citep{Gneiting2014}.
-For example, \citet{McSharry2005} produced probabilistic forecasts for electricity demand, \citet{BenTaieb2017} for smart meter data, \citet{Pinson2009} for wind power generation, and \citet{Gel2004}, \citet{Gneiting2005a} and \citet{Gneiting2005} for various weather variables.
-
-%Although there is a rich and growing literature on producing coherent point forecasts of hierarchical time series, little  attention has been given to coherent probabilistic forecasts.
-The only relevant paper we are aware of is \citet{BenTaieb2017}, who recently proposed an algorithm to produce coherent probabilistic forecasts and applied it to UK electricity smart meter data.
-In their approach, a sample from the bottom-level forecast distribution is first generated, and then aggregated to obtain coherent probabilistic forecasts of the upper levels of the hierarchy.
-Hence this method is a bottom-up approach.
-They propose to first use the MinT algorithm to reconcile the means of the bottom-level forecast distributions, and then a copula-based approach is employed to model the dependency structure of the hierarchy.
-The resulting multi-dimensional distribution is used to generating empirical forecast distributions for all bottom-level series.
-Thus, while \citet{BenTaieb2017} provide coherent probabilistic forecasts, they do no forecast reconciliation of the distributions.
-In that sense, their approach is analogous to bottom-up point forecasting rather than forecast reconciliation.
-%
-%After introducing our notation in Section~\ref{sec:notation}, we define what is meant by probabilistic forecast reconciliation for hierarchical time series in Section~\ref{sec:definitions}.
-First, we provide a new definition for coherency of point forecasts, and the reconciliation of a set of incoherent point forecasts, using  concepts related to vector spaces and measure theory.
-Based on these, we provide a rigorous definition for probabilistic forecast reconciliation, and how we can reconcile the incoherent forecast densities in practice.
-%
-%Further, due to the aggregation structure of the hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate.
-In Section~\ref{sec:reconciliation}, we discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation, and in Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts.
-%
-%Some theoretical results on probabilistic forecast reconciliation in the Gaussian framework are given in Section~\ref{sec:gaussian}, including a simulation study to show the importance of reconciliation in the probabilistic framework.
-%
-%We conclude with some thoughts on extensions and limitations in Section~\ref{sec:conclusions}.
-
-\section{Hierarchical Time Series}\label{sec:notation}
-
-In the section, and throughout the paper, we will try to follow notational conventions used in \citet{Wickramasuriya2017} as much as possible.
-A {\em hierarchical time series} is a collection of $n$ variables where some variables are aggregates of other variables.
-For example in the hierarchy depicted in Figure~\ref{fig1} below, the variable labelled $Tot$ is the sum of the series $A$
-and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.
-The {\em bottom level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables, in the example in Figure~\ref{fig1} these are the series $AA$, $AB$, $BA$ and $BB$.
+This issue has been extensively covered for point forecasting in a literature we review below, while the case of probabilistic forecasting is a gap that we seek to address in this work.
+
+Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level.
+To describe these we use the small hierarchy in Figure~\ref{fig1}.
+In the bottom-up \citep{Dunn1976} approach, forecasts are produced at the most disaggregated level (Series {\em AA}, {\em AB}, {\em BA} and {\em BB}) and then summed to recover all top level-series.
+Alternatively, in the top-down approach \citep{Gross1990} a top-level forecast is first produced (Series {\em Tot}) and bottom level forecasts are recovered as  historical or forecasted proportions of the top-level forecast.
+A middle-out approach is a hybrid between these two that for the hierarchy below would produce first stage forecasts for Series {\em A} and {\em B}.
 
@@
 \end{figure}
+
+In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular.
+For these methods, first stage forecasts are independently produced for all series rather than series at a single level.
+Since these so-called `base' forecasts are rarely coherent in practice,  they are subsequently adjusted  or `reconciled' to ensure coherence.
+To  date reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators.
+These include Ordinary Least Squares {OLS} \cite{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017} and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017}, more commonly referred to as MinT since it minimises the trace of  the squared error matrix.
+These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and in some sense hedge against the risk of model misspecification at a single level.
+
+A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \cite[see][and references therein]{Gneiting2014}.
+Indeed to the best of our knowledge, the as yet unpublished work of \cite{BenTaieb2017} is the only paper to deal with the issue of coherent probabilistic forecasts, and although the means of the predictive distributions are reconciled, the overall distributions are constructed in a bottom up fashion.
+In contrast, the main objective of our paper is to generalise both coherence and reconciliation from point to probabilistic forecasting.
+
+To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we  first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections.
+In addition to being highly intuitive, this allows us to establish a number of theoretical results.
+We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts while the second shows that reconciled forecasts dominate unreconciled forecasts since projections are bounded operators.
+We provide definitions of coherence and forecast reconciliation in the probabilistic setting and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation.
+We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class.
+We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly estimated in practice, we provide a heuristic argument in favour of MinT reconciliation.
+
+We also cover the issue of forecast evaluation of probabilistic forecasts via scoring rules.
+In particular we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.
+As such we recommend the use of the energy score and variogram score for comparing reconciled to unreconciled forecasts.
+Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be  made on the full hierarchy for the latter two scores.
+
+The remainder of the papers is  structured as follows.
+In Section~\ref{sec:notation}, hierarchical time series are discussed in general and notation is  defined.
+In section \ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.
+Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results.
+In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian} and Section~\ref{sec:conclusions} concludes.
+
+%In the bottom-up approach, forecasts of the lowest level are first generated and they are simply aggregated to forecast upper levels of the hierarchy \citep{Dunn1976}.
+In contrast, the top-down approach involves forecasting the most aggregated series first and then disaggregating these forecasts down the hierarchy based on the corresponding proportions of observed data \citep{Gross1990}.
+Many studies have discussed the relative advantages and disadvantages of bottom-up and top-down methods, and situations in which each would provide reliable forecasts \citep{Schwarzkopf1988,Kahn1998, Lapide1998,Fliedner2001}.
+A compromise between these two approaches is the middle-out method which entails forecasting each series of a selected middle level in the hierarchy and then forecasting upper levels by the bottom-up method and lower levels by the top-down method.
+
+%It is apparent that these three approaches use only part of the information available when producing coherent forecasts.
+This might result in inaccurate forecasts.
+For example, if the bottom-level series are highly volatile or noisy, and hence challenging to forecast, then the resulting forecasts from the bottom-up approach are likely to be inaccurate.
+
+%As an alternative to these traditional methods, \citet{Hyndman2011} proposed to utilize the information from all levels of the hierarchy to obtain coherent point forecasts in  a two stage process.
+In the first stage, the forecasts of all series are independently obtained by fitting univariate models for individual series in the hierarchy.
+It is very unlikely that these forecasts are coherent.
+Thus in the second stage, these forecasts are optimally combined through a regression model to obtain coherent forecasts.
+This second step is referred to as ``reconciliation'' since it takes a set of incoherent forecasts and revises them to be coherent.
+The approach was further improved by \citet{Wickramasuriya2017} who proposed the ``MinT'' algorithm to obtain optimally reconciled point forecasts by minimizing the mean squared coherent forecast errors.
+
+%Traditional bottom-up, top-down and middle-out forecasting methods are not strictly reconciliation methods since they use only a part of the information from the hierarchy to produce coherent forecasts.
+
+%Previous studies on coherent point forecasting have shown that reconciliation provides better coherent forecasts than the traditional bottom-up and top-down methods \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017}.
+However, this idea has not been explored in the context of probabilistic forecasting.
+
+%Point forecasts are limited because they provide no indication of forecast uncertainty.
+Providing prediction intervals helps, but a richer description of forecast uncertainty is obtained by estimating the entire forecast distribution.
+These are often called ``probabilistic forecasts'' \citep{Gneiting2014}.
+For example, \citet{McSharry2005} produced probabilistic forecasts for electricity demand, \citet{BenTaieb2017} for smart meter data, \citet{Pinson2009} for wind power generation, and \citet{Gel2004}, \citet{Gneiting2005a} and \citet{Gneiting2005} for various weather variables.
+
+%Although there is a rich and growing literature on producing coherent point forecasts of hierarchical time series, little  attention has been given to coherent probabilistic forecasts.
+The only relevant paper we are aware of is \citet{BenTaieb2017}, who recently proposed an algorithm to produce coherent probabilistic forecasts and applied it to UK electricity smart meter data.
+In their approach, a sample from the bottom-level forecast distribution is first generated, and then aggregated to obtain coherent probabilistic forecasts of the upper levels of the hierarchy.
+Hence this method is a bottom-up approach.
+They propose to first use the MinT algorithm to reconcile the means of the bottom-level forecast distributions, and then a copula-based approach is employed to model the dependency structure of the hierarchy.
+The resulting multi-dimensional distribution is used to generating empirical forecast distributions for all bottom-level series.
+Thus, while \citet{BenTaieb2017} provide coherent probabilistic forecasts, they do no forecast reconciliation of the distributions.
+In that sense, their approach is analogous to bottom-up point forecasting rather than forecast reconciliation.
+%
+%After introducing our notation in Section~\ref{sec:notation}, we define what is meant by probabilistic forecast reconciliation for hierarchical time series in Section~\ref{sec:definitions}.
+First, we provide a new definition for coherency of point forecasts, and the reconciliation of a set of incoherent point forecasts, using  concepts related to vector spaces and measure theory.
+Based on these, we provide a rigorous definition for probabilistic forecast reconciliation, and how we can reconcile the incoherent forecast densities in practice.
+%
+%Further, due to the aggregation structure of the hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate.
+In Section~\ref{sec:reconciliation}, we discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation, and in Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts.
+%
+%Some theoretical results on probabilistic forecast reconciliation in the Gaussian framework are given in Section~\ref{sec:gaussian}, including a simulation study to show the importance of reconciliation in the probabilistic framework.
+%
+%We conclude with some thoughts on extensions and limitations in Section~\ref{sec:conclusions}.
+
+\section{Hierarchical Time Series}\label{sec:notation}
+
+In the section, and throughout the paper, we will try to follow notational conventions used in \citet{Wickramasuriya2017} as much as possible.
+A {\em hierarchical time series} is a collection of $n$ variables where some variables are aggregates of other variables.
+For example in the hierarchy depicted in Figure~\ref{fig1} below, the variable labelled $Tot$ is the sum of the series $A$
+and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.
+The {\em bottom level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables, in the example in Figure~\ref{fig1} these are the series $AA$, $AB$, $BA$ and $BB$.
 

### 2018-07-05 ProbabilisticCoherence.tex
Old Section 2 merged with coherence section

@@
 Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level.
-To describe these we use the small hierarchy in Figure~\ref{fig1}.
-In the bottom-up \citep{Dunn1976} approach, forecasts are produced at the most disaggregated level (Series {\em AA}, {\em AB}, {\em BA} and {\em BB}) and then summed to recover all top level-series.
-Alternatively, in the top-down approach \citep{Gross1990} a top-level forecast is first produced (Series {\em Tot}) and bottom level forecasts are recovered as  historical or forecasted proportions of the top-level forecast.
-A middle-out approach is a hybrid between these two that for the hierarchy below would produce first stage forecasts for Series {\em A} and {\em B}.
+To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$
+and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.
+In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (Series $AA$, $AB$, $BA$ and $BB$) and then summed to recover all top level-series.
+Alternatively, in the top-down approach \citep{Gross1990} a top-level forecast is first produced (Series $Tot$) and bottom level forecasts are recovered as  historical or forecasted proportions of the top-level forecast.
+A middle-out approach is a hybrid between these two that for the hierarchy below would produce first stage forecasts for Series $A$ and $B$.
 
@@
 The remainder of the papers is  structured as follows.
-In Section~\ref{sec:notation}, hierarchical time series are discussed in general and notation is  defined.
 In section \ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.
@@
 
-\section{Hierarchical Time Series}\label{sec:notation}
-
-In the section, and throughout the paper, we will try to follow notational conventions used in \citet{Wickramasuriya2017} as much as possible.
-A {\em hierarchical time series} is a collection of $n$ variables where some variables are aggregates of other variables.
-For example in the hierarchy depicted in Figure~\ref{fig1} below, the variable labelled $Tot$ is the sum of the series $A$
-and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.
-The {\em bottom level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables, in the example in Figure~\ref{fig1} these are the series $AA$, $AB$, $BA$ and $BB$.
-
-We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprised of observations of all variables in the hierarchy at time $t$,  and $\bm{b}_t \in \mathbb{R}^m$ is a vector comprised of observations of all bottom-level series at time $t$.
+%\section{Hierarchical Time Series}\label{sec:notation}
+\section{Coherent forecasts}\label{sec:definitions}
+\subsection{Notation and Preliminaries}\label{sec:notation}
+
+Throughout the paper, we will follow notational conventions used in \citet{Wickramasuriya2017} as much as possible.
+A {\em hierarchical time series} is a collection of $n$ variables where some variables are aggregates of other variables and we let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprised of observations of all variables in the hierarchy at time $t$.
+For example for the hierarchy in Figure~\ref{fig1}, $n=7$ and $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.
+The {\em bottom level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables, we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.
+For example for the hierarchy in Figure~\ref{fig1}, $m=4$ and $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.
 The hierarchical structure of the data imply the following holds for all $t$
@@
 \end{equation}
-where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints.
-For the hierarchy in Figure~\ref{fig1}, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and
+where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints.  For the hierarchy in Figure~\ref{fig1}
 $$ 
@@
 
-\section{Coherent forecasts}\label{sec:definitions}
+\subsection{Coherent Point Forecasts}\label{sec:cohpointf}
 
@@
 \end{definition}
+
+\subsection{Coherent Probabilistic Forecasts}\label{sec:cohprobf}
 

### 2018-07-05 ProbabilisticCoherence.tex
Minor cleanup of coherence section

@@
 It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect aggregation constraints.
-We follow other authors \cite{Wickramasuriya2017}\todo{FPP?} in using the nomenclature {\em coherence} to describe this property.
+We follow other authors \citep{Wickramasuriya2017, FPP2018} in using the nomenclature {\em coherence} to describe this property.
 %While coherent point forecasts have been discussed many times previously, the definitions of coherence previously given are vague and are not easily extended to the situation of probabilistic forecasting.
-
 We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem thus facilitating the development of the probabilistic forecast reconciliation in section~\ref{sec:reconciliation}.
-
-Recall that $\bm{y}_t \in \mathbb{R}^n$ is a $n$-dimensional time series subject to the linear aggregation constraint $\bm{y}_t = \bm{S}\bm{b}_t$, where $\bm{b}_t \in \mathbb{R}^m$ and $\bm{S}$ is an $n \times m$ constant matrix.
 
@@
 \end{definition}
-A probabilistic forecast for time $t+h$ is coherent if uncertainty in $\bm{y_{t+h|h}}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.
+A probabilistic forecast for time $t+h$ is coherent if uncertainty in ${\bm y}_{t+h}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.
 

### 2018-07-06 ProbabilisticCoherence.tex
Cleanup of point reconciliation

@@
 
+As discussed, reconciliation is distinct from coherence, since the former refers to a process whereby incoherent forecasts are made coherent.
 Initially we define point forecast reconciliation, before extending the idea to the probabilistic setting.
@@
 
-Many choices of $g(.)$ currently extant in the literature including the so called OLS \cite{Hyndman2011}, WLS \todo{First WLS  reference?} and MinT\cite{Wickramasuriya2017} methods are special cases where $s\circ g$ is a projection and are summarised in Table~\ref{table:2}.
-These can be defined so that ${\bm G}=\left({\bm R'_{\perp}}{\bm S}\right)^{-1}{\bm S}'$ and ${\bm d}={\bm 0}$.
-Here, ${\bm R_{\perp}}$ is a $n\times m$ orthogonal complement to the an $n \times (n-m)$ matrix $\bm{R}$ where the columns of the latter span the null space of $\mathfrak{s}_{\perp}$.
+Many choices of $g(.)$ currently extant in the literature including the OLS, WLS and MinT methods are special cases where $s\circ g$ is a projection.
+These can be defined so that ${\bm G}=\left({\bm R'_{\perp}}{\bm S}\right)^{-1}{\bm R}_{\perp}'$ and ${\bm d}={\bm 0}$.
+Here, ${\bm R_{\perp}}$ is a $n\times m$ orthogonal complement to the an $n \times (n-m)$ matrix $\bm{R}$ where the columns of the latter span the null space of $\mathfrak{s}$.
 For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
 In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
-For the example provided, ${\bm R}_\perp'={\bm S}$ and reconciliation corresponds to the so called `OLS' method \cite{Hyndman2011}.
+For this example, ${\bm R}_\perp'={\bm S}$ and reconciliation corresponds to the OLS method.
 For the case where ${\bm R}_\perp'\neq{\bm S}$, for example WLS and MinT, there are two possible interpretations.
 One is that these are oblique projections in Euclidean space where the columns of $\bm{R}$ are `directions' along which incoherent point forecasts are projected onto the coherent space $\mathfrak{s}$.
-Alternatively, since ${\bm R}_\perp'$ is usually written in the form ${\bm S}'{\bm W}^{-1}$, these projections can be thought of as orthogonal projections after applying the transformation ${\bm W^{-1/2}}$.
-A schematic providing a geometric interpretation of point reconciliation is given in Figure~\ref{fig:pointfr_sch}.
-
-\begin{table}
-	\caption{Several possible estimates of $\bm{R}'_\bot$.
-For $n<T$, $\bm{\hat{W}}_{T+1}^{sam}$ is an unbiased and consistent estimator for $\bm{W}_{T+1}$.
-$\bm{\hat{W}}_{T+1}^{shr}$ is a shrinkage estimator which is more suitable for large dimensions.
-$\bm{\hat{W}}_{T+1}^{shr}$ was proposed by \citet{Schafer2005} and also used by \citet{Wickramasuriya2017}, where Diag($\bm{A}$) denotes the diagonal matrix of $\bm{A}$, $\tau = \frac{\sum_{i \ne j}\hat{\text{Var}}(\hat{r}_{ij})}{\sum_{i \ne j}\hat{r}_{ij}^2}$, and $\hat{r}_{ij}$ is the $ij$th element of the sample correlation matrix.}\label{table:2}
+Alternatively, since ${\bm R}_\perp'$ is usually written in the form ${\bm S}'{\bm W}^{-1}$, these projections can be thought of as orthogonal projections after pre-multiplying by ${\bm W^{-1/2}}$.
+A schematic providing a geometric interpretation of point reconciliation is given in Figure~\ref{fig:pointfr_sch}, while  and are Table~\ref{table:2} summarises existing reconciliation methods.
+
+\begin{table}[!h]
+	\caption{Summary of reconciliation methods that are projections.
+Here, $\bm{\hat{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, while $\bm{\hat{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}.
+Also $\tau = \frac{\sum_{i \ne j}\hat{\text{Var}}(\hat{w}_{ij})}{\sum_{i \ne j}{\hat{w}}^2_{ij}}$ where $w_{ij}$ are elements of $\hat{\bm W}^{sam}$.}\label{table:2}
 	\centering\setstretch{1.5}
@@
 		\toprule
-		\textbf{Method} & \textbf{Estimate of $\bm{W}_{h}$} & \textbf{Estimate of $\bm{R}'_\bot$}      \\
+		\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
 		\midrule
@@
 		MinT(Sample)    &
-		$\bm{\hat{W}}_{T+1}^{sam}$ &
-		$\bm{S}'(\bm{\hat{W}}_{T+1}^{sam})^{-1}$ \\
+		$\bm{\hat{W}}^{sam}$ &
+		$\bm{S}'(\bm{\hat{W}}^{sam})^{-1}$ \\
 		MinT(Shrink)    &
-		$\bm{\hat{W}}_{T+1}^{shr} = \tau\text{Diag}(\bm{\hat{W}}_{T+1}^{sam}) + (1-\tau)\bm{\hat{W}}_{T+1}^{sam}$ &
-		$\bm{S}'(\bm{\hat{W}}_{T+1}^{shr})^{-1}$ \\
+		$\tau\text{Diag}(\bm{\hat{W}}^{sam}) + (1-\tau)\bm{\hat{W}}^{sam}$ &
+		$\bm{S}'(\bm{\hat{W}}^{shr})^{-1}$ \\
 		WLS       &
-		$\bm{\hat{W}}_{T+1}^{wls} = \text{Diag}(\bm{\hat{W}}_{T+1}^{shr})$ &
-		$\bm{S}'(\bm{\hat{W}}_{T+1}^{wls})^{-1}$ \\
+		$\text{Diag}(\bm{\hat{W}}^{shr})$ &
+		$\bm{S}'(\bm{\hat{W}}^{wls})^{-1}$ \\
 		\bottomrule
@@
 	\caption{Summary of probabilistic point reconciliation.
-The mapping $G(.)$ projects the unreconciled forecast $\hat{\bm y}$ onto   Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:pointfr_sch}
+The mapping $s\circ g$ projects the unreconciled forecast $\hat{\bm y}$ onto $\mathfrak{s}$.
+Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:pointfr_sch}
 \end{figure}
@@
 Let $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$ respectively after a change of basis.
-The process of reconciliation involves setting $\tilde{\bm{b}}_{t+h|t}$ to be the values of the reconciled bottom-level series and setting $\tilde{\bm{a}}_{t+h}=\bm{0}$ to ensure coherence.
+The process of reconciliation involves setting the values of the reconciled bottom-level series to be $\tilde{\bm{b}}_{t+h|t}$ and setting $\tilde{\bm{a}}_{t+h}=\bm{0}$ to ensure coherence.
 From properties of linear algebra it follows that
@@
 Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of ${\bm R}$.
-For example \cite{Hyndman2011} consider $\tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h}$ which minimises the Euclidean distance between $\hat{\bm y}$ and $\tilde{\bm y}$.
-\cite{Wickramasuriya2017} consider $\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}' \bm{W}^{-1}_{h}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h}$, where ${\bm W}$ is an estimate of the variance covariance matrix of the unreconciled errors.
-This
+For example OLS minimises the Euclidean distance between $\hat{\bm y}$ and $\tilde{\bm y}$.
+\cite{Wickramasuriya2017} while MinT
 minimises the Mahalonobis distance between $\hat{\bm y}$ and $\tilde{\bm y}$.
 Bottom up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom level series.
-As such, bottom up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.\todo{mention reducing distance to truth?}.
+As such, bottom up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.
 
@@
 \begin{theo}[Unbiasedness preserving property]
-  The reconciled point forecast will also be an unbiased prediction as long as $s\circ g$ is a projection 
+  For unbiased $\hat{\bm y}_{t+h|t}$, the reconciled point forecast will also be an unbiased prediction as long as $s\circ g$ is a projection 
 \end{theo}
@@
 \end{proof}
-We note the same result does not hold for general ${\bm G}$ even though the range of $s\circ g$ is $\mathfrak{s}$.
+We note the same result does not hold for general $g$ even when the range of $s\circ g$ is $\mathfrak{s}$.
 Now let ${\bm y}_{t+h}$ be the realisation of the data generating process at time $t+h$ and let $||{\bm v}||_2$ be the L2 norm of vector ${\bm v}$.

### 2018-07-06 ProbabilisticCoherence.tex
Cleanup of probabilistic reconciliation

@@
 We now extend the methodology of point forecast reconciliation to probabilistic forecasts
-
 %For probabilistic forecasts, reconciliation implies finding the probability measure of the coherent forecasts using the information from an incoherent probabilistic forecast measure.
 A more formal definition is given below.
-
 Let $(\mathbb{R}^n, \mathscr{F}_{\mathbb{R}^n}, \hat{\nu})$ be an probability triple, that is incoherent and that characterises forecast uncertainty for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.
-This may be obtained from the first stage of the forecasting process e.g.
+This is obtained from the first stage of the forecasting process e.g.
 by modelling and forecasting each series individually.
@@
   \begin{definition} \label{def:reconprob}
-  We define the reconciled probability measure of $\hat{\nu}$ with respect to the mapping $g(.)$ as a probability measure $\tilde{\nu}$ on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_\mathfrak{s}$ where the following holds
+  The reconciled probability measure of $\hat{\nu}$ with respect to the mapping $g(.)$ is a probability measure $\tilde{\nu}$ on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_\mathfrak{s}$ where the following holds
   \begin{equation}
@@
 	\caption{Summary of probabilistic forecast reconciliation.
-The probability that ${\bm y}_{t+h|t}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that ${\bm y}_{t+h|t}$ lies in the shaded blue area under the unreconciled probabilistic forecast.
+The probability that ${\bm y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that ${\bm y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast.
 Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:probfr_sch}
@@
 While $\hat{\nu}$ is a probability measure for an $n$-vector $\hat{\bm{y}}_{t+h|t}$,  probability statements in terms of a different coordinate system can be made via an appropriate change of basis.
-Letting $f(.)$ be generic notation for a probability density functions and following the notation from our definition of point forecast reconciliation where $\hat{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t}$ we obtain
+Letting $f(.)$ be generic notation for a probability density function and following the notation from our definition of point forecast reconciliation where $\hat{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t}$ we obtain
 
@@
 
-After a change in basis
+In an alternative basis
 
 \begin{equation}
-f(\tilde{\bm b},\tilde{\bm a})=(2\pi)^{-\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{-\frac{1}{2}}\Big|(\bm{S} ~  \bm{R})\Big|\exp\left\{-\frac{1}{2}q\right\}\,,
+f(\tilde{\bm b},\tilde{\bm a})=(2\pi)^{-\frac{n}{2}}\Big|\bm{\hat{\Sigma}}\Big|^{-\frac{1}{2}}\Big|(\bm{S} ~  \bm{R})\Big|\exp\left\{-\frac{1}{2}q\right\}\,,
 \end{equation}
@@
 Let the true predictive distribution of ${\bm y}_{t+h|t}$ also belong to the elliptical class with location parameter ${\bm \mu}$ and scale matrix ${\bm \Sigma}$.
-Then the affine reconciliation mapping $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ with $\bm{G}_{opt}={\bm A}{\bm\Sigma}^{-1/2}$ and ${\bm d}_{opt}={\bm \mu}-{\bm S}{\bm G}_{opt}\hat{\bm \mu}$ recovers the true predictive density where ${\bm A}$ is any $m\times n$ matrix such that ${\bm A}{\bm A}'={\bm \Omega}$ and ${\bm \Omega}$ is the true variance covariance matrix of the predictive distribution for the bottom level.
+Then the linear reconciliation mapping $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ with $\bm{G}_{opt}={\bm A}{\bm\Sigma}^{-1/2}$ and ${\bm d}_{opt}={\bm \mu}-{\bm S}{\bm G}_{opt}\hat{\bm \mu}$ recovers the true predictive density where ${\bm A}$ is any $m\times n$ matrix such that ${\bm A}{\bm A}'={\bm \Omega}$ and ${\bm \Omega}$ is a sub-matrix of ${\bm \Sigma}$ corresponding to the bottom level series.
 \end{theo}
 \begin{proof}
-   Since elliptical distributions are closed under affine transformations, and are closed under marginalisation, reconciliation of an elliptical distribution yields an elliptical distribution (although the unreconciled and unreconciled distributions may be different members of the class of elliptical distributions).
+   Since elliptical distributions are closed under affine transformations, and are closed under marginalisation, reconciliation of an elliptical distribution yields an elliptical distribution (although the unreconciled and reconciled distributions may be different members of the class of elliptical distributions).
 The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}_{opt}{\bm \Sigma}{\bm G}_{opt}'{\bm S}'$ while the location matrix is given by $\bm{S}\bm{G}_{opt}\hat{\bm \mu}+{\bm d}_{opt}$.
@@
 A number of insights can be drawn from this theorem.
-First, although a linear mapping $g(.)$ can be used to recover the true density in the elliptical case, the same does not hold in general.
+First, although a linear mapping $g(.)$ can be used to recover the true predictive in the elliptical case, the same does not hold in general.
 Second, $g(.)$ is not, in general, a projection matrix.
-The conditions for which a the true predictive density can be recovered by reconciliation are given below.
+The conditions for which a the true predictive density can be recovered by a projection are given below.
 
 \begin{theo}[True predictive via projection]
-	Assume that the true predictive distribution is elliptical with location ${\bm mu}$ and scale ${\bm Sigma}$.
-Consider reconciliation via a projection $g({\bm y})=({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}{\bm y}$
-	The true predictive distribution can be recovered via reconciliation of an elliptical distribution with location $\hat{\bm \mu}$ $\hat{\bm \Sigma}$ and scale when the following conditions hold.
+	Assume that the true predictive distribution is elliptical with location ${\bm \mu}$ and scale ${\bm \Sigma}$.
+Consider reconciliation via a projection $g({\bm y})=({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}{\bm y}$.
+The true predictive distribution can be recovered via reconciliation of an elliptical distribution with location $\hat{\bm \mu}$ and scale $\hat{\bm \Sigma}$  when the following conditions hold.
 	\begin{align}
 	sp(\hat{\bm\mu}-{\bm \mu})&\subset sp(\bm{R})\\
-    sp(\bm{\Sigma}^{1/2}-{\bm \Sigma}^{1/2})&\subset sp({\bm R})\\
+    sp(\hat{\bm \Sigma}^{1/2}-{\bm \Sigma}^{1/2})&\subset sp({\bm R})\\
 	\end{align}
@@
 	\end{align*}
-  Since ${\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}$ is a projection onto $\mathfrak{s}$ and ${\bm \mu}\in\mathfrak{s}$ the first term simplified to ${\bm \mu}$.
-If ${\bm \mu}-\hat{\bm \mu}$ lies in the span of ${\bm R}$ then multiplication by ${\bm R}'_{\perp}$ reduced the second term to ${\bm 0}$.
+  Since ${\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}$ is a projection onto $\mathfrak{s}$ and ${\bm \mu}\in\mathfrak{s}$ the first term simplifies to ${\bm \mu}$.
+If ${\bm \mu}-\hat{\bm \mu}$ lies in the span of ${\bm R}$ then multiplication by ${\bm R}'_{\perp}$ reduces the second term to ${\bm 0}$.
 By a similar argument it can be shown that $\tilde{\bm \Sigma}^{1/2}={\bm \Sigma}^{1/2}$.
@@
 As such an orthogonal projection after transformation by the inverse of the one step ahead in-sample errors may be more intuitively appealing.
-This is exactly what the MinT projection estimates, and as simulations will show in Section~\ref{sec:gaussian}, this projection leads to the best empirical results.
+This is exactly what the MinT projection provides, and as simulations will show in Section~\ref{sec:gaussian}, this projection leads to the best empirical results.
 

### 2018-07-06 ProbabilisticCoherence.tex
Cleanup of evaluation section

@@
 The first is to compare unreconciled densities to reconciled densities.
-Although reconciliation is a valuable goal in and of itself since it can be important in aligning decision making across, for example, different units of an enterprise, in the point forecasting literature, forecast reconciliation has also been shown to improve forecast performance \todo{Some References}.
+Although reconciliation is a valuable goal in and of itself since it can be important in aligning decision making across, for example, different units of an enterprise, in the point forecasting literature, forecast reconciliation has also been shown to improve forecast performance \citep{AthEtAl2017, Wickramasuriya2017}.
 It will be worthwhile to see whether the same holds in the probabilistic forecasting case.
@@
 In the simulations of section~\ref{sec:gaussian} we consider two scoring rules.
-The log score is given by the log of the marginal density of each variable.
+The log score is given by the log density, in this case for each margin of the probabilistic forecast.
 The cumulative rank probability score generalises mean square error and is given by
 \begin{align} \label{eq:CRPS}
-\text{CRPS}(\breve{F}_i,y_{T+h,i}) &=\int \left(\breve{F}_i(\breve{y}_i)-\mathbb{1}(y_i<y_{T+h,i})\right)dy_i\\ &=\E_{\breve{Y}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}\E_{\breve{Y}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|\,,
+\text{CRPS}(\breve{F}_i,y_{i}) &=\int \left(\breve{F}_i(\breve{Y}_i)-\mathbb{1}(y_i<y_{i})\right)d\breve{Y}_i\\ &=\E_{\breve{Y}_i}|\breve{Y}_{i}-y_{i}| - \frac{1}{2}\E_{\breve{Y}_i}|\breve{Y}_{i}-\breve{Y}^*_{i}|\,,
 \end{align}
-where $\breve{Y}_i$ and $\breve{Y}^*_{T+h,i}$ are independent copies of a random variable with distribution $\breve{F}_i$ and the latter is the predictive distribution for the $i^{th}$ margin of a forecast for time $t+h$ made at time $t$.
+where $\breve{F}_i$ is the cumulative distribution function of the $i^{th}$ margin of the probabilistic forecast, $\breve{Y}_i$ and $\breve{Y}^*_{T+h,i}$ are independent copies of a random variable with distribution $\breve{F}_i$ and $y_i$ is the outcome of the $i^{th}$ margin.
 The expectations in the second line can be approximated by Monte Carlo when a sample from the predictive distribution is available.
 
-An advantage to this approach is that it allows the forecaster to evaluate the levels and individual series of the hierarchy where the gains to reconciliation are greatest.
-For this reason this approach has been used in the limited literature on probabilistic forecasting for hierarchies \cite{BenTaieb2017} and Jeon et al \todo{Jeon Panagiotelis and Petropoulos reference} to date.
-A major shortcomings to this approach however is that, evaluating univariate scores on the margins do not account for the dependence in the hierarchy.
+An advantage to this approach is that it allows the forecaster to evaluate the levels and individual series of the hierarchy where the gains from reconciliation are greatest.
+For this reason this approach has been used in the limited literature on probabilistic forecasting for hierarchies \citep{BenTaieb2017, JeoEtAl2018} to date.
+A major shortcomings of this approach however, is that evaluating univariate scores on the margins do not account for the dependence in the hierarchy.
 
@@
 
-While the a number of alternative proper scoring rules are available for univariate forecasts, the multivariate case is somewhat more limited.
+While a number of alternative proper scoring rules are available for univariate forecasts, the multivariate case is somewhat more limited.
 Here we focus on three scoring rules: the log score, the energy score and the variogram score.
-These are summarized in table~\ref{table:scoringrules}.
-
-\begin{table}[!bh]
-  \caption{Scoring rules to evaluate multivariate forecast densities.
+%These are summarized in table~\ref{table:scoringrules}.
+%
+%\begin{table}[!bh]
+%  \caption{Scoring rules to evaluate multivariate forecast densities.
 Here, $\breve{\bm{y}}_{T+h}$ and $\breve{\bm{y}}^*_{T+h}$ are two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with density function $\breve{\bm{f}}(\cdot)$ at time $T+h$, and $\bm{y}_{T+h}$ is the vector of realizations.
@@
 The variogram score is given for order $p$, where $w_{ij}$ denote non-negative weights.}\label{table:scoringrules}
-  \centering\small\setstretch{1.3}
-  \begin{tabular}{@{}lp{8.1cm}l@{}}
-    \toprule
-    \textbf{Scoring rule}  & \textbf{Expression} & \textbf{Reference}           \\
-    \midrule
-    \text{Log score}       &
-    $\text{LS}(\breve{\bm{F}},\bm{y}_{T+h}) = -\log {\breve{\bm{f}}(\bm{y}_{T+h})}$ &
-    \citet{Gneiting2007}  \\\\[-0.2cm]
-    \text{Energy score}    &
-    $\text{ES}(\breve{\bm{Y}}_{T+h},\bm{y}_{T+h}) =
-    \E_{\breve{\bm{F}}}
-    \|\breve{\bm{Y}}_{T+h}-\bm{y}_{T+h}\|^\alpha -$ \par\hfill
-    $\frac{1}{2}\E_{\breve{\bm{F}}}\|\breve{\bm{Y}}_{T+h}-\breve{\bm{Y}}^*_{T+h}\|^\alpha$, \,\, $\alpha \in (0,2]$ &
-    \citet{Gneiting2008}  \\\\[-0.2cm]
-    \text{Variogram score} &
-    $\text{VS}(\breve{\bm{F}}, \bm{y}_{T+h}) =
-    \sum\limits_{i=1}^{n}
-    \sum\limits_{j=1}^{n}
-    w_{ij}\Big(|y_{T+h,i} - y_{T+h,j}|^p -$ \par\hfill
-    $\E_{\breve{\bm{F}}}|\breve{Y}_{T+h,i}-\breve{Y}_{T+h,j}|^p\Big)^2$     &
-    \citet{SCHEUERER2015} \\
-    \bottomrule
-  \end{tabular}
-\end{table}
+%  \centering\small\setstretch{1.3}
+%  \begin{tabular}{@{}lp{8.1cm}l@{}}
+%    \toprule
+%    \textbf{Scoring rule}  & \textbf{Expression} & \textbf{Reference}           \\
+%    \midrule
+%    \text{Log score}       &
+%    $\text{LS}(\breve{\bm{F}},\bm{y}_{T+h}) = -\log {\breve{\bm{f}}(\bm{y}_{T+h})}$ &
+%    \citet{Gneiting2007}  \\\\[-0.2cm]
+%    \text{Energy score}    &
+%    $\text{ES}(\breve{\bm{Y}}_{T+h},\bm{y}_{T+h}) =
+%    \E_{\breve{\bm{F}}}
+%    \|\breve{\bm{Y}}_{T+h}-\bm{y}_{T+h}\|^\alpha -$ \par\hfill
+%    $\frac{1}{2}\E_{\breve{\bm{F}}}\|\breve{\bm{Y}}_{T+h}-\breve{\bm{Y}}^*_{T+h}\|^\alpha$, \,\, $\alpha \in (0,2]$ &
+%    \citet{Gneiting2008}  \\\\[-0.2cm]
+%    \text{Variogram score} &
+%    $\text{VS}(\breve{\bm{F}}, \bm{y}_{T+h}) =
+%    \sum\limits_{i=1}^{n}
+%    \sum\limits_{j=1}^{n}
+%    w_{ij}\Big(|y_{T+h,i} - y_{T+h,j}|^p -$ \par\hfill
+%    $\E_{\breve{\bm{F}}}|\breve{Y}_{T+h,i}-\breve{Y}_{T+h,j}|^p\Big)^2$     &
+%    \citet{SCHEUERER2015} \\
+%    \bottomrule
+%  \end{tabular}
+%\end{table}
 
 The log score can be approximated using a sample of values from the probabilistic forecast density \citep{Jordan2017} however it is more commonly used when a parametric form for the density is available for the probabilistic forecast.
-So far, we have mainly defined probabilistic forecasts in terms of probability measures.
-Although densities can be obtained for both reconciled and unreconciled forecasts, the degeneracy of reconciled forecasts is problematic when using log scores.
-We will discuss this further in the next subsection.
-
-The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the representation in Table~\ref{table:scoringrules} in terms of expectations leads itself to easy computation when samples from the probabilistic forecast are available.
-An interesting case is where $\alpha=2$, where it can be easily shown that
+The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the representation in terms of expectations leads itself to easy computation when samples from the probabilistic forecast are available.
+An interesting limiting case is where $\alpha=2$, where it can be easily shown that
 \begin{equation} \label{eq:(5.1)}
@@
 In contrast, \citet{SCHEUERER2015} have shown that the variogram score has a higher discrimination ability of misspecified means, variances and correlation structures than the energy score.
-For a finite sample of size $B$ from the multivariate forecast density $\breve{\bm{F}}$, the empirical variogram score is defined as
+When $\breve{\bm Y}$ is a random variable from probabilistic forecast $\breve{F}$, the empirical variogram score is defined as
 \begin{equation}
-\text{VS}(\breve{\bm{F}}, \bm{y}_{T+h}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{T+h,i} - y_{T+h,j}|^p - \frac{1}{B} \displaystyle\sum_{k=1}^{B} |\breve{Y}^k_{T+h,i}-\breve{Y}^k_{T+h,j}|^p\right)^2.
+\text{VS}(\breve{F}, \bm{y}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{i} - y_{j}|^p - E_{\breve{Y}_i,\breve{Y}_j} |\breve{Y}^k_{i}-\breve{Y}^k_{j}|^p\right)^2.
 \end{equation}
@@
 \begin{theo}[Impropriety of log score]
-	When the true data generating process is a coherent measure, then the log score is improper with respect to the class of incoherent measures.
+	When the true data generating process is coherent, then the log score is improper with respect to the class of incoherent measures.
 \end{theo}
@@
 An example of the $n\times n$ ${\bm U}$ could be the matrix of left singular vectors of ${\bm S}$.
-For a non-degenerate probability measure on $\mathbb{R}^n$, the density is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^n$.
+%For a non-degenerate probability measure on $\mathbb{R}^n$, the density is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^n$.
 %For a coherent probability measure the density after rotation is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^m$.
 
-Consider the case where the true density is $f_1(\bm{z}^{(1)}_t)\mathbb{1}\left({\bm{z}^{(2)}_t}\right)$, and is compared to an incoherent density is given by $f_1(\bm{z}^{(1)}_t)f_2(\bm{z}^{(2)}_t)$, where $f_2$ is highly concentrated around $0$ but still a proper density.
+Consider the case where the true predictive density is $f_1({\bm z}^{(1)}_t)\mathbb{1}\left({\bm z}^{(2)}_t={\bm 0}\right)$, and we evaluate an incoherent density is given by $f_1({\bm z}^{(1)}_t)f_2({\bm z}^{(2)}_t)$, where $f_2$ is highly concentrated around $0$ but still a non-degenerate.
 For example $f_2$ may be Gaussian with variance $\sigma^2{\bm I}$ with $\sigma^2 < (2\pi)^{-1}$.
-The log score under the true DGP is
+The log score under the true data generating process is
 $$
-S\left(\tilde{f},\bm{z}^{(1)}_t\right) = -\log f_1\left(\bm{z}^{(1)}_t\right),
+S\left(\tilde{f},{\bm z}^{(1)}_t\right) = -\log f_1\left({\bm z}^{(1)}_t\right),
 $$
@@
 
-After taking expectations $ES(f,f) > ES(\hat{f},f)$, violating the condition \eqref{eq:(3.1.)} for a proper scoring rule.  
+After taking expectations $ES(f,f) > ES(\hat{f},f)$, violating the condition in Equation~\eqref{eq:(3.1.)} for a proper scoring rule.  
 \end{proof}
 
-A similar issue also arises when discrete random variables are modelled as if they were continuous, an issue discussed in Section 4.1, page 366 of \cite{Gneiting2007}.
-This implies that the log score should not be used to evaluate multivariate densities with degeneracies and should be avoided when comparing reconciled and unreconciled probabilistic forecasts.
+A similar issue also arises when discrete random variables are modelled as if they were continuous, an issue discussed in Section 4.1 of \cite{Gneiting2007}.
+This implies that the log score should be avoided when comparing reconciled and unreconciled probabilistic forecasts.
 
@@
 This may suggest that it is adequate to merely compare two coherent forecasts to  one  another using  the basis series only.
-We now show how this is  dependent on the specific scoring rule used.
+We now show how this  depends on the specific scoring rule used.
 
@@
 This term depends  only on the structure of the  hierarchy and is fixed across different reconciliation methods.
-Therefore if one method achieves a lower expected log score compared to an alternative method  when assessed using the bottom level series, the same ordering is preserved when an assessment is made on the basis of the full hierarchy.
+Therefore if one method achieves a lower expected log score compared to an alternative method  using the bottom level series only, the same ordering is preserved when an assessment is made on the basis of the full hierarchy.
 
@@
 
-The properties of multivariate scoring rules in the context of evaluating reconciled probabilistic forecasts in Table~\ref{tab:prop}.
+The properties of multivariate scoring rules in the context of evaluating reconciled probabilistic forecasts are summarised in Table~\ref{tab:prop}.
 

### 2018-07-06 ProbabilisticCoherence.tex
Cleanup of simulation and conclusions

@@
 We now turn our attention to comparing different reconciliation methods in a simulation study where the data is conditionally Gaussian.
-We choose the Gaussian case due to its analytical tractability which allows for evaluation on the basis of all scoring rules (including the log score).
+We choose the Gaussian case due to its analytical tractability which allows for evaluation using all scoring rules (including the log score).
 The non-Gaussian case lies beyond the scope of this simulation study, but can be handled by a bootstrapping approach proposed in separate work.
@@
 $$
-and similar inequalities hold when $\varepsilon_{AA,t}$ is replaced by $\varepsilon_{AB,t}$, $\varepsilon_{BA,t}$ and $\varepsilon_{BB,t}$ in the second and third terms.
+and similar inequalities hold when $\varepsilon_{AA,t}$ is replaced by $\varepsilon_{AB,t}$, $\varepsilon_{BA,t}$ and $\varepsilon_{BB,t}$ in the third term.
 %Therefore
@@
 %$$\bm{l}_1\bm{\Sigma} \bm{l}_1' - \bm{l}_2\bm{\Sigma} \bm{l}_2' \le \sigma^2_v \le \frac{4}{3}(\sigma^2_u + \bm{l}_3\bm{\Sigma} \bm{l}_3' - \bm{l}_2\bm{\Sigma} \bm{l}_2').$$
-The values of $\bm{\Sigma}$, $\sigma^2_u$ and $\sigma^2_v$, that we use and which satisfy these constraints are:
-$\bm{\Sigma} =
+The values of $\bm{\Sigma}$, $\sigma^2_u$ and $\sigma^2_v$, that we use and which satisfy these constraints are $\sigma^2_u = 19$, $\sigma^2_u = 18$ and
+$$
+\bm{\Sigma} =
 \begin{pmatrix}
@@
 0.4 & 1.4 & 1.8 & 3.0 \\
-\end{pmatrix}$,
-$\sigma^2_u = 19$ and $\sigma^2_u = 18$ in our simulation setting.
-
-We generate data a sample size of $T=501$.
+\end{pmatrix}\,.
+$$
+
+We generate data with a sample size of $T=501$.
 Univariate ARIMA models are selected for each series using the \textit{auto.arima} function in the \textit{forecast} package \citep{hyndman2017forecasting} in R \citep{Rcore}.
-The same package was used to fit each series independently using the first 500 observations, and evaluate 1-step ahead base (incoherent) probabilstic forecasts.
-These were then reconciled using different projections summarzied in Table~\ref{table:2}.
-This process was replicated using $1000$ different data sets from the same data generating processes.\todo{Are the DGPs the same in all cases?}
+The same package was used to fit each series independently using the first 500 observations, and evaluate 1-step ahead base (incoherent) probabilistic forecasts.
+These were then reconciled using different projections summarised in Table~\ref{table:2}.
+This process was replicated using $1000$ different data sets from the same data generating processes.
 
@@
 To facilitate comparisons, we report skill scores \citep{Gneiting2007}.
-For a given forecasting method, evaluated by a particular scoring rule $S(\cdot)$, the skill score %is calculated as
+For a given forecasting method, evaluated by a particular scoring rule, the skill score %is calculated as
 %\begin{equation}
@@
 Overall, the MinT methods provide the best performance irrespective of the scoring rule, and all methods that reconcile using information at all levels of the forecast improve upon unreconciled forecasts.
-Bottom up forecasts perform even worse than unreconciled forecasts.
+Bottom up forecasts perform even worse than unreconciled forecasts in some cases.
 
@@
 When broken down in this fashion, the methods based on MinT perform best for all series and always outperform bottom up and unreconciled forecasts.
-The same cannot be said for OLS which performs worse than bottom up and incoherent forecasts on every individual series\todo{Puzzling it does so bad, but outperforms unreconciled on joint evaluation}.
 
@@
 By redefining coherent forecasts and forecast reconciliation in geometric terms we have established two new theoretical results that support the use of projections for point forecast reconciliation, and crucially have extended these concepts to probabilistic forecasting.
-We show that for elliptical distributions, the true predictive density can be recovered by linear reconciliation and establish conditions for which this linear mapping is a projection.
+We show that for elliptical distributions, the true predictive density can be recovered by linear reconciliation and establish conditions for when this linear mapping is a projection.
 Although this optimal projection cannot feasibly be obtained in practice, a projection similar to the MinT procedure provides a good approximation in practice.

### 2018-07-07 ProbabilisticCoherence.tex
Improved wording for abstract and intro

@@
 
-\theoremstyle{theo}
+%\theoremstyle{theo}
 \newtheorem{theo}{Theorem}[section]
@@
 \begin{abstract}
-  Adjusting forecasts to ensure coherence with aggregation constraints that hold for real data - a process known as forecast reconiliation - is extended from point forecasts to probabilistic forecasts.
-This is achieved by redefining forecast reconciliation in terms of linear mappings in general, and projections more specifically.
-New theorems establish that the true predictive distribution can be recovered in the elliptical case by a linear mapping and general conditions are derived for when this linear mapping is a projection.
-A geometric interpretation is also used to prove two new theoretical results for point forecasting; that  reconciliation via projection a) preserves unbiasedness and b) dominates unreconciled forecasts in a mean squared error sense.
-Strategies for forecast evaluation based on scoring rules are discussed and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive disstribution coheres with aggregation constraints.
-Finally evidence from simulation study show that reconciliation based on an oblique projection, derived from the MinT method of \cite{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
+  Forecast reconciliation involves adjusting forecasts to ensure coherence with aggregation constraints.
+We extend this concept from point forecasts to probabilistic forecasts by redefining forecast reconciliation in terms of linear mappings in general, and projections more specifically.
+New theorems establish that the true predictive distribution can be recovered in the elliptical case by a linear mapping, and general conditions are derived for when this linear mapping is a projection.
+A geometric interpretation is also used to prove two new theoretical results for point forecasting; that reconciliation via projection both preserves unbiasedness and dominates unreconciled forecasts in a mean squared error sense.
+Strategies for forecast evaluation based on scoring rules are discussed, and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive distribution coheres with aggregation constraints.
+Finally, evidence from a simulation study shows that reconciliation based on an oblique projection, derived from the MinT method of \citet{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
 \end{abstract}
 
-%
 \section{Introduction}\label{sec:intro}
+
 %Sketch narrative to tell
@@
 Large collections of time series often follow some aggregation structure.
-For example, the electricity demand of a country can be disaggregated according to a geographical hierarchy of states, cities, and individual households or by a temporal hierarchy of yearly, quarterly and monthly demand.
+For example, the electricity demand of a country can be disaggregated according to a geographic hierarchy of states, cities, and individual households, or by a temporal hierarchy of yearly, quarterly and monthly demand.
 In these so-called hierarchical time series, forecasts are often required for all individual series.
-To ensure aligned decision making it is important for forecasts at the most disaggregated - or bottom-level - to add up to forecasts at more aggregated - or higher - levels.
-This property is referred to as ``coherence''.
+To ensure aligned decision making, it is important for forecasts at the most disaggregated level add up to forecasts at more aggregated levels.
+This property is called ``coherence''.
 This issue has been extensively covered for point forecasting in a literature we review below, while the case of probabilistic forecasting is a gap that we seek to address in this work.
 
-Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level.
-To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$
-and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.
-In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (Series $AA$, $AB$, $BA$ and $BB$) and then summed to recover all top level-series.
-Alternatively, in the top-down approach \citep{Gross1990} a top-level forecast is first produced (Series $Tot$) and bottom level forecasts are recovered as  historical or forecasted proportions of the top-level forecast.
-A middle-out approach is a hybrid between these two that for the hierarchy below would produce first stage forecasts for Series $A$ and $B$.
+Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level of the hierarchy.
+To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$ and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.
+In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (Series $AA$, $AB$, $BA$ and $BB$) and then summed to recover all higher-level series.
+Alternatively, in the top-down approach \citep{Gross1990}, a top-level forecast is first produced (Series $Tot$) and bottom level forecasts are recovered by disaggregating the forecast using either historical or forecasted proportions.
+A middle-out approach is a hybrid between these two, that for the hierarchy below would produce first stage forecasts for Series $A$ and $B$.
 
@@
 Since these so-called `base' forecasts are rarely coherent in practice, they are subsequently adjusted or `reconciled' to ensure coherence.
-To  date reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators.
-These include Ordinary Least Squares {OLS} \cite{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017} and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017}, more commonly referred to as MinT since it minimises the trace of  the squared error matrix.
-These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and in some sense hedge against the risk of model misspecification at a single level.
-
-A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \cite[see][and references therein]{Gneiting2014}.
-Indeed to the best of our knowledge, the as yet unpublished work of \cite{BenTaieb2017} is the only paper to deal with the issue of coherent probabilistic forecasts, and although the means of the predictive distributions are reconciled, the overall distributions are constructed in a bottom up fashion.
+To date, reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators.
+These include Ordinary Least Squares {OLS} \citep{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix.
+These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and, in some sense, hedge against the risk of model misspecification at a single level.
+
+A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \citep[see][and references therein]{Gneiting2014}.
+Indeed to the best of our knowledge, the (as yet unpublished) work of \citep{BenTaieb2017} is the only paper to deal with the issue of coherent probabilistic forecasts, and although they reconcile the means of the predictive distributions, the overall distributions are constructed in a bottom-up fashion rather than use a reconciliation process.
 In contrast, the main objective of our paper is to generalise both coherence and reconciliation from point to probabilistic forecasting.
@@
 In addition to being highly intuitive, this allows us to establish a number of theoretical results.
-We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts while the second shows that reconciled forecasts dominate unreconciled forecasts since projections are bounded operators.
-We provide definitions of coherence and forecast reconciliation in the probabilistic setting and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation.
+We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts, while the second shows that reconciled forecasts dominate unreconciled forecasts since projections are bounded operators.
+We provide definitions of coherence and forecast reconciliation in the probabilistic setting, and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation.
 We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class.
@@
 We also cover the issue of forecast evaluation of probabilistic forecasts via scoring rules.
-In particular we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.
-As such we recommend the use of the energy score and variogram score for comparing reconciled to unreconciled forecasts.
+In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.
+As such we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts.
 Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.
@@
 The remainder of the papers is structured as follows.
-In section \ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.
+In Section~\ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.
 Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results.
-In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian} and Section~\ref{sec:conclusions} concludes.
+In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules, while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian}.
+Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.
 
@@
 In the first stage, the forecasts of all series are independently obtained by fitting univariate models for individual series in the hierarchy.
-It is very unlikely that these forecasts are coherent.
+It is unlikely that these forecasts are coherent.
 Thus in the second stage, these forecasts are optimally combined through a regression model to obtain coherent forecasts.
@@
 %\section{Hierarchical Time Series}\label{sec:notation}
+
 \section{Coherent forecasts}\label{sec:definitions}
+
 \subsection{Notation and Preliminaries}\label{sec:notation}
@@
 For example for the hierarchy in Figure~\ref{fig1}, $m=4$ and $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.
-The hierarchical structure of the data imply the following holds for all $t$
+The hierarchical structure of the data imply the following holds for all $t$:
 \begin{equation}
@@
 $$
-
 where $\bm{I}_4$ is a $4\times 4$ identity matrix.
@@
   \end{equation}
-
 \end{definition}
@@
 Here, $\bm{\hat{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, while $\bm{\hat{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}.
-Also $\tau = \frac{\sum_{i \ne j}\hat{\text{Var}}(\hat{w}_{ij})}{\sum_{i \ne j}{\hat{w}}^2_{ij}}$ where $w_{ij}$ are elements of $\hat{\bm W}^{sam}$.}\label{table:2}
+Also $\tau = \frac{\sum_{i \neq j}\hat{\text{Var}}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$ where $w_{ij}$ are elements of $\hat{\bm W}^{sam}$.}\label{table:2}
 	\centering\setstretch{1.5}
@@
 For example OLS minimises the Euclidean distance between $\hat{\bm y}$ and $\tilde{\bm y}$.
-\cite{Wickramasuriya2017} while MinT
+\citet{Wickramasuriya2017} while MinT
 minimises the Mahalonobis distance between $\hat{\bm y}$ and $\tilde{\bm y}$.
@@
 \begin{proof}
-	Since the aggregation constraints must hold for all realisations, ${\bm y}_{t+h}\in\frak{s}$ and ${\bm y}_{t+h}={\bm S}{\bm G}{\bm y}_{t+h}$ whenever ${\bm S}{\bm G}$ is a projection.  Therefore 
+	Since the aggregation constraints must hold for all realisations, ${\bm y}_{t+h}\in\mathfrak{s}$ and ${\bm y}_{t+h}={\bm S}{\bm G}{\bm y}_{t+h}$ whenever ${\bm S}{\bm G}$ is a projection. Therefore
 	\begin{align}
@@
 In this limiting case, the energy score only measures the accuracy of the forecast mean, and not the entire distribution and the energy score is proper, but not strictly proper.
-\citet{Pinson2013a} also argues that the energy score has very low discriminative ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
+\citet{Pinson2013a} also argues that the energy score has low discriminative ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
 
@@
 
-A similar issue also arises when discrete random variables are modelled as if they were continuous, an issue discussed in Section 4.1 of \cite{Gneiting2007}.
+A similar issue also arises when discrete random variables are modelled as if they were continuous, an issue discussed in Section 4.1 of \citet{Gneiting2007}.
 This implies that the log score should be avoided when comparing reconciled and unreconciled probabilistic forecasts.

### 2018-07-08 ProbabilisticCoherence.tex
Updating in Dubai

@@
 Throughout the paper, we will follow notational conventions used in \citet{Wickramasuriya2017} as much as possible.
-A {\em hierarchical time series} is a collection of $n$ variables where some variables are aggregates of other variables and we let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprised of observations of all variables in the hierarchy at time $t$.
-For example for the hierarchy in Figure~\ref{fig1}, $n=7$ and $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.
-The {\em bottom level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables, we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.
-For example for the hierarchy in Figure~\ref{fig1}, $m=4$ and $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.
+A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables.
+We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$.
+For example, for the hierarchy in Figure~\ref{fig1}, $n=7$ and $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.
+The \emph{bottom level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.
+For example, for the hierarchy in Figure~\ref{fig1}, $m=4$ and $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.
 The hierarchical structure of the data imply the following holds for all $t$:
@@
   \bm{S} = \begin{pmatrix}
-               1& 1 &1 &1  \\
-               1 &1 & 0 &0 \\
-               0&0  & 1 & 1 \\
+               1 & 1 & 1 & 1  \\
+               1 & 1 & 0 & 0 \\
+               0 & 0 & 1 & 1 \\
                & \multicolumn{2}{c}{\bm{I}_4} &
@@
 $$
-where $\bm{I}_4$ is a $4\times 4$ identity matrix.
+where $\bm{I}_4$ is the $4\times 4$ identity matrix.
 
@@
 
-It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect aggregation constraints.
-We follow other authors \citep{Wickramasuriya2017, FPP2018} in using the nomenclature {\em coherence} to describe this property.
+It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect the inherent aggregation constraints.
+We follow other authors \citep{Wickramasuriya2017, FPP2018} in using the nomenclature \emph{coherence} to describe this property.
 %While coherent point forecasts have been discussed many times previously, the definitions of coherence previously given are vague and are not easily extended to the situation of probabilistic forecasting.
-We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem thus facilitating the development of the probabilistic forecast reconciliation in section~\ref{sec:reconciliation}.
+We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem, thus facilitating the development of the probabilistic forecast reconciliation in Section~\ref{sec:reconciliation}.
 
 \begin{definition}[Coherent subspace]\label{def:cohspace}
- The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e. $\mathfrak{s}=\mbox{span}(\bm{S})$, is defined as the {\em coherent space}.
+ The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e. $\mathfrak{s}=\mbox{span}(\bm{S})$, is defined as the \emph{coherent space}.
 \end{definition}
 
-Also at times is will be useful to think of pre-multiplication by $\bm{S}$ as a linear mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$ in which case we use the notation $s(.)$.
-Although the codomain of $s(.)$ is $\mathbb{R}^n$ its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.
+It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a linear mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$.
+Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.
 
@@
     ]
-
     \node at (2,3) {$s$};
-
     \node at (0,5) {$\mathbb{R}^m$(domain of $s$)};
@@
     %\node[bullet,label=below:$f(x)$] at (4,2.5){};
-
     \draw (0,2.5) ellipse (1.02cm and 2.2cm);
@@
     \draw (4,2.5) ellipse (0.51cm and 1.1cm);
-
     \draw[projection, label=below:$f$] (0.3,2.5) -- (3.8,2.5) ;
-
     \end{tikzpicture}
-    \newline
   \end{center}
@@
 \end{definition}
-A probabilistic forecast for time $t+h$ is coherent if uncertainty in ${\bm y}_{t+h}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.
+A probabilistic forecast for time $t+h$ is coherent if uncertainty in $\bm{y}_{t+h}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.
 
@@
 
-These definitions of the coherent space $\mathfrak{s}$ and coherent point and probabilistic forecasts are defined in terms of the mapping $s(.)$ and may give the impression that the bottom level series play an important role in the definition.
-However, alternative definitions could be formed using any set of basis vectors that spans $\mathfrak{s}$.
+These definitions of the coherent space $\mathfrak{s}$, and coherent point and probabilistic forecasts in terms of the mapping $s(.)$, may give the impression that the bottom level series play an important role in the definition.
+However, alternative definitions could be formed using any set of basis vectors that span $\mathfrak{s}$.
 For example, consider the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$.
-In this case the matrix $\bm{S}$ has columns $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$ and premultiplying by $\bm{S}$ transforms arbitrary values of $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy.
+In this case the matrix $\bm{S}$ has columns $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$, and premultiplying by $\bm{S}$ transforms arbitrary values of $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy.
 However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy.
@@
 In general, we call the series (or linear combinations thereof) used in the definitions of coherence \textit{basis series}.
-Unless stated otherwise, we will always assume that the basis series are the bottom level series as in Definition~\ref{def:cohpoint} and Defintion~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.
+Unless stated otherwise, we will always assume that the basis series are the bottom level series as in Definition~\ref{def:cohpoint} and Definition~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.
 
@@
 According to their definition, probabilistic forecasts are coherent when a convolution of forecast distributions of disaggregate series is identical to the forecast distribution of the corresponding aggregate series.
-Their definition is consistent with our definition, our reason for providing a different definition is that the geometric understanding of coherence will facilitate our definitions of point and probabilistic forecast reconciliation to which we now turn our attention.
+Their definition is consistent with our definition; our reason for providing a different definition is that the geometric understanding of coherence will facilitate our definitions of point and probabilistic forecast reconciliation to which we now turn our attention.
 
@@
 Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ using information up to and including time $t$.
-Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively and $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})={\bm G}{\bm y}+{\bm d}$.
+Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively, and let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})=\bm{G}\bm{y}+\bm{d}$.
+
 \begin{definition}\label{def:reconpoint}
@@
 	\begin{equation}
-    \tilde{\bm{y}}_{t+h|t}=\bm{S}\left(\bm{G}\hat{\bm{y}}_{t+h|t}+{\bm d}\right)\,.
+	  \tilde{\bm{y}}_{t+h|t}=\bm{S}\left(\bm{G}\hat{\bm{y}}_{t+h|t}+\bm{d}\right)\,.
 	\end{equation}
@@
 
-Many choices of $g(.)$ currently extant in the literature including the OLS, WLS and MinT methods are special cases where $s\circ g$ is a projection.
-These can be defined so that ${\bm G}=\left({\bm R'_{\perp}}{\bm S}\right)^{-1}{\bm R}_{\perp}'$ and ${\bm d}={\bm 0}$.
-Here, ${\bm R_{\perp}}$ is a $n\times m$ orthogonal complement to the an $n \times (n-m)$ matrix $\bm{R}$ where the columns of the latter span the null space of $\mathfrak{s}$.
+Many choices of $g(.)$ currently extant in the literature, including the OLS, WLS and MinT methods, are special cases where $s\circ g$ is a projection.
+These can be defined so that $\bm{G}=\left({\bm{R}'_{\perp}}\bm{S}\right)^{-1}\bm{R}_{\perp}'$ and $\bm{d}=\bm{0}$.
+Here, ${\bm{R}_{\perp}}$ is a $n\times m$ orthogonal complement to the an $n \times (n-m)$ matrix $\bm{R}$ where the columns of the latter span the null space of $\mathfrak{s}$.
 For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
 In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
-For this example, ${\bm R}_\perp'={\bm S}$ and reconciliation corresponds to the OLS method.
-For the case where ${\bm R}_\perp'\neq{\bm S}$, for example WLS and MinT, there are two possible interpretations.
+For this example, $\bm{R}_\perp'=\bm{S}$ and reconciliation corresponds to the OLS method.
+For the case where $\bm{R}_\perp'\neq\bm{S}$, for example WLS and MinT, there are two possible interpretations.
 One is that these are oblique projections in Euclidean space where the columns of $\bm{R}$ are `directions' along which incoherent point forecasts are projected onto the coherent space $\mathfrak{s}$.
-Alternatively, since ${\bm R}_\perp'$ is usually written in the form ${\bm S}'{\bm W}^{-1}$, these projections can be thought of as orthogonal projections after pre-multiplying by ${\bm W^{-1/2}}$.
+Alternatively, since $\bm{R}_\perp'$ is usually written in the form $\bm{S}'{\bm{W}}^{-1}$, these projections can be thought of as orthogonal projections after pre-multiplying by ${\bm{W}^{-1/2}}$.
 A schematic providing a geometric interpretation of point reconciliation is given in Figure~\ref{fig:pointfr_sch}, while and are Table~\ref{table:2} summarises existing reconciliation methods.
@@
 Here, $\bm{\hat{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, while $\bm{\hat{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}.
-Also $\tau = \frac{\sum_{i \neq j}\hat{\text{Var}}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$ where $w_{ij}$ are elements of $\hat{\bm W}^{sam}$.}\label{table:2}
+Also $\tau = \frac{\sum_{i \neq j}\hat{\text{Var}}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$ where $w_{ij}$ are elements of $\hat{\bm{W}}^{sam}$.}\label{table:2}
 	\centering\setstretch{1.5}
@@
 	\caption{Summary of probabilistic point reconciliation.
-The mapping $s\circ g$ projects the unreconciled forecast $\hat{\bm y}$ onto $\mathfrak{s}$.
+The mapping $s\circ g$ projects the unreconciled forecast $\hat{\bm{y}}$ onto $\mathfrak{s}$.
 Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:pointfr_sch}
@@
 
-Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of ${\bm R}$.
-For example OLS minimises the Euclidean distance between $\hat{\bm y}$ and $\tilde{\bm y}$.
+Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$.
+For example OLS minimises the Euclidean distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$.
 \citet{Wickramasuriya2017} while MinT
-minimises the Mahalonobis distance between $\hat{\bm y}$ and $\tilde{\bm y}$.
+minimises the Mahalonobis distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$.
 Bottom up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom level series.
@@
 Before generalising the concept of point reconciliation to probabilistic forecasts we state two theorems that motivate the use of projections for point forecast reconciliation.
-First, let ${\bm \mu}_{t+h|t}:=E({\bm y}_{t+h}|{\bm y}_{1},\dots,{\bm y}_{t})$ and assume $\hat{\bm y}_{t+h|t}$ is an unbiased prediction, that is $E_{1:t}\left(\hat{\bm y}_{t+h|t}\right)=\mu_{t+h|t}$ where the subscript $1:t$ denotes an expectation taken over the training sample.
+First, let $\bm{\mu}_{t+h|t}:=E(\bm{y}_{t+h}|\bm{y}_{1},\dots,\bm{y}_{t})$ and assume $\hat{\bm{y}}_{t+h|t}$ is an unbiased prediction, that is $E_{1:t}\left(\hat{\bm{y}}_{t+h|t}\right)=\mu_{t+h|t}$ where the subscript $1:t$ denotes an expectation taken over the training sample.
 
 \begin{theo}[Unbiasedness preserving property]
-  For unbiased $\hat{\bm y}_{t+h|t}$, the reconciled point forecast will also be an unbiased prediction as long as $s\circ g$ is a projection
+  For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast will also be an unbiased prediction as long as $s\circ g$ is a projection
 \end{theo}
@@
 	\begin{align*}
-	E_{1:t}\left(\tilde{\bm y}_{t+h|t}\right)&=E_{1:t}\left({\bm S}{\bm G}\hat{\bm y}_{t+h|t}\right)\\
-	&={\bm S}{\bm G}E_{1:t}\left(\hat{\bm y}_{t+h|t}\right)\\
-    &={\bm S}{\bm G}{\bm \mu}_{t+h|t}\\
+	E_{1:t}\left(\tilde{\bm{y}}_{t+h|t}\right)&=E_{1:t}\left(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}\right)\\
+	&=\bm{S}\bm{G}E_{1:t}\left(\hat{\bm{y}}_{t+h|t}\right)\\
+    &=\bm{S}\bm{G}\bm{\mu}_{t+h|t}\\
 	\end{align*}
-	Since the aggregation constraints hold for the true data generating process ${\bm \mu}_{t+h|t}$ must lie in $\mathfrak{s}$.
-If ${\bm S}{\bm G}$ is a projection then it is equivalent to the identity map for all vectors that lie in its range.
-Therefore ${\bm S}{\bm G}{\bm \mu}_{t+h|t}={\bm \mu}_{t+h|t}$ when ${\bm S}{\bm G}$ is a projection matrix.
+	Since the aggregation constraints hold for the true data generating process $\bm{\mu}_{t+h|t}$ must lie in $\mathfrak{s}$.
+If $\bm{S}\bm{G}$ is a projection then it is equivalent to the identity map for all vectors that lie in its range.
+Therefore $\bm{S}\bm{G}\bm{\mu}_{t+h|t}=\bm{\mu}_{t+h|t}$ when $\bm{S}\bm{G}$ is a projection matrix.
 \end{proof}
 We note the same result does not hold for general $g$ even when the range of $s\circ g$ is $\mathfrak{s}$.
-Now let ${\bm y}_{t+h}$ be the realisation of the data generating process at time $t+h$ and let $||{\bm v}||_2$ be the L2 norm of vector ${\bm v}$.
+Now let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$ and let $||\bm{v}||_2$ be the L2 norm of vector $\bm{v}$.
 The following theorem shows that reconciliation never increases, and in most cases reduces the sum of squared errors of point forecasts.
@@
 \begin{theo}[Distance reducing property]
-	If $\tilde{\bm y}_{t+h|t}={\bm S}{\bm G}\hat{\bm y}_{t+h|t}$ where ${\bm G}$ is such that ${\bm S}{\bm G}$ is an orthogonal projection then the following inequality holds
+	If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$ where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection then the following inequality holds
 	  \begin{equation}
-	    ||(\tilde{\bm y}_{t+h|t}-{\bm y}_{t+h})||^2_2\le||(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||^2_2
+	    ||(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||^2_2\le||(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||^2_2
 	  \end{equation}
@@
 \begin{proof}
-	Since the aggregation constraints must hold for all realisations, ${\bm y}_{t+h}\in\mathfrak{s}$ and ${\bm y}_{t+h}={\bm S}{\bm G}{\bm y}_{t+h}$ whenever ${\bm S}{\bm G}$ is a projection. Therefore
+	Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ whenever $\bm{S}\bm{G}$ is a projection. Therefore
 	\begin{align}
-	||(\tilde{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2&=||({\bm S}{\bm G}\hat{\bm y}_{t+h|t}-{\bm S}{\bm G}{\bm y}_{t+h})||_2\\
-	&=||{\bm S}{\bm G}(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2\\
+	||(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||_2&=||(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})||_2\\
+	&=||\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||_2\\
 	\end{align}
@@
 	 \begin{equation*}
-	 ||{\bm S}{\bm G}(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2\le
-	 ||(\hat{\bm y}_{t+h|t}-{\bm y}_{t+h})||_2
+	 ||\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||_2\le
+	 ||(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||_2
 	 \end{equation*}
 \end{proof}
-The inequality is strict whenever $\hat{\bm y}_{t+h|t}\notin\mathfrak{s}$.
+The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.
 
@@
 	\caption{Summary of probabilistic forecast reconciliation.
-The probability that ${\bm y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that ${\bm y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast.
+The probability that $\bm{y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that $\bm{y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast.
 Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:probfr_sch}
@@
 
-Suppose an unreconciled probabilistic forecast is Gaussian with mean $\hat{\bm \mu}$ and variance-covariance matrix $\hat{\bm \Sigma}$.
+Suppose an unreconciled probabilistic forecast is Gaussian with mean $\hat{\bm{\mu}}$ and variance-covariance matrix $\hat{\bm{\Sigma}}$.
 The subscripts $t+h|t$ are suppressed for brevity.
@@
 \begin{equation}
-  f(\hat{\bm{y}})=(2\pi)^{-n/2}|\hat{\bm{\Sigma}}|^{-1/2}\exp\left\{-\frac{1}{2}\left[(\hat{\bm y}-\hat{\bm \mu})'\hat{\bm{\Sigma}}^{-1}(\hat{\bm y}-\hat{\bm \mu})\right]\right\}
+  f(\hat{\bm{y}})=(2\pi)^{-n/2}|\hat{\bm{\Sigma}}|^{-1/2}\exp\left\{-\frac{1}{2}\left[(\hat{\bm{y}}-\hat{\bm{\mu}})'\hat{\bm{\Sigma}}^{-1}(\hat{\bm{y}}-\hat{\bm{\mu}})\right]\right\}
 \end{equation}
@@
 \begin{equation}
-f(\tilde{\bm b},\tilde{\bm a})=(2\pi)^{-\frac{n}{2}}\Big|\bm{\hat{\Sigma}}\Big|^{-\frac{1}{2}}\Big|(\bm{S} ~  \bm{R})\Big|\exp\left\{-\frac{1}{2}q\right\}\,,
+f(\tilde{\bm{b}},\tilde{\bm{a}})=(2\pi)^{-\frac{n}{2}}\Big|\bm{\hat{\Sigma}}\Big|^{-\frac{1}{2}}\Big|(\bm{S} ~  \bm{R})\Big|\exp\left\{-\frac{1}{2}q\right\}\,,
 \end{equation}
@@
 We now show that the true predictive distribution can be recovered for elliptical distributions via linear reconciliation.
-Here, for any square matrix ${\bm C}$, ${\bm C}^{1/2}$ and ${\bm C}^{-1/2}$ are defined to satisfy ${\bm C}^{1/2}\left({\bm C}^{1/2}\right)'={\bm C}$ and ${\bm C}^{-1/2}\left({\bm C}^{-1/2}\right)'={\bm C}^{-1}$, for example ${\bm C}^{1/2}$ may be obtained via the Cholesky or eigenvalue decompositions.
+Here, for any square matrix $\bm{C}$, $\bm{C}^{1/2}$ and $\bm{C}^{-1/2}$ are defined to satisfy $\bm{C}^{1/2}\left(\bm{C}^{1/2}\right)'=\bm{C}$ and $\bm{C}^{-1/2}\left(\bm{C}^{-1/2}\right)'=\bm{C}^{-1}$, for example $\bm{C}^{1/2}$ may be obtained via the Cholesky or eigenvalue decompositions.
 \begin{theo}[Reconciliation for Elliptical Distributions]
-	Let an unreconciled probabilistic forecast come from the elliptical class with location parameter $\hat{\bm \mu}$ and scale matrix $\hat{\bm \Sigma}$.
-Let the true predictive distribution of ${\bm y}_{t+h|t}$ also belong to the elliptical class with location parameter ${\bm \mu}$ and scale matrix ${\bm \Sigma}$.
-Then the linear reconciliation mapping $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ with $\bm{G}_{opt}={\bm A}{\bm\Sigma}^{-1/2}$ and ${\bm d}_{opt}={\bm \mu}-{\bm S}{\bm G}_{opt}\hat{\bm \mu}$ recovers the true predictive density where ${\bm A}$ is any $m\times n$ matrix such that ${\bm A}{\bm A}'={\bm \Omega}$ and ${\bm \Omega}$ is a sub-matrix of ${\bm \Sigma}$ corresponding to the bottom level series.
+	Let an unreconciled probabilistic forecast come from the elliptical class with location parameter $\hat{\bm{\mu}}$ and scale matrix $\hat{\bm{\Sigma}}$.
+Let the true predictive distribution of $\bm{y}_{t+h|t}$ also belong to the elliptical class with location parameter $\bm{\mu}$ and scale matrix $\bm{\Sigma}$.
+Then the linear reconciliation mapping $g(\breve{\bm{y}})=\bm{G}_{opt}\breve{\bm{y}}+\bm{d}_{opt}$ with $\bm{G}_{opt}={\bm{a}}{\bm\Sigma}^{-1/2}$ and $\bm{d}_{opt}=\bm{\mu}-\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}$ recovers the true predictive density where ${\bm{a}}$ is any $m\times n$ matrix such that ${\bm{a}}{\bm{a}}'=\bm{\Omega}$ and $\bm{\Omega}$ is a sub-matrix of $\bm{\Sigma}$ corresponding to the bottom level series.
 \end{theo}
@@
    Since elliptical distributions are closed under affine transformations, and are closed under marginalisation, reconciliation of an elliptical distribution yields an elliptical distribution (although the unreconciled and reconciled distributions may be different members of the class of elliptical distributions).
-The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}_{opt}{\bm \Sigma}{\bm G}_{opt}'{\bm S}'$ while the location matrix is given by $\bm{S}\bm{G}_{opt}\hat{\bm \mu}+{\bm d}_{opt}$.
+The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}_{opt}\bm{\Sigma}\bm{G}_{opt}'\bm{S}'$ while the location matrix is given by $\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}+\bm{d}_{opt}$.
 The reconciled scale matrix is
    \begin{align*}
-   \tilde{\bm \Sigma}_{opt}=&{\bm S}{\bm A}{\bm\Sigma}^{-1/2}{\bm \Sigma}\left({\bm\Sigma}^{-1/2}\right)'{\bm A}'{\bm S}'\\
-   =&{\bm S}{\bm \Omega}{\bm S}'\\
-   =&{\bm \Sigma}
+   \tilde{\bm{\Sigma}}_{opt}=&\bm{S}{\bm{a}}{\bm\Sigma}^{-1/2}\bm{\Sigma}\left({\bm\Sigma}^{-1/2}\right)'{\bm{a}}'\bm{S}'\\
+   =&\bm{S}\bm{\Omega}\bm{S}'\\
+   =&\bm{\Sigma}
    \end{align*}
-   For the choices of ${\bf G}_{opt}$ and ${\bf d}_{opt}$ given above, the reconciled location vector is
+   For the choices of $\bm{G}_{opt}$ and $\bm{d}_{opt}$ given above, the reconciled location vector is
    \begin{align*}
-   \tilde{\bm \mu}_{opt}=&{\bm S}{\bm G}_{opt}\hat{\bm \mu}+{\bm \mu}-{\bm S}{\bm G}_{opt}\hat{\bm \mu}\\
-   =&{\bm \mu}\\
+   \tilde{\bm{\mu}}_{opt}=& \bm{S}\bm{G}_{opt}\hat{\bm{\mu}}+\bm{\mu}-\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}\\
+   =&\bm{\mu}\\
    \end{align*}
@@
 \begin{theo}[True predictive via projection]
-	Assume that the true predictive distribution is elliptical with location ${\bm \mu}$ and scale ${\bm \Sigma}$.
-Consider reconciliation via a projection $g({\bm y})=({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}{\bm y}$.
-The true predictive distribution can be recovered via reconciliation of an elliptical distribution with location $\hat{\bm \mu}$ and scale $\hat{\bm \Sigma}$  when the following conditions hold.
+	Assume that the true predictive distribution is elliptical with location $\bm{\mu}$ and scale $\bm{\Sigma}$.
+Consider reconciliation via a projection $g(\bm{y})=(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\bm{y}$.
+The true predictive distribution can be recovered via reconciliation of an elliptical distribution with location $\hat{\bm{\mu}}$ and scale $\hat{\bm{\Sigma}}$  when the following conditions hold.
 	\begin{align}
-	sp(\hat{\bm\mu}-{\bm \mu})&\subset sp(\bm{R})\\
-    sp(\hat{\bm \Sigma}^{1/2}-{\bm \Sigma}^{1/2})&\subset sp({\bm R})\\
+	sp(\hat{\bm\mu}-\bm{\mu})&\subset sp(\bm{R})\\
+    sp(\hat{\bm{\Sigma}}^{1/2}-\bm{\Sigma}^{1/2})&\subset sp(\bm{R})\\
 	\end{align}
@@
 	\begin{align*}
-		\tilde{\bm \mu}&={\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}\hat{\bm \mu}\\
-		&={\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}\left(\hat{\bm \mu}+{\bm \mu}-{\bm \mu}\right)\\
-		&={\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}{\bm \mu}+{\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}\left(\hat{\bm \mu}-{\bm \mu}\right)\\
+		\tilde{\bm{\mu}}&=\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\hat{\bm{\mu}}\\
+		&=\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\left(\hat{\bm{\mu}}+\bm{\mu}-\bm{\mu}\right)\\
+		&=\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\bm{\mu}+\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\left(\hat{\bm{\mu}}-\bm{\mu}\right)\\
 	\end{align*}
-  Since ${\bm S}({\bm R}'_{\perp}{\bm S})^{-1}{\bm R}'_{\perp}$ is a projection onto $\mathfrak{s}$ and ${\bm \mu}\in\mathfrak{s}$ the first term simplifies to ${\bm \mu}$.
-If ${\bm \mu}-\hat{\bm \mu}$ lies in the span of ${\bm R}$ then multiplication by ${\bm R}'_{\perp}$ reduces the second term to ${\bm 0}$.
-By a similar argument it can be shown that $\tilde{\bm \Sigma}^{1/2}={\bm \Sigma}^{1/2}$.
+  Since $\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}$ is a projection onto $\mathfrak{s}$ and $\bm{\mu}\in\mathfrak{s}$ the first term simplifies to $\bm{\mu}$.
+If $\bm{\mu}-\hat{\bm{\mu}}$ lies in the span of $\bm{R}$ then multiplication by $\bm{R}'_{\perp}$ reduces the second term to $\bm{0}$.
+By a similar argument it can be shown that $\tilde{\bm{\Sigma}}^{1/2}=\bm{\Sigma}^{1/2}$.
 The closure property of elliptical distributions under affine transformations ensures that the full true predictive distribution can be recovered.
@@
 Although these conditions will rarely hold in practice and only apply to a limited class of distributions they do provide some insight into selecting a projection for reconciliation.
-If the value of $\hat{\bm \mu}$ were equi-probable in all directions then a projection orthogonal to $\mathfrak{s}$ would be a sensible choice for ${\bm R}$ since it would in some sense represent a `median' direction for ${\bm \mu}-\hat{\bm \mu}$.
-However, the one step ahead in-sample errors are usually correlated suggesting that $\hat{\bm \mu}$ is more likely to fall in some directions than others.
+If the value of $\hat{\bm{\mu}}$ were equi-probable in all directions then a projection orthogonal to $\mathfrak{s}$ would be a sensible choice for $\bm{R}$ since it would in some sense represent a `median' direction for $\bm{\mu}-\hat{\bm{\mu}}$.
+However, the one step ahead in-sample errors are usually correlated suggesting that $\hat{\bm{\mu}}$ is more likely to fall in some directions than others.
 As such an orthogonal projection after transformation by the inverse of the one step ahead in-sample errors may be more intuitively appealing.
@@
 
-%However, these expressions do provide some insight on why some choices for ${\bm G}$ in the point forecast reconciliation literature may also work well for probabilistic forecasts.
+%However, these expressions do provide some insight on why some choices for $\bm{G}$ in the point forecast reconciliation literature may also work well for probabilistic forecasts.
 To illustrate, first rearrange the equation for the optimal value of  $\bm{G}_{opt}={\bm\Omega}^{1/2}\hat{\bm\Sigma}^{-1/2}$ as ${\bm\Omega}^{1/2}=\bm{G}_{opt}\hat{\bm\Sigma}^{1/2}$.
-For arbitrary ${\bm G}\hat{\bm\Sigma}^{1/2}$ is an approximation for ${\bm\Omega}^{1/2}$.
+For arbitrary $\bm{G}\hat{\bm\Sigma}^{1/2}$ is an approximation for ${\bm\Omega}^{1/2}$.
 This approximation has similarities with the way bottom level estimates are produced for point forecast reconciliation.
 Rather than mapping a vector of point forecasts to reconcilied bottom level forecasts, the columns of  $\hat{\bm\Sigma}^{1/2}$ are mapped to an approximation of the columns of ${\bm\Omega}^{1/2}$.
-The value for $\tilde{\bm \mu}_{opt}$ includes a projection of $\hat{\bm \mu}$ onto $\mathfrak{s}$.
-While it is infeasible to obtain the translation ${\bm d}$, it is worthwhile noting that this measures the difference between the reconciled mean and true mean.
+The value for $\tilde{\bm{\mu}}_{opt}$ includes a projection of $\hat{\bm{\mu}}$ onto $\mathfrak{s}$.
+While it is infeasible to obtain the translation $\bm{d}$, it is worthwhile noting that this measures the difference between the reconciled mean and true mean.
 
@@
 In contrast, \citet{SCHEUERER2015} have shown that the variogram score has a higher discrimination ability of misspecified means, variances and correlation structures than the energy score.
-When $\breve{\bm Y}$ is a random variable from probabilistic forecast $\breve{F}$, the empirical variogram score is defined as
+When $\breve{\bm{y}}$ is a random variable from probabilistic forecast $\breve{F}$, the empirical variogram score is defined as
 \begin{equation}
@@
 \begin{proof}
-Consider a rotated version of hierarchical time series $\bm{z}_t={\bm U}{\bm y}_t$ so that the first $m$ elements of $\bm{z}_t$ denoted $\bm{z}^{(1)}_t$ are unconstrained, while the remaining $n-m$ elements denoted $\bm{z}^{(2)}_t$ equal $0$ when the aggregation constraints hold.
-An example of the $n\times n$ ${\bm U}$ could be the matrix of left singular vectors of ${\bm S}$.
+Consider a rotated version of hierarchical time series $\bm{z}_t=\bm{U}\bm{y}_t$ so that the first $m$ elements of $\bm{z}_t$ denoted $\bm{z}^{(1)}_t$ are unconstrained, while the remaining $n-m$ elements denoted $\bm{z}^{(2)}_t$ equal $0$ when the aggregation constraints hold.
+An example of the $n\times n$ $\bm{U}$ could be the matrix of left singular vectors of $\bm{S}$.
 %For a non-degenerate probability measure on $\mathbb{R}^n$, the density is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^n$.
@@
 
-Consider the case where the true predictive density is $f_1({\bm z}^{(1)}_t)\mathbb{1}\left({\bm z}^{(2)}_t={\bm 0}\right)$, and we evaluate an incoherent density is given by $f_1({\bm z}^{(1)}_t)f_2({\bm z}^{(2)}_t)$, where $f_2$ is highly concentrated around $0$ but still a non-degenerate.
-For example $f_2$ may be Gaussian with variance $\sigma^2{\bm I}$ with $\sigma^2 < (2\pi)^{-1}$.
+Consider the case where the true predictive density is $f_1(\bm{z}^{(1)}_t)\mathbb{1}\left(\bm{z}^{(2)}_t=\bm{0}\right)$, and we evaluate an incoherent density is given by $f_1(\bm{z}^{(1)}_t)f_2(\bm{z}^{(2)}_t)$, where $f_2$ is highly concentrated around $0$ but still a non-degenerate.
+For example $f_2$ may be Gaussian with variance $\sigma^2{\bm{I}}$ with $\sigma^2 < (2\pi)^{-1}$.
 The log score under the true data generating process is
 $$
-S\left(\tilde{f},{\bm z}^{(1)}_t\right) = -\log f_1\left({\bm z}^{(1)}_t\right),
+S\left(\tilde{f},\bm{z}^{(1)}_t\right) = -\log f_1\left(\bm{z}^{(1)}_t\right),
 $$
@@
 For the log score, suppose the coherent probabilistic forecast has density $f(\bm{b})$.
-The density for the full hierarchy is given by $f(\bm{y})=f(\bm{Sb})=f(\bm{b})J^{-1}$ where $J=\prod_{j=1}^{m}\lambda_j$ is a pseudo-determinant of the non-square  matrix ${\bm S}$ and $\lambda_j$ are the non-zero singular values of ${\bm S}$.
+The density for the full hierarchy is given by $f(\bm{y})=f(\bm{Sb})=f(\bm{b})J^{-1}$ where $J=\prod_{j=1}^{m}\lambda_j$ is a pseudo-determinant of the non-square  matrix $\bm{S}$ and $\lambda_j$ are the non-zero singular values of $\bm{S}$.
 Therefore for any coherent density the log score of the full hierarchy differs from the log score for the bottom level series by the term $log(J)$.
@@
 In the context of two coherent forecasts the same is true of a semi-orthogonal transformation from a lower dimensional basis series to the full hierarchy.
-However,  when ${\bm S}$ is  the usual summing matrix, it is not semi-orthogonal.
+However,  when $\bm{S}$ is  the usual summing matrix, it is not semi-orthogonal.
 As such the energy score computed on the bottom level series will differ from the energy score computed using the full hierarchy and the ordering of different reconciliation methods may change depending on the basis series used.

### 2018-07-08 ProbabilisticCoherence.tex
Some improved English in Section 3

@@
 \usepackage{monashwp}
-\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx}
+\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
 \usepackage{mathrsfs, float, booktabs,todonotes,amsthm}
@@
 In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (Series $AA$, $AB$, $BA$ and $BB$) and then summed to recover all higher-level series.
-Alternatively, in the top-down approach \citep{Gross1990}, a top-level forecast is first produced (Series $Tot$) and bottom level forecasts are recovered by disaggregating the forecast using either historical or forecasted proportions.
+Alternatively, in the top-down approach \citep{Gross1990}, a top-level forecast is first produced (Series $Tot$) and bottom-level forecasts are recovered by disaggregating the forecast using either historical or forecasted proportions.
 A middle-out approach is a hybrid between these two, that for the hierarchy below would produce first stage forecasts for Series $A$ and $B$.
@@
 	\end{center}
-	\caption{Two level hierarchical diagram.}\label{fig1}
+	\caption{A example of a two level hierarchical structure.}\label{fig1}
 \end{figure}
@@
 For example, for the hierarchy in Figure~\ref{fig1}, $n=7$ and $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.
-The \emph{bottom level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.
+The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.
 For example, for the hierarchy in Figure~\ref{fig1}, $m=4$ and $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.
@@
 where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints. For the hierarchy in Figure~\ref{fig1}
-$$
+\[
   \bm{S} = \begin{pmatrix}
@@
            \end{pmatrix},
-$$
+\]
 where $\bm{I}_4$ is the $4\times 4$ identity matrix.
@@
 \begin{definition}[Coherent subspace]\label{def:cohspace}
- The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e. $\mathfrak{s}=\mbox{span}(\bm{S})$, is defined as the \emph{coherent space}.
+ The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e. $\mathfrak{s}=\text{span}(\bm{S})$, is defined as the \emph{coherent space}.
 \end{definition}
@@
     \node at (4,5) {$\mathbb{R}^n$(codomain of $s$)};
-    \node at (4.5,1.0) {$\mathfrak{s}$(image of $s$)};
+    \node at (4.7,2.0) {$\mathfrak{s}$(image of $s$)};
     %\node[bullet,label=below:$f(x)$] at (4,2.5){};
@@
   The measure $\breve{\nu}$ is coherent if it has the property
-  $$
+  \[
     \breve{\nu}(s(\mathcal{B})) = \nu(\mathcal{B}) \quad \forall \mathcal{B} \in \mathscr{F}_{\mathbb{R}^m},
-  $$
+  \]
 \end{definition}
+
 A probabilistic forecast for time $t+h$ is coherent if uncertainty in $\bm{y}_{t+h}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.
@@
 
-These definitions of the coherent space $\mathfrak{s}$, and coherent point and probabilistic forecasts in terms of the mapping $s(.)$, may give the impression that the bottom level series play an important role in the definition.
+These definitions of the coherent space $\mathfrak{s}$, and coherent point and probabilistic forecasts in terms of the mapping $s(.)$, may give the impression that the bottom-level series play an important role in the definition.
 However, alternative definitions could be formed using any set of basis vectors that span $\mathfrak{s}$.
@@
 However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy.
-The definitions above could be made in terms of any series and not just the bottom level series.
+The definitions above could be made in terms of any series and not just the bottom-level series.
 In general, we call the series (or linear combinations thereof) used in the definitions of coherence \textit{basis series}.
-Unless stated otherwise, we will always assume that the basis series are the bottom level series as in Definition~\ref{def:cohpoint} and Definition~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.
+Unless stated otherwise, we will always assume that the basis series are the bottom-level series as in Definition~\ref{def:cohpoint} and Definition~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.
 
@@
 
-Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ using information up to and including time $t$.
+Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ conditional on information up to and including time $t$.
 Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively, and let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})=\bm{G}\bm{y}+\bm{d}$.
@@
 	\begin{equation}
-	  \tilde{\bm{y}}_{t+h|t}=\bm{S}\left(\bm{G}\hat{\bm{y}}_{t+h|t}+\bm{d}\right)\,.
+	  \tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{G}\hat{\bm{y}}_{t+h|t}+\bm{d})\,.
 	\end{equation}
@@
 
-Many choices of $g(.)$ currently extant in the literature, including the OLS, WLS and MinT methods, are special cases where $s\circ g$ is a projection.
-These can be defined so that $\bm{G}=\left({\bm{R}'_{\perp}}\bm{S}\right)^{-1}\bm{R}_{\perp}'$ and $\bm{d}=\bm{0}$.
-Here, ${\bm{R}_{\perp}}$ is a $n\times m$ orthogonal complement to the an $n \times (n-m)$ matrix $\bm{R}$ where the columns of the latter span the null space of $\mathfrak{s}$.
+Several choices of $g(.)$ currently extant in the literature, including the OLS, WLS and MinT methods, are special cases where $s\circ g$ is a projection.
+These can be defined so that $\bm{G}=({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ and $\bm{d}=\bm{0}$.
+Here, ${\bm{R}_{\perp}}$ is a $n\times m$ orthogonal complement to the $n \times (n-m)$ matrix $\bm{R}$, where the columns of the latter span the null space of $\mathfrak{s}$.
 For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
@@
 Alternatively, since $\bm{R}_\perp'$ is usually written in the form $\bm{S}'{\bm{W}}^{-1}$, these projections can be thought of as orthogonal projections after pre-multiplying by ${\bm{W}^{-1/2}}$.
-A schematic providing a geometric interpretation of point reconciliation is given in Figure~\ref{fig:pointfr_sch}, while and are Table~\ref{table:2} summarises existing reconciliation methods.
+A schematic providing a geometric interpretation of point reconciliation is given in Figure~\ref{fig:pointfr_sch}, while Table~\ref{table:2} summarises existing reconciliation methods.
 
@@
 	\caption{Summary of reconciliation methods that are projections.
-Here, $\bm{\hat{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, while $\bm{\hat{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}.
-Also $\tau = \frac{\sum_{i \neq j}\hat{\text{Var}}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$ where $w_{ij}$ are elements of $\hat{\bm{W}}^{sam}$.}\label{table:2}
+Here, $\hat{\bm{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, $\hat{\bm{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}, $\hat{\bm{W}}^{wls}$ is the diagonal matrix with diagonal elements $w_{ii}$, and $\tau = \frac{\sum_{i \neq j}\hat{\text{Var}}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$, where $w_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{W}}^{sam}$.}\label{table:2}
 	\centering\setstretch{1.5}
@@
 		MinT(Sample)    &
-		$\bm{\hat{W}}^{sam}$ &
-		$\bm{S}'(\bm{\hat{W}}^{sam})^{-1}$ \\
+		$\hat{\bm{W}}^{sam}$ &
+		$\bm{S}'(\hat{\bm{W}}^{sam})^{-1}$ \\
 		MinT(Shrink)    &
-		$\tau\text{Diag}(\bm{\hat{W}}^{sam}) + (1-\tau)\bm{\hat{W}}^{sam}$ &
-		$\bm{S}'(\bm{\hat{W}}^{shr})^{-1}$ \\
+		$\tau\text{Diag}(\hat{\bm{W}}^{sam}) + (1-\tau)\hat{\bm{W}}^{sam}$ &
+		$\bm{S}'(\hat{\bm{W}}^{shr})^{-1}$ \\
 		WLS       &
-		$\text{Diag}(\bm{\hat{W}}^{shr})$ &
-		$\bm{S}'(\bm{\hat{W}}^{wls})^{-1}$ \\
+		$\text{Diag}(\hat{\bm{W}}^{shr})$ &
+		$\bm{S}'(\hat{\bm{W}}^{wls})^{-1}$ \\
 		\bottomrule
@@
 
-%$$
+%\[
 %\bm{S} =
@@
 %\end{pmatrix}.
-%$$
+%\]
 %
@@
 The mapping $s\circ g$ projects the unreconciled forecast $\hat{\bm{y}}$ onto $\mathfrak{s}$.
-Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:pointfr_sch}
+Since the smallest hierarchy involves three dimensions, this figure is only a schematic.}\label{fig:pointfr_sch}
 \end{figure}
 
-To illustrate further note that the columns of $\bm{S}$ and $\bm{R}$ provide a basis for $\mathbb{R}^n$.
-As such any incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$, can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$.
-Let $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$ respectively after a change of basis.
-The process of reconciliation involves setting the values of the reconciled bottom-level series to be $\tilde{\bm{b}}_{t+h|t}$ and setting $\tilde{\bm{a}}_{t+h}=\bm{0}$ to ensure coherence.
+The columns of $\bm{S}$ and $\bm{R}$ provide a basis for $\mathbb{R}^n$.
+As such, any incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$, can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$.
+Let $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$ respectively, after a change of basis.
+The process of reconciliation involves setting the values of the reconciled bottom-level series to be $\tilde{\bm{b}}_{t+h|t}$, and setting $\tilde{\bm{a}}_{t+h}=\bm{0}$ to ensure coherence.
 From properties of linear algebra it follows that
@@
 \[
-\tilde{\bm{y}}_{t+h|t} = \bm{S}\tilde{\bm{b}}_{t+h|t}
+  \tilde{\bm{y}}_{t+h|t} = \bm{S}\tilde{\bm{b}}_{t+h|t}.
 \]
@@
 Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$.
-For example OLS minimises the Euclidean distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$.
-\citet{Wickramasuriya2017} while MinT
-minimises the Mahalonobis distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$.
-Bottom up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom level series.
-As such, bottom up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.
+For example OLS minimises the Euclidean distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$, while \citet{Wickramasuriya2017} show that MinT minimises the Mahalonobis distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$.
+Bottom-up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom-level series.
+As such, bottom-up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.
 
@@
 
-Before generalising the concept of point reconciliation to probabilistic forecasts we state two theorems that motivate the use of projections for point forecast reconciliation.
-First, let $\bm{\mu}_{t+h|t}:=E(\bm{y}_{t+h}|\bm{y}_{1},\dots,\bm{y}_{t})$ and assume $\hat{\bm{y}}_{t+h|t}$ is an unbiased prediction, that is $E_{1:t}\left(\hat{\bm{y}}_{t+h|t}\right)=\mu_{t+h|t}$ where the subscript $1:t$ denotes an expectation taken over the training sample.
+Before generalising the concept of point reconciliation to probabilistic forecasts, we state two theorems that motivate the use of projections for point forecast reconciliation.
+First, let $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ and assume $\hat{\bm{y}}_{t+h|t}$ is an unbiased prediction; that is $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\mu_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
 
 \begin{theo}[Unbiasedness preserving property]
-  For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast will also be an unbiased prediction as long as $s\circ g$ is a projection
+  For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast will also be an unbiased prediction as long as $s\circ g$ is a projection.
 \end{theo}
@@
 	The expected value of the reconciled forecast is given by
-	\begin{align*}
-	E_{1:t}\left(\tilde{\bm{y}}_{t+h|t}\right)&=E_{1:t}\left(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}\right)\\
-	&=\bm{S}\bm{G}E_{1:t}\left(\hat{\bm{y}}_{t+h|t}\right)\\
-    &=\bm{S}\bm{G}\bm{\mu}_{t+h|t}\\
-	\end{align*}
-	Since the aggregation constraints hold for the true data generating process $\bm{\mu}_{t+h|t}$ must lie in $\mathfrak{s}$.
-If $\bm{S}\bm{G}$ is a projection then it is equivalent to the identity map for all vectors that lie in its range.
+	\[
+  	\E_{1:t}(\tilde{\bm{y}}_{t+h|t})
+	  = \E_{1:t}(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t})
+  	= \bm{S}\bm{G}\E_{1:t}(\hat{\bm{y}}_{t+h|t})
+    = \bm{S}\bm{G}\bm{\mu}_{t+h|t}.
+	\]
+	Since the aggregation constraints hold for the true data generating process, $\bm{\mu}_{t+h|t}$ must lie in $\mathfrak{s}$.
+If $\bm{S}\bm{G}$ is a projection, then it is equivalent to the identity map for all vectors that lie in its range.
 Therefore $\bm{S}\bm{G}\bm{\mu}_{t+h|t}=\bm{\mu}_{t+h|t}$ when $\bm{S}\bm{G}$ is a projection matrix.
@@
 We note the same result does not hold for general $g$ even when the range of $s\circ g$ is $\mathfrak{s}$.
-Now let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$ and let $||\bm{v}||_2$ be the L2 norm of vector $\bm{v}$.
-The following theorem shows that reconciliation never increases, and in most cases reduces the sum of squared errors of point forecasts.
+Now let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$, and let $\|\bm{v}\|_2$ be the $L_2$ norm of vector $\bm{v}$.
+The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.
 
 \begin{theo}[Distance reducing property]
-	If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$ where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection then the following inequality holds
+	If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection, then the following inequality holds:
 	  \begin{equation}
-	    ||(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||^2_2\le||(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||^2_2
+	    \|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2.
 	  \end{equation}
@@
 	\begin{align}
-	||(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||_2&=||(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})||_2\\
-	&=||\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||_2\\
+	\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
+	&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\\
 	\end{align}
@@
 	 \begin{equation*}
-	 ||\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||_2\le
-	 ||(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})||_2
+	 \|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le
+	 \|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
 	 \end{equation*}
@@
 
+\todo[inline]{Equivalent to GTOP result in MinT paper?}
+
 \subsection{Probabilistic forecast reconciliation}
 
-We now extend the methodology of point forecast reconciliation to probabilistic forecasts
+We now extend the methodology of point forecast reconciliation to probabilistic forecasts.
 %For probabilistic forecasts, reconciliation implies finding the probability measure of the coherent forecasts using the information from an incoherent probabilistic forecast measure.
 A more formal definition is given below.
-Let $(\mathbb{R}^n, \mathscr{F}_{\mathbb{R}^n}, \hat{\nu})$ be an probability triple, that is incoherent and that characterises forecast uncertainty for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.
-This is obtained from the first stage of the forecasting process e.g.
-by modelling and forecasting each series individually.
-Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear mapping.
-Let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$.
+Let $(\mathbb{R}^n, \mathscr{F}_{\mathbb{R}^n}, \hat{\nu})$ be a probability triple that is incoherent and which characterises forecast uncertainty for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.
+This is obtained from the first stage of the forecasting process; e.g., by modelling and forecasting each series individually.
+Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear mapping, and let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$.
+
 \begin{definition} \label{def:reconprob}
-  The reconciled probability measure of $\hat{\nu}$ with respect to the mapping $g(.)$ is a probability measure $\tilde{\nu}$ on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_\mathfrak{s}$ where the following holds
+  The reconciled probability measure of $\hat{\nu}$ with respect to the mapping $g(.)$ is a probability measure $\tilde{\nu}$ on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_\mathfrak{s}$ such that
   \begin{equation}
@@
   \end{equation}
-  where $g^{-1}(\mathcal{B}):=\left\{\breve{\bm{y}}\in \mathbb{R}^n:g(\breve{\bm{y}})\in \mathcal{B} \right\}$ is the pre-image of $\mathcal{B}$, that is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $\mathcal{B}$.
+  where $g^{-1}(\mathcal{B}):=\{\breve{\bm{y}}\in \mathbb{R}^n:g(\breve{\bm{y}})\in \mathcal{B}\}$ is the pre-image of $\mathcal{B}$, that is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $\mathcal{B}$.
 \end{definition}
@@
 The probability that $\bm{y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that $\bm{y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast.
-Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:probfr_sch}
+Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic.}\label{fig:probfr_sch}
 \end{figure}
 
-Recall that when $s\circ g$ is a projection, the case of point forecast reconciliation could be broken down into three steps.
-In the first, $\hat{\bm{y}}_{t+h|t}$ is transformed into coordinates $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ via a change of basis.
-In the second, $\tilde{\bm{a}}_{t+h|t}$ is discarded and $\tilde{\bm{b}}_{t+h|t}$ are kept as the bottom level reconciled forecasts.
-In the third, reconciled forecasts for the entire hierarchy are recovered via $\tilde{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}$.
+Recall that when $s\circ g$ is a projection, the case of point forecast reconciliation can be broken down into three steps.
+\begin{compactenum}
+\item  $\hat{\bm{y}}_{t+h|t}$ is transformed into coordinates $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ via a change of basis.
+\item $\tilde{\bm{a}}_{t+h|t}$ is discarded and $\tilde{\bm{b}}_{t+h|t}$ are kept as the bottom-level reconciled forecasts.
+\item Reconciled forecasts for the entire hierarchy are recovered via $\tilde{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}$.
+\end{compactenum}
 We now outline the analogues to these three steps for probabilistic forecasts when predictive densities are available.
@@
 While $\hat{\nu}$ is a probability measure for an $n$-vector $\hat{\bm{y}}_{t+h|t}$, probability statements in terms of a different coordinate system can be made via an appropriate change of basis.
-Letting $f(.)$ be generic notation for a probability density function and following the notation from our definition of point forecast reconciliation where $\hat{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t}$ we obtain
-
+Letting $f(.)$ be generic notation for a probability density function, and following the notation from our definition of point forecast reconciliation where $\hat{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t}$, we obtain
 \begin{equation}
-f(\hat{\bm{y}}_{t+h|t})=f(\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t})|\left(\bm{S}~\bm{R}\right)|
+f(\hat{\bm{y}}_{t+h|t})=f(\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t})|(\bm{S}~\bm{R})|
 \end{equation}
-
-The expression $\hat{\nu}(g^{-1}(\mathcal{B}))$ in Definition~\ref{def:reconprob} is equivalent to the probability statement $\mbox{Pr}(\hat{\bm{y}}_{t+h|t}\in g^{-1}(\mathcal{B}))$.
-After the change of basis this is equivalent to $\mbox{Pr}(\tilde{\bm{b}}\in \mathcal{B})$ which implies
-
+The expression $\hat{\nu}(g^{-1}(\mathcal{B}))$ in Definition~\ref{def:reconprob} is equivalent to the probability statement $\text{Pr}(\hat{\bm{y}}_{t+h|t}\in g^{-1}(\mathcal{B}))$.
+After the change of basis, this is equivalent to $\text{Pr}(\tilde{\bm{b}}\in \mathcal{B})$, which implies
 \begin{align}
-\mbox{Pr}(\hat{\bm{y}}_{t+h|t}\in g^{-1}(\mathcal{B}))&=\int\limits_{g^{-1}(\mathcal{B})}f(\hat{\bm{y}}_{t+h|t})d\hat{\bm{y}}_{t+h|t}\\
-&=\int\limits_{\mathcal{B}}\int f(\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t})|\left(\bm{S}~\bm{R}\right)|d\tilde{\bm{a}}_{t+h|t}d\tilde{\bm{b}}_{t+h|t}
+\text{Pr}(\hat{\bm{y}}_{t+h|t}\in g^{-1}(\mathcal{B}))&=\int\limits_{g^{-1}(\mathcal{B})}f(\hat{\bm{y}}_{t+h|t})d\hat{\bm{y}}_{t+h|t}\\
+&=\int\limits_{\mathcal{B}}\int f(\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t})|(\bm{S}~\bm{R})|d\tilde{\bm{a}}_{t+h|t}d\tilde{\bm{b}}_{t+h|t}.
 \end{align}
-
-After integrating out over $\tilde{\bm{a}}_{t+h|t}$, a step analogous to setting $\tilde{\bm{a}}_{t+h|t}=0$ for point forecasting, we obtain an expression that gives the probability the reconciled bottom level series lies in the region $\mathcal{B}$.
+After integrating out over $\tilde{\bm{a}}_{t+h|t}$, a step analogous to setting $\tilde{\bm{a}}_{t+h|t}=0$ for point forecasting, we obtain an expression that gives the probability that the reconciled bottom-level series lies in the region $\mathcal{B}$.
 This corresponds to $\nu(\mathcal{B})$ in Definition~\ref{def:reconprob}.
-To make a valid probability statement about the entire hierarchy we simply use the bottom level probabilistic forecasts together with Definition~\ref{def:cohprob}.
+To make a valid probability statement about the entire hierarchy we simply use the bottom-level probabilistic forecasts together with Definition~\ref{def:cohprob}.
 
@@
 The unreconciled density
-
 \begin{equation}
-  f(\hat{\bm{y}})=(2\pi)^{-n/2}|\hat{\bm{\Sigma}}|^{-1/2}\exp\left\{-\frac{1}{2}\left[(\hat{\bm{y}}-\hat{\bm{\mu}})'\hat{\bm{\Sigma}}^{-1}(\hat{\bm{y}}-\hat{\bm{\mu}})\right]\right\}
+  f(\hat{\bm{y}})=(2\pi)^{-n/2}|\hat{\bm{\Sigma}}|^{-1/2}\exp\left\{-\frac{1}{2}\left[(\hat{\bm{y}}-\hat{\bm{\mu}})'\hat{\bm{\Sigma}}^{-1}(\hat{\bm{y}}-\hat{\bm{\mu}})\right]\right\}.
 \end{equation}
-
-In an alternative basis
-
+In an alternative basis,
 \begin{equation}
-f(\tilde{\bm{b}},\tilde{\bm{a}})=(2\pi)^{-\frac{n}{2}}\Big|\bm{\hat{\Sigma}}\Big|^{-\frac{1}{2}}\Big|(\bm{S} ~  \bm{R})\Big|\exp\left\{-\frac{1}{2}q\right\}\,,
+f(\tilde{\bm{b}},\tilde{\bm{a}})=(2\pi)^{-\frac{n}{2}}\Big|\hat{\bm{\Sigma}}\Big|^{-\frac{1}{2}}\Big|(\bm{S} ~  \bm{R})\Big|\exp\{-\frac{1}{2}q\}\,,
 \end{equation}
@@
 \begin{equation}
-q=(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\bm{\hat{\mu}})' \bm{\hat{\Sigma}}^{-1}(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\bm{\hat{\mu}})
+q=(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\hat{\bm{\mu}})' \hat{\bm{\Sigma}}^{-1}(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\hat{\bm{\mu}}).
 \end{equation}
-
 The quadratic form $q$ can be rearranged as
@@
 q& =
-\left((\bm{S} ~  \bm{R})\bt-\bm{\hat{\mu}}\right)' \bm{\hat{\Sigma}}^{-1}\left((\bm{S} ~ \bm{R})\bt-\bm{\hat{\mu}}\right),\\
+\left((\bm{S} ~  \bm{R})\bt-\hat{\bm{\mu}}\right)' \hat{\bm{\Sigma}}^{-1}\left((\bm{S} ~ \bm{R})\bt-\hat{\bm{\mu}}\right),\\
 & =
-\left(\bt-(\bm{S} ~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\right)' \Big[(\bm{S}  \bm{R})^{-1}\bm{\hat{\Sigma}_{t+h}}\left((\bm{S} ~ \bm{R})^{-1}\right)'\Big]^{-1}
-\left(\bt-(\bm{S} ~ \bm{R})^{-1}\bm{\hat{\mu}}_{t+h}\right)\,.
+\left(\bt-(\bm{S} ~ \bm{R})^{-1}\hat{\bm{\mu}}_{t+h}\right)' \Big[(\bm{S}  \bm{R})^{-1}\hat{\bm{\Sigma}_{t+h}}\left((\bm{S} ~ \bm{R})^{-1}\right)'\Big]^{-1}
+\left(\bt-(\bm{S} ~ \bm{R})^{-1}\hat{\bm{\mu}}_{t+h}\right)\,.
 \end{align*}
-
 Recall that
-$$
+\[
   (\bm{S} ~ \bm{R})^{-1} =
@@
   \end{pmatrix}\,.
-$$
+\]
 Then $q$ can be rearranged further as
 \begin{align*}
-q& =%\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\bm{\hat{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|\PQ \Big|}
+q& =%\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\hat{\bm{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|\PQ \Big|}
 %\exp \Big\{-\frac{1}{2}
-\left[\bt-\PQ\bm{\hat{\mu}}_{t+h}\right]'%\\[-0.5cm]
-\left[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\right]^{-1}\left[\bt-\PQ\bm{\hat{\mu}}_{t+h}\right] %\Big\},
+\left[\bt-\PQ\hat{\bm{\mu}}_{t+h}\right]'%\\[-0.5cm]
+\left[\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\right]^{-1}\left[\bt-\PQ\hat{\bm{\mu}}_{t+h}\right] %\Big\},
 \\[0.5cm]
- & =%\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big|^{\frac{1}{2}}}
+ & =%\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\Big|^{\frac{1}{2}}}
 %\exp \Big\{-\frac{1}{2}
-\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}\\ \tilde{\bm{a}}- \bm{H}\bm{\hat{\mu}}\end{pmatrix}' %&\\[-0.5cm]
+\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix}' %&\\[-0.5cm]
 %& \hspace*{7cm}
- \left[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\right]^{-1}\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}\\ \tilde{\bm{a}}- \bm{H}\bm{\hat{\mu}}\end{pmatrix} %\Big\}.
+ \left[\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\right]^{-1}\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix}. %\Big\}.
 \end{align*}
-%Since $\Big[\PQ\bm{\hat{\Sigma}_{t+h}}\PQ'\Big] = \begin{pmatrix}
-%\bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{P}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'
-%\bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\bm{\hat{\Sigma}_{t+h}}\bm{Q}'
+%Since $\Big[\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\Big] = \begin{pmatrix}
+%\bm{P}\hat{\bm{\Sigma}_{t+h}}\bm{P}' & \bm{P}\hat{\bm{\Sigma}_{t+h}}\bm{Q}'
+%\bm{Q}\hat{\bm{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\hat{\bm{\Sigma}_{t+h}}\bm{Q}'
 %\end{pmatrix}$ we have
 
-Similar manipulations on determinant of the covariance matrix lead to the following expression for the density
-
+Similar manipulations on the determinant of the covariance matrix lead to the following expression for the density:
 \begin{align*}
@@
 \begin{pmatrix}
-  \bm{G}\bm{\hat{\Sigma}}\bm{G}' & \bm{G}\bm{\hat{\Sigma}}\bm{H}' \\
-  \bm{H}\bm{\hat{\Sigma}}\bm{G}' & \bm{H}\bm{\hat{\Sigma}}\bm{H}'
+  \bm{G}\hat{\bm{\Sigma}}\bm{G}' & \bm{G}\hat{\bm{\Sigma}}\bm{H}' \\
+  \bm{H}\hat{\bm{\Sigma}}\bm{G}' & \bm{H}\hat{\bm{\Sigma}}\bm{H}'
 \end{pmatrix}
 \right|^{-\frac{1}{2}}
-\exp \left\{-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}\\ \tilde{\bm{a}}- \bm{H}\bm{\hat{\mu}}\end{pmatrix}'\right.\\
+\exp \left\{-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix}'\right.\\
 &\hspace*{7cm}
 \left.\begin{pmatrix}
-\bm{G}\bm{\hat{\Sigma}}\bm{G}' & \bm{G}\bm{\hat{\Sigma}}\bm{H}' \\
-\bm{H}\bm{\hat{\Sigma}}\bm{G}' & \bm{H}\bm{\hat{\Sigma}}\bm{H}'
+\bm{G}\hat{\bm{\Sigma}}\bm{G}' & \bm{G}\hat{\bm{\Sigma}}\bm{H}' \\
+\bm{H}\hat{\bm{\Sigma}}\bm{G}' & \bm{H}\hat{\bm{\Sigma}}\bm{H}'
 \end{pmatrix}^{-1}
-\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}\\ \tilde{\bm{a}}- \bm{H}\bm{\hat{\mu}}\end{pmatrix} \right\}.
+\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix} \right\}.
 \end{align*}
-Marginalising out $\tilde{\bm{a}}$, leads to the following bottom level reconciled forecasts.
+Marginalising out $\tilde{\bm{a}}$ leads to the following bottom-level reconciled forecasts:
 \begin{equation}\label{ex:2.1}
-f(\tilde{\bm{b}})=(2\pi)^{-\frac{m}{2}}\Big|\bm{G}\bm{\hat{\Sigma}}\bm{G}'\Big|^{\frac{1}{2}}
-\exp \Big\{-\frac{1}{2} (\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}})' (\bm{G}\bm{\hat{\Sigma}}\bm{G}')^{-1}(\tilde{\bm{b}} - \bm{G}\bm{\hat{\mu}}) \Big\}.
+f(\tilde{\bm{b}})=(2\pi)^{-\frac{m}{2}}\Big|\bm{G}\hat{\bm{\Sigma}}\bm{G}'\Big|^{\frac{1}{2}}
+\exp \Big\{-\frac{1}{2} (\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}})' (\bm{G}\hat{\bm{\Sigma}}\bm{G}')^{-1}(\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}) \Big\}.
 \end{equation}
 
-%Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\bm{\hat{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
+%Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\hat{\bm{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
 Then from \eqref{4.7} it follows that
@@
 %\end{equation}
-Which implies that the reconciled probabilistic forecast for the bottom level series is $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{G}\bm{\hat{\mu}}_{t+h}, \bm{G}\hat{\bm{\Sigma}}_{t+h}\bm{G}')$.
-The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean  $\bm{SG}\bm{\hat{\mu}}$ and rank deficient covariance matrix $\bm{SG}\hat{\bm{\Sigma}}_{t+h}\bm{G}'\bm{S}'$.
+This implies that the reconciled probabilistic forecast for the bottom-level series is $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{G}\hat{\bm{\mu}}_{t+h}, \bm{G}\hat{\bm{\Sigma}}_{t+h}\bm{G}')$.
+The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean $\bm{SG}\hat{\bm{\mu}}$ and rank deficient covariance matrix $\bm{SG}\hat{\bm{\Sigma}}_{t+h}\bm{G}'\bm{S}'$.
+
 \subsection{Elliptical Distributions}
+
 We now show that the true predictive distribution can be recovered for elliptical distributions via linear reconciliation.
-Here, for any square matrix $\bm{C}$, $\bm{C}^{1/2}$ and $\bm{C}^{-1/2}$ are defined to satisfy $\bm{C}^{1/2}\left(\bm{C}^{1/2}\right)'=\bm{C}$ and $\bm{C}^{-1/2}\left(\bm{C}^{-1/2}\right)'=\bm{C}^{-1}$, for example $\bm{C}^{1/2}$ may be obtained via the Cholesky or eigenvalue decompositions.
+Here, for any square matrix $\bm{C}$, $\bm{C}^{1/2}$ and $\bm{C}^{-1/2}$ are defined to satisfy $\bm{C}^{1/2}(\bm{C}^{1/2})'=\bm{C}$ and $\bm{C}^{-1/2}(\bm{C}^{-1/2})'=\bm{C}^{-1}$, for example $\bm{C}^{1/2}$ may be obtained via the Cholesky or eigenvalue decompositions.
+
 \begin{theo}[Reconciliation for Elliptical Distributions]
@@
 Let the true predictive distribution of $\bm{y}_{t+h|t}$ also belong to the elliptical class with location parameter $\bm{\mu}$ and scale matrix $\bm{\Sigma}$.
-Then the linear reconciliation mapping $g(\breve{\bm{y}})=\bm{G}_{opt}\breve{\bm{y}}+\bm{d}_{opt}$ with $\bm{G}_{opt}={\bm{a}}{\bm\Sigma}^{-1/2}$ and $\bm{d}_{opt}=\bm{\mu}-\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}$ recovers the true predictive density where ${\bm{a}}$ is any $m\times n$ matrix such that ${\bm{a}}{\bm{a}}'=\bm{\Omega}$ and $\bm{\Omega}$ is a sub-matrix of $\bm{\Sigma}$ corresponding to the bottom level series.
+Then the linear reconciliation mapping $g(\breve{\bm{y}})=\bm{G}_{opt}\breve{\bm{y}}+\bm{d}_{opt}$ with $\bm{G}_{opt}={\bm{a}}{\bm\Sigma}^{-1/2}$ and $\bm{d}_{opt}=\bm{\mu}-\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}$ recovers the true predictive density where ${\bm{a}}$ is any $m\times n$ matrix such that ${\bm{a}}{\bm{a}}'=\bm{\Omega}$ and $\bm{\Omega}$ is a sub-matrix of $\bm{\Sigma}$ corresponding to the bottom-level series.
 \end{theo}
+
 \begin{proof}
    Since elliptical distributions are closed under affine transformations, and are closed under marginalisation, reconciliation of an elliptical distribution yields an elliptical distribution (although the unreconciled and reconciled distributions may be different members of the class of elliptical distributions).
-The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}_{opt}\bm{\Sigma}\bm{G}_{opt}'\bm{S}'$ while the location matrix is given by $\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}+\bm{d}_{opt}$.
+The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}_{opt}\bm{\Sigma}\bm{G}_{opt}'\bm{S}'$, while the location matrix is given by $\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}+\bm{d}_{opt}$.
 The reconciled scale matrix is
-   \begin{align*}
-   \tilde{\bm{\Sigma}}_{opt}=&\bm{S}{\bm{a}}{\bm\Sigma}^{-1/2}\bm{\Sigma}\left({\bm\Sigma}^{-1/2}\right)'{\bm{a}}'\bm{S}'\\
-   =&\bm{S}\bm{\Omega}\bm{S}'\\
-   =&\bm{\Sigma}
-   \end{align*}
+   \[
+     \tilde{\bm{\Sigma}}_{opt}
+       = \bm{S}{\bm{a}}{\bm\Sigma}^{-1/2}\bm{\Sigma}\left({\bm\Sigma}^{-1/2}\right)'{\bm{a}}'\bm{S}'
+       = \bm{S}\bm{\Omega}\bm{S}'
+       = \bm{\Sigma}.
+   \]
    For the choices of $\bm{G}_{opt}$ and $\bm{d}_{opt}$ given above, the reconciled location vector is
-   \begin{align*}
-   \tilde{\bm{\mu}}_{opt}=& \bm{S}\bm{G}_{opt}\hat{\bm{\mu}}+\bm{\mu}-\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}\\
-   =&\bm{\mu}\\
-   \end{align*}
+   \[
+     \tilde{\bm{\mu}}_{opt}= \bm{S}\bm{G}_{opt}\hat{\bm{\mu}}+\bm{\mu}-\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}
+   = \bm{\mu}.
+   \]
 \end{proof}
+
 A number of insights can be drawn from this theorem.
@@
 Consider reconciliation via a projection $g(\bm{y})=(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\bm{y}$.
-The true predictive distribution can be recovered via reconciliation of an elliptical distribution with location $\hat{\bm{\mu}}$ and scale $\hat{\bm{\Sigma}}$  when the following conditions hold.
+The true predictive distribution can be recovered via reconciliation of an elliptical distribution with location $\hat{\bm{\mu}}$ and scale $\hat{\bm{\Sigma}}$  when the following conditions hold:
 	\begin{align}
@@
 \end{theo}
+
 \begin{proof}
@@
 		&=\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\left(\hat{\bm{\mu}}+\bm{\mu}-\bm{\mu}\right)\\
-		&=\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\bm{\mu}+\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\left(\hat{\bm{\mu}}-\bm{\mu}\right)\\
+		&=\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\bm{\mu}+\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\left(\hat{\bm{\mu}}-\bm{\mu}\right).
 	\end{align*}
-  Since $\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}$ is a projection onto $\mathfrak{s}$ and $\bm{\mu}\in\mathfrak{s}$ the first term simplifies to $\bm{\mu}$.
-If $\bm{\mu}-\hat{\bm{\mu}}$ lies in the span of $\bm{R}$ then multiplication by $\bm{R}'_{\perp}$ reduces the second term to $\bm{0}$.
+  Since $\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}$ is a projection onto $\mathfrak{s}$ and $\bm{\mu}\in\mathfrak{s}$, the first term simplifies to $\bm{\mu}$.
+If $\bm{\mu}-\hat{\bm{\mu}}$ lies in the span of $\bm{R}$, then multiplication by $\bm{R}'_{\perp}$ reduces the second term to $\bm{0}$.
 By a similar argument it can be shown that $\tilde{\bm{\Sigma}}^{1/2}=\bm{\Sigma}^{1/2}$.
@@
 \end{proof}
-Although these conditions will rarely hold in practice and only apply to a limited class of distributions they do provide some insight into selecting a projection for reconciliation.
-If the value of $\hat{\bm{\mu}}$ were equi-probable in all directions then a projection orthogonal to $\mathfrak{s}$ would be a sensible choice for $\bm{R}$ since it would in some sense represent a `median' direction for $\bm{\mu}-\hat{\bm{\mu}}$.
-However, the one step ahead in-sample errors are usually correlated suggesting that $\hat{\bm{\mu}}$ is more likely to fall in some directions than others.
-As such an orthogonal projection after transformation by the inverse of the one step ahead in-sample errors may be more intuitively appealing.
+
+Although these conditions will rarely hold in practice and only apply to a limited class of distributions, they do provide some insight into selecting a projection for reconciliation.
+If the value of $\hat{\bm{\mu}}$ were equi-probable in all directions, then a projection orthogonal to $\mathfrak{s}$ would be a sensible choice for $\bm{R}$ since it would in some sense represent a `median' direction for $\bm{\mu}-\hat{\bm{\mu}}$.
+However, the one-step-ahead in-sample errors are usually correlated suggesting that $\hat{\bm{\mu}}$ is more likely to fall in some directions than others.
+Therefore an orthogonal projection after transformation by the inverse of the one-step-ahead in-sample error covariance matrix may be more intuitively appealing.
 This is exactly what the MinT projection provides, and as simulations will show in Section~\ref{sec:gaussian}, this projection leads to the best empirical results.
@@
 For arbitrary $\bm{G}\hat{\bm\Sigma}^{1/2}$ is an approximation for ${\bm\Omega}^{1/2}$.
-This approximation has similarities with the way bottom level estimates are produced for point forecast reconciliation.
-Rather than mapping a vector of point forecasts to reconcilied bottom level forecasts, the columns of  $\hat{\bm\Sigma}^{1/2}$ are mapped to an approximation of the columns of ${\bm\Omega}^{1/2}$.
+This approximation has similarities with the way bottom-level estimates are produced for point forecast reconciliation.
+Rather than mapping a vector of point forecasts to reconcilied bottom-level forecasts, the columns of  $\hat{\bm\Sigma}^{1/2}$ are mapped to an approximation of the columns of ${\bm\Omega}^{1/2}$.
 The value for $\tilde{\bm{\mu}}_{opt}$ includes a projection of $\hat{\bm{\mu}}$ onto $\mathfrak{s}$.
@@
 The log score under the true data generating process is
-$$
+\[
 S\left(\tilde{f},\bm{z}^{(1)}_t\right) = -\log f_1\left(\bm{z}^{(1)}_t\right),
-$$
+\]
 while that of the unreconciled density is
@@
 The density for the full hierarchy is given by $f(\bm{y})=f(\bm{Sb})=f(\bm{b})J^{-1}$ where $J=\prod_{j=1}^{m}\lambda_j$ is a pseudo-determinant of the non-square  matrix $\bm{S}$ and $\lambda_j$ are the non-zero singular values of $\bm{S}$.
-Therefore for any coherent density the log score of the full hierarchy differs from the log score for the bottom level series by the term $log(J)$.
+Therefore for any coherent density the log score of the full hierarchy differs from the log score for the bottom-level series by the term $log(J)$.
 This term depends  only on the structure of the  hierarchy and is fixed across different reconciliation methods.
-Therefore if one method achieves a lower expected log score compared to an alternative method  using the bottom level series only, the same ordering is preserved when an assessment is made on the basis of the full hierarchy.
+Therefore if one method achieves a lower expected log score compared to an alternative method  using the bottom-level series only, the same ordering is preserved when an assessment is made on the basis of the full hierarchy.
 
@@
 However,  when $\bm{S}$ is  the usual summing matrix, it is not semi-orthogonal.
-As such the energy score computed on the bottom level series will differ from the energy score computed using the full hierarchy and the ordering of different reconciliation methods may change depending on the basis series used.
+As such the energy score computed on the bottom-level series will differ from the energy score computed using the full hierarchy and the ordering of different reconciliation methods may change depending on the basis series used.
 In this case we recommend computing energy score using the full hierarchy.
@@
 %For example, suppose the data from $i$th series follows a ARMA$(p,q)$ model. i.e.,
-%$$
+%\[
 %Y_{t,i}=\alpha_1Y_{t-1,i}+\dots+\alpha_pY_{t-p,i}+\varepsilon_t + \beta_1\varepsilon_{t-1,i}+\dots+\beta_q\varepsilon_{t-q,i},
-%$$
+%\]
 %where $\varepsilon_t \sim \mathcal{NID}(0, \sigma_i^2)$. Then,
-%$$
+%\[
 %\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}] = \alpha_1Y_{T+h-1,i}+\dots+\alpha_pY_{T+h-p,i}+ \beta_1\varepsilon_{T+h-1,i}+\dots+\beta_q\varepsilon_{T+h-q,i}.
-%$$
+%\]
 %
 %Since $\bm{\alpha} = (\alpha_1,\dots,\alpha_p)'$ and $\bm{\beta} = (\beta_1,\dots,\beta_q)'$ are unknown in practice and thus estimated using the maximum likelihood method.
-Let $\bm{\hat{\alpha}}$ and $\bm{\hat{\beta}}$ denote the maximum likelihood estimates of $\bm{\alpha}$ and $\bm{\beta}$ respectively.
-\citet{Yao2006} showed that $\bm{\hat{\alpha}}$ and $\bm{\hat{\beta}}$ are asymptotically consistent estimators.
+Let $\hat{\bm{\alpha}}$ and $\hat{\bm{\beta}}$ denote the maximum likelihood estimates of $\bm{\alpha}$ and $\bm{\beta}$ respectively.
+\citet{Yao2006} showed that $\hat{\bm{\alpha}}$ and $\hat{\bm{\beta}}$ are asymptotically consistent estimators.
 Thus the point forecasts from this estimated model, $\hat{Y}_{T+h,i}$, will also be a consistent estimator for $\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}]$.
@@
 Then the expectation of the energy score with respect to the true distribution is equivalent to the trace of mean squared forecast error; i.e.,
-%$$
+%\[
 %\E_{\bm{G}}[eS(\bm{\tilde{Y}_{T+h},y_{T+h}})]= \text{Tr}\{\E_{\bm{y}_{T+h}}[(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})'|\mathcal{I}_{T}]\}.
-%$$
+%\]
 %
@@
 and the total series is given by
-$$y_{Tot,t} = w_{AA,t} + w_{AB,t} + w_{BA,t} + w_{BB,t}.$$
+\[
+  y_{Tot,t} = w_{AA,t} + w_{AB,t} + w_{BA,t} + w_{BB,t}.
+\]
 
 To ensure noisier disaggregate series than aggregate series, we choose $\bm{\Sigma}, \sigma^2_u$ and $\sigma^2_v$ such that
-$$
-\text{Var}(\varepsilon_{AA,t}+\varepsilon_{AB,t}+\varepsilon_{BA,t}+\varepsilon_{BB,t}) \le \text{Var}(\varepsilon_{AA,t}+\varepsilon_{AB,t}-v_t) \le \text{Var}(\varepsilon_{AA,t}+u_t-0.5v_t)\,,
-$$
+\[
+  \text{Var}(\varepsilon_{AA,t} + \varepsilon_{AB,t} + \varepsilon_{BA,t} + \varepsilon_{BB,t})
+  \le \text{Var}(\varepsilon_{AA,t}+\varepsilon_{AB,t}-v_t)
+  \le \text{Var}(\varepsilon_{AA,t}+u_t-0.5v_t)\,,
+\]
 and similar inequalities hold when $\varepsilon_{AA,t}$ is replaced by $\varepsilon_{AB,t}$, $\varepsilon_{BA,t}$ and $\varepsilon_{BB,t}$ in the third term.
 %Therefore
-%$$
+%\[
 %\bm{l}_1\bm{\Sigma} \bm{l}_1' \le \bm{l}_2\bm{\Sigma} \bm{l}_2' + \sigma^2_v \le  \bm{l}_3\bm{\Sigma} \bm{l}_3' + \sigma^2_u + \frac{1}{4}\sigma^2_v,
-%$$
+%\]
 %where $\bm{l}_1 = (1,1,1,1)'$, $\bm{l}_2 = (1,1,0,0)'$ and $\bm{l}_3 = (1,0,0,0)'$, and hence
-%$$\bm{l}_1\bm{\Sigma} \bm{l}_1' - \bm{l}_2\bm{\Sigma} \bm{l}_2' \le \sigma^2_v \le \frac{4}{3}(\sigma^2_u + \bm{l}_3\bm{\Sigma} \bm{l}_3' - \bm{l}_2\bm{\Sigma} \bm{l}_2').$$
+%\[\bm{l}_1\bm{\Sigma} \bm{l}_1' - \bm{l}_2\bm{\Sigma} \bm{l}_2' \le \sigma^2_v \le \frac{4}{3}(\sigma^2_u + \bm{l}_3\bm{\Sigma} \bm{l}_3' - \bm{l}_2\bm{\Sigma} \bm{l}_2').\]
 The values of $\bm{\Sigma}$, $\sigma^2_u$ and $\sigma^2_v$, that we use and which satisfy these constraints are $\sigma^2_u = 19$, $\sigma^2_u = 18$ and
-$$
+\[
 \bm{\Sigma} =
@@
 \end{pmatrix}\,.
-$$
+\]
 
@@
 In all cases skill scores are calculated with the bottom-up method as reference.
-All log scores are evaluated on the basis of bottom level series only, however these only differ from the log scores for the full hierarchy by a fixed constant.
+All log scores are evaluated on the basis of bottom-level series only, however these only differ from the log scores for the full hierarchy by a fixed constant.
 The cell for log score of unreconciled forecasts is left blank since the log score is not proper in this context.
 Overall, the MinT methods provide the best performance irrespective of the scoring rule, and all methods that reconcile using information at all levels of the forecast improve upon unreconciled forecasts.
-Bottom up forecasts perform even worse than unreconciled forecasts in some cases.
+Bottom-up forecasts perform even worse than unreconciled forecasts in some cases.
 
@@
 The log score and CRPS are considered while skill scores are computed with the unreconciled forecast as a reference.
-When broken down in this fashion, the methods based on MinT perform best for all series and always outperform bottom up and unreconciled forecasts.
+When broken down in this fashion, the methods based on MinT perform best for all series and always outperform bottom-up and unreconciled forecasts.
 
@@
 ``Skill score'' columns give the percentage skill score with reference to the bottom-up method.
-Entries in these columns show the percentage increase of score for different reconciliation methods relative to the bottom-up method.
-}\label{table:3}
+Entries in these columns show the percentage increase of score for different reconciliation methods relative to the bottom-up method.}\label{table:3}
 

### 2018-07-08 ProbabilisticCoherence.tex
Some improved English in Section 4+

@@
 \def\E{\text{E}}
+\def\var{\text{Var}}
 \mathtoolsset{showonlyrefs=true}
@@
 In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.
-As such we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts.
+Therefore we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts.
 Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.
@@
 
-\subsection{Notation and Preliminaries}\label{sec:notation}
+\subsection{Notation and preliminaries}\label{sec:notation}
 
@@
 
-\subsection{Coherent Point Forecasts}\label{sec:cohpointf}
+\subsection{Coherent point forecasts}\label{sec:cohpointf}
 
@@
 \begin{definition}[Coherent subspace]\label{def:cohspace}
- The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e. $\mathfrak{s}=\text{span}(\bm{S})$, is defined as the \emph{coherent space}.
+ The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$, is defined as the \emph{coherent space}.
 \end{definition}
@@
 
-\subsection{Coherent Probabilistic Forecasts}\label{sec:cohprobf}
+\subsection{Coherent probabilistic forecasts}\label{sec:cohprobf}
 
@@
 For example, consider the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$.
-In this case the matrix $\bm{S}$ has columns $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$, and premultiplying by $\bm{S}$ transforms arbitrary values of $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy.
+In this case the matrix $\bm{S}$ has columns $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$, and pre-multiplying by $\bm{S}$ transforms arbitrary values of $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy.
 However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy.
@@
 	\caption{Summary of reconciliation methods that are projections.
-Here, $\hat{\bm{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, $\hat{\bm{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}, $\hat{\bm{W}}^{wls}$ is the diagonal matrix with diagonal elements $w_{ii}$, and $\tau = \frac{\sum_{i \neq j}\hat{\text{Var}}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$, where $w_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{W}}^{sam}$.}\label{table:2}
+Here, $\hat{\bm{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, $\hat{\bm{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}, $\hat{\bm{W}}^{wls}$ is the diagonal matrix with diagonal elements $w_{ii}$, and $\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$, where $w_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{W}}^{sam}$.}\label{table:2}
 	\centering\setstretch{1.5}
@@
 The columns of $\bm{S}$ and $\bm{R}$ provide a basis for $\mathbb{R}^n$.
-As such, any incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$, can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$.
+Therefore any incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$.
 Let $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$ respectively, after a change of basis.
@@
 Bottom-up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom-level series.
-As such, bottom-up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.
+Therefore bottom-up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.
 
@@
 
-\subsection{Elliptical Distributions}
+\subsection{Elliptical distributions}
 
@@
 The first is to compare unreconciled densities to reconciled densities.
-Although reconciliation is a valuable goal in and of itself since it can be important in aligning decision making across, for example, different units of an enterprise, in the point forecasting literature, forecast reconciliation has also been shown to improve forecast performance \citep{AthEtAl2017, Wickramasuriya2017}.
+Reconciliation itself is a valuable goal since it can be important in aligning decision making across, for example, different units of an enterprise.
+In the point forecasting literature, forecast reconciliation has also been shown to improve forecast performance \citep{AthEtAl2017, Wickramasuriya2017}.
 It will be worthwhile to see whether the same holds in the probabilistic forecasting case.
@@
 
-\subsection{Univariate Scoring rules}
-
-One way to evaluate probabilistic forecasts is via the application of univariate scoring rules to each variable in a hierarchy.
-A summary can be taken of the expected scores across each margin for example a mean or median.
-In the simulations of section~\ref{sec:gaussian} we consider two scoring rules.
+\subsection{Univariate scoring rules}
+
+One way to evaluate hierarchical probabilistic forecasts is via the application of univariate scoring rules to each variable in the hierarchy.
+A summary can be taken of the expected scores across each margin, for example a mean or median.
+In the simulations of Section~\ref{sec:gaussian}, we consider two scoring rules.
 The log score is given by the log density, in this case for each margin of the probabilistic forecast.
@@
 \end{align}
-where $\breve{F}_i$ is the cumulative distribution function of the $i^{th}$ margin of the probabilistic forecast, $\breve{Y}_i$ and $\breve{Y}^*_{T+h,i}$ are independent copies of a random variable with distribution $\breve{F}_i$ and $y_i$ is the outcome of the $i^{th}$ margin.
+where $\breve{F}_i$ is the cumulative distribution function of the $i$th margin of the probabilistic forecast, $\breve{Y}_i$ and $\breve{Y}^*_{T+h,i}$ are independent copies of a random variable with distribution $\breve{F}_i$, and $y_i$ is the outcome of the $i$th margin.
 The expectations in the second line can be approximated by Monte Carlo when a sample from the predictive distribution is available.
@@
 For this reason this approach has been used in the limited literature on probabilistic forecasting for hierarchies \citep{BenTaieb2017, JeoEtAl2018} to date.
-A major shortcomings of this approach however, is that evaluating univariate scores on the margins do not account for the dependence in the hierarchy.
-
-\subsection{Multivariate Scoring rules}
+A major shortcoming of this approach however, is that evaluating univariate scores on the margins does not account for the dependence in the hierarchy.
+
+\subsection{Multivariate scoring rules}
 
@@
 
-The log score can be approximated using a sample of values from the probabilistic forecast density \citep{Jordan2017} however it is more commonly used when a parametric form for the density is available for the probabilistic forecast.
+The log score can be approximated using a sample of values from the probabilistic forecast density \citep{Jordan2017}; however it is more commonly used when a parametric form for the density is available for the probabilistic forecast.
+
 The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the representation in terms of expectations leads itself to easy computation when samples from the probabilistic forecast are available.
@@
 where $\breve{\bm{\mu}}_{T+h} =\E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $.
-In this limiting case, the energy score only measures the accuracy of the forecast mean, and not the entire distribution and the energy score is proper, but not strictly proper.
-\citet{Pinson2013a} also argues that the energy score has low discriminative ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
-
-In contrast, \citet{SCHEUERER2015} have shown that the variogram score has a higher discrimination ability of misspecified means, variances and correlation structures than the energy score.
+In this limiting case, the energy score only measures the accuracy of the forecast mean (not the entire distribution), and the energy score is proper but not strictly proper.
+\citet{Pinson2013a} also argue that the energy score has low discriminative ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
+
+In contrast, \citet{SCHEUERER2015} have shown that the variogram score has a higher discrimination ability for misspecified means, variances and correlation structures than the energy score.
 When $\breve{\bm{y}}$ is a random variable from probabilistic forecast $\breve{F}$, the empirical variogram score is defined as
@@
 
-\subsubsection{Comparing Unreconciled Forecasts to Reconciled Forecasts}
-
-For both reconciled and unreconciled densities it is possible to obtain a density from the probability measures defined in \ref{sec:definitions}.
-As such it may seem sensible to compare unreconciled densities to reconciled densities on the basis of log score.
-The following theorem shows that using the log score may fail in the case of multivariate distributions with a degeneracy.
+\subsubsection{Comparing unreconciled forecasts to reconciled forecasts}
+
+For both reconciled and unreconciled densities it is possible to obtain a density from the probability measures defined in Section~\ref{sec:definitions}.
+Therefore it may seem sensible to compare unreconciled densities to reconciled densities on the basis of log score.
+However, the following theorem shows that using the log score may fail in the case of multivariate distributions with a degeneracy.
 
@@
 \end{theo}
+
 \begin{proof}
-Consider a rotated version of hierarchical time series $\bm{z}_t=\bm{U}\bm{y}_t$ so that the first $m$ elements of $\bm{z}_t$ denoted $\bm{z}^{(1)}_t$ are unconstrained, while the remaining $n-m$ elements denoted $\bm{z}^{(2)}_t$ equal $0$ when the aggregation constraints hold.
-An example of the $n\times n$ $\bm{U}$ could be the matrix of left singular vectors of $\bm{S}$.
+Consider a rotated version of hierarchical time series, $\bm{z}_t=\bm{U}\bm{y}_t$, so that the first $m$ elements of $\bm{z}_t$ denoted $\bm{z}^{(1)}_t$ are unconstrained, while the remaining $n-m$ elements denoted $\bm{z}^{(2)}_t$ equal $0$ when the aggregation constraints hold.
+An example of the $n\times n$ $\bm{U}$ is the matrix of left singular vectors of $\bm{S}$.
 %For a non-degenerate probability measure on $\mathbb{R}^n$, the density is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^n$.
@@
 
-Consider the case where the true predictive density is $f_1(\bm{z}^{(1)}_t)\mathbb{1}\left(\bm{z}^{(2)}_t=\bm{0}\right)$, and we evaluate an incoherent density is given by $f_1(\bm{z}^{(1)}_t)f_2(\bm{z}^{(2)}_t)$, where $f_2$ is highly concentrated around $0$ but still a non-degenerate.
-For example $f_2$ may be Gaussian with variance $\sigma^2{\bm{I}}$ with $\sigma^2 < (2\pi)^{-1}$.
+Consider the case where the true predictive density is $f_1(\bm{z}^{(1)}_t)\mathbb{1}\left(\bm{z}^{(2)}_t=\bm{0}\right)$, and we evaluate an incoherent density given by $f_1(\bm{z}^{(1)}_t)f_2(\bm{z}^{(2)}_t)$, where $f_2$ is highly concentrated around $0$ but still non-degenerate.
+For example, $f_2$ may be Gaussian with variance $\sigma^2{\bm{I}}$ with $\sigma^2 < (2\pi)^{-1}$.
 The log score under the true data generating process is
@@
 \end{align}
-
 After taking expectations $ES(f,f) > ES(\hat{f},f)$, violating the condition in Equation~\eqref{eq:(3.1.)} for a proper scoring rule.
@@
 
-A similar issue also arises when discrete random variables are modelled as if they were continuous, an issue discussed in Section 4.1 of \citet{Gneiting2007}.
+A similar issue also arises when discrete random variables are modelled as if they were continuous, an issue discussed in Section~4.1 of \citet{Gneiting2007}.
 This implies that the log score should be avoided when comparing reconciled and unreconciled probabilistic forecasts.
 
-\subsubsection{Comparing Reconciled Forecasts to one another}
-
-Coherent probabilistic forecasts can be completely characterised in terms of basis series; if a probabilistic forecast is  available for the basis series then a probabilistic forecast can be recovered for  the  entire hierarchy via Definition~\ref{def:cohprob}.
+\subsubsection{Comparing reconciled forecasts to one another}
+
+Coherent probabilistic forecasts can be completely characterised in terms of basis series; if a probabilistic forecast is available for the basis series, then a probabilistic forecast can be recovered for the entire hierarchy via Definition~\ref{def:cohprob}.
 This may suggest that it is adequate to merely compare two coherent forecasts to one another using the basis series only.
@@
 For the log score, suppose the coherent probabilistic forecast has density $f(\bm{b})$.
-The density for the full hierarchy is given by $f(\bm{y})=f(\bm{Sb})=f(\bm{b})J^{-1}$ where $J=\prod_{j=1}^{m}\lambda_j$ is a pseudo-determinant of the non-square  matrix $\bm{S}$ and $\lambda_j$ are the non-zero singular values of $\bm{S}$.
-Therefore for any coherent density the log score of the full hierarchy differs from the log score for the bottom-level series by the term $log(J)$.
+The density for the full hierarchy is given by $f(\bm{y})=f(\bm{Sb})=f(\bm{b})J^{-1}$, where $J=\prod_{j=1}^{m}\lambda_j$ is a pseudo-determinant of the non-square matrix $\bm{S}$ and $\lambda_j$ are the non-zero singular values of $\bm{S}$.
+Therefore for any coherent density, the log score of the full hierarchy differs from the log score for the bottom-level series by the term $log(J)$.
 This term depends only on the structure of the hierarchy and is fixed across different reconciliation methods.
@@
 The same property does not hold for all scores in general.
-For example, energy score can be expressed in terms of expectations of norms.
-In general, since norms are invariant under orthogonal rotations the energy score is also invariant under orthogonal transformations \citep{Szekely2013,Gneiting2007}.
-In the context of two coherent forecasts the same is true of a semi-orthogonal transformation from a lower dimensional basis series to the full hierarchy.
+For example, the energy score can be expressed in terms of expectations of norms.
+In general, since norms are invariant under orthogonal rotations, the energy score is also invariant under orthogonal transformations \citep{Szekely2013,Gneiting2007}.
+In the context of two coherent forecasts, the same is true of a semi-orthogonal transformation from a lower dimensional basis series to the full hierarchy.
 However, when $\bm{S}$ is the usual summing matrix, it is not semi-orthogonal.
-As such the energy score computed on the bottom-level series will differ from the energy score computed using the full hierarchy and the ordering of different reconciliation methods may change depending on the basis series used.
-In this case we recommend computing energy score using the full hierarchy.
+Therefore the energy score computed on the bottom-level series will differ from the energy score computed using the full hierarchy and the ordering of different reconciliation methods may change depending on the basis series used.
+In this case we recommend computing the energy score using the full hierarchy.
 Although the discussion here is related to energy score, the same logic holds for other multivariate scores that are not invariant to orthogonal rotations, for example the variogram score.
@@
 	\label{tab:prop}
-
 \end{table}
@@
 
-\section{Simulation Study}\label{sec:gaussian}
+\section{Simulation study}\label{sec:gaussian}
 
@@
 We choose the Gaussian case due to its analytical tractability which allows for evaluation using all scoring rules (including the log score).
-The non-Gaussian case lies beyond the scope of this simulation study, but can be handled by a bootstrapping approach proposed in separate work.
+The non-Gaussian case lies beyond the scope of this simulation study.
 
@@
 First $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from ARIMA$(p,d,q)$ processes, where $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability.
-The errors driving these ARIMA processes denoted $\varepsilon$ are jointly normal $\{\varepsilon_{AA,t},\varepsilon_{AB,t},\varepsilon_{BA,t},\varepsilon_{BB,t}\} \overset{iid}{\sim} \mathcal{N}(\bm{0}, \bm{\Sigma})~\forall t$.
+The errors driving these ARIMA processes are jointly normal, and denoted by $\{\varepsilon_{AA,t},\varepsilon_{AB,t},\varepsilon_{BA,t},\varepsilon_{BB,t}\} \overset{iid}{\sim} \mathcal{N}(\bm{0}, \bm{\Sigma})~\forall t$.
 The parameters for the AR and MA components are randomly and uniformly generated from $[0.3,0.5]$ and $[0.3,0.7]$ respectively.
@@
 \end{align*}
-where $u_t \sim \mathcal{N}(0,\sigma^2_u)$ and $v_t \sim \mathcal{N}(0,\sigma^2_v)$.
-The aggregate series at in the middle level level, are given by:
+where $u_t \sim \mathcal{N}(0,\sigma^2_u)$ and $v_t \sim \mathcal{N}(0,\sigma^2_v)$. The aggregate series in the middle level are given by:
 \begin{align*}
@@
 \]
-
-To ensure noisier disaggregate series than aggregate series, we choose $\bm{\Sigma}, \sigma^2_u$ and $\sigma^2_v$ such that
+To ensure the disaggregate series are noisier than the aggregate series, we choose $\bm{\Sigma}, \sigma^2_u$ and $\sigma^2_v$ such that
 \[
-  \text{Var}(\varepsilon_{AA,t} + \varepsilon_{AB,t} + \varepsilon_{BA,t} + \varepsilon_{BB,t})
-  \le \text{Var}(\varepsilon_{AA,t}+\varepsilon_{AB,t}-v_t)
-  \le \text{Var}(\varepsilon_{AA,t}+u_t-0.5v_t)\,,
+  \var(\varepsilon_{AA,t} + \varepsilon_{AB,t} + \varepsilon_{BA,t} + \varepsilon_{BB,t})
+  \le \var(\varepsilon_{AA,t}+\varepsilon_{AB,t}-v_t)
+  \le \var(\varepsilon_{AA,t}+u_t-0.5v_t)\,,
 \]
@@
 %\[\bm{l}_1\bm{\Sigma} \bm{l}_1' - \bm{l}_2\bm{\Sigma} \bm{l}_2' \le \sigma^2_v \le \frac{4}{3}(\sigma^2_u + \bm{l}_3\bm{\Sigma} \bm{l}_3' - \bm{l}_2\bm{\Sigma} \bm{l}_2').\]
-The values of $\bm{\Sigma}$, $\sigma^2_u$ and $\sigma^2_v$, that we use and which satisfy these constraints are $\sigma^2_u = 19$, $\sigma^2_u = 18$ and
+The values of $\bm{\Sigma}$, $\sigma^2_u$ and $\sigma^2_v$ that we use and which satisfy these constraints are $\sigma^2_u = 19$, $\sigma^2_u = 18$ and
 \[
@@
 Tables~\ref{table:4} and~\ref{table:5} break down the forecasting performance of different reconciliation methods by considering univariate scores on each individual margin.
-The log score and CRPS are considered while skill scores are computed with the unreconciled forecast as a reference.
+The log score and CRPS are considered, while skill scores are computed with the unreconciled forecast as a reference.
 When broken down in this fashion, the methods based on MinT perform best for all series and always outperform bottom-up and unreconciled forecasts.
@@
 	\caption{Comparison of coherent forecasts.
-``Energy score'' and ``Variogram score'' columns give scores based on the joint forecast distribution of whole hierarchy.
-``Log score'' column gives the log scores of the joint forecast distribution of bottom level.
+``Energy score'' and ``Variogram score'' columns give scores based on the joint forecast distribution of the whole hierarchy.
+``Log score'' column gives the log scores of the joint forecast distribution of the bottom level.
 ``Skill score'' columns give the percentage skill score with reference to the bottom-up method.
-Entries in these columns show the percentage increase of score for different reconciliation methods relative to the bottom-up method.}\label{table:3}
+Entries in these columns show the percentage increase of scores for different reconciliation methods relative to the bottom-up method.}\label{table:3}
 
@@
 
-By redefining coherent forecasts and forecast reconciliation in geometric terms we have established two new theoretical results that support the use of projections for point forecast reconciliation, and crucially have extended these concepts to probabilistic forecasting.
-We show that for elliptical distributions, the true predictive density can be recovered by linear reconciliation and establish conditions for when this linear mapping is a projection.
-Although this optimal projection cannot feasibly be obtained in practice, a projection similar to the MinT procedure provides a good approximation in practice.
+By redefining coherent forecasts and forecast reconciliation in geometric terms, we have established two new theoretical results that support the use of projections for point forecast reconciliation, and have allowed us to extend these concepts to probabilistic forecasting.
+We have shown that for elliptical distributions the true predictive density can be recovered by linear reconciliation and we have established conditions for when this linear mapping is a projection.
+Although this optimal projection cannot feasibly be obtained in practice, a projection similar to the MinT procedure provides a good approximation in applications.
 This is supported by the results of a simulation study.
-Finally, we also discuss strategies for evaluating probabilistic forecasts for hierarchical time series establishing a key results regarding the impropriety of the log score with respect to incoherent forecasts.
+Finally, we have also discussed strategies for evaluating probabilistic forecasts for hierarchical time series, establishing a key result regarding the impropriety of the log score with respect to incoherent forecasts.
 
@@
 For example, having defined what amounts to an entire class of reconciliation methods for probabilistic forecasts it will be worthwhile investigating which specific projections are optimal.
-This is likely to depend on the specific scoring rule employed as well as the properties of base forecasts.
-Another avenue worth investigation is to consider whether it is possible to recover the true predictive distribution for non-elliptical distributions possible via a non-linear mapping $g(.)$.
+This is likely to depend on the specific scoring rule employed as well as the properties of the base forecasts.
+Another avenue worth investigating is to consider whether it is possible to recover the true predictive distribution for non-elliptical distributions via a non-linear mapping $g(.)$.
 

### 2018-07-23 ProbabilisticCoherence.tex
Fixed equation (1) in section 4
Changes related to George comments

@@
 In these so-called hierarchical time series, forecasts are often required for all individual series.
-To ensure aligned decision making, it is important for forecasts at the most disaggregated level add up to forecasts at more aggregated levels.
+To ensure aligned decision making, it is important that forecasts at the most disaggregated level add up to forecasts at more aggregated levels.
 This property is called ``coherence''.
@@
 To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$ and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.
-In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (Series $AA$, $AB$, $BA$ and $BB$) and then summed to recover all higher-level series.
-Alternatively, in the top-down approach \citep{Gross1990}, a top-level forecast is first produced (Series $Tot$) and bottom-level forecasts are recovered by disaggregating the forecast using either historical or forecasted proportions.
-A middle-out approach is a hybrid between these two, that for the hierarchy below would produce first stage forecasts for Series $A$ and $B$.
+In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (series $AA$, $AB$, $BA$ and $BB$) and then summed to recover all higher-level series.
+Alternatively, in the top-down approach \citep{Gross1990}, a top-level forecast is first produced (series $Tot$) and bottom-level forecasts are recovered by disaggregating the forecast using either historical or forecasted proportions.
+A middle-out approach is a hybrid between these two, that for the hierarchy below would produce first stage forecasts for series $A$ and $B$.
 
@@
 	\end{center}
-	\caption{A example of a two level hierarchical structure.}\label{fig1}
+	\caption{An example of a two level hierarchical structure.}\label{fig1}
 \end{figure}
@@
 Since these so-called `base' forecasts are rarely coherent in practice, they are subsequently adjusted or `reconciled' to ensure coherence.
+Note that we use coherence and reconciliation as distinct terms, in contrast to their at times ambiguous usage in the past.
 To date, reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators.
-These include Ordinary Least Squares {OLS} \citep{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix.
+These include Ordinary Least Squares {OLS} \cite{AthEtAl2009}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix.
 These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and, in some sense, hedge against the risk of model misspecification at a single level.
@@
 Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_{\mathfrak{s}}$.
-Here $\mathscr{F}_{\mathfrak{s}}$ is formed as collection of sets $s(\mathcal{B})$, where $s(\mathcal{B})$ denotes the image of the set $\mathcal{B}\in \mathscr{F}_{\mathbb{R}^m}$ under the mapping $s(.)$.
+Here $\mathscr{F}_{\mathfrak{s}}$ is formed as a collection of sets $s(\mathcal{B})$, where $s(\mathcal{B})$ denotes the image of the set $\mathcal{B}\in \mathscr{F}_{\mathbb{R}^m}$ under the mapping $s(.)$.
 
@@
 In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
-For this example, $\bm{R}_\perp'=\bm{S}$ and reconciliation corresponds to the OLS method.
+For this three variable hierarchy, $\bm{R}_\perp'=\bm{S}$ and reconciliation corresponds to the OLS method.
 For the case where $\bm{R}_\perp'\neq\bm{S}$, for example WLS and MinT, there are two possible interpretations.
@@
 	\end{align}
-	The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators\todo{Find reference or prove}, therefore
+	The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators\todo{Hunter}, therefore
 	 \begin{equation*}
@@
 The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.
-
-\todo[inline]{Equivalent to GTOP result in MinT paper?}
 
@@
 
-We now show that the true predictive distribution can be recovered for elliptical distributions via linear reconciliation.
+We now show that the true predictive distribution can be recovered for elliptical distributions by linear reconciliation via pre-multiplication and translation respectively by a matrix we denote ${\bm G}_{opt}$ and vector we denote  ${\bm d}_{opt}$.
 Here, for any square matrix $\bm{C}$, $\bm{C}^{1/2}$ and $\bm{C}^{-1/2}$ are defined to satisfy $\bm{C}^{1/2}(\bm{C}^{1/2})'=\bm{C}$ and $\bm{C}^{-1/2}(\bm{C}^{-1/2})'=\bm{C}^{-1}$, for example $\bm{C}^{1/2}$ may be obtained via the Cholesky or eigenvalue decompositions.
@@
 \begin{equation}\label{eq:(3.1.)}
-\E_{\bm{Q}}[S(P,\omega)] \le \E_{\bm{Q}}[S(Q,\omega)],
+\E_{\bm{Q}}[S(Q,\omega)] \le \E_{\bm{Q}}[S(P,\omega)],
 \end{equation}

### 2018-07-23 ProbabilisticCoherence.tex
more or george comments

@@
 To date, reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators.
-These include Ordinary Least Squares {OLS} \cite{AthEtAl2009}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix.
+These include Ordinary Least Squares {OLS} \citep{AthEtAl2009}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix.
 These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and, in some sense, hedge against the risk of model misspecification at a single level.
@@
 Many studies have discussed the relative advantages and disadvantages of bottom-up and top-down methods, and situations in which each would provide reliable forecasts \citep{Schwarzkopf1988,Kahn1998, Lapide1998,Fliedner2001}.
-A compromise between these two approaches is the middle-out method which entails forecasting each series of a selected middle level in the hierarchy and then forecasting upper levels by the bottom-up method and lower levels by the top-down method.
+A compromise between these two approaches is the middle-out method which entails forecasting each series of a selected middle-level in the hierarchy and then forecasting upper levels by the bottom-up method and lower levels by the top-down method.
 
@@
 
-%Consider a simple hierarchy with two bottom-level series $A$ and $B$ that add up to the top level series $Tot$.
+%Consider a simple hierarchy with two bottom-level series $A$ and $B$ that add up to the top-level series $Tot$.
 Suppose the forecasts of these series at time $t+h$ are given by $\breve{\bm{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$.
@@
 	\end{align}
-	The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators\todo{Hunter}, therefore
+	The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators \citep{Hun2001}, therefore
 	 \begin{equation*}
@@
 \begin{equation}\label{eq:(3.1.)}
-\E_{\bm{Q}}[S(Q,\omega)] \le \E_{\bm{Q}}[S(P,\omega)],
+\E_{\bm{Q}}[S(P,\omega)] \le \E_{\bm{Q}}[S(Q,\omega)],
 \end{equation}
@@
 \end{align}
-where $\breve{F}_i$ is the cumulative distribution function of the $i$th margin of the probabilistic forecast, $\breve{Y}_i$ and $\breve{Y}^*_{T+h,i}$ are independent copies of a random variable with distribution $\breve{F}_i$, and $y_i$ is the outcome of the $i$th margin.
+where $\breve{F}_i$ is the cumulative distribution function of the $i$th margin of the probabilistic forecast, $\breve{Y}_i$ and $\breve{Y}^*_{i}$ are independent copies of a random variable with distribution $\breve{F}_i$, and $y_i$ is the outcome of the $i$th margin.
 The expectations in the second line can be approximated by Monte Carlo when a sample from the predictive distribution is available.
@@
 The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the representation in terms of expectations leads itself to easy computation when samples from the probabilistic forecast are available.
-An interesting limiting case is where $\alpha=2$, where it can be easily shown that
-\begin{equation} \label{eq:(5.1)}
-\text{ES}(\breve{\bm{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
-\end{equation}
-where $\breve{\bm{\mu}}_{T+h} =\E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $.
-In this limiting case, the energy score only measures the accuracy of the forecast mean (not the entire distribution), and the energy score is proper but not strictly proper.
+An interesting limiting case is where $\alpha=2$, where it can be easily shown that energy score simplifies to mean squared error around the mean of the predictive distribution.
+In this limiting case, the energy score is proper but not strictly proper.
 \citet{Pinson2013a} also argue that the energy score has low discriminative ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
@@
 \begin{equation}
-\text{VS}(\breve{F}, \bm{y}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{i} - y_{j}|^p - E_{\breve{Y}_i,\breve{Y}_j} |\breve{Y}^k_{i}-\breve{Y}^k_{j}|^p\right)^2.
+\text{VS}(\breve{F}, \bm{y}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{i} - y_{j}|^p - E_{\breve{Y}_i,\breve{Y}_j} |\breve{Y}_{i}-\breve{Y}_{j}|^p\right)^2.
 \end{equation}
@@
 \[
-S\left(\tilde{f},\bm{z}^{(1)}_t\right) = -\log f_1\left(\bm{z}^{(1)}_t\right),
+S\left(f,\bm{z}^{(1)}_t\right) = -\log f_1\left(\bm{z}^{(1)}_t\right),
 \]
@@
 &= -\log f_1(\bm{z}^{(1)}_t)+\frac{n-m}{2}\log(2\pi\sigma^2)\\
-&<-\log f_1(\bm{z}^{(1)}_t).
+&<-\log f_1(\bm{z}^{(1)}_t)=S\left(f,\bm{z}^{(1)}_t\right).
 \end{align}
@@
 In this case we recommend computing the energy score using the full hierarchy.
-Although the discussion here is related to energy score, the same logic holds for other multivariate scores that are not invariant to orthogonal rotations, for example the variogram score.
+Although the discussion here is related to energy score, the same logic holds for other multivariate scores, for example the variogram score.
 
@@
 	\hline
-	Log Score & Not proper & Ordering preserved if compared using\\ &&bottom level only\\
+	Log Score & Not proper & Ordering preserved if compared using\\ &&bottom-level only\\
 	Energy/ & Proper & Full hierarchy should be used\\
@@
 \end{align*}
-where $u_t \sim \mathcal{N}(0,\sigma^2_u)$ and $v_t \sim \mathcal{N}(0,\sigma^2_v)$. The aggregate series in the middle level are given by:
+where $u_t \sim \mathcal{N}(0,\sigma^2_u)$ and $v_t \sim \mathcal{N}(0,\sigma^2_v)$. The aggregate series in the middle-level are given by:
 \begin{align*}
@@
 Tables~\ref{table:4} and~\ref{table:5} break down the forecasting performance of different reconciliation methods by considering univariate scores on each individual margin.
+Tables~\ref{table:4} summarises results for the top and middle-level, Table~\ref{table:5} does the same for bottom-level.
 The log score and CRPS are considered, while skill scores are computed with the unreconciled forecast as a reference.
@@
 ``Energy score'' and ``Variogram score'' columns give scores based on the joint forecast distribution of the whole hierarchy.
-``Log score'' column gives the log scores of the joint forecast distribution of the bottom level.
+``Log score'' column gives the log scores of the joint forecast distribution of the bottom-level.
 ``Skill score'' columns give the percentage skill score with reference to the bottom-up method.
@@
 We have shown that for elliptical distributions the true predictive density can be recovered by linear reconciliation and we have established conditions for when this linear mapping is a projection.
-Although this optimal projection cannot feasibly be obtained in practice, a projection similar to the MinT procedure provides a good approximation in applications.
+Although this projection cannot feasibly be obtained in practice, a projection similar to the MinT procedure provides a good approximation in applications.
 This is supported by the results of a simulation study.

### 2018-08-08 ProbabilisticCoherence.tex
Fixed equation (1) in section 4
some changes made in light of Mervyn's suggestions

@@
   Forecast reconciliation involves adjusting forecasts to ensure coherence with aggregation constraints.
-We extend this concept from point forecasts to probabilistic forecasts by redefining forecast reconciliation in terms of linear mappings in general, and projections more specifically.
-New theorems establish that the true predictive distribution can be recovered in the elliptical case by a linear mapping, and general conditions are derived for when this linear mapping is a projection.
+We extend this concept from point forecasts to probabilistic forecasts by redefining forecast reconciliation in terms of linear functions in general, and projections more specifically.
+New theorems establish that the true predictive distribution can be recovered in the elliptical case by linear reconciliation, and general conditions are derived for when this is a projection.
 A geometric interpretation is also used to prove two new theoretical results for point forecasting; that reconciliation via projection both preserves unbiasedness and dominates unreconciled forecasts in a mean squared error sense.
@@
 Large collections of time series often follow some aggregation structure.
-For example, the electricity demand of a country can be disaggregated according to a geographic hierarchy of states, cities, and individual households, or by a temporal hierarchy of yearly, quarterly and monthly demand.
-In these so-called hierarchical time series, forecasts are often required for all individual series.
+For example, the electricity demand of a country can be disaggregated according to a geographic hierarchy of states, cities, and individual households.
 To ensure aligned decision making, it is important that forecasts at the most disaggregated level add up to forecasts at more aggregated levels.
 This property is called ``coherence''.
-This issue has been extensively covered for point forecasting in a literature we review below, while the case of probabilistic forecasting is a gap that we seek to address in this work.
+On the other hand ``reconciliation'' is a process whereby incoherent forecasts are made coherent.
+Both of these concepts have been developed extensively for point forecasting.
+Generalising both of these concepts, particularly the latter, to probabilistic forecasting is a gap that we seek to address in this work.
+We do so by first providing a novel geometric interpretation to coherence and reconciliation in the point forecasting case.
+This can easily be generalised to probabilistic forecasting allowing us to derive further results for elliptical distributions as well as provide insight into forecast evaluation via multivariate  scoring rules.
 
@@
 A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \citep[see][and references therein]{Gneiting2014}.
-Indeed to the best of our knowledge, the (as yet unpublished) work of \citep{BenTaieb2017} is the only paper to deal with the issue of coherent probabilistic forecasts, and although they reconcile the means of the predictive distributions, the overall distributions are constructed in a bottom-up fashion rather than use a reconciliation process.
+Indeed to the best of our knowledge, the (as yet unpublished) work of \citep{BenTaieb2017} is the only paper to deal with coherent probabilistic forecasts, and although they reconcile the means of the predictive distributions, the overall distributions are constructed in a bottom-up fashion rather than use a reconciliation process.
 In contrast, the main objective of our paper is to generalise both coherence and reconciliation from point to probabilistic forecasting.
@@
 In addition to being highly intuitive, this allows us to establish a number of theoretical results.
-We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts, while the second shows that reconciled forecasts dominate unreconciled forecasts since projections are bounded operators.
+We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts, while the second shows that reconciled forecasts dominate unreconciled forecasts via the distance reducing property of projections.
 We provide definitions of coherence and forecast reconciliation in the probabilistic setting, and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation.
@@
 
-We also cover the issue of forecast evaluation of probabilistic forecasts via scoring rules.
+We also cover the topic of forecast evaluation of probabilistic forecasts via scoring rules.
 In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.
@@
 
-The remainder of the papers is structured as follows.
+The remainder of the paper is structured as follows.
 In Section~\ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.
@@
 
-Throughout the paper, we will follow notational conventions used in \citet{Wickramasuriya2017} as much as possible.
 A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables.
 We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$.
-For example, for the hierarchy in Figure~\ref{fig1}, $n=7$ and $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.
 The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.
-For example, for the hierarchy in Figure~\ref{fig1}, $m=4$ and $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.
 The hierarchical structure of the data imply the following holds for all $t$:
@@
 \end{equation}
-where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints. For the hierarchy in Figure~\ref{fig1}
+where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints.
+
+To clarify these concepts consider the example of the hierarchy in Figure~\ref{fig1}, $n=7$ and $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.
+For example, for the hierarchy in Figure~\ref{fig1}, $m=4$ and $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.
+For the hierarchy in Figure~\ref{fig1}
 \[
@@
 
+While most applications of hierarchical time series to date have involved data that respect an aggregation structure, in principle the ${\bm S}$ can encode any linear constraints including weighted sums or even cases where some variables in the hierarchy are formed by taking the difference of two other variables.
+
 \subsection{Coherent point forecasts}\label{sec:cohpointf}
@@
 
-It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a linear mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$.
+It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$.
 Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.
@@
 
-Let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple, where $\mathscr{F}_{\mathbb{R}^m}$ is the usual $\sigma$-algebra on $\mathbb{R}^m$.
+Let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple, where $\mathscr{F}_{\mathbb{R}^m}$ is the usual Borel $\sigma$-algebra on $\mathbb{R}^m$.
 Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_{\mathfrak{s}}$.
-Here $\mathscr{F}_{\mathfrak{s}}$ is formed as a collection of sets $s(\mathcal{B})$, where $s(\mathcal{B})$ denotes the image of the set $\mathcal{B}\in \mathscr{F}_{\mathbb{R}^m}$ under the mapping $s(.)$.
+Here $\mathscr{F}_{\mathfrak{s}}$ is a collection of sets $s(\mathcal{B})$, where $s(\mathcal{B})$ denotes the image of the set $\mathcal{B}\in \mathscr{F}_{\mathbb{R}^m}$ under the mapping $s(.)$.
 
@@
 As discussed, reconciliation is distinct from coherence, since the former refers to a process whereby incoherent forecasts are made coherent.
-Initially we define point forecast reconciliation, before extending the idea to the probabilistic setting.
+Although reconciliation methods for point forecasts are extant in the literature they are rarely defined explicitly.
+We do so here in slightly more general terms than usual.
+We then extend this idea to the novel concept of probabilistic reconciliation.
 
@@
 Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ conditional on information up to and including time $t$.
+We now introduce a linear function that converts unreconciled forecasts into new bottom level forecasts.
 Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively, and let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})=\bm{G}\bm{y}+\bm{d}$.
+A composition of $g$ and $s(.)$ gives the following definition for point forecast reconciliation.
 
@@
 Several choices of $g(.)$ currently extant in the literature, including the OLS, WLS and MinT methods, are special cases where $s\circ g$ is a projection.
-These can be defined so that $\bm{G}=({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ and $\bm{d}=\bm{0}$.
-Here, ${\bm{R}_{\perp}}$ is a $n\times m$ orthogonal complement to the $n \times (n-m)$ matrix $\bm{R}$, where the columns of the latter span the null space of $\mathfrak{s}$.
+These can be defined so that $\bm{G}=({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ and $\bm{d}=\bm{0}$, were, ${\bm{R}_{\perp}}$ is a $n\times m$ orthogonal complement to an $n \times (n-m)$ matrix $\bm{R}$, where the columns of the latter span the null space of $\mathfrak{s}$.
 For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
@@
 Let $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$ respectively, after a change of basis.
-The process of reconciliation involves setting the values of the reconciled bottom-level series to be $\tilde{\bm{b}}_{t+h|t}$, and setting $\tilde{\bm{a}}_{t+h}=\bm{0}$ to ensure coherence.
+The process of reconciliation involves setting the values of the reconciled bottom-level series to be $\tilde{\bm{b}}_{t+h|t}$, and ignoring $\tilde{\bm{a}}_{t+h}$ to ensure coherence.
 From properties of linear algebra it follows that
@@
 \]
-while setting $\tilde{\bm{a}}_{t+h|t}=\bm{0}$ gives the reconciled point forecast
+while the reconciled point forecast is
 \[
@@
 \begin{theo}[Unbiasedness preserving property]
-  For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast will also be an unbiased prediction as long as $s\circ g$ is a projection.
+  For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also be an unbiased prediction as long as $s\circ g$ is a projection.
 \end{theo}
@@
 \begin{theo}[Distance reducing property]
-	If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection, then the following inequality holds:
+	If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
 	  \begin{equation}
@@
 A more formal definition is given below.
-Let $(\mathbb{R}^n, \mathscr{F}_{\mathbb{R}^n}, \hat{\nu})$ be a probability triple that is incoherent and which characterises forecast uncertainty for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.
+Let $(\mathbb{R}^n, \mathscr{F}_{\mathbb{R}^n}, \hat{\nu})$ be a probability triple that is not coherent and which characterises forecast uncertainty for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.
 This is obtained from the first stage of the forecasting process; e.g., by modelling and forecasting each series individually.
-Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear mapping, and let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$.
+Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear function, and let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$.
 
@@
 This definition extends the notion of forecast reconciliation to the probabilistic setting.
-Under point reconciliation methods, the reconciled point forecast is equal to the unreconciled point forecast after the latter is passed through two linear mappings.
-Similarly, probabilistic forecast reconciliation assigns the same probability to two sets where the points in one set are obtained by passing all points in the other set through two linear mappings.
-This is depicted schematically when $s\circ g$ is a projection in Figure~\ref{fig:probfr_sch}.
+Under point reconciliation methods, the reconciled point forecast is equal to the unreconciled point forecast after the latter is passed through two linear functions.
+Similarly, probabilistic forecast reconciliation assigns the same probability to two sets where the points in one set are obtained by passing all points in the other set through two linear functions.
+This is depicted in Figure~\ref{fig:probfr_sch} schematically when $s\circ g$ is a projection.
 
@@
 A number of insights can be drawn from this theorem.
-First, although a linear mapping $g(.)$ can be used to recover the true predictive in the elliptical case, the same does not hold in general.
+First, although a linear function $g(.)$ can be used to recover the true predictive in the elliptical case, the same does not hold in general.
 Second, $g(.)$ is not, in general, a projection matrix.
@@
 \begin{equation}\label{eq:(3.1.)}
-\E_{\bm{Q}}[S(P,\omega)] \le \E_{\bm{Q}}[S(Q,\omega)],
+\E_{\bm{Q}}[S(Q,\omega)] \le \E_{\bm{Q}}[S(P,\omega)] ,
 \end{equation}
@@
 By redefining coherent forecasts and forecast reconciliation in geometric terms, we have established two new theoretical results that support the use of projections for point forecast reconciliation, and have allowed us to extend these concepts to probabilistic forecasting.
-We have shown that for elliptical distributions the true predictive density can be recovered by linear reconciliation and we have established conditions for when this linear mapping is a projection.
+We have shown that for elliptical distributions the true predictive density can be recovered by linear reconciliation and we have established conditions for when this is a projection.
 Although this projection cannot feasibly be obtained in practice, a projection similar to the MinT procedure provides a good approximation in applications.
 This is supported by the results of a simulation study.
-Finally, we have also discussed strategies for evaluating probabilistic forecasts for hierarchical time series, establishing a key result regarding the impropriety of the log score with respect to incoherent forecasts.
+Finally, we have also discussed strategies for evaluating probabilistic forecasts for hierarchical time series advocating the use of multivariate scoring rules on the full hierarchy, while establishing a key result regarding the impropriety of the log score with respect to incoherent forecasts.
 
@@
 This is likely to depend on the specific scoring rule employed as well as the properties of the base forecasts.
-Another avenue worth investigating is to consider whether it is possible to recover the true predictive distribution for non-elliptical distributions via a non-linear mapping $g(.)$.
+Another avenue worth investigating is to consider whether it is possible to recover the true predictive distribution for non-elliptical distributions via a non-linear function $g(.)$.
 

### 2018-08-08 Presentation/ProbForeRec.tex
updated presentation up to probabilistic

@@
 \title{Probabilistic Forecast Reconciliation}
-\date{June 20, 2018}
+\date{August 15, 2018}
 \author[GPAH]{Puwasala Gamakumara, Anastasios Panagiotelis, George Athanasopoulos and Rob Hyndman}
@@
   \end{frame}
+  \begin{frame}{Coherent Subspace}
+    \begin{definition} 
+	  The {\bf coherent subspace} is the linear subspace spanned by the columns of ${\bm S}$, i.e. $\mathfrak{s}=\mbox{sp}({\bm S})$
+    \end{definition}
+    Instead of using bottom-level series a different combination of $m$ {\bf basis series} could be used (e.g.
+top and $m-1$ bottom).
+Although ${\bm S}$ would be different $\mathfrak{s}$ would be the same.
+  \end{frame}
+  \begin{frame}{Coherent Point Forecast}
+  \begin{definition} 
+  	A {\bf coherent point forecast} is any forecast lying in the linear subspace $\mathfrak{s}$
+  \end{definition}
+  \end{frame}
+  \begin{frame}{Reconciled Point Forecast}
+  Let $\hat{\bm y}\in\mathbb{R}^n$ be an incoherent forecast and $g(.)$ be a function $g:\mathbb{R}^n\rightarrow\mathbb{R}^m$.
+  \begin{definition} 
+	A {\bf point forecast} $\tilde{\bm y}$ is reconciled with respect to $g(.)$ iff 
+	\begin{equation*}
+    \tilde{\bm y}={\bm S}g(\hat{\bm y})
+	\end{equation*}
+  \end{definition}
+  when $g(.)$ is linear it is easier to write $\tilde{\bm y}={\bm S}{\bm G}{\bm y}$
+  \end{frame}
+  \begin{frame}{Special Case: Projection}
+  \begin{itemize}
+   \item An important special case is where ${\bm S}{\bm G}$ is a projection.
+  \begin{itemize}
+  	\item ${\bm S}{\bm G}$ is symmetric
+  	\item ${\bm S}{\bm G}$ is idempotent
+  \end{itemize}
+  \item Let ${\bm v}\in\mathfrak{s}$ 
+    \begin{itemize}
+    	\item ${\bm S}{\bm G}{\bm v}$ will also lie in $\mathfrak{s}$.
+    	\item ${\bm S}{\bm G}{\bm v}={\bm v}$ only when ${\bm S}{\bm G}$ is a projection.
+    \end{itemize}
+  \end{itemize}
+  \end{frame}
   \begin{frame}{Geometry}
@@
   \end{frame}
+  \begin{frame}{Projections preserve unbiasedness}
+	Let $\hat{\bm y}_{t+h|t}$ be an unbiased forecast that is $E_{1:t}(\hat{\bm y}_{t+h|t})={\bm \mu_{t+h|t}}$ where ${\bm \mu_{t+h|t}}=E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$
+	\begin{theorem}
+	  The reconciled forecast $\tilde{\bm y}_{t+h|t}={\bm S}{\bm G}\hat{\bm y}_{t+h|t}$ will also be unbiased iff ${\bm S}{\bm G}$ is a projection.
+    \end{theorem}
+    Previously, this was often stated as an assumption that ${\bm S}{\bm G}{\bm S}={\bm S}$.    
+  \end{frame}
+  \begin{frame}{Proof}
+  Very easy proof
+  \begin{align*}
+  E_{1:t}(\tilde{\bm{y}}_{t+h|t})
+  &= E_{1:t}(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t})\\
+  &= \bm{S}\bm{G}E_{1:t}(\hat{\bm{y}}_{t+h|t})\\
+  &= \bm{S}\bm{G}\bm{\mu}_{t+h|t}\\
+  &= \bm{\mu}_{t+h|t}
+  \end{align*}
+  The last equality does not hold for ${\bm G}$ in general.
+  \end{frame}
+  \begin{frame}{Why reconciliation works}
+  \begin{itemize}
+  	\item The realised observation always lies on $\mathfrak{s}$.
+  	\item Orthogonal projections always get us `closer' to all points in $\mathfrak{s}$ including the actual realisation.
+  	\item Ergo reconciliation reduces the error, not only in expectation, but always. 
+  	\item Oblique projections have the same property for non-Euclidean distance. 
+  \end{itemize}
+  \end{frame}
+  \begin{frame}{Geometry}
+  \vspace{-2.3cm}
+  \centering 
+  \input{Figs/orth_pointforerec_schematic}
+  \end{frame}
   \section{Probabilistic Reconciliation}
-  \begin{frame}{Coherent Subspace}
-  	\begin{definition} 
-  		The {\bf coherent subspace} is the linear subspace spanned by the columns of ${\bm S}$, i.e. $\mathfrak{s}=\mbox{sp}({\bm S})$
-  	\end{definition}
-    Instead of using bottom-level series a different combination of $m$ {\bf basis series} could be used (e.g.
-top and $m-1$ bottom).
-Although ${\bm S}$ would be different $\mathfrak{s}$ would be the same.
-  \end{frame}
   \begin{frame}{Coherent Probabilistic Forecast}
@@
   \begin{frame}{Reconciled Probabilistic Forecast}
-  	Let $g:\mathbb{R}^n\rightarrow\mathbb{R}^m$ be a linear map.  Then 
+  	Let $g:\mathbb{R}^n\rightarrow\mathbb{R}^m$ be a linear function.  Then 
   	\begin{definition}

### 2018-08-08 Presentation/ProbForeRec.tex
updated presentation

@@
   \end{definition}
-  when $g(.)$ is linear it is easier to write $\tilde{\bm y}={\bm S}{\bm G}{\bm y}$
+  when $g(.)$ is linear it is easier to write $\tilde{\bm y}={\bm S}{\bm G}\hat{\bm y}$
   \end{frame}
@@
   \end{align*}
-  The last equality does not hold for ${\bm G}$ in general.
+  The last equality does not hold for ${\bm G}$ in general but does hold when ${\bm S}{\bm G}$ is a projection.
   \end{frame}
@@
   	\item Orthogonal projections always get us `closer' to all points in $\mathfrak{s}$ including the actual realisation.
-  	\item Ergo reconciliation reduces the error, not only in expectation, but always. 
+  	\item Ergo reconciliation reduces the error and not just in expectation. 
   	\item Oblique projections have the same property for non-Euclidean distance. 
@@
   \begin{frame}{Elliptical distributions}
-  	Let the unreconciled density be elliptical with location  $\hat{\bm{\mu}}$ and scale $\hat{\bm{\Sigma}}$ and let the true predictive density be elliptical with location  ${\bm{\mu}}$ and scale ${\bm{S}}{\bm{\Omega}}{\bm{S}}'$.
+  	Let the true predictive densities be elliptical.
   	\begin{theorem}
-  		The true predictive distribution can be recovered via linear reconciliation.
-The optimal (but infeasible) mapping is $g(\breve{\bm y})={\bm G}_{opt}\breve{\bm y}+{\bm d}_{opt}$ where $\bm{G}_{opt}={\bm\Omega}^{1/2}{\hat{\bm{\Sigma}}}^{-1/2}$ and ${\bm d}_{opt}={\bm G}_{opt}\left({\bm \mu}-\hat{\bm \mu}\right)$.
+  		There exists a function $g(.)$ such that the true predictive distribution can be recovered by linear reconciliation as long as the unreconciled probabilistic forecast comes from the correct elliptical class.
   	\end{theorem}
-    This follows from the closure property of elliptical distributions under affine transformations and marginalisation.
+    This follows from the closure property of elliptical distributions under affine transformations and marginalisation.  Conditions are also derived for when this $g(.)$ is also a projection.
   \end{frame}
@@
   \end{frame}
-  \begin{frame}{Reconciled v Unreconciled}
+  \begin{frame}{Coherent v Incoherent}
 	When comparing reconciled and unreconciled probabilistic forecasts on the basis of log score
@@
    	\begin{itemize}
-   		\item If you want to see tables with numbers see the paper.
    		\item The main takeaway messages are:
@@
    \end{frame}
-    \begin{frame}{The paper}
-    	\begin{itemize}
-    		\item A paper will be available soon (end of July).
-    		\item Google {\em EBS Monash Working Paper}.
-    		\item Or email me :)
-    	\end{itemize}
-    \end{frame}
 \end{document}

### 2018-08-21 ProbabilisticCoherence.tex
converted to JASA style

@@
-\documentclass[a4paper, 11pt]{article}
-\usepackage{monashwp}
+%&latex
+\documentclass[12pt]{article}
+\usepackage{amsmath}
+\usepackage{graphicx,psfrag,epsf}
+\usepackage{enumerate}
+\usepackage{natbib}
+\usepackage{url} % not crucial - just used below for the URL
+
 \usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
@@
 \usepackage{amsfonts}
-\hypersetup{citecolor=blue,linkcolor=blue,urlcolor=blue}
-\DeclareNameAlias{sortname}{last-first}
+
+\pdfminorversion=4
+% NOTE: To produce blinded version, replace "0" with "1" below.
+\newcommand{\blind}{0}
+
+% DON'T change margins - should be 1 inch all around.
+\addtolength{\oddsidemargin}{-.5in}%
+\addtolength{\evensidemargin}{-.5in}%
+\addtolength{\textwidth}{1in}%
+\addtolength{\textheight}{-.3in}%
+\addtolength{\topmargin}{-.8in}%
+
 \DeclareMathOperator*{\argmin}{arg\,min}
@@
 \def\var{\text{Var}}
-\mathtoolsset{showonlyrefs=true}
 
@@
 
-\bibliography{References_paper1}
-
-\title{Probabilistic Forecasts in Hierarchical~Time~Series}
-\author{Puwasala Gamakumara\\ Anastasios Panagiotelis\\ George Athanasopoulos\\ Rob J Hyndman}
-
-\addresses{\textbf{Puwasala Gamakumara}\\
+\begin{document}
+
+	%\bibliographystyle{natbib}
+
+	\def\spacingset#1{\renewcommand{\baselinestretch}%
+		{#1}\small\normalsize} \spacingset{1}
+
+	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+	\if1\blind
+	{
+		\title{\bf Probabilistic Forecasts in Hierarchical~Time~Series}
+		\author{Puwasala Gamakumara\thanks{
+				The authors gratefully acknowledge \textit{please remember to list all relevant funding sources in the unblinded version}}\hspace{.2cm}\\
 			    Department of Econometrics and Business Statistics,\\
 			    Monash University,\\ VIC 3800, Australia.\\
-  Email: Puwasala.Gamakumara@monash.edu \\[1cm]
-  \textbf{Anastasios Panagiotelis}\\
+			    Email: Puwasala.Gamakumara@monash.edu \\
+			    and \\
+			    Anastasios Panagiotelis\\
 			    Department of Econometrics and Business Statistics,\\
 		    	Monash University,\\ VIC 3800, Australia.\\
-  Email: Anastasios.Panagiotelis@monash.edu\\[1cm]
-  \textbf{George Athanasopoulos}\\
+			    Email: Anastasios.Panagiotelis@monash.edu \\
+			    and \\
+		        George Athanasopoulos\\
 		        Department of Econometrics and Business Statistics,\\
 		        Monash University,\\ VIC 3800, Australia.\\
-  Email: George.Athanasopoulos@monash.edu\\[1cm]
-  \textbf{Rob J Hyndman}\\
+		        Email: george.athanasopoulos@monash.edu \\
+		        and \\
+	            Rob J Hyndman\\
 	            Department of Econometrics and Business Statistics,\\
 	            Monash University,\\ VIC 3800, Australia.\\
-  Email: Rob.Hyndman@monash.edu}
-
-\lfoot{\sf Gamakumara, Panagiotelis, Athanasopoulos \& Hyndman: \today}
-
-\begin{document}
-
+	            Email: rob.hyndman@monash.edu \\}
 		\maketitle
+	} \fi
+
+	\if0\blind
+	{
+		\bigskip
+		\bigskip
+		\bigskip
+		\begin{center}
+			{\LARGE\bf Probabilistic Forecasts in Hierarchical~Time~Series}
+		\end{center}
+		\medskip
+	} \fi
+
+	\bigskip
 
@@
 \end{abstract}
+
+\noindent%
+{\it Keywords:}  3 to 6 keywords, that do not appear in the title
+\vfill
+
+\newpage
+\spacingset{1.45} % DON'T change the spacing!
 
@@
 Here, $\hat{\bm{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, $\hat{\bm{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}, $\hat{\bm{W}}^{wls}$ is the diagonal matrix with diagonal elements $w_{ii}$, and $\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$, where $w_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{W}}^{sam}$.}\label{table:2}
-	\centering\setstretch{1.5}
+	\centering
 	\begin{tabular}{lll}
@@
 \newpage
-\printbibliography
+
+\bibliographystyle{agsm}
+
+\bibliography{References_paper1}
+
 \end{document}

### 2018-08-21 ProbabilisticCoherence.tex
Added keywords and acknowledgements

@@
 % NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{0}
+\newcommand{\blind}{1}
 
@@
 		        \author{Puwasala Gamakumara\thanks{
-				The authors gratefully acknowledge \textit{please remember to list all relevant funding sources in the unblinded version}}\hspace{.2cm}\\
+		        The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.  We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
 			    Department of Econometrics and Business Statistics,\\
@@
 \noindent%
-{\it Keywords:}  3 to 6 keywords, that do not appear in the title
+{\it Keywords:}  Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
 \vfill

### 2018-08-24 ProbabilisticCoherence.tex
Few minor cleanups based on last reading. Now submitted to JASA.

@@
 \noindent%
-{\it Keywords:}  Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
+{\it Keywords:}  Forecast Reconciliation, Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
 \vfill
@@
 \section{Introduction}\label{sec:intro}
-
-%Sketch narrative to tell
-%\begin{itemize}
-%	\item Coherence is important in point forecasting to
-%	\begin{itemize}
-%		\item Align decisions
-%		\item Improve forecasts
-%	\end{itemize}
-%	\item We propose a geometric interpretation via linear transformations including special case of projections.
-%	\item These nest existing methods but the interpretation has advantages
-%	\begin{itemize}
-%		\item Prove that projections preserve unbiasedness. Previously assumed in special cases.
-%		\item Prove reconciliation (using projection) always improves sum of squared errors (or a scaled/transformed version thereof).
-%		\item Most importantly generalises to probabilistic forecasting.
-%	\end{itemize}
-%    \item For elliptical distributions, true predictive can be recovered via linear reconciliation and in special cases, via projection.
-%    \item Discuss evaluation of forecasts
-%    \begin{itemize}
-%    	\item Log score improper when coherent v incoherent
-%    	\item Energy score cn be used instead
-%    	\item Discuss scores for coherent v coherent.
-%    \end{itemize}
-%    \item Finally evidence MinT is best from simulation
-%\end{itemize}
 
@@
 To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$ and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.
-In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (series $AA$, $AB$, $BA$ and $BB$) and then summed to recover all higher-level series.
+In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (series $AA$, $AB$, $BA$ and $BB$) and then summed to recover forecasts for all higher-level series.
 Alternatively, in the top-down approach \citep{Gross1990}, a top-level forecast is first produced (series $Tot$) and bottom-level forecasts are recovered by disaggregating the forecast using either historical or forecasted proportions.
-A middle-out approach is a hybrid between these two, that for the hierarchy below would produce first stage forecasts for series $A$ and $B$.
+A middle-out approach is a hybrid between these two, that for the hierarchy in Figure~\ref{fig1} would produce first stage forecasts for series $A$ and $B$.
 
@@
 To date, reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators.
-These include Ordinary Least Squares {OLS} \citep{AthEtAl2009}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix.
-These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and, in some sense, hedge against the risk of model misspecification at a single level.
+These include Ordinary Least Squares {OLS} \citep{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix.
+These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{AthEtAl2009,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and, in some sense, hedge against the risk of model misspecification at a single level.
 
@@
 
-%In the bottom-up approach, forecasts of the lowest level are first generated and they are simply aggregated to forecast upper levels of the hierarchy \citep{Dunn1976}.
-In contrast, the top-down approach involves forecasting the most aggregated series first and then disaggregating these forecasts down the hierarchy based on the corresponding proportions of observed data \citep{Gross1990}.
-Many studies have discussed the relative advantages and disadvantages of bottom-up and top-down methods, and situations in which each would provide reliable forecasts \citep{Schwarzkopf1988,Kahn1998, Lapide1998,Fliedner2001}.
-A compromise between these two approaches is the middle-out method which entails forecasting each series of a selected middle-level in the hierarchy and then forecasting upper levels by the bottom-up method and lower levels by the top-down method.
-
-%It is apparent that these three approaches use only part of the information available when producing coherent forecasts.
-This might result in inaccurate forecasts.
-For example, if the bottom-level series are highly volatile or noisy, and hence challenging to forecast, then the resulting forecasts from the bottom-up approach are likely to be inaccurate.
-
-%As an alternative to these traditional methods, \citet{Hyndman2011} proposed to utilize the information from all levels of the hierarchy to obtain coherent point forecasts in a two stage process.
-In the first stage, the forecasts of all series are independently obtained by fitting univariate models for individual series in the hierarchy.
-It is unlikely that these forecasts are coherent.
-Thus in the second stage, these forecasts are optimally combined through a regression model to obtain coherent forecasts.
-This second step is referred to as ``reconciliation'' since it takes a set of incoherent forecasts and revises them to be coherent.
-The approach was further improved by \citet{Wickramasuriya2017} who proposed the ``MinT'' algorithm to obtain optimally reconciled point forecasts by minimizing the mean squared coherent forecast errors.
-
-%Traditional bottom-up, top-down and middle-out forecasting methods are not strictly reconciliation methods since they use only a part of the information from the hierarchy to produce coherent forecasts.
-
-%Previous studies on coherent point forecasting have shown that reconciliation provides better coherent forecasts than the traditional bottom-up and top-down methods \citep{Hyndman2011,VanErven2015a,Wickramasuriya2017}.
-However, this idea has not been explored in the context of probabilistic forecasting.
-
-%Point forecasts are limited because they provide no indication of forecast uncertainty.
-Providing prediction intervals helps, but a richer description of forecast uncertainty is obtained by estimating the entire forecast distribution.
-These are often called ``probabilistic forecasts'' \citep{Gneiting2014}.
-For example, \citet{McSharry2005} produced probabilistic forecasts for electricity demand, \citet{BenTaieb2017} for smart meter data, \citet{Pinson2009} for wind power generation, and \citet{Gel2004}, \citet{Gneiting2005a} and \citet{Gneiting2005} for various weather variables.
-
-%Although there is a rich and growing literature on producing coherent point forecasts of hierarchical time series, little attention has been given to coherent probabilistic forecasts.
-The only relevant paper we are aware of is \citet{BenTaieb2017}, who recently proposed an algorithm to produce coherent probabilistic forecasts and applied it to UK electricity smart meter data.
-In their approach, a sample from the bottom-level forecast distribution is first generated, and then aggregated to obtain coherent probabilistic forecasts of the upper levels of the hierarchy.
-Hence this method is a bottom-up approach.
-They propose to first use the MinT algorithm to reconcile the means of the bottom-level forecast distributions, and then a copula-based approach is employed to model the dependency structure of the hierarchy.
-The resulting multi-dimensional distribution is used to generating empirical forecast distributions for all bottom-level series.
-Thus, while \citet{BenTaieb2017} provide coherent probabilistic forecasts, they do no forecast reconciliation of the distributions.
-In that sense, their approach is analogous to bottom-up point forecasting rather than forecast reconciliation.
-%
-%After introducing our notation in Section~\ref{sec:notation}, we define what is meant by probabilistic forecast reconciliation for hierarchical time series in Section~\ref{sec:definitions}.
-First, we provide a new definition for coherency of point forecasts, and the reconciliation of a set of incoherent point forecasts, using concepts related to vector spaces and measure theory.
-Based on these, we provide a rigorous definition for probabilistic forecast reconciliation, and how we can reconcile the incoherent forecast densities in practice.
-%
-%Further, due to the aggregation structure of the hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate.
-In Section~\ref{sec:reconciliation}, we discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation, and in Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts.
-%
-%Some theoretical results on probabilistic forecast reconciliation in the Gaussian framework are given in Section~\ref{sec:gaussian}, including a simulation study to show the importance of reconciliation in the probabilistic framework.
-%
-%We conclude with some thoughts on extensions and limitations in Section~\ref{sec:conclusions}.
-
-%\section{Hierarchical Time Series}\label{sec:notation}
-
 \section{Coherent forecasts}\label{sec:definitions}
@@
 The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.
-The hierarchical structure of the data imply the following holds for all $t$:
+The hierarchical structure of the data implies that
 \begin{equation}
@@
 \end{equation}
-where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints.
-
-To clarify these concepts consider the example of the hierarchy in Figure~\ref{fig1}, $n=7$ and $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.
-For example, for the hierarchy in Figure~\ref{fig1}, $m=4$ and $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$.
-For the hierarchy in Figure~\ref{fig1}
+where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints, holds for all $t$.
+
+To clarify these concepts consider the example of the hierarchy in Figure~\ref{fig1}.
+For this hierarchy, $n=7$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$ and
 \[
@@
 
-While most applications of hierarchical time series to date have involved data that respect an aggregation structure, in principle the ${\bm S}$ can encode any linear constraints including weighted sums or even cases where some variables in the hierarchy are formed by taking the difference of two other variables.
+While most applications of hierarchical time series to date have involved data that respect an aggregation structure, in principle the matrix ${\bm S}$ can encode any linear constraints including weighted sums or even cases where some variables in the hierarchy are formed by taking the difference of two other variables.
 
@@
 
-It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect the inherent aggregation constraints.
+It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect inherent aggregation constraints.
 We follow other authors \citep{Wickramasuriya2017, FPP2018} in using the nomenclature \emph{coherence} to describe this property.
-%While coherent point forecasts have been discussed many times previously, the definitions of coherence previously given are vague and are not easily extended to the situation of probabilistic forecasting.
-We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem, thus facilitating the development of the probabilistic forecast reconciliation in Section~\ref{sec:reconciliation}.
+We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem, thus facilitating the development of probabilistic forecast reconciliation in Section~\ref{sec:reconciliation}.
 
@@
 
-A probabilistic forecast for time $t+h$ is coherent if uncertainty in $\bm{y}_{t+h}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.
-
-%Definition~\ref{def:cohprob} implies the probability measure on $\mathbb{C}^m$ is equivalent to the probability measure on $(\mathbb{R}^m, \bm{\mathscr{F}}^m)$.
-Hence, there is no density anywhere outside the linear subspace $\mathbb{C}^m$.
-That is, a \textit{coherent probability density forecast} is any density $\bm{f}(\breve{\bm{y}}_{t+h})$ such that $\bm{f}(\breve{\bm{y}}_{t+h})=0$ for all $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}^{n-m}$.
-
-%The following example will help to understand these definitions more clearly.
-
-%Consider a simple hierarchy with two bottom-level series $A$ and $B$ that add up to the top-level series $Tot$.
-Suppose the forecasts of these series at time $t+h$ are given by $\breve{\bm{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$.
-Due to the aggregation constraint of the hierarchy we have $\breve{y}_{Tot,t+h}=\breve{y}_{A,t+h}+\breve{y}_{B,t+h}$.
-This implies that, even though $\breve{\bm{y}}_{t+h} \in \mathbb{R}^3$, the points actually lie in $\mathbb{C}^2$, which is a two dimensional subspace within that $\mathbb{R}^3$ space.
-Therefore, any $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}$ is impossible, so that $f(\breve{\bm{y}}_{t+h})=0$ for any $\breve{\bm{y}}_{t+h} \in \bm{\mathbb{N}}$.
-
-These definitions of the coherent space $\mathfrak{s}$, and coherent point and probabilistic forecasts in terms of the mapping $s(.)$, may give the impression that the bottom-level series play an important role in the definition.
+A probabilistic forecast for time $t+h$ is coherent if uncertainty in $\bm{\breve{y}}_{t+h}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.
+
+These definitions of the coherent space $\mathfrak{s}$, coherent point and coherent probabilistic forecasts in terms of the mapping $s(.)$, may give the impression that the bottom-level series play an important role.
 However, alternative definitions could be formed using any set of basis vectors that span $\mathfrak{s}$.
@@
 
-%Because the basis is not unique for a given coherent subspace, Definition~\ref{def:cohprob} is not unique, and one can redefine the coherent probabilistic forecasts with respect to any basis.
-However, we stick to Definition~\ref{def:cohprob} and consider the basis defined by the columns of $\bm{S}$ in what follows.
-
-%Definitions~\ref{def:cohpoint} and~\ref{def:cohprob} facilitate extension to probabilistic forecast reconciliation which we discuss in the next section.
 To the best of our knowledge, the only other definition of coherent probabilistic forecasts is given by \citet{BenTaieb2017} who define coherent probabilistic forecasts in terms of convolutions.
@@
 
-%\[
-%\bm{S} =
-%\begin{pmatrix}
-%1& 1 \\ 1 & 0 \\ 0&1
-%\end{pmatrix}
-%\quad \text{and} \quad
-%\bm{R} =
-%\begin{pmatrix}
-%1 \\ -1 \\ -1
-%\end{pmatrix}.
-%\]
-%
-%Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively.
-Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$.
-Now, using the insights of Definition~\ref{def:reconpoint}, we can use the following steps to reconcile the point forecasts.
-
-%\subsubsection*{Step 1: Change of basis}
-
 \begin{figure}
@@
 	\caption{Summary of probabilistic point reconciliation.
-The mapping $s\circ g$ projects the unreconciled forecast $\hat{\bm{y}}$ onto $\mathfrak{s}$.
+The mapping $s\circ g$ projects the unreconciled forecast $\hat{\bm{y}}_{t+h|h}$ onto $\mathfrak{s}$, yielding the reconciled forecast $\tilde{\bm{y}}_{t+h|h}$ with subscripts dropped in the figure for ease of presentation.
 Since the smallest hierarchy involves three dimensions, this figure is only a schematic.}\label{fig:pointfr_sch}
@@
 Let $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$ respectively, after a change of basis.
-The process of reconciliation involves setting the values of the reconciled bottom-level series to be $\tilde{\bm{b}}_{t+h|t}$, and ignoring $\tilde{\bm{a}}_{t+h}$ to ensure coherence.
+The process of reconciliation involves setting the values of the reconciled bottom-level series to be $\tilde{\bm{b}}_{t+h|t}$, and ignoring $\tilde{\bm{a}}_{t+h|t}$ to ensure coherence.
 From properties of linear algebra it follows that
-%\[
-%(\bm{S} ~ \vdots~ \bm{R})
-%(\tilde{\bm{b}}'_{t+h},~ \tilde{\bm{t}}'_{t+h})'
-%= \hat{\bm{y}}_{t+h},
-%\]
 \[
@@
 
-%\begin{equation}\label{4.3}
-%(\tilde{\bm{b}}'_{t+h}, ~ \tilde{\bm{t}}'_{t+h})' =
-%(\bm{S} ~ \vdots~ \bm{R})^{-1}
-%\hat{\bm{y}}_{t+h}.
-%\end{equation}
-
 In order to find $\tilde{\bm{b}}_{t+h|t}$ we require the inverse $(\bm{S} ~ \bm{R})^{-1}$ which is given by
@@
 where $\bm{S}_{\bot}$ is the orthogonal complements of $\bm{S}$.
-Thus it follows that $\tilde{\bm{b}}_{t+h}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$.
+Thus it follows that $\tilde{\bm{b}}_{t+h|t}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$.
 Here $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ corresponds to $\bm{G}$ as defined previously.
@@
 Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$.
-For example OLS minimises the Euclidean distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$, while \citet{Wickramasuriya2017} show that MinT minimises the Mahalonobis distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$.
+For example OLS minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$, while \citet{Wickramasuriya2017} show that MinT minimises the Mahalonobis distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$.
 Bottom-up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom-level series.
@@
 
-%\begin{equation} \label{4.4}
-%\begin{pmatrix}
-%\tilde{\bm{b}}_{t+h} \\ \cdots \\ \tilde{\bm{t}}_{t+h}
-%\end{pmatrix} = \begin{pmatrix}
-%(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ \cdots \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
-%\end{pmatrix}\hat{\bm{y}}_{t+h}.
-%\end{equation}
-%From \eqref{4.4} it follows that
-%\begin{equation}
-%\tilde{\bm{b}}_{t+h}=(\bm{R}'_\bot %\bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}
-%\end{equation}
-
-%\subsubsection*{Step 2: Obtaining reconciled point forecasts for the whole hierarchy}
-%
-%This step directly follows from the definition for coherent forecasts.
-To obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \mathbb{R}^n$ to the $\mathbb{C}^m$ through $\bm{S}$.
-Thus we have,
-%\begin{equation}
-%\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \qquad \tilde{\bm{y}}_{t+h} \in \mathbb{C}^m<\mathbb{R}^n.
-%\end{equation}
-
-%Finding a suitable $\bm{R}$ with respect to a certain loss function will lead to optimally reconciled point forecasts of the hierarchy.
-%If $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$, then the definition for linear reconciliation of point forecasts in previous studies coincides with our explanation.
-
-%In our context, we need to find $\bm{R}$ such that $\bm{R}'_\bot \bm{S}$ is invertible; i.e, $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \bm{S}=\bm{I}$.
-This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}
-
-%\citet{Hyndman2011} proposed to choose
-%\begin{equation}
-%\tilde{\bm{b}}^{OLS}_{t+h}=(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h},
-%\end{equation}
-%where, in this context, $\bm{R}'_\bot = \bm{S}'$. Thus the reconciled point forecasts for the entire hierarchy are given by
-%\begin{equation}
-%\tilde{\bm{y}}^{OLS}_{t+h}=\bm{S}(\bm{S}' \bm{S})^{-1}\bm{S}' \hat{\bm{y}}_{t+h}.
-%\end{equation}
-%They referred this to as the OLS solution and the loss function they considered is equivalent to the Euclidean norm between $\hat{\bm{y}}_{t+h}$ and $\tilde{\bm{y}}_{t+h}$; i.e.
-$<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>$.
-%
-%According to a recent study by \citet{Wickramasuriya2017}, selecting $\bm{R}'_\bot = \bm{S}'\bm{W}^{-1}_{h}$ will minimize the trace of mean squared reconciled forecast errors under the property of unbiasedness, where $\bm{W}^{-1}_{h}$ is the variance of the incoherent forecast errors.
-This will result in
-%\begin{equation}
-%\tilde{\bm{b}}^{MinT}_{t+h}=(\bm{S}'\bm{W}^{-1}_{h} \bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h},
-%\end{equation}
-%and thus,
-%\begin{equation}
-%\tilde{\bm{y}}^{MinT}_{t+h}=\bm{S}(\bm{S}' \bm{W}^{-1}_{h}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}_{h} \hat{\bm{y}}_{t+h}.
-%\end{equation}
-%
-%They referred this to as the MinT solution.
-The loss function they considered is equivalent to the Mahalanobis distance between $\hat{\bm{y}}_{T+h}$ and $\tilde{\bm{y}}_{T+h}$.
-i.e.
-$<\hat{\bm{y}}_{T+h}, \tilde{\bm{y}}_{T+h}>_{\bm{W}_h}$.
-
 Before generalising the concept of point reconciliation to probabilistic forecasts, we state two theorems that motivate the use of projections for point forecast reconciliation.
@@
 \begin{theo}[Unbiasedness preserving property]
-  For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also be an unbiased prediction as long as $s\circ g$ is a projection.
+  For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also an unbiased prediction as long as $s\circ g$ is a projection.
 \end{theo}
@@
 \end{compactenum}
-We now outline the analogues to these three steps for probabilistic forecasts when predictive densities are available.
+We now outline the analogous steps for probabilistic forecasts when predictive densities are available.
 
@@
 
-%Recall that $\hat{\bm{y}}_{t+h}$ is a set of incoherent point forecasts and the coordinates of $\hat{\bm{y}}_{t+h}$ with respect to the basis $\bm{B}$ are given by \eqref{4.3}.
-Suppose $\hat{\bm{f}}(\cdot)$ is the probability density of $\hat{\bm{y}}_{t+h}$.
-Our goal is to reconcile $\hat{\bm{f}}(\cdot)$ such that the density lives on $\mathbb{C}^m$.
-In order to obtain this reconciled density, we need to project $\hat{\bm{f}}(\hat{\bm{y}}_{t+h})$ onto $\mathbb{C}^m$ along the direction of $\mathbb{N}^{n-m}$.
-
-%Let the density of $\hat{\bm{y}}_{t+h}$ with respect to basis $\bm{B}$ be denoted by $\bm{f_B}(\cdot)$.
-Then it follows from \eqref{4.3}, and standard results for densities of transformed variables, that
-%\begin{equation}\label{4.5}
-%\bm{f_B}(\tilde{\bm{b}}_{t+h},\tilde{\bm{t}}_{t+h})=\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h}) \,\Big|\bm{S} ~ \vdots~ \bm{R}\Big|,
-%\end{equation}
-%where $|\cdot|$ denotes the determinant of a matrix.
-Now that we have the density of $(\tilde{\bm{b}}'_{t+h} , \tilde{\bm{t}}'_{t+h})'$, the marginal density of $\tilde{\bm{b}}_{t+h}$ can be obtained by integrating \eqref{4.5} over the range of $\tilde{\bm{t}}_{t+h}$.
-This will result in the reconciled density of the bottom-level series $\tilde{\bm{b}}_{t+h}$,
-%\begin{equation}\label{4.6}
-%\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})=\int_{\lim(\tilde{\bm{t}}_{t+h})}\hat{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}+\bm{R}\tilde{\bm{t}}_{t+h})\,  \Big|\bm{S} ~ \vdots~ \bm{R}\Big| \, d\tilde{\bm{t}}_{t+h}.
-%\end{equation}
-%
-%Finally to get the reconciled density of the whole hierarchy, we simply follow Definition~\ref{def:cohprob} to obtain
-%\begin{equation}\label{4.7}
-%\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\bm{S}\circ \tilde{\bm{f}}(\tilde{\bm{b}}_{t+h}).
-%\end{equation}
-%This final step will transform every point in the density $\tilde{\bm{f}}(\tilde{\bm{b}}_{t+h})$ to the space $\mathbb{C}^m<\mathbb{R}^n$.
-The following example illustrates how this method can be used to reconcile an incoherent Gaussian forecast distribution.
-
 \subsubsection*{Example: Gaussian Distributions}
@@
 The subscripts $t+h|t$ are suppressed for brevity.
-The unreconciled density
+Let the unreconciled density be given by
 \begin{equation}
@@
 %\end{equation}
-This implies that the reconciled probabilistic forecast for the bottom-level series is $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{G}\hat{\bm{\mu}}_{t+h}, \bm{G}\hat{\bm{\Sigma}}_{t+h}\bm{G}')$.
-The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean $\bm{SG}\hat{\bm{\mu}}$ and rank deficient covariance matrix $\bm{SG}\hat{\bm{\Sigma}}_{t+h}\bm{G}'\bm{S}'$.
+This implies that the reconciled probabilistic forecast for the bottom-level series is $\tilde{\bm{b}} \sim \mathcal{N}(\bm{G}\hat{\bm{\mu}}, \bm{G}\hat{\bm{\Sigma}}\bm{G}')$.
+The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean $\bm{SG}\hat{\bm{\mu}}$ and rank deficient covariance matrix $\bm{SG}\hat{\bm{\Sigma}}\bm{G}'\bm{S}'$.
 
@@
 	Let an unreconciled probabilistic forecast come from the elliptical class with location parameter $\hat{\bm{\mu}}$ and scale matrix $\hat{\bm{\Sigma}}$.
-Let the true predictive distribution of $\bm{y}_{t+h|t}$ also belong to the elliptical class with location parameter $\bm{\mu}$ and scale matrix $\bm{\Sigma}$.
-Then the linear reconciliation mapping $g(\breve{\bm{y}})=\bm{G}_{opt}\breve{\bm{y}}+\bm{d}_{opt}$ with $\bm{G}_{opt}={\bm{a}}{\bm\Sigma}^{-1/2}$ and $\bm{d}_{opt}=\bm{\mu}-\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}$ recovers the true predictive density where ${\bm{a}}$ is any $m\times n$ matrix such that ${\bm{a}}{\bm{a}}'=\bm{\Omega}$ and $\bm{\Omega}$ is a sub-matrix of $\bm{\Sigma}$ corresponding to the bottom-level series.
+Let the true predictive distribution of $\bm{y}$ also belong to the elliptical class with location parameter $\bm{\mu}$ and scale matrix $\bm{\Sigma}$.
+Then the linear reconciliation mapping $g(\breve{\bm{y}})=\bm{G}_{opt}\breve{\bm{y}}+\bm{d}_{opt}$ with $\bm{G}_{opt}={\bm{a}}\hat{\bm\Sigma}^{-1/2}$ and $\bm{d}_{opt}=\bm{\mu}-\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}$ recovers the true predictive density where ${\bm{a}}$ is any $m\times n$ matrix such that ${\bm{a}}{\bm{a}}'=\bm{\Omega}$ and $\bm{\Omega}$ is a sub-matrix of $\bm{\Sigma}$ corresponding to the bottom-level series.
 \end{theo}
@@
    Since elliptical distributions are closed under affine transformations, and are closed under marginalisation, reconciliation of an elliptical distribution yields an elliptical distribution (although the unreconciled and reconciled distributions may be different members of the class of elliptical distributions).
-The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}_{opt}\bm{\Sigma}\bm{G}_{opt}'\bm{S}'$, while the location matrix is given by $\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}+\bm{d}_{opt}$.
+The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}_{opt}\hat{\bm{\Sigma}}\bm{G}_{opt}'\bm{S}'$, while the location matrix is given by $\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}+\bm{d}_{opt}$.
 The reconciled scale matrix is
@@
      \tilde{\bm{\Sigma}}_{opt}
-       = \bm{S}{\bm{a}}{\bm\Sigma}^{-1/2}\bm{\Sigma}\left({\bm\Sigma}^{-1/2}\right)'{\bm{a}}'\bm{S}'
+       = \bm{S}{\bm{a}}\hat{\bm\Sigma}^{-1/2}\hat{\bm{\Sigma}}\left(\hat{\bm\Sigma}^{-1/2}\right)'{\bm{a}}'\bm{S}'
        = \bm{S}\bm{\Omega}\bm{S}'
@@
 A summary can be taken of the expected scores across each margin, for example a mean or median.
-In the simulations of Section~\ref{sec:gaussian}, we consider two scoring rules.
+In the simulations of Section~\ref{sec:gaussian}, we consider two such scoring rules.
 The log score is given by the log density, in this case for each margin of the probabilistic forecast.
@@
 \begin{align} \label{eq:CRPS}
-\text{CRPS}(\breve{F}_i,y_{i}) &=\int \left(\breve{F}_i(\breve{Y}_i)-\mathbb{1}(y_i<y_{i})\right)d\breve{Y}_i\\ &=\E_{\breve{Y}_i}|\breve{Y}_{i}-y_{i}| - \frac{1}{2}\E_{\breve{Y}_i}|\breve{Y}_{i}-\breve{Y}^*_{i}|\,,
+\text{CRPS}(\breve{F}_i,y_{i}) &=\int \left(\breve{F}_i(\breve{Y}_i)-\mathbb{1}(\breve{Y}_i<y_{i})\right)d\breve{Y}_i\\ &=\E_{\breve{Y}_i}|\breve{Y}_{i}-y_{i}| - \frac{1}{2}\E_{\breve{Y}_i}|\breve{Y}_{i}-\breve{Y}^*_{i}|\,,
 \end{align}
@@
 While a number of alternative proper scoring rules are available for univariate forecasts, the multivariate case is somewhat more limited.
-Here we focus on three scoring rules: the log score, the energy score and the variogram score.
-%These are summarized in table~\ref{table:scoringrules}.
-%
-%\begin{table}[!bh]
-%  \caption{Scoring rules to evaluate multivariate forecast densities.
-Here, $\breve{\bm{y}}_{T+h}$ and $\breve{\bm{y}}^*_{T+h}$ are two independent random vectors from the coherent forecast distribution $\breve{\bm{F}}$ with density function $\breve{\bm{f}}(\cdot)$ at time $T+h$, and $\bm{y}_{T+h}$ is the vector of realizations.
-Further, $\breve{Y}_{T+h,i}$ and $\breve{Y}_{T+h,j}$ are the $i$th and $j$th components of the vector $\breve{\bm{Y}}_{T+h}$.
-The variogram score is given for order $p$, where $w_{ij}$ denote non-negative weights.}\label{table:scoringrules}
-%  \centering\small\setstretch{1.3}
-%  \begin{tabular}{@{}lp{8.1cm}l@{}}
-%    \toprule
-%    \textbf{Scoring rule}  & \textbf{Expression} & \textbf{Reference}           \\
-%    \midrule
-%    \text{Log score}       &
-%    $\text{LS}(\breve{\bm{F}},\bm{y}_{T+h}) = -\log {\breve{\bm{f}}(\bm{y}_{T+h})}$ &
-%    \citet{Gneiting2007}  \\\\[-0.2cm]
-%    \text{Energy score}    &
-%    $\text{ES}(\breve{\bm{Y}}_{T+h},\bm{y}_{T+h}) =
-%    \E_{\breve{\bm{F}}}
-%    \|\breve{\bm{Y}}_{T+h}-\bm{y}_{T+h}\|^\alpha -$ \par\hfill
-%    $\frac{1}{2}\E_{\breve{\bm{F}}}\|\breve{\bm{Y}}_{T+h}-\breve{\bm{Y}}^*_{T+h}\|^\alpha$, \,\, $\alpha \in (0,2]$ &
-%    \citet{Gneiting2008}  \\\\[-0.2cm]
-%    \text{Variogram score} &
-%    $\text{VS}(\breve{\bm{F}}, \bm{y}_{T+h}) =
-%    \sum\limits_{i=1}^{n}
-%    \sum\limits_{j=1}^{n}
-%    w_{ij}\Big(|y_{T+h,i} - y_{T+h,j}|^p -$ \par\hfill
-%    $\E_{\breve{\bm{F}}}|\breve{Y}_{T+h,i}-\breve{Y}_{T+h,j}|^p\Big)^2$     &
-%    \citet{SCHEUERER2015} \\
-%    \bottomrule
-%  \end{tabular}
-%\end{table}
+Here we focus on three scoring rules: the log score (LS), the energy score (ES) and the variogram score (VS).
 
@@
 
-The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the representation in terms of expectations leads itself to easy computation when samples from the probabilistic forecast are available.
+The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the following representation in terms of expectations
+\begin{equation}
+\text{ES}(\breve{\bm{Y}}_{T+h},\bm{y}_{T+h}) =
+\E_{\breve{\bm{Y}}}
+||\breve{\bm{Y}}_{T+h}-\bm{y}_{T+h}||^\alpha -\frac{1}{2}\E_{\breve{\bm{Y}}}||\breve{\bm{Y}}_{T+h}-\breve{\bm{Y}}^*_{T+h}||^\alpha, \,\, \alpha \in (0,2]\,, 
+\end{equation}
+lends itself to easy computation when samples from the probabilistic forecast are available.
 An interesting limiting case is where $\alpha=2$, where it can be easily shown that energy score simplifies to mean squared error around the mean of the predictive distribution.
@@
 
-%For example, assume you have a Gaussian coherent predictive density $\bm{\tilde{f}}_{T+h}$. Then the log score is given by
-
-%\begin{equation}
-%LS(\bm{\tilde{f}_{T+h},y_{T+h}}) = -\log \left(\frac{1}{(2\pi)^{\frac{m}{2}}|\bm{\tilde{\Sigma}}_{T+h}|^{\frac{1}{2}}}\exp\left[-\frac{1}{2}(\bm{y}_{T+h}-\bm{\tilde{\mu}}_{T+h})^T %\bm{\tilde{\Sigma}_{T+h}}^{-1}(\bm{y}_{T+h}-\bm{\tilde{\mu}}_{T+h})\right]\right),
-%\end{equation}
-
-%
-%where $\bm{\tilde{\mu}}_{T+h}$ and $\bm{\tilde{\Sigma}}_{T+h}$ are the coherent mean and variance-covariance matrix of the predictive Gaussian density and both lies in the linear %subspace spanned by $\mathbb{C}^m$.
-Then $\bm{\tilde{\Sigma}}_{T+h}$ is always a singular matrix and hence the determinant will be zero.
-Therefore the density function of %degenerate Gaussian distribution is undefined.
-However, we could use the pseudo determinant, i.e.
-product of positive eigenvalues and the pseudo inverse to calculate the log score %to compare the predictive ability of coherent forecast densities.
-
 \subsubsection{Comparing unreconciled forecasts to reconciled forecasts}
@@
 An example of the $n\times n$ $\bm{U}$ is the matrix of left singular vectors of $\bm{S}$.
-%For a non-degenerate probability measure on $\mathbb{R}^n$, the density is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^n$.
-%For a coherent probability measure the density after rotation is the Radon-Nikodym derivative with respect to the usual Lesbegue measure on $\mathbb{R}^m$.
 
@@
 \[
-S\left(f,\bm{z}^{(1)}_t\right) = -\log f_1\left(\bm{z}^{(1)}_t\right),
+LS\left(f,\bm{z}^{(1)}_t\right) = -\log f_1\left(\bm{z}^{(1)}_t\right),
 \]
@@
 \begin{align}
-S\left(\hat{f},\bm{z}^{(1)}_t\right) &= -\log f_1(\bm{z}^{(1)}_t)-f_2(\bm{z}^{(1)}_t)\\
+LS\left(\hat{f},\bm{z}^{(1)}_t\right) &= -\log f_1(\bm{z}^{(1)}_t)-f_2(\bm{z}^{(1)}_t)\\
 &= -\log f_1(\bm{z}^{(1)}_t)+\frac{n-m}{2}\log(2\pi\sigma^2)\\
-&<-\log f_1(\bm{z}^{(1)}_t)=S\left(f,\bm{z}^{(1)}_t\right).
+&<-\log f_1(\bm{z}^{(1)}_t)=LS\left(f,\bm{z}^{(1)}_t\right).
 \end{align}
-After taking expectations $ES(f,f) > ES(\hat{f},f)$, violating the condition in Equation~\eqref{eq:(3.1.)} for a proper scoring rule.
+After taking expectations $E\left[LS(f,f)\right] > E\left[LS(\hat{f},f)\right]$, violating the condition in Equation~\eqref{eq:(3.1.)} for a proper scoring rule.
 \end{proof}
@@
 	Energy/ & Proper & Full hierarchy should be used\\
-	Variogram Score & &\\
+	Variogram Score & Proper & Full hierarchy should be used\\
 	\hline
@@
 
-%\subsection{Comparison of coherent and incoherent forecast densities}
-%
-%It is also important to assess how the coherent or reconciled forecast densities improve the predictive ability compared to the incoherent forecasts.
-Clearly, we cannot use multivariate scoring rules, even for the basis set of series, since the coherent and incoherent forecast densities lie in two different metric spaces.
-%
-%However we could compare the individual margins of the forecast density of the hierarchy using univariate proper scoring rules.
-The widely used Continuous Ranked Probability Score (CRPS) could then be used.
-This is defined as
-%%\begin{equation} \label{eq:(3.6)}
-%%\text{CRPS}(\breve{F}_i,y_{T+h,i}) = \E_{\breve{F}_i}|\breve{Y}_{T+h,i}-y_{T+h,i}| - \frac{1}{2}\E_{\breve{F}_i}|\breve{Y}_{T+h,i}-\breve{Y}^*_{T+h,i}|,
-%%\end{equation}
-%where $\breve{Y}_{T+h,i}$ and $\breve{Y}^*_{T+h,i}$ are two independent copies from the $i$th reconciled marginal forecast distribution $\tilde{F}_i$ of the hierarchy, and $y_{T+h,i}$ is the $i$th realization from the true marginal distribution $G_i$.
-We could also use univariate log scores, for which we could assume a parametric forecast distribution.
-
 \section{Simulation study}\label{sec:gaussian}
-
-%An important special case for probabilistic forecasting arises when we can assume a multivariate Gaussian distribution.
-That is, suppose all the historical data in the hierarchy follows a multivariate Gaussian distribution, $\bm{y}_T \sim \mathcal{N}(\bm{\mu}_T, \bm{\Sigma}_T)$, where both $\bm{\mu}_T$ and $\bm{\Sigma}_T$ live in $\mathbb{C}^m$ by nature of the hierarchical structure of the data.
-We are interested in estimating the predictive Gaussian distribution of $\bm{Y}_{T+h}| \bm{\mathcal{I}}_T$, where $\bm{\mathcal{I}}_T= \{\bm{y}_1,\bm{y}_2,\dots.,\bm{y}_T\}$, which should also live in $\mathbb{C}^m$.
-%
-%It is well known that the optimal point forecasts with respect to the minimal mean square error are given by the conditional expectations, $\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}],$ $i=1,\dots,n$.
-Suppose we independently fit time series models for each series in the hierarchy.
-Then the point forecasts, $\hat{Y}_{T+h,i}$, from the estimated models are unbiased and consistent estimators of $\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}]$, assuming the parameter estimates of the fitted models are unbiased and asymptotically consistent.
-\todo{Only for linear models?}
-%
-%For example, suppose the data from $i$th series follows a ARMA$(p,q)$ model. i.e.,
-%\[
-%Y_{t,i}=\alpha_1Y_{t-1,i}+\dots+\alpha_pY_{t-p,i}+\varepsilon_t + \beta_1\varepsilon_{t-1,i}+\dots+\beta_q\varepsilon_{t-q,i},
-%\]
-%where $\varepsilon_t \sim \mathcal{NID}(0, \sigma_i^2)$. Then,
-%\[
-%\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}] = \alpha_1Y_{T+h-1,i}+\dots+\alpha_pY_{T+h-p,i}+ \beta_1\varepsilon_{T+h-1,i}+\dots+\beta_q\varepsilon_{T+h-q,i}.
-%\]
-%
-%Since $\bm{\alpha} = (\alpha_1,\dots,\alpha_p)'$ and $\bm{\beta} = (\beta_1,\dots,\beta_q)'$ are unknown in practice and thus estimated using the maximum likelihood method.
-Let $\hat{\bm{\alpha}}$ and $\hat{\bm{\beta}}$ denote the maximum likelihood estimates of $\bm{\alpha}$ and $\bm{\beta}$ respectively.
-\citet{Yao2006} showed that $\hat{\bm{\alpha}}$ and $\hat{\bm{\beta}}$ are asymptotically consistent estimators.
-Thus the point forecasts from this estimated model, $\hat{Y}_{T+h,i}$, will also be a consistent estimator for $\E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}]$.
-i.e.,
-%\begin{equation} \label{eq:(6.01)}
-%\hat{Y}_{T+h,i} \overset{p}{\to} \E[Y_{T+h,i}\mid y_{1,i},\dots,y_{T,i}] \quad \text{as} \quad T \to \infty.
-%\end{equation}
-%
-%Let $\hat{\bm{Y}}_{T+h}=(\hat{Y}_{T+h,1},\dots,\hat{Y}_{T+h,n})'$ and suppose \eqref{eq:(6.01)} holds for $i=1,\dots,n$. Then from Slutsky's theorem it follows that
-%\begin{equation}\label{eq:(6.02)}
-%\hat{\bm{Y}}_{T+h} \overset{p}{\to} \E[\bm{Y}_{T+h}|\bm{\mathcal{I}}_T] \quad \text{as} \quad T \to \infty.
-%\end{equation}
-%Further, let the forecast error due to $\hat{\bm{Y}}_{T+h}$ be given by
-%\begin{equation}
-%\hat{\bm{e}}_{T+h} = \bm{Y}_{T+h}-\hat{\bm{Y}}_{T+h},
-%\end{equation}
-%and consider the variance of $\hat{\bm{e}}_{T+h}$,
-%\begin{align*}
-%\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = &
-%\E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)- \hat{\bm{Y}}_{T+h})\\
-%& \quad
-%(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) + \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T],\\
-%= &
-%\E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T]\\
-%& \quad
-%+ \E[\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
-%& \quad
-%+  \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T]\\
-%&  \quad
-%+ \E[\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T].
-%\end{align*}
-%
-%From \eqref{eq:(6.02)} it immediately follows that
-%\begin{align*}
-%&\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] \overset{p}{\to} \E[(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))(\bm{Y}_{T+h} - \E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T))'|\bm{\mathcal{I}}_T].
-%\end{align*}
-%That is,
-%\begin{equation}
-%\bm{W}_{T+h} \overset{p}{\to} \text{Var}(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T) \quad \text{as} \quad T \to \infty,
-%\end{equation}
-%where $\E[(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h} - \hat{\bm{Y}}_{T+h})'|\bm{\mathcal{I}}_T] = \bm{W}_{T+h}$.
-%
-%Even though $\hat{\bm{Y}}_{T+h}$ and $\bm{W}_{T+h}$ are asymptotically consistent estimators for $\E(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ and $\text{Var}(\bm{Y}_{T+h}|\bm{\mathcal{I}}_T)$ respectively, they are not coherent since they do not lie in the coherent subspace.
-Thus the Gaussian forecast distribution with mean $\hat{\bm{Y}}_{T+h}$ and variance $\bm{W}_{T+h}$ will be incoherent, and we denote it by
-%\begin{equation}\label{eq:(6.03)}
-%\widehat{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathcal{N}(\hat{\bm{Y}}_{T+h}, \bm{W}_{T+h})
-%\end{equation}
-%
-%Since our primary objective is to find the coherent forecast density of the hierarchy, we need to reconcile \eqref{eq:(6.03)}.
-Using \eqref{eq:gaussianreconciled}, the reconciled Gaussian forecast distribution is then given by
-%\begin{equation}\label{eq:(6.04)}
-%\widetilde{\bm{Y}_{T+h,i}|\bm{\mathcal{I}}_T} \sim \mathcal{N}(\bm{SP}\hat{\bm{Y}}_{T+h}, \bm{SP}\bm{W}_{T+h}\bm{P}'\bm{S}'),
-%\end{equation}
-%where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
-%
-%\textbf{Result 1}: Choosing $\bm{R}'_\bot = \bm{S}'\bm{W}_{T+h}^{-1}$ will ensure that at least the mean of the predictive Gaussian distribution is optimally reconciled with respect to the energy score.
-%
-%Result 1 can be easily shown as follows.
-From \eqref{eq:(5.1)}, the energy score at the upper limit of $\alpha=2$ is given by $\|\bm{y}_{T+h}-\bm{SP}\hat{\bm{y}}_{T+h}\|^2$.
-Then the expectation of the energy score with respect to the true distribution is equivalent to the trace of mean squared forecast error; i.e.,
-%\[
-%\E_{\bm{G}}[eS(\bm{\tilde{Y}_{T+h},y_{T+h}})]= \text{Tr}\{\E_{\bm{y}_{T+h}}[(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})(\bm{Y}_{T+h}-\bm{SP}\hat{\bm{Y}}_{T+h})'|\mathcal{I}_{T}]\}.
-%\]
-%
-%From Theorem 1 of \citet{Wickramasuriya2017} it immediately follows that $\bm{P} = (\bm{S}'\bm{W}_{T+h}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}_{T+h}^{-1}$ minimizes the expected energy score, if we constrain the reconciled forecasts to be unbiased.
-Thus we have $\bm{R}'_\bot = \bm{S}'\bm{W}_{T+h}^{-1}$.
-%
-%It should be noted that $\bm{W}_{T+h}$ can be estimated in different ways, which yields different estimates of $\bm{R}'_\bot$. Table~\ref{table:2} summarizes some of these methods.
-%
-
-%All of these forecasting methods are well-established in the context of point forecast reconciliation \citep{Hyndman2011, Hyndman2016,Wickramasuriya2017}.
-Here, we are showing how these reconciliation methods can be used in the context of probabilistic forecast reconciliation, at least in the Gaussian framework.
 
@@
 and similar inequalities hold when $\varepsilon_{AA,t}$ is replaced by $\varepsilon_{AB,t}$, $\varepsilon_{BA,t}$ and $\varepsilon_{BB,t}$ in the third term.
-%Therefore
-%\[
-%\bm{l}_1\bm{\Sigma} \bm{l}_1' \le \bm{l}_2\bm{\Sigma} \bm{l}_2' + \sigma^2_v \le  \bm{l}_3\bm{\Sigma} \bm{l}_3' + \sigma^2_u + \frac{1}{4}\sigma^2_v,
-%\]
-%where $\bm{l}_1 = (1,1,1,1)'$, $\bm{l}_2 = (1,1,0,0)'$ and $\bm{l}_3 = (1,0,0,0)'$, and hence
-%\[\bm{l}_1\bm{\Sigma} \bm{l}_1' - \bm{l}_2\bm{\Sigma} \bm{l}_2' \le \sigma^2_v \le \frac{4}{3}(\sigma^2_u + \bm{l}_3\bm{\Sigma} \bm{l}_3' - \bm{l}_2\bm{\Sigma} \bm{l}_2').\]
 The values of $\bm{\Sigma}$, $\sigma^2_u$ and $\sigma^2_v$ that we use and which satisfy these constraints are $\sigma^2_u = 19$, $\sigma^2_u = 18$ and
@@
 To facilitate comparisons, we report skill scores \citep{Gneiting2007}.
-For a given forecasting method, evaluated by a particular scoring rule, the skill score %is calculated as
-%\begin{equation}
-%Ss[S_B(\cdot)] = \frac{S_B(\bm{Y},\bm{y})^{\text{ref}} - S_B(\breve{\bm{Y}},\bm{y})}{S_B(\bm{Y},\bm{y})^{\text{ref}}}\times 100\%,
-%\end{equation}
-%where $S_B(\cdot)$ is the average score over $B$ samples and $S_B(\bm{Y},\bm{y})^{\text{ref}}$ is the average score for the reference forecasting method. Thus $Ss[S_B(\cdot)]$
+For a given forecasting method, evaluated by a particular scoring rule, the skill score
 gives the percentage improvement of the preferred forecasting method relative to a reference method.
-A negative valued skill score indicates that a method is worse than the reference method, whereas any positive value indicates that method is superior to the reference method.
+A negative valued skill score indicates that a method is worse than the reference method, whereas any positive value indicates that the method is superior to the reference method.
 
@@
 
-%Due to the aggregation nature of hierarchy, the probability density is a degenerate density.
-Thus the forecast distribution that we opt to find should also lie in a lower dimensional subspace of $\mathbb{R}^{n}$.
-
-%As it was well established that the reconciliation outperforms other conventional point forecasting methods in the hierarchical literature, we proposed to use reconciliation in probabilistic framework to obtain coherent degenerate densities.
-We provided a distinct definition for density forecast reconciliation and how it can be used to reconcile incoherent densities in practice.
-
-%Assuming a multivariate Gaussian distribution for the hierarchy, we showed how to obtain reconciled Gaussian forecast densities, utilizing available information in the hierarchy.
-An extensive Monte Carlo simulation study further showed that the MinT reconciliation method \citep{Wickramasuriya2017} is useful in producing improved coherent probabilistic forecasts at least in the Gaussian framework.
-
 \newpage

### 2018-11-05 Presentation/ProbForeRec.tex
revamp first few motivating slides

@@
   \section{Concepts}
+  \begin{frame}{Motivating Examples}
+  \begin{itemize}
+  	\item Gross Domestic Product
+  	\begin{itemize}
+  		\item An aggregate of consumption, investment, government spending and trade balance
+  		\item Further breakdown, e.g. consumption of food, rent, etc.
+  	\end{itemize}
+    \item Retail sales
+    \begin{itemize}
+    	\item Aggregate of different product category sales
+    	\item Further breakdown into individual stock keeping units.  
+    \end{itemize}
+    \item Potentially need forecasts of all time series.
+  \end{itemize}
+  \end{frame}
+  \begin{frame}{Incoherent Forecasts}
+  \begin{itemize}
+    \item Potential approaches
+  	\begin{itemize}
+  		\item Univariate models
+  		\item Multivariate models
+  		\item Judgemental forecasts
+  	\end{itemize}
+  \item Forecasts may not respect aggregation structure. ({\bf Incoherent})
+  \item Outcome {\em will} respect aggregation  structure. ({\bf Coherent})
+  \item Motivation is aggregation but can be generalised to any linear constraints.
+  \end{itemize}
+  \end{frame}
+  \begin{frame}{Reconciliation}
+  \begin{itemize}
+  	\item Begin with a vector of forecasts that are incoherent.
+  	\item Adjust these {\bf ex post} to make them coherent.
+  	\item There are good solutions for point forecasting that:
+  	\begin{itemize}
+  		\item Guarantee coherent forecasts.
+  		\item Improve forecast accuracy overall.
+  	\end{itemize}
+  	\item Generalisation to probabilistic forecasts is our contribution.
+  	\item Getting there necessitates a rethink of the existing point forecasting literature. 
+  \end{itemize}
+  \end{frame}
+
   \begin{frame}{Hierarchical and Grouped Time Series}

### 2018-11-06 Presentation/ProbForeRec.tex
background to point forecast reconciliati rework

@@
 \usetikzlibrary{arrows,positioning,shapes,fit,calc}
+\usepackage[greek,english]{babel}
+
 \title{Probabilistic Forecast Reconciliation}
@@
   \end{frame}
-  \section{Concepts}
+  \section{Motivation}
   \begin{frame}{Motivating Examples}
@@
   	\end{itemize}
-  \item Forecasts may not respect aggregation structure. ({\bf Incoherent})
-  \item Outcome {\em will} respect aggregation  structure. ({\bf Coherent})
+  \item Forecasts do not respect aggregation structure ({\bf Incoherent})
+  \item Outcome {\em does} respect aggregation  structure ({\bf Coherent})
   \item Motivation is aggregation but can be generalised to any linear constraints.
@@
   \end{frame}
-
-  \begin{frame}{Hierarchical and Grouped Time Series}
+  \begin{frame}{What we do NOT do}
   \begin{itemize}
-  	  \item Collections of time series are often characterised by aggregation constraints
+  	\item All information is contained in the most disaggregate series.
+  	\item In principle using the correct multivariate model for the most disaggregate series and aggregating them should work.
+  	\item Disaggregate series are: 
   	\begin{itemize}
-  	    \item Cross-Sectionally
-  		\item Temporally
+  		\item Very noisy
+  		\item High-dimensional
+  		\item Prone to model misspecification
   	\end{itemize} 
-      \item {\bf Coherent} forecasts respect such constraints. 
-      \item Independently produced forecasts are generally incoherent.
   \end{itemize}
+  \end{frame}
+  \section{Point Forecast Reconciliation}
+ \begin{frame}{A simple hierarchy}
+  	Consider a hierarchy given by
   	\begin{figure}
 	    \begin{center}
-		\leaf{AA} \leaf{AB} 
+		\leaf{\alt<2>{\color{blue}AA}{AA}} \leaf{\alt<2>{\color{blue}AB}{AB}} 
 		\branch{2}{A}
-		\leaf{BA} \leaf{BB}
+		\leaf{\alt<2>{\color{blue}BA}{BA}} \leaf{\alt<2>{\color{blue}BB}{BB}}
 		\branch{2}{B}
@@
     \end{figure}
-\end{frame}  
-  \begin{frame}{Forecast Reconciliation}
     \begin{itemize}
-  	  \item Forecast reconciliation involves
-  	  \begin{enumerate}
-  	  	\item Producing incoherent {\bf base} forecasts for all series in an $n\times 1$ vector $\hat{\bm y}$
-        \item Adjusting base forecasts to obtain coherent {\bf reconciled} forecasts in an $n\times 1$ vector $\tilde{\bm y}$
-  	  \end{enumerate} 
-      \item Why do we care?
-        \begin{enumerate}
-        	\item Aligned decision making.
-        	\item Improved forecast accuracy
-        \end{enumerate}
+    	\item Let $n$ be the number of series, $\bm{y}$ be an n-vector of all series.
+    	\only<2>{\item Let {\color{blue}$m$} be the bottom level series and {\color{blue}$\bm{b}$} be an {\color{blue}$m$}-vector of the bottom level series.}
     \end{itemize}    
 \end{frame}  
-  \begin{frame}{Reconciliation in two steps}
-  	\begin{itemize}
-  		\item Many reconciliation methods involve two steps
-  		\begin{enumerate}
-  			\item Pre-multiply $\hat{\bm y}$ by a $m\times n$ matrix $\bm G$ to obtain {\bf bottom} level series ${\bm b}={\bm G}{\hat{\bm y}}$ 
-  			\item Pre-multiply ${\bm b}$ by a $n\times m$ matrix $\bm S$ to obtain ${\tilde{\bm y}}$, i.e. $\tilde{\bm y}={\bm S}{{\bm b}}$
-  		\end{enumerate}
-  	    \item The matrix ${\bm S}$ defines the aggregation constraints, e.g.
+\begin{frame}{The ${\bm S}$ matrix}
+    The matrix ${\bm S}$ defines the aggregation constraints, e.g.
     \begin{equation*}
@@
     \end{equation*}
-  	    \item Choice of ${\bm G}$ defines reconciliation method, e.g.
-OLS: ${\bm G}=\left(\bm{S}'\bm{S}\right)^{-1}{\bm S'}$ and Bottom Up: ${\bm G}=\left(\bm{0}_{m\times n-m}~\bm{I}_{m\times m}\right)$
+    Coherence holds when
+    \begin{equation*}
+    {\bm y}={\bm S}{\bm b}
+    \end{equation*} 
+\end{frame}
+\begin{frame}{As a regression model}
+  \begin{itemize}
+  	\item Cast the problem as a regression model with base forecasts $\hat{\bm{y}}$ as the ``dependent variable'' and ${\bm S}$ as the ``design matrix''. 
+  	\begin{equation*}
+  	\hat{\bm{y}}={\bm{S}}{\bm\beta}+{\bm e}
+  	\end{equation*}
+  	\item Initial approach (Athanasopoulos et al, 2009; Hyndman et al, 2011) was to fit by OLS  yielding reconciled forecasts:
+  	\begin{equation*}
+  	\tilde{\bm{y}}={\bm S}({\bm S}'{\bm S})^{-1}{\bm S}'{\hat{\bm{y}}}
+  	\end{equation*}
   \end{itemize}
 \end{frame}
+\begin{frame}{Generalisation}
+  \begin{itemize}  
+  \item Wherever we can use OLS we can use GLS
+  \begin{equation*}
+  \tilde{\bm{y}}={\bm S}({\bm S}'{\bm W}^{-1}{\bm S})^{-1}{\bm S}'{\bm W}^{-1}{\hat{\bm{y}}}
+  \end{equation*}
+  \item Diagonal ${\bm W}$ considered by Athanasopoulos et al (2017)
+  \item MinT approach (Wickremasuriya et al, 2018) use a ${\bm W}$ that is an estimate of the {\em in-sample} forecast error covariance matrix.
+  \end{itemize}
+\end{frame}
+%  \begin{frame}{Reconciliation in two steps}
+%  	\begin{itemize}
+%  		\item Many reconciliation methods involve two steps
+%  		\begin{enumerate}
+%  			\item Pre-multiply $\hat{\bm y}$ by a $m\times n$ matrix $\bm G$ to obtain {\bf bottom} level series ${\bm b}={\bm G}{\hat{\bm y}}$ 
+%  			\item Pre-multiply ${\bm b}$ by a $n\times m$ matrix $\bm S$ to obtain ${\tilde{\bm y}}$, i.e. $\tilde{\bm y}={\bm S}{{\bm b}}$
+%  		\end{enumerate}
+%
+%  	    \item Choice of ${\bm G}$ defines reconciliation method, e.g.
+OLS: ${\bm G}=\left(\bm{S}'\bm{S}\right)^{-1}{\bm S'}$ and Bottom Up: ${\bm G}=\left(\bm{0}_{m\times n-m}~\bm{I}_{m\times m}\right)$
+%    \end{itemize}
+%  \end{frame}
+\begin{frame}
+\centering
+\includegraphics[height=5cm]{Figs/Plato.jpeg}\\
+\textgreek{AGEWMTETRHTOS MHDEIS EISITW}\\
+Those without knowledge of geometry may not enter.
+\end{frame}
+
   \begin{frame}{Coherent Subspace}
@@
     \end{definition}
-    Instead of using bottom-level series a different combination of $m$ {\bf basis series} could be used (e.g.
-top and $m-1$ bottom).
+    Instead of using bottom-level series a different combination of $m$ {\bf basis series} could be used (e.g. top and $m-1$ bottom).\\
     Although ${\bm S}$ would be different $\mathfrak{s}$ would be the same.
@@
   \end{frame}
-  \begin{frame}{Special Case: Projection}
-  \begin{itemize}
-   \item An important special case is where ${\bm S}{\bm G}$ is a projection.
-  \begin{itemize}
-  	\item ${\bm S}{\bm G}$ is symmetric
-  	\item ${\bm S}{\bm G}$ is idempotent
-  \end{itemize}
-  \item Let ${\bm v}\in\mathfrak{s}$ 
-    \begin{itemize}
-    	\item ${\bm S}{\bm G}{\bm v}$ will also lie in $\mathfrak{s}$.
-    	\item ${\bm S}{\bm G}{\bm v}={\bm v}$ only when ${\bm S}{\bm G}$ is a projection.
-    \end{itemize}
-  \end{itemize}
-  \end{frame}
   \begin{frame}{Geometry}
@@
   \input{Figs/orth_pointforerec_schematic}
+  \end{frame}
+%  \begin{frame}{Special Case: Projection}
+%  \begin{itemize}
+%   \item An important special case is where ${\bm S}{\bm G}$ is a projection.
+%  \begin{itemize}
+%  	\item ${\bm S}{\bm G}$ is symmetric
+%  	\item ${\bm S}{\bm G}$ is idempotent
+%  \end{itemize}
+%  \item Let ${\bm v}\in\mathfrak{s}$ 
+%    \begin{itemize}
+%    	\item ${\bm S}{\bm G}{\bm v}$ will also lie in $\mathfrak{s}$.
+%    	\item ${\bm S}{\bm G}{\bm v}={\bm v}$ only when ${\bm S}{\bm G}$ is a projection.
+%    \end{itemize}
+%  \end{itemize}
+%  \end{frame}
+%
+%  \begin{frame}{Geometry: Oblique Projection}
+%  	\vspace{-0.9cm}
+%  	\centering
+%  	\input{Figs/pointforerec_schematic}
+%  \end{frame}
+%  \begin{frame}{Projections preserve unbiasedness}
+%	Let $\hat{\bm y}_{t+h|t}$ be an unbiased forecast that is $E_{1:t}(\hat{\bm y}_{t+h|t})={\bm \mu_{t+h|t}}$ where ${\bm \mu_{t+h|t}}=E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$
+%	\begin{theorem}
+%	  The reconciled forecast $\tilde{\bm y}_{t+h|t}={\bm S}{\bm G}\hat{\bm y}_{t+h|t}$ will also be unbiased iff ${\bm S}{\bm G}$ is a projection.
+%    \end{theorem}
+%    Previously, this was often stated as an assumption that ${\bm S}{\bm G}{\bm S}={\bm S}$.    
+%  \end{frame}
+%  \begin{frame}{Proof}
+%  Very easy proof
+%  \begin{align*}
+%  E_{1:t}(\tilde{\bm{y}}_{t+h|t})
+%  &= E_{1:t}(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t})\\
+%  &= \bm{S}\bm{G}E_{1:t}(\hat{\bm{y}}_{t+h|t})\\
+%  &= \bm{S}\bm{G}\bm{\mu}_{t+h|t}\\
+%  &= \bm{\mu}_{t+h|t}
+%  \end{align*}
+%  The last equality does not hold for ${\bm G}$ in general but does hold when ${\bm S}{\bm G}$ is a projection.
+%  \end{frame}
+  \begin{frame}{Why reconciliation works}
+  \begin{itemize}
+  	\item The realised observation always lies on $\mathfrak{s}$.
+  	\item Orthogonal projections always get us `closer' to all points in $\mathfrak{s}$ including the actual realisation.
+  	\item Ergo reconciliation reduces the error and not just in expectation. 
+  	\item What about the MinT approach? 
+  \end{itemize}
+  \end{frame}
+  \begin{frame}{Finding a direction}
+  \begin{itemize}
+  \item Consider the covariance matrix of ${\bm y}-\hat{\bm{y}}$.
+   \item This can be estimated using in-sample forecast errors.
+  \item This provides information about the likely direction of an error.
+  \item Projecting along this direction is more likely to result in a reconciled forecast closer to the target.
+  \end{itemize}  
+\end{frame}
+  \begin{frame}{Animation}
+  content...
   \end{frame}
@@
   \end{frame}
-  \begin{frame}{Projections preserve unbiasedness}
-	Let $\hat{\bm y}_{t+h|t}$ be an unbiased forecast that is $E_{1:t}(\hat{\bm y}_{t+h|t})={\bm \mu_{t+h|t}}$ where ${\bm \mu_{t+h|t}}=E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$
-	\begin{theorem}
-	  The reconciled forecast $\tilde{\bm y}_{t+h|t}={\bm S}{\bm G}\hat{\bm y}_{t+h|t}$ will also be unbiased iff ${\bm S}{\bm G}$ is a projection.
-    \end{theorem}
-    Previously, this was often stated as an assumption that ${\bm S}{\bm G}{\bm S}={\bm S}$.    
-  \end{frame}
-  \begin{frame}{Proof}
-  Very easy proof
-  \begin{align*}
-  E_{1:t}(\tilde{\bm{y}}_{t+h|t})
-  &= E_{1:t}(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t})\\
-  &= \bm{S}\bm{G}E_{1:t}(\hat{\bm{y}}_{t+h|t})\\
-  &= \bm{S}\bm{G}\bm{\mu}_{t+h|t}\\
-  &= \bm{\mu}_{t+h|t}
-  \end{align*}
-  The last equality does not hold for ${\bm G}$ in general but does hold when ${\bm S}{\bm G}$ is a projection.
-  \end{frame}
-  \begin{frame}{Why reconciliation works}
+  \begin{frame}{Is this overkill?}
   \begin{itemize}
-  	\item The realised observation always lies on $\mathfrak{s}$.
-  	\item Orthogonal projections always get us `closer' to all points in $\mathfrak{s}$ including the actual realisation.
-  	\item Ergo reconciliation reduces the error and not just in expectation. 
-  	\item Oblique projections have the same property for non-Euclidean distance. 
+  	\item Is this geometric interpretation really necessary?
+  	\item When we generalise to probabilistic forecasts the regression interpretation does not really fit.
+  	\item Geometric ideas can easily be generalised. 
   \end{itemize}
-  \end{frame}
-  \begin{frame}{Geometry}
-  \vspace{-2.3cm}
-  \centering 
-  \input{Figs/orth_pointforerec_schematic}
   \end{frame}

### 2018-11-07 Presentation/ProbForeRec.tex
Few more edits on presentation

@@
-\documentclass{beamer}
+\documentclass[handout]{beamer}
 \usetheme{Warsaw}
@@
 \title{Probabilistic Forecast Reconciliation}
-\date{August 15, 2018}
+\date{November 14, 2018}
 \author[GPAH]{Puwasala Gamakumara, Anastasios Panagiotelis, George Athanasopoulos and Rob Hyndman}
@@
   	\end{itemize}
-    \item Retail sales
+    \item Wind power
     \begin{itemize}
-    	\item Aggregate of different product category sales
-    	\item Further breakdown into individual stock keeping units.  
+    	\item Forecasts required at a daily and hourly resolution.
+    	\item Daily series is aggregate of 24 hourly series.  
     \end{itemize}
@@
   \begin{itemize}
-  	\item Begin with a vector of forecasts that are incoherent.
+  	\item Begin with a vector of {\em base} forecasts that are incoherent.
   	\item Adjust these {\bf ex post} to make them coherent.
@@
     	\item Let $n$ be the number of series, $\bm{y}$ be an n-vector of all series.
-    	\only<2>{\item Let {\color{blue}$m$} be the bottom level series and {\color{blue}$\bm{b}$} be an {\color{blue}$m$}-vector of the bottom level series.}
+    	\only<2>{\item Let {\color{blue}$m$} be the number of bottom level series and {\color{blue}$\bm{b}$} be an {\color{blue}$m$}-vector of the bottom level series.}
     \end{itemize}    
@@
 \begin{frame}{The ${\bm S}$ matrix}
-    The matrix ${\bm S}$ defines the aggregation constraints, e.g.
+    The $n\times m$ matrix ${\bm S}$ defines the aggregation constraints, e.g.
     \begin{equation*}
@@
     \begin{definition} 
-	  The {\bf coherent subspace} is the linear subspace spanned by the columns of ${\bm S}$, i.e. $\mathfrak{s}=\mbox{sp}({\bm S})$
+	  The {\bf coherent subspace} is the $m$-dimensional linear subspace of $\mathbb{R}^n$ spanned by the columns of ${\bm S}$, i.e. $\mathfrak{s}=\mbox{sp}({\bm S})$
     \end{definition}
@@
   \item This provides information about the likely direction of an error.
-  \item Projecting along this direction is more likely to result in a reconciled forecast closer to the target.
+  \item Projecting along this direction is more likely to result in a reconciled forecast that is closer to the target.
   \end{itemize}  
@@
     \begin{definition}
-      The probability measure $\nu$ is coherent if
+      The probability measure $\mu$ is coherent if
       \begin{equation*}
@@
   \begin{frame}{Reconciled Probabilistic Forecast}
-  	Let $g:\mathbb{R}^n\rightarrow\mathbb{R}^m$ be a linear function.  Then 
+  	Let $g:\mathbb{R}^n\rightarrow\mathbb{R}^m$ be a mapping.  Then 
   	\begin{definition}
@@
   \begin{frame}{Elliptical distributions}
-  	Let the true predictive densities be elliptical.
+  	Consider case where the base true predictive distributions are elliptical.
   	\begin{theorem}
-  		There exists a function $g(.)$ such that the true predictive distribution can be recovered by linear reconciliation as long as the unreconciled probabilistic forecast comes from the correct elliptical class.
+  		There exists a function $\bm{G}$ such that the true predictive distribution can be recovered by linear reconciliation.
   	\end{theorem}
-    This follows from the closure property of elliptical distributions under affine transformations and marginalisation.  Conditions are also derived for when this $g(.)$ is also a projection.
+    This follows from the closure property of elliptical distributions under affine transformations and marginalisation.  
   \end{frame}
@@
   		\item Suppose $\bm{\hat{y}}^{[1]},\ldots,\bm{\hat{y}}^{[J]}$ is a sample from the unreconciled probabilistic forecast.
-  		\item Then setting $\tilde{\bm y}^{[j]}=s\circ g(\hat{\bm y}^{[j]})=\bm{S}\bm{G}\hat{\bm y}^{[j]}$ produces a sample from the reconciled distribution with respect to $g$.
+  		\item Then setting $\tilde{\bm y}^{[j]}=\bm{S}\bm{G}\hat{\bm y}^{[j]}$ produces a sample from the reconciled distribution with respect to $g$.
   	\end{itemize}
@@
   \section{Scoring}
-  \begin{frame}{Univariate v Multivariate Scores}
-    Scoring rules can be used to evaluate probabilistic forecasts
+  \begin{frame}{Multivariate Scores}
     \begin{itemize}
-    	\item Univariate
-    	\begin{itemize}
-    		\item Log Score
-    		\item Continuous Rank Probability Score
-    	\end{itemize}
-    	\item Multivariate
+    \item Scoring rules can be used to evaluate probabilistic forecasts
         \begin{itemize}
@@
 	      \item Energy Score
+	      \item Variogram score
+        \end{itemize}
+    \item We may want to compare
+    \begin{itemize}
+    	\item Coherent v Incoherent
+    	\item Coherent v Coherent
     \end{itemize}
     \end{itemize}
-    These may be computed using densities or a sample.
-  \end{frame}
-  \begin{frame}{Approaches}
-  	\begin{enumerate}
-  		\item Use a summary of all univariate scores.
-  		\item Make comparisons on the joint distribution of bottom level series only.
-        \item Make comparisons using the full joint distribution
-  \end{enumerate}
-  There are pitfalls to the third approach.
   \end{frame}
   \begin{frame}{Coherent v Incoherent}
-	When comparing reconciled and unreconciled probabilistic forecasts on the basis of log score
+	When using log score
 	\begin{theorem}
@@
   \end{frame}
-  \begin{frame}{Reconciled v Reconciled}
-	\begin{itemize}
-		\item For two reconciled probabilistic forecasts log score can be used.
-		\item Comparisons can be made on the basis of bottom level series (or any basis series).
-		\item By the definition of coherence $\log (f({\bm b}))=\log (f({\bm S}{\bm b}){\bm J})$
-		\item The Jacobian does not affect the ordering of log score.
-	\end{itemize}
-  \end{frame}
-  \begin{frame}{Energy  score}
-  	\begin{itemize}
-  		\item Using bottom level series only is a bad idea for energy score.
-  		\item Energy score is invariant to orthogonal transformation but not affine transformations.
-  		\item Since ${\bm S}$ is not a rotation the ranking of different methods based on the full hierarchy may differ from the ranking based on bottom level series only.
-  	\end{itemize}
-  \end{frame}
   \begin{frame}{Simulations}
    	\begin{itemize}
+   		\item We have run lots of simulations
    		\item The main takeaway messages are:

### 2018-11-10 Presentation/ProbForeRec.tex
added more pictures to presentation

@@
-\documentclass[handout]{beamer}
+\documentclass{beamer}
 \usetheme{Warsaw}
@@
   \begin{itemize}
+  	\item Multiple time series $\rightarrow$ some series are aggregates of others.
   	\item Gross Domestic Product
+  	\pause
   	\begin{itemize}
@@
   	\end{itemize}
+    \pause
     \item Wind power
@@
     \end{itemize}
+    \pause
     \item Potentially need forecasts of all time series.
@@
     \item Potential approaches
+    \pause
   	\begin{itemize}
+  		\item Multivariate models
+  		\pause
   		\item Univariate models
-  		\item Multivariate models
+  		\pause
   		\item Judgemental forecasts
   	\end{itemize}
-  \item Forecasts do not respect aggregation structure ({\bf Incoherent})
-  \item Outcome {\em does} respect aggregation  structure ({\bf Coherent})
+  \pause
+  \item Forecasts do not respect aggregation structure \pause({\bf Incoherent})\pause
+  \item Outcome {\em does} respect aggregation  structure \pause ({\bf Coherent})\pause
   \item Motivation is aggregation but can be generalised to any linear constraints.
@@
   	\item Begin with a vector of {\em base} forecasts that are incoherent.
+  	\pause
   	\item Adjust these {\bf ex post} to make them coherent.
+  	\pause
   	\item There are good solutions for point forecasting that:
+  	\pause
   	\begin{itemize}
@@
   	\end{itemize}
+  	\pause
   	\item Generalisation to probabilistic forecasts is our contribution.
+  	\pause
   	\item Getting there necessitates a rethink of the existing point forecasting literature. 
@@
   \end{frame}
-  \begin{frame}{What we do NOT do}
-  \begin{itemize}
-  	\item All information is contained in the most disaggregate series.
-  	\item In principle using the correct multivariate model for the most disaggregate series and aggregating them should work.
-  	\item Disaggregate series are: 
-  	\begin{itemize}
-  		\item Very noisy
-  		\item High-dimensional
-  		\item Prone to model misspecification
-  	\end{itemize} 
-  \end{itemize}
-  \end{frame}
+%  \begin{frame}{What we do NOT do}
+%  \begin{itemize}
+%  	\item All information is contained in the most disaggregate series.
+%  	\item In principle using the correct multivariate model for the most disaggregate series and aggregating them should work.
+%  	\item Disaggregate series are: 
+%  	\begin{itemize}
+%  		\item Very noisy
+%  		\item High-dimensional
+%  		\item Prone to model misspecification
+%  	\end{itemize} 
+%  \end{itemize}
+%  \end{frame}
   \section{Point Forecast Reconciliation}
@@
     \begin{itemize}
-    	\item Let $n$ be the number of series, $\bm{y}$ be an n-vector of all series.
-    	\only<2>{\item Let {\color{blue}$m$} be the number of bottom level series and {\color{blue}$\bm{b}$} be an {\color{blue}$m$}-vector of the bottom level series.}
+    	\item Let $n$ be the number of series, $\bm{y}_t$ be an n-vector of all series.
+    	\only<2>{\item Let {\color{blue}$m$} be the number of bottom level series and {\color{blue}$\bm{b}_t$} be an {\color{blue}$m$}-vector of the bottom level series.}
     \end{itemize}    
@@
 \begin{frame}{The ${\bm S}$ matrix}
+  Coherence holds when
+  \begin{equation*}
+  {\bm y}={\bm S}{\bm b}
+  \end{equation*} 
     The $n\times m$ matrix ${\bm S}$ defines the aggregation constraints, e.g.
@@
     \end{equation*}    
-    Coherence holds when
-    \begin{equation*}
-    {\bm y}={\bm S}{\bm b}
-    \end{equation*} 
 \end{frame}
@@
   \begin{itemize}
-  	\item Cast the problem as a regression model with base forecasts $\hat{\bm{y}}$ as the ``dependent variable'' and ${\bm S}$ as the ``design matrix''. 
+  	\item Cast the problem as a regression model with base forecasts $\hat{\bm{y}}_{T+h}$ as the ``dependent variable'' and ${\bm S}$ as the ``design matrix''. 
   	\begin{equation*}
-  	\hat{\bm{y}}={\bm{S}}{\bm\beta}+{\bm e}
+  	\hat{\bm{y}}_{T+h}={\bm{S}}{\bm\beta}_{T+h}+{\bm e}_{T+h}
   	\end{equation*}
@@
   	\begin{equation*}
-  	\tilde{\bm{y}}={\bm S}({\bm S}'{\bm S})^{-1}{\bm S}'{\hat{\bm{y}}}
+  	\tilde{\bm{y}}_{T+h}={\bm S}({\bm S}'{\bm S})^{-1}{\bm S}'{\hat{\bm{y}}}_{T+h}
   	\end{equation*}
@@
   \begin{equation*}
-  \tilde{\bm{y}}={\bm S}({\bm S}'{\bm W}^{-1}{\bm S})^{-1}{\bm S}'{\bm W}^{-1}{\hat{\bm{y}}}
+  \tilde{\bm{y}}_{T+h}={\bm S}({\bm S}'{\bm W}^{-1}{\bm S})^{-1}{\bm S}'{\bm W}^{-1}{\hat{\bm{y}}}_{T+h}
   \end{equation*}
@@
   	\item Ergo reconciliation reduces the error and not just in expectation. 
+  	\pause
   	\item What about the MinT approach? 
@@
   \begin{itemize}
-  \item Consider the covariance matrix of ${\bm y}-\hat{\bm{y}}$.
+  \item Consider the covariance matrix of ${\bm y}_{T+h}-\hat{\bm{y}}_{T+h}$.
+   \pause
    \item This can be estimated using in-sample forecast errors.
+   \begin{equation*}
+   \bm{W}=\sum\limits_{t=1}^T ({\bm y}_{t}-\hat{\bm{y}}_{t})({\bm y}_{t}-\hat{\bm{y}}_{t})'
+   \end{equation*}
+  \pause
   \item This provides information about the likely direction of an error.
+  \pause
   \item Projecting along this direction is more likely to result in a reconciled forecast that is closer to the target.
@@
 \end{frame}
-  \begin{frame}{Animation}
-  content...
+\begin{frame}{In-Sample errors}
+\vspace{-0.9cm}
+\centering
+\input{Figs/insample}
+\end{frame}
+\begin{frame}{Most likely direction}
+\vspace{-0.9cm}
+\centering
+\input{Figs/insampledir}
+\end{frame}
+  \begin{frame}{Geometry: Oblique Projection}
+\vspace{-0.9cm}
+\centering
+\input{Figs/oblique_justification1}
+\end{frame}
+  \begin{frame}{Geometry: Oblique Projection}
+\vspace{-0.9cm}
+\centering
+\input{Figs/oblique_justification2}
 \end{frame}
@@
   	\item Is this geometric interpretation really necessary?
+  	\pause
   	\item When we generalise to probabilistic forecasts the regression interpretation does not really fit.
+  	\pause
   	\item Geometric ideas can easily be generalised. 
@@
   \begin{frame}{Reconciled Probabilistic Forecast}
-  	Let $g:\mathbb{R}^n\rightarrow\mathbb{R}^m$ be a mapping.  Then 
+  	Let $g:\mathbb{R}^n\rightarrow\mathbb{R}^m$ be a function.  Then 
   	\begin{definition}
@@
   \begin{frame}{Elliptical distributions}
-  	Consider case where the base true predictive distributions are elliptical.
+  	Consider case where the base and true predictive distributions are elliptical.
   	\begin{theorem}
-  		There exists a function $\bm{G}$ such that the true predictive distribution can be recovered by linear reconciliation.
+  		There exists a matrix $\bm{G}$ such that the true predictive distribution can be recovered by linear reconciliation.
   	\end{theorem}
@@
   		\item Often densities are unavailable but we can simulate a sample from the predictive distribution.
-  		\item Suppose $\bm{\hat{y}}^{[1]},\ldots,\bm{\hat{y}}^{[J]}$ is a sample from the unreconciled probabilistic forecast.
-  		\item Then setting $\tilde{\bm y}^{[j]}=\bm{S}\bm{G}\hat{\bm y}^{[j]}$ produces a sample from the reconciled distribution with respect to $g$.
+  		\pause
+  		\item Suppose $\bm{\hat{y}}_{T+h}^{[1]},\ldots,\bm{\hat{y}}_{T+h}^{[J]}$ is a sample from the unreconciled probabilistic forecast.
+  		\pause
+  		\item Then setting $\tilde{\bm y}_{T+h}^{[j]}=\bm{S}\bm{G}\hat{\bm y}_{T+h}^{[j]}$ produces a sample from the reconciled distribution with respect to $g$.
   	\end{itemize}
@@
     \item Scoring rules can be used to evaluate probabilistic forecasts
+        \pause
         \begin{itemize}
@@
         \end{itemize}
+    \pause
     \item We may want to compare
@@
    	\begin{itemize}
-   		\item We have run lots of simulations
+   		\item We have run lots of simulations.
+   		\pause
    		\item The main takeaway messages are:
+   		    \pause
    		    \begin{itemize}
    		    	\item Reconciliation is better than no reconciliation.
+   		    	\pause
    		    	\item Bottom up does not do well.
-   		    	\item OLS (an orthogonal projection) does poorly.
+   		    	\pause
+   		    	\item OLS (an orthogonal projection) does reasonably well.
+   		    	\pause
    		    	\item MinT (an oblique projection) does best.
@@
      	\item The optimal feasible reconciliation method remains an open question even for elliptical distributions.
+     	\pause
      	\begin{itemize}
@@
      	\end{itemize}
+        \pause
+        \item How should probabilistic reconciliation work for non-elliptical distributions.
+        \pause
         \item Are non-linear reconciliation methods worthwhile?
-        \item How should probabilistic reconciliation work for non-elliptical distributions.
+        \pause
         \item Further development of multivariate scoring rules.

### 2018-11-12 Presentation/ProbForeRec.tex
More slides added to pres

@@
 \usetheme{Warsaw}
-\usepackage{amsmath,amsthm, bm, tikz,qtree}
+\usepackage{amsmath,amsthm, bm, tikz,qtree,multirow,booktabs}
 \usetikzlibrary{arrows,positioning,shapes,fit,calc}
@@
   	\item Multiple time series $\rightarrow$ some series are aggregates of others.
+  	\pause
   	\item Gross Domestic Product
@@
     \pause
-    \item Wind power
+    \item Wind power \hyperlink{aelos}{\beamerbutton{}}
     \begin{itemize}
     	\item Forecasts required at a daily and hourly resolution.
-    	\item Daily series is aggregate of 24 hourly series.  
+    	\item Daily series is aggregate of 24 hourly series.\label{afterdat}  
     \end{itemize}
@@
   \end{itemize}
+  \hfill\hyperlink{bu}{\beamerbutton{}}
   \end{frame}
-  \begin{frame}{Reconciliation}
+  \begin{frame}{Reconciliation}\label{cont}
   \begin{itemize}
@@
     	\item Let $n$ be the number of series, $\bm{y}_t$ be an n-vector of all series.
-    	\only<2>{\item Let {\color{blue}$m$} be the number of bottom level series and {\color{blue}$\bm{b}_t$} be an {\color{blue}$m$}-vector of the bottom level series.}
+    	\pause\item Let {\color{blue}$m$} be the number of bottom level series and {\color{blue}$\bm{b}_t$} be an {\color{blue}$m$}-vector of the bottom level series.
     \end{itemize}    
@@
   \begin{equation*}
-  {\bm y}={\bm S}{\bm b}
+  {\bm y}_t={\bm S}{\bm b}_t
   \end{equation*} 
@@
    	\end{itemize}
+   \hfill\hyperlink{sim}{\beamerbutton{}}
    \end{frame}
-   \begin{frame}{Looking ahead}
+   \begin{frame}{Looking ahead}\label{simdisc}
      \begin{itemize}
@@
         \item Are non-linear reconciliation methods worthwhile?
-        \pause
-        \item Further development of multivariate scoring rules.
      \end{itemize}	
    \end{frame}
+  \begin{frame}
+    \Huge{Thank You!}\\
+  \pause\Huge{Questions?}
+  \end{frame}
+  \begin{frame}{Aeolos Wind Farm}\label{aelos}
+  \centering
+  \includegraphics[height=7cm]{Figs/Aeolos_Unscaled}
+  \end{frame}
+  \begin{frame}{Aeolos Wind Farm}
+  \centering
+  \includegraphics[height=7cm]{Figs/Aeolos_Unscaled}
+  \end{frame}
+  \begin{frame}{Aeolos Wind Farm}
+\centering
+\includegraphics[height=7cm]{Figs/Aeolos_Scaled}
+  \hfill\hyperlink{afterdat}{\beamerbutton{}}
+\end{frame}
+  \begin{frame}{What we do NOT do}\label{bu}
+  \begin{itemize}
+  	\item All information is contained in the most disaggregate series.
+  	\item In principle using the correct multivariate model for the most disaggregate series and aggregating them should work.
+  	\item Disaggregate series are: 
+  	\begin{itemize}
+  		\item Very noisy
+  		\item High-dimensional
+  		\item Prone to model misspecification
+  	\end{itemize} 
+  \end{itemize}
+  \hfill\hyperlink{cont}{\beamerbutton{}}
+  \end{frame}
+  \begin{frame}{Simulation Results}\label{sim}
+  Hierarchy from earlier bottom series are ARIMA models.  Training sample of 500, one-step ahead forecasts, 1000 replications.
+  \begin{table}
+  	\centering\small
+  	\begin{tabular}{lccc}
+  		\toprule
+  		Forecasting &{\text{Energy score}} & {\text{Variogram score}} & {\text{Log score}} \\
+  		\midrule
+  		MinT(Sample) &  {\bf 10.01}   & {\bf 8.41}  & {\bf 11.29} \\
+  		OLS          &  10.53   & 8.86  & 11.54 \\
+  		Bottom-up    &  12.35   & 9.22  & 12.05 \\
+  		Incoherent	 &  11.12   & 9.53  \\
+  		\bottomrule
+  	\end{tabular}
+  \end{table}
+\hfill\hyperlink{simdisc}{\beamerbutton{}}
+\end{frame}
 \end{document}

### 2018-11-13 Presentation/ProbForeRec.tex
finalised talk

@@
   	\pause
-  	\item Gross Domestic Product
+  	\item Gross Domestic Product \hyperlink{GDP}{\beamerbutton{}}
   	\pause
@@
   \end{frame}
-  \begin{frame}{With a sample}
-  	\begin{itemize}
-  		\item Often densities are unavailable but we can simulate a sample from the predictive distribution.
-  		\pause
-  		\item Suppose $\bm{\hat{y}}_{T+h}^{[1]},\ldots,\bm{\hat{y}}_{T+h}^{[J]}$ is a sample from the unreconciled probabilistic forecast.
-  		\pause
-  		\item Then setting $\tilde{\bm y}_{T+h}^{[j]}=\bm{S}\bm{G}\hat{\bm y}_{T+h}^{[j]}$ produces a sample from the reconciled distribution with respect to $g$.
-  	\end{itemize}
-  \end{frame}
+%  \begin{frame}{With a sample}
+%  	\begin{itemize}
+%  		\item Often densities are unavailable but we can simulate a sample from the predictive distribution.
+%  		\pause
+%  		\item Suppose $\bm{\hat{y}}_{T+h}^{[1]},\ldots,\bm{\hat{y}}_{T+h}^{[J]}$ is a sample from the unreconciled probabilistic forecast.
+%  		\pause
+%  		\item Then setting $\tilde{\bm y}_{T+h}^{[j]}=\bm{S}\bm{G}\hat{\bm y}_{T+h}^{[j]}$ produces a sample from the reconciled distribution with respect to $g$.
+%  	\end{itemize}
+%  \end{frame}
   \section{Scoring}
@@
   \end{frame}
+  \begin{frame}{GDP}\label{GDP}
+\centering
+\includegraphics[height=7cm]{Figs/GDP}
+\hfill\hyperlink{afterdat}{\beamerbutton{}}
+\end{frame}
   \begin{frame}{Aeolos Wind Farm}\label{aelos}
@@
   \begin{itemize}
+  	\item Use disaggregate series as predictors (although we can).
   	\item All information is contained in the most disaggregate series.

### 2019-04-11 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Outlined first two papers

--- 2018-08-24 ProbabilisticCoherence.tex
@@
 \usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
-\usepackage{mathrsfs, float, booktabs,todonotes,amsthm}
+\usepackage{mathrsfs, float, booktabs,todonotes,amsthm, xcolor}
 \usepackage[bb=boondox]{mathalfa}
@@
 	{
-		\title{\bf Probabilistic Forecasts in Hierarchical~Time~Series}
+		\title{\bf Hierarchical Forecasts Reconciliation}
 		\author{Puwasala Gamakumara\thanks{
@@
 		\begin{center}
-			{\LARGE\bf Probabilistic Forecasts in Hierarchical~Time~Series}
+			{\LARGE\bf Hierarchical Forecasts Reconciliation}
 		\end{center}
@@
 
-\begin{abstract}
-  Forecast reconciliation involves adjusting forecasts to ensure coherence with aggregation constraints.
+	\begin{abstract} TBC
+		%  Forecast reconciliation involves adjusting forecasts to ensure coherence with aggregation constraints.
 We extend this concept from point forecasts to probabilistic forecasts by redefining forecast reconciliation in terms of linear functions in general, and projections more specifically.
@@
 
-\noindent%
-{\it Keywords:}  Forecast Reconciliation, Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
-\vfill
+%	\noindent%
+%	{\it Keywords:}  Forecast Reconciliation, Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
+%	\vfill
 
@@
 
-Large collections of time series often follow some aggregation structure.
+%	Large collections of time series often follow some aggregation structure.
 For example, the electricity demand of a country can be disaggregated according to a geographic hierarchy of states, cities, and individual households.
@@
 This can easily be generalised to probabilistic forecasting allowing us to derive further results for elliptical distributions as well as provide insight into forecast evaluation via multivariate  scoring rules.
-
-Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level of the hierarchy.
+%	
+%	Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level of the hierarchy.
 To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$ and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.
@@
 A middle-out approach is a hybrid between these two, that for the hierarchy in Figure~\ref{fig1} would produce first stage forecasts for series $A$ and $B$.
+%	
+%	
+%	In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular.
+For these methods, first stage forecasts are independently produced for all series rather than series at a single level.
+Since these so-called `base' forecasts are rarely coherent in practice, they are subsequently adjusted or `reconciled' to ensure coherence.
+Note that we use coherence and reconciliation as distinct terms, in contrast to their at times ambiguous usage in the past.
+To date, reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators.
+These include Ordinary Least Squares {OLS} \citep{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix.
+These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{AthEtAl2009,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and, in some sense, hedge against the risk of model misspecification at a single level.
+%	
+%	A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \citep[see][and references therein]{Gneiting2014}.
+Indeed to the best of our knowledge, the (as yet unpublished) work of \citep{BenTaieb2017} is the only paper to deal with coherent probabilistic forecasts, and although they reconcile the means of the predictive distributions, the overall distributions are constructed in a bottom-up fashion rather than use a reconciliation process.
+In contrast, the main objective of our paper is to generalise both coherence and reconciliation from point to probabilistic forecasting.
+%	
+%	To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections.
+In addition to being highly intuitive, this allows us to establish a number of theoretical results.
+We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts, while the second shows that reconciled forecasts dominate unreconciled forecasts via the distance reducing property of projections.
+We provide definitions of coherence and forecast reconciliation in the probabilistic setting, and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation.
+We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class.
+We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly estimated in practice, we provide a heuristic argument in favour of MinT reconciliation.
+%	
+%	We also cover the topic of forecast evaluation of probabilistic forecasts via scoring rules.
+In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.
+Therefore we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts.
+Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.
+%	
+%	The remainder of the paper is structured as follows.
+In Section~\ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.
+Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results.
+In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules, while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian}.
+Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.
+
+	\section{Forecasts reconciliation}\label{sec:definitions}
+
+	\subsection{Notation and preliminaries}\label{sec:notation}
 
@@
 		\end{figure}
-
-In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular.
-For these methods, first stage forecasts are independently produced for all series rather than series at a single level.
-Since these so-called `base' forecasts are rarely coherent in practice, they are subsequently adjusted or `reconciled' to ensure coherence.
-Note that we use coherence and reconciliation as distinct terms, in contrast to their at times ambiguous usage in the past.
-To date, reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators.
-These include Ordinary Least Squares {OLS} \citep{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix.
-These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{AthEtAl2009,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and, in some sense, hedge against the risk of model misspecification at a single level.
-
-A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \citep[see][and references therein]{Gneiting2014}.
-Indeed to the best of our knowledge, the (as yet unpublished) work of \citep{BenTaieb2017} is the only paper to deal with coherent probabilistic forecasts, and although they reconcile the means of the predictive distributions, the overall distributions are constructed in a bottom-up fashion rather than use a reconciliation process.
-In contrast, the main objective of our paper is to generalise both coherence and reconciliation from point to probabilistic forecasting.
-
-To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections.
-In addition to being highly intuitive, this allows us to establish a number of theoretical results.
-We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts, while the second shows that reconciled forecasts dominate unreconciled forecasts via the distance reducing property of projections.
-We provide definitions of coherence and forecast reconciliation in the probabilistic setting, and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation.
-We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class.
-We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly estimated in practice, we provide a heuristic argument in favour of MinT reconciliation.
-
-We also cover the topic of forecast evaluation of probabilistic forecasts via scoring rules.
-In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.
-Therefore we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts.
-Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.
-
-The remainder of the paper is structured as follows.
-In Section~\ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.
-Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results.
-In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules, while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian}.
-Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.
-
-\section{Coherent forecasts}\label{sec:definitions}
-
-\subsection{Notation and preliminaries}\label{sec:notation}
 
@@
 
-\subsection{Coherent probabilistic forecasts}\label{sec:cohprobf}
-
-Let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple, where $\mathscr{F}_{\mathbb{R}^m}$ is the usual Borel $\sigma$-algebra on $\mathbb{R}^m$.
-Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_{\mathfrak{s}}$.
-Here $\mathscr{F}_{\mathfrak{s}}$ is a collection of sets $s(\mathcal{B})$, where $s(\mathcal{B})$ denotes the image of the set $\mathcal{B}\in \mathscr{F}_{\mathbb{R}^m}$ under the mapping $s(.)$.
-
-\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
-  The measure $\breve{\nu}$ is coherent if it has the property
-  \[
-    \breve{\nu}(s(\mathcal{B})) = \nu(\mathcal{B}) \quad \forall \mathcal{B} \in \mathscr{F}_{\mathbb{R}^m},
-  \]
-\end{definition}
-
-A probabilistic forecast for time $t+h$ is coherent if uncertainty in $\bm{\breve{y}}_{t+h}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.
-
 	These definitions of the coherent space $\mathfrak{s}$, coherent point and coherent probabilistic forecasts in terms of the mapping $s(.)$, may give the impression that the bottom-level series play an important role.
@@
 In general, we call the series (or linear combinations thereof) used in the definitions of coherence \textit{basis series}.
-Unless stated otherwise, we will always assume that the basis series are the bottom-level series as in Definition~\ref{def:cohpoint} and Definition~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.
+Unless stated otherwise, we will always assume that the basis series are the bottom-level series as in Definition~\ref{def:cohpoint}, since this facilitates comparison with existing approaches in the literature.
 
-To the best of our knowledge, the only other definition of coherent probabilistic forecasts is given by \citet{BenTaieb2017} who define coherent probabilistic forecasts in terms of convolutions.
-According to their definition, probabilistic forecasts are coherent when a convolution of forecast distributions of disaggregate series is identical to the forecast distribution of the corresponding aggregate series.
-Their definition is consistent with our definition; our reason for providing a different definition is that the geometric understanding of coherence will facilitate our definitions of point and probabilistic forecast reconciliation to which we now turn our attention.
-
-\section{Forecast reconciliation}\label{sec:reconciliation}
+	\subsection{Point forecast reconciliation}\label{sec:reconciliation}
 
@@
 We do so here in slightly more general terms than usual.
-We then extend this idea to the novel concept of probabilistic reconciliation.
-
-\subsection{Point forecast reconciliation}
+	%We then extend this idea to the novel concept of probabilistic reconciliation.
 
@@
 For example OLS minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$, while \citet{Wickramasuriya2017} show that MinT minimises the Mahalonobis distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$.
+\textcolor{red}{Explain why MinT works well}.
 Bottom-up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom-level series.
@@
 
-Before generalising the concept of point reconciliation to probabilistic forecasts, we state two theorems that motivate the use of projections for point forecast reconciliation.
+	We now state two theorems that motivate the use of projections for point forecast reconciliation.
 First, let $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ and assume $\hat{\bm{y}}_{t+h|t}$ is an unbiased prediction; that is $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\mu_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
@@
 
-\subsection{Probabilistic forecast reconciliation}
+	\section{Bias correction}
 
-We now extend the methodology of point forecast reconciliation to probabilistic forecasts.
-%For probabilistic forecasts, reconciliation implies finding the probability measure of the coherent forecasts using the information from an incoherent probabilistic forecast measure.
-A more formal definition is given below.
-Let $(\mathbb{R}^n, \mathscr{F}_{\mathbb{R}^n}, \hat{\nu})$ be a probability triple that is not coherent and which characterises forecast uncertainty for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.
-This is obtained from the first stage of the forecasting process; e.g., by modelling and forecasting each series individually.
-Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear function, and let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$.
+	\section{Application}
 
-\begin{definition} \label{def:reconprob}
-  The reconciled probability measure of $\hat{\nu}$ with respect to the mapping $g(.)$ is a probability measure $\tilde{\nu}$ on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_\mathfrak{s}$ such that
-  \begin{equation}
-  \tilde{\nu}(s(\mathcal{B})) = \nu(\mathcal{B})= \hat{\nu}(g^{-1}(\mathcal{B})) \qquad \forall \mathcal{B} \in \mathscr{F}_{\mathbb{R}^m}\,,
-  \end{equation}
-  where $g^{-1}(\mathcal{B}):=\{\breve{\bm{y}}\in \mathbb{R}^n:g(\breve{\bm{y}})\in \mathcal{B}\}$ is the pre-image of $\mathcal{B}$, that is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $\mathcal{B}$.
-\end{definition}
-
-This definition extends the notion of forecast reconciliation to the probabilistic setting.
-Under point reconciliation methods, the reconciled point forecast is equal to the unreconciled point forecast after the latter is passed through two linear functions.
-Similarly, probabilistic forecast reconciliation assigns the same probability to two sets where the points in one set are obtained by passing all points in the other set through two linear functions.
-This is depicted in Figure~\ref{fig:probfr_sch} schematically when $s\circ g$ is a projection.
-
-\begin{figure}
-	\input{Figs/probforerec_schematic.tex}
-	\caption{Summary of probabilistic forecast reconciliation.
-The probability that $\bm{y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that $\bm{y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast.
-Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic.}\label{fig:probfr_sch}
-\end{figure}
-
-Recall that when $s\circ g$ is a projection, the case of point forecast reconciliation can be broken down into three steps.
-\begin{compactenum}
-\item  $\hat{\bm{y}}_{t+h|t}$ is transformed into coordinates $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ via a change of basis.
-\item $\tilde{\bm{a}}_{t+h|t}$ is discarded and $\tilde{\bm{b}}_{t+h|t}$ are kept as the bottom-level reconciled forecasts.
-\item Reconciled forecasts for the entire hierarchy are recovered via $\tilde{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}$.
-\end{compactenum}
-We now outline the analogous steps for probabilistic forecasts when predictive densities are available.
-
-While $\hat{\nu}$ is a probability measure for an $n$-vector $\hat{\bm{y}}_{t+h|t}$, probability statements in terms of a different coordinate system can be made via an appropriate change of basis.
-Letting $f(.)$ be generic notation for a probability density function, and following the notation from our definition of point forecast reconciliation where $\hat{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t}$, we obtain
-\begin{equation}
-f(\hat{\bm{y}}_{t+h|t})=f(\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t})|(\bm{S}~\bm{R})|
-\end{equation}
-The expression $\hat{\nu}(g^{-1}(\mathcal{B}))$ in Definition~\ref{def:reconprob} is equivalent to the probability statement $\text{Pr}(\hat{\bm{y}}_{t+h|t}\in g^{-1}(\mathcal{B}))$.
-After the change of basis, this is equivalent to $\text{Pr}(\tilde{\bm{b}}\in \mathcal{B})$, which implies
-\begin{align}
-\text{Pr}(\hat{\bm{y}}_{t+h|t}\in g^{-1}(\mathcal{B}))&=\int\limits_{g^{-1}(\mathcal{B})}f(\hat{\bm{y}}_{t+h|t})d\hat{\bm{y}}_{t+h|t}\\
-&=\int\limits_{\mathcal{B}}\int f(\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t})|(\bm{S}~\bm{R})|d\tilde{\bm{a}}_{t+h|t}d\tilde{\bm{b}}_{t+h|t}.
-\end{align}
-After integrating out over $\tilde{\bm{a}}_{t+h|t}$, a step analogous to setting $\tilde{\bm{a}}_{t+h|t}=0$ for point forecasting, we obtain an expression that gives the probability that the reconciled bottom-level series lies in the region $\mathcal{B}$.
-This corresponds to $\nu(\mathcal{B})$ in Definition~\ref{def:reconprob}.
-To make a valid probability statement about the entire hierarchy we simply use the bottom-level probabilistic forecasts together with Definition~\ref{def:cohprob}.
-
-\subsubsection*{Example: Gaussian Distributions}
-
-Suppose an unreconciled probabilistic forecast is Gaussian with mean $\hat{\bm{\mu}}$ and variance-covariance matrix $\hat{\bm{\Sigma}}$.
-The subscripts $t+h|t$ are suppressed for brevity.
-Let the unreconciled density be given by
-\begin{equation}
-  f(\hat{\bm{y}})=(2\pi)^{-n/2}|\hat{\bm{\Sigma}}|^{-1/2}\exp\left\{-\frac{1}{2}\left[(\hat{\bm{y}}-\hat{\bm{\mu}})'\hat{\bm{\Sigma}}^{-1}(\hat{\bm{y}}-\hat{\bm{\mu}})\right]\right\}.
-\end{equation}
-In an alternative basis,
-\begin{equation}
-f(\tilde{\bm{b}},\tilde{\bm{a}})=(2\pi)^{-\frac{n}{2}}\Big|\hat{\bm{\Sigma}}\Big|^{-\frac{1}{2}}\Big|(\bm{S} ~  \bm{R})\Big|\exp\{-\frac{1}{2}q\}\,,
-\end{equation}
-where
-\begin{equation}
-q=(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\hat{\bm{\mu}})' \hat{\bm{\Sigma}}^{-1}(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\hat{\bm{\mu}}).
-\end{equation}
-The quadratic form $q$ can be rearranged as
-\begin{align*}
-q& =
-\left((\bm{S} ~  \bm{R})\bt-\hat{\bm{\mu}}\right)' \hat{\bm{\Sigma}}^{-1}\left((\bm{S} ~ \bm{R})\bt-\hat{\bm{\mu}}\right),\\
-& =
-\left(\bt-(\bm{S} ~ \bm{R})^{-1}\hat{\bm{\mu}}_{t+h}\right)' \Big[(\bm{S}  \bm{R})^{-1}\hat{\bm{\Sigma}_{t+h}}\left((\bm{S} ~ \bm{R})^{-1}\right)'\Big]^{-1}
-\left(\bt-(\bm{S} ~ \bm{R})^{-1}\hat{\bm{\mu}}_{t+h}\right)\,.
-\end{align*}
-Recall that
-\[
-  (\bm{S} ~ \bm{R})^{-1} =
-  \begin{pmatrix}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot  \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot \end{pmatrix} :=
-  \begin{pmatrix}
-  \bm{G} \\\bm{H}
-  \end{pmatrix}\,.
-\]
-Then $q$ can be rearranged further as
-\begin{align*}
-q& =%\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\hat{\bm{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|\PQ \Big|}
-%\exp \Big\{-\frac{1}{2}
-\left[\bt-\PQ\hat{\bm{\mu}}_{t+h}\right]'%\\[-0.5cm]
-\left[\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\right]^{-1}\left[\bt-\PQ\hat{\bm{\mu}}_{t+h}\right] %\Big\},
-\\[0.5cm]
- & =%\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\Big|^{\frac{1}{2}}}
-%\exp \Big\{-\frac{1}{2}
-\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix}' %&\\[-0.5cm]
-%& \hspace*{7cm}
- \left[\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\right]^{-1}\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix}. %\Big\}.
-\end{align*}
-%Since $\Big[\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\Big] = \begin{pmatrix}
-%\bm{P}\hat{\bm{\Sigma}_{t+h}}\bm{P}' & \bm{P}\hat{\bm{\Sigma}_{t+h}}\bm{Q}'
-%\bm{Q}\hat{\bm{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\hat{\bm{\Sigma}_{t+h}}\bm{Q}'
-%\end{pmatrix}$ we have
-
-Similar manipulations on the determinant of the covariance matrix lead to the following expression for the density:
-\begin{align*}
-f(\tilde{\bm{b}},\tilde{\bm{a}})&
-=(2\pi)^{-\frac{n}{2}}\left|
-\begin{pmatrix}
-  \bm{G}\hat{\bm{\Sigma}}\bm{G}' & \bm{G}\hat{\bm{\Sigma}}\bm{H}' \\
-  \bm{H}\hat{\bm{\Sigma}}\bm{G}' & \bm{H}\hat{\bm{\Sigma}}\bm{H}'
-\end{pmatrix}
-\right|^{-\frac{1}{2}}
-\exp \left\{-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix}'\right.\\
-&\hspace*{7cm}
-\left.\begin{pmatrix}
-\bm{G}\hat{\bm{\Sigma}}\bm{G}' & \bm{G}\hat{\bm{\Sigma}}\bm{H}' \\
-\bm{H}\hat{\bm{\Sigma}}\bm{G}' & \bm{H}\hat{\bm{\Sigma}}\bm{H}'
-\end{pmatrix}^{-1}
-\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix} \right\}.
-\end{align*}
-Marginalising out $\tilde{\bm{a}}$ leads to the following bottom-level reconciled forecasts:
-\begin{equation}\label{ex:2.1}
-f(\tilde{\bm{b}})=(2\pi)^{-\frac{m}{2}}\Big|\bm{G}\hat{\bm{\Sigma}}\bm{G}'\Big|^{\frac{1}{2}}
-\exp \Big\{-\frac{1}{2} (\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}})' (\bm{G}\hat{\bm{\Sigma}}\bm{G}')^{-1}(\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}) \Big\}.
-\end{equation}
-
-%Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\hat{\bm{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
-Then from \eqref{4.7} it follows that
-%\begin{equation}\label{eq:gaussianreconciled}
-%\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
-%\end{equation}
-This implies that the reconciled probabilistic forecast for the bottom-level series is $\tilde{\bm{b}} \sim \mathcal{N}(\bm{G}\hat{\bm{\mu}}, \bm{G}\hat{\bm{\Sigma}}\bm{G}')$.
-The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean $\bm{SG}\hat{\bm{\mu}}$ and rank deficient covariance matrix $\bm{SG}\hat{\bm{\Sigma}}\bm{G}'\bm{S}'$.
-
-\subsection{Elliptical distributions}
-
-We now show that the true predictive distribution can be recovered for elliptical distributions by linear reconciliation via pre-multiplication and translation respectively by a matrix we denote ${\bm G}_{opt}$ and vector we denote  ${\bm d}_{opt}$.
-Here, for any square matrix $\bm{C}$, $\bm{C}^{1/2}$ and $\bm{C}^{-1/2}$ are defined to satisfy $\bm{C}^{1/2}(\bm{C}^{1/2})'=\bm{C}$ and $\bm{C}^{-1/2}(\bm{C}^{-1/2})'=\bm{C}^{-1}$, for example $\bm{C}^{1/2}$ may be obtained via the Cholesky or eigenvalue decompositions.
-
-\begin{theo}[Reconciliation for Elliptical Distributions]
-	Let an unreconciled probabilistic forecast come from the elliptical class with location parameter $\hat{\bm{\mu}}$ and scale matrix $\hat{\bm{\Sigma}}$.
-Let the true predictive distribution of $\bm{y}$ also belong to the elliptical class with location parameter $\bm{\mu}$ and scale matrix $\bm{\Sigma}$.
-Then the linear reconciliation mapping $g(\breve{\bm{y}})=\bm{G}_{opt}\breve{\bm{y}}+\bm{d}_{opt}$ with $\bm{G}_{opt}={\bm{a}}\hat{\bm\Sigma}^{-1/2}$ and $\bm{d}_{opt}=\bm{\mu}-\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}$ recovers the true predictive density where ${\bm{a}}$ is any $m\times n$ matrix such that ${\bm{a}}{\bm{a}}'=\bm{\Omega}$ and $\bm{\Omega}$ is a sub-matrix of $\bm{\Sigma}$ corresponding to the bottom-level series.
-\end{theo}
-
-\begin{proof}
-   Since elliptical distributions are closed under affine transformations, and are closed under marginalisation, reconciliation of an elliptical distribution yields an elliptical distribution (although the unreconciled and reconciled distributions may be different members of the class of elliptical distributions).
-The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}_{opt}\hat{\bm{\Sigma}}\bm{G}_{opt}'\bm{S}'$, while the location matrix is given by $\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}+\bm{d}_{opt}$.
-The reconciled scale matrix is
-   \[
-     \tilde{\bm{\Sigma}}_{opt}
-       = \bm{S}{\bm{a}}\hat{\bm\Sigma}^{-1/2}\hat{\bm{\Sigma}}\left(\hat{\bm\Sigma}^{-1/2}\right)'{\bm{a}}'\bm{S}'
-       = \bm{S}\bm{\Omega}\bm{S}'
-       = \bm{\Sigma}.
-   \]
-   For the choices of $\bm{G}_{opt}$ and $\bm{d}_{opt}$ given above, the reconciled location vector is
-   \[
-     \tilde{\bm{\mu}}_{opt}= \bm{S}\bm{G}_{opt}\hat{\bm{\mu}}+\bm{\mu}-\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}
-   = \bm{\mu}.
-   \]
-\end{proof}
-
-A number of insights can be drawn from this theorem.
-First, although a linear function $g(.)$ can be used to recover the true predictive in the elliptical case, the same does not hold in general.
-Second, $g(.)$ is not, in general, a projection matrix.
-The conditions for which a the true predictive density can be recovered by a projection are given below.
-
-\begin{theo}[True predictive via projection]
-	Assume that the true predictive distribution is elliptical with location $\bm{\mu}$ and scale $\bm{\Sigma}$.
-Consider reconciliation via a projection $g(\bm{y})=(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\bm{y}$.
-The true predictive distribution can be recovered via reconciliation of an elliptical distribution with location $\hat{\bm{\mu}}$ and scale $\hat{\bm{\Sigma}}$  when the following conditions hold:
-	\begin{align}
-	sp(\hat{\bm\mu}-\bm{\mu})&\subset sp(\bm{R})\\
-    sp(\hat{\bm{\Sigma}}^{1/2}-\bm{\Sigma}^{1/2})&\subset sp(\bm{R})\\
-	\end{align}
-\end{theo}
-
-\begin{proof}
-	The reconciled location vector will be given by
-	\begin{align*}
-		\tilde{\bm{\mu}}&=\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\hat{\bm{\mu}}\\
-		&=\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\left(\hat{\bm{\mu}}+\bm{\mu}-\bm{\mu}\right)\\
-		&=\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\bm{\mu}+\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\left(\hat{\bm{\mu}}-\bm{\mu}\right).
-	\end{align*}
-  Since $\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}$ is a projection onto $\mathfrak{s}$ and $\bm{\mu}\in\mathfrak{s}$, the first term simplifies to $\bm{\mu}$.
-If $\bm{\mu}-\hat{\bm{\mu}}$ lies in the span of $\bm{R}$, then multiplication by $\bm{R}'_{\perp}$ reduces the second term to $\bm{0}$.
-By a similar argument it can be shown that $\tilde{\bm{\Sigma}}^{1/2}=\bm{\Sigma}^{1/2}$.
-The closure property of elliptical distributions under affine transformations ensures that the full true predictive distribution can be recovered.
-\end{proof}
-
-Although these conditions will rarely hold in practice and only apply to a limited class of distributions, they do provide some insight into selecting a projection for reconciliation.
-If the value of $\hat{\bm{\mu}}$ were equi-probable in all directions, then a projection orthogonal to $\mathfrak{s}$ would be a sensible choice for $\bm{R}$ since it would in some sense represent a `median' direction for $\bm{\mu}-\hat{\bm{\mu}}$.
-However, the one-step-ahead in-sample errors are usually correlated suggesting that $\hat{\bm{\mu}}$ is more likely to fall in some directions than others.
-Therefore an orthogonal projection after transformation by the inverse of the one-step-ahead in-sample error covariance matrix may be more intuitively appealing.
-This is exactly what the MinT projection provides, and as simulations will show in Section~\ref{sec:gaussian}, this projection leads to the best empirical results.
-
-%However, these expressions do provide some insight on why some choices for $\bm{G}$ in the point forecast reconciliation literature may also work well for probabilistic forecasts.
-To illustrate, first rearrange the equation for the optimal value of  $\bm{G}_{opt}={\bm\Omega}^{1/2}\hat{\bm\Sigma}^{-1/2}$ as ${\bm\Omega}^{1/2}=\bm{G}_{opt}\hat{\bm\Sigma}^{1/2}$.
-For arbitrary $\bm{G}\hat{\bm\Sigma}^{1/2}$ is an approximation for ${\bm\Omega}^{1/2}$.
-This approximation has similarities with the way bottom-level estimates are produced for point forecast reconciliation.
-Rather than mapping a vector of point forecasts to reconcilied bottom-level forecasts, the columns of  $\hat{\bm\Sigma}^{1/2}$ are mapped to an approximation of the columns of ${\bm\Omega}^{1/2}$.
-The value for $\tilde{\bm{\mu}}_{opt}$ includes a projection of $\hat{\bm{\mu}}$ onto $\mathfrak{s}$.
-While it is infeasible to obtain the translation $\bm{d}$, it is worthwhile noting that this measures the difference between the reconciled mean and true mean.
-
-\section{Evaluation of hierarchical probabilistic forecasts}\label{sec:evaluation}
-
-The necessary final step in hierarchical forecasting is to make sure that our forecast distributions are accurate.
-In general, forecasters prefer to maximize the sharpness of the forecast distribution subject to calibration \citep{Gneiting2014}.
-Therefore the probabilistic forecasts should be evaluated with respect to these two properties.
-
-Calibration refers to the statistical compatibility between probabilistic forecasts and realizations.
-In other words, random draws from a perfectly calibrated forecast distribution should be equivalent in distribution to the realizations.
-On the other hand, sharpness refers to the spread or the concentration of the predictive distributions and it is a property of the forecasts only.
-The more concentrated the forecast distributions, the sharper the forecasts \citep{Gneiting2008}.
-However, independently assessing the calibration and sharpness will not help to properly evaluate the probabilistic forecasts.
-Therefore we need to assess these properties simultaneously using scoring rules.
-
-Scoring rules are summary measures obtained based on the relationship between the forecast distributions and the realizations.
-In some studies, researchers take the scoring rules to be positively oriented, in which case the scores should be maximized \citep{Gneiting2007}.
-However, scoring rules have also been defined to be negatively oriented, and then the scores should be minimized \citep{Gneiting2014}.
-We follow the latter convention here.
-
-Let $P$ be a forecast distribution and let $Q$ be the true data generating process respectively.
-Furthermore let $\omega$ be a realization from $Q$.
-Then a scoring rule is a function $S(P,\omega)$ that maps $P,\omega$ to $\mathbb{R}$.
-It is a ``proper'' scoring rule if
-\begin{equation}\label{eq:(3.1.)}
-\E_{\bm{Q}}[S(Q,\omega)] \le \E_{\bm{Q}}[S(P,\omega)] ,
-\end{equation}
-where $\E_{Q}[S(P,\omega)]$ is the expected score under the true distribution $Q$ \citep{Gneiting2008, Gneiting2014}. When this inequality is strict, the scoring rule is said to be strictly proper.
-
-In the context of probabilistic forecast reconciliation there could be two motivations for using scoring rules.
-The first is to compare unreconciled densities to reconciled densities.
-Reconciliation itself is a valuable goal since it can be important in aligning decision making across, for example, different units of an enterprise.
-In the point forecasting literature, forecast reconciliation has also been shown to improve forecast performance \citep{AthEtAl2017, Wickramasuriya2017}.
-It will be worthwhile to see whether the same holds in the probabilistic forecasting case.
-The second motivation for using scoring rules is to compare two or more sets of reconciled probabilistic forecasts to one another.
-The objective here is to evaluate which reconciliation mapping $g(.)$ works best in practice.
-
-\subsection{Univariate scoring rules}
-
-One way to evaluate hierarchical probabilistic forecasts is via the application of univariate scoring rules to each variable in the hierarchy.
-A summary can be taken of the expected scores across each margin, for example a mean or median.
-In the simulations of Section~\ref{sec:gaussian}, we consider two such scoring rules.
-The log score is given by the log density, in this case for each margin of the probabilistic forecast.
-The cumulative rank probability score generalises mean square error and is given by
-\begin{align} \label{eq:CRPS}
-\text{CRPS}(\breve{F}_i,y_{i}) &=\int \left(\breve{F}_i(\breve{Y}_i)-\mathbb{1}(\breve{Y}_i<y_{i})\right)d\breve{Y}_i\\ &=\E_{\breve{Y}_i}|\breve{Y}_{i}-y_{i}| - \frac{1}{2}\E_{\breve{Y}_i}|\breve{Y}_{i}-\breve{Y}^*_{i}|\,,
-\end{align}
-where $\breve{F}_i$ is the cumulative distribution function of the $i$th margin of the probabilistic forecast, $\breve{Y}_i$ and $\breve{Y}^*_{i}$ are independent copies of a random variable with distribution $\breve{F}_i$, and $y_i$ is the outcome of the $i$th margin.
-The expectations in the second line can be approximated by Monte Carlo when a sample from the predictive distribution is available.
-
-An advantage to this approach is that it allows the forecaster to evaluate the levels and individual series of the hierarchy where the gains from reconciliation are greatest.
-For this reason this approach has been used in the limited literature on probabilistic forecasting for hierarchies \citep{BenTaieb2017, JeoEtAl2018} to date.
-A major shortcoming of this approach however, is that evaluating univariate scores on the margins does not account for the dependence in the hierarchy.
-
-\subsection{Multivariate scoring rules}
-
-While a number of alternative proper scoring rules are available for univariate forecasts, the multivariate case is somewhat more limited.
-Here we focus on three scoring rules: the log score (LS), the energy score (ES) and the variogram score (VS).
-
-The log score can be approximated using a sample of values from the probabilistic forecast density \citep{Jordan2017}; however it is more commonly used when a parametric form for the density is available for the probabilistic forecast.
-
-The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the following representation in terms of expectations
-\begin{equation}
-\text{ES}(\breve{\bm{Y}}_{T+h},\bm{y}_{T+h}) =
-\E_{\breve{\bm{Y}}}
-||\breve{\bm{Y}}_{T+h}-\bm{y}_{T+h}||^\alpha -\frac{1}{2}\E_{\breve{\bm{Y}}}||\breve{\bm{Y}}_{T+h}-\breve{\bm{Y}}^*_{T+h}||^\alpha, \,\, \alpha \in (0,2]\,, 
-\end{equation}
-lends itself to easy computation when samples from the probabilistic forecast are available.
-An interesting limiting case is where $\alpha=2$, where it can be easily shown that energy score simplifies to mean squared error around the mean of the predictive distribution.
-In this limiting case, the energy score is proper but not strictly proper.
-\citet{Pinson2013a} also argue that the energy score has low discriminative ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
-
-In contrast, \citet{SCHEUERER2015} have shown that the variogram score has a higher discrimination ability for misspecified means, variances and correlation structures than the energy score.
-When $\breve{\bm{y}}$ is a random variable from probabilistic forecast $\breve{F}$, the empirical variogram score is defined as
-\begin{equation}
-\text{VS}(\breve{F}, \bm{y}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{i} - y_{j}|^p - E_{\breve{Y}_i,\breve{Y}_j} |\breve{Y}_{i}-\breve{Y}_{j}|^p\right)^2.
-\end{equation}
-\citet{SCHEUERER2015} recommend using $p=0.5$.
-
-\subsubsection{Comparing unreconciled forecasts to reconciled forecasts}
-
-For both reconciled and unreconciled densities it is possible to obtain a density from the probability measures defined in Section~\ref{sec:definitions}.
-Therefore it may seem sensible to compare unreconciled densities to reconciled densities on the basis of log score.
-However, the following theorem shows that using the log score may fail in the case of multivariate distributions with a degeneracy.
-
-\begin{theo}[Impropriety of log score]
-	When the true data generating process is coherent, then the log score is improper with respect to the class of incoherent measures.
-\end{theo}
-
-\begin{proof}
-Consider a rotated version of hierarchical time series, $\bm{z}_t=\bm{U}\bm{y}_t$, so that the first $m$ elements of $\bm{z}_t$ denoted $\bm{z}^{(1)}_t$ are unconstrained, while the remaining $n-m$ elements denoted $\bm{z}^{(2)}_t$ equal $0$ when the aggregation constraints hold.
-An example of the $n\times n$ $\bm{U}$ is the matrix of left singular vectors of $\bm{S}$.
-
-Consider the case where the true predictive density is $f_1(\bm{z}^{(1)}_t)\mathbb{1}\left(\bm{z}^{(2)}_t=\bm{0}\right)$, and we evaluate an incoherent density given by $f_1(\bm{z}^{(1)}_t)f_2(\bm{z}^{(2)}_t)$, where $f_2$ is highly concentrated around $0$ but still non-degenerate.
-For example, $f_2$ may be Gaussian with variance $\sigma^2{\bm{I}}$ with $\sigma^2 < (2\pi)^{-1}$.
-The log score under the true data generating process is
-\[
-LS\left(f,\bm{z}^{(1)}_t\right) = -\log f_1\left(\bm{z}^{(1)}_t\right),
-\]
-while that of the unreconciled density is
-\begin{align}
-LS\left(\hat{f},\bm{z}^{(1)}_t\right) &= -\log f_1(\bm{z}^{(1)}_t)-f_2(\bm{z}^{(1)}_t)\\
-&= -\log f_1(\bm{z}^{(1)}_t)+\frac{n-m}{2}\log(2\pi\sigma^2)\\
-&<-\log f_1(\bm{z}^{(1)}_t)=LS\left(f,\bm{z}^{(1)}_t\right).
-\end{align}
-After taking expectations $E\left[LS(f,f)\right] > E\left[LS(\hat{f},f)\right]$, violating the condition in Equation~\eqref{eq:(3.1.)} for a proper scoring rule.
-\end{proof}
-
-A similar issue also arises when discrete random variables are modelled as if they were continuous, an issue discussed in Section~4.1 of \citet{Gneiting2007}.
-This implies that the log score should be avoided when comparing reconciled and unreconciled probabilistic forecasts.
-
-\subsubsection{Comparing reconciled forecasts to one another}
-
-Coherent probabilistic forecasts can be completely characterised in terms of basis series; if a probabilistic forecast is available for the basis series, then a probabilistic forecast can be recovered for the entire hierarchy via Definition~\ref{def:cohprob}.
-This may suggest that it is adequate to merely compare two coherent forecasts to one another using the basis series only.
-We now show how this depends on the specific scoring rule used.
-
-For the log score, suppose the coherent probabilistic forecast has density $f(\bm{b})$.
-The density for the full hierarchy is given by $f(\bm{y})=f(\bm{Sb})=f(\bm{b})J^{-1}$, where $J=\prod_{j=1}^{m}\lambda_j$ is a pseudo-determinant of the non-square matrix $\bm{S}$ and $\lambda_j$ are the non-zero singular values of $\bm{S}$.
-Therefore for any coherent density, the log score of the full hierarchy differs from the log score for the bottom-level series by the term $log(J)$.
-This term depends only on the structure of the hierarchy and is fixed across different reconciliation methods.
-Therefore if one method achieves a lower expected log score compared to an alternative method using the bottom-level series only, the same ordering is preserved when an assessment is made on the basis of the full hierarchy.
-
-The same property does not hold for all scores in general.
-For example, the energy score can be expressed in terms of expectations of norms.
-In general, since norms are invariant under orthogonal rotations, the energy score is also invariant under orthogonal transformations \citep{Szekely2013,Gneiting2007}.
-In the context of two coherent forecasts, the same is true of a semi-orthogonal transformation from a lower dimensional basis series to the full hierarchy.
-However, when $\bm{S}$ is the usual summing matrix, it is not semi-orthogonal.
-Therefore the energy score computed on the bottom-level series will differ from the energy score computed using the full hierarchy and the ordering of different reconciliation methods may change depending on the basis series used.
-In this case we recommend computing the energy score using the full hierarchy.
-Although the discussion here is related to energy score, the same logic holds for other multivariate scores, for example the variogram score.
-
-The properties of multivariate scoring rules in the context of evaluating reconciled probabilistic forecasts are summarised in Table~\ref{tab:prop}.
-
-\begin{table}
-	\centering
-	\begin{tabular}{rll}
-	& Coherent v Incoherent &Coherent v Coherent\\
-	\hline
-	Log Score & Not proper & Ordering preserved if compared using\\ &&bottom-level only\\
-	Energy/ & Proper & Full hierarchy should be used\\
-	Variogram Score & Proper & Full hierarchy should be used\\
-	\hline
-    \end{tabular}
-	\caption{Summary of properties of scoring rules in the context of reconciled probabilistic forecasts.}
-	\label{tab:prop}
-\end{table}
-
-\section{Simulation study}\label{sec:gaussian}
-
-We now turn our attention to comparing different reconciliation methods in a simulation study where the data is conditionally Gaussian.
-We choose the Gaussian case due to its analytical tractability which allows for evaluation using all scoring rules (including the log score).
-The non-Gaussian case lies beyond the scope of this simulation study.
-
-For the data generating process, we consider the hierarchy given in Figure~\ref{fig1}, comprising two aggregation levels with four bottom-level series.
-Each bottom-level series will be generated first, and then summed to obtain the data for the upper-level series.
-In practice, hierarchical time series tend to contain much noisier series at lower levels of aggregation.
-In order to replicate this feature in our simulations, we follow the data generating process proposed by \citet{Wickramasuriya2017}.
-
-First $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from ARIMA$(p,d,q)$ processes, where $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability.
-The errors driving these ARIMA processes are jointly normal, and denoted by $\{\varepsilon_{AA,t},\varepsilon_{AB,t},\varepsilon_{BA,t},\varepsilon_{BB,t}\} \overset{iid}{\sim} \mathcal{N}(\bm{0}, \bm{\Sigma})~\forall t$.
-The parameters for the AR and MA components are randomly and uniformly generated from $[0.3,0.5]$ and $[0.3,0.7]$ respectively.
-Then the bottom-level series $\{y_{AA,t},y_{AB,t},y_{BA,t},y_{BB,t}\}$ are given by:
-\begin{align*}
-y_{AA,t} &= w_{AA,t} + u_t - 0.5v_t,\\
-y_{AB,t} &= w_{AB,t} - u_t - 0.5v_t,\\
-y_{BA,t} &= w_{BA,t} + u_t + 0.5v_t,\\
-y_{BB,t} &= w_{BB,t} - u_t + 0.5v_t,
-\end{align*}
-where $u_t \sim \mathcal{N}(0,\sigma^2_u)$ and $v_t \sim \mathcal{N}(0,\sigma^2_v)$. The aggregate series in the middle-level are given by:
-\begin{align*}
-y_{A,t} &= w_{AA,t} + w_{AB,t} - v_t,\\
-y_{B,t} &= w_{BA,t} + w_{BB,t} + v_t,
-\end{align*}
-and the total series is given by
-\[
-  y_{Tot,t} = w_{AA,t} + w_{AB,t} + w_{BA,t} + w_{BB,t}.
-\]
-To ensure the disaggregate series are noisier than the aggregate series, we choose $\bm{\Sigma}, \sigma^2_u$ and $\sigma^2_v$ such that
-\[
-  \var(\varepsilon_{AA,t} + \varepsilon_{AB,t} + \varepsilon_{BA,t} + \varepsilon_{BB,t})
-  \le \var(\varepsilon_{AA,t}+\varepsilon_{AB,t}-v_t)
-  \le \var(\varepsilon_{AA,t}+u_t-0.5v_t)\,,
-\]
-and similar inequalities hold when $\varepsilon_{AA,t}$ is replaced by $\varepsilon_{AB,t}$, $\varepsilon_{BA,t}$ and $\varepsilon_{BB,t}$ in the third term.
-The values of $\bm{\Sigma}$, $\sigma^2_u$ and $\sigma^2_v$ that we use and which satisfy these constraints are $\sigma^2_u = 19$, $\sigma^2_u = 18$ and
-\[
-\bm{\Sigma} =
-\begin{pmatrix}
-5.0 & 3.1 & 0.6 & 0.4 \\
-3.1 & 4.0 & 0.9 & 1.4 \\
-0.6 & 0.9 & 2.0 & 1.8 \\
-0.4 & 1.4 & 1.8 & 3.0 \\
-\end{pmatrix}\,.
-\]
-
-We generate data with a sample size of $T=501$.
-Univariate ARIMA models are selected for each series using the \textit{auto.arima} function in the \textit{forecast} package \citep{hyndman2017forecasting} in R \citep{Rcore}.
-The same package was used to fit each series independently using the first 500 observations, and evaluate 1-step ahead base (incoherent) probabilistic forecasts.
-These were then reconciled using different projections summarised in Table~\ref{table:2}.
-This process was replicated using $1000$ different data sets from the same data generating processes.
-
-To assess the predictive performance of different forecasting methods, we use scoring rules as discussed in Section~\ref{sec:evaluation}.
-To facilitate comparisons, we report skill scores \citep{Gneiting2007}.
-For a given forecasting method, evaluated by a particular scoring rule, the skill score
-gives the percentage improvement of the preferred forecasting method relative to a reference method.
-A negative valued skill score indicates that a method is worse than the reference method, whereas any positive value indicates that the method is superior to the reference method.
-
-Table~\ref{table:3} summarizes the forecasting performance of unreconciled, bottom-up, OLS, WLS and two MinT reconciliation methods using log score, energy score and variogram score.
-In all cases skill scores are calculated with the bottom-up method as reference.
-All log scores are evaluated on the basis of bottom-level series only, however these only differ from the log scores for the full hierarchy by a fixed constant.
-The cell for log score of unreconciled forecasts is left blank since the log score is not proper in this context.
-Overall, the MinT methods provide the best performance irrespective of the scoring rule, and all methods that reconcile using information at all levels of the forecast improve upon unreconciled forecasts.
-Bottom-up forecasts perform even worse than unreconciled forecasts in some cases.
-
-Tables~\ref{table:4} and~\ref{table:5} break down the forecasting performance of different reconciliation methods by considering univariate scores on each individual margin.
-Tables~\ref{table:4} summarises results for the top and middle-level, Table~\ref{table:5} does the same for bottom-level.
-The log score and CRPS are considered, while skill scores are computed with the unreconciled forecast as a reference.
-When broken down in this fashion, the methods based on MinT perform best for all series and always outperform bottom-up and unreconciled forecasts.
-
-\begin{table}
-	\caption{Comparison of coherent forecasts.
-``Energy score'' and ``Variogram score'' columns give scores based on the joint forecast distribution of the whole hierarchy.
-``Log score'' column gives the log scores of the joint forecast distribution of the bottom-level.
-``Skill score'' columns give the percentage skill score with reference to the bottom-up method.
-Entries in these columns show the percentage increase of scores for different reconciliation methods relative to the bottom-up method.}\label{table:3}
-
-	\centering\small
-	\begin{tabular}{@{}lSSSSSS@{}}
-		\toprule
-		Forecasting &
-		\multicolumn{2}{c}{\text{Energy score}} &
-		\multicolumn{2}{c}{\text{Variogram score}} &
-		\multicolumn{2}{c}{\text{Log score}} \\
-		\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(l){6-7}
-		method &
-		\text{Mean score} & \text{Skill score \%} &
-		\text{Mean score} & \text{Skill score \%} &
-		\text{Mean score} & \text{Skill score \%}\\
-		\midrule
-		MinT(Shrink) &  10.03 & 18.79  & 8.44  & 8.46 & 11.30 &  6.22 \\
-		MinT(Sample) &  10.01 & 18.95  & 8.41  & 8.79 & 11.29 &  6.31 \\
-		MinT(WLS)    &  10.53 & 14.74  & 9.02  & 2.17 & 12.61 & -4.65 \\
-		OLS          &  10.53 & 14.74  & 8.86  & 3.09 & 11.54 &  4.23\\
-		Bottom-up    &  12.35 &    	   & 9.22  &      & 12.05 &  \\
-		Incoherent	 &  11.12 &   	   & 9.53  &      &       &  \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{table}
-	\caption{Comparison of incoherent vs coherent forecasts based on the univariate forecast distribution of aggregate series.
-The ``Incoherent'' row shows the average scores for incoherent forecasts.
-Each entry above this row represents the percentage skill score with reference to the incoherent forecasts.
-These entries show the percentage increase in score for different forecasting methods relative to the incoherent forecasts.}\label{table:4}
-	\centering\small
-	\begin{tabular}{@{}lSSSSSS@{}}
-		\toprule
-		Forecasting &
-		\multicolumn{2}{c}{\text{Total}} &
-		\multicolumn{2}{c}{\text{Series - A}} &
-		\multicolumn{2}{c}{\text{Series - B}} \\
-		\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(l){6-7}
-		method      &  CRPS   & LogS    & CRPS   & LogS     & CRPS   & LogS     \\
-		\midrule
-		MinT(Shrink) &   0.74  &   0.00   & 10.49   &  3.24  &  9.16  &  2.73    \\
-		MinT(Sample) &   0.74  &   0.00   & 10.49   &  3.24  &  9.16  &  2.73    \\
-		MinT(WLS)    &  -2.96  &  -2.36   &  6.10   & -4.12  &  5.66  & -3.03    \\
-		OLS          &  -9.26  &  -3.36   &  7.07   &  2.06  &  7.01  &  1.82    \\
-		Bottom-up    & -91.48  & -22.22   & -8.05   & -2.06  & -6.20  & -1.82    \\
-		\midrule
-		\textit{Incoherent} & $\mathbi{2.70}$ & $\mathbi{2.97}$ & $\mathbi{4.10}$ & $\mathbi{3.40}$ & $\mathbi{3.71}$ & $\mathbi{3.30}$ \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{table}
-	\caption{Comparison of incoherent vs coherent forecasts based univariate forecast distribution of bottom-level series.
-The ``Incoherent'' row shows the average scores for incoherent forecasts.}\label{table:5}
-	\centering\tabcolsep=0.08cm\small
-	\begin{tabular}{@{}lSSSSSSSS@{}}
-		\toprule
-		Forecasting &
-		\multicolumn{2}{c}{\text{Series - AA}} &
-		\multicolumn{2}{c}{\text{Series - AB}} &
-		\multicolumn{2}{c}{\text{Series - BA}} &
-		\multicolumn{2}{c}{\text{Series - BB}} \\
-		\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(l){8-9}
-		method       & CRPS   & LogS    & CRPS   & LogS    & CRPS   & LogS    & CRPS   & LogS \\
-		\midrule
-		MinT(Shrink) &  7.61  &  2.43  &  10.82  &  3.02  &  5.93  &  1.86  &  7.76  & 2.47  \\
-		MinT(Sample) &  7.88  &  2.43  &  11.08  &  3.02  &  6.20  &  1.86  &  8.05  & 2.47  \\
-		MinT(WLS)    &  3.53  &  0.00  &   6.33  &  0.60  &  2.43  & -0.62  &  4.89  & 0.62  \\
-		OLS          &  2.99  &  0.91  &   5.28  &  1.51  &  2.90  &  0.62  &  4.31  & 1.23  \\
-		\midrule
-		\textit{Incoherent} & $\mathbi{3.68}$ & $\mathbi{3.29}$ & $\mathbi{3.79}$ & $\mathbi{3.31}$ & $\mathbi{3.45}$ & $\mathbi{3.22}$ & $\mathbi{3.48}$ & $\mathbi{3.24}$ \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\section{Conclusions}\label{sec:conclusions}
-
-%Although the problem of hierarchical point forecasts is well studied in the literature, there is a lack of attention in the context of probabilistic forecasts.
-Thus we attempted to fill this gap in the literature by providing substantial theoretical background to the problem.
-
-By redefining coherent forecasts and forecast reconciliation in geometric terms, we have established two new theoretical results that support the use of projections for point forecast reconciliation, and have allowed us to extend these concepts to probabilistic forecasting.
-We have shown that for elliptical distributions the true predictive density can be recovered by linear reconciliation and we have established conditions for when this is a projection.
-Although this projection cannot feasibly be obtained in practice, a projection similar to the MinT procedure provides a good approximation in applications.
-This is supported by the results of a simulation study.
-Finally, we have also discussed strategies for evaluating probabilistic forecasts for hierarchical time series advocating the use of multivariate scoring rules on the full hierarchy, while establishing a key result regarding the impropriety of the log score with respect to incoherent forecasts.
-
-In many ways this paper sets up a substantial future research agenda.
-For example, having defined what amounts to an entire class of reconciliation methods for probabilistic forecasts it will be worthwhile investigating which specific projections are optimal.
-This is likely to depend on the specific scoring rule employed as well as the properties of the base forecasts.
-Another avenue worth investigating is to consider whether it is possible to recover the true predictive distribution for non-elliptical distributions via a non-linear function $g(.)$.
+	\section{Conclusions}
 

### 2019-04-11 Hierarchical-forecast-reconciliation/SimulationStudy/Results/Simulation results.tex
Outlined first two papers

--- 2018-08-24 ProbabilisticCoherence.tex
@@
-%&latex
-\documentclass[12pt]{article}
-\usepackage{amsmath}
-\usepackage{graphicx,psfrag,epsf}
-\usepackage{enumerate}
-\usepackage{natbib}
-\usepackage{url} % not crucial - just used below for the URL
-
-\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
+\documentclass[a4paper, 11pt]{article}
+%\usepackage{monashwp}
+\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx}
 \usepackage{mathrsfs, float, booktabs,todonotes,amsthm}
@@
 \usepackage{amsfonts}
-
-\pdfminorversion=4
-% NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{1}
-
-% DON'T change margins - should be 1 inch all around.
-\addtolength{\oddsidemargin}{-.5in}%
-\addtolength{\evensidemargin}{-.5in}%
-\addtolength{\textwidth}{1in}%
-\addtolength{\textheight}{-.3in}%
-\addtolength{\topmargin}{-.8in}%
-
-\DeclareMathOperator*{\argmin}{arg\,min}
+%\DeclareNameAlias{sortname}{last-first}
+%\DeclareMathOperator*{\argmin}{arg\,min}
 \newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type
@@
 \def\E{\text{E}}
-\def\var{\text{Var}}
-
-\def\PQ{\begin{pmatrix}\bm{G}\\[-0.2cm]\bm{H}\end{pmatrix}}
-\def\bt{\begin{pmatrix}\tilde{\bm{b}}\\[-0.2cm]\tilde{\bm{a}}\end{pmatrix}}
-
-%\theoremstyle{theo}
-\newtheorem{theo}{Theorem}[section]
-
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
+%\mathtoolsset{showonlyrefs=true}
 
@@
 
-	%\bibliographystyle{natbib}
-
-	\def\spacingset#1{\renewcommand{\baselinestretch}%
-		{#1}\small\normalsize} \spacingset{1}
-
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-	\if1\blind
-	{
-		\title{\bf Probabilistic Forecasts in Hierarchical~Time~Series}
-		        \author{Puwasala Gamakumara\thanks{
-		        The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.  We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
-			    Department of Econometrics and Business Statistics,\\
-			    Monash University,\\ VIC 3800, Australia.\\
-			    Email: Puwasala.Gamakumara@monash.edu \\
-			    and \\
-			    Anastasios Panagiotelis\\
-			    Department of Econometrics and Business Statistics,\\
-		    	Monash University,\\ VIC 3800, Australia.\\
-			    Email: Anastasios.Panagiotelis@monash.edu \\
-			    and \\
-		        George Athanasopoulos\\
-		        Department of Econometrics and Business Statistics,\\
-		        Monash University,\\ VIC 3800, Australia.\\
-		        Email: george.athanasopoulos@monash.edu \\
-		        and \\
-	            Rob J Hyndman\\
-	            Department of Econometrics and Business Statistics,\\
-	            Monash University,\\ VIC 3800, Australia.\\
-	            Email: rob.hyndman@monash.edu \\}
-		\maketitle
-	} \fi
-
-	\if0\blind
-	{
-		\bigskip
-		\bigskip
-		\bigskip
-		\begin{center}
-			{\LARGE\bf Probabilistic Forecasts in Hierarchical~Time~Series}
-		\end{center}
-		\medskip
-	} \fi
-
-	\bigskip
-
-\begin{abstract}
-  Forecast reconciliation involves adjusting forecasts to ensure coherence with aggregation constraints.
-We extend this concept from point forecasts to probabilistic forecasts by redefining forecast reconciliation in terms of linear functions in general, and projections more specifically.
-New theorems establish that the true predictive distribution can be recovered in the elliptical case by linear reconciliation, and general conditions are derived for when this is a projection.
-A geometric interpretation is also used to prove two new theoretical results for point forecasting; that reconciliation via projection both preserves unbiasedness and dominates unreconciled forecasts in a mean squared error sense.
-Strategies for forecast evaluation based on scoring rules are discussed, and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive distribution coheres with aggregation constraints.
-Finally, evidence from a simulation study shows that reconciliation based on an oblique projection, derived from the MinT method of \citet{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
-\end{abstract}
-
-\noindent%
-{\it Keywords:}  Forecast Reconciliation, Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
-\vfill
-
-\newpage
-\spacingset{1.45} % DON'T change the spacing!
-
-\section{Introduction}\label{sec:intro}
-
-Large collections of time series often follow some aggregation structure.
-For example, the electricity demand of a country can be disaggregated according to a geographic hierarchy of states, cities, and individual households.
-To ensure aligned decision making, it is important that forecasts at the most disaggregated level add up to forecasts at more aggregated levels.
-This property is called ``coherence''.
-On the other hand ``reconciliation'' is a process whereby incoherent forecasts are made coherent.
-Both of these concepts have been developed extensively for point forecasting.
-Generalising both of these concepts, particularly the latter, to probabilistic forecasting is a gap that we seek to address in this work.
-We do so by first providing a novel geometric interpretation to coherence and reconciliation in the point forecasting case.
-This can easily be generalised to probabilistic forecasting allowing us to derive further results for elliptical distributions as well as provide insight into forecast evaluation via multivariate  scoring rules.
-
-Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level of the hierarchy.
-To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$ and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.
-In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (series $AA$, $AB$, $BA$ and $BB$) and then summed to recover forecasts for all higher-level series.
-Alternatively, in the top-down approach \citep{Gross1990}, a top-level forecast is first produced (series $Tot$) and bottom-level forecasts are recovered by disaggregating the forecast using either historical or forecasted proportions.
-A middle-out approach is a hybrid between these two, that for the hierarchy in Figure~\ref{fig1} would produce first stage forecasts for series $A$ and $B$.
-
-\begin{figure}[H]
-	\begin{center}
-		\leaf{AA} \leaf{AB}
-		\branch{2}{A}
-		\leaf{BA} \leaf{BB}
-		\branch{2}{B}
-		\branch{2}{Tot}
-		\qobitree
-	\end{center}
-	\caption{An example of a two level hierarchical structure.}\label{fig1}
-\end{figure}
-
-In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular.
-For these methods, first stage forecasts are independently produced for all series rather than series at a single level.
-Since these so-called `base' forecasts are rarely coherent in practice, they are subsequently adjusted or `reconciled' to ensure coherence.
-Note that we use coherence and reconciliation as distinct terms, in contrast to their at times ambiguous usage in the past.
-To date, reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators.
-These include Ordinary Least Squares {OLS} \citep{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix.
-These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{AthEtAl2009,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and, in some sense, hedge against the risk of model misspecification at a single level.
-
-A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \citep[see][and references therein]{Gneiting2014}.
-Indeed to the best of our knowledge, the (as yet unpublished) work of \citep{BenTaieb2017} is the only paper to deal with coherent probabilistic forecasts, and although they reconcile the means of the predictive distributions, the overall distributions are constructed in a bottom-up fashion rather than use a reconciliation process.
-In contrast, the main objective of our paper is to generalise both coherence and reconciliation from point to probabilistic forecasting.
-
-To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections.
-In addition to being highly intuitive, this allows us to establish a number of theoretical results.
-We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts, while the second shows that reconciled forecasts dominate unreconciled forecasts via the distance reducing property of projections.
-We provide definitions of coherence and forecast reconciliation in the probabilistic setting, and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation.
-We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class.
-We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly estimated in practice, we provide a heuristic argument in favour of MinT reconciliation.
-
-We also cover the topic of forecast evaluation of probabilistic forecasts via scoring rules.
-In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.
-Therefore we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts.
-Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.
-
-The remainder of the paper is structured as follows.
-In Section~\ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.
-Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results.
-In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules, while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian}.
-Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.
-
-\section{Coherent forecasts}\label{sec:definitions}
-
-\subsection{Notation and preliminaries}\label{sec:notation}
-
-A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables.
-We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$.
-The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.
-The hierarchical structure of the data implies that
-\begin{equation}
-\bm{y}_t = \bm{Sb}_t,
-\end{equation}
-where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints, holds for all $t$.
-
-To clarify these concepts consider the example of the hierarchy in Figure~\ref{fig1}.
-For this hierarchy, $n=7$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$ and
-\[
-  \bm{S} = \begin{pmatrix}
-               1 & 1 & 1 & 1  \\
-               1 & 1 & 0 & 0 \\
-               0 & 0 & 1 & 1 \\
-               & \multicolumn{2}{c}{\bm{I}_4} &
-           \end{pmatrix},
-\]
-where $\bm{I}_4$ is the $4\times 4$ identity matrix.
-
-While most applications of hierarchical time series to date have involved data that respect an aggregation structure, in principle the matrix ${\bm S}$ can encode any linear constraints including weighted sums or even cases where some variables in the hierarchy are formed by taking the difference of two other variables.
-
-\subsection{Coherent point forecasts}\label{sec:cohpointf}
-
-It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect inherent aggregation constraints.
-We follow other authors \citep{Wickramasuriya2017, FPP2018} in using the nomenclature \emph{coherence} to describe this property.
-We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem, thus facilitating the development of probabilistic forecast reconciliation in Section~\ref{sec:reconciliation}.
-
-\begin{definition}[Coherent subspace]\label{def:cohspace}
- The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$, is defined as the \emph{coherent space}.
-\end{definition}
-
-It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$.
-Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.
-
-\begin{figure}[H]
-  \begin{center}
-    \begin{tikzpicture}[
-    >=stealth,
-    bullet/.style={
-      fill=black,
-      circle,
-      minimum width=1.5cm,
-      inner sep=0pt
-    },
-    projection/.style={
-      ->,
-      thick,
-      label,
-      shorten <=2pt,
-      shorten >=2pt
-    },
-    every fit/.style={
-      ellipse,
-      draw,
-      inner sep=0pt
-    }
-    ]
-    \node at (2,3) {$s$};
-    \node at (0,5) {$\mathbb{R}^m$(domain of $s$)};
-    \node at (4,5) {$\mathbb{R}^n$(codomain of $s$)};
-    \node at (4.7,2.0) {$\mathfrak{s}$(image of $s$)};
-    %\node[bullet,label=below:$f(x)$] at (4,2.5){};
-    \draw (0,2.5) ellipse (1.02cm and 2.2cm);
-    \draw (4,2.5) ellipse (1.02cm and 2.2cm);
-    \draw (4,2.5) ellipse (0.51cm and 1.1cm);
-    \draw[projection, label=below:$f$] (0.3,2.5) -- (3.8,2.5) ;
-    \end{tikzpicture}
-  \end{center}
-  \caption{The domain, codomain and image of the mapping $s$.}\label{fig2}
-\end{figure}
-
-\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
-  Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a point forecast of the values of all series in the hierarchy at time $t+h$, made using information up to and including time $t$.
-Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathfrak{s}$.
-\end{definition}
-
-\subsection{Coherent probabilistic forecasts}\label{sec:cohprobf}
-
-Let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple, where $\mathscr{F}_{\mathbb{R}^m}$ is the usual Borel $\sigma$-algebra on $\mathbb{R}^m$.
-Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_{\mathfrak{s}}$.
-Here $\mathscr{F}_{\mathfrak{s}}$ is a collection of sets $s(\mathcal{B})$, where $s(\mathcal{B})$ denotes the image of the set $\mathcal{B}\in \mathscr{F}_{\mathbb{R}^m}$ under the mapping $s(.)$.
-
-\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
-  The measure $\breve{\nu}$ is coherent if it has the property
-  \[
-    \breve{\nu}(s(\mathcal{B})) = \nu(\mathcal{B}) \quad \forall \mathcal{B} \in \mathscr{F}_{\mathbb{R}^m},
-  \]
-\end{definition}
-
-A probabilistic forecast for time $t+h$ is coherent if uncertainty in $\bm{\breve{y}}_{t+h}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.
-
-These definitions of the coherent space $\mathfrak{s}$, coherent point and coherent probabilistic forecasts in terms of the mapping $s(.)$, may give the impression that the bottom-level series play an important role.
-However, alternative definitions could be formed using any set of basis vectors that span $\mathfrak{s}$.
-For example, consider the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$.
-In this case the matrix $\bm{S}$ has columns $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$, and pre-multiplying by $\bm{S}$ transforms arbitrary values of $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy.
-However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy.
-The definitions above could be made in terms of any series and not just the bottom-level series.
-In general, we call the series (or linear combinations thereof) used in the definitions of coherence \textit{basis series}.
-Unless stated otherwise, we will always assume that the basis series are the bottom-level series as in Definition~\ref{def:cohpoint} and Definition~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.
-
-To the best of our knowledge, the only other definition of coherent probabilistic forecasts is given by \citet{BenTaieb2017} who define coherent probabilistic forecasts in terms of convolutions.
-According to their definition, probabilistic forecasts are coherent when a convolution of forecast distributions of disaggregate series is identical to the forecast distribution of the corresponding aggregate series.
-Their definition is consistent with our definition; our reason for providing a different definition is that the geometric understanding of coherence will facilitate our definitions of point and probabilistic forecast reconciliation to which we now turn our attention.
-
-\section{Forecast reconciliation}\label{sec:reconciliation}
-
-As discussed, reconciliation is distinct from coherence, since the former refers to a process whereby incoherent forecasts are made coherent.
-Although reconciliation methods for point forecasts are extant in the literature they are rarely defined explicitly.
-We do so here in slightly more general terms than usual.
-We then extend this idea to the novel concept of probabilistic reconciliation.
-
-\subsection{Point forecast reconciliation}
-
-Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ conditional on information up to and including time $t$.
-We now introduce a linear function that converts unreconciled forecasts into new bottom level forecasts.
-Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively, and let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})=\bm{G}\bm{y}+\bm{d}$.
-A composition of $g$ and $s(.)$ gives the following definition for point forecast reconciliation.
-
-\begin{definition}\label{def:reconpoint}
-	The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $g(.)$ iff
-	\begin{equation}
-	  \tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{G}\hat{\bm{y}}_{t+h|t}+\bm{d})\,.
-	\end{equation}
-\end{definition}
-
-Several choices of $g(.)$ currently extant in the literature, including the OLS, WLS and MinT methods, are special cases where $s\circ g$ is a projection.
-These can be defined so that $\bm{G}=({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ and $\bm{d}=\bm{0}$, were, ${\bm{R}_{\perp}}$ is a $n\times m$ orthogonal complement to an $n \times (n-m)$ matrix $\bm{R}$, where the columns of the latter span the null space of $\mathfrak{s}$.
-For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
-In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
-For this three variable hierarchy, $\bm{R}_\perp'=\bm{S}$ and reconciliation corresponds to the OLS method.
-For the case where $\bm{R}_\perp'\neq\bm{S}$, for example WLS and MinT, there are two possible interpretations.
-One is that these are oblique projections in Euclidean space where the columns of $\bm{R}$ are `directions' along which incoherent point forecasts are projected onto the coherent space $\mathfrak{s}$.
-Alternatively, since $\bm{R}_\perp'$ is usually written in the form $\bm{S}'{\bm{W}}^{-1}$, these projections can be thought of as orthogonal projections after pre-multiplying by ${\bm{W}^{-1/2}}$.
-A schematic providing a geometric interpretation of point reconciliation is given in Figure~\ref{fig:pointfr_sch}, while Table~\ref{table:2} summarises existing reconciliation methods.
-
-\begin{table}[!h]
-	\caption{Summary of reconciliation methods that are projections.
-Here, $\hat{\bm{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, $\hat{\bm{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}, $\hat{\bm{W}}^{wls}$ is the diagonal matrix with diagonal elements $w_{ii}$, and $\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$, where $w_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{W}}^{sam}$.}\label{table:2}
-	\centering
-	\begin{tabular}{lll}
-		\toprule
-		\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
-		\midrule
-		OLS             &
-		$\bm{I}$  &
-		$\bm{S}'$  \\
-		MinT(Sample)    &
-		$\hat{\bm{W}}^{sam}$ &
-		$\bm{S}'(\hat{\bm{W}}^{sam})^{-1}$ \\
-		MinT(Shrink)    &
-		$\tau\text{Diag}(\hat{\bm{W}}^{sam}) + (1-\tau)\hat{\bm{W}}^{sam}$ &
-		$\bm{S}'(\hat{\bm{W}}^{shr})^{-1}$ \\
-		WLS       &
-		$\text{Diag}(\hat{\bm{W}}^{shr})$ &
-		$\bm{S}'(\hat{\bm{W}}^{wls})^{-1}$ \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{figure}
-	\input{Figs/pointforerec_schematic.tex}
-	\caption{Summary of probabilistic point reconciliation.
-The mapping $s\circ g$ projects the unreconciled forecast $\hat{\bm{y}}_{t+h|h}$ onto $\mathfrak{s}$, yielding the reconciled forecast $\tilde{\bm{y}}_{t+h|h}$ with subscripts dropped in the figure for ease of presentation.
-Since the smallest hierarchy involves three dimensions, this figure is only a schematic.}\label{fig:pointfr_sch}
-\end{figure}
-
-The columns of $\bm{S}$ and $\bm{R}$ provide a basis for $\mathbb{R}^n$.
-Therefore any incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$.
-Let $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$ respectively, after a change of basis.
-The process of reconciliation involves setting the values of the reconciled bottom-level series to be $\tilde{\bm{b}}_{t+h|t}$, and ignoring $\tilde{\bm{a}}_{t+h|t}$ to ensure coherence.
-From properties of linear algebra it follows that
-\[
-  \hat{\bm{y}}_{t+h|t} = (\bm{S} ~ \bm{R})
-  \begin{pmatrix}
-  \tilde{\bm{b}}_{t+h|t}\\ \tilde{\bm{a}}_{t+h|t}
-  \end{pmatrix}= \bm{S}\tilde{\bm{b}}_{t+h|t} + \bm{R}\tilde{\bm{a}}_{t+h|t},
-\]
-while the reconciled point forecast is
-\[
-  \tilde{\bm{y}}_{t+h|t} = \bm{S}\tilde{\bm{b}}_{t+h|t}.
-\]
-
-In order to find $\tilde{\bm{b}}_{t+h|t}$ we require the inverse $(\bm{S} ~ \bm{R})^{-1}$ which is given by
-\begin{equation}
-(\bm{S} ~ \bm{R})^{-1} = \begin{pmatrix}
-(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
-\end{pmatrix}\,,
-\end{equation}
-where $\bm{S}_{\bot}$ is the orthogonal complements of $\bm{S}$.
-Thus it follows that $\tilde{\bm{b}}_{t+h|t}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$.
-Here $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ corresponds to $\bm{G}$ as defined previously.
-
-Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$.
-For example OLS minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$, while \citet{Wickramasuriya2017} show that MinT minimises the Mahalonobis distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$.
-Bottom-up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom-level series.
-Therefore bottom-up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.
-
-Before generalising the concept of point reconciliation to probabilistic forecasts, we state two theorems that motivate the use of projections for point forecast reconciliation.
-First, let $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ and assume $\hat{\bm{y}}_{t+h|t}$ is an unbiased prediction; that is $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\mu_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
-
-\begin{theo}[Unbiasedness preserving property]
-  For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also an unbiased prediction as long as $s\circ g$ is a projection.
-\end{theo}
-\begin{proof}
-	The expected value of the reconciled forecast is given by
-	\[
-  	\E_{1:t}(\tilde{\bm{y}}_{t+h|t})
-	  = \E_{1:t}(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t})
-  	= \bm{S}\bm{G}\E_{1:t}(\hat{\bm{y}}_{t+h|t})
-    = \bm{S}\bm{G}\bm{\mu}_{t+h|t}.
-	\]
-	Since the aggregation constraints hold for the true data generating process, $\bm{\mu}_{t+h|t}$ must lie in $\mathfrak{s}$.
-If $\bm{S}\bm{G}$ is a projection, then it is equivalent to the identity map for all vectors that lie in its range.
-Therefore $\bm{S}\bm{G}\bm{\mu}_{t+h|t}=\bm{\mu}_{t+h|t}$ when $\bm{S}\bm{G}$ is a projection matrix.
-\end{proof}
-We note the same result does not hold for general $g$ even when the range of $s\circ g$ is $\mathfrak{s}$.
-Now let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$, and let $\|\bm{v}\|_2$ be the $L_2$ norm of vector $\bm{v}$.
-The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.
-
-\begin{theo}[Distance reducing property]
-	If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
-	  \begin{equation}
-	    \|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2.
-	  \end{equation}
-\end{theo}
-\begin{proof}
-	Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ whenever $\bm{S}\bm{G}$ is a projection. Therefore
-	\begin{align}
-	\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
-	&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\\
-	\end{align}
-	The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators \citep{Hun2001}, therefore
-	 \begin{equation*}
-	 \|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le
-	 \|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
-	 \end{equation*}
-\end{proof}
-The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.
-
-\subsection{Probabilistic forecast reconciliation}
-
-We now extend the methodology of point forecast reconciliation to probabilistic forecasts.
-%For probabilistic forecasts, reconciliation implies finding the probability measure of the coherent forecasts using the information from an incoherent probabilistic forecast measure.
-A more formal definition is given below.
-Let $(\mathbb{R}^n, \mathscr{F}_{\mathbb{R}^n}, \hat{\nu})$ be a probability triple that is not coherent and which characterises forecast uncertainty for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.
-This is obtained from the first stage of the forecasting process; e.g., by modelling and forecasting each series individually.
-Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear function, and let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$.
-
-\begin{definition} \label{def:reconprob}
-  The reconciled probability measure of $\hat{\nu}$ with respect to the mapping $g(.)$ is a probability measure $\tilde{\nu}$ on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_\mathfrak{s}$ such that
-  \begin{equation}
-  \tilde{\nu}(s(\mathcal{B})) = \nu(\mathcal{B})= \hat{\nu}(g^{-1}(\mathcal{B})) \qquad \forall \mathcal{B} \in \mathscr{F}_{\mathbb{R}^m}\,,
-  \end{equation}
-  where $g^{-1}(\mathcal{B}):=\{\breve{\bm{y}}\in \mathbb{R}^n:g(\breve{\bm{y}})\in \mathcal{B}\}$ is the pre-image of $\mathcal{B}$, that is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $\mathcal{B}$.
-\end{definition}
-
-This definition extends the notion of forecast reconciliation to the probabilistic setting.
-Under point reconciliation methods, the reconciled point forecast is equal to the unreconciled point forecast after the latter is passed through two linear functions.
-Similarly, probabilistic forecast reconciliation assigns the same probability to two sets where the points in one set are obtained by passing all points in the other set through two linear functions.
-This is depicted in Figure~\ref{fig:probfr_sch} schematically when $s\circ g$ is a projection.
-
-\begin{figure}
-	\input{Figs/probforerec_schematic.tex}
-	\caption{Summary of probabilistic forecast reconciliation.
-The probability that $\bm{y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that $\bm{y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast.
-Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic.}\label{fig:probfr_sch}
-\end{figure}
-
-Recall that when $s\circ g$ is a projection, the case of point forecast reconciliation can be broken down into three steps.
-\begin{compactenum}
-\item  $\hat{\bm{y}}_{t+h|t}$ is transformed into coordinates $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ via a change of basis.
-\item $\tilde{\bm{a}}_{t+h|t}$ is discarded and $\tilde{\bm{b}}_{t+h|t}$ are kept as the bottom-level reconciled forecasts.
-\item Reconciled forecasts for the entire hierarchy are recovered via $\tilde{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}$.
-\end{compactenum}
-We now outline the analogous steps for probabilistic forecasts when predictive densities are available.
-
-While $\hat{\nu}$ is a probability measure for an $n$-vector $\hat{\bm{y}}_{t+h|t}$, probability statements in terms of a different coordinate system can be made via an appropriate change of basis.
-Letting $f(.)$ be generic notation for a probability density function, and following the notation from our definition of point forecast reconciliation where $\hat{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t}$, we obtain
-\begin{equation}
-f(\hat{\bm{y}}_{t+h|t})=f(\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t})|(\bm{S}~\bm{R})|
-\end{equation}
-The expression $\hat{\nu}(g^{-1}(\mathcal{B}))$ in Definition~\ref{def:reconprob} is equivalent to the probability statement $\text{Pr}(\hat{\bm{y}}_{t+h|t}\in g^{-1}(\mathcal{B}))$.
-After the change of basis, this is equivalent to $\text{Pr}(\tilde{\bm{b}}\in \mathcal{B})$, which implies
-\begin{align}
-\text{Pr}(\hat{\bm{y}}_{t+h|t}\in g^{-1}(\mathcal{B}))&=\int\limits_{g^{-1}(\mathcal{B})}f(\hat{\bm{y}}_{t+h|t})d\hat{\bm{y}}_{t+h|t}\\
-&=\int\limits_{\mathcal{B}}\int f(\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t})|(\bm{S}~\bm{R})|d\tilde{\bm{a}}_{t+h|t}d\tilde{\bm{b}}_{t+h|t}.
-\end{align}
-After integrating out over $\tilde{\bm{a}}_{t+h|t}$, a step analogous to setting $\tilde{\bm{a}}_{t+h|t}=0$ for point forecasting, we obtain an expression that gives the probability that the reconciled bottom-level series lies in the region $\mathcal{B}$.
-This corresponds to $\nu(\mathcal{B})$ in Definition~\ref{def:reconprob}.
-To make a valid probability statement about the entire hierarchy we simply use the bottom-level probabilistic forecasts together with Definition~\ref{def:cohprob}.
-
-\subsubsection*{Example: Gaussian Distributions}
-
-Suppose an unreconciled probabilistic forecast is Gaussian with mean $\hat{\bm{\mu}}$ and variance-covariance matrix $\hat{\bm{\Sigma}}$.
-The subscripts $t+h|t$ are suppressed for brevity.
-Let the unreconciled density be given by
-\begin{equation}
-  f(\hat{\bm{y}})=(2\pi)^{-n/2}|\hat{\bm{\Sigma}}|^{-1/2}\exp\left\{-\frac{1}{2}\left[(\hat{\bm{y}}-\hat{\bm{\mu}})'\hat{\bm{\Sigma}}^{-1}(\hat{\bm{y}}-\hat{\bm{\mu}})\right]\right\}.
-\end{equation}
-In an alternative basis,
-\begin{equation}
-f(\tilde{\bm{b}},\tilde{\bm{a}})=(2\pi)^{-\frac{n}{2}}\Big|\hat{\bm{\Sigma}}\Big|^{-\frac{1}{2}}\Big|(\bm{S} ~  \bm{R})\Big|\exp\{-\frac{1}{2}q\}\,,
-\end{equation}
-where
-\begin{equation}
-q=(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\hat{\bm{\mu}})' \hat{\bm{\Sigma}}^{-1}(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\hat{\bm{\mu}}).
-\end{equation}
-The quadratic form $q$ can be rearranged as
-\begin{align*}
-q& =
-\left((\bm{S} ~  \bm{R})\bt-\hat{\bm{\mu}}\right)' \hat{\bm{\Sigma}}^{-1}\left((\bm{S} ~ \bm{R})\bt-\hat{\bm{\mu}}\right),\\
-& =
-\left(\bt-(\bm{S} ~ \bm{R})^{-1}\hat{\bm{\mu}}_{t+h}\right)' \Big[(\bm{S}  \bm{R})^{-1}\hat{\bm{\Sigma}_{t+h}}\left((\bm{S} ~ \bm{R})^{-1}\right)'\Big]^{-1}
-\left(\bt-(\bm{S} ~ \bm{R})^{-1}\hat{\bm{\mu}}_{t+h}\right)\,.
-\end{align*}
-Recall that
-\[
-  (\bm{S} ~ \bm{R})^{-1} =
-  \begin{pmatrix}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot  \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot \end{pmatrix} :=
-  \begin{pmatrix}
-  \bm{G} \\\bm{H}
-  \end{pmatrix}\,.
-\]
-Then $q$ can be rearranged further as
-\begin{align*}
-q& =%\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\hat{\bm{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|\PQ \Big|}
-%\exp \Big\{-\frac{1}{2}
-\left[\bt-\PQ\hat{\bm{\mu}}_{t+h}\right]'%\\[-0.5cm]
-\left[\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\right]^{-1}\left[\bt-\PQ\hat{\bm{\mu}}_{t+h}\right] %\Big\},
-\\[0.5cm]
- & =%\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\Big|^{\frac{1}{2}}}
-%\exp \Big\{-\frac{1}{2}
-\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix}' %&\\[-0.5cm]
-%& \hspace*{7cm}
- \left[\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\right]^{-1}\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix}. %\Big\}.
-\end{align*}
-%Since $\Big[\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\Big] = \begin{pmatrix}
-%\bm{P}\hat{\bm{\Sigma}_{t+h}}\bm{P}' & \bm{P}\hat{\bm{\Sigma}_{t+h}}\bm{Q}'
-%\bm{Q}\hat{\bm{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\hat{\bm{\Sigma}_{t+h}}\bm{Q}'
-%\end{pmatrix}$ we have
-
-Similar manipulations on the determinant of the covariance matrix lead to the following expression for the density:
-\begin{align*}
-f(\tilde{\bm{b}},\tilde{\bm{a}})&
-=(2\pi)^{-\frac{n}{2}}\left|
-\begin{pmatrix}
-  \bm{G}\hat{\bm{\Sigma}}\bm{G}' & \bm{G}\hat{\bm{\Sigma}}\bm{H}' \\
-  \bm{H}\hat{\bm{\Sigma}}\bm{G}' & \bm{H}\hat{\bm{\Sigma}}\bm{H}'
-\end{pmatrix}
-\right|^{-\frac{1}{2}}
-\exp \left\{-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix}'\right.\\
-&\hspace*{7cm}
-\left.\begin{pmatrix}
-\bm{G}\hat{\bm{\Sigma}}\bm{G}' & \bm{G}\hat{\bm{\Sigma}}\bm{H}' \\
-\bm{H}\hat{\bm{\Sigma}}\bm{G}' & \bm{H}\hat{\bm{\Sigma}}\bm{H}'
-\end{pmatrix}^{-1}
-\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix} \right\}.
-\end{align*}
-Marginalising out $\tilde{\bm{a}}$ leads to the following bottom-level reconciled forecasts:
-\begin{equation}\label{ex:2.1}
-f(\tilde{\bm{b}})=(2\pi)^{-\frac{m}{2}}\Big|\bm{G}\hat{\bm{\Sigma}}\bm{G}'\Big|^{\frac{1}{2}}
-\exp \Big\{-\frac{1}{2} (\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}})' (\bm{G}\hat{\bm{\Sigma}}\bm{G}')^{-1}(\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}) \Big\}.
-\end{equation}
-
-%Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\hat{\bm{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
-Then from \eqref{4.7} it follows that
-%\begin{equation}\label{eq:gaussianreconciled}
-%\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
-%\end{equation}
-This implies that the reconciled probabilistic forecast for the bottom-level series is $\tilde{\bm{b}} \sim \mathcal{N}(\bm{G}\hat{\bm{\mu}}, \bm{G}\hat{\bm{\Sigma}}\bm{G}')$.
-The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean $\bm{SG}\hat{\bm{\mu}}$ and rank deficient covariance matrix $\bm{SG}\hat{\bm{\Sigma}}\bm{G}'\bm{S}'$.
-
-\subsection{Elliptical distributions}
-
-We now show that the true predictive distribution can be recovered for elliptical distributions by linear reconciliation via pre-multiplication and translation respectively by a matrix we denote ${\bm G}_{opt}$ and vector we denote  ${\bm d}_{opt}$.
-Here, for any square matrix $\bm{C}$, $\bm{C}^{1/2}$ and $\bm{C}^{-1/2}$ are defined to satisfy $\bm{C}^{1/2}(\bm{C}^{1/2})'=\bm{C}$ and $\bm{C}^{-1/2}(\bm{C}^{-1/2})'=\bm{C}^{-1}$, for example $\bm{C}^{1/2}$ may be obtained via the Cholesky or eigenvalue decompositions.
-
-\begin{theo}[Reconciliation for Elliptical Distributions]
-	Let an unreconciled probabilistic forecast come from the elliptical class with location parameter $\hat{\bm{\mu}}$ and scale matrix $\hat{\bm{\Sigma}}$.
-Let the true predictive distribution of $\bm{y}$ also belong to the elliptical class with location parameter $\bm{\mu}$ and scale matrix $\bm{\Sigma}$.
-Then the linear reconciliation mapping $g(\breve{\bm{y}})=\bm{G}_{opt}\breve{\bm{y}}+\bm{d}_{opt}$ with $\bm{G}_{opt}={\bm{a}}\hat{\bm\Sigma}^{-1/2}$ and $\bm{d}_{opt}=\bm{\mu}-\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}$ recovers the true predictive density where ${\bm{a}}$ is any $m\times n$ matrix such that ${\bm{a}}{\bm{a}}'=\bm{\Omega}$ and $\bm{\Omega}$ is a sub-matrix of $\bm{\Sigma}$ corresponding to the bottom-level series.
-\end{theo}
-
-\begin{proof}
-   Since elliptical distributions are closed under affine transformations, and are closed under marginalisation, reconciliation of an elliptical distribution yields an elliptical distribution (although the unreconciled and reconciled distributions may be different members of the class of elliptical distributions).
-The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}_{opt}\hat{\bm{\Sigma}}\bm{G}_{opt}'\bm{S}'$, while the location matrix is given by $\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}+\bm{d}_{opt}$.
-The reconciled scale matrix is
-   \[
-     \tilde{\bm{\Sigma}}_{opt}
-       = \bm{S}{\bm{a}}\hat{\bm\Sigma}^{-1/2}\hat{\bm{\Sigma}}\left(\hat{\bm\Sigma}^{-1/2}\right)'{\bm{a}}'\bm{S}'
-       = \bm{S}\bm{\Omega}\bm{S}'
-       = \bm{\Sigma}.
-   \]
-   For the choices of $\bm{G}_{opt}$ and $\bm{d}_{opt}$ given above, the reconciled location vector is
-   \[
-     \tilde{\bm{\mu}}_{opt}= \bm{S}\bm{G}_{opt}\hat{\bm{\mu}}+\bm{\mu}-\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}
-   = \bm{\mu}.
-   \]
-\end{proof}
-
-A number of insights can be drawn from this theorem.
-First, although a linear function $g(.)$ can be used to recover the true predictive in the elliptical case, the same does not hold in general.
-Second, $g(.)$ is not, in general, a projection matrix.
-The conditions for which a the true predictive density can be recovered by a projection are given below.
-
-\begin{theo}[True predictive via projection]
-	Assume that the true predictive distribution is elliptical with location $\bm{\mu}$ and scale $\bm{\Sigma}$.
-Consider reconciliation via a projection $g(\bm{y})=(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\bm{y}$.
-The true predictive distribution can be recovered via reconciliation of an elliptical distribution with location $\hat{\bm{\mu}}$ and scale $\hat{\bm{\Sigma}}$  when the following conditions hold:
-	\begin{align}
-	sp(\hat{\bm\mu}-\bm{\mu})&\subset sp(\bm{R})\\
-    sp(\hat{\bm{\Sigma}}^{1/2}-\bm{\Sigma}^{1/2})&\subset sp(\bm{R})\\
-	\end{align}
-\end{theo}
-
-\begin{proof}
-	The reconciled location vector will be given by
-	\begin{align*}
-		\tilde{\bm{\mu}}&=\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\hat{\bm{\mu}}\\
-		&=\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\left(\hat{\bm{\mu}}+\bm{\mu}-\bm{\mu}\right)\\
-		&=\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\bm{\mu}+\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\left(\hat{\bm{\mu}}-\bm{\mu}\right).
-	\end{align*}
-  Since $\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}$ is a projection onto $\mathfrak{s}$ and $\bm{\mu}\in\mathfrak{s}$, the first term simplifies to $\bm{\mu}$.
-If $\bm{\mu}-\hat{\bm{\mu}}$ lies in the span of $\bm{R}$, then multiplication by $\bm{R}'_{\perp}$ reduces the second term to $\bm{0}$.
-By a similar argument it can be shown that $\tilde{\bm{\Sigma}}^{1/2}=\bm{\Sigma}^{1/2}$.
-The closure property of elliptical distributions under affine transformations ensures that the full true predictive distribution can be recovered.
-\end{proof}
-
-Although these conditions will rarely hold in practice and only apply to a limited class of distributions, they do provide some insight into selecting a projection for reconciliation.
-If the value of $\hat{\bm{\mu}}$ were equi-probable in all directions, then a projection orthogonal to $\mathfrak{s}$ would be a sensible choice for $\bm{R}$ since it would in some sense represent a `median' direction for $\bm{\mu}-\hat{\bm{\mu}}$.
-However, the one-step-ahead in-sample errors are usually correlated suggesting that $\hat{\bm{\mu}}$ is more likely to fall in some directions than others.
-Therefore an orthogonal projection after transformation by the inverse of the one-step-ahead in-sample error covariance matrix may be more intuitively appealing.
-This is exactly what the MinT projection provides, and as simulations will show in Section~\ref{sec:gaussian}, this projection leads to the best empirical results.
-
-%However, these expressions do provide some insight on why some choices for $\bm{G}$ in the point forecast reconciliation literature may also work well for probabilistic forecasts.
-To illustrate, first rearrange the equation for the optimal value of  $\bm{G}_{opt}={\bm\Omega}^{1/2}\hat{\bm\Sigma}^{-1/2}$ as ${\bm\Omega}^{1/2}=\bm{G}_{opt}\hat{\bm\Sigma}^{1/2}$.
-For arbitrary $\bm{G}\hat{\bm\Sigma}^{1/2}$ is an approximation for ${\bm\Omega}^{1/2}$.
-This approximation has similarities with the way bottom-level estimates are produced for point forecast reconciliation.
-Rather than mapping a vector of point forecasts to reconcilied bottom-level forecasts, the columns of  $\hat{\bm\Sigma}^{1/2}$ are mapped to an approximation of the columns of ${\bm\Omega}^{1/2}$.
-The value for $\tilde{\bm{\mu}}_{opt}$ includes a projection of $\hat{\bm{\mu}}$ onto $\mathfrak{s}$.
-While it is infeasible to obtain the translation $\bm{d}$, it is worthwhile noting that this measures the difference between the reconciled mean and true mean.
-
-\section{Evaluation of hierarchical probabilistic forecasts}\label{sec:evaluation}
-
-The necessary final step in hierarchical forecasting is to make sure that our forecast distributions are accurate.
-In general, forecasters prefer to maximize the sharpness of the forecast distribution subject to calibration \citep{Gneiting2014}.
-Therefore the probabilistic forecasts should be evaluated with respect to these two properties.
-
-Calibration refers to the statistical compatibility between probabilistic forecasts and realizations.
-In other words, random draws from a perfectly calibrated forecast distribution should be equivalent in distribution to the realizations.
-On the other hand, sharpness refers to the spread or the concentration of the predictive distributions and it is a property of the forecasts only.
-The more concentrated the forecast distributions, the sharper the forecasts \citep{Gneiting2008}.
-However, independently assessing the calibration and sharpness will not help to properly evaluate the probabilistic forecasts.
-Therefore we need to assess these properties simultaneously using scoring rules.
-
-Scoring rules are summary measures obtained based on the relationship between the forecast distributions and the realizations.
-In some studies, researchers take the scoring rules to be positively oriented, in which case the scores should be maximized \citep{Gneiting2007}.
-However, scoring rules have also been defined to be negatively oriented, and then the scores should be minimized \citep{Gneiting2014}.
-We follow the latter convention here.
-
-Let $P$ be a forecast distribution and let $Q$ be the true data generating process respectively.
-Furthermore let $\omega$ be a realization from $Q$.
-Then a scoring rule is a function $S(P,\omega)$ that maps $P,\omega$ to $\mathbb{R}$.
-It is a ``proper'' scoring rule if
-\begin{equation}\label{eq:(3.1.)}
-\E_{\bm{Q}}[S(Q,\omega)] \le \E_{\bm{Q}}[S(P,\omega)] ,
-\end{equation}
-where $\E_{Q}[S(P,\omega)]$ is the expected score under the true distribution $Q$ \citep{Gneiting2008, Gneiting2014}. When this inequality is strict, the scoring rule is said to be strictly proper.
-
-In the context of probabilistic forecast reconciliation there could be two motivations for using scoring rules.
-The first is to compare unreconciled densities to reconciled densities.
-Reconciliation itself is a valuable goal since it can be important in aligning decision making across, for example, different units of an enterprise.
-In the point forecasting literature, forecast reconciliation has also been shown to improve forecast performance \citep{AthEtAl2017, Wickramasuriya2017}.
-It will be worthwhile to see whether the same holds in the probabilistic forecasting case.
-The second motivation for using scoring rules is to compare two or more sets of reconciled probabilistic forecasts to one another.
-The objective here is to evaluate which reconciliation mapping $g(.)$ works best in practice.
-
-\subsection{Univariate scoring rules}
-
-One way to evaluate hierarchical probabilistic forecasts is via the application of univariate scoring rules to each variable in the hierarchy.
-A summary can be taken of the expected scores across each margin, for example a mean or median.
-In the simulations of Section~\ref{sec:gaussian}, we consider two such scoring rules.
-The log score is given by the log density, in this case for each margin of the probabilistic forecast.
-The cumulative rank probability score generalises mean square error and is given by
-\begin{align} \label{eq:CRPS}
-\text{CRPS}(\breve{F}_i,y_{i}) &=\int \left(\breve{F}_i(\breve{Y}_i)-\mathbb{1}(\breve{Y}_i<y_{i})\right)d\breve{Y}_i\\ &=\E_{\breve{Y}_i}|\breve{Y}_{i}-y_{i}| - \frac{1}{2}\E_{\breve{Y}_i}|\breve{Y}_{i}-\breve{Y}^*_{i}|\,,
-\end{align}
-where $\breve{F}_i$ is the cumulative distribution function of the $i$th margin of the probabilistic forecast, $\breve{Y}_i$ and $\breve{Y}^*_{i}$ are independent copies of a random variable with distribution $\breve{F}_i$, and $y_i$ is the outcome of the $i$th margin.
-The expectations in the second line can be approximated by Monte Carlo when a sample from the predictive distribution is available.
-
-An advantage to this approach is that it allows the forecaster to evaluate the levels and individual series of the hierarchy where the gains from reconciliation are greatest.
-For this reason this approach has been used in the limited literature on probabilistic forecasting for hierarchies \citep{BenTaieb2017, JeoEtAl2018} to date.
-A major shortcoming of this approach however, is that evaluating univariate scores on the margins does not account for the dependence in the hierarchy.
-
-\subsection{Multivariate scoring rules}
-
-While a number of alternative proper scoring rules are available for univariate forecasts, the multivariate case is somewhat more limited.
-Here we focus on three scoring rules: the log score (LS), the energy score (ES) and the variogram score (VS).
-
-The log score can be approximated using a sample of values from the probabilistic forecast density \citep{Jordan2017}; however it is more commonly used when a parametric form for the density is available for the probabilistic forecast.
-
-The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the following representation in terms of expectations
-\begin{equation}
-\text{ES}(\breve{\bm{Y}}_{T+h},\bm{y}_{T+h}) =
-\E_{\breve{\bm{Y}}}
-||\breve{\bm{Y}}_{T+h}-\bm{y}_{T+h}||^\alpha -\frac{1}{2}\E_{\breve{\bm{Y}}}||\breve{\bm{Y}}_{T+h}-\breve{\bm{Y}}^*_{T+h}||^\alpha, \,\, \alpha \in (0,2]\,, 
-\end{equation}
-lends itself to easy computation when samples from the probabilistic forecast are available.
-An interesting limiting case is where $\alpha=2$, where it can be easily shown that energy score simplifies to mean squared error around the mean of the predictive distribution.
-In this limiting case, the energy score is proper but not strictly proper.
-\citet{Pinson2013a} also argue that the energy score has low discriminative ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
-
-In contrast, \citet{SCHEUERER2015} have shown that the variogram score has a higher discrimination ability for misspecified means, variances and correlation structures than the energy score.
-When $\breve{\bm{y}}$ is a random variable from probabilistic forecast $\breve{F}$, the empirical variogram score is defined as
-\begin{equation}
-\text{VS}(\breve{F}, \bm{y}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{i} - y_{j}|^p - E_{\breve{Y}_i,\breve{Y}_j} |\breve{Y}_{i}-\breve{Y}_{j}|^p\right)^2.
-\end{equation}
-\citet{SCHEUERER2015} recommend using $p=0.5$.
-
-\subsubsection{Comparing unreconciled forecasts to reconciled forecasts}
-
-For both reconciled and unreconciled densities it is possible to obtain a density from the probability measures defined in Section~\ref{sec:definitions}.
-Therefore it may seem sensible to compare unreconciled densities to reconciled densities on the basis of log score.
-However, the following theorem shows that using the log score may fail in the case of multivariate distributions with a degeneracy.
-
-\begin{theo}[Impropriety of log score]
-	When the true data generating process is coherent, then the log score is improper with respect to the class of incoherent measures.
-\end{theo}
-
-\begin{proof}
-Consider a rotated version of hierarchical time series, $\bm{z}_t=\bm{U}\bm{y}_t$, so that the first $m$ elements of $\bm{z}_t$ denoted $\bm{z}^{(1)}_t$ are unconstrained, while the remaining $n-m$ elements denoted $\bm{z}^{(2)}_t$ equal $0$ when the aggregation constraints hold.
-An example of the $n\times n$ $\bm{U}$ is the matrix of left singular vectors of $\bm{S}$.
-
-Consider the case where the true predictive density is $f_1(\bm{z}^{(1)}_t)\mathbb{1}\left(\bm{z}^{(2)}_t=\bm{0}\right)$, and we evaluate an incoherent density given by $f_1(\bm{z}^{(1)}_t)f_2(\bm{z}^{(2)}_t)$, where $f_2$ is highly concentrated around $0$ but still non-degenerate.
-For example, $f_2$ may be Gaussian with variance $\sigma^2{\bm{I}}$ with $\sigma^2 < (2\pi)^{-1}$.
-The log score under the true data generating process is
-\[
-LS\left(f,\bm{z}^{(1)}_t\right) = -\log f_1\left(\bm{z}^{(1)}_t\right),
-\]
-while that of the unreconciled density is
-\begin{align}
-LS\left(\hat{f},\bm{z}^{(1)}_t\right) &= -\log f_1(\bm{z}^{(1)}_t)-f_2(\bm{z}^{(1)}_t)\\
-&= -\log f_1(\bm{z}^{(1)}_t)+\frac{n-m}{2}\log(2\pi\sigma^2)\\
-&<-\log f_1(\bm{z}^{(1)}_t)=LS\left(f,\bm{z}^{(1)}_t\right).
-\end{align}
-After taking expectations $E\left[LS(f,f)\right] > E\left[LS(\hat{f},f)\right]$, violating the condition in Equation~\eqref{eq:(3.1.)} for a proper scoring rule.
-\end{proof}
-
-A similar issue also arises when discrete random variables are modelled as if they were continuous, an issue discussed in Section~4.1 of \citet{Gneiting2007}.
-This implies that the log score should be avoided when comparing reconciled and unreconciled probabilistic forecasts.
-
-\subsubsection{Comparing reconciled forecasts to one another}
-
-Coherent probabilistic forecasts can be completely characterised in terms of basis series; if a probabilistic forecast is available for the basis series, then a probabilistic forecast can be recovered for the entire hierarchy via Definition~\ref{def:cohprob}.
-This may suggest that it is adequate to merely compare two coherent forecasts to one another using the basis series only.
-We now show how this depends on the specific scoring rule used.
-
-For the log score, suppose the coherent probabilistic forecast has density $f(\bm{b})$.
-The density for the full hierarchy is given by $f(\bm{y})=f(\bm{Sb})=f(\bm{b})J^{-1}$, where $J=\prod_{j=1}^{m}\lambda_j$ is a pseudo-determinant of the non-square matrix $\bm{S}$ and $\lambda_j$ are the non-zero singular values of $\bm{S}$.
-Therefore for any coherent density, the log score of the full hierarchy differs from the log score for the bottom-level series by the term $log(J)$.
-This term depends only on the structure of the hierarchy and is fixed across different reconciliation methods.
-Therefore if one method achieves a lower expected log score compared to an alternative method using the bottom-level series only, the same ordering is preserved when an assessment is made on the basis of the full hierarchy.
-
-The same property does not hold for all scores in general.
-For example, the energy score can be expressed in terms of expectations of norms.
-In general, since norms are invariant under orthogonal rotations, the energy score is also invariant under orthogonal transformations \citep{Szekely2013,Gneiting2007}.
-In the context of two coherent forecasts, the same is true of a semi-orthogonal transformation from a lower dimensional basis series to the full hierarchy.
-However, when $\bm{S}$ is the usual summing matrix, it is not semi-orthogonal.
-Therefore the energy score computed on the bottom-level series will differ from the energy score computed using the full hierarchy and the ordering of different reconciliation methods may change depending on the basis series used.
-In this case we recommend computing the energy score using the full hierarchy.
-Although the discussion here is related to energy score, the same logic holds for other multivariate scores, for example the variogram score.
-
-The properties of multivariate scoring rules in the context of evaluating reconciled probabilistic forecasts are summarised in Table~\ref{tab:prop}.
-
-\begin{table}
-	\centering
-	\begin{tabular}{rll}
-	& Coherent v Incoherent &Coherent v Coherent\\
-	\hline
-	Log Score & Not proper & Ordering preserved if compared using\\ &&bottom-level only\\
-	Energy/ & Proper & Full hierarchy should be used\\
-	Variogram Score & Proper & Full hierarchy should be used\\
-	\hline
-    \end{tabular}
-	\caption{Summary of properties of scoring rules in the context of reconciled probabilistic forecasts.}
-	\label{tab:prop}
-\end{table}
-
-\section{Simulation study}\label{sec:gaussian}
-
-We now turn our attention to comparing different reconciliation methods in a simulation study where the data is conditionally Gaussian.
-We choose the Gaussian case due to its analytical tractability which allows for evaluation using all scoring rules (including the log score).
-The non-Gaussian case lies beyond the scope of this simulation study.
-
-For the data generating process, we consider the hierarchy given in Figure~\ref{fig1}, comprising two aggregation levels with four bottom-level series.
-Each bottom-level series will be generated first, and then summed to obtain the data for the upper-level series.
-In practice, hierarchical time series tend to contain much noisier series at lower levels of aggregation.
-In order to replicate this feature in our simulations, we follow the data generating process proposed by \citet{Wickramasuriya2017}.
-
-First $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from ARIMA$(p,d,q)$ processes, where $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability.
-The errors driving these ARIMA processes are jointly normal, and denoted by $\{\varepsilon_{AA,t},\varepsilon_{AB,t},\varepsilon_{BA,t},\varepsilon_{BB,t}\} \overset{iid}{\sim} \mathcal{N}(\bm{0}, \bm{\Sigma})~\forall t$.
-The parameters for the AR and MA components are randomly and uniformly generated from $[0.3,0.5]$ and $[0.3,0.7]$ respectively.
-Then the bottom-level series $\{y_{AA,t},y_{AB,t},y_{BA,t},y_{BB,t}\}$ are given by:
-\begin{align*}
-y_{AA,t} &= w_{AA,t} + u_t - 0.5v_t,\\
-y_{AB,t} &= w_{AB,t} - u_t - 0.5v_t,\\
-y_{BA,t} &= w_{BA,t} + u_t + 0.5v_t,\\
-y_{BB,t} &= w_{BB,t} - u_t + 0.5v_t,
-\end{align*}
-where $u_t \sim \mathcal{N}(0,\sigma^2_u)$ and $v_t \sim \mathcal{N}(0,\sigma^2_v)$. The aggregate series in the middle-level are given by:
-\begin{align*}
-y_{A,t} &= w_{AA,t} + w_{AB,t} - v_t,\\
-y_{B,t} &= w_{BA,t} + w_{BB,t} + v_t,
-\end{align*}
-and the total series is given by
-\[
-  y_{Tot,t} = w_{AA,t} + w_{AB,t} + w_{BA,t} + w_{BB,t}.
-\]
-To ensure the disaggregate series are noisier than the aggregate series, we choose $\bm{\Sigma}, \sigma^2_u$ and $\sigma^2_v$ such that
-\[
-  \var(\varepsilon_{AA,t} + \varepsilon_{AB,t} + \varepsilon_{BA,t} + \varepsilon_{BB,t})
-  \le \var(\varepsilon_{AA,t}+\varepsilon_{AB,t}-v_t)
-  \le \var(\varepsilon_{AA,t}+u_t-0.5v_t)\,,
-\]
-and similar inequalities hold when $\varepsilon_{AA,t}$ is replaced by $\varepsilon_{AB,t}$, $\varepsilon_{BA,t}$ and $\varepsilon_{BB,t}$ in the third term.
-The values of $\bm{\Sigma}$, $\sigma^2_u$ and $\sigma^2_v$ that we use and which satisfy these constraints are $\sigma^2_u = 19$, $\sigma^2_u = 18$ and
-\[
-\bm{\Sigma} =
-\begin{pmatrix}
-5.0 & 3.1 & 0.6 & 0.4 \\
-3.1 & 4.0 & 0.9 & 1.4 \\
-0.6 & 0.9 & 2.0 & 1.8 \\
-0.4 & 1.4 & 1.8 & 3.0 \\
-\end{pmatrix}\,.
-\]
-
-We generate data with a sample size of $T=501$.
-Univariate ARIMA models are selected for each series using the \textit{auto.arima} function in the \textit{forecast} package \citep{hyndman2017forecasting} in R \citep{Rcore}.
-The same package was used to fit each series independently using the first 500 observations, and evaluate 1-step ahead base (incoherent) probabilistic forecasts.
-These were then reconciled using different projections summarised in Table~\ref{table:2}.
-This process was replicated using $1000$ different data sets from the same data generating processes.
-
-To assess the predictive performance of different forecasting methods, we use scoring rules as discussed in Section~\ref{sec:evaluation}.
-To facilitate comparisons, we report skill scores \citep{Gneiting2007}.
-For a given forecasting method, evaluated by a particular scoring rule, the skill score
-gives the percentage improvement of the preferred forecasting method relative to a reference method.
-A negative valued skill score indicates that a method is worse than the reference method, whereas any positive value indicates that the method is superior to the reference method.
-
-Table~\ref{table:3} summarizes the forecasting performance of unreconciled, bottom-up, OLS, WLS and two MinT reconciliation methods using log score, energy score and variogram score.
-In all cases skill scores are calculated with the bottom-up method as reference.
-All log scores are evaluated on the basis of bottom-level series only, however these only differ from the log scores for the full hierarchy by a fixed constant.
-The cell for log score of unreconciled forecasts is left blank since the log score is not proper in this context.
-Overall, the MinT methods provide the best performance irrespective of the scoring rule, and all methods that reconcile using information at all levels of the forecast improve upon unreconciled forecasts.
-Bottom-up forecasts perform even worse than unreconciled forecasts in some cases.
-
-Tables~\ref{table:4} and~\ref{table:5} break down the forecasting performance of different reconciliation methods by considering univariate scores on each individual margin.
-Tables~\ref{table:4} summarises results for the top and middle-level, Table~\ref{table:5} does the same for bottom-level.
-The log score and CRPS are considered, while skill scores are computed with the unreconciled forecast as a reference.
-When broken down in this fashion, the methods based on MinT perform best for all series and always outperform bottom-up and unreconciled forecasts.
+%
 
@@
 	\caption{Comparison of coherent forecasts.
-``Energy score'' and ``Variogram score'' columns give scores based on the joint forecast distribution of the whole hierarchy.
-``Log score'' column gives the log scores of the joint forecast distribution of the bottom-level.
+``Energy score'' and ``Variogram score'' columns give scores based on the joint forecast distribution of whole hierarchy.
+``Log score'' column gives the log scores of the joint forecast distribution of bottom level.
 ``Skill score'' columns give the percentage skill score with reference to the bottom-up method.
-Entries in these columns show the percentage increase of scores for different reconciliation methods relative to the bottom-up method.}\label{table:3}
+Entries in these columns show the percentage increase of score for different reconciliation methods relative to the bottom-up method.
+}\label{table:3}
 
@@
 
-\section{Conclusions}\label{sec:conclusions}
-
-%Although the problem of hierarchical point forecasts is well studied in the literature, there is a lack of attention in the context of probabilistic forecasts.
-Thus we attempted to fill this gap in the literature by providing substantial theoretical background to the problem.
-
-By redefining coherent forecasts and forecast reconciliation in geometric terms, we have established two new theoretical results that support the use of projections for point forecast reconciliation, and have allowed us to extend these concepts to probabilistic forecasting.
-We have shown that for elliptical distributions the true predictive density can be recovered by linear reconciliation and we have established conditions for when this is a projection.
-Although this projection cannot feasibly be obtained in practice, a projection similar to the MinT procedure provides a good approximation in applications.
-This is supported by the results of a simulation study.
-Finally, we have also discussed strategies for evaluating probabilistic forecasts for hierarchical time series advocating the use of multivariate scoring rules on the full hierarchy, while establishing a key result regarding the impropriety of the log score with respect to incoherent forecasts.
-
-In many ways this paper sets up a substantial future research agenda.
-For example, having defined what amounts to an entire class of reconciliation methods for probabilistic forecasts it will be worthwhile investigating which specific projections are optimal.
-This is likely to depend on the specific scoring rule employed as well as the properties of the base forecasts.
-Another avenue worth investigating is to consider whether it is possible to recover the true predictive distribution for non-elliptical distributions via a non-linear function $g(.)$.
-
-\newpage
-
-\bibliographystyle{agsm}
-
-\bibliography{References_paper1}
-
 \end{document}

### 2019-04-11 Probabilistic-forecasts-for-hierarchical-time-series/ProbabilisticCoherence.tex
Outlined first two papers

--- 2018-08-24 ProbabilisticCoherence.tex
@@
 	{
-		\title{\bf Probabilistic Forecasts in Hierarchical~Time~Series}
+		\title{\bf Probabilistic Forecasts for Hierarchical~Time~Series}
 		        \author{Puwasala Gamakumara\thanks{
@@
 		\begin{center}
-			{\LARGE\bf Probabilistic Forecasts in Hierarchical~Time~Series}
+			{\LARGE\bf Probabilistic Forecasts for Hierarchical~Time~Series}
 		\end{center}
@@
 \begin{abstract}
-  Forecast reconciliation involves adjusting forecasts to ensure coherence with aggregation constraints.
+	TBC
+%  Forecast reconciliation involves adjusting forecasts to ensure coherence with aggregation constraints.
 We extend this concept from point forecasts to probabilistic forecasts by redefining forecast reconciliation in terms of linear functions in general, and projections more specifically.
@@
 
-\noindent%
-{\it Keywords:}  Forecast Reconciliation, Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
-\vfill
+%\noindent%
+%{\it Keywords:}  Forecast Reconciliation, Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
+%\vfill
 
@@
 Large collections of time series often follow some aggregation structure.
-For example, the electricity demand of a country can be disaggregated according to a geographic hierarchy of states, cities, and individual households.
+For example, the tourism flow of a country can be disaggregated along a geographic hierarchy of states, zones, and cities.
+These are ordinarily referred to as hierarchical time series.
 To ensure aligned decision making, it is important that forecasts at the most disaggregated level add up to forecasts at more aggregated levels.
@@
 Generalising both of these concepts, particularly the latter, to probabilistic forecasting is a gap that we seek to address in this work.
-We do so by first providing a novel geometric interpretation to coherence and reconciliation in the point forecasting case.
-This can easily be generalised to probabilistic forecasting allowing us to derive further results for elliptical distributions as well as provide insight into forecast evaluation via multivariate  scoring rules.
+We do so by extending the geometric interpretation to coherence and reconciliation in the point forecasting case outlined in (\textcolor{red}{cite the first paper}) to the probabilistic framework.
+This is allowing us to derive further results for parametric as well as non-parametric distributional forecasts for hierarchical time series.
+%elliptical distributions as well as provide insight into forecast evaluation via multivariate scoring rules.
 
@@
 
-To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections.
+\textcolor{red}{To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections.
 In addition to being highly intuitive, this allows us to establish a number of theoretical results.
@@
 We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class.
-We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly estimated in practice, we provide a heuristic argument in favour of MinT reconciliation.
+We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly estimated in practice, we provide a heuristic argument in favour of MinT reconciliation.}
 
-We also cover the topic of forecast evaluation of probabilistic forecasts via scoring rules.
+\textcolor{red}{We also cover the topic of forecast evaluation of probabilistic forecasts via scoring rules.
 In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.
 Therefore we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts.
-Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.
+Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.}
 
-The remainder of the paper is structured as follows.
+\textcolor{red}{The remainder of the paper is structured as follows.
 In Section~\ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.
@@
 In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules, while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian}.
-Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.
+Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.}
 
@@
 
-A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables.
+\textcolor{red}{A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables.
 We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$.
 The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.
-The hierarchical structure of the data implies that
+The hierarchical structure of the data implies that}
 \begin{equation}
@@
 \end{equation}
-where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints, holds for all $t$.
+\textcolor{red}{where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints, holds for all $t$. }
 
-To clarify these concepts consider the example of the hierarchy in Figure~\ref{fig1}.
-For this hierarchy, $n=7$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$ and
+\textcolor{red}{To clarify these concepts consider the example of the hierarchy in Figure~\ref{fig1}.
+For this hierarchy, $n=7$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$ and}
 \[
@@
 \]
-where $\bm{I}_4$ is the $4\times 4$ identity matrix.
+\textcolor{red}{where $\bm{I}_4$ is the $4\times 4$ identity matrix.}
 
-While most applications of hierarchical time series to date have involved data that respect an aggregation structure, in principle the matrix ${\bm S}$ can encode any linear constraints including weighted sums or even cases where some variables in the hierarchy are formed by taking the difference of two other variables.
+\textcolor{red}{While most applications of hierarchical time series to date have involved data that respect an aggregation structure, in principle the matrix ${\bm S}$ can encode any linear constraints including weighted sums or even cases where some variables in the hierarchy are formed by taking the difference of two other variables.}
 
-\subsection{Coherent point forecasts}\label{sec:cohpointf}
-
-It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect inherent aggregation constraints.
+%\subsection{Coherent point forecasts}\label{sec:cohpointf}
+%
+%It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect inherent aggregation constraints.
 We follow other authors \citep{Wickramasuriya2017, FPP2018} in using the nomenclature \emph{coherence} to describe this property.
 We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem, thus facilitating the development of probabilistic forecast reconciliation in Section~\ref{sec:reconciliation}.
-
-\begin{definition}[Coherent subspace]\label{def:cohspace}
- The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$, is defined as the \emph{coherent space}.
-\end{definition}
-
-It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$.
+%
+%\begin{definition}[Coherent subspace]\label{def:cohspace}
+% The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$, is defined as the \emph{coherent space}.
+%\end{definition}
+%
+%It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$.
 Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.
-
-\begin{figure}[H]
-  \begin{center}
-    \begin{tikzpicture}[
-    >=stealth,
-    bullet/.style={
-      fill=black,
-      circle,
-      minimum width=1.5cm,
-      inner sep=0pt
-    },
-    projection/.style={
-      ->,
-      thick,
-      label,
-      shorten <=2pt,
-      shorten >=2pt
-    },
-    every fit/.style={
-      ellipse,
-      draw,
-      inner sep=0pt
-    }
-    ]
-    \node at (2,3) {$s$};
-    \node at (0,5) {$\mathbb{R}^m$(domain of $s$)};
-    \node at (4,5) {$\mathbb{R}^n$(codomain of $s$)};
-    \node at (4.7,2.0) {$\mathfrak{s}$(image of $s$)};
-    %\node[bullet,label=below:$f(x)$] at (4,2.5){};
-    \draw (0,2.5) ellipse (1.02cm and 2.2cm);
-    \draw (4,2.5) ellipse (1.02cm and 2.2cm);
-    \draw (4,2.5) ellipse (0.51cm and 1.1cm);
-    \draw[projection, label=below:$f$] (0.3,2.5) -- (3.8,2.5) ;
-    \end{tikzpicture}
-  \end{center}
-  \caption{The domain, codomain and image of the mapping $s$.}\label{fig2}
-\end{figure}
-
-\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
-  Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a point forecast of the values of all series in the hierarchy at time $t+h$, made using information up to and including time $t$.
+%
+%\begin{figure}[H]
+%  \begin{center}
+%    \begin{tikzpicture}[
+%    >=stealth,
+%    bullet/.style={
+%      fill=black,
+%      circle,
+%      minimum width=1.5cm,
+%      inner sep=0pt
+%    },
+%    projection/.style={
+%      ->,
+%      thick,
+%      label,
+%      shorten <=2pt,
+%      shorten >=2pt
+%    },
+%    every fit/.style={
+%      ellipse,
+%      draw,
+%      inner sep=0pt
+%    }
+%    ]
+%    \node at (2,3) {$s$};
+%    \node at (0,5) {$\mathbb{R}^m$(domain of $s$)};
+%    \node at (4,5) {$\mathbb{R}^n$(codomain of $s$)};
+%    \node at (4.7,2.0) {$\mathfrak{s}$(image of $s$)};
+%    %\node[bullet,label=below:$f(x)$] at (4,2.5){};
+%    \draw (0,2.5) ellipse (1.02cm and 2.2cm);
+%    \draw (4,2.5) ellipse (1.02cm and 2.2cm);
+%    \draw (4,2.5) ellipse (0.51cm and 1.1cm);
+%    \draw[projection, label=below:$f$] (0.3,2.5) -- (3.8,2.5) ;
+%    \end{tikzpicture}
+%  \end{center}
+%  \caption{The domain, codomain and image of the mapping $s$.}\label{fig2}
+%\end{figure}
+%
+%\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
+%  Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a point forecast of the values of all series in the hierarchy at time $t+h$, made using information up to and including time $t$.
 Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathfrak{s}$.
-\end{definition}
+%\end{definition}
 
@@
 
-These definitions of the coherent space $\mathfrak{s}$, coherent point and coherent probabilistic forecasts in terms of the mapping $s(.)$, may give the impression that the bottom-level series play an important role.
-However, alternative definitions could be formed using any set of basis vectors that span $\mathfrak{s}$.
-For example, consider the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$.
-In this case the matrix $\bm{S}$ has columns $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$, and pre-multiplying by $\bm{S}$ transforms arbitrary values of $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy.
-However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy.
-The definitions above could be made in terms of any series and not just the bottom-level series.
-In general, we call the series (or linear combinations thereof) used in the definitions of coherence \textit{basis series}.
-Unless stated otherwise, we will always assume that the basis series are the bottom-level series as in Definition~\ref{def:cohpoint} and Definition~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.
+\textcolor{red}{Add a sentence about taking bottom level series as basis series.
+ }
 
@@
 
-As discussed, reconciliation is distinct from coherence, since the former refers to a process whereby incoherent forecasts are made coherent.
-Although reconciliation methods for point forecasts are extant in the literature they are rarely defined explicitly.
-We do so here in slightly more general terms than usual.
-We then extend this idea to the novel concept of probabilistic reconciliation.
+\textcolor{red}{We extend this idea to the novel concept of probabilistic reconciliation.}
 
-\subsection{Point forecast reconciliation}
-
-Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ conditional on information up to and including time $t$.
+%\subsection{Point forecast reconciliation}
+%
+%Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ conditional on information up to and including time $t$.
 We now introduce a linear function that converts unreconciled forecasts into new bottom level forecasts.
-Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively, and let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})=\bm{G}\bm{y}+\bm{d}$.
+%Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively, and let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})=\bm{G}\bm{y}+\bm{d}$.
 A composition of $g$ and $s(.)$ gives the following definition for point forecast reconciliation.
-
-\begin{definition}\label{def:reconpoint}
-	The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $g(.)$ iff
-	\begin{equation}
-	  \tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{G}\hat{\bm{y}}_{t+h|t}+\bm{d})\,.
-	\end{equation}
-\end{definition}
-
-Several choices of $g(.)$ currently extant in the literature, including the OLS, WLS and MinT methods, are special cases where $s\circ g$ is a projection.
+%
+%\begin{definition}\label{def:reconpoint}
+%	The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $g(.)$ iff
+%	\begin{equation}
+%	  \tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{G}\hat{\bm{y}}_{t+h|t}+\bm{d})\,.
+%	\end{equation}
+%\end{definition}
+%
+%Several choices of $g(.)$ currently extant in the literature, including the OLS, WLS and MinT methods, are special cases where $s\circ g$ is a projection.
 These can be defined so that $\bm{G}=({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ and $\bm{d}=\bm{0}$, were, ${\bm{R}_{\perp}}$ is a $n\times m$ orthogonal complement to an $n \times (n-m)$ matrix $\bm{R}$, where the columns of the latter span the null space of $\mathfrak{s}$.
@@
 A schematic providing a geometric interpretation of point reconciliation is given in Figure~\ref{fig:pointfr_sch}, while Table~\ref{table:2} summarises existing reconciliation methods.
-
-\begin{table}[!h]
-	\caption{Summary of reconciliation methods that are projections.
+%
+%\begin{table}[!h]
+%	\caption{Summary of reconciliation methods that are projections.
 Here, $\hat{\bm{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, $\hat{\bm{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}, $\hat{\bm{W}}^{wls}$ is the diagonal matrix with diagonal elements $w_{ii}$, and $\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$, where $w_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{W}}^{sam}$.}\label{table:2}
-	\centering
-	\begin{tabular}{lll}
-		\toprule
-		\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
-		\midrule
-		OLS             &
-		$\bm{I}$  &
-		$\bm{S}'$  \\
-		MinT(Sample)    &
-		$\hat{\bm{W}}^{sam}$ &
-		$\bm{S}'(\hat{\bm{W}}^{sam})^{-1}$ \\
-		MinT(Shrink)    &
-		$\tau\text{Diag}(\hat{\bm{W}}^{sam}) + (1-\tau)\hat{\bm{W}}^{sam}$ &
-		$\bm{S}'(\hat{\bm{W}}^{shr})^{-1}$ \\
-		WLS       &
-		$\text{Diag}(\hat{\bm{W}}^{shr})$ &
-		$\bm{S}'(\hat{\bm{W}}^{wls})^{-1}$ \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{figure}
-	\input{Figs/pointforerec_schematic.tex}
-	\caption{Summary of probabilistic point reconciliation.
+%	\centering
+%	\begin{tabular}{lll}
+%		\toprule
+%		\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
+%		\midrule
+%		OLS             &
+%		$\bm{I}$  &
+%		$\bm{S}'$  \\
+%		MinT(Sample)    &
+%		$\hat{\bm{W}}^{sam}$ &
+%		$\bm{S}'(\hat{\bm{W}}^{sam})^{-1}$ \\
+%		MinT(Shrink)    &
+%		$\tau\text{Diag}(\hat{\bm{W}}^{sam}) + (1-\tau)\hat{\bm{W}}^{sam}$ &
+%		$\bm{S}'(\hat{\bm{W}}^{shr})^{-1}$ \\
+%		WLS       &
+%		$\text{Diag}(\hat{\bm{W}}^{shr})$ &
+%		$\bm{S}'(\hat{\bm{W}}^{wls})^{-1}$ \\
+%		\bottomrule
+%	\end{tabular}
+%\end{table}
+%
+%
+%\begin{figure}
+%	\input{Figs/pointforerec_schematic.tex}
+%	\caption{Summary of probabilistic point reconciliation.
 The mapping $s\circ g$ projects the unreconciled forecast $\hat{\bm{y}}_{t+h|h}$ onto $\mathfrak{s}$, yielding the reconciled forecast $\tilde{\bm{y}}_{t+h|h}$ with subscripts dropped in the figure for ease of presentation.
 Since the smallest hierarchy involves three dimensions, this figure is only a schematic.}\label{fig:pointfr_sch}
-\end{figure}
-
-The columns of $\bm{S}$ and $\bm{R}$ provide a basis for $\mathbb{R}^n$.
+%\end{figure}
+%
+%The columns of $\bm{S}$ and $\bm{R}$ provide a basis for $\mathbb{R}^n$.
 Therefore any incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$.
@@
 From properties of linear algebra it follows that
-\[
-  \hat{\bm{y}}_{t+h|t} = (\bm{S} ~ \bm{R})
-  \begin{pmatrix}
-  \tilde{\bm{b}}_{t+h|t}\\ \tilde{\bm{a}}_{t+h|t}
-  \end{pmatrix}= \bm{S}\tilde{\bm{b}}_{t+h|t} + \bm{R}\tilde{\bm{a}}_{t+h|t},
-\]
-while the reconciled point forecast is
-\[
-  \tilde{\bm{y}}_{t+h|t} = \bm{S}\tilde{\bm{b}}_{t+h|t}.
-\]
-
-In order to find $\tilde{\bm{b}}_{t+h|t}$ we require the inverse $(\bm{S} ~ \bm{R})^{-1}$ which is given by
-\begin{equation}
-(\bm{S} ~ \bm{R})^{-1} = \begin{pmatrix}
-(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
-\end{pmatrix}\,,
-\end{equation}
-where $\bm{S}_{\bot}$ is the orthogonal complements of $\bm{S}$.
+%\[
+%  \hat{\bm{y}}_{t+h|t} = (\bm{S} ~ \bm{R})
+%  \begin{pmatrix}
+%  \tilde{\bm{b}}_{t+h|t}\\ \tilde{\bm{a}}_{t+h|t}
+%  \end{pmatrix}= \bm{S}\tilde{\bm{b}}_{t+h|t} + \bm{R}\tilde{\bm{a}}_{t+h|t},
+%\]
+%while the reconciled point forecast is
+%\[
+%  \tilde{\bm{y}}_{t+h|t} = \bm{S}\tilde{\bm{b}}_{t+h|t}.
+%\]
+%
+%
+%In order to find $\tilde{\bm{b}}_{t+h|t}$ we require the inverse $(\bm{S} ~ \bm{R})^{-1}$ which is given by
+%\begin{equation}
+%(\bm{S} ~ \bm{R})^{-1} = \begin{pmatrix}
+%(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
+%\end{pmatrix}\,,
+%\end{equation}
+%where $\bm{S}_{\bot}$ is the orthogonal complements of $\bm{S}$.
 Thus it follows that $\tilde{\bm{b}}_{t+h|t}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$.
 Here $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ corresponds to $\bm{G}$ as defined previously.
-
-Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$.
+%
+%Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$.
 For example OLS minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$, while \citet{Wickramasuriya2017} show that MinT minimises the Mahalonobis distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$.
@@
 Therefore bottom-up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.
-
-Before generalising the concept of point reconciliation to probabilistic forecasts, we state two theorems that motivate the use of projections for point forecast reconciliation.
+%
+%Before generalising the concept of point reconciliation to probabilistic forecasts, we state two theorems that motivate the use of projections for point forecast reconciliation.
 First, let $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ and assume $\hat{\bm{y}}_{t+h|t}$ is an unbiased prediction; that is $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\mu_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
-
-\begin{theo}[Unbiasedness preserving property]
-  For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also an unbiased prediction as long as $s\circ g$ is a projection.
-\end{theo}
-\begin{proof}
-	The expected value of the reconciled forecast is given by
-	\[
-  	\E_{1:t}(\tilde{\bm{y}}_{t+h|t})
-	  = \E_{1:t}(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t})
-  	= \bm{S}\bm{G}\E_{1:t}(\hat{\bm{y}}_{t+h|t})
-    = \bm{S}\bm{G}\bm{\mu}_{t+h|t}.
-	\]
-	Since the aggregation constraints hold for the true data generating process, $\bm{\mu}_{t+h|t}$ must lie in $\mathfrak{s}$.
+%
+%\begin{theo}[Unbiasedness preserving property]
+%  For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also an unbiased prediction as long as $s\circ g$ is a projection.
+%\end{theo}
+%\begin{proof}
+%	The expected value of the reconciled forecast is given by
+%	\[
+%  	\E_{1:t}(\tilde{\bm{y}}_{t+h|t})
+%	  = \E_{1:t}(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t})
+%  	= \bm{S}\bm{G}\E_{1:t}(\hat{\bm{y}}_{t+h|t})
+%    = \bm{S}\bm{G}\bm{\mu}_{t+h|t}.
+%	\]
+%	Since the aggregation constraints hold for the true data generating process, $\bm{\mu}_{t+h|t}$ must lie in $\mathfrak{s}$.
 If $\bm{S}\bm{G}$ is a projection, then it is equivalent to the identity map for all vectors that lie in its range.
 Therefore $\bm{S}\bm{G}\bm{\mu}_{t+h|t}=\bm{\mu}_{t+h|t}$ when $\bm{S}\bm{G}$ is a projection matrix.
-\end{proof}
-We note the same result does not hold for general $g$ even when the range of $s\circ g$ is $\mathfrak{s}$.
+%\end{proof}
+%We note the same result does not hold for general $g$ even when the range of $s\circ g$ is $\mathfrak{s}$.
 Now let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$, and let $\|\bm{v}\|_2$ be the $L_2$ norm of vector $\bm{v}$.
 The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.
-
-\begin{theo}[Distance reducing property]
-	If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
-	  \begin{equation}
-	    \|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2.
-	  \end{equation}
-\end{theo}
-\begin{proof}
-	Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ whenever $\bm{S}\bm{G}$ is a projection. Therefore
-	\begin{align}
-	\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
-	&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\\
-	\end{align}
-	The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators \citep{Hun2001}, therefore
-	 \begin{equation*}
-	 \|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le
-	 \|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
-	 \end{equation*}
-\end{proof}
-The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.
+%
+%\begin{theo}[Distance reducing property]
+%	If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
+%	  \begin{equation}
+%	    \|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2.
+%	  \end{equation}
+%\end{theo}
+%\begin{proof}
+%	Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ whenever $\bm{S}\bm{G}$ is a projection. Therefore
+%	\begin{align}
+%	\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
+%	&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\\
+%	\end{align}
+%	The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators \citep{Hun2001}, therefore
+%	 \begin{equation*}
+%	 \|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le
+%	 \|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
+%	 \end{equation*}
+%\end{proof}
+%The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.
+%
 
@@
 It is a ``proper'' scoring rule if
-\begin{equation}\label{eq:(3.1.)}
+\begin{equation}\label{eq:prop_score}
 \E_{\bm{Q}}[S(Q,\omega)] \le \E_{\bm{Q}}[S(P,\omega)] ,
@@
 The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the following representation in terms of expectations
-\begin{equation}
+\begin{equation}\label{eq:Energy_score}
 \text{ES}(\breve{\bm{Y}}_{T+h},\bm{y}_{T+h}) =
@@
 
-\section{Simulation study}\label{sec:gaussian}
+\section{A novel non-parametric bootstrap approach}\label{sec:non-para}
 
-We now turn our attention to comparing different reconciliation methods in a simulation study where the data is conditionally Gaussian.
-We choose the Gaussian case due to its analytical tractability which allows for evaluation using all scoring rules (including the log score).
-The non-Gaussian case lies beyond the scope of this simulation study.
+\subsection{Incoherent probabilistic forecasts}
+
+Our proposed method initially involves obtaining probabilistic forecasts without considering the aggregation constraints.
+That is we first get the incoherent probabilistic forecasts.
+Then we reconcile these to obtain the coherent probabilistic forecasts of the hierarchy.
+
+Suppose we fit univariate models for each series in the hierarchy. Based on the fitted models, we obtain the sample paths at time $t+h$ as, 
+\begin{equation}\label{eq:(2.1)}
+\bm{y}^b_{t+h} = E(\bm{y}_{t+h}|\bm{\mathcal{I}}_{t+h}) + \bm{e}^b_{t+h},
+\end{equation}
+where $E(\bm{y}_{t+h}|\bm{\mathcal{I}}_{t+h})$ is the conditional mean of the forecast distribution of the hierarchy at time $t+h$.
+$\bm{e}^b_{t+h}$ denotes the in-sample bootstrapped errors and these captures the contemporaneous correlation structure of the hierarchy.
+
+Let $\hat{\bm{y}}_k \in \mathbb{R}^n$ is a vector comprising the fitted values of each series in the hierarchy at time $k$.
+Further let $\bm{\Gamma}_{(t \times n)}=(\bm{e}_1,\bm{e}_2,.....,\bm{e}_t)'$ denote the in-sample residual matrix where $\bm{e}_k=\bm{y}_k-\hat{\bm{y}}_k$ for $k = 1,\cdots, t$.
+$\hat{\bm{e}}_k \in \mathbb{R}^n$ consists of residuals in each node at time $k$ and stacked in the same order as $\bm{y}_k$.
+We block bootstrap a sample of size $h$ from $\bm{\Gamma}$ which we denoted by $\bm{e}^b_{t+h}$.
+These bootstrapped errors will be incorporated as the error series for simulating future paths in (\ref{eq:(2.1)}).
+Taking blocked bootstrapped in-sample errors in generating future paths will implicitly model the dependency structure of the hierarchy.
+
+Notice that $\bm{y}^b_{t+h} \in \mathbb{R}^n$ does not lie in the coherent subspace.
+Thus we call $\bm{y}^b_{t+h}$ as incoherent sample paths.
+Thousands of these sample paths will form an empirical sample from the incoherent forecast distribution of the hierarchy.
+
+\subsection{Reconciliation of incoherent future paths}
+
+It is expected that the probabilistic forecasts should be coherent in order to reflect the properties of real data.
+Thus we reconcile the incoherent future paths obtained in previous section to get coherent probabilistic forecasts.
+
+Following the definition for reconciliation, we project each sample path to the coherent subspace $\mathfrak{s}$ via the projection $\bm{SG}$. Thus we have, 
+\begin{equation} \label{eq:(2.2)}
+\tilde{\bm{y}}_{t+h}^b = \bm{SG}\bm{y}_{t+h}^b,
+\end{equation} 
+These reconciled future paths will form an empirical sample from the coherent forecast distribution that lies in the coherent subspace.
+
+\subsection{Optimal reconciliation of incoherent future paths}
+
+We propose to find the optimal $\bm{G}$ for reconciling future paths by minimising a proper multivariate scoring rule. The respective objective function can be written as,
+
+\begin{equation} \label{eq:Obj_func_1}
+\operatornamewithlimits{argmin}_{\bm{G}} \quad \E_{Q}[S(\bm{SG}\bm{y}_{t+h}^b, \bm{y}_{t+h})]. 
+\end{equation}
+where $S$ is a proper scoring rule that follows (\ref{eq:prop_score}).
+Recall that the energy score given in (\ref{eq:Energy_score}) is a proper scoring rule and it can be approximated using Monte-Carlo sample paths as follows,
+\begin{equation}\label{eq:ES_with_Samples}
+\text{ES}(\breve{\bm{Y}}_{T+h},\bm{y}_{T+h}) \approx \frac{1}{B}\sum_{i=1}^{B}||\bm{SG}\bm{y}_{T+h,i,j}^b -\bm{y}_{T+h}||-\frac{1}{2(B-1)}\sum_{i=1}^{B-1}||\bm{SG}(\bm{y}_{T+h,i,j}^b -\bm{y}_{T+h,i+1,j}^b)||.
+\end{equation}
+where $B$ is the empirical sample size from the coherent forecast distribution. Now we can rewrite the objective function in (\ref{eq:Obj_func_1}) as,
+
+\begin{equation}\label{eq:Obj_func_2}
+\operatornamewithlimits{argmin}_{\bm{G}} \frac{1}{N}\sum_{j=1}^{N}\left\{\frac{1}{B}\sum_{i=1}^{B}||\bm{SG}\bm{y}_{T+h,i,j}^b -\bm{y}_{T+h}||-\frac{1}{2(B-1)}\sum_{i=1}^{B-1}||\bm{SG}(\bm{y}_{T+h,i,j}^b -\bm{y}_{T+h,i+1,j}^b)||\right\}
+\end{equation}
+
+We can use numerical optimization methods to find the matrix $\bm{G}$ that minimizes above objective function and thus obtain the reconciled future paths.
+
+%We propose to find an optimal $\bm{G}$ for reconciling future paths by minimizing a proper scoring rule defined in \ref{eq:prop_score}.
+Scoring rule is a numerical value  $Sc(\breve{\bm{Y}},\bm{y})$ assign to each pair $(\breve{\bm{Y}},\bm{y})$, where $\breve{\bm{Y}}$ is a $n$-dimensional random vector from the forecast distribution $\breve{\bm{F}}$ and $\bm{y}$ is a realization.
+A proper scoring rule is defined as,
+%\begin{equation}\label{eq:(2.3)}
+%\E_{\bm{G}}[Sc(\bm{Y},\bm{y})] \le \E_{\bm{G}}[Sc(\breve{\bm{Y}},\bm{y})],
+%\end{equation}
+%where $\bm{Y}$ is a random variable from the true distribution $\bm{G}$ \citep{Gneiting2014}.
+%
+%Thus the minimization problem for finding the optimal $\bm{R}_\bot$ will be 
+%\begin{equation}
+%\operatornamewithlimits{argmin}_{\bm{R}'_\bot} \quad \E_{\bm{G}}[Sc(\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot\bm{y}_{t+h}^b, \bm{y}_{t+h})]. 
+%\end{equation}
+
+\subsection{Simulation study}\label{sec:Bootsrap-sim}
+
+We now turn our attention to comparing different reconciliation methods with optimal reconciliation in a simulation study.
 
@@
 
-First $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from ARIMA$(p,d,q)$ processes, where $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability.
+\textcolor{red}{Explain the data generating process - Dependence structure is imposed with copula.}
+%First $\{w_{AA,t},w_{AB,t},w_{BA,t},w_{BB,t}\}$ are generated from ARIMA$(p,d,q)$ processes, where $(p,q)$ and $d$ take integers from $\{1,2\}$ and $\{0,1\}$ respectively with equal probability.
 The errors driving these ARIMA processes are jointly normal, and denoted by $\{\varepsilon_{AA,t},\varepsilon_{AB,t},\varepsilon_{BA,t},\varepsilon_{BB,t}\} \overset{iid}{\sim} \mathcal{N}(\bm{0}, \bm{\Sigma})~\forall t$.
@@
 Then the bottom-level series $\{y_{AA,t},y_{AB,t},y_{BA,t},y_{BB,t}\}$ are given by:
-\begin{align*}
-y_{AA,t} &= w_{AA,t} + u_t - 0.5v_t,\\
-y_{AB,t} &= w_{AB,t} - u_t - 0.5v_t,\\
-y_{BA,t} &= w_{BA,t} + u_t + 0.5v_t,\\
-y_{BB,t} &= w_{BB,t} - u_t + 0.5v_t,
-\end{align*}
-where $u_t \sim \mathcal{N}(0,\sigma^2_u)$ and $v_t \sim \mathcal{N}(0,\sigma^2_v)$. The aggregate series in the middle-level are given by:
-\begin{align*}
-y_{A,t} &= w_{AA,t} + w_{AB,t} - v_t,\\
-y_{B,t} &= w_{BA,t} + w_{BB,t} + v_t,
-\end{align*}
-and the total series is given by
-\[
-  y_{Tot,t} = w_{AA,t} + w_{AB,t} + w_{BA,t} + w_{BB,t}.
-\]
+%\begin{align*}
+%y_{AA,t} &= w_{AA,t} + u_t - 0.5v_t,\\
+%y_{AB,t} &= w_{AB,t} - u_t - 0.5v_t,\\
+%y_{BA,t} &= w_{BA,t} + u_t + 0.5v_t,\\
+%y_{BB,t} &= w_{BB,t} - u_t + 0.5v_t,
+%\end{align*}
+%where $u_t \sim \mathcal{N}(0,\sigma^2_u)$ and $v_t \sim \mathcal{N}(0,\sigma^2_v)$. The aggregate series in the middle-level are given by:
+%\begin{align*}
+%y_{A,t} &= w_{AA,t} + w_{AB,t} - v_t,\\
+%y_{B,t} &= w_{BA,t} + w_{BB,t} + v_t,
+%\end{align*}
+%and the total series is given by
+%\[
+%  y_{Tot,t} = w_{AA,t} + w_{AB,t} + w_{BA,t} + w_{BB,t}.
+%\]
+
 To ensure the disaggregate series are noisier than the aggregate series, we choose $\bm{\Sigma}, \sigma^2_u$ and $\sigma^2_v$ such that
@@
 and similar inequalities hold when $\varepsilon_{AA,t}$ is replaced by $\varepsilon_{AB,t}$, $\varepsilon_{BA,t}$ and $\varepsilon_{BB,t}$ in the third term.
-The values of $\bm{\Sigma}$, $\sigma^2_u$ and $\sigma^2_v$ that we use and which satisfy these constraints are $\sigma^2_u = 19$, $\sigma^2_u = 18$ and
+The values of $\bm{\Sigma}$, $\sigma^2_u$ and $\sigma^2_v$ that we use and which satisfy these constraints are $\sigma^2_u = 10$, $\sigma^2_v = 7$ and
 \[
@@
 
-We generate data with a sample size of $T=501$.
+\textcolor{red}{
+	\begin{itemize}
+		\item Explain how the simulation is set up including the optimal reconciliation
+		\item Evaluation process - Used skill scores
+		\item Discussion of results
+	\end{itemize}}
+%We generate data with a sample size of $T=501$.
 Univariate ARIMA models are selected for each series using the \textit{auto.arima} function in the \textit{forecast} package \citep{hyndman2017forecasting} in R \citep{Rcore}.
@@
 
-To assess the predictive performance of different forecasting methods, we use scoring rules as discussed in Section~\ref{sec:evaluation}.
+%To assess the predictive performance of different forecasting methods, we use scoring rules as discussed in Section~\ref{sec:evaluation}.
 To facilitate comparisons, we report skill scores \citep{Gneiting2007}.
 For a given forecasting method, evaluated by a particular scoring rule, the skill score
-gives the percentage improvement of the preferred forecasting method relative to a reference method.
+%gives the percentage improvement of the preferred forecasting method relative to a reference method.
 A negative valued skill score indicates that a method is worse than the reference method, whereas any positive value indicates that the method is superior to the reference method.
-
-Table~\ref{table:3} summarizes the forecasting performance of unreconciled, bottom-up, OLS, WLS and two MinT reconciliation methods using log score, energy score and variogram score.
+%
+%Table~\ref{table:3} summarizes the forecasting performance of unreconciled, bottom-up, OLS, WLS and two MinT reconciliation methods using log score, energy score and variogram score.
 In all cases skill scores are calculated with the bottom-up method as reference.
@@
 Bottom-up forecasts perform even worse than unreconciled forecasts in some cases.
-
-Tables~\ref{table:4} and~\ref{table:5} break down the forecasting performance of different reconciliation methods by considering univariate scores on each individual margin.
+%
+%Tables~\ref{table:4} and~\ref{table:5} break down the forecasting performance of different reconciliation methods by considering univariate scores on each individual margin.
 Tables~\ref{table:4} summarises results for the top and middle-level, Table~\ref{table:5} does the same for bottom-level.
@@
 When broken down in this fashion, the methods based on MinT perform best for all series and always outperform bottom-up and unreconciled forecasts.
+%
 
-\begin{table}
-	\caption{Comparison of coherent forecasts.
-``Energy score'' and ``Variogram score'' columns give scores based on the joint forecast distribution of the whole hierarchy.
-``Log score'' column gives the log scores of the joint forecast distribution of the bottom-level.
-``Skill score'' columns give the percentage skill score with reference to the bottom-up method.
-Entries in these columns show the percentage increase of scores for different reconciliation methods relative to the bottom-up method.}\label{table:3}
-
-	\centering\small
-	\begin{tabular}{@{}lSSSSSS@{}}
-		\toprule
-		Forecasting &
-		\multicolumn{2}{c}{\text{Energy score}} &
-		\multicolumn{2}{c}{\text{Variogram score}} &
-		\multicolumn{2}{c}{\text{Log score}} \\
-		\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(l){6-7}
-		method &
-		\text{Mean score} & \text{Skill score \%} &
-		\text{Mean score} & \text{Skill score \%} &
-		\text{Mean score} & \text{Skill score \%}\\
-		\midrule
-		MinT(Shrink) &  10.03 & 18.79  & 8.44  & 8.46 & 11.30 &  6.22 \\
-		MinT(Sample) &  10.01 & 18.95  & 8.41  & 8.79 & 11.29 &  6.31 \\
-		MinT(WLS)    &  10.53 & 14.74  & 9.02  & 2.17 & 12.61 & -4.65 \\
-		OLS          &  10.53 & 14.74  & 8.86  & 3.09 & 11.54 &  4.23\\
-		Bottom-up    &  12.35 &    	   & 9.22  &      & 12.05 &  \\
-		Incoherent	 &  11.12 &   	   & 9.53  &      &       &  \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{table}
-	\caption{Comparison of incoherent vs coherent forecasts based on the univariate forecast distribution of aggregate series.
-The ``Incoherent'' row shows the average scores for incoherent forecasts.
-Each entry above this row represents the percentage skill score with reference to the incoherent forecasts.
-These entries show the percentage increase in score for different forecasting methods relative to the incoherent forecasts.}\label{table:4}
-	\centering\small
-	\begin{tabular}{@{}lSSSSSS@{}}
-		\toprule
-		Forecasting &
-		\multicolumn{2}{c}{\text{Total}} &
-		\multicolumn{2}{c}{\text{Series - A}} &
-		\multicolumn{2}{c}{\text{Series - B}} \\
-		\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(l){6-7}
-		method      &  CRPS   & LogS    & CRPS   & LogS     & CRPS   & LogS     \\
-		\midrule
-		MinT(Shrink) &   0.74  &   0.00   & 10.49   &  3.24  &  9.16  &  2.73    \\
-		MinT(Sample) &   0.74  &   0.00   & 10.49   &  3.24  &  9.16  &  2.73    \\
-		MinT(WLS)    &  -2.96  &  -2.36   &  6.10   & -4.12  &  5.66  & -3.03    \\
-		OLS          &  -9.26  &  -3.36   &  7.07   &  2.06  &  7.01  &  1.82    \\
-		Bottom-up    & -91.48  & -22.22   & -8.05   & -2.06  & -6.20  & -1.82    \\
-		\midrule
-		\textit{Incoherent} & $\mathbi{2.70}$ & $\mathbi{2.97}$ & $\mathbi{4.10}$ & $\mathbi{3.40}$ & $\mathbi{3.71}$ & $\mathbi{3.30}$ \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{table}
-	\caption{Comparison of incoherent vs coherent forecasts based univariate forecast distribution of bottom-level series.
-The ``Incoherent'' row shows the average scores for incoherent forecasts.}\label{table:5}
-	\centering\tabcolsep=0.08cm\small
-	\begin{tabular}{@{}lSSSSSSSS@{}}
-		\toprule
-		Forecasting &
-		\multicolumn{2}{c}{\text{Series - AA}} &
-		\multicolumn{2}{c}{\text{Series - AB}} &
-		\multicolumn{2}{c}{\text{Series - BA}} &
-		\multicolumn{2}{c}{\text{Series - BB}} \\
-		\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(l){8-9}
-		method       & CRPS   & LogS    & CRPS   & LogS    & CRPS   & LogS    & CRPS   & LogS \\
-		\midrule
-		MinT(Shrink) &  7.61  &  2.43  &  10.82  &  3.02  &  5.93  &  1.86  &  7.76  & 2.47  \\
-		MinT(Sample) &  7.88  &  2.43  &  11.08  &  3.02  &  6.20  &  1.86  &  8.05  & 2.47  \\
-		MinT(WLS)    &  3.53  &  0.00  &   6.33  &  0.60  &  2.43  & -0.62  &  4.89  & 0.62  \\
-		OLS          &  2.99  &  0.91  &   5.28  &  1.51  &  2.90  &  0.62  &  4.31  & 1.23  \\
-		\midrule
-		\textit{Incoherent} & $\mathbi{3.68}$ & $\mathbi{3.29}$ & $\mathbi{3.79}$ & $\mathbi{3.31}$ & $\mathbi{3.45}$ & $\mathbi{3.22}$ & $\mathbi{3.48}$ & $\mathbi{3.24}$ \\
-		\bottomrule
-	\end{tabular}
-\end{table}
+\section{Forecasting Australian domestic tourism flow}
 
@@
 
-By redefining coherent forecasts and forecast reconciliation in geometric terms, we have established two new theoretical results that support the use of projections for point forecast reconciliation, and have allowed us to extend these concepts to probabilistic forecasting.
+%By redefining coherent forecasts and forecast reconciliation in geometric terms, we have established two new theoretical results that support the use of projections for point forecast reconciliation, and have allowed us to extend these concepts to probabilistic forecasting.
 We have shown that for elliptical distributions the true predictive density can be recovered by linear reconciliation and we have established conditions for when this is a projection.
@@
 Finally, we have also discussed strategies for evaluating probabilistic forecasts for hierarchical time series advocating the use of multivariate scoring rules on the full hierarchy, while establishing a key result regarding the impropriety of the log score with respect to incoherent forecasts.
-
-In many ways this paper sets up a substantial future research agenda.
+%
+%In many ways this paper sets up a substantial future research agenda.
 For example, having defined what amounts to an entire class of reconciliation methods for probabilistic forecasts it will be worthwhile investigating which specific projections are optimal.

### 2019-04-11 Probabilistic-forecasts-for-hierarchical-time-series/Supplementary-material/Supplementary-material.tex
Outlined first two papers

--- 2018-08-24 ProbabilisticCoherence.tex
@@
 
-\begin{abstract}
-  Forecast reconciliation involves adjusting forecasts to ensure coherence with aggregation constraints.
-We extend this concept from point forecasts to probabilistic forecasts by redefining forecast reconciliation in terms of linear functions in general, and projections more specifically.
-New theorems establish that the true predictive distribution can be recovered in the elliptical case by linear reconciliation, and general conditions are derived for when this is a projection.
-A geometric interpretation is also used to prove two new theoretical results for point forecasting; that reconciliation via projection both preserves unbiasedness and dominates unreconciled forecasts in a mean squared error sense.
-Strategies for forecast evaluation based on scoring rules are discussed, and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive distribution coheres with aggregation constraints.
-Finally, evidence from a simulation study shows that reconciliation based on an oblique projection, derived from the MinT method of \citet{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
-\end{abstract}
+\section{Supplementary material}
 
-\noindent%
-{\it Keywords:}  Forecast Reconciliation, Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
-\vfill
+\subsection{Simulation study - under Gaussian assumptions}\label{sec:gaussian}
 
-\newpage
-\spacingset{1.45} % DON'T change the spacing!
-
-\section{Introduction}\label{sec:intro}
-
-Large collections of time series often follow some aggregation structure.
-For example, the electricity demand of a country can be disaggregated according to a geographic hierarchy of states, cities, and individual households.
-To ensure aligned decision making, it is important that forecasts at the most disaggregated level add up to forecasts at more aggregated levels.
-This property is called ``coherence''.
-On the other hand ``reconciliation'' is a process whereby incoherent forecasts are made coherent.
-Both of these concepts have been developed extensively for point forecasting.
-Generalising both of these concepts, particularly the latter, to probabilistic forecasting is a gap that we seek to address in this work.
-We do so by first providing a novel geometric interpretation to coherence and reconciliation in the point forecasting case.
-This can easily be generalised to probabilistic forecasting allowing us to derive further results for elliptical distributions as well as provide insight into forecast evaluation via multivariate  scoring rules.
-
-Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level of the hierarchy.
-To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$ and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.
-In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (series $AA$, $AB$, $BA$ and $BB$) and then summed to recover forecasts for all higher-level series.
-Alternatively, in the top-down approach \citep{Gross1990}, a top-level forecast is first produced (series $Tot$) and bottom-level forecasts are recovered by disaggregating the forecast using either historical or forecasted proportions.
-A middle-out approach is a hybrid between these two, that for the hierarchy in Figure~\ref{fig1} would produce first stage forecasts for series $A$ and $B$.
-
-\begin{figure}[H]
-	\begin{center}
-		\leaf{AA} \leaf{AB}
-		\branch{2}{A}
-		\leaf{BA} \leaf{BB}
-		\branch{2}{B}
-		\branch{2}{Tot}
-		\qobitree
-	\end{center}
-	\caption{An example of a two level hierarchical structure.}\label{fig1}
-\end{figure}
-
-In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular.
-For these methods, first stage forecasts are independently produced for all series rather than series at a single level.
-Since these so-called `base' forecasts are rarely coherent in practice, they are subsequently adjusted or `reconciled' to ensure coherence.
-Note that we use coherence and reconciliation as distinct terms, in contrast to their at times ambiguous usage in the past.
-To date, reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators.
-These include Ordinary Least Squares {OLS} \citep{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix.
-These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{AthEtAl2009,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and, in some sense, hedge against the risk of model misspecification at a single level.
-
-A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \citep[see][and references therein]{Gneiting2014}.
-Indeed to the best of our knowledge, the (as yet unpublished) work of \citep{BenTaieb2017} is the only paper to deal with coherent probabilistic forecasts, and although they reconcile the means of the predictive distributions, the overall distributions are constructed in a bottom-up fashion rather than use a reconciliation process.
-In contrast, the main objective of our paper is to generalise both coherence and reconciliation from point to probabilistic forecasting.
-
-To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections.
-In addition to being highly intuitive, this allows us to establish a number of theoretical results.
-We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts, while the second shows that reconciled forecasts dominate unreconciled forecasts via the distance reducing property of projections.
-We provide definitions of coherence and forecast reconciliation in the probabilistic setting, and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation.
-We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class.
-We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly estimated in practice, we provide a heuristic argument in favour of MinT reconciliation.
-
-We also cover the topic of forecast evaluation of probabilistic forecasts via scoring rules.
-In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.
-Therefore we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts.
-Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.
-
-The remainder of the paper is structured as follows.
-In Section~\ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.
-Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results.
-In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules, while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian}.
-Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.
-
-\section{Coherent forecasts}\label{sec:definitions}
-
-\subsection{Notation and preliminaries}\label{sec:notation}
-
-A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables.
-We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$.
-The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.
-The hierarchical structure of the data implies that
-\begin{equation}
-\bm{y}_t = \bm{Sb}_t,
-\end{equation}
-where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints, holds for all $t$.
-
-To clarify these concepts consider the example of the hierarchy in Figure~\ref{fig1}.
-For this hierarchy, $n=7$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$ and
-\[
-  \bm{S} = \begin{pmatrix}
-               1 & 1 & 1 & 1  \\
-               1 & 1 & 0 & 0 \\
-               0 & 0 & 1 & 1 \\
-               & \multicolumn{2}{c}{\bm{I}_4} &
-           \end{pmatrix},
-\]
-where $\bm{I}_4$ is the $4\times 4$ identity matrix.
-
-While most applications of hierarchical time series to date have involved data that respect an aggregation structure, in principle the matrix ${\bm S}$ can encode any linear constraints including weighted sums or even cases where some variables in the hierarchy are formed by taking the difference of two other variables.
-
-\subsection{Coherent point forecasts}\label{sec:cohpointf}
-
-It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect inherent aggregation constraints.
-We follow other authors \citep{Wickramasuriya2017, FPP2018} in using the nomenclature \emph{coherence} to describe this property.
-We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem, thus facilitating the development of probabilistic forecast reconciliation in Section~\ref{sec:reconciliation}.
-
-\begin{definition}[Coherent subspace]\label{def:cohspace}
- The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$, is defined as the \emph{coherent space}.
-\end{definition}
-
-It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$.
-Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.
-
-\begin{figure}[H]
-  \begin{center}
-    \begin{tikzpicture}[
-    >=stealth,
-    bullet/.style={
-      fill=black,
-      circle,
-      minimum width=1.5cm,
-      inner sep=0pt
-    },
-    projection/.style={
-      ->,
-      thick,
-      label,
-      shorten <=2pt,
-      shorten >=2pt
-    },
-    every fit/.style={
-      ellipse,
-      draw,
-      inner sep=0pt
-    }
-    ]
-    \node at (2,3) {$s$};
-    \node at (0,5) {$\mathbb{R}^m$(domain of $s$)};
-    \node at (4,5) {$\mathbb{R}^n$(codomain of $s$)};
-    \node at (4.7,2.0) {$\mathfrak{s}$(image of $s$)};
-    %\node[bullet,label=below:$f(x)$] at (4,2.5){};
-    \draw (0,2.5) ellipse (1.02cm and 2.2cm);
-    \draw (4,2.5) ellipse (1.02cm and 2.2cm);
-    \draw (4,2.5) ellipse (0.51cm and 1.1cm);
-    \draw[projection, label=below:$f$] (0.3,2.5) -- (3.8,2.5) ;
-    \end{tikzpicture}
-  \end{center}
-  \caption{The domain, codomain and image of the mapping $s$.}\label{fig2}
-\end{figure}
-
-\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
-  Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a point forecast of the values of all series in the hierarchy at time $t+h$, made using information up to and including time $t$.
-Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathfrak{s}$.
-\end{definition}
-
-\subsection{Coherent probabilistic forecasts}\label{sec:cohprobf}
-
-Let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple, where $\mathscr{F}_{\mathbb{R}^m}$ is the usual Borel $\sigma$-algebra on $\mathbb{R}^m$.
-Let $\breve{\nu}$ be a probability measure on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_{\mathfrak{s}}$.
-Here $\mathscr{F}_{\mathfrak{s}}$ is a collection of sets $s(\mathcal{B})$, where $s(\mathcal{B})$ denotes the image of the set $\mathcal{B}\in \mathscr{F}_{\mathbb{R}^m}$ under the mapping $s(.)$.
-
-\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
-  The measure $\breve{\nu}$ is coherent if it has the property
-  \[
-    \breve{\nu}(s(\mathcal{B})) = \nu(\mathcal{B}) \quad \forall \mathcal{B} \in \mathscr{F}_{\mathbb{R}^m},
-  \]
-\end{definition}
-
-A probabilistic forecast for time $t+h$ is coherent if uncertainty in $\bm{\breve{y}}_{t+h}$ conditional on all information up to time $t$ is characterised by the probability triple $(\mathfrak{s},\mathscr{F}_{\mathfrak{s}},\breve{\nu})$.
-
-These definitions of the coherent space $\mathfrak{s}$, coherent point and coherent probabilistic forecasts in terms of the mapping $s(.)$, may give the impression that the bottom-level series play an important role.
-However, alternative definitions could be formed using any set of basis vectors that span $\mathfrak{s}$.
-For example, consider the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$.
-In this case the matrix $\bm{S}$ has columns $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$, and pre-multiplying by $\bm{S}$ transforms arbitrary values of $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy.
-However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy.
-The definitions above could be made in terms of any series and not just the bottom-level series.
-In general, we call the series (or linear combinations thereof) used in the definitions of coherence \textit{basis series}.
-Unless stated otherwise, we will always assume that the basis series are the bottom-level series as in Definition~\ref{def:cohpoint} and Definition~\ref{def:cohprob}, since this facilitates comparison with existing approaches in the literature.
-
-To the best of our knowledge, the only other definition of coherent probabilistic forecasts is given by \citet{BenTaieb2017} who define coherent probabilistic forecasts in terms of convolutions.
-According to their definition, probabilistic forecasts are coherent when a convolution of forecast distributions of disaggregate series is identical to the forecast distribution of the corresponding aggregate series.
-Their definition is consistent with our definition; our reason for providing a different definition is that the geometric understanding of coherence will facilitate our definitions of point and probabilistic forecast reconciliation to which we now turn our attention.
-
-\section{Forecast reconciliation}\label{sec:reconciliation}
-
-As discussed, reconciliation is distinct from coherence, since the former refers to a process whereby incoherent forecasts are made coherent.
-Although reconciliation methods for point forecasts are extant in the literature they are rarely defined explicitly.
-We do so here in slightly more general terms than usual.
-We then extend this idea to the novel concept of probabilistic reconciliation.
-
-\subsection{Point forecast reconciliation}
-
-Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ conditional on information up to and including time $t$.
-We now introduce a linear function that converts unreconciled forecasts into new bottom level forecasts.
-Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively, and let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})=\bm{G}\bm{y}+\bm{d}$.
-A composition of $g$ and $s(.)$ gives the following definition for point forecast reconciliation.
-
-\begin{definition}\label{def:reconpoint}
-	The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $g(.)$ iff
-	\begin{equation}
-	  \tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{G}\hat{\bm{y}}_{t+h|t}+\bm{d})\,.
-	\end{equation}
-\end{definition}
-
-Several choices of $g(.)$ currently extant in the literature, including the OLS, WLS and MinT methods, are special cases where $s\circ g$ is a projection.
-These can be defined so that $\bm{G}=({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ and $\bm{d}=\bm{0}$, were, ${\bm{R}_{\perp}}$ is a $n\times m$ orthogonal complement to an $n \times (n-m)$ matrix $\bm{R}$, where the columns of the latter span the null space of $\mathfrak{s}$.
-For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
-In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
-For this three variable hierarchy, $\bm{R}_\perp'=\bm{S}$ and reconciliation corresponds to the OLS method.
-For the case where $\bm{R}_\perp'\neq\bm{S}$, for example WLS and MinT, there are two possible interpretations.
-One is that these are oblique projections in Euclidean space where the columns of $\bm{R}$ are `directions' along which incoherent point forecasts are projected onto the coherent space $\mathfrak{s}$.
-Alternatively, since $\bm{R}_\perp'$ is usually written in the form $\bm{S}'{\bm{W}}^{-1}$, these projections can be thought of as orthogonal projections after pre-multiplying by ${\bm{W}^{-1/2}}$.
-A schematic providing a geometric interpretation of point reconciliation is given in Figure~\ref{fig:pointfr_sch}, while Table~\ref{table:2} summarises existing reconciliation methods.
-
-\begin{table}[!h]
-	\caption{Summary of reconciliation methods that are projections.
-Here, $\hat{\bm{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, $\hat{\bm{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}, $\hat{\bm{W}}^{wls}$ is the diagonal matrix with diagonal elements $w_{ii}$, and $\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$, where $w_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{W}}^{sam}$.}\label{table:2}
-	\centering
-	\begin{tabular}{lll}
-		\toprule
-		\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
-		\midrule
-		OLS             &
-		$\bm{I}$  &
-		$\bm{S}'$  \\
-		MinT(Sample)    &
-		$\hat{\bm{W}}^{sam}$ &
-		$\bm{S}'(\hat{\bm{W}}^{sam})^{-1}$ \\
-		MinT(Shrink)    &
-		$\tau\text{Diag}(\hat{\bm{W}}^{sam}) + (1-\tau)\hat{\bm{W}}^{sam}$ &
-		$\bm{S}'(\hat{\bm{W}}^{shr})^{-1}$ \\
-		WLS       &
-		$\text{Diag}(\hat{\bm{W}}^{shr})$ &
-		$\bm{S}'(\hat{\bm{W}}^{wls})^{-1}$ \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{figure}
-	\input{Figs/pointforerec_schematic.tex}
-	\caption{Summary of probabilistic point reconciliation.
-The mapping $s\circ g$ projects the unreconciled forecast $\hat{\bm{y}}_{t+h|h}$ onto $\mathfrak{s}$, yielding the reconciled forecast $\tilde{\bm{y}}_{t+h|h}$ with subscripts dropped in the figure for ease of presentation.
-Since the smallest hierarchy involves three dimensions, this figure is only a schematic.}\label{fig:pointfr_sch}
-\end{figure}
-
-The columns of $\bm{S}$ and $\bm{R}$ provide a basis for $\mathbb{R}^n$.
-Therefore any incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$.
-Let $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$ respectively, after a change of basis.
-The process of reconciliation involves setting the values of the reconciled bottom-level series to be $\tilde{\bm{b}}_{t+h|t}$, and ignoring $\tilde{\bm{a}}_{t+h|t}$ to ensure coherence.
-From properties of linear algebra it follows that
-\[
-  \hat{\bm{y}}_{t+h|t} = (\bm{S} ~ \bm{R})
-  \begin{pmatrix}
-  \tilde{\bm{b}}_{t+h|t}\\ \tilde{\bm{a}}_{t+h|t}
-  \end{pmatrix}= \bm{S}\tilde{\bm{b}}_{t+h|t} + \bm{R}\tilde{\bm{a}}_{t+h|t},
-\]
-while the reconciled point forecast is
-\[
-  \tilde{\bm{y}}_{t+h|t} = \bm{S}\tilde{\bm{b}}_{t+h|t}.
-\]
-
-In order to find $\tilde{\bm{b}}_{t+h|t}$ we require the inverse $(\bm{S} ~ \bm{R})^{-1}$ which is given by
-\begin{equation}
-(\bm{S} ~ \bm{R})^{-1} = \begin{pmatrix}
-(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
-\end{pmatrix}\,,
-\end{equation}
-where $\bm{S}_{\bot}$ is the orthogonal complements of $\bm{S}$.
-Thus it follows that $\tilde{\bm{b}}_{t+h|t}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$.
-Here $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ corresponds to $\bm{G}$ as defined previously.
-
-Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$.
-For example OLS minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$, while \citet{Wickramasuriya2017} show that MinT minimises the Mahalonobis distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$.
-Bottom-up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom-level series.
-Therefore bottom-up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.
-
-Before generalising the concept of point reconciliation to probabilistic forecasts, we state two theorems that motivate the use of projections for point forecast reconciliation.
-First, let $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ and assume $\hat{\bm{y}}_{t+h|t}$ is an unbiased prediction; that is $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\mu_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
-
-\begin{theo}[Unbiasedness preserving property]
-  For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also an unbiased prediction as long as $s\circ g$ is a projection.
-\end{theo}
-\begin{proof}
-	The expected value of the reconciled forecast is given by
-	\[
-  	\E_{1:t}(\tilde{\bm{y}}_{t+h|t})
-	  = \E_{1:t}(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t})
-  	= \bm{S}\bm{G}\E_{1:t}(\hat{\bm{y}}_{t+h|t})
-    = \bm{S}\bm{G}\bm{\mu}_{t+h|t}.
-	\]
-	Since the aggregation constraints hold for the true data generating process, $\bm{\mu}_{t+h|t}$ must lie in $\mathfrak{s}$.
-If $\bm{S}\bm{G}$ is a projection, then it is equivalent to the identity map for all vectors that lie in its range.
-Therefore $\bm{S}\bm{G}\bm{\mu}_{t+h|t}=\bm{\mu}_{t+h|t}$ when $\bm{S}\bm{G}$ is a projection matrix.
-\end{proof}
-We note the same result does not hold for general $g$ even when the range of $s\circ g$ is $\mathfrak{s}$.
-Now let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$, and let $\|\bm{v}\|_2$ be the $L_2$ norm of vector $\bm{v}$.
-The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.
-
-\begin{theo}[Distance reducing property]
-	If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
-	  \begin{equation}
-	    \|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2.
-	  \end{equation}
-\end{theo}
-\begin{proof}
-	Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ whenever $\bm{S}\bm{G}$ is a projection. Therefore
-	\begin{align}
-	\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
-	&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\\
-	\end{align}
-	The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators \citep{Hun2001}, therefore
-	 \begin{equation*}
-	 \|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le
-	 \|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
-	 \end{equation*}
-\end{proof}
-The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.
-
-\subsection{Probabilistic forecast reconciliation}
-
-We now extend the methodology of point forecast reconciliation to probabilistic forecasts.
-%For probabilistic forecasts, reconciliation implies finding the probability measure of the coherent forecasts using the information from an incoherent probabilistic forecast measure.
-A more formal definition is given below.
-Let $(\mathbb{R}^n, \mathscr{F}_{\mathbb{R}^n}, \hat{\nu})$ be a probability triple that is not coherent and which characterises forecast uncertainty for all variables in the hierarchy at time $t+h$ conditional on all information up to time $t$.
-This is obtained from the first stage of the forecasting process; e.g., by modelling and forecasting each series individually.
-Let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m $ be a linear function, and let $(\mathbb{R}^m, \mathscr{F}_{\mathbb{R}^m}, \nu)$ be a probability triple defined on $\mathbb{R}^m$.
-
-\begin{definition} \label{def:reconprob}
-  The reconciled probability measure of $\hat{\nu}$ with respect to the mapping $g(.)$ is a probability measure $\tilde{\nu}$ on $\mathfrak{s}$ with $\sigma$-algebra $\mathscr{F}_\mathfrak{s}$ such that
-  \begin{equation}
-  \tilde{\nu}(s(\mathcal{B})) = \nu(\mathcal{B})= \hat{\nu}(g^{-1}(\mathcal{B})) \qquad \forall \mathcal{B} \in \mathscr{F}_{\mathbb{R}^m}\,,
-  \end{equation}
-  where $g^{-1}(\mathcal{B}):=\{\breve{\bm{y}}\in \mathbb{R}^n:g(\breve{\bm{y}})\in \mathcal{B}\}$ is the pre-image of $\mathcal{B}$, that is the set of all points in $\mathbb{R}^n$ that $g(.)$ maps to a point in $\mathcal{B}$.
-\end{definition}
-
-This definition extends the notion of forecast reconciliation to the probabilistic setting.
-Under point reconciliation methods, the reconciled point forecast is equal to the unreconciled point forecast after the latter is passed through two linear functions.
-Similarly, probabilistic forecast reconciliation assigns the same probability to two sets where the points in one set are obtained by passing all points in the other set through two linear functions.
-This is depicted in Figure~\ref{fig:probfr_sch} schematically when $s\circ g$ is a projection.
-
-\begin{figure}
-	\input{Figs/probforerec_schematic.tex}
-	\caption{Summary of probabilistic forecast reconciliation.
-The probability that $\bm{y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that $\bm{y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast.
-Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic.}\label{fig:probfr_sch}
-\end{figure}
-
-Recall that when $s\circ g$ is a projection, the case of point forecast reconciliation can be broken down into three steps.
-\begin{compactenum}
-\item  $\hat{\bm{y}}_{t+h|t}$ is transformed into coordinates $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ via a change of basis.
-\item $\tilde{\bm{a}}_{t+h|t}$ is discarded and $\tilde{\bm{b}}_{t+h|t}$ are kept as the bottom-level reconciled forecasts.
-\item Reconciled forecasts for the entire hierarchy are recovered via $\tilde{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}$.
-\end{compactenum}
-We now outline the analogous steps for probabilistic forecasts when predictive densities are available.
-
-While $\hat{\nu}$ is a probability measure for an $n$-vector $\hat{\bm{y}}_{t+h|t}$, probability statements in terms of a different coordinate system can be made via an appropriate change of basis.
-Letting $f(.)$ be generic notation for a probability density function, and following the notation from our definition of point forecast reconciliation where $\hat{\bm{y}}_{t+h|t}=\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t}$, we obtain
-\begin{equation}
-f(\hat{\bm{y}}_{t+h|t})=f(\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t})|(\bm{S}~\bm{R})|
-\end{equation}
-The expression $\hat{\nu}(g^{-1}(\mathcal{B}))$ in Definition~\ref{def:reconprob} is equivalent to the probability statement $\text{Pr}(\hat{\bm{y}}_{t+h|t}\in g^{-1}(\mathcal{B}))$.
-After the change of basis, this is equivalent to $\text{Pr}(\tilde{\bm{b}}\in \mathcal{B})$, which implies
-\begin{align}
-\text{Pr}(\hat{\bm{y}}_{t+h|t}\in g^{-1}(\mathcal{B}))&=\int\limits_{g^{-1}(\mathcal{B})}f(\hat{\bm{y}}_{t+h|t})d\hat{\bm{y}}_{t+h|t}\\
-&=\int\limits_{\mathcal{B}}\int f(\bm{S}\tilde{\bm{b}}_{t+h|t}+\bm{R}\tilde{\bm{a}}_{t+h|t})|(\bm{S}~\bm{R})|d\tilde{\bm{a}}_{t+h|t}d\tilde{\bm{b}}_{t+h|t}.
-\end{align}
-After integrating out over $\tilde{\bm{a}}_{t+h|t}$, a step analogous to setting $\tilde{\bm{a}}_{t+h|t}=0$ for point forecasting, we obtain an expression that gives the probability that the reconciled bottom-level series lies in the region $\mathcal{B}$.
-This corresponds to $\nu(\mathcal{B})$ in Definition~\ref{def:reconprob}.
-To make a valid probability statement about the entire hierarchy we simply use the bottom-level probabilistic forecasts together with Definition~\ref{def:cohprob}.
-
-\subsubsection*{Example: Gaussian Distributions}
-
-Suppose an unreconciled probabilistic forecast is Gaussian with mean $\hat{\bm{\mu}}$ and variance-covariance matrix $\hat{\bm{\Sigma}}$.
-The subscripts $t+h|t$ are suppressed for brevity.
-Let the unreconciled density be given by
-\begin{equation}
-  f(\hat{\bm{y}})=(2\pi)^{-n/2}|\hat{\bm{\Sigma}}|^{-1/2}\exp\left\{-\frac{1}{2}\left[(\hat{\bm{y}}-\hat{\bm{\mu}})'\hat{\bm{\Sigma}}^{-1}(\hat{\bm{y}}-\hat{\bm{\mu}})\right]\right\}.
-\end{equation}
-In an alternative basis,
-\begin{equation}
-f(\tilde{\bm{b}},\tilde{\bm{a}})=(2\pi)^{-\frac{n}{2}}\Big|\hat{\bm{\Sigma}}\Big|^{-\frac{1}{2}}\Big|(\bm{S} ~  \bm{R})\Big|\exp\{-\frac{1}{2}q\}\,,
-\end{equation}
-where
-\begin{equation}
-q=(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\hat{\bm{\mu}})' \hat{\bm{\Sigma}}^{-1}(\bm{S}\tilde{\bm{b}}+\bm{R}\tilde{\bm{a}}-\hat{\bm{\mu}}).
-\end{equation}
-The quadratic form $q$ can be rearranged as
-\begin{align*}
-q& =
-\left((\bm{S} ~  \bm{R})\bt-\hat{\bm{\mu}}\right)' \hat{\bm{\Sigma}}^{-1}\left((\bm{S} ~ \bm{R})\bt-\hat{\bm{\mu}}\right),\\
-& =
-\left(\bt-(\bm{S} ~ \bm{R})^{-1}\hat{\bm{\mu}}_{t+h}\right)' \Big[(\bm{S}  \bm{R})^{-1}\hat{\bm{\Sigma}_{t+h}}\left((\bm{S} ~ \bm{R})^{-1}\right)'\Big]^{-1}
-\left(\bt-(\bm{S} ~ \bm{R})^{-1}\hat{\bm{\mu}}_{t+h}\right)\,.
-\end{align*}
-Recall that
-\[
-  (\bm{S} ~ \bm{R})^{-1} =
-  \begin{pmatrix}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot  \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot \end{pmatrix} :=
-  \begin{pmatrix}
-  \bm{G} \\\bm{H}
-  \end{pmatrix}\,.
-\]
-Then $q$ can be rearranged further as
-\begin{align*}
-q& =%\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\hat{\bm{\Sigma}}_{t+h}\Big|^{\frac{1}{2}}\Big|\PQ \Big|}
-%\exp \Big\{-\frac{1}{2}
-\left[\bt-\PQ\hat{\bm{\mu}}_{t+h}\right]'%\\[-0.5cm]
-\left[\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\right]^{-1}\left[\bt-\PQ\hat{\bm{\mu}}_{t+h}\right] %\Big\},
-\\[0.5cm]
- & =%\frac{1}{(2\pi)^{\frac{n}{2}}\Big|\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\Big|^{\frac{1}{2}}}
-%\exp \Big\{-\frac{1}{2}
-\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix}' %&\\[-0.5cm]
-%& \hspace*{7cm}
- \left[\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\right]^{-1}\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix}. %\Big\}.
-\end{align*}
-%Since $\Big[\PQ\hat{\bm{\Sigma}_{t+h}}\PQ'\Big] = \begin{pmatrix}
-%\bm{P}\hat{\bm{\Sigma}_{t+h}}\bm{P}' & \bm{P}\hat{\bm{\Sigma}_{t+h}}\bm{Q}'
-%\bm{Q}\hat{\bm{\Sigma}_{t+h}}\bm{P}' & \bm{Q}\hat{\bm{\Sigma}_{t+h}}\bm{Q}'
-%\end{pmatrix}$ we have
-
-Similar manipulations on the determinant of the covariance matrix lead to the following expression for the density:
-\begin{align*}
-f(\tilde{\bm{b}},\tilde{\bm{a}})&
-=(2\pi)^{-\frac{n}{2}}\left|
-\begin{pmatrix}
-  \bm{G}\hat{\bm{\Sigma}}\bm{G}' & \bm{G}\hat{\bm{\Sigma}}\bm{H}' \\
-  \bm{H}\hat{\bm{\Sigma}}\bm{G}' & \bm{H}\hat{\bm{\Sigma}}\bm{H}'
-\end{pmatrix}
-\right|^{-\frac{1}{2}}
-\exp \left\{-\frac{1}{2} \begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix}'\right.\\
-&\hspace*{7cm}
-\left.\begin{pmatrix}
-\bm{G}\hat{\bm{\Sigma}}\bm{G}' & \bm{G}\hat{\bm{\Sigma}}\bm{H}' \\
-\bm{H}\hat{\bm{\Sigma}}\bm{G}' & \bm{H}\hat{\bm{\Sigma}}\bm{H}'
-\end{pmatrix}^{-1}
-\begin{pmatrix}\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}\\ \tilde{\bm{a}}- \bm{H}\hat{\bm{\mu}}\end{pmatrix} \right\}.
-\end{align*}
-Marginalising out $\tilde{\bm{a}}$ leads to the following bottom-level reconciled forecasts:
-\begin{equation}\label{ex:2.1}
-f(\tilde{\bm{b}})=(2\pi)^{-\frac{m}{2}}\Big|\bm{G}\hat{\bm{\Sigma}}\bm{G}'\Big|^{\frac{1}{2}}
-\exp \Big\{-\frac{1}{2} (\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}})' (\bm{G}\hat{\bm{\Sigma}}\bm{G}')^{-1}(\tilde{\bm{b}} - \bm{G}\hat{\bm{\mu}}) \Big\}.
-\end{equation}
-
-%Equation \eqref{ex:2.1} implies $\tilde{\bm{b}}_{t+h} \sim \mathcal{N}(\bm{P}\hat{\bm{\mu}}_{t+h}, \bm{P}\hat{\bm{\Sigma}}_{t+h}\bm{P}')$, where $\bm{P} = (\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$.
-Then from \eqref{4.7} it follows that
-%\begin{equation}\label{eq:gaussianreconciled}
-%\tilde{\bm{f}}(\tilde{\bm{y}}_{t+h})=\tilde{\bm{f}}(\bm{S}\tilde{\bm{b}}_{t+h}).
-%\end{equation}
-This implies that the reconciled probabilistic forecast for the bottom-level series is $\tilde{\bm{b}} \sim \mathcal{N}(\bm{G}\hat{\bm{\mu}}, \bm{G}\hat{\bm{\Sigma}}\bm{G}')$.
-The reconciled probabilistic forecasts for the whole hierarchy follow a degenerate Gaussian distribution with mean $\bm{SG}\hat{\bm{\mu}}$ and rank deficient covariance matrix $\bm{SG}\hat{\bm{\Sigma}}\bm{G}'\bm{S}'$.
-
-\subsection{Elliptical distributions}
-
-We now show that the true predictive distribution can be recovered for elliptical distributions by linear reconciliation via pre-multiplication and translation respectively by a matrix we denote ${\bm G}_{opt}$ and vector we denote  ${\bm d}_{opt}$.
-Here, for any square matrix $\bm{C}$, $\bm{C}^{1/2}$ and $\bm{C}^{-1/2}$ are defined to satisfy $\bm{C}^{1/2}(\bm{C}^{1/2})'=\bm{C}$ and $\bm{C}^{-1/2}(\bm{C}^{-1/2})'=\bm{C}^{-1}$, for example $\bm{C}^{1/2}$ may be obtained via the Cholesky or eigenvalue decompositions.
-
-\begin{theo}[Reconciliation for Elliptical Distributions]
-	Let an unreconciled probabilistic forecast come from the elliptical class with location parameter $\hat{\bm{\mu}}$ and scale matrix $\hat{\bm{\Sigma}}$.
-Let the true predictive distribution of $\bm{y}$ also belong to the elliptical class with location parameter $\bm{\mu}$ and scale matrix $\bm{\Sigma}$.
-Then the linear reconciliation mapping $g(\breve{\bm{y}})=\bm{G}_{opt}\breve{\bm{y}}+\bm{d}_{opt}$ with $\bm{G}_{opt}={\bm{a}}\hat{\bm\Sigma}^{-1/2}$ and $\bm{d}_{opt}=\bm{\mu}-\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}$ recovers the true predictive density where ${\bm{a}}$ is any $m\times n$ matrix such that ${\bm{a}}{\bm{a}}'=\bm{\Omega}$ and $\bm{\Omega}$ is a sub-matrix of $\bm{\Sigma}$ corresponding to the bottom-level series.
-\end{theo}
-
-\begin{proof}
-   Since elliptical distributions are closed under affine transformations, and are closed under marginalisation, reconciliation of an elliptical distribution yields an elliptical distribution (although the unreconciled and reconciled distributions may be different members of the class of elliptical distributions).
-The scale matrix of the reconciled forecast is given by $\bm{S}\bm{G}_{opt}\hat{\bm{\Sigma}}\bm{G}_{opt}'\bm{S}'$, while the location matrix is given by $\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}+\bm{d}_{opt}$.
-The reconciled scale matrix is
-   \[
-     \tilde{\bm{\Sigma}}_{opt}
-       = \bm{S}{\bm{a}}\hat{\bm\Sigma}^{-1/2}\hat{\bm{\Sigma}}\left(\hat{\bm\Sigma}^{-1/2}\right)'{\bm{a}}'\bm{S}'
-       = \bm{S}\bm{\Omega}\bm{S}'
-       = \bm{\Sigma}.
-   \]
-   For the choices of $\bm{G}_{opt}$ and $\bm{d}_{opt}$ given above, the reconciled location vector is
-   \[
-     \tilde{\bm{\mu}}_{opt}= \bm{S}\bm{G}_{opt}\hat{\bm{\mu}}+\bm{\mu}-\bm{S}\bm{G}_{opt}\hat{\bm{\mu}}
-   = \bm{\mu}.
-   \]
-\end{proof}
-
-A number of insights can be drawn from this theorem.
-First, although a linear function $g(.)$ can be used to recover the true predictive in the elliptical case, the same does not hold in general.
-Second, $g(.)$ is not, in general, a projection matrix.
-The conditions for which a the true predictive density can be recovered by a projection are given below.
-
-\begin{theo}[True predictive via projection]
-	Assume that the true predictive distribution is elliptical with location $\bm{\mu}$ and scale $\bm{\Sigma}$.
-Consider reconciliation via a projection $g(\bm{y})=(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\bm{y}$.
-The true predictive distribution can be recovered via reconciliation of an elliptical distribution with location $\hat{\bm{\mu}}$ and scale $\hat{\bm{\Sigma}}$  when the following conditions hold:
-	\begin{align}
-	sp(\hat{\bm\mu}-\bm{\mu})&\subset sp(\bm{R})\\
-    sp(\hat{\bm{\Sigma}}^{1/2}-\bm{\Sigma}^{1/2})&\subset sp(\bm{R})\\
-	\end{align}
-\end{theo}
-
-\begin{proof}
-	The reconciled location vector will be given by
-	\begin{align*}
-		\tilde{\bm{\mu}}&=\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\hat{\bm{\mu}}\\
-		&=\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\left(\hat{\bm{\mu}}+\bm{\mu}-\bm{\mu}\right)\\
-		&=\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\bm{\mu}+\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}\left(\hat{\bm{\mu}}-\bm{\mu}\right).
-	\end{align*}
-  Since $\bm{S}(\bm{R}'_{\perp}\bm{S})^{-1}\bm{R}'_{\perp}$ is a projection onto $\mathfrak{s}$ and $\bm{\mu}\in\mathfrak{s}$, the first term simplifies to $\bm{\mu}$.
-If $\bm{\mu}-\hat{\bm{\mu}}$ lies in the span of $\bm{R}$, then multiplication by $\bm{R}'_{\perp}$ reduces the second term to $\bm{0}$.
-By a similar argument it can be shown that $\tilde{\bm{\Sigma}}^{1/2}=\bm{\Sigma}^{1/2}$.
-The closure property of elliptical distributions under affine transformations ensures that the full true predictive distribution can be recovered.
-\end{proof}
-
-Although these conditions will rarely hold in practice and only apply to a limited class of distributions, they do provide some insight into selecting a projection for reconciliation.
-If the value of $\hat{\bm{\mu}}$ were equi-probable in all directions, then a projection orthogonal to $\mathfrak{s}$ would be a sensible choice for $\bm{R}$ since it would in some sense represent a `median' direction for $\bm{\mu}-\hat{\bm{\mu}}$.
-However, the one-step-ahead in-sample errors are usually correlated suggesting that $\hat{\bm{\mu}}$ is more likely to fall in some directions than others.
-Therefore an orthogonal projection after transformation by the inverse of the one-step-ahead in-sample error covariance matrix may be more intuitively appealing.
-This is exactly what the MinT projection provides, and as simulations will show in Section~\ref{sec:gaussian}, this projection leads to the best empirical results.
-
-%However, these expressions do provide some insight on why some choices for $\bm{G}$ in the point forecast reconciliation literature may also work well for probabilistic forecasts.
-To illustrate, first rearrange the equation for the optimal value of  $\bm{G}_{opt}={\bm\Omega}^{1/2}\hat{\bm\Sigma}^{-1/2}$ as ${\bm\Omega}^{1/2}=\bm{G}_{opt}\hat{\bm\Sigma}^{1/2}$.
-For arbitrary $\bm{G}\hat{\bm\Sigma}^{1/2}$ is an approximation for ${\bm\Omega}^{1/2}$.
-This approximation has similarities with the way bottom-level estimates are produced for point forecast reconciliation.
-Rather than mapping a vector of point forecasts to reconcilied bottom-level forecasts, the columns of  $\hat{\bm\Sigma}^{1/2}$ are mapped to an approximation of the columns of ${\bm\Omega}^{1/2}$.
-The value for $\tilde{\bm{\mu}}_{opt}$ includes a projection of $\hat{\bm{\mu}}$ onto $\mathfrak{s}$.
-While it is infeasible to obtain the translation $\bm{d}$, it is worthwhile noting that this measures the difference between the reconciled mean and true mean.
-
-\section{Evaluation of hierarchical probabilistic forecasts}\label{sec:evaluation}
-
-The necessary final step in hierarchical forecasting is to make sure that our forecast distributions are accurate.
-In general, forecasters prefer to maximize the sharpness of the forecast distribution subject to calibration \citep{Gneiting2014}.
-Therefore the probabilistic forecasts should be evaluated with respect to these two properties.
-
-Calibration refers to the statistical compatibility between probabilistic forecasts and realizations.
-In other words, random draws from a perfectly calibrated forecast distribution should be equivalent in distribution to the realizations.
-On the other hand, sharpness refers to the spread or the concentration of the predictive distributions and it is a property of the forecasts only.
-The more concentrated the forecast distributions, the sharper the forecasts \citep{Gneiting2008}.
-However, independently assessing the calibration and sharpness will not help to properly evaluate the probabilistic forecasts.
-Therefore we need to assess these properties simultaneously using scoring rules.
-
-Scoring rules are summary measures obtained based on the relationship between the forecast distributions and the realizations.
-In some studies, researchers take the scoring rules to be positively oriented, in which case the scores should be maximized \citep{Gneiting2007}.
-However, scoring rules have also been defined to be negatively oriented, and then the scores should be minimized \citep{Gneiting2014}.
-We follow the latter convention here.
-
-Let $P$ be a forecast distribution and let $Q$ be the true data generating process respectively.
-Furthermore let $\omega$ be a realization from $Q$.
-Then a scoring rule is a function $S(P,\omega)$ that maps $P,\omega$ to $\mathbb{R}$.
-It is a ``proper'' scoring rule if
-\begin{equation}\label{eq:(3.1.)}
-\E_{\bm{Q}}[S(Q,\omega)] \le \E_{\bm{Q}}[S(P,\omega)] ,
-\end{equation}
-where $\E_{Q}[S(P,\omega)]$ is the expected score under the true distribution $Q$ \citep{Gneiting2008, Gneiting2014}. When this inequality is strict, the scoring rule is said to be strictly proper.
-
-In the context of probabilistic forecast reconciliation there could be two motivations for using scoring rules.
-The first is to compare unreconciled densities to reconciled densities.
-Reconciliation itself is a valuable goal since it can be important in aligning decision making across, for example, different units of an enterprise.
-In the point forecasting literature, forecast reconciliation has also been shown to improve forecast performance \citep{AthEtAl2017, Wickramasuriya2017}.
-It will be worthwhile to see whether the same holds in the probabilistic forecasting case.
-The second motivation for using scoring rules is to compare two or more sets of reconciled probabilistic forecasts to one another.
-The objective here is to evaluate which reconciliation mapping $g(.)$ works best in practice.
-
-\subsection{Univariate scoring rules}
-
-One way to evaluate hierarchical probabilistic forecasts is via the application of univariate scoring rules to each variable in the hierarchy.
-A summary can be taken of the expected scores across each margin, for example a mean or median.
-In the simulations of Section~\ref{sec:gaussian}, we consider two such scoring rules.
-The log score is given by the log density, in this case for each margin of the probabilistic forecast.
-The cumulative rank probability score generalises mean square error and is given by
-\begin{align} \label{eq:CRPS}
-\text{CRPS}(\breve{F}_i,y_{i}) &=\int \left(\breve{F}_i(\breve{Y}_i)-\mathbb{1}(\breve{Y}_i<y_{i})\right)d\breve{Y}_i\\ &=\E_{\breve{Y}_i}|\breve{Y}_{i}-y_{i}| - \frac{1}{2}\E_{\breve{Y}_i}|\breve{Y}_{i}-\breve{Y}^*_{i}|\,,
-\end{align}
-where $\breve{F}_i$ is the cumulative distribution function of the $i$th margin of the probabilistic forecast, $\breve{Y}_i$ and $\breve{Y}^*_{i}$ are independent copies of a random variable with distribution $\breve{F}_i$, and $y_i$ is the outcome of the $i$th margin.
-The expectations in the second line can be approximated by Monte Carlo when a sample from the predictive distribution is available.
-
-An advantage to this approach is that it allows the forecaster to evaluate the levels and individual series of the hierarchy where the gains from reconciliation are greatest.
-For this reason this approach has been used in the limited literature on probabilistic forecasting for hierarchies \citep{BenTaieb2017, JeoEtAl2018} to date.
-A major shortcoming of this approach however, is that evaluating univariate scores on the margins does not account for the dependence in the hierarchy.
-
-\subsection{Multivariate scoring rules}
-
-While a number of alternative proper scoring rules are available for univariate forecasts, the multivariate case is somewhat more limited.
-Here we focus on three scoring rules: the log score (LS), the energy score (ES) and the variogram score (VS).
-
-The log score can be approximated using a sample of values from the probabilistic forecast density \citep{Jordan2017}; however it is more commonly used when a parametric form for the density is available for the probabilistic forecast.
-
-The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the following representation in terms of expectations
-\begin{equation}
-\text{ES}(\breve{\bm{Y}}_{T+h},\bm{y}_{T+h}) =
-\E_{\breve{\bm{Y}}}
-||\breve{\bm{Y}}_{T+h}-\bm{y}_{T+h}||^\alpha -\frac{1}{2}\E_{\breve{\bm{Y}}}||\breve{\bm{Y}}_{T+h}-\breve{\bm{Y}}^*_{T+h}||^\alpha, \,\, \alpha \in (0,2]\,, 
-\end{equation}
-lends itself to easy computation when samples from the probabilistic forecast are available.
-An interesting limiting case is where $\alpha=2$, where it can be easily shown that energy score simplifies to mean squared error around the mean of the predictive distribution.
-In this limiting case, the energy score is proper but not strictly proper.
-\citet{Pinson2013a} also argue that the energy score has low discriminative ability for incorrectly specified covariances, even though it discriminates the misspecified means well.
-
-In contrast, \citet{SCHEUERER2015} have shown that the variogram score has a higher discrimination ability for misspecified means, variances and correlation structures than the energy score.
-When $\breve{\bm{y}}$ is a random variable from probabilistic forecast $\breve{F}$, the empirical variogram score is defined as
-\begin{equation}
-\text{VS}(\breve{F}, \bm{y}) = \displaystyle\sum_{i=1}^{n}\displaystyle\sum_{j=1}^{n}w_{ij}\left(|y_{i} - y_{j}|^p - E_{\breve{Y}_i,\breve{Y}_j} |\breve{Y}_{i}-\breve{Y}_{j}|^p\right)^2.
-\end{equation}
-\citet{SCHEUERER2015} recommend using $p=0.5$.
-
-\subsubsection{Comparing unreconciled forecasts to reconciled forecasts}
-
-For both reconciled and unreconciled densities it is possible to obtain a density from the probability measures defined in Section~\ref{sec:definitions}.
-Therefore it may seem sensible to compare unreconciled densities to reconciled densities on the basis of log score.
-However, the following theorem shows that using the log score may fail in the case of multivariate distributions with a degeneracy.
-
-\begin{theo}[Impropriety of log score]
-	When the true data generating process is coherent, then the log score is improper with respect to the class of incoherent measures.
-\end{theo}
-
-\begin{proof}
-Consider a rotated version of hierarchical time series, $\bm{z}_t=\bm{U}\bm{y}_t$, so that the first $m$ elements of $\bm{z}_t$ denoted $\bm{z}^{(1)}_t$ are unconstrained, while the remaining $n-m$ elements denoted $\bm{z}^{(2)}_t$ equal $0$ when the aggregation constraints hold.
-An example of the $n\times n$ $\bm{U}$ is the matrix of left singular vectors of $\bm{S}$.
-
-Consider the case where the true predictive density is $f_1(\bm{z}^{(1)}_t)\mathbb{1}\left(\bm{z}^{(2)}_t=\bm{0}\right)$, and we evaluate an incoherent density given by $f_1(\bm{z}^{(1)}_t)f_2(\bm{z}^{(2)}_t)$, where $f_2$ is highly concentrated around $0$ but still non-degenerate.
-For example, $f_2$ may be Gaussian with variance $\sigma^2{\bm{I}}$ with $\sigma^2 < (2\pi)^{-1}$.
-The log score under the true data generating process is
-\[
-LS\left(f,\bm{z}^{(1)}_t\right) = -\log f_1\left(\bm{z}^{(1)}_t\right),
-\]
-while that of the unreconciled density is
-\begin{align}
-LS\left(\hat{f},\bm{z}^{(1)}_t\right) &= -\log f_1(\bm{z}^{(1)}_t)-f_2(\bm{z}^{(1)}_t)\\
-&= -\log f_1(\bm{z}^{(1)}_t)+\frac{n-m}{2}\log(2\pi\sigma^2)\\
-&<-\log f_1(\bm{z}^{(1)}_t)=LS\left(f,\bm{z}^{(1)}_t\right).
-\end{align}
-After taking expectations $E\left[LS(f,f)\right] > E\left[LS(\hat{f},f)\right]$, violating the condition in Equation~\eqref{eq:(3.1.)} for a proper scoring rule.
-\end{proof}
-
-A similar issue also arises when discrete random variables are modelled as if they were continuous, an issue discussed in Section~4.1 of \citet{Gneiting2007}.
-This implies that the log score should be avoided when comparing reconciled and unreconciled probabilistic forecasts.
-
-\subsubsection{Comparing reconciled forecasts to one another}
-
-Coherent probabilistic forecasts can be completely characterised in terms of basis series; if a probabilistic forecast is available for the basis series, then a probabilistic forecast can be recovered for the entire hierarchy via Definition~\ref{def:cohprob}.
-This may suggest that it is adequate to merely compare two coherent forecasts to one another using the basis series only.
-We now show how this depends on the specific scoring rule used.
-
-For the log score, suppose the coherent probabilistic forecast has density $f(\bm{b})$.
-The density for the full hierarchy is given by $f(\bm{y})=f(\bm{Sb})=f(\bm{b})J^{-1}$, where $J=\prod_{j=1}^{m}\lambda_j$ is a pseudo-determinant of the non-square matrix $\bm{S}$ and $\lambda_j$ are the non-zero singular values of $\bm{S}$.
-Therefore for any coherent density, the log score of the full hierarchy differs from the log score for the bottom-level series by the term $log(J)$.
-This term depends only on the structure of the hierarchy and is fixed across different reconciliation methods.
-Therefore if one method achieves a lower expected log score compared to an alternative method using the bottom-level series only, the same ordering is preserved when an assessment is made on the basis of the full hierarchy.
-
-The same property does not hold for all scores in general.
-For example, the energy score can be expressed in terms of expectations of norms.
-In general, since norms are invariant under orthogonal rotations, the energy score is also invariant under orthogonal transformations \citep{Szekely2013,Gneiting2007}.
-In the context of two coherent forecasts, the same is true of a semi-orthogonal transformation from a lower dimensional basis series to the full hierarchy.
-However, when $\bm{S}$ is the usual summing matrix, it is not semi-orthogonal.
-Therefore the energy score computed on the bottom-level series will differ from the energy score computed using the full hierarchy and the ordering of different reconciliation methods may change depending on the basis series used.
-In this case we recommend computing the energy score using the full hierarchy.
-Although the discussion here is related to energy score, the same logic holds for other multivariate scores, for example the variogram score.
-
-The properties of multivariate scoring rules in the context of evaluating reconciled probabilistic forecasts are summarised in Table~\ref{tab:prop}.
-
-\begin{table}
-	\centering
-	\begin{tabular}{rll}
-	& Coherent v Incoherent &Coherent v Coherent\\
-	\hline
-	Log Score & Not proper & Ordering preserved if compared using\\ &&bottom-level only\\
-	Energy/ & Proper & Full hierarchy should be used\\
-	Variogram Score & Proper & Full hierarchy should be used\\
-	\hline
-    \end{tabular}
-	\caption{Summary of properties of scoring rules in the context of reconciled probabilistic forecasts.}
-	\label{tab:prop}
-\end{table}
-
-\section{Simulation study}\label{sec:gaussian}
-
-We now turn our attention to comparing different reconciliation methods in a simulation study where the data is conditionally Gaussian.
+This simulation study was designed to compare different reconciliation methods assuming the data is conditionally Gaussian.
 We choose the Gaussian case due to its analytical tractability which allows for evaluation using all scoring rules (including the log score).
@@
 
-\section{Conclusions}\label{sec:conclusions}
-
-%Although the problem of hierarchical point forecasts is well studied in the literature, there is a lack of attention in the context of probabilistic forecasts.
-Thus we attempted to fill this gap in the literature by providing substantial theoretical background to the problem.
-
-By redefining coherent forecasts and forecast reconciliation in geometric terms, we have established two new theoretical results that support the use of projections for point forecast reconciliation, and have allowed us to extend these concepts to probabilistic forecasting.
-We have shown that for elliptical distributions the true predictive density can be recovered by linear reconciliation and we have established conditions for when this is a projection.
-Although this projection cannot feasibly be obtained in practice, a projection similar to the MinT procedure provides a good approximation in applications.
-This is supported by the results of a simulation study.
-Finally, we have also discussed strategies for evaluating probabilistic forecasts for hierarchical time series advocating the use of multivariate scoring rules on the full hierarchy, while establishing a key result regarding the impropriety of the log score with respect to incoherent forecasts.
-
-In many ways this paper sets up a substantial future research agenda.
-For example, having defined what amounts to an entire class of reconciliation methods for probabilistic forecasts it will be worthwhile investigating which specific projections are optimal.
-This is likely to depend on the specific scoring rule employed as well as the properties of the base forecasts.
-Another avenue worth investigating is to consider whether it is possible to recover the true predictive distribution for non-elliptical distributions via a non-linear function $g(.)$.
-
 \newpage

### 2019-04-26 Hierarchical-forecast-reconciliation/Figs/Schem_3D.tex
Update section 2 and 3

% Created by tikzDevice version 0.12 on 2019-04-26 11:42:01
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,505.89);
\begin{scope}
\path[clip] ( 37.20, 61.20) rectangle (468.69,456.69);
\definecolor{drawColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.18, 75.85) -- (162.26,214.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.28, 75.85) -- (218.36,214.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.38, 75.85) -- (274.45,214.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.47, 75.85) -- (330.55,214.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.57, 75.85) -- (386.65,214.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.67, 75.85) -- (442.74,214.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.18, 75.85) -- (333.67, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.00,103.63) -- (355.48,103.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.81,131.41) -- (377.30,131.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.63,159.19) -- (399.11,159.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.44,186.97) -- (420.93,186.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.26,214.75) -- (442.74,214.75);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.86, 75.85) -- (336.47, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.68,103.63) -- (358.29,103.63);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.49,131.41) -- (380.10,131.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (396.31,159.19) -- (401.92,159.19);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.12,186.97) -- (423.73,186.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.94,214.75) -- (445.55,214.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.18, 73.57) -- ( 53.18, 78.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.28, 73.57) -- (109.28, 78.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.38, 73.57) -- (165.38, 78.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.47, 73.57) -- (221.47, 78.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.57, 73.57) -- (277.57, 78.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.67, 73.57) -- (333.67, 78.12);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.38, 75.85) -- ( 55.99, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.38,121.31) -- ( 55.99,121.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.38,166.77) -- ( 55.99,166.77);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.38,212.22) -- ( 55.99,212.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.38,257.68) -- ( 55.99,257.68);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.38,303.14) -- ( 55.99,303.14);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 53.18, 57.60) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (109.28, 57.60) {0.1};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (165.38, 57.60) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (221.47, 57.60) {0.3};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (277.57, 57.60) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (333.67, 57.60) {0.5};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 40.80, 75.85) {0.0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 40.80,121.31) {0.1};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 40.80,166.77) {0.2};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 40.80,212.22) {0.3};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 40.80,257.68) {0.4};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 40.80,303.14) {0.5};
\end{scope}
\begin{scope}
\path[clip] ( 37.20, 61.20) rectangle (468.69,456.69);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (345.67, 74.01) {0.0};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (367.48,101.79) {0.1};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (389.30,129.57) {0.2};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (411.11,157.35) {0.3};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (432.93,185.13) {0.4};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (454.74,212.91) {0.5};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.18, 75.85) --
	(333.67, 75.85);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at (193.42, 33.60) {$X$};
\end{scope}
\begin{scope}
\path[clip] ( 37.20, 61.20) rectangle (468.69,456.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.67, 75.85) --
	(442.74,214.75);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at (484.29,214.75) {$Y$};
\end{scope}
\begin{scope}
\path[clip] ( 37.20, 61.20) rectangle (468.69,456.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.18, 75.85) --
	( 53.18,303.14);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at ( 16.80,189.49) {$Z$};
\end{scope}
\begin{scope}
\path[clip] ( 37.20, 61.20) rectangle (468.69,456.69);
\definecolor{drawColor}{RGB}{255,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.01,313.24) circle (  3.00);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor,fill opacity=0.20] ( 53.18, 75.85) --
	(162.26,328.40) --
	(442.74,442.04) --
	(333.67,189.49) --
	cycle;
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 53.18, 75.85) -- (162.26,328.40);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.28, 98.58) -- (218.36,351.12);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.38,121.31) -- (274.45,373.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (221.47,144.04) -- (330.55,396.58);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (277.57,166.77) -- (386.65,419.31);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (333.67,189.49) -- (442.74,442.04);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 53.18, 75.85) -- (333.67,189.49);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 75.00,126.36) -- (355.48,240.00);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 96.81,176.87) -- (377.30,290.51);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.63,227.38) -- (399.11,341.02);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (140.44,277.89) -- (420.93,391.53);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.26,328.40) -- (442.74,442.04);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 53.18, 75.85) -- (420.93,414.26);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (415.53,397.02) --
	(420.93,414.26) --
	(403.30,410.31);
\definecolor{drawColor}{RGB}{0,0,255}
\definecolor{fillColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (277.57,282.34) circle (  3.00);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (209.01,313.24) -- (277.57,282.34);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (259.59,280.53) --
	(277.57,282.34) --
	(267.02,297.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.00] at (422.26,415.64) {{$\mathfrak{L}$}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at (209.01,289.76) {{$\mu$}};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at (277.57,258.86) {{$\bar{\mu}$}};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (227.47,309.94) {{\Huge ${\color{blue} s\circ g}$}};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (278.67,212.91) {{\Huge $\mathfrak{s}$}};
\end{scope}
\end{tikzpicture}

### 2019-04-26 Hierarchical-forecast-reconciliation/Figs/Schematic_3D.tex
Update section 2 and 3

% Created by tikzDevice version 0.12 on 2019-04-24 12:29:57
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,505.89);
\begin{scope}
\path[clip] ( 37.20, 61.20) rectangle (468.69,456.69);
\definecolor{drawColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.18, 75.85) -- (162.26,234.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.28, 75.85) -- (218.36,234.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.38, 75.85) -- (274.45,234.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.47, 75.85) -- (330.55,234.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.57, 75.85) -- (386.65,234.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.67, 75.85) -- (442.74,234.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.18, 75.85) -- (333.67, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.00,107.57) -- (355.48,107.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 96.81,139.28) -- (377.30,139.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (118.63,171.00) -- (399.11,171.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (140.44,202.72) -- (420.93,202.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (162.26,234.44) -- (442.74,234.44);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (330.86, 75.85) -- (336.47, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (352.68,107.57) -- (358.29,107.57);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (374.49,139.28) -- (380.10,139.28);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (396.31,171.00) -- (401.92,171.00);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (418.12,202.72) -- (423.73,202.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (439.94,234.44) -- (445.55,234.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.18, 73.77) -- ( 53.18, 77.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (109.28, 73.77) -- (109.28, 77.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (165.38, 73.77) -- (165.38, 77.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (221.47, 73.77) -- (221.47, 77.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (277.57, 73.77) -- (277.57, 77.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.67, 73.77) -- (333.67, 77.92);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.38, 75.85) -- ( 55.99, 75.85);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.38,127.75) -- ( 55.99,127.75);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.38,179.65) -- ( 55.99,179.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.38,231.55) -- ( 55.99,231.55);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.38,283.45) -- ( 55.99,283.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 53.18, 57.60) {0.0};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (109.28, 57.60) {0.2};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (165.38, 57.60) {0.4};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (221.47, 57.60) {0.6};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (277.57, 57.60) {0.8};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at (333.67, 57.60) {1.0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 40.80, 75.85) {0.0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 40.80,127.75) {0.5};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 40.80,179.65) {1.0};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 40.80,231.55) {1.5};

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 40.80,283.45) {2.0};
\end{scope}
\begin{scope}
\path[clip] ( 37.20, 61.20) rectangle (468.69,456.69);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (345.67, 74.01) {0.0};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (367.48,105.73) {0.2};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (389.30,137.45) {0.4};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (411.11,169.16) {0.6};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (432.93,200.88) {0.8};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  0.80] at (454.74,232.60) {1.0};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.18, 75.85) --
	(333.67, 75.85);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at (193.42, 33.60) {$y_A$};
\end{scope}
\begin{scope}
\path[clip] ( 37.20, 61.20) rectangle (468.69,456.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (333.67, 75.85) --
	(442.74,234.44);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at (484.29,234.44) {$y_B$};
\end{scope}
\begin{scope}
\path[clip] ( 37.20, 61.20) rectangle (468.69,456.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 53.18, 75.85) --
	( 53.18,283.45);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (505.89,505.89);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,rotate= 90.00,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at ( 16.80,179.65) {$y_{Tot}$};
\end{scope}
\begin{scope}
\path[clip] ( 37.20, 61.20) rectangle (468.69,456.69);
\definecolor{fillColor}{RGB}{255,0,0}

\path[fill=fillColor] (278.15,375.56) circle (  2.25);

\path[fill=fillColor] (279.97,367.03) circle (  2.25);

\path[fill=fillColor] (395.40,405.29) circle (  2.25);

\path[fill=fillColor] (394.76,401.87) circle (  2.25);

\path[fill=fillColor] (302.20,357.05) circle (  2.25);

\path[fill=fillColor] (201.44,282.97) circle (  2.25);

\path[fill=fillColor] (230.08,293.24) circle (  2.25);

\path[fill=fillColor] (150.40,253.03) circle (  2.25);

\path[fill=fillColor] (348.72,300.19) circle (  2.25);

\path[fill=fillColor] (279.47,272.24) circle (  2.25);

\path[fill=fillColor] (130.81,206.23) circle (  2.25);

\path[fill=fillColor] (246.98,242.98) circle (  2.25);

\path[fill=fillColor] (320.19,269.31) circle (  2.25);

\path[fill=fillColor] (104.67,179.99) circle (  2.25);

\path[fill=fillColor] (164.26,171.82) circle (  2.25);

\path[fill=fillColor] (256.24,194.27) circle (  2.25);

\path[fill=fillColor] (323.55,218.87) circle (  2.25);

\path[fill=fillColor] (131.69,125.53) circle (  2.25);

\path[fill=fillColor] (260.12,172.00) circle (  2.25);

\path[fill=fillColor] (129.70,105.84) circle (  2.25);
\definecolor{fillColor}{RGB}{0,0,0}

\path[fill=fillColor,fill opacity=0.20] ( 53.18, 75.85) --
	(162.26,338.24) --
	(442.74,442.04) --
	(333.67,179.65) --
	cycle;
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 53.18, 75.85) -- (162.26,338.24);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.28, 96.61) -- (218.36,359.00);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.38,117.37) -- (274.45,379.76);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (221.47,138.13) -- (330.55,400.52);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (277.57,158.89) -- (386.65,421.28);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (333.67,179.65) -- (442.74,442.04);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 53.18, 75.85) -- (333.67,179.65);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 75.00,128.33) -- (355.48,232.13);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 96.81,180.80) -- (377.30,284.61);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.63,233.28) -- (399.11,337.09);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (140.44,285.76) -- (420.93,389.56);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.26,338.24) -- (442.74,442.04);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 53.18, 75.85) -- (386.65,317.48);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (379.28,300.98) --
	(386.65,317.48) --
	(368.68,315.61);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.00] at (387.98,318.86) {{$\mathfrak{L}$}};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (222.57,232.24) {{\Huge $\mathfrak{s}$}};
\end{scope}
\end{tikzpicture}

### 2019-04-26 Hierarchical-forecast-reconciliation/Figs/orth_pointforerec_schematic.tex
Update section 2 and 3

% Created by tikzDevice version 0.12 on 2019-04-26 17:19:46
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,505.89);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (263.88,456.69);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.84,130.32) --
	( 68.84,317.41);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 22.07,177.10) --
	(209.16,177.10);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 68.84,177.10) -- (232.54,258.95);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (222.59,243.87) --
	(232.54,258.95) --
	(214.51,260.03);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (238.54,256.65) {{\large $\mathfrak{s}$}};
\definecolor{drawColor}{RGB}{0,0,255}
\definecolor{fillColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.00,317.41) circle (  3.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (139.00,335.41) {{\large $\color{blue}{\hat{\bm{y}}}$}};
\definecolor{drawColor}{RGB}{255,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.09,233.22) circle (  3.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (181.09,209.48) {{\large $\color{red}{\tilde{\bm{y}}}$}};
\definecolor{drawColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.00,317.41) -- (181.09,233.22);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.02,243.18) --
	(181.09,233.22) --
	(182.18,251.26);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (139.00,317.41) -- (108.93,197.14);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.96,214.51) --
	(108.93,197.14) --
	(121.49,210.13);
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.93,197.14) circle (  3.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (108.93,173.40) {{\large $\color{black}{{\bm{y}}}$}};
\end{scope}
\end{tikzpicture}

### 2019-04-26 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Update section 2 and 3

@@
 \usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
-\usepackage{mathrsfs, float, booktabs,todonotes,amsthm, xcolor}
+\usepackage{mathrsfs, float, booktabs,todonotes,amsthm, xcolor,sidenotes}
 \usepackage[bb=boondox]{mathalfa}
@@
 
-	\section{Forecasts reconciliation}\label{sec:definitions}
+\section{Coherent forecasts}\label{sec:CoheForecasts}
 
@@
 
-	It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect inherent aggregation constraints.
+	It is desirable that point forecasts should in some sense respect inherent aggregation constraints.
 We follow other authors \citep{Wickramasuriya2017, FPP2018} in using the nomenclature \emph{coherence} to describe this property.
-We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem, thus facilitating the development of probabilistic forecast reconciliation in Section~\ref{sec:reconciliation}.
+We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem.
 
@@
 
-	These definitions of the coherent space $\mathfrak{s}$, coherent point and coherent probabilistic forecasts in terms of the mapping $s(.)$, may give the impression that the bottom-level series play an important role.
+	These definitions of the coherent space $\mathfrak{s}$ and coherent point forecasts in terms of the mapping $s(.)$, may give the impression that the bottom-level series play an important role.
 However, alternative definitions could be formed using any set of basis vectors that span $\mathfrak{s}$.
@@
 Unless stated otherwise, we will always assume that the basis series are the bottom-level series as in Definition~\ref{def:cohpoint}, since this facilitates comparison with existing approaches in the literature.
+
+\section{Forecasts reconciliation}\label{sec:Reconciliation}
 
@@
 	Several choices of $g(.)$ currently extant in the literature, including the OLS, WLS and MinT methods, are special cases where $s\circ g$ is a projection.
-These can be defined so that $\bm{G}=({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ and $\bm{d}=\bm{0}$, were, ${\bm{R}_{\perp}}$ is a $n\times m$ orthogonal complement to an $n \times (n-m)$ matrix $\bm{R}$, where the columns of the latter span the null space of $\mathfrak{s}$.
+These can be defined so that $\bm{G}=({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ and $\bm{d}=\bm{0}$, where, ${\bm{R}_{\perp}}$ is a $n\times m$ orthogonal complement to an $n \times (n-m)$ matrix $\bm{R}$, where the columns of the latter span the null space of $\mathfrak{s}$.
 For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
 In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
-For this three variable hierarchy, $\bm{R}_\perp'=\bm{S}$ and reconciliation corresponds to the OLS method.
-For the case where $\bm{R}_\perp'\neq\bm{S}$, for example WLS and MinT, there are two possible interpretations.
-One is that these are oblique projections in Euclidean space where the columns of $\bm{R}$ are `directions' along which incoherent point forecasts are projected onto the coherent space $\mathfrak{s}$.
-Alternatively, since $\bm{R}_\perp'$ is usually written in the form $\bm{S}'{\bm{W}}^{-1}$, these projections can be thought of as orthogonal projections after pre-multiplying by ${\bm{W}^{-1/2}}$.
-A schematic providing a geometric interpretation of point reconciliation is given in Figure~\ref{fig:pointfr_sch}, while Table~\ref{table:2} summarises existing reconciliation methods.
+In OLS reconciliation, $\bm{R}_{\perp}'= \bm{S}'$ whereas in MinT or WLS reconciliation $\bm{R}_{\perp}'$ takes the form $\bm{S'W}^{-1}$.
+We will be discussing these projections distinctly in the next subsection.
 
-	\begin{table}[!h]
-		\caption{Summary of reconciliation methods that are projections.
+%	\begin{table}[!h]
+%		\caption{Summary of reconciliation methods that are projections.
 Here, $\hat{\bm{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, $\hat{\bm{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}, $\hat{\bm{W}}^{wls}$ is the diagonal matrix with diagonal elements $w_{ii}$, and $\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$, where $w_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{W}}^{sam}$.}\label{table:2}
-		\centering
-		\begin{tabular}{lll}
-			\toprule
-			\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
-			\midrule
-			OLS             &
-			$\bm{I}$  &
-			$\bm{S}'$  \\
-			MinT(Sample)    &
-			$\hat{\bm{W}}^{sam}$ &
-			$\bm{S}'(\hat{\bm{W}}^{sam})^{-1}$ \\
-			MinT(Shrink)    &
-			$\tau\text{Diag}(\hat{\bm{W}}^{sam}) + (1-\tau)\hat{\bm{W}}^{sam}$ &
-			$\bm{S}'(\hat{\bm{W}}^{shr})^{-1}$ \\
-			WLS       &
-			$\text{Diag}(\hat{\bm{W}}^{shr})$ &
-			$\bm{S}'(\hat{\bm{W}}^{wls})^{-1}$ \\
-			\bottomrule
-		\end{tabular}
-	\end{table}
+%		\centering
+%		\begin{tabular}{lll}
+%			\toprule
+%			\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
+%			\midrule
+%			OLS             &
+%			$\bm{I}$  &
+%			$\bm{S}'$  \\
+%			MinT(Sample)    &
+%			$\hat{\bm{W}}^{sam}$ &
+%			$\bm{S}'(\hat{\bm{W}}^{sam})^{-1}$ \\
+%			MinT(Shrink)    &
+%			$\tau\text{Diag}(\hat{\bm{W}}^{sam}) + (1-\tau)\hat{\bm{W}}^{sam}$ &
+%			$\bm{S}'(\hat{\bm{W}}^{shr})^{-1}$ \\
+%			WLS       &
+%			$\text{Diag}(\hat{\bm{W}}^{shr})$ &
+%			$\bm{S}'(\hat{\bm{W}}^{wls})^{-1}$ \\
+%			\bottomrule
+%		\end{tabular}
+%	\end{table}
 
@@
 
-	Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$.
-For example OLS minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$, while \citet{Wickramasuriya2017} show that MinT minimises the Mahalonobis distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$.
-\textcolor{red}{Explain why MinT works well}.
-Bottom-up methods minimise distance between reconciled and unreconciled forecasts only along dimensions corresponding to the bottom-level series.
-Therefore bottom-up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.
+	\subsection{Motivation of using projections}
 
-	We now state two theorems that motivate the use of projections for point forecast reconciliation.
-First, let $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ and assume $\hat{\bm{y}}_{t+h|t}$ is an unbiased prediction; that is $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\mu_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
+	We have seen from the above discussion that projection is playing an important role in point forecast reconciliation.
+Now we turn our attention to the following two theorems that explains the motivation of using projection in this context.
+
+	First, let $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ and assume $\hat{\bm{y}}_{t+h|t}$ is an unbiased prediction; that is $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
 
 	\begin{theo}[Unbiasedness preserving property]
-		For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also an unbiased prediction as long as $s\circ g$ is a projection.
+		For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also an unbiased prediction as long as $s\circ g$ is a projection onto $\mathfrak{s}$.
 	\end{theo}
@@
 	\end{proof}
-	We note the same result does not hold for general $g$ even when the range of $s\circ g$ is $\mathfrak{s}$.
+
+	We note the above result holds when the projection $s\circ g$ is only onto the coherent subspace $\mathfrak{s}$.
+That is the result does not hold for any general $g$ even when the range of $s\circ g$ is $\mathfrak{s}$.
+To describe this more explicitly suppose $s\circ g$ is a projection to any linear subspace $\mathfrak{L}$ of $\mathfrak{s}$.
+Then $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$ as the projection will move $\bm{\mu}_{t+h|t}$ to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$ as depicted in the figure \ref{fig:Schematic_3D}.
+Thus $\E_{1:t}(\tilde{\bm{y}}_{t+h|t}) \ne \bm{\mu}_{t+h|t}$ which breaks the unbiasedness.
+Recall the top-down method \citep{Gross1990} with
+	\begin{equation}\label{eq:top-downG}
+	\bm{G}=\begin{pmatrix}
+	\bm{p} & \bm{0}_{(m \times n-1)}
+	\end{pmatrix}
+	\end{equation}
+    where $\bm{p} = (p_1,\dots,p_m)'$ is an $m$-dimensional vector consisting a set of proportions which is use to disaggregate the top-level forecasts along the hierarchy.
+\cite{Hyndman2011} claimed that this method is not producing unbiased coherent forecasts even if the base forecasts are unbiased since $\bm{SGS} \ne \bm{S}$ for $\bm{G}$ in (\ref{eq:top-downG}).
+However the more rational explanation is that, in top-down approach the projection $s\circ g$ is not onto $\mathfrak{s}$, but to a linear subspace of $\mathfrak{s}$ spanned by $\bm{p}$.
+Thus from above explanation it follows that  $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$ and hence not producing unbiased forecasts.
+
+	\begin{figure}[!b]
+		\centering
+		\vspace{-0.9cm}
+		\small
+		\resizebox{\linewidth}{!}{
+			\input{Figs/Schem_3D}
+		}
+		\caption{$\mathfrak{L}$ is a linear subspace of the coherent subspace $\mathfrak{s}$.
+If $s\circ g$ is a projection not onto $\mathfrak{s}$ but onto $\mathfrak{L}$, then $\bm{\mu} \in \mathfrak{s}$ will be moved to $\bar{\bm{\mu}} \in \mathfrak{L}$.}\label{fig:Schematic_3D}
+	\end{figure}
+
+%	Representation of a coherent subspace in a three dimensional hierarchy where $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$.
+The coherent subspace is depicted as a gray two dimensional plane labelled $\mathfrak{s}$.
+Note that the columns of $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ form a basis for $\mathfrak{s}$.
+The red points lying on $\mathfrak{s}$ can be either realisations or coherent forecasts.
+
 	Now let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$, and let $\|\bm{v}\|_2$ be the $L_2$ norm of vector $\bm{v}$.
@@
 	\begin{proof}
-		Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ whenever $\bm{S}\bm{G}$ is a projection. Therefore
+		Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ whenever $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$.
+Therefore,
 		\begin{align}
 		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
-		&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\\
+		&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
 		\end{align}
@@
 	The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.
+
+	Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$.
+Following subsections will explicitly discuss the different projection based reconciliation methods and their optimality based on distinct distance measures.
+
+	\subsubsection{OLS reconciliation}
+
+	Recall that in OLS reconciliation, $\bm{R}_\perp=\bm{S}$ and thus it orthogonally projects $\hat{\bm{y}}$ to the coherent subspace.
+Further, it minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$.
+In addition to that figure \ref{fig:Schematic_OLSRecon} also shows that $\tilde{\bm{y}}$ is always closer to $\bm{y}$ than $\hat{\bm{y}}$ in terms of the Euclidean distance which is directly followed from the Pythagorean theorem.
+It also implies that the sum of squared error for OLS reconciled forecasts are always less than that for base forecasts.
+
+	\begin{figure}[t!]
+		\centering
+		\vspace{-0.9cm}
+		\tiny
+		\resizebox{\linewidth}{!}{
+			\input{Figs/orth_pointforerec_schematic}
+		}
+		\caption{$\hat{\bm{y}}$ is orthogonally projected onto $\mathfrak{s}$ }\label{fig:Schematic_OLSRecon}
+	\end{figure}
+
+	\subsubsection{MinT reconciliation}
+
+	In MinT reconciliation, $\bm{R}'_\perp$ is taking the form $\bm{S}'{\bm{W}}^{-1}$, where it can be thought of as orthogonal projections after pre-multiplying by ${\bm{W}^{-1/2}}$.
+That is, the coordinates of incoherent space will be scaled by $\bm{W}^{-1/2}$ which is then followed by the orthogonal projection.
+Alternatively this can be interpreted as an oblique projections in Euclidean space where the columns of $\bm{R}$ is the `direction' along which incoherent point forecasts are projected onto the coherent space $\mathfrak{s}$ as depicted in figure \ref{fig:pointfr_sch}.
+In terms of distances, MinT minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$ in the transformed space which is same as the scaled Euclidean distance in the original space.
+Latter is also referred to as the Mahalonobis distance.
+We also note that the WLS is a special case of MinT where $\bm{W}^{-1}$ is a diagonal matrix.
+
+	\citet{Wickramasuriya2017} showed that the MinT is optimal with respect to the mean squared forecast errors. 
+	We can provide a more general geometrical explanation for this optimality using the schematic in figure \ref{fig:MinT_justification}.
+Consider the h-step ahead reconciled forecast errors.
+These can be always approximated by the insample h-step ahead forecast errors.
+Since these errors are coherent, they lies in a direction that is closer to the coherent subspace $\mathfrak{s}$.
+Therefore if you project $\hat{\bm{y}}$ along the direction of these insample forecast errors, then you can get closer to the true value $\bm{y}$ as depicted in the schematic.
+Further, unlike OLS, the squared error for MinT reconciled forecasts is not always less than that of base forecasts in every single replication although it outperforms on average.
+
+	 \begin{figure}[!b]
+	 		\centering
+	 		%\vspace{-0.9cm}
+	 		\small
+	 		\resizebox{\linewidth}{!}{
+	 			\input{Figs/MinT_justification}
+	 		}
+	 		\caption{A schematic to represent MinT reconciliation.
+Points in orange colour represent the insample errors.
+$\bm{R}$ shows the direction of the insample errors.
+$\hat{\bm{y}}$ is projected onto $\mathfrak{s}$ along the the direction of $\bm{R}$.}\label{fig:MinT_justification}
+	 \end{figure}
+
+	\subsubsection{Bottom-up method}
+
+	Bottom-up method is one of the traditional and simplest ways of producing coherent forecasts.
+Under this approach, the incoherent forecasts are projected to the coherent subspace along the direction which is perpendicular to the bottom level series.
+In terms of distances, this method minimises the distance between reconciled and unreconciled forecasts only along the dimension corresponding to the bottom-level series.
+Therefore bottom-up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.
 

### 2019-04-26 Hierarchical-forecast-reconciliation/Figs/schematics.r

@@ -2,53 +2,10 @@
 
 library(latex2exp)
 library(tikzDevice)
+library(scatterplot3d)
 options(tikzLatexPackages=c(getOption("tikzLatexPackages"),"\\usepackage{amsfonts}","\\usepackage{bm}"),
         tikzFooter = "\\caption{a caption}")
 
-
-
-##Point forecast reconciliation.
-
-tikz('../../Presentations/CUFE2018/figs/orth_pointforerec_schematic.tex',width=4)
-plot.new()
-plot.window(xlim = c(-0.25,4),ylim = c(-0.5,5),asp=1)
-lines(c(0,0),c(-1,5))
-lines(c(-1,5),c(0,0))
-#lines(c(-1,3.5),c(-0.5,1.75),lwd=2)
-arrows(0,0,3.5,1.75,lwd=3)
-text(3.5,1.75,"{\\large ${\\bm S}$}",pos=4)
-#text(2,1,"{\\huge $\\mathfrak{s}$}",pos=1,offset = 1.3)
-#lines(c(-0.25,1),c(-1,4),lwd=2)
-#arrows(0,0,1,4,lwd=3)
-#text(1,4,"{\\Large ${\\bm R}$}",pos=3)
-
-
-
-yhat<-c(1.5,3)
-
-points(1.5,3,pch=20,cex=2,col='blue')
-text(1.5,3,"{\\large $\\color{blue}{\\hat{\\bm{y}}}$}",pos = 3,offset = 1.5)
-
-SP<-matrix(c(0.8,0.4,0.4,0.2),2,2)
-
-ytilde<-SP%*%yhat
-
-points(ytilde[1],ytilde[2],pch=20,cex=2,col='red')
-text(ytilde[1],ytilde[2],"{\\large $\\color{red}{\\tilde{\\bm{y}}}$}",pos=1,offset = 1.5)
-
-
-
-#lines(c(0,2),c(-3,5),lty=2)
-arrows(yhat[1],yhat[2],ytilde[1],ytilde[2],col='blue')
-
-
-#text(1.25,2,"{\\large ${\\color{blue} S\\circ P}$}",pos=4)
-
-points(6/7,3/7,pch=20,cex=2,col='black')
-text(6/7,3/7,"{\\large $\\color{black}{{\\bm{y}}}$}",pos=1,offset = 1.5)
-
-
-dev.off()
 
 
[…]

### 2019-05-02 Hierarchical-forecast-reconciliation/Figs/3D_hierarchy.tex
Add figure representing 3D hierarchy

--- 2019-04-26 Hierarchical-forecast-reconciliation/Figs/Schematic_3D.tex
@@
-% Created by tikzDevice version 0.12 on 2019-04-24 12:29:57
+% Created by tikzDevice version 0.12 on 2019-05-02 18:48:27
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 53.18, 75.85) -- (386.65,317.48);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 53.18, 75.85) -- (333.67,179.65);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (379.28,300.98) --
-	(386.65,317.48) --
-	(368.68,315.61);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (322.13,165.75) --
+	(333.67,179.65) --
+	(315.86,182.69);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.00] at (387.98,318.86) {{$\mathfrak{L}$}};
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 53.18, 75.85) -- (162.26,338.24);
+
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (164.59,320.32) --
+	(162.26,338.24) --
+	(147.91,327.26);
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.00] at (335.27,183.85) {\bfseries s};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.40] at (344.34,180.84) {1};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.00] at (163.87,342.44) {\bfseries s};
+
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.40] at (172.94,339.43) {2};
 

### 2019-05-02 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Slight changes on figures
Add figure representing 3D hierarchy

@@
 
+		\begin{figure}[H]
+		\centering
+		\vspace{-0.9cm}
+		\small
+		\resizebox{\linewidth}{!}{
+			\input{Figs/3D_hierarchy}
+		}
+		\caption{Depiction of a three dimensional hierarchy with $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$.
+The gray colour two dimensional plane reflects the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that spans $\mathfrak{s}$.
+The points in $\mathfrak{s}$ represents realisations or coherent forecasts}\label{fig:3D_hierarchy}
+	\end{figure}
+
 	These definitions of the coherent space $\mathfrak{s}$ and coherent point forecasts in terms of the mapping $s(.)$, may give the impression that the bottom-level series play an important role.
 However, alternative definitions could be formed using any set of basis vectors that span $\mathfrak{s}$.
-For example, consider the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$.
-In this case the matrix $\bm{S}$ has columns $(1,1,0)'$ and $(1,0,1)'$ spanning $\mathfrak{s}$, and pre-multiplying by $\bm{S}$ transforms arbitrary values of $y_{2,t}$ and $y_{3,t}$ into a coherent vector for the full hierarchy.
-However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{1,t}$ and $y_{2,t}$ into a coherent vector for the full hierarchy.
+For example, consider the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.
+Figure \ref{fig:3D_hierarchy} represent this in a 3-D diagram.
+In this case the matrix $\bm{S}$ has columns $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$ spanning $\mathfrak{s}$ which is depicted in gray colour two dimensional plane.
+Pre-multiplying by $\bm{S}$ transforms arbitrary values of $y_{A,t}$ and $y_{B,t}$ into a coherent vector for the full hierarchy.
+These coherent points always lies in the $\mathfrak{s}$ plane as the red points depicted in the figure.
+
+	However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{Tot,t}$ and $y_{A,t}$ into a coherent vector for the full hierarchy.
 The definitions above could be made in terms of any series and not just the bottom-level series.
@@
 To describe this more explicitly suppose $s\circ g$ is a projection to any linear subspace $\mathfrak{L}$ of $\mathfrak{s}$.
-Then $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$ as the projection will move $\bm{\mu}_{t+h|t}$ to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$ as depicted in the figure \ref{fig:Schematic_3D}.
+Then $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$ as the projection will move $\bm{\mu}_{t+h|t}$ to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$ as depicted in the Figure \ref{fig:Schematic_3D}.
 Thus $\E_{1:t}(\tilde{\bm{y}}_{t+h|t}) \ne \bm{\mu}_{t+h|t}$ which breaks the unbiasedness.
@@
 Further, it minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$.
-In addition to that figure \ref{fig:Schematic_OLSRecon} also shows that $\tilde{\bm{y}}$ is always closer to $\bm{y}$ than $\hat{\bm{y}}$ in terms of the Euclidean distance which is directly followed from the Pythagorean theorem.
+In addition to that Figure \ref{fig:Schematic_OLSRecon} also shows that $\tilde{\bm{y}}$ is always closer to $\bm{y}$ than $\hat{\bm{y}}$ in terms of the Euclidean distance which is directly followed from the Pythagorean theorem.
 It also implies that the sum of squared error for OLS reconciled forecasts are always less than that for base forecasts.
 
-	\begin{figure}[t!]
+	\clearpage		
+	\begin{figure}[!ht]
 		\centering
@@
 That is, the coordinates of incoherent space will be scaled by $\bm{W}^{-1/2}$ which is then followed by the orthogonal projection.
-Alternatively this can be interpreted as an oblique projections in Euclidean space where the columns of $\bm{R}$ is the `direction' along which incoherent point forecasts are projected onto the coherent space $\mathfrak{s}$ as depicted in figure \ref{fig:pointfr_sch}.
+Alternatively this can be interpreted as an oblique projections in Euclidean space where the columns of $\bm{R}$ is the `direction' along which incoherent point forecasts are projected onto the coherent space $\mathfrak{s}$ as depicted in Figure \ref{fig:pointfr_sch}.
 In terms of distances, MinT minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$ in the transformed space which is same as the scaled Euclidean distance in the original space.
@@
 	\citet{Wickramasuriya2017} showed that the MinT is optimal with respect to the mean squared forecast errors. 
-	We can provide a more general geometrical explanation for this optimality using the schematic in figure \ref{fig:MinT_justification}.
+	We can provide a more general geometrical explanation to this optimality using the schematic in Figure \ref{fig:MinT_justification}.
 Consider the h-step ahead reconciled forecast errors.
@@
 Since these errors are coherent, they lies in a direction that is closer to the coherent subspace $\mathfrak{s}$.
-Therefore if you project $\hat{\bm{y}}$ along the direction of these insample forecast errors, then you can get closer to the true value $\bm{y}$ as depicted in the schematic.
+Therefore if you project $\hat{\bm{y}}$ along the direction of these in-sample forecast errors, then you can get closer to the true value $\bm{y}$ as depicted in the schematic.
 Further, unlike OLS, the squared error for MinT reconciled forecasts is not always less than that of base forecasts in every single replication although it outperforms on average.
 
-	 \begin{figure}[!b]
+	 \begin{figure}[H]
 	 		\centering

### 2019-05-02 Hierarchical-forecast-reconciliation/Figs/schematics.r

@@ -3,9 +3,39 @@
 library(latex2exp)
 library(tikzDevice)
 library(scatterplot3d)
+library(tidyverse)
 options(tikzLatexPackages=c(getOption("tikzLatexPackages"),"\\usepackage{amsfonts}","\\usepackage{bm}"),
         tikzFooter = "\\caption{a caption}")
 
+## 3D hierarchy
+set.seed(1989)
+
+X <- matrix(runif(40),20,2) %>% as.data.frame()
+X[,3] <- X[,1] + X[,2]
+
+colnames(X) <- c(expression('$y_A$'), 
+                 expression('$y_B$'), 
+                 expression('$y_{Tot}$'))
+
+tikz('3D_hierarchy.tex',standAlone = FALSE)
+
+s3d <- scatterplot3d(X, color = "red",
+                     angle=55, pch = 16, grid=TRUE, box=FALSE,cex.lab = 2)
+
+
+# Add regression plane
+s3d$plane3d(0,1,1, draw_lines = T, draw_polygon = T)
+
+#
+#s1pro<-s3d$xyz.convert(1,1,0)
+s1 <- s3d$xyz.convert(1,0,1)
+s2 <- s3d$xyz.convert(0,1,1)
+arrows(0,0,s1$x,s1$y,lwd = 3)
+arrows(0,0,s2$x,s2$y,lwd = 3)
+text(s1$x,s1$y, TeX('$\\textbf{s}_1$}'),col = 1, adj = c(-.1, -.1),cex = 2)
+text(s2$x,s2$y, TeX('$\\textbf{s}_2$}'),col = 1, adj = c(-.1, -.1),cex = 2)
+text(3, 3, "{\\Huge $\\mathfrak{s}$}",col = 1, adj = c(-.1, -.1))
+dev.off()
 
 
 ##Point forecast reconciliation.

### 2019-06-28 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Rewrote definitions associated with coherence

@@
 
+    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \todo{citations}, before elaborating on some of the limitations of this understanding.
+A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables.
+We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$.
+The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.
+The hierarchical structure of the data implies that
+
+    \begin{equation}
+    \bm{y}_t = \bm{Sb}_t,
+    \end{equation}
+    where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints, holds for all $t$.
+
 		\begin{figure}[H]
@@
 			\end{center}
-			\caption{An example of a two level hierarchical structure.}\label{fig1}
+			\caption{An example of a two level hierarchical structure.}\label{fig:basichier}
 		\end{figure}
 
-	A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables.
-We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$.
-The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.
-The hierarchical structure of the data implies that
-	\begin{equation}
-	\bm{y}_t = \bm{Sb}_t,
-	\end{equation}
-	where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints, holds for all $t$.
-
-	To clarify these concepts consider the example of the hierarchy in Figure~\ref{fig1}.
+	To clarify these concepts consider the example of the hierarchy in Figure~\ref{fig:basichier}.
 For this hierarchy, $n=7$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$ and
@@
 
-	While most applications of hierarchical time series to date have involved data that respect an aggregation structure, in principle the matrix ${\bm S}$ can encode any linear constraints including weighted sums or even cases where some variables in the hierarchy are formed by taking the difference of two other variables.
+	While such a definition is completely serviceable, it obscures the full generality of the methodologies developed in the literature on hierarchical time series.
+There are only two important characteristics of the data that we are interested in; the first is that they are multivariate, the second is that they adhere to linear constraints.
+Below we provide definitions that provide geometric intuition behind the data and methodologies employed in the hierarchical forecasting.
 
-	\subsection{Coherent point forecasts}\label{sec:cohpointf}
-
-	It is desirable that point forecasts should in some sense respect inherent aggregation constraints.
-We follow other authors \citep{Wickramasuriya2017, FPP2018} in using the nomenclature \emph{coherence} to describe this property.
-We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem.
+	\subsection{Coherence}\label{sec:cohpointf}
 
 	 \begin{definition}[Coherent subspace]\label{def:cohspace}
-		The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$, is defined as the \emph{coherent space}.
+	 	The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which a set of linear constraints hold for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
 	 \end{definition}
 
-	It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$.
-Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.
+     To further illustrate, Figure \ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.
+The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space, i.e.
+$m=2$ and $n=3$.
+It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$.
+In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.
+However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom level series, $y_{A,t}$ and $y_{B,t}$.
+In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$, which also span the coherent subspace.
+Thus, while there are multiple ways to define a hierarchy and an associated `$\bm{S}$ matrix', the columns of any `$\bm{S}$ matrix' will always span the same unique coherent subspace.
 
-	\begin{figure}[H]
-		\begin{center}
-			\begin{tikzpicture}[
-			>=stealth,
-			bullet/.style={
-				fill=black,
-				circle,
-				minimum width=1.5cm,
-				inner sep=0pt
-			},
-			projection/.style={
-				->,
-				thick,
-				label,
-				shorten <=2pt,
-				shorten >=2pt
-			},
-			every fit/.style={
-				ellipse,
-				draw,
-				inner sep=0pt
-			}
-			]
-			\node at (2,3) {$s$};
-			\node at (0,5) {$\mathbb{R}^m$(domain of $s$)};
-			\node at (4,5) {$\mathbb{R}^n$(codomain of $s$)};
-			\node at (4.7,2.0) {$\mathfrak{s}$(image of $s$)};
-			%\node[bullet,label=below:$f(x)$] at (4,2.5){};
-			\draw (0,2.5) ellipse (1.02cm and 2.2cm);
-			\draw (4,2.5) ellipse (1.02cm and 2.2cm);
-			\draw (4,2.5) ellipse (0.51cm and 1.1cm);
-			\draw[projection, label=below:$f$] (0.3,2.5) -- (3.8,2.5) ;
-			\end{tikzpicture}
-		\end{center}
-		\caption{The domain, codomain and image of the mapping $s$.}\label{fig2}
-	\end{figure}
-
-	\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
-		Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a point forecast of the values of all series in the hierarchy at time $t+h$, made using information up to and including time $t$.
-Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathfrak{s}$.
-	\end{definition}
+     Also notable by its absence in the above definition is any reference to {\em aggregation}.
+As the literature has shown, the linear constraints need not be aggregation constraints at all.
+For example \todo{find reference} consider weighted sums, while \todo{include Li and Tang reference} consider an example where one variable is the difference of two other variables.
 
@@
 
-	These definitions of the coherent space $\mathfrak{s}$ and coherent point forecasts in terms of the mapping $s(.)$, may give the impression that the bottom-level series play an important role.
-However, alternative definitions could be formed using any set of basis vectors that span $\mathfrak{s}$.
-For example, consider the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.
-Figure \ref{fig:3D_hierarchy} represent this in a 3-D diagram.
-In this case the matrix $\bm{S}$ has columns $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$ spanning $\mathfrak{s}$ which is depicted in gray colour two dimensional plane.
-Pre-multiplying by $\bm{S}$ transforms arbitrary values of $y_{A,t}$ and $y_{B,t}$ into a coherent vector for the full hierarchy.
-These coherent points always lies in the $\mathfrak{s}$ plane as the red points depicted in the figure.
+	 \begin{definition}[Hierarchical Time Series]\label{def:cohspace}
+	 	A hierarchical time series is an $n$-dimensional multivariate time series such that all observed values $\bm{y}_1,\ldots,\bm{y}_T$ and all future values $\bm{y}_{T+1},\bm{y}_{T+2},\ldots$  lie in the coherent subspace, i.e.
+$\bm{y}_t\in\mathfrak{s}\quad\forall t$.
+	 \end{definition}
 
-	However the columns $(1,0,1)'$ and $(0,1,-1)'$ also span $\mathfrak{s}$ and define a mapping that transforms arbitrary values of $y_{Tot,t}$ and $y_{A,t}$ into a coherent vector for the full hierarchy.
-The definitions above could be made in terms of any series and not just the bottom-level series.
-In general, we call the series (or linear combinations thereof) used in the definitions of coherence \textit{basis series}.
-Unless stated otherwise, we will always assume that the basis series are the bottom-level series as in Definition~\ref{def:cohpoint}, since this facilitates comparison with existing approaches in the literature.
+	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.
+In fact, the term {\em hierarchical} is misleading since the literature has covered instances that cannot easily be depicted as hierarchies as in Figure~\ref{fig:basichier}.
+These include \todo{include references}.
+Furthermore, although the definition makes clear reference to time series, this definition can be easily generalised to any vector-valued data for which some constraints are known to hold.
+
+%	It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$.
+Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.
+%	
+%	\begin{figure}[H]
+%		\begin{center}
+%			\begin{tikzpicture}[
+%			>=stealth,
+%			bullet/.style={
+%				fill=black,
+%				circle,
+%				minimum width=1.5cm,
+%				inner sep=0pt
+%			},
+%			projection/.style={
+%				->,
+%				thick,
+%				label,
+%				shorten <=2pt,
+%				shorten >=2pt
+%			},
+%			every fit/.style={
+%				ellipse,
+%				draw,
+%				inner sep=0pt
+%			}
+%			]
+%			\node at (2,3) {$s$};
+%			\node at (0,5) {$\mathbb{R}^m$(domain of $s$)};
+%			\node at (4,5) {$\mathbb{R}^n$(codomain of $s$)};
+%			\node at (4.7,2.0) {$\mathfrak{s}$(image of $s$)};
+%			%\node[bullet,label=below:$f(x)$] at (4,2.5){};
+%			\draw (0,2.5) ellipse (1.02cm and 2.2cm);
+%			\draw (4,2.5) ellipse (1.02cm and 2.2cm);
+%			\draw (4,2.5) ellipse (0.51cm and 1.1cm);
+%			\draw[projection, label=below:$f$] (0.3,2.5) -- (3.8,2.5) ;
+%			\end{tikzpicture}
+%		\end{center}
+%		\caption{The domain, codomain and image of the mapping $s$.}\label{fig2}
+%	\end{figure}
+
+	\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
+		Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a point forecast of the values of all series in the hierarchy at time $t+h$, made using information up to and including time $t$.
+Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathfrak{s}$.
+	\end{definition}
+
+    Without any loss of generality, that above definition could also be applied to prediction for multivariate data in general, rather than just forecasting of time series.
+While the observed data will be coherent by definition, it is important to note that there are a number of reasons why forecasts or predictions may be incoherent.
+First, since applications of hierarchical forecasting tend to be very high dimensional a common strategy in practice is to produce forecasts for each time series independently using univariate models.
+Second, even where a multivariate model is used for the full vector of observations, it may be difficult to capture the linear constraints inherent in the data particularly for complicated non-linear models.
+Third, in some cases judgemental adjustments may be made inducing incoherent forecasts.
 

### 2019-06-30 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Changes to reconciliation section

@@
 
-\section{Forecasts reconciliation}\label{sec:Reconciliation}
+\section{Forecast reconciliation}\label{sec:Reconciliation}
 
-	\subsection{Point forecast reconciliation}\label{sec:reconciliation}
+	As discussed in the previous section, for a number of reasons, coherence is not guaranteed when forecasts are produced for all series.To ensure aligned decision making, it is desirable to adjust forecasts ex post to endure coherence.
+This process is referred to as {\em reconciliation}.
+In the most general terms, reconciliation can be defined as follows
 
-	As discussed, reconciliation is distinct from coherence, since the former refers to a process whereby incoherent forecasts are made coherent.
-Although reconciliation methods for point forecasts are extant in the literature they are rarely defined explicitly.
-We do so here in slightly more general terms than usual.
-	%We then extend this idea to the novel concept of probabilistic reconciliation.
-
-	Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ conditional on information up to and including time $t$.
-We now introduce a linear function that converts unreconciled forecasts into new bottom level forecasts.
-	Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively, and let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})=\bm{G}\bm{y}+\bm{d}$.
-A composition of $g$ and $s(.)$ gives the following definition for point forecast reconciliation.
-
-	\begin{definition}\label{def:reconpoint}
-		The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $g(.)$ iff
+	\begin{definition}[Reconciled forecasts]\label{def:reconpoint}
+		Let $\psi$ be a mapping, $\psi:\mathbb{R}^n\rightarrow\mathfrak{s}$.  The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $\psi(.)$ iff
 		\begin{equation}
-		\tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{G}\hat{\bm{y}}_{t+h|t}+\bm{d})\,.
+		\tilde{\bm{y}}_{t+h|t}=\psi\left(\hat{\bm{y}}_{t+h|t}\right)\,.
 		\end{equation}
@@
 
-	Several choices of $g(.)$ currently extant in the literature, including the OLS, WLS and MinT methods, are special cases where $s\circ g$ is a projection.
-These can be defined so that $\bm{G}=({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ and $\bm{d}=\bm{0}$, where, ${\bm{R}_{\perp}}$ is a $n\times m$ orthogonal complement to an $n \times (n-m)$ matrix $\bm{R}$, where the columns of the latter span the null space of $\mathfrak{s}$.
-For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
+	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, and with few exceptions, these belong more specifically to the class of projections.
+This involves pre-multiplying $\hat{\bm{y}}_{t+h|t}$ by a projection matrix that can be written down in a number of ways.
+In \todo{references}, the projection matrix is written in the form $\bm{SG}$ (with $\bm{P}$ used in place of $\bm{G}$ in some cases).
+This facilitates an interpretation of reconciliation as a two-step process, in the first step base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.
+It should be noted that if $\bm{G}$ is set arbitrarily, then $\bm{SG}$ will not necessarily be a projection.
+However for a large class of reconciliation methods, $\bm{G}$ is determined by treating forecast reconciliation as a problem in linear regression model.
+In this case least squares estimators result in values of $\bm{G}$ that do in fact imply that $\bm{SG}$ is a projection.
+
+    First, the linear subspace onto which all points are projected, or the image of the projection, must be defined.
+In our context this can be defined by the $m$ columns of the matrix $\bm{S}$.
+Second, the direction along which points are projected must be defined.
+This will be achieved by defining a matrix $\bm{R}$ with $n-m$ columns then span the direction of projection.
+A schematic of this is presented \todo{include}.
+A projection matrix can then be constructed as $\bm{S}({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ where, ${\bm{R}_{\perp}}$ is an $n\times m$ orthogonal complement to $\bm{R}$ such that ${\bm{R}'_{\perp}}\bm{R}=\bm{0}$.
+It is simple to verify that this construction satisfies the properties of a projection matrix, namely symmetry and idempotence.
+
+	A straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
 In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
 In OLS reconciliation, $\bm{R}_{\perp}'= \bm{S}'$ whereas in MinT or WLS reconciliation $\bm{R}_{\perp}'$ takes the form $\bm{S'W}^{-1}$.
-We will be discussing these projections distinctly in the next subsection.
+We will be discussing these projections distinctly in the next subsection\todo{needs work}.
+
+%	\subsection{Reconciliation in general}\label{sec:reconciliation}
+%
+%	
+%	As discussed, reconciliation is distinct from coherence, since the former refers to a process whereby incoherent forecasts are made coherent.
+Although reconciliation methods for point forecasts are extant in the literature they are rarely defined explicitly.
+We do so here in slightly more general terms than usual.
+%	%We then extend this idea to the novel concept of probabilistic reconciliation.
+%	
+%	Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ conditional on information up to and including time $t$.
+We now introduce a linear function that converts unreconciled forecasts into new bottom level forecasts.
+%	Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively, and let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})=\bm{G}\bm{y}+\bm{d}$.
+A composition of $g$ and $s(.)$ gives the following definition for point forecast reconciliation.
+%	
+%	\begin{definition}\label{def:reconpoint}
+%		The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $g(.)$ iff
+%		\begin{equation}
+%		\tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{G}\hat{\bm{y}}_{t+h|t}+\bm{d})\,.
+%		\end{equation}
+%	\end{definition}
 
@@
 %	\end{table}
-
-	\begin{figure}
-		\input{Figs/pointforerec_schematic.tex}
-		\caption{Summary of probabilistic point reconciliation.
+%	
+%	
+%	\begin{figure}
+%		\input{Figs/pointforerec_schematic.tex}
+%		\caption{Summary of probabilistic point reconciliation.
 The mapping $s\circ g$ projects the unreconciled forecast $\hat{\bm{y}}_{t+h|h}$ onto $\mathfrak{s}$, yielding the reconciled forecast $\tilde{\bm{y}}_{t+h|h}$ with subscripts dropped in the figure for ease of presentation.
 Since the smallest hierarchy involves three dimensions, this figure is only a schematic.}\label{fig:pointfr_sch}
-	\end{figure}
-
-	The columns of $\bm{S}$ and $\bm{R}$ provide a basis for $\mathbb{R}^n$.
+%	\end{figure}
+%	
+%	The columns of $\bm{S}$ and $\bm{R}$ provide a basis for $\mathbb{R}^n$.
 Therefore any incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$.
@@
 From properties of linear algebra it follows that
-	\[
-	\hat{\bm{y}}_{t+h|t} = (\bm{S} ~ \bm{R})
-	\begin{pmatrix}
-	\tilde{\bm{b}}_{t+h|t}\\ \tilde{\bm{a}}_{t+h|t}
-	\end{pmatrix}= \bm{S}\tilde{\bm{b}}_{t+h|t} + \bm{R}\tilde{\bm{a}}_{t+h|t},
-	\]
-	while the reconciled point forecast is
-	\[
-	\tilde{\bm{y}}_{t+h|t} = \bm{S}\tilde{\bm{b}}_{t+h|t}.
-	\]
-
-	In order to find $\tilde{\bm{b}}_{t+h|t}$ we require the inverse $(\bm{S} ~ \bm{R})^{-1}$ which is given by
-	\begin{equation}
-	(\bm{S} ~ \bm{R})^{-1} = \begin{pmatrix}
-	(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
-	\end{pmatrix}\,,
-	\end{equation}
-	where $\bm{S}_{\bot}$ is the orthogonal complements of $\bm{S}$.
+%	\[
+%	\hat{\bm{y}}_{t+h|t} = (\bm{S} ~ \bm{R})
+%	\begin{pmatrix}
+%	\tilde{\bm{b}}_{t+h|t}\\ \tilde{\bm{a}}_{t+h|t}
+%	\end{pmatrix}= \bm{S}\tilde{\bm{b}}_{t+h|t} + \bm{R}\tilde{\bm{a}}_{t+h|t},
+%	\]
+%	while the reconciled point forecast is
+%	\[
+%	\tilde{\bm{y}}_{t+h|t} = \bm{S}\tilde{\bm{b}}_{t+h|t}.
+%	\]
+%	
+%	
+%	In order to find $\tilde{\bm{b}}_{t+h|t}$ we require the inverse $(\bm{S} ~ \bm{R})^{-1}$ which is given by
+%	\begin{equation}
+%	(\bm{S} ~ \bm{R})^{-1} = \begin{pmatrix}
+%	(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
+%	\end{pmatrix}\,,
+%	\end{equation}
+%	where $\bm{S}_{\bot}$ is the orthogonal complements of $\bm{S}$.
 Thus it follows that $\tilde{\bm{b}}_{t+h|t}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$.

### 2019-07-01 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
removed line to make pdflatex work
rewriting of unbiasedness preserving property

@@
-%&latex
 \documentclass[12pt]{article}
@@
 \newtheorem{definition}{Definition}[section]
+
+\theoremstyle{property}
+\newtheorem{property}{Property}[section]
 
@@
 
-	While such a definition is completely serviceable, it obscures the full generality of the methodologies developed in the literature on hierarchical time series.
-There are only two important characteristics of the data that we are interested in; the first is that they are multivariate, the second is that they adhere to linear constraints.
-Below we provide definitions that provide geometric intuition behind the data and methodologies employed in the hierarchical forecasting.
+	While such a definition is completely serviceable, it obscures the full generality of many methodologies developed in the literature on so-called hierarchical time series.
+In fact, to apply concepts such as coherence and reconciliation, the data only require two important characteristics; the first is that they are multivariate, the second is that they adhere to linear constraints.
+Below we redefine the concepts of coherence and hierarchical time series using a geometric interpretation, before turning our attention to forecast reconciliation in Section~\ref{sec:Reconciliation}.
 
@@
 	 \begin{definition}[Coherent subspace]\label{def:cohspace}
-	 	The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which a set of linear constraints hold for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
+	 	The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which a set of linear constraints holds for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
 	 \end{definition}
@@
 However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom level series, $y_{A,t}$ and $y_{B,t}$.
-In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$, which also span the coherent subspace.
-Thus, while there are multiple ways to define a hierarchy and an associated `$\bm{S}$ matrix', the columns of any `$\bm{S}$ matrix' will always span the same unique coherent subspace.
+In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$.
+However, while there are multiple ways to define an $\bm{S}$ matrix, in all cases the columns will span the same coherent subspace, which is unique.
 
@@
 These include \todo{include references}.
-Furthermore, although the definition makes clear reference to time series, this definition can be easily generalised to any vector-valued data for which some constraints are known to hold.
+Furthermore, although the definition makes clear reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
 
@@
 While the observed data will be coherent by definition, it is important to note that there are a number of reasons why forecasts or predictions may be incoherent.
+\todo{some discussion about why reconciliation v single level}
+
     First, since applications of hierarchical forecasting tend to be very high dimensional a common strategy in practice is to produce forecasts for each time series independently using univariate models.
@@
 
-	As discussed in the previous section, for a number of reasons, coherence is not guaranteed when forecasts are produced for all series.To ensure aligned decision making, it is desirable to adjust forecasts ex post to endure coherence.
+	As discussed in the previous section, for a number of reasons, coherence is not guaranteed when forecasts are produced for all series.
+To ensure aligned decision making, it is desirable to adjust forecasts ex post to ensure coherence.
 This process is referred to as {\em reconciliation}.
@@
 
-	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, and with few exceptions, these belong more specifically to the class of projections.
-This involves pre-multiplying $\hat{\bm{y}}_{t+h|t}$ by a projection matrix that can be written down in a number of ways.
-In \todo{references}, the projection matrix is written in the form $\bm{SG}$ (with $\bm{P}$ used in place of $\bm{G}$ in some cases).
+	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.
+In \todo{references}, this matrix is written in the form $\bm{SG}$ (with $\bm{P}$ used in place of $\bm{G}$ in some cases), where $\bm{G}$ is an $(n-m)\times n$ matrix.
 This facilitates an interpretation of reconciliation as a two-step process, in the first step base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.
-It should be noted that if $\bm{G}$ is set arbitrarily, then $\bm{SG}$ will not necessarily be a projection.
-However for a large class of reconciliation methods, $\bm{G}$ is determined by treating forecast reconciliation as a problem in linear regression model.
-In this case least squares estimators result in values of $\bm{G}$ that do in fact imply that $\bm{SG}$ is a projection.
 
-    First, the linear subspace onto which all points are projected, or the image of the projection, must be defined.
-In our context this can be defined by the $m$ columns of the matrix $\bm{S}$.
-Second, the direction along which points are projected must be defined.
-This will be achieved by defining a matrix $\bm{R}$ with $n-m$ columns then span the direction of projection.
-A schematic of this is presented \todo{include}.
-A projection matrix can then be constructed as $\bm{S}({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ where, ${\bm{R}_{\perp}}$ is an $n\times m$ orthogonal complement to $\bm{R}$ such that ${\bm{R}'_{\perp}}\bm{R}=\bm{0}$.
-It is simple to verify that this construction satisfies the properties of a projection matrix, namely symmetry and idempotence.
+	\subsection{Unbiasedness preserving property}
 
-	A straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
-In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
-In OLS reconciliation, $\bm{R}_{\perp}'= \bm{S}'$ whereas in MinT or WLS reconciliation $\bm{R}_{\perp}'$ takes the form $\bm{S'W}^{-1}$.
-We will be discussing these projections distinctly in the next subsection\todo{needs work}.
+	A sensible property is that reconciliation should not change base forecasts that are already coherent.  That is 
+	\begin{equation}	
+	\label{eq:propcohnochange}
+	\tilde{\bm{y}}_{t+h|t}=\bm{SG}\hat{\bm{y}}_{t+h|t}=\hat{\bm{y}}_{t+h|t}\mbox{ iff }
+	\hat{\bm{y}}_{t+h|t}\in\mathfrak{s}\,.
+	\end{equation}
 
-%	\subsection{Reconciliation in general}\label{sec:reconciliation}
-%
-%	
-%	As discussed, reconciliation is distinct from coherence, since the former refers to a process whereby incoherent forecasts are made coherent.
-Although reconciliation methods for point forecasts are extant in the literature they are rarely defined explicitly.
-We do so here in slightly more general terms than usual.
-%	%We then extend this idea to the novel concept of probabilistic reconciliation.
-%	
-%	Let $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be any set of incoherent point forecasts at time $t+h$ conditional on information up to and including time $t$.
-We now introduce a linear function that converts unreconciled forecasts into new bottom level forecasts.
-%	Let $\bm{G}$ and $\bm{d}$ be an $m\times n$ matrix and $m\times 1$ vector respectively, and let $g:\mathbb{R}^n \rightarrow \mathbb{R}^m$ be the mapping $g(\bm{y})=\bm{G}\bm{y}+\bm{d}$.
-A composition of $g$ and $s(.)$ gives the following definition for point forecast reconciliation.
-%	
-%	\begin{definition}\label{def:reconpoint}
-%		The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $g(.)$ iff
-%		\begin{equation}
-%		\tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{G}\hat{\bm{y}}_{t+h|t}+\bm{d})\,.
-%		\end{equation}
-%	\end{definition}
+	Using geometric intuition, it should be clear that the property in Equation~\ref{eq:propcohnochange} will hold when $\bm{SG}$ is a projection matrix \todo{perhaps find a reference - it is so fundamental that is is on wikipedia and wolfram mathworld}.
+This also implies that the the property in Equation~\ref{eq:propcohnochange} does not hold for arbitrary $\bm{G}$.
+For this reason it is often assumed that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.
+Enforcing these assumptions are equivalent to assuming that  $\bm{SG}$ is a projection matrix.\todo{perhaps elaborate in a proof in appendix}
 
-%	\begin{table}[!h]
-%		\caption{Summary of reconciliation methods that are projections.
-Here, $\hat{\bm{W}}^{sam}$ is the variance covariance matrix of one-step ahead forecast errors, $\hat{\bm{W}}^{shr}$ is a shrinkage estimator more suited to large dimensions proposed by \citet{Schafer2005}, $\hat{\bm{W}}^{wls}$ is the diagonal matrix with diagonal elements $w_{ii}$, and $\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{w}_{ij})}{\sum_{i \neq j}{\hat{w}}^2_{ij}}$, where $w_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{W}}^{sam}$.}\label{table:2}
-%		\centering
-%		\begin{tabular}{lll}
-%			\toprule
-%			\textbf{Method} & \textbf{$\bm{W}$} & \textbf{ $\bm{R}'_\bot$}      \\
-%			\midrule
-%			OLS             &
-%			$\bm{I}$  &
-%			$\bm{S}'$  \\
-%			MinT(Sample)    &
-%			$\hat{\bm{W}}^{sam}$ &
-%			$\bm{S}'(\hat{\bm{W}}^{sam})^{-1}$ \\
-%			MinT(Shrink)    &
-%			$\tau\text{Diag}(\hat{\bm{W}}^{sam}) + (1-\tau)\hat{\bm{W}}^{sam}$ &
-%			$\bm{S}'(\hat{\bm{W}}^{shr})^{-1}$ \\
-%			WLS       &
-%			$\text{Diag}(\hat{\bm{W}}^{shr})$ &
-%			$\bm{S}'(\hat{\bm{W}}^{wls})^{-1}$ \\
-%			\bottomrule
-%		\end{tabular}
-%	\end{table}
-%	
-%	
-%	\begin{figure}
-%		\input{Figs/pointforerec_schematic.tex}
-%		\caption{Summary of probabilistic point reconciliation.
-The mapping $s\circ g$ projects the unreconciled forecast $\hat{\bm{y}}_{t+h|h}$ onto $\mathfrak{s}$, yielding the reconciled forecast $\tilde{\bm{y}}_{t+h|h}$ with subscripts dropped in the figure for ease of presentation.
-Since the smallest hierarchy involves three dimensions, this figure is only a schematic.}\label{fig:pointfr_sch}
-%	\end{figure}
-%	
-%	The columns of $\bm{S}$ and $\bm{R}$ provide a basis for $\mathbb{R}^n$.
-Therefore any incoherent set of point forecasts $\hat{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ can be expressed in terms of coordinates in the basis defined by $\bm{S}$ and $\bm{R}$.
-Let $\tilde{\bm{b}}_{t+h|t}$ and $\tilde{\bm{a}}_{t+h|t}$ be the coordinates corresponding to $\bm{S}$ and $\bm{R}$ respectively, after a change of basis.
-The process of reconciliation involves setting the values of the reconciled bottom-level series to be $\tilde{\bm{b}}_{t+h|t}$, and ignoring $\tilde{\bm{a}}_{t+h|t}$ to ensure coherence.
-From properties of linear algebra it follows that
-%	\[
-%	\hat{\bm{y}}_{t+h|t} = (\bm{S} ~ \bm{R})
-%	\begin{pmatrix}
-%	\tilde{\bm{b}}_{t+h|t}\\ \tilde{\bm{a}}_{t+h|t}
-%	\end{pmatrix}= \bm{S}\tilde{\bm{b}}_{t+h|t} + \bm{R}\tilde{\bm{a}}_{t+h|t},
-%	\]
-%	while the reconciled point forecast is
-%	\[
-%	\tilde{\bm{y}}_{t+h|t} = \bm{S}\tilde{\bm{b}}_{t+h|t}.
-%	\]
-%	
-%	
-%	In order to find $\tilde{\bm{b}}_{t+h|t}$ we require the inverse $(\bm{S} ~ \bm{R})^{-1}$ which is given by
-%	\begin{equation}
-%	(\bm{S} ~ \bm{R})^{-1} = \begin{pmatrix}
-%	(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \\ (\bm{S}'_\bot \bm{R})^{-1}\bm{S}'_\bot
-%	\end{pmatrix}\,,
-%	\end{equation}
-%	where $\bm{S}_{\bot}$ is the orthogonal complements of $\bm{S}$.
-Thus it follows that $\tilde{\bm{b}}_{t+h|t}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h|t}$.
-Here $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$ corresponds to $\bm{G}$ as defined previously.
-
-	\subsection{Motivation of using projections}
-
-	We have seen from the above discussion that projection is playing an important role in point forecast reconciliation.
-Now we turn our attention to the following two theorems that explains the motivation of using projection in this context.
-
-	First, let $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ and assume $\hat{\bm{y}}_{t+h|t}$ is an unbiased prediction; that is $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
+	The property that projections map all vectors in the coherent subspace onto themselves is useful in proving the unbiasedness preserving property of reconciliation, previously proven by\todo{reference Shanika and maybe van Erven Culigari}.
+Suppose that the target of a point forecast is $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ where the expectation is taken over the predictive density.
+Our point forecast is an estimate of this quantity that is random due to sampling variation.
+The point forecast will be unbiased if $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
 
 	\begin{theo}[Unbiasedness preserving property]
-		For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also an unbiased prediction as long as $s\circ g$ is a projection onto $\mathfrak{s}$.
+		For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also an unbiased prediction as long as $\bm{SG}$ is a projection onto $\mathfrak{s}$.
 	\end{theo}
@@
 		\]
-		Since the aggregation constraints hold for the true data generating process, $\bm{\mu}_{t+h|t}$ must lie in $\mathfrak{s}$.
-If $\bm{S}\bm{G}$ is a projection, then it is equivalent to the identity map for all vectors that lie in its range.
-Therefore $\bm{S}\bm{G}\bm{\mu}_{t+h|t}=\bm{\mu}_{t+h|t}$ when $\bm{S}\bm{G}$ is a projection matrix.
+		Since $\bm{\mu}_{t+h|t}$ is an expectation taken with respect to the degenerate predictive density it must lie in $\mathfrak{s}$.
+We have already established that when $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$ then it maps all vectors in $\mathfrak{s}$ onto themselves.
+As such $\bm{S}\bm{G}\bm{\mu}_{t+h|t}=\bm{\mu}_{t+h|t}$ when $\bm{S}\bm{G}$ is a projection matrix.
 	\end{proof}
 
-	We note the above result holds when the projection $s\circ g$ is only onto the coherent subspace $\mathfrak{s}$.
-That is the result does not hold for any general $g$ even when the range of $s\circ g$ is $\mathfrak{s}$.
-To describe this more explicitly suppose $s\circ g$ is a projection to any linear subspace $\mathfrak{L}$ of $\mathfrak{s}$.
-Then $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$ as the projection will move $\bm{\mu}_{t+h|t}$ to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$ as depicted in the Figure \ref{fig:Schematic_3D}.
-Thus $\E_{1:t}(\tilde{\bm{y}}_{t+h|t}) \ne \bm{\mu}_{t+h|t}$ which breaks the unbiasedness.
-Recall the top-down method \citep{Gross1990} with
+	We note that the above result holds when the projection $\bm{SG}$ is only onto the coherent subspace $\mathfrak{s}$ and not for all projection matrices in general.
+To describe this more explicitly suppose $\bm{SG}$ has as its image  $\mathfrak{L}$ which is itself a a lower dimensional linear subspace of $\mathfrak{s}$, i.e.
+$\mathfrak{L}\subset\mathfrak{s}$.
+Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$,  $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$.
+This is depicted in Figure~\ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.
+Therefore in this case, the reconciled forecast will have as its expectation $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and be biased.
+This result has implications in practice, in particular, the top-down method \citep{Gross1990} has
 	\begin{equation}\label{eq:top-downG}
@@
     where $\bm{p} = (p_1,\dots,p_m)'$ is an $m$-dimensional vector consisting a set of proportions which is use to disaggregate the top-level forecasts along the hierarchy.
-\cite{Hyndman2011} claimed that this method is not producing unbiased coherent forecasts even if the base forecasts are unbiased since $\bm{SGS} \ne \bm{S}$ for $\bm{G}$ in (\ref{eq:top-downG}).
-However the more rational explanation is that, in top-down approach the projection $s\circ g$ is not onto $\mathfrak{s}$, but to a linear subspace of $\mathfrak{s}$ spanned by $\bm{p}$.
-Thus from above explanation it follows that  $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$ and hence not producing unbiased forecasts.
+In this case it can be verified that $\bm{SG}$ is idempotent, i,e.
+$\bm{SGSG}=\bm{SG}$ and therefore $\bm{SG}$ is a projection matrix.
+However the image of this projection is not an $m$-dimensional subspace but a $1$-dimensional subspace.
+As such, top-down reconciliation will bias base forecasts when those base forecasts are unbiased.
 
@@
 The red points lying on $\mathfrak{s}$ can be either realisations or coherent forecasts.
+
+	\subsection{Why do projections work?}
 
@@
 	\subsubsection{MinT reconciliation}
+
+	    First, the linear subspace onto which all points are projected, or the image of the projection, must be defined.
+In our context this can be defined by the $m$ columns of the matrix $\bm{S}$.
+Second, the direction along which points are projected must be defined.
+This will be achieved by defining a matrix $\bm{R}$ with $n-m$ columns then span the direction of projection.
+A schematic of this is presented \todo{include}.
+A projection matrix can then be constructed as $\bm{S}({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ where, ${\bm{R}_{\perp}}$ is an $n\times m$ orthogonal complement to $\bm{R}$ such that ${\bm{R}'_{\perp}}\bm{R}=\bm{0}$.
+It is simple to verify that this construction satisfies the properties of a projection matrix, namely symmetry and idempotence.
+
+	A straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
+In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
+In OLS reconciliation, $\bm{R}_{\perp}'= \bm{S}'$ whereas in MinT or WLS reconciliation $\bm{R}_{\perp}'$ takes the form $\bm{S'W}^{-1}$.
+We will be discussing these projections distinctly in the next subsection\todo{needs work}.
 

### 2019-07-02 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
More changes to writing

@@
 	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.
-In \todo{references}, this matrix is written in the form $\bm{SG}$ (with $\bm{P}$ used in place of $\bm{G}$ in some cases), where $\bm{G}$ is an $(n-m)\times n$ matrix.
-This facilitates an interpretation of reconciliation as a two-step process, in the first step base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.
+One way to achieve this is with a matrix $\bm{SG}$ (with $\bm{P}$ used in place of $\bm{G}$ in some cases), where $\bm{G}$ is an $(n-m)\times n$ matrix.
+This facilitates an interpretation of reconciliation as a two-step process, in the first step, base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.
 
-	\subsection{Unbiasedness preserving property}
+	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix.
+We begin by considering the special case of an orthogonal projection whereby $\bm{G}=\left(\bm{S}'\bm{S}\right)^{-1}\bm{S}'$.
+This is equivalent to so called OLS reconciliation as introduced by \cite{Hyndman2011} where the connection between OLS and orthogonal projection should be clear.
+
+	\subsection{Orthogonal projection}
+
+	In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.
+The  first is that reconciliation should adjust the base forecasts as little as possible, i.e.
+the base and reconciled forecast should be `close'.
+The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the truth.
+
+	To address the first of these properties we make the concept of closeness more concrete, by considering the Euclidean distance between the base forecast $\hat{\bm{y}}$ and the reconciled forecast  $\tilde{\bm{y}}$.
+A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ will be as small as possible given that $\tilde{\bm{y}}\in\mathfrak{s}$.
+In this way reconciliation via orthogonal projection does not lead to large adjustments of the base forecasts.
+
+	The second property introduced above has been the focus of theoretical results in the forecast reconciliation literature.
+He we provide a more streamlined version of proofs by \cite{VanErven2015a} and \cite{Wickramasuriya2017} before providing geometrical intuition aimed at simplifying the reader's understanding of these proofs.
+
+	Consider the Euclidean distance between a forecast and the target, which is equivalent to the root total squared error.
+Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$, and let $\|\bm{v}\|_2$ be the $L_2$ norm of vector $\bm{v}$.
+The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.
+
+	\begin{theo}[Distance reducing property]
+		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
+		\begin{equation}
+		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2.
+		\end{equation}
+	\end{theo}
+	\begin{proof}
+		Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ whenever $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$.
+Therefore,
+		\begin{align}
+		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
+		&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
+		\end{align}
+		The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators \citep{Hun2001}, therefore
+		\begin{equation*}
+		\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le
+		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
+		\end{equation*}
+	\end{proof}
+	The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.
+
+	\todo{compare to van Erven and Wickremasuriya more explictly}
+
+	The simple geometric intuition behind the proof is demonstrated in Figure~\ref{fig:Schematic_OLSRecon}.
+In this schematic, the coherent subspace is depicted as a black arrow.
+The base forecast $\hat{\bm{y}}$ is shown as a blue dot.
+Since it is incoherent it does not lie of $\mathfrak{s}$.
+Reconciliation is an orthogonal projection from $\hat{\bm{y}}$ to the coherent subspace yielding the reconciled forecast $\tilde{\bm{y}}$ shown in red.
+Finally, the target of the forecast $\bm{y}$ is displayed as a black point, and although its exact location is unknown to the forecaster, it is known that it will lie somewhere along the coherent subspace.
+
+	\begin{figure}[H]
+		\centering
+		\vspace{-0.9cm}
+		\tiny
+		\resizebox{\linewidth}{!}{\input{Figs/orth_pointforerec_schematic}}
+		\label{fig:Schematic_OLSRecon}
+		\caption{$\hat{\bm{y}}$ is orthogonally projected onto $\mathfrak{s}$}
+
+	\end{figure}
+
+	Figure~\ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle.
+In this triangle the distance between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.
+As such reconciliation is guaranteed to reduce the squared error of the forecast.
+
+    The theorem is in some ways perhaps more powerful than perhaps previously understood.
+The theorem is often stated in terms of expectations\todo{check other proofs}.
+However, the distance reducing property result is stronger than that since it will hold for any realisation and any forecast.
+Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.
+
+    However, in other ways, the theorem is weaker than perhaps often understood.
+First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.
+In particular, this measure is the root of the sum of squared errors of {\em all} variables in the hierarchy.
+As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to worse forecasts for individual series.
+Second, although orthogonal projections are guaranteed to improve on base forecasts both for all realisations and in expectation, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.
+As such referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT.
+It is to oblique projections that we now turn our attention.
+
+	\subsection{Oblique Projections}
+
+	First, the linear subspace onto which all points are projected, or the image of the projection, must be defined.
+In our context this can be defined by the $m$ columns of the matrix $\bm{S}$.
+Second, the direction along which points are projected must be defined.
+This will be achieved by defining a matrix $\bm{R}$ with $n-m$ columns then span the direction of projection.
+A schematic of this is presented \todo{include}.
+A projection matrix can then be constructed as $\bm{S}({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ where, ${\bm{R}_{\perp}}$ is an $n\times m$ orthogonal complement to $\bm{R}$ such that ${\bm{R}'_{\perp}}\bm{R}=\bm{0}$.
+It is simple to verify that this construction satisfies the properties of a projection matrix, namely symmetry and idempotence.
+
+	A straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
+In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
+In OLS reconciliation, $\bm{R}_{\perp}'= \bm{S}'$ whereas in MinT or WLS reconciliation $\bm{R}_{\perp}'$ takes the form $\bm{S'W}^{-1}$.
+We will be discussing these projections distinctly in the next subsection\todo{needs work}.
+
+	In MinT reconciliation, $\bm{R}'_\perp$ is taking the form $\bm{S}'{\bm{W}}^{-1}$, where it can be thought of as orthogonal projections after pre-multiplying by ${\bm{W}^{-1/2}}$.
+That is, the coordinates of incoherent space will be scaled by $\bm{W}^{-1/2}$ which is then followed by the orthogonal projection.
+Alternatively this can be interpreted as an oblique projections in Euclidean space where the columns of $\bm{R}$ is the `direction' along which incoherent point forecasts are projected onto the coherent space $\mathfrak{s}$ as depicted in Figure \ref{fig:pointfr_sch}.
+In terms of distances, MinT minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$ in the transformed space which is same as the scaled Euclidean distance in the original space.
+Latter is also referred to as the Mahalonobis distance.
+We also note that the WLS is a special case of MinT where $\bm{W}^{-1}$ is a diagonal matrix.
+
+	\citet{Wickramasuriya2017} showed that the MinT is optimal with respect to the mean squared forecast errors. 
+	We can provide a more general geometrical explanation to this optimality using the schematic in Figure \ref{fig:MinT_justification}.
+Consider the h-step ahead reconciled forecast errors.
+These can be always approximated by the insample h-step ahead forecast errors.
+Since these errors are coherent, they lies in a direction that is closer to the coherent subspace $\mathfrak{s}$.
+Therefore if you project $\hat{\bm{y}}$ along the direction of these in-sample forecast errors, then you can get closer to the true value $\bm{y}$ as depicted in the schematic.
+Further, unlike OLS, the squared error for MinT reconciled forecasts is not always less than that of base forecasts in every single replication although it outperforms on average.
+
+	\begin{figure}[H]
+		\centering
+		%\vspace{-0.9cm}
+		\small
+		\resizebox{\linewidth}{!}{
+			\input{Figs/MinT_justification}
+		}
+		\caption{A schematic to represent MinT reconciliation.
+Points in orange colour represent the insample errors.
+$\bm{R}$ shows the direction of the insample errors.
+$\hat{\bm{y}}$ is projected onto $\mathfrak{s}$ along the the direction of $\bm{R}$.}\label{fig:MinT_justification}
+	\end{figure}
+
+	\section{The issue of bias}
 
@@
 
-	\subsection{Why do projections work?}
-
-	Now let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$, and let $\|\bm{v}\|_2$ be the $L_2$ norm of vector $\bm{v}$.
-The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.
-
-	\begin{theo}[Distance reducing property]
-		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
-		\begin{equation}
-		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2.
-		\end{equation}
-	\end{theo}
-	\begin{proof}
-		Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ whenever $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$.
-Therefore,
-		\begin{align}
-		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
-		&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
-		\end{align}
-		The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators \citep{Hun2001}, therefore
-		\begin{equation*}
-		\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le
-		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
-		\end{equation*}
-	\end{proof}
-	The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.
-
-	Point reconciliation methods based on projections will always minimise the distance between unreconciled and reconciled forecasts, however the specific distance will depend on the choice of $\bm{R}$.
-Following subsections will explicitly discuss the different projection based reconciliation methods and their optimality based on distinct distance measures.
-
-	\subsubsection{OLS reconciliation}
-
-	Recall that in OLS reconciliation, $\bm{R}_\perp=\bm{S}$ and thus it orthogonally projects $\hat{\bm{y}}$ to the coherent subspace.
-Further, it minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$.
-In addition to that Figure \ref{fig:Schematic_OLSRecon} also shows that $\tilde{\bm{y}}$ is always closer to $\bm{y}$ than $\hat{\bm{y}}$ in terms of the Euclidean distance which is directly followed from the Pythagorean theorem.
-It also implies that the sum of squared error for OLS reconciled forecasts are always less than that for base forecasts.
-
-	\clearpage		
-	\begin{figure}[!ht]
-		\centering
-		\vspace{-0.9cm}
-		\tiny
-		\resizebox{\linewidth}{!}{
-			\input{Figs/orth_pointforerec_schematic}
-		}
-		\caption{$\hat{\bm{y}}$ is orthogonally projected onto $\mathfrak{s}$ }\label{fig:Schematic_OLSRecon}
-	\end{figure}
-
-	\subsubsection{MinT reconciliation}
-
-	    First, the linear subspace onto which all points are projected, or the image of the projection, must be defined.
-In our context this can be defined by the $m$ columns of the matrix $\bm{S}$.
-Second, the direction along which points are projected must be defined.
-This will be achieved by defining a matrix $\bm{R}$ with $n-m$ columns then span the direction of projection.
-A schematic of this is presented \todo{include}.
-A projection matrix can then be constructed as $\bm{S}({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ where, ${\bm{R}_{\perp}}$ is an $n\times m$ orthogonal complement to $\bm{R}$ such that ${\bm{R}'_{\perp}}\bm{R}=\bm{0}$.
-It is simple to verify that this construction satisfies the properties of a projection matrix, namely symmetry and idempotence.
-
-	A straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
-In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
-In OLS reconciliation, $\bm{R}_{\perp}'= \bm{S}'$ whereas in MinT or WLS reconciliation $\bm{R}_{\perp}'$ takes the form $\bm{S'W}^{-1}$.
-We will be discussing these projections distinctly in the next subsection\todo{needs work}.
-
-	In MinT reconciliation, $\bm{R}'_\perp$ is taking the form $\bm{S}'{\bm{W}}^{-1}$, where it can be thought of as orthogonal projections after pre-multiplying by ${\bm{W}^{-1/2}}$.
-That is, the coordinates of incoherent space will be scaled by $\bm{W}^{-1/2}$ which is then followed by the orthogonal projection.
-Alternatively this can be interpreted as an oblique projections in Euclidean space where the columns of $\bm{R}$ is the `direction' along which incoherent point forecasts are projected onto the coherent space $\mathfrak{s}$ as depicted in Figure \ref{fig:pointfr_sch}.
-In terms of distances, MinT minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$ in the transformed space which is same as the scaled Euclidean distance in the original space.
-Latter is also referred to as the Mahalonobis distance.
-We also note that the WLS is a special case of MinT where $\bm{W}^{-1}$ is a diagonal matrix.
-
-	\citet{Wickramasuriya2017} showed that the MinT is optimal with respect to the mean squared forecast errors. 
-	We can provide a more general geometrical explanation to this optimality using the schematic in Figure \ref{fig:MinT_justification}.
-Consider the h-step ahead reconciled forecast errors.
-These can be always approximated by the insample h-step ahead forecast errors.
-Since these errors are coherent, they lies in a direction that is closer to the coherent subspace $\mathfrak{s}$.
-Therefore if you project $\hat{\bm{y}}$ along the direction of these in-sample forecast errors, then you can get closer to the true value $\bm{y}$ as depicted in the schematic.
-Further, unlike OLS, the squared error for MinT reconciled forecasts is not always less than that of base forecasts in every single replication although it outperforms on average.
-
-	 \begin{figure}[H]
-	 		\centering
-	 		%\vspace{-0.9cm}
-	 		\small
-	 		\resizebox{\linewidth}{!}{
-	 			\input{Figs/MinT_justification}
-	 		}
-	 		\caption{A schematic to represent MinT reconciliation.
-Points in orange colour represent the insample errors.
-$\bm{R}$ shows the direction of the insample errors.
-$\hat{\bm{y}}$ is projected onto $\mathfrak{s}$ along the the direction of $\bm{R}$.}\label{fig:MinT_justification}
-	 \end{figure}
-
-	\subsubsection{Bottom-up method}
-
-	Bottom-up method is one of the traditional and simplest ways of producing coherent forecasts.
-Under this approach, the incoherent forecasts are projected to the coherent subspace along the direction which is perpendicular to the bottom level series.
-In terms of distances, this method minimises the distance between reconciled and unreconciled forecasts only along the dimension corresponding to the bottom-level series.
-Therefore bottom-up methods should be thought of as a boundary case of reconciliation methods, since they ultimately do not use information at all levels of the hierarchy.
-
 	\section{Bias correction}

### 2019-07-02 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Tidying up of everything but ooblique projections

@@
 
-    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \todo{citations}, before elaborating on some of the limitations of this understanding.
+    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \cite{Wickramasuriya2017}, \cite{FPP2018} and others, before elaborating on some of the limitations of this understanding.
 A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables.
@@
 The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.
-The hierarchical structure of the data implies that
+The hierarchical structure of the data implies that the following holds for all $t$
 
@@
     \end{equation}
-    where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints, holds for all $t$.
+    where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints.
 
@@
 
-	While such a definition is completely serviceable, it obscures the full generality of many methodologies developed in the literature on so-called hierarchical time series.
-In fact, to apply concepts such as coherence and reconciliation, the data only require two important characteristics; the first is that they are multivariate, the second is that they adhere to linear constraints.
-Below we redefine the concepts of coherence and hierarchical time series using a geometric interpretation, before turning our attention to forecast reconciliation in Section~\ref{sec:Reconciliation}.
+	While such a definition is completely serviceable, it obscures the full generality of the literature on so-called hierarchical time series.
+In fact, concepts such as coherence and reconciliation, defined in full below, only require the data to have two important characteristics; the first is that they are multivariate, the second is that they adhere to linear constraints.
 
 	\subsection{Coherence}\label{sec:cohpointf}
+
+	The property that data adhere to some linear constraints is referred to as {\em coherence}.  We now provide definitions aimed at providing geometric intuition of hierarchical time series.
 
@@
 However, while there are multiple ways to define an $\bm{S}$ matrix, in all cases the columns will span the same coherent subspace, which is unique.
-
-     Also notable by its absence in the above definition is any reference to {\em aggregation}.
-As the literature has shown, the linear constraints need not be aggregation constraints at all.
-For example \todo{find reference} consider weighted sums, while \todo{include Li and Tang reference} consider an example where one variable is the difference of two other variables.
 
@@
 	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.
-In fact, the term {\em hierarchical} is misleading since the literature has covered instances that cannot easily be depicted as hierarchies as in Figure~\ref{fig:basichier}.
-These include \todo{include references}.
-Furthermore, although the definition makes clear reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
+Also notable by its absence in the above definition is any reference to {\em aggregation}.
+In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot easily be depicted in a similar fashion to Figure~\ref{fig:basichier} and or do not involve aggregation.
+{\bf Include brief summary of all non-traditional hierarchies - e.g.
+grouped hierarchies, temporal hierarchies with wierd overlapping, problems where we look at differences between variables etc.}  Finally, although the Definition~\ref{def:cohspace} makes clear reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
 
@@
 	\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
-		Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a point forecast of the values of all series in the hierarchy at time $t+h$, made using information up to and including time $t$.
+		Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a vector of point forecasts of all series in the hierarchy at time $t+h$, made using information up to and including time $t$.
 Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathfrak{s}$.
@@
 	\begin{definition}[Reconciled forecasts]\label{def:reconpoint}
-		Let $\psi$ be a mapping, $\psi:\mathbb{R}^n\rightarrow\mathfrak{s}$.  The point forecast $\tilde{\bm{y}}_{t+h|t}$ ``reconciles'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $\psi(.)$ iff
-		\begin{equation}
-		\tilde{\bm{y}}_{t+h|t}=\psi\left(\hat{\bm{y}}_{t+h|t}\right)\,.
-		\end{equation}
+		Let $\psi$ be a mapping, $\psi:\mathbb{R}^n\rightarrow\mathfrak{s}$.
+The point forecast $\tilde{\bm{y}}_{t+h|t}=\psi\left(\hat{\bm{y}}_{t+h|t}\right)$ is said to ``reconcile'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $\psi(.)$
 	\end{definition}
@@
 	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.
-One way to achieve this is with a matrix $\bm{SG}$ (with $\bm{P}$ used in place of $\bm{G}$ in some cases), where $\bm{G}$ is an $(n-m)\times n$ matrix.
+One way to achieve this is with a matrix $\bm{SG}$, where $\bm{G}$ is an $(n-m)\times n$ matrix  (with some authors using $\bm{P}$ used in place of $\bm{G}$).
 This facilitates an interpretation of reconciliation as a two-step process, in the first step, base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.
 
-	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix.
+	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix onto $\mathfrak{s}$.
+In general a projection matrix has the idemoptence property, i.e.
+$\bm{SG}^2=\bm{SG}$.
+However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped onto itself by that projection.
+\todo{perhaps find a reference - it is so fundamental that is is on wikipedia and wolfram mathworld}  In our context this means that for any $\bm{v}\in\mathfrak{s}$, $\bm{SGv}=\bm{v}$.
+
 	We begin by considering the special case of an orthogonal projection whereby $\bm{G}=\left(\bm{S}'\bm{S}\right)^{-1}\bm{S}'$.
@@
 	To address the first of these properties we make the concept of closeness more concrete, by considering the Euclidean distance between the base forecast $\hat{\bm{y}}$ and the reconciled forecast  $\tilde{\bm{y}}$.
-A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ will be as small as possible given that $\tilde{\bm{y}}\in\mathfrak{s}$.
-In this way reconciliation via orthogonal projection does not lead to large adjustments of the base forecasts.
+A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ will be as small as possible while still ensuring that $\tilde{\bm{y}}\in\mathfrak{s}$.
+In this sense reconciliation via orthogonal projection does leads to the smallest possible adjustments of the base forecasts.
 
@@
 
-	Consider the Euclidean distance between a forecast and the target, which is equivalent to the root total squared error.
+	Consider the Euclidean distance between a forecast and the target.
+This is equivalent to the root of the sum of squared errors over the entire hierarchy.
 Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$, and let $\|\bm{v}\|_2$ be the $L_2$ norm of vector $\bm{v}$.
@@
 
-	\begin{theo}[Distance reducing property]
+	\begin{theo}[Distance reducing property]\label{th:distred}
 		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
@@
 The base forecast $\hat{\bm{y}}$ is shown as a blue dot.
-Since it is incoherent it does not lie of $\mathfrak{s}$.
+Since it is incoherent it does not lie in $\mathfrak{s}$.
 Reconciliation is an orthogonal projection from $\hat{\bm{y}}$ to the coherent subspace yielding the reconciled forecast $\tilde{\bm{y}}$ shown in red.
@@
 
-    The theorem is in some ways perhaps more powerful than perhaps previously understood.
-The theorem is often stated in terms of expectations\todo{check other proofs}.
-However, the distance reducing property result is stronger than that since it will hold for any realisation and any forecast.
+    Theorem~\ref{th:distred} is in some ways more powerful than perhaps previously understood.
+It is often stated in terms of expectations\todo{check other proofs}.
+However, the distance reducing property result is even stronger since it will hold for any realisation and any forecast.
 Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.
 
-    However, in other ways, the theorem is weaker than perhaps often understood.
+    However, in other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood.
 First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.
@@
 
-	\section{The issue of bias}
+	\section{Bias in forecast reconciliation}
 
-	A sensible property is that reconciliation should not change base forecasts that are already coherent.  That is 
-	\begin{equation}	
-	\label{eq:propcohnochange}
-	\tilde{\bm{y}}_{t+h|t}=\bm{SG}\hat{\bm{y}}_{t+h|t}=\hat{\bm{y}}_{t+h|t}\mbox{ iff }
-	\hat{\bm{y}}_{t+h|t}\in\mathfrak{s}\,.
-	\end{equation}
+	Before turning our attention to the issue of bias itself it is important to state a sensible property that any reconciliation method should have.
+That is if base forecasts are already coherent then reconciliation should not change the forecast.
+As stated in Section~\ref{sec:Reconciliation}, this property holds when $\bm{SG}$ is a projection matrix.
+This implies for arbitrary $\bm{G}$, reconciliation may in fact change an already coherent forecast.
 
-	Using geometric intuition, it should be clear that the property in Equation~\ref{eq:propcohnochange} will hold when $\bm{SG}$ is a projection matrix \todo{perhaps find a reference - it is so fundamental that is is on wikipedia and wolfram mathworld}.
-This also implies that the the property in Equation~\ref{eq:propcohnochange} does not hold for arbitrary $\bm{G}$.
-For this reason it is often assumed that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.
-Enforcing these assumptions are equivalent to assuming that  $\bm{SG}$ is a projection matrix.\todo{perhaps elaborate in a proof in appendix}
+	The property that projections map all vectors in the coherent subspace onto themselves is useful in proving the unbiasedness preserving property of reconciliation \todo{reference Shanika and maybe van Erven Culigari}.
+Before restating this proof using a  clear geometric interpretation we discuss in a precise fashion what is meant by unbiasedness.
 
-	The property that projections map all vectors in the coherent subspace onto themselves is useful in proving the unbiasedness preserving property of reconciliation, previously proven by\todo{reference Shanika and maybe van Erven Culigari}.
 	Suppose that the target of a point forecast is $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ where the expectation is taken over the predictive density.
-Our point forecast is an estimate of this quantity that is random due to sampling variation.
-The point forecast will be unbiased if $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
+Our point forecast can be thought of as an estimate of this quantity.
+The forecast is random due to uncertainty in the training sample and it is with respect to this uncertainty that unbiasedness refers.
+More concretely, the point forecast will be unbiased if $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
 
@@
 
-	\begin{figure}[!b]
+	\begin{figure}[H]
 		\centering
@@
 	\end{figure}
+
+	Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.
+Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix.
+\todo{perhaps elaborate in a proof in appendix}  When the problem is viewed through the prism of imposing a constraint $\bm{GS}=\bm{I}$ to ensure unbiasedness is preserved, one may be tempted to deal with biased forecasts by selecting $\bm{G}$ is an unconstrained manner.
+However, equipped with a geometric understanding of the problem, we would advise against this approach.
+Our own solution to dealing with biased forecasts is discussed in detail in the next section.
 

### 2019-07-03 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added discussion of generalised Euclidean disatance

@@
 
+	In particular, this measure is the
+
+	One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the root of the sum of squared errors of {\em all} variables in the hierarchy.
+A clear shortcoming of this measure of forecast accuracy is that forecasts errors in all series should not necessarily be treated equally.
+For example, in hierarchies, top-level series tend to have a much larger scale than bottom level series.
+Even when two series are on a similar scale, series that are more predictable or less variable will tend to be downweighted by simply aggregating square errors.
+An even more sophisticated understanding may take the correlation between series into account.
+All of these considerations lead towards reconciliation of the form $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, where $\bm{W}$ is a symmetric matrix.
+Generally, it is assumed that $\bm{W}$ is invertible, otherwise a pseudo inverse can be used.
+
+	It should be noted that  $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix.
+However this matrix can be considered to be an orthogonal projection for a different geometry, namely the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
+One way to understand this geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$.
+This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{-1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{-1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{-1/2}\tilde{\bm{y}}$.
+The transformed reconciled forecast results from an orthogonal projection in the transformed space since
+
+	\begin{align}
+	\tilde{\bm{y}}^*&=\bm{W}^{-1/2}\tilde{\bm{y}}\\&=\bm{W}^{-1/2}\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}
+	\\&=\bm{S}^*\left(\bm{S}^{*'}\bm{S}^*\right)^{-1}\bm{S}^{*'}\hat{\bm{y}^*}
+	\end{align}
+
+	Another way of understanding the generalised Euclidean geometry is that it is defined by the norm $\bm{v}'\bm{W}^{1}\bm{v}$.
+This interpretation is quite instructive when it comes to thinking about the connection between distances and loss functions.
+In the generalised Euclidean geometry, the distance between the reconciled forecast and the realisation is given by $(\hat{\bm{y}}-\bm{y})'\bm{W}^{-1}(\hat{\bm{y}}-\bm{y})$.
+For diagonal $\bm{W}$ this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix this is equivalent to a Mahalanobis distance.
+As such Theorem~\ref{th:distred} can easily be generalised.
+If the objective function is some weighted sum of squared errors, or a Mahalanobis distance, then the projection matrix $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts, for an appropriately selected $\bm{W}$.
+
 	First, the linear subspace onto which all points are projected, or the image of the projection, must be defined.

### 2019-07-03 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
tidy up

@@
 {\bf Include brief summary of all non-traditional hierarchies - e.g.
-grouped hierarchies, temporal hierarchies with wierd overlapping, problems where we look at differences between variables etc.}  Finally, although the Definition~\ref{def:cohspace} makes clear reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
+grouped hierarchies, temporal hierarchies with wierd overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes clear reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
 
@@
 
-	As discussed in the previous section, for a number of reasons, coherence is not guaranteed when forecasts are produced for all series.
+	As discussed in the previous section, coherence is not guaranteed for a number of reasons.
 To ensure aligned decision making, it is desirable to adjust forecasts ex post to ensure coherence.
@@
 	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.
-One way to achieve this is with a matrix $\bm{SG}$, where $\bm{G}$ is an $(n-m)\times n$ matrix  (with some authors using $\bm{P}$ used in place of $\bm{G}$).
+One way to achieve this is with a matrix $\bm{SG}$, where $\bm{G}$ is an $(n-m)\times n$ matrix  (some authors use $\bm{P}$ used in place of $\bm{G}$).
 This facilitates an interpretation of reconciliation as a two-step process, in the first step, base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.
@@
 	We begin by considering the special case of an orthogonal projection whereby $\bm{G}=\left(\bm{S}'\bm{S}\right)^{-1}\bm{S}'$.
-This is equivalent to so called OLS reconciliation as introduced by \cite{Hyndman2011} where the connection between OLS and orthogonal projection should be clear.
+This is equivalent to so called OLS reconciliation as introduced by \cite{Hyndman2011}.
+We refrain from any discussion of regression models focusing instead on geometric interpretations.
+However the connection between OLS and orthogonal projection should be clear, in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection of the data onto the span of the regressors.
 
@@
 the base and reconciled forecast should be `close'.
-The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the truth.
+The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realisation that is the target of the forecast.
 
@@
 A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ will be as small as possible while still ensuring that $\tilde{\bm{y}}\in\mathfrak{s}$.
-In this sense reconciliation via orthogonal projection does leads to the smallest possible adjustments of the base forecasts.
+In this sense reconciliation via orthogonal projection leads to the smallest possible adjustments of the base forecasts.
 
@@
 	\begin{proof}
-		Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ whenever $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$.
+		Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ since $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$.
 Therefore,
@@
 	\subsection{Oblique Projections}
-
-	In particular, this measure is the
 

### 2019-07-03 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Intution about MinT provided

@@
 Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.
-
+    f
     However, in other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood.
@@
 
-	First, the linear subspace onto which all points are projected, or the image of the projection, must be defined.
-In our context this can be defined by the $m$ columns of the matrix $\bm{S}$.
-Second, the direction along which points are projected must be defined.
-This will be achieved by defining a matrix $\bm{R}$ with $n-m$ columns then span the direction of projection.
-A schematic of this is presented \todo{include}.
-A projection matrix can then be constructed as $\bm{S}({\bm{R}'_{\perp}}\bm{S})^{-1}\bm{R}_{\perp}'$ where, ${\bm{R}_{\perp}}$ is an $n\times m$ orthogonal complement to $\bm{R}$ such that ${\bm{R}'_{\perp}}\bm{R}=\bm{0}$.
-It is simple to verify that this construction satisfies the properties of a projection matrix, namely symmetry and idempotence.
+	\subsection{MinT}
 
-	A straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.
-In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$.
-In OLS reconciliation, $\bm{R}_{\perp}'= \bm{S}'$ whereas in MinT or WLS reconciliation $\bm{R}_{\perp}'$ takes the form $\bm{S'W}^{-1}$.
-We will be discussing these projections distinctly in the next subsection\todo{needs work}.
+	While the properties discussed so far hold for any projection matrix, the MinT method of \cite{Wickramasuriya2017} has an additional optimality property.
+\cite{Wickramasuriya2017} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by an oblique projection with a particular choice of $\bm{W}$.
+This choice is that $\bm{W}$ should be the forecast error covariance matrix where errors come from using the base forecasts.
+Although the base forecast error covariance matrix is unknown, it can be estimated using in-sample errors.
 
-	In MinT reconciliation, $\bm{R}'_\perp$ is taking the form $\bm{S}'{\bm{W}}^{-1}$, where it can be thought of as orthogonal projections after pre-multiplying by ${\bm{W}^{-1/2}}$.
-That is, the coordinates of incoherent space will be scaled by $\bm{W}^{-1/2}$ which is then followed by the orthogonal projection.
-Alternatively this can be interpreted as an oblique projections in Euclidean space where the columns of $\bm{R}$ is the `direction' along which incoherent point forecasts are projected onto the coherent space $\mathfrak{s}$ as depicted in Figure \ref{fig:pointfr_sch}.
-In terms of distances, MinT minimises the Euclidean distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$ in the transformed space which is same as the scaled Euclidean distance in the original space.
-Latter is also referred to as the Mahalonobis distance.
-We also note that the WLS is a special case of MinT where $\bm{W}^{-1}$ is a diagonal matrix.
-
-	\citet{Wickramasuriya2017} showed that the MinT is optimal with respect to the mean squared forecast errors. 
-	We can provide a more general geometrical explanation to this optimality using the schematic in Figure \ref{fig:MinT_justification}.
-Consider the h-step ahead reconciled forecast errors.
-These can be always approximated by the insample h-step ahead forecast errors.
-Since these errors are coherent, they lies in a direction that is closer to the coherent subspace $\mathfrak{s}$.
-Therefore if you project $\hat{\bm{y}}$ along the direction of these in-sample forecast errors, then you can get closer to the true value $\bm{y}$ as depicted in the schematic.
-Further, unlike OLS, the squared error for MinT reconciled forecasts is not always less than that of base forecasts in every single replication although it outperforms on average.
+	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.
+Suppose the in-sample errors are given by the orange points.
+They provide information on the most likely direction of large deviations from the coherent subspace.
+This direction is denoted by $\bm{R}$.
+Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts.
+One such forecast is depicted in blue as $\hat{\bm{y}}$.
+An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection.
+Imagining a similar oblique projection along $\bm{R}$ for all the grey points yield reconciled forecasts tightly packed near the target $\bm{y}$.
+In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts.\todo{needs picture with all points projected obliquely then orthogonally}.
 
@@
 		\resizebox{\linewidth}{!}{
-			\input{Figs/MinT_justification}
+			\input{Figs/insampledir}
 		}
@@
 Points in orange colour represent the insample errors.
-$\bm{R}$ shows the direction of the insample errors.
-$\hat{\bm{y}}$ is projected onto $\mathfrak{s}$ along the the direction of $\bm{R}$.}\label{fig:MinT_justification}
+$\bm{R}$ shows the most likely direction of deviations from the coherent subspace.
+$\hat{\bm{y}}$ is projected onto $\mathfrak{s}$ along the the direction of $\bm{R}$.}\label{fig:MinT_justification1}
+	\end{figure}
+
+	\begin{figure}[H]
+		\centering
+		%\vspace{-0.9cm}
+		\small
+		\resizebox{\linewidth}{!}{
+			\input{Figs/oblique_justification2}
+		}
+		\caption{A schematic to represent MinT reconciliation.
+Grey points indicate potential realisations of the base forecast while the blue dot indicates one such realisation.
+The black dot ${\bm y}$ denotes the (unknown) target of the forecast.}\label{fig:MinT_justification2}
 	\end{figure}

### 2019-07-03 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
fixed up bias, some bullet points for intro

@@
 	\section{Introduction}\label{sec:intro}
+
+	Have to explain why we are writing this
+	\begin{itemize}
+		\item Geometric intuition - restate existing results but with a new understanding.
+		\item In particular champion projections.
+		\item State that paper is in some ways a review paper.
+		\item Propose a simple solution to the issue of bias.
+	\end{itemize}
 
@@
 That is if base forecasts are already coherent then reconciliation should not change the forecast.
-As stated in Section~\ref{sec:Reconciliation}, this property holds when $\bm{SG}$ is a projection matrix.
-This implies for arbitrary $\bm{G}$, reconciliation may in fact change an already coherent forecast.
+As stated in Section~\ref{sec:Reconciliation}, this property holds only when $\bm{SG}$ is a projection matrix.
+As a corollary, reconciling using an arbitrary $\bm{G}$,  may in fact change an already coherent forecast.
 
@@
 
-	We note that the above result holds when the projection $\bm{SG}$ is only onto the coherent subspace $\mathfrak{s}$ and not for all projection matrices in general.
+	We note that the above result holds when the projection $\bm{SG}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general.
 To describe this more explicitly suppose $\bm{SG}$ has as its image  $\mathfrak{L}$ which is itself a a lower dimensional linear subspace of $\mathfrak{s}$, i.e.
@@
 This is depicted in Figure~\ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.
-Therefore in this case, the reconciled forecast will have as its expectation $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and be biased.
-This result has implications in practice, in particular, the top-down method \citep{Gross1990} has
+In this case, the reconciled forecast will have as its expectation $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and be biased.
+
+	This result has implications in practice. The top-down method \citep{Gross1990} has 
 	\begin{equation}\label{eq:top-downG}
@@
 	\end{equation}
-    where $\bm{p} = (p_1,\dots,p_m)'$ is an $m$-dimensional vector consisting a set of proportions which is use to disaggregate the top-level forecasts along the hierarchy.
+    where $\bm{p} = (p_1,\dots,p_m)'$ is an $m$-dimensional vector consisting a set of proportions used to disaggregate the top-level forecast.
 In this case it can be verified that $\bm{SG}$ is idempotent, i,e.
@@
 However the image of this projection is not an $m$-dimensional subspace but a $1$-dimensional subspace.
-As such, top-down reconciliation will bias base forecasts when those base forecasts are unbiased.
+As such, top-down reconciliation produces biased forecasts even when the base forecasts are unbiased.
 
@@
 Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix.
-\todo{perhaps elaborate in a proof in appendix}  When the problem is viewed through the prism of imposing a constraint $\bm{GS}=\bm{I}$ to ensure unbiasedness is preserved, one may be tempted to deal with biased forecasts by selecting $\bm{G}$ is an unconstrained manner.
+\todo{perhaps elaborate in a proof in appendix}  However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$.
+This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ is an unconstrained manner.
 However, equipped with a geometric understanding of the problem, we would advise against this approach.
-Our own solution to dealing with biased forecasts is discussed in detail in the next section.
+Dropping the constraint is not just about bias $\bm{GS}=\bm{I}$ but rather moves away projections and all of their attractive properties.
+Our own solution to dealing with biased forecasts is to bias correct, or translate the forecast prior to reconciling via projections.
+It is to this approach that we now turn our attention.
 

### 2019-07-04 Application-R/Application-PrisonData/PrisonData-results.Rmd
Added the application on Prison data

---
title: "Prison Data Analysis"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(fpp2)
library(Matrix)
library(hts)
library(readr)
library(BigVAR)
library(vars)
library(tibble)
library(kableExtra)

```

Prison data disaggregate into $4$ grouping variables, namely states(8), gender(2), legal status(2) and indigenous/non-indigenous. We chose only states, gender and legal status as the grouping variables in this analysis. Thus we have $m=32$ bottom level series and $n=81$ total number of series in the hierarchy.

```{r echo=FALSE}
load("PrisonData_PointFRecon_LASSOandLS.RData")

Prison.gts %>% aggts(level=0:3) %>% autoplot()

```

In this experiment we are trying to show that the reconciliation via projection still increase the accuracy for biased incoherent forecasts after adjusting for bias. To show this, we first obtain the incoherent forecasts via lasso type models.

For all aggregate-level series we fit AR(1) model including all bottom-level series at lag $1$ as exogenous variables. i.e., we fit the following model,

$$y'_{i,t} = \gamma + \alpha_1 y'_{i,t-1} + \alpha_2 y'_{i,t-2} + \alpha_3 y'_{i,t-3} + \alpha_4 y'_{i,t-4} + \boldsymbol{\beta b'}_{t-1} + \boldsymbol{u}_t, \quad i=1,...,n-m, \quad t=1,...,T.$$

where $\boldsymbol{b}_t$ is the vector of bottom level series. When estimating the parameters, we add lasso type penalisation. Thus we are minimising the following objective function to estimate $\gamma, \alpha$ and $\boldsymbol{\beta}$. 
$$\operatorname{min}_{\gamma, \alpha, \boldsymbol{\beta}} \sum_{t=1}^T ||y'_{i,t} - \gamma - \alpha_1 y'_{i,t-1}- \alpha_2 y'_{i,t-2} - \alpha_3 y'_{i,t-3} - \alpha_4 y'_{i,t-4} - \boldsymbol{\beta b}_{t-1}||_2^2 + \lambda(||\boldsymbol{\alpha}||_1+||\boldsymbol{\beta}||_1),$$
where, 
$\boldsymbol{\alpha} = (\alpha_1, \alpha_2, \alpha_3, \alpha_4)$.

The forecasts follows from this optimisation will be biased. Also we get the least squares estimator without the regularisation thus giving us unbiased forecasts.

Similarly for bottom-level series we fit a VAR(1) system with the penalty and without penalty to get biased and unbiased forecasts.

### Experiment 1

We consider data from Q1-2005 to Q4-2013 as the training set and Q1-2014 to Q4-2018 as test set. This will give us more observations than the number of paramters to be estimated. Thus least squares estimation method will also works.

```{r echo=FALSE}

DF %>% 
  filter(`F-method`=="Lasso") %>% 
  group_by(`F-method`, `R-method`) %>% 
  summarise(MSE = round(mean(SquaredE), digits = 4)) %>% 
  kable(format = "latex") %>% kable_styling("striped")

DF %>% 
  filter(`F-method`=="Least Squares") %>% 
  group_by(`F-method`, `R-method`) %>% 
  summarise(MSE = round(mean(SquaredE), digits = 4)) %>% 
  kable(format = "latex") %>% kable_styling("striped")

```

```{r echo=FALSE}
DF %>% 
  group_by(`F-method`, `R-method`, Replication) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  filter(`F-method`=="Lasso", `R-method`%in% c("Base_bias.adjust", "OLS")) %>% 
  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
  geom_line() + ggtitle("OLS vs Base(LASSO)")

```

```{r echo=FALSE}
DF %>% 
  group_by(`F-method`, `R-method`, Replication) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  filter(`F-method`=="Lasso", `R-method`%in% c("Base_bias.adjust", "MinT(Shrink)")) %>% 
  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
  geom_line() + ggtitle("MinT(Shrink) vs Base(LASSO)")

```

```{r echo=FALSE}
DF %>% 
  group_by(`F-method`, `R-method`, Replication) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  filter(`F-method`=="Least Squares", `R-method`%in% c("Base", "OLS")) %>% 
  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
  geom_line() + ggtitle("OLS vs Base(Least squares)")

```

```{r echo=FALSE}
DF %>% 
  group_by(`F-method`, `R-method`, Replication) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  filter(`F-method`=="Least Squares", `R-method`%in% c("Base", "MinT(Shrink)")) %>% 
  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
  geom_line() + ggtitle("MinT(Shrink) vs Base(Least squares)")

```

### 2019-07-04 Application-R/Application-PrisonData/Exampl-fpp2.R

@@ -1,0 +1,35 @@
+library(fpp2)
+library(tidyverse)
+library(hts)
+
+prison.gts <- gts(prison/1e3, characters = c(3,1,9),
+                  gnames = c("State", "Gender", "Legal",
+                             "State*Gender", "State*Legal",
+                             "Gender*Legal"))
+
+prison.gts %>% aggts(level=0:3) %>% autoplot()
+Prison_allts <- allts(prison.gts)
+
+#BU forecasts for prison data
+Fc1 <- forecast(prison.gts, method="bu", fmethod="arima")
+
+
+S <- smatrix(prison.gts)
+
+#Bottom up G
+m <- ncol(prison)
+n <- ncol(Prison_allts)
+
+Null.ma <- matrix(0,m,(n-m))
+BU_G <- cbind(Null.ma, diag(1,m,m))
+
+Base_forecasts <- matrix(NA, nrow = 8, ncol = n)
+
+for(i in 1:n) {
+  fit_training <- auto.arima(Prison_allts[,i])
+  Base_forecasts[,i] <- forecast(fit_training, h=8)$mean
+}
+
+Recon_BU <- S %*% BU_G %*% t(Base_forecasts)
+
+

### 2019-07-04 Application-R/Application-PrisonData/Experiment/LassoForTotalSeries.R

@@ -1,0 +1,128 @@
+library(tsibble)
+library(matrixcalc)
+library(reshape2)
+
+Prison_bot.ts <- read.csv("Prison.bottom.TS.csv")[,-1]
+
+Prison.gts <- gts(Prison_bot.ts/1e3, characters = c(3,1,9),
+                  gnames = c("State", "Gender", "Legal",
+                             "State*Gender", "State*Legal",
+                             "Gender*Legal"))
+
+
+Prison_allts <- allts(Prison.gts)
+
+m <- ncol(Prison_bot.ts)
+n <- ncol(Prison_allts)
+j=1
+Train <- Prison_allts[j:(40+j-1),]
+Test <- Prison_allts[(40+j):56,]
+Bts_tr <- Train[,(n-m+1):n]
+
+
+##-- Using glmnet package --##
+
+library(glmnet)
+
+
+y <- Train[,1]
+
+y_diff1 <- diff(y, lag = 1)
+B_diff <- diff(Bts_tr, lag = 1)
+
+y_diff1_1 <- lag(y_diff1, 1)
+y_diff1_2 <- lag(y_diff1, 2)
+y_diff1_3 <- lag(y_diff1, 3)
+y_diff1_4 <- lag(y_diff1, 4)
+
+B_diff_1 <- matrix(0, nrow = length(y_diff1), ncol = m)
+
+for (i in 1:m) {
+  
+  B_diff_1[,i] <- lag(B_diff[,i], 1)
+  
+}
+
+colnames(B_diff_1) <- colnames(Bts_tr)
+
+y1 <- y_diff1_1[-(1:4)]
+y2 <- y_diff1_2[-(1:4)]
+y3 <- y_diff1_3[-(1:4)]
+y4 <- y_diff1_4[-(1:4)]
+X <- data.frame(y1, y2, y3, y4, B_diff_1[-(1:4),]) %>% as.matrix()
+
+Y <- y_diff1[-(1:4)]
+
+y_1 <- lag(y, 1)[-1]
+
+
+##--LASSO--##
+
+Pars <- list()
+lambda <- seq(0, 0.25, 0.01)
+y_fc <- numeric(length(lambda))
+mean.resid <- numeric(length(lambda))
+MSE <- numeric(length(lambda))
+Non_zero_Coef <- character(length(lambda))
+
[…]

### 2019-07-04 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
better bridging paragraph between section 2 and section 3

@@
 	{
-		\title{\bf Hierarchical Forecasts Reconciliation}
+		\title{\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.}
 		\author{Puwasala Gamakumara\thanks{
@@
 Also notable by its absence in the above definition is any reference to {\em aggregation}.
-In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot easily be depicted in a similar fashion to Figure~\ref{fig:basichier} and or do not involve aggregation.
+In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure~\ref{fig:basichier} and/or do not involve aggregation.
 {\bf Include brief summary of all non-traditional hierarchies - e.g.
-grouped hierarchies, temporal hierarchies with wierd overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes clear reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
+grouped hierarchies, temporal hierarchies with wierd overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
 
@@
 
-    Without any loss of generality, that above definition could also be applied to prediction for multivariate data in general, rather than just forecasting of time series.
-While the observed data will be coherent by definition, it is important to note that there are a number of reasons why forecasts or predictions may be incoherent.
-\todo{some discussion about why reconciliation v single level}
+    Without any loss of generality, the above definition could also be applied to prediction for multivariate data in general, rather than just forecasting of time series.
+Much of the early literature that dealt with the problem of forecasting hierarchical time series \citep[see][and references therein]{Gross1990} produced forecasts at a single level of the hierarchy in the first stage.
+Subsequently forecasts for all series were recovered through aggregation, disaggregation according to historical or forecast proportions or some combination of both.
+As such incoherent forecasts were not a problem in these earlier papers.
 
-    First, since applications of hierarchical forecasting tend to be very high dimensional a common strategy in practice is to produce forecasts for each time series independently using univariate models.
-Second, even where a multivariate model is used for the full vector of observations, it may be difficult to capture the linear constraints inherent in the data particularly for complicated non-linear models.
-Third, in some cases judgemental adjustments may be made inducing incoherent forecasts.
+    Forecasting a single level of the hierarchy did not, however echo common practice within many industries.\todo{might need refs}  In many organisations different departments or `silos' each produced their own forecasts, often with their own information sets and judgemental adjustments.
+This approach does have several advantages over only forecasting a single level.
+First, there is no loss of information since all bottom levels are modelled.
+Second, modelling top level series often identifies features such as trend and seasonality that cannot be detected in noisy disaggregate data.
+Unfortunately, however, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.
+This problem of incoherent forecasts cannot in general be solved by multivariate modelling either.
+Instead, the solution to incoherent forecasts is to make an ex post adjustment that ensures coherence, a process known as {\em forecast reconciliation}
 
@@
 
-	As discussed in the previous section, coherence is not guaranteed for a number of reasons.
-To ensure aligned decision making, it is desirable to adjust forecasts ex post to ensure coherence.
-This process is referred to as {\em reconciliation}.
+	The problem of forecast reconciliation is predicated on there being an $n$-vector of forecasts that are incoherent.
+We will call these {\em base forecasts} and denote them as $\hat{\bm{y}}_{t+h|h}$, where the subscript $t+h|h$ implies that the forecast is made as time $t$ for a period $h$ steps into the future.
+In the sequel, this subscript will be dropped at times for ease of exposition.
 In the most general terms, reconciliation can be defined as follows
@@
 		Let $\psi$ be a mapping, $\psi:\mathbb{R}^n\rightarrow\mathfrak{s}$.
-The point forecast $\tilde{\bm{y}}_{t+h|t}=\psi\left(\hat{\bm{y}}_{t+h|t}\right)$ is said to ``reconcile'' $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $\psi(.)$
+The point forecast $\tilde{\bm{y}}_{t+h|t}=\psi\left(\hat{\bm{y}}_{t+h|t}\right)$ is said to ``reconcile'' a base forecast $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $\psi(.)$
 	\end{definition}

### 2019-07-18 Application-R/Application-PrisonData/Bias-with-log-trans/PrisonData-LogTrans-results.Rmd
Fitting models with log transformed data

---
title: "Prison Data Analysis"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(fpp2)
library(Matrix)
library(hts)
library(readr)
library(BigVAR)
library(vars)
library(tibble)
library(kableExtra)
library(reshape2)

```

Prison data disaggregate into $4$ grouping variables, namely states(8), gender(2), legal status(2) and indigenous/non-indigenous. We chose only states, gender and legal status as the grouping variables in this analysis. Thus we have $m=32$ bottom level series and $n=81$ total number of series in the hierarchy.

```{r echo=FALSE}
load("PrisonData_PointFRecon_LogTrans_UnivARIMA.RData")

Prison.gts %>% aggts(level=0:3) %>% autoplot()

```

In this experiment we are trying to show that the reconciliation via projection still increase the accuracy for biased incoherent forecasts after adjusting for bias.

### Experiment 1 - Univariate ARIMA models with log transformation

We consider data from Q1-2005 to Q4-2013 as the training set and Q1-2014 to Q4-2018 as test set. we fit univariate ARIMA models for each series for log transformed data. The back-transformed forecasts will be biased. Unbiased forecasts will be obtained by adjusting the bias forecasts.

```{r echo=FALSE}

DF %>% 
  group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) -> Avg_MSE

Avg_MSE_tab1 <- Avg_MSE %>% dcast(`R-method` ~ Forecast_Horizon + `F-method`, value.var = "MSE")

colnames(Avg_MSE_tab1) <- c("R-method", rep(c("Biased", "Unbiased"), 4))

Avg_MSE_tab1 %>% 
  kable(format = "latex") %>% 
  kableExtra::add_header_above(c(" " = 1, "h=1" = 2, "h=2" = 2, "h=3" = 2, "h=4" = 2))

Avg_MSE %>% filter(`F-method` == "ARIMA_bias", `R-method` == "Base") %>% 
  slice() %>% 
  ungroup() %>% 
  dplyr::select(MSE) %>% 
  as_vector() -> ARIMA_bias_Base

Avg_MSE %>% filter(`F-method` == "ARIMA_unbias", `R-method` == "Base") %>% 
  slice() %>% 
  ungroup() %>% 
  dplyr::select(MSE) %>% 
  as_vector() -> ARIMA_unbias_Base

Avg_MSE %>% 
  spread(key = `F-method`, value = MSE) %>% 
  mutate(Bias_SS.MSE = round((1-(ARIMA_bias/ARIMA_bias_Base))*100, digits = 2), 
         Unbias_SS.MSE = round((1-(ARIMA_unbias/ARIMA_unbias_Base))*100, digits = 2)) -> Avg_SS.MSE

Avg_SS.MSE %>% 
  filter(`R-method` == "Base") %>% 
  mutate(Bias_SS.MSE = ARIMA_bias, Unbias_SS.MSE = ARIMA_unbias) %>% 
  rbind(Avg_SS.MSE) %>% 
  filter(Bias_SS.MSE != 0) %>% 
  dplyr::select(-ARIMA_bias, -ARIMA_unbias) %>% 
  gather(Bias_SS.MSE, Unbias_SS.MSE, key = "F-method", value = Skill.Score) -> Avg_SS.MSE

Avg_SS.MSE_tab1 <- Avg_SS.MSE %>% dcast(`R-method` ~ Forecast_Horizon + `F-method`, value.var = "Skill.Score")

colnames(Avg_SS.MSE_tab1) <- c("R-method", rep(c("Biased", "Unbiased"), 4))

Avg_SS.MSE_tab1 %>% 
  kable(format = "latex") %>% 
  kableExtra::add_header_above(c(" " = 1, "h=1" = 2, "h=2" = 2, "h=3" = 2, "h=4" = 2))

```

```{r echo=FALSE}

DF %>% 
  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  filter(`F-method`=="ARIMA_bias", `R-method`%in% c("Base", "OLS")) %>% 
  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
  geom_line() + 
  facet_wrap( ~ Forecast_Horizon, scales = "free_y") + 
  ggtitle("OLS Vs Base (Biased)")

DF %>% 
  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS")) %>% 
  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
  geom_line() + 
  facet_wrap( ~ Forecast_Horizon, scales = "free_y")+ 
  ggtitle("OLS Vs Base (Unbiased)")

DF %>% 
  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  filter(`F-method`=="ARIMA_bias", `R-method`%in% c("Base", "MinT(Shrink)")) %>% 
  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
  geom_line() + 
  facet_wrap( ~ Forecast_Horizon, scales = "free_y") + 
  ggtitle("MinT(Shrink) Vs Base (Biased)")

DF %>% 
  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "MinT(Shrink)")) %>% 
  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
  geom_line() + 
  facet_wrap( ~ Forecast_Horizon, scales = "free_y")+ 
  ggtitle("MinT(Shrink) Vs Base (Unbiased)")

```

### Experiment 2 - Time series regression with ARIMA errors for log transformed data

In this exercise we fit time series regression models with ARIMA errors for each series for log transformed data. All bottom level series were considered as the regressors for each aggregate level series. Lag of all bottom level series except the bottom level regresand were considered as the regressors. All models were fitted to the back-transformed series. Then the back-transformed forecasts will be biased. Unbiased forecasts will be obtained by adjusting the bias forecasts.

```{r echo=FALSE}
load("PrisonData_PointFRecon_LogTrans_DynReg_H1-H4.RData")
```

```{r echo=FALSE}

DF %>% 
  group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) -> Avg_MSE

Avg_MSE_tab1 <- Avg_MSE %>% dcast(`R-method` ~ Forecast_Horizon + `F-method`, value.var = "MSE")

colnames(Avg_MSE_tab1) <- c("R-method", rep(c("Biased", "Unbiased"), 4))

Avg_MSE_tab1 %>% 
  kable(format = "latex") %>% 
  kableExtra::add_header_above(c(" " = 1, "h=1" = 2, "h=2" = 2, "h=3" = 2, "h=4" = 2))

Avg_MSE %>% filter(`F-method` == "ARIMA_bias", `R-method` == "Base") %>% 
  slice() %>% 
  ungroup() %>% 
  dplyr::select(MSE) %>% 
  as_vector() -> ARIMA_bias_Base

Avg_MSE %>% filter(`F-method` == "ARIMA_unbias", `R-method` == "Base") %>% 
  slice() %>% 
  ungroup() %>% 
  dplyr::select(MSE) %>% 
  as_vector() -> ARIMA_unbias_Base

Avg_MSE %>% 
  spread(key = `F-method`, value = MSE) %>% 
  mutate(Bias_SS.MSE = round((1-(ARIMA_bias/ARIMA_bias_Base))*100, digits = 2), 
         Unbias_SS.MSE = round((1-(ARIMA_unbias/ARIMA_unbias_Base))*100, digits = 2)) -> Avg_SS.MSE

Avg_SS.MSE %>% 
  filter(`R-method` == "Base") %>% 
  mutate(Bias_SS.MSE = ARIMA_bias, Unbias_SS.MSE = ARIMA_unbias) %>% 
  rbind(Avg_SS.MSE) %>% 
  filter(Bias_SS.MSE != 0) %>% 
  dplyr::select(-ARIMA_bias, -ARIMA_unbias) %>% 
  gather(Bias_SS.MSE, Unbias_SS.MSE, key = "F-method", value = Skill.Score) -> Avg_SS.MSE

Avg_SS.MSE_tab1 <- Avg_SS.MSE %>% dcast(`R-method` ~ Forecast_Horizon + `F-method`, value.var = "Skill.Score")

colnames(Avg_SS.MSE_tab1) <- c("R-method", rep(c("Biased", "Unbiased"), 4))

Avg_SS.MSE_tab1 %>% 
  kable(format = "latex") %>% 
  kableExtra::add_header_above(c(" " = 1, "h=1" = 2, "h=2" = 2, "h=3" = 2, "h=4" = 2))

```

### 2019-07-18 Application-R/Application-PrisonData/Bias-with-log-trans/PrisonData_PointFRecon_LogTrans_DynReg.R

@@ -1,0 +1,366 @@
+## This file contains the analysis of Prison data using Hierarchical forecasting methods. 
+## Data form a grouped hierarchy with 3 grouping variables - 8-states, 2-Gender, 2-Legal-status. 
+## Length of data expands from Q1-2005 to Q4-2018
+
+# For aggregate series we fit time series regression with ARIMA errors for the log transformed data. 
+# Bottom level series are used as the regressors.  
+# The back transformed data will be biased and we bias adjust to get unbiased point forecasts.
+
+# For bottom level series we fit univariate ARIMA models with log transformations
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+Prison_bot.ts <- read.csv("Prison.bottom.TS.csv")[,-1]
+
+Prison.gts <- gts(Prison_bot.ts, characters = c(3,1,9),
+                  gnames = c("State", "Gender", "Legal",
+                             "State*Gender", "State*Legal",
+                             "Gender*Legal"))
+
+
+Prison_allts <- allts(Prison.gts)
+Prison_bot.ts_lag1 <- apply(Prison_bot.ts, 2, lag)
+# Prison_allts_log <- apply(Prison_allts, 2, log)
+
+m <- ncol(Prison_bot.ts)
+n <- ncol(Prison_allts)
+H <- 1
+C <- 20 # number of replications
+
+S <- smatrix(Prison.gts)
+
+#Code to get shrinkage estimator
+
+lowerD <- function(x)
+{
+  n2 <- nrow(x)
+  return(diag(apply(x, 2, crossprod) / n2))
+}
+
+shrink.estim <- function(x, tar)
+{
+  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
+    stop("The data matrix must be numeric!")
+  p1 <- ncol(x)
+  n2 <- nrow(x)
+  covm <- crossprod(x) / n2
+  corm <- cov2cor(covm)
+  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
+  v <- (1/(n2 * (n2 - 1))) * (crossprod(xs^2) - 1/n2 * (crossprod(xs))^2)
[…]

### 2019-07-18 Application-R/Application-PrisonData/Trash/Exercises-VAR-models/Fitting-VAR.R

@@ -1,0 +1,22 @@
+# This is a small exercise for fitting VAR models in R
+# Using USconsumption data
+
+library(fpp2)
+library(tidyverse)
+library(vars)
+
+autoplot(usconsumption)
+
+ar(usconsumption, order = 2)
+
+#This will gives the optimal VAR order according to different information criteria
+VARselect(usconsumption, lag.max = 8, type = "const")
+
+#Fitting VAR model with order 3
+var <- VAR(usconsumption, p=3, type = "const")
+
+#tests the serial correlation of residuals
+serial.test(var, lags.pt = 10, type = "PT.asymptotic")
+
+#Forecasting
+Fc <- forecast(var)

### 2019-07-18 Application-R/Application-PrisonData/Trash/PrisonData_PointFRecon_LogTrans_TSReg.R

@@ -1,0 +1,378 @@
+## This file contains the analysis of Prison data using Hierarchical forecasting methods. 
+## Data form a grouped hierarchy with 3 grouping variables - 8-states, 2-Gender, 2-Legal-status. 
+## Length of data expands from Q1-2005 to Q4-2018
+
+# For aggregate series we fit time series regression for the log transformed data. 
+# Bottom level series are used as the regressors.  
+# The back transformed data will be biased and we bias adjust to get unbiased point forecasts.
+
+# For bottom level series we fit time series regression models with log transformations
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+Prison_bot.ts <- read.csv("Prison.bottom.TS.csv")[,-1]
+
+Prison.gts <- gts(Prison_bot.ts, characters = c(3,1,9),
+                  gnames = c("State", "Gender", "Legal",
+                             "State*Gender", "State*Legal",
+                             "Gender*Legal"))
+
+
+Prison_allts <- allts(Prison.gts)
+Prison_allts_lag <- apply(Prison_allts, 2, lag)
+Prison_bot.ts_lag1 <- apply(Prison_bot.ts, 2, lag)
+# Prison_allts_log <- apply(Prison_allts, 2, log)
+
+m <- ncol(Prison_bot.ts)
+n <- ncol(Prison_allts)
+H <- 1
+C <- 20 # number of replications
+
+S <- smatrix(Prison.gts)
+
+#Code to get shrinkage estimator
+
+lowerD <- function(x)
+{
+  n2 <- nrow(x)
+  return(diag(apply(x, 2, crossprod) / n2))
+}
+
+shrink.estim <- function(x, tar)
+{
+  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
+    stop("The data matrix must be numeric!")
+  p1 <- ncol(x)
+  n2 <- nrow(x)
+  covm <- crossprod(x) / n2
+  corm <- cov2cor(covm)
+  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
[…]

### 2019-07-18 Application-R/Simulation/PointFRecon_LogTrans_DynReg_H1-H4.R

@@ -1,0 +1,412 @@
+## This file contains the analysis of Prison data using Hierarchical forecasting methods. 
+## Data form a grouped hierarchy with 3 grouping variables - 8-states, 2-Gender, 2-Legal-status. 
+## Length of data expands from Q1-2005 to Q4-2018
+
+# For aggregate seriesand bottom level series we fit dynamic regression with ARIMA errors for the log transformed data. 
+# Bottom level series are used as the regressors.  
+# The back transformed data will be biased and we bias adjust to get unbiased point forecasts.
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+Bottom.level_TS <- read.csv("Bottom_level.csv")[,-1]
+
+Hierarchy <- suppressMessages(hts(Bottom.level_TS, list(2, c(2,2))))
+AllTS <- allts(Hierarchy)
+
+#Generating the summing matrix
+S <- smatrix(Hierarchy)
+
+N <- 750
+m <- ncol(Bottom.level_TS)
+n <- ncol(AllTS)
+L <- 250    # Length of the training set
+H <- 3
+C <- 500 # number of replications
+
+AllTS <- AllTS %>% 
+  as.data.frame() %>% 
+  slice(1:N)
+
+
+#Code to get shrinkage estimator
+
+lowerD <- function(x)
+{
+  n2 <- nrow(x)
+  return(diag(apply(x, 2, crossprod) / n2))
+}
+
+shrink.estim <- function(x, tar)
+{
+  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
+    stop("The data matrix must be numeric!")
+  p1 <- ncol(x)
+  n2 <- nrow(x)
+  covm <- crossprod(x) / n2
+  corm <- cov2cor(covm)
+  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
+  v <- (1/(n2 * (n2 - 1))) * (crossprod(xs^2) - 1/n2 * (crossprod(xs))^2)
+  diag(v) <- 0
+  corapn <- cov2cor(tar)
+  d <- (corm - corapn)^2
+  lambda <- sum(v)/sum(d)
+  lambda <- max(min(lambda, 1), 0)
+  shrink.cov <- lambda * tar + (1 - lambda) * covm
+  return(list(shrink.cov, c("The shrinkage intensity lambda is:",
[…]

### 2019-07-18 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex

@@
 the base and reconciled forecast should be `close'.
-The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realisation that is the target of the forecast.
+The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value that is targeted by the forecast.
 
 	To address the first of these properties we make the concept of closeness more concrete, by considering the Euclidean distance between the base forecast $\hat{\bm{y}}$ and the reconciled forecast  $\tilde{\bm{y}}$.
-A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ will be as small as possible while still ensuring that $\tilde{\bm{y}}\in\mathfrak{s}$.
+A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ is minimal for over any possible $\tilde{\bm{y}}\in\mathfrak{s}$.
 In this sense reconciliation via orthogonal projection leads to the smallest possible adjustments of the base forecasts.
@@
 		\begin{equation}
-		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2.
+		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
 		\end{equation}
@@
 The base forecast $\hat{\bm{y}}$ is shown as a blue dot.
-Since it is incoherent it does not lie in $\mathfrak{s}$.
+Since $\hat{\bm{y}}$ is incoherent it does not lie in $\mathfrak{s}$.
 Reconciliation is an orthogonal projection from $\hat{\bm{y}}$ to the coherent subspace yielding the reconciled forecast $\tilde{\bm{y}}$ shown in red.
@@
 
-	Figure~\ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle.
-In this triangle the distance between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.
+	Figure~\ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle with $\tilde{y}$ at the right-angled vertex.
+In this triangle the line between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.
 As such reconciliation is guaranteed to reduce the squared error of the forecast.
+\todo{Do we just include this as the proof rather than the existing proof to 3.1}
 
@@
 It is often stated in terms of expectations\todo{check other proofs}.
-However, the distance reducing property result is even stronger since it will hold for any realisation and any forecast.
+However, the distance reducing property will hold for any realisation and any forecast and not just on average.
 Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.
-    f
+
     However, in other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood.
@@
 As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to worse forecasts for individual series.
-Second, although orthogonal projections are guaranteed to improve on base forecasts both for all realisations and in expectation, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.
+Second, although orthogonal projections are guaranteed to improve on base forecasts, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.
 As such referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT.
@@
 
-	Another way of understanding the generalised Euclidean geometry is that it is defined by the norm $\bm{v}'\bm{W}^{1}\bm{v}$.
+	Another way of understanding the generalised Euclidean geometry is that it is defined by the norm $\bm{v}'\bm{W}^{-1}\bm{v}$.
 This interpretation is quite instructive when it comes to thinking about the connection between distances and loss functions.
@@
 This direction is denoted by $\bm{R}$.
-Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts.
-One such forecast is depicted in blue as $\hat{\bm{y}}$.
+Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).
+One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.
 An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection.
@@
 
-	The property that projections map all vectors in the coherent subspace onto themselves is useful in proving the unbiasedness preserving property of reconciliation \todo{reference Shanika and maybe van Erven Culigari}.
+	The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation \todo{reference Shanika and maybe van Erven Culigari}.
 Before restating this proof using a  clear geometric interpretation we discuss in a precise fashion what is meant by unbiasedness.
@@
 	Suppose that the target of a point forecast is $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ where the expectation is taken over the predictive density.
-Our point forecast can be thought of as an estimate of this quantity.
-The forecast is random due to uncertainty in the training sample and it is with respect to this uncertainty that unbiasedness refers.
+Our point forecast can be thought of as an estimate of this quantity.\todo{or do we want to define unbiasedness of a forecast as the expected value of the forecast equals realisation?}  The forecast is random due to uncertainty in the training sample and it is with respect to this uncertainty that unbiasedness refers.
 More concretely, the point forecast will be unbiased if $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
@@
 \todo{perhaps elaborate in a proof in appendix}  However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$.
-This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ is an unconstrained manner.
+This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.
 However, equipped with a geometric understanding of the problem, we would advise against this approach.
-Dropping the constraint is not just about bias $\bm{GS}=\bm{I}$ but rather moves away projections and all of their attractive properties.
+The constraint $\bm{GS}=\bm{I}$  is not just about bias and dropping the constraint compromises all of the attractive properties of projections.
 Our own solution to dealing with biased forecasts is to bias correct, or translate the forecast prior to reconciling via projections.
@@
 	\section{Bias correction}
+
+	Our approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y_{t+h}}-\hat{\bm{y}_{t+h|t}}$ for all $t+h$ in the training sample.
+This can be then subtracted from future forecasts.
+As stated in the discussion of MinT, in-sample errors are already used to estimate the optimal direction of projection.
+As such we see no problems with using the same errors to bias correct.
+Geometrically, the intuition is simple.
+In Figure~\ref{fig:MinT_justification1}, the orange points are centered around the origin as would be expected from an unbiased forecast.
+If forecasts are biased, then errors should simply be translated until they are centered at the origin.
 

### 2019-07-25 Application-R/Application-PrisonData/Bias-with-log-trans/PrisonData-LogTrans-results.Rmd
Continued with the prison data analysis - Fitted TS-regression models

@@
 
+```{r}
+
+# Avg_MSE_Base <- Avg_MSE %>% 
+#   filter(`R-method` == "Base") %>% 
+#   ungroup() %>% 
+#   mutate(`F-method` = recode(`F-method`, "ARIMA_bias"= "Bias", "ARIMA_unbias" = "Unbiase"))
+# 
+# Avg_MSE_MinT <- Avg_MSE %>% 
+#   filter(`R-method` == "MinT(Shrink)") %>% 
+#   ungroup() %>% 
+#   mutate(`F-method` = recode(`F-method`, "ARIMA_bias"= "Bias", "ARIMA_unbias" = "Unbiase")) 
+# 
+# 
+# Avg_MSE_Base %>% 
+#   ggplot(aes(x = Forecast_Horizon, y = MSE, color = `F-method`, shape = `F-method`)) + 
+#   geom_point(size = 3) + 
+#   scale_color_manual(values = c("Green", "Red")) +
+#   scale_shape_manual(values=0:1) + 
+#   geom_point(data = Avg_MSE_MinT, aes(x = Forecast_Horizon, y = MSE, 
+#                                       color = `F-method`, shape = `F-method`), size = 3) + 
+#   scale_shape_manual(values=2:3) +
+#   geom_line()
+
+```
+
 ```{r echo=FALSE}
-
-DF %>% 
+DF_MSE <- DF %>% 
   group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
   summarise(MSE = mean(SquaredE)) %>% 
-  filter(`F-method`=="ARIMA_bias", `R-method`%in% c("Base", "OLS")) %>% 
-  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
-  geom_line() + 
-  facet_wrap( ~ Forecast_Horizon, scales = "free_y") + 
-  ggtitle("OLS Vs Base (Biased)")
+  mutate(Forecast_Horizon = recode(Forecast_Horizon, "1" = "h=1", "2" = "h=2", "3"= "h=3", "4" = "h=4"))
 
-DF %>% 
-  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
-  summarise(MSE = mean(SquaredE)) %>% 
-  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS")) %>% 
-  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
-  geom_line() + 
-  facet_wrap( ~ Forecast_Horizon, scales = "free_y")+ 
-  ggtitle("OLS Vs Base (Unbiased)")
+DF_MSE %>% 
+  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS", "MinT(Shrink)")) %>% 
+  spread(key = `R-method`, value = MSE) %>% 
+  mutate("Base-OLS" = Base - OLS,
+         "Base-MinT" = Base - `MinT(Shrink)` ) %>% 
+  dplyr::select(Replication, Forecast_Horizon, `Base-OLS`, `Base-MinT`) %>% 
+  gather(`Base-MinT`, `Base-OLS`, key = Method, value = MSE) %>% 
+  ggplot(aes(x = Method, y = MSE)) + geom_boxplot() + facet_wrap(~`Forecast_Horizon`)
 
-DF %>% 
-  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
-  summarise(MSE = mean(SquaredE)) %>% 
-  filter(`F-method`=="ARIMA_bias", `R-method`%in% c("Base", "MinT(Shrink)")) %>% 
-  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
-  geom_line() + 
-  facet_wrap( ~ Forecast_Horizon, scales = "free_y") + 
-  ggtitle("MinT(Shrink) Vs Base (Biased)")
-
-DF %>% 
-  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
-  summarise(MSE = mean(SquaredE)) %>% 
-  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "MinT(Shrink)")) %>% 
-  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
-  geom_line() + 
-  facet_wrap( ~ Forecast_Horizon, scales = "free_y")+ 
-  ggtitle("MinT(Shrink) Vs Base (Unbiased)")
+# DF %>% 
+#   group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
+#   summarise(MSE = mean(SquaredE)) %>% 
+#   filter(`F-method`=="ARIMA_bias", `R-method`%in% c("Base", "OLS")) %>% 
+#   ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
+#   geom_line() + 
+#   facet_wrap( ~ Forecast_Horizon, scales = "free_y") + 
+#   ggtitle("OLS Vs Base (Biased)")
+# 
+# DF %>% 
+#   group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
+#   summarise(MSE = mean(SquaredE)) %>% 
+#   filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS")) %>% 
+#   ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
+#   geom_line() + 
+#   facet_wrap( ~ Forecast_Horizon, scales = "free_y")+ 
+#   ggtitle("OLS Vs Base (Unbiased)")
+# 
+# DF %>% 
+#   group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
+#   summarise(MSE = mean(SquaredE)) %>% 
+#   filter(`F-method`=="ARIMA_bias", `R-method`%in% c("Base", "MinT(Shrink)")) %>% 
+#   ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
+#   geom_line() + 
+#   facet_wrap( ~ Forecast_Horizon, scales = "free_y") + 
+#   ggtitle("MinT(Shrink) Vs Base (Biased)")
+# 
+# DF %>% 
+#   group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
+#   summarise(MSE = mean(SquaredE)) %>% 
+#   filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "MinT(Shrink)")) %>% 
+#   ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
+#   geom_line() + 
+#   facet_wrap( ~ Forecast_Horizon, scales = "free_y")+ 
+#   ggtitle("MinT(Shrink) Vs Base (Unbiased)")
 
 ```
+
+\newpage
 

### 2019-07-25 Application-R/Application-PrisonData/Bias-with-log-trans/PrisonData_PointFRecon_LogTrans_UnivARIMA.R

@@ -298,11 +298,24 @@ DF %>%
   geom_line() + 
   facet_wrap( ~ Forecast_Horizon, scales = "free_y")
 
-DF %>% 
+
+## Box-plots for the differences of MSE between OLS, MinT vs the base
+
+DF_MSE <- DF %>% 
   group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
   summarise(MSE = mean(SquaredE)) %>% 
-  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "MinT(Shrink)")) %>% 
-  ggplot(aes(x = Replication, y = MSE, color = `R-method`)) + 
-  geom_line() + 
-  facet_wrap( ~ Forecast_Horizon, scales = "free_y")
+  mutate(Forecast_Horizon = recode(Forecast_Horizon, "1" = "h=1", "2" = "h=2", "3"= "h=3", "4" = "h=4"))
+
+
+DF_MSE %>% 
+  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS", "MinT(Shrink)")) %>% 
+  spread(key = `R-method`, value = MSE) %>% 
+  mutate("Base-OLS" = Base - OLS,
+         "Base-MinT" = Base - `MinT(Shrink)` ) %>% 
+  select(Replication, Forecast_Horizon, `Base-OLS`, `Base-MinT`) %>% 
+  gather(`Base-MinT`, `Base-OLS`, key = Method, value = MSE) %>% 
+  ggplot(aes(x = Method, y = MSE)) + geom_boxplot() + facet_wrap(~`Forecast_Horizon`)
+  
+  
+  
 

### 2019-07-30 Application-R/Application-PrisonData/Bias-with-log-trans/PrisonData-LogTrans-results.Rmd
Added application on tourism data

@@
 ```{r}
+Avg_MSE %>% 
+   spread(key = `F-method`, value = MSE) %>% 
+   mutate(Bias_SS.MSE = round((1-(ARIMA_bias/ARIMA_bias_Base))*100, digits = 2), 
+          Unbias_SS.MSE = round((1-(ARIMA_unbias/ARIMA_bias_Base))*100, digits = 2)) -> Avg_MSE_SS
+
+Avg_MSE_SS %>% 
+  gather(key = "F-method", value = SS_MSE, Bias_SS.MSE, Unbias_SS.MSE) %>% 
+  mutate(`F-method` = recode(`F-method`, "Bias_SS.MSE" = "Bias", "Unbias_SS.MSE" = "Unbias")) %>%
+  filter(`R-method` %in% c("MinT(Shrink)", "OLS", "WLS")) %>% 
+  ggplot(aes(x = Forecast_Horizon, y = SS_MSE, color = `F-method`, shape = `F-method`)) + 
+  facet_wrap(~ `R-method`, scales = "free_y") +
+  geom_point(size = 3) + 
+  scale_shape_manual(values = 15:16) +
+  scale_color_manual(values = c("Red", "#33CC33")) + 
+  ylab("Skill Score (MSE) %") + 
+  xlab("h")
+
+```
+
+```{r}
 
@@
 DF_MSE %>% 
-  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS", "MinT(Shrink)")) %>% 
+  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>% 
   spread(key = `R-method`, value = MSE) %>% 
   mutate("Base-OLS" = Base - OLS,
-         "Base-MinT" = Base - `MinT(Shrink)` ) %>% 
-  dplyr::select(Replication, Forecast_Horizon, `Base-OLS`, `Base-MinT`) %>% 
-  gather(`Base-MinT`, `Base-OLS`, key = Method, value = MSE) %>% 
-  ggplot(aes(x = Method, y = MSE)) + geom_boxplot() + facet_wrap(~`Forecast_Horizon`)
+         "Base-MinT" = Base - `MinT(Shrink)`,
+         "Base-WLS" = Base - WLS) %>% 
+  dplyr::select(Replication, Forecast_Horizon, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>% 
+  gather(`Base-OLS`, `Base-WLS`, `Base-MinT`,  key = Method, value = MSE) %>% 
+  ggplot(aes(x = Method, y = MSE)) + geom_boxplot() + facet_wrap(~`Forecast_Horizon`, scales = "free_y")
 

### 2019-07-30 Application-R/Application-PrisonData/Bias-with-log-trans/PrisonData_PointFRecon_LogTrans_UnivARIMA_H1-H4.R

@@ -1,0 +1,329 @@
+## This file contains the analysis of Prison data using Hierarchical forecasting methods. 
+## Data form a grouped hierarchy with 3 grouping variables - 8-states, 2-Gender, 2-Legal-status. 
+## Length of data expands from Q1-2005 to Q4-2018
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get unbiased point forecasts.
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+Prison_bot.ts <- read.csv("Prison.bottom.TS.csv")[,-1]
+
+Prison.gts <- gts(Prison_bot.ts, characters = c(3,1,9),
+                  gnames = c("State", "Gender", "Legal",
+                             "State*Gender", "State*Legal",
+                             "Gender*Legal"))
+
+
+Prison_allts <- allts(Prison.gts)
+# Prison_allts_log <- apply(Prison_allts, 2, log)
+
+m <- ncol(Prison_bot.ts)
+n <- ncol(Prison_allts)
+H <- 4 
+C <- 20 # number of replications
+
+S <- smatrix(Prison.gts)
+
+#Code to get shrinkage estimator
+
+lowerD <- function(x)
+{
+  n2 <- nrow(x)
+  return(diag(apply(x, 2, crossprod) / n2))
+}
+
+shrink.estim <- function(x, tar)
+{
+  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
+    stop("The data matrix must be numeric!")
+  p1 <- ncol(x)
+  n2 <- nrow(x)
+  covm <- crossprod(x) / n2
+  corm <- cov2cor(covm)
+  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
+  v <- (1/(n2 * (n2 - 1))) * (crossprod(xs^2) - 1/n2 * (crossprod(xs))^2)
+  diag(v) <- 0
+  corapn <- cov2cor(tar)
+  d <- (corm - corapn)^2
+  lambda <- sum(v)/sum(d)
+  lambda <- max(min(lambda, 1), 0)
[…]

### 2019-07-30 Application-R/Application-TourismData/TourismData_LogTransBiasCorrection_UnivARIMA.R

@@ -1,0 +1,424 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
+                                                            c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
+                                                              3,4,2,3,1,1,1,2,2,3,4))))
+AllTS <- allts(Hierarchy) %>% 
+  as_tibble()
+n <- ncol(AllTS)
+l1 <- 1
+l2 <- sum(7)
+l3 <- sum(6,5,4,4,3,3,2)
+m <- ncol(OvernightTrips_Region)
+H <- 6
+L <- 100 #Size of the training sample 
+C <- nrow(AllTS) - L
+
+
+#Generating the summing matrix
+S <- smatrix(Hierarchy)
+#Code to get shrinkage estimator
+
+lowerD <- function(x)
+{
+  n2 <- nrow(x)
+  return(diag(apply(x, 2, crossprod) / n2))
+}
+
+shrink.estim <- function(x, tar)
+{
+  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
+    stop("The data matrix must be numeric!")
+  p1 <- ncol(x)
+  n2 <- nrow(x)
+  covm <- crossprod(x) / n2
+  corm <- cov2cor(covm)
+  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
[…]

### 2019-07-30 Application-R/Application-TourismData/TourismData_LogTransBiasCorrection_UnivARIMA_1-25.R

@@ -1,0 +1,427 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
+                                                              c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
+                                                                3,4,2,3,1,1,1,2,2,3,4))))
+AllTS <- allts(Hierarchy) %>% 
+  as_tibble()
+n <- ncol(AllTS)
+l1 <- 1
+l2 <- sum(7)
+l3 <- sum(6,5,4,4,3,3,2)
+m <- ncol(OvernightTrips_Region)
+H <- 6
+L <- 100 #Size of the training sample 
+C <- nrow(AllTS) - L
+
+
+#Generating the summing matrix
+S <- smatrix(Hierarchy)
+#Code to get shrinkage estimator
+
+lowerD <- function(x)
+{
+  n2 <- nrow(x)
+  return(diag(apply(x, 2, crossprod) / n2))
+}
+
+shrink.estim <- function(x, tar)
+{
+  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
+    stop("The data matrix must be numeric!")
+  p1 <- ncol(x)
+  n2 <- nrow(x)
+  covm <- crossprod(x) / n2
+  corm <- cov2cor(covm)
+  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
[…]

### 2019-07-30 Application-R/Application-TourismData/TourismData_LogTransBiasCorrection_UnivARIMA_26-50.R

@@ -1,0 +1,427 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
+                                                              c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
+                                                                3,4,2,3,1,1,1,2,2,3,4))))
+AllTS <- allts(Hierarchy) %>% 
+  as_tibble()
+n <- ncol(AllTS)
+l1 <- 1
+l2 <- sum(7)
+l3 <- sum(6,5,4,4,3,3,2)
+m <- ncol(OvernightTrips_Region)
+H <- 6
+L <- 100 #Size of the training sample 
+C <- nrow(AllTS) - L
+
+
+#Generating the summing matrix
+S <- smatrix(Hierarchy)
+#Code to get shrinkage estimator
+
+lowerD <- function(x)
+{
+  n2 <- nrow(x)
+  return(diag(apply(x, 2, crossprod) / n2))
+}
+
+shrink.estim <- function(x, tar)
+{
+  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
+    stop("The data matrix must be numeric!")
+  p1 <- ncol(x)
+  n2 <- nrow(x)
+  covm <- crossprod(x) / n2
+  corm <- cov2cor(covm)
+  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
[…]

### 2019-07-30 Application-R/Application-TourismData/TourismData_LogTransBiasCorrection_UnivARIMA_76-100.R

@@ -1,0 +1,427 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
+                                                              c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
+                                                                3,4,2,3,1,1,1,2,2,3,4))))
+AllTS <- allts(Hierarchy) %>% 
+  as_tibble()
+n <- ncol(AllTS)
+l1 <- 1
+l2 <- sum(7)
+l3 <- sum(6,5,4,4,3,3,2)
+m <- ncol(OvernightTrips_Region)
+H <- 6
+L <- 100 #Size of the training sample 
+C <- nrow(AllTS) - L
+
+
+#Generating the summing matrix
+S <- smatrix(Hierarchy)
+#Code to get shrinkage estimator
+
+lowerD <- function(x)
+{
+  n2 <- nrow(x)
+  return(diag(apply(x, 2, crossprod) / n2))
+}
+
+shrink.estim <- function(x, tar)
+{
+  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
+    stop("The data matrix must be numeric!")
+  p1 <- ncol(x)
+  n2 <- nrow(x)
+  covm <- crossprod(x) / n2
+  corm <- cov2cor(covm)
+  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
[…]

### 2019-07-30 Hierarchical-forecast-reconciliation/Figs/ObliqueProjection.tex
Added some schematics of orthogonal and oblique projections

% Created by tikzDevice version 0.12 on 2019-07-25 19:35:10
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}

\usepackage{amsfonts}
\usepackage{bm}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,361.35);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (336.15,312.15);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.46, 49.37) --
	( 75.46,302.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 12.94, 91.62) --
	(361.35, 91.62);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 75.46, 91.62) -- (294.26,165.55);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (282.33,151.98) --
	(294.26,165.55) --
	(276.55,169.10);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (300.26,163.26) {{\huge $\mathfrak{s}$}};
\definecolor{drawColor}{RGB}{190,190,190}
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.81,109.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.77, 91.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.52,137.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.19, 15.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.43,138.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.74,158.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.46, 85.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.26, 82.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.25, 97.76) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.75,110.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.05,168.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 77.69, 13.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.35, 49.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.55,134.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.15,244.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.98,100.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.97, 27.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.92,152.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.94,153.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.70, 45.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.68,148.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.40, 56.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.57, 88.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.03, 87.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.18, 90.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.69, 80.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.71,119.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.87,132.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.35,168.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.99, 71.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.22,188.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 86.48, 66.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 95.92, 14.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.98, 97.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.16,134.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.44,121.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.97, 83.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.38, 45.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.00,140.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.99, 82.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.36, 76.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.71, 92.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.58, 55.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.74,134.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.13,133.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 85.18, 15.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.23, 39.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 95.58, 73.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 81.79, 25.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.20, 17.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.11, 40.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.73, 44.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.26,123.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.28, 30.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.76,139.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.30,126.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.24, 88.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.53,121.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.55, 37.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.54,141.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.74,124.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.06,128.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.36,177.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.09,122.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.02,127.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 93.66, 83.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.90, 34.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.26, 16.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.72,179.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.53, 29.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.90, 99.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.87, 58.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.81, 96.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.53,173.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.18, 60.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.54,114.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.72,119.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.66,108.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.02,175.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.47,102.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.92, 96.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.77,106.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.12,137.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.50,129.21) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 97.40, 72.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.96,105.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.07, 65.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.75,163.30) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.12,133.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.19,138.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.65, 66.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.21, 87.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.28, 99.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.33, 68.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 97.80, 62.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.43,108.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.35,175.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 86.62, 17.17) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.34, 98.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.64,103.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.15,100.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.35,111.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.14,101.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.59,103.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.58,107.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.38,106.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.75,104.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.74,105.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.23,102.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.77,107.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.41,102.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.37,106.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.37,106.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.94,105.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.71,108.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.30,106.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.19,108.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.83,108.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.46,104.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.70,103.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.34,106.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.38,103.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.73,107.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.20,103.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.58,107.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 97.88, 99.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.54,101.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.52,105.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.32,109.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.36,100.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.33, 96.30) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 97.36, 99.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.69,109.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.75,105.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.71,117.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.77,107.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.77,104.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.78,100.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.34,105.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.53,102.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.54,101.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.33,109.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.23,102.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.67,103.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.61, 98.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.07,105.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.77,106.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.99,101.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.36,102.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.64,100.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.92,102.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.97, 98.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.77,110.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 95.89, 98.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.41,108.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.12,111.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.73,101.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.95,107.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 93.81, 97.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 97.44, 99.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.94,103.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.20,110.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.54,105.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.14, 98.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.23,103.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.16, 99.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.60,105.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.43,110.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.71,107.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.36,109.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.37,107.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.62,105.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.61,104.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.70,108.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.78,101.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.80, 97.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.94,108.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.80,105.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.60,108.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.74,105.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.87,104.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.92,100.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.78,109.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.46,105.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.39,102.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.85,104.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.06,107.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.46,108.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.00,103.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.34,103.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.18,106.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.57,103.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.28,108.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.15,104.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.44,103.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.89,101.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.77,101.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.06,105.34) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 75.46, 91.62) -- (137.97,260.61);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (141.02,242.80) --
	(137.97,260.61) --
	(124.07,249.07);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (137.97,266.61) {{\Large ${\bm R}$}};
\definecolor{drawColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 99.81,109.09) -- ( 96.34, 98.67);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.77, 91.59) -- (109.64,103.17);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.52,137.68) -- (102.15,100.64);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (102.19, 15.17) -- (134.35,111.52);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.43,138.47) -- (105.14,101.65);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 75.15,  0.00) -- (109.59,103.15);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.74,158.62) -- (121.58,107.20);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (111.46, 85.40) -- (118.38,106.12);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (107.26, 82.46) -- (114.75,104.90);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.25, 97.76) -- (115.74,105.23);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (110.75,110.22) -- (108.23,102.69);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.05,168.36) -- (122.77,107.60);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 77.69, 13.39) -- (107.41,102.41);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 99.35, 49.13) -- (118.37,106.12);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (129.55,134.28) -- (120.37,106.79);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.15,244.07) -- (116.94,105.63);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.98,100.77) -- (126.71,108.94);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 92.97, 27.56) -- (119.30,106.43);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.92,152.20) -- (124.19,108.09);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (140.94,153.90) -- (125.83,108.64);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 94.70, 45.59) -- (114.46,104.80);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (124.68,148.06) -- (109.70,103.19);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.40, 56.04) -- (120.34,106.78);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.57, 88.66) -- (109.38,103.08);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.03, 87.86) -- (123.73,107.93);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.18, 90.98) -- (109.20,103.02);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.69, 80.89) -- (122.58,107.54);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.71,119.64) -- ( 97.88, 99.20);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.87,132.04) -- (103.54,101.11);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.35,168.22) -- (117.52,105.83);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 92.66,  0.00) -- (129.32,109.82);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 90.99, 71.97) -- (100.36,100.03);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (120.22,188.84) -- ( 89.33, 96.30);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 86.48, 66.43) -- ( 97.36, 99.02);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 95.92, 14.10) -- (127.69,109.27);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.98, 97.61) -- (117.75,105.91);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (158.16,134.05) -- (152.71,117.72);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.44,121.94) -- (123.77,107.94);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.97, 83.84) -- (112.77,104.23);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 84.38, 45.73) -- (102.78,100.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (129.00,140.72) -- (117.34,105.77);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (100.99, 82.87) -- (107.53,102.45);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 96.36, 76.95) -- (104.54,101.44);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (122.71, 92.64) -- (128.33,109.48);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 92.58, 55.79) -- (108.23,102.69);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.74,134.03) -- (111.67,103.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (108.13,133.27) -- ( 96.61, 98.77);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 85.18, 15.46) -- (115.07,105.00);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.23, 39.42) -- (120.77,106.93);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 95.58, 73.41) -- (104.99,101.60);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 81.79, 25.79) -- (107.36,102.40);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 73.20, 17.93) -- (100.64,100.13);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 87.11, 40.26) -- (107.92,102.59);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 78.73, 44.25) -- ( 96.97, 98.89);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (135.26,123.77) -- (130.77,110.31);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 73.28, 30.79) -- ( 95.89, 98.52);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.76,139.84) -- (126.41,108.83);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (139.30,126.97) -- (134.12,111.44);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (101.24, 88.41) -- (105.73,101.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.53,121.03) -- (121.95,107.33);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 73.55, 37.13) -- ( 93.81, 97.82);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (111.54,141.26) -- ( 97.44, 99.05);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.74,124.31) -- (111.94,103.95);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.06,128.01) -- (131.20,110.45);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (141.36,177.20) -- (117.54,105.84);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.09,122.43) -- ( 96.14, 98.61);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (119.02,127.02) -- (111.23,103.71);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 93.66, 83.14) -- ( 99.16, 99.63);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 92.90, 34.52) -- (116.60,105.52);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 99.26, 16.80) -- (130.43,110.19);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (146.72,179.49) -- (122.71,107.59);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (101.53, 29.10) -- (128.36,109.49);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.90, 99.73) -- (121.37,107.13);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (100.87, 58.35) -- (116.62,105.53);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (111.81, 96.46) -- (114.61,104.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (146.53,173.68) -- (124.70,108.26);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 90.18, 60.45) -- (103.78,101.19);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.54,114.69) -- ( 92.80, 97.48);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (127.72,119.33) -- (123.94,108.00);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.66,108.17) -- (116.80,105.59);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (148.02,175.72) -- (125.60,108.56);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.47,102.09) -- (117.74,105.91);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (111.92, 96.12) -- (114.87,104.93);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.77,106.44) -- (102.92,100.90);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.12,137.61) -- (128.78,109.64);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.50,129.21) -- (115.46,105.13);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 97.40, 72.49) -- (107.39,102.41);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.96,105.25) -- (114.85,104.93);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (107.07, 65.13) -- (121.06,107.03);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.75,163.30) -- (125.46,108.51);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.12,133.94) -- (111.00,103.63);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.19,138.57) -- (109.34,103.07);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.65, 66.20) -- (120.18,106.73);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.21, 87.43) -- (110.57,103.48);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.28, 99.79) -- (126.28,108.79);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (101.33, 68.94) -- (113.15,104.35);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 97.80, 62.91) -- (111.44,103.78);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.43,108.84) -- (103.89,101.23);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (129.35,175.14) -- (104.77,101.52);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 86.62, 17.17) -- (116.06,105.34);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.97,104.29) circle (  3.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (112.97, 86.55) {{\huge $\color{black}{\bm{y}}$}};
\end{scope}
\end{tikzpicture}

\end{document}

### 2019-07-30 Hierarchical-forecast-reconciliation/Figs/Orthproj.tex
Added some schematics of orthogonal and oblique projections

% Created by tikzDevice version 0.12 on 2019-07-25 19:34:36
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}

\usepackage{amsfonts}
\usepackage{bm}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,361.35);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (336.15,312.15);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.46, 49.37) --
	( 75.46,302.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 12.94, 91.62) --
	(361.35, 91.62);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 75.46, 91.62) -- (294.26,165.55);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (282.33,151.98) --
	(294.26,165.55) --
	(276.55,169.10);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (300.26,163.26) {{\huge $\mathfrak{s}$}};
\definecolor{drawColor}{RGB}{190,190,190}
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.73,104.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.96, 97.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.75,158.76) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.40,151.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.23,132.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 67.77, 37.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.74, 64.30) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.42, 57.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.34,119.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.42,110.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.22,194.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.14,120.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.75, 94.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.46,159.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.12, 78.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.91,246.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.00, 75.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.54, 44.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.06, 63.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.94, 76.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.47,142.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.23,157.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.43,158.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.22,161.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.88, 98.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.00, 83.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.04, 85.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.87,141.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.00,105.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.17, 88.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.15, -1.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.13, 76.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.24,170.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.33, 55.24) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.14, 34.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.83, 70.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.18, 37.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.63, 69.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.36,141.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.54, 10.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.31,100.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.09, 96.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.67,148.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.98,130.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.55, 93.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.67,184.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.64,100.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.87,105.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.41,135.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.14, 59.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.14,108.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.78,130.30) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.46,191.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.08,131.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.73,129.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 77.69, 38.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.64,162.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.94,188.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.08,148.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.23,100.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.40,120.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.88,184.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.24,126.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.95, 53.81) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.34,121.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.85, 10.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.63, 98.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.24,125.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.52, 18.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.96,179.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.23,131.81) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.43,161.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.78,270.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.20,114.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.39, 82.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.64, 54.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.04, 80.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.26,104.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.76, 73.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.08,127.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.98,194.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.01, 89.21) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.86,135.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.03,149.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.65, 96.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.52,153.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.68,172.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.42,141.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.02,103.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.57,163.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.23,162.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.51,128.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.37,117.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.85,213.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.12, 87.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.18,169.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 83.18, 59.04) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 75.46, 91.62) -- (137.97,260.61);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (141.02,242.80) --
	(137.97,260.61) --
	(124.07,249.07);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (137.97,266.61) {{\Large ${\bm R}$}};
\definecolor{drawColor}{RGB}{255,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.47,100.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.03,100.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.83,123.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.34,117.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.78,114.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 37.19, 78.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.11, 96.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 67.02, 88.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.30,110.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.89,111.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (199.23,133.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.34,113.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.13,101.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.44,121.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.45, 94.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (241.05,147.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.75, 97.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.89, 88.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.00, 96.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.44, 96.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.51,118.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.91,121.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.21,118.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.63,126.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.02,102.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.79, 98.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.00,102.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.12,117.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.76,104.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.01,100.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 19.17, 72.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.26, 96.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.99,121.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 77.83, 92.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 48.46, 82.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 81.92, 93.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 55.41, 84.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.46, 90.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.82,112.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 26.44, 75.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.84,103.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.19,100.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.15,121.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.90,111.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 95.30, 98.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.98,125.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.02,102.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.52,102.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.64,112.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 76.09, 91.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.78,105.24) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.01,111.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (188.00,129.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.92,113.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.35,112.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 45.79, 81.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.36,119.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.13,128.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.60,115.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.01, 99.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.11,107.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.70,126.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.14,111.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 51.07, 83.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.23,105.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 26.29, 75.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 11.37, 69.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  8.62, 69.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.81,106.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.55,108.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 43.99, 80.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.37,126.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.06,117.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.54,121.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (255.15,152.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.89,104.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.13, 97.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.56, 92.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.85, 99.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.83,103.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.00, 96.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.02,110.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (202.09,134.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.08,101.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.31,117.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.35,119.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.13,104.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.88,115.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.22,125.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.97,112.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.93,104.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.12,120.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.80,120.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.05,112.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.46,109.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (204.61,135.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.34, 96.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.71,126.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 62.36, 87.19) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.73,104.11) -- (101.47,100.41);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (102.96, 97.64) -- (101.03,100.26);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.75,158.76) -- (169.83,123.51);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.40,151.64) -- (153.34,117.93);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.23,132.34) -- (141.78,114.03);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 67.77, 37.36) -- ( 37.19, 78.69);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (112.74, 64.30) -- ( 89.11, 96.23);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 90.42, 57.14) -- ( 67.02, 88.77);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.34,119.54) -- (130.30,110.15);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (134.42,110.64) -- (133.89,111.36);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.22,194.28) -- (199.23,133.44);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (134.14,120.23) -- (139.34,113.20);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (111.75, 94.39) -- (106.13,101.98);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (135.46,159.17) -- (163.44,121.35);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 96.12, 78.87) -- ( 84.45, 94.66);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.91,246.43) -- (241.05,147.57);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.00, 75.49) -- ( 92.75, 97.46);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 99.54, 44.60) -- ( 66.89, 88.72);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.06, 63.01) -- ( 91.00, 96.87);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.94, 76.74) -- ( 89.44, 96.34);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.47,142.71) -- (154.51,118.33);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.23,157.90) -- (164.91,121.84);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (124.43,158.48) -- (154.21,118.23);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.22,161.85) -- (177.63,126.14);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.88, 98.42) -- (107.02,102.28);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.00, 83.00) -- ( 94.79, 98.15);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (122.04, 85.32) -- (109.00,102.95);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.87,141.85) -- (151.12,117.19);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.00,105.58) -- (113.76,104.56);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (112.17, 88.54) -- (103.01,100.93);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.89,  0.00) -- ( 19.17, 72.60);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.13, 76.86) -- ( 91.26, 96.96);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (129.24,170.18) -- (164.99,121.87);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.33, 55.24) -- ( 77.83, 92.42);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 84.14, 34.27) -- ( 48.46, 82.50);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.83, 70.96) -- ( 81.92, 93.80);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 90.18, 37.85) -- ( 55.41, 84.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 89.63, 69.09) -- ( 73.46, 90.95);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.36,141.37) -- (136.82,112.35);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 74.54, 10.03) -- ( 26.44, 75.05);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.31,100.58) -- (111.84,103.91);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.09, 96.39) -- (101.19,100.31);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (145.67,148.26) -- (165.15,121.92);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (120.98,130.52) -- (134.90,111.70);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 21.96,  0.00) -- (  0.00, 29.67);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.55, 93.92) -- ( 95.30, 98.32);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.67,184.11) -- (175.98,125.58);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (108.64,100.10) -- (107.02,102.28);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.87,105.03) -- (108.52,102.79);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (119.41,135.58) -- (136.64,112.29);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (100.14, 59.33) -- ( 76.09, 91.83);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.14,108.82) -- (115.78,105.24);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.78,130.30) -- (133.01,111.07);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (142.46,191.20) -- (188.00,129.65);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.08,131.10) -- (140.92,113.74);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (124.73,129.59) -- (137.35,112.53);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 77.69, 38.48) -- ( 45.79, 81.60);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.64,162.50) -- (158.36,119.63);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (139.94,188.07) -- (184.13,128.34);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.08,148.46) -- (145.60,115.32);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.23,100.64) -- ( 99.01, 99.58);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (111.40,120.16) -- (121.11,107.04);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (134.88,184.04) -- (177.70,126.17);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.24,126.18) -- (134.14,111.45);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.95, 53.81) -- ( 51.07, 83.38);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.34,121.46) -- (116.23,105.40);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 73.85, 10.74) -- ( 26.29, 75.01);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 63.13,  0.00) -- ( 11.37, 69.96);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 59.69,  0.00) -- (  8.62, 69.03);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (125.63, 98.74) -- (119.81,106.60);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.24,125.53) -- (126.55,108.88);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 90.52, 18.10) -- ( 43.99, 80.99);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.96,179.32) -- (177.37,126.05);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (140.23,131.81) -- (151.06,117.16);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.43,161.73) -- (162.54,121.04);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.78,270.43) -- (255.15,152.34);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.20,114.65) -- (112.89,104.27);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.39, 82.71) -- ( 94.13, 97.93);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.64, 54.72) -- ( 78.56, 92.67);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.04, 80.34) -- ( 98.85, 99.52);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (110.26,104.34) -- (110.83,103.57);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.76, 73.89) -- ( 90.00, 96.53);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.08,127.54) -- (130.02,110.05);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (157.98,194.02) -- (202.09,134.41);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.01, 89.21) -- (104.08,101.29);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.86,135.43) -- (151.31,117.25);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.03,149.79) -- (158.35,119.63);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.65, 96.89) -- (113.13,104.35);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.52,153.41) -- (144.88,115.08);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (141.68,172.35) -- (176.22,125.67);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.42,141.54) -- (136.97,112.40);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.02,103.15) -- (113.93,104.62);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (130.57,163.54) -- (162.12,120.90);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.23,162.78) -- (159.80,120.12);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (125.51,128.03) -- (137.05,112.43);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.37,117.42) -- (127.46,109.19);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (146.85,213.31) -- (204.61,135.26);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 96.12, 87.14) -- ( 89.34, 96.31);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (147.18,169.12) -- (178.71,126.51);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 83.18, 59.04) -- ( 62.36, 87.19);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.97,104.29) circle (  3.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (112.97, 86.55) {{\huge $\color{black}{\bm{y}}$}};
\end{scope}
\end{tikzpicture}

\end{document}

### 2019-07-30 Hierarchical-forecast-reconciliation/Figs/orth_pointforerec_schematic.tex
Added some schematics of orthogonal and oblique projections

@@
-% Created by tikzDevice version 0.12 on 2019-04-26 17:19:46
+% Created by tikzDevice version 0.12 on 2019-07-25 17:17:29
 % !TEX encoding = UTF-8 Unicode
@@
 \definecolor{fillColor}{RGB}{255,255,255}
-\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,505.89);
+\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (289.08,289.08);
 \begin{scope}
-\path[clip] ( 49.20, 61.20) rectangle (263.88,456.69);
+\path[clip] ( 49.20, 61.20) rectangle (263.88,239.88);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 68.84,130.32) --
-	( 68.84,317.41);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.60, 49.44) --
+	( 87.60,196.50);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 22.07,177.10) --
-	(209.16,177.10);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.84, 86.20) --
+	(197.90, 86.20);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 68.84,177.10) -- (232.54,258.95);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 87.60, 86.20) -- (216.28,150.54);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (222.59,243.87) --
-	(232.54,258.95) --
-	(214.51,260.03);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (206.33,135.46) --
+	(216.28,150.54) --
+	(198.25,151.62);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (238.54,256.65) {{\large $\mathfrak{s}$}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (222.28,148.24) {{\large $\mathfrak{s}$}};
 \definecolor{drawColor}{RGB}{0,0,255}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.00,317.41) circle (  3.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.75,196.50) circle (  3.00);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (139.00,335.41) {{\large $\color{blue}{\hat{\bm{y}}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (142.75,214.50) {{\large $\color{blue}{\hat{\bm{y}}}$}};
 \definecolor{drawColor}{RGB}{255,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.09,233.22) circle (  3.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.84,130.32) circle (  3.00);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (181.09,209.48) {{\large $\color{red}{\tilde{\bm{y}}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (175.84,106.58) {{\large $\color{red}{\tilde{\bm{y}}}$}};
 \definecolor{drawColor}{RGB}{0,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (139.00,317.41) -- (181.09,233.22);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (142.75,196.50) -- (175.84,130.32);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (166.02,243.18) --
-	(181.09,233.22) --
-	(182.18,251.26);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (160.76,140.27) --
+	(175.84,130.32) --
+	(176.92,148.35);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (139.00,317.41) -- (108.93,197.14);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (142.75,196.50) -- (119.12,101.96);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.96,214.51) --
-	(108.93,197.14) --
-	(121.49,210.13);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.15,119.33) --
+	(119.12,101.96) --
+	(131.68,114.95);
 \definecolor{fillColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.93,197.14) circle (  3.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.12,101.96) circle (  3.00);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (108.93,173.40) {{\large $\color{black}{{\bm{y}}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (119.12, 78.22) {{\large $\color{black}{{\bm{y}}}$}};
 \end{scope}

### 2019-07-30 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Added some schematics of orthogonal and oblique projections

@@
 \usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
-\usepackage{mathrsfs, float, booktabs,todonotes,amsthm, xcolor,sidenotes}
+\usepackage{mathrsfs, float, booktabs,todonotes,amsthm, xcolor,sidenotes, caption, subcaption}
+
 \usepackage[bb=boondox]{mathalfa}
@@
 
+	\begin{figure}[H]
+		\centering
+		%\vspace{-0.9cm}
+		\small
+		\resizebox{\linewidth}{!}{
+			\includegraphics{Figs/OrthProj.pdf}}
+		\caption{\textcolor{red}{include caption}}\label{fig:Orthogonal_projection}
+	\end{figure}
+
+	\begin{figure}[H]
+	\centering
+	%\vspace{-0.9cm}
+	\small
+	\resizebox{\linewidth}{!}{
+		\includegraphics{Figs/ObliqueProjection.pdf}}
+	\caption{\textcolor{red}{include caption}}\label{fig:Oblique_projection}
+	\end{figure}
+
+%		\begin{figure}[H]
+%		\centering
+%		%\vspace{-0.9cm}
+%		\small
+%		\resizebox{\linewidth}{!}{
+%			\input{Figs/ObliqueProjection}
+%		}
+%		\caption{\textcolor{red}{write caption}}\label{fig:Oblique_projection}
+%	\end{figure}
+
+%\begin{figure}
+%	\centering
+%	\begin{subfigure}{0.47\textwidth}
+%		\resizebox{\linewidth}{!}{
+%			\input{Figs/Orth.proj.tex}}
+%		\caption{bla bla}
+%	\end{subfigure}
+%	\begin{subfigure}{0.47\textwidth}
+%		\resizebox{\linewidth}{!}{
+%			\input{Figs/ObliqueProjection.tex}}
+%			\caption{bla bla}
+%	\end{subfigure}
+%\end{figure}
+
 	\section{Bias in forecast reconciliation}
@@
 	We note that the above result holds when the projection $\bm{SG}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general.
-To describe this more explicitly suppose $\bm{SG}$ has as its image  $\mathfrak{L}$ which is itself a a lower dimensional linear subspace of $\mathfrak{s}$, i.e.
+To describe this more explicitly suppose $\bm{SG}$ has as its image  $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e.
 $\mathfrak{L}\subset\mathfrak{s}$.
@@
 This is depicted in Figure~\ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.
-In this case, the reconciled forecast will have as its expectation $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and be biased.
+In this case, the expectation of reconciled forecast will be $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and hence biased.
 
@@
 
-	Our approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y_{t+h}}-\hat{\bm{y}_{t+h|t}}$ for all $t+h$ in the training sample.
+	Our approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
+	}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.
 This can be then subtracted from future forecasts.

### 2019-07-30 Hierarchical-forecast-reconciliation/Figs/schematics.r

@@ -69,7 +69,7 @@ dev.off()
 
 ##OLS reconciliation
 
-tikz('orth_pointforerec_schematic.tex',width=4)
+tikz('orth_pointforerec_schematic.tex',width=4, height = 4)
 plot.new()
 plot.window(xlim = c(-0.25,4),ylim = c(-0.5,4),asp=1)
 lines(c(0,0),c(-1,3))
@@ -103,10 +103,52 @@ text(y[1],y[2],"{\\large $\\color{black}{{\\bm{y}}}$}",pos=1,offset = 1.5)
 
 dev.off()
 
+#--Orthogonal projection of the points
+
+# Possible estimates
+
+tikz('OrthProj.tex',height=5, width = 5, standAlone = TRUE)
+plot.new()
+plot.window(xlim = c(-0.25,4),ylim = c(-0.5,5))
+lines(c(0,0),c(-1,5))
+lines(c(-1,5),c(0,0))
+#lines(c(-1,3.5),c(-0.5,1.75),lwd=2)
+arrows(0,0,3.5,1.75,lwd=3)
+text(3.5,1.75,"{\\huge $\\mathfrak{s}$}",pos=4)
+
+rmat<-matrix(c(1,4,-0.5,0.25),2,2,byrow = FALSE)
+e<-t(rmat%*%matrix(rnorm(200,0,0.3),2,100))
+e_sample <- e + matrix(rep(c(0.6,0.3), 100), nrow = 100, ncol = 2, byrow = T)
+points(e_sample[,1],e_sample[,2],pch=19,col='gray')
+
+arrows(0,0,1,4,lwd=3)
+text(1,4,"{\\Large ${\\bm R}$}",pos=3)
+
+S <- c(2,1)
+SP = S %*% solve(t(S) %*% S) %*% t(S)
+# SP<-matrix(c(0.8,0.4,0.4,0.2),2,2)
+
+e_OLS <- t(SP%*%t(e_sample))
+points(e_OLS[,1],e_OLS[,2],pch=19,col='red')
+
+arrows(x0 = e_sample[,1], y0 = e_sample[,2], 
+       x1 = e_OLS[,1], y1 = e_OLS[,2], code = 0,
+       lty = 2, col = "blue")
+
+# points(1.5,3,pch=20,cex=2,col='blue')
+# text(1.5,3,"{\\huge $\\color{blue}{\\hat{\\bm{y}}}$}",pos = 3,offset = 1.5)
+
[…]

### 2019-08-06 Application-R/Application-TourismData/Results/TourismData-results.Rmd
More analysis on tourism data

---
title: "Tourism Data Analysis"
output:
  pdf_document: default
  html_document: default
date: "31 July 2019"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(fpp2)
library(Matrix)
library(hts)
library(readr)
library(BigVAR)
library(vars)
library(tibble)
library(kableExtra)
library(reshape2)
library(ggpubr)
library(gridExtra)
```

<!-- ### Estimating the bias from the mean of the insample residuals -->
<!-- ```{r, echo=FALSE} -->
<!-- DF_Exp_1 <- read.csv("DF_Exp-1.csv")[,-1] -->

<!-- DF_Exp_1 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_Exp_1 -->

<!-- DF_Exp_1 %>%  -->
<!--   group_by(`F.method`, `R.method`, Forecast_Horizon) %>%  -->
<!--   summarise(MSE = mean(SquaredE)) -> Avg_MSE_Exp1 -->

<!-- Avg_MSE_tab1_Exp1 <- Avg_MSE_Exp1 %>%  -->
<!--   dcast(`R.method` ~ Forecast_Horizon + `F.method`, value.var = "MSE")  -->

<!-- colnames(Avg_MSE_tab1_Exp1) <- c("R.method", rep(c("Biased", "Unbiased"), 6)) -->

<!-- Avg_MSE_tab1_Exp1 %>%  -->
<!--   kable(format = "latex") %>%  -->
<!--   kableExtra::add_header_above(c(" " = 1, "h=1" = 2, "h=2" = 2, "h=3" = 2, "h=4" = 2, -->
<!--                                  "h=5" = 2, "h=6" = 2))  -->

<!-- ``` -->

### Bias adjusted forecasts are given as follows:

$$ y_t = 
  \begin{cases} 
   \exp{x_t}[1+\frac{\sigma_h^2}{2}] & \text{if } \lambda = 0 \\ \\
   (\lambda x_t + 1)^{1/\lambda}[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda x_t + 1)^2}]       & \text{Otherwise}
  \end{cases}$$

### For BoxCox transformed data (Using the BoxCox function in the forecast package)

In this exercise I have used the `BoxCox.lambda()` function in forecast package to automatically find a proper transformation for each series.
```{r, echo=FALSE}
load("TourismData_BoxCoxTransBiasCorrection_UnivARIMA.RData")

DF %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCox_1

DF_BoxCox_1 %>% 
  group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) -> Avg_MSE_BC_1

Avg_MSE_tab1_BC_1 <- Avg_MSE_BC_1 %>% 
  dcast(`R-method` ~ Forecast_Horizon + `F-method`, value.var = "MSE")

colnames(Avg_MSE_tab1_BC_1) <- c("R-method", rep(c("Biased", "Unbiased"), 6))

Avg_MSE_tab1_BC_1 %>% 
  kable(format = "latex") %>% 
  kableExtra::add_header_above(c(" " = 1, "h=1" = 2, "h=2" = 2, "h=3" = 2, "h=4" = 2,
                                 "h=5" = 2, "h=6" = 2))

DF_BoxCox_1 %>% 
  mutate(Forecast_Horizon = recode(Forecast_Horizon, "1" = "h=1",  "2" = "h=2",
                                    "3" = "h=3",  "4" = "h=4",  "5" = "h=5",  
                                   "6" = "h=6")) %>%
  filter(`R-method` == "Base") %>% 
  group_by(`F-method`, `R-method`, Forecast_Horizon, Replication) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  spread(key = `F-method`, value = MSE) %>% 
  mutate("Bias-Unbias" = `ARIMA_bias` - `ARIMA_unbias`) %>% 
  ggplot(aes(x = Replication, y = `Bias-Unbias`)) + geom_point() + 
  facet_wrap(~Forecast_Horizon, scales = "free_y") +
  ylab("MSE (bias - unbias)") + 
  ggtitle("MSE Difference between Biased-base and Unbiased-base")

```

The above graph shows the difference between the MSE of `Base-biased forecasts` and `Base-unbiased forecasts`. As we can see, this difference is very large for some of the replications which courses the large average MSE in unbiased-base forecasts shown in the table 1.

However an important thing to notice here is that although the unbiased base forecasts are terrible, MinT has adjusted these through the reconciliation. In fact the MinT reconciled unbiased forecasts are even better than the MinT reconciled biased forecasts.

We have also noticed that the based-bias adjusted forecasts are going worst for only one variable which is `Adelaide Hills`. If we visualise this time series we get,

```{r}
AllTS %>% 
  dplyr::select(`Adelaide Hills`) %>% 
  as.ts() %>% 
  autoplot()
```

We can see this variable has a very unusual observation which might be an outlier. To avoid this, I have replaced this observation with the average of it's adjacent observations. Then I have refitted the models for automatically chosen BoxCox transformed data and back-transformed and back-transformed bias-adjusted forecasts were obtained. The results are as follows.

```{r echo=FALSE}
load("TourismData_BoxCoxTransBiasCorrection_UnivARIMA_new.RData")

DF %>% 
  mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCox_2

DF_BoxCox_2 %>% 
  group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) -> Avg_MSE_BC_2

Avg_MSE_tab1_BC_2 <- Avg_MSE_BC_2 %>% 
  dcast(`R-method` ~ Forecast_Horizon + `F-method`, value.var = "MSE")

colnames(Avg_MSE_tab1_BC_2) <- c("R-method", rep(c("Biased", "Unbiased"), 6))

Avg_MSE_tab1_BC_2 %>% 
  kable(format = "latex") %>% 
  kableExtra::add_header_above(c(" " = 1, "h=1" = 2, "h=2" = 2, "h=3" = 2, "h=4" = 2,
                                 "h=5" = 2, "h=6" = 2))

```

These results also shows that, even though the bias-adjusted based forecasts are worst than that of biased base forecasts, the MinT reconicilation is outperforming.

```{r}
Avg_MSE_BC_2 %>% filter(`F-method` == "ARIMA_bias", `R-method` == "Base") %>% 
  slice() %>% 
  ungroup() %>% 
  dplyr::select(MSE) %>% 
  as_vector() -> ARIMA_bias_Base

Avg_MSE_BC_2 %>% 
   spread(key = `F-method`, value = MSE) %>% 
   mutate(Bias_SS.MSE = round((1-(ARIMA_bias/ARIMA_bias_Base))*100, digits = 2), 
          Unbias_SS.MSE = round((1-(ARIMA_unbias/ARIMA_bias_Base))*100, digits = 2)) -> Avg_MSE_BC_2_SS

Avg_MSE_BC_2_SS %>% 
  gather(key = "F-method", value = SS_MSE, Bias_SS.MSE, Unbias_SS.MSE) %>% 
  mutate(`F-method` = recode(`F-method`, "Bias_SS.MSE" = "Bias", "Unbias_SS.MSE" = "Unbias")) %>%
  ungroup() %>% 
  rename("Forecasting method" = "F-method") %>% 
  mutate(`R-method` = factor(`R-method`, levels = c("Base", "MinT(Shrink)", "WLS", "OLS"))) %>% 
  filter(`R-method` %in% c("Base", "MinT(Shrink)", "WLS", "OLS" )) %>%
  ggplot(aes(x = Forecast_Horizon, y = SS_MSE, 
             color = `Forecasting method`, shape = `Forecasting method`)) + 
  theme(legend.position="bottom") +
  facet_wrap(~ `R-method`, scales = "free_y") +
  geom_point(size = 3) + 
  scale_shape_manual(values = 15:16) +
  scale_color_manual(values = c("Red", "#33CC33")) + 
  ylab("Skill Score (MSE) %") + 
  xlab("h")

```

```{r}

DF_MSE <- DF %>% 
  mutate(SquaredE = (`Actual` - `Forecasts`)^2) %>% 
  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  mutate(Forecast_Horizon = recode(Forecast_Horizon, "1" = "h=1", "2" = "h=2", "3"= "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6"))

DF_MSE %>% 
  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>% 
  spread(key = `R-method`, value = MSE) %>% 
  mutate("Base-OLS" = Base - OLS,
         "Base-MinT" = Base - `MinT(Shrink)`,
         "Base-WLS" = Base - WLS) %>% 
  dplyr::select(Replication, Forecast_Horizon, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>% 
  gather(`Base-OLS`, `Base-WLS`, `Base-MinT`,  key = Method, value = MSE) %>% 
  ggplot(aes(x = Method, y = MSE)) + geom_boxplot() + facet_wrap(~`Forecast_Horizon`, scales = "free_y")
```

### For Log transformed data

In this exercise I have used only the log transformation. As we can see from the results, the bias adjusted forecasts are outperforming biased forecasts as we would expect. 
```{r, echo=FALSE}
load("TourismData_LogTransBiasCorrection_UnivARIMA.RData")

DF -> DF_Log

DF_Log %>% 
  group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) -> Avg_MSE_Log

Avg_MSE_tab1_Log <- Avg_MSE_Log %>% 
  dcast(`R-method` ~ Forecast_Horizon + `F-method`, value.var = "MSE")

colnames(Avg_MSE_tab1_Log) <- c("R-method", rep(c("Biased", "Unbiased"), 6))

Avg_MSE_tab1_Log %>% 
  kable(format = "latex") %>% 
  kableExtra::add_header_above(c(" " = 1, "h=1" = 2, "h=2" = 2, "h=3" = 2, "h=4" = 2,
                                 "h=5" = 2, "h=6" = 2))

```

### 2019-08-06 Application-R/Application-TourismData/Trash/Bias-correction-problem/Results.Rmd
More analysis on tourism data

---
title: "Bias vs Bias adjusted forecasts for Tourism data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(fpp2)
library(hts)
load("TourismData_BoxCoxTrans-BiasCorrection_UnivARIMA.RData")

```

Univariate ARIMA models were fitted for the transformed data (using BoxCox transformation). 
The back transformed data was adjusted for bias to get unbiased forecasts

Table shows the MSE for base-biased and base-unbiased forecasts for $h=1,..,6$

```{r}

DF %>% 
  group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  ungroup() %>% 
  mutate(Forecast_Horizon = recode(Forecast_Horizon, "1" = "h=1",  "2" = "h=2",
                                    "3" = "h=3",  "4" = "h=4",  "5" = "h=5",  
                                   "6" = "h=6"),
         `F-method` = recode(`F-method`, "ARIMA_bias" = "Base-biased", 
                             "ARIMA_unbias" = "Base-unbiased")) %>% 
  select(-`R-method`) %>% 
  spread(key = Forecast_Horizon, value = MSE)

DF %>% 
  mutate(Forecast_Horizon = recode(Forecast_Horizon, "1" = "h=1",  "2" = "h=2",
                                    "3" = "h=3",  "4" = "h=4",  "5" = "h=5",  
                                   "6" = "h=6")) %>%
  group_by(`F-method`, `R-method`, Forecast_Horizon, Replication) %>% 
  summarise(MSE = mean(SquaredE)) %>% 
  spread(key = `F-method`, value = MSE) %>% 
  mutate("Bias-Unbias" = `ARIMA_bias` - `ARIMA_unbias`) %>% 
  ggplot(aes(x = Replication, y = `Bias-Unbias`)) + geom_point() + 
  facet_wrap(~Forecast_Horizon, scales = "free_y") +
  ylab("MSE (bias - unbias)")

```

### 2019-08-06 Application-R/Application-TourismData/Bias-correction/TourismData_BoxCoxTransBiasCorrection_UnivARIMA.R

@@ -1,0 +1,383 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
+                                                            c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
+                                                              3,4,2,3,1,1,1,2,2,3,4))))
+AllTS <- allts(Hierarchy) %>% 
+  as_tibble()
+n <- ncol(AllTS)
+l1 <- 1
+l2 <- sum(7)
+l3 <- sum(6,5,4,4,3,3,2)
+m <- ncol(OvernightTrips_Region)
+H <- 6
+L <- 100 #Size of the training sample 
+C <- nrow(AllTS) - L
+
+
+#Generating the summing matrix
+S <- smatrix(Hierarchy)
+#Code to get shrinkage estimator
+
+lowerD <- function(x)
+{
+  n2 <- nrow(x)
+  return(diag(apply(x, 2, crossprod) / n2))
+}
+
+shrink.estim <- function(x, tar)
+{
+  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
+    stop("The data matrix must be numeric!")
+  p1 <- ncol(x)
+  n2 <- nrow(x)
+  covm <- crossprod(x) / n2
+  corm <- cov2cor(covm)
[…]

### 2019-08-06 Application-R/Application-TourismData/Bias-correction/TourismData_BoxCoxTransBiasCorrection_UnivARIMA_new.R

@@ -1,0 +1,406 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the BoxCOx transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+# We noticed that there is an unusual observation in the Adelaide Hills series. So we
+# replace that odd value with the average of adjecent values
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
+                                                            c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
+                                                              3,4,2,3,1,1,1,2,2,3,4))))
+AllTS <- allts(Hierarchy) %>% 
+  as_tibble()
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+AllTS %>% 
+  select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(AllTS$`Adelaide Hills`==a) -> x
+
+AllTS %>% 
+  select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+AllTS_new <- AllTS %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
[…]

### 2019-08-06 Application-R/Application-TourismData/Bias-correction/TourismData_LogTransBiasCorrection_UnivARIMA.R

@@ -1,0 +1,378 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
+                                                            c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
+                                                              3,4,2,3,1,1,1,2,2,3,4))))
+AllTS <- allts(Hierarchy) %>% 
+  as_tibble()
+n <- ncol(AllTS)
+l1 <- 1
+l2 <- sum(7)
+l3 <- sum(6,5,4,4,3,3,2)
+m <- ncol(OvernightTrips_Region)
+H <- 6
+L <- 100 #Size of the training sample 
+C <- nrow(AllTS) - L
+
+
+#Generating the summing matrix
+S <- smatrix(Hierarchy)
+#Code to get shrinkage estimator
+
+lowerD <- function(x)
+{
+  n2 <- nrow(x)
+  return(diag(apply(x, 2, crossprod) / n2))
+}
+
+shrink.estim <- function(x, tar)
+{
+  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
+    stop("The data matrix must be numeric!")
+  p1 <- ncol(x)
+  n2 <- nrow(x)
+  covm <- crossprod(x) / n2
+  corm <- cov2cor(covm)
+  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
[…]

### 2019-08-06 Application-R/Application-TourismData/Data_preprocessing.R

@@ -1,19 +1,0 @@
-## Change Geelong to Geelong and the Bellarine
-
-
-library(tidyverse)
-Data_OvernightTrips <- read_csv("Tourism_Australia_FullDataSet_upto_2017.csv", skip = 9)
-Data_Nights <- read_csv("VN_FullDataSet Edited by George2017.csv", skip = 6)[,-1] %>%
-  rename(Year = `Calendar year`)
-
-Data_OvernightTrips <- Data_OvernightTrips[,names(Data_Nights)]
-
-Data_OvernightTrips %>% 
-  mutate(Wimmera = Wimmera+Mallee) %>% 
-  select(-Mallee) %>% 
-  rename(Wimmera_Mallee = Wimmera) -> Data_OvernightTrips
-
-write.csv(Data_OvernightTrips, "OvernightTrips_2017.csv")
-
-
-

### 2019-08-06 Application-R/Application-TourismData/Results/TimePlots.R

@@ -1,0 +1,138 @@
+library(tidyverse)
+library(gridExtra)
+
+load("TourismData_LogTransBiasCorrection_UnivARIMA.RData")
+
+#Total Series
+AllTS %>% 
+  dplyr::select("Total") %>% 
+  ts(start = c(1998, 1), frequency = 12) %>% 
+  autoplot() + ylab("Overnight trips") + xlab("Time") + 
+  ggtitle("Total") + theme(legend.position="bottom") -> Plot_total
+
+#States
+
+AllTS %>% 
+  dplyr::select("A", "B", "C", "D", "E", "F", "G" ) %>% 
+  rename("NSW" = "A", "Victoria" = "B", "Queensland" = "C", 
+         "South Australia" = "D", "Western Australia" = "E", "Tasmania" = "F",
+         "Northern Territory" = "G") %>% 
+  ts(start = c(1998, 1), frequency = 12) %>% 
+  autoplot() + ylab("Overnight trips") + xlab("Time") + 
+  ggtitle("States") + theme(legend.position="bottom") -> Plot_Sates
+
+#Zones
+
+AllTS %>% 
+  dplyr::select("AA", "AB", "AC", "AD", "AE", "AF", "BA", "BB", "BC", "BD", "BE",
+                "CA", "CB", "CC", "CD", "DA", "DB", "DC", "DD", "EA", "EB","EC", 
+                "FA", "FB", "FC", "GA", "GB") %>% 
+  ts(start = c(1998, 1), frequency = 12) %>% 
+  autoplot() + ylab("Overnight trips") + xlab("Time") + 
+  ggtitle("States") + theme(legend.position="bottom")
+
+
+# Series related to State - A
+AllTS %>% 
+  dplyr::select("A") %>% 
+  ts(start = c(1998, 1), frequency = 12) %>% 
+  autoplot() + ylab("Overnight trips") + xlab("Time") + 
+  ggtitle("State-A") + theme(legend.position="bottom") -> Plot_A
+
+AllTS %>% 
+  dplyr::select("AA", "AB", "AC", "AD", "AE", "AF") %>% 
+  ts(start = c(1998, 1), frequency = 12) %>%  
+  as.tsibble() %>% rename("Zones" = "key") %>% 
+  ggplot(aes(x = index, y = value, color = Zones)) + 
+  geom_line()  + ylab("Overnight trips") + xlab("Time") + 
[…]

### 2019-08-06 Application-R/Application-TourismData/TourismData_LogTransBiasCorrection_UnivARIMA_26-50.R

@@ -1,427 +1,0 @@
-## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
-## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
-## Length of data expands from Jan-1998 to Dec-2017
-
-# Here we fit univariate ARIMA models for the log transformed data
-# The back transformed data will be biased and we bias adjust to get 
-# unbiased point forecasts.
-
-
-library(tidyverse)
-library(fpp2)
-library(Matrix)
-library(hts)
-library(readr)
-library(tibble)
-
-# Import bottom level data
-#Importing data
-
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
-Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
-                                                              c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
-                                                                3,4,2,3,1,1,1,2,2,3,4))))
-AllTS <- allts(Hierarchy) %>% 
-  as_tibble()
-n <- ncol(AllTS)
-l1 <- 1
-l2 <- sum(7)
-l3 <- sum(6,5,4,4,3,3,2)
-m <- ncol(OvernightTrips_Region)
-H <- 6
-L <- 100 #Size of the training sample 
-C <- nrow(AllTS) - L
-
-
-#Generating the summing matrix
-S <- smatrix(Hierarchy)
-#Code to get shrinkage estimator
-
-lowerD <- function(x)
-{
-  n2 <- nrow(x)
-  return(diag(apply(x, 2, crossprod) / n2))
-}
-
-shrink.estim <- function(x, tar)
-{
-  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
-    stop("The data matrix must be numeric!")
-  p1 <- ncol(x)
-  n2 <- nrow(x)
-  covm <- crossprod(x) / n2
-  corm <- cov2cor(covm)
-  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
[…]

### 2019-08-06 Application-R/Application-TourismData/TourismData_LogTransBiasCorrection_UnivARIMA_76-100.R

@@ -1,427 +1,0 @@
-## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
-## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
-## Length of data expands from Jan-1998 to Dec-2017
-
-# Here we fit univariate ARIMA models for the log transformed data
-# The back transformed data will be biased and we bias adjust to get 
-# unbiased point forecasts.
-
-
-library(tidyverse)
-library(fpp2)
-library(Matrix)
-library(hts)
-library(readr)
-library(tibble)
-
-# Import bottom level data
-#Importing data
-
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
-Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
-                                                              c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
-                                                                3,4,2,3,1,1,1,2,2,3,4))))
-AllTS <- allts(Hierarchy) %>% 
-  as_tibble()
-n <- ncol(AllTS)
-l1 <- 1
-l2 <- sum(7)
-l3 <- sum(6,5,4,4,3,3,2)
-m <- ncol(OvernightTrips_Region)
-H <- 6
-L <- 100 #Size of the training sample 
-C <- nrow(AllTS) - L
-
-
-#Generating the summing matrix
-S <- smatrix(Hierarchy)
-#Code to get shrinkage estimator
-
-lowerD <- function(x)
-{
-  n2 <- nrow(x)
-  return(diag(apply(x, 2, crossprod) / n2))
-}
-
-shrink.estim <- function(x, tar)
-{
-  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
-    stop("The data matrix must be numeric!")
-  p1 <- ncol(x)
-  n2 <- nrow(x)
-  covm <- crossprod(x) / n2
-  corm <- cov2cor(covm)
-  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
[…]

### 2019-08-06 Application-R/Application-TourismData/Trash/Bias-correction-Exp-1/TourismData_LogTransBiasCorrection_UnivARIMA.R

@@ -1,0 +1,420 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
+                                                            c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
+                                                              3,4,2,3,1,1,1,2,2,3,4))))
+AllTS <- allts(Hierarchy) %>% 
+  as_tibble()
+n <- ncol(AllTS)
+l1 <- 1
+l2 <- sum(7)
+l3 <- sum(6,5,4,4,3,3,2)
+m <- ncol(OvernightTrips_Region)
+H <- 6
+L <- 100 #Size of the training sample 
+C <- nrow(AllTS) - L
+
+
+#Generating the summing matrix
+S <- smatrix(Hierarchy)
+#Code to get shrinkage estimator
+
+lowerD <- function(x)
+{
+  n2 <- nrow(x)
+  return(diag(apply(x, 2, crossprod) / n2))
+}
+
+shrink.estim <- function(x, tar)
+{
+  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
+    stop("The data matrix must be numeric!")
+  p1 <- ncol(x)
+  n2 <- nrow(x)
+  covm <- crossprod(x) / n2
+  corm <- cov2cor(covm)
+  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
[…]

### 2019-08-06 Application-R/Application-TourismData/Trash/Bias-correction-Exp-1/TourismData_LogTransBiasCorrection_UnivARIMA_51-100.R

@@ -1,0 +1,427 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
+                                                              c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
+                                                                3,4,2,3,1,1,1,2,2,3,4))))
+AllTS <- allts(Hierarchy) %>% 
+  as_tibble()
+n <- ncol(AllTS)
+l1 <- 1
+l2 <- sum(7)
+l3 <- sum(6,5,4,4,3,3,2)
+m <- ncol(OvernightTrips_Region)
+H <- 6
+L <- 100 #Size of the training sample 
+C <- nrow(AllTS) - L
+
+
+#Generating the summing matrix
+S <- smatrix(Hierarchy)
+#Code to get shrinkage estimator
+
+lowerD <- function(x)
+{
+  n2 <- nrow(x)
+  return(diag(apply(x, 2, crossprod) / n2))
+}
+
+shrink.estim <- function(x, tar)
+{
+  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
+    stop("The data matrix must be numeric!")
+  p1 <- ncol(x)
+  n2 <- nrow(x)
+  covm <- crossprod(x) / n2
+  corm <- cov2cor(covm)
+  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
[…]

### 2019-08-06 Application-R/Application-TourismData/Trash/Bias-correction-problem/TourismData_BoxCoxTrans-BiasCorrection_UnivARIMA_2.R

@@ -1,0 +1,162 @@
+
+# Univariate ARIMA models were fitted for the transformed data (Used BoxCox transformation)
+# The back transformed data will be adjusted for bias to get unbiased data
+
+
+library(tidyverse)
+library(fpp2)
+library(hts)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+#generating the hierarchy
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
+                                                              c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
+                                                                3,4,2,3,1,1,1,2,2,3,4))))
+AllTS <- allts(Hierarchy) %>% 
+  as_tibble()
+n <- ncol(AllTS)
+m <- ncol(OvernightTrips_Region)
+H <- 6
+L <- 100 #Size of the training sample 
+C <- nrow(AllTS) - L # Number of replications
+
+
+# Generating the summing matrix
+S <- smatrix(Hierarchy)
+
+
+# Data frame to store results
+
+DF <- tibble("Series" = character(),
+             "F-method" = character(),
+             "R-method" = character(),
+             "Forecast_Horizon" = double(),
+             "Forecasts" = double(),
+             "Actual" = double(),
+             "Replication" = integer())
+
+# A function to return back transformed and back transformed bias adjusted forecasts
+# (Given the forecasts in the transformed space)
+
+Fc_backtransformed <- function(Fc, sigma2, lambda){
+  
+  if(lambda == 0){
+    
+    Fc_backtrans <- exp(Fc)
+    Fc_backtrans_biasadj <- Fc_backtrans*(1 + sigma2/2)
+    
+  }
+  else{
+    
+    q <- (lambda*Fc + 1)
+    
+    Fc_backtrans <- q^(1/lambda)
+    
+    a <- sigma2*(1-lambda)
+    b <- 2*q^2
+    Fc_backtrans_biasadj <- Fc_backtrans*(1 + a/b)
+    
+  }
+  
+  return(rbind(Fc_backtrans = Fc_backtrans, Fc_backtrans_biasadj = Fc_backtrans_biasadj))
+  
[…]

### 2019-08-06 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex

@@
 
-	The second property introduced above has been the focus of theoretical results in the forecast reconciliation literature.
-He we provide a more streamlined version of proofs by \cite{VanErven2015a} and \cite{Wickramasuriya2017} before providing geometrical intuition aimed at simplifying the reader's understanding of these proofs.
+	The property that reconciliation should improve forecasts was touched upon in Section 2.3 of \cite{Wickramasuriya2017}.
+The discussion in that paper focuses on the case of MinT.
+Here we provide a new explicit proof of that result first in the case of an orthogonal projection where the geometric intuition of the proof is clear and then generalise the result to reconciliation by any projection matrix in Section~\ref{sec:oblique}.
 
@@
 This is equivalent to the root of the sum of squared errors over the entire hierarchy.
-Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$, and let $\|\bm{v}\|_2$ be the $L_2$ norm of vector $\bm{v}$.
+Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$.
 The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.
@@
 	\begin{theo}[Distance reducing property]\label{th:distred}
-		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
+		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the Euclidean sense) projection onto $\mathfrak{s}$ and let $\|\bm{v}\|$ be the $L_2$ norm (in the Euclidean sense) of vector $\bm{v}$ then:
 		\begin{equation}
-		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
+		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|.
 		\end{equation}
@@
 	\begin{proof}
-		Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ since $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$.
-Therefore,
-		\begin{align}
-		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
-		&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
-		\end{align}
-		The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators \citep{Hun2001}, therefore
-		\begin{equation*}
-		\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le
-		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
-		\end{equation*}
+		Since, $\bm{y}_{t+h},\tilde{\bm{y}}_{t+h}\in\mathfrak{s}$ and since the projection is orthogonal, by Pythagoras' theorem
+		\begin{equation}
+		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2=\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h})\|^2+\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2.
+		\end{equation}
+
+		Since $\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h})\|^2\ge 0$ this implies,
+		\begin{equation}
+		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2\ge\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2.
+		\end{equation}
+		with equality only holding when $\tilde{\bm{y}}_{t+h|t}=\hat{\bm{y}}_{t+h}$.  Taking the square root of both sides proves the desired result.
 	\end{proof}
-	The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.
-
-	\todo{compare to van Erven and Wickremasuriya more explictly}
 
@@
 The base forecast $\hat{\bm{y}}$ is shown as a blue dot.
-Since $\hat{\bm{y}}$ is incoherent it does not lie in $\mathfrak{s}$.
+Since $\hat{\bm{y}}$ is incoherent, $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$ and in this case the inequality is strict.
 Reconciliation is an orthogonal projection from $\hat{\bm{y}}$ to the coherent subspace yielding the reconciled forecast $\tilde{\bm{y}}$ shown in red.
@@
 As such reconciliation is guaranteed to reduce the squared error of the forecast.
-\todo{Do we just include this as the proof rather than the existing proof to 3.1}
 
     Theorem~\ref{th:distred} is in some ways more powerful than perhaps previously understood.
-It is often stated in terms of expectations\todo{check other proofs}.
-However, the distance reducing property will hold for any realisation and any forecast and not just on average.
+Crucially, the result is not a result that requires taking expectations.
+This distance reducing property will hold for any realisation and any forecast and not just on average.
 Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.
+\todo{include evidence from small empirical example.}
 
@@
 
-	\subsection{Oblique Projections}
+	\subsection{Oblique Projections}\label{sec:oblique}
 
@@
 In the generalised Euclidean geometry, the distance between the reconciled forecast and the realisation is given by $(\hat{\bm{y}}-\bm{y})'\bm{W}^{-1}(\hat{\bm{y}}-\bm{y})$.
-For diagonal $\bm{W}$ this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix this is equivalent to a Mahalanobis distance.
-As such Theorem~\ref{th:distred} can easily be generalised.
-If the objective function is some weighted sum of squared errors, or a Mahalanobis distance, then the projection matrix $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts, for an appropriately selected $\bm{W}$.
+For diagonal $\bm{W}$, this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix, this is equivalent to a Mahalanobis distance.
+As such Theorem~\ref{th:distred} can easily be generalised as follows:
+
+	\begin{theo}[General distance reducing property]\label{th:gdistred}
+        If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the generalised Euclidean sense) projection onto $\mathfrak{s}$ and let $\|\bm{v}\|_{\bm{W}}$ be the $L_2$ norm (in the generalised Euclidean sense with respect to $\bm{W}$) of vector $\bm{v}$ then:
+		\begin{equation}
+		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{\bm W}\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{\bm W}.
+		\end{equation}
+	\end{theo}
+	\begin{proof}
+    The proof is identical to the proof for Theorem~\ref{th:distred} but relies on the generalised Pythagorean Theorem (applicable to Generalised Euclidean space) rather than the Pythagorean Theorem.
+    \end{proof}
+
+	The implication of Theorem~\ref{th:gdistred} is that if the objective function is some weighted sum of squared errors, or a Mahalanobis distance, then the projection matrix $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts, for an appropriately selected $\bm{W}$.
+
+	Note here that we rely here on the generalised Pythagorean Theorem (which involves an equality).
+In contrast, \cite{Wickramasuriya2017} follow \cite{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.
+The proof of \cite{Wickramasuriya2017} requires an assumptions about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.
+The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.
+As such the statement from \cite{Wickramasuriya2017} that {\em``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified; this is only true in with respect to a loss function that depends on ${\bm W}$.
+If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts\todo{include empirical example}.
 
@@
 In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts.\todo{needs picture with all points projected obliquely then orthogonally}.
+In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal is expectation.
 
@@
 
-	The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation \todo{reference Shanika and maybe van Erven Culigari}.
+	The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation \cite{Wickramasuriya2017}.
 Before restating this proof using a  clear geometric interpretation we discuss in a precise fashion what is meant by unbiasedness.

### 2019-08-12 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Complete first draft - Added Introduction, Application and Conclutions

@@
 
-	Have to explain why we are writing this
-	\begin{itemize}
-		\item Geometric intuition - restate existing results but with a new understanding.
-		\item In particular champion projections.
-		\item State that paper is in some ways a review paper.
-		\item Propose a simple solution to the issue of bias.
-	\end{itemize}
+	A collection of multiple time series with some aggregation structure arises in many disciplines such as manufacturing, engineering, marketing, medicine, etc.
+These are often known as hierarchical time series.
+Making coherent forecasts for these series that are in line with the inherent aggregation constraints is an essential requirement for decision making.
+Early studies on this literature use a single level forecasting approaches.
+That is, forecasting the series in a single level of the hierarchy and then aggregate or disaggregate these forecasts to get coherent forecasts for remaining series.
+The well known Bottom-up \citep{Dunn1976} and Top-down \citep{Gross1990, Athanasopoulos2009} methods are examples for these traditional methods.
+Multiple studies also discuss the relative advantages and disadvantages of these methods, for example, \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.
 
-%	Large collections of time series often follow some aggregation structure.
-For example, the electricity demand of a country can be disaggregated according to a geographic hierarchy of states, cities, and individual households.
-To ensure aligned decision making, it is important that forecasts at the most disaggregated level add up to forecasts at more aggregated levels.
-This property is called ``coherence''.
-On the other hand ``reconciliation'' is a process whereby incoherent forecasts are made coherent.
-Both of these concepts have been developed extensively for point forecasting.
-Generalising both of these concepts, particularly the latter, to probabilistic forecasting is a gap that we seek to address in this work.
-We do so by first providing a novel geometric interpretation to coherence and reconciliation in the point forecasting case.
-This can easily be generalised to probabilistic forecasting allowing us to derive further results for elliptical distributions as well as provide insight into forecast evaluation via multivariate  scoring rules.
-%	
-%	Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level of the hierarchy.
-To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$ and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.
-In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (series $AA$, $AB$, $BA$ and $BB$) and then summed to recover forecasts for all higher-level series.
-Alternatively, in the top-down approach \citep{Gross1990}, a top-level forecast is first produced (series $Tot$) and bottom-level forecasts are recovered by disaggregating the forecast using either historical or forecasted proportions.
-A middle-out approach is a hybrid between these two, that for the hierarchy in Figure~\ref{fig1} would produce first stage forecasts for series $A$ and $B$.
-%	
-%	
-%	In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular.
-For these methods, first stage forecasts are independently produced for all series rather than series at a single level.
-Since these so-called `base' forecasts are rarely coherent in practice, they are subsequently adjusted or `reconciled' to ensure coherence.
-Note that we use coherence and reconciliation as distinct terms, in contrast to their at times ambiguous usage in the past.
-To date, reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators.
-These include Ordinary Least Squares {OLS} \citep{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix.
-These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{AthEtAl2009,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and, in some sense, hedge against the risk of model misspecification at a single level.
-%	
-%	A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \citep[see][and references therein]{Gneiting2014}.
-Indeed to the best of our knowledge, the (as yet unpublished) work of \citep{BenTaieb2017} is the only paper to deal with coherent probabilistic forecasts, and although they reconcile the means of the predictive distributions, the overall distributions are constructed in a bottom-up fashion rather than use a reconciliation process.
-In contrast, the main objective of our paper is to generalise both coherence and reconciliation from point to probabilistic forecasting.
-%	
-%	To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections.
-In addition to being highly intuitive, this allows us to establish a number of theoretical results.
-We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts, while the second shows that reconciled forecasts dominate unreconciled forecasts via the distance reducing property of projections.
-We provide definitions of coherence and forecast reconciliation in the probabilistic setting, and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation.
-We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class.
-We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly estimated in practice, we provide a heuristic argument in favour of MinT reconciliation.
-%	
-%	We also cover the topic of forecast evaluation of probabilistic forecasts via scoring rules.
-In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.
-Therefore we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts.
-Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.
-%	
-%	The remainder of the paper is structured as follows.
-In Section~\ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.
-Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results.
-In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules, while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian}.
-Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.
+	A shortcoming of these traditional methods is that they do not use all the information available in the hierarchy to make coherent forecasts.
+To overcome this issue, \cite{Hyndman2011} propose to utilise all the information available in the hierarchy via a ``Reconciliation" process.
+This is a two-stages process where the first stage involves making forecasts for all series in the hierarchy without considering the aggregation constraints (also known as base forecasts), which is then followed by the reconciliation stage that combines these forecasts imposing the aggregation constraints of the hierarchy.
+A later study by \cite{WicEtAl2019} proposed to optimally combine the base forecasts by minimising the trace of the mean squared errors of reconciled forecasts where they derived an analytical solution to produce reconciled forecasts.
+An important feature of this method is that it imposes the correlation structure of the whole hierarchy to produce reconciled point forecasts.
 
+	While reviewing the existing studies in this literature, our attempt is to give a new understanding to the whole hierarchical forecasting problem with a geometric intuition.
+We first provide a geometric interpretation of coherency and reconciliation in terms of projections.
+Then we rehash all existing reconciliation methods into a single framework based on projections.
+In addition to being highly intuitive, this allows us to establish new theoretical results.
+We prove two new theorems about point forecast reconciliation, the first showing that reconciled forecasts dominate unreconciled forecasts via the distance reducing property of projections while the second shows that reconciliation via projections preserves the unbiasedness of base forecasts.
+
+	Unbiasedness of base forecasts is a strong assumption in many of the existing methods which will be limited only to a selective number of forecasting methods.
+We propose a simple solution to this barrier.
+That is to correct the bias in base forecasts before doing the projection-based reconciliation.
+This allows using any advanced statistical method despite the unbiasedness to produce base forecasts without worrying about the unbiasedness.
+Using an empirical study, we further show that the reconciled forecasts follow from biased corrected base forecasts will improve the forecast accuracy compared to that of the biased forecasts.
+
+	The remainder of this paper is structured as follows.
+In Section~\ref{sec:CoheForecasts} coherent point forecasting is defined geometrically while section~\ref{sec:Reconciliation} contains definitions of projection-based reconciliation as well as our main theoretical results.
+Section~\ref{sec:BiasInRecon} discuss the unbiased preserving property of projection-based reconciliation and Section \ref{sec:BiasCorrection} contains our proposed method to correct the bias in base forecasts.
+In Section \ref{sec:EmpStudy} we apply these methods to get coherent forecasts for domestic tourism flow in Australia and Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.
 \section{Coherent forecasts}\label{sec:CoheForecasts}
@@
 
-    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \cite{Wickramasuriya2017}, \cite{FPP2018} and others, before elaborating on some of the limitations of this understanding.
+    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \cite{WicEtAl2019}, \cite{FPP2018} and others, before elaborating on some of the limitations of this understanding.
 A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables.
@@
 {\bf Include brief summary of all non-traditional hierarchies - e.g.
-grouped hierarchies, temporal hierarchies with wierd overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
+grouped hierarchies, temporal hierarchies with weird overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
 
@@
 However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped onto itself by that projection.
-\todo{perhaps find a reference - it is so fundamental that is is on wikipedia and wolfram mathworld}  In our context this means that for any $\bm{v}\in\mathfrak{s}$, $\bm{SGv}=\bm{v}$.
+This is a fundamental property of projections and also proved in lemma 2.4 in \citet{rao1974}.
+In our context this means that for any $\bm{v}\in\mathfrak{s}$, $\bm{SGv}=\bm{v}$.
 
@@
 
-	The property that reconciliation should improve forecasts was touched upon in Section 2.3 of \cite{Wickramasuriya2017}.
+	The property that reconciliation should improve forecasts was touched upon in Section 2.3 of \cite{WicEtAl2019}.
 The discussion in that paper focuses on the case of MinT.
@@
 
-	\begin{figure}[H]
+	\begin{figure}[H]\label{fig:Schematic_OLSRecon}
 		\centering
@@
 		\resizebox{\linewidth}{!}{\input{Figs/orth_pointforerec_schematic}}
-		\label{fig:Schematic_OLSRecon}
 		\caption{$\hat{\bm{y}}$ is orthogonally projected onto $\mathfrak{s}$}
@@
 Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.
-\todo{include evidence from small empirical example.}
 
@@
 	Note here that we rely here on the generalised Pythagorean Theorem (which involves an equality).
-In contrast, \cite{Wickramasuriya2017} follow \cite{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.
-The proof of \cite{Wickramasuriya2017} requires an assumptions about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.
+In contrast, \cite{WicEtAl2019} follow \cite{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.
+The proof of \cite{WicEtAl2019} requires an assumptions about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.
 The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.
-As such the statement from \cite{Wickramasuriya2017} that {\em``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified; this is only true in with respect to a loss function that depends on ${\bm W}$.
-If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts\todo{include empirical example}.
+As such the statement from \cite{WicEtAl2019} that {\em``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified; this is only true in with respect to a loss function that depends on ${\bm W}$.
+If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts.
 
@@
 
-	While the properties discussed so far hold for any projection matrix, the MinT method of \cite{Wickramasuriya2017} has an additional optimality property.
-\cite{Wickramasuriya2017} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by an oblique projection with a particular choice of $\bm{W}$.
+	While the properties discussed so far hold for any projection matrix, the MinT method of \cite{WicEtAl2019} has an additional optimality property.
+\cite{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by an oblique projection with a particular choice of $\bm{W}$.
 This choice is that $\bm{W}$ should be the forecast error covariance matrix where errors come from using the base forecasts.
@@
 One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.
-An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection.
-Imagining a similar oblique projection along $\bm{R}$ for all the grey points yield reconciled forecasts tightly packed near the target $\bm{y}$.
-In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts.\todo{needs picture with all points projected obliquely then orthogonally}.
+An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection showed as in Figure \ref{fig:Orthogonal_projection_all_points}.
+Figure \ref{fig:Oblique_projection_all_points} depicts a similar oblique projection along $\bm{R}$ for all the gray points yield reconciled forecasts tightly packed near the target $\bm{y}$.
+In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts.
 In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal is expectation.
@@
 			\includegraphics{Figs/OrthProj.pdf}}
-		\caption{\textcolor{red}{include caption}}\label{fig:Orthogonal_projection}
+		\caption{All gray points are orthogonally projected onto the coherent subspace $\mathfrak{s}$.
+Reconciled forecasts marked in red dots are widely spread about the target $\bm{y}$.}\label{fig:Orthogonal_projection_all_points}
 	\end{figure}
@@
 		\includegraphics{Figs/ObliqueProjection.pdf}}
-	\caption{\textcolor{red}{include caption}}\label{fig:Oblique_projection}
+	\caption{All gray points are obliquely projected along the direction of $\bm{R}$.
+Reconciled points denoted in red dots are concentrated about the target $\bm{y}$.}\label{fig:Oblique_projection_all_points}
 	\end{figure}
@@
 
-	\section{Bias in forecast reconciliation}
+	\section{Bias in forecast reconciliation}\label{sec:BiasInRecon}
 
@@
 
-	The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation \cite{Wickramasuriya2017}.
+	The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation \cite{WicEtAl2019}.
 Before restating this proof using a  clear geometric interpretation we discuss in a precise fashion what is meant by unbiasedness.
@@
 
-	\section{Bias correction}
-
+	\section{Bias correction} \label{sec:BiasCorrection}
+	\todo{Need to discuss and rewrite this section since we are using different bias correction method in the empirical study}
 	Our approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
@@
 
-	\section{Application}
+	\section{Empirical study} \label{sec:EmpStudy}
 
-	\section{Conclusions}
+	Total tourism flow of any country can naturally disaggregate along a geographical hierarchy.
+Producing accurate forecasts for these hierarchical time series while preserving the coherency is important for making align business decisions in the tourism industry.
+Many applications related to Australian tourism flow have pronounced that reconciliation improves the point forecast accuracy (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}).
 
+	Using a similar empirical application to tourism forecasting in Australia, we show how to use projection-based reconciliation when we have a set of biased incoherent forecasts.
+As we mentioned in the previous section our focus is to bias adjust the incoherent forecasts first and then do the reconciliation.
+
+	\subsubsection*{Data:}
+	We use ``overnight trips" as a measure of domestic tourism flow in Australia.
+Total ``overnight trips" in Australia can be disaggregated into 7 states, 27 zones and 75 regions forming a geographical hierarchy with $110$ total number of series and $75$ bottom level series.
+More information about the series of this hierarchy is given in Table \ref{table:A1} in the appendix.
+Data were obtained from the National Visitor Survey (NVS) which were collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more.
+Data form a monthly series starting from January 1998 to December 2017 which gives a total of $240$ observations per series.
+
+	We produce $h=1$ to $h=6$ months ahead forecasts using a rolling window approach.
+First training window of $100$ observations is considered from Jan-$1998$ to Apr-$2006$ and produce forecasts for May-$2006$ to Oct-$2006$.
+Then we roll the training window one month at a time where the final forecast is produced for Dec-$2017$.
+This directs to $140 \quad 1$-step-ahead, $139 \quad 2$-step-ahead through $135 \quad 6$-step-ahead forecasts left for evaluation.
+
+	\subsubsection*{Preliminary analysis:}
+
+	While observing the patterns of individual series, we noticed that the signal-to-noise ratio decreases with the disaggregate level of the hierarchy.
+From Figure \ref{fig:Total_TSplots} and \ref{fig:States_Zones_Regs_TSplots} this is depicted well as we see much noisier series in bottom levels whereas the noise level is comparatively stabilised in the upper levels.
+We have also observed that the overnight trips for `Adelaide Hills` has an anomalous observation on December-2002.
+We replaced this observation with the average overnight trips on December-2001 and December-2003 for the same destination.
+
+	\begin{figure}
+		\centering
+		\small
+		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/Total_TSplot.pdf}
+		\caption{Time plot for total overnight trips.}\label{fig:Total_TSplots}
+	\end{figure}
+
+	\begin{figure}
+		\centering
+		\small
+		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots.pdf}
+		\caption{Time plot for some selected series from different disaggregate levels of the hierarchy.}\label{fig:States_Zones_Regs_TSplots}
+	\end{figure}
+
+	\subsubsection*{Base forecasts and reconciliation:}
+
+	We first transform each series in the hierarchy using the Box-Cox transformation as given in equation (\ref{eq:BoxCox_transformation}) to stabilise any variations in the data.
+
+	\begin{equation} \label{eq:BoxCox_transformation}
+	x_t = 
+	\begin{cases} 
+	\log(y_t) & \text{if } \lambda = 0 \\
+	\frac{y_t^\lambda - 1}{\lambda}  & \text{if } \lambda \ne 0
+	\end{cases}
+	\end{equation}
+
+	We use "guerrero" method \citep{guerrero1993time} implemented in \verb|BoxCox.lambda()| function in \verb|forecast| package R software \citep{Rforecast} to select optimal $\lambda$.
+Then  we fit univariate ARIMA models for the transformed series.
+We use \verb|auto.arima()| function in \verb|forecast| package to choose the best model that minimises the AIC.
+Using the fitted models we produce $h=1,...,6$ months ahead forecasts for each series in the hierarchy.
+These forecasts are then back-transformed using equation (\ref{eq:BoxCox_back-transformation}) to scale them back into the original space.
+However, the back transformed forecasts will be biased \citep{FPP2018}.
+
+	\begin{equation} \label{eq:BoxCox_back-transformation}
+	y_{t+h} = 
+	\begin{cases} 
+	\exp({x_{t+h}}) & \text{if } \lambda = 0 \\
+	(\lambda x_{t+h} + 1)^{1/\lambda}  & \text{if } \lambda \ne 0
+	\end{cases}
+	\end{equation}
+
+	Hence the reconciled forecasts follow from these will also biased.
+This is the exact scenario that we want to demonstrate in this study.
+As we proposed before, we first bias correct the base forecasts prior to the reconciliation.
+We use the mathematical formula in equation (\ref{eq:BoxCox_BT_biasadj}) to calculate the back-transformed and bias-adjusted forecasts.
+
+	\begin{equation} \label{eq:BoxCox_BT_biasadj}
+	 y_{t+h} = 
+	\begin{cases} 
+	\exp({x_{t+h}})[1+\frac{\sigma_h^2}{2}] & \text{if } \lambda = 0 \\
+	(\lambda x_{t+h} + 1)^{1/\lambda}[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda x_{t+h} + 1)^2}]       & \text{if } \lambda \ne 0
+	\end{cases}
+	\end{equation}
+	where, $x_{t+h}$ is the $h$-step-ahead forecasts from the Box-Cox transformed series and $\sigma_h^2$ is the variance of $x_{t+h}$.
+
+	Once we get the base forecasts for all series in the hierarchy, we can do the projection-based reconciliation to get coherent forecasts.
+We reconcile both biased and bias-corrected (unbiased) base forecasts to demonstrate how the reconciliation follows from unbiased base forecasts improves the forecast accuracy.
+MinT(Shrink), WLS, OLS and bottom-up methods are used for reconciliation.
+
+	\subsubsection*{Results and discussion:}
+
+	Mean Squared Error (MSE) is used to measure the forecast accuracy and results are presented in Table \ref{tab:Results_MSE}.
+Recall that projections preserve the unbiasedness in reconciled forecasts only if the base forecasts are unbiased.
+As a consequence, the reconciled forecasts follow from the biased base forecasts will also be biased.
+We can see from the results that unbiased-reconciled forecasts from MinT(Shrink) and WLS are better than that of biased-reconciled forecasts although the unbiased-base forecasts are not necessarily better than the biased-base forecasts.
+Furthermore, unbiased MinT reconciled forecasts are outperforming all biased and unbiased forecasts.
+These results are true for all forecast horizons.
+
+	\begin{table}
+		\caption {Average {MSE($\times 10^3$)} of base and reconciled point forecasts at forecasts horizons $h=1,...,6$ are presented.
+Bias and unbiased columns represent the results for biased-base/biased-reconciled and unbiased-base/unbiased-reconciled forecasts respectively.
+Comparisons can be made across biased vs unbiased forecasts as well as base vs reconciled forecasts.}
+		\label{tab:Results_MSE}
+		\centering\tabcolsep=0.08cm
+
+		\resizebox{\linewidth}{!}{
+		\begin{tabular}{@{}lSSSSSSSSSSSS@{}}
+			\toprule
+			\multicolumn{1}{c}{ } & \multicolumn{2}{c}{h=1} & \multicolumn{2}{c}{h=2} & \multicolumn{2}{c}{h=3} & \multicolumn{2}{c}{h=4} & \multicolumn{2}{c}{h=5} & \multicolumn{2}{c}{h=6} \\
+			\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11} \cmidrule(lr){12-13}
+			Method & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased\\
+			\midrule
+			Base & 12.18 & 161.63 & 13.14 & 243.13 & 14.08 & 269.20 & 15.88 & 325.41 & 15.49 & 332.11 & 15.79 & 344.40\\
+			\hline
+			MinT(Shrink) & 10.14 & $\bm{9.96}$ & 11.47 & $\bm{10.78}$ & 12.55 & $\bm{11.94}$ & 15.53 & $\bm{14.03}$ & 14.63 & $\bm{13.46}$ & 15.28 & $\bm{13.78}$\\
+			\hline
+			WLS & 15.62 & 13.97 & 15.93 & 13.71 & 16.65 & 14.50 & 18.91 & 16.26 & 18.76 & 16.20 & 18.85 & 15.83\\	
+			\hline
+			OLS & 11.73 & 135.17 & 12.80 & 204.42 & 13.73 & 225.59 & 15.56 & 272.41 & 15.17 & 278.08 & 15.49 & 288.21\\
+			\hline
+			Bottom-up & 17.86 & 15.55 & 17.86 & 14.90 & 18.47 & 15.61 & 20.50 & 17.21 & 20.34 & 17.04 & 20.39 & 16.69\\
+
+			\bottomrule
+		\end{tabular}
+	}
+	\end{table}
+
+%	\begin{figure}
+%		\centering
+%		\small
+%		\includegraphics[width = \textwidth]{Empirical-results/Final-results/SS_MSE_Results.pdf}
+%		\caption{\textcolor{red}{include caption}}\label{fig:MSE_SkillScore}
+%	\end{figure}
+%
+
+	Following the distance reducing property in Theorem \ref{th:distred} and the discussion therein, we have noted that the orthogonal projections will always improve the base forecasts with respect to the mean squared errors whereas, the oblique projections will not always, but improves only on average.
+Figure \ref{fig:BaseVSRecon_Fc} shows the MSE difference between base forecasts and reconciled forecasts - MinT, OLS and WLS for all replications in different forecast horizons.
+Recall that OLS reconciliation is doing orthogonal projection whereas MinT and WLS are doing oblique projections onto the coherent subspace.
+It is apparent from the plot that the MSE difference for OLS is always positive, implying that OLS improves the base in terms of MSE in all replications.
+On the other hand,  there are some instances that this difference for MinT and WLS is negative which is reflected from the short negative tails of box-plots.
+This implies that oblique projections will not improve the base forecasts in every case.
+However, these projections will outperform the base with respect to MSE on average which is again reflected from the highly positive skewed MSE differences.
+
+	 \begin{figure}[H]
+		\centering
+		\small
+		\includegraphics[width = \textwidth]{Empirical-results/Final-results/Base-Recon.pdf}
+		\caption{Difference of MSE between Base forecasts and reconciled forecasts over the replications in distinct forecast horizons.
+Positive values of the difference implies reconciliation improves the forecast accuracy than base forecasts.}\label{fig:BaseVSRecon_Fc}
+	\end{figure}
+
+	\section{Conclusions} \label{sec:conclusions}
+
+	By redefining coherent point forecast and point forecast reconciliation, we rehash all existing reconciliation methods into a single projection based geometric framework.
+We have also established new theoretical results that support the use of projections for point forecast reconciliation.
+We show that projection of unbiased base forecasts onto the coherent subspace will always produce unbiased reconciled forecasts.
+Yet the projection-based reconciliation can be used to reconciled bias base forecasts after bias adjustments.
+Empirical results from the application of these methods to forecasting Australian domestic tourism flow show that reconciled forecast follows from bias-adjusted base improves the forecast accuracy and unbiased MinT reconciliation is outperforming.
+
+	These new geometric interpretations of hierarchical forecast reconciliation facilitate extensions of the problem to a probabilistic framework. We leave this discussion into a different paper. 	
+	\newpage
+	\section{Appendix}
+
+	\begin{table} 
+		\caption{Geographical hierarchy of Australian tourism flow}\label{table:A1}
+
+		\resizebox{\linewidth}{!}{
+			\begin{tabular}{lllllllllll}
+				\toprule
+				\multicolumn{3}{c}{\textbf{Level 0 - Total}}   &  &  \multicolumn{3}{l}{\textit{Zones cont.}}   &  & \multicolumn{3}{l}{\textit{Regions cont.}} \\
+				\cmidrule(lr){1-3}
+				1 & {\text{Tot}} & {Australia} &  & 48  & AED & Blue Mountains && 99 & FAA & Hobert and South\\
+				\cmidrule(lr){1-3}
+				\multicolumn{3}{c}{\textbf{Level 1 - States}}  &  & 49  & AFA & Canberra  && 100 & FBA & East Coast\\
+				\cmidrule(lr){1-3}
+				2 & A & NSW 				&  & 50  & BAA & Melbourne && 101 & FBB & Launceston, Tamar \& North\\
+				3 & B & Victoria 			&  & 51  & BAB & Peninsula && 102 & FCA & North West\\
+				4 & C & Queensland 			&  & 52  & BAC & Geelong && 103 & FCB& Wilderness West\\
+				5 & D & South Australia     &  & 53  & BBA & Western && 104 & GAA& Darwin\\
+				6 & E & Western Australia   &  & 54  & BCA & Lakes && 105 & GAB& Kakadu Arnhem\\
+				7 & F & Tasmania   			&  & 55  & BCB & Grippsland && 106 & GAC& Katherine Daly\\
+				8 & G & Northern Territory &  &  56  & BCD & Phillip Island && 107 & GBA& Barkly\\
+				\cmidrule(lr){1-3} 
+				\multicolumn{3}{c}{\textbf{Level 2 - Zones}}  &  &  57  & BDA & Central Murray && 108 & GBB& Lasseter\\
+				\cmidrule(lr){1-3}
+				9 	& AA & Metro NSW 	  	   	&  & 58  & BDB & Goulburn && 109 & GBC& Alice Springs\\
+				10 	& AB & North Coast NSW 	   	&  & 59  & BDC & High Country && 110 & GBD& MacDonnell\\
+				11	& AC & South Coast NSW	   	&  & 60  & BDD & Melbourne East &&&&\\
+				12	& AD & South NSW 			&  & 61  & BDE & Upper Yarra &&&& \\
+				13	& AE & North NSW 			&  & 62  & BDF & Murray East &&&&\\
+				14	& AC & ACT					&  & 63  & BEA & Wimmera+Mallee &&&&\\
+				15	& BA & Metro VIC			&  & 64  & BEB & Western Grampians &&&&\\ 		
+				16	& BB & West Coast VIC		&  & 65  & BEC & Bendigo Loddon &&&&\\
+				17	& BC & East Coast VIC		&  & 66  & BED & Macedon &&&&\\ 
+				18	& BC & North East VIC		&  & 67  & BEE & Spa Country &&&&\\ 
+				19	& BD & North West VIC		&  & 68  & BEF & Ballarat &&&&\\
+				20  & CA & Metro QLD			&  & 69  & BEG & Central Highlands &&&&\\
+				21  & CB & Central Coast QLD	&  & 70  & CAA & Gold Coast &&&&\\
+				22  & CC & North Coast QLD		&  & 71  & CAB & Brisbane &&&&\\
+				23  & CD & Inland QLD			&  & 72  & CAC & Sunshine Coast &&&&\\
+				24	& DA & Metro SA				&  & 73  & CBA & Central Queensland &&&&\\	
+				25	& DB & South Coast SA		&  & 74  & CBB & Bundaberg &&&&\\	
+				26	& DC & Inland SA			&  & 75  & CBC & Fraser Coast &&&&\\	
+				27	& DD & West Coast SA		&  & 76  & CBD & Mackay &&&&\\
+
+				28	& EA & West Coast WA 	& & 77  & CCA & Whitsundays &&&&\\	
+				29	& EB & North WA			& & 78  & CCB & Northern &&&&\\	
+				30	& EC & South WA 		& & 79  & CCC & Tropical North Queensland &&&&\\	
+				31	& FA & South TAS		& & 80  & CDA & Darling Downs &&&&\\
+				32	& FB & North East TAS	& & 81  & CDB & Outback &&&&\\	
+				33	& FC & North West TAS	& & 82  & DAA & Adelaide &&&&\\
+				34	& GA & North Coast NT	& & 83  & DAB & Barossa &&&&\\
+				35	& GB & Central NT		& & 84  & DAC & Adelaide Hills &&&&\\
+				\cmidrule(lr){1-3}
+				\multicolumn{3}{c}{\textbf{Level 2 - Regions}} & & 85  & DBA & Limestone Coast &&&&\\
+				\cmidrule(lr){1-3}
+				36	& AAA & Sydney 			& 	& 86  & DBB & Fleurieu Peninsula &&&&\\
+				37	& AAB & Central Coast	&	& 87  & DBC & Kangaroo Island &&&&\\
+				38  & ABA & Hunter 			& 	& 88  & DCA & Murraylands &&&&\\
+				39  & ABB & North Coast NSW & 	& 89  & DCB & Riverland &&&&\\
+				40  & ABC & Hunter			& 	& 90  & DCC & Clare Valley &&&&\\
+				41  & ACA & South Coast		& 	& 91  & DCD & Flinders Range and Outback &&&&\\
+				42  & ADA & Snowy Mountains & 	& 92  & DDA & Eyre Peninsula &&&&\\
+				43  & ADB & Capital Country & 	& 93  & DDB & Yorke Peninsula &&&&\\
+				44  & ADC & The Murray 		& 	& 94  & EAA & Australia's Coral Coast &&&&\\
+				45  & ADD & Riverina 		& 	& 95  & EAB & Experience Perth &&&&\\
+				45  & AEA & Central NSW 	& 	& 96  & EAC & Australia's South West &&&&\\
+				46  & AEB & New England North West &  & 97  & EBA & Australia's North West &&&&\\
+				47  & AEC & Outback NSW & & 98  & ECA & Australia's Golden Outback &&&&\\
+				\bottomrule
+			\end{tabular}
+		}
+	\end{table}
 	\newpage

### 2019-08-12 Hierarchical-forecast-reconciliation/Appendix.tex
Adjusted the table in Appendix

--- 2019-07-30 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
@@
-\documentclass[12pt]{article}
-\usepackage{amsmath}
-\usepackage{graphicx,psfrag,epsf}
-\usepackage{enumerate}
-\usepackage{natbib}
-\usepackage{url} % not crucial - just used below for the URL
 	
-\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
-\usepackage{mathrsfs, float, booktabs,todonotes,amsthm, xcolor,sidenotes, caption, subcaption}
+	\begin{table} 
+		\caption{Geographical hierarchy of Australian tourism flow}\label{table:A1}
+		\centering\tabcolsep=0.08cm
+		\tiny
+		\resizebox{\linewidth}{!}{
+			\begin{tabular}{lllllllllll}
+				\toprule
+				\multicolumn{3}{c}{\textbf{Level 0 - Total}}   &  &  \multicolumn{3}{l}{\textit{Zones cont.}}   &  & \multicolumn{3}{l}{\textit{Regions cont.}} \\
+				\cmidrule(lr){1-3}
+				1 & {\text{Tot}} & {Australia} &  & 48  & AED & Blue Mountains && 99 & FAA & Hobert and South\\
+				\cmidrule(lr){1-3}
+				\multicolumn{3}{c}{\textbf{Level 1 - States}}  &  & 49  & AFA & Canberra  && 100 & FBA & East Coast\\
+				\cmidrule(lr){1-3}
+				2 & A & NSW 				&  & 50  & BAA & Melbourne && 101 & FBB & Launceston, Tamar \& North\\
+				3 & B & Victoria 			&  & 51  & BAB & Peninsula && 102 & FCA & North West\\
+				4 & C & Queensland 			&  & 52  & BAC & Geelong && 103 & FCB& Wilderness West\\
+				5 & D & South Australia     &  & 53  & BBA & Western && 104 & GAA& Darwin\\
+				6 & E & Western Australia   &  & 54  & BCA & Lakes && 105 & GAB& Kakadu Arnhem\\
+				7 & F & Tasmania   			&  & 55  & BCB & Grippsland && 106 & GAC& Katherine Daly\\
+				8 & G & Northern Territory &  &  56  & BCD & Phillip Island && 107 & GBA& Barkly\\
+				\cmidrule(lr){1-3} 
+				\multicolumn{3}{c}{\textbf{Level 2 - Zones}}  &  &  57  & BDA & Central Murray && 108 & GBB& Lasseter\\
+				\cmidrule(lr){1-3}
+				9 	& AA & Metro NSW 	  	   	&  & 58  & BDB & Goulburn && 109 & GBC& Alice Springs\\
+				10 	& AB & North Coast NSW 	   	&  & 59  & BDC & High Country && 110 & GBD& MacDonnell\\
+				11	& AC & South Coast NSW	   	&  & 60  & BDD & Melbourne East &&&&\\
+				12	& AD & South NSW 			&  & 61  & BDE & Upper Yarra &&&& \\
+				13	& AE & North NSW 			&  & 62  & BDF & Murray East &&&&\\
+				14	& AC & ACT					&  & 63  & BEA & Wimmera+Mallee &&&&\\
+				15	& BA & Metro VIC			&  & 64  & BEB & Western Grampians &&&&\\ 		
+				16	& BB & West Coast VIC		&  & 65  & BEC & Bendigo Loddon &&&&\\
+				17	& BC & East Coast VIC		&  & 66  & BED & Macedon &&&&\\ 
+				18	& BC & North East VIC		&  & 67  & BEE & Spa Country &&&&\\ 
+				19	& BD & North West VIC		&  & 68  & BEF & Ballarat &&&&\\
+				20  & CA & Metro QLD			&  & 69  & BEG & Central Highlands &&&&\\
+				21  & CB & Central Coast QLD	&  & 70  & CAA & Gold Coast &&&&\\
+				22  & CC & North Coast QLD		&  & 71  & CAB & Brisbane &&&&\\
+				23  & CD & Inland QLD			&  & 72  & CAC & Sunshine Coast &&&&\\
+				24	& DA & Metro SA				&  & 73  & CBA & Central Queensland &&&&\\	
+				25	& DB & South Coast SA		&  & 74  & CBB & Bundaberg &&&&\\	
+				26	& DC & Inland SA			&  & 75  & CBC & Fraser Coast &&&&\\	
+				27	& DD & West Coast SA		&  & 76  & CBD & Mackay &&&&\\
 
-\usepackage[bb=boondox]{mathalfa}
-\usepackage{tikz}
-\usetikzlibrary{arrows,positioning,shapes,fit,calc}
-\usepackage{amsfonts}
-
-\pdfminorversion=4
-% NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{1}
-
-% DON'T change margins - should be 1 inch all around.
-\addtolength{\oddsidemargin}{-.5in}%
-\addtolength{\evensidemargin}{-.5in}%
-\addtolength{\textwidth}{1in}%
-\addtolength{\textheight}{-.3in}%
-\addtolength{\topmargin}{-.8in}%
-
-\DeclareMathOperator*{\argmin}{arg\,min}
-\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type
-\def\mathbi#1{\textit{ #1}}
-\def\mathB#1{\textbf{ #1}}
-\def\E{\text{E}}
-\def\var{\text{Var}}
-
-\def\PQ{\begin{pmatrix}\bm{G}\\[-0.2cm]\bm{H}\end{pmatrix}}
-\def\bt{\begin{pmatrix}\tilde{\bm{b}}\\[-0.2cm]\tilde{\bm{a}}\end{pmatrix}}
-
-%\theoremstyle{theo}
-\newtheorem{theo}{Theorem}[section]
-
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-
-\theoremstyle{property}
-\newtheorem{property}{Property}[section]
-
-\begin{document}
-
-	%\bibliographystyle{natbib}
-
-	\def\spacingset#1{\renewcommand{\baselinestretch}%
-		{#1}\small\normalsize} \spacingset{1}
-
-	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-	\if1\blind
-	{
-		\title{\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.}
-		\author{Puwasala Gamakumara\thanks{
-				The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.  We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
-			Department of Econometrics and Business Statistics,\\
-			Monash University,\\ VIC 3800, Australia.\\
-			Email: Puwasala.Gamakumara@monash.edu \\
-			and \\
-			Anastasios Panagiotelis\\
-			Department of Econometrics and Business Statistics,\\
-			Monash University,\\ VIC 3800, Australia.\\
-			Email: Anastasios.Panagiotelis@monash.edu \\
-			and \\
-			George Athanasopoulos\\
-			Department of Econometrics and Business Statistics,\\
-			Monash University,\\ VIC 3800, Australia.\\
-			Email: george.athanasopoulos@monash.edu \\
-			and \\
-			Rob J Hyndman\\
-			Department of Econometrics and Business Statistics,\\
-			Monash University,\\ VIC 3800, Australia.\\
-			Email: rob.hyndman@monash.edu \\}
-		\maketitle
-	} \fi
-
-	\if0\blind
-	{
-		\bigskip
-		\bigskip
-		\bigskip
-		\begin{center}
-			{\LARGE\bf Hierarchical Forecasts Reconciliation}
-		\end{center}
-		\medskip
-	} \fi
-
-	\bigskip
-
-	\begin{abstract} TBC
-		%  Forecast reconciliation involves adjusting forecasts to ensure coherence with aggregation constraints.
-We extend this concept from point forecasts to probabilistic forecasts by redefining forecast reconciliation in terms of linear functions in general, and projections more specifically.
-New theorems establish that the true predictive distribution can be recovered in the elliptical case by linear reconciliation, and general conditions are derived for when this is a projection.
-A geometric interpretation is also used to prove two new theoretical results for point forecasting; that reconciliation via projection both preserves unbiasedness and dominates unreconciled forecasts in a mean squared error sense.
-Strategies for forecast evaluation based on scoring rules are discussed, and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive distribution coheres with aggregation constraints.
-Finally, evidence from a simulation study shows that reconciliation based on an oblique projection, derived from the MinT method of \citet{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
-	\end{abstract}
-
-%	\noindent%
-%	{\it Keywords:}  Forecast Reconciliation, Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
-%	\vfill
-
-	\newpage
-	\spacingset{1.45} % DON'T change the spacing!
-
-	\section{Introduction}\label{sec:intro}
-
-	Have to explain why we are writing this
-	\begin{itemize}
-		\item Geometric intuition - restate existing results but with a new understanding.
-		\item In particular champion projections.
-		\item State that paper is in some ways a review paper.
-		\item Propose a simple solution to the issue of bias.
-	\end{itemize}
-
-%	Large collections of time series often follow some aggregation structure.
-For example, the electricity demand of a country can be disaggregated according to a geographic hierarchy of states, cities, and individual households.
-To ensure aligned decision making, it is important that forecasts at the most disaggregated level add up to forecasts at more aggregated levels.
-This property is called ``coherence''.
-On the other hand ``reconciliation'' is a process whereby incoherent forecasts are made coherent.
-Both of these concepts have been developed extensively for point forecasting.
-Generalising both of these concepts, particularly the latter, to probabilistic forecasting is a gap that we seek to address in this work.
-We do so by first providing a novel geometric interpretation to coherence and reconciliation in the point forecasting case.
-This can easily be generalised to probabilistic forecasting allowing us to derive further results for elliptical distributions as well as provide insight into forecast evaluation via multivariate  scoring rules.
-%	
-%	Traditional approaches to ensure coherent point forecasts produce first-stage forecasts at a single level of the hierarchy.
-To describe these we use the small hierarchy in Figure~\ref{fig1} where the variable labelled $Tot$ is the sum of the series $A$ and series $B$, the series $A$ is the sum of series $AA$ and series $AB$ and the series $B$ is the sum of the series $BA$ and $BB$.
-In the bottom-up approach \citep{Dunn1976}, forecasts are produced at the most disaggregated level (series $AA$, $AB$, $BA$ and $BB$) and then summed to recover forecasts for all higher-level series.
-Alternatively, in the top-down approach \citep{Gross1990}, a top-level forecast is first produced (series $Tot$) and bottom-level forecasts are recovered by disaggregating the forecast using either historical or forecasted proportions.
-A middle-out approach is a hybrid between these two, that for the hierarchy in Figure~\ref{fig1} would produce first stage forecasts for series $A$ and $B$.
-%	
-%	
-%	In recent years, reconciliation methods introduced by \citet{Hyndman2011} have become increasingly popular.
-For these methods, first stage forecasts are independently produced for all series rather than series at a single level.
-Since these so-called `base' forecasts are rarely coherent in practice, they are subsequently adjusted or `reconciled' to ensure coherence.
-Note that we use coherence and reconciliation as distinct terms, in contrast to their at times ambiguous usage in the past.
-To date, reconciliation has typically been formulated as a regression problem with alternative reconciliation methods resembling different least squares estimators.
-These include Ordinary Least Squares {OLS} \citep{Hyndman2011}, Weighted Least Squares {WLS} \citep{AthEtAl2017}, and a Generalised Least Squares (GLS) estimator \citep{Wickramasuriya2017} named MinT since it minimises the trace of the squared error matrix.
-These methods have been shown to outperform traditional alternatives across a range of simulated and real-world datasets \citep{AthEtAl2009,VanErven2015a,Wickramasuriya2017} since they use information at all levels of the hierarchy and, in some sense, hedge against the risk of model misspecification at a single level.
-%	
-%	A shortcoming of the existing literature is a focus on point forecasting despite an increased understanding over the past decade of the importance of providing a full predictive distribution for forecast uncertainty \citep[see][and references therein]{Gneiting2014}.
-Indeed to the best of our knowledge, the (as yet unpublished) work of \citep{BenTaieb2017} is the only paper to deal with coherent probabilistic forecasts, and although they reconcile the means of the predictive distributions, the overall distributions are constructed in a bottom-up fashion rather than use a reconciliation process.
-In contrast, the main objective of our paper is to generalise both coherence and reconciliation from point to probabilistic forecasting.
-%	
-%	To facilitate the extension of point forecast reconciliation to probabilistic forecasting, we first provide a geometric interpretation of existing point reconciliation methods, framing them in terms of projections.
-In addition to being highly intuitive, this allows us to establish a number of theoretical results.
-We prove two new theorems about point forecast reconciliation, the first showing that reconciliation via projections preserves the unbiasedness of base forecasts, while the second shows that reconciled forecasts dominate unreconciled forecasts via the distance reducing property of projections.
-We provide definitions of coherence and forecast reconciliation in the probabilistic setting, and describe how these definitions lead to a reconciliation procedure that merely involves a change of basis and marginalisation.
-We show that probabilistic reconciliation via linear transformations can recover the true predictive distribution as long as the latter is in the elliptical class.
-We provide conditions for which this linear transformation is a projection, and although this projection cannot be feasibly estimated in practice, we provide a heuristic argument in favour of MinT reconciliation.
-%	
-%	We also cover the topic of forecast evaluation of probabilistic forecasts via scoring rules.
-In particular, we prove that for a coherent data generating process, the log score is not proper with respect to incoherent forecasts.
-Therefore we recommend the use of the energy score or variogram score for comparing reconciled to unreconciled forecasts.
-Two or more reconciled forecasts can be compared using log score, energy score or variogram score, although we show that comparisons should be made on the full hierarchy for the latter two scores.
-%	
-%	The remainder of the paper is structured as follows.
-In Section~\ref{sec:definitions} coherence is defined geometrically for both point and probabilistic forecasts.
-Section~\ref{sec:reconciliation} contains definitions of point and probabilistic forecast reconciliation as well as our main theoretical results.
-In Section~\ref{sec:evaluation} we consider the evaluation of probabilistic hierarchical forecasts via scoring rules, while a simulation study comparing unreconciled probabilistic forecasts and different kinds of reconciled probabilistic forecasts is provided in Section~\ref{sec:gaussian}.
-Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.
-
-\section{Coherent forecasts}\label{sec:CoheForecasts}
-
-	\subsection{Notation and preliminaries}\label{sec:notation}
-
-    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \cite{Wickramasuriya2017}, \cite{FPP2018} and others, before elaborating on some of the limitations of this understanding.
-A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables.
-We let $\bm{y}_t \in \mathbb{R}^n$ be a vector comprising observations of all variables in the hierarchy at time $t$.
-The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.
-The hierarchical structure of the data implies that the following holds for all $t$
-
-    \begin{equation}
-    \bm{y}_t = \bm{Sb}_t,
-    \end{equation}
-    where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints.
-
-		\begin{figure}[H]
-			\begin{center}
-				\leaf{AA} \leaf{AB}
-				\branch{2}{A}
-				\leaf{BA} \leaf{BB}
-				\branch{2}{B}
-				\branch{2}{Tot}
-				\qobitree
-			\end{center}
-			\caption{An example of a two level hierarchical structure.}\label{fig:basichier}
-		\end{figure}
-
-	To clarify these concepts consider the example of the hierarchy in Figure~\ref{fig:basichier}.
-For this hierarchy, $n=7$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$ and
-	\[
-	\bm{S} = \begin{pmatrix}
-	1 & 1 & 1 & 1  \\
-	1 & 1 & 0 & 0 \\
-	0 & 0 & 1 & 1 \\
-	& \multicolumn{2}{c}{\bm{I}_4} &
-	\end{pmatrix},
-	\]
-	where $\bm{I}_4$ is the $4\times 4$ identity matrix.
-
-	While such a definition is completely serviceable, it obscures the full generality of the literature on so-called hierarchical time series.
-In fact, concepts such as coherence and reconciliation, defined in full below, only require the data to have two important characteristics; the first is that they are multivariate, the second is that they adhere to linear constraints.
-
-	\subsection{Coherence}\label{sec:cohpointf}
-
-	The property that data adhere to some linear constraints is referred to as {\em coherence}.  We now provide definitions aimed at providing geometric intuition of hierarchical time series.
-
-	 \begin{definition}[Coherent subspace]\label{def:cohspace}
-	 	The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which a set of linear constraints holds for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
-	 \end{definition}
-
-     To further illustrate, Figure \ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.
-The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space, i.e.
-$m=2$ and $n=3$.
-It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$.
-In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.
-However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom level series, $y_{A,t}$ and $y_{B,t}$.
-In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$.
-However, while there are multiple ways to define an $\bm{S}$ matrix, in all cases the columns will span the same coherent subspace, which is unique.
-
-     \begin{figure}[H]
-     	\centering
-     	\vspace{-0.9cm}
-     	\small
-     	\resizebox{\linewidth}{!}{
-     		\input{Figs/3D_hierarchy}
+				28	& EA & West Coast WA 	& & 77  & CCA & Whitsundays &&&&\\	
+				29	& EB & North WA			& & 78  & CCB & Northern &&&&\\	
+				30	& EC & South WA 		& & 79  & CCC & Tropical North Queensland &&&&\\	
+				31	& FA & South TAS		& & 80  & CDA & Darling Downs &&&&\\
+				32	& FB & North East TAS	& & 81  & CDB & Outback &&&&\\	
+				33	& FC & North West TAS	& & 82  & DAA & Adelaide &&&&\\
+				34	& GA & North Coast NT	& & 83  & DAB & Barossa &&&&\\
+				35	& GB & Central NT		& & 84  & DAC & Adelaide Hills &&&&\\
+				\cmidrule(lr){1-3}
+				\multicolumn{3}{c}{\textbf{Level 2 - Regions}} & & 85  & DBA & Limestone Coast &&&&\\
+				\cmidrule(lr){1-3}
+				36	& AAA & Sydney 			& 	& 86  & DBB & Fleurieu Peninsula &&&&\\
+				37	& AAB & Central Coast	&	& 87  & DBC & Kangaroo Island &&&&\\
+				38  & ABA & Hunter 			& 	& 88  & DCA & Murraylands &&&&\\
+				39  & ABB & North Coast NSW & 	& 89  & DCB & Riverland &&&&\\
+				40  & ABC & Hunter			& 	& 90  & DCC & Clare Valley &&&&\\
+				41  & ACA & South Coast		& 	& 91  & DCD & Flinders Range and Outback &&&&\\
+				42  & ADA & Snowy Mountains & 	& 92  & DDA & Eyre Peninsula &&&&\\
+				43  & ADB & Capital Country & 	& 93  & DDB & Yorke Peninsula &&&&\\
+				44  & ADC & The Murray 		& 	& 94  & EAA & Australia's Coral Coast &&&&\\
+				45  & ADD & Riverina 		& 	& 95  & EAB & Experience Perth &&&&\\
+				45  & AEA & Central NSW 	& 	& 96  & EAC & Australia's South West &&&&\\
+				46  & AEB & New England North West &  & 97  & EBA & Australia's North West &&&&\\
+				47  & AEC & Outback NSW & & 98  & ECA & Australia's Golden Outback &&&&\\
+				\bottomrule
+			\end{tabular}
 		}
-     	\caption{Depiction of a three dimensional hierarchy with $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$.
-The gray colour two dimensional plane reflects the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that spans $\mathfrak{s}$.
-The points in $\mathfrak{s}$ represents realisations or coherent forecasts}\label{fig:3D_hierarchy}
-     \end{figure}
-
-	 \begin{definition}[Hierarchical Time Series]\label{def:cohspace}
-	 	A hierarchical time series is an $n$-dimensional multivariate time series such that all observed values $\bm{y}_1,\ldots,\bm{y}_T$ and all future values $\bm{y}_{T+1},\bm{y}_{T+2},\ldots$  lie in the coherent subspace, i.e.
-$\bm{y}_t\in\mathfrak{s}\quad\forall t$.
-	 \end{definition}
-
-	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.
-Also notable by its absence in the above definition is any reference to {\em aggregation}.
-In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure~\ref{fig:basichier} and/or do not involve aggregation.
-{\bf Include brief summary of all non-traditional hierarchies - e.g.
-grouped hierarchies, temporal hierarchies with wierd overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
-
-%	It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$.
-Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.
-%	
-%	\begin{figure}[H]
-%		\begin{center}
-%			\begin{tikzpicture}[
-%			>=stealth,
-%			bullet/.style={
-%				fill=black,
-%				circle,
-%				minimum width=1.5cm,
-%				inner sep=0pt
-%			},
-%			projection/.style={
-%				->,
-%				thick,
-%				label,
-%				shorten <=2pt,
-%				shorten >=2pt
-%			},
-%			every fit/.style={
-%				ellipse,
-%				draw,
-%				inner sep=0pt
-%			}
-%			]
-%			\node at (2,3) {$s$};
-%			\node at (0,5) {$\mathbb{R}^m$(domain of $s$)};
-%			\node at (4,5) {$\mathbb{R}^n$(codomain of $s$)};
-%			\node at (4.7,2.0) {$\mathfrak{s}$(image of $s$)};
-%			%\node[bullet,label=below:$f(x)$] at (4,2.5){};
-%			\draw (0,2.5) ellipse (1.02cm and 2.2cm);
-%			\draw (4,2.5) ellipse (1.02cm and 2.2cm);
-%			\draw (4,2.5) ellipse (0.51cm and 1.1cm);
-%			\draw[projection, label=below:$f$] (0.3,2.5) -- (3.8,2.5) ;
-%			\end{tikzpicture}
-%		\end{center}
-%		\caption{The domain, codomain and image of the mapping $s$.}\label{fig2}
-%	\end{figure}
-
-	\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
-		Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a vector of point forecasts of all series in the hierarchy at time $t+h$, made using information up to and including time $t$.
-Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathfrak{s}$.
-	\end{definition}
-
-    Without any loss of generality, the above definition could also be applied to prediction for multivariate data in general, rather than just forecasting of time series.
-Much of the early literature that dealt with the problem of forecasting hierarchical time series \citep[see][and references therein]{Gross1990} produced forecasts at a single level of the hierarchy in the first stage.
-Subsequently forecasts for all series were recovered through aggregation, disaggregation according to historical or forecast proportions or some combination of both.
-As such incoherent forecasts were not a problem in these earlier papers.
-
-    Forecasting a single level of the hierarchy did not, however echo common practice within many industries.\todo{might need refs}  In many organisations different departments or `silos' each produced their own forecasts, often with their own information sets and judgemental adjustments.
-This approach does have several advantages over only forecasting a single level.
-First, there is no loss of information since all bottom levels are modelled.
-Second, modelling top level series often identifies features such as trend and seasonality that cannot be detected in noisy disaggregate data.
-Unfortunately, however, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.
-This problem of incoherent forecasts cannot in general be solved by multivariate modelling either.
-Instead, the solution to incoherent forecasts is to make an ex post adjustment that ensures coherence, a process known as {\em forecast reconciliation}
-
-\section{Forecast reconciliation}\label{sec:Reconciliation}
-
-	The problem of forecast reconciliation is predicated on there being an $n$-vector of forecasts that are incoherent.
-We will call these {\em base forecasts} and denote them as $\hat{\bm{y}}_{t+h|h}$, where the subscript $t+h|h$ implies that the forecast is made as time $t$ for a period $h$ steps into the future.
-In the sequel, this subscript will be dropped at times for ease of exposition.
-In the most general terms, reconciliation can be defined as follows
-
-	\begin{definition}[Reconciled forecasts]\label{def:reconpoint}
-		Let $\psi$ be a mapping, $\psi:\mathbb{R}^n\rightarrow\mathfrak{s}$.
-The point forecast $\tilde{\bm{y}}_{t+h|t}=\psi\left(\hat{\bm{y}}_{t+h|t}\right)$ is said to ``reconcile'' a base forecast $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $\psi(.)$
-	\end{definition}
-
-	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.
-One way to achieve this is with a matrix $\bm{SG}$, where $\bm{G}$ is an $(n-m)\times n$ matrix  (some authors use $\bm{P}$ used in place of $\bm{G}$).
-This facilitates an interpretation of reconciliation as a two-step process, in the first step, base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.
-
-	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix onto $\mathfrak{s}$.
-In general a projection matrix has the idemoptence property, i.e.
-$\bm{SG}^2=\bm{SG}$.
-However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped onto itself by that projection.
-\todo{perhaps find a reference - it is so fundamental that is is on wikipedia and wolfram mathworld}  In our context this means that for any $\bm{v}\in\mathfrak{s}$, $\bm{SGv}=\bm{v}$.
-
-	We begin by considering the special case of an orthogonal projection whereby $\bm{G}=\left(\bm{S}'\bm{S}\right)^{-1}\bm{S}'$.
-This is equivalent to so called OLS reconciliation as introduced by \cite{Hyndman2011}.
-We refrain from any discussion of regression models focusing instead on geometric interpretations.
-However the connection between OLS and orthogonal projection should be clear, in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection of the data onto the span of the regressors.
-
-	\subsection{Orthogonal projection}
-
-	In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.
-The  first is that reconciliation should adjust the base forecasts as little as possible, i.e.
-the base and reconciled forecast should be `close'.
-The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value that is targeted by the forecast.
-
-	To address the first of these properties we make the concept of closeness more concrete, by considering the Euclidean distance between the base forecast $\hat{\bm{y}}$ and the reconciled forecast  $\tilde{\bm{y}}$.
-A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ is minimal for over any possible $\tilde{\bm{y}}\in\mathfrak{s}$.
-In this sense reconciliation via orthogonal projection leads to the smallest possible adjustments of the base forecasts.
-
-	The second property introduced above has been the focus of theoretical results in the forecast reconciliation literature.
-He we provide a more streamlined version of proofs by \cite{VanErven2015a} and \cite{Wickramasuriya2017} before providing geometrical intuition aimed at simplifying the reader's understanding of these proofs.
-
-	Consider the Euclidean distance between a forecast and the target.
-This is equivalent to the root of the sum of squared errors over the entire hierarchy.
-Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$, and let $\|\bm{v}\|_2$ be the $L_2$ norm of vector $\bm{v}$.
-The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.
-
-	\begin{theo}[Distance reducing property]\label{th:distred}
-		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
-		\begin{equation}
-		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
-		\end{equation}
-	\end{theo}
-	\begin{proof}
-		Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ since $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$.
-Therefore,
-		\begin{align}
-		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
-		&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
-		\end{align}
-		The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators \citep{Hun2001}, therefore
-		\begin{equation*}
-		\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le
-		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
-		\end{equation*}
-	\end{proof}
-	The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.
-
-	\todo{compare to van Erven and Wickremasuriya more explictly}
-
-	The simple geometric intuition behind the proof is demonstrated in Figure~\ref{fig:Schematic_OLSRecon}.
-In this schematic, the coherent subspace is depicted as a black arrow.
-The base forecast $\hat{\bm{y}}$ is shown as a blue dot.
-Since $\hat{\bm{y}}$ is incoherent it does not lie in $\mathfrak{s}$.
-Reconciliation is an orthogonal projection from $\hat{\bm{y}}$ to the coherent subspace yielding the reconciled forecast $\tilde{\bm{y}}$ shown in red.
-Finally, the target of the forecast $\bm{y}$ is displayed as a black point, and although its exact location is unknown to the forecaster, it is known that it will lie somewhere along the coherent subspace.
-
-	\begin{figure}[H]
-		\centering
-		\vspace{-0.9cm}
-		\tiny
-		\resizebox{\linewidth}{!}{\input{Figs/orth_pointforerec_schematic}}
-		\label{fig:Schematic_OLSRecon}
-		\caption{$\hat{\bm{y}}$ is orthogonally projected onto $\mathfrak{s}$}
-
-	\end{figure}
-
-	Figure~\ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle with $\tilde{y}$ at the right-angled vertex.
-In this triangle the line between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.
-As such reconciliation is guaranteed to reduce the squared error of the forecast.
-\todo{Do we just include this as the proof rather than the existing proof to 3.1}
-
-    Theorem~\ref{th:distred} is in some ways more powerful than perhaps previously understood.
-It is often stated in terms of expectations\todo{check other proofs}.
-However, the distance reducing property will hold for any realisation and any forecast and not just on average.
-Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.
-
-    However, in other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood.
-First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.
-In particular, this measure is the root of the sum of squared errors of {\em all} variables in the hierarchy.
-As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to worse forecasts for individual series.
-Second, although orthogonal projections are guaranteed to improve on base forecasts, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.
-As such referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT.
-It is to oblique projections that we now turn our attention.
-
-	\subsection{Oblique Projections}
-
-	One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the root of the sum of squared errors of {\em all} variables in the hierarchy.
-A clear shortcoming of this measure of forecast accuracy is that forecasts errors in all series should not necessarily be treated equally.
-For example, in hierarchies, top-level series tend to have a much larger scale than bottom level series.
-Even when two series are on a similar scale, series that are more predictable or less variable will tend to be downweighted by simply aggregating square errors.
-An even more sophisticated understanding may take the correlation between series into account.
-All of these considerations lead towards reconciliation of the form $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, where $\bm{W}$ is a symmetric matrix.
-Generally, it is assumed that $\bm{W}$ is invertible, otherwise a pseudo inverse can be used.
-
-	It should be noted that  $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix.
-However this matrix can be considered to be an orthogonal projection for a different geometry, namely the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
-One way to understand this geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$.
-This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{-1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{-1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{-1/2}\tilde{\bm{y}}$.
-The transformed reconciled forecast results from an orthogonal projection in the transformed space since
-
-	\begin{align}
-	\tilde{\bm{y}}^*&=\bm{W}^{-1/2}\tilde{\bm{y}}\\&=\bm{W}^{-1/2}\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}
-	\\&=\bm{S}^*\left(\bm{S}^{*'}\bm{S}^*\right)^{-1}\bm{S}^{*'}\hat{\bm{y}^*}
-	\end{align}
-
-	Another way of understanding the generalised Euclidean geometry is that it is defined by the norm $\bm{v}'\bm{W}^{-1}\bm{v}$.
-This interpretation is quite instructive when it comes to thinking about the connection between distances and loss functions.
-In the generalised Euclidean geometry, the distance between the reconciled forecast and the realisation is given by $(\hat{\bm{y}}-\bm{y})'\bm{W}^{-1}(\hat{\bm{y}}-\bm{y})$.
-For diagonal $\bm{W}$ this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix this is equivalent to a Mahalanobis distance.
-As such Theorem~\ref{th:distred} can easily be generalised.
-If the objective function is some weighted sum of squared errors, or a Mahalanobis distance, then the projection matrix $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts, for an appropriately selected $\bm{W}$.
-
-	\subsection{MinT}
-
-	While the properties discussed so far hold for any projection matrix, the MinT method of \cite{Wickramasuriya2017} has an additional optimality property.
-\cite{Wickramasuriya2017} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by an oblique projection with a particular choice of $\bm{W}$.
-This choice is that $\bm{W}$ should be the forecast error covariance matrix where errors come from using the base forecasts.
-Although the base forecast error covariance matrix is unknown, it can be estimated using in-sample errors.
-
-	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.
-Suppose the in-sample errors are given by the orange points.
-They provide information on the most likely direction of large deviations from the coherent subspace.
-This direction is denoted by $\bm{R}$.
-Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).
-One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.
-An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection.
-Imagining a similar oblique projection along $\bm{R}$ for all the grey points yield reconciled forecasts tightly packed near the target $\bm{y}$.
-In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts.\todo{needs picture with all points projected obliquely then orthogonally}.
-
-	\begin{figure}[H]
-		\centering
-		%\vspace{-0.9cm}
-		\small
-		\resizebox{\linewidth}{!}{
-			\input{Figs/insampledir}
-		}
-		\caption{A schematic to represent MinT reconciliation.
-Points in orange colour represent the insample errors.
-$\bm{R}$ shows the most likely direction of deviations from the coherent subspace.
-$\hat{\bm{y}}$ is projected onto $\mathfrak{s}$ along the the direction of $\bm{R}$.}\label{fig:MinT_justification1}
-	\end{figure}
-
-	\begin{figure}[H]
-		\centering
-		%\vspace{-0.9cm}
-		\small
-		\resizebox{\linewidth}{!}{
-			\input{Figs/oblique_justification2}
-		}
-		\caption{A schematic to represent MinT reconciliation.
-Grey points indicate potential realisations of the base forecast while the blue dot indicates one such realisation.
-The black dot ${\bm y}$ denotes the (unknown) target of the forecast.}\label{fig:MinT_justification2}
-	\end{figure}
-
-	\begin{figure}[H]
-		\centering
-		%\vspace{-0.9cm}
-		\small
-		\resizebox{\linewidth}{!}{
-			\includegraphics{Figs/OrthProj.pdf}}
-		\caption{\textcolor{red}{include caption}}\label{fig:Orthogonal_projection}
-	\end{figure}
-
-	\begin{figure}[H]
-	\centering
-	%\vspace{-0.9cm}
-	\small
-	\resizebox{\linewidth}{!}{
-		\includegraphics{Figs/ObliqueProjection.pdf}}
-	\caption{\textcolor{red}{include caption}}\label{fig:Oblique_projection}
-	\end{figure}
-
-%		\begin{figure}[H]
-%		\centering
-%		%\vspace{-0.9cm}
-%		\small
-%		\resizebox{\linewidth}{!}{
-%			\input{Figs/ObliqueProjection}
-%		}
-%		\caption{\textcolor{red}{write caption}}\label{fig:Oblique_projection}
-%	\end{figure}
-
-%\begin{figure}
-%	\centering
-%	\begin{subfigure}{0.47\textwidth}
-%		\resizebox{\linewidth}{!}{
-%			\input{Figs/Orth.proj.tex}}
-%		\caption{bla bla}
-%	\end{subfigure}
-%	\begin{subfigure}{0.47\textwidth}
-%		\resizebox{\linewidth}{!}{
-%			\input{Figs/ObliqueProjection.tex}}
-%			\caption{bla bla}
-%	\end{subfigure}
-%\end{figure}
-
-	\section{Bias in forecast reconciliation}
-
-	Before turning our attention to the issue of bias itself it is important to state a sensible property that any reconciliation method should have.
-That is if base forecasts are already coherent then reconciliation should not change the forecast.
-As stated in Section~\ref{sec:Reconciliation}, this property holds only when $\bm{SG}$ is a projection matrix.
-As a corollary, reconciling using an arbitrary $\bm{G}$,  may in fact change an already coherent forecast.
-
-	The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation \todo{reference Shanika and maybe van Erven Culigari}.
-Before restating this proof using a  clear geometric interpretation we discuss in a precise fashion what is meant by unbiasedness.
-
-	Suppose that the target of a point forecast is $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ where the expectation is taken over the predictive density.
-Our point forecast can be thought of as an estimate of this quantity.\todo{or do we want to define unbiasedness of a forecast as the expected value of the forecast equals realisation?}  The forecast is random due to uncertainty in the training sample and it is with respect to this uncertainty that unbiasedness refers.
-More concretely, the point forecast will be unbiased if $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
-
-	\begin{theo}[Unbiasedness preserving property]
-		For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also an unbiased prediction as long as $\bm{SG}$ is a projection onto $\mathfrak{s}$.
-	\end{theo}
-	\begin{proof}
-		The expected value of the reconciled forecast is given by
-		\[
-		\E_{1:t}(\tilde{\bm{y}}_{t+h|t})
-		= \E_{1:t}(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t})
-		= \bm{S}\bm{G}\E_{1:t}(\hat{\bm{y}}_{t+h|t})
-		= \bm{S}\bm{G}\bm{\mu}_{t+h|t}.
-		\]
-		Since $\bm{\mu}_{t+h|t}$ is an expectation taken with respect to the degenerate predictive density it must lie in $\mathfrak{s}$.
-We have already established that when $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$ then it maps all vectors in $\mathfrak{s}$ onto themselves.
-As such $\bm{S}\bm{G}\bm{\mu}_{t+h|t}=\bm{\mu}_{t+h|t}$ when $\bm{S}\bm{G}$ is a projection matrix.
-	\end{proof}
-
-	We note that the above result holds when the projection $\bm{SG}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general.
-To describe this more explicitly suppose $\bm{SG}$ has as its image  $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e.
-$\mathfrak{L}\subset\mathfrak{s}$.
-Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$,  $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$.
-This is depicted in Figure~\ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.
-In this case, the expectation of reconciled forecast will be $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and hence biased.
-
-	This result has implications in practice. The top-down method \citep{Gross1990} has 
-	\begin{equation}\label{eq:top-downG}
-	\bm{G}=\begin{pmatrix}
-	\bm{p} & \bm{0}_{(m \times n-1)}
-	\end{pmatrix}
-	\end{equation}
-    where $\bm{p} = (p_1,\dots,p_m)'$ is an $m$-dimensional vector consisting a set of proportions used to disaggregate the top-level forecast.
-In this case it can be verified that $\bm{SG}$ is idempotent, i,e.
-$\bm{SGSG}=\bm{SG}$ and therefore $\bm{SG}$ is a projection matrix.
-However the image of this projection is not an $m$-dimensional subspace but a $1$-dimensional subspace.
-As such, top-down reconciliation produces biased forecasts even when the base forecasts are unbiased.
-
-	\begin{figure}[H]
-		\centering
-		\vspace{-0.9cm}
-		\small
-		\resizebox{\linewidth}{!}{
-			\input{Figs/Schem_3D}
-		}
-		\caption{$\mathfrak{L}$ is a linear subspace of the coherent subspace $\mathfrak{s}$.
-If $s\circ g$ is a projection not onto $\mathfrak{s}$ but onto $\mathfrak{L}$, then $\bm{\mu} \in \mathfrak{s}$ will be moved to $\bar{\bm{\mu}} \in \mathfrak{L}$.}\label{fig:Schematic_3D}
-	\end{figure}
-
-	Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.
-Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix.
-\todo{perhaps elaborate in a proof in appendix}  However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$.
-This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.
-However, equipped with a geometric understanding of the problem, we would advise against this approach.
-The constraint $\bm{GS}=\bm{I}$  is not just about bias and dropping the constraint compromises all of the attractive properties of projections.
-Our own solution to dealing with biased forecasts is to bias correct, or translate the forecast prior to reconciling via projections.
-It is to this approach that we now turn our attention.
-
-%	Representation of a coherent subspace in a three dimensional hierarchy where $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$.
-The coherent subspace is depicted as a gray two dimensional plane labelled $\mathfrak{s}$.
-Note that the columns of $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ form a basis for $\mathfrak{s}$.
-The red points lying on $\mathfrak{s}$ can be either realisations or coherent forecasts.
-
-	\section{Bias correction}
-
-	Our approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
-	}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.
-This can be then subtracted from future forecasts.
-As stated in the discussion of MinT, in-sample errors are already used to estimate the optimal direction of projection.
-As such we see no problems with using the same errors to bias correct.
-Geometrically, the intuition is simple.
-In Figure~\ref{fig:MinT_justification1}, the orange points are centered around the origin as would be expected from an unbiased forecast.
-If forecasts are biased, then errors should simply be translated until they are centered at the origin.
-
-	\section{Application}
-
-	\section{Conclusions}
-
-	\newpage
-
-	\bibliographystyle{agsm}
-
-	\bibliography{References_paper1}
-
-\end{document}
+\end{table}

### 2019-08-12 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Adjusted the table in Appendix

@@
 \usepackage{url} % not crucial - just used below for the URL 
-
+\usepackage{floatpag}
+\usepackage{lipsum}
 \usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx,paralist}
@@
 		\centering\tabcolsep=0.08cm
-
 		\resizebox{\linewidth}{!}{
@@
 	These new geometric interpretations of hierarchical forecast reconciliation facilitate extensions of the problem to a probabilistic framework. We leave this discussion into a different paper.
+
 	\newpage
 	\section{Appendix}
+	\thisfloatpagestyle{empty}
+	\input{Appendix}
 
-	\begin{table} 
-		\caption{Geographical hierarchy of Australian tourism flow}\label{table:A1}
-
-		\resizebox{\linewidth}{!}{
-			\begin{tabular}{lllllllllll}
-				\toprule
-				\multicolumn{3}{c}{\textbf{Level 0 - Total}}   &  &  \multicolumn{3}{l}{\textit{Zones cont.}}   &  & \multicolumn{3}{l}{\textit{Regions cont.}} \\
-				\cmidrule(lr){1-3}
-				1 & {\text{Tot}} & {Australia} &  & 48  & AED & Blue Mountains && 99 & FAA & Hobert and South\\
-				\cmidrule(lr){1-3}
-				\multicolumn{3}{c}{\textbf{Level 1 - States}}  &  & 49  & AFA & Canberra  && 100 & FBA & East Coast\\
-				\cmidrule(lr){1-3}
-				2 & A & NSW 				&  & 50  & BAA & Melbourne && 101 & FBB & Launceston, Tamar \& North\\
-				3 & B & Victoria 			&  & 51  & BAB & Peninsula && 102 & FCA & North West\\
-				4 & C & Queensland 			&  & 52  & BAC & Geelong && 103 & FCB& Wilderness West\\
-				5 & D & South Australia     &  & 53  & BBA & Western && 104 & GAA& Darwin\\
-				6 & E & Western Australia   &  & 54  & BCA & Lakes && 105 & GAB& Kakadu Arnhem\\
-				7 & F & Tasmania   			&  & 55  & BCB & Grippsland && 106 & GAC& Katherine Daly\\
-				8 & G & Northern Territory &  &  56  & BCD & Phillip Island && 107 & GBA& Barkly\\
-				\cmidrule(lr){1-3} 
-				\multicolumn{3}{c}{\textbf{Level 2 - Zones}}  &  &  57  & BDA & Central Murray && 108 & GBB& Lasseter\\
-				\cmidrule(lr){1-3}
-				9 	& AA & Metro NSW 	  	   	&  & 58  & BDB & Goulburn && 109 & GBC& Alice Springs\\
-				10 	& AB & North Coast NSW 	   	&  & 59  & BDC & High Country && 110 & GBD& MacDonnell\\
-				11	& AC & South Coast NSW	   	&  & 60  & BDD & Melbourne East &&&&\\
-				12	& AD & South NSW 			&  & 61  & BDE & Upper Yarra &&&& \\
-				13	& AE & North NSW 			&  & 62  & BDF & Murray East &&&&\\
-				14	& AC & ACT					&  & 63  & BEA & Wimmera+Mallee &&&&\\
-				15	& BA & Metro VIC			&  & 64  & BEB & Western Grampians &&&&\\ 		
-				16	& BB & West Coast VIC		&  & 65  & BEC & Bendigo Loddon &&&&\\
-				17	& BC & East Coast VIC		&  & 66  & BED & Macedon &&&&\\ 
-				18	& BC & North East VIC		&  & 67  & BEE & Spa Country &&&&\\ 
-				19	& BD & North West VIC		&  & 68  & BEF & Ballarat &&&&\\
-				20  & CA & Metro QLD			&  & 69  & BEG & Central Highlands &&&&\\
-				21  & CB & Central Coast QLD	&  & 70  & CAA & Gold Coast &&&&\\
-				22  & CC & North Coast QLD		&  & 71  & CAB & Brisbane &&&&\\
-				23  & CD & Inland QLD			&  & 72  & CAC & Sunshine Coast &&&&\\
-				24	& DA & Metro SA				&  & 73  & CBA & Central Queensland &&&&\\	
-				25	& DB & South Coast SA		&  & 74  & CBB & Bundaberg &&&&\\	
-				26	& DC & Inland SA			&  & 75  & CBC & Fraser Coast &&&&\\	
-				27	& DD & West Coast SA		&  & 76  & CBD & Mackay &&&&\\
-
-				28	& EA & West Coast WA 	& & 77  & CCA & Whitsundays &&&&\\	
-				29	& EB & North WA			& & 78  & CCB & Northern &&&&\\	
-				30	& EC & South WA 		& & 79  & CCC & Tropical North Queensland &&&&\\	
-				31	& FA & South TAS		& & 80  & CDA & Darling Downs &&&&\\
-				32	& FB & North East TAS	& & 81  & CDB & Outback &&&&\\	
-				33	& FC & North West TAS	& & 82  & DAA & Adelaide &&&&\\
-				34	& GA & North Coast NT	& & 83  & DAB & Barossa &&&&\\
-				35	& GB & Central NT		& & 84  & DAC & Adelaide Hills &&&&\\
-				\cmidrule(lr){1-3}
-				\multicolumn{3}{c}{\textbf{Level 2 - Regions}} & & 85  & DBA & Limestone Coast &&&&\\
-				\cmidrule(lr){1-3}
-				36	& AAA & Sydney 			& 	& 86  & DBB & Fleurieu Peninsula &&&&\\
-				37	& AAB & Central Coast	&	& 87  & DBC & Kangaroo Island &&&&\\
-				38  & ABA & Hunter 			& 	& 88  & DCA & Murraylands &&&&\\
-				39  & ABB & North Coast NSW & 	& 89  & DCB & Riverland &&&&\\
-				40  & ABC & Hunter			& 	& 90  & DCC & Clare Valley &&&&\\
-				41  & ACA & South Coast		& 	& 91  & DCD & Flinders Range and Outback &&&&\\
-				42  & ADA & Snowy Mountains & 	& 92  & DDA & Eyre Peninsula &&&&\\
-				43  & ADB & Capital Country & 	& 93  & DDB & Yorke Peninsula &&&&\\
-				44  & ADC & The Murray 		& 	& 94  & EAA & Australia's Coral Coast &&&&\\
-				45  & ADD & Riverina 		& 	& 95  & EAB & Experience Perth &&&&\\
-				45  & AEA & Central NSW 	& 	& 96  & EAC & Australia's South West &&&&\\
-				46  & AEB & New England North West &  & 97  & EBA & Australia's North West &&&&\\
-				47  & AEC & Outback NSW & & 98  & ECA & Australia's Golden Outback &&&&\\
-				\bottomrule
-			\end{tabular}
-		}
-	\end{table}
 	\newpage

### 2019-08-15 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Minor rewriting

@@
      	\caption{Depiction of a three dimensional hierarchy with $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$.
-The gray colour two dimensional plane reflects the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that spans $\mathfrak{s}$.
-The points in $\mathfrak{s}$ represents realisations or coherent forecasts}\label{fig:3D_hierarchy}
+The gray coloured two dimensional plane depicts the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that spans $\mathfrak{s}$.
+The red points in $\mathfrak{s}$ represent realisations or coherent forecasts}\label{fig:3D_hierarchy}
      \end{figure}
@@
 	\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
-		Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a vector of point forecasts of all series in the hierarchy at time $t+h$, made using information up to and including time $t$.
+		Let $\breve{\bm{y}}_{t+h|t} \in \mathbb{R}^n$ be a vector of point forecasts of all series in the hierarchy where the subscript $t+h|h$ implies that the forecast is made as time $t$ for a period $h$ steps into the future.
 Then $\breve{\bm{y}}_{t+h|t}$ is \emph{coherent} if $\breve{\bm{y}}_{t+h|t} \in \mathfrak{s}$.
@@
 	The problem of forecast reconciliation is predicated on there being an $n$-vector of forecasts that are incoherent.
-We will call these {\em base forecasts} and denote them as $\hat{\bm{y}}_{t+h|h}$, where the subscript $t+h|h$ implies that the forecast is made as time $t$ for a period $h$ steps into the future.
+We will call these {\em base forecasts} and denote them as $\hat{\bm{y}}_{t+h|h}$.
 In the sequel, this subscript will be dropped at times for ease of exposition.
@@
 	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix onto $\mathfrak{s}$.
-In general a projection matrix has the idemoptence property, i.e.
+In general a projection matrix is defined via the idemoptence property, i.e.
 $\bm{SG}^2=\bm{SG}$.
-However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped onto itself by that projection.
-This is a fundamental property of projections and also proved in lemma 2.4 in \citet{rao1974}.
-In our context this means that for any $\bm{v}\in\mathfrak{s}$, $\bm{SGv}=\bm{v}$.
+However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped to itself by that projection \citep[see Lemma 2.4 in][for a proof]{rao1974}.
+In our context this implies that for any $\bm{v}\in\mathfrak{s}$, $\bm{SGv}=\bm{v}$.
 
@@
 We refrain from any discussion of regression models focusing instead on geometric interpretations.
-However the connection between OLS and orthogonal projection should be clear, in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection of the data onto the span of the regressors.
+However the connection between OLS and orthogonal projection should be clear, in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection of the response onto the span of the regressors.
 
@@
 the base and reconciled forecast should be `close'.
-The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value that is targeted by the forecast.
+The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value targeted by the forecast.
 
@@
 The discussion in that paper focuses on the case of MinT.
-Here we provide a new explicit proof of that result first in the case of an orthogonal projection where the geometric intuition of the proof is clear and then generalise the result to reconciliation by any projection matrix in Section~\ref{sec:oblique}.
+Here we provide a new explicit proof of that result.
+We do so first in the case of an orthogonal projection where the geometric intuition of the proof is clear and then generalise the result to reconciliation using any projection matrix in Section~\ref{sec:oblique}.
 
@@
 		\resizebox{\linewidth}{!}{\input{Figs/orth_pointforerec_schematic}}
-		\caption{$\hat{\bm{y}}$ is orthogonally projected onto $\mathfrak{s}$}
+		\caption{Orthogonal projection of $\hat{\bm{y}}$ onto $\mathfrak{s}$ yielding the reconciled forecast $\tilde{\bm{y}}$}
 
@@
 
-	It should be noted that  $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix.
-However this matrix can be considered to be an orthogonal projection for a different geometry, namely the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
+	It should be noted that  $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix in the usual Euclidean geometry.
+However this matrix can be considered to be an orthogonal projection for a different geometry defined by the norm $||\bm{v}||_{{\bm W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, which we will call the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
 One way to understand this geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$.
@@
 
-	Another way of understanding the generalised Euclidean geometry is that it is defined by the norm $\bm{v}'\bm{W}^{-1}\bm{v}$.
-This interpretation is quite instructive when it comes to thinking about the connection between distances and loss functions.
+	Thinking of the problem in terms of a geometry defined by the norm $\bm{v}'\bm{W}^{-1}\bm{v}$ is also quite instructive when it comes to thinking about the connection between distances and loss functions.
 In the generalised Euclidean geometry, the distance between the reconciled forecast and the realisation is given by $(\hat{\bm{y}}-\bm{y})'\bm{W}^{-1}(\hat{\bm{y}}-\bm{y})$.
-For diagonal $\bm{W}$, this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix, this is equivalent to a Mahalanobis distance.
+For diagonal $\bm{W}^{-1}$, this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix, this is equivalent to a Mahalanobis distance.
 As such Theorem~\ref{th:distred} can easily be generalised as follows:
@@
 	\begin{theo}[General distance reducing property]\label{th:gdistred}
-        If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the generalised Euclidean sense) projection onto $\mathfrak{s}$ and let $\|\bm{v}\|_{\bm{W}}$ be the $L_2$ norm (in the generalised Euclidean sense with respect to $\bm{W}$) of vector $\bm{v}$ then:
+        If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the generalised Euclidean sense) projection onto $\mathfrak{s}$ then:
 		\begin{equation}
-		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{\bm W}\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{\bm W}.
+		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{{\bm W}^{-1}}\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{{\bm W}^{-1}}.
 		\end{equation}
@@
 If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts.
+
+	{\bf Discuss results in Figure 11 here}
 
@@
 In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts.
-In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal is expectation.
+In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal in expectation.
 
@@
 The constraint $\bm{GS}=\bm{I}$  is not just about bias and dropping the constraint compromises all of the attractive properties of projections.
-Our own solution to dealing with biased forecasts is to bias correct, or translate the forecast prior to reconciling via projections.
-It is to this approach that we now turn our attention.
+Opening the door to reconciliation methods that change already coherent base forecast would seem to suggest an increase in the variability of the forecast.
+This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance is to reduce variance.
 
-%	Representation of a coherent subspace in a three dimensional hierarchy where $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$.
-The coherent subspace is depicted as a gray two dimensional plane labelled $\mathfrak{s}$.
-Note that the columns of $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ form a basis for $\mathfrak{s}$.
-The red points lying on $\mathfrak{s}$ can be either realisations or coherent forecasts.
+	Our own solution to dealing with biased forecasts is to bias correct {\em before} reconciliation.
+In many cases the method for bias correction will be context specific.
+For instance, in  our empirical study in Section~\ref{sec:EmpStudy} we consider a scenario where bias is induced via taking a Box-Cox transformation before modelling.
+In this well-known case a number of bias correction methods exist.
+Our particular choice of bias correction will be the Guererro method \citep{guerrero1993time}.
 
-	\section{Bias correction} \label{sec:BiasCorrection}
-	\todo{Need to discuss and rewrite this section since we are using different bias correction method in the empirical study}
-	Our approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
+	Alternatively, a more general purpose approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
 	}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.

### 2019-08-17 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
new first paragraph

@@
 	\section{Introduction}\label{sec:intro}
+
+	The past decade has seen rapid development in methodology for forecasting time series that adhere to linear aggregation constraints.
+Of particular prominence have been {\em forecast reconciliation} methods involving two steps; first separate forecasts are produced for all series, then these are adjusted ex post to ensure coherence with the linear constraints.
+Forecast reconciliation has mostly been formulated as a regression model, see \cite{Hyndman2011} and \cite{WicEtAl2019} for examples.
+This setup can be counter-intuitive since a vector of forecasts coming from different time series models is also assumed to be the dependent variable in a regression model.
+In this paper, we eschew a regression interpretation in favour of a novel, geometric understanding of forecast reconciliation.
+In doing so, we review and provide clearer insight into existing approaches, and achieve a clearer understanding of the interplay between forecasts bias and reconciliation methods.
 

### 2019-08-17 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
background in intro

@@
 
-	A collection of multiple time series with some aggregation structure arises in many disciplines such as manufacturing, engineering, marketing, medicine, etc.
-These are often known as hierarchical time series.
-Making coherent forecasts for these series that are in line with the inherent aggregation constraints is an essential requirement for decision making.
-Early studies on this literature use a single level forecasting approaches.
-That is, forecasting the series in a single level of the hierarchy and then aggregate or disaggregate these forecasts to get coherent forecasts for remaining series.
-The well known Bottom-up \citep{Dunn1976} and Top-down \citep{Gross1990, Athanasopoulos2009} methods are examples for these traditional methods.
-Multiple studies also discuss the relative advantages and disadvantages of these methods, for example, \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.
+	Multivariate time series that follow an aggregation structure arise in many disciplines such as manufacturing, engineering, marketing and medicine\todo{include references}.
+Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making.
+Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom up fashion \citep{Dunn1976} or disaggregating in a Top-down \citep{Gross1990, Athanasopoulos2009} fashion.
+For reviews of these approaches see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.
 
-	A shortcoming of these traditional methods is that they do not use all the information available in the hierarchy to make coherent forecasts.
-To overcome this issue, \cite{Hyndman2011} propose to utilise all the information available in the hierarchy via a ``Reconciliation" process.
-This is a two-stages process where the first stage involves making forecasts for all series in the hierarchy without considering the aggregation constraints (also known as base forecasts), which is then followed by the reconciliation stage that combines these forecasts imposing the aggregation constraints of the hierarchy.
-A later study by \cite{WicEtAl2019} proposed to optimally combine the base forecasts by minimising the trace of the mean squared errors of reconciled forecasts where they derived an analytical solution to produce reconciled forecasts.
-An important feature of this method is that it imposes the correlation structure of the whole hierarchy to produce reconciled point forecasts.
+	In contrast to these approaches \cite{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as {\em base} forecasts.
+Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could be improved via further adjustment.
+A framework was proposed whereby the forecasts were assumed to follow a regression model.
+The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts.
+This approach and later modifications have subsequently been shown to outperform bottom up and top down approaches in a variety of empirical settings\todo{references}.
+
+	Some theoretical insight into the good performance of forecast reconciliation methods has been provided by \cite{VanErven2015a} and \cite{WicEtAl2019}.
+Both papers provide a proof that reconciliation is guaranteed to improve base forecasts.
+The latter paper also proposes a particular version of reconciliation known as the Minimum Trace (MinT) method.
+This is optimal in the sense of minimising the trace of reconciled forecast error covariance matrix under the assumption that base forecasts are unbiased.
 

### 2019-08-17 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
first draft intro

@@
 
-	The past decade has seen rapid development in methodology for forecasting time series that adhere to linear aggregation constraints.
+	The past decade has seen rapid development in methodology for forecasting time series that follow a hierarchical aggregation structure.
 Of particular prominence have been {\em forecast reconciliation} methods involving two steps; first separate forecasts are produced for all series, then these are adjusted ex post to ensure coherence with the linear constraints.
-Forecast reconciliation has mostly been formulated as a regression model, see \cite{Hyndman2011} and \cite{WicEtAl2019} for examples.
-This setup can be counter-intuitive since a vector of forecasts coming from different time series models is also assumed to be the dependent variable in a regression model.
+Forecast reconciliation has mostly been formulated using a regression model, see \cite{Hyndman2011} and \cite{WicEtAl2019} for examples.
+This setup can be counter-intuitive since a vector comprised of forecasts from different time series models is also assumed to be the dependent variable in a regression model.
 In this paper, we eschew a regression interpretation in favour of a novel, geometric understanding of forecast reconciliation.
@@
 
-	Multivariate time series that follow an aggregation structure arise in many disciplines such as manufacturing, engineering, marketing and medicine\todo{include references}.
+	Multivariate time series following an aggregation structure arise in many disciplines such as manufacturing, engineering, marketing and medicine\todo{include references}.
 Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making.
 Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom up fashion \citep{Dunn1976} or disaggregating in a Top-down \citep{Gross1990, Athanasopoulos2009} fashion.
-For reviews of these approaches see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.
+For reviews of these approaches including a discussion of their advantages and disadvantages see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.
 
 	In contrast to these approaches \cite{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as {\em base} forecasts.
-Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could be improved via further adjustment.
-A framework was proposed whereby the forecasts were assumed to follow a regression model.
+Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could thus be improved via further adjustment.
+A framework was proposed whereby the base forecasts were assumed to follow a regression model.
 The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts.
@@
 
-	Some theoretical insight into the good performance of forecast reconciliation methods has been provided by \cite{VanErven2015a} and \cite{WicEtAl2019}.
+	Some theoretical insight into the performance of forecast reconciliation methods has been provided by \cite{VanErven2015a} and \cite{WicEtAl2019}.
 Both papers provide a proof that reconciliation is guaranteed to improve base forecasts.
@@
 
-	While reviewing the existing studies in this literature, our attempt is to give a new understanding to the whole hierarchical forecasting problem with a geometric intuition.
-We first provide a geometric interpretation of coherency and reconciliation in terms of projections.
-Then we rehash all existing reconciliation methods into a single framework based on projections.
-In addition to being highly intuitive, this allows us to establish new theoretical results.
-We prove two new theorems about point forecast reconciliation, the first showing that reconciled forecasts dominate unreconciled forecasts via the distance reducing property of projections while the second shows that reconciliation via projections preserves the unbiasedness of base forecasts.
+	Our main contribution is to propose a geometric interpretation of the entire hierarchical forecasting problem.
+In this setting, we show that reconciled forecasts will have a number of attractive properties when they are obtained via projections.
+We believe that this is clearer and more intuitive than explanations based on regression modelling, notwithstanding the fact that most popular existing methods are indeed projections.
+As such, this paper is in part a review of existing results cast in a new light, one that we believe to be warranted as forecast reconciliation methodologies becomes more popular.
+However, we also propose three major and novel results.
 
-	Unbiasedness of base forecasts is a strong assumption in many of the existing methods which will be limited only to a selective number of forecasting methods.
-We propose a simple solution to this barrier.
-That is to correct the bias in base forecasts before doing the projection-based reconciliation.
-This allows using any advanced statistical method despite the unbiasedness to produce base forecasts without worrying about the unbiasedness.
-Using an empirical study, we further show that the reconciled forecasts follow from biased corrected base forecasts will improve the forecast accuracy compared to that of the biased forecasts.
+	First, our approach makes it clear that the defining characteristic of so-called {\em hierarchical time series} is not aggregation but linear constraints.
+As a result forecast reconciliation can be applied in contexts where there are no clear candidates of {\em bottom level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling.
+Second, we provide a new proof that reconciled forecasts dominate unreconciled forecasts which makes explicit the link between a reconciliation method and a loss function.
+We believe that this link is lacking in previous work that attempt to establish similar results, in particular \cite{VanErven2015a} and \cite{WicEtAl2019}.
+Futhermore, unlike \cite{VanErven2015a} and \cite{WicEtAl2019} our proof does not require an assumption about convexity.
+Third, we revisit the issue of bias.
+We prove that reconciliation using certain projection matrices will guarantee reconciled forecasts will be unbiased if base forecasts are also unbiased.
+A natural question that arises is what to do in the case of biased reconciled forecasts.
+Rather than addressing this issue by considering matrices that are not projections, we propose to bias-correct before reconciliation.
+This is evaluated in an extensive empirical study where we find that even when bias correction fails, the extent of the problem is mitigated by reconciling forecasts.
 
 	The remainder of this paper is structured as follows.
-In Section~\ref{sec:CoheForecasts} coherent point forecasting is defined geometrically while section~\ref{sec:Reconciliation} contains definitions of projection-based reconciliation as well as our main theoretical results.
-Section~\ref{sec:BiasInRecon} discuss the unbiased preserving property of projection-based reconciliation and Section \ref{sec:BiasCorrection} contains our proposed method to correct the bias in base forecasts.
-In Section \ref{sec:EmpStudy} we apply these methods to get coherent forecasts for domestic tourism flow in Australia and Section~\ref{sec:conclusions} concludes with some discussion and thoughts on future research.
+Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines so called hierarchical time series in a way that does not depend on any notion of bottom level series.
+Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projection and includes our proof that reconciled forecasts is guaranteed to dominate base forecasts with respect to a specific loss function.
+In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose method for bias correction.
+In Section \ref{sec:EmpStudy} we evaluate these methods for in an extensive emprirical application to domestic tourism flow in Australia.
+Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the  future of research in forecast reconciliation.
 \section{Coherent forecasts}\label{sec:CoheForecasts}

### 2019-08-17 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
polished intro

@@
 
-	The past decade has seen rapid development in methodology for forecasting time series that follow a hierarchical aggregation structure.
-Of particular prominence have been {\em forecast reconciliation} methods involving two steps; first separate forecasts are produced for all series, then these are adjusted ex post to ensure coherence with the linear constraints.
+	The past decade has seen rapid development in methodologies for forecasting time series that follow a hierarchical aggregation structure.
+Of particular prominence have been {\em forecast reconciliation} methods involving two steps; first separate forecasts are produced for all series, then these are adjusted ex post to ensure coherence with aggregation constraints.
 Forecast reconciliation has mostly been formulated using a regression model, see \cite{Hyndman2011} and \cite{WicEtAl2019} for examples.
@@
 In this paper, we eschew a regression interpretation in favour of a novel, geometric understanding of forecast reconciliation.
-In doing so, we review and provide clearer insight into existing approaches, and achieve a clearer understanding of the interplay between forecasts bias and reconciliation methods.
+This allows us to develop novel proofs and a clearer understanding of the interplay between forecast bias and reconciliation methods.
 
@@
 Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making.
-Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom up fashion \citep{Dunn1976} or disaggregating in a Top-down \citep{Gross1990, Athanasopoulos2009} fashion.
+Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom up fashion \citep{Dunn1976} or disaggregating in a top-down fashion \citep{Gross1990, Athanasopoulos2009}.
 For reviews of these approaches including a discussion of their advantages and disadvantages see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.
 
-	In contrast to these approaches \cite{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as {\em base} forecasts.
+	In contrast to these methods, \cite{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as {\em base} forecasts.
 Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could thus be improved via further adjustment.
@@
 In this setting, we show that reconciled forecasts will have a number of attractive properties when they are obtained via projections.
-We believe that this is clearer and more intuitive than explanations based on regression modelling, notwithstanding the fact that most popular existing methods are indeed projections.
-As such, this paper is in part a review of existing results cast in a new light, one that we believe to be warranted as forecast reconciliation methodologies becomes more popular.
-However, we also propose three major and novel results.
+We believe that this is clearer and more intuitive than explanations based on regression modelling, notwithstanding the fact that regression based-methods themselves are indeed projections.
+As such, this paper is in part a review of existing results cast in a new light, but one that we believe to be warranted as forecast reconciliation methodologies have become more popular.
+In addition, we also propose three major and novel results.
 
@@
 Second, we provide a new proof that reconciled forecasts dominate unreconciled forecasts which makes explicit the link between a reconciliation method and a loss function.
-We believe that this link is lacking in previous work that attempt to establish similar results, in particular \cite{VanErven2015a} and \cite{WicEtAl2019}.
+We believe that this link is lacking in previous work that attempts to establish similar results, in particular \cite{VanErven2015a} and \cite{WicEtAl2019}.
 Futhermore, unlike \cite{VanErven2015a} and \cite{WicEtAl2019} our proof does not require an assumption about convexity.
 Third, we revisit the issue of bias.
-We prove that reconciliation using certain projection matrices will guarantee reconciled forecasts will be unbiased if base forecasts are also unbiased.
+We prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts as long as base forecasts are also unbiased.
 A natural question that arises is what to do in the case of biased reconciled forecasts.
@@
 Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines so called hierarchical time series in a way that does not depend on any notion of bottom level series.
-Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projection and includes our proof that reconciled forecasts is guaranteed to dominate base forecasts with respect to a specific loss function.
-In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose method for bias correction.
+Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projections and includes a proof that reconciled forecasts dominate base forecasts with respect to a specific loss function.
+In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose methods for bias correction.
 In Section \ref{sec:EmpStudy} we evaluate these methods for in an extensive emprirical application to domestic tourism flow in Australia.

### 2019-08-17 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
rewrote conclusion

@@
 
-	By redefining coherent point forecast and point forecast reconciliation, we rehash all existing reconciliation methods into a single projection based geometric framework.
+	%By redefining coherent point forecast and point forecast reconciliation, we rehash all existing reconciliation methods into a single projection based geometric framework.
 We have also established new theoretical results that support the use of projections for point forecast reconciliation.
@@
 
-	These new geometric interpretations of hierarchical forecast reconciliation facilitate extensions of the problem to a probabilistic framework. We leave this discussion into a different paper.
+	Defining concepts such as coherence and reconciliation in geometric terms provides new insights into forecast reconciliation methods.
+We have also provided evidence that reconciliation, particularly using the MinT method, can mitigate the effect of poor bias correction.
+Our intention in proposing a geometric interpretation is also to provoke research into new areas.
+We now discuss three such possibilites.
+
+	First, it should be possible to extend to the concept of coherence to non-linear constraints.
+In these cases the coherent space may need to be defined by a manifold.
+Although much more challenging, it is still possible define reconciled forecasts in terms of projections onto a manifold.
+Second, since we have established that the concept of bottom-level series is not crucial in forecast reconciliation an open question is whether is may be better to construct base forecasts of linear combinations of the time series rather than the time series themselves.
+Finally, the geometric interpretations of hierarchical forecast reconciliation facilitates an extension into a probabilistic framework, an issue that we investigate in a separate paper.
 

### 2019-08-19 Application-R/Application-TourismData/Final-results/TourismData-Final-results.Rmd
New results on tourism data

---
title: "Tourism Data Analysis"
output:
  pdf_document: 
    keep_tex: yes
  html_document: default
date: "31 July 2019"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(fpp2)
library(Matrix)
library(hts)
library(readr)
library(BigVAR)
library(vars)
library(tibble)
library(kableExtra)
library(reshape2)
```

# BoxCox Transformation

```{r, echo=FALSE}
DF_BoxCoxTrans <- read.csv("DF_BoxCoxTrans.csv")[,-1]

DF_BoxCoxTrans %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans

DF_BoxCoxTrans %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_MSE_h1

Avg_BoxCox_MSE_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = MSE) %>% 
  kable(format = "latex")

```

# More analysis on BoxCox transformed resulst

```{r}
DF_BoxCoxTrans %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon, Series) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(R.method == "Base", Forecast_Horizon == 1, 
         F.method %in%c("Bias","Unbiased_M1")) %>% 
  ungroup() %>% 
  dplyr::select(-R.method, -Forecast_Horizon) %>% 
  spread(key = F.method, value = MSE) %>% 
  mutate("Bias-Unbiase" = Bias - Unbiased_M1) %>% 
  filter(`Bias-Unbiase` < -5)

```
Bias correction is giving wiered results for `Total` series.

```{r echo=FALSE}
DF_BoxCoxTrans %>% 
  filter(Forecast_Horizon == 1, Series == "Total") -> DF_BoxCoxTrans_Tot_h1

# DF_BoxCoxTrans_h1 %>% 
#   filter(Series == "Total", R.method == "Base", F.method == "Bias") %>% 
#   dplyr::select(Actual, Replication) -> Total_BoxCox_True

DF_BoxCoxTrans_Tot_h1 %>% 
  filter(R.method == "Base", F.method %in%c("Bias","Unbiased_M1")) %>%
  ungroup() %>% 
  dplyr::select(F.method, Forecasts, Actual, Replication) %>% 
  spread(key = F.method, value = Forecasts) %>% 
  gather(-Replication, key = "Forecasts/Actual", value = Val) -> DF_BoxCoxTrans_Tot_h1

DF_BoxCoxTrans_Tot_h1 %>% 
  mutate(`Forecasts/Actual` = recode(`Forecasts/Actual`, "Unbiased_M1" = "Unbiased")) %>%   ggplot() + 
  geom_line(aes(x = Replication, y = Val, color = `Forecasts/Actual`)) + 
  ylab("Forecasts/Actual") + 
  ggtitle("Forecasts follow from BoxCox Transformation") + 
  theme(legend.position="bottom")

```

```{r}
OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]

## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##

OvernightTrips_Region %>% 
  dplyr::select(`Adelaide Hills`) %>% 
  filter(`Adelaide Hills` > 80) %>% 
  as.numeric() -> a

which(OvernightTrips_Region$`Adelaide Hills`==a) -> x

OvernightTrips_Region %>% 
  dplyr::select(`Adelaide Hills`) %>% 
  filter(row_number() %in% c(60+12,60-12)) %>% 
  summarise(mean(`Adelaide Hills`)) %>% 
  as.numeric() -> b

OvernightTrips_Region_new <- OvernightTrips_Region %>% 
  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
                                      TRUE ~ as.double(`Adelaide Hills`)))

#generating the hierarchy
#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, 
                                  list(7, c(6,5,4,4,3,3,2), c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,3,4,2,3,1,1,1,2,2,3,4))))

AllTS_new <- allts(Hierarchy) %>%
  as_tibble()

lambda <- numeric()

for (j in 1:140) {#C=140

  Train <- AllTS_new[j:(100+j-1), "Total"] %>% as.ts()

  lambda[j] <- BoxCox.lambda(Train)

}
```

# Log Transformation

```{r, echo=FALSE}
DF_LogTrans <- read.csv("DF_LogTrans.csv")[,-1]

DF_LogTrans %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans

DF_LogTrans %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_MSE_h1

Avg_Log_MSE_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = MSE) %>% 
  kable(format = "latex")

```

```{r echo=FALSE}
DF_LogTrans %>% 
  filter(Forecast_Horizon == 1) -> DF_LogTrans_h1

DF_LogTrans_h1 %>% 
  filter(Series == "Total", R.method == "Base", F.method == "Bias") %>% 
  dplyr::select(Actual, Replication) -> Total_Log_True

DF_LogTrans_h1 %>% 
  filter(Series == "Total", R.method == "Base", F.method %in%c("Bias","Unbiased_M1")) -> Total_Log_Fc

ggplot() + 
  geom_line(data = Total_Log_Fc, aes(x = Replication, y = Forecasts, color = `F.method`)) + 
  geom_line(data = Total_Log_True, mapping = aes(x = Replication, y = Actual)) + 
  ylab("Forecasts/Actual") + 
  ggtitle("Forecasts follows from Log Transformation")

```

```{r, echo=FALSE}

DF_MSE <- DF_LogTrans %>% 
  mutate(SquaredE = (`Actual` - `Forecasts`)^2) %>% 
  filter(`Forecast_Horizon` == 1) %>% 
  dplyr::select(-`Forecast_Horizon`) %>% 
  group_by(`F.method`, `R.method`, Replication) %>% 
  summarise(MSE = mean(SquaredE))

DF_MSE %>% 
  filter(`F.method`=="Unbiased_M1", `R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>% 
  spread(key = `R.method`, value = MSE) %>% 
  mutate("Base-OLS" = Base - OLS,
         "Base-MinT" = Base - `MinT(Shrink)`,
         "Base-WLS" = Base - WLS) %>% 
  dplyr::select(Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>% 
  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>% 
  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>% 
  ggplot(aes(x = Method, y = MSE)) + 
  geom_boxplot() + 
  ylab("MSE") + xlab("Reconciliation Method")

```

### 2019-08-19 Application-R/Application-TourismData/Trash/Bias-correction-Method-2/LogTrans/Results/TourismData-BoxCoxTrans-results.Rmd
New results on tourism data

---
title: "Tourism Data Analysis"
output:
  pdf_document: default
  html_document: default
date: "31 July 2019"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(fpp2)
library(Matrix)
library(hts)
library(readr)
library(BigVAR)
library(vars)
library(tibble)
library(kableExtra)
library(reshape2)
```

Bias is estimated as the insample residual mean
```{r, echo=FALSE}
DF_1_50 <- read.csv("DF_1-50.csv")[,-1]
DF_51_100 <- read.csv("DF_51-100.csv")[,-1]
DF_101_140 <- read.csv("DF_101-140.csv")[,-1]

rbind(DF_1_50, DF_51_100, DF_101_140) %>% 
  as.data.frame() -> DF

DF %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF

DF %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(MSE = mean(SquaredE)) -> Avg_MSE

Avg_MSE_tab1 <- Avg_MSE %>% dcast(`R.method` ~ Forecast_Horizon + `F.method`, value.var = "MSE")

colnames(Avg_MSE_tab1) <- c("R.method", rep(c("Biased", "Unbiased"), 6))

Avg_MSE_tab1 %>% 
  kable(format = "latex") %>% 
  kableExtra::add_header_above(c(" " = 1, "h=1" = 2, "h=2" = 2, "h=3" = 2, "h=4" = 2,
                                 "h=5" = 2, "h=6" = 2))

```

### 2019-08-19 Application-R/Application-TourismData/Trash/Results/TourismData-results.Rmd
New results on tourism data

--- 2019-08-06 Application-R/Application-TourismData/Results/TourismData-results.Rmd
@@
   dplyr::select(`Adelaide Hills`) %>% 
-  as.ts() %>% 
+  ts(start = c(1998, 1), frequency = 12) %>% 
   autoplot()
@@
 
-We can see this variable has a very unusual observation which might be an outlier.
-To avoid this, I have replaced this observation with the average of it's adjacent observations.
-Then I have refitted the models for automatically chosen BoxCox transformed data and back-transformed and back-transformed bias-adjusted forecasts were obtained.
+We can see this variable has an anomalous observation on Dec-2002 which might be an outlier.
+
+```{r}
+AllTS %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  slice(3:102) %>% 
+  as.ts() %>% 
+  BoxCox.lambda() -> lambda
+
+```
+
+If we do Box-Cox transformation for this series we get  $\lambda = `r lambda`$. The transformed series with this $\lambda$ looks like
+
+```{r}
+AllTS %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  slice(3:102) %>% 
+  ts(start = c(1998, 1), frequency = 12) %>% 
+  BoxCox(lambda = lambda) %>% 
+  autoplot()
+
+```
+
+```{r echo=FALSE}
+TS <- AllTS %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  slice(3:102) %>% 
+  ts(start = c(1998, 1), frequency = 12)
+```
+
+```{r echo=FALSE}
+# TS %>% 
+#   auto.arima(lambda = "auto") %>% 
+#   forecast(h=6, biasadj = FALSE) %>% 
+#   autoplot() + 
+#   ggtitle("Biased forecasts")
+# 
+# TS %>% 
+#   auto.arima(lambda = "auto") %>% 
+#   forecast(h=6, biasadj = TRUE) %>% 
+#   autoplot() + 
+#   ggtitle("Bias-adjusted forecasts")
+
+```
+
+I have replaced the anomalous observation in this series with the average of December for predecessive and successive years of 2002.
+Then I have refitted the models for automatically chosen Box-Cox transformed data.
+Back-transformed and back-transformed bias-adjusted forecasts were then obtained.
 The results are as follows.
@@
   group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
-  summarise(MSE = mean(SquaredE)) -> Avg_MSE_BC_2
+  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) -> Avg_MSE_BC_2
 
@@
 
-These results also shows that, even though the bias-adjusted based forecasts are worst than that of biased base forecasts, the MinT reconicilation is outperforming.
+These results also shows that, even though the bias-adjusted based forecasts are worst than that of biased base forecasts, the MinT reconciliation is outperforming.
 
-```{r}
+```{r echo=FALSE}
 Avg_MSE_BC_2 %>% filter(`F-method` == "ARIMA_bias", `R-method` == "Base") %>% 
@@
 
-```{r}
+```{r echo=FALSE}
 
@@
   dplyr::select(Replication, Forecast_Horizon, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
-  gather(`Base-OLS`, `Base-WLS`, `Base-MinT`,  key = Method, value = MSE) %>% 
-  ggplot(aes(x = Method, y = MSE)) + geom_boxplot() + facet_wrap(~`Forecast_Horizon`, scales = "free_y")
+  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>% 
+  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>% 
+  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>% 
+  ggplot(aes(x = Method, y = MSE)) + 
+  geom_boxplot() + 
+  facet_wrap(~`Forecast_Horizon`, scales = "free_y") + 
+  ylab("MSE") + xlab("Reconciliation Method")
+
 ```
@@
 DF_Log %>% 
+  mutate(SquaredE = (`Actual` - `Forecasts`)^2) %>% 
   group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
-  summarise(MSE = mean(SquaredE)) -> Avg_MSE_Log
+  summarise(MSE = mean(SquaredE)/1e3) -> Avg_MSE_Log
 

### 2019-08-19 Application-R/Application-TourismData/Bias-correction-Method-1/Data_preprocessing.R

@@ -1,29 +1,0 @@
-## Change Geelong to Geelong and the Bellarine
-
-
-library(tidyverse)
-Data_OvernightTrips <- read_csv("Tourism_Australia_FullDataSet_upto_2017.csv", skip = 9)
-Data_Nights <- read_csv("VN_FullDataSet.csv", skip = 6)[,-1] %>%
-  rename(Year = `Calendar year`)
-
-
-Data_OvernightTrips <- Data_OvernightTrips[,names(Data_Nights)]
-
-Data_OvernightTrips %>% 
-  mutate(Wimmera = Wimmera+Mallee) %>% 
-  dplyr::select(-Mallee) %>% 
-  rename(Wimmera_Mallee = Wimmera) -> Data_OvernightTrips
-
-# colnames(Data_OvernightTrips) <- c("Year", "Month returned", "AAA", "AAB",	"ABA", "ABB",	"ACA", "ADA",	"ADB", "ADC",	"ADD", "AEA",	"AEB",
-#                            "AEC", "AED",	"AFA", "BAA",	"BAB", "BAC",	"BBA", "BCA",	"BCB", "BCC",	"BDA",
-#                            "BDB", "BDC",	"BDD", "BDE",	"BDF", "BEA", "BEB", "BEC",	"BED", "BEE",	"BEF",
-#                            "BEG", "CAA", "CAB",	"CAC",	"CBA", "CBB",	"CBC", "CBD",	"CCA", "CCB",
-#                            "CCC", "CDA",	"CDB", "DAA",	"DAB", "DAC",	"DBA", "DBB",	"DBC", "DCA",	"DCB", "DCC",
-#                            "DCD", "DDA",	"DDB", "EAA",	"EAB", "EAC",	"EBA", "ECA",	"FAA", "FBA",	"FBB", "FCA",
-#                            "FCB", "GAA", "GAB", "GAC", "GBA", "GBB",	"GBC", "GBD")
-
-
-write.csv(Data_OvernightTrips, "OvernightTrips_2017.csv")
-
-
-

### 2019-08-19 Application-R/Application-TourismData/Bias-correction-Method-2/BoxCoxTrans/TourismData_BoxCoxTransBiasCorrectionM2_UnivARIMA_AnomalyAdj_1-50.R

@@ -1,417 +1,0 @@
-## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
-## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
-## Length of data expands from Jan-1998 to Dec-2017
-
-# Here we fit univariate ARIMA models for the BoxCOx transformed data
-# The back transformed data will be biased and we bias adjust to get 
-# unbiased point forecasts.
-
-# We noticed that there is an unusual observation in the Adelaide Hills series. So we
-# replace that odd value with the average of adjecent values
-
-
-library(tidyverse)
-library(fpp2)
-library(Matrix)
-library(hts)
-library(readr)
-library(tibble)
-
-# Import bottom level data
-
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(`Adelaide Hills` > 80) %>% 
-  as.numeric() -> a
-
-which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(row_number() %in% c(60+12,60-12)) %>% 
-  summarise(mean(`Adelaide Hills`)) %>% 
-  as.numeric() -> b
-
-OvernightTrips_Region_new <- OvernightTrips_Region %>% 
-  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
-                                      TRUE ~ as.double(`Adelaide Hills`)))
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
-Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-19 Application-R/Application-TourismData/Bias-correction-Method-2/BoxCoxTrans/TourismData_BoxCoxTransBiasCorrectionM2_UnivARIMA_AnomalyAdj_101-140.R

@@ -1,417 +1,0 @@
-## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
-## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
-## Length of data expands from Jan-1998 to Dec-2017
-
-# Here we fit univariate ARIMA models for the BoxCOx transformed data
-# The back transformed data will be biased and we bias adjust to get 
-# unbiased point forecasts.
-
-# We noticed that there is an unusual observation in the Adelaide Hills series. So we
-# replace that odd value with the average of adjecent values
-
-
-library(tidyverse)
-library(fpp2)
-library(Matrix)
-library(hts)
-library(readr)
-library(tibble)
-
-# Import bottom level data
-
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(`Adelaide Hills` > 80) %>% 
-  as.numeric() -> a
-
-which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(row_number() %in% c(60+12,60-12)) %>% 
-  summarise(mean(`Adelaide Hills`)) %>% 
-  as.numeric() -> b
-
-OvernightTrips_Region_new <- OvernightTrips_Region %>% 
-  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
-                                      TRUE ~ as.double(`Adelaide Hills`)))
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
-Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
-                                                                  c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
[…]

### 2019-08-19 Application-R/Application-TourismData/Bias-correction-Method-2/LogTrans/TourismData_LogTransBiasCorrectionM2_UnivARIMA.R

@@ -1,422 +1,0 @@
-## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
-## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
-## Length of data expands from Jan-1998 to Dec-2017
-
-# Here we fit univariate ARIMA models for the log transformed data
-# The back transformed data will be biased and we bias adjust to get 
-# unbiased point forecasts.
-
-
-library(tidyverse)
-library(fpp2)
-library(Matrix)
-library(hts)
-library(readr)
-library(tibble)
-
-# Import bottom level data
-#Importing data
-
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
-Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
-                                                            c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
-                                                              3,4,2,3,1,1,1,2,2,3,4))))
-AllTS <- allts(Hierarchy) %>% 
-  as_tibble()
-n <- ncol(AllTS)
-l1 <- 1
-l2 <- sum(7)
-l3 <- sum(6,5,4,4,3,3,2)
-m <- ncol(OvernightTrips_Region)
-H <- 6
-L <- 100 #Size of the training sample 
-C <- nrow(AllTS) - L
-
-
-#Generating the summing matrix
-S <- smatrix(Hierarchy)
-#Code to get shrinkage estimator
-
-lowerD <- function(x)
-{
-  n2 <- nrow(x)
-  return(diag(apply(x, 2, crossprod) / n2))
-}
-
-shrink.estim <- function(x, tar)
-{
-  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
-    stop("The data matrix must be numeric!")
-  p1 <- ncol(x)
-  n2 <- nrow(x)
-  covm <- crossprod(x) / n2
-  corm <- cov2cor(covm)
-  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
[…]

### 2019-08-19 Application-R/Application-TourismData/Bias-correction-Method-2/LogTrans/TourismData_LogTransBiasCorrectionM2_UnivARIMA_101-140.R

@@ -1,422 +1,0 @@
-## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
-## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
-## Length of data expands from Jan-1998 to Dec-2017
-
-# Here we fit univariate ARIMA models for the log transformed data
-# The back transformed data will be biased and we bias adjust to get 
-# unbiased point forecasts.
-
-
-library(tidyverse)
-library(fpp2)
-library(Matrix)
-library(hts)
-library(readr)
-library(tibble)
-
-# Import bottom level data
-#Importing data
-
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
-Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
-                                                              c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
-                                                                3,4,2,3,1,1,1,2,2,3,4))))
-AllTS <- allts(Hierarchy) %>% 
-  as_tibble()
-n <- ncol(AllTS)
-l1 <- 1
-l2 <- sum(7)
-l3 <- sum(6,5,4,4,3,3,2)
-m <- ncol(OvernightTrips_Region)
-H <- 6
-L <- 100 #Size of the training sample 
-C <- nrow(AllTS) - L
-
-
-#Generating the summing matrix
-S <- smatrix(Hierarchy)
-#Code to get shrinkage estimator
-
-lowerD <- function(x)
-{
-  n2 <- nrow(x)
-  return(diag(apply(x, 2, crossprod) / n2))
-}
-
-shrink.estim <- function(x, tar)
-{
-  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
-    stop("The data matrix must be numeric!")
-  p1 <- ncol(x)
-  n2 <- nrow(x)
-  covm <- crossprod(x) / n2
-  corm <- cov2cor(covm)
-  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
[…]

### 2019-08-19 Application-R/Application-TourismData/Bias-correction-Method-2/LogTrans/TourismData_LogTransBiasCorrectionM2_UnivARIMA_51-100.R

@@ -1,422 +1,0 @@
-## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
-## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
-## Length of data expands from Jan-1998 to Dec-2017
-
-# Here we fit univariate ARIMA models for the log transformed data
-# The back transformed data will be biased and we bias adjust to get 
-# unbiased point forecasts.
-
-
-library(tidyverse)
-library(fpp2)
-library(Matrix)
-library(hts)
-library(readr)
-library(tibble)
-
-# Import bottom level data
-#Importing data
-
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
-Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
-                                                              c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
-                                                                3,4,2,3,1,1,1,2,2,3,4))))
-AllTS <- allts(Hierarchy) %>% 
-  as_tibble()
-n <- ncol(AllTS)
-l1 <- 1
-l2 <- sum(7)
-l3 <- sum(6,5,4,4,3,3,2)
-m <- ncol(OvernightTrips_Region)
-H <- 6
-L <- 100 #Size of the training sample 
-C <- nrow(AllTS) - L
-
-
-#Generating the summing matrix
-S <- smatrix(Hierarchy)
-#Code to get shrinkage estimator
-
-lowerD <- function(x)
-{
-  n2 <- nrow(x)
-  return(diag(apply(x, 2, crossprod) / n2))
-}
-
-shrink.estim <- function(x, tar)
-{
-  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
-    stop("The data matrix must be numeric!")
-  p1 <- ncol(x)
-  n2 <- nrow(x)
-  covm <- crossprod(x) / n2
-  corm <- cov2cor(covm)
-  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
[…]

### 2019-08-19 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/TourismForecasting_BoxCoxTrans_BiasAdjust.R

@@ -1,0 +1,402 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-19 Application-R/Application-TourismData/Bias_correction/LogTrans/Results/Analysis.R

@@ -1,0 +1,21 @@
+
+library(tidyverse)
+
+
+
+DF_LogTrans_1_50 <- read.csv("DF_LogTrans_1-50.csv")[,-1]
+DF_LogTrans_51_100 <- read.csv("DF_LogTrans_51-100.csv")[,-1]
+DF_LogTrans_101_140 <- read.csv("DF_LogTrans_101-140.csv")[,-1]
+
+rbind(DF_LogTrans_1_50, DF_LogTrans_51_100, DF_LogTrans_101_140) %>% 
+  as.data.frame() -> DF_LogTrans
+write.csv(x=DF_LogTrans, file = "DF_LogTrans.csv")
+
+
+DF_LogTrans %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans
+
+DF_LogTrans %>% 
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  summarise(MSE = mean(SquaredE)) %>% 
+  spread(key = Forecast_Horizon, value = MSE)
+

### 2019-08-19 Application-R/Application-TourismData/Bias_correction/LogTrans/TourismForecasting_LogTrans_BiasAdjust_101-140.R

@@ -1,0 +1,404 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
+                                                                  c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
[…]

### 2019-08-19 Application-R/Application-TourismData/Bias_correction/LogTrans/TourismForecasting_LogTrans_BiasAdjust_51-100.R

@@ -1,0 +1,404 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
+                                                                  c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
[…]

### 2019-08-19 Application-R/Application-TourismData/Final-results/Time-Plots/TimePlots.R

@@ -1,0 +1,205 @@
+library(tidyverse)
+library(gridExtra)
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, 
+                                  list(7, c(6,5,4,4,3,3,2), c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,3,4,2,3,1,1,1,2,2,3,4))))
+
+AllTS_new <- allts(Hierarchy) %>%
+  as_tibble()
+
+AllTS_new <- AllTS_new + 1 # Add 1 since some series has zero observations and this will affect taking log transformations
+
+#Total Series
+AllTS_new %>% 
+  dplyr::select("Total") %>% 
+  ts(start = c(1998, 1), frequency = 12) %>% 
+  autoplot() + ylab("Overnight trips") + xlab("Time") + 
+  ggtitle("Total overnight trips") + theme(legend.position="bottom") -> Plot_total
+
+#States
+
+AllTS_new %>% 
+  dplyr::select("A", "B", "C", "D", "E", "F", "G" ) %>% 
+  rename("NSW" = "A", "Victoria" = "B", "Queensland" = "C", 
+         "South Australia" = "D", "Western Australia" = "E", "Tasmania" = "F",
[…]

### 2019-08-19 Application-R/Application-TourismData/Results/TimePlots.R

@@ -1,175 +1,0 @@
-library(tidyverse)
-library(gridExtra)
-
-load("TourismData_LogTransBiasCorrection_UnivARIMA.RData")
-
-#Total Series
-AllTS %>% 
-  dplyr::select("Total") %>% 
-  ts(start = c(1998, 1), frequency = 12) %>% 
-  autoplot() + ylab("Overnight trips") + xlab("Time") + 
-  ggtitle("Total overnight trips") + theme(legend.position="bottom") -> Plot_total
-
-#States
-
-AllTS %>% 
-  dplyr::select("A", "B", "C", "D", "E", "F", "G" ) %>% 
-  rename("NSW" = "A", "Victoria" = "B", "Queensland" = "C", 
-         "South Australia" = "D", "Western Australia" = "E", "Tasmania" = "F",
-         "Northern Territory" = "G") %>% 
-  ts(start = c(1998, 1), frequency = 12) %>% 
-  autoplot() + ylab("Overnight trips") + xlab("Time") + 
-  ggtitle("States") + theme(legend.position="bottom") -> Plot_Sates
-
-#Zones
-
-# "AA", "AB", "AC", "AD", "AE", "AF", "BA", "BB", "BC", "BD", "BE",
-# "CA", "CB", "CC", "CD", "DA", "DB", "DC", "DD", "EA", "EB","EC", 
-# "FA", "FB", "FC", "GA", "GB"
-
-AllTS %>% 
-  dplyr::select("AA", "AF", "BB", "BE",
-                "CA", "CD", "DC", "DD", "EB","EC", 
-                "FA", "FB", "GA", "GB") %>% 
-  rename("Metro NSW" = "AA", "ACT" = "AF", "West Coast VIC" = "BB",
-         "North East VIC" = "BE", "Metro QLD" = "CA", "Inland QLD" = "CD",
-         "Inland SA" = "DC", "West Coast SA" = "DD", "North WA" = "EB",
-         "South WA" = "EC", "South TAS" = "FA", "North East TAS" = "FB",
-         "North Coast NT" = "GA", "Central NT" = "GB") %>% 
-  ts(start = c(1998, 1), frequency = 12) %>% 
-  autoplot() + ylab("Overnight trips") + xlab("Time") + 
-  ggtitle("Zones") + theme(legend.position="bottom") -> Plot_Zones
-
-
-AllTS %>% 
-  dplyr::select("Central Coast", "Hunter",
[…]

### 2019-08-19 Application-R/Application-TourismData/Trash/Bias-correction-Method-1/Data_preprocessing.R

@@ -1,0 +1,29 @@
+## Change Geelong to Geelong and the Bellarine
+
+
+library(tidyverse)
+Data_OvernightTrips <- read_csv("Tourism_Australia_FullDataSet_upto_2017.csv", skip = 9)
+Data_Nights <- read_csv("VN_FullDataSet.csv", skip = 6)[,-1] %>%
+  rename(Year = `Calendar year`)
+
+
+Data_OvernightTrips <- Data_OvernightTrips[,names(Data_Nights)]
+
+Data_OvernightTrips %>% 
+  mutate(Wimmera = Wimmera+Mallee) %>% 
+  dplyr::select(-Mallee) %>% 
+  rename(Wimmera_Mallee = Wimmera) -> Data_OvernightTrips
+
+# colnames(Data_OvernightTrips) <- c("Year", "Month returned", "AAA", "AAB",	"ABA", "ABB",	"ACA", "ADA",	"ADB", "ADC",	"ADD", "AEA",	"AEB",
+#                            "AEC", "AED",	"AFA", "BAA",	"BAB", "BAC",	"BBA", "BCA",	"BCB", "BCC",	"BDA",
+#                            "BDB", "BDC",	"BDD", "BDE",	"BDF", "BEA", "BEB", "BEC",	"BED", "BEE",	"BEF",
+#                            "BEG", "CAA", "CAB",	"CAC",	"CBA", "CBB",	"CBC", "CBD",	"CCA", "CCB",
+#                            "CCC", "CDA",	"CDB", "DAA",	"DAB", "DAC",	"DBA", "DBB",	"DBC", "DCA",	"DCB", "DCC",
+#                            "DCD", "DDA",	"DDB", "EAA",	"EAB", "EAC",	"EBA", "ECA",	"FAA", "FBA",	"FBB", "FCA",
+#                            "FCB", "GAA", "GAB", "GAC", "GBA", "GBB",	"GBC", "GBD")
+
+
+write.csv(Data_OvernightTrips, "OvernightTrips_2017.csv")
+
+
+

### 2019-08-19 Application-R/Application-TourismData/Trash/Bias-correction-Method-1/TourismData_BoxCoxTransBiasCorrectionM1_UnivARIMA_AnomalyAdj.R

@@ -1,0 +1,408 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the BoxCOx transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+# We noticed that there is an unusual observation in the Adelaide Hills series. So we
+# replace that odd value with the average of adjecent values
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-19 Application-R/Application-TourismData/Trash/Bias-correction-Method-2/BoxCoxTrans/Results/Analysis.R

@@ -1,0 +1,21 @@
+
+library(tidyverse)
+
+
+
+DF_1_50 <- read.csv("DF_1-50.csv")[,-1]
+DF_51_100 <- read.csv("DF_51-100.csv")[,-1]
+DF_101_140 <- read.csv("DF_101-140.csv")[,-1]
+
+rbind(DF_1_50, DF_51_100, DF_101_140) %>% 
+  as.data.frame() -> DF
+write.csv(x=DF, file = "DF_BoxCoxTrans_BiasAdj_M2.csv")
+
+
+DF %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF
+
+DF %>% 
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  summarise(MSE = mean(SquaredE)) %>% 
+  spread(key = Forecast_Horizon, value = MSE)
+

### 2019-08-19 Application-R/Application-TourismData/Trash/Bias-correction-Method-2/BoxCoxTrans/TourismData_BoxCoxTransBiasCorrectionM2_UnivARIMA_AnomalyAdj_1-50.R

@@ -1,0 +1,417 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the BoxCOx transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+# We noticed that there is an unusual observation in the Adelaide Hills series. So we
+# replace that odd value with the average of adjecent values
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-19 Application-R/Application-TourismData/Trash/Bias-correction-Method-2/Data_preprocessing.R

@@ -1,0 +1,19 @@
+## Change Geelong to Geelong and the Bellarine
+
+
+library(tidyverse)
+Data_OvernightTrips <- read_csv("Tourism_Australia_FullDataSet_upto_2017.csv", skip = 9)
+Data_Nights <- read_csv("VN_FullDataSet Edited by George2017.csv", skip = 6)[,-1] %>%
+  rename(Year = `Calendar year`)
+
+Data_OvernightTrips <- Data_OvernightTrips[,names(Data_Nights)]
+
+Data_OvernightTrips %>% 
+  mutate(Wimmera = Wimmera+Mallee) %>% 
+  select(-Mallee) %>% 
+  rename(Wimmera_Mallee = Wimmera) -> Data_OvernightTrips
+
+write.csv(Data_OvernightTrips, "OvernightTrips_2017.csv")
+
+
+

### 2019-08-19 Application-R/Application-TourismData/Trash/Bias-correction-Method-2/LogTrans/TourismData_LogTransBiasCorrectionM2_UnivARIMA_101-140.R

@@ -1,0 +1,422 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
+                                                              c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
+                                                                3,4,2,3,1,1,1,2,2,3,4))))
+AllTS <- allts(Hierarchy) %>% 
+  as_tibble()
+n <- ncol(AllTS)
+l1 <- 1
+l2 <- sum(7)
+l3 <- sum(6,5,4,4,3,3,2)
+m <- ncol(OvernightTrips_Region)
+H <- 6
+L <- 100 #Size of the training sample 
+C <- nrow(AllTS) - L
+
+
+#Generating the summing matrix
+S <- smatrix(Hierarchy)
+#Code to get shrinkage estimator
+
+lowerD <- function(x)
+{
+  n2 <- nrow(x)
+  return(diag(apply(x, 2, crossprod) / n2))
+}
+
+shrink.estim <- function(x, tar)
+{
+  if (is.matrix(x) == TRUE && is.numeric(x) == FALSE)
+    stop("The data matrix must be numeric!")
+  p1 <- ncol(x)
+  n2 <- nrow(x)
+  covm <- crossprod(x) / n2
+  corm <- cov2cor(covm)
+  xs <- scale(x, center = FALSE, scale = sqrt(diag(covm)))
[…]

### 2019-08-22 Application-R/Application-TourismData/Final-results/TourismData-Final-results.Rmd

@@
   ggtitle("Forecasts follow from BoxCox Transformation") + 
-  theme(legend.position="bottom")
+  theme(legend.position="bottom", legend.title = element_blank())
 
@@
 
-for (j in 1:140) {#C=140
+# for (j in 1:140) {#C=140
+#   
+#   Train <- AllTS_new[j:(100+j-1), "Total"] %>% as.ts()
+# 
+#   lambda[j] <- BoxCox.lambda(Train)
+#   
+#   
+# }
 
+j = 130
 Train <- AllTS_new[j:(100+j-1), "Total"] %>% as.ts()
 
-  lambda[j] <- BoxCox.lambda(Train)
-
-}
+fit <- auto.arima(Train, lambda = "auto")
+summary(fit)
 ```

### 2019-08-22 Application-R/Application-TourismData/Trash/Bias_correction/BoxCoxTrans/Results/TourismData-BoxCoxTrans-results.Rmd

---
title: "Tourism Data Analysis"
output:
  pdf_document: default
  html_document: default
date: "31 July 2019"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(fpp2)
library(Matrix)
library(hts)
library(readr)
library(BigVAR)
library(vars)
library(tibble)
library(kableExtra)
library(reshape2)
```

Bias is estimated as the insample residual mean
```{r, echo=FALSE}
DF_BoxCoxTrans <- read.csv("DF_BoxCoxTrans.csv")[,-1]

DF_BoxCoxTrans %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans

DF_BoxCoxTrans %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_MSE_h1

Avg_MSE_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = MSE) %>% 
  kable(format = "latex")

```

### 2019-08-22 Hierarchical-forecast-reconciliation/Figs/InsampDir_1.tex
Modified schematics of orthogonal and oblique projections

% Created by tikzDevice version 0.12 on 2019-08-21 20:48:44
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}

\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,361.35);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (336.15,312.15);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.66, 49.37) --
	( 93.66,302.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.85, 91.62) --
	(357.70, 91.62);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 93.66, 91.62) -- (278.49,165.55);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (267.32,151.35) --
	(278.49,165.55) --
	(260.61,168.13);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.50] at (284.49,159.81) {{$\huge \mathfrak{s}$}};
\definecolor{drawColor}{RGB}{255,165,0}
\definecolor{fillColor}{RGB}{255,165,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.27,151.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.39, -1.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 86.69, 59.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 93.83,107.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.42, 96.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.13,164.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.44, 82.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.66, 88.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.66,140.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.08, 73.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.44,  6.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.19,133.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 70.78,  4.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 59.84, 11.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.20, 24.24) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.60, 63.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 80.42, 64.76) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 86.97, 33.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 77.85, 31.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.13,155.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.16,138.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.73,141.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.03,186.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.01, 22.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.45, 93.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.08, 64.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.96,162.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 75.35, 45.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.14, 77.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 83.27, 71.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.23, 89.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.86, 87.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 68.03, 19.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.39, 34.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 79.24, 42.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.69,117.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.26,166.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 82.79, 55.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.67, 88.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.96, 45.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.83,141.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.17,107.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.17, 97.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.57,126.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.07,128.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.25, 90.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.67,126.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.50, 56.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.20,178.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.84, 56.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 82.89, 59.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.79,107.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.73,117.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.14,107.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 83.09, 93.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.39,125.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.67,128.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.51, 68.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 93.51,115.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 81.98, 69.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.89, 59.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.62,101.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.73, 84.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.47, 64.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 83.27, 46.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.65, 57.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 82.57, 34.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.86, 82.30) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.20, 94.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.10, 73.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.75,128.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.57,114.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.09, 52.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.07,  3.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.20,164.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.47,111.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.43,184.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.01, 37.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 85.49, 52.81) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 97.33,122.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.73, 21.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.42,164.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 70.87,  0.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.25,148.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.72, 84.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.68,174.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.76, 54.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.27,108.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.79, 90.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 95.37, 95.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.47,103.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 60.51, -0.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 86.87, 97.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.37, 82.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.47,105.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.31, 63.15) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 93.66, 91.62) -- (146.47,260.61);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (150.42,242.98) --
	(146.47,260.61) --
	(133.18,248.37);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (146.47,266.61) {{${\bm R}$}};
\end{scope}
\end{tikzpicture}
\caption{a caption}
\end{document}

### 2019-08-22 Hierarchical-forecast-reconciliation/Figs/InsampDir_2.tex
Modified schematics of orthogonal and oblique projections

% Created by tikzDevice version 0.12 on 2019-08-21 20:48:46
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}

\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,361.35);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (336.15,312.15);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.66, 49.37) --
	( 93.66,302.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.85, 91.62) --
	(357.70, 91.62);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 93.66, 91.62) -- (278.49,165.55);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (267.32,151.35) --
	(278.49,165.55) --
	(260.61,168.13);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.50] at (284.49,159.81) {{$\huge \mathfrak{s}$}};
\definecolor{drawColor}{RGB}{190,190,190}
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.96,163.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.08, 11.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.37, 72.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.51,120.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.10,109.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.81,177.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.12, 95.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.35,100.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.34,152.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.76, 86.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.12, 19.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.87,146.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.46, 17.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.52, 24.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.89, 36.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.29, 76.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.10, 77.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.65, 46.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.54, 43.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.82,168.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.85,151.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.42,154.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.71,198.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.70, 34.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.14,106.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.76, 77.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.65,175.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.04, 58.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.82, 90.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.96, 83.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.92,102.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.54,100.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.71, 32.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.08, 46.81) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.92, 55.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.38,130.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.95,179.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.47,  9.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.48, 67.81) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.35,101.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.65, 57.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.51,153.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.85,120.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.86,110.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.25,139.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.76,141.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.94,103.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.35,139.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.19, 69.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.88,191.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.52, 69.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.58, 71.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.47,120.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.42,130.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.83,120.21) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.78,106.24) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.07,138.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.35,141.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.19, 81.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.19,128.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.66, 82.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.57, 72.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.31,114.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.41, 96.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.15, 77.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.96, 58.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.34, 70.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.26, 46.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.54, 94.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.88,107.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.78, 85.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.44,141.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.25,127.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.77, 64.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 97.75, 15.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.88,177.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.16,124.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.12,196.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.70, 50.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.17, 65.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.01,134.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.41, 33.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.11,177.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.55, 13.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.93,160.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.40, 96.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.36,187.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.44, 67.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.96,121.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.48,103.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.06,108.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.15,116.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.19, 12.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.56,110.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.05, 95.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.16,118.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.00, 75.82) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 93.66, 91.62) -- (146.47,260.61);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (150.42,242.98) --
	(146.47,260.61) --
	(133.18,248.37);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (146.47,266.61) {{${\bm R}$}};
\definecolor{drawColor}{RGB}{0,0,255}
\definecolor{fillColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.87,218.36) circle (  3.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (172.87,236.36) {{$\color{blue}{\hat{\bm{y}}}$}};
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.34,104.29) circle (  3.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (125.34, 77.92) {\bfseries\itshape {$\color{black}{\bm{y}}$}};
\end{scope}
\end{tikzpicture}
\caption{a caption}
\end{document}

### 2019-08-22 Hierarchical-forecast-reconciliation/Figs/ObliqProj.tex
Modified schematics of orthogonal and oblique projections

% Created by tikzDevice version 0.12 on 2019-08-21 20:48:51
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}

\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,361.35);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (336.15,312.15);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.66, 49.37) --
	( 93.66,302.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.85, 91.62) --
	(357.70, 91.62);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 93.66, 91.62) -- (278.49,165.55);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (267.32,151.35) --
	(278.49,165.55) --
	(260.61,168.13);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.50] at (284.49,159.81) {{$\Huge \mathfrak{s}$}};
\definecolor{drawColor}{RGB}{190,190,190}
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.96,163.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.08, 11.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.37, 72.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.51,120.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.10,109.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.81,177.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.12, 95.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.35,100.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.34,152.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.76, 86.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.12, 19.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.87,146.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.46, 17.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.52, 24.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.89, 36.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.29, 76.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.10, 77.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.65, 46.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.54, 43.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.82,168.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.85,151.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.42,154.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.71,198.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.70, 34.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.14,106.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.76, 77.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.65,175.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.04, 58.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.82, 90.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.96, 83.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.92,102.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.54,100.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.71, 32.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.08, 46.81) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.92, 55.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.38,130.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.95,179.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.47,  9.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.48, 67.81) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.35,101.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.65, 57.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.51,153.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.85,120.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.86,110.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.25,139.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.76,141.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.94,103.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.35,139.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.19, 69.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.88,191.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.52, 69.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.58, 71.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.47,120.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.42,130.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.83,120.21) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.78,106.24) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.07,138.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.35,141.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.19, 81.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.19,128.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.66, 82.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.57, 72.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.31,114.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.41, 96.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.15, 77.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.96, 58.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.34, 70.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.26, 46.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.54, 94.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.88,107.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.78, 85.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.44,141.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.25,127.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.77, 64.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 97.75, 15.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.88,177.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.16,124.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.12,196.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.70, 50.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.17, 65.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.01,134.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.41, 33.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.11,177.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.55, 13.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.93,160.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.40, 96.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.36,187.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.44, 67.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.96,121.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.48,103.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.06,108.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.15,116.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.19, 12.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.56,110.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.05, 95.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.16,118.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.00, 75.82) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.85,100.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.55,103.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.88,105.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.43,102.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.48,107.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.66,100.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.37, 96.30) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.91,100.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.86,109.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.10,110.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.69, 96.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.82,112.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.84,100.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.67,105.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.07, 99.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.90,103.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.34,101.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.07,101.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.63,108.81) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.05,104.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.58,104.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.19,107.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.04,100.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.91, 98.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.48,103.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.27,106.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.51,100.76) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.04,106.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.61,102.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.96,108.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.25,102.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.76,108.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.31,103.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.65,102.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.17,103.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.83,104.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.74,106.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.55,107.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.71,107.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.86,104.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.11,100.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.25,115.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.34,100.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.55,111.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.72, 99.24) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.24,101.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.41,105.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.95,100.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.14,103.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.71,106.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.75,106.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.19, 99.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.69,103.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.33,109.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.99,107.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.78,106.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.78, 99.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.68,105.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.20,102.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.34,106.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.32,101.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.33,101.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.05,108.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.99,102.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.16,109.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.69,103.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.35,105.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.81,110.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.40,106.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.80,102.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.31,105.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.62,104.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.60, 91.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.54,102.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.11,105.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.53, 97.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.98,100.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.82,103.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.46,102.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.84,102.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.01,108.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.44,101.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.66,105.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.60,102.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.23,106.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.29,111.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.95,105.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.60,107.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.60,104.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.02,102.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.90, 96.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.51,109.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.64,103.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.92,104.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.99,105.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.70,101.24) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.83,100.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.11,105.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.50,105.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.90,106.92) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 93.66, 91.62) -- (146.47,260.61);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (150.42,242.98) --
	(146.47,260.61) --
	(133.18,248.37);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (146.47,266.61) {{${\bm R}$}};
\definecolor{drawColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.96,163.73) -- (115.85,100.50);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.08, 11.50) -- (124.55,103.98);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.37, 72.11) -- (127.88,105.31);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (125.51,120.08) -- (120.43,102.33);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.10,109.32) -- (132.48,107.15);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.81,177.38) -- (114.66,100.02);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.12, 95.44) -- (105.37, 96.30);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 88.02,  0.00) -- (116.91,100.92);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.35,100.94) -- (138.86,109.70);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (152.34,152.96) -- (140.10,110.19);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.76, 86.62) -- (106.69, 96.83);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (119.12, 19.22) -- (145.82,112.48);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (129.87,146.43) -- (116.84,100.89);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (102.46, 17.18) -- (127.67,105.22);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 91.52, 24.12) -- (113.07, 99.38);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.89, 36.92) -- (122.90,103.31);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (110.29, 76.46) -- (117.34,101.09);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (112.10, 77.44) -- (119.07,101.78);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.65, 46.02) -- (136.63,108.81);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.54, 43.80) -- (127.05,104.98);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.82,168.09) -- (125.58,104.39);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (145.85,151.63) -- (133.19,107.43);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.42,154.29) -- (116.04,100.57);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.71,198.70) -- (109.91, 98.12);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.70, 34.85) -- (124.48,103.95);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.14,106.19) -- (131.27,106.66);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.76, 77.19) -- (116.51,100.76);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.65,175.46) -- (132.04,106.97);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (107.04, 58.08) -- (119.61,102.00);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (130.82, 90.58) -- (135.96,108.54);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.96, 83.79) -- (120.25,102.25);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.92,102.02) -- (135.76,108.46);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.54,100.41) -- (122.31,103.08);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 99.71, 32.37) -- (119.65,102.02);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.08, 46.81) -- (122.17,103.02);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (110.92, 55.53) -- (124.83,104.09);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.38,130.03) -- (131.74,106.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.95,179.20) -- (134.55,107.98);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.47,  9.01) -- (133.71,107.64);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.48, 67.81) -- (124.86,104.10);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.35,101.45) -- (116.11,100.60);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.65, 57.86) -- (154.25,115.86);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.51,153.69) -- (116.34,100.69);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (146.85,120.00) -- (144.55,111.98);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.86,110.20) -- (112.72, 99.24);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.25,139.52) -- (117.24,101.05);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.76,141.66) -- (128.41,105.52);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.94,103.57) -- (114.95,100.14);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.35,139.07) -- (123.14,103.41);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (119.19, 69.29) -- (129.71,106.04);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.88,191.15) -- (131.75,106.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.52, 69.16) -- (113.19, 99.43);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.58, 71.80) -- (123.69,103.63);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (140.47,120.08) -- (137.33,109.09);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (140.42,130.22) -- (133.99,107.75);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.83,120.21) -- (129.78,106.07);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.78,106.24) -- (112.78, 99.27);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.07,138.44) -- (128.68,105.63);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.35,141.58) -- (121.20,102.64);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.19, 81.33) -- (130.34,106.29);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (125.19,128.58) -- (117.32,101.08);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.66, 82.08) -- (119.33,101.89);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.57, 72.38) -- (137.05,108.98);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (124.31,114.14) -- (120.99,102.55);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (135.41, 96.73) -- (139.16,109.82);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.15, 77.32) -- (123.69,103.63);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.96, 58.71) -- (128.35,105.50);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.34, 70.01) -- (139.81,110.08);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.26, 46.86) -- (131.40,106.71);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (119.54, 94.98) -- (121.80,102.88);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (127.88,107.08) -- (127.31,105.08);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 94.85,  0.00) -- (124.62,104.00);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 68.26,  0.00) -- ( 94.60, 91.99);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.78, 85.74) -- (120.54,102.37);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.44,141.08) -- (127.11,105.00);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.25,127.65) -- (107.53, 97.17);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.77, 64.90) -- (115.98,100.55);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 97.75, 15.71) -- (122.82,103.28);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (141.88,177.16) -- (120.46,102.34);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.16,124.14) -- (119.84,102.09);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.12,196.67) -- (137.01,108.96);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.70, 50.04) -- (118.44,101.53);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.17, 65.49) -- (128.66,105.62);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (129.01,134.88) -- (119.60,102.00);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (110.41, 33.95) -- (131.23,106.65);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.11,177.59) -- (144.29,111.87);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (102.55, 13.53) -- (128.95,105.74);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (147.93,160.74) -- (132.60,107.20);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.40, 96.73) -- (125.60,104.39);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (145.36,187.60) -- (121.02,102.56);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.44, 67.38) -- (106.90, 96.91);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (141.96,121.60) -- (138.51,109.56);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.48,103.04) -- (123.64,103.61);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (127.06,108.50) -- (125.92,104.52);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.15,116.40) -- (127.99,105.35);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 92.19, 12.13) -- (117.70,101.24);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.56,110.02) -- (115.83,100.49);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.05, 95.13) -- (129.11,105.80);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.16,118.35) -- (128.50,105.55);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.00, 75.82) -- (131.90,106.92);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.34,104.29) circle (  3.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (125.34, 77.94) {{$\color{black}{\bm{y}}$}};
\end{scope}
\end{tikzpicture}
\caption{a caption}
\end{document}

### 2019-08-22 Hierarchical-forecast-reconciliation/Figs/Trash/MinT_justification.tex
Modified schematics of orthogonal and oblique projections

% Created by tikzDevice version 0.12 on 2019-04-26 17:05:14
% !TEX encoding = UTF-8 Unicode
\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (505.89,361.35);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (480.69,312.15);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 88.68, 49.37) --
	( 88.68,302.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (  0.00, 91.62) --
	(505.89, 91.62);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 88.68, 91.62) -- (417.71,165.55);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (404.42,153.31) --
	(417.71,165.55) --
	(400.46,170.93);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (423.71,163.26) {{\huge $\mathfrak{s}$}};
\definecolor{drawColor}{RGB}{255,165,0}
\definecolor{fillColor}{RGB}{255,165,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.18, 99.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 22.11, 23.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.82, 25.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.52,249.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 88.40, 74.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.90,154.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.06, 96.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.85,140.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.71,114.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 88.38, 48.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.09,128.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.36,155.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 39.03, 12.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.88, 38.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 56.17, 28.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 85.80, 54.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 47.41, 52.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.94,150.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.18,139.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 95.80,121.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.02,211.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.25,206.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 82.62, 84.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 83.48, 92.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 83.01, 75.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 82.07,126.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 49.87, 16.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.07,128.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 80.59, 56.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.03, 84.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 34.77, 47.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 82.02,102.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 81.91, 57.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.54, 30.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 85.09, 91.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.07,147.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 23.54,  9.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.37,199.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.50, 94.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 64.66,114.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.23, 94.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 64.90, 41.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.00, 88.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 76.55, 93.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.00,145.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.12, 53.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.25,181.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.97,115.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.02, 85.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 71.46, 60.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.88, 71.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 60.68, 58.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.50,168.18) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 76.49, 80.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.16,172.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 93.92,105.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.24, 44.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 32.17,  1.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.25,161.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.50, 60.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.90,148.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 39.03, 35.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 82.94, 53.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 65.97, 56.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.19,117.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.71,123.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.96,185.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 64.06, 72.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.63,165.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.45,121.76) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.03,142.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 86.52, 93.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.60,129.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 79.80, 90.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.05,115.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.75,111.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.43,143.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 80.42,105.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 80.86, 68.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 57.01, 71.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 65.41, 48.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.98,131.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 65.74, 28.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 60.72,  4.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 44.62,  9.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.12, 94.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.62,177.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.22,122.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.99,101.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.05,100.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.14,151.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.04, 70.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 79.89, 79.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.54,117.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 83.94, 88.32) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 88.68, 91.62) -- (182.69,260.61);

\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (182.98,242.54) --
	(182.69,260.61) --
	(167.19,251.33);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (182.69,266.61) {{\Large ${\bm R}$}};

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (108.22,  0.00) --
	(276.70,302.86);
\definecolor{drawColor}{RGB}{0,0,255}
\definecolor{fillColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (229.69,218.36) circle (  3.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (229.69,236.36) {{\huge $\color{blue}{\hat{\bm{y}}}$}};
\definecolor{drawColor}{RGB}{255,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.26,109.72) circle (  3.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (169.26, 85.99) {{\huge $\color{red}{\tilde{\bm{y}}}$}};
\definecolor{drawColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (229.69,218.36) -- (169.26,109.72);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (168.97,127.79) --
	(169.26,109.72) --
	(184.76,119.01);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.09,104.29) circle (  3.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (145.09, 86.55) {{\huge $\color{black}{\bm{y}}$}};
\end{scope}
\end{tikzpicture}

### 2019-08-22 Hierarchical-forecast-reconciliation/Figs/Orthproj.tex
Rewrite the empirical section and modified some schematics in section 3 and 4

@@
-% Created by tikzDevice version 0.12 on 2019-07-25 19:34:36
+% Created by tikzDevice version 0.12 on 2019-08-21 20:48:49
 % !TEX encoding = UTF-8 Unicode
@@
 \usepackage{amsfonts}
+\usepackage{bm}
+\usepackage{amsfonts}
 \usepackage{bm}\begin{document}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.46, 49.37) --
-	( 75.46,302.86);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.66, 49.37) --
+	( 93.66,302.86);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 12.94, 91.62) --
-	(361.35, 91.62);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.85, 91.62) --
+	(357.70, 91.62);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 75.46, 91.62) -- (294.26,165.55);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 93.66, 91.62) -- (278.49,165.55);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (282.33,151.98) --
-	(294.26,165.55) --
-	(276.55,169.10);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (267.32,151.35) --
+	(278.49,165.55) --
+	(260.61,168.13);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (300.26,163.26) {{\huge $\mathfrak{s}$}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.50] at (284.49,159.81) {{$\huge \mathfrak{s}$}};
 \definecolor{drawColor}{RGB}{190,190,190}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.73,104.11) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.96,163.73) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.96, 97.64) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.08, 11.50) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.75,158.76) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.37, 72.11) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.40,151.64) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.51,120.08) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.23,132.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.10,109.32) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 67.77, 37.36) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.81,177.38) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.74, 64.30) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.12, 95.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.42, 57.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.35,100.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.34,119.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.34,152.96) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.42,110.64) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.76, 86.62) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.22,194.28) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.12, 19.22) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.14,120.23) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.87,146.43) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.75, 94.39) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.46, 17.18) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.46,159.17) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.52, 24.12) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.12, 78.87) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.89, 36.92) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.91,246.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.29, 76.46) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.00, 75.49) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.10, 77.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.54, 44.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.65, 46.02) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.06, 63.01) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.54, 43.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.94, 76.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.82,168.09) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.47,142.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.85,151.63) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.23,157.90) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.42,154.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.43,158.48) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.71,198.70) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.22,161.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.70, 34.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.88, 98.42) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.14,106.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.00, 83.00) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.76, 77.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.04, 85.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.65,175.46) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.87,141.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.04, 58.08) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.00,105.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.82, 90.58) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.17, 88.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.96, 83.79) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.15, -1.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.92,102.02) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.13, 76.86) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.54,100.41) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.24,170.18) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.71, 32.37) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.33, 55.24) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.08, 46.81) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.14, 34.27) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.92, 55.53) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.83, 70.96) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.38,130.03) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.18, 37.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.95,179.20) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.63, 69.09) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.47,  9.01) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.36,141.37) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.48, 67.81) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.54, 10.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.35,101.45) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.31,100.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.65, 57.86) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.09, 96.39) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.51,153.69) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.67,148.26) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.85,120.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.98,130.52) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.86,110.20) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.55, 93.92) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.25,139.52) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.67,184.11) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.76,141.66) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.64,100.10) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.94,103.57) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.87,105.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.35,139.07) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.41,135.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.19, 69.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.14, 59.33) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.88,191.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.14,108.82) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.52, 69.16) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.78,130.30) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.58, 71.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.46,191.20) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.47,120.08) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.08,131.10) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.42,130.22) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.73,129.59) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.83,120.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 77.69, 38.48) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.78,106.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.64,162.50) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.07,138.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.94,188.07) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.35,141.58) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.08,148.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.19, 81.33) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.23,100.64) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.19,128.58) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.40,120.16) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.66, 82.08) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.88,184.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.57, 72.38) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.24,126.18) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.31,114.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.95, 53.81) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.41, 96.73) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.34,121.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.15, 77.32) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.85, 10.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.96, 58.71) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.63, 98.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.34, 70.01) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.24,125.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.26, 46.86) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.52, 18.10) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.54, 94.98) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.96,179.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.88,107.08) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.23,131.81) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.78, 85.74) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.43,161.73) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.44,141.08) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.78,270.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.25,127.65) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.20,114.65) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.77, 64.90) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.39, 82.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 97.75, 15.71) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.64, 54.72) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.88,177.16) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.04, 80.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.16,124.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.26,104.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.12,196.67) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.76, 73.89) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.70, 50.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.08,127.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.17, 65.49) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.98,194.02) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.01,134.88) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.01, 89.21) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.41, 33.95) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.86,135.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.11,177.59) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.03,149.79) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.55, 13.53) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.65, 96.89) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.93,160.74) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.52,153.41) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.40, 96.73) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.68,172.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.36,187.60) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.42,141.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.44, 67.38) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.02,103.15) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.96,121.60) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.57,163.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.48,103.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.23,162.78) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.06,108.50) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.51,128.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.15,116.40) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.37,117.42) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.19, 12.13) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.85,213.31) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.56,110.02) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.12, 87.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.05, 95.13) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.18,169.12) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.16,118.35) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 83.18, 59.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.00, 75.82) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 75.46, 91.62) -- (137.97,260.61);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 93.66, 91.62) -- (146.47,260.61);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (141.02,242.80) --
-	(137.97,260.61) --
-	(124.07,249.07);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (150.42,242.98) --
+	(146.47,260.61) --
+	(133.18,248.37);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (137.97,266.61) {{\Large ${\bm R}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (146.47,266.61) {{${\bm R}$}};
 \definecolor{drawColor}{RGB}{255,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.47,100.41) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.95,118.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.03,100.26) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 57.14, 77.01) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.83,123.51) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.67, 95.62) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.34,117.93) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.37,107.50) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.78,114.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.06,107.78) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 37.19, 78.69) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.06,122.58) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.11, 96.23) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.74, 96.05) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 67.02, 88.77) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 30.63, 66.41) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.30,110.15) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.47,107.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.89,111.36) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.28,122.67) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (199.23,133.44) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.24, 93.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.34,113.20) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 77.83, 85.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.13,101.98) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.03,114.17) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.44,121.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 63.48, 79.55) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.45, 94.66) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 58.20, 77.43) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (241.05,147.57) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.49, 83.95) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.75, 97.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.39, 93.91) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.89, 88.72) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.32, 94.68) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.00, 96.87) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.85, 90.50) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.44, 96.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 82.45, 87.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.51,118.33) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.03,122.97) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.91,121.84) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.41,120.32) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.21,118.23) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.20,116.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.63,126.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.24,127.45) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.02,102.28) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.10, 83.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.79, 98.15) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.93,106.53) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.00,102.95) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.33, 93.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.12,117.19) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.97,126.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.76,104.56) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.59, 89.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.01,100.93) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.87,103.30) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 19.17, 72.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.78, 96.87) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.26, 96.96) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.07,106.58) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.99,121.87) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.36,102.30) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 77.83, 92.42) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 68.87, 81.71) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 48.46, 82.50) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 81.19, 86.63) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 81.92, 93.80) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.42, 89.92) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 55.41, 84.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.64,113.61) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.46, 90.95) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (186.48,128.75) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.82,112.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 61.80, 78.88) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 26.44, 75.05) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.41, 93.52) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.84,103.91) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.73,100.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.19,100.31) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.97, 98.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.15,121.92) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.98,116.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.90,111.70) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.41,114.32) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 95.30, 98.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.71,102.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.98,125.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.29,112.27) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.02,102.28) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.76,116.06) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.52,102.79) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.46,101.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.64,112.29) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.14,113.81) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 76.09, 91.83) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.92, 95.32) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.78,105.24) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (193.21,131.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.01,111.07) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.12, 90.60) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (188.00,129.65) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.48, 94.35) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.92,113.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.34,112.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.35,112.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.37,114.30) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 45.79, 81.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.09,110.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.36,119.63) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.86,101.30) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.13,128.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.60,115.20) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.60,115.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.60,113.99) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.01, 99.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.14, 99.01) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.11,107.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.37,109.10) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.70,126.17) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.89, 96.11) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.14,111.45) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.37, 98.30) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 51.07, 83.38) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.44,105.93) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.23,105.40) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.62,106.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 26.29, 75.01) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.50, 95.96) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 11.37, 69.96) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.24, 91.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  8.62, 69.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.60, 98.39) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.81,106.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.76, 89.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.55,108.88) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.04,100.57) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 43.99, 80.99) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.77,105.66) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.37,126.05) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 24.55, 63.98) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.06,117.16) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 21.01, 62.56) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.54,121.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.42, 97.52) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (255.15,152.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.41,115.52) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.89,104.27) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.75,106.05) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.13, 97.93) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.99, 90.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.56, 92.67) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 58.98, 77.75) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.85, 99.52) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.01,124.16) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.83,103.57) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.92,108.52) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.00, 96.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (200.95,134.54) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.02,110.05) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 80.90, 86.52) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (202.09,134.41) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.40, 93.92) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.08,101.29) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.57,111.58) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.31,117.25) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.23, 85.45) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.35,119.63) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.20,131.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.13,104.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 61.73, 78.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.88,115.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.64,122.81) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.22,125.67) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.01,102.16) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.97,112.40) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.01,127.36) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.93,104.62) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 85.37, 88.30) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.12,120.90) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.29,113.07) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.80,120.12) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.22,103.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.05,112.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.82,105.68) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.46,109.19) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.04,108.57) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (204.61,135.26) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 52.74, 75.25) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.34, 96.31) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.78,103.27) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.71,126.51) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.33,102.69) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 62.36, 87.19) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.82,109.28) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.23, 97.85) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.73,104.11) -- (101.47,100.41);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.96,163.73) -- (161.95,118.94);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (102.96, 97.64) -- (101.03,100.26);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.08, 11.50) -- ( 57.14, 77.01);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.75,158.76) -- (169.83,123.51);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.37, 72.11) -- (103.67, 95.62);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.40,151.64) -- (153.34,117.93);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (125.51,120.08) -- (133.37,107.50);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.23,132.34) -- (141.78,114.03);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.10,109.32) -- (134.06,107.78);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 67.77, 37.36) -- ( 37.19, 78.69);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.81,177.38) -- (171.06,122.58);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (112.74, 64.30) -- ( 89.11, 96.23);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.12, 95.44) -- (104.74, 96.05);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 90.42, 57.14) -- ( 67.02, 88.77);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.14,  0.00) -- ( 30.63, 66.41);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.34,119.54) -- (130.30,110.15);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.35,100.94) -- (132.47,107.14);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (134.42,110.64) -- (133.89,111.36);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (152.34,152.96) -- (171.28,122.67);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.22,194.28) -- (199.23,133.44);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.76, 86.62) -- ( 99.24, 93.85);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (134.14,120.23) -- (139.34,113.20);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (119.12, 19.22) -- ( 77.83, 85.29);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (111.75, 94.39) -- (106.13,101.98);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (129.87,146.43) -- (150.03,114.17);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (135.46,159.17) -- (163.44,121.35);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (102.46, 17.18) -- ( 63.48, 79.55);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 96.12, 78.87) -- ( 84.45, 94.66);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 91.52, 24.12) -- ( 58.20, 77.43);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.91,246.43) -- (241.05,147.57);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.89, 36.92) -- ( 74.49, 83.95);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.00, 75.49) -- ( 92.75, 97.46);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (110.29, 76.46) -- ( 99.39, 93.91);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 99.54, 44.60) -- ( 66.89, 88.72);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (112.10, 77.44) -- (101.32, 94.68);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.06, 63.01) -- ( 91.00, 96.87);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.65, 46.02) -- ( 90.85, 90.50);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.94, 76.74) -- ( 89.44, 96.34);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.54, 43.80) -- ( 82.45, 87.14);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.47,142.71) -- (154.51,118.33);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.82,168.09) -- (172.03,122.97);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.23,157.90) -- (164.91,121.84);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (145.85,151.63) -- (165.41,120.32);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (124.43,158.48) -- (154.21,118.23);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.42,154.29) -- (155.20,116.24);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.22,161.85) -- (177.63,126.14);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.71,198.70) -- (183.24,127.45);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.88, 98.42) -- (107.02,102.28);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.70, 34.85) -- ( 74.10, 83.80);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.00, 83.00) -- ( 94.79, 98.15);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.14,106.19) -- (130.93,106.53);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (122.04, 85.32) -- (109.00,102.95);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.76, 77.19) -- ( 99.33, 93.89);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.87,141.85) -- (151.12,117.19);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.65,175.46) -- (181.97,126.94);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.00,105.58) -- (113.76,104.56);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (107.04, 58.08) -- ( 87.59, 89.19);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (112.17, 88.54) -- (103.01,100.93);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (130.82, 90.58) -- (122.87,103.30);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.89,  0.00) -- ( 19.17, 72.60);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.96, 83.79) -- (106.78, 96.87);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.13, 76.86) -- ( 91.26, 96.96);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.92,102.02) -- (131.07,106.58);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (129.24,170.18) -- (164.99,121.87);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.54,100.41) -- (120.36,102.30);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.33, 55.24) -- ( 77.83, 92.42);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 99.71, 32.37) -- ( 68.87, 81.71);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 84.14, 34.27) -- ( 48.46, 82.50);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.08, 46.81) -- ( 81.19, 86.63);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.83, 70.96) -- ( 81.92, 93.80);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (110.92, 55.53) -- ( 89.42, 89.92);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 90.18, 37.85) -- ( 55.41, 84.85);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.38,130.03) -- (148.64,113.61);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 89.63, 69.09) -- ( 73.46, 90.95);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.95,179.20) -- (186.48,128.75);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.36,141.37) -- (136.82,112.35);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.47,  9.01) -- ( 61.80, 78.88);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 74.54, 10.03) -- ( 26.44, 75.05);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.48, 67.81) -- ( 98.41, 93.52);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.31,100.58) -- (111.84,103.91);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.35,101.45) -- (116.73,100.85);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.09, 96.39) -- (101.19,100.31);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.65, 57.86) -- (111.97, 98.94);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (145.67,148.26) -- (165.15,121.92);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.51,153.69) -- (154.98,116.15);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (120.98,130.52) -- (134.90,111.70);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (146.85,120.00) -- (150.41,114.32);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 21.96,  0.00) -- (  0.00, 29.67);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.86,110.20) -- (120.71,102.44);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.55, 93.92) -- ( 95.30, 98.32);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.25,139.52) -- (145.29,112.27);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.67,184.11) -- (175.98,125.58);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.76,141.66) -- (154.76,116.06);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (108.64,100.10) -- (107.02,102.28);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.94,103.57) -- (117.46,101.14);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.87,105.03) -- (108.52,102.79);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.35,139.07) -- (149.14,113.81);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (119.41,135.58) -- (136.64,112.29);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (119.19, 69.29) -- (102.92, 95.32);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (100.14, 59.33) -- ( 76.09, 91.83);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.88,191.15) -- (193.21,131.44);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.14,108.82) -- (115.78,105.24);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.52, 69.16) -- ( 91.12, 90.60);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.78,130.30) -- (133.01,111.07);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.58, 71.80) -- (100.48, 94.35);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (142.46,191.20) -- (188.00,129.65);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (140.47,120.08) -- (145.34,112.29);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.08,131.10) -- (140.92,113.74);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (140.42,130.22) -- (150.37,114.30);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (124.73,129.59) -- (137.35,112.53);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.83,120.21) -- (140.09,110.19);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 77.69, 38.48) -- ( 45.79, 81.60);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.78,106.24) -- (117.86,101.30);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.64,162.50) -- (158.36,119.63);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.07,138.44) -- (152.60,115.20);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (139.94,188.07) -- (184.13,128.34);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.35,141.58) -- (149.60,113.99);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.08,148.46) -- (145.60,115.32);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.19, 81.33) -- (112.14, 99.01);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.23,100.64) -- ( 99.01, 99.58);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (125.19,128.58) -- (137.37,109.10);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (111.40,120.16) -- (121.11,107.04);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.66, 82.08) -- (104.89, 96.11);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (134.88,184.04) -- (177.70,126.17);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.57, 72.38) -- (110.37, 98.30);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.24,126.18) -- (134.14,111.45);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (124.31,114.14) -- (129.44,105.93);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.95, 53.81) -- ( 51.07, 83.38);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (135.41, 96.73) -- (129.62,106.00);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.34,121.46) -- (116.23,105.40);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.15, 77.32) -- (104.50, 95.96);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 73.85, 10.74) -- ( 26.29, 75.01);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.96, 58.71) -- ( 94.24, 91.85);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 63.13,  0.00) -- ( 11.37, 69.96);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.34, 70.01) -- (110.60, 98.39);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 59.69,  0.00) -- (  8.62, 69.03);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.26, 46.86) -- ( 87.76, 89.26);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (125.63, 98.74) -- (119.81,106.60);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (119.54, 94.98) -- (116.04,100.57);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.24,125.53) -- (126.55,108.88);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (127.88,107.08) -- (128.77,105.66);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 90.52, 18.10) -- ( 43.99, 80.99);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 64.54,  0.00) -- ( 24.55, 63.98);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.96,179.32) -- (177.37,126.05);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 60.10,  0.00) -- ( 21.01, 62.56);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (140.23,131.81) -- (151.06,117.16);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.78, 85.74) -- (108.42, 97.52);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.43,161.73) -- (162.54,121.04);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.44,141.08) -- (153.41,115.52);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.78,270.43) -- (255.15,152.34);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.25,127.65) -- (129.75,106.05);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.20,114.65) -- (112.89,104.27);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.77, 64.90) -- ( 89.99, 90.15);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.39, 82.71) -- ( 94.13, 97.93);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 97.75, 15.71) -- ( 58.98, 77.75);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.64, 54.72) -- ( 78.56, 92.67);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (141.88,177.16) -- (175.01,124.16);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.04, 80.34) -- ( 98.85, 99.52);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.16,124.14) -- (135.92,108.52);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (110.26,104.34) -- (110.83,103.57);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.12,196.67) -- (200.95,134.54);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.76, 73.89) -- ( 90.00, 96.53);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.70, 50.04) -- ( 80.90, 86.52);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.08,127.54) -- (130.02,110.05);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.17, 65.49) -- ( 99.40, 93.92);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (157.98,194.02) -- (202.09,134.41);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (129.01,134.88) -- (143.57,111.58);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.01, 89.21) -- (104.08,101.29);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (110.41, 33.95) -- ( 78.23, 85.45);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.86,135.43) -- (151.31,117.25);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.11,177.59) -- (192.20,131.04);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.03,149.79) -- (158.35,119.63);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (102.55, 13.53) -- ( 61.73, 78.85);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.65, 96.89) -- (113.13,104.35);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (147.93,160.74) -- (171.64,122.81);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.52,153.41) -- (144.88,115.08);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.40, 96.73) -- (120.01,102.16);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (141.68,172.35) -- (176.22,125.67);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (145.36,187.60) -- (183.01,127.36);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.42,141.54) -- (136.97,112.40);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.44, 67.38) -- ( 85.37, 88.30);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.02,103.15) -- (113.93,104.62);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (141.96,121.60) -- (147.29,113.07);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (130.57,163.54) -- (162.12,120.90);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.48,103.04) -- (123.22,103.44);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.23,162.78) -- (159.80,120.12);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (127.06,108.50) -- (128.82,105.68);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (125.51,128.03) -- (137.05,112.43);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.15,116.40) -- (136.04,108.57);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.37,117.42) -- (127.46,109.19);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 92.19, 12.13) -- ( 52.74, 75.25);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (146.85,213.31) -- (204.61,135.26);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.56,110.02) -- (122.78,103.27);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 96.12, 87.14) -- ( 89.34, 96.31);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.05, 95.13) -- (121.33,102.69);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (147.18,169.12) -- (178.71,126.51);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.16,118.35) -- (137.82,109.28);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 83.18, 59.04) -- ( 62.36, 87.19);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.00, 75.82) -- (109.23, 97.85);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.97,104.29) circle (  3.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.34,104.29) circle (  3.00);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (112.97, 86.55) {{\huge $\color{black}{\bm{y}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (125.34, 77.94) {{$\color{black}{\bm{y}}$}};
 \end{scope}
 \end{tikzpicture}
-
+\caption{a caption}
 \end{document}

### 2019-08-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Rewrite the empirical section and modified some schematics in section 3 and 4

@@
 
-	To clarify these concepts consider the example of the hierarchy in Figure~\ref{fig:basichier}.
+	To clarify these concepts consider the example of the hierarchy in Figure \ref{fig:basichier}.
 For this hierarchy, $n=7$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$ and
@@
 It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$.
-In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.
+In Figure \ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.
 However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom level series, $y_{A,t}$ and $y_{B,t}$.
@@
 Also notable by its absence in the above definition is any reference to {\em aggregation}.
-In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure~\ref{fig:basichier} and/or do not involve aggregation.
+In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure\ref{fig:basichier} and/or do not involve aggregation.
 {\bf Include brief summary of all non-traditional hierarchies - e.g.
@@
 %	It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$.
-Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.
+Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure \ref{fig2}.
 %	
@@
 
-	The simple geometric intuition behind the proof is demonstrated in Figure~\ref{fig:Schematic_OLSRecon}.
+	The simple geometric intuition behind the proof is demonstrated in Figure \ref{fig:Schematic_OLSRecon}.
 In this schematic, the coherent subspace is depicted as a black arrow.
@@
 
-	Figure~\ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle with $\tilde{y}$ at the right-angled vertex.
+	Figure \ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle with $\tilde{y}$ at the right-angled vertex.
 In this triangle the line between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.
@@
 
-	{\bf Discuss results in Figure 11 here}
+	{\bf Discuss results in Figure 4 here}
+
+	\begin{figure}[H]
+		\centering
+		\small
+		\includegraphics[width = \textwidth]{Figs/BaseVsRecon_Emp_results.pdf}
+		\caption{Difference of MSE between Base forecasts and reconciled forecasts over the replications is presented.
+Positive values of the difference implies reconciliation improves the forecast accuracy than base forecasts.}\label{fig:BaseVSRecon_Fc}
+	\end{figure}
 
@@
 
-	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.
+	Figure \ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.
 Suppose the in-sample errors are given by the orange points.
@@
 This direction is denoted by $\bm{R}$.
-Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).
+Figure \ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).
 One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.
@@
 
-	\begin{figure}[H]
-		\centering
-		%\vspace{-0.9cm}
-		\small
-		\resizebox{\linewidth}{!}{
-			\input{Figs/insampledir}
-		}
-		\caption{A schematic to represent MinT reconciliation.
+%	\begin{figure}[H]
+%		\centering
+%		%\vspace{-0.9cm}
+%		\small
+%		\resizebox{\linewidth}{!}{
+%			\input{Figs/insampledir}
+%		}
+%		\caption{A schematic to represent MinT reconciliation.
 Points in orange colour represent the insample errors.
@@
 $\hat{\bm{y}}$ is projected onto $\mathfrak{s}$ along the the direction of $\bm{R}$.}\label{fig:MinT_justification1}
-	\end{figure}
-
-	\begin{figure}[H]
-		\centering
-		%\vspace{-0.9cm}
-		\small
-		\resizebox{\linewidth}{!}{
-			\input{Figs/oblique_justification2}
-		}
-		\caption{A schematic to represent MinT reconciliation.
+%	\end{figure}
+%		
+%	\begin{figure}[H]
+%		\centering
+%		%\vspace{-0.9cm}
+%		\small
+%		\resizebox{\linewidth}{!}{
+%			\input{Figs/oblique_justification2}
+%		}
+%		\caption{A schematic to represent MinT reconciliation.
 Grey points indicate potential realisations of the base forecast while the blue dot indicates one such realisation.
 The black dot ${\bm y}$ denotes the (unknown) target of the forecast.}\label{fig:MinT_justification2}
-	\end{figure}
+%	\end{figure}
+%	
+%	\begin{figure}[H]
+%		\centering
+%		%\vspace{-0.9cm}
+%		\small
+%		\resizebox{\linewidth}{!}{
+%			\includegraphics{Figs/OrthProj.pdf}}
+%		\caption{All gray points are orthogonally projected onto the coherent subspace $\mathfrak{s}$.
+Reconciled forecasts marked in red dots are widely spread about the target $\bm{y}$.}\label{fig:Orthogonal_projection_all_points}
+%	\end{figure}
+%	
+%	
+%	\begin{figure}[H] 
+%	\centering
+%	%\vspace{-0.9cm}
+%	\small
+%	\resizebox{\linewidth}{!}{
+%		\includegraphics{Figs/ObliqueProjection.pdf}}
+%	\caption{All gray points are obliquely projected along the direction of $\bm{R}$.
+Reconciled points denoted in red dots are concentrated about the target $\bm{y}$.}\label{fig:Oblique_projection_all_points}
+%	\end{figure}
 
-	\begin{figure}[H]
+%%%%%%%%%%%%%%%%%%%
+
+	\begin{figure}
 		\centering
-		%\vspace{-0.9cm}
-		\small
-		\resizebox{\linewidth}{!}{
-			\includegraphics{Figs/OrthProj.pdf}}
-		\caption{All gray points are orthogonally projected onto the coherent subspace $\mathfrak{s}$.
-Reconciled forecasts marked in red dots are widely spread about the target $\bm{y}$.}\label{fig:Orthogonal_projection_all_points}
-	\end{figure}
+		\begin{subfigure}[t]{0.45\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{Figs/InsampDir_1.pdf} 
+%			\label{fig:InsampDir_1}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.45\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{Figs/InsampDir_2.pdf} 
+%			\label{fig:InsampDir_2}
+		\end{subfigure}
 
-	\begin{figure}[H] 
+		\vspace{1cm}
+
+		\begin{subfigure}[t]{0.45\textwidth}
 			\centering
-	%\vspace{-0.9cm}
-	\small
-	\resizebox{\linewidth}{!}{
-		\includegraphics{Figs/ObliqueProjection.pdf}}
-	\caption{All gray points are obliquely projected along the direction of $\bm{R}$.
-Reconciled points denoted in red dots are concentrated about the target $\bm{y}$.}\label{fig:Oblique_projection_all_points}
+			\includegraphics[width=\linewidth]{Figs/OrthProj.pdf} 
+%			\label{fig:OrthProj}
+		\end{subfigure}
+		\hfill
+		\begin{subfigure}[t]{0.5\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{Figs/ObliqProj.pdf} 
+%			\label{fig:ObliqProj}
+		\end{subfigure}
+
+%		\begin{subfigure}[t]{\textwidth}
+%			\centering
+%			\includegraphics[width=\linewidth]{example-image-c.pdf} 
+%			\caption{Price regulation} \label{fig:timing3}
+%		\end{subfigure}
+		\caption{A schematic to represent orthogonal and oblique reconciliation.
+Points in orange colour in top left figure represent the insample errors.
+$\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$.
+Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation.
+The black dot ${\bm y}$ denotes the (unknown) target of the forecast.
+Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection}
 	\end{figure}
@@
 Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$,  $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$.
-This is depicted in Figure~\ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.
+This is depicted in Figure \ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.
 In this case, the expectation of reconciled forecast will be $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and hence biased.
@@
 Opening the door to reconciliation methods that change already coherent base forecast would seem to suggest an increase in the variability of the forecast.
-This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance is to reduce variance.
+This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance.
 
@@
 Geometrically, the intuition is simple.
-In Figure~\ref{fig:MinT_justification1}, the orange points are centered around the origin as would be expected from an unbiased forecast.
+In top left panel in Figure \ref{fig:OthogonalVSOblique_projection}, the orange points are centered around the origin as would be expected from an unbiased forecast.
 If forecasts are biased, then errors should simply be translated until they are centered at the origin.
@@
 
-	Total tourism flow of any country can naturally disaggregate along a geographical hierarchy.
-Producing accurate forecasts for these hierarchical time series while preserving the coherency is important for making align business decisions in the tourism industry.
-Many applications related to Australian tourism flow have pronounced that reconciliation improves the point forecast accuracy (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}).
+	Using an empirical application to forecast Australian domestic tourism flow, we illustrate the usefulness of projection based reconciliation in practice.
+Previous studies have pronounced that the reconciliation improves point forecast accuracy in domestic tourism flow in Australia (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}).
+However, our motivation in this study is to demonstrate how the bias correction methods discussed in previous section along with the projection-based reconciliation help to improve the forecast accuracy.
 
-	Using a similar empirical application to tourism forecasting in Australia, we show how to use projection-based reconciliation when we have a set of biased incoherent forecasts.
-As we mentioned in the previous section our focus is to bias adjust the incoherent forecasts first and then do the reconciliation.
+	\subsection{Data}
 
-	\subsubsection*{Data:}
 	We use ``overnight trips" as a measure of domestic tourism flow in Australia.
@@
 
-	We produce $h=1$ to $h=6$ months ahead forecasts using a rolling window approach.
-First training window of $100$ observations is considered from Jan-$1998$ to Apr-$2006$ and produce forecasts for May-$2006$ to Oct-$2006$.
+	As we can see from the time plots in Figure \ref{fig:Total_TSplots}, the total overnight trips has a strong seasonal pattern.
+Most overnight trips seems to be happening in January which is associated with the summer season in southern hemisphere.
+On the other hand the least trips are happening in February perhaps due to the end of summer holidays.
+We could also observe a slight downward trend in total overnight trips from 2005 to 2010 and then started increasing since 2010.
+
+	Figure \ref{fig:States_Zones_Regs_TSplots} shows time plots for some selected series from states, zones and regions of the hierarchy.
+While observing the series in state level, we could see that Northern Territory(NT) has a different seasonal patterns compared to the other states.
+Highest overnight trips to NT happens during June - August where July being the peak.
+Lowest trips happens during December - February.
+This is perhaps Australians prefer to visit North of Australia during its dry season rather than in wet season.
+This pattern also reflect in zones and regions associated to NT as well as regions in north Queensland.
+All other states and their associated zones and regions show peak overnight trips in January.
+
+	Further we noticed that the signal-to-noise ratio decreases with the level of disaggregation of the hierarchy.
+We can see much noisier series in regional and zone levels whereas the noise is comparatively stabilised in the upper levels.
+We have also observed that the overnight trips to `Adelaide Hills' has an anomalous observation on December-2002.
+We replace this observation with the average overnight trips on December-2001 and December-2003 for the same destination.
+
+	Using this data we produce $h=1$ to $h=6$ month ahead forecasts based on a rolling window approach.
+First a training window of $100$ observations is considered from Jan-$1998$ to Apr-$2006$ and  forecasts produce for May-$2006$ to Oct-$2006$.
 Then we roll the training window one month at a time where the final forecast is produced for Dec-$2017$.
-This directs to $140 \quad 1$-step-ahead, $139 \quad 2$-step-ahead through $135 \quad 6$-step-ahead forecasts left for evaluation.
-
-	\subsubsection*{Preliminary analysis:}
-
-	While observing the patterns of individual series, we noticed that the signal-to-noise ratio decreases with the disaggregate level of the hierarchy.
-From Figure \ref{fig:Total_TSplots} and \ref{fig:States_Zones_Regs_TSplots} this is depicted well as we see much noisier series in bottom levels whereas the noise level is comparatively stabilised in the upper levels.
-We have also observed that the overnight trips for `Adelaide Hills` has an anomalous observation on December-2002.
-We replaced this observation with the average overnight trips on December-2001 and December-2003 for the same destination.
+This leads to $140 \quad 1$-step-ahead, $139 \quad 2$-step-ahead through $135 \quad 6$-step-ahead forecasts left for evaluation.
 
@@
 		\small
-		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/Total_TSplot.pdf}
-		\caption{Time plot for total overnight trips.}\label{fig:Total_TSplots}
+		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/Total_TSplots.pdf}
+		\caption{Total overnight trips are presented in log scale.
+Top panel shows the time plot.
+Bottom left panel shows the sub-series plot for each month whereas bottom right panel shows the seasonal plot coloured by year  }\label{fig:Total_TSplots}
 	\end{figure}
@@
 		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots.pdf}
-		\caption{Time plot for some selected series from different disaggregate levels of the hierarchy.}\label{fig:States_Zones_Regs_TSplots}
+		\caption{Time plot of overnight trips for some selected series from different disaggregate levels of the hierarchy.
+All values are presented in log scale.
+To avoid impact from the zero values we added a constant 1 to all observations}\label{fig:States_Zones_Regs_TSplots}
 	\end{figure}
 
-	\subsubsection*{Base forecasts and reconciliation:}
+	\subsection{Base forecasts and reconciliation:}
 
-	We first transform each series in the hierarchy using the Box-Cox transformation as given in equation (\ref{eq:BoxCox_transformation}) to stabilise any variations in the data.
+	First we transform each series in the hierarchy to stabilise any variations in the data.
+We use two types of transformation, namely, log transformation and more general Box-Cox transformation.
+Equation (\ref{eq:BoxCox_transformation}) gives the mathematical formula for these transformations.
+A constant is added to each series to avoid the impact of zero observations when taking log transformations.
+We note here that the two transformations were applied separately to the series in the hierarchy and treated distinctly.
 
@@
 	\begin{cases} 
-	\log(y_t) & \text{if } \lambda = 0 \\
-	\frac{y_t^\lambda - 1}{\lambda}  & \text{if } \lambda \ne 0
+	\log(y_t) & \text{if log transformation, $\lambda = 0$} \\
+	\frac{y_t^\lambda - 1}{\lambda}  & \text{if Box-Cox transformation, $\lambda \ne 0$} 
 	\end{cases}
@@
 
-	We use "guerrero" method \citep{guerrero1993time} implemented in \verb|BoxCox.lambda()| function in \verb|forecast| package R software \citep{Rforecast} to select optimal $\lambda$.
+	The ``Guerrero" method \citep{guerrero1993time} implemented in \verb|BoxCox.lambda()| function in \verb|forecast| package in R software \citep{Rforecast} is use to select optimal $\lambda$ for Box-Cox transformation.
+For log transformation we simply choose $\lambda = 0$.
 Then  we fit univariate ARIMA models for the transformed series.
-We use \verb|auto.arima()| function in \verb|forecast| package to choose the best model that minimises the AIC.
-Using the fitted models we produce $h=1,...,6$ months ahead forecasts for each series in the hierarchy.
+\verb|auto.arima()| function in \verb|forecast| package is use to choose the best model that minimises the AIC.
+Using the fitted models, forecasts are produced for $6$ forecast horizons for each series in the hierarchy.
 These forecasts are then back-transformed using equation (\ref{eq:BoxCox_back-transformation}) to scale them back into the original space.
-However, the back transformed forecasts will be biased \citep{FPP2018}.
+However, the back transformed forecasts will be biased \citep{guerrero1993time}.
 
@@
 	\begin{cases} 
-	\exp({x_{t+h}}) & \text{if } \lambda = 0 \\
-	(\lambda x_{t+h} + 1)^{1/\lambda}  & \text{if } \lambda \ne 0
+	\exp({x_{t+h}}) & \text{if log transformation, $\lambda = 0$} \\
+	(\lambda x_{t+h} + 1)^{1/\lambda}  & \text{if Box-Cox transformation, $\lambda \ne 0$}
 	\end{cases}
@@
 
-	Hence the reconciled forecasts follow from these will also biased.
+	Hence the reconciled forecasts that follow from these forecasts will also be biased.
 This is the exact scenario that we want to demonstrate in this study.
-As we proposed before, we first bias correct the base forecasts prior to the reconciliation.
-We use the mathematical formula in equation (\ref{eq:BoxCox_BT_biasadj}) to calculate the back-transformed and bias-adjusted forecasts.
+As proposed before, we first adjust for the bias in base forecasts prior to the reconciliation.
+We use the de-biasing factor proposed by \cite{taylor1986retransformed} to calculate the back-transformed bias-adjusted forecasts.
+These are given in equation (\ref{eq:BoxCox_BT_biasadj}) .
 
@@
 	\begin{cases} 
-	\exp({x_{t+h}})[1+\frac{\sigma_h^2}{2}] & \text{if } \lambda = 0 \\
-	(\lambda x_{t+h} + 1)^{1/\lambda}[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda x_{t+h} + 1)^2}]       & \text{if } \lambda \ne 0
+	\exp({x_{t+h}})[1+\frac{\sigma_h^2}{2}] & \text{if log transformation, $\lambda = 0$} \\
+	(\lambda x_{t+h} + 1)^{1/\lambda}[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda x_{t+h} + 1)^2}]       & \text{if Box-Cox transformation, $\lambda \ne 0$}
 	\end{cases}
 	\end{equation}
-	where, $x_{t+h}$ is the $h$-step-ahead forecasts from the Box-Cox transformed series and $\sigma_h^2$ is the variance of $x_{t+h}$.
+	where, $x_{t+h}$ is the $h$-step-ahead forecasts from the log/Box-Cox transformed series and $\sigma_h^2$ is the variance of $x_{t+h}$.
+Unbiased forecasts from this method is referred to as Unbiased (Method-1).
+We also applied a more general bias adjustment method by estimating the bias using in-sample residual means as explained in Section \ref{sec:BiasInRecon}.
+Unbiased forecasts from this general method is referred to as Unbiased (Method-2).\todo{Should we give more concise words for these two methods??}
 
 	Once we get the base forecasts for all series in the hierarchy, we can do the projection-based reconciliation to get coherent forecasts.
-We reconcile both biased and bias-corrected (unbiased) base forecasts to demonstrate how the reconciliation follows from unbiased base forecasts improves the forecast accuracy.
+We reconcile both biased and bias-corrected (Unbiased) base forecasts to demonstrate how the reconciliation follows from unbiased base forecasts improves the forecast accuracy.
 MinT(Shrink), WLS, OLS and bottom-up methods are used for reconciliation.
 
-	\subsubsection*{Results and discussion:}
+%	
+%	\begin{table}
+%		\caption {Average {MSE($\times 10^3$)} of base and reconciled point forecasts at forecasts horizons $h=1,...,6$ are presented.
+Bias and unbiased columns represent the results for biased-base/biased-reconciled and unbiased-base/unbiased-reconciled forecasts respectively.
+Comparisons can be made across biased vs unbiased forecasts as well as base vs reconciled forecasts.}
+%		\label{tab:Results_MSE}
+%		\centering\tabcolsep=0.08cm
+%		\resizebox{\linewidth}{!}{
+%		\begin{tabular}{@{}lSSSSSSSSSSSS@{}}
+%			\toprule
+%			\multicolumn{1}{c}{ } & \multicolumn{2}{c}{h=1} & \multicolumn{2}{c}{h=2} & \multicolumn{2}{c}{h=3} & \multicolumn{2}{c}{h=4} & \multicolumn{2}{c}{h=5} & \multicolumn{2}{c}{h=6} \\
+%			\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11} \cmidrule(lr){12-13}
+%			Method & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased\\
+%			\midrule
+%			Base & 12.18 & 161.63 & 13.14 & 243.13 & 14.08 & 269.20 & 15.88 & 325.41 & 15.49 & 332.11 & 15.79 & 344.40\\
+%			\hline
+%			MinT(Shrink) & 10.14 & $\bm{9.96}$ & 11.47 & $\bm{10.78}$ & 12.55 & $\bm{11.94}$ & 15.53 & $\bm{14.03}$ & 14.63 & $\bm{13.46}$ & 15.28 & $\bm{13.78}$\\
+%			\hline
+%			WLS & 15.62 & 13.97 & 15.93 & 13.71 & 16.65 & 14.50 & 18.91 & 16.26 & 18.76 & 16.20 & 18.85 & 15.83\\	
+%			\hline
+%			OLS & 11.73 & 135.17 & 12.80 & 204.42 & 13.73 & 225.59 & 15.56 & 272.41 & 15.17 & 278.08 & 15.49 & 288.21\\
+%			\hline
+%			Bottom-up & 17.86 & 15.55 & 17.86 & 14.90 & 18.47 & 15.61 & 20.50 & 17.21 & 20.34 & 17.04 & 20.39 & 16.69\\
+%			
+%			\bottomrule
+%		\end{tabular}
+%	}
+%	\end{table}
 
-	Mean Squared Error (MSE) is used to measure the forecast accuracy and results are presented in Table \ref{tab:Results_MSE}.
+%%%%%%%%%%%%%%%%%%%
+
+\subsection{Results and discussion}
+
+%	Mean Squared Error (MSE) is used to measure the forecast accuracy and results are presented in Table \ref{tab:Results_MSE}.
 Recall that projections preserve the unbiasedness in reconciled forecasts only if the base forecasts are unbiased.
@@
 \begin{table}
-		\caption {Average {MSE($\times 10^3$)} of base and reconciled point forecasts at forecasts horizons $h=1,...,6$ are presented.
-Bias and unbiased columns represent the results for biased-base/biased-reconciled and unbiased-base/unbiased-reconciled forecasts respectively.
-Comparisons can be made across biased vs unbiased forecasts as well as base vs reconciled forecasts.}
+	\caption {Average {MSE($\times 10^3$)} of base and reconciled $1$-step-ahead point forecasts are presented for log transformation and Box-Cox transformation.
+Unbiased(Method-1) follows from the bias adjustment via Taylor's de-biasing factor whereas Unbiased(Method-2) follows from residual mean adjustment.}
 	\label{tab:Results_MSE}
-		\centering\tabcolsep=0.08cm
+	\centering
+
 	\resizebox{\linewidth}{!}{
-		\begin{tabular}{@{}lSSSSSSSSSSSS@{}}
+		\begin{tabular}{@{}lcccccc@{}}
 			\toprule
-			\multicolumn{1}{c}{ } & \multicolumn{2}{c}{h=1} & \multicolumn{2}{c}{h=2} & \multicolumn{2}{c}{h=3} & \multicolumn{2}{c}{h=4} & \multicolumn{2}{c}{h=5} & \multicolumn{2}{c}{h=6} \\
-			\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11} \cmidrule(lr){12-13}
-			Method & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased\\
+			\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Log Transformation} &
+			\multicolumn{3}{c}{Box-Cox Transformation}\\
+			\cmidrule(lr){2-4} \cmidrule(lr){5-7}
+			R.method & Biased & Unbiased & Unbiased & Biased & Unbiased & Unbiased \\
+			& & (Method-1) & (Method-2) && (Method-1) &(Method-2)\\
 			\midrule
-			Base & 12.18 & 161.63 & 13.14 & 243.13 & 14.08 & 269.20 & 15.88 & 325.41 & 15.49 & 332.11 & 15.79 & 344.40\\
+			Base & 12.06 & 11.87 & 12.52 & 12.27 & 139.94 & 13.45\\
 			\hline
-			MinT(Shrink) & 10.14 & $\bm{9.96}$ & 11.47 & $\bm{10.78}$ & 12.55 & $\bm{11.94}$ & 15.53 & $\bm{14.03}$ & 14.63 & $\bm{13.46}$ & 15.28 & $\bm{13.78}$\\
+			Bottom-up & 17.37 & 15.47 & 21.58 & 18.06 & 15.76 & 23.33\\
 			\hline
-			WLS & 15.62 & 13.97 & 15.93 & 13.71 & 16.65 & 14.50 & 18.91 & 16.26 & 18.76 & 16.20 & 18.85 & 15.83\\	
+			OLS & 11.59 & 11.41 & 11.98 & 11.84 & 116.91 & 12.96\\
 			\hline
-			OLS & 11.73 & 135.17 & 12.80 & 204.42 & 13.73 & 225.59 & 15.56 & 272.41 & 15.17 & 278.08 & 15.49 & 288.21\\
+			WLS & 15.00 & 13.83 & 17.55 & 15.83 & 14.20 & 19.51\\
 			\hline
-			Bottom-up & 17.86 & 15.55 & 17.86 & 14.90 & 18.47 & 15.61 & 20.50 & 17.21 & 20.34 & 17.04 & 20.39 & 16.69\\
-
+			MinT(Shrink) & 9.36 & $\bm{9.25}$ & 10.35 & 10.27 & $\bm{10.11}$ & 12.43\\
 			\bottomrule
@@
 	}
+
 \end{table}
 
+Mean Squared Error (MSE) is used to measure the forecast accuracy.
+Average MSE over $140$ replications for $1$-step-ahead forecasts are presented for log transformation and Box-Cox transformation separately in Table \ref{tab:Results_MSE}.
+
+Let us first consider the results from log transformation.
+We see that the unbiased forecasts from Method-1 has less MSE compared to the biased forecasts in base level.
+This holds for all reconciled forecasts as well.
+It implies that the bias correction has improved the forecast accuracy.
+Further, unbiased reconciled forecasts from OLS and MinT perform better than the base forecasts.
+Moreover, Unbiased MinT reconciled forecasts are outperforming.
+We also note that the bias correction via Method-2 has not necessarily work well in this empirical example.
+
+Now turning to the results from Box-Cox transformation, we see that the bias correction via Method-1 has worsen the base forecasts.
+The same result holds for OLS reconciled forecasts as well.
+We also observed that this has happened because the bias correction is doing worst for some replications in ``Total" series as depicted in Figure \ref{fig:Total_FcVsTrue_BoxCox}.
+\textcolor{red}{This because for these replications the selected model has a drift term with a very large standard error.
+This will blow up the bias-adjusted forecasts.}
+
+However reconciled forecast from, Bottom-up, WLS or MinT has mitigate the effect from this unusual result in unbiased base forecasts. Most importantly, Unbiased MinT is outperforming all forecasts.
+
+We have presented results only for one forecast horizon. However, results for other forecast horizons follows the same conclusions.
+
+\begin{figure}
+	\centering
+	\small
+	\includegraphics[width = \textwidth]{Empirical-results/Final-results/Total_FcVsTrue_BoxCox.pdf}
+	\caption{Actual values vs the base forecasts for Total overnight trips follows from Box-Cox transformation}\label{fig:Total_FcVsTrue_BoxCox}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%
+
+%\begin{table}
+%	\caption {\textcolor{red}{RESULTS FROM LOG TRANSFORMATION
+%			Average {MSE($\times 10^3$)} of base and reconciled point forecasts at forecasts horizons $h=1,...,6$ are presented.
+Bias and unbiased columns represent the results for biased-base/biased-reconciled and unbiased-base/unbiased-reconciled forecasts respectively.
+Comparisons can be made across biased vs unbiased forecasts as well as base vs reconciled forecasts.}}
+%	\label{tab:Results_MSE_LogTrans}
+%	\centering\tabcolsep=0.001cm
+%	\small
+%	\resizebox{\linewidth}{!}{
+%		\begin{tabular}{@{}lSSS@{}}
+%		
+%		R.method & Biased & Unbiased (Method-1) & Unbiased (Method-2)\\
+%		\midrule
+%		Base & 12.06 & 11.87 & 12.52\\
+%		\hline
+%		Bottom-up & 17.37 & 15.47 & 21.58\\
+%		\hline
+%		MinT(Shrink) & 9.36 & 9.25 & 10.35\\
+%		\hline
+%		OLS & 11.59 & 11.41 & 11.98\\
+%		\hline
+%		WLS & 15.00 & 13.83 & 17.55 \\
+%		\bottomrule
+%	\end{tabular}
+%}
+%
+%\end{table}
+%
+%\begin{table}
+%	\caption {\textcolor{red}{RESULTS FROM BOXCOX TRANSFORMATION
+%			Average {MSE($\times 10^3$)} of base and reconciled point forecasts at forecasts horizons $h=1,...,6$ are presented.
+Bias and unbiased columns represent the results for biased-base/biased-reconciled and unbiased-base/unbiased-reconciled forecasts respectively.
+Comparisons can be made across biased vs unbiased forecasts as well as base vs reconciled forecasts.}}
+%	\label{tab:Results_MSE_BoxCoxTrans}
+%	\centering\tabcolsep=0.08cm
+%	\resizebox{\linewidth}{!}{
+%		\begin{tabular}{@{}lSSS@{}}
+%			
+%			R.method & Biased & Unbiased (Method-1) & Unbiased (Method-2)\\
+%			\midrule
+%			Base & 12.27 & 139.94 & 13.45\\
+%			\hline
+%			Bottom-up & 18.06 & 15.76 & 23.33\\
+%			\hline
+%			MinT(Shrink) & 10.27 & 10.11 & 12.43\\
+%			\hline
+%			OLS & 11.84 & 116.91 & 12.96\\
+%			\hline
+%			WLS & 15.83 & 14.20 & 19.51\\		
+%			\bottomrule
+%		\end{tabular}
+%	}
+%	
+%\end{table}
+%	
 %	\begin{figure}
@@
 
-	Following the distance reducing property in Theorem \ref{th:distred} and the discussion therein, we have noted that the orthogonal projections will always improve the base forecasts with respect to the mean squared errors whereas, the oblique projections will not always, but improves only on average.
+%	Following the distance reducing property in Theorem \ref{th:distred} and the discussion therein, we have noted that the orthogonal projections will always improve the base forecasts with respect to the mean squared errors whereas, the oblique projections will not always, but improves only on average.
 Figure \ref{fig:BaseVSRecon_Fc} shows the MSE difference between base forecasts and reconciled forecasts - MinT, OLS and WLS for all replications in different forecast horizons.
@@
 However, these projections will outperform the base with respect to MSE on average which is again reflected from the highly positive skewed MSE differences.
-
-	 \begin{figure}[H]
-		\centering
-		\small
-		\includegraphics[width = \textwidth]{Empirical-results/Final-results/Base-Recon.pdf}
-		\caption{Difference of MSE between Base forecasts and reconciled forecasts over the replications in distinct forecast horizons.
-Positive values of the difference implies reconciliation improves the forecast accuracy than base forecasts.}\label{fig:BaseVSRecon_Fc}
-	\end{figure}
 
@@
 
-	\newpage
 	\section{Appendix}

### 2019-08-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Revision 1

--- 2019-08-17 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
@@
 		\title{\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.}
-		\author{Puwasala Gamakumara\thanks{
+		\author{Anastasios Panagiotelis\thanks{
 				The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.  We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
+			Department of Econometrics and Business Statistics,\\
+			Monash University,\\ VIC 3145, Australia.\\
+			Email: Anastasios.Panagiotelis@monash.edu \\
+			and \\
+			Puwasala Gamakumara\\
 			Department of Econometrics and Business Statistics,\\
@@
 			and \\
-			Anastasios Panagiotelis\\
-			Department of Econometrics and Business Statistics,\\
-			Monash University,\\ VIC 3800, Australia.\\
-			Email: Anastasios.Panagiotelis@monash.edu \\
-			and \\
 			George Athanasopoulos\\
 			Department of Econometrics and Business Statistics,\\
-			Monash University,\\ VIC 3800, Australia.\\
-			Email: george.athanasopoulos@monash.edu \\
+			Monash University,\\ VIC 3145, Australia.\\
+			Email: George.Athanasopoulos@monash.edu \\
 			and \\
@@
 			Monash University,\\ VIC 3800, Australia.\\
-			Email: rob.hyndman@monash.edu \\}
+			Email: Rob.Hyndman@monash.edu \\}
 		\maketitle
@@
 Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making.
-Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom up fashion \citep{Dunn1976} or disaggregating in a top-down fashion \citep{Gross1990, Athanasopoulos2009}.
+Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom-up fashion \citep{Dunn1976} or disaggregating in a top-down fashion \citep{Gross1990, Athanasopoulos2009}.
 For reviews of these approaches including a discussion of their advantages and disadvantages see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.
@@
 The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts.
-This approach and later modifications have subsequently been shown to outperform bottom up and top down approaches in a variety of empirical settings\todo{references}.
+This approach and later modifications have subsequently been shown to outperform bottom-up and top-down approaches in a variety of empirical settings\todo{references}.
 
@@
 	The remainder of this paper is structured as follows.
-Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines so called hierarchical time series in a way that does not depend on any notion of bottom level series.
+Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines so called hierarchical time series in a way that does not depend on any notion of bottom-level series.
 Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projections and includes a proof that reconciled forecasts dominate base forecasts with respect to a specific loss function.
@@
 
-    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \cite{WicEtAl2019}, \cite{FPP2018} and others, before elaborating on some of the limitations of this understanding.
+    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \cite{AthEtAl2019_MacroBook}, \cite{FPP2018} and others, before elaborating on some of the limitations of this understanding.
 A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables.
@@
 In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.
-However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom level series, $y_{A,t}$ and $y_{B,t}$.
+However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom-level series, $y_{A,t}$ and $y_{B,t}$.
 In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$.
@@
      	\caption{Depiction of a three dimensional hierarchy with $y_{\text{Tot}} = y_{\text{A}} + y_{\text{B}}$.
-The gray coloured two dimensional plane depicts the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that spans $\mathfrak{s}$.
+The gray coloured two dimensional plane depicts the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that span $\mathfrak{s}$.
 The red points in $\mathfrak{s}$ represent realisations or coherent forecasts}\label{fig:3D_hierarchy}
@@
 In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure~\ref{fig:basichier} and/or do not involve aggregation.
-{\bf Include brief summary of all non-traditional hierarchies - e.g.
-grouped hierarchies, temporal hierarchies with weird overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
+Examples include, temporal hierarchies which involve grouped structures \citep[see][]{AthEtAl2017}, overlapping temporal hierarchies \citep[see][]{JeoEtAl2019}, applications for which the difference rather than the aggregate is of interest \cite[see][]{LiTan2019}, or structures that involve both cross-sectional and temporal dimensions referred to as cross-temporal structures \citep[see][]{KouAth2019}.
+Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
 
@@
     Without any loss of generality, the above definition could also be applied to prediction for multivariate data in general, rather than just forecasting of time series.
+
     Much of the early literature that dealt with the problem of forecasting hierarchical time series \citep[see][and references therein]{Gross1990} produced forecasts at a single level of the hierarchy in the first stage.
@@
 This approach does have several advantages over only forecasting a single level.
-First, there is no loss of information since all bottom levels are modelled.
-Second, modelling top level series often identifies features such as trend and seasonality that cannot be detected in noisy disaggregate data.
-Unfortunately, however, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.
-This problem of incoherent forecasts cannot in general be solved by multivariate modelling either.
-Instead, the solution to incoherent forecasts is to make an ex post adjustment that ensures coherence, a process known as {\em forecast reconciliation}
+First, there is no loss of information since all levels and series are modelled.
+Second, modelling higher level series often identifies features such as trend and seasonality that cannot be detected in noisy disaggregate data.
+However, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.\footnote{There are some special cases of using simple approaches such as na\"{i}ve, which extrapolate the coherent nature of the data to the forecasts.} This problem of incoherent forecasts cannot in general be solved by multivariate modelling either.
+Instead, the solution is to make an ex post adjustment that ensures coherence, a process known as {\em forecast reconciliation}
 
@@
 
-	The problem of forecast reconciliation is predicated on there being an $n$-vector of forecasts that are incoherent.
-We will call these {\em base forecasts} and denote them as $\hat{\bm{y}}_{t+h|h}$.
+	The concept of forecast reconciliation is predicated on there being an $n$-vector of forecasts that are incoherent.
+We call these {\em base forecasts} and denote them as $\hat{\bm{y}}_{t+h|t}$.
+The subscript $t+h/t$ implies that the forecast is made at time $t$ for a period $h$ steps into the future.
 In the sequel, this subscript will be dropped at times for ease of exposition.
-In the most general terms, reconciliation can be defined as follows
+In the most general terms, reconciliation can be defined as follows.
 
@@
 		Let $\psi$ be a mapping, $\psi:\mathbb{R}^n\rightarrow\mathfrak{s}$.
-The point forecast $\tilde{\bm{y}}_{t+h|t}=\psi\left(\hat{\bm{y}}_{t+h|t}\right)$ is said to ``reconcile'' a base forecast $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $\psi(.)$
+The point forecast $\tilde{\bm{y}}_{t+h|t}=\psi\left(\hat{\bm{y}}_{t+h|t}\right)$ ``reconciles'' a base forecast $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $\psi(.)$
 	\end{definition}
@@
 	All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.
-One way to achieve this is with a matrix $\bm{SG}$, where $\bm{G}$ is an $(n-m)\times n$ matrix  (some authors use $\bm{P}$ used in place of $\bm{G}$).
-This facilitates an interpretation of reconciliation as a two-step process, in the first step, base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom level forecasts, in the second step, these mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.
+One way to achieve this is with a matrix $\bm{SG}$, where $\bm{G}$ is an $m\times n$ matrix  (some authors use $\bm{P}$ in place of $\bm{G}$).
+This facilitates an interpretation of reconciliation as a two-step process.
+In the first step, base forecasts $\hat{\bm{y}}_{t+h|t}$ are combined to form a new set of bottom-level forecasts.
+In the second step, these are mapped to a full vector of coherent forecasts via pre-multiplication by $\bm{S}$.
 
 	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix onto $\mathfrak{s}$.
-In general a projection matrix is defined via the idemoptence property, i.e.
-$\bm{SG}^2=\bm{SG}$.
+In general a projection matrix is defined via its idempotence property, i.e.
+$(\bm{SG})^2=\bm{SG}$.
 However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped to itself by that projection \citep[see Lemma 2.4 in][for a proof]{rao1974}.
@@
 	In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.  
-The  first is that reconciliation should adjust the base forecasts as little as possible, i.e.
-the base and reconciled forecast should be `close'.
-The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value targeted by the forecast.
+\begin{itemize}
+  \item The  first is that reconciliation should adjust the base forecasts as little as possible, i.e. the base and reconciled forecasts should be `close'. 
+  \item The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value targeted by the forecast.
+\end{itemize}
 
@@
 	Consider the Euclidean distance between a forecast and the target.
-This is equivalent to the root of the sum of squared errors over the entire hierarchy.
+This is equivalent to the root of the sum of squared forecast errors over the entire hierarchy.
 Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$.
@@
 	\begin{proof}
-		Since, $\bm{y}_{t+h},\tilde{\bm{y}}_{t+h}\in\mathfrak{s}$ and since the projection is orthogonal, by Pythagoras' theorem
+		Since, $\bm{y}_{t+h|t},\tilde{\bm{y}}_{t+h|t}\in\mathfrak{s}$ and since the projection is orthogonal, by Pythagoras' theorem
 		\begin{equation}
-		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2=\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h})\|^2+\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2.
+		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2=\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2+\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2.
 		\end{equation}
 
-		Since $\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h})\|^2\ge 0$ this implies,
+		Since $\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2\ge 0$ this implies,
 		\begin{equation}
@@
 		\end{equation}
-		with equality only holding when $\tilde{\bm{y}}_{t+h|t}=\hat{\bm{y}}_{t+h}$.  Taking the square root of both sides proves the desired result.
+		with equality only holding when $\tilde{\bm{y}}_{t+h|t}=\hat{\bm{y}}_{t+h|t}$.  Taking the square root of both sides proves the desired result.
 	\end{proof}
@@
 
-	\begin{figure}[H]\label{fig:Schematic_OLSRecon}
+	\begin{figure}[H]
 		\centering
@@
 		\resizebox{\linewidth}{!}{\input{Figs/orth_pointforerec_schematic}}
-		\caption{Orthogonal projection of $\hat{\bm{y}}$ onto $\mathfrak{s}$ yielding the reconciled forecast $\tilde{\bm{y}}$}
+		\caption{Orthogonal projection of $\hat{\bm{y}}$ onto $\mathfrak{s}$ yielding the reconciled forecast $\tilde{\bm{y}}$}\label{fig:Schematic_OLSRecon}
 
@@
 First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.
-In particular, this measure is the root of the sum of squared errors of {\em all} variables in the hierarchy.
-As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to worse forecasts for individual series.
+In particular, this measure is the root of the sum of squared forecast errors of {\em all} variables in the hierarchy.
+As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to less accurate forecasts for individual series.
 Second, although orthogonal projections are guaranteed to improve on base forecasts, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.
@@
 	One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the root of the sum of squared errors of {\em all} variables in the hierarchy.
-A clear shortcoming of this measure of forecast accuracy is that forecasts errors in all series should not necessarily be treated equally.
-For example, in hierarchies, top-level series tend to have a much larger scale than bottom level series.
-Even when two series are on a similar scale, series that are more predictable or less variable will tend to be downweighted by simply aggregating square errors.
+A clear shortcoming of this measure of forecast accuracy is that forecast errors in all series should not necessarily be treated equally.
+For example, in hierarchies, top-level series tend to have a much larger scale than bottom-level series.
+Even when two series are on a similar scale, series that are more predictable or less variable will tend to be downweighted by simply aggregating squared errors.
 An even more sophisticated understanding may take the correlation between series into account.
@@
 	It should be noted that  $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix in the usual Euclidean geometry.
-However this matrix can be considered to be an orthogonal projection for a different geometry defined by the norm $||\bm{v}||_{{\bm W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, which we will call the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
+However this matrix can be considered to be an orthogonal projection for a different geometry defined by the norm\break $||\bm{v}||_{{\bm W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
 One way to understand this geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$.
@@
 	\tilde{\bm{y}}^*&=\bm{W}^{-1/2}\tilde{\bm{y}}\\&=\bm{W}^{-1/2}\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}
-	\\&=\bm{S}^*\left(\bm{S}^{*'}\bm{S}^*\right)^{-1}\bm{S}^{*'}\hat{\bm{y}^*}
+	\\&=\bm{S}^*\left(\bm{S}^{*'}\bm{S}^*\right)^{-1}\bm{S}^{*'}\hat{\bm{y}^*}.
 	\end{align}
@@
 
-	Note here that we rely here on the generalised Pythagorean Theorem (which involves an equality).
+	\todo{Rob can you please read to make sure you are happy with this.}Note here that we rely here on the generalised Pythagorean Theorem (which involves an equality).
 In contrast, \cite{WicEtAl2019} follow \cite{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.
-The proof of \cite{WicEtAl2019} requires an assumptions about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.
+The proof of \cite{WicEtAl2019} requires an assumption about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.
 The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.
@@
 One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.
-An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection showed as in Figure \ref{fig:Orthogonal_projection_all_points}.
-Figure \ref{fig:Oblique_projection_all_points} depicts a similar oblique projection along $\bm{R}$ for all the gray points yield reconciled forecasts tightly packed near the target $\bm{y}$.
-In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts.
+An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection shown in Figure \ref{fig:Orthogonal_projection_all_points}.
+Figure \ref{fig:Oblique_projection_all_points} depicts an oblique projection along $\bm{R}$ for all the gray points, yielding reconciled forecasts tightly packed near the target $\bm{y}$.
+In this sense, the oblique MinT projection minimises the forecast error variance of the reconciled forecasts.
 In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal in expectation.
@@
 
-	The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation \cite{WicEtAl2019}.
+	The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation of \cite{WicEtAl2019}.
 Before restating this proof using a  clear geometric interpretation we discuss in a precise fashion what is meant by unbiasedness.
@@
 	Suppose that the target of a point forecast is $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ where the expectation is taken over the predictive density.
-Our point forecast can be thought of as an estimate of this quantity.\todo{or do we want to define unbiasedness of a forecast as the expected value of the forecast equals realisation?}  The forecast is random due to uncertainty in the training sample and it is with respect to this uncertainty that unbiasedness refers.
+Our point forecast can be thought of as an estimate of this quantity.
+The forecast is random due to uncertainty in the training sample and it is with respect to this uncertainty that unbiasedness is referred to \todo{or do we want to define unbiasedness of a forecast as the expected value of the forecast equals realisation?
+George: are these not equivalent?
+Should be put both?
+Rob what do think?}.
 More concretely, the point forecast will be unbiased if $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
@@
 Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix.
-\todo{perhaps elaborate in a proof in appendix}  However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$.
+However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$.
 This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.
@@
 
+    \subsection{Bias correction}
+
 	Our own solution to dealing with biased forecasts is to bias correct {\em before} reconciliation.
@@
 Our particular choice of bias correction will be the Guererro method \citep{guerrero1993time}.
+\textcolor{red}{TODO: Read this again after the empirical application has been completed.
+I am saying this because my understanding is that we use the Guererro method to choose the lambda for the BoxCox transformation.
+Then we back transform the forecasts using the same lambda once with bias correcting using the factor that comes out of a Taylor series expansion around $\mu$ (programmed in fable/forecast package) and once without it hence looking at medians and not means - hence biased base forecasts.
+If my understanding here is correct I am not sure we can say we are using the Guererro method to bias correct.}
 
-	Alternatively, a more general purpose approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
-	}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.
+	Alternatively, a more general purpose approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.
 This can be then subtracted from future forecasts.
@@
 	We use ``overnight trips" as a measure of domestic tourism flow in Australia.
-Total ``overnight trips" in Australia can be disaggregated into 7 states, 27 zones and 75 regions forming a geographical hierarchy with $110$ total number of series and $75$ bottom level series.
+Total ``overnight trips" in Australia can be disaggregated into 7 states, 27 zones and 75 regions forming a geographical hierarchy with $110$ total number of series and $75$ bottom-level series.
 More information about the series of this hierarchy is given in Table \ref{table:A1} in the appendix.
@@
 	While observing the patterns of individual series, we noticed that the signal-to-noise ratio decreases with the disaggregate level of the hierarchy.
-From Figure \ref{fig:Total_TSplots} and \ref{fig:States_Zones_Regs_TSplots} this is depicted well as we see much noisier series in bottom levels whereas the noise level is comparatively stabilised in the upper levels.
+From Figure \ref{fig:Total_TSplots} and \ref{fig:States_Zones_Regs_TSplots} this is depicted well as we see much noisier series in the bottom-level whereas the noise level is comparatively stabilised in the upper levels.
 We have also observed that the overnight trips for `Adelaide Hills` has an anomalous observation on December-2002.

### 2019-08-22 Hierarchical-forecast-reconciliation/Figs/Orthproj.tex

--- 2019-07-30 Hierarchical-forecast-reconciliation/Figs/Orthproj.tex
@@
-% Created by tikzDevice version 0.12 on 2019-07-25 19:34:36
+% Created by tikzDevice version 0.12 on 2019-08-22 15:40:42
 % !TEX encoding = UTF-8 Unicode
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.46, 49.37) --
-	( 75.46,302.86);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (113.46, 49.37) --
+	(113.46,302.86);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 12.94, 91.62) --
-	(361.35, 91.62);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 71.21, 91.62) --
+	(324.70, 91.62);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 75.46, 91.62) -- (294.26,165.55);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (113.46, 91.62) -- (261.33,165.55);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (282.33,151.98) --
-	(294.26,165.55) --
-	(276.55,169.10);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (251.37,150.47) --
+	(261.33,165.55) --
+	(243.29,166.63);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (300.26,163.26) {{\huge $\mathfrak{s}$}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.50] at (267.33,159.81) {{$\huge \mathfrak{s}$}};
 \definecolor{drawColor}{RGB}{190,190,190}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.73,104.11) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.70,163.73) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.96, 97.64) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.00, 11.50) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.75,158.76) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.23, 72.11) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.40,151.64) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.94,120.08) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.23,132.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.02,109.32) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 67.77, 37.36) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.98,177.38) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.74, 64.30) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.63, 95.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.42, 57.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.61,100.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.34,119.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.41,152.96) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.42,110.64) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.54, 86.62) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.22,194.28) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.83, 19.22) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.14,120.23) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.43,146.43) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.75, 94.39) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.50, 17.18) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.46,159.17) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.75, 24.12) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.12, 78.87) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.64, 36.92) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.91,246.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.77, 76.46) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.00, 75.49) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.22, 77.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.54, 44.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.46, 46.02) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.06, 63.01) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.16, 43.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.94, 76.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.59,168.09) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.47,142.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.21,151.63) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.23,157.90) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.67,154.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.43,158.48) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.50,198.70) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.22,161.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.29, 34.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.88, 98.42) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.44,106.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.00, 83.00) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.35, 77.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.04, 85.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.85,175.46) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.87,141.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.17, 58.08) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.00,105.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.19, 90.58) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.17, 88.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.50, 83.79) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.15, -1.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.67,102.02) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.13, 76.86) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.77,100.41) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.24,170.18) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.30, 32.37) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.33, 55.24) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.40, 46.81) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.14, 34.27) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.27, 55.53) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.83, 70.96) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.24,130.03) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.18, 37.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.49,179.20) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.63, 69.09) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.91,  9.01) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.36,141.37) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.12, 67.81) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.54, 10.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.62,101.45) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.31,100.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.65, 57.86) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.09, 96.39) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.75,153.69) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.67,148.26) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.02,120.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.98,130.52) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.22,110.20) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.55, 93.92) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.14,139.52) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.67,184.11) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.54,141.66) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.64,100.10) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.28,103.57) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.87,105.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.22,139.07) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.41,135.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.89, 69.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.14, 59.33) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.24,191.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.14,108.82) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.15, 69.16) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.78,130.30) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.20, 71.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.46,191.20) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.91,120.08) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.08,131.10) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.87,130.22) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.73,129.59) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.60,120.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 77.69, 38.48) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.36,106.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.64,162.50) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.99,138.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.94,188.07) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.42,141.58) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.08,148.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.09, 81.33) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.23,100.64) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.69,128.58) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.40,120.16) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.46, 82.08) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.88,184.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.79, 72.38) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.24,126.18) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.98,114.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.95, 53.81) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.86, 96.73) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.34,121.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.46, 77.32) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.85, 10.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.50, 58.71) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.63, 98.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.21, 70.01) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.24,125.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.94, 46.86) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.52, 18.10) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.17, 94.98) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.96,179.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.84,107.08) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.23,131.81) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.16, 85.74) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.43,161.73) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.49,141.08) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.78,270.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.54,127.65) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.20,114.65) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.15, 64.90) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.39, 82.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.74, 15.71) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.64, 54.72) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.04,177.16) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.04, 80.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.46,124.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.26,104.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.23,196.67) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.76, 73.89) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.49, 50.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.08,127.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.27, 65.49) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.98,194.02) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.75,134.88) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.01, 89.21) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.87, 33.95) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.86,135.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.02,177.59) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.03,149.79) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.58, 13.53) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.65, 96.89) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.88,160.74) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.52,153.41) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.26, 96.73) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.68,172.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.83,187.60) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.42,141.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.29, 67.38) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.02,103.15) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.10,121.60) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.57,163.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.32,103.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.23,162.78) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.18,108.50) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.51,128.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.46,116.40) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.37,117.42) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.29, 12.13) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.85,213.31) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.38,110.02) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.12, 87.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.38, 95.13) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.18,169.12) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.26,118.35) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 83.18, 59.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.93, 75.82) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 75.46, 91.62) -- (137.97,260.61);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (113.46, 91.62) -- (155.71,260.61);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (141.02,242.80) --
-	(137.97,260.61) --
-	(124.07,249.07);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (160.68,243.24) --
+	(155.71,260.61) --
+	(143.15,247.62);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (137.97,266.61) {{\Large ${\bm R}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (155.71,266.61) {{${\bm R}$}};
 \definecolor{drawColor}{RGB}{255,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.47,100.41) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.10,118.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.03,100.26) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.25, 77.01) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.83,123.51) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.47, 95.62) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.34,117.93) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.23,107.50) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.78,114.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.79,107.78) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 37.19, 78.69) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.39,122.58) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.11, 96.23) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.33, 96.05) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 67.02, 88.77) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 63.04, 66.41) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.30,110.15) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.51,107.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.89,111.36) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.56,122.67) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (199.23,133.44) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.93, 93.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.34,113.20) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.80, 85.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.13,101.98) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.56,114.17) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.44,121.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.32, 79.55) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.45, 94.66) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 85.09, 77.43) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (241.05,147.57) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.13, 83.95) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.75, 97.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.04, 93.91) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.89, 88.72) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.59, 94.68) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.00, 96.87) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.22, 90.50) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.44, 96.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.50, 87.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.51,118.33) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.16,122.97) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.91,121.84) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.87,120.32) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.21,118.23) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.70,116.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.63,126.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (185.13,127.45) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.02,102.28) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 97.82, 83.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.79, 98.15) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.28,106.53) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.00,102.95) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.00, 93.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.12,117.19) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.11,126.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.76,104.56) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.61, 89.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.01,100.93) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.83,103.30) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 19.17, 72.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.96, 96.87) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.26, 96.96) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.39,106.58) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.99,121.87) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.82,102.30) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 77.83, 92.42) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 93.63, 81.71) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 48.46, 82.50) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.49, 86.63) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 81.92, 93.80) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.07, 89.92) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 55.41, 84.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.45,113.61) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.46, 90.95) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.72,128.75) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.82,112.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.98, 78.88) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 26.44, 75.05) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.26, 93.52) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.84,103.91) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.92,100.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.19,100.31) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.11, 98.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.15,121.92) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.52,116.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.90,111.70) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.86,114.32) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 95.30, 98.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.10,102.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.98,125.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.77,112.27) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.02,102.28) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.34,116.06) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.52,102.79) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.50,101.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.64,112.29) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.85,113.81) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 76.09, 91.83) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.87, 95.32) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.78,105.24) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (193.10,131.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.01,111.07) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.43, 90.60) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (188.00,129.65) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.92, 94.35) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.92,113.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.81,112.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.35,112.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.83,114.30) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 45.79, 81.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.61,110.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.36,119.63) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.82,101.30) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.13,128.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.62,115.20) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.60,115.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.21,113.99) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.01, 99.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.25, 99.01) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.11,107.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.43,109.10) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.70,126.17) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.45, 96.11) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.14,111.45) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.83, 98.30) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 51.07, 83.38) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.08,105.93) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.23,105.40) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.23,106.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 26.29, 75.01) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.14, 95.96) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 11.37, 69.96) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.93, 91.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  8.62, 69.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.01, 98.39) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.81,106.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.74, 89.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.55,108.88) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.37,100.57) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 43.99, 80.99) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.55,105.66) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.37,126.05) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 58.18, 63.98) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.06,117.16) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 55.34, 62.56) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.54,121.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.27, 97.52) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (255.15,152.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.27,115.52) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.89,104.27) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.33,106.05) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.13, 97.93) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.53, 90.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.56, 92.67) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 85.72, 77.75) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.85, 99.52) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.54,124.16) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.83,103.57) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.27,108.52) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.00, 96.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (199.30,134.54) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.02,110.05) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.26, 86.52) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (202.09,134.41) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.06, 93.92) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.08,101.29) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.39,111.58) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.31,117.25) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.12, 85.45) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.35,119.63) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.29,131.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.13,104.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.92, 78.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.88,115.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.85,122.81) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.22,125.67) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.54,102.16) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.97,112.40) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.95,127.36) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.93,104.62) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.83, 88.30) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.12,120.90) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.37,113.07) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.80,120.12) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.11,103.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.05,112.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.59,105.68) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.46,109.19) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.37,108.57) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (204.61,135.26) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 80.73, 75.25) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.34, 96.31) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.76,103.27) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.71,126.51) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.60,102.69) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 62.36, 87.19) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.79,109.28) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.92, 97.85) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.73,104.11) -- (101.47,100.41);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (145.70,163.73) -- (168.10,118.94);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (102.96, 97.64) -- (101.03,100.26);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.00, 11.50) -- ( 84.25, 77.01);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.75,158.76) -- (169.83,123.51);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.23, 72.11) -- (121.47, 95.62);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.40,151.64) -- (153.34,117.93);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.94,120.08) -- (145.23,107.50);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.23,132.34) -- (141.78,114.03);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (145.02,109.32) -- (145.79,107.78);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 67.77, 37.36) -- ( 37.19, 78.69);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (147.98,177.38) -- (175.39,122.58);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (112.74, 64.30) -- ( 89.11, 96.23);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (122.63, 95.44) -- (122.33, 96.05);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 90.42, 57.14) -- ( 67.02, 88.77);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 96.24,  0.00) -- ( 63.04, 66.41);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.34,119.54) -- (130.30,110.15);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (147.61,100.94) -- (144.51,107.14);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (134.42,110.64) -- (133.89,111.36);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.41,152.96) -- (175.56,122.67);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.22,194.28) -- (199.23,133.44);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.54, 86.62) -- (117.93, 93.85);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (134.14,120.23) -- (139.34,113.20);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.83, 19.22) -- (100.80, 85.29);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (111.75, 94.39) -- (106.13,101.98);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (142.43,146.43) -- (158.56,114.17);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (135.46,159.17) -- (163.44,121.35);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (120.50, 17.18) -- ( 89.32, 79.55);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 96.12, 78.87) -- ( 84.45, 94.66);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (111.75, 24.12) -- ( 85.09, 77.43);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.91,246.43) -- (241.05,147.57);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.64, 36.92) -- ( 98.13, 83.95);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.00, 75.49) -- ( 92.75, 97.46);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.77, 76.46) -- (118.04, 93.91);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 99.54, 44.60) -- ( 66.89, 88.72);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.22, 77.44) -- (119.59, 94.68);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.06, 63.01) -- ( 91.00, 96.87);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.46, 46.02) -- (111.22, 90.50);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.94, 76.74) -- ( 89.44, 96.34);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.16, 43.80) -- (104.50, 87.14);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.47,142.71) -- (154.51,118.33);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (153.59,168.09) -- (176.16,122.97);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.23,157.90) -- (164.91,121.84);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.21,151.63) -- (170.87,120.32);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (124.43,158.48) -- (154.21,118.23);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.67,154.29) -- (162.70,116.24);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.22,161.85) -- (177.63,126.14);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (149.50,198.70) -- (185.13,127.45);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.88, 98.42) -- (107.02,102.28);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (122.29, 34.85) -- ( 97.82, 83.80);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.00, 83.00) -- ( 94.79, 98.15);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.44,106.19) -- (143.28,106.53);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (122.04, 85.32) -- (109.00,102.95);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.35, 77.19) -- (118.00, 93.89);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.87,141.85) -- (151.12,117.19);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (159.85,175.46) -- (184.11,126.94);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.00,105.58) -- (113.76,104.56);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (124.17, 58.08) -- (108.61, 89.19);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (112.17, 88.54) -- (103.01,100.93);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.19, 90.58) -- (136.83,103.30);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.89,  0.00) -- ( 19.17, 72.60);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (130.50, 83.79) -- (123.96, 96.87);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.13, 76.86) -- ( 91.26, 96.96);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (145.67,102.02) -- (143.39,106.58);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (129.24,170.18) -- (164.99,121.87);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (135.77,100.41) -- (134.82,102.30);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.33, 55.24) -- ( 77.83, 92.42);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.30, 32.37) -- ( 93.63, 81.71);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 84.14, 34.27) -- ( 48.46, 82.50);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.40, 46.81) -- (103.49, 86.63);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.83, 70.96) -- ( 81.92, 93.80);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (127.27, 55.53) -- (110.07, 89.92);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 90.18, 37.85) -- ( 55.41, 84.85);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (149.24,130.03) -- (157.45,113.61);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 89.63, 69.09) -- ( 73.46, 90.95);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.49,179.20) -- (187.72,128.75);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.36,141.37) -- (136.82,112.35);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (122.91,  9.01) -- ( 87.98, 78.88);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 74.54, 10.03) -- ( 26.44, 75.05);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (130.12, 67.81) -- (117.26, 93.52);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.31,100.58) -- (111.84,103.91);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.62,101.45) -- (131.92,100.85);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.09, 96.39) -- (101.19,100.31);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (148.65, 57.86) -- (128.11, 98.94);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (145.67,148.26) -- (165.15,121.92);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.75,153.69) -- (162.52,116.15);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (120.98,130.52) -- (134.90,111.70);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (156.02,120.00) -- (158.86,114.32);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 21.96,  0.00) -- (  0.00, 29.67);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.22,110.20) -- (135.10,102.44);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.55, 93.92) -- ( 95.30, 98.32);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (141.14,139.52) -- (154.77,112.27);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.67,184.11) -- (175.98,125.58);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (149.54,141.66) -- (162.34,116.06);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (108.64,100.10) -- (107.02,102.28);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.28,103.57) -- (132.50,101.14);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.87,105.03) -- (108.52,102.79);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (145.22,139.07) -- (157.85,113.81);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (119.41,135.58) -- (136.64,112.29);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.89, 69.29) -- (120.87, 95.32);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (100.14, 59.33) -- ( 76.09, 91.83);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.24,191.15) -- (193.10,131.44);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.14,108.82) -- (115.78,105.24);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (122.15, 69.16) -- (111.43, 90.60);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.78,130.30) -- (133.01,111.07);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (130.20, 71.80) -- (118.92, 94.35);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (142.46,191.20) -- (188.00,129.65);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (150.91,120.08) -- (154.81,112.29);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.08,131.10) -- (140.92,113.74);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (150.87,130.22) -- (158.83,114.30);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (124.73,129.59) -- (137.35,112.53);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (145.60,120.21) -- (150.61,110.19);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 77.69, 38.48) -- ( 45.79, 81.60);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (130.36,106.24) -- (132.82,101.30);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.64,162.50) -- (158.36,119.63);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (148.99,138.44) -- (160.62,115.20);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (139.94,188.07) -- (184.13,128.34);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (144.42,141.58) -- (158.21,113.99);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.08,148.46) -- (145.60,115.32);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.09, 81.33) -- (128.25, 99.01);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.23,100.64) -- ( 99.01, 99.58);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.69,128.58) -- (148.43,109.10);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (111.40,120.16) -- (121.11,107.04);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (129.46, 82.08) -- (122.45, 96.11);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (134.88,184.04) -- (177.70,126.17);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (139.79, 72.38) -- (126.83, 98.30);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.24,126.18) -- (134.14,111.45);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.98,114.14) -- (142.08,105.93);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.95, 53.81) -- ( 51.07, 83.38);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (146.86, 96.73) -- (142.23,106.00);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.34,121.46) -- (116.23,105.40);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.46, 77.32) -- (122.14, 95.96);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 73.85, 10.74) -- ( 26.29, 75.01);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (130.50, 58.71) -- (113.93, 91.85);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 63.13,  0.00) -- ( 11.37, 69.96);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (141.21, 70.01) -- (127.01, 98.39);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 59.69,  0.00) -- (  8.62, 69.03);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (129.94, 46.86) -- (108.74, 89.26);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (125.63, 98.74) -- (119.81,106.60);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (134.17, 94.98) -- (131.37,100.57);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.24,125.53) -- (126.55,108.88);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (140.84,107.08) -- (141.55,105.66);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 90.52, 18.10) -- ( 43.99, 80.99);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 90.17,  0.00) -- ( 58.18, 63.98);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.96,179.32) -- (177.37,126.05);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 86.62,  0.00) -- ( 55.34, 62.56);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (140.23,131.81) -- (151.06,117.16);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.16, 85.74) -- (125.27, 97.52);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.43,161.73) -- (162.54,121.04);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (148.49,141.08) -- (161.27,115.52);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.78,270.43) -- (255.15,152.34);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.54,127.65) -- (142.33,106.05);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.20,114.65) -- (112.89,104.27);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.15, 64.90) -- (110.53, 90.15);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.39, 82.71) -- ( 94.13, 97.93);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.74, 15.71) -- ( 85.72, 77.75);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.64, 54.72) -- ( 78.56, 92.67);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (152.04,177.16) -- (178.54,124.16);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.04, 80.34) -- ( 98.85, 99.52);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (139.46,124.14) -- (147.27,108.52);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (110.26,104.34) -- (110.83,103.57);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (168.23,196.67) -- (199.30,134.54);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.76, 73.89) -- ( 90.00, 96.53);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.49, 50.04) -- (103.26, 86.52);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.08,127.54) -- (130.02,110.05);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.27, 65.49) -- (118.06, 93.92);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (157.98,194.02) -- (202.09,134.41);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (141.75,134.88) -- (153.39,111.58);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.01, 89.21) -- (104.08,101.29);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.87, 33.95) -- (101.12, 85.45);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.86,135.43) -- (151.31,117.25);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.02,177.59) -- (192.29,131.04);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.03,149.79) -- (158.35,119.63);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (120.58, 13.53) -- ( 87.92, 78.85);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.65, 96.89) -- (113.13,104.35);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (156.88,160.74) -- (175.85,122.81);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.52,153.41) -- (144.88,115.08);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.26, 96.73) -- (134.54,102.16);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (141.68,172.35) -- (176.22,125.67);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.83,187.60) -- (184.95,127.36);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.42,141.54) -- (136.97,112.40);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.29, 67.38) -- (106.83, 88.30);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.02,103.15) -- (113.93,104.62);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (152.10,121.60) -- (156.37,113.07);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (130.57,163.54) -- (162.12,120.90);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.32,103.04) -- (137.11,103.44);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.23,162.78) -- (159.80,120.12);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (140.18,108.50) -- (141.59,105.68);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (125.51,128.03) -- (137.05,112.43);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.46,116.40) -- (147.37,108.57);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.37,117.42) -- (127.46,109.19);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (112.29, 12.13) -- ( 80.73, 75.25);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (146.85,213.31) -- (204.61,135.26);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.38,110.02) -- (136.76,103.27);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 96.12, 87.14) -- ( 89.34, 96.31);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (139.38, 95.13) -- (135.60,102.69);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (147.18,169.12) -- (178.71,126.51);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (144.26,118.35) -- (148.79,109.28);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 83.18, 59.04) -- ( 62.36, 87.19);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.93, 75.82) -- (125.92, 97.85);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.97,104.29) circle (  3.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.81,104.29) circle (  3.00);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (112.97, 86.55) {{\huge $\color{black}{\bm{y}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (138.81, 77.94) {{$\color{black}{\bm{y}}$}};
 \end{scope}
 \end{tikzpicture}
-
+\caption{a caption}
 \end{document}

### 2019-08-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
trying to pull

--- 2019-08-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
@@
 	 \end{definition}
-
      To further illustrate, Figure \ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.
@@
 It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$.
-In Figure \ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.
-However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom level series, $y_{A,t}$ and $y_{B,t}$.
+In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.
+However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom-level series, $y_{A,t}$ and $y_{B,t}$.
 In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$.
@@
 Also notable by its absence in the above definition is any reference to {\em aggregation}.
-In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure\ref{fig:basichier} and/or do not involve aggregation.
-{\bf Include brief summary of all non-traditional hierarchies - e.g.
-grouped hierarchies, temporal hierarchies with weird overlapping, problems where we look at differences between variables etc.}  Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
+In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure~\ref{fig:basichier} and/or do not involve aggregation.
+Examples include, temporal hierarchies which involve grouped structures \citep[see][]{AthEtAl2017}, overlapping temporal hierarchies \citep[see][]{JeoEtAl2019}, applications for which the difference rather than the aggregate is of interest \cite[see][]{LiTan2019}, or structures that involve both cross-sectional and temporal dimensions referred to as cross-temporal structures \citep[see][]{KouAth2019}.
+Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
 
@@
 
-	Figure \ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.
+	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.
 Suppose the in-sample errors are given by the orange points.
@@
 This direction is denoted by $\bm{R}$.
-Figure \ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).
+Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).
 One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.
-An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection showed as in Figure \ref{fig:Orthogonal_projection_all_points}.
-Figure \ref{fig:Oblique_projection_all_points} depicts a similar oblique projection along $\bm{R}$ for all the gray points yield reconciled forecasts tightly packed near the target $\bm{y}$.
-In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts.
+An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection shown in Figure \ref{fig:Orthogonal_projection_all_points}.
+Figure \ref{fig:Oblique_projection_all_points} depicts an oblique projection along $\bm{R}$ for all the gray points, yielding reconciled forecasts tightly packed near the target $\bm{y}$.
+In this sense, the oblique MinT projection minimises the forecast error variance of the reconciled forecasts.
 In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal in expectation.
@@
 Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$,  $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$.
-This is depicted in Figure \ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.
+This is depicted in Figure~\ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.
 In this case, the expectation of reconciled forecast will be $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and hence biased.
@@
 Opening the door to reconciliation methods that change already coherent base forecast would seem to suggest an increase in the variability of the forecast.
-This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance.
+This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance is to reduce variance.
+
+    \subsection{Bias correction}
 
@@
 Our particular choice of bias correction will be the Guererro method \citep{guerrero1993time}.
+\textcolor{red}{TODO: Read this again after the empirical application has been completed.
+I am saying this because my understanding is that we use the Guererro method to choose the lambda for the BoxCox transformation.
+Then we back transform the forecasts using the same lambda once with bias correcting using the factor that comes out of a Taylor series expansion around $\mu$ (programmed in fable/forecast package) and once without it hence looking at medians and not means - hence biased base forecasts.
+If my understanding here is correct I am not sure we can say we are using the Guererro method to bias correct.}
 
@@
 	\begin{cases}
-	\exp({x_{t+h}})[1+\frac{\sigma_h^2}{2}] & \text{if log transformation, $\lambda = 0$} \\
-	(\lambda x_{t+h} + 1)^{1/\lambda}[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda x_{t+h} + 1)^2}]       & \text{if Box-Cox transformation, $\lambda \ne 0$}
+	\exp({x_{t+h}})[1+\frac{\sigma_h^2}{2}] & \text{if } \lambda = 0 \\
+	(\lambda x_{t+h} + 1)^{1/\lambda}[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda x_{t+h} + 1)^2}]       & \text{if } \lambda \ne 0
 	\end{cases}
 	\end{equation}
-	where, $x_{t+h}$ is the $h$-step-ahead forecasts from the log/Box-Cox transformed series and $\sigma_h^2$ is the variance of $x_{t+h}$.
-Unbiased forecasts from this method is referred to as Unbiased (Method-1).
-We also applied a more general bias adjustment method by estimating the bias using in-sample residual means as explained in Section \ref{sec:BiasInRecon}.
-Unbiased forecasts from this general method is referred to as Unbiased (Method-2).\todo{Should we give more concise words for these two methods??}
+	where, $x_{t+h}$ is the $h$-step-ahead forecasts from the Box-Cox transformed series and $\sigma_h^2$ is the variance of $x_{t+h}$.
 
@@
 	\centering
-
 	\resizebox{\linewidth}{!}{
@@
 
-%	Following the distance reducing property in Theorem \ref{th:distred} and the discussion therein, we have noted that the orthogonal projections will always improve the base forecasts with respect to the mean squared errors whereas, the oblique projections will not always, but improves only on average.
-Figure \ref{fig:BaseVSRecon_Fc} shows the MSE difference between base forecasts and reconciled forecasts - MinT, OLS and WLS for all replications in different forecast horizons.
-Recall that OLS reconciliation is doing orthogonal projection whereas MinT and WLS are doing oblique projections onto the coherent subspace.
-It is apparent from the plot that the MSE difference for OLS is always positive, implying that OLS improves the base in terms of MSE in all replications.
-On the other hand,  there are some instances that this difference for MinT and WLS is negative which is reflected from the short negative tails of box-plots.
-This implies that oblique projections will not improve the base forecasts in every case.
-However, these projections will outperform the base with respect to MSE on average which is again reflected from the highly positive skewed MSE differences.
-
 \section{Conclusions} \label{sec:conclusions}

### 2019-08-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
fake change
Data section revision

@@
 
-\pdfminorversion=4
+%\pdfminorversion=4
 % NOTE: To produce blinded version, replace "0" with "1" below.
@@
 \addtolength{\textwidth}{1in}%
-\addtolength{\textheight}{-.3in}%
+\addtolength{\textheight}{1in}%
 \addtolength{\topmargin}{-.8in}%
@@
 The black dot ${\bm y}$ denotes the (unknown) target of the forecast.
-Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection}
+Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows an oblique projection.} \label{fig:OthogonalVSOblique_projection}
 	\end{figure}
@@
 
-	Using an empirical application to forecast Australian domestic tourism flow, we illustrate the usefulness of projection based reconciliation in practice.
+	\textcolor{red}{GA: I will rewrite/review this when we decide where we put all our results - I am referring to the projection results - currently I think it is best that everything goes here and we make a comment at the end of Section 3.3 guiding the reader to the results here.
+This will make the empirical application a bit broader not only about bias correction, i.e., both about showing how projections work and how bias correction works.} Using an empirical application to forecast Australian domestic tourism flow, we illustrate the usefulness of projection based reconciliation in practice.
 Previous studies have pronounced that the reconciliation improves point forecast accuracy in domestic tourism flow in Australia (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}).
@@
 
-	We use ``overnight trips" as a measure of domestic tourism flow in Australia.
-Total ``overnight trips" in Australia can be disaggregated into 7 states, 27 zones and 75 regions forming a geographical hierarchy with $110$ total number of series and $75$ bottom level series.
-More information about the series of this hierarchy is given in Table \ref{table:A1} in the appendix.
-Data were obtained from the National Visitor Survey (NVS) which were collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more.
-Data form a monthly series starting from January 1998 to December 2017 which gives a total of $240$ observations per series.
+	We use ``overnight trips'' across Australia as a measure of domestic tourism flows.
+The data are provided by the National Visitor Survey (NVS) and are collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more.
+Tourism flows in Australia can be disaggregated into 7 states, 27 zones and 75 regions forming a natural geographical hierarchy that is of interest to tourism operators and policy makers.
+Hence, there are $110$ series across the hierarchy with $75$ bottom-level series.
+More information about the series and the geographical hierarchy is presented in Table \ref{table:A1} in the Appendix.
+The data span the period January 1998 to December 2017, which gives a total of $240$ observations per series.
 
-	As we can see from the time plots in Figure \ref{fig:Total_TSplots}, the total overnight trips has a strong seasonal pattern.
-Most overnight trips seems to be happening in January which is associated with the summer season in southern hemisphere.
-On the other hand the least trips are happening in February perhaps due to the end of summer holidays.
-We could also observe a slight downward trend in total overnight trips from 2005 to 2010 and then started increasing since 2010.
+Figure \ref{fig:Total_TSplots} shows time, sub-series and seasonal plots of the total aggregate overnight trips.
+As is usual with tourism flows these show a strong seasonal pattern.
+Overnight trips peak in January corresponding to the summer vacation season in Australia.
+There are also some lower peaks observed in April, July and October corresponding to school holidays.
+On the other hand the month with the least overnight trips is February indicating that people travel least for the month following their summer vacation.
+The time plot shows a pronounced upward trend starting from around 2010 till the end of the sample, with the data being fairly flat from the beginning of the sample and a slight downward trend during 2004-2010.
 
-	Figure \ref{fig:States_Zones_Regs_TSplots} shows time plots for some selected series from states, zones and regions of the hierarchy.
-While observing the series in state level, we could see that Northern Territory(NT) has a different seasonal patterns compared to the other states.
-Highest overnight trips to NT happens during June - August where July being the peak.
-Lowest trips happens during December - February.
-This is perhaps Australians prefer to visit North of Australia during its dry season rather than in wet season.
-This pattern also reflect in zones and regions associated to NT as well as regions in north Queensland.
-All other states and their associated zones and regions show peak overnight trips in January.
+The top panel of Figure \ref{fig:States_Zones_Regs_TSplots} shows time plots for the seven states, hence the first-level of the hierarchy.
+The panels below show some selected series from the second-level zones and the bottom-level regions of the geographical hierarchy.
+The plots display the diversity of time series features, within but also between levels.
+For example, noticeable at the first-level is the asynchronous seasonal pattern of the Northern Territory to the other states.
+For the Northern Territory the high tourist season occurs during June-August with July being the peak, while the low season is during December-February.
+This reflects the tropical climate of the Northern Territory, with Australians mostly visiting the North during its dry winter-season rather than the wet summer season.
+Noticeable as we move to the lower levels is the variation in the signal-to-noise ratio, with the regional bottom-level series being noisier compared to the series from levels above.
+This of course highlights the importance of modelling series at all levels without any loss of valuable information.
 
-	Further we noticed that the signal-to-noise ratio decreases with the level of disaggregation of the hierarchy.
-We can see much noisier series in regional and zone levels whereas the noise is comparatively stabilised in the upper levels.
-We have also observed that the overnight trips to `Adelaide Hills' has an anomalous observation on December-2002.
+We should note here that we have observed an anomalous observation for `Adelaide Hills' for December-2002.
 We replace this observation with the average overnight trips on December-2001 and December-2003 for the same destination.
+\textcolor{red}{Puwasala can you please describe here how this was anomalous.
+I'm wondering if this is a Bali bombing effect where we had a huge spike in Australian domestic tourism because of the Bali bombings in Oct with Australians travelling within Australia due to them being scared basically.}
 
-	Using this data we produce $h=1$ to $h=6$ month ahead forecasts based on a rolling window approach.
-First a training window of $100$ observations is considered from Jan-$1998$ to Apr-$2006$ and  forecasts produce for May-$2006$ to Oct-$2006$.
-Then we roll the training window one month at a time where the final forecast is produced for Dec-$2017$.
-This leads to $140 \quad 1$-step-ahead, $139 \quad 2$-step-ahead through $135 \quad 6$-step-ahead forecasts left for evaluation.
+Starting from a training window of $100$ observations, i.e., Jan-$1998$ to Apr-$2006$ we generate $h=1$ to $h=6$ steps-ahead forecasts.
+Using a rolling window we repeat the exercise until the end of the sample.
+This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $135~6$-steps-ahead forecasts available for forecast evaluation.
 
@@
 		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/Total_TSplots.pdf}
-		\caption{Total overnight trips are presented in log scale.
-Top panel shows the time plot.
-Bottom left panel shows the sub-series plot for each month whereas bottom right panel shows the seasonal plot coloured by year  }\label{fig:Total_TSplots}
+		\caption{Total domestic overnight trips (in logs) for Australia from January 1998 to December 2017.
+The top-panel shows a time plot; the bottom-left panel a sub-series plot for each month; the bottom-right panel shows a seasonal plot coloured by year.} \label{fig:Total_TSplots}
 	\end{figure}
@@
 		\small
-		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots.pdf}
+		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots1.pdf}
 		\caption{Time plot of overnight trips for some selected series from different disaggregate levels of the hierarchy.
@@
 
-	\subsection{Base forecasts and reconciliation:}
+	\subsection{Transformations and bias adjustments}
 
-	First we transform each series in the hierarchy to stabilise any variations in the data.
-We use two types of transformation, namely, log transformation and more general Box-Cox transformation.
-Equation (\ref{eq:BoxCox_transformation}) gives the mathematical formula for these transformations.
-A constant is added to each series to avoid the impact of zero observations when taking log transformations.
-We note here that the two transformations were applied separately to the series in the hierarchy and treated distinctly.
+	We first transform each series in the hierarchy using two types of transformations. Namely, we perform a log-transformation and also a more general Box-Cox transformation
 
@@
 	\begin{cases}
-	\log(y_t) & \text{if log transformation, $\lambda = 0$} \\
-	\frac{y_t^\lambda - 1}{\lambda}  & \text{if Box-Cox transformation, $\lambda \ne 0$} 
+	\log(y_t) & \text{for log transformation} \\
+	\frac{y_t^\lambda - 1}{\lambda}  & \text{for Box-Cox transformation, $\lambda \ne 0$}
 	\end{cases}
@@
 
-	The ``Guerrero" method \citep{guerrero1993time} implemented in \verb|BoxCox.lambda()| function in \verb|forecast| package in R software \citep{Rforecast} is use to select optimal $\lambda$ for Box-Cox transformation.
-For log transformation we simply choose $\lambda = 0$.
+.
+Equation (\ref{eq:BoxCox_transformation}) gives the mathematical formula for these transformations.
+A constant (in particular $1$) is added to each series to avoid the impact of zero observations when taking log transformations, as some zeros exist in the bottom-level series.
+
+We note here that the two sets of transformations (log and the general Box-Cox) were applied separately to the series in the hierarchy and are treated distinctly.	The ``Guerrero" method \citep{guerrero1993time} implemented in \verb|BoxCox.lambda()| function in \verb|forecast| package in R software \citep{Rforecast} is uses to select $\lambda$ for the Box-Cox transformations.
+For the log transformations we simply set $\lambda = 0$.
+
 Then  we fit univariate ARIMA models for the transformed series.
@@
 	\section{Appendix}
-	\thisfloatpagestyle{empty}
+	%\thisfloatpagestyle{empty}
 	\input{Appendix}

### 2019-08-23 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
First go at Empirical Section

@@
 The data are provided by the National Visitor Survey (NVS) and are collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more.
-Tourism flows in Australia can be disaggregated into 7 states, 27 zones and 75 regions forming a natural geographical hierarchy that is of interest to tourism operators and policy makers.
+We disaggregate Tourism flows into 7 states, 27 zones and 75 regions forming a natural geographical hierarchy that is of interest to tourism operators and policy makers.
 Hence, there are $110$ series across the hierarchy with $75$ bottom-level series.
@@
 
-Figure \ref{fig:Total_TSplots} shows time, sub-series and seasonal plots of the total aggregate overnight trips.
-As is usual with tourism flows these show a strong seasonal pattern.
+Figure \ref{fig:Total_TSplots} shows time, sub-series and seasonal plots of the aggregate overnight trips for Australia.
+As is usual with tourism data, overnight these show a strong seasonal pattern.
 Overnight trips peak in January corresponding to the summer vacation season in Australia.
-There are also some lower peaks observed in April, July and October corresponding to school holidays.
+There are also some lower peaks observed in April, July and October corresponding to school term breaks.
 On the other hand the month with the least overnight trips is February indicating that people travel least for the month following their summer vacation.
-The time plot shows a pronounced upward trend starting from around 2010 till the end of the sample, with the data being fairly flat from the beginning of the sample and a slight downward trend during 2004-2010.
+The time plot also shows a pronounced upward trend starting from around 2010 till the end of the sample, with flows being fairly flat from the beginning of the sample and a slight downward trend during 2004-2010.
 
@@
 The plots display the diversity of time series features, within but also between levels.
-For example, noticeable at the first-level is the asynchronous seasonal pattern of the Northern Territory to the other states.
+For example, noticeable at the first-level is the asynchronous seasonal pattern between Northern Territory and the other states.
 For the Northern Territory the high tourist season occurs during June-August with July being the peak, while the low season is during December-February.
@@
 This of course highlights the importance of modelling series at all levels without any loss of valuable information.
-
-We should note here that we have observed an anomalous observation for `Adelaide Hills' for December-2002.
-We replace this observation with the average overnight trips on December-2001 and December-2003 for the same destination.
-\textcolor{red}{Puwasala can you please describe here how this was anomalous.
-I'm wondering if this is a Bali bombing effect where we had a huge spike in Australian domestic tourism because of the Bali bombings in Oct with Australians travelling within Australia due to them being scared basically.}
+We should note here that we observed an anomalous (extremely high) observation for `Adelaide Hills' for December-2002.
+We replaced this observation with the average overnight trips on December-2001 and December-2003 for the same destination.
 
 Starting from a training window of $100$ observations, i.e., Jan-$1998$ to Apr-$2006$ we generate $h=1$ to $h=6$ steps-ahead forecasts.
-Using a rolling window we repeat the exercise until the end of the sample.
+Using a rolling window we repeat the exercise one observation at a time until the end of the sample.
 This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $135~6$-steps-ahead forecasts available for forecast evaluation.
@@
 		\small
-		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots1.pdf}
+		\includegraphics[width= \textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots1.pdf}
 		\caption{Time plot of overnight trips for some selected series from different disaggregate levels of the hierarchy.
@@
 
-	\subsection{Transformations and bias adjustments}
+\clearpage
+	\subsection{Transformations and bias adjustment}
 
-	We first transform each series in the hierarchy using two types of transformations. Namely, we perform a log-transformation and also a more general Box-Cox transformation
+	We first transform each series in the hierarchy using two types of transformations.
+Namely, we perform a log-transformation and also the more general Box-Cox transformation.
+A Box-Cox transformation is defined as,
 
 \begin{equation} \label{eq:BoxCox_transformation}
-	x_t =
+	w_t =
 	\begin{cases}
-	\log(y_t) & \text{for log transformation} \\
-	\frac{y_t^\lambda - 1}{\lambda}  & \text{for Box-Cox transformation, $\lambda \ne 0$}
+	\log(y_t) & \text{if}~\lambda=0;\\
+	\frac{y_t^\lambda - 1}{\lambda}  & \text{otherwise}.
 	\end{cases}
@@
 
-.
-Equation (\ref{eq:BoxCox_transformation}) gives the mathematical formula for these transformations.
-A constant (in particular $1$) is added to each series to avoid the impact of zero observations when taking log transformations, as some zeros exist in the bottom-level series.
+We first set $\lambda=0$ and hence consider only a log transformation.
+For the second more general Box-Cox transformation we select $\lambda$ using the ``Guerrero'' method \citep{guerrero1993time} implemented in the \verb|BoxCox.lambda()| function in the \verb|forecast| package in R \citep{Rforecast}.
+As observations with zero value exist in some of the bottom-level series, before transforming we add a constant (more specifically $1$) to each series.
+This overcomes the challenge of undefined transformed values for zero observations when we specifically implement the log transformation or when $\lambda$ is selected to be zero by the ``Guerrero'' method.
+The constant is subtracted from the final forecasts.
 
-We note here that the two sets of transformations (log and the general Box-Cox) were applied separately to the series in the hierarchy and are treated distinctly.	The ``Guerrero" method \citep{guerrero1993time} implemented in \verb|BoxCox.lambda()| function in \verb|forecast| package in R software \citep{Rforecast} is uses to select $\lambda$ for the Box-Cox transformations.
-For the log transformations we simply set $\lambda = 0$.
+After transformation we fit univariate ARIMA models to each transformed series.
+The \verb|auto.arima()| function in the \verb|forecast| package is used to choose the best model that minimises the AICc.
+Using the fitted models, forecasts are produced for $h=1$ to $6$-steps ahead for each series in the hierarchy.
 
-Then  we fit univariate ARIMA models for the transformed series.
-\verb|auto.arima()| function in \verb|forecast| package is use to choose the best model that minimises the AIC.
-Using the fitted models, forecasts are produced for $6$ forecast horizons for each series in the hierarchy.
-These forecasts are then back-transformed using equation (\ref{eq:BoxCox_back-transformation}) to scale them back into the original space.
-However, the back transformed forecasts will be biased \citep{guerrero1993time}.
+The forecasts are then back-transformed by simply reversing the Box-Cox transformation using
 
 \begin{equation} \label{eq:BoxCox_back-transformation}
-	y_{t+h} =
+	\hat{y}_{t+h|t} =
 	\begin{cases}
-	\exp({x_{t+h}}) & \text{if log transformation, $\lambda = 0$} \\
-	(\lambda x_{t+h} + 1)^{1/\lambda}  & \text{if Box-Cox transformation, $\lambda \ne 0$}
+	\exp({\hat{w}_{t+h|t}}) & \text{if}~\lambda = 0; \\
+	(\lambda \hat{w}_{t+h|t} + 1)^{1/\lambda}  & \text{otherwise.}
 	\end{cases}
@@
 
-	Hence the reconciled forecasts that follow from these forecasts will also be biased.
-This is the exact scenario that we want to demonstrate in this study.
-As proposed before, we first adjust for the bias in base forecasts prior to the reconciliation.
-We use the de-biasing factor proposed by \cite{taylor1986retransformed} to calculate the back-transformed bias-adjusted forecasts.
-These are given in equation (\ref{eq:BoxCox_BT_biasadj}) .
+These back-transformed forecasts are potentially biased as they are not the mean of the forecast distribution but the median (assuming that the distribution of the transformed space is symmetric).
+Hence, the reconciled forecasts that follow from these forecasts will also be biased.
+This is the exact scenario that we want to demonstrate in this study and we next move to our proposed solution of bias correcting the base forecasts before reconciling for which we explore two scenarios.
+
+Using a Taylor series expansion \todo{Rob do we need a reference here or is this obvious/well known?} the back-transformed mean of the forecast distribution for a Box-Cox transformation is given by
 
 \begin{equation} \label{eq:BoxCox_BT_biasadj}
-	 y_{t+h} =
+	 \hat{y}_{t+h|t} =
 	\begin{cases}
-	\exp({x_{t+h}})[1+\frac{\sigma_h^2}{2}] & \text{if } \lambda = 0 \\
-	(\lambda x_{t+h} + 1)^{1/\lambda}[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda x_{t+h} + 1)^2}]       & \text{if } \lambda \ne 0
+	\exp({\hat{w}_{t+h|t}})[1+\frac{\sigma_h^2}{2}] & \text{if}~\lambda = 0; \\
+	(\lambda \hat{w}_{t+h|t} + 1)^{1/\lambda}[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda \hat{w}_{t+h|t} + 1)^2}]       & \text{if}~\lambda \ne 0,
 	\end{cases}
 	\end{equation}
-	where, $x_{t+h}$ is the $h$-step-ahead forecasts from the Box-Cox transformed series and $\sigma_h^2$ is the variance of $x_{t+h}$.
+where, $\hat{w}_{t+h|t}$ is the $h$-step-ahead forecast from the Box-Cox transformed series and $\sigma_h^2$ is the variance of $\hat{w}_{t+h|t}$.
+Using the mean of the forecast distribution returns bias adjusted base forecasts compared to the simple back-transformation of \eqref{eq:BoxCox_back-transformation}.
+We refer to this as Method-1 in the results that follow.
 
-	Once we get the base forecasts for all series in the hierarchy, we can do the projection-based reconciliation to get coherent forecasts.
-We reconcile both biased and bias-corrected (Unbiased) base forecasts to demonstrate how the reconciliation follows from unbiased base forecasts improves the forecast accuracy.
-MinT(Shrink), WLS, OLS and bottom-up methods are used for reconciliation.
+The second scenario of bias adjustment we explore is using the in-sample forecast error mean of the biased forecasts to adjust the out of sample forecasts.
+We refer to this a Method-2 in the results that follow.
 
-%	
-%	\begin{table}
-%		\caption {Average {MSE($\times 10^3$)} of base and reconciled point forecasts at forecasts horizons $h=1,...,6$ are presented.
-Bias and unbiased columns represent the results for biased-base/biased-reconciled and unbiased-base/unbiased-reconciled forecasts respectively.
-Comparisons can be made across biased vs unbiased forecasts as well as base vs reconciled forecasts.}
-%		\label{tab:Results_MSE}
-%		\centering\tabcolsep=0.08cm
-%		\resizebox{\linewidth}{!}{
-%		\begin{tabular}{@{}lSSSSSSSSSSSS@{}}
-%			\toprule
-%			\multicolumn{1}{c}{ } & \multicolumn{2}{c}{h=1} & \multicolumn{2}{c}{h=2} & \multicolumn{2}{c}{h=3} & \multicolumn{2}{c}{h=4} & \multicolumn{2}{c}{h=5} & \multicolumn{2}{c}{h=6} \\
-%			\cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11} \cmidrule(lr){12-13}
-%			Method & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased & Biased & Unbiased\\
-%			\midrule
-%			Base & 12.18 & 161.63 & 13.14 & 243.13 & 14.08 & 269.20 & 15.88 & 325.41 & 15.49 & 332.11 & 15.79 & 344.40\\
-%			\hline
-%			MinT(Shrink) & 10.14 & $\bm{9.96}$ & 11.47 & $\bm{10.78}$ & 12.55 & $\bm{11.94}$ & 15.53 & $\bm{14.03}$ & 14.63 & $\bm{13.46}$ & 15.28 & $\bm{13.78}$\\
-%			\hline
-%			WLS & 15.62 & 13.97 & 15.93 & 13.71 & 16.65 & 14.50 & 18.91 & 16.26 & 18.76 & 16.20 & 18.85 & 15.83\\	
-%			\hline
-%			OLS & 11.73 & 135.17 & 12.80 & 204.42 & 13.73 & 225.59 & 15.56 & 272.41 & 15.17 & 278.08 & 15.49 & 288.21\\
-%			\hline
-%			Bottom-up & 17.86 & 15.55 & 17.86 & 14.90 & 18.47 & 15.61 & 20.50 & 17.21 & 20.34 & 17.04 & 20.39 & 16.69\\
-%			
-%			\bottomrule
-%		\end{tabular}
-%	}
-%	\end{table}
-
-%%%%%%%%%%%%%%%%%%%
+Using the three sets of base forecasts we generate coherent forecasts using the bottom-up approach but also implementing OLS, WLS and MinT reconciliation projections and compare the results for when the base forecasts are biased and bias-adjusted (unbiased).
+We discuss the results next.
 
@@
 
-Mean Squared Error (MSE) is used to measure the forecast accuracy.
-Average MSE over $140$ replications for $1$-step-ahead forecasts are presented for log transformation and Box-Cox transformation separately in Table \ref{tab:Results_MSE}.
+Table \ref{tab:Results_MSE} presents the Mean Squared Error (MSE) over the $140$ replications for $1$-step-ahead forecasts.
+Note that the conclusion that follow extend almost identically to forecast horizons $2-6$.
+We do not present these here to save space but they are available upon request.
+
+General findings:
+
+- Bias adjusting using Method 1, i.e., a proper method improves forecast accuracy.
+- Bias adjusting using Method 2, does not.
+The transformations we consider here are multiplicative type transformations - the in-sample residual adjustment is an additive adjustment hence it does not help.
+
+\textcolor{red}{I have stopped here. Will continue after we have all results.}
 

### 2019-08-23 Hierarchical-forecast-reconciliation/Empirical-results/TS-plots/TimePlots.R

@@ -200,11 +200,11 @@ grid.arrange(arrangeGrob(Plot_regions_1),
              ncol = 2) -> Plot_regions
 
 # ok tried to play with the save below but cannot get as good as
-# using the export with max plot window
+# using the pdf export with save to device with width 10 and height 12.4
 
-# pdf("Timeplots.pdf",paper="a4",height = 12,width = 30)
-# grid.arrange(arrangeGrob(Plot_Sates, Plot_Zones, Plot_regions ))
-# dev.off()
+#pdf("Timeplots4.pdf",paper="a4",height = 10.27,width = 9.7)
+grid.arrange(arrangeGrob(Plot_Sates, Plot_Zones, Plot_regions ))
+#dev.off()
 
 
 ###############################

### 2019-08-24 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added appendix with proof sf that SGS=S

@@
 	%\thisfloatpagestyle{empty}
+	\subsection{Proof $\bm{S}\bm{G}\bm{S}=\bm{S}$ implies $\bm{S}\bm{G}$ is a projection}
+	Here we establish that if $\bm{S}\bm{G}$ is a projection onto the linear subspace spanned by $\bm{S}$ then $\bm{S}\bm{G}\bm{S}=\bm{S}$.
+We also prove that the converse holds, namely that if the condition $\bm{S}\bm{G}\bm{S}=\bm{S}$ holds then $\bm{S}\bm{G}$ must be a projection onto the linear subspace spanned by $\bm{S}$.
+
+	To establish the first statement let $\bm{s}_j$ be the $j^{th}$ column of $\bm{S}$.
+Since by definition, $\bm{s}_j$ lies in in $\mathfrak{s}$, it must hold that $\bm{S}\bm{G}\bm{s}_j=\bm{s}_j$.
+Stacking these vectors horizontally
+	\begin{align}
+	\bm{S}\bm{G}\bm{S}&=\begin{pmatrix}
+	\bm{S}\bm{G}\bm{s}_1, & \bm{S}\bm{G}\bm{s}_2, & \cdots & \bm{S}\bm{G}\bm{s}_m
+	\end{pmatrix}\\
+	&=\begin{pmatrix}
+	\bm{s}_1, & \bm{s}_2, & \cdots & \bm{s}_m
+	\end{pmatrix}\\
+	&=\bm{S}
+	\end{align}
+
+	To establish the converse it suffices to postmultiply the condition $\bm{S}\bm{G}\bm{S}=\bm{S}$ by $\bm{G}$.
+This yields $\bm{S}\bm{G}\bm{S}\bm{G}=\bm{S}\bm{G}$ which in turn implies idempotence since $(\bm{S}\bm{G})^2=\bm{S}\bm{G}$.
 	\input{Appendix}
-
 	\newpage

### 2019-08-27 Application-R/Application-TourismData/Final-results/TourismData-Final-results.Rmd
Repeating the analysis constraining for BoxCox lambda

--- 2019-08-19 Application-R/Application-TourismData/Final-results/TourismData-Final-results.Rmd
@@
 library(tidyverse)
-library(fpp2)
 library(Matrix)
@@
 library(readr)
-library(BigVAR)
-library(vars)
 library(tibble)
 library(kableExtra)
-library(reshape2)
+# library(reshape2)
+```
+
+# Box and whisker plots for orthogonal and oblique projections
+
+```{r, echo=FALSE}
+OvernightTrips_OriginalScale_Fc <- read.csv("OvernightTrips_OriginalScale_Fc.csv")[,-1]
+
+OvernightTrips_OriginalScale_Fc %>% 
+  mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2) %>% 
+  group_by(`R.method`, Fc_horizon, Replication) %>% 
+  summarise(MSE = mean(SquaredE)) -> OvernightTrips_OriginalScale_MSE
+
+DF_MSE <- DF_LogTrans %>%
+  mutate(SquaredE = (`Actual` - `Forecasts`)^2) %>%
+  filter(`Forecast_Horizon` == 1) %>%
+  dplyr::select(-`Forecast_Horizon`) %>%
+  group_by(`F.method`, `R.method`, Replication) %>%
+  summarise(MSE = mean(SquaredE))
+
+DF_MSE %>%
+  filter(`F.method`=="Unbiased_M1", `R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>%
+  spread(key = `R.method`, value = MSE) %>%
+  mutate("Base-OLS" = Base - OLS,
+         "Base-MinT" = Base - `MinT(Shrink)`,
+         "Base-WLS" = Base - WLS) %>%
+  dplyr::select(Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
+  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>%
+  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>%
+  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>%
+  ggplot(aes(x = Method, y = MSE)) +
+  geom_boxplot() +
+  ylab("MSE") + xlab("Reconciliation Method")
+
 ```
@@
 
-# More analysis on BoxCox transformed resulst
+# More analysis on BoxCox transformed results
 
-```{r}
+```{r echo=FALSE}
 DF_BoxCoxTrans %>% 
@@
   mutate("Bias-Unbiase" = Bias - Unbiased_M1) %>% 
-  filter(`Bias-Unbiase` < -5)
+  filter(`Bias-Unbiase` < -100)
 
 ```
+
 Bias correction is giving wiered results for `Total` series.
@@
   filter(Forecast_Horizon == 1, Series == "Total") -> DF_BoxCoxTrans_Tot_h1
+
+# DF_BoxCoxTrans %>% 
+#   filter(Forecast_Horizon == 1, Series == "A") -> DF_BoxCoxTrans_A_h1
+# 
+# DF_BoxCoxTrans %>% 
+#   filter(Forecast_Horizon == 1, Series == "B") -> DF_BoxCoxTrans_B_h1
 
@@
   ylab("Forecasts/Actual") + 
-  ggtitle("Forecasts follow from BoxCox Transformation") + 
-  theme(legend.position="bottom")
+  ggtitle("Forecasts for Total series follow from BoxCox Transformation") + 
+  theme(legend.position="bottom", legend.title = element_blank())
+
+#  DF_BoxCoxTrans_A_h1 %>% 
+#   filter(R.method == "Base", F.method %in%c("Bias","Unbiased_M1")) %>%
+#   ungroup() %>% 
+#   dplyr::select(F.method, Forecasts, Actual, Replication) %>% 
+#   spread(key = F.method, value = Forecasts) %>% 
+#   gather(-Replication, key = "Forecasts/Actual", value = Val) -> DF_BoxCoxTrans_A_h1
+#   
+# DF_BoxCoxTrans_A_h1 %>% 
+#   mutate(`Forecasts/Actual` = recode(`Forecasts/Actual`, "Unbiased_M1" = "Unbiased")) %>%   ggplot() + 
+#   geom_line(aes(x = Replication, y = Val, color = `Forecasts/Actual`)) + 
+#   ylab("Forecasts/Actual") + 
+#   ggtitle("Forecasts for NSW series follow from BoxCox Transformation") + 
+#   theme(legend.position="bottom", legend.title = element_blank()) 
+#  
+#  DF_BoxCoxTrans_B_h1 %>% 
+#   filter(R.method == "Base", F.method %in%c("Bias","Unbiased_M1")) %>%
+#   ungroup() %>% 
+#   dplyr::select(F.method, Forecasts, Actual, Replication) %>% 
+#   spread(key = F.method, value = Forecasts) %>% 
+#   gather(-Replication, key = "Forecasts/Actual", value = Val) -> DF_BoxCoxTrans_B_h1
+#   
+# DF_BoxCoxTrans_B_h1 %>% 
+#   mutate(`Forecasts/Actual` = recode(`Forecasts/Actual`, "Unbiased_M1" = "Unbiased")) %>%   ggplot() + 
+#   geom_line(aes(x = Replication, y = Val, color = `Forecasts/Actual`)) + 
+#   ylab("Forecasts/Actual") + 
+#   ggtitle("Forecasts for Victoria series follow from BoxCox Transformation") + 
+#   theme(legend.position="bottom", legend.title = element_blank())
 
@@
 ```{r}
+
+DF_BoxCoxTrans_Tot_h1 %>% 
+  spread(key = `Forecasts/Actual`, value = Val) %>% 
+  mutate("Unb-Act" = Unbiased_M1 - Actual) %>% 
+  filter(`Unb-Act`>1000)
+
+```
+
+Very large bias corrected forecasts are given for some replications. For example in the rolling window Jul-2003 to Oct-2011. Observing the model auto.arima fits:
+
+```{r echo=FALSE}
 OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
@@
 #Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
-Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, 
-                                  list(7, c(6,5,4,4,3,3,2), c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,3,4,2,3,1,1,1,2,2,3,4))))
-
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
+                                                                  c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
+                                                                    3,4,2,3,1,1,1,2,2,3,4))))
 AllTS_new <- allts(Hierarchy) %>%
@@
 
-lambda <- numeric()
+L <- 100
 
-for (j in 1:140) {#C=140
+```
 
-  Train <- AllTS_new[j:(100+j-1), "Total"] %>% as.ts()
+```{r echo=FALSE}
+j = 67
+Train <- AllTS_new[j:(L+j-1),]
+TS <- Train[,"Total"] %>% ts(frequency = 12)
+fit <- auto.arima(TS, lambda = "auto", biasadj = FALSE, stepwise = FALSE, approximation = FALSE)
+Fc <- forecast(fit, h=1)
 
-  lambda[j] <- BoxCox.lambda(Train)
+Fc_trans <- Fc$mean
+L_PI <- Fc$lower[,"95%"]
+sig_h <- (Fc_trans - L_PI)/1.96
+sig2_h <- sig_h^2
 
-}
+summary(fit)
+
 ```
+
+The estimated drift term has a very large standard error. Further the variance of $\hat{y}_{t+1}$ is `r sig2_h` which is very large
 
@@
 ```
-
-```{r echo=FALSE}
-DF_LogTrans %>% 
-  filter(Forecast_Horizon == 1) -> DF_LogTrans_h1
-
-DF_LogTrans_h1 %>% 
-  filter(Series == "Total", R.method == "Base", F.method == "Bias") %>% 
-  dplyr::select(Actual, Replication) -> Total_Log_True
-
-DF_LogTrans_h1 %>% 
-  filter(Series == "Total", R.method == "Base", F.method %in%c("Bias","Unbiased_M1")) -> Total_Log_Fc
-
-ggplot() + 
-  geom_line(data = Total_Log_Fc, aes(x = Replication, y = Forecasts, color = `F.method`)) + 
-  geom_line(data = Total_Log_True, mapping = aes(x = Replication, y = Actual)) + 
-  ylab("Forecasts/Actual") + 
-  ggtitle("Forecasts follows from Log Transformation")
-
-```
-
-```{r, echo=FALSE}
-
-DF_MSE <- DF_LogTrans %>% 
-  mutate(SquaredE = (`Actual` - `Forecasts`)^2) %>% 
-  filter(`Forecast_Horizon` == 1) %>% 
-  dplyr::select(-`Forecast_Horizon`) %>% 
-  group_by(`F.method`, `R.method`, Replication) %>% 
-  summarise(MSE = mean(SquaredE))
-
-DF_MSE %>% 
-  filter(`F.method`=="Unbiased_M1", `R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>% 
-  spread(key = `R.method`, value = MSE) %>% 
-  mutate("Base-OLS" = Base - OLS,
-         "Base-MinT" = Base - `MinT(Shrink)`,
-         "Base-WLS" = Base - WLS) %>% 
-  dplyr::select(Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
-  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>% 
-  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>% 
-  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>% 
-  ggplot(aes(x = Method, y = MSE)) + 
-  geom_boxplot() + 
-  ylab("MSE") + xlab("Reconciliation Method")
-
-```

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Results/Analysis.R

@@ -1,21 +1,0 @@
-
-library(tidyverse)
-
-
-
-DF_BoxCoxTrans_1_50 <- read.csv("DF_BoxCoxTrans_1-50.csv")[,-1]
-DF_BoxCoxTrans_51_100 <- read.csv("DF_BoxCoxTrans_51-100.csv")[,-1]
-DF_BoxCoxTrans_101_140 <- read.csv("DF_BoxCoxTrans_101-140.csv")[,-1]
-
-rbind(DF_BoxCoxTrans_1_50, DF_BoxCoxTrans_51_100, DF_BoxCoxTrans_101_140) %>% 
-  as.data.frame() -> DF_BoxCoxTrans
-write.csv(x=DF_BoxCoxTrans, file = "DF_BoxCoxTrans.csv")
-
-
-DF_BoxCoxTrans %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans
-
-DF_BoxCoxTrans %>% 
-  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
-  summarise(MSE = mean(SquaredE)) %>% 
-  spread(key = Forecast_Horizon, value = MSE)
-

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Set-1/TourismForecasting_BoxCoxTrans_BiasAdjust_set1.R

@@ -1,0 +1,434 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+library(tsibble)
+library(fable)
+library(fabletools)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Set-1/TourismForecasting_BoxCoxTrans_BiasAdjust_set1_1-50.R

@@ -1,0 +1,434 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+library(tsibble)
+library(fable)
+library(fabletools)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Set-1/TourismForecasting_BoxCoxTrans_BiasAdjust_set1_101-140.R

@@ -1,0 +1,434 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+library(tsibble)
+library(fable)
+library(fabletools)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Set-2/TourismForecasting_BoxCoxTrans_BiasAdjust_set2_101-140.R

@@ -1,0 +1,436 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the Box-Cox transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#Box-Cox transformation lambda is selected from Guerrero method constrained in (-0.5,2)
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+library(tsibble)
+library(fable)
+library(fabletools)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
[…]

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/TourismForecasting_BoxCoxTrans_BiasAdjust.R

@@ -1,402 +1,0 @@
-## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
-## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
-## Length of data expands from Jan-1998 to Dec-2017
-
-# Here we fit univariate ARIMA models for the log transformed data
-# The back transformed data will be biased and we bias adjust to get 
-# unbiased point forecasts.
-
-#We use two methods for bias correction
-# M1 - Bias correction via formulation
-# M2 - Bias correction via residual mean adjustment
-
-library(tidyverse)
-library(fpp2)
-library(Matrix)
-library(hts)
-library(readr)
-library(tibble)
-
-# Import bottom level data
-#Importing data
-
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(`Adelaide Hills` > 80) %>% 
-  as.numeric() -> a
-
-which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(row_number() %in% c(60+12,60-12)) %>% 
-  summarise(mean(`Adelaide Hills`)) %>% 
-  as.numeric() -> b
-
-OvernightTrips_Region_new <- OvernightTrips_Region %>% 
-  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
-                                      TRUE ~ as.double(`Adelaide Hills`)))
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
-Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/TourismForecasting_BoxCoxTrans_BiasAdjust_51-100.R

@@ -1,402 +1,0 @@
-## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
-## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
-## Length of data expands from Jan-1998 to Dec-2017
-
-# Here we fit univariate ARIMA models for the log transformed data
-# The back transformed data will be biased and we bias adjust to get 
-# unbiased point forecasts.
-
-#We use two methods for bias correction
-# M1 - Bias correction via formulation
-# M2 - Bias correction via residual mean adjustment
-
-library(tidyverse)
-library(fpp2)
-library(Matrix)
-library(hts)
-library(readr)
-library(tibble)
-
-# Import bottom level data
-#Importing data
-
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(`Adelaide Hills` > 80) %>% 
-  as.numeric() -> a
-
-which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(row_number() %in% c(60+12,60-12)) %>% 
-  summarise(mean(`Adelaide Hills`)) %>% 
-  as.numeric() -> b
-
-OvernightTrips_Region_new <- OvernightTrips_Region %>% 
-  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
-                                      TRUE ~ as.double(`Adelaide Hills`)))
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
-Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Trash/Results/Analysis.R

@@ -1,0 +1,33 @@
+
+library(tidyverse)
+
+
+
+DF_BoxCoxTrans_1_25 <- read.csv("DF_BoxCoxTrans_1-25.csv")[,-1] %>% select(-SquaredE)
+DF_BoxCoxTrans_26_50 <- read.csv("DF_BoxCoxTrans_26-50.csv")[,-1] %>% select(-SquaredE)
+
+DF_BoxCoxTrans_51_75 <- read.csv("DF_BoxCoxTrans_51-75.csv")[,-1] %>% select(-SquaredE)
+DF_BoxCoxTrans_76_100 <- read.csv("DF_BoxCoxTrans_76-100.csv")[,-1] %>% select(-SquaredE)
+
+DF_BoxCoxTrans_101_125 <- read.csv("DF_BoxCoxTrans_101-125.csv")[,-1] %>% select(-SquaredE)
+DF_BoxCoxTrans_126_140 <- read.csv("DF_BoxCoxTrans_126-140.csv")[,-1]
+
+rbind(DF_BoxCoxTrans_1_25, DF_BoxCoxTrans_26_50, DF_BoxCoxTrans_51_75, 
+      DF_BoxCoxTrans_76_100, DF_BoxCoxTrans_101_125, DF_BoxCoxTrans_126_140) %>% 
+  as.data.frame() -> DF_BoxCoxTrans
+write.csv(x=DF_BoxCoxTrans, file = "DF_BoxCoxTrans.csv")
+
+
+DF_BoxCoxTrans %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans
+
+DF_BoxCoxTrans %>% 
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  summarise(MSE = mean(SquaredE)) %>% 
+  spread(key = Forecast_Horizon, value = MSE)
+
+
+DF_BoxCoxTrans %>% 
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  filter(Replication != 115) %>% 
+  summarise(MSE = mean(SquaredE)) %>% 
+  spread(key = Forecast_Horizon, value = MSE)

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Trash/TourismForecasting_BoxCoxTrans_BiasAdjust_1-25.R

@@ -1,0 +1,405 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Trash/TourismForecasting_BoxCoxTrans_BiasAdjust_101-125.R

@@ -1,0 +1,405 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
+                                                                  c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
[…]

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Trash/TourismForecasting_BoxCoxTrans_BiasAdjust_126-140.R

@@ -1,0 +1,405 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
+                                                                  c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
[…]

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Trash/TourismForecasting_BoxCoxTrans_BiasAdjust_26-50.R

@@ -1,0 +1,411 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Trash/TourismForecasting_BoxCoxTrans_BiasAdjust_76-100.R

@@ -1,0 +1,405 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
+                                                                  c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
[…]

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/LogTrans/Results/Analysis.R

@@ -14,8 +14,22 @@ write.csv(x=DF_LogTrans, file = "DF_LogTrans.csv")
 
 DF_LogTrans %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans
 
-DF_LogTrans %>% 
+# DF_LogTrans_1_50 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_1_50
+# DF_LogTrans_51_100 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_51_100
+# DF_LogTrans_101_140 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_101_140
+# 
+# DF_LogTrans_101_140 %>% filter(Replication != 130) %>% 
+#   group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+#   summarise(MSE = mean(SquaredE)) %>% 
+#   spread(key = Forecast_Horizon, value = MSE)
+
+
+DF_LogTrans %>% filter(Replication != 103) %>% 
   group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
   summarise(MSE = mean(SquaredE)) %>% 
-  spread(key = Forecast_Horizon, value = MSE)
+  filter(Forecast_Horizon == 1) %>% 
+  ungroup() %>% 
+  dplyr::select(-Forecast_Horizon) %>% 
+  spread(key = F.method, value = MSE)
+
 

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/LogTrans/TourismForecasting_LogTrans_BiasAdjust.R

@@ -126,11 +126,11 @@ for (j in 1:1) {#C=140
   
   for (i in 1:n) {
     
-    TS <- Train[,i] %>% as.ts()
+    TS <- Train[,i] %>% ts(frequency = 12)
     TS_adj <- TS+1 # adding 1 since some series has zero values which is problamatic when taking log transformation
     
-    fit_bias <- auto.arima(TS_adj, lambda = 0, allowdrift = F, biasadj = FALSE)
-    fit_unbias <- auto.arima(TS_adj, lambda = 0, allowdrift = F, biasadj = TRUE)
+    fit_bias <- auto.arima(TS_adj, lambda = 0, biasadj = FALSE)
+    fit_unbias <- auto.arima(TS_adj, lambda = 0, biasadj = TRUE)
     
     #--Biased and Biased adjusted_M1 forecasts--#
     

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/LogTrans/TourismForecasting_LogTrans_BiasAdjust_1-50.R

@@ -126,11 +126,11 @@ for (j in 1:50) {#C=140
   
   for (i in 1:n) {
     
-    TS <- Train[,i] %>% as.ts()
+    TS <- Train[,i] %>% ts(frequency = 12)
     TS_adj <- TS+1 # adding 1 since some series has zero values which is problamatic when taking log transformation
     
-    fit_bias <- auto.arima(TS_adj, lambda = 0, allowdrift = F, biasadj = FALSE)
-    fit_unbias <- auto.arima(TS_adj, lambda = 0, allowdrift = F, biasadj = TRUE)
+    fit_bias <- auto.arima(TS_adj, lambda = 0, biasadj = FALSE)
+    fit_unbias <- auto.arima(TS_adj, lambda = 0, biasadj = TRUE)
     
     #--Biased and Biased adjusted_M1 forecasts--#
     

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/LogTrans/TourismForecasting_LogTrans_BiasAdjust_101-140.R

@@ -124,13 +124,13 @@ for (j in 101:140) {#C=140
   
   Start_fit <- Sys.time()
   
-  for (i in 1:n) {
+  for (i in 87:n) {
     
-    TS <- Train[,i] %>% as.ts()
+    TS <- Train[,i] %>% ts(frequency = 12)
     TS_adj <- TS+1 # adding 1 since some series has zero values which is problamatic when taking log transformation
     
-    fit_bias <- auto.arima(TS_adj, lambda = 0, allowdrift = F, biasadj = FALSE)
-    fit_unbias <- auto.arima(TS_adj, lambda = 0, allowdrift = F, biasadj = TRUE)
+    fit_bias <- auto.arima(TS_adj, lambda = 0, biasadj = FALSE)
+    fit_unbias <- auto.arima(TS_adj, lambda = 0, biasadj = TRUE)
     
     #--Biased and Biased adjusted_M1 forecasts--#
     
@@ -401,4 +401,7 @@ DF %>%
   group_by(`F-method`, `R-method`, Forecast_Horizon) %>% 
   summarise(MSE = mean(SquaredE)) %>% 
   spread(key = Forecast_Horizon, value = MSE)
+
+#j = 103, i=86
+
 

### 2019-08-27 Application-R/Application-TourismData/Bias_correction/Original-scale/TourismForecasting_originalScale_51-100.R

@@ -1,0 +1,341 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+library(tsibble)
+library(fable)
+library(fabletools)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-27 Application-R/Application-TourismData/Trash/Final-results/Time-Plots/TimePlots.R

@@ -1,0 +1,230 @@
+library(tidyverse)
+library(gridExtra)
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, 
+                                  list(7, c(6,5,4,4,3,3,2), c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,3,4,2,3,1,1,1,2,2,3,4))))
+
+AllTS <- allts(Hierarchy) %>%
+  as_tibble()
+
+AllTS_new <- AllTS + 1 # Add 1 since some series has zero observations and this will affect taking log transformations
+
+#Total Series
+
+AllTS %>% log() %>% 
+  dplyr::select("Total") %>% 
+  ts(start = c(1998, 1), frequency = 12) %>% 
+  autoplot() + ylab("log(Overnight trips)") + xlab("Time") + 
+  theme(legend.position="bottom") -> TSPlot_total
+
+AllTS %>% log() %>% 
+  dplyr::select("Total") %>% 
+  ts(start = c(1998, 1), frequency = 12) %>% 
+  ggsubseriesplot() + ylab("log(Overnight trips)") + 
+  theme(legend.position="bottom") +
+  ggtitle("Subseries plot") -> subseries_total
+
+AllTS %>% log() %>% 
[…]

### 2019-08-27 Application-R/Application-TourismData/Trash/Results/TimePlots.R

@@ -1,7 +1,25 @@
 library(tidyverse)
 library(gridExtra)
 
-load("TourismData_LogTransBiasCorrection_UnivARIMA.RData")
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region, list(7, c(6,5,4,4,3,3,2), 
+                                                                  c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
+                                                                    3,4,2,3,1,1,1,2,2,3,4))))
+AllTS <- allts(Hierarchy) %>%
+  as_tibble()
+
+n<-ncol(AllTS)
+l1<-1
+l2<-sum(7)
+l3<-sum(6,5,4,4,3,3,2)
+m<-ncol(Bottom_level)
+
 
 #Total Series
 AllTS %>% 
@@ -21,7 +39,11 @@ AllTS %>%
   autoplot() + ylab("Overnight trips") + xlab("Time") + 
   ggtitle("States") + theme(legend.position="bottom") -> Plot_Sates
 
-#Zones
+#############
+  #Zones#
+#############
+
+#(l1+l2+1):(l1+l2+l3)
 
 # "AA", "AB", "AC", "AD", "AE", "AF", "BA", "BB", "BC", "BD", "BE",
 # "CA", "CB", "CC", "CD", "DA", "DB", "DC", "DD", "EA", "EB","EC", 
@@ -69,107 +91,107 @@ grid.arrange(arrangeGrob(Plot_Sates, Plot_Zones, Plot_regions ))
 
 ###############################
 
-# Series related to State - A
-AllTS %>% 
-  dplyr::select("A") %>% 
-  ts(start = c(1998, 1), frequency = 12) %>% 
-  autoplot() + ylab("Overnight trips") + xlab("Time") + 
-  ggtitle("State-A") + theme(legend.position="bottom") -> Plot_A
-
-AllTS %>% 
-  dplyr::select("AA", "AB", "AC", "AD", "AE", "AF") %>% 
-  ts(start = c(1998, 1), frequency = 12) %>%  
[…]

### 2019-08-27 Hierarchical-forecast-reconciliation/Figs/InsampDir_1.tex
Modifying some schematics

@@
-% Created by tikzDevice version 0.12 on 2019-08-21 20:48:44
+% Created by tikzDevice version 0.12.3 on 2019-08-27 15:52:22
 % !TEX encoding = UTF-8 Unicode
-\documentclass[10pt]{article}
-\usepackage{tikz}
-
-\usepackage[active,tightpage,psfixbb]{preview}
-
-\PreviewEnvironment{pgfpicture}
-
-\setlength\PreviewBorder{0pt}
-
-\usepackage{amsfonts}
-\usepackage{bm}
-\usepackage{amsfonts}
-\usepackage{bm}\begin{document}
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.66, 49.37) --
-	( 93.66,302.86);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.11, 70.49) --
+	(149.11,302.86);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.85, 91.62) --
-	(357.70, 91.62);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.02,157.63) --
+	(294.33,157.63);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 93.66, 91.62) -- (278.49,165.55);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (149.11,157.63) -- (250.77,208.46);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (267.32,151.35) --
-	(278.49,165.55) --
-	(260.61,168.13);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (240.81,193.38) --
+	(250.77,208.46) --
+	(232.73,209.54);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.50] at (284.49,159.81) {{$\huge \mathfrak{s}$}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.50] at (256.77,202.72) {{$\huge \mathfrak{s}$}};
 \definecolor{drawColor}{RGB}{255,165,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.27,151.06) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.84,198.49) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.39, -1.17) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.11, 93.84) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 86.69, 59.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.27,135.50) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 93.83,107.40) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.20,168.48) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.42, 96.65) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.37,161.09) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.13,164.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.41,207.88) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.44, 82.77) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.99,151.55) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.66, 88.27) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.84, 73.95) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.66,140.29) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.16,155.33) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.08, 73.94) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.96,191.09) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.44,  6.55) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.24,145.48) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.19,133.75) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.68, 99.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 70.78,  4.51) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.60,186.60) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 59.84, 11.44) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.52, 97.74) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.20, 24.24) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.51,102.51) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.60, 63.79) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.31,111.31) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 80.42, 64.76) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.83,138.50) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 86.97, 33.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.83,139.17) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 77.85, 31.13) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.43,117.57) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.13,155.42) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.41,116.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.16,138.95) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.27,201.49) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.73,141.62) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.38,190.17) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.03,186.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.45,192.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.01, 22.17) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.46,222.54) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.45, 93.52) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.75,109.88) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.08, 64.52) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.29,158.93) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.96,162.78) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.54,139.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 75.35, 45.41) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.58,206.56) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.14, 77.91) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.04,125.86) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 83.27, 71.11) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.12,148.20) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.23, 89.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.40,143.53) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.86, 87.73) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.82,156.07) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 68.03, 19.69) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.02,154.96) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.39, 34.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.01,108.18) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 79.24, 42.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.51,118.11) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.69,117.36) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.18,124.10) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.26,166.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.28,175.33) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 82.79, 55.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.39,209.13) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.67, 88.77) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.18, 92.12) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.96, 45.19) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.13,132.55) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.83,141.02) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.16,155.67) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.17,107.33) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.87,125.71) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.17, 97.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.50,191.59) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.57,126.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.94,168.43) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.07,128.98) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.89,161.69) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.25, 90.90) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.71,181.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.67,126.40) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.48,183.32) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.50, 56.62) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.93,157.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.20,178.48) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.51,181.54) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.84, 56.48) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.72,133.57) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 82.89, 59.12) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.90,217.35) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.79,107.40) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.66,133.47) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.73,117.55) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.19,135.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.14,107.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.43,168.48) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 83.09, 93.56) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.40,175.46) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.39,125.77) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.77,168.58) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.67,128.91) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.30,158.97) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.51, 68.66) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.11,181.11) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 93.51,115.90) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.96,183.27) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 81.98, 69.40) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.92,141.84) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.89, 59.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.02,174.33) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.62,101.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.68,142.36) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.73, 84.06) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.78,135.69) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.47, 64.65) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.54,164.40) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 83.27, 46.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.64,152.43) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.65, 57.33) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.05,139.09) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 82.57, 34.18) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.40,126.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 87.86, 82.30) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.75,134.06) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.20, 94.40) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.01,118.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.10, 73.07) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.92,151.22) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.75,128.40) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.50,159.54) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.57,114.97) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.10, 63.06) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.09, 52.23) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.30, 79.78) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.07,  3.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.85,144.88) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.20,164.48) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.76,182.92) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.47,111.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.11,173.69) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.43,184.00) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.34,130.55) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.01, 37.37) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.93, 96.73) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 85.49, 52.81) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.21,207.72) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 97.33,122.20) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.55,171.27) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.73, 21.28) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.33,221.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.42,164.91) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.20,120.33) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 70.87,  0.86) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.61,130.95) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.25,148.07) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.13,178.66) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.72, 84.06) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.90,109.27) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.68,174.93) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.88,208.02) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.76, 54.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.57, 95.23) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.27,108.93) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.53,196.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.79, 90.37) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.04,152.43) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 95.37, 95.83) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.12,214.90) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.47,103.72) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.31,132.25) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 60.51, -0.55) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.25,169.53) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 86.87, 97.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.08,156.77) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.37, 82.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.05,160.52) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.47,105.67) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.30,165.95) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.31, 63.15) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.87, 94.27) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.37,161.57) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.50,151.33) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.86,167.29) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.82,138.06) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 93.66, 91.62) -- (146.47,260.61);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (149.11,157.63) -- (178.15,273.81);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (150.42,242.98) --
-	(146.47,260.61) --
-	(133.18,248.37);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (183.12,256.44) --
+	(178.15,273.81) --
+	(165.59,260.82);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (146.47,266.61) {{${\bm R}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (178.15,279.81) {{${\bm R}$}};
 \end{scope}
 \end{tikzpicture}
-\caption{a caption}
-\end{document}

### 2019-08-27 Hierarchical-forecast-reconciliation/Figs/InsampDir_2.tex
Modifying some schematics

@@
-% Created by tikzDevice version 0.12 on 2019-08-21 20:48:46
+% Created by tikzDevice version 0.12.3 on 2019-08-27 15:52:28
 % !TEX encoding = UTF-8 Unicode
-\documentclass[10pt]{article}
-\usepackage{tikz}
-
-\usepackage[active,tightpage,psfixbb]{preview}
-
-\PreviewEnvironment{pgfpicture}
-
-\setlength\PreviewBorder{0pt}
-
-\usepackage{amsfonts}
-\usepackage{bm}
-\usepackage{amsfonts}
-\usepackage{bm}\begin{document}
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.66, 49.37) --
-	( 93.66,302.86);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.11, 70.49) --
+	(149.11,302.86);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.85, 91.62) --
-	(357.70, 91.62);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.02,157.63) --
+	(294.33,157.63);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 93.66, 91.62) -- (278.49,165.55);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (149.11,157.63) -- (250.77,208.46);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (267.32,151.35) --
-	(278.49,165.55) --
-	(260.61,168.13);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (240.81,193.38) --
+	(250.77,208.46) --
+	(232.73,209.54);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.50] at (284.49,159.81) {{$\huge \mathfrak{s}$}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.50] at (256.77,202.72) {{$\huge \mathfrak{s}$}};
 \definecolor{drawColor}{RGB}{190,190,190}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.96,163.73) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.27,207.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.08, 11.50) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.54,102.55) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.37, 72.11) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.70,144.22) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.51,120.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.63,177.20) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.10,109.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.80,169.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.81,177.38) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.84,216.59) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.12, 95.44) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.41,160.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.35,100.94) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.26, 82.66) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.34,152.96) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.59,164.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.76, 86.62) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.38,199.81) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.12, 19.22) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.66,154.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.87,146.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.11,107.86) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.46, 17.18) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.03,195.31) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.52, 24.12) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.95,106.46) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.89, 36.92) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.93,111.22) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.29, 76.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.73,120.02) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.10, 77.44) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.25,147.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.65, 46.02) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.25,147.88) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.54, 43.80) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.85,126.28) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.82,168.09) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.84,124.76) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.85,151.63) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.70,210.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.42,154.29) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.81,198.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.71,198.70) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.88,200.72) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.70, 34.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.89,231.25) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.14,106.19) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.18,118.60) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.76, 77.19) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.72,167.65) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.65,175.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.97,147.71) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.04, 58.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.00,215.27) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.82, 90.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.47,134.57) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.96, 83.79) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.55,156.92) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.92,102.02) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.82,152.25) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.54,100.41) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.25,164.78) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.71, 32.37) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.44,163.67) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.08, 46.81) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.44,116.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.92, 55.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.94,126.82) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.38,130.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.60,132.82) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.95,179.20) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.70,184.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.47,  9.01) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.82,217.84) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.48, 67.81) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.60,100.84) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.35,101.45) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.56,141.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.65, 57.86) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.59,164.39) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.51,153.69) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.30,134.42) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.85,120.00) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.93,200.31) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.86,110.20) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.36,177.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.25,139.52) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.32,170.41) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.76,141.66) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.14,190.56) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.94,103.57) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.91,192.03) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.35,139.07) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.36,165.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.19, 69.29) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.94,190.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.88,191.15) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.15,142.28) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.52, 69.16) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.33,226.06) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.58, 71.80) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.08,142.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.47,120.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.61,144.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.42,130.22) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.86,177.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.83,120.21) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.83,184.17) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.78,106.24) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.20,177.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.07,138.44) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.72,167.68) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.35,141.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.54,189.82) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.19, 81.33) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.39,191.98) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.19,128.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.35,150.56) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.66, 82.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.45,183.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.57, 72.38) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.11,151.07) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.31,114.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.21,144.40) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.41, 96.73) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.97,173.11) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.15, 77.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.07,161.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.96, 58.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.48,147.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.34, 70.01) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.82,135.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.26, 46.86) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.18,142.77) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.54, 94.98) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.44,126.86) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.88,107.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.34,159.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.78, 85.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.93,168.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.44,141.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.52, 71.78) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.25,127.65) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.73, 88.49) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.77, 64.90) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.28,153.59) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 97.75, 15.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.19,191.63) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.88,177.16) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.53,182.40) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.16,124.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.77,139.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.12,196.67) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.36,105.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.70, 50.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.63,216.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.17, 65.49) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.98,179.99) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.01,134.88) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (186.76,229.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.41, 33.95) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.63,129.05) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.11,177.59) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.04,139.66) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.55, 13.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.55,187.37) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.93,160.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.32,117.99) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.40, 96.73) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.30,216.73) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.36,187.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.00,103.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.44, 67.38) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.96,205.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.96,121.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.47,161.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.48,103.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.55,223.62) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.06,108.50) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.74,140.97) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.15,116.40) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.67,178.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.19, 12.13) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.51,165.48) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.56,110.02) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.48,169.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.05, 95.13) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.73,174.67) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.16,118.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.30,102.98) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.00, 75.82) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.80,170.28) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.92,160.04) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.28,176.01) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.25,146.77) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 93.66, 91.62) -- (146.47,260.61);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (149.11,157.63) -- (178.15,273.81);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (150.42,242.98) --
-	(146.47,260.61) --
-	(133.18,248.37);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (183.12,256.44) --
+	(178.15,273.81) --
+	(165.59,260.82);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (146.47,266.61) {{${\bm R}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (178.15,279.81) {{${\bm R}$}};
 \definecolor{drawColor}{RGB}{0,0,255}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.87,218.36) circle (  3.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.67,244.77) circle (  3.00);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (172.87,236.36) {{$\color{blue}{\hat{\bm{y}}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (201.39,262.77) {{$\small \color{blue}{\hat{\bm{y}}}$}};
 \definecolor{fillColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.34,104.29) circle (  3.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.53,166.34) circle (  3.00);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (125.34, 77.92) {\bfseries\itshape {$\color{black}{\bm{y}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (166.53,139.97) {\bfseries\itshape {$\color{black}{\bm{y}}$}};
 \end{scope}
 \end{tikzpicture}
-\caption{a caption}
-\end{document}

### 2019-08-27 Hierarchical-forecast-reconciliation/Figs/ObliqProj.tex
Modifying some schematics

@@
-% Created by tikzDevice version 0.12 on 2019-08-21 20:48:51
+% Created by tikzDevice version 0.12.3 on 2019-08-27 15:52:34
 % !TEX encoding = UTF-8 Unicode
-\documentclass[10pt]{article}
-\usepackage{tikz}
-
-\usepackage[active,tightpage,psfixbb]{preview}
-
-\PreviewEnvironment{pgfpicture}
-
-\setlength\PreviewBorder{0pt}
-
-\usepackage{amsfonts}
-\usepackage{bm}
-\usepackage{amsfonts}
-\usepackage{bm}\begin{document}
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 93.66, 49.37) --
-	( 93.66,302.86);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.11, 70.49) --
+	(149.11,302.86);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 40.85, 91.62) --
-	(357.70, 91.62);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.02,157.63) --
+	(294.33,157.63);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 93.66, 91.62) -- (278.49,165.55);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (149.11,157.63) -- (250.77,208.46);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (267.32,151.35) --
-	(278.49,165.55) --
-	(260.61,168.13);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (240.81,193.38) --
+	(250.77,208.46) --
+	(232.73,209.54);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.50] at (284.49,159.81) {{$\Huge \mathfrak{s}$}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.50] at (256.77,202.72) {{$\Huge \mathfrak{s}$}};
 \definecolor{drawColor}{RGB}{190,190,190}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.96,163.73) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.27,207.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.08, 11.50) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.54,102.55) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.37, 72.11) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.70,144.22) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.51,120.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.63,177.20) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.10,109.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.80,169.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.81,177.38) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.84,216.59) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.12, 95.44) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.41,160.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.35,100.94) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.26, 82.66) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.34,152.96) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.59,164.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.76, 86.62) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.38,199.81) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.12, 19.22) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.66,154.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.87,146.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.11,107.86) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.46, 17.18) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.03,195.31) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.52, 24.12) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.95,106.46) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.89, 36.92) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.93,111.22) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.29, 76.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.73,120.02) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.10, 77.44) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.25,147.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.65, 46.02) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.25,147.88) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.54, 43.80) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.85,126.28) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.82,168.09) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.84,124.76) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.85,151.63) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.70,210.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.42,154.29) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.81,198.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.71,198.70) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.88,200.72) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.70, 34.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.89,231.25) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.14,106.19) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.18,118.60) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.76, 77.19) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.72,167.65) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.65,175.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.97,147.71) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.04, 58.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.00,215.27) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.82, 90.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.47,134.57) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.96, 83.79) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.55,156.92) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.92,102.02) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.82,152.25) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.54,100.41) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.25,164.78) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.71, 32.37) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.44,163.67) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.08, 46.81) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.44,116.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.92, 55.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.94,126.82) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.38,130.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.60,132.82) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.95,179.20) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.70,184.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.47,  9.01) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.82,217.84) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.48, 67.81) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.60,100.84) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.35,101.45) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.56,141.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.65, 57.86) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.59,164.39) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.51,153.69) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.30,134.42) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.85,120.00) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.93,200.31) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.86,110.20) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.36,177.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.25,139.52) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.32,170.41) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.76,141.66) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.14,190.56) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.94,103.57) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.91,192.03) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.35,139.07) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.36,165.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.19, 69.29) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.94,190.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.88,191.15) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.15,142.28) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.52, 69.16) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.33,226.06) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.58, 71.80) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.08,142.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.47,120.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.61,144.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.42,130.22) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.86,177.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.83,120.21) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.83,184.17) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.78,106.24) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.20,177.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.07,138.44) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.72,167.68) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.35,141.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.54,189.82) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.19, 81.33) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.39,191.98) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.19,128.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.35,150.56) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.66, 82.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.45,183.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.57, 72.38) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.11,151.07) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.31,114.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.21,144.40) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.41, 96.73) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.97,173.11) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.15, 77.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.07,161.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.96, 58.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.48,147.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.34, 70.01) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.82,135.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.26, 46.86) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.18,142.77) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.54, 94.98) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.44,126.86) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.88,107.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.34,159.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.78, 85.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.93,168.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.44,141.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.52, 71.78) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.25,127.65) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.73, 88.49) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.77, 64.90) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.28,153.59) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 97.75, 15.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.19,191.63) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.88,177.16) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.53,182.40) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.16,124.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.77,139.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.12,196.67) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.36,105.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.70, 50.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.63,216.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.17, 65.49) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.98,179.99) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.01,134.88) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (186.76,229.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.41, 33.95) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.63,129.05) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.11,177.59) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.04,139.66) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.55, 13.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.55,187.37) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.93,160.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.32,117.99) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.40, 96.73) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.30,216.73) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.36,187.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.00,103.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.44, 67.38) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.96,205.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.96,121.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.47,161.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.48,103.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.55,223.62) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.06,108.50) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.74,140.97) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.15,116.40) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.67,178.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.19, 12.13) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.51,165.48) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.56,110.02) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.48,169.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.05, 95.13) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.73,174.67) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.16,118.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.30,102.98) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.00, 75.82) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.80,170.28) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.92,160.04) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.28,176.01) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.25,146.77) circle (  2.25);
 \definecolor{drawColor}{RGB}{255,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.85,100.50) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.31,163.73) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.55,103.98) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.10,166.13) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.88,105.31) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.93,167.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.43,102.33) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.83,164.99) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.48,107.15) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.46,168.31) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.66,100.02) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.66,163.41) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.37, 96.30) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.55,160.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.91,100.92) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.90,164.03) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.86,109.70) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.97,170.06) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.10,110.19) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.65,170.40) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.69, 96.83) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.27,161.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.82,112.48) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.80,171.97) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.84,100.89) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.86,164.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.67,105.22) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.81,166.98) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.07, 99.38) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.79,162.97) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.90,103.31) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.19,165.67) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.34,101.09) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.13,164.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.07,101.78) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.09,164.62) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.63,108.81) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.74,169.45) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.05,104.98) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.47,166.81) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.58,104.39) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.66,166.41) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.19,107.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.85,168.50) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.04,100.57) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.42,163.78) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.91, 98.12) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.05,162.10) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.48,103.95) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.06,166.11) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.27,106.66) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.80,167.97) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.51,100.76) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.68,163.91) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.04,106.97) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.22,168.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.61,102.00) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.38,164.77) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.96,108.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.38,169.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.25,102.25) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.73,164.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.76,108.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.26,169.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.31,103.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.87,165.51) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.65,102.02) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.40,164.78) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.17,103.02) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.79,165.47) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.83,104.09) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.25,166.20) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.74,106.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.05,168.10) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.55,107.98) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.60,168.88) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.71,107.64) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.13,168.64) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.86,104.10) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.27,166.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.11,100.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.46,163.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.25,115.86) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.43,174.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.34,100.69) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.58,163.87) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.55,111.98) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.10,171.63) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.72, 99.24) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.59,162.87) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.24,101.05) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.08,164.11) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.41,105.52) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.22,167.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.95,100.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.82,163.49) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.14,103.41) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.32,165.74) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.71,106.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.94,167.54) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.75,106.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.06,168.10) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.19, 99.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.85,163.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.69,103.63) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.63,165.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.33,109.09) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.13,169.64) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.99,107.75) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.29,168.72) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.78,106.07) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.97,167.56) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.78, 99.27) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.63,162.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.68,105.63) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.37,167.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.20,102.64) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.26,165.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.34,106.29) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.28,167.72) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.32,101.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.12,164.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.33,101.89) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.23,164.69) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.05,108.98) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.97,169.56) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.99,102.55) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.14,165.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.16,109.82) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.13,170.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.69,103.63) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.62,165.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.35,105.50) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.19,167.17) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.81,110.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.49,170.32) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.40,106.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.86,168.01) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.80,102.88) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.59,165.37) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.31,105.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.62,166.88) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.62,104.00) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.14,166.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.60, 91.99) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.62,157.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.54,102.37) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.90,165.02) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.11,105.00) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.51,166.83) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.53, 97.17) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.73,161.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.98,100.55) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.38,163.77) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.82,103.28) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.15,165.65) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.46,102.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.85,165.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.84,102.09) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.51,164.83) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.01,108.96) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.95,169.55) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.44,101.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.74,164.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.66,105.62) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.36,167.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.60,102.00) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.38,164.76) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.23,106.65) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.77,167.96) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.29,111.87) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.96,171.55) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.95,105.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.52,167.34) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.60,107.20) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.53,168.34) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.60,104.39) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.67,166.41) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.02,102.56) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.16,165.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.90, 96.91) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.39,161.27) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.51,109.56) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.78,169.96) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.64,103.61) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.60,165.87) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.92,104.52) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.85,166.50) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.99,105.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.99,167.07) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.70,101.24) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.33,164.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.83,100.49) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.30,163.73) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.11,105.80) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.60,167.38) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.50,105.55) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.27,167.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.90,106.92) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.14,168.15) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 93.66, 91.62) -- (146.47,260.61);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (149.11,157.63) -- (178.15,273.81);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (150.42,242.98) --
-	(146.47,260.61) --
-	(133.18,248.37);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (183.12,256.44) --
+	(178.15,273.81) --
+	(165.59,260.82);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (146.47,266.61) {{${\bm R}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (178.15,279.81) {{${\bm R}$}};
 \definecolor{drawColor}{RGB}{0,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.96,163.73) -- (115.85,100.50);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (171.27,207.21) -- (161.31,163.73);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.08, 11.50) -- (124.55,103.98);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.54,102.55) -- (166.10,166.13);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.37, 72.11) -- (127.88,105.31);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.70,144.22) -- (167.93,167.04);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (125.51,120.08) -- (120.43,102.33);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (166.63,177.20) -- (163.83,164.99);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.10,109.32) -- (132.48,107.15);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (170.80,169.80) -- (170.46,168.31);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.81,177.38) -- (114.66,100.02);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (172.84,216.59) -- (160.66,163.41);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.12, 95.44) -- (105.37, 96.30);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.41,160.26) -- (155.55,160.85);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 88.02,  0.00) -- (116.91,100.92);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.26, 82.66) -- (161.90,164.03);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.35,100.94) -- (138.86,109.70);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (172.59,164.04) -- (173.97,170.06);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (152.34,152.96) -- (140.10,110.19);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.38,199.81) -- (174.65,170.40);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.76, 86.62) -- (106.69, 96.83);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.66,154.19) -- (156.27,161.21);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (119.12, 19.22) -- (145.82,112.48);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.11,107.86) -- (177.80,171.97);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (129.87,146.43) -- (116.84,100.89);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.03,195.31) -- (161.86,164.00);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (102.46, 17.18) -- (127.67,105.22);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (153.95,106.46) -- (167.81,166.98);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 91.52, 24.12) -- (113.07, 99.38);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (147.93,111.22) -- (159.79,162.97);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.89, 36.92) -- (122.90,103.31);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.73,120.02) -- (165.19,165.67);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (110.29, 76.46) -- (117.34,101.09);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (158.25,147.21) -- (162.13,164.14);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (112.10, 77.44) -- (119.07,101.78);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (159.25,147.88) -- (163.09,164.62);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.65, 46.02) -- (136.63,108.81);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.85,126.28) -- (172.74,169.45);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.54, 43.80) -- (127.05,104.98);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (157.84,124.76) -- (167.47,166.81);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.82,168.09) -- (125.58,104.39);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (176.70,210.21) -- (166.66,166.41);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (145.85,151.63) -- (133.19,107.43);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (177.81,198.89) -- (170.85,168.50);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.42,154.29) -- (116.04,100.57);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.88,200.72) -- (161.42,163.78);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.71,198.70) -- (109.91, 98.12);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.89,231.25) -- (158.05,162.10);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.70, 34.85) -- (124.48,103.95);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.18,118.60) -- (166.06,166.11);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.14,106.19) -- (131.27,106.66);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.72,167.65) -- (169.80,167.97);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.76, 77.19) -- (116.51,100.76);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (157.97,147.71) -- (161.68,163.91);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.65,175.46) -- (132.04,106.97);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.00,215.27) -- (170.22,168.19);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (107.04, 58.08) -- (119.61,102.00);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (156.47,134.57) -- (163.38,164.77);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (130.82, 90.58) -- (135.96,108.54);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.55,156.92) -- (172.38,169.26);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.96, 83.79) -- (120.25,102.25);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.82,152.25) -- (163.73,164.94);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.92,102.02) -- (135.76,108.46);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (171.25,164.78) -- (172.26,169.21);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.54,100.41) -- (122.31,103.08);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (164.44,163.67) -- (164.87,165.51);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 99.71, 32.37) -- (119.65,102.02);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (152.44,116.89) -- (163.40,164.78);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.08, 46.81) -- (122.17,103.02);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.94,126.82) -- (164.79,165.47);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (110.92, 55.53) -- (124.83,104.09);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (158.60,132.82) -- (166.25,166.20);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.38,130.03) -- (131.74,106.85);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.70,184.04) -- (170.05,168.10);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.95,179.20) -- (134.55,107.98);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (182.82,217.84) -- (171.60,168.88);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.47,  9.01) -- (133.71,107.64);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.60,100.84) -- (171.13,168.64);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.48, 67.81) -- (124.86,104.10);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.56,141.26) -- (166.27,166.21);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.35,101.45) -- (116.11,100.60);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (161.59,164.39) -- (161.46,163.80);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.65, 57.86) -- (154.25,115.86);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.30,134.42) -- (182.43,174.29);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.51,153.69) -- (116.34,100.69);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.93,200.31) -- (161.58,163.87);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (146.85,120.00) -- (144.55,111.98);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (178.36,177.14) -- (177.10,171.63);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.86,110.20) -- (112.72, 99.24);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (161.32,170.41) -- (159.59,162.87);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.25,139.52) -- (117.24,101.05);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (168.14,190.56) -- (162.08,164.11);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.76,141.66) -- (128.41,105.52);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.91,192.03) -- (168.22,167.19);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.94,103.57) -- (114.95,100.14);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (161.36,165.85) -- (160.82,163.49);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.35,139.07) -- (123.14,103.41);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (170.94,190.26) -- (165.32,165.74);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (119.19, 69.29) -- (129.71,106.04);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.15,142.28) -- (168.94,167.54);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.88,191.15) -- (131.75,106.85);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (183.33,226.06) -- (170.06,168.10);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.52, 69.16) -- (113.19, 99.43);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.08,142.19) -- (159.85,163.00);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.58, 71.80) -- (123.69,103.63);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.61,144.00) -- (165.63,165.89);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (140.47,120.08) -- (137.33,109.09);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (174.86,177.19) -- (173.13,169.64);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (140.42,130.22) -- (133.99,107.75);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (174.83,184.17) -- (171.29,168.72);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.83,120.21) -- (129.78,106.07);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (171.20,177.29) -- (168.97,167.56);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.78,106.24) -- (112.78, 99.27);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.72,167.68) -- (159.63,162.89);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.07,138.44) -- (128.68,105.63);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.54,189.82) -- (168.37,167.26);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.35,141.58) -- (121.20,102.64);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (170.39,191.98) -- (164.26,165.21);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.19, 81.33) -- (130.34,106.29);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.35,150.56) -- (169.28,167.72);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (125.19,128.58) -- (117.32,101.08);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (166.45,183.04) -- (162.12,164.14);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.66, 82.08) -- (119.33,101.89);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.11,151.07) -- (163.23,164.69);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.57, 72.38) -- (137.05,108.98);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.21,144.40) -- (172.97,169.56);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (124.31,114.14) -- (120.99,102.55);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.97,173.11) -- (164.14,165.15);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (135.41, 96.73) -- (139.16,109.82);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (172.07,161.14) -- (174.13,170.14);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.15, 77.32) -- (123.69,103.63);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (161.48,147.80) -- (165.62,165.89);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.96, 58.71) -- (128.35,105.50);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.82,135.00) -- (168.19,167.17);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.34, 70.01) -- (139.81,110.08);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (168.18,142.77) -- (174.49,170.32);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.26, 46.86) -- (131.40,106.71);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.44,126.86) -- (169.86,168.01);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (119.54, 94.98) -- (121.80,102.88);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.34,159.94) -- (164.59,165.37);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (127.88,107.08) -- (127.31,105.08);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.93,168.26) -- (167.62,166.88);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 94.85,  0.00) -- (124.62,104.00);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (144.52, 71.78) -- (166.14,166.15);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 68.26,  0.00) -- ( 94.60, 91.99);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.73, 88.49) -- (149.62,157.89);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.78, 85.74) -- (120.54,102.37);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (161.28,153.59) -- (163.90,165.02);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.44,141.08) -- (127.11,105.00);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.19,191.63) -- (167.51,166.83);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.25,127.65) -- (107.53, 97.17);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (161.53,182.40) -- (156.73,161.44);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.77, 64.90) -- (115.98,100.55);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.77,139.26) -- (161.38,163.77);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 97.75, 15.71) -- (122.82,103.28);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.36,105.44) -- (165.15,165.65);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (141.88,177.16) -- (120.46,102.34);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (175.63,216.44) -- (163.85,165.00);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.16,124.14) -- (119.84,102.09);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (166.98,179.99) -- (163.51,164.83);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.12,196.67) -- (137.01,108.96);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (186.76,229.85) -- (172.95,169.55);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.70, 50.04) -- (118.44,101.53);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.63,129.05) -- (162.74,164.44);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.17, 65.49) -- (128.66,105.62);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.04,139.66) -- (168.36,167.26);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (129.01,134.88) -- (119.60,102.00);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (168.55,187.37) -- (163.38,164.76);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (110.41, 33.95) -- (131.23,106.65);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (158.32,117.99) -- (169.77,167.96);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.11,177.59) -- (144.29,111.87);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (187.30,216.73) -- (176.96,171.55);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (102.55, 13.53) -- (128.95,105.74);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.00,103.94) -- (168.52,167.34);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (147.93,160.74) -- (132.60,107.20);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (178.96,205.15) -- (170.53,168.34);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.40, 96.73) -- (125.60,104.39);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.47,161.15) -- (166.67,166.41);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (145.36,187.60) -- (121.02,102.56);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (177.55,223.62) -- (164.16,165.15);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.44, 67.38) -- (106.90, 96.91);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.74,140.97) -- (156.39,161.27);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (141.96,121.60) -- (138.51,109.56);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (175.67,178.24) -- (173.78,169.96);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.48,103.04) -- (123.64,103.61);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.51,165.48) -- (165.60,165.87);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (127.06,108.50) -- (125.92,104.52);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.48,169.24) -- (166.85,166.50);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (131.15,116.40) -- (127.99,105.35);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.73,174.67) -- (167.99,167.07);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 92.19, 12.13) -- (117.70,101.24);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (148.30,102.98) -- (162.33,164.24);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.56,110.02) -- (115.83,100.49);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.80,170.28) -- (161.30,163.73);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.05, 95.13) -- (129.11,105.80);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (166.92,160.04) -- (168.60,167.38);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.16,118.35) -- (128.50,105.55);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (170.28,176.01) -- (168.27,167.21);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.00, 75.82) -- (131.90,106.92);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.25,146.77) -- (170.14,168.15);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.34,104.29) circle (  3.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.53,166.34) circle (  3.00);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (125.34, 77.94) {{$\color{black}{\bm{y}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (166.53,140.00) {{$\color{black}{\bm{y}}$}};
 \end{scope}
 \end{tikzpicture}
-\caption{a caption}
-\end{document}

### 2019-08-27 Hierarchical-forecast-reconciliation/Figs/schematics_projections.R

@@ -4,12 +4,13 @@ library(latex2exp)
 library(tikzDevice)
 library(scatterplot3d)
 library(tidyverse)
-options(tikzLatexPackages=c(getOption("tikzLatexPackages"),"\\usepackage{amsfonts}","\\usepackage{bm}"),
+options(tikzDefaultEngine = 'pdftex', tikzLatexPackages=c(getOption("tikzLatexPackages"),"\\usepackage{amsfonts}","\\usepackage{bm}"),
         tikzFooter = "\\caption{a caption}")
 
 
 # Generating errors
 set.seed(1989)
+rmat<-matrix(c(1,4,-0.5,0.25),2,2,byrow = FALSE)
 e<-t(rmat%*%matrix(rnorm(200,0,0.3),2,100))
 e_sample <- e + matrix(rep(c(0.6,0.3), 100), nrow = 100, ncol = 2, byrow = T)
 
@@ -21,9 +22,9 @@ tikz('InsampDir_1.tex',height=5, width = 5, standAlone = TRUE)
 # dev.control(displaylist="enable")
 
 plot.new()
-plot.window(xlim = c(-0.25,4),ylim = c(-0.5,5), asp = 1)
-lines(c(0,0),c(-1,5))
-lines(c(-1,5),c(0,0))
+plot.window(xlim = c(-1,4),ylim = c(-3,5), asp = 1)
+lines(c(0,0),c(-3,5))
+lines(c(-2,5),c(0,0))
 #lines(c(-1,3.5),c(-0.5,1.75),lwd=2)
 arrows(0,0,3.5,1.75,lwd=3)
 text(3.5,1.75,"{$\\huge \\mathfrak{s}$}",pos=4, cex = 2.5)
@@ -40,6 +41,8 @@ text(1,4,"{${\\bm R}$}",pos=3, cex = 2.5)
 dev.off()
 tools::texi2dvi('InsampDir_1.tex',pdf=T)
 
+tools::texi2pdf('InsampDir_1.tex')
+
 
 ####################
 
@@ -49,9 +52,9 @@ tikz('InsampDir_2.tex',height=5, width = 5, standAlone = TRUE)
 # dev.control(displaylist="enable")
 
 plot.new()
[…]

### 2019-08-27 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Adding modified schematics and new box and whisker plots for projections

--- 2019-08-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
@@
 \usepackage{mathrsfs, float, booktabs,todonotes,amsthm, xcolor,sidenotes, caption, subcaption}
+\usepackage[export]{adjustbox}
 
@@
 
-%\pdfminorversion=4
+\pdfminorversion=4
 % NOTE: To produce blinded version, replace "0" with "1" below.
@@
 \addtolength{\textwidth}{1in}%
-\addtolength{\textheight}{1in}%
+\addtolength{\textheight}{-.3in}%
 \addtolength{\topmargin}{-.8in}%
@@
 		\small
-		\includegraphics[width = \textwidth]{Figs/BaseVsRecon_Emp_results.pdf}
-		\caption{Difference of MSE between Base forecasts and reconciled forecasts over the replications is presented.
+		\includegraphics[width = \textwidth]{Figs/OrthVsOblq_Proj_Emp_results.pdf}
+		\caption{MSE difference between base forecasts and reconciled forecasts over the replications is presented for forecast horizons $h = 1,...,6$.
 Positive values of the difference implies reconciliation improves the forecast accuracy than base forecasts.}\label{fig:BaseVSRecon_Fc}
@@
 
-	\begin{figure}
-		\centering
-		\begin{subfigure}[t]{0.45\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{Figs/InsampDir_1.pdf}
-%			\label{fig:InsampDir_1}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[t]{0.45\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{Figs/InsampDir_2.pdf}
-%			\label{fig:InsampDir_2}
-		\end{subfigure}
-
-		\vspace{1cm}
-
-		\begin{subfigure}[t]{0.45\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{Figs/OrthProj.pdf}
-%			\label{fig:OrthProj}
-		\end{subfigure}
-		\hfill
-		\begin{subfigure}[t]{0.5\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{Figs/ObliqProj.pdf}
-%			\label{fig:ObliqProj}
-		\end{subfigure}
-
-%		\begin{subfigure}[t]{\textwidth}
-%			\centering
-%			\includegraphics[width=\linewidth]{example-image-c.pdf}
-%			\caption{Price regulation} \label{fig:timing3}
+%	\begin{figure}
+%		\centering
+%		\begin{subfigure}[t]{0.45\textwidth}
+%			\centering
+%			\includegraphics[width=\linewidth]{Figs/InsampDir_1.pdf} 
+%%			\label{fig:InsampDir_1}
 %		\end{subfigure}
-		\caption{A schematic to represent orthogonal and oblique reconciliation.
+%		\hfill
+%		\begin{subfigure}[t]{0.45\textwidth}
+%			\centering
+%			\includegraphics[width=\linewidth]{Figs/InsampDir_2.pdf} 
+%%			\label{fig:InsampDir_2}
+%		\end{subfigure}
+%		
+%		\vspace{1cm}
+%		
+%		\begin{subfigure}[t]{0.45\textwidth}
+%			\centering
+%			\includegraphics[width=\linewidth]{Figs/OrthProj.pdf} 
+%%			\label{fig:OrthProj}
+%		\end{subfigure}
+%		\hfill
+%		\begin{subfigure}[t]{0.45\textwidth}
+%			\centering
+%			\includegraphics[width=\linewidth]{Figs/ObliqProj.pdf} 
+%%			\label{fig:ObliqProj}
+%		\end{subfigure}
+%		
+%%		\begin{subfigure}[t]{\textwidth}
+%%			\centering
+%%			\includegraphics[width=\linewidth]{example-image-c.pdf} 
+%%			\caption{Price regulation} \label{fig:timing3}
+%%		\end{subfigure}
+%		\caption{A schematic to represent orthogonal and oblique reconciliation.
 Points in orange colour in top left figure represent the insample errors.
@@
 The black dot ${\bm y}$ denotes the (unknown) target of the forecast.
-Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows an oblique projection.} \label{fig:OthogonalVSOblique_projection}
+Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection}
+%	\end{figure}
+
+	\begin{figure}
+
+	\begin{adjustbox}{minipage=\linewidth,scale=0.7}
+	\begin{subfigure}[t]{0.45\textwidth}
+%		\centering
+		\input{Figs/InsampDir_1} 
+		%			\label{fig:InsampDir_1}
+	\end{subfigure}
+	\hspace{1cm}
+	\begin{subfigure}[t]{0.45\textwidth}
+%		\centering
+		\input{Figs/InsampDir_2} 
+		%			\label{fig:InsampDir_2}
+	\end{subfigure}
+
+	\vfill
+%	\vspace{0.3cm}
+
+	\begin{subfigure}[t]{0.45\textwidth}
+%		\centering
+		\input{Figs/OrthProj} 
+		%			\label{fig:OrthProj}
+	\end{subfigure}
+	\hspace{1cm}
+	\begin{subfigure}[t]{0.45\textwidth}
+%		\centering
+		\input{Figs/ObliqProj} 
+		%			\label{fig:ObliqProj}
+	\end{subfigure}
+
+	%		\begin{subfigure}[t]{\textwidth}
+	%			\centering
+	%			\includegraphics[width=\linewidth]{example-image-c.pdf} 
+	%			\caption{Price regulation} \label{fig:timing3}
+	%		\end{subfigure}
+
+	\end{adjustbox}
+\caption{A schematic to represent orthogonal and oblique reconciliation.
+Orange colour points in top left figure represent the insample errors.
+$\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$.
+Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation.
+The black dot ${\bm y}$ denotes the (unknown) target of the forecast.
+Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection}
 \end{figure}
@@
 
-	\textcolor{red}{GA: I will rewrite/review this when we decide where we put all our results - I am referring to the projection results - currently I think it is best that everything goes here and we make a comment at the end of Section 3.3 guiding the reader to the results here.
-This will make the empirical application a bit broader not only about bias correction, i.e., both about showing how projections work and how bias correction works.} Using an empirical application to forecast Australian domestic tourism flow, we illustrate the usefulness of projection based reconciliation in practice.
+	Using an empirical application to forecast Australian domestic tourism flow, we illustrate the usefulness of projection based reconciliation in practice.
 Previous studies have pronounced that the reconciliation improves point forecast accuracy in domestic tourism flow in Australia (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}).
@@
 
-	We use ``overnight trips'' across Australia as a measure of domestic tourism flows.
-The data are provided by the National Visitor Survey (NVS) and are collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more.
-Tourism flows in Australia can be disaggregated into 7 states, 27 zones and 75 regions forming a natural geographical hierarchy that is of interest to tourism operators and policy makers.
-Hence, there are $110$ series across the hierarchy with $75$ bottom-level series.
-More information about the series and the geographical hierarchy is presented in Table \ref{table:A1} in the Appendix.
-The data span the period January 1998 to December 2017, which gives a total of $240$ observations per series.
-
-Figure \ref{fig:Total_TSplots} shows time, sub-series and seasonal plots of the total aggregate overnight trips.
-As is usual with tourism flows these show a strong seasonal pattern.
-Overnight trips peak in January corresponding to the summer vacation season in Australia.
-There are also some lower peaks observed in April, July and October corresponding to school holidays.
-On the other hand the month with the least overnight trips is February indicating that people travel least for the month following their summer vacation.
-The time plot shows a pronounced upward trend starting from around 2010 till the end of the sample, with the data being fairly flat from the beginning of the sample and a slight downward trend during 2004-2010.
-
-The top panel of Figure \ref{fig:States_Zones_Regs_TSplots} shows time plots for the seven states, hence the first-level of the hierarchy.
-The panels below show some selected series from the second-level zones and the bottom-level regions of the geographical hierarchy.
-The plots display the diversity of time series features, within but also between levels.
-For example, noticeable at the first-level is the asynchronous seasonal pattern of the Northern Territory to the other states.
-For the Northern Territory the high tourist season occurs during June-August with July being the peak, while the low season is during December-February.
-This reflects the tropical climate of the Northern Territory, with Australians mostly visiting the North during its dry winter-season rather than the wet summer season.
-Noticeable as we move to the lower levels is the variation in the signal-to-noise ratio, with the regional bottom-level series being noisier compared to the series from levels above.
-This of course highlights the importance of modelling series at all levels without any loss of valuable information.
-
-We should note here that we have observed an anomalous observation for `Adelaide Hills' for December-2002.
+	We use ``overnight trips" as a measure of domestic tourism flow in Australia.
+Total ``overnight trips" in Australia can be disaggregated into 7 states, 27 zones and 75 regions forming a geographical hierarchy with $110$ total number of series and $75$ bottom level series.
+More information about the series of this hierarchy is given in Table \ref{table:A1} in the appendix.
+Data were obtained from the National Visitor Survey (NVS) which were collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more.
+Data form a monthly series starting from January 1998 to December 2017 which gives a total of $240$ observations per series.
+
+	As we can see from the time plots in Figure \ref{fig:Total_TSplots}, the total overnight trips has a strong seasonal pattern.
+Most overnight trips seems to be happening in January which is associated with the summer season in southern hemisphere.
+On the other hand the least trips are happening in February perhaps due to the end of summer holidays.
+We could also observe a slight downward trend in total overnight trips from 2005 to 2010 and then started increasing since 2010.
+
+	Figure \ref{fig:States_Zones_Regs_TSplots} shows time plots for some selected series from states, zones and regions of the hierarchy.
+While observing the series in state level, we could see that Northern Territory(NT) has a different seasonal patterns compared to the other states.
+Highest overnight trips to NT happens during June - August where July being the peak.
+Lowest trips happens during December - February.
+This is perhaps Australians prefer to visit North of Australia during its dry season rather than in wet season.
+This pattern also reflect in zones and regions associated to NT as well as regions in north Queensland.
+All other states and their associated zones and regions show peak overnight trips in January.
+
+	Further we noticed that the signal-to-noise ratio decreases with the level of disaggregation of the hierarchy.
+We can see much noisier series in regional and zone levels whereas the noise is comparatively stabilised in the upper levels.
+We have also observed that the overnight trips to `Adelaide Hills' has an anomalous observation on December-2002.
 We replace this observation with the average overnight trips on December-2001 and December-2003 for the same destination.
-\textcolor{red}{Puwasala can you please describe here how this was anomalous.
-I'm wondering if this is a Bali bombing effect where we had a huge spike in Australian domestic tourism because of the Bali bombings in Oct with Australians travelling within Australia due to them being scared basically.}
-
-Starting from a training window of $100$ observations, i.e., Jan-$1998$ to Apr-$2006$ we generate $h=1$ to $h=6$ steps-ahead forecasts.
-Using a rolling window we repeat the exercise until the end of the sample.
-This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $135~6$-steps-ahead forecasts available for forecast evaluation.
+
+	Using this data we produce $h=1$ to $h=6$ month ahead forecasts based on a rolling window approach.
+First a training window of $100$ observations is considered from Jan-$1998$ to Apr-$2006$ and  forecasts produce for May-$2006$ to Oct-$2006$.
+Then we roll the training window one month at a time where the final forecast is produced for Dec-$2017$.
+This leads to $140 \quad 1$-step-ahead, $139 \quad 2$-step-ahead through $135 \quad 6$-step-ahead forecasts left for evaluation.
 
@@
 		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/Total_TSplots.pdf}
-		\caption{Total domestic overnight trips (in logs) for Australia from January 1998 to December 2017.
-The top-panel shows a time plot; the bottom-left panel a sub-series plot for each month; the bottom-right panel shows a seasonal plot coloured by year.} \label{fig:Total_TSplots}
+		\caption{Total overnight trips are presented in log scale.
+Top panel shows the time plot.
+Bottom left panel shows the sub-series plot for each month whereas bottom right panel shows the seasonal plot coloured by year  }\label{fig:Total_TSplots}
 	\end{figure}
@@
 		\small
-		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots1.pdf}
+		\includegraphics[width = \textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots.pdf}
 		\caption{Time plot of overnight trips for some selected series from different disaggregate levels of the hierarchy.
@@
 
-	\subsection{Transformations and bias adjustments}
-
-	We first transform each series in the hierarchy using two types of transformations. Namely, we perform a log-transformation and also a more general Box-Cox transformation
+	\subsection{Base forecasts and reconciliation:}
+
+	First we transform each series in the hierarchy to stabilise any variations in the data.
+We use two types of transformation, namely, log transformation and more general Box-Cox transformation.
+Equation (\ref{eq:BoxCox_transformation}) gives the mathematical formula for these transformations.
+A constant is added to each series to avoid the impact of zero observations when taking log transformations.
+We note here that the two transformations were applied separately to the series in the hierarchy and treated distinctly.
 
@@
 	\begin{cases} 
-	\log(y_t) & \text{for log transformation} \\
-	\frac{y_t^\lambda - 1}{\lambda}  & \text{for Box-Cox transformation, $\lambda \ne 0$}
+	\log(y_t) & \text{if log transformation, $\lambda = 0$} \\
+	\frac{y_t^\lambda - 1}{\lambda}  & \text{if Box-Cox transformation, $\lambda \ne 0$} 
 	\end{cases}
@@
 
-.
-Equation (\ref{eq:BoxCox_transformation}) gives the mathematical formula for these transformations.
-A constant (in particular $1$) is added to each series to avoid the impact of zero observations when taking log transformations, as some zeros exist in the bottom-level series.
-
-We note here that the two sets of transformations (log and the general Box-Cox) were applied separately to the series in the hierarchy and are treated distinctly.	The ``Guerrero" method \citep{guerrero1993time} implemented in \verb|BoxCox.lambda()| function in \verb|forecast| package in R software \citep{Rforecast} is uses to select $\lambda$ for the Box-Cox transformations.
-For the log transformations we simply set $\lambda = 0$.
-
+	The ``Guerrero" method \citep{guerrero1993time} implemented in \verb|BoxCox.lambda()| function in \verb|forecast| package in R software \citep{Rforecast} is use to select optimal $\lambda$ for Box-Cox transformation.
+For log transformation we simply choose $\lambda = 0$.
 Then  we fit univariate ARIMA models for the transformed series.
@@
 	\section{Appendix}
-	%\thisfloatpagestyle{empty}
+	\thisfloatpagestyle{empty}
 	\input{Appendix}

### 2019-08-27 Hierarchical-forecast-reconciliation/Figs/Orthproj.tex
Modifying some schematics

--- 2019-07-30 Hierarchical-forecast-reconciliation/Figs/Orthproj.tex
@@
-% Created by tikzDevice version 0.12 on 2019-07-25 19:34:36
+% Created by tikzDevice version 0.12.3 on 2019-08-27 15:52:31
 % !TEX encoding = UTF-8 Unicode
-\documentclass[10pt]{article}
-\usepackage{tikz}
-
-\usepackage[active,tightpage,psfixbb]{preview}
-
-\PreviewEnvironment{pgfpicture}
-
-\setlength\PreviewBorder{0pt}
-
-\usepackage{amsfonts}
-\usepackage{bm}\begin{document}
 
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 75.46, 49.37) --
-	( 75.46,302.86);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.11, 70.49) --
+	(149.11,302.86);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 12.94, 91.62) --
-	(361.35, 91.62);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.02,157.63) --
+	(294.33,157.63);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 75.46, 91.62) -- (294.26,165.55);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (149.11,157.63) -- (250.77,208.46);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (282.33,151.98) --
-	(294.26,165.55) --
-	(276.55,169.10);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (240.81,193.38) --
+	(250.77,208.46) --
+	(232.73,209.54);
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (300.26,163.26) {{\huge $\mathfrak{s}$}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  2.50] at (256.77,202.72) {{$\huge \mathfrak{s}$}};
 \definecolor{drawColor}{RGB}{190,190,190}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.73,104.11) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.27,207.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (102.96, 97.64) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.54,102.55) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.75,158.76) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.70,144.22) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.40,151.64) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.63,177.20) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.23,132.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.80,169.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 67.77, 37.36) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.84,216.59) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.74, 64.30) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.41,160.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.42, 57.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.26, 82.66) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.34,119.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.59,164.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.42,110.64) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.38,199.81) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.22,194.28) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.66,154.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.14,120.23) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.11,107.86) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.75, 94.39) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.03,195.31) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.46,159.17) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.95,106.46) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.12, 78.87) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.93,111.22) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.91,246.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.73,120.02) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.00, 75.49) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.25,147.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.54, 44.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.25,147.88) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.06, 63.01) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.85,126.28) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.94, 76.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.84,124.76) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.47,142.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.70,210.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.23,157.90) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.81,198.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.43,158.48) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.88,200.72) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.22,161.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.89,231.25) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.88, 98.42) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.18,118.60) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.00, 83.00) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.72,167.65) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (122.04, 85.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.97,147.71) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.87,141.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.00,215.27) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.00,105.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.47,134.57) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.17, 88.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.55,156.92) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.15, -1.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.82,152.25) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.13, 76.86) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.25,164.78) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.24,170.18) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.44,163.67) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.33, 55.24) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.44,116.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.14, 34.27) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.94,126.82) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.83, 70.96) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.60,132.82) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.18, 37.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.70,184.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.63, 69.09) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.82,217.84) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.36,141.37) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.60,100.84) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 74.54, 10.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.56,141.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.31,100.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.59,164.39) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.09, 96.39) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.30,134.42) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.67,148.26) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.93,200.31) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (120.98,130.52) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.36,177.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.55, 93.92) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.32,170.41) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.67,184.11) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.14,190.56) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.64,100.10) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.91,192.03) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.87,105.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.36,165.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.41,135.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.94,190.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (100.14, 59.33) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.15,142.28) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.14,108.82) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.33,226.06) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.78,130.30) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.08,142.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.46,191.20) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.61,144.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.08,131.10) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.86,177.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (124.73,129.59) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.83,184.17) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 77.69, 38.48) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.20,177.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.64,162.50) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.72,167.68) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.94,188.07) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.54,189.82) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.08,148.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.39,191.98) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.23,100.64) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.35,150.56) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.40,120.16) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.45,183.04) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.88,184.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.11,151.07) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (123.24,126.18) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.21,144.40) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 72.95, 53.81) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.97,173.11) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.34,121.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.07,161.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.85, 10.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.48,147.80) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.63, 98.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.82,135.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.24,125.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.18,142.77) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.52, 18.10) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.44,126.86) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.96,179.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.34,159.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.23,131.81) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.93,168.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.43,161.73) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.52, 71.78) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.78,270.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.73, 88.49) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.20,114.65) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.28,153.59) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (105.39, 82.71) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.19,191.63) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.64, 54.72) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.53,182.40) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.04, 80.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.77,139.26) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.26,104.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.36,105.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.76, 73.89) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.63,216.44) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (117.08,127.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.98,179.99) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.98,194.02) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (186.76,229.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.01, 89.21) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.63,129.05) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.86,135.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.04,139.66) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.03,149.79) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.55,187.37) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (118.65, 96.89) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.32,117.99) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.52,153.41) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.30,216.73) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.68,172.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.00,103.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.42,141.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.96,205.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.02,103.15) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.47,161.15) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.57,163.54) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.55,223.62) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.23,162.78) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.74,140.97) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.51,128.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.67,178.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.37,117.42) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.51,165.48) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.85,213.31) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.48,169.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 96.12, 87.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.73,174.67) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.18,169.12) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.30,102.98) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 83.18, 59.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.80,170.28) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.92,160.04) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.28,176.01) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.25,146.77) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,0}
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 75.46, 91.62) -- (137.97,260.61);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (149.11,157.63) -- (178.15,273.81);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (141.02,242.80) --
-	(137.97,260.61) --
-	(124.07,249.07);
+\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (183.12,256.44) --
+	(178.15,273.81) --
+	(165.59,260.82);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (137.97,266.61) {{\Large ${\bm R}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (178.15,279.81) {{${\bm R}$}};
 \definecolor{drawColor}{RGB}{255,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.47,100.41) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (186.67,176.41) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.03,100.26) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.02,147.59) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.83,123.51) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.62,160.38) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.34,117.93) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.95,168.55) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.78,114.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.33,168.74) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 37.19, 78.69) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (191.68,178.92) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.11, 96.23) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.20,160.68) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 67.02, 88.77) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (114.44,140.30) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.30,110.15) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.45,168.30) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.89,111.36) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (191.80,178.98) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (199.23,133.44) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.18,159.16) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.34,113.20) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.40,153.28) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (106.13,101.98) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.11,173.13) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.44,121.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.51,149.33) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 84.45, 94.66) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (129.61,147.88) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (241.05,147.57) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.56,152.36) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 92.75, 97.46) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.26,159.20) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 66.89, 88.72) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.32,159.74) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.00, 96.87) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.57,156.86) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.44, 96.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.95,154.55) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.51,118.33) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.21,179.18) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.91,121.84) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (188.57,177.36) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.21,118.23) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.96,174.55) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.63,126.14) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (198.38,182.27) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.02,102.28) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (138.35,152.25) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.79, 98.15) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.61,167.88) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.00,102.95) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.23,159.19) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.12,117.19) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (197.68,181.92) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.76,104.56) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.77,155.96) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (103.01,100.93) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.17,165.66) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 19.17, 72.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.33,161.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 91.26, 96.96) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.68,167.92) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.99,121.87) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.79,164.97) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 77.83, 92.42) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.48,150.81) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 48.46, 82.50) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.25,154.20) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 81.92, 93.80) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.78,156.47) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 55.41, 84.85) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (179.35,172.75) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 73.46, 90.95) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (200.16,183.16) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.82,112.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.59,148.87) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 26.44, 75.05) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.72,158.94) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.84,103.91) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.80,163.97) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (101.19,100.31) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.18,162.67) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.15,121.92) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.83,174.49) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.90,111.70) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.32,173.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 95.30, 98.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.99,165.07) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.98,125.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.50,171.83) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (107.02,102.28) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.71,174.43) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (108.52,102.79) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.20,164.18) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.64,112.29) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (179.62,172.89) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 76.09, 91.83) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.20,160.18) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (115.78,105.24) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (203.86,185.01) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.01,111.07) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.71,156.93) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (188.00,129.65) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.86,159.51) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.92,113.74) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.53,171.84) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.35,112.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.30,173.23) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 45.79, 81.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.65,170.40) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.36,119.63) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.42,164.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.13,128.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.53,173.84) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.60,115.32) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (179.87,173.01) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 99.01, 99.58) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.27,162.71) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.11,107.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.15,169.65) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.70,126.17) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.29,160.72) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.14,111.45) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.30,162.23) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 51.07, 83.38) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.79,167.47) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (116.23,105.40) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.88,167.52) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 26.29, 75.01) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.07,160.61) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 11.37, 69.96) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.43,157.79) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (  8.62, 69.03) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.42,162.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.81,106.60) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.86,156.01) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.55,108.88) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.42,163.79) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 43.99, 80.99) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.42,167.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (177.37,126.05) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.10,138.63) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.06,117.16) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (109.15,137.65) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.54,121.04) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.23,161.69) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (255.15,152.34) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.97,174.06) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.89,104.27) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.96,167.55) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 94.13, 97.93) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.09,156.62) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 78.56, 92.67) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.03,148.09) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 98.85, 99.52) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (193.85,180.00) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (110.83,103.57) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.35,169.25) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 90.00, 96.53) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.12,187.14) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.02,110.05) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.09,154.12) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (202.09,134.41) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.27,159.21) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (104.08,101.29) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.56,171.36) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.31,117.25) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.62,153.39) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.35,119.63) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (203.31,184.73) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.13,104.35) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.55,148.85) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.88,115.08) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.00,179.07) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.22,125.67) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.60,164.88) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.97,112.40) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (198.25,182.20) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.93,104.62) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.55,155.35) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.12,120.90) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.60,172.38) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.80,120.12) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.37,165.76) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.05,112.43) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.45,167.30) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (127.46,109.19) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.42,169.29) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (204.61,135.26) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.60,146.38) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 89.34, 96.31) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.12,165.64) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.71,126.51) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.33,165.24) circle (  2.25);
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] ( 62.36, 87.19) circle (  2.25);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.40,169.78) circle (  2.25);
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.67,161.91) circle (  2.25);
 \definecolor{drawColor}{RGB}{0,0,255}
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.73,104.11) -- (101.47,100.41);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (171.27,207.21) -- (186.67,176.41);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (102.96, 97.64) -- (101.03,100.26);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.54,102.55) -- (129.02,147.59);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.75,158.76) -- (169.83,123.51);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.70,144.22) -- (154.62,160.38);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.40,151.64) -- (153.34,117.93);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (166.63,177.20) -- (170.95,168.55);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.23,132.34) -- (141.78,114.03);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (170.80,169.80) -- (171.33,168.74);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 67.77, 37.36) -- ( 37.19, 78.69);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (172.84,216.59) -- (191.68,178.92);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (112.74, 64.30) -- ( 89.11, 96.23);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.41,160.26) -- (155.20,160.68);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 90.42, 57.14) -- ( 67.02, 88.77);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (143.26, 82.66) -- (114.44,140.30);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.34,119.54) -- (130.30,110.15);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (172.59,164.04) -- (170.45,168.30);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (134.42,110.64) -- (133.89,111.36);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.38,199.81) -- (191.80,178.98);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.22,194.28) -- (199.23,133.44);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.66,154.19) -- (152.18,159.16);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (134.14,120.23) -- (139.34,113.20);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.11,107.86) -- (140.40,153.28);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (111.75, 94.39) -- (106.13,101.98);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.03,195.31) -- (180.11,173.13);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (135.46,159.17) -- (163.44,121.35);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (153.95,106.46) -- (132.51,149.33);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 96.12, 78.87) -- ( 84.45, 94.66);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (147.93,111.22) -- (129.61,147.88);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.91,246.43) -- (241.05,147.57);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.73,120.02) -- (138.56,152.36);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.00, 75.49) -- ( 92.75, 97.46);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (158.25,147.21) -- (152.26,159.20);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 99.54, 44.60) -- ( 66.89, 88.72);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (159.25,147.88) -- (153.32,159.74);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.06, 63.01) -- ( 91.00, 96.87);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.85,126.28) -- (147.57,156.86);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (103.94, 76.74) -- ( 89.44, 96.34);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (157.84,124.76) -- (142.95,154.55);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.47,142.71) -- (154.51,118.33);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (176.70,210.21) -- (192.21,179.18);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (138.23,157.90) -- (164.91,121.84);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (177.81,198.89) -- (188.57,177.36);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (124.43,158.48) -- (154.21,118.23);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.88,200.72) -- (182.96,174.55);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.22,161.85) -- (177.63,126.14);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.89,231.25) -- (198.38,182.27);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (109.88, 98.42) -- (107.02,102.28);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.18,118.60) -- (138.35,152.25);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.00, 83.00) -- ( 94.79, 98.15);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.72,167.65) -- (169.61,167.88);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (122.04, 85.32) -- (109.00,102.95);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (157.97,147.71) -- (152.23,159.19);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.87,141.85) -- (151.12,117.19);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.00,215.27) -- (197.68,181.92);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.00,105.58) -- (113.76,104.56);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (156.47,134.57) -- (145.77,155.96);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (112.17, 88.54) -- (103.01,100.93);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.55,156.92) -- (165.17,165.66);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.89,  0.00) -- ( 19.17, 72.60);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.82,152.25) -- (156.33,161.24);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.13, 76.86) -- ( 91.26, 96.96);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (171.25,164.78) -- (169.68,167.92);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (129.24,170.18) -- (164.99,121.87);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (164.44,163.67) -- (163.79,164.97);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.33, 55.24) -- ( 77.83, 92.42);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (152.44,116.89) -- (135.48,150.81);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 84.14, 34.27) -- ( 48.46, 82.50);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.94,126.82) -- (142.25,154.20);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.83, 70.96) -- ( 81.92, 93.80);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (158.60,132.82) -- (146.78,156.47);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 90.18, 37.85) -- ( 55.41, 84.85);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.70,184.04) -- (179.35,172.75);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 89.63, 69.09) -- ( 73.46, 90.95);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (182.82,217.84) -- (200.16,183.16);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.36,141.37) -- (136.82,112.35);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.60,100.84) -- (131.59,148.87);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 74.54, 10.03) -- ( 26.44, 75.05);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.56,141.26) -- (151.72,158.94);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.31,100.58) -- (111.84,103.91);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (161.59,164.39) -- (161.80,163.97);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.09, 96.39) -- (101.19,100.31);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.30,134.42) -- (159.18,162.67);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (145.67,148.26) -- (165.15,121.92);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.93,200.31) -- (182.83,174.49);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (120.98,130.52) -- (134.90,111.70);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (178.36,177.14) -- (180.32,173.24);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 21.96,  0.00) -- (  0.00, 29.67);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (161.32,170.41) -- (163.99,165.07);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.55, 93.92) -- ( 95.30, 98.32);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (168.14,190.56) -- (177.50,171.83);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.67,184.11) -- (175.98,125.58);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.91,192.03) -- (182.71,174.43);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (108.64,100.10) -- (107.02,102.28);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (161.36,165.85) -- (162.20,164.18);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.87,105.03) -- (108.52,102.79);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (170.94,190.26) -- (179.62,172.89);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (119.41,135.58) -- (136.64,112.29);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.15,142.28) -- (154.20,160.18);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (100.14, 59.33) -- ( 76.09, 91.83);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (183.33,226.06) -- (203.86,185.01);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.14,108.82) -- (115.78,105.24);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.08,142.19) -- (147.71,156.93);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.78,130.30) -- (133.01,111.07);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.61,144.00) -- (152.86,159.51);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (142.46,191.20) -- (188.00,129.65);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (174.86,177.19) -- (177.53,171.84);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.08,131.10) -- (140.92,113.74);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (174.83,184.17) -- (180.30,173.23);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (124.73,129.59) -- (137.35,112.53);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (171.20,177.29) -- (174.65,170.40);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 77.69, 38.48) -- ( 45.79, 81.60);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.72,167.68) -- (162.42,164.29);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (126.64,162.50) -- (158.36,119.63);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.54,189.82) -- (181.53,173.84);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (139.94,188.07) -- (184.13,128.34);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (170.39,191.98) -- (179.87,173.01);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.08,148.46) -- (145.60,115.32);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.35,150.56) -- (159.27,162.71);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 98.23,100.64) -- ( 99.01, 99.58);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (166.45,183.04) -- (173.15,169.65);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (111.40,120.16) -- (121.11,107.04);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.11,151.07) -- (155.29,160.72);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (134.88,184.04) -- (177.70,126.17);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.21,144.40) -- (158.30,162.23);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (123.24,126.18) -- (134.14,111.45);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.97,173.11) -- (168.79,167.47);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 72.95, 53.81) -- ( 51.07, 83.38);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (172.07,161.14) -- (168.88,167.52);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (104.34,121.46) -- (116.23,105.40);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (161.48,147.80) -- (155.07,160.61);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 73.85, 10.74) -- ( 26.29, 75.01);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.82,135.00) -- (149.43,157.79);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 63.13,  0.00) -- ( 11.37, 69.96);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (168.18,142.77) -- (158.42,162.29);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 59.69,  0.00) -- (  8.62, 69.03);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.44,126.86) -- (145.86,156.01);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (125.63, 98.74) -- (119.81,106.60);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.34,159.94) -- (161.42,163.79);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.24,125.53) -- (126.55,108.88);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.93,168.26) -- (168.42,167.29);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 90.52, 18.10) -- ( 43.99, 80.99);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (144.52, 71.78) -- (111.10,138.63);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.96,179.32) -- (177.37,126.05);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (133.73, 88.49) -- (109.15,137.65);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (140.23,131.81) -- (151.06,117.16);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (161.28,153.59) -- (157.23,161.69);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (132.43,161.73) -- (162.54,121.04);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.19,191.63) -- (181.97,174.06);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.78,270.43) -- (255.15,152.34);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (161.53,182.40) -- (168.96,167.55);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.20,114.65) -- (112.89,104.27);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.77,139.26) -- (147.09,156.62);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (105.39, 82.71) -- ( 94.13, 97.93);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.36,105.44) -- (130.03,148.09);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.64, 54.72) -- ( 78.56, 92.67);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (175.63,216.44) -- (193.85,180.00);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.04, 80.34) -- ( 98.85, 99.52);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (166.98,179.99) -- (172.35,169.25);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (110.26,104.34) -- (110.83,103.57);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (186.76,229.85) -- (208.12,187.14);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (106.76, 73.89) -- ( 90.00, 96.53);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.63,129.05) -- (142.09,154.12);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (117.08,127.54) -- (130.02,110.05);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.04,139.66) -- (152.27,159.21);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (157.98,194.02) -- (202.09,134.41);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (168.55,187.37) -- (176.56,171.36);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (113.01, 89.21) -- (104.08,101.29);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (158.32,117.99) -- (140.62,153.39);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (137.86,135.43) -- (151.31,117.25);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (187.30,216.73) -- (203.31,184.73);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.03,149.79) -- (158.35,119.63);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.00,103.94) -- (131.55,148.85);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (118.65, 96.89) -- (113.13,104.35);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (178.96,205.15) -- (192.00,179.07);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (116.52,153.41) -- (144.88,115.08);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.47,161.15) -- (163.60,164.88);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (141.68,172.35) -- (176.22,125.67);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (177.55,223.62) -- (198.25,182.20);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.42,141.54) -- (136.97,112.40);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.74,140.97) -- (144.55,155.35);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (115.02,103.15) -- (113.93,104.62);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (175.67,178.24) -- (178.60,172.38);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (130.57,163.54) -- (162.12,120.90);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.51,165.48) -- (165.37,165.76);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (128.23,162.78) -- (159.80,120.12);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.48,169.24) -- (168.45,167.30);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (125.51,128.03) -- (137.05,112.43);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.73,174.67) -- (172.42,169.29);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (121.37,117.42) -- (127.46,109.19);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (148.30,102.98) -- (126.60,146.38);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (146.85,213.31) -- (204.61,135.26);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.80,170.28) -- (165.12,165.64);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 96.12, 87.14) -- ( 89.34, 96.31);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (166.92,160.04) -- (164.33,165.24);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (147.18,169.12) -- (178.71,126.51);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (170.28,176.01) -- (173.40,169.78);
 
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 83.18, 59.04) -- ( 62.36, 87.19);
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.25,146.77) -- (157.67,161.91);
 \definecolor{drawColor}{RGB}{0,0,0}
@@
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (112.97,104.29) circle (  3.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.53,166.34) circle (  3.00);
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (112.97, 86.55) {{\huge $\color{black}{\bm{y}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.50] at (166.53,140.00) {{$\color{black}{\bm{y}}$}};
 \end{scope}
 \end{tikzpicture}
-
-\end{document}

### 2019-08-27 Application-R/Application-TourismData/Final-results/TourismData-Final-results.Rmd

@@
 OvernightTrips_OriginalScale_Fc %>% 
-  mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2) %>% 
+  mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2, 
+         Fc_horizon = recode(Fc_horizon, "1" = "h=1", "2" = "h=2",
+                             "3" = "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6")) %>% 
   group_by(`R.method`, Fc_horizon, Replication) %>% 
@@
 
-DF_MSE <- DF_LogTrans %>%
-  mutate(SquaredE = (`Actual` - `Forecasts`)^2) %>%
-  filter(`Forecast_Horizon` == 1) %>%
-  dplyr::select(-`Forecast_Horizon`) %>%
-  group_by(`F.method`, `R.method`, Replication) %>%
-  summarise(MSE = mean(SquaredE))
-
-DF_MSE %>%
-  filter(`F.method`=="Unbiased_M1", `R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>%
+OvernightTrips_OriginalScale_MSE %>%
+  filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>%
   spread(key = `R.method`, value = MSE) %>%
@@
          "Base-WLS" = Base - WLS) %>%
-  dplyr::select(Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
+  dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
   rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>%
@@
   ggplot(aes(x = Method, y = MSE)) +
-  geom_boxplot() +
+  geom_boxplot() + facet_wrap(~ Fc_horizon) +
   ylab("MSE") + xlab("Reconciliation Method")

### 2019-08-27 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Small corrections

@@
 	 \begin{definition}[Hierarchical Time Series]\label{def:cohspace}
-	 	A hierarchical time series is an $n$-dimensional multivariate time series such that all observed values $\bm{y}_1,\ldots,\bm{y}_T$ and all future values $\bm{y}_{T+1},\bm{y}_{T+2},\ldots$  lie in the coherent subspace, i.e.
-$\bm{y}_t\in\mathfrak{s}\quad\forall t$.
+	 	A hierarchical time series is an $n$-dimensional multivariate time series such that all observed values $\bm{y}_1,\ldots,\bm{y}_T$ and all future values $\bm{y}_{T+1},\bm{y}_{T+2},\ldots$  lie in the coherent subspace, i.e., $\bm{y}_t\in\mathfrak{s}\quad\forall t$.
 	 \end{definition}
@@
 The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.
-As such the statement from \cite{WicEtAl2019} that {\em``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified; this is only true in with respect to a loss function that depends on ${\bm W}$.
+As such the statement from \cite{WicEtAl2019} that {\em``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified; this is only true with respect to a loss function that depends on ${\bm W}$.
 If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts.

### 2019-08-28 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Minor typo

@@
 
-	Figure \ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle with $\tilde{y}$ at the right-angled vertex.
+	Figure \ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle with $\tilde{\bm{y}}$ at the right-angled vertex.
 In this triangle the line between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.

### 2019-08-28 Hierarchical-forecast-reconciliation/Figs/InsampDir_1_George.tex
Fixed Graphs

% Created by tikzDevice version 0.12.3 on 2019-08-28 21:58:34
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}

\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,361.35);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (336.15,312.15);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.11, 70.49) --
	(149.11,302.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.02,157.63) --
	(294.33,157.63);

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (149.11,157.63) -- (282.71,193.94);

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (269.98,181.12) --
	(282.71,193.94) --
	(265.25,198.55);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (288.71,191.64) {{$\large \mathfrak{s}$}};

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (149.11,157.63) -- (218.82,297.05);

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (219.90,279.01) --
	(218.82,297.05) --
	(203.74,287.09);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (218.82,303.05) {{$\large \bm{R}$}};
\definecolor{drawColor}{RGB}{255,165,0}
\definecolor{fillColor}{RGB}{255,165,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.22,157.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.24,207.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.31,235.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (188.95,211.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.66,153.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.38,119.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.05,132.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.73,140.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (191.55,238.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.32,166.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.73,193.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.57,173.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (137.73,129.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.76,177.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.25,124.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.71,119.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.43,182.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.99,167.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.92,158.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.73,134.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.57,157.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (142.34,138.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (135.37,112.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.74,185.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.49,190.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.56,161.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.67,166.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.77,171.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.26,142.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.46,138.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.50,209.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.57,136.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.71,179.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.36,195.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.67,160.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.03,161.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.61,140.37) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.03,118.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (185.58,226.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.99,148.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.09,171.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.11,171.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.36,184.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.57,195.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.93,175.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.24,195.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.48,154.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (130.95,126.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.95,137.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (132.29,151.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.74,134.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.50,142.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.59,176.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.32,175.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.65,222.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.52,173.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (179.51,214.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.57,135.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (143.62,130.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (128.13,116.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.65,165.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.61,184.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.08,173.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.85,167.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.86,157.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.99,157.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.76,157.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.15,168.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.79,141.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.84,171.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.38,213.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.25,214.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.30,155.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.36,212.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.64,156.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (121.57,102.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.05,203.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.09,190.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.27,164.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.93,202.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (133.50,115.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.33,190.09) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (125.68,105.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.93,156.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.49,176.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.82,139.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.82,191.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.91,142.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.66,188.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (185.57,237.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (111.56, 74.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.05,190.39) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.93,115.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (131.90,133.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.63,191.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.23,228.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (113.14, 96.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (139.31,148.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (141.87,131.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.90,131.92) circle (  2.25);
\end{scope}
\end{tikzpicture}
\caption{a caption}
\end{document}

### 2019-08-28 Hierarchical-forecast-reconciliation/Figs/InsampDir_2_George.tex
Fixed Graphs

% Created by tikzDevice version 0.12.3 on 2019-08-28 21:58:40
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}

\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,361.35);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (336.15,312.15);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.11, 70.49) --
	(149.11,302.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.02,157.63) --
	(294.33,157.63);

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (149.11,157.63) -- (282.71,193.94);

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (269.98,181.12) --
	(282.71,193.94) --
	(265.25,198.55);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (288.71,191.64) {{$\large \mathfrak{s}$}};

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (149.11,157.63) -- (218.82,297.05);

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (219.90,279.01) --
	(218.82,297.05) --
	(203.74,287.09);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (218.82,303.05) {{$\large \bm{R}$}};
\definecolor{drawColor}{RGB}{190,190,190}
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.45,177.76) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (193.47,227.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (212.54,256.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (212.19,231.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.90,173.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.62,139.76) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.28,153.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.97,160.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (214.79,258.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.55,187.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.96,213.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.80,194.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.97,150.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.00,197.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.49,145.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.95,140.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.66,203.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.23,188.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.15,179.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.97,154.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.81,177.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.58,158.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.61,133.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.98,205.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.72,211.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.79,182.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (179.91,186.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.01,191.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.49,162.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.70,159.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (195.73,229.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.81,156.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.94,199.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (197.59,216.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.91,180.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.26,182.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.84,160.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.26,138.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.82,247.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.23,168.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.32,191.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.34,191.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.59,204.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.81,215.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.17,196.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.47,215.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.72,174.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.19,147.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.19,158.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.53,171.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.98,154.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.73,163.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.83,197.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.55,196.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.88,242.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.76,193.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (202.74,234.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.80,155.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.86,150.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.37,136.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.89,186.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.85,204.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.32,193.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.09,188.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.09,178.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.22,177.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.00,178.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.38,188.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.03,161.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.08,191.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.62,234.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.48,234.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.53,175.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.60,232.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.88,176.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.80,122.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (193.29,224.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (191.33,210.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.50,185.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.17,223.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.74,135.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.57,210.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.91,125.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.17,176.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.72,197.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.05,159.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.06,212.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.15,163.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.89,209.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.81,258.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.80, 94.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (196.29,210.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.17,136.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.14,153.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (188.87,212.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (210.47,249.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.38,116.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.55,169.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.11,152.24) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.13,152.25) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,255}
\definecolor{fillColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (211.55,233.15) circle (  3.00);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (211.55,239.15) {{$\color{blue}{\hat{\bm{y}}}$}};
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.73,161.12) circle (  3.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (160.73,149.38) {{$\color{black}{\bm{y}}$}};
\end{scope}
\end{tikzpicture}
\caption{a caption}
\end{document}

### 2019-08-28 Hierarchical-forecast-reconciliation/Figs/InsampDir_3_George.tex
Fixed Graphs

--- 2019-08-28 Hierarchical-forecast-reconciliation/Figs/InsampDir_2_George.tex
@@
-% Created by tikzDevice version 0.12.3 on 2019-08-28 21:58:40
+% Created by tikzDevice version 0.12.3 on 2019-08-28 21:58:46
 % !TEX encoding = UTF-8 Unicode
@@
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.13,152.25) circle (  2.25);
+\definecolor{drawColor}{RGB}{0,0,0}
+\definecolor{fillColor}{RGB}{0,0,0}
+
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.73,161.12) circle (  3.00);
+
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (160.73,149.38) {{$\color{black}{\bm{y}}$}};
 \definecolor{drawColor}{RGB}{0,0,255}
@@
 \node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (211.55,239.15) {{$\color{blue}{\hat{\bm{y}}}$}};
-\definecolor{fillColor}{RGB}{0,0,0}
+\definecolor{drawColor}{RGB}{255,0,0}
+\definecolor{fillColor}{RGB}{255,0,0}
 
-\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.73,161.12) circle (  3.00);
+\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.70,164.89) circle (  3.00);
+\definecolor{drawColor}{RGB}{0,0,0}
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (160.73,149.38) {{$\color{black}{\bm{y}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (176.70,150.25) {{$\color{red}{\tilde{\bm{y}}}$}};
+
+\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (153.46,116.97) --
+	(242.05,294.14);
+\definecolor{drawColor}{RGB}{0,0,255}
+
+\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (211.55,233.15) -- (176.70,164.89);
+
+\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (175.77,182.93) --
+	(176.70,164.89) --
+	(191.86,174.72);
 \end{scope}

### 2019-08-28 Hierarchical-forecast-reconciliation/Figs/ObliqProj_George.tex
Fixed Graphs

% Created by tikzDevice version 0.12.3 on 2019-08-28 21:58:54
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}

\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,361.35);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (336.15,312.15);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.11, 70.49) --
	(149.11,302.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.02,157.63) --
	(294.33,157.63);

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (149.11,157.63) -- (282.71,193.94);

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (269.98,181.12) --
	(282.71,193.94) --
	(265.25,198.55);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (288.71,191.64) {{$\large \mathfrak{s}$}};

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (149.11,157.63) -- (218.82,297.05);

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (219.90,279.01) --
	(218.82,297.05) --
	(203.74,287.09);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (218.82,303.05) {{$\large \bm{R}$}};
\definecolor{drawColor}{RGB}{190,190,190}
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.45,177.76) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (193.47,227.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (212.54,256.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (212.19,231.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.90,173.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.62,139.76) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.28,153.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.97,160.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (214.79,258.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.55,187.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.96,213.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.80,194.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.97,150.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.00,197.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.49,145.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.95,140.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.66,203.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.23,188.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.15,179.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.97,154.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.81,177.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.58,158.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.61,133.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.98,205.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.72,211.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.79,182.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (179.91,186.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.01,191.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.49,162.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.70,159.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (195.73,229.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.81,156.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.94,199.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (197.59,216.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.91,180.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.26,182.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.84,160.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.26,138.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.82,247.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.23,168.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.32,191.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.34,191.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.59,204.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.81,215.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.17,196.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.47,215.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.72,174.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.19,147.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.19,158.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.53,171.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.98,154.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.73,163.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.83,197.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.55,196.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.88,242.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.76,193.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (202.74,234.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.80,155.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.86,150.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.37,136.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.89,186.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.85,204.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.32,193.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.09,188.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.09,178.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.22,177.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.00,178.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.38,188.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.03,161.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.08,191.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.62,234.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.48,234.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.53,175.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.60,232.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.88,176.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.80,122.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (193.29,224.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (191.33,210.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.50,185.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.17,223.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.74,135.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.57,210.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.91,125.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.17,176.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.72,197.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.05,159.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.06,212.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.15,163.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.89,209.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.81,258.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.80, 94.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (196.29,210.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.17,136.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.14,153.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (188.87,212.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (210.47,249.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.38,116.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.55,169.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.11,152.24) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.13,152.25) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.57,159.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.66,161.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.06,162.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.91,166.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.83,162.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.76,161.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.91,163.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.67,160.23) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.27,163.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.34,161.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.48,162.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.93,163.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.73,162.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.96,161.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.45,161.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (179.17,165.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.60,161.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.37,163.41) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.02,164.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.72,162.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.95,160.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.52,162.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.47,164.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.65,158.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.26,163.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.18,159.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.64,162.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.38,160.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.19,161.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.11,161.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.11,161.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.12,159.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.12,162.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.81,164.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.90,166.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.61,164.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.80,162.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.31,162.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.80,162.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (179.91,166.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.70,161.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.56,164.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.94,161.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.43,162.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.39,162.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.36,163.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.82,162.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.66,160.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.25,162.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.81,157.55) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.86,158.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.67,165.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.63,161.03) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.69,162.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.28,161.48) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.61,159.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.46,162.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.05,162.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.19,164.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.13,161.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.61,164.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (147.15,157.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.06,159.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.27,163.38) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.05,161.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.84,161.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.82,161.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.89,162.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.04,159.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.60,163.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.45,164.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.27,162.57) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.54,161.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.45,160.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.59,161.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.13,161.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.40,161.51) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.46,162.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.45,161.80) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.36,160.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.77,163.25) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.86,162.73) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.22,162.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.91,161.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.02,161.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.19,162.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.32,160.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.37,161.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.58,160.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.69,161.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.10,162.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.27,164.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.19,163.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.05,160.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.98,161.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.48,163.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.78,159.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.22,160.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.43,163.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.42,161.25) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.45,177.76) -- (154.57,159.12);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (193.47,227.88) -- (161.66,161.04);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (212.54,256.22) -- (168.06,162.78);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (212.19,231.97) -- (180.91,166.27);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.90,173.64) -- (168.83,162.99);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.62,139.76) -- (161.76,161.07);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (164.28,153.29) -- (168.91,163.01);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (158.97,160.85) -- (158.67,160.23);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (214.79,258.72) -- (169.27,163.11);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (175.55,187.15) -- (163.34,161.50);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (190.96,213.78) -- (166.48,162.35);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (183.80,194.26) -- (168.93,163.02);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.97,150.32) -- (166.73,162.42);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.00,197.45) -- (163.96,161.67);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (156.49,145.07) -- (164.45,161.80);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (166.95,140.12) -- (179.17,165.80);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.66,203.16) -- (161.60,161.03);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (182.23,188.32) -- (170.37,163.41);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (180.15,179.11) -- (173.02,164.13);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.97,154.53) -- (166.72,162.42);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (168.81,177.36) -- (160.95,160.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.58,158.56) -- (167.52,162.63);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (158.61,133.04) -- (173.47,164.25);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (174.98,205.50) -- (152.65,158.59);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (194.72,211.11) -- (172.26,163.92);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.79,182.13) -- (157.18,159.82);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (179.91,186.62) -- (168.64,162.94);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (176.01,191.70) -- (161.38,160.96);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (164.49,162.36) -- (164.19,161.73);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.70,159.01) -- (165.11,161.98);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (195.73,229.96) -- (163.11,161.44);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.81,156.79) -- (156.12,159.53);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (183.94,199.70) -- (166.12,162.25);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (197.59,216.12) -- (172.81,164.07);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (187.91,180.99) -- (180.90,166.27);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.26,182.20) -- (172.61,164.02);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (166.84,160.70) -- (167.80,162.71);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.26,138.82) -- (165.31,162.03);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (208.82,247.05) -- (168.80,162.98);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.23,168.77) -- (179.91,166.00);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (176.32,191.78) -- (161.70,161.05);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (187.34,191.40) -- (174.56,164.55);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (182.59,204.49) -- (161.94,161.12);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (192.81,215.92) -- (167.43,162.61);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (184.17,196.00) -- (168.39,162.87);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (194.47,215.89) -- (169.36,163.13);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (171.72,174.56) -- (165.82,162.17);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.19,147.17) -- (160.66,160.77);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.19,158.22) -- (167.25,162.56);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.53,171.65) -- (148.81,157.55);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.98,154.98) -- (153.86,158.92);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (175.73,163.16) -- (176.67,165.12);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (178.83,197.15) -- (161.63,161.03);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (183.55,196.00) -- (167.69,162.68);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (201.88,242.58) -- (163.28,161.48);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.76,193.86) -- (157.61,159.94);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (202.74,234.90) -- (168.46,162.89);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.80,155.68) -- (167.05,162.51);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (166.86,150.88) -- (173.19,164.17);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.37,136.72) -- (163.13,161.44);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (184.89,186.16) -- (174.61,164.56);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.85,204.78) -- (147.15,157.10);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (172.32,193.68) -- (156.06,159.52);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (182.09,188.20) -- (170.27,163.38);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (170.09,178.05) -- (162.05,161.15);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (172.22,177.42) -- (164.84,161.90);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (170.00,178.27) -- (161.82,161.08);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (180.38,188.98) -- (167.89,162.73);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (157.03,161.59) -- (156.04,159.51);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (183.08,191.50) -- (169.60,163.20);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (207.62,234.19) -- (174.45,164.52);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (201.48,234.43) -- (167.27,162.57);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (168.53,175.71) -- (161.54,161.01);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (194.60,232.44) -- (160.45,160.71);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.88,176.60) -- (162.59,161.29);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (144.80,122.95) -- (163.13,161.44);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (193.29,224.31) -- (163.40,161.51);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (191.33,210.92) -- (168.46,162.89);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (175.50,185.01) -- (164.45,161.80);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (190.17,223.31) -- (160.36,160.69);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (156.74,135.87) -- (169.77,163.25);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (190.57,210.43) -- (167.86,162.73);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (148.91,125.92) -- (166.22,162.28);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.17,176.36) -- (161.91,161.11);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.72,197.04) -- (165.02,161.95);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.05,159.89) -- (166.19,162.27);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (183.06,212.10) -- (158.32,160.13);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (164.15,163.15) -- (163.37,161.50);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.89,209.17) -- (158.58,160.20);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (208.81,258.20) -- (162.69,161.32);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (134.80, 94.67) -- (167.10,162.52);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (196.29,210.72) -- (174.27,164.47);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (158.17,136.28) -- (171.19,163.63);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.14,153.94) -- (158.05,160.06);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (188.87,212.11) -- (164.98,161.94);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (210.47,249.26) -- (169.48,163.17);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.38,116.86) -- (156.78,159.71);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.55,169.19) -- (158.22,160.11);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.11,152.24) -- (170.43,163.43);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (158.13,152.25) -- (162.42,161.25);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.73,161.12) circle (  3.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (160.73,149.38) {{$\color{black}{\bm{y}}$}};
\end{scope}
\end{tikzpicture}
\caption{a caption}
\end{document}

### 2019-08-28 Hierarchical-forecast-reconciliation/Figs/OrthProj_George.tex
Fixed Graphs

% Created by tikzDevice version 0.12.3 on 2019-08-28 21:58:51
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

\usepackage[active,tightpage,psfixbb]{preview}

\PreviewEnvironment{pgfpicture}

\setlength\PreviewBorder{0pt}

\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage{amsfonts}
\usepackage{bm}\begin{document}

\begin{tikzpicture}[x=1pt,y=1pt]
\definecolor{fillColor}{RGB}{255,255,255}
\path[use as bounding box,fill=fillColor,fill opacity=0.00] (0,0) rectangle (361.35,361.35);
\begin{scope}
\path[clip] ( 49.20, 61.20) rectangle (336.15,312.15);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (149.11, 70.49) --
	(149.11,302.86);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 91.02,157.63) --
	(294.33,157.63);

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (149.11,157.63) -- (282.71,193.94);

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (269.98,181.12) --
	(282.71,193.94) --
	(265.25,198.55);

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (288.71,191.64) {{$\large \mathfrak{s}$}};

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (149.11,157.63) -- (218.82,297.05);

\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (219.90,279.01) --
	(218.82,297.05) --
	(203.74,287.09);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (218.82,303.05) {{$\large \bm{R}$}};
\definecolor{drawColor}{RGB}{190,190,190}
\definecolor{fillColor}{RGB}{190,190,190}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.45,177.76) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (193.47,227.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (212.54,256.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (212.19,231.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.90,173.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.62,139.76) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.28,153.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.97,160.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (214.79,258.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.55,187.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.96,213.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.80,194.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.97,150.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.00,197.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.49,145.07) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.95,140.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.66,203.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.23,188.32) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.15,179.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.97,154.53) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.81,177.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.58,158.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.61,133.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.98,205.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.72,211.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.79,182.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (179.91,186.62) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.01,191.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.49,162.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.70,159.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (195.73,229.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.81,156.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.94,199.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (197.59,216.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.91,180.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.26,182.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.84,160.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.26,138.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.82,247.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.23,168.77) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.32,191.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.34,191.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.59,204.49) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.81,215.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.17,196.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.47,215.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.72,174.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.19,147.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.19,158.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.53,171.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.98,154.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.73,163.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (178.83,197.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.55,196.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.88,242.58) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.76,193.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (202.74,234.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.80,155.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.86,150.88) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.37,136.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (184.89,186.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.85,204.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.32,193.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.09,188.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.09,178.05) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.22,177.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (170.00,178.27) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.38,188.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.03,161.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.08,191.50) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.62,234.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.48,234.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (168.53,175.71) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.60,232.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.88,176.60) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (144.80,122.95) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (193.29,224.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (191.33,210.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.50,185.01) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.17,223.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.74,135.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.57,210.43) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (148.91,125.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (169.17,176.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.72,197.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.05,159.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.06,212.10) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.15,163.15) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.89,209.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.81,258.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (134.80, 94.67) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (196.29,210.72) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.17,136.28) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (155.14,153.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (188.87,212.11) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (210.47,249.26) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.38,116.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.55,169.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (165.11,152.24) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.13,152.25) circle (  2.25);
\definecolor{drawColor}{RGB}{255,0,0}
\definecolor{fillColor}{RGB}{255,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (167.56,162.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (208.20,173.69) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (233.13,180.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (226.66,178.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (176.24,165.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (146.92,157.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.14,161.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (159.10,160.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (235.85,181.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.20,166.35) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (202.29,172.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.69,168.93) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.30,160.13) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (188.88,168.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.80,158.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.29,160.94) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.95,169.00) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.72,168.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.45,166.96) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (161.23,160.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.45,163.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.68,161.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.73,158.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (185.31,167.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (205.12,172.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.71,164.04) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (185.13,167.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (182.78,166.78) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.63,161.85) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.04,161.42) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (210.83,174.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (154.21,159.02) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.19,169.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (209.06,173.92) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (191.15,169.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (185.27,167.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (166.40,162.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (149.15,157.64) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (227.34,178.89) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.84,166.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (183.09,166.86) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (193.26,169.63) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.15,169.33) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (204.55,172.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (191.47,169.14) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (206.10,173.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (174.45,164.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.19,158.20) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.23,161.74) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (158.63,160.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (151.11,158.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.30,164.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (186.79,167.87) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (190.89,168.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (219.75,176.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (181.23,166.36) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (218.61,176.52) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.30,161.21) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (163.93,161.66) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (145.92,156.76) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.65,168.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.35,166.12) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (179.85,165.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (187.56,168.08) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.82,164.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (175.64,164.84) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.79,164.34) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (186.17,167.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (157.48,159.91) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.31,168.56) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (222.97,177.70) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (217.32,176.17) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (171.77,163.79) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (210.40,174.29) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (173.25,164.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (136.32,154.16) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (207.13,173.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.91,171.98) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (180.62,166.19) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (203.97,172.54) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (150.71,158.06) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (201.08,171.75) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (140.90,155.40) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (172.53,163.99) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (189.45,168.59) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.53,161.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (194.51,169.97) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.51,161.82) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (192.68,169.47) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (230.15,179.65) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (119.85,149.68) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (206.48,173.22) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (152.14,158.45) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (153.79,158.90) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (199.92,171.44) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (229.43,179.46) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (126.94,151.61) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (164.55,161.83) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (162.64,161.31) circle (  2.25);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (156.15,159.54) circle (  2.25);
\definecolor{drawColor}{RGB}{0,0,255}

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.45,177.76) -- (167.56,162.64);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (193.47,227.88) -- (208.20,173.69);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (212.54,256.22) -- (233.13,180.46);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (212.19,231.97) -- (226.66,178.70);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.90,173.64) -- (176.24,165.00);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.62,139.76) -- (146.92,157.04);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (164.28,153.29) -- (162.14,161.17);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (158.97,160.85) -- (159.10,160.35);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (214.79,258.72) -- (235.85,181.20);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (175.55,187.15) -- (181.20,166.35);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (190.96,213.78) -- (202.29,172.08);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (183.80,194.26) -- (190.69,168.93);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (160.97,150.32) -- (158.30,160.13);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.00,197.45) -- (188.88,168.44);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (156.49,145.07) -- (152.80,158.63);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (166.95,140.12) -- (161.29,160.94);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.66,203.16) -- (190.95,169.00);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (182.23,188.32) -- (187.72,168.12);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (180.15,179.11) -- (183.45,166.96);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.97,154.53) -- (161.23,160.92);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (168.81,177.36) -- (172.45,163.97);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.58,158.56) -- (164.68,161.86);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (158.61,133.04) -- (151.73,158.34);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (174.98,205.50) -- (185.31,167.47);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (194.72,211.11) -- (205.12,172.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (167.79,182.13) -- (172.71,164.04);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (179.91,186.62) -- (185.13,167.42);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (176.01,191.70) -- (182.78,166.78);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (164.49,162.36) -- (164.63,161.85);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.70,159.01) -- (163.04,161.42);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (195.73,229.96) -- (210.83,174.40);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.81,156.79) -- (154.21,159.02);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (183.94,199.70) -- (192.19,169.34);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (197.59,216.12) -- (209.06,173.92);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (187.91,180.99) -- (191.15,169.06);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.26,182.20) -- (185.27,167.46);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (166.84,160.70) -- (166.40,162.33);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.26,138.82) -- (149.15,157.64);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (208.82,247.05) -- (227.34,178.89);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.23,168.77) -- (181.84,166.52);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (176.32,191.78) -- (183.09,166.86);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (187.34,191.40) -- (193.26,169.63);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (182.59,204.49) -- (192.15,169.33);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (192.81,215.92) -- (204.55,172.70);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (184.17,196.00) -- (191.47,169.14);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (194.47,215.89) -- (206.10,173.12);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (171.72,174.56) -- (174.45,164.52);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (154.19,147.17) -- (151.19,158.20);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.19,158.22) -- (164.23,161.74);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.53,171.65) -- (158.63,160.22);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.98,154.98) -- (151.11,158.17);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (175.73,163.16) -- (175.30,164.75);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (178.83,197.15) -- (186.79,167.87);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (183.55,196.00) -- (190.89,168.98);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (201.88,242.58) -- (219.75,176.83);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (173.76,193.86) -- (181.23,166.36);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (202.74,234.90) -- (218.61,176.52);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (163.80,155.68) -- (162.30,161.21);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (166.86,150.88) -- (163.93,161.66);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (151.37,136.72) -- (145.92,156.76);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (184.89,186.16) -- (189.65,168.65);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.85,204.78) -- (180.35,166.12);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (172.32,193.68) -- (179.85,165.98);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (182.09,188.20) -- (187.56,168.08);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (170.09,178.05) -- (173.82,164.34);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (172.22,177.42) -- (175.64,164.84);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (170.00,178.27) -- (173.79,164.34);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (180.38,188.98) -- (186.17,167.70);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (157.03,161.59) -- (157.48,159.91);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (183.08,191.50) -- (189.31,168.56);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (207.62,234.19) -- (222.97,177.70);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (201.48,234.43) -- (217.32,176.17);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (168.53,175.71) -- (171.77,163.79);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (194.60,232.44) -- (210.40,174.29);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.88,176.60) -- (173.25,164.19);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (144.80,122.95) -- (136.32,154.16);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (193.29,224.31) -- (207.13,173.40);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (191.33,210.92) -- (201.91,171.98);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (175.50,185.01) -- (180.62,166.19);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (190.17,223.31) -- (203.97,172.54);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (156.74,135.87) -- (150.71,158.06);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (190.57,210.43) -- (201.08,171.75);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (148.91,125.92) -- (140.90,155.40);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (169.17,176.36) -- (172.53,163.99);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.72,197.04) -- (189.45,168.59);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.05,159.89) -- (164.53,161.82);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (183.06,212.10) -- (194.51,169.97);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (164.15,163.15) -- (164.51,161.82);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (181.89,209.17) -- (192.68,169.47);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (208.81,258.20) -- (230.15,179.65);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (134.80, 94.67) -- (119.85,149.68);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (196.29,210.72) -- (206.48,173.22);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (158.17,136.28) -- (152.14,158.45);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (155.14,153.94) -- (153.79,158.90);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (188.87,212.11) -- (199.92,171.44);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (210.47,249.26) -- (229.43,179.46);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (136.38,116.86) -- (126.94,151.61);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (162.55,169.19) -- (164.55,161.83);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (165.11,152.24) -- (162.64,161.31);

\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (158.13,152.25) -- (156.15,159.54);
\definecolor{drawColor}{RGB}{0,0,0}
\definecolor{fillColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (160.73,161.12) circle (  3.00);

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (160.73,149.38) {{$\color{black}{\bm{y}}$}};
\end{scope}
\end{tikzpicture}
\caption{a caption}
\end{document}

### 2019-08-29 Application-R/Application-TourismData/Final-results/TourismData-Final-results.Rmd
More things on analysis

@@
 
-# Box and whisker plots for orthogonal and oblique projections
+# Box and whisker plots for orthogonal and oblique projections from better models
 
@@
 
-# BoxCox Transformation
+# Box and whisker plots for orthogonal and oblique projections from misspecified models
 
 ```{r, echo=FALSE}
-DF_BoxCoxTrans <- read.csv("DF_BoxCoxTrans.csv")[,-1]
+OvernightTrips_OriginalScaleMisspecified_Fc <- read.csv("OvernightTrips_OriginalScaleMisspecified_Fc.csv")[,-1]
 
-DF_BoxCoxTrans %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans
+OvernightTrips_OriginalScaleMisspecified_Fc %>%
+  mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2,
+         Fc_horizon = recode(Fc_horizon, "1" = "h=1", "2" = "h=2",
+                             "3" = "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6")) %>%
+  group_by(`R.method`, Fc_horizon, Replication) %>%
+  summarise(MSE = mean(SquaredE)) -> OvernightTrips_OriginalScaleMisspecified_MSE
 
-DF_BoxCoxTrans %>%
-  group_by(`F.method`, `R.method`, Forecast_Horizon) %>%
-  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>%
-  filter(Forecast_Horizon == 1) %>%
-  ungroup() %>%
-  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_MSE_h1
-
-Avg_BoxCox_MSE_h1 %>%
-  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)",
-                           Unbiased_M2 = "Unbiased (Method 2)")) %>%
-  spread(key = F.method, value = MSE) %>%
-  kable(format = "latex")
+OvernightTrips_OriginalScaleMisspecified_MSE %>%
+  filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>%
+  spread(key = `R.method`, value = MSE) %>%
+  mutate("Base-OLS" = Base - OLS,
+         "Base-MinT" = Base - `MinT(Shrink)`,
+         "Base-WLS" = Base - WLS) %>%
+  dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
+  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>%
+  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>%
+  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>%
+  ggplot(aes(x = Method, y = MSE)) +
+  geom_boxplot() + facet_wrap(~ Fc_horizon) +
+  ylab("MSE") + xlab("Reconciliation Method")
 
 ```
-
-# More analysis on BoxCox transformed results
-
-```{r echo=FALSE}
-DF_BoxCoxTrans %>% 
-  group_by(`F.method`, `R.method`, Forecast_Horizon, Series) %>% 
-  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
-  filter(R.method == "Base", Forecast_Horizon == 1, 
-         F.method %in%c("Bias","Unbiased_M1")) %>% 
-  ungroup() %>% 
-  dplyr::select(-R.method, -Forecast_Horizon) %>% 
-  spread(key = F.method, value = MSE) %>% 
-  mutate("Bias-Unbiase" = Bias - Unbiased_M1) %>% 
-  filter(`Bias-Unbiase` < -100)
-
-```
-
-Bias correction is giving wiered results for `Total` series.
-
-```{r echo=FALSE}
-DF_BoxCoxTrans %>% 
-  filter(Forecast_Horizon == 1, Series == "Total") -> DF_BoxCoxTrans_Tot_h1
-
-# DF_BoxCoxTrans %>% 
-#   filter(Forecast_Horizon == 1, Series == "A") -> DF_BoxCoxTrans_A_h1
-# 
-# DF_BoxCoxTrans %>% 
-#   filter(Forecast_Horizon == 1, Series == "B") -> DF_BoxCoxTrans_B_h1
-
-# DF_BoxCoxTrans_h1 %>% 
-#   filter(Series == "Total", R.method == "Base", F.method == "Bias") %>% 
-#   dplyr::select(Actual, Replication) -> Total_BoxCox_True
-
-DF_BoxCoxTrans_Tot_h1 %>% 
-  filter(R.method == "Base", F.method %in%c("Bias","Unbiased_M1")) %>%
-  ungroup() %>% 
-  dplyr::select(F.method, Forecasts, Actual, Replication) %>% 
-  spread(key = F.method, value = Forecasts) %>% 
-  gather(-Replication, key = "Forecasts/Actual", value = Val) -> DF_BoxCoxTrans_Tot_h1
-
-DF_BoxCoxTrans_Tot_h1 %>% 
-  mutate(`Forecasts/Actual` = recode(`Forecasts/Actual`, "Unbiased_M1" = "Unbiased")) %>%   ggplot() + 
-  geom_line(aes(x = Replication, y = Val, color = `Forecasts/Actual`)) + 
-  ylab("Forecasts/Actual") + 
-  ggtitle("Forecasts for Total series follow from BoxCox Transformation") + 
-  theme(legend.position="bottom", legend.title = element_blank())
-
-#  DF_BoxCoxTrans_A_h1 %>% 
-#   filter(R.method == "Base", F.method %in%c("Bias","Unbiased_M1")) %>%
-#   ungroup() %>% 
-#   dplyr::select(F.method, Forecasts, Actual, Replication) %>% 
-#   spread(key = F.method, value = Forecasts) %>% 
-#   gather(-Replication, key = "Forecasts/Actual", value = Val) -> DF_BoxCoxTrans_A_h1
-#   
-# DF_BoxCoxTrans_A_h1 %>% 
-#   mutate(`Forecasts/Actual` = recode(`Forecasts/Actual`, "Unbiased_M1" = "Unbiased")) %>%   ggplot() + 
-#   geom_line(aes(x = Replication, y = Val, color = `Forecasts/Actual`)) + 
-#   ylab("Forecasts/Actual") + 
-#   ggtitle("Forecasts for NSW series follow from BoxCox Transformation") + 
-#   theme(legend.position="bottom", legend.title = element_blank()) 
-#  
-#  DF_BoxCoxTrans_B_h1 %>% 
-#   filter(R.method == "Base", F.method %in%c("Bias","Unbiased_M1")) %>%
-#   ungroup() %>% 
-#   dplyr::select(F.method, Forecasts, Actual, Replication) %>% 
-#   spread(key = F.method, value = Forecasts) %>% 
-#   gather(-Replication, key = "Forecasts/Actual", value = Val) -> DF_BoxCoxTrans_B_h1
-#   
-# DF_BoxCoxTrans_B_h1 %>% 
-#   mutate(`Forecasts/Actual` = recode(`Forecasts/Actual`, "Unbiased_M1" = "Unbiased")) %>%   ggplot() + 
-#   geom_line(aes(x = Replication, y = Val, color = `Forecasts/Actual`)) + 
-#   ylab("Forecasts/Actual") + 
-#   ggtitle("Forecasts for Victoria series follow from BoxCox Transformation") + 
-#   theme(legend.position="bottom", legend.title = element_blank())
-
-```
-
-```{r}
-
-DF_BoxCoxTrans_Tot_h1 %>% 
-  spread(key = `Forecasts/Actual`, value = Val) %>% 
-  mutate("Unb-Act" = Unbiased_M1 - Actual) %>% 
-  filter(`Unb-Act`>1000)
-
-```
-
-Very large bias corrected forecasts are given for some replications. For example in the rolling window Jul-2003 to Oct-2011. Observing the model auto.arima fits:
-
-```{r echo=FALSE}
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(`Adelaide Hills` > 80) %>% 
-  as.numeric() -> a
-
-which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(row_number() %in% c(60+12,60-12)) %>% 
-  summarise(mean(`Adelaide Hills`)) %>% 
-  as.numeric() -> b
-
-OvernightTrips_Region_new <- OvernightTrips_Region %>% 
-  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
-                                      TRUE ~ as.double(`Adelaide Hills`)))
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
-Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
-                                                                  c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
-                                                                    3,4,2,3,1,1,1,2,2,3,4))))
-AllTS_new <- allts(Hierarchy) %>%
-  as_tibble()
-
-L <- 100
-
-```
-
-```{r echo=FALSE}
-j = 67
-Train <- AllTS_new[j:(L+j-1),]
-TS <- Train[,"Total"] %>% ts(frequency = 12)
-fit <- auto.arima(TS, lambda = "auto", biasadj = FALSE, stepwise = FALSE, approximation = FALSE)
-Fc <- forecast(fit, h=1)
-
-Fc_trans <- Fc$mean
-L_PI <- Fc$lower[,"95%"]
-sig_h <- (Fc_trans - L_PI)/1.96
-sig2_h <- sig_h^2
-
-summary(fit)
-
-```
-
-The estimated drift term has a very large standard error. Further the variance of $\hat{y}_{t+1}$ is `r sig2_h` which is very large
 
@@
 ```{r, echo=FALSE}
-DF_LogTrans <- read.csv("DF_LogTrans.csv")[,-1]
+DF_LogTrans <- read.csv("OvernightTrips_LogTrans_Fc.csv")[,-1]
 
@@
 ```
+
+# BoxCox Transformation for $\lambda \in (0,1)$
+
+```{r, echo=FALSE}
+DF_BoxCoxTrans_set1 <- read.csv("OvernightTrips_BoxCoxTrans_set1_Fc.csv")[,-1]
+
+DF_BoxCoxTrans_set1 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_set1
+
+DF_BoxCoxTrans_set1 %>%
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>%
+  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>%
+  filter(Forecast_Horizon == 1) %>%
+  ungroup() %>%
+  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_set1_MSE_h1
+
+Avg_BoxCox_set1_MSE_h1 %>%
+  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)",
+                           Unbiased_M2 = "Unbiased (Method 2)")) %>%
+  spread(key = F.method, value = MSE) %>%
+  kable(format = "latex")
+
+```
+
+# BoxCox Transformation for $\lambda \in (-0.5,2)$
+
+```{r, echo=FALSE}
+DF_BoxCoxTrans_set2 <- read.csv("OvernightTrips_BoxCoxTrans_set2_Fc.csv")[,-1]
+
+DF_BoxCoxTrans_set2 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_set2
+
+DF_BoxCoxTrans_set2 %>%
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>%
+  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>%
+  filter(Forecast_Horizon == 1) %>%
+  ungroup() %>%
+  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_set2_MSE_h1
+
+Avg_BoxCox_set2_MSE_h1 %>%
+  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)",
+                           Unbiased_M2 = "Unbiased (Method 2)")) %>%
+  spread(key = F.method, value = MSE) %>%
+  kable(format = "latex")
+
+```

### 2019-08-29 Application-R/Application-TourismData/Trash/Results/TourismData-results.Rmd
More things on analysis

@@
 library(readr)
-library(BigVAR)
-library(vars)
 library(tibble)
@@
 ```{r echo=FALSE}
-load("TourismData_BoxCoxTransBiasCorrection_UnivARIMA_new.RData")
+load("TourismData_BoxCoxTransBiasCorrectionM1_UnivARIMA_AnomalyAdj.RData")
 
@@
 ```{r, echo=FALSE}
-load("TourismData_LogTransBiasCorrection_UnivARIMA.RData")
+load("TourismData_LogTransBiasCorrectionM1_UnivARIMA.RData")
 
@@
 ```
+
+```{r}
+
+DF_log_MSE <- DF_Log %>% 
+  mutate(SquaredE = (`Actual` - `Forecasts`)^2) %>% 
+  group_by(`F-method`, `R-method`, Replication, Forecast_Horizon) %>% 
+  summarise(MSE = mean(SquaredE)) %>% 
+  mutate(Forecast_Horizon = recode(Forecast_Horizon, "1" = "h=1", "2" = "h=2", "3"= "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6"))
+
+DF_log_MSE %>% 
+  filter(`F-method`=="ARIMA_unbias", `R-method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS"), Forecast_Horizon == "h=1") %>% 
+  spread(key = `R-method`, value = MSE) %>% 
+  mutate("Base-OLS" = Base - OLS,
+         "Base-MinT" = Base - `MinT(Shrink)`,
+         "Base-WLS" = Base - WLS) %>% 
+  dplyr::select(Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
+  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>% 
+  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>% 
+  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>% 
+  ggplot(aes(x = Method, y = MSE)) + 
+  geom_boxplot() + 
+  ylab("MSE") + xlab("Reconciliation Method")
+
+  ```

### 2019-08-29 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Set-1/Results/Analysis.R

@@ -1,0 +1,27 @@
+
+library(tidyverse)
+
+
+
+DF_BoxCoxTrans_1_50 <- read.csv("DF_BoxCoxTrans_set1_1-50.csv")[,-1]
+DF_BoxCoxTrans_51_100 <- read.csv("DF_BoxCoxTrans_set1_51-100.csv")[,-1]
+DF_BoxCoxTrans_101_140 <- read.csv("DF_BoxCoxTrans_set1_101-140.csv")[,-1]
+
+rbind(DF_BoxCoxTrans_1_50, DF_BoxCoxTrans_51_100, DF_BoxCoxTrans_101_140) %>% 
+  as.data.frame() -> DF_BoxCoxTrans
+write.csv(x=DF_BoxCoxTrans, file = "DF_BoxCoxTrans_set1.csv")
+
+
+DF_BoxCoxTrans %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans
+
+DF_BoxCoxTrans %>% 
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  summarise(MSE = mean(SquaredE)) %>% 
+  spread(key = Forecast_Horizon, value = MSE)
+
+
+DF_BoxCoxTrans %>% 
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  filter(Replication != 115) %>% 
+  summarise(MSE = mean(SquaredE)) %>% 
+  spread(key = Forecast_Horizon, value = MSE)

### 2019-08-29 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Set-2/Results-Odd/Analysis.R

@@ -1,0 +1,27 @@
+
+library(tidyverse)
+
+
+
+DF_BoxCoxTrans_1_50 <- read.csv("DF_BoxCoxTrans_set2_1-50.csv")[,-1] 
+DF_BoxCoxTrans_51_100 <- read.csv("DF_BoxCoxTrans_set2_51-100.csv")[,-1]
+DF_BoxCoxTrans_101_140 <- read.csv("DF_BoxCoxTrans_set2_101-140.csv")[,-1]
+
+rbind(DF_BoxCoxTrans_1_50, DF_BoxCoxTrans_51_100, DF_BoxCoxTrans_101_140) %>% 
+  as.data.frame() -> DF_BoxCoxTrans
+write.csv(x=DF_BoxCoxTrans, file = "DF_BoxCoxTrans_set2.csv")
+
+
+DF_BoxCoxTrans %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans
+
+DF_BoxCoxTrans %>% 
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  summarise(MSE = mean(SquaredE)) %>% 
+  spread(key = Forecast_Horizon, value = MSE)
+
+
+DF_BoxCoxTrans %>% 
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  filter(Replication != 115) %>% 
+  summarise(MSE = mean(SquaredE)) %>% 
+  spread(key = Forecast_Horizon, value = MSE)

### 2019-08-29 Application-R/Application-TourismData/Bias_correction/Original-scale/TourismForecasting_originalScale_1-50.R

@@ -1,341 +1,0 @@
-## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
-## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
-## Length of data expands from Jan-1998 to Dec-2017
-
-# Here we fit univariate ARIMA models for the log transformed data
-# The back transformed data will be biased and we bias adjust to get 
-# unbiased point forecasts.
-
-#We use two methods for bias correction
-# M1 - Bias correction via formulation
-# M2 - Bias correction via residual mean adjustment
-
-library(tidyverse)
-library(fpp2)
-library(Matrix)
-library(hts)
-library(readr)
-library(tibble)
-library(tsibble)
-library(fable)
-library(fabletools)
-
-# Import bottom level data
-#Importing data
-
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(`Adelaide Hills` > 80) %>% 
-  as.numeric() -> a
-
-which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(row_number() %in% c(60+12,60-12)) %>% 
-  summarise(mean(`Adelaide Hills`)) %>% 
-  as.numeric() -> b
-
-OvernightTrips_Region_new <- OvernightTrips_Region %>% 
-  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
-                                      TRUE ~ as.double(`Adelaide Hills`)))
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
-Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-29 Application-R/Application-TourismData/Bias_correction/Original-scale/TourismForecasting_originalScale_101-140.R

@@ -1,341 +1,0 @@
-## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
-## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
-## Length of data expands from Jan-1998 to Dec-2017
-
-# Here we fit univariate ARIMA models for the log transformed data
-# The back transformed data will be biased and we bias adjust to get 
-# unbiased point forecasts.
-
-#We use two methods for bias correction
-# M1 - Bias correction via formulation
-# M2 - Bias correction via residual mean adjustment
-
-library(tidyverse)
-library(fpp2)
-library(Matrix)
-library(hts)
-library(readr)
-library(tibble)
-library(tsibble)
-library(fable)
-library(fabletools)
-
-# Import bottom level data
-#Importing data
-
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(`Adelaide Hills` > 80) %>% 
-  as.numeric() -> a
-
-which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(row_number() %in% c(60+12,60-12)) %>% 
-  summarise(mean(`Adelaide Hills`)) %>% 
-  as.numeric() -> b
-
-OvernightTrips_Region_new <- OvernightTrips_Region %>% 
-  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
-                                      TRUE ~ as.double(`Adelaide Hills`)))
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
-Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-29 Application-R/Application-TourismData/OrthVsOblq_projections/Original-scale-MisspecifiedModels/TourismForecasting_originalScaleMisspecified_1-50.R

@@ -1,0 +1,341 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+library(tsibble)
+library(fable)
+library(fabletools)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-29 Application-R/Application-TourismData/OrthVsOblq_projections/Original-scale-MisspecifiedModels/TourismForecasting_originalScaleMisspecified_51-100.R

@@ -1,0 +1,341 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+library(tsibble)
+library(fable)
+library(fabletools)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-08-29 Application-R/Application-TourismData/OrthVsOblq_projections/Original-scale_betterModels/Results/Analysis.R

@@ -1,0 +1,24 @@
+
+library(tidyverse)
+
+
+
+OvernightTrips_OriginalScale_Fc_1_50 <- read.csv("DF_OriginalScale_1-50.csv")[,-1]
+OvernightTrips_OriginalScale_Fc_51_100 <- read.csv("DF_OriginalScale_51-100.csv")[,-1]
+OvernightTrips_OriginalScale_Fc_101_140 <- read.csv("DF_OriginalScale_101-140.csv")[,-1]
+
+rbind(OvernightTrips_OriginalScale_Fc_1_50, OvernightTrips_OriginalScale_Fc_51_100, 
+      OvernightTrips_OriginalScale_Fc_101_140) %>% 
+  as_tibble() -> OvernightTrips_OriginalScale_Fc
+write.csv(x=OvernightTrips_OriginalScale_Fc, file = "OvernightTrips_OriginalScale_Fc.csv")
+
+
+OvernightTrips_OriginalScale_Fc %>% 
+  mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2) -> OvernightTrips_OriginalScale_Fc
+
+OvernightTrips_OriginalScale_Fc %>% 
+  group_by(`R.method`, Fc_horizon) %>% 
+  summarise(MSE = mean(SquaredE)) %>% 
+  spread(key = Fc_horizon, value = MSE)
+
+

### 2019-08-29 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Fixed Graphs
Small corrections
Some coding and small changes to tex

@@
 	{
-		\title{\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.}
+		\title{\bf Forecast Reconciliation: A geometric view with new insights on bias correction.}
 		\author{Anastasios Panagiotelis\thanks{
@@
 
+\begin{figure}[!h]
+    \centering
+    \begin{subfigure}[!h]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{Figs/InsampDir_1_George.pdf}
+        \caption{\small}
+    \end{subfigure}
+    \begin{subfigure}[!h]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{Figs/InsampDir_2_George.pdf}
+        \caption{\small}
+    \end{subfigure}
+    \begin{subfigure}[!h]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{Figs/ObliqProj_George.pdf}
+        \caption{\small}
+    \end{subfigure}
+     \begin{subfigure}[!h]{0.49\textwidth}
+        \includegraphics[width=\textwidth]{Figs/OrthProj_George.pdf}
+        \caption{\small}
+    \end{subfigure}
+    \caption{A schematic to represent orthogonal and oblique reconciliation.
+Orange colour points in top left figure represent the insample errors.
+$\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$.
+Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation.
+The black dot ${\bm y}$ denotes the (unknown) target of the forecast.
+Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection_new}
+\end{figure}
+
 %		\begin{figure}[H]
@@
 	To establish the first statement let $\bm{s}_j$ be the $j^{th}$ column of $\bm{S}$.
-Since by definition, $\bm{s}_j$ lies in in $\mathfrak{s}$, it must hold that $\bm{S}\bm{G}\bm{s}_j=\bm{s}_j$.
+Since by definition, $\bm{s}_j$ lies in $\mathfrak{s}$, it must hold that $\bm{S}\bm{G}\bm{s}_j=\bm{s}_j$.
 Stacking these vectors horizontally

### 2019-08-29 Application-R/Application-TourismData/George/Seasonal200.R

@@ -1,0 +1,299 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods.
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions.
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the BoxCOx transformed data
+# The back transformed data will be biased and we bias adjust to get
+# unbiased point forecasts.
+
+# We noticed that there is an unusual observation in the Adelaide Hills series. So we
+# replace that odd value with the average of adjecent values
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>%
+  dplyr::select(`Adelaide Hills`) %>%
+  filter(`Adelaide Hills` > 80) %>%
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>%
+  dplyr::select(`Adelaide Hills`) %>%
+  filter(row_number() %in% c(60+12,60-12)) %>%
+  summarise(mean(`Adelaide Hills`)) %>%
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>%
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b,
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2),
[…]

### 2019-08-29 Hierarchical-forecast-reconciliation/Figs/InsampDir_1_George.tex
Fixed graphs further

@@
-% Created by tikzDevice version 0.12.3 on 2019-08-28 21:58:34
+% Created by tikzDevice version 0.12.3 on 2019-08-29 11:23:10
 % !TEX encoding = UTF-8 Unicode
@@
 
-\usepackage{amsfonts}
-\usepackage{bm}
-\usepackage{amsfonts}
-\usepackage{bm}
-\usepackage{amsfonts}
-\usepackage{bm}
-\usepackage{amsfonts}
-\usepackage{bm}
-\usepackage{amsfonts}
-\usepackage{bm}
-\usepackage{amsfonts}
-\usepackage{bm}
-\usepackage{amsfonts}
-\usepackage{bm}
 \usepackage{amsfonts}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (288.71,191.64) {{$\large \mathfrak{s}$}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (288.71,191.64) {{$\huge \mathfrak{s}$}};
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (218.82,303.05) {{$\large \bm{R}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (218.82,303.05) {{$\huge \bm{R}$}};
 \definecolor{drawColor}{RGB}{255,165,0}

### 2019-08-29 Hierarchical-forecast-reconciliation/Figs/InsampDir_2_George.tex
Fixed graphs further

@@
-% Created by tikzDevice version 0.12.3 on 2019-08-28 21:58:40
+% Created by tikzDevice version 0.12.3 on 2019-08-29 11:23:19
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (218.82,303.05) {{$\large \bm{R}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (218.82,303.05) {{$\huge \bm{R}$}};
 \definecolor{drawColor}{RGB}{190,190,190}

### 2019-08-29 Hierarchical-forecast-reconciliation/Figs/InsampDir_3_George.tex
Fixed graphs further

@@
-% Created by tikzDevice version 0.12.3 on 2019-08-28 21:58:46
+% Created by tikzDevice version 0.12.3 on 2019-08-29 11:23:28
 % !TEX encoding = UTF-8 Unicode

### 2019-08-29 Hierarchical-forecast-reconciliation/Figs/ObliqProj_George.tex
Fixed graphs further

@@
-% Created by tikzDevice version 0.12.3 on 2019-08-28 21:58:54
+% Created by tikzDevice version 0.12.3 on 2019-08-29 11:23:36
 % !TEX encoding = UTF-8 Unicode

### 2019-08-29 Hierarchical-forecast-reconciliation/Figs/OrthProj_George.tex
Fixed graphs further

@@
-% Created by tikzDevice version 0.12.3 on 2019-08-28 21:58:51
+% Created by tikzDevice version 0.12.3 on 2019-08-29 11:23:33
 % !TEX encoding = UTF-8 Unicode

### 2019-08-29 Hierarchical-forecast-reconciliation/Figs/schematics_projections_George.R

@@ -27,10 +27,10 @@ lines(c(0,0),c(-3,5))
 lines(c(-2,5),c(0,0))
 #lines(c(-1,3.5),c(-0.5,1.75),lwd=2)
 arrows(0,0,4.6,1.25,lwd=2)
-text(4.6,1.25,"{$\\large \\mathfrak{s}$}",pos=4, cex = 1)
+text(4.6,1.25,"{$\\huge \\mathfrak{s}$}",pos=4, cex = 1)
 
 arrows(0,0,2.4,4.8,lwd=2)
-text(2.4,4.8,"{$\\large \\bm{R}$}",pos=3, cex = 1)
+text(2.4,4.8,"{$\\huge \\bm{R}$}",pos=3, cex = 1)
 
 #rmat<-matrix(c(1,4,-0.5,0.25),2,2,byrow = FALSE)
 # e<-t(rmat%*%matrix(rnorm(200,0,0.3),2,100))
@@ -54,11 +54,11 @@ lines(c(0,0),c(-3,5))
 lines(c(-2,5),c(0,0))
 #lines(c(-1,3.5),c(-0.5,1.75),lwd=2)
 arrows(0,0,4.6,1.25,lwd=2)
-text(4.6,1.25,"{$\\large \\mathfrak{s}$}",pos=4, cex = 1)
+text(4.6,1.25,"{$\\huge \\mathfrak{s}$}",pos=4, cex = 1)
 
 
 arrows(0,0,2.4,4.8,lwd=2)
-text(2.4,4.8,"{$\\large \\bm{R}$}",pos=3, cex = 1)
+text(2.4,4.8,"{$\\huge \\bm{R}$}",pos=3, cex = 1)
 
 #rmat<-matrix(c(1,4,-0.5,0.25),2,2,byrow = FALSE)
 # e<-t(rmat%*%matrix(rnorm(200,0,0.3),2,100))
@@ -89,11 +89,11 @@ lines(c(0,0),c(-3,5))
 lines(c(-2,5),c(0,0))
 #lines(c(-1,3.5),c(-0.5,1.75),lwd=2)
 arrows(0,0,4.6,1.25,lwd=2)
-text(4.6,1.25,"{$\\large \\mathfrak{s}$}",pos=4, cex = 1)
+text(4.6,1.25,"{$\\huge \\mathfrak{s}$}",pos=4, cex = 1)
 
 
 arrows(0,0,2.4,4.8,lwd=2)
[…]

### 2019-08-31 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Graph

@@
     \centering
-    \begin{subfigure}[!h]{0.49\textwidth}
+    \begin{subfigure}[!h]{0.48\textwidth}
         \includegraphics[width=\textwidth]{Figs/InsampDir_1_George.pdf}
-        \caption{\small}
+        \caption{}
     \end{subfigure}
-    \begin{subfigure}[!h]{0.49\textwidth}
+    \begin{subfigure}[!h]{0.48\textwidth}
         \includegraphics[width=\textwidth]{Figs/InsampDir_2_George.pdf}
-        \caption{\small}
+        \caption{}
     \end{subfigure}
-    \begin{subfigure}[!h]{0.49\textwidth}
+    \begin{subfigure}[!h]{0.48\textwidth}
         \includegraphics[width=\textwidth]{Figs/ObliqProj_George.pdf}
-        \caption{\small}
+        \caption{}
     \end{subfigure}
-     \begin{subfigure}[!h]{0.49\textwidth}
+    \begin{subfigure}[!h]{0.48\textwidth}
         \includegraphics[width=\textwidth]{Figs/OrthProj_George.pdf}
-        \caption{\small}
+        \caption{}
     \end{subfigure}
     \caption{A schematic to represent orthogonal and oblique reconciliation.
-Orange colour points in top left figure represent the insample errors.
-$\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$.
+Orange colour points in top left figure represent the insample errors.$\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$.
 Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation.
 The black dot ${\bm y}$ denotes the (unknown) target of the forecast.
-Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection_new}
+Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.
+} \label{fig:OthogonalVSOblique_projection_new}
 \end{figure}

### 2019-08-31 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
changed summary at end of intro

@@
 In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose methods for bias correction.
-In Section \ref{sec:EmpStudy} we evaluate these methods for in an extensive emprirical application to domestic tourism flow in Australia.
+In Section \ref{sec:EmpStudy} we conduct an extensive empirical application to domestic tourism flow in Australia with two objectives; first to demonstrate the theorems discussed in~\ref{sec:Reconciliation}, second to evaluate the methods for bias correction discussed in~\ref{sec:BiasInRecon}.
 Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the  future of research in forecast reconciliation.
@@
 %		\centering
-		\input{Figs/OrthProj}
+		\input{Figs/Orthproj}
 		%			\label{fig:OrthProj}

### 2019-08-31 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
moved boxplot
added discussion of boxplots

@@
 
-	\subsection{Orthogonal projection}
+	\subsection{Orthogonal projection}\label{sec:orthogonal}
 
@@
 If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts.
-
-	{\bf Discuss results in Figure 4 here}
-
-	\begin{figure}[H]
-		\centering
-		\small
-		\includegraphics[width = \textwidth]{Figs/OrthVsOblq_Proj_Emp_results.pdf}
-		\caption{MSE difference between base forecasts and reconciled forecasts over the replications is presented for forecast horizons $h = 1,...,6$.
-Positive values of the difference implies reconciliation improves the forecast accuracy than base forecasts.}\label{fig:BaseVSRecon_Fc}
-	\end{figure}
+This will be demonstrated using a real data set in the empirical study in section~\ref{sec:comparebase}.
 
@@
 
-Starting from a training window of $100$ observations, i.e., Jan-$1998$ to Apr-$2006$ we generate $h=1$ to $h=6$ steps-ahead forecasts.
-Using a rolling window we repeat the exercise one observation at a time until the end of the sample.
-This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $135~6$-steps-ahead forecasts available for forecast evaluation.
-
 	\begin{figure}
@@
 \clearpage
+
+    \subsection{Comparison to Base Forecasts}\label{sec:comparebase}
+
+    To demonstrate the implications of Theorem~\ref{th:distred} we consider the improvement of different reconciliation methods over base forecasts.
+For each series the ARIMA model minimising AICc is chosen using the \verb|auto.arima()| function in the \verb|forecast| package.
+Using these fitted models, base forecasts are produced for $h=1$ to $6$-steps ahead for each series in the hierarchy.
+This is first carried out with a training sample of $100$ observations, i.e., Jan-$1998$ to Apr-$2006$.
+The training window is then rolled forward one observation at a time until the end of the sample.
+This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $135~6$-steps-ahead forecasts available for forecast evaluation.
+
+    After obtaining the base forecasts these are reconciled using three different methods; OLS reconciliation, WLS reconciliation using variance scaling\todo{George please check} and MinT use a shrinkage estimator for ${\bm W}$.
+Squared forecast errors are computed for each series and aggregated, i.e.
+we compute the loss function described in Section~\ref{sec:othogonal}.
+We then compute the difference in this loss function between base forecasts and reconciled forecasts, where positive values indicat that reconciled forecasts are more accurate.
+The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of this measure over each rolling window.
+As the theory predicts, OLS reconciliation always leads to an improvement relative to base forecasts, the entire boxplot for OLS reconciliation is above zero.
+This is not the case for WLS and MinT which for some windows perform worse than base forecasts.
+The boxplots also demonstrate that OLS reconciliation is more stable than WLS and MinT reconciliation, a result not entirely unsurprising since the latter two methods require estimation of a ${\bm W}$ matrix which in practice is not trivial.
+Nonetheless when averaging over the entire rolling window the MinT estimator performs best on average which is again precisely what the theorem proved in \cite{WicEtAl2019} would suggest.
+
+    \begin{figure}[H]
+    	\centering
+    	\small
+    	\includegraphics[width = \textwidth]{Figs/OrthVsOblq_Proj_Emp_results.pdf}
+    	\caption{MSE difference between base forecasts and reconciled forecasts over the replications is presented for forecast horizons $h = 1,...,6$.
+Positive values of the difference implies reconciliation improves the forecast accuracy than base forecasts.}\label{fig:BaseVSRecon_Fc}
+    \end{figure}
+
 	\subsection{Transformations and bias adjustment}

### 2019-08-31 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
changes to preamble of section 5

@@
 Previous studies have pronounced that the reconciliation improves point forecast accuracy in domestic tourism flow in Australia (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}).
-However, our motivation in this study is to demonstrate how the bias correction methods discussed in previous section along with the projection-based reconciliation help to improve the forecast accuracy.
+However, our motivation in this study is twofold.
+First, we demonstrate the implications of Theorem~\ref{th:distred} by comparing reconciled and base forecasts and in contrast to previous studies we consider individual periods rather than computing averages over a rolling window.
+The second, we demonstrate how the bias correction methods discussed in previous section along with the projection-based reconciliation help to improve the forecast accuracy.
 

### 2019-09-01 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
minor changes

@@
 %	\end{figure}
-
-	\begin{figure}
-
-	\begin{adjustbox}{minipage=\linewidth,scale=0.7}
-	\begin{subfigure}[t]{0.45\textwidth}
-%		\centering
-		\input{Figs/InsampDir_1}
-		%			\label{fig:InsampDir_1}
-	\end{subfigure}
-	\hspace{1cm}
-	\begin{subfigure}[t]{0.45\textwidth}
-%		\centering
-		\input{Figs/InsampDir_2}
-		%			\label{fig:InsampDir_2}
-	\end{subfigure}
-
-	\vfill
-%	\vspace{0.3cm}
-
-	\begin{subfigure}[t]{0.45\textwidth}
-%		\centering
-		\input{Figs/Orthproj}
-		%			\label{fig:OrthProj}
-	\end{subfigure}
-	\hspace{1cm}
-	\begin{subfigure}[t]{0.45\textwidth}
-%		\centering
-		\input{Figs/ObliqProj}
-		%			\label{fig:ObliqProj}
-	\end{subfigure}
-
-	%		\begin{subfigure}[t]{\textwidth}
-	%			\centering
-	%			\includegraphics[width=\linewidth]{example-image-c.pdf}
-	%			\caption{Price regulation} \label{fig:timing3}
+%
+%	\begin{figure}
+%	
+%	\begin{adjustbox}{minipage=\linewidth,scale=0.7}
+%	\begin{subfigure}[t]{0.45\textwidth}
+%%		\centering
+%		\input{Figs/InsampDir_1}
+%		%			\label{fig:InsampDir_1}
 %	\end{subfigure}
-
-	\end{adjustbox}
-\caption{A schematic to represent orthogonal and oblique reconciliation.
+%	\hspace{1cm}
+%	\begin{subfigure}[t]{0.45\textwidth}
+%%		\centering
+%		\input{Figs/InsampDir_2}
+%		%			\label{fig:InsampDir_2}
+%	\end{subfigure}
+%	
+%	\vfill
+%%	\vspace{0.3cm}
+%	
+%	\begin{subfigure}[t]{0.45\textwidth}
+%%		\centering
+%		\input{Figs/Orthproj}
+%		%			\label{fig:OrthProj}
+%	\end{subfigure}
+%	\hspace{1cm}
+%	\begin{subfigure}[t]{0.45\textwidth}
+%%		\centering
+%		\input{Figs/ObliqProj}
+%		%			\label{fig:ObliqProj}
+%	\end{subfigure}
+%	
+%	%		\begin{subfigure}[t]{\textwidth}
+%	%			\centering
+%	%			\includegraphics[width=\linewidth]{example-image-c.pdf}
+%	%			\caption{Price regulation} \label{fig:timing3}
+%	%		\end{subfigure}
+%	
+%	\end{adjustbox}
+%\caption{A schematic to represent orthogonal and oblique reconciliation.
 Orange colour points in top left figure represent the insample errors.
@@
 Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection}
-\end{figure}
-
-\begin{figure}[!h]
+%\end{figure}
+
+\begin{figure}[H]
     \centering
@@
 Our point forecast can be thought of as an estimate of this quantity.
-The forecast is random due to uncertainty in the training sample and it is with respect to this uncertainty that unbiasedness is referred to \todo{or do we want to define unbiasedness of a forecast as the expected value of the forecast equals realisation?
-George: are these not equivalent?
-Should be put both?
-Rob what do think?}.
+The forecast is random due to uncertainty in the training sample and it is with respect to this uncertainty that unbiasedness is referred to.
 More concretely, the point forecast will be unbiased if $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
@@
 In many cases the method for bias correction will be context specific.
-For instance, in  our empirical study in Section~\ref{sec:EmpStudy} we consider a scenario where bias is induced via taking a Box-Cox transformation before modelling.
-In this well-known case a number of bias correction methods exist.
-Our particular choice of bias correction will be the Guererro method \citep{guerrero1993time}.
-\textcolor{red}{TODO: Read this again after the empirical application has been completed.
+For instance, in  our empirical study in Section~\ref{sec:EmpStudy} we consider a scenario where bias is induced via taking either a log transformation or a Box-Cox transformation before modelling.
+In this well-known case a number of bias correction methods exist based on Taylor expansions.
+%\textcolor{red}{TODO: Read this again after the empirical application has been completed.
 I am saying this because my understanding is that we use the Guererro method to choose the lambda for the BoxCox transformation.
@@
 As stated in the discussion of MinT, in-sample errors are already used to estimate the optimal direction of projection.
-As such we see no problems with using the same errors to bias correct.
+As such it may be possible to use the same errors to bias correct.
 Geometrically, the intuition is simple.
-In top left panel in Figure \ref{fig:OthogonalVSOblique_projection}, the orange points are centered around the origin as would be expected from an unbiased forecast.
+In top left panel in Figure \ref{fig:OthogonalVSOblique_projection_new}, the orange points are centered around the origin as would be expected from an unbiased forecast.
 If forecasts are biased, then errors should simply be translated until they are centered at the origin.
+Nonetheless there are also a number of pitfalls to such an approach.
+First, for the very construction we consider, where bias is induced by taking a log or Box Cox transformation, bias should be corrected by a multiplicative rather than an additive factor.
+Second, if in-sample errors are non-stationary due to model misspecification structural breaks then the proposes method for bias correction may break down.
 
@@
 
-	\textcolor{red}{GA: I will rewrite/review this when we decide where we put all our results - I am referring to the projection results - currently I think it is best that everything goes here and we make a comment at the end of Section 3.3 guiding the reader to the results here.
-This will make the empirical application a bit broader not only about bias correction, i.e., both about showing how projections work and how bias correction works.} Using an empirical application to forecast Australian domestic tourism flow, we illustrate the usefulness of projection based reconciliation in practice.
+	%\textcolor{red}{GA: I will rewrite/review this when we decide where we put all our results - I am referring to the projection results - currently I think it is best that everything goes here and we make a comment at the end of Section 3.3 guiding the reader to the results here.
+This will make the empirical application a bit broader not only about bias correction, i.e., both about showing how projections work and how bias correction works.}
+	Using an empirical application to forecast Australian domestic tourism flow, we illustrate the usefulness of projection based reconciliation in practice.
 Previous studies have pronounced that the reconciliation improves point forecast accuracy in domestic tourism flow in Australia (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}).
@@
 First, we demonstrate the implications of Theorem~\ref{th:distred} by comparing reconciled and base forecasts and in contrast to previous studies we consider individual periods rather than computing averages over a rolling window.
-The second, we demonstrate how the bias correction methods discussed in previous section along with the projection-based reconciliation help to improve the forecast accuracy.
+Second, we demonstrate how the bias correction methods discussed in previous section along with the projection-based reconciliation help to improve the forecast accuracy.
 
@@
 
-    After obtaining the base forecasts these are reconciled using three different methods; OLS reconciliation, WLS reconciliation using variance scaling\todo{George please check} and MinT use a shrinkage estimator for ${\bm W}$.
+    After obtaining the base forecasts these are reconciled using three different methods; OLS reconciliation, WLS reconciliation using variance scaling \todo{George please check} and MinT use a shrinkage estimator for ${\bm W}$.
 Squared forecast errors are computed for each series and aggregated, i.e.
-we compute the loss function described in Section~\ref{sec:othogonal}.
+we compute the loss function described in Section~\ref{sec:orthogonal}.
 We then compute the difference in this loss function between base forecasts and reconciled forecasts, where positive values indicat that reconciled forecasts are more accurate.
@@
 The boxplots also demonstrate that OLS reconciliation is more stable than WLS and MinT reconciliation, a result not entirely unsurprising since the latter two methods require estimation of a ${\bm W}$ matrix which in practice is not trivial.
-Nonetheless when averaging over the entire rolling window the MinT estimator performs best on average which is again precisely what the theorem proved in \cite{WicEtAl2019} would suggest.
+Nonetheless when averaging over the entire rolling window the MinT estimator performs best on average which is again precisely what the theorem proved in \cite{WicEtAl2019} would suggest.\todo{Get correct results in for figure with boxplots}
 

### 2019-09-02 Application-R/Application-TourismData/Final-results/TourismData-Final-results.Rmd
More on bias correction

@@
 
-# Box and whisker plots for orthogonal and oblique projections from better models
+<!-- # Box and whisker plots for orthogonal and oblique projections from better models -->
+
+<!-- ```{r, echo=FALSE} -->
+<!-- OvernightTrips_OriginalScale_Fc <- read.csv("OvernightTrips_OriginalScale_Fc.csv")[,-1] -->
+
+<!-- OvernightTrips_OriginalScale_Fc %>% -->
+<!--   mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2, -->
+<!--          Fc_horizon = recode(Fc_horizon, "1" = "h=1", "2" = "h=2", -->
+<!--                              "3" = "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6")) %>% -->
+<!--   group_by(`R.method`, Fc_horizon, Replication) %>% -->
+<!--   summarise(MSE = mean(SquaredE)) -> OvernightTrips_OriginalScale_MSE -->
+
+<!-- OvernightTrips_OriginalScale_MSE %>% -->
+<!--   filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>% -->
+<!--   spread(key = `R.method`, value = MSE) %>% -->
+<!--   mutate("Base-OLS" = Base - OLS, -->
+<!--          "Base-MinT" = Base - `MinT(Shrink)`, -->
+<!--          "Base-WLS" = Base - WLS) %>% -->
+<!--   dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>% -->
+<!--   rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>% -->
+<!--   gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>% -->
+<!--   mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>% -->
+<!--   ggplot(aes(x = Method, y = MSE)) + -->
+<!--   geom_boxplot() + facet_wrap(~ Fc_horizon) + -->
+<!--   ylab("MSE") + xlab("Reconciliation Method") -->
+
+<!-- library(scales) -->
+
+<!-- asinh_trans <- function(){ -->
+<!--   trans_new(name = 'asinh', transform = function(x) asinh(x),  -->
+<!--             inverse = function(x) sinh(x)) -->
+<!-- } -->
+
+<!-- OvernightTrips_OriginalScale_MSE %>% -->
+<!--   filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>% -->
+<!--   spread(key = `R.method`, value = MSE) %>% -->
+<!--   mutate("Base-OLS" = Base - OLS, -->
+<!--          "Base-MinT" = Base - `MinT(Shrink)`, -->
+<!--          "Base-WLS" = Base - WLS) %>% -->
+<!--   dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>% -->
+<!--   rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>% -->
+<!--   gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>% -->
+<!--   mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>% -->
+<!--   ggplot(aes(x = Method, y = MSE)) + -->
+<!--   geom_boxplot() + scale_y_continuous(trans = 'asinh',breaks=c(-10000,-1000,-100,0,100,1000,10000))+ -->
+<!--   facet_wrap(~ Fc_horizon)+ -->
+<!--   theme_bw() -->
+
+<!-- ``` -->
+
+<!-- # Box and whisker plots for orthogonal and oblique projections from misspecified models -->
+
+<!-- ```{r, echo=FALSE} -->
+<!-- OvernightTrips_OriginalScaleMisspecified_Fc <- read.csv("OvernightTrips_OriginalScaleMisspecified_Fc.csv")[,-1] -->
+
+<!-- OvernightTrips_OriginalScaleMisspecified_Fc %>% -->
+<!--   mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2, -->
+<!--          Fc_horizon = recode(Fc_horizon, "1" = "h=1", "2" = "h=2", -->
+<!--                              "3" = "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6")) %>% -->
+<!--   group_by(`R.method`, Fc_horizon, Replication) %>% -->
+<!--   summarise(MSE = mean(SquaredE)) -> OvernightTrips_OriginalScaleMisspecified_MSE -->
+
+<!-- OvernightTrips_OriginalScaleMisspecified_MSE %>% -->
+<!--   filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>% -->
+<!--   spread(key = `R.method`, value = MSE) %>% -->
+<!--   mutate("Base-OLS" = Base - OLS, -->
+<!--          "Base-MinT" = Base - `MinT(Shrink)`, -->
+<!--          "Base-WLS" = Base - WLS) %>% -->
+<!--   dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>% -->
+<!--   rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>% -->
+<!--   gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>% -->
+<!--   mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>% -->
+<!--   ggplot(aes(x = Method, y = MSE)) + -->
+<!--   geom_boxplot() + facet_wrap(~ Fc_horizon) + -->
+<!--   ylab("MSE") + xlab("Reconciliation Method") -->
+
+<!-- ``` -->
+
+# Log Transformation with 100 observations of training window (Average MSE calculated over 140 replications)
 
 ```{r, echo=FALSE}
-OvernightTrips_OriginalScale_Fc <- read.csv("OvernightTrips_OriginalScale_Fc.csv")[,-1]
+DF_LogTrans_WL100 <- read.csv("DF_LogTrans_WL100.csv")[,-1]
 
-OvernightTrips_OriginalScale_Fc %>%
-  mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2,
-         Fc_horizon = recode(Fc_horizon, "1" = "h=1", "2" = "h=2",
-                             "3" = "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6")) %>%
-  group_by(`R.method`, Fc_horizon, Replication) %>%
-  summarise(MSE = mean(SquaredE)) -> OvernightTrips_OriginalScale_MSE
+DF_LogTrans_WL100 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_WL100
 
-OvernightTrips_OriginalScale_MSE %>%
-  filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>%
-  spread(key = `R.method`, value = MSE) %>%
-  mutate("Base-OLS" = Base - OLS,
-         "Base-MinT" = Base - `MinT(Shrink)`,
-         "Base-WLS" = Base - WLS) %>%
-  dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
-  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>%
-  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>%
-  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>%
-  ggplot(aes(x = Method, y = MSE)) +
-  geom_boxplot() + facet_wrap(~ Fc_horizon) +
-  ylab("MSE") + xlab("Reconciliation Method")
-
-```
-
-# Box and whisker plots for orthogonal and oblique projections from misspecified models
-
-```{r, echo=FALSE}
-OvernightTrips_OriginalScaleMisspecified_Fc <- read.csv("OvernightTrips_OriginalScaleMisspecified_Fc.csv")[,-1]
-
-OvernightTrips_OriginalScaleMisspecified_Fc %>%
-  mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2,
-         Fc_horizon = recode(Fc_horizon, "1" = "h=1", "2" = "h=2",
-                             "3" = "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6")) %>%
-  group_by(`R.method`, Fc_horizon, Replication) %>%
-  summarise(MSE = mean(SquaredE)) -> OvernightTrips_OriginalScaleMisspecified_MSE
-
-OvernightTrips_OriginalScaleMisspecified_MSE %>%
-  filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>%
-  spread(key = `R.method`, value = MSE) %>%
-  mutate("Base-OLS" = Base - OLS,
-         "Base-MinT" = Base - `MinT(Shrink)`,
-         "Base-WLS" = Base - WLS) %>%
-  dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
-  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>%
-  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>%
-  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>%
-  ggplot(aes(x = Method, y = MSE)) +
-  geom_boxplot() + facet_wrap(~ Fc_horizon) +
-  ylab("MSE") + xlab("Reconciliation Method")
-
-```
-
-# Log Transformation
-
-```{r, echo=FALSE}
-DF_LogTrans <- read.csv("OvernightTrips_LogTrans_Fc.csv")[,-1]
-
-DF_LogTrans %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans
-
-DF_LogTrans %>% 
+DF_LogTrans_WL100 %>% 
   group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
@@
   ungroup() %>% 
-  dplyr::select(-Forecast_Horizon)-> Avg_Log_MSE_h1
+  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_MSE_h1
 
-Avg_Log_MSE_h1 %>% 
+Avg_Log_WL100_MSE_h1 %>% 
   mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
@@
 
-# BoxCox Transformation for $\lambda \in (0,1)$
+# Log Transformation with 180 observations of training window (Average MSE calculated over 60 replications)
 
 ```{r, echo=FALSE}
-DF_BoxCoxTrans_set1 <- read.csv("OvernightTrips_BoxCoxTrans_set1_Fc.csv")[,-1]
+DF_LogTrans_WL180 <- read.csv("DF_LogTrans_WL180.csv")[,-1]
 
-DF_BoxCoxTrans_set1 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_set1
+DF_LogTrans_WL180 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_WL180
 
-DF_BoxCoxTrans_set1 %>%
+DF_LogTrans_WL180 %>% 
   group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
@@
   ungroup() %>% 
-  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_set1_MSE_h1
+  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL180_MSE_h1
 
-Avg_BoxCox_set1_MSE_h1 %>%
+Avg_Log_WL180_MSE_h1 %>% 
   mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
@@
 
-# BoxCox Transformation for $\lambda \in (-0.5,2)$
+<!-- # BoxCox Transformation for $\lambda \in (0,1)$ -->
+
+<!-- ```{r, echo=FALSE} -->
+<!-- DF_BoxCoxTrans_set1 <- read.csv("OvernightTrips_BoxCoxTrans_set1_Fc.csv")[,-1] -->
+
+<!-- DF_BoxCoxTrans_set1 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_set1 -->
+
+<!-- DF_BoxCoxTrans_set1 %>% -->
+<!--   group_by(`F.method`, `R.method`, Forecast_Horizon) %>% -->
+<!--   summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% -->
+<!--   filter(Forecast_Horizon == 1) %>% -->
+<!--   ungroup() %>% -->
+<!--   dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_set1_MSE_h1 -->
+
+<!-- Avg_BoxCox_set1_MSE_h1 %>% -->
+<!--   mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", -->
+<!--                            Unbiased_M2 = "Unbiased (Method 2)")) %>% -->
+<!--   spread(key = F.method, value = MSE) %>% -->
+<!--   kable(format = "latex") -->
+
+<!-- ``` -->
+
+# BoxCox Transformation for $\lambda \in (-0.5,2)$ with 100 observations of training window (Average MSE calculated over 140 replications)
 
 ```{r, echo=FALSE}
-DF_BoxCoxTrans_set2 <- read.csv("OvernightTrips_BoxCoxTrans_set2_Fc.csv")[,-1]
+DF_BoxCoxTrans_WL100 <- read.csv("DF_BoxCoxTrans_WL100.csv")[,-1]
 
-DF_BoxCoxTrans_set2 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_set2
+DF_BoxCoxTrans_WL100 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_WL100
 
-DF_BoxCoxTrans_set2 %>%
+DF_BoxCoxTrans_WL100 %>%
   group_by(`F.method`, `R.method`, Forecast_Horizon) %>%
@@
   ungroup() %>%
-  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_set2_MSE_h1
+  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_WL100_MSE_h1
 
-Avg_BoxCox_set2_MSE_h1 %>%
+Avg_BoxCox_WL100_MSE_h1 %>%
   mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)",
@@
 ```
+
+# BoxCox Transformation for $\lambda \in (-0.5,2)$ with 180 observations of training window (Average MSE calculated over 60 replications)
+
+```{r, echo=FALSE}
+DF_BoxCoxTrans_WL180 <- read.csv("DF_BoxCoxTrans_WL180.csv")[,-1]
+
+DF_BoxCoxTrans_WL180 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_WL180
+
+DF_BoxCoxTrans_WL180 %>%
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>%
+  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>%
+  filter(Forecast_Horizon == 1) %>%
+  ungroup() %>%
+  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_WL180_MSE_h1
+
+Avg_BoxCox_WL180_MSE_h1 %>%
+  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)",
+                           Unbiased_M2 = "Unbiased (Method 2)")) %>%
+  spread(key = F.method, value = MSE) %>%
+  kable(format = "latex")
+
+```

### 2019-09-02 Application-R/Application-TourismData/Final-results/Trash/TourismData-Final-results.Rmd
More on bias correction

---
title: "Tourism Data Analysis"
output:
  pdf_document: 
    keep_tex: yes
  html_document: default
date: "31 July 2019"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(Matrix)
library(hts)
library(readr)
library(tibble)
library(kableExtra)
# library(reshape2)
```

# Box and whisker plots for orthogonal and oblique projections from better models

```{r, echo=FALSE}
OvernightTrips_OriginalScale_Fc <- read.csv("OvernightTrips_OriginalScale_Fc.csv")[,-1]

OvernightTrips_OriginalScale_Fc %>%
  mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2,
         Fc_horizon = recode(Fc_horizon, "1" = "h=1", "2" = "h=2",
                             "3" = "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6")) %>%
  group_by(`R.method`, Fc_horizon, Replication) %>%
  summarise(MSE = mean(SquaredE)) -> OvernightTrips_OriginalScale_MSE

OvernightTrips_OriginalScale_MSE %>%
  filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>%
  spread(key = `R.method`, value = MSE) %>%
  mutate("Base-OLS" = Base - OLS,
         "Base-MinT" = Base - `MinT(Shrink)`,
         "Base-WLS" = Base - WLS) %>%
  dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>%
  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>%
  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>%
  ggplot(aes(x = Method, y = MSE)) +
  geom_boxplot() + facet_wrap(~ Fc_horizon) +
  ylab("MSE") + xlab("Reconciliation Method")

library(scales)

asinh_trans <- function(){
  trans_new(name = 'asinh', transform = function(x) asinh(x), 
            inverse = function(x) sinh(x))
}

OvernightTrips_OriginalScale_MSE %>%
  filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>%
  spread(key = `R.method`, value = MSE) %>%
  mutate("Base-OLS" = Base - OLS,
         "Base-MinT" = Base - `MinT(Shrink)`,
         "Base-WLS" = Base - WLS) %>%
  dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>%
  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>%
  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>%
  ggplot(aes(x = Method, y = MSE)) +
  geom_boxplot() + scale_y_continuous(trans = 'asinh',breaks=c(-10000,-1000,-100,0,100,1000,10000))+
  facet_wrap(~ Fc_horizon)+
  theme_bw()

```

# Box and whisker plots for orthogonal and oblique projections from misspecified models

```{r, echo=FALSE}
OvernightTrips_OriginalScaleMisspecified_Fc <- read.csv("OvernightTrips_OriginalScaleMisspecified_Fc.csv")[,-1]

OvernightTrips_OriginalScaleMisspecified_Fc %>%
  mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2,
         Fc_horizon = recode(Fc_horizon, "1" = "h=1", "2" = "h=2",
                             "3" = "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6")) %>%
  group_by(`R.method`, Fc_horizon, Replication) %>%
  summarise(MSE = mean(SquaredE)) -> OvernightTrips_OriginalScaleMisspecified_MSE

OvernightTrips_OriginalScaleMisspecified_MSE %>%
  filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>%
  spread(key = `R.method`, value = MSE) %>%
  mutate("Base-OLS" = Base - OLS,
         "Base-MinT" = Base - `MinT(Shrink)`,
         "Base-WLS" = Base - WLS) %>%
  dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>%
  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>%
  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>%
  ggplot(aes(x = Method, y = MSE)) +
  geom_boxplot() + facet_wrap(~ Fc_horizon) +
  ylab("MSE") + xlab("Reconciliation Method")

```

# Log Transformation

```{r, echo=FALSE}
DF_LogTrans <- read.csv("OvernightTrips_LogTrans_Fc.csv")[,-1]

DF_LogTrans %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans

DF_LogTrans %>% 
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>% 
  filter(Forecast_Horizon == 1) %>% 
  ungroup() %>% 
  dplyr::select(-Forecast_Horizon)-> Avg_Log_MSE_h1

Avg_Log_MSE_h1 %>% 
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
  spread(key = F.method, value = MSE) %>% 
  kable(format = "latex")

```

# BoxCox Transformation for $\lambda \in (0,1)$

```{r, echo=FALSE}
DF_BoxCoxTrans_set1 <- read.csv("OvernightTrips_BoxCoxTrans_set1_Fc.csv")[,-1]

DF_BoxCoxTrans_set1 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_set1

DF_BoxCoxTrans_set1 %>%
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>%
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>%
  filter(Forecast_Horizon == 1) %>%
  ungroup() %>%
  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_set1_MSE_h1

Avg_BoxCox_set1_MSE_h1 %>%
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)",
                           Unbiased_M2 = "Unbiased (Method 2)")) %>%
  spread(key = F.method, value = MSE) %>%
  kable(format = "latex")

```

# BoxCox Transformation for $\lambda \in (-0.5,2)$

```{r, echo=FALSE}
DF_BoxCoxTrans_set2 <- read.csv("OvernightTrips_BoxCoxTrans_set2_Fc.csv")[,-1]

DF_BoxCoxTrans_set2 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_set2

DF_BoxCoxTrans_set2 %>%
  group_by(`F.method`, `R.method`, Forecast_Horizon) %>%
  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>%
  filter(Forecast_Horizon == 1) %>%
  ungroup() %>%
  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_set2_MSE_h1

Avg_BoxCox_set2_MSE_h1 %>%
  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)",
                           Unbiased_M2 = "Unbiased (Method 2)")) %>%
  spread(key = F.method, value = MSE) %>%
  kable(format = "latex")

```

### 2019-09-02 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Set-2/Results-New/Analysis.R

@@ -1,27 +1,0 @@
-
-library(tidyverse)
-
-
-
-DF_BoxCoxTrans_1_50 <- read.csv("DF_BoxCoxTrans_set2_1-50.csv")[,-1] 
-DF_BoxCoxTrans_51_100 <- read.csv("DF_BoxCoxTrans_set2_51-100.csv")[,-1]
-DF_BoxCoxTrans_101_140 <- read.csv("DF_BoxCoxTrans_set2_101-140.csv")[,-1]
-
-rbind(DF_BoxCoxTrans_1_50, DF_BoxCoxTrans_51_100, DF_BoxCoxTrans_101_140) %>% 
-  as.data.frame() -> DF_BoxCoxTrans
-write.csv(x=DF_BoxCoxTrans, file = "DF_BoxCoxTrans_set2.csv")
-
-
-DF_BoxCoxTrans %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans
-
-DF_BoxCoxTrans %>% 
-  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
-  summarise(MSE = mean(SquaredE)) %>% 
-  spread(key = Forecast_Horizon, value = MSE)
-
-
-DF_BoxCoxTrans %>% 
-  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
-  filter(Replication != 115) %>% 
-  summarise(MSE = mean(SquaredE)) %>% 
-  spread(key = Forecast_Horizon, value = MSE)

### 2019-09-02 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Set-2/TourismForecasting_BoxCoxTrans_BiasAdjust_set2_1-50.R

@@ -1,436 +1,0 @@
-## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
-## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
-## Length of data expands from Jan-1998 to Dec-2017
-
-# Here we fit univariate ARIMA models for the Box-Cox transformed data
-# The back transformed data will be biased and we bias adjust to get 
-# unbiased point forecasts.
-
-#Box-Cox transformation lambda is selected from Guerrero method limited between (-0.5,2)
-
-#We use two methods for bias correction
-# M1 - Bias correction via formulation
-# M2 - Bias correction via residual mean adjustment
-
-library(tidyverse)
-library(fpp2)
-library(Matrix)
-library(hts)
-library(readr)
-library(tibble)
-library(tsibble)
-library(fable)
-library(fabletools)
-
-# Import bottom level data
-#Importing data
-
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(`Adelaide Hills` > 80) %>% 
-  as.numeric() -> a
-
-which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(row_number() %in% c(60+12,60-12)) %>% 
-  summarise(mean(`Adelaide Hills`)) %>% 
-  as.numeric() -> b
-
-OvernightTrips_Region_new <- OvernightTrips_Region %>% 
-  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
-                                      TRUE ~ as.double(`Adelaide Hills`)))
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
[…]

### 2019-09-02 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Set-2/TourismForecasting_BoxCoxTrans_BiasAdjust_set2_51-100.R

@@ -1,436 +1,0 @@
-## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
-## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
-## Length of data expands from Jan-1998 to Dec-2017
-
-# Here we fit univariate ARIMA models for the Box-Cox transformed data
-# The back transformed data will be biased and we bias adjust to get 
-# unbiased point forecasts.
-
-#Box-Cox transformation lambda is selected from Guerrero method limited between (-0.5,2)
-
-#We use two methods for bias correction
-# M1 - Bias correction via formulation
-# M2 - Bias correction via residual mean adjustment
-
-library(tidyverse)
-library(fpp2)
-library(Matrix)
-library(hts)
-library(readr)
-library(tibble)
-library(tsibble)
-library(fable)
-library(fabletools)
-
-# Import bottom level data
-#Importing data
-
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(`Adelaide Hills` > 80) %>% 
-  as.numeric() -> a
-
-which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(row_number() %in% c(60+12,60-12)) %>% 
-  summarise(mean(`Adelaide Hills`)) %>% 
-  as.numeric() -> b
-
-OvernightTrips_Region_new <- OvernightTrips_Region %>% 
-  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
-                                      TRUE ~ as.double(`Adelaide Hills`)))
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
[…]

### 2019-09-02 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Set-2/WindowLength-100/Results/Analysis.R

@@ -1,0 +1,22 @@
+
+library(tidyverse)
+
+
+
+DF_BoxCoxTrans_WL100_1_50 <- read.csv("DF_BoxCoxTrans_WL100_1-50.csv")[,-1] %>% select(-SquaredE)
+DF_BoxCoxTrans_WL100_51_100 <- read.csv("DF_BoxCoxTrans_WL100_51-100.csv")[,-1] %>% select(-SquaredE)
+DF_BoxCoxTrans_WL100_101_140 <- read.csv("DF_BoxCoxTrans_WL100_101-140.csv")[,-1]
+
+rbind(DF_BoxCoxTrans_WL100_1_50, DF_BoxCoxTrans_WL100_51_100, DF_BoxCoxTrans_WL100_101_140) %>% 
+  as.data.frame() -> DF_BoxCoxTrans_WL100
+write.csv(x=DF_BoxCoxTrans_WL100, file = "DF_BoxCoxTrans_WL100.csv")
+
+
+DF_BoxCoxTrans_WL100 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_WL100
+
+DF_BoxCoxTrans_WL100 %>% 
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  summarise(MSE = mean(SquaredE)) %>% 
+  spread(key = Forecast_Horizon, value = MSE)
+
+

### 2019-09-02 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Set-2/WindowLength-100/TourismForecasting_BoxCoxTrans_BiasAdjust_set2_WL100_1-50.R

@@ -1,0 +1,441 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the Box-Cox transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#Box-Cox transformation lambda is selected from Guerrero method limited between (-0.5,2)
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+#This analysis takes a rolling window approach and we use window length as 100
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+library(tsibble)
+library(fable)
+library(fabletools)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
[…]

### 2019-09-02 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Set-2/WindowLength-100/TourismForecasting_BoxCoxTrans_BiasAdjust_set2_WL100_101-140.R

@@ -1,0 +1,441 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the Box-Cox transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#Box-Cox transformation lambda is selected from Guerrero method limited between (-0.5,2)
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+#This analysis takes a rolling window approach and we use window length as 100
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+library(tsibble)
+library(fable)
+library(fabletools)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
[…]

### 2019-09-02 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Set-2/WindowLength-100/TourismForecasting_BoxCoxTrans_BiasAdjust_set2_WL100_51-100.R

@@ -1,0 +1,441 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the Box-Cox transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#Box-Cox transformation lambda is selected from Guerrero method limited between (-0.5,2)
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+#This analysis takes a rolling window approach and we use window length as 100
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+library(tsibble)
+library(fable)
+library(fabletools)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
[…]

### 2019-09-02 Application-R/Application-TourismData/Bias_correction/BoxCoxTrans/Set-2/WindowLength-180/TourismForecasting_BoxCoxTrans_BiasAdjust_set2_WL180.R

@@ -1,0 +1,441 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the Box-Cox transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#Box-Cox transformation lambda is selected from Guerrero method limited between (-0.5,2)
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+#This analysis takes a rolling window approach and we use window length as 180
+
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+library(tsibble)
+library(fable)
+library(fabletools)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
[…]

### 2019-09-02 Application-R/Application-TourismData/Bias_correction/LogTrans/TourismForecasting_LogTrans_BiasAdjust_51-100.R

@@ -1,404 +1,0 @@
-## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
-## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
-## Length of data expands from Jan-1998 to Dec-2017
-
-# Here we fit univariate ARIMA models for the log transformed data
-# The back transformed data will be biased and we bias adjust to get 
-# unbiased point forecasts.
-
-#We use two methods for bias correction
-# M1 - Bias correction via formulation
-# M2 - Bias correction via residual mean adjustment
-
-library(tidyverse)
-library(fpp2)
-library(Matrix)
-library(hts)
-library(readr)
-library(tibble)
-
-# Import bottom level data
-#Importing data
-
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(`Adelaide Hills` > 80) %>% 
-  as.numeric() -> a
-
-which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(row_number() %in% c(60+12,60-12)) %>% 
-  summarise(mean(`Adelaide Hills`)) %>% 
-  as.numeric() -> b
-
-OvernightTrips_Region_new <- OvernightTrips_Region %>% 
-  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
-                                      TRUE ~ as.double(`Adelaide Hills`)))
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
-Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
-                                                                  c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,
[…]

### 2019-09-02 Application-R/Application-TourismData/Bias_correction/LogTrans/WindowLength100/TourismForecasting_LogTrans_BiasAdjust-WindowL100.R

@@ -1,0 +1,405 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+#This analysis takes a rolling window approach and we use window length as 100
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-09-02 Application-R/Application-TourismData/Bias_correction/LogTrans/WindowLength100/TourismForecasting_LogTrans_BiasAdjust-WindowL100_1-50.R

@@ -1,0 +1,405 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+#This analysis takes a rolling window approach and we use window length as 100
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-09-02 Application-R/Application-TourismData/Bias_correction/LogTrans/WindowLength100/TourismForecasting_LogTrans_BiasAdjust-WindowL100_51-100.R

@@ -1,0 +1,405 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+#This analysis takes a rolling window approach and we use window length as 100
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-09-02 Application-R/Application-TourismData/Bias_correction/LogTrans/WindowLength100/Trash/Results/Analysis.R

@@ -1,0 +1,35 @@
+
+library(tidyverse)
+
+
+
+DF_LogTrans_1_50 <- read.csv("DF_LogTrans_1-50.csv")[,-1]
+DF_LogTrans_51_100 <- read.csv("DF_LogTrans_51-100.csv")[,-1]
+DF_LogTrans_101_140 <- read.csv("DF_LogTrans_101-140.csv")[,-1]
+
+rbind(DF_LogTrans_1_50, DF_LogTrans_51_100, DF_LogTrans_101_140) %>% 
+  as.data.frame() -> DF_LogTrans
+write.csv(x=DF_LogTrans, file = "DF_LogTrans.csv")
+
+
+DF_LogTrans %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans
+
+# DF_LogTrans_1_50 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_1_50
+# DF_LogTrans_51_100 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_51_100
+# DF_LogTrans_101_140 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_101_140
+# 
+# DF_LogTrans_101_140 %>% filter(Replication != 130) %>% 
+#   group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+#   summarise(MSE = mean(SquaredE)) %>% 
+#   spread(key = Forecast_Horizon, value = MSE)
+
+
+DF_LogTrans %>% filter(Replication != 103) %>% 
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  summarise(MSE = mean(SquaredE)) %>% 
+  filter(Forecast_Horizon == 1) %>% 
+  ungroup() %>% 
+  dplyr::select(-Forecast_Horizon) %>% 
+  spread(key = F.method, value = MSE)
+
+

### 2019-09-02 Application-R/Application-TourismData/Bias_correction/LogTrans/WindowLength180/TourismForecasting_LogTrans_BiasAdjust-WindowL180.R

@@ -1,0 +1,405 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+#This analysis takes a rolling window approach and we use window length as 180
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-09-02 Application-R/Application-TourismData/Bias_correction/LogTrans/WindowLength180/TourismForecasting_LogTrans_BiasAdjust-WindowL180_51-60.R

@@ -1,0 +1,405 @@
+## This file contains the analysis of Tourism data using Hierarchical forecasting methods. 
+## Data form a hierarchy with 3 levels - 8-states, -Zones, -Regions. 
+## Length of data expands from Jan-1998 to Dec-2017
+
+# Here we fit univariate ARIMA models for the log transformed data
+# The back transformed data will be biased and we bias adjust to get 
+# unbiased point forecasts.
+
+#We use two methods for bias correction
+# M1 - Bias correction via formulation
+# M2 - Bias correction via residual mean adjustment
+
+#This analysis takes a rolling window approach and we use window length as 180
+
+library(tidyverse)
+library(fpp2)
+library(Matrix)
+library(hts)
+library(readr)
+library(tibble)
+
+# Import bottom level data
+#Importing data
+
+OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
+
+## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(`Adelaide Hills` > 80) %>% 
+  as.numeric() -> a
+
+which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
+
+OvernightTrips_Region %>% 
+  dplyr::select(`Adelaide Hills`) %>% 
+  filter(row_number() %in% c(60+12,60-12)) %>% 
+  summarise(mean(`Adelaide Hills`)) %>% 
+  as.numeric() -> b
+
+OvernightTrips_Region_new <- OvernightTrips_Region %>% 
+  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
+                                      TRUE ~ as.double(`Adelaide Hills`)))
+
+#generating the hierarchy
+#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
+Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, list(7, c(6,5,4,4,3,3,2), 
[…]

### 2019-09-02 Application-R/Application-TourismData/Final-results/Time-Plots/TimePlots.R

@@ -1,275 +1,0 @@
-library(tidyverse)
-library(gridExtra)
-
-OvernightTrips_Region <- read_csv("OvernightTrips_2017.csv")[,-(1:3)]
-
-## Replacing the odd value in `Adelaide Hills` with the average of its adjecent numbers ##
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(`Adelaide Hills` > 80) %>% 
-  as.numeric() -> a
-
-which(OvernightTrips_Region$`Adelaide Hills`==a) -> x
-
-OvernightTrips_Region %>% 
-  dplyr::select(`Adelaide Hills`) %>% 
-  filter(row_number() %in% c(60+12,60-12)) %>% 
-  summarise(mean(`Adelaide Hills`)) %>% 
-  as.numeric() -> b
-
-OvernightTrips_Region_new <- OvernightTrips_Region %>% 
-  mutate(`Adelaide Hills` = case_when(`Adelaide Hills`%% a == 0 ~ b, 
-                                      TRUE ~ as.double(`Adelaide Hills`)))
-
-#generating the hierarchy
-#Hierarchy<-suppressMessages(hts(Bottom_level, list(7, c(14,21,12,12,5,5,7))))
-Hierarchy <- suppressMessages(hts(OvernightTrips_Region_new, 
-                                  list(7, c(6,5,4,4,3,3,2), c(2,2,1,4,4,1,3,1,3,6,7,3,4,3,2,3,3,4,2,3,1,1,1,2,2,3,4))))
-
-AllTS <- allts(Hierarchy) %>%
-  as_tibble()
-
-n<-ncol(AllTS)
-l1<-1
-l2<-sum(7)
-l3<-sum(6,5,4,4,3,3,2)
-m<-ncol(OvernightTrips_Region)
-
-
-AllTS_new <- AllTS + 1 # Add 1 since some series has zero observations and this will affect taking log transformations
-
-
-###################
-  #Total Series#
-###################
-
-AllTS %>% log() %>% 
-  dplyr::select("Total") %>% 
-  ts(start = c(1998, 1), frequency = 12) %>% 
-  autoplot() + ylab("log(Overnight trips)") + xlab("Time") + 
-  theme(legend.position="bottom") -> TSPlot_total
-
-AllTS %>% log() %>% 
-  dplyr::select("Total") %>% 
-  ts(start = c(1998, 1), frequency = 12) %>% 
[…]

### 2019-09-02 Hierarchical-forecast-reconciliation/Figs/InsampDir_1_George.tex
Working on paper

@@
-% Created by tikzDevice version 0.12.3 on 2019-08-29 11:23:10
+% Created by tikzDevice version 0.12.3 on 2019-09-02 10:24:06
 % !TEX encoding = UTF-8 Unicode
@@
 
-\usepackage{amsfonts}
-\usepackage{bm}
 \usepackage{amsfonts}
@@
 
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (288.71,191.64) {{$\huge \mathfrak{s}$}};
+\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.30] at (288.71,190.95) {{$\huge \mathfrak{s}$}};
 
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (218.82,303.05) {{$\huge \bm{R}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (218.82,303.05) {{$\huge \bm{R}$}};
 \definecolor{drawColor}{RGB}{255,165,0}

### 2019-09-02 Hierarchical-forecast-reconciliation/Figs/InsampDir_2_George.tex
Working on paper

@@
-% Created by tikzDevice version 0.12.3 on 2019-08-29 11:23:19
+% Created by tikzDevice version 0.12.3 on 2019-09-02 10:24:12
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (218.82,303.05) {{$\huge \bm{R}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (218.82,303.05) {{$\huge \bm{R}$}};
 \definecolor{drawColor}{RGB}{190,190,190}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (211.55,239.15) {{$\color{blue}{\hat{\bm{y}}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (211.55,239.15) {{$\color{blue}{\hat{\bm{y}}}$}};
 \definecolor{fillColor}{RGB}{0,0,0}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (160.73,149.38) {{$\color{black}{\bm{y}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (160.73,148.23) {{$\color{black}{\bm{y}}$}};
 \end{scope}

### 2019-09-02 Hierarchical-forecast-reconciliation/Figs/InsampDir_3_George.tex
Working on paper

@@
-% Created by tikzDevice version 0.12.3 on 2019-08-29 11:23:28
+% Created by tikzDevice version 0.12.3 on 2019-09-02 10:24:16
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (160.73,149.38) {{$\color{black}{\bm{y}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (160.73,148.23) {{$\color{black}{\bm{y}}$}};
 \definecolor{drawColor}{RGB}{0,0,255}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (211.55,239.15) {{$\color{blue}{\hat{\bm{y}}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (211.55,239.15) {{$\color{blue}{\hat{\bm{y}}}$}};
 \definecolor{drawColor}{RGB}{255,0,0}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (176.70,150.25) {{$\color{red}{\tilde{\bm{y}}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.20] at (176.70,149.10) {{$\color{red}{\tilde{\bm{y}}}$}};
 

### 2019-09-02 Application-R/Application-TourismData/George/Seasonal100.R

@@ -50,7 +50,6 @@ AllTS_new <- allts(Hierarchy) %>%
   as_tibble()
 
 
-
 n <- ncol(AllTS_new)
 l1 <- 1
 l2 <- sum(7)
@@ -100,6 +99,12 @@ DF <- tibble("Series" = character(),
              "Actual" = double(),
              "Replication" = integer())
 
+TREND <- tibble("Replication"=integer(),
+                "d"=integer(),
+                "D"=integer(),
+                "intercept"=integer(),
+                "drift"=integer())
+
 # A function to return back transformed forecasts and bias adjust back transformed forecasts
 # given the forecasts in the transformed space
 
@@ -147,7 +152,14 @@ for (j in 1:C) {#C = 140
   for (i in 1:n) {
 
     TS <- Train[,i] %>% ts(frequency = 12)
+    #TS <- Train[,i] %>% as.ts()
+
     fit <- auto.arima(TS)
+
+    if (i==1){
+    TR<- c(fit$arma[6],fit$arma[7],
+             !is.na(fit$coef["intercept"]),!is.na(fit$coef["drift"]))
+    }
 
     Fc <- forecast(fit, h=min(H, nrow(Test)))
     Fc_mean <- Fc$mean
@@ -191,6 +203,11 @@ for (j in 1:C) {#C = 140
                        Actual = as.numeric(Test_1),
                        Replication = rep(j, n*min(H, nrow(Test_1))))
 
+  TREND <- TREND %>% add_row(Replication = j,
+                             d=TR[1],
+                             D=TR[2],
+                             intercept=TR[3],
+                             drift=TR[4])
 
   ###--Reconciliation--###
 
@@ -264,13 +281,13 @@ DF %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF
 
 DF %>%
   group_by(`F-method`, `R-method`, Forecast_Horizon) %>%
-  summarise(MSE = mean(SquaredE)) %>%
+  summarise(MSE = mean(SquaredE, na.rm = TRUE)) %>%
   spread(key = Forecast_Horizon, value = MSE)
[…]

### 2019-09-02 Application-R/Application-TourismData/George/Seasonal200.R

@@ -60,6 +60,14 @@ H <- 12
 L <- 200 #Size of the training sample
 C <- nrow(AllTS_new) - L
 
+AllTS_new$Total %>% ts(start = 1998, frequency = 12) %>%
+  autoplot() +geom_vline(xintercept=2006, colour='black', size=1.2) +
+  geom_vline(xintercept=2016.917, colour='black', size=1.2) +
+  geom_vline(xintercept=2006.333, colour='blue', size=1.2)+
+  geom_vline(xintercept=2008.417, colour='blue', size=1.2)+
+  geom_vline(xintercept=2014.67, colour='red', size=1.2)+
+  geom_vline(xintercept=2016.75, colour='red', size=1.2)+
+  geom_vline(xintercept=2012.75, colour='green', size=1.2)
 
 #Generating the summing matrix
 S <- smatrix(Hierarchy)
@@ -294,6 +302,30 @@ DF_MSE %>%
   select(Replication, Forecast_Horizon, `Base-OLS`, `Base-MinT`,`Base-WLS`,`Base-WLS_sd`) %>%
   gather(`Base-OLS`,`Base-MinT`, `Base-WLS`,`Base-WLS_sd`, key = Method, value = MSE) %>%
   ggplot(aes(x = Method, y = MSE)) + geom_boxplot() + facet_wrap(~`Forecast_Horizon`)
+
+DF_MSE %>%
+  filter(`F-method`=="ARIMA", `R-method`%in% c("Base", "OLS", "MinT(Shrink)","WLS","WLS_sd"),
+         `Forecast_Horizon`%in% 1:12) %>%
+  spread(key = `R-method`, value = MSE) %>%
+  mutate("Base-OLS" = Base - OLS,
+         "Base-MinT" = Base - `MinT(Shrink)`,
+         "Base-WLS" = Base - WLS,
+         "Base-WLS_sd" = Base - WLS_sd) %>%
+  select(Replication, Forecast_Horizon, `Base-OLS`, `Base-MinT`,`Base-WLS`,`Base-WLS_sd`) %>%
+  gather(`Base-OLS`,`Base-MinT`, `Base-WLS`,`Base-WLS_sd`, key = Method, value = MSE) %>%
+  ggplot(aes(x = Replication, y = MSE,color=Method)) + geom_line() + facet_wrap(~`Forecast_Horizon`)
+
+
+
+# Average measures
+
[…]

### 2019-09-02 Hierarchical-forecast-reconciliation/Figs/schematics_projections_George.R

@@ -27,10 +27,10 @@ lines(c(0,0),c(-3,5))
 lines(c(-2,5),c(0,0))
 #lines(c(-1,3.5),c(-0.5,1.75),lwd=2)
 arrows(0,0,4.6,1.25,lwd=2)
-text(4.6,1.25,"{$\\huge \\mathfrak{s}$}",pos=4, cex = 1)
+text(4.6,1.25,"{$\\huge \\mathfrak{s}$}",pos=4, cex = 1.3)
 
 arrows(0,0,2.4,4.8,lwd=2)
-text(2.4,4.8,"{$\\huge \\bm{R}$}",pos=3, cex = 1)
+text(2.4,4.8,"{$\\huge \\bm{R}$}",pos=3, cex = 1.2)
 
 #rmat<-matrix(c(1,4,-0.5,0.25),2,2,byrow = FALSE)
 # e<-t(rmat%*%matrix(rnorm(200,0,0.3),2,100))
@@ -54,11 +54,11 @@ lines(c(0,0),c(-3,5))
 lines(c(-2,5),c(0,0))
 #lines(c(-1,3.5),c(-0.5,1.75),lwd=2)
 arrows(0,0,4.6,1.25,lwd=2)
-text(4.6,1.25,"{$\\huge \\mathfrak{s}$}",pos=4, cex = 1)
+text(4.6,1.25,"{$\\huge \\mathfrak{s}$}",pos=4, cex = 1.3)
 
 
 arrows(0,0,2.4,4.8,lwd=2)
-text(2.4,4.8,"{$\\huge \\bm{R}$}",pos=3, cex = 1)
+text(2.4,4.8,"{$\\huge \\bm{R}$}",pos=3, cex = 1.2)
 
 #rmat<-matrix(c(1,4,-0.5,0.25),2,2,byrow = FALSE)
 # e<-t(rmat%*%matrix(rnorm(200,0,0.3),2,100))
@@ -66,10 +66,10 @@ text(2.4,4.8,"{$\\huge \\bm{R}$}",pos=3, cex = 1)
 points(e_sample[,1],e_sample[,2],pch=19,col='gray')
 
 points(2.15,2.6,pch=20,cex=2,col='blue')
-text(2.15,2.6,"{$\\color{blue}{\\hat{\\bm{y}}}$}",pos = 3,cex = 1)
+text(2.15,2.6,"{$\\color{blue}{\\hat{\\bm{y}}}$}",pos = 3,cex = 1.2)
 
[…]

### 2019-09-02 Hierarchical-forecast-reconciliation/Figs/ObliqProj_George.tex

@@
-% Created by tikzDevice version 0.12.3 on 2019-08-29 11:23:36
+% Created by tikzDevice version 0.12.3 on 2019-09-02 10:24:30
 % !TEX encoding = UTF-8 Unicode

### 2019-09-02 Hierarchical-forecast-reconciliation/Figs/OrthProj_George.tex

@@
-% Created by tikzDevice version 0.12.3 on 2019-08-29 11:23:33
+% Created by tikzDevice version 0.12.3 on 2019-09-02 10:24:23
 % !TEX encoding = UTF-8 Unicode

### 2019-09-02 Hierarchical-forecast-reconciliation/Figs/orth_pointforerec_schematic.tex
Modified schematics of orthogonal and oblique projections

@@
-% Created by tikzDevice version 0.12 on 2019-07-25 17:17:29
+% Created by tikzDevice version 0.12.3 on 2019-09-02 11:12:43
 % !TEX encoding = UTF-8 Unicode
+\documentclass[10pt]{article}
+\usepackage{tikz}
+
+\usepackage[active,tightpage,psfixbb]{preview}
+
+\PreviewEnvironment{pgfpicture}
+
+\setlength\PreviewBorder{0pt}
+
+\usepackage{amsfonts}
+\usepackage{bm}
+\usepackage{amsfonts}
+\usepackage{bm}
+\usepackage{amsfonts}
+\usepackage{bm}
+\usepackage{amsfonts}
+\usepackage{bm}
+\usepackage{amsfonts}
+\usepackage{bm}\begin{document}
+
 \begin{tikzpicture}[x=1pt,y=1pt]
@@
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 87.60, 49.44) --
-	( 87.60,196.50);
+	( 87.60,233.26);
 
 \path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.84, 86.20) --
-	(197.90, 86.20);
+	(234.67, 86.20);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] ( 87.60, 86.20) -- (216.28,150.54);
+\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] ( 87.60, 86.20) -- (216.28,150.54);
 
-\path[draw=drawColor,line width= 1.2pt,line join=round,line cap=round] (206.33,135.46) --
+\path[draw=drawColor,line width= 0.8pt,line join=round,line cap=round] (206.33,135.46) --
 	(216.28,150.54) --
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (142.75,214.50) {{\large $\color{blue}{\hat{\bm{y}}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (142.75,202.50) {{\large $\color{blue}{\hat{\bm{y}}}$}};
 \definecolor{drawColor}{RGB}{255,0,0}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (175.84,106.58) {{\large $\color{red}{\tilde{\bm{y}}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (175.84,118.58) {{\large $\color{red}{\tilde{\bm{y}}}$}};
 \definecolor{drawColor}{RGB}{0,0,255}
@@
 \path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (142.75,196.50) -- (119.12,101.96);
-
-\path[draw=drawColor,line width= 0.4pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] (114.15,119.33) --
-	(119.12,101.96) --
-	(131.68,114.95);
 \definecolor{fillColor}{RGB}{0,0,0}
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (119.12, 78.22) {{\large $\color{black}{{\bm{y}}}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (119.12, 90.22) {{\large $\color{black}{{\bm{y}}}$}};
 \end{scope}
 \end{tikzpicture}
+\caption{a caption}
+\end{document}

### 2019-09-02 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex

@@
 
-	Consider the Euclidean distance between a forecast and the target.
+	Consider the Euclidean distance between the target and a forecast.
 This is equivalent to the root of the sum of squared forecast errors over the entire hierarchy.
@@
 		\begin{equation}
-		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|.
+		\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|\le\|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|.
 		\end{equation}
@@
 		Since, $\bm{y}_{t+h|t},\tilde{\bm{y}}_{t+h|t}\in\mathfrak{s}$ and since the projection is orthogonal, by Pythagoras' theorem
-		\begin{equation}
-		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2=\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2+\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2.
+		\begin{equation} \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|^2=\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2+\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|^2.
 		\end{equation}
@@
 		Since $\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2\ge 0$ this implies,
-		\begin{equation}
-		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2\ge\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2.
+		\begin{equation} \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|^2\ge\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|^2.
 		\end{equation}
@@
 	\begin{figure}[H]
-		\centering
-		\vspace{-0.9cm}
-		\tiny
-		\resizebox{\linewidth}{!}{\input{Figs/orth_pointforerec_schematic}}
+		\centering \includegraphics[width=0.6\textwidth]{Figs/orth_pointforerec_schematic.pdf}
 		\caption{Orthogonal projection of $\hat{\bm{y}}$ onto $\mathfrak{s}$ yielding the reconciled forecast $\tilde{\bm{y}}$}\label{fig:Schematic_OLSRecon}
-
 	\end{figure}
@@
 Thinking of the problem in terms of a geometry defined by the norm $\bm{v}'\bm{W}^{-1}\bm{v}$ is also quite instructive when it comes to thinking about the connection between distances and loss functions.
-In the generalised Euclidean geometry, the distance between the reconciled forecast and the realisation is given by $(\hat{\bm{y}}-\bm{y})'\bm{W}^{-1}(\hat{\bm{y}}-\bm{y})$.
+In the generalised Euclidean geometry, the distance between the reconciled forecast and the realisation is given by $(\bm{y}-\hat{\bm{y}})'\bm{W}^{-1}(\bm{y}-\hat{\bm{y}})$.
 For diagonal $\bm{W}^{-1}$, this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix, this is equivalent to a Mahalanobis distance.
@@
 		\begin{equation}
-		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{{\bm W}^{-1}}\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_{{\bm W}^{-1}}.
+		\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|_{{\bm W}^{-1}}\le\|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|_{{\bm W}^{-1}}.
 		\end{equation}
@@
 If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts.
-This will be demonstrated using a real data set in the empirical study in section~\ref{sec:comparebase}.
+This will be demonstrated using a real data set in the empirical study in Section~\ref{sec:comparebase}.
 
@@
 
-	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.
-Suppose the in-sample errors are given by the orange points.
-They provide information on the most likely direction of large deviations from the coherent subspace.
+	Figure~\ref{fig:OthogonalVSOblique_projection} provides geometrical intuition into the MinT method.
+Suppose that the orange points in panel (a) represent in-sample forecast errors.
+These provide information on the most likely direction of large deviations from the coherent subspace $\mathfrak{s}$.
 This direction is denoted by $\bm{R}$.
-Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).
+Panel (b) shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).
 One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.
-An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection shown in Figure \ref{fig:Orthogonal_projection_all_points}.
-Figure \ref{fig:Oblique_projection_all_points} depicts an oblique projection along $\bm{R}$ for all the gray points, yielding reconciled forecasts tightly packed near the target $\bm{y}$.
+An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection.
+Panel (c) shows the orthogonal projection of every potential base forecast onto the coherent subspace.
+Panel (d) depicts an oblique projection along $\bm{R}$ for all the gray points.
+The oblique projection yields reconciled forecasts tightly packed near the target $\bm{y}$.
 In this sense, the oblique MinT projection minimises the forecast error variance of the reconciled forecasts.
 In contrast to the result in Theorem~\ref{th:gdistred}, this property is a statistical property in the sense that MinT is optimal in expectation.
-
-%	\begin{figure}[H]
-%		\centering
-%		%\vspace{-0.9cm}
-%		\small
-%		\resizebox{\linewidth}{!}{
-%			\input{Figs/insampledir}
-%		}
-%		\caption{A schematic to represent MinT reconciliation.
-Points in orange colour represent the insample errors.
-$\bm{R}$ shows the most likely direction of deviations from the coherent subspace.
-$\hat{\bm{y}}$ is projected onto $\mathfrak{s}$ along the the direction of $\bm{R}$.}\label{fig:MinT_justification1}
-%	\end{figure}
-%		
-%	\begin{figure}[H]
-%		\centering
-%		%\vspace{-0.9cm}
-%		\small
-%		\resizebox{\linewidth}{!}{
-%			\input{Figs/oblique_justification2}
-%		}
-%		\caption{A schematic to represent MinT reconciliation.
-Grey points indicate potential realisations of the base forecast while the blue dot indicates one such realisation.
-The black dot ${\bm y}$ denotes the (unknown) target of the forecast.}\label{fig:MinT_justification2}
-%	\end{figure}
-%	
-%	\begin{figure}[H]
-%		\centering
-%		%\vspace{-0.9cm}
-%		\small
-%		\resizebox{\linewidth}{!}{
-%			\includegraphics{Figs/OrthProj.pdf}}
-%		\caption{All gray points are orthogonally projected onto the coherent subspace $\mathfrak{s}$.
-Reconciled forecasts marked in red dots are widely spread about the target $\bm{y}$.}\label{fig:Orthogonal_projection_all_points}
-%	\end{figure}
-%	
-%	
-%	\begin{figure}[H]
-%	\centering
-%	%\vspace{-0.9cm}
-%	\small
-%	\resizebox{\linewidth}{!}{
-%		\includegraphics{Figs/ObliqueProjection.pdf}}
-%	\caption{All gray points are obliquely projected along the direction of $\bm{R}$.
-Reconciled points denoted in red dots are concentrated about the target $\bm{y}$.}\label{fig:Oblique_projection_all_points}
-%	\end{figure}
-
-%%%%%%%%%%%%%%%%%%%
-
-%	\begin{figure}
-%		\centering
-%		\begin{subfigure}[t]{0.45\textwidth}
-%			\centering
-%			\includegraphics[width=\linewidth]{Figs/InsampDir_1.pdf}
-%%			\label{fig:InsampDir_1}
-%		\end{subfigure}
-%		\hfill
-%		\begin{subfigure}[t]{0.45\textwidth}
-%			\centering
-%			\includegraphics[width=\linewidth]{Figs/InsampDir_2.pdf}
-%%			\label{fig:InsampDir_2}
-%		\end{subfigure}
-%		
-%		\vspace{1cm}
-%		
-%		\begin{subfigure}[t]{0.45\textwidth}
-%			\centering
-%			\includegraphics[width=\linewidth]{Figs/OrthProj.pdf}
-%%			\label{fig:OrthProj}
-%		\end{subfigure}
-%		\hfill
-%		\begin{subfigure}[t]{0.45\textwidth}
-%			\centering
-%			\includegraphics[width=\linewidth]{Figs/ObliqProj.pdf}
-%%			\label{fig:ObliqProj}
-%		\end{subfigure}
-%		
-%%		\begin{subfigure}[t]{\textwidth}
-%%			\centering
-%%			\includegraphics[width=\linewidth]{example-image-c.pdf}
-%%			\caption{Price regulation} \label{fig:timing3}
-%%		\end{subfigure}
-%		\caption{A schematic to represent orthogonal and oblique reconciliation.
-Points in orange colour in top left figure represent the insample errors.
-$\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$.
-Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation.
-The black dot ${\bm y}$ denotes the (unknown) target of the forecast.
-Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection}
-%	\end{figure}
-%
-%	\begin{figure}
-%	
-%	\begin{adjustbox}{minipage=\linewidth,scale=0.7}
-%	\begin{subfigure}[t]{0.45\textwidth}
-%%		\centering
-%		\input{Figs/InsampDir_1}
-%		%			\label{fig:InsampDir_1}
-%	\end{subfigure}
-%	\hspace{1cm}
-%	\begin{subfigure}[t]{0.45\textwidth}
-%%		\centering
-%		\input{Figs/InsampDir_2}
-%		%			\label{fig:InsampDir_2}
-%	\end{subfigure}
-%	
-%	\vfill
-%%	\vspace{0.3cm}
-%	
-%	\begin{subfigure}[t]{0.45\textwidth}
-%%		\centering
-%		\input{Figs/Orthproj}
-%		%			\label{fig:OrthProj}
-%	\end{subfigure}
-%	\hspace{1cm}
-%	\begin{subfigure}[t]{0.45\textwidth}
-%%		\centering
-%		\input{Figs/ObliqProj}
-%		%			\label{fig:ObliqProj}
-%	\end{subfigure}
-%	
-%	%		\begin{subfigure}[t]{\textwidth}
-%	%			\centering
-%	%			\includegraphics[width=\linewidth]{example-image-c.pdf}
-%	%			\caption{Price regulation} \label{fig:timing3}
-%	%		\end{subfigure}
-%	
-%	\end{adjustbox}
-%\caption{A schematic to represent orthogonal and oblique reconciliation.
-Orange colour points in top left figure represent the insample errors.
-$\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$.
-Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation.
-The black dot ${\bm y}$ denotes the (unknown) target of the forecast.
-Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.} \label{fig:OthogonalVSOblique_projection}
-%\end{figure}
 
@@
     \begin{subfigure}[!h]{0.48\textwidth}
+        \includegraphics[width=\textwidth]{Figs/OrthProj_George.pdf}
+        \caption{}
+    \end{subfigure}    \begin{subfigure}[!h]{0.48\textwidth}
         \includegraphics[width=\textwidth]{Figs/ObliqProj_George.pdf}
@@
     \end{subfigure}
-    \begin{subfigure}[!h]{0.48\textwidth}
-        \includegraphics[width=\textwidth]{Figs/OrthProj_George.pdf}
-        \caption{}
-    \end{subfigure}
-    \caption{A schematic to represent orthogonal and oblique reconciliation.
-Orange colour points in top left figure represent the insample errors.$\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$.
-Grey points in top right figure indicate  potential realisations of the base forecast while the blue dot ${\hat{\bm y}}$ indicates one such realisation.
+    \caption{A schematic representing orthogonal and oblique reconciliations.
+The orange points in (a) represent in-sample errors.
+$\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$.
+Grey points in (b) indicate  potential base forecasts while the blue dot ${\hat{\bm y}}$ represents one such realisation.
 The black dot ${\bm y}$ denotes the (unknown) target of the forecast.
-Bottom left figure shows the orthogonal projection of all potential realisations onto the coherent subspace while bottom right figure shows the oblique projection.
-} \label{fig:OthogonalVSOblique_projection_new}
+(c) shows the orthogonal projection of all potential base forecasts onto the coherent subspace while (d) shows an oblique projection.} \label{fig:OthogonalVSOblique_projection}
 \end{figure}
-
-%		\begin{figure}[H]
-%		\centering
-%		%\vspace{-0.9cm}
-%		\small
-%		\resizebox{\linewidth}{!}{
-%			\input{Figs/ObliqueProjection}
-%		}
-%		\caption{\textcolor{red}{write caption}}\label{fig:Oblique_projection}
-%	\end{figure}
-
-%\begin{figure}
-%	\centering
-%	\begin{subfigure}{0.47\textwidth}
-%		\resizebox{\linewidth}{!}{
-%			\input{Figs/Orth.proj.tex}}
-%		\caption{bla bla}
-%	\end{subfigure}
-%	\begin{subfigure}{0.47\textwidth}
-%		\resizebox{\linewidth}{!}{
-%			\input{Figs/ObliqueProjection.tex}}
-%			\caption{bla bla}
-%	\end{subfigure}
-%\end{figure}
 
@@
 		\caption{$\mathfrak{L}$ is a linear subspace of the coherent subspace $\mathfrak{s}$.
-If $s\circ g$ is a projection not onto $\mathfrak{s}$ but onto $\mathfrak{L}$, then $\bm{\mu} \in \mathfrak{s}$ will be moved to $\bar{\bm{\mu}} \in \mathfrak{L}$.}\label{fig:Schematic_3D}
+If a projection is onto $\mathfrak{L}$ instead of $\mathfrak{s}$, then $\bm{\mu} \in \mathfrak{s}$ will be moved to $\bm{\mu}^* \in \mathfrak{L}$.}\label{fig:Schematic_3D}
 	\end{figure}
@@
 However, equipped with a geometric understanding of the problem, we would advise against this approach.
-The constraint $\bm{GS}=\bm{I}$  is not just about bias and dropping the constraint compromises all of the attractive properties of projections.
-Opening the door to reconciliation methods that change already coherent base forecast would seem to suggest an increase in the variability of the forecast.
-This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance is to reduce variance.
+The constraint $\bm{GS}=\bm{I}$  is not just about bias.
+Dropping the constraint compromises all of the attractive properties of projections.
+Opening the door to reconciliation methods that change already coherent base forecasts would seem to suggest an increase in the variability of the forecast.
+This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance.
 
@@
 Geometrically, the intuition is simple.
-In top left panel in Figure \ref{fig:OthogonalVSOblique_projection_new}, the orange points are centered around the origin as would be expected from an unbiased forecast.
+In panel (a) of Figure \ref{fig:OthogonalVSOblique_projection}, the orange points are centered around the origin as would be expected from an unbiased forecast.
 If forecasts are biased, then errors should simply be translated until they are centered at the origin.
@@
 First, for the very construction we consider, where bias is induced by taking a log or Box Cox transformation, bias should be corrected by a multiplicative rather than an additive factor.
-Second, if in-sample errors are non-stationary due to model misspecification structural breaks then the proposes method for bias correction may break down.
+Second, if in-sample errors are non-stationary due to model misspecification or structural breaks, then the proposed method for bias correction may break down.
 
@@
 This will make the empirical application a bit broader not only about bias correction, i.e., both about showing how projections work and how bias correction works.}
-	Using an empirical application to forecast Australian domestic tourism flow, we illustrate the usefulness of projection based reconciliation in practice.
-Previous studies have pronounced that the reconciliation improves point forecast accuracy in domestic tourism flow in Australia (\cite{Athanasopoulos2009}, \cite{Hyndman2011}, \cite{WicEtAl2019}).
+	Using an empirical application to forecast Australian domestic tourism flows, we illustrate the usefulness of projection based reconciliation in practice.
+Previous studies have found that reconciliation improves point forecast accuracy in domestic tourism flows for Australia \citep[see for example][]{Athanasopoulos2009, Hyndman2011,WicEtAl2019}.
 However, our motivation in this study is twofold.
-First, we demonstrate the implications of Theorem~\ref{th:distred} by comparing reconciled and base forecasts and in contrast to previous studies we consider individual periods rather than computing averages over a rolling window.
-Second, we demonstrate how the bias correction methods discussed in previous section along with the projection-based reconciliation help to improve the forecast accuracy.
+First, we demonstrate the implications of Theorem~\ref{th:distred} by comparing reconciled and base forecasts.
+In contrast to previous studies we consider individual periods rather than computing averages over a rolling window.
+Second, we demonstrate how the bias correction methods discussed in the previous section along with the projection-based reconciliation help to improve forecast accuracy.
 
@@
 
-	We use ``overnight trips'' across Australia as a measure of domestic tourism flows.
+	We consider ``overnight trips'' across Australia as a measure of domestic tourism flows.
 The data are provided by the National Visitor Survey (NVS) and are collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more.
-We disaggregate Tourism flows into 7 states, 27 zones and 75 regions forming a natural geographical hierarchy that is of interest to tourism operators and policy makers.
+We disaggregate tourism flows into 7 states, 27 zones and 75 regions forming a natural geographical hierarchy that is of interest to tourism operators and policy makers.
 Hence, there are $110$ series across the hierarchy with $75$ bottom-level series.
@@
 
-Figure \ref{fig:Total_TSplots} shows time, sub-series and seasonal plots of the aggregate overnight trips for Australia.
-As is usual with tourism data, overnight these show a strong seasonal pattern.
-Overnight trips peak in January corresponding to the summer vacation season in Australia.
+Figure \ref{fig:Total_TSplots} shows time, sub-series and seasonal plots of the aggregate overnight trips.
+As is usual with tourism data, these show a strong seasonal pattern with peaks observed every January corresponding to the summer vacation season in Australia.
 There are also some lower peaks observed in April, July and October corresponding to school term breaks.
@@
 
-The top panel of Figure \ref{fig:States_Zones_Regs_TSplots} shows time plots for the seven states, hence the first-level of the hierarchy.
-The panels below show some selected series from the second-level zones and the bottom-level regions of the geographical hierarchy.
+The top panel of Figure \ref{fig:States_Zones_Regs_TSplots} shows time plots for the seven states, hence the first-level of the geographical hierarchy.
+The panels below show some selected series from the second-level zones and the bottom-level regions.
 The plots display the diversity of time series features, within but also between levels.
-For example, noticeable at the first-level is the asynchronous seasonal pattern between Northern Territory and the other states.
+For example, noticeable at the first-level is the asynchronous seasonal pattern between the Northern Territory and the other states.
 For the Northern Territory the high tourist season occurs during June-August with July being the peak, while the low season is during December-February.
 This reflects the tropical climate of the Northern Territory, with Australians mostly visiting the North during its dry winter-season rather than the wet summer season.
-Noticeable as we move to the lower levels is the variation in the signal-to-noise ratio, with the regional bottom-level series being noisier compared to the series from levels above.
+Noticeable as we move to the lower levels is the variation in the signal-to-noise ratio, with the regional bottom-level series being much noisier compared to the series from levels above.
 This of course highlights the importance of modelling series at all levels without any loss of valuable information.
@@
 
-    After obtaining the base forecasts these are reconciled using three different methods; OLS reconciliation, WLS reconciliation using variance scaling \todo{George please check} and MinT use a shrinkage estimator for ${\bm W}$.
-Squared forecast errors are computed for each series and aggregated, i.e.
-we compute the loss function described in Section~\ref{sec:orthogonal}.
-We then compute the difference in this loss function between base forecasts and reconciled forecasts, where positive values indicat that reconciled forecasts are more accurate.
+    After obtaining the base forecasts these are reconciled using three different methods; OLS reconciliation, WLS reconciliation using variance scaling and MinT using a shrinkage estimator for ${\bm W}$.
+Squared forecast errors are computed for each series and aggregated across the whole hierarchy, i.e., we compute the loss function described in Section~\ref{sec:orthogonal}.
+We then compute the difference in this loss function between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate.
+We also include bottom-up forecasts in this comparison for completeness.
+
     The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of this measure over each rolling window.
-As the theory predicts, OLS reconciliation always leads to an improvement relative to base forecasts, the entire boxplot for OLS reconciliation is above zero.
-This is not the case for WLS and MinT which for some windows perform worse than base forecasts.
+We only present the results for $h=1$ but the story is identical for the other longer forecast horizons.
+
+    As the theory predicts, OLS reconciliation always leads to an improvement relative to base forecasts.
+The entire boxplot for OLS reconciliation is above zero.
+This is not the case for WLS and MinT which for some windows generate forecasts less accurate than the base forecasts.
+
     The boxplots also demonstrate that OLS reconciliation is more stable than WLS and MinT reconciliation, a result not entirely unsurprising since the latter two methods require estimation of a ${\bm W}$ matrix which in practice is not trivial.
-Nonetheless when averaging over the entire rolling window the MinT estimator performs best on average which is again precisely what the theorem proved in \cite{WicEtAl2019} would suggest.\todo{Get correct results in for figure with boxplots}
+Nonetheless when averaging over the entire rolling window the MinT estimator performs best on average which is again precisely what the theorem proved in \cite{WicEtAl2019} would suggest.
+The average MSE across the entire rolling window of 140 replications are shown in Table \ref{tab:AveraveDifferences}.
 
@@
     	\small
-    	\includegraphics[width = \textwidth]{Figs/OrthVsOblq_Proj_Emp_results.pdf}
-    	\caption{MSE difference between base forecasts and reconciled forecasts over the replications is presented for forecast horizons $h = 1,...,6$.
-Positive values of the difference implies reconciliation improves the forecast accuracy than base forecasts.}\label{fig:BaseVSRecon_Fc}
+    	\includegraphics[width = \textwidth]{Figs/BoxPlot.pdf}
+    	\caption{MSE differences between base forecasts and reconciled forecasts using OLS, MinT and WLS, and also the bottom-up approach for $h = 1$.
+A positive value indicates that the coherent forecasts are an improvement over the base forecasts.
+}\label{fig:BaseVSRecon_Fc}
 \end{figure}
+
+\begin{table}[H]
+	\caption {Average {MSE($\times 10^3$)} across the whole hierarchy and over all 140 replications for h=1.}
+	\label{tab:AveraveDifferences}
+	\centering \tabcolsep=0.4cm
+		\begin{tabular}{lccccc}
+	\toprule
+            & Base & OLS & MinT & WLS & Bottom-up \\
+     MSE    & 4.31 & 4.20 & 4.16 & 4.48 & 5.28 \\
+    \bottomrule
+    \end{tabular}
+\end{table}
 
@@
 			R.method & Biased & Unbiased & Unbiased & Biased & Unbiased & Unbiased \\
-			& & (Method-1) & (Method-2) && (Method-1) &(Method-2)\\
-			\midrule
+			& & (Method-1) & (Method-2) && (Method-1) &(Method-2)\\ \midrule 
 			Base & 12.06 & 11.87 & 12.52 & 12.27 & 139.94 & 13.45\\
-			\hline
 			Bottom-up & 17.37 & 15.47 & 21.58 & 18.06 & 15.76 & 23.33\\
-			\hline
 			OLS & 11.59 & 11.41 & 11.98 & 11.84 & 116.91 & 12.96\\
-			\hline
 			WLS & 15.00 & 13.83 & 17.55 & 15.83 & 14.20 & 19.51\\
-			\hline
 			MinT(Shrink) & 9.36 & $\bm{9.25}$ & 10.35 & 10.27 & $\bm{10.11}$ & 12.43\\
@@
 We have presented results only for one forecast horizon. However, results for other forecast horizons follows the same conclusions.
-
-\begin{figure}
-	\centering
-	\small
-	\includegraphics[width = \textwidth]{Empirical-results/Final-results/Total_FcVsTrue_BoxCox.pdf}
-	\caption{Actual values vs the base forecasts for Total overnight trips follows from Box-Cox transformation}\label{fig:Total_FcVsTrue_BoxCox}
-\end{figure}
 

### 2019-09-03 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Last night's changes

@@
 
-\clearpage
-
     \subsection{Comparison to Base Forecasts}\label{sec:comparebase}
@@
     The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of this measure over each rolling window.
-We only present the results for $h=1$ but the story is identical for the other longer forecast horizons.
+We only present the results for $h=1$ but the results and conclusions that follow are almost identical for the other longer forecast horizons.
+We do not present these here to save space but they are available upon request.
 
@@
 This is not the case for WLS and MinT which for some windows generate forecasts less accurate than the base forecasts.
-
 The boxplots also demonstrate that OLS reconciliation is more stable than WLS and MinT reconciliation, a result not entirely unsurprising since the latter two methods require estimation of a ${\bm W}$ matrix which in practice is not trivial.
 Nonetheless when averaging over the entire rolling window the MinT estimator performs best on average which is again precisely what the theorem proved in \cite{WicEtAl2019} would suggest.
-The average MSE across the entire rolling window of 140 replications are shown in Table \ref{tab:AveraveDifferences}.
+The average MSEs across the entire rolling window of 140 replications are shown in Table \ref{tab:AveraveDifferences}.
 
@@
     	\caption{MSE differences between base forecasts and reconciled forecasts using OLS, MinT and WLS, and also the bottom-up approach for $h = 1$.
-A positive value indicates that the coherent forecasts are an improvement over the base forecasts.
-}\label{fig:BaseVSRecon_Fc}
+A positive value indicates that the coherent forecasts are an improvement over the base forecasts.} \label{fig:BaseVSRecon_Fc}
 \end{figure}
@@
 \begin{table}[H]
-	\caption {Average {MSE($\times 10^3$)} across the whole hierarchy and over all 140 replications for h=1.}
-	\label{tab:AveraveDifferences}
+	\caption {Average {MSE($\times 10^3$)} over all 140 rolling window replications for $h=1$.} \label{tab:AveraveDifferences}
 	\centering \tabcolsep=0.4cm
@@
             & Base & OLS & MinT & WLS & Bottom-up \\
-     MSE    & 4.31 & 4.20 & 4.16 & 4.48 & 5.28 \\
+     MSE    & 4.31 & 4.20 & \textbf{4.16} & 4.48 & 5.28 \\
     \bottomrule
@@
 \end{equation}
-
 We first set $\lambda=0$ and hence consider only a log transformation.
 For the second more general Box-Cox transformation we select $\lambda$ using the ``Guerrero'' method \citep{guerrero1993time} implemented in the \verb|BoxCox.lambda()| function in the \verb|forecast| package in R \citep{Rforecast}.
-As observations with zero value exist in some of the bottom-level series, before transforming we add a constant (more specifically $1$) to each series.
+In order to avoid extreme and volatile transformations we restrict $\lambda \in (0.5,2)$.
+As zero observations exist in some of the bottom-level series, before transforming we add a constant (more specifically $1$) to each series.
 This overcomes the challenge of undefined transformed values for zero observations when we specifically implement the log transformation or when $\lambda$ is selected to be zero by the ``Guerrero'' method.
@@
 
-The forecasts are then back-transformed by simply reversing the Box-Cox transformation using
-
+The forecasts are then back-transformed by simply reversing the Box-Cox transformation using,
 \begin{equation} \label{eq:BoxCox_back-transformation}
@@
 	\begin{cases}
-	\exp({\hat{w}_{t+h|t}}) & \text{if}~\lambda = 0; \\
+	\exp({\hat{w}_{t+h|t}}) & \text{if}~\lambda = 0, \\
 	(\lambda \hat{w}_{t+h|t} + 1)^{1/\lambda}  & \text{otherwise.}
@@
 \end{equation}
-
 These back-transformed forecasts are potentially biased as they are not the mean of the forecast distribution but the median (assuming that the distribution of the transformed space is symmetric).
 Hence, the reconciled forecasts that follow from these forecasts will also be biased.
-This is the exact scenario that we want to demonstrate in this study and we next move to our proposed solution of bias correcting the base forecasts before reconciling for which we explore two scenarios.
+We refer to these as ``Biased'' forecasts in the results that follow.
+This is the exact scenario we want to demonstrate in this study and we next move to our proposed solution of bias correcting the base forecasts before reconciling for which we explore two scenarios.
 
@@
 	\begin{cases}
-	\exp({\hat{w}_{t+h|t}})[1+\frac{\sigma_h^2}{2}] & \text{if}~\lambda = 0; \\
+	\exp({\hat{w}_{t+h|t}})[1+\frac{\sigma_h^2}{2}] & \text{if}~\lambda = 0, \\
 	(\lambda \hat{w}_{t+h|t} + 1)^{1/\lambda}[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda \hat{w}_{t+h|t} + 1)^2}]       & \text{if}~\lambda \ne 0,
@@
 We refer to this as Method-1 in the results that follow.
+The second scenario of bias adjustment we explore is using the in-sample forecast error mean of the biased forecasts to adjust the out-of-sample forecasts.
+We refer to this as Method-2 in the results that follow.
 
-The second scenario of bias adjustment we explore is using the in-sample forecast error mean of the biased forecasts to adjust the out of sample forecasts.
-We refer to this a Method-2 in the results that follow.
+Using the three sets of base forecasts for each transformation, we generate coherent forecasts using the bottom-up approach but also implementing OLS, WLS and MinT reconciliation projections and compare the results for when the base forecasts are biased and bias-adjusted (unbiased).
+Table \ref{tab:Results_MSE} presents the results over the $140$ rolling window replications for $1$-step-ahead forecasts.
+Note that the conclusions that follow extend almost identically to longer forecast horizons.
+We do not present these here to save space but they are available upon request.
 
-Using the three sets of base forecasts we generate coherent forecasts using the bottom-up approach but also implementing OLS, WLS and MinT reconciliation projections and compare the results for when the base forecasts are biased and bias-adjusted (unbiased).
-We discuss the results next.
+Recall that reconciliation approaches via projections preserve unbiasedness in the reconciled forecasts iff the base forecasts are unbiased.
+Hence, the two columns labelled ``Biased'' contain results for biased base but also reconciled forecasts.
+Using Method-1 for first bias adjusting the base forecasts and then reconciling, results in forecast improvements for all methods for both the log and the Box-Cox transformation induced bias.
+In this case MinT returns the lowest MSE across all forecasts.
+Notice that the ``Box-Cox biased'' base forecasts carry a higher bias compared to the ``log biased'' base forecasts.
+Even for these MinT reconciliation of bias adjusted base forecasts generates very accurate forecasts, almost as accurate as the forecasts that come from the less biased log transformation.
 
-\subsection{Results and discussion}
-
-%	Mean Squared Error (MSE) is used to measure the forecast accuracy and results are presented in Table \ref{tab:Results_MSE}.
-Recall that projections preserve the unbiasedness in reconciled forecasts only if the base forecasts are unbiased.
-As a consequence, the reconciled forecasts follow from the biased base forecasts will also be biased.
-We can see from the results that unbiased-reconciled forecasts from MinT(Shrink) and WLS are better than that of biased-reconciled forecasts although the unbiased-base forecasts are not necessarily better than the biased-base forecasts.
-Furthermore, unbiased MinT reconciled forecasts are outperforming all biased and unbiased forecasts.
-These results are true for all forecast horizons.
+In contrast to the results from using Method-1 for bias adjustment before reconciliation, using Method-2 has an adverse effect on the forecast accuracy of the reconciled forecasts.
+In this case the reconciled unbiased forecasts are less accurate than the biased reconciled forecasts.
+This reflects the fact and sends the warning that implementing an inappropriate bias adjustment, in this case using an additive factor rather than a multiplicative factor, will hinder forecast accuracy and extra care must be taken in this bias adjustment procedure.
 
 \begin{table}
-	\caption {Average {MSE($\times 10^3$)} of base and reconciled $1$-step-ahead point forecasts are presented for log transformation and Box-Cox transformation.
-Unbiased(Method-1) follows from the bias adjustment via Taylor's de-biasing factor whereas Unbiased(Method-2) follows from residual mean adjustment.}
+	\caption {Average {MSE($\times 10^3$)} of $1$-step-ahead point forecasts from log and Box-Cox transformed series.
+Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in  \eqref{eq:BoxCox_back-transformation} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
 	\label{tab:Results_MSE}
 	\centering
-	\resizebox{\linewidth}{!}{
-		\begin{tabular}{@{}lcccccc@{}}
+		\begin{tabular}{lcccccc}
 			\toprule
@@
 			\cmidrule(lr){2-4} \cmidrule(lr){5-7}
-			R.method & Biased & Unbiased & Unbiased & Biased & Unbiased & Unbiased \\
+			Method & Biased & Unbiased & Unbiased & Biased & Unbiased & Unbiased \\
 			& & (Method-1) & (Method-2) && (Method-1) &(Method-2)\\ \midrule
-			Base & 12.06 & 11.87 & 12.52 & 12.27 & 139.94 & 13.45\\
-			Bottom-up & 17.37 & 15.47 & 21.58 & 18.06 & 15.76 & 23.33\\
-			OLS & 11.59 & 11.41 & 11.98 & 11.84 & 116.91 & 12.96\\
-			WLS & 15.00 & 13.83 & 17.55 & 15.83 & 14.20 & 19.51\\
-			MinT(Shrink) & 9.36 & $\bm{9.25}$ & 10.35 & 10.27 & $\bm{10.11}$ & 12.43\\
+			Base      & 4.47 & 4.43 & 4.51 & 4.59 & 4.52 & 4.78\\
+			OLS       & 4.34 & 4.31 & 4.36 & 4.46 & 4.40 & 4.63\\
+			MinT      & 4.32 & \textbf{4.16} & 4.61 & 4.29 & \textbf{4.17} & 4.54\\
+			WLS       & 4.82 & 4.38 & 5.43 & 4.77 & 4.42 & 5.23\\
+			Bottom-up & 6.36 & 5.26 & 8.06 & 6.21 & 5.31 & 7.46\\
 			\bottomrule
 		\end{tabular}	
-	}
-
 \end{table}
-
-Table \ref{tab:Results_MSE} presents the Mean Squared Error (MSE) over the $140$ replications for $1$-step-ahead forecasts.
-Note that the conclusion that follow extend almost identically to forecast horizons $2-6$.
-We do not present these here to save space but they are available upon request.
-
-General findings:
-
-- Bias adjusting using Method 1, i.e., a proper method improves forecast accuracy.
-- Bias adjusting using Method 2, does not.
-The transformations we consider here are multiplicative type transformations - the in-sample residual adjustment is an additive adjustment hence it does not help.
-
-\textcolor{red}{I have stopped here. Will continue after we have all results.}
-
-Let us first consider the results from log transformation.
-We see that the unbiased forecasts from Method-1 has less MSE compared to the biased forecasts in base level.
-This holds for all reconciled forecasts as well.
-It implies that the bias correction has improved the forecast accuracy.
-Further, unbiased reconciled forecasts from OLS and MinT perform better than the base forecasts.
-Moreover, Unbiased MinT reconciled forecasts are outperforming.
-We also note that the bias correction via Method-2 has not necessarily work well in this empirical example.
-
-Now turning to the results from Box-Cox transformation, we see that the bias correction via Method-1 has worsen the base forecasts.
-The same result holds for OLS reconciled forecasts as well.
-We also observed that this has happened because the bias correction is doing worst for some replications in ``Total" series as depicted in Figure \ref{fig:Total_FcVsTrue_BoxCox}.
-\textcolor{red}{This because for these replications the selected model has a drift term with a very large standard error.
-This will blow up the bias-adjusted forecasts.}
-
-However reconciled forecast from, Bottom-up, WLS or MinT has mitigate the effect from this unusual result in unbiased base forecasts. Most importantly, Unbiased MinT is outperforming all forecasts.
-
-We have presented results only for one forecast horizon. However, results for other forecast horizons follows the same conclusions.
-
-%%%%%%%%%%%%%%%%%%%
-
-%\begin{table}
-%	\caption {\textcolor{red}{RESULTS FROM LOG TRANSFORMATION
-%			Average {MSE($\times 10^3$)} of base and reconciled point forecasts at forecasts horizons $h=1,...,6$ are presented.
-Bias and unbiased columns represent the results for biased-base/biased-reconciled and unbiased-base/unbiased-reconciled forecasts respectively.
-Comparisons can be made across biased vs unbiased forecasts as well as base vs reconciled forecasts.}}
-%	\label{tab:Results_MSE_LogTrans}
-%	\centering\tabcolsep=0.001cm
-%	\small
-%	\resizebox{\linewidth}{!}{
-%		\begin{tabular}{@{}lSSS@{}}
-%		
-%		R.method & Biased & Unbiased (Method-1) & Unbiased (Method-2)\\
-%		\midrule
-%		Base & 12.06 & 11.87 & 12.52\\
-%		\hline
-%		Bottom-up & 17.37 & 15.47 & 21.58\\
-%		\hline
-%		MinT(Shrink) & 9.36 & 9.25 & 10.35\\
-%		\hline
-%		OLS & 11.59 & 11.41 & 11.98\\
-%		\hline
-%		WLS & 15.00 & 13.83 & 17.55 \\
-%		\bottomrule
-%	\end{tabular}
-%}
-%
-%\end{table}
-%
-%\begin{table}
-%	\caption {\textcolor{red}{RESULTS FROM BOXCOX TRANSFORMATION
-%			Average {MSE($\times 10^3$)} of base and reconciled point forecasts at forecasts horizons $h=1,...,6$ are presented.
-Bias and unbiased columns represent the results for biased-base/biased-reconciled and unbiased-base/unbiased-reconciled forecasts respectively.
-Comparisons can be made across biased vs unbiased forecasts as well as base vs reconciled forecasts.}}
-%	\label{tab:Results_MSE_BoxCoxTrans}
-%	\centering\tabcolsep=0.08cm
-%	\resizebox{\linewidth}{!}{
-%		\begin{tabular}{@{}lSSS@{}}
-%			
-%			R.method & Biased & Unbiased (Method-1) & Unbiased (Method-2)\\
-%			\midrule
-%			Base & 12.27 & 139.94 & 13.45\\
-%			\hline
-%			Bottom-up & 18.06 & 15.76 & 23.33\\
-%			\hline
-%			MinT(Shrink) & 10.27 & 10.11 & 12.43\\
-%			\hline
-%			OLS & 11.84 & 116.91 & 12.96\\
-%			\hline
-%			WLS & 15.83 & 14.20 & 19.51\\		
-%			\bottomrule
-%		\end{tabular}
-%	}
-%	
-%\end{table}
-%	
-%	\begin{figure}
-%		\centering
-%		\small
-%		\includegraphics[width = \textwidth]{Empirical-results/Final-results/SS_MSE_Results.pdf}
-%		\caption{\textcolor{red}{include caption}}\label{fig:MSE_SkillScore}
-%	\end{figure}
-%
 

### 2019-09-03 Hierarchical-forecast-reconciliation/Appendix.tex
Trying again

@@
+\subsection{Australian Tourism Data}
 
-	\begin{table} 
+	\begin{table}[H]
 		\caption{Geographical hierarchy of Australian tourism flow}\label{table:A1}
@@
 				\toprule
-				\multicolumn{3}{c}{\textbf{Level 0 - Total}}   &  &  \multicolumn{3}{l}{\textit{Zones cont.}}   &  & \multicolumn{3}{l}{\textit{Regions cont.}} \\
+				\multicolumn{3}{c}{\textbf{Level 0 - Total}}    &&  \multicolumn{3}{l}{\textit{Zones cont.}}   &  & \multicolumn{3}{l}{\textit{Regions cont.}} \\
 				\cmidrule(lr){1-3}
-				1 & {\text{Tot}} & {Australia} &  & 48  & AED & Blue Mountains && 99 & FAA & Hobert and South\\
+				1 & {\text{Tot}} & {Australia}                  && 48  & AED & Blue Mountains && 99 & FAA & Hobert and South\\
 				\cmidrule(lr){1-3}
-				\multicolumn{3}{c}{\textbf{Level 1 - States}}  &  & 49  & AFA & Canberra  && 100 & FBA & East Coast\\
+				\multicolumn{3}{c}{\textbf{Level 1 - States}}               && 49  & AFA & Canberra  && 100 & FBA & East Coast\\
 				\cmidrule(lr){1-3}

### 2019-09-03 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Final revision George

@@
      	\small
-     	\resizebox{\linewidth}{!}{
+     	\resizebox{0.8\linewidth}{!}{
      		\input{Figs/3D_hierarchy}
@@
 		Since, $\bm{y}_{t+h|t},\tilde{\bm{y}}_{t+h|t}\in\mathfrak{s}$ and since the projection is orthogonal, by Pythagoras' theorem
-		\begin{equation} \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|^2=\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2+\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|^2.
+		\begin{equation} \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|^2=\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|^2+\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2.
 		\end{equation}
@@
 \cite{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by an oblique projection with a particular choice of $\bm{W}$.
-This choice is that $\bm{W}$ should be the forecast error covariance matrix where errors come from using the base forecasts.
+Their choice is that $\bm{W}$ should be the forecast error covariance matrix where errors come from using the base forecasts.
 Although the base forecast error covariance matrix is unknown, it can be estimated using in-sample errors.
@@
 One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.
-An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection.
+An oblique projection of the blue point back along the direction of $\bm{R}$, yields a reconciled forecast closer to the target, especially compared to an orthogonal projection.
 Panel (c) shows the orthogonal projection of every potential base forecast onto the coherent subspace.
@@
 		\small
-		\resizebox{\linewidth}{!}{
+		\resizebox{0.8\linewidth}{!}{
 			\input{Figs/Schem_3D}
@@
 	We consider ``overnight trips'' across Australia as a measure of domestic tourism flows.
-The data are provided by the National Visitor Survey (NVS) and are collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more.
-We disaggregate tourism flows into 7 states, 27 zones and 75 regions forming a natural geographical hierarchy that is of interest to tourism operators and policy makers.
+The data are provided by the National Visitor Survey and are collected through telephone interviews from an annual sample of $120,000$ Australian residents aged $15$ years or more.
+We disaggregate tourism flows into 7 states, 27 zones and 75 regions forming a natural geographical hierarchy that is of interest to tourism operators and policy makers amongst others.
 Hence, there are $110$ series across the hierarchy with $75$ bottom-level series.
@@
 For each series the ARIMA model minimising AICc is chosen using the \verb|auto.arima()| function in the \verb|forecast| package.
-Using these fitted models, base forecasts are produced for $h=1$ to $6$-steps ahead for each series in the hierarchy.
+Using these fitted models, base forecasts are produced for $h=1$ to $12$-steps ahead for each series in the hierarchy.
 This is first carried out with a training sample of $100$ observations, i.e., Jan-$1998$ to Apr-$2006$.
 The training window is then rolled forward one observation at a time until the end of the sample.
-This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $135~6$-steps-ahead forecasts available for forecast evaluation.
+This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $129~12$-steps-ahead forecasts available for forecast evaluation.
 
-    After obtaining the base forecasts these are reconciled using three different methods; OLS reconciliation, WLS reconciliation using variance scaling and MinT using a shrinkage estimator for ${\bm W}$.
-Squared forecast errors are computed for each series and aggregated across the whole hierarchy, i.e., we compute the loss function described in Section~\ref{sec:orthogonal}.
+    After obtaining the base forecasts these are reconciled using three different projection methods: OLS reconciliation, MinT using a shrinkage estimator for ${\bm W}$ and WLS reconciliation using variance scaling.
+Squared forecast errors are computed for each series and aggregated across the entire hierarchy, i.e., we compute the loss function described in Section~\ref{sec:orthogonal}.
 We then compute the difference in this loss function between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate.
@@
 The entire boxplot for OLS reconciliation is above zero.
-This is not the case for WLS and MinT which for some windows generate forecasts less accurate than the base forecasts.
-The boxplots also demonstrate that OLS reconciliation is more stable than WLS and MinT reconciliation, a result not entirely unsurprising since the latter two methods require estimation of a ${\bm W}$ matrix which in practice is not trivial.
-Nonetheless when averaging over the entire rolling window the MinT estimator performs best on average which is again precisely what the theorem proved in \cite{WicEtAl2019} would suggest.
-The average MSEs across the entire rolling window of 140 replications are shown in Table \ref{tab:AveraveDifferences}.
+This is not the case for MinT and WLS which for some windows generate forecasts less accurate than the base forecasts.
+The boxplots also demonstrate that OLS reconciliation is more stable than MinT and WLS reconciliation, a result not entirely unsurprising since the latter two methods require estimation of a ${\bm W}$ matrix which in practice is not trivial.
+Nonetheless when averaging over the entire rolling window the MinT estimator performs best on average, which is again precisely what the theorem proved in \cite{WicEtAl2019} would suggest.
+The average MSE values across the entire rolling window of 140 replications are shown in Table \ref{tab:AveraveDifferences}.
 
@@
 
-\begin{equation} \label{eq:BoxCox_transformation}
+\begin{equation*} \label{eq:BoxCox_transformation}
 	w_t =
@@
 	\end{cases}
-\end{equation}
+\end{equation*}
 We first set $\lambda=0$ and hence consider only a log transformation.
@@
 The \verb|auto.arima()| function in the \verb|forecast| package is used to choose the best model that minimises the AICc.
-Using the fitted models, forecasts are produced for $h=1$ to $6$-steps ahead for each series in the hierarchy.
+Using the fitted models, forecasts are produced for $h=1$ to $12$-steps ahead for each series in the hierarchy.
+The same rolling window described in Section \ref{sec:comparebase} is used here as well.
 
@@
 Hence, the reconciled forecasts that follow from these forecasts will also be biased.
-We refer to these as ``Biased'' forecasts in the results that follow.
+We refer to these as ``Biased'' base forecasts in the results that follow.
 This is the exact scenario we want to demonstrate in this study and we next move to our proposed solution of bias correcting the base forecasts before reconciling for which we explore two scenarios.
@@
 
-Using the three sets of base forecasts for each transformation, we generate coherent forecasts using the bottom-up approach but also implementing OLS, WLS and MinT reconciliation projections and compare the results for when the base forecasts are biased and bias-adjusted (unbiased).
+Using the three sets of base forecasts from each of the two transformations, we generate coherent forecasts implementing OLS, MinT and WLS reconciliation projections, and also the bottom-up approach and compare the results for when the base forecasts are biased and bias-adjusted, i.e., unbiased.
 Table \ref{tab:Results_MSE} presents the results over the $140$ rolling window replications for $1$-step-ahead forecasts.
-Note that the conclusions that follow extend almost identically to longer forecast horizons.
+We note that as was the case with Section \ref{sec:comparebase} the conclusions that follow extend almost identically to longer forecast horizons.
 We do not present these here to save space but they are available upon request.
@@
 
-In contrast to the results from using Method-1 for bias adjustment before reconciliation, using Method-2 has an adverse effect on the forecast accuracy of the reconciled forecasts.
+In contrast to the results from using Method-1 for bias adjusting before reconciliation, using Method-2 has an adverse effect on the forecast accuracy of the reconciled forecasts.
 In this case the reconciled unbiased forecasts are less accurate than the biased reconciled forecasts.
-This reflects the fact and sends the warning that implementing an inappropriate bias adjustment, in this case using an additive factor rather than a multiplicative factor, will hinder forecast accuracy and extra care must be taken in this bias adjustment procedure.
+This reflects the fact and sends the warning that implementing inappropriate bias adjustment, in this case using an additive rather than a multiplicative factor, will hinder forecast accuracy and extra care must be taken in this bias adjustment procedure.
 
@@
 	\caption {Average {MSE($\times 10^3$)} of $1$-step-ahead point forecasts from log and Box-Cox transformed series.
-Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in  \eqref{eq:BoxCox_back-transformation} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
+Biased denotes forecasts from simply reversing the transformation via \eqref{eq:BoxCox_back-transformation}.
+Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in \eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
 	\label{tab:Results_MSE}
@@
 Although much more challenging, it is still possible define reconciled forecasts in terms of projections onto a manifold.
-Second, since we have established that the concept of bottom-level series is not crucial in forecast reconciliation an open question is whether is may be better to construct base forecasts of linear combinations of the time series rather than the time series themselves.
+Second, since we have established that the concept of bottom-level series is not crucial in forecast reconciliation an open question is whether it may be better to construct base forecasts of linear combinations of the time series rather than the time series themselves.
 Finally, the geometric interpretations of hierarchical forecast reconciliation facilitates an extension into a probabilistic framework, an issue that we investigate in a separate paper.

### 2019-09-03 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Small changes

@@
 		\title{\bf Forecast Reconciliation: A geometric view with new insights on bias correction.}
-		\author{Anastasios Panagiotelis\thanks{
-				The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.  We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
+		\author{Anastasios Panagiotelis\\
 			Department of Econometrics and Business Statistics,\\
@@
 			and \\
-			George Athanasopoulos\\
+			George Athanasopoulos\thanks{Corresponding Author.
+The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.
+We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
 			Department of Econometrics and Business Statistics,\\

### 2019-09-04 Hierarchical-forecast-reconciliation/Appendix.tex
Adding more references and adjusting table in Appendix

@@
 			\toprule
-				\multicolumn{3}{c}{\textbf{Level 0 - Total}}    &&  \multicolumn{3}{l}{\textit{Zones cont.}}   &  & \multicolumn{3}{l}{\textit{Regions cont.}} \\
+			\multicolumn{3}{c}{\textbf{Level 0 - Total}}    &&  \multicolumn{3}{l}{\textit{Regions cont.}}   &  & \multicolumn{3}{l}{\textit{Regions cont.}} \\
 			\cmidrule(lr){1-3}
-				1 & {\text{Tot}} & {Australia}                  && 48  & AED & Blue Mountains && 99 & FAA & Hobert and South\\
+			1 & {\text{Tot}} & {Australia} &&  37	& AAB & Central Coast && 76  & CBD & Mackay   \\
 			\cmidrule(lr){1-3}
-				\multicolumn{3}{c}{\textbf{Level 1 - States}}               && 49  & AFA & Canberra  && 100 & FBA & East Coast\\
+			\multicolumn{3}{c}{\textbf{Level 1 - States}} && 38  & ABA & Hunter && 77  & CCA & Whitsundays\\
 			\cmidrule(lr){1-3}
-				2 & A & NSW 				&  & 50  & BAA & Melbourne      && 101 & FBB & Launceston, Tamar \& North\\
-				3 & B & Victoria 			&  & 51  & BAB & Peninsula      && 102 & FCA & North West\\
-				4 & C & Queensland 			&  & 52  & BAC & Geelong        && 103 & FCB& Wilderness West\\
-				5 & D & South Australia     &  & 53  & BBA & Western        && 104 & GAA& Darwin\\
-				6 & E & Western Australia   &  & 54  & BCA & Lakes          && 105 & GAB& Kakadu Arnhem\\
-				7 & F & Tasmania   			&  & 55  & BCB & Grippsland     && 106 & GAC& Katherine Daly\\
-				8 & G & Northern Territory &  &  56  & BCD & Phillip Island && 107 & GBA& Barkly\\
+			2 & A & NSW 				&  & 39  & ABB & North Coast NSW   && 78  & CCB & Northern  \\
+			3 & B & Victoria 			&  & 40  & ACA & South Coast  && 79  & CCC & Tropical North Queensland \\
+			4 & C & Queensland 			&  & 41  & ADA & Snowy Mountains &&80  & CDA & Darling Downs   \\
+			5 & D & South Australia     &  & 42  & ADB & Capital Country && 81  & CDB & Outback  \\
+			6 & E & Western Australia   &  & 43  & ADC & The Murray   && 82  & DAA & Adelaide\\
+			7 & F & Tasmania   			&  & 44  & ADD & Riverina  && 83  & DAB & Barossa\\
+			8 & G & Northern Territory  &  & 45  & AEA & Central NSW &&  84  & DAC & Adelaide Hills \\
 			\cmidrule(lr){1-3}
-				\multicolumn{3}{c}{\textbf{Level 2 - Zones}}  &  &  57  & BDA & Central Murray && 108 & GBB& Lasseter\\
+			\multicolumn{3}{c}{\textbf{Level 2 - Zones}}  &  &  46  & AEB & New England North West    &&85  & DBA & Limestone Coast\\
 			\cmidrule(lr){1-3}
-				9 	& AA & Metro NSW 	  	   	&  & 58  & BDB & Goulburn && 109 & GBC& Alice Springs\\
-				10 	& AB & North Coast NSW 	   	&  & 59  & BDC & High Country && 110 & GBD& MacDonnell\\
-				11	& AC & South Coast NSW	   	&  & 60  & BDD & Melbourne East &&&&\\
-				12	& AD & South NSW 			&  & 61  & BDE & Upper Yarra &&&& \\
-				13	& AE & North NSW 			&  & 62  & BDF & Murray East &&&&\\
-				14	& AC & ACT					&  & 63  & BEA & Wimmera+Mallee &&&&\\
-				15	& BA & Metro VIC			&  & 64  & BEB & Western Grampians &&&&\\ 		
-				16	& BB & West Coast VIC		&  & 65  & BEC & Bendigo Loddon &&&&\\
-				17	& BC & East Coast VIC		&  & 66  & BED & Macedon &&&&\\
-				18	& BC & North East VIC		&  & 67  & BEE & Spa Country &&&&\\
-				19	& BD & North West VIC		&  & 68  & BEF & Ballarat &&&&\\
-				20  & CA & Metro QLD			&  & 69  & BEG & Central Highlands &&&&\\
-				21  & CB & Central Coast QLD	&  & 70  & CAA & Gold Coast &&&&\\
-				22  & CC & North Coast QLD		&  & 71  & CAB & Brisbane &&&&\\
-				23  & CD & Inland QLD			&  & 72  & CAC & Sunshine Coast &&&&\\
-				24	& DA & Metro SA				&  & 73  & CBA & Central Queensland &&&&\\	
-				25	& DB & South Coast SA		&  & 74  & CBB & Bundaberg &&&&\\	
-				26	& DC & Inland SA			&  & 75  & CBC & Fraser Coast &&&&\\	
-				27	& DD & West Coast SA		&  & 76  & CBD & Mackay &&&&\\
+			9 	& AA & Metro NSW 	  	   	&  & 47  & AEC & Outback NSW   && 86  & DBB & Fleurieu Peninsula\\
+			10 	& AB & North Coast NSW 	   	&  & 48  & AED & Blue Mountains  && 87  & DBC & Kangaroo Island\\
+			11	& AC & South Coast NSW	   	&  & 49  & AFA & Canberra   &&88  & DCA & Murraylands \\
+			12	& AD & South NSW 			&  & 50  & BAA & Melbourne &&89  & DCB & Riverland\\
+			13	& AE & North NSW 			&  & 51  & BAB & Peninsula    &&90  & DCC & Clare Valley\\
+			14	& AC & ACT					&  &  52  & BAC & Geelong  &&91  & DCD & Flinders Range and Outback \\
+			15	& BA & Metro VIC			&  &  53  & BBA & Western   &&92  & DDA & Eyre Peninsula\\ 		
+			16	& BB & West Coast VIC		&  &  54  & BCA & Lakes  && 93  & DDB & Yorke Peninsula\\
+			17	& BC & East Coast VIC		&  &  55  & BCB & Grippsland    &&94  & EAA & Australia's Coral Coast\\
+			18	& BC & North East VIC		&  &  56  & BCD & Phillip Island   && 95  & EAB & Experience Perth \\
+			19	& BD & North West VIC		&  &  57  & BDA & Central Murray    &&96  & EAC & Australia's South West\\
+			20  & CA & Metro QLD			&  & 58  & BDB & Goulburn    &&97  & EBA & Australia's North West \\
+			21  & CB & Central Coast QLD	&  & 59  & BDC & High Country   &&98  & ECA & Australia's Golden Outback\\
+			22  & CC & North Coast QLD		&  &  60  & BDD & Melbourne East &&99 & FAA & Hobert and South\\
+			23  & CD & Inland QLD			&  &   61  & BDE & Upper Yarra &&100 & FBA & East Coast\\
+			24	& DA & Metro SA				&  & 62  & BDF & Murray East  && 101 & FBB & Launceston, Tamar \& North\\	
+			25	& DB & South Coast SA		&  &  63  & BEA & Wimmera+Mallee &&102 & FCA & North West\\	
+			26	& DC & Inland SA			&  & 64  & BEB & Western Grampians &&103 & FCB& Wilderness West\\	
+			27	& DD & West Coast SA		&  &65  & BEC & Bendigo Loddon  &&104 & GAA& Darwin\\
 
-				28	& EA & West Coast WA 	& & 77  & CCA & Whitsundays &&&&\\	
-				29	& EB & North WA			& & 78  & CCB & Northern &&&&\\	
-				30	& EC & South WA 		& & 79  & CCC & Tropical North Queensland &&&&\\	
-				31	& FA & South TAS		& & 80  & CDA & Darling Downs &&&&\\
-				32	& FB & North East TAS	& & 81  & CDB & Outback &&&&\\	
-				33	& FC & North West TAS	& & 82  & DAA & Adelaide &&&&\\
-				34	& GA & North Coast NT	& & 83  & DAB & Barossa &&&&\\
-				35	& GB & Central NT		& & 84  & DAC & Adelaide Hills &&&&\\
+			28	& EA & West Coast WA 	& &  66  & BED & Macedon    &&105 & GAB& Kakadu Arnhem\\	
+			29	& EB & North WA			& &  67  & BEE & Spa Country   && 106 & GAC& Katherine Daly\\	
+			30	& EC & South WA 		& &   68  & BEF & Ballarat     &&107 & GBA& Barkly\\	
+			31	& FA & South TAS		& &  69  & BEG & Central Highlands  &&108 & GBB& Lasseter\\
+			32	& FB & North East TAS	& & 70  & CAA & Gold Coast  &&109 & GBC& Alice Springs\\	
+			33	& FC & North West TAS	& & 71  & CAB & Brisbane  &&110 & GBD& MacDonnell\\
+			34	& GA & North Coast NT	& & 72  & CAC & Sunshine Coast &&\\
+			35	& GB & Central NT		& &  73  & CBA & Central Queensland      &&\\
 			\cmidrule(lr){1-3}
-				\multicolumn{3}{c}{\textbf{Level 2 - Regions}} & & 85  & DBA & Limestone Coast &&&&\\
+			\multicolumn{3}{c}{\textbf{Level 2 - Regions}} & & 74  & CBB & Bundaberg    &&\\
 			\cmidrule(lr){1-3}
-				36	& AAA & Sydney 			& 	& 86  & DBB & Fleurieu Peninsula &&&&\\
-				37	& AAB & Central Coast	&	& 87  & DBC & Kangaroo Island &&&&\\
-				38  & ABA & Hunter 			& 	& 88  & DCA & Murraylands &&&&\\
-				39  & ABB & North Coast NSW & 	& 89  & DCB & Riverland &&&&\\
-				40  & ABC & Hunter			& 	& 90  & DCC & Clare Valley &&&&\\
-				41  & ACA & South Coast		& 	& 91  & DCD & Flinders Range and Outback &&&&\\
-				42  & ADA & Snowy Mountains & 	& 92  & DDA & Eyre Peninsula &&&&\\
-				43  & ADB & Capital Country & 	& 93  & DDB & Yorke Peninsula &&&&\\
-				44  & ADC & The Murray 		& 	& 94  & EAA & Australia's Coral Coast &&&&\\
-				45  & ADD & Riverina 		& 	& 95  & EAB & Experience Perth &&&&\\
-				45  & AEA & Central NSW 	& 	& 96  & EAC & Australia's South West &&&&\\
-				46  & AEB & New England North West &  & 97  & EBA & Australia's North West &&&&\\
-				47  & AEC & Outback NSW & & 98  & ECA & Australia's Golden Outback &&&&\\
+			36	& AAA & Sydney 			& 	& 75  & CBC & Fraser Coast &&\\
+
 			\bottomrule

### 2019-09-04 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Adding more references and adjusting table in Appendix

@@
 
-	Multivariate time series following an aggregation structure arise in many disciplines such as manufacturing, engineering, marketing and medicine\todo{include references}.
+	Multivariate time series following an aggregation structure arise in many sectors such as retail, energy, insurance, health and welfare and economics \citep{Karmy2019, Taieb2017, Almeida2016, JeoEtAl2019, Mahkya2017, LiTan2019, Shang2017}.
 Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making.
@@
 The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts.
-This approach and later modifications have subsequently been shown to outperform bottom-up and top-down approaches in a variety of empirical settings\todo{references}.
+This approach and later modifications have subsequently been shown to outperform bottom-up and top-down approaches in a variety of empirical settings \citep{Hyndman2016, Athanasopoulos2009, Shang2017}.
 
@@
 This yields $\bm{S}\bm{G}\bm{S}\bm{G}=\bm{S}\bm{G}$ which in turn implies idempotence since $(\bm{S}\bm{G})^2=\bm{S}\bm{G}$.
+
 	\input{Appendix}

### 2019-09-04 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added abstract

@@
 
-	\begin{abstract} TBC
-		%  Forecast reconciliation involves adjusting forecasts to ensure coherence with aggregation constraints.
-We extend this concept from point forecasts to probabilistic forecasts by redefining forecast reconciliation in terms of linear functions in general, and projections more specifically.
-New theorems establish that the true predictive distribution can be recovered in the elliptical case by linear reconciliation, and general conditions are derived for when this is a projection.
-A geometric interpretation is also used to prove two new theoretical results for point forecasting; that reconciliation via projection both preserves unbiasedness and dominates unreconciled forecasts in a mean squared error sense.
-Strategies for forecast evaluation based on scoring rules are discussed, and it is shown that the popular log score is an improper scoring rule with respect to the class of unreconciled forecasts when the true predictive distribution coheres with aggregation constraints.
-Finally, evidence from a simulation study shows that reconciliation based on an oblique projection, derived from the MinT method of \citet{Wickramasuriya2017} for point forecasting, outperforms both reconciled and unreconciled alternatives.
+	\begin{abstract} 
+		A geometric interpretation is developed for so-called {\em reconciliation} methodologies which are used to forecast time series that adhere to known linear constraints.
+In particular, a general framework is established nesting many existing popular reconciliation methods within the class of {\em projections}.
+This interpretation facilitates the derivation of novel results that explain why and how reconciliation via projection is guaranteed to improve forecasts with respect to a specific class of loss functions.
+This result is later demonstrated empirically.
+The geometric interpretation is also used to provide a new proof that forecast reconciliation results in unbiased forecasts as long as the initial so-called {\em base} forecasts are also unbiased.
+Approaches for dealing with biased base forecasts are proposed and explored in an extensive empirical study on Australian tourism demand.
+Overall, the method of bias-correcting before carrying out reconciliation is shown to outperform alternatives that only bias-correct or only reconcile forecasts.
+
 	\end{abstract}

### 2019-09-04 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Georges changes

@@
 
-	Multivariate time series following an aggregation structure arise in many sectors such as retail, energy, insurance, health and welfare and economics \citep{Karmy2019, Taieb2017, Almeida2016, JeoEtAl2019, Mahkya2017, LiTan2019, Shang2017}.
+	Multivariate time series following an aggregation structure arise in many sectors such as retail, energy, insurance, health and welfare and economics \citep[see for example][]{KarMal2019, Taieb2017, NysEtAl2019, AlmVan2016, JeoEtAl2019, Mahkya2017, LiTan2019, Shang2017, AthEtAl2019_MacroBook}.
 Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making.
@@
 The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts.
-This approach and later modifications have subsequently been shown to outperform bottom-up and top-down approaches in a variety of empirical settings \citep{Hyndman2016, Athanasopoulos2009, Shang2017}.
-
-	Some theoretical insight into the performance of forecast reconciliation methods has been provided by \cite{VanErven2015a} and \cite{WicEtAl2019}.
+This approach and later modifications have subsequently been shown to outperform bottom-up and top-down approaches in a variety of empirical settings \citep[see for example][among others]{Athanasopoulos2009, AthEtAl2017, WicEtAl2019}.	Some theoretical insight into the performance of forecast reconciliation methods has been provided by \cite{VanErven2015a} and \cite{WicEtAl2019}.
 Both papers provide a proof that reconciliation is guaranteed to improve base forecasts.
@@
 
-    Forecasting a single level of the hierarchy did not, however echo common practice within many industries.\todo{might need refs}  In many organisations different departments or `silos' each produced their own forecasts, often with their own information sets and judgemental adjustments.
-This approach does have several advantages over only forecasting a single level.
+    Forecasting a single level of the hierarchy did not, however echo common practice within many industries.
+In many organisations different departments or `silos' each produced their own forecasts, often with their own information sets and judgemental adjustments.
+\footnote{\cite{Cha2013} discusses silos and the importance of information and data sharing across an organisation.}  This approach does have several advantages over only forecasting a single level.
 First, there is no loss of information since all levels and series are modelled.

### 2019-09-04 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Final Revision

@@
 	\begin{abstract}
-		A geometric interpretation is developed for so-called {\em reconciliation} methodologies which are used to forecast time series that adhere to known linear constraints.
+\spacingset{1.45}
+        A geometric interpretation is developed for so-called {\em reconciliation} methodologies used to forecast time series that adhere to known linear constraints.
 In particular, a general framework is established nesting many existing popular reconciliation methods within the class of {\em projections}.
-This interpretation facilitates the derivation of novel results that explain why and how reconciliation via projection is guaranteed to improve forecasts with respect to a specific class of loss functions.
-This result is later demonstrated empirically.
-The geometric interpretation is also used to provide a new proof that forecast reconciliation results in unbiased forecasts as long as the initial so-called {\em base} forecasts are also unbiased.
-Approaches for dealing with biased base forecasts are proposed and explored in an extensive empirical study on Australian tourism demand.
+This interpretation facilitates the derivation of novel results that explain why and how reconciliation via projection is guaranteed to improve forecast accuracy with respect to a specific class of loss functions.
+The result is also demonstrated empirically.
+The geometric interpretation is further used to provide a new proof that forecast reconciliation results in unbiased forecasts as long as the initial so-called {\em base} forecasts are also unbiased.
+Approaches for dealing with biased base forecasts are proposed and explored in an extensive empirical study on Australian tourism flows.
 Overall, the method of bias-correcting before carrying out reconciliation is shown to outperform alternatives that only bias-correct or only reconcile forecasts.
@@
 
-    \begin{equation}
+    \begin{equation*}
     \bm{y}_t = \bm{Sb}_t,
-    \end{equation}
+    \end{equation*}
     where $\bm{S}$ is an $n \times m$ constant matrix that encodes the aggregation constraints.
@@
 		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the Euclidean sense) projection onto $\mathfrak{s}$ and let $\|\bm{v}\|$ be the $L_2$ norm (in the Euclidean sense) of vector $\bm{v}$ then:
-		\begin{equation}
+		\begin{equation*}
 		\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|\le\|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|.
-		\end{equation}
+		\end{equation*}
 	\end{theo}
@@
 		Since, $\bm{y}_{t+h|t},\tilde{\bm{y}}_{t+h|t}\in\mathfrak{s}$ and since the projection is orthogonal, by Pythagoras' theorem
-		\begin{equation} \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|^2=\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|^2+\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2.
-		\end{equation}
+		\begin{equation*} \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|^2=\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|^2+\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2.
+		\end{equation*}
 
 		Since $\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2\ge 0$ this implies,
-		\begin{equation} \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|^2\ge\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|^2.
-		\end{equation}
+		\begin{equation*} \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|^2\ge\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|^2.
+		\end{equation*}
 		with equality only holding when $\tilde{\bm{y}}_{t+h|t}=\hat{\bm{y}}_{t+h|t}$.  Taking the square root of both sides proves the desired result.
@@
 
-	\begin{align}
+	\begin{align*}
 	\tilde{\bm{y}}^*&=\bm{W}^{-1/2}\tilde{\bm{y}}\\&=\bm{W}^{-1/2}\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}
 	\\&=\bm{S}^*\left(\bm{S}^{*'}\bm{S}^*\right)^{-1}\bm{S}^{*'}\hat{\bm{y}^*}.
-	\end{align}
+	\end{align*}
 
@@
         If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the generalised Euclidean sense) projection onto $\mathfrak{s}$ then:
-		\begin{equation}
+		\begin{equation*}
 		\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|_{{\bm W}^{-1}}\le\|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|_{{\bm W}^{-1}}.
-		\end{equation}
+		\end{equation*}
 	\end{theo}
@@
     This result has implications in practice. The top-down method \citep{Gross1990} has
-	\begin{equation}\label{eq:top-downG}
+	\begin{equation*}
 	\bm{G}=\begin{pmatrix}
@@
 	\end{pmatrix}
-	\end{equation}
+	\end{equation*}
     where $\bm{p} = (p_1,\dots,p_m)'$ is an $m$-dimensional vector consisting a set of proportions used to disaggregate the top-level forecast.
@@
 	Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.
-Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix.
-However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$.
+Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix (see Section \ref{app:projection-proof} in the Appendix for a proof).\todo{Rob can you please read this carefully and see if you are happy with the following statements about bias correction.} However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$.
 This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.
@@
 In this well-known case a number of bias correction methods exist based on Taylor expansions.
-%\textcolor{red}{TODO: Read this again after the empirical application has been completed.
-I am saying this because my understanding is that we use the Guererro method to choose the lambda for the BoxCox transformation.
-Then we back transform the forecasts using the same lambda once with bias correcting using the factor that comes out of a Taylor series expansion around $\mu$ (programmed in fable/forecast package) and once without it hence looking at medians and not means - hence biased base forecasts.
-If my understanding here is correct I am not sure we can say we are using the Guererro method to bias correct.}
 
@@
 
-	%\textcolor{red}{GA: I will rewrite/review this when we decide where we put all our results - I am referring to the projection results - currently I think it is best that everything goes here and we make a comment at the end of Section 3.3 guiding the reader to the results here.
-This will make the empirical application a bit broader not only about bias correction, i.e., both about showing how projections work and how bias correction works.}
 	Using an empirical application to forecast Australian domestic tourism flows, we illustrate the usefulness of projection based reconciliation in practice.
@@
 where, $\hat{w}_{t+h|t}$ is the $h$-step-ahead forecast from the Box-Cox transformed series and $\sigma_h^2$ is the variance of $\hat{w}_{t+h|t}$.
-Using the mean of the forecast distribution returns bias adjusted base forecasts compared to the simple back-transformation of \eqref{eq:BoxCox_back-transformation}.
-We refer to this as Method-1 in the results that follow.
+Using the mean of the forecast distribution returns bias adjusted base forecasts compared to the simple back-transformation of Eq.~\eqref{eq:BoxCox_back-transformation}.
+We refer to this as ``Method-1'' in the results that follow.
 The second scenario of bias adjustment we explore is using the in-sample forecast error mean of the biased forecasts to adjust the out-of-sample forecasts.
-We refer to this as Method-2 in the results that follow.
+We refer to this as ``Method-2'' in the results that follow.
 
@@
 	\caption {Average {MSE($\times 10^3$)} of $1$-step-ahead point forecasts from log and Box-Cox transformed series.
-Biased denotes forecasts from simply reversing the transformation via \eqref{eq:BoxCox_back-transformation}.
-Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in \eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
+Biased denotes forecasts from simply reversing the transformation via Eq.~\eqref{eq:BoxCox_back-transformation}.
+Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in Eq.~\eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
 	\label{tab:Results_MSE}
@@
 
+\clearpage
 	\section{Appendix} 
 	%\thisfloatpagestyle{empty}
-	\subsection{Proof $\bm{S}\bm{G}\bm{S}=\bm{S}$ implies $\bm{S}\bm{G}$ is a projection}
+	\subsection{Proof $\bm{S}\bm{G}\bm{S}=\bm{S}$ implies $\bm{S}\bm{G}$ is a projection} \label{app:projection-proof}
 	Here we establish that if $\bm{S}\bm{G}$ is a projection onto the linear subspace spanned by $\bm{S}$ then $\bm{S}\bm{G}\bm{S}=\bm{S}$.
@@
 Stacking these vectors horizontally
-	\begin{align}
+	\begin{align*}
 	\bm{S}\bm{G}\bm{S}&=\begin{pmatrix}
@@
 	&=\bm{S}
-	\end{align}
+	\end{align*}
 

### 2019-09-04 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
One more Final revision :-)

@@
 	Defining concepts such as coherence and reconciliation in geometric terms provides new insights into forecast reconciliation methods.
-We have also provided evidence that reconciliation, particularly using the MinT method, can mitigate the effect of poor bias correction.
+We have also provided evidence that bias correction before reconciliation, improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation.
 Our intention in proposing a geometric interpretation is also to provoke research into new areas.
-We now discuss three such possibilites.
+We now discuss three such possibilities.
 
@@
 In these cases the coherent space may need to be defined by a manifold.
-Although much more challenging, it is still possible define reconciled forecasts in terms of projections onto a manifold.
+Although much more challenging, it is still possible to define reconciled forecasts in terms of projections onto a manifold.
 Second, since we have established that the concept of bottom-level series is not crucial in forecast reconciliation an open question is whether it may be better to construct base forecasts of linear combinations of the time series rather than the time series themselves.
-Finally, the geometric interpretations of hierarchical forecast reconciliation facilitates an extension into a probabilistic framework, an issue that we investigate in a separate paper.
+Finally, the geometric interpretations of hierarchical forecast reconciliation facilitates an extension into a probabilistic framework.
+The latter two are issues we investigate in separate papers.
 

### 2019-09-05 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
A minor change
Cleaned up preamble
Better spacing on front page

@@
 
-%\theoremstyle{theo}
 \newtheorem{theo}{Theorem}[section]
@@
 
-\theoremstyle{property}
-\newtheorem{property}{Property}[section]
+\def\spacingset#1{\renewcommand{\baselinestretch}%
+    {#1}\small\normalsize} \spacingset{1}
 
 \begin{document}
-
-	%\bibliographystyle{natbib}
-
-	\def\spacingset#1{\renewcommand{\baselinestretch}%
-		{#1}\small\normalsize} \spacingset{1}
 
@@
 {
-		\title{\bf Forecast Reconciliation: A geometric view with new insights on bias correction.}
+  \title{\bf Forecast reconciliation: A geometric view with new insights on bias correction}
   \author{Anastasios Panagiotelis\\
     Department of Econometrics and Business Statistics,\\
-			Monash University,\\ VIC 3145, Australia.\\
-			Email: Anastasios.Panagiotelis@monash.edu \\
-			and \\
+    Monash University, VIC 3145, Australia.\\
+    Email: Anastasios.Panagiotelis@monash.edu \\[0.6cm]
     Puwasala Gamakumara\\
     Department of Econometrics and Business Statistics,\\
-			Monash University,\\ VIC 3800, Australia.\\
-			Email: Puwasala.Gamakumara@monash.edu \\
-			and \\
+    Monash University, VIC 3800, Australia.\\
+    Email: Puwasala.Gamakumara@monash.edu \\[0.6cm]
     George Athanasopoulos\thanks{Corresponding Author.
@@
     Department of Econometrics and Business Statistics,\\
-			Monash University,\\ VIC 3145, Australia.\\
-			Email: George.Athanasopoulos@monash.edu \\
-			and \\
+    Monash University, VIC 3145, Australia.\\
+    Email: George.Athanasopoulos@monash.edu \\[0.6cm]
     Rob J Hyndman\\
     Department of Econometrics and Business Statistics,\\
-			Monash University,\\ VIC 3800, Australia.\\
-			Email: Rob.Hyndman@monash.edu \\}
+    Monash University, VIC 3800, Australia.\\
+    Email: Rob.Hyndman@monash.edu\\[1.5cm]}
 		\maketitle
@@
 
-	\bigskip
+\newpage
 
@@
 For the second more general Box-Cox transformation we select $\lambda$ using the ``Guerrero'' method \citep{guerrero1993time} implemented in the \verb|BoxCox.lambda()| function in the \verb|forecast| package in R \citep{Rforecast}.
-In order to avoid extreme and volatile transformations we restrict $\lambda \in (0.5,2)$.
+In order to avoid extreme and volatile transformations we restrict $\lambda \in (-0.5,2)$.
 As zero observations exist in some of the bottom-level series, before transforming we add a constant (more specifically $1$) to each series.

### 2019-09-05 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Abstract

@@
 \spacingset{1.45}
-        A geometric interpretation is developed for so-called {\em reconciliation} methodologies used to forecast time series that adhere to known linear constraints.
-In particular, a general framework is established nesting many existing popular reconciliation methods within the class of {\em projections}.
+  A geometric interpretation is developed for so-called \emph{reconciliation} methodologies used to forecast time series that adhere to known linear constraints.
+In particular, a general framework is established nesting many existing popular reconciliation methods within the class of \emph{projections}.
 This interpretation facilitates the derivation of novel results that explain why and how reconciliation via projection is guaranteed to improve forecast accuracy with respect to a specific class of loss functions.
 The result is also demonstrated empirically.
-The geometric interpretation is further used to provide a new proof that forecast reconciliation results in unbiased forecasts as long as the initial so-called {\em base} forecasts are also unbiased.
+The geometric interpretation is further used to provide a new proof that forecast reconciliation results in unbiased forecasts provided the initial \emph{base} forecasts are also unbiased.
 Approaches for dealing with biased base forecasts are proposed and explored in an extensive empirical study on Australian tourism flows.

### 2019-09-05 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Revisions to Intro

@@
 The past decade has seen rapid development in methodologies for forecasting time series that follow a hierarchical aggregation structure.
-Of particular prominence have been {\em forecast reconciliation} methods involving two steps; first separate forecasts are produced for all series, then these are adjusted ex post to ensure coherence with aggregation constraints.
-Forecast reconciliation has mostly been formulated using a regression model, see \cite{Hyndman2011} and \cite{WicEtAl2019} for examples.
+Of particular prominence have been \emph{forecast reconciliation} methods involving two steps: first separate forecasts are produced for all series, then these are adjusted ex~post to ensure coherence with aggregation constraints.
+Forecast reconciliation has mostly been formulated using a regression model, see \citet{Hyndman2011} and \citet{WicEtAl2019} for examples.
 This setup can be counter-intuitive since a vector comprised of forecasts from different time series models is also assumed to be the dependent variable in a regression model.
@@
 Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom-up fashion \citep{Dunn1976} or disaggregating in a top-down fashion \citep{Gross1990, Athanasopoulos2009}.
-For reviews of these approaches including a discussion of their advantages and disadvantages see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.
+For reviews of these approaches, including a discussion of their advantages and disadvantages, see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.
 
-	In contrast to these methods, \cite{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as {\em base} forecasts.
+In contrast to these methods, \citet{Hyndman2011} proposed forecasting all series in the hierarchy, referring to these as \emph{base} forecasts.
 Since base forecasts were produced independently they were not guaranteed to adhere to aggregation constraints and could thus be improved via further adjustment.
-A framework was proposed whereby the base forecasts were assumed to follow a regression model.
+A framework was proposed whereby the aggregation constraints were expressed in a regression model for the base forecasts.
 The predicted values from this model were guaranteed to adhere to the linear constraints by construction and could thus be used as a new set of forecasts.
-This approach and later modifications have subsequently been shown to outperform bottom-up and top-down approaches in a variety of empirical settings \citep[see for example][among others]{Athanasopoulos2009, AthEtAl2017, WicEtAl2019}.	Some theoretical insight into the performance of forecast reconciliation methods has been provided by \cite{VanErven2015a} and \cite{WicEtAl2019}.
+This approach and later modifications have subsequently been shown to outperform bottom-up and top-down approaches in a variety of empirical settings \citep[see for example][among others]{Athanasopoulos2009, AthEtAl2017, WicEtAl2019}.
+Some theoretical insight into the performance of forecast reconciliation methods has been provided by \citet{VanErven2015a} and \citet{WicEtAl2019}.
 Both papers provide a proof that reconciliation is guaranteed to improve base forecasts.
 The latter paper also proposes a particular version of reconciliation known as the Minimum Trace (MinT) method.
-This is optimal in the sense of minimising the trace of reconciled forecast error covariance matrix under the assumption that base forecasts are unbiased.
+This is optimal in the sense of minimising the trace of the reconciled forecast error covariance matrix under the assumption that the base forecasts are unbiased.
 
@@
 We believe that this is clearer and more intuitive than explanations based on regression modelling, notwithstanding the fact that regression based-methods themselves are indeed projections.
-As such, this paper is in part a review of existing results cast in a new light, but one that we believe to be warranted as forecast reconciliation methodologies have become more popular.
+As such, this paper is in part a review of existing results cast in a new light.
 In addition, we also propose three major and novel results.
 
-	First, our approach makes it clear that the defining characteristic of so-called {\em hierarchical time series} is not aggregation but linear constraints.
-As a result forecast reconciliation can be applied in contexts where there are no clear candidates of {\em bottom level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling.
+First, our approach makes it clear that the defining characteristic of so-called \emph{hierarchical time series} is not aggregation but linear constraints.
+As a result forecast reconciliation can be applied in contexts where there are no clear candidates of \emph{bottom level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling.
 Second, we provide a new proof that reconciled forecasts dominate unreconciled forecasts which makes explicit the link between a reconciliation method and a loss function.
-We believe that this link is lacking in previous work that attempts to establish similar results, in particular \cite{VanErven2015a} and \cite{WicEtAl2019}.
-Futhermore, unlike \cite{VanErven2015a} and \cite{WicEtAl2019} our proof does not require an assumption about convexity.
+We believe that this link is lacking in previous work that attempts to establish similar results, in particular \citet{VanErven2015a} and \citet{WicEtAl2019}.
+Futhermore, unlike \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity.
 Third, we revisit the issue of bias.
-We prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts as long as base forecasts are also unbiased.
+We prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased.
 A natural question that arises is what to do in the case of biased reconciled forecasts.

### 2019-09-05 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Section 2 revision

@@
 Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the future of research in forecast reconciliation.
+
 \section{Coherent forecasts}\label{sec:CoheForecasts}
@@
 
-    We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \cite{AthEtAl2019_MacroBook}, \cite{FPP2018} and others, before elaborating on some of the limitations of this understanding.
+We briefly define the concept of a \emph{hierarchical time series} in a fashion similar to \citet{AthEtAl2019_MacroBook}, \citet{FPP2018} and others, before elaborating on some of the limitations of this understanding.
 A \emph{hierarchical time series} is a collection of $n$ variables indexed by time, where some variables are aggregates of other variables.
@@
 The \emph{bottom-level series} are defined as those $m$ variables that cannot be formed as aggregates of other variables; we let $\bm{b}_t \in \mathbb{R}^m$ be a vector comprised of observations of all bottom-level series at time $t$.
-The hierarchical structure of the data implies that the following holds for all $t$
-
+The hierarchical structure of the data implies that the following holds for all $t$:
 \begin{equation*}
-    \bm{y}_t = \bm{Sb}_t,
+  \bm{y}_t = \bm{S}\bm{b}_t,
 \end{equation*}
@@
 
-		\begin{figure}[H]
+\begin{figure}[!hbt]
   \begin{center}
@@
 
-	To clarify these concepts consider the example of the hierarchy in Figure \ref{fig:basichier}.
+To clarify these concepts, consider the example of the hierarchy in Figure~\ref{fig:basichier}.
 For this hierarchy, $n=7$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$ and
@@
 While such a definition is completely serviceable, it obscures the full generality of the literature on so-called hierarchical time series.
-In fact, concepts such as coherence and reconciliation, defined in full below, only require the data to have two important characteristics; the first is that they are multivariate, the second is that they adhere to linear constraints.
+In fact, concepts such as coherence and reconciliation, defined in full below, only require the data to have two important characteristics: the first is that they are multivariate, the second is that they adhere to linear constraints.
 
@@
 
-	The property that data adhere to some linear constraints is referred to as {\em coherence}.  We now provide definitions aimed at providing geometric intuition of hierarchical time series.
+The property that data adhere to some linear constraints is referred to as \emph{coherence}. We now provide definitions aimed at providing geometric intuition of hierarchical time series.
 
@@
 \end{definition}
-     To further illustrate, Figure \ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.
-The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space, i.e.
+
+To further illustrate, Figure~\ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.
+The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space; i.e.
 $m=2$ and $n=3$.
-It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$, i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$.
+It is worth noting that the coherent subspace is spanned by the columns of $\bm{S}$; i.e.\ $\mathfrak{s}=\text{span}(\bm{S})$.
 In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.
@@
 
-     \begin{figure}[H]
+\begin{figure}[!hbt]
    \centering
@@
 
-	 Despite the common use of the term {\em hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.
-Also notable by its absence in the above definition is any reference to {\em aggregation}.
-In some ways, terms such as {\em hierarchical} and {\em aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure~\ref{fig:basichier} and/or do not involve aggregation.
+Despite the common use of the term \emph{hierarchical time series}, it should be clear from the definition that the data need not necessarily follow a hierarchy.
+Also notable by its absence in the above definition is any reference to \emph{aggregation}.
+In some ways, terms such as \emph{hierarchical} and \emph{aggregation} can be misleading since the literature has covered instances that cannot be depicted in a similar fashion to Figure~\ref{fig:basichier} and/or do not involve aggregation.
 Examples include, temporal hierarchies which involve grouped structures \citep[see][]{AthEtAl2017}, overlapping temporal hierarchies \citep[see][]{JeoEtAl2019}, applications for which the difference rather than the aggregate is of interest \cite[see][]{LiTan2019}, or structures that involve both cross-sectional and temporal dimensions referred to as cross-temporal structures \citep[see][]{KouAth2019}.
@@
 %  It will sometimes be useful to think of pre-multiplication by $\bm{S}$ as a mapping from $\mathbb{R}^m$ to $\mathbb{R}^n$, in which case we use the notation $s(.)$.
-Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure \ref{fig2}.
+Although the codomain of $s(.)$ is $\mathbb{R}^n$, its image is the coherent space $\mathfrak{s}$ as depicted in Figure~\ref{fig2}.
 %
@@
 Much of the early literature that dealt with the problem of forecasting hierarchical time series \citep[see][and references therein]{Gross1990} produced forecasts at a single level of the hierarchy in the first stage.
-Subsequently forecasts for all series were recovered through aggregation, disaggregation according to historical or forecast proportions or some combination of both.
-As such incoherent forecasts were not a problem in these earlier papers.
+Subsequently forecasts for all series were recovered through aggregation, disaggregation according to historical or forecast proportions, or some combination of both.
+Consequently, incoherent forecasts were not a problem in these earlier papers.
 
@@
 In many organisations different departments or `silos' each produced their own forecasts, often with their own information sets and judgemental adjustments.
-\footnote{\cite{Cha2013} discusses silos and the importance of information and data sharing across an organisation.}  This approach does have several advantages over only forecasting a single level.
+\footnote{\citet{Cha2013} discusses silos and the importance of information and data sharing across an organisation.} This approach does have several advantages over only forecasting a single level.
 First, there is no loss of information since all levels and series are modelled.
@@
 However, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.\footnote{There are some special cases of using simple approaches such as na\"{i}ve, which extrapolate the coherent nature of the data to the forecasts.} This problem of incoherent forecasts cannot in general be solved by multivariate modelling either.
-Instead, the solution is to make an ex post adjustment that ensures coherence, a process known as {\em forecast reconciliation}
+Instead, the solution is to make an ex post adjustment that ensures coherence, a process known as \emph{forecast reconciliation}
 

### 2019-09-05 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Revisions to Section 3

@@
 The concept of forecast reconciliation is predicated on there being an $n$-vector of forecasts that are incoherent.
-We call these {\em base forecasts} and denote them as $\hat{\bm{y}}_{t+h|t}$.
-The subscript $t+h/t$ implies that the forecast is made at time $t$ for a period $h$ steps into the future.
+We call these \emph{base forecasts} and denote them as $\hat{\bm{y}}_{t+h|t}$.
 In the sequel, this subscript will be dropped at times for ease of exposition.
@@
   Let $\psi$ be a mapping, $\psi:\mathbb{R}^n\rightarrow\mathfrak{s}$.
-The point forecast $\tilde{\bm{y}}_{t+h|t}=\psi\left(\hat{\bm{y}}_{t+h|t}\right)$ ``reconciles'' a base forecast $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $\psi(.)$
+The point forecast $\tilde{\bm{y}}_{t+h|t}=\psi(\hat{\bm{y}}_{t+h|t})$ ``reconciles'' a base forecast $\hat{\bm{y}}_{t+h|t}$ with respect to the mapping $\psi(.)$
 \end{definition}
@@
 All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.
-One way to achieve this is with a matrix $\bm{SG}$, where $\bm{G}$ is an $m\times n$ matrix  (some authors use $\bm{P}$ in place of $\bm{G}$).
+One way to achieve this is with a matrix $\bm{S}\bm{G}$, where $\bm{G}$ is an $m\times n$ matrix (some authors use $\bm{P}$ in place of $\bm{G}$).
 This facilitates an interpretation of reconciliation as a two-step process.
@@
 
-	Although pre-multiplying base forecasts by $\bm{SG}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{SG}$ has the specific structure of a {\em projection} matrix onto $\mathfrak{s}$.
+Although pre-multiplying base forecasts by $\bm{S}\bm{G}$ will result in coherent forecasts, a number of desirable properties arise when $\bm{S}\bm{G}$ has the specific structure of a \emph{projection} matrix onto $\mathfrak{s}$.
 In general a projection matrix is defined via its idempotence property, i.e.
-$(\bm{SG})^2=\bm{SG}$.
+$(\bm{S}\bm{G})^2=\bm{S}\bm{G}$.
 However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped to itself by that projection \citep[see Lemma 2.4 in][for a proof]{rao1974}.
-In our context this implies that for any $\bm{v}\in\mathfrak{s}$, $\bm{SGv}=\bm{v}$.
+In our context this implies that for any $\bm{v}\in\mathfrak{s}$, $\bm{S}\bm{G}\bm{v}=\bm{v}$.
 
-	We begin by considering the special case of an orthogonal projection whereby $\bm{G}=\left(\bm{S}'\bm{S}\right)^{-1}\bm{S}'$.
-This is equivalent to so called OLS reconciliation as introduced by \cite{Hyndman2011}.
+We begin by considering the special case of an orthogonal projection whereby $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$.
+This is equivalent to so called OLS reconciliation as introduced by \citet{Hyndman2011}.
 We refrain from any discussion of regression models focusing instead on geometric interpretations.
@@
 \begin{itemize}
-  \item The  first is that reconciliation should adjust the base forecasts as little as possible, i.e. the base and reconciled forecasts should be `close'.
+\item The first is that reconciliation should adjust the base forecasts as little as possible; i.e. the base and reconciled forecasts should be `close'.
 \item The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value targeted by the forecast.
@@
 To address the first of these properties we make the concept of closeness more concrete, by considering the Euclidean distance between the base forecast $\hat{\bm{y}}$ and the reconciled forecast $\tilde{\bm{y}}$.
-A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ is minimal for over any possible $\tilde{\bm{y}}\in\mathfrak{s}$.
+A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ is minimal over any possible $\tilde{\bm{y}}\in\mathfrak{s}$.
 In this sense reconciliation via orthogonal projection leads to the smallest possible adjustments of the base forecasts.
 
-	The property that reconciliation should improve forecasts was touched upon in Section 2.3 of \cite{WicEtAl2019}.
-The discussion in that paper focuses on the case of MinT.
+The property that reconciliation should improve forecasts was touched upon in Section 2.3 of \citet{WicEtAl2019}.
+The discussion in that paper focuses on the case of MinT\@.
 Here we provide a new explicit proof of that result.
@@
 \begin{theo}[Distance reducing property]\label{th:distred}
-		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the Euclidean sense) projection onto $\mathfrak{s}$ and let $\|\bm{v}\|$ be the $L_2$ norm (in the Euclidean sense) of vector $\bm{v}$ then:
+  If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection (in the Euclidean sense) onto $\mathfrak{s}$ and let $\|\bm{v}\|$ be the $L_2$ norm (in the Euclidean sense) of vector $\bm{v}$ then:
   \begin{equation*}
@@
 \begin{proof}
-		Since, $\bm{y}_{t+h|t},\tilde{\bm{y}}_{t+h|t}\in\mathfrak{s}$ and since the projection is orthogonal, by Pythagoras' theorem
+  Since $\bm{y}_{t+h|t},\tilde{\bm{y}}_{t+h|t}\in\mathfrak{s}$ and since the projection is orthogonal, by Pythagoras' theorem
   \begin{equation*} \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|^2=\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|^2+\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2.
@@
   Since $\|(\tilde{\bm{y}}_{t+h|t}-\hat{\bm{y}}_{t+h|t})\|^2\ge 0$ this implies,
-		\begin{equation*} \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|^2\ge\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|^2.
+  \begin{equation*} \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|^2\ge\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|^2,
   \end{equation*}
@@
 
-	The simple geometric intuition behind the proof is demonstrated in Figure \ref{fig:Schematic_OLSRecon}.
-In this schematic, the coherent subspace is depicted as a black arrow.
-The base forecast $\hat{\bm{y}}$ is shown as a blue dot.
+The simple geometric intuition behind the proof is demonstrated in Figure~\ref{fig:Schematic_OLSRecon}.
+In this schematic, the coherent subspace is depicted as a black arrow, and the base forecast $\hat{\bm{y}}$ is shown as a blue dot.
 Since $\hat{\bm{y}}$ is incoherent, $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$ and in this case the inequality is strict.
@@
 
-	\begin{figure}[H]
+\begin{figure}[!hbt]
   \centering \includegraphics[width=0.6\textwidth]{Figs/orth_pointforerec_schematic.pdf}
-		\caption{Orthogonal projection of $\hat{\bm{y}}$ onto $\mathfrak{s}$ yielding the reconciled forecast $\tilde{\bm{y}}$}\label{fig:Schematic_OLSRecon}
+  \caption{Orthogonal projection of $\hat{\bm{y}}$ onto $\mathfrak{s}$ yielding the reconciled forecast $\tilde{\bm{y}}$.}\label{fig:Schematic_OLSRecon}
 \end{figure}
 
-	Figure \ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle with $\tilde{\bm{y}}$ at the right-angled vertex.
+Figure~\ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle with $\tilde{\bm{y}}$ at the right-angled vertex.
 In this triangle the line between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.
-As such reconciliation is guaranteed to reduce the squared error of the forecast.
+Therefore reconciliation is guaranteed to reduce the squared error of the forecast.
 
@@
 First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.
-In particular, this measure is the root of the sum of squared forecast errors of {\em all} variables in the hierarchy.
-As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to less accurate forecasts for individual series.
+In particular, this measure is the root of the sum of squared forecast errors of \emph{all} variables in the hierarchy.
+Consequently, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to less accurate forecasts for individual series.
 Second, although orthogonal projections are guaranteed to improve on base forecasts, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.
-As such referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT.
+Therefore, referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT\@.
 It is to oblique projections that we now turn our attention.
@@
 
-	One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the root of the sum of squared errors of {\em all} variables in the hierarchy.
+One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the root of the sum of squared errors of \emph{all} variables in the hierarchy.
 A clear shortcoming of this measure of forecast accuracy is that forecast errors in all series should not necessarily be treated equally.
@@
 An even more sophisticated understanding may take the correlation between series into account.
-All of these considerations lead towards reconciliation of the form $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, where $\bm{W}$ is a symmetric matrix.
+All of these considerations lead towards reconciliation of the form $\tilde{\bm{y}}=\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, where $\bm{W}$ is a symmetric matrix.
 Generally, it is assumed that $\bm{W}$ is invertible, otherwise a pseudo inverse can be used.
 
-	It should be noted that  $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix in the usual Euclidean geometry.
+It should be noted that $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix in the usual Euclidean geometry.
 However this matrix can be considered to be an orthogonal projection for a different geometry defined by the norm\break $||\bm{v}||_{{\bm W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
@@
 The transformed reconciled forecast results from an orthogonal projection in the transformed space since
-
 \begin{align*}
-	\tilde{\bm{y}}^*&=\bm{W}^{-1/2}\tilde{\bm{y}}\\&=\bm{W}^{-1/2}\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}
-	\\&=\bm{S}^*\left(\bm{S}^{*'}\bm{S}^*\right)^{-1}\bm{S}^{*'}\hat{\bm{y}^*}.
+  \tilde{\bm{y}}^*
+    & = \bm{W}^{-1/2}\tilde{\bm{y}} \\
+    & = \bm{W}^{-1/2}\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}} \\
+    & = \bm{S}^*(\bm{S}^{*'}\bm{S}^*)^{-1}\bm{S}^{*'}\hat{\bm{y}^*}.
 \end{align*}
@@
 For diagonal $\bm{W}^{-1}$, this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix, this is equivalent to a Mahalanobis distance.
-As such Theorem~\ref{th:distred} can easily be generalised as follows:
+Therefore Theorem~\ref{th:distred} can easily be generalised as follows.
 
 \begin{theo}[General distance reducing property]\label{th:gdistred}
-        If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal (in the generalised Euclidean sense) projection onto $\mathfrak{s}$ then:
+  If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection (in the generalised Euclidean sense) onto $\mathfrak{s}$ then:
   \begin{equation*}
-		\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|_{{\bm W}^{-1}}\le\|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|_{{\bm W}^{-1}}.
+    \|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|_{{\bm W}^{-1}}
+      \le\
+    |(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|_{{\bm W}^{-1}}.
   \end{equation*}
@@
 \begin{proof}
-    The proof is identical to the proof for Theorem~\ref{th:distred} but relies on the generalised Pythagorean Theorem (applicable to Generalised Euclidean space) rather than the Pythagorean Theorem.
+  The proof is identical to the proof for Theorem~\ref{th:distred} but relies on the Generalised Pythagorean Theorem (applicable to Generalised Euclidean space) rather than the Pythagorean Theorem.
   \end{proof}
 
-	The implication of Theorem~\ref{th:gdistred} is that if the objective function is some weighted sum of squared errors, or a Mahalanobis distance, then the projection matrix $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts, for an appropriately selected $\bm{W}$.
+The implication of Theorem~\ref{th:gdistred} is that if the objective function is some weighted sum of squared errors, or a Mahalanobis distance, then the projection matrix $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts, for an appropriately selected $\bm{W}$.
 
-	\todo{Rob can you please read to make sure you are happy with this.}Note here that we rely here on the generalised Pythagorean Theorem (which involves an equality).
-In contrast, \cite{WicEtAl2019} follow \cite{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.
-The proof of \cite{WicEtAl2019} requires an assumption about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.
+Note here that we rely here on the Generalised Pythagorean Theorem (which involves an equality).
+In contrast, \citet{WicEtAl2019} follow \citet{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.
+The proof of \citet{WicEtAl2019} requires an assumption about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.
 The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.
-As such the statement from \cite{WicEtAl2019} that {\em``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified; this is only true with respect to a loss function that depends on ${\bm W}$.
+As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified ---  this is only true with respect to a loss function that depends on $\bm{W}$.
 If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts.
@@
 
-	While the properties discussed so far hold for any projection matrix, the MinT method of \cite{WicEtAl2019} has an additional optimality property.
-\cite{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by an oblique projection with a particular choice of $\bm{W}$.
+While the properties discussed so far hold for any projection matrix, the MinT method of \citet{WicEtAl2019} has an additional optimality property.
+\citet{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by an oblique projection with a particular choice of $\bm{W}$.
 Their choice is that $\bm{W}$ should be the forecast error covariance matrix where errors come from using the base forecasts.
@@
 Figure~\ref{fig:OthogonalVSOblique_projection} provides geometrical intuition into the MinT method.
-Suppose that the orange points in panel (a) represent in-sample forecast errors.
+Suppose that the orange points in panel~(a) represent in-sample forecast errors.
 These provide information on the most likely direction of large deviations from the coherent subspace $\mathfrak{s}$.
 This direction is denoted by $\bm{R}$.
-Panel (b) shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).
+Panel~(b) shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).
 One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.
 An oblique projection of the blue point back along the direction of $\bm{R}$, yields a reconciled forecast closer to the target, especially compared to an orthogonal projection.
-Panel (c) shows the orthogonal projection of every potential base forecast onto the coherent subspace.
-Panel (d) depicts an oblique projection along $\bm{R}$ for all the gray points.
+Panel~(c) shows the orthogonal projection of every potential base forecast onto the coherent subspace.
+Panel~(d) depicts an oblique projection along $\bm{R}$ for all the gray points.
 The oblique projection yields reconciled forecasts tightly packed near the target $\bm{y}$.
@@
 
-\begin{figure}[H]
+\begin{figure}[!p]
   \centering
-    \begin{subfigure}[!h]{0.48\textwidth}
+  \begin{subfigure}[!h]{0.415\textwidth}
       \includegraphics[width=\textwidth]{Figs/InsampDir_1_George.pdf}
@@
   \end{subfigure}
-    \begin{subfigure}[!h]{0.48\textwidth}
+  \begin{subfigure}[!h]{0.415\textwidth}
       \includegraphics[width=\textwidth]{Figs/InsampDir_2_George.pdf}
@@
   \end{subfigure}
-    \begin{subfigure}[!h]{0.48\textwidth}
+  \begin{subfigure}[!h]{0.415\textwidth}
       \includegraphics[width=\textwidth]{Figs/OrthProj_George.pdf}
       \caption{}
-    \end{subfigure}    \begin{subfigure}[!h]{0.48\textwidth}
+  \end{subfigure}
+  \begin{subfigure}[!h]{0.415\textwidth}
       \includegraphics[width=\textwidth]{Figs/ObliqProj_George.pdf}

### 2019-09-05 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Revisions to Section 4

@@
 Before turning our attention to the issue of bias itself it is important to state a sensible property that any reconciliation method should have.
-That is if base forecasts are already coherent then reconciliation should not change the forecast.
-As stated in Section~\ref{sec:Reconciliation}, this property holds only when $\bm{SG}$ is a projection matrix.
+That is if base forecasts are already coherent then reconciliation should not change the forecasts.
+As stated in Section~\ref{sec:Reconciliation}, this property holds only when $\bm{S}\bm{G}$ is a projection matrix.
 As a corollary, reconciling using an arbitrary $\bm{G}$, may in fact change an already coherent forecast.
 
-	The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation of \cite{WicEtAl2019}.
-Before restating this proof using a  clear geometric interpretation we discuss in a precise fashion what is meant by unbiasedness.
+The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation of \citet{WicEtAl2019}.
+Before restating this proof using a clear geometric interpretation, we discuss in a precise fashion what is meant by unbiasedness.
 
@@
 Our point forecast can be thought of as an estimate of this quantity.
-The forecast is random due to uncertainty in the training sample and it is with respect to this uncertainty that unbiasedness is referred to.
-More concretely, the point forecast will be unbiased if $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
+The forecast is random due to uncertainty in the training sample and it is with respect to this uncertainty that unbiasedness is defined.
+Specifically, the point forecast will be unbiased if $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.
 
 \begin{theo}[Unbiasedness preserving property]
-		For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also an unbiased prediction as long as $\bm{SG}$ is a projection onto $\mathfrak{s}$.
+  For unbiased $\hat{\bm{y}}_{t+h|t}$, the reconciled point forecast is also an unbiased prediction as long as $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$.
 \end{theo}
@@
 
-	We note that the above result holds when the projection $\bm{SG}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general.
-To describe this more explicitly suppose $\bm{SG}$ has as its image  $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e.
+We note that the above result holds when the projection $\bm{S}\bm{G}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general.
+To describe this more explicitly suppose $\bm{S}\bm{G}$ has as its image $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e.
 $\mathfrak{L}\subset\mathfrak{s}$.
@@
 \begin{equation*}
-	\bm{G}=\begin{pmatrix}
+  \bm{G} = \begin{pmatrix}
              \bm{p} & \bm{0}_{(m \times n-1)}
-	\end{pmatrix}
+           \end{pmatrix},
 \end{equation*}
 where $\bm{p} = (p_1,\dots,p_m)'$ is an $m$-dimensional vector consisting a set of proportions used to disaggregate the top-level forecast.
-In this case it can be verified that $\bm{SG}$ is idempotent, i,e.
-$\bm{SGSG}=\bm{SG}$ and therefore $\bm{SG}$ is a projection matrix.
+In this case it can be verified that $\bm{S}\bm{G}$ is idempotent, i,e.
+$\bm{S}\bm{G}\bm{S}\bm{G}=\bm{S}\bm{G}$ and therefore $\bm{S}\bm{G}$ is a projection matrix.
 However the image of this projection is not an $m$-dimensional subspace but a $1$-dimensional subspace.
@@
 
-	\begin{figure}[H]
+\begin{figure}[!hbt]
   \centering
@@
 
-	Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.
-Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix (see Section \ref{app:projection-proof} in the Appendix for a proof).\todo{Rob can you please read this carefully and see if you are happy with the following statements about bias correction.} However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$.
+Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{S}\bm{G}\bm{S}=\bm{S}$ or alternatively that $\bm{G}\bm{S}=\bm{I}$.
+Both of these conditions are equivalent to assuming that $\bm{S}\bm{G}$ is a projection matrix (see Section~\ref{app:projection-proof} in the Appendix for a proof).
+However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{G}\bm{S}=\bm{I}$.
 This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.
 However, equipped with a geometric understanding of the problem, we would advise against this approach.
-The constraint $\bm{GS}=\bm{I}$  is not just about bias.
+The constraint $\bm{G}\bm{S}=\bm{I}$ is not just about bias.
 Dropping the constraint compromises all of the attractive properties of projections.
-Opening the door to reconciliation methods that change already coherent base forecasts would seem to suggest an increase in the variability of the forecast.
+It also opens the door to reconciliation methods that change already coherent base forecasts, which suggests an increase in the variability of the forecasts.
 This seems particularly perverse when the motivation for using a biased method in the first place is to reduce variance.
@@
 
-	Our own solution to dealing with biased forecasts is to bias correct {\em before} reconciliation.
+Our own solution to dealing with biased forecasts is to bias correct \emph{before} reconciliation.
 In many cases the method for bias correction will be context specific.
@@
 
-	Alternatively, a more general purpose approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y
-	}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.
-This can be then subtracted from future forecasts.
+Alternatively, a more general purpose approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t}$ for all $t+h$ in the training sample.
+This can then be subtracted from future forecasts.
 As stated in the discussion of MinT, in-sample errors are already used to estimate the optimal direction of projection.
@@
 Geometrically, the intuition is simple.
-In panel (a) of Figure \ref{fig:OthogonalVSOblique_projection}, the orange points are centered around the origin as would be expected from an unbiased forecast.
+In panel~(a) of Figure~\ref{fig:OthogonalVSOblique_projection}, the orange points are centered around the origin as would be expected from an unbiased forecast.
 If forecasts are biased, then errors should simply be translated until they are centered at the origin.

### 2019-09-05 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Better pagination
Fix label

@@
 \usepackage[export]{adjustbox}
+\usepackage[section]{placeins}
 
@@
 \addtolength{\topmargin}{-.8in}%
+\sloppy
+\allowdisplaybreaks
 
@@
 
-	 \begin{definition}[Hierarchical Time Series]\label{def:cohspace}
+\begin{definition}[Hierarchical Time Series]\label{def:hts}
    A hierarchical time series is an $n$-dimensional multivariate time series such that all observed values $\bm{y}_1,\ldots,\bm{y}_T$ and all future values $\bm{y}_{T+1},\bm{y}_{T+2},\ldots$ lie in the coherent subspace, i.e., $\bm{y}_t\in\mathfrak{s}\quad\forall t$.
@@
 Examples include, temporal hierarchies which involve grouped structures \citep[see][]{AthEtAl2017}, overlapping temporal hierarchies \citep[see][]{JeoEtAl2019}, applications for which the difference rather than the aggregate is of interest \cite[see][]{LiTan2019}, or structures that involve both cross-sectional and temporal dimensions referred to as cross-temporal structures \citep[see][]{KouAth2019}.
-Finally, although Definition~\ref{def:cohspace} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
+Finally, although Definition~\ref{def:hts} makes reference to time series, this definition can be easily generalised to any vector-valued data for which some linear constraints are known to hold for all realisations.
 

### 2019-09-05 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Section 5 revisions

@@
 It should be noted that $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix in the usual Euclidean geometry.
-However this matrix can be considered to be an orthogonal projection for a different geometry defined by the norm\break $||\bm{v}||_{{\bm W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
+However this matrix can be considered to be an orthogonal projection for a different geometry defined by the norm\break $||\bm{v}||_{\bm{W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
 One way to understand this geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$.
@@
   \begin{equation*}
-    \|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|_{{\bm W}^{-1}}
+    \|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|_{\bm{W}^{-1}}
       \le\
-    |(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|_{{\bm W}^{-1}}.
+    |(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|_{\bm{W}^{-1}}.
   \end{equation*}
@@
 
-We note that the above result holds when the projection $\bm{S}\bm{G}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general.
+The above result holds when the projection $\bm{S}\bm{G}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general.
 To describe this more explicitly suppose $\bm{S}\bm{G}$ has as its image $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e.
@@
 
-\section{Empirical study} \label{sec:EmpStudy}
+\section{Empirical study}\label{sec:EmpStudy}
 
-	Using an empirical application to forecast Australian domestic tourism flows, we illustrate the usefulness of projection based reconciliation in practice.
+Using an empirical application to forecast Australian domestic tourism flows, we illustrate the usefulness of projection-based reconciliation in practice.
 Previous studies have found that reconciliation improves point forecast accuracy in domestic tourism flows for Australia \citep[see for example][]{Athanasopoulos2009, Hyndman2011,WicEtAl2019}.
@@
 First, we demonstrate the implications of Theorem~\ref{th:distred} by comparing reconciled and base forecasts.
-In contrast to previous studies we consider individual periods rather than computing averages over a rolling window.
+In contrast to previous studies, we consider individual periods rather than computing averages over a rolling window.
 Second, we demonstrate how the bias correction methods discussed in the previous section along with the projection-based reconciliation help to improve forecast accuracy.
@@
 Hence, there are $110$ series across the hierarchy with $75$ bottom-level series.
-More information about the series and the geographical hierarchy is presented in Table \ref{table:A1} in the Appendix.
+More information about the series and the geographical hierarchy is presented in Table~\ref{table:A1} in the Appendix.
 The data span the period January 1998 to December 2017, which gives a total of $240$ observations per series.
 
-Figure \ref{fig:Total_TSplots} shows time, sub-series and seasonal plots of the aggregate overnight trips.
+Figure~\ref{fig:Total_TSplots} shows time, sub-series and seasonal plots of the aggregate overnight trips.
 As is usual with tourism data, these show a strong seasonal pattern with peaks observed every January corresponding to the summer vacation season in Australia.
 There are also some lower peaks observed in April, July and October corresponding to school term breaks.
-On the other hand the month with the least overnight trips is February indicating that people travel least for the month following their summer vacation.
-The time plot also shows a pronounced upward trend starting from around 2010 till the end of the sample, with flows being fairly flat from the beginning of the sample and a slight downward trend during 2004-2010.
+On the other hand, the month with the least overnight trips is February indicating that people travel least for the month following their summer vacation.
+The time plot also shows a pronounced upward trend starting from around 2010 to the end of the sample, with flows being fairly flat from the beginning of the sample and a slight downward trend during 2004--2010.
 
-The top panel of Figure \ref{fig:States_Zones_Regs_TSplots} shows time plots for the seven states, hence the first-level of the geographical hierarchy.
+The top panel of Figure~\ref{fig:States_Zones_Regs_TSplots} shows time plots for the seven states, hence the first level of the geographical hierarchy.
 The panels below show some selected series from the second-level zones and the bottom-level regions.
 The plots display the diversity of time series features, within but also between levels.
-For example, noticeable at the first-level is the asynchronous seasonal pattern between the Northern Territory and the other states.
+For example, noticeable at the first level is the asynchronous seasonal pattern between the Northern Territory and the other states.
 For the Northern Territory the high tourist season occurs during June-August with July being the peak, while the low season is during December-February.
@@
 This of course highlights the importance of modelling series at all levels without any loss of valuable information.
-We should note here that we observed an anomalous (extremely high) observation for `Adelaide Hills' for December-2002.
-We replaced this observation with the average overnight trips on December-2001 and December-2003 for the same destination.
+We should note here that we observed an anomalous (extremely high) observation for `Adelaide Hills' for December 2002.
+We replaced this observation with the average overnight trips on December 2001 and December 2003 for the same destination.
 
@@
   \small
-		\includegraphics[width= \textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots1.pdf}
+  \includegraphics[width= .95\textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots1.pdf}
   \caption{Time plot of overnight trips for some selected series from different disaggregate levels of the hierarchy.
@@
 
-    After obtaining the base forecasts these are reconciled using three different projection methods: OLS reconciliation, MinT using a shrinkage estimator for ${\bm W}$ and WLS reconciliation using variance scaling.
-Squared forecast errors are computed for each series and aggregated across the entire hierarchy, i.e., we compute the loss function described in Section~\ref{sec:orthogonal}.
+After obtaining the base forecasts these are reconciled using three different projection methods: OLS reconciliation, MinT using a shrinkage estimator for $\bm{W}$ and WLS reconciliation using variance scaling.
+Squared forecast errors are computed for each series and aggregated across the entire hierarchy; i.e., we compute the loss function described in Section~\ref{sec:orthogonal}.
 We then compute the difference in this loss function between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate.
@@
 The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of this measure over each rolling window.
-We only present the results for $h=1$ but the results and conclusions that follow are almost identical for the other longer forecast horizons.
+We only present the results for $h=1$, but the results and conclusions that follow are almost identical for the other longer forecast horizons.
 We do not present these here to save space but they are available upon request.
@@
 This is not the case for MinT and WLS which for some windows generate forecasts less accurate than the base forecasts.
-The boxplots also demonstrate that OLS reconciliation is more stable than MinT and WLS reconciliation, a result not entirely unsurprising since the latter two methods require estimation of a ${\bm W}$ matrix which in practice is not trivial.
-Nonetheless when averaging over the entire rolling window the MinT estimator performs best on average, which is again precisely what the theorem proved in \cite{WicEtAl2019} would suggest.
+The boxplots also demonstrate that OLS reconciliation is more stable than MinT and WLS reconciliation, a result not entirely unsurprising since the latter two methods require estimation of a $\bm{W}$ matrix which in practice is not trivial.
+Nonetheless when averaging over the entire rolling window the MinT estimator performs best on average, which is again precisely what the theorem proved in \citet{WicEtAl2019} would suggest.
 The average MSE values across the entire rolling window of 140 replications are shown in Table \ref{tab:AveraveDifferences}.
 
-\begin{figure}[H]
+\begin{figure}[!hbt]
     \centering
@@
     \caption{MSE differences between base forecasts and reconciled forecasts using OLS, MinT and WLS, and also the bottom-up approach for $h = 1$.
-A positive value indicates that the coherent forecasts are an improvement over the base forecasts.} \label{fig:BaseVSRecon_Fc}
+A positive value indicates that the coherent forecasts are an improvement over the base forecasts.}\label{fig:BaseVSRecon_Fc}
 \end{figure}
 
-\begin{table}[H]
-	\caption {Average {MSE($\times 10^3$)} over all 140 rolling window replications for $h=1$.} \label{tab:AveraveDifferences}
+\begin{table}[!hbt]
+\caption {Average {MSE($\times 10^3$)} over all 140 rolling window replications for $h=1$.}\label{tab:AveraveDifferences}
   \centering \tabcolsep=0.4cm
@@
 A Box-Cox transformation is defined as,
-
-\begin{equation*} \label{eq:BoxCox_transformation}
-	w_t =
-	\begin{cases}
+\begin{equation*}\label{eq:BoxCox_transformation}
+w_t = \begin{cases}
         \log(y_t)                        & \text{if}~\lambda=0;\\
@@
 Using the fitted models, forecasts are produced for $h=1$ to $12$-steps ahead for each series in the hierarchy.
-The same rolling window described in Section \ref{sec:comparebase} is used here as well.
+The same rolling window described in Section~\ref{sec:comparebase} is used here as well.
 
@@
 
-Using a Taylor series expansion \todo{Rob do we need a reference here or is this obvious/well known?} the back-transformed mean of the forecast distribution for a Box-Cox transformation is given by
-
-\begin{equation} \label{eq:BoxCox_BT_biasadj}
+Using a Taylor series expansion \citep{guerrero1993time}, the back-transformed mean of the forecast distribution for a Box-Cox transformation is given by
+\begin{equation}\label{eq:BoxCox_BT_biasadj}
   \hat{y}_{t+h|t} =
     \begin{cases}
-	\exp({\hat{w}_{t+h|t}})[1+\frac{\sigma_h^2}{2}] & \text{if}~\lambda = 0, \\
-	(\lambda \hat{w}_{t+h|t} + 1)^{1/\lambda}[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda \hat{w}_{t+h|t} + 1)^2}]       & \text{if}~\lambda \ne 0,
+      \exp(\hat{w}_{t+h|t})\left[1+\frac{\sigma_h^2}{2}\right] & \text{if}~\lambda = 0, \\
+      (\lambda \hat{w}_{t+h|t} + 1)^{1/\lambda}
+        \left[1 + \frac{\sigma_h^2(1-\lambda)}{2(\lambda \hat{w}_{t+h|t} + 1)^2}\right]
+                                                      & \text{if}~\lambda \ne 0,
 \end{cases}
 \end{equation}
-where, $\hat{w}_{t+h|t}$ is the $h$-step-ahead forecast from the Box-Cox transformed series and $\sigma_h^2$ is the variance of $\hat{w}_{t+h|t}$.
-Using the mean of the forecast distribution returns bias adjusted base forecasts compared to the simple back-transformation of Eq.~\eqref{eq:BoxCox_back-transformation}.
+where $\hat{w}_{t+h|t}$ is the $h$-step-ahead forecast from the Box-Cox transformed series and $\sigma_h^2$ is the variance of $\hat{w}_{t+h|t}$.
+Using the mean of the forecast distribution returns bias-adjusted base forecasts compared to the simple back-transformation of Eq.~\eqref{eq:BoxCox_back-transformation}.
 We refer to this as ``Method-1'' in the results that follow.
@@
 Using the three sets of base forecasts from each of the two transformations, we generate coherent forecasts implementing OLS, MinT and WLS reconciliation projections, and also the bottom-up approach and compare the results for when the base forecasts are biased and bias-adjusted, i.e., unbiased.
-Table \ref{tab:Results_MSE} presents the results over the $140$ rolling window replications for $1$-step-ahead forecasts.
-We note that as was the case with Section \ref{sec:comparebase} the conclusions that follow extend almost identically to longer forecast horizons.
+Table~\ref{tab:Results_MSE} presents the results over the $140$ rolling window replications for $1$-step-ahead forecasts.
+As was the case with Section~\ref{sec:comparebase}, the conclusions that follow extend almost identically to longer forecast horizons.
 We do not present these here to save space but they are available upon request.
 
-Recall that reconciliation approaches via projections preserve unbiasedness in the reconciled forecasts iff the base forecasts are unbiased.
-Hence, the two columns labelled ``Biased'' contain results for biased base but also reconciled forecasts.
-Using Method-1 for first bias adjusting the base forecasts and then reconciling, results in forecast improvements for all methods for both the log and the Box-Cox transformation induced bias.
-In this case MinT returns the lowest MSE across all forecasts.
-Notice that the ``Box-Cox biased'' base forecasts carry a higher bias compared to the ``log biased'' base forecasts.
-Even for these MinT reconciliation of bias adjusted base forecasts generates very accurate forecasts, almost as accurate as the forecasts that come from the less biased log transformation.
-
-In contrast to the results from using Method-1 for bias adjusting before reconciliation, using Method-2 has an adverse effect on the forecast accuracy of the reconciled forecasts.
-In this case the reconciled unbiased forecasts are less accurate than the biased reconciled forecasts.
-This reflects the fact and sends the warning that implementing inappropriate bias adjustment, in this case using an additive rather than a multiplicative factor, will hinder forecast accuracy and extra care must be taken in this bias adjustment procedure.
-
-\begin{table}
+\begin{table}[!b]
 \caption {Average {MSE($\times 10^3$)} of $1$-step-ahead point forecasts from log and Box-Cox transformed series.
@@
 \end{table}
+
+Recall that reconciliation approaches via projections preserve unbiasedness in the reconciled forecasts iff the base forecasts are unbiased.
+Hence, the two columns labelled ``Biased'' contain results for biased base but also reconciled forecasts.
+Using Method-1 for first bias adjusting the base forecasts and then reconciling, results in forecast improvements for all methods for both the log and the Box-Cox transformation induced bias.
+In this case MinT returns the lowest MSE across all forecasts.
+Notice that the ``Box-Cox biased'' base forecasts carry a higher bias compared to the ``log biased'' base forecasts.
+Even for these MinT reconciliation of bias adjusted base forecasts generates very accurate forecasts, almost as accurate as the forecasts that come from the less biased log transformation.
+
+In contrast to the results from using Method-1 for bias adjusting before reconciliation, using Method-2 has an adverse effect on the forecast accuracy of the reconciled forecasts.
+In this case the reconciled unbiased forecasts are less accurate than the biased reconciled forecasts.
+This reflects the fact and sends the warning that implementing inappropriate bias adjustment, in this case using an additive rather than a multiplicative factor, will hinder forecast accuracy and extra care must be taken in this bias adjustment procedure.
 

### 2019-09-05 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Section 6 revisions

@@
 The black dot ${\bm y}$ denotes the (unknown) target of the forecast.
-(c) shows the orthogonal projection of all potential base forecasts onto the coherent subspace while (d) shows an oblique projection.} \label{fig:OthogonalVSOblique_projection}
+(c) shows the orthogonal projection of all potential base forecasts onto the coherent subspace while (d) shows an oblique projection.}\label{fig:OthogonalVSOblique_projection}
 \end{figure}
@@
   \caption{Total domestic overnight trips (in logs) for Australia from January 1998 to December 2017.
-The top-panel shows a time plot; the bottom-left panel a sub-series plot for each month; the bottom-right panel shows a seasonal plot coloured by year.} \label{fig:Total_TSplots}
+The top-panel shows a time plot; the bottom-left panel a sub-series plot for each month; the bottom-right panel shows a seasonal plot coloured by year.}\label{fig:Total_TSplots}
 \end{figure}
@@
 The forecasts are then back-transformed by simply reversing the Box-Cox transformation using,
-\begin{equation} \label{eq:BoxCox_back-transformation}
+\begin{equation}\label{eq:BoxCox_back-transformation}
   \hat{y}_{t+h|t} =
@@
 
-\section{Conclusions} \label{sec:conclusions}
+\section{Conclusions}\label{sec:conclusions}
 
-	%By redefining coherent point forecast and point forecast reconciliation, we rehash all existing reconciliation methods into a single projection based geometric framework.
+%By redefining coherent point forecast and point forecast reconciliation, we rehash all existing reconciliation methods into a single projection-based geometric framework.
 We have also established new theoretical results that support the use of projections for point forecast reconciliation.
@@
 Defining concepts such as coherence and reconciliation in geometric terms provides new insights into forecast reconciliation methods.
-We have also provided evidence that bias correction before reconciliation, improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation.
+We have also provided evidence that bias correction before reconciliation improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation.
 Our intention in proposing a geometric interpretation is also to provoke research into new areas.
@@
 
-	First, it should be possible to extend to the concept of coherence to non-linear constraints.
+First, it should be possible to extend the concept of coherence to non-linear constraints.
 In these cases the coherent space may need to be defined by a manifold.
 Although much more challenging, it is still possible to define reconciled forecasts in terms of projections onto a manifold.
-Second, since we have established that the concept of bottom-level series is not crucial in forecast reconciliation an open question is whether it may be better to construct base forecasts of linear combinations of the time series rather than the time series themselves.
+Second, since we have established that the concept of bottom-level series is not crucial in forecast reconciliation, an open question is whether it may be better to construct base forecasts of linear combinations of the time series rather than the time series themselves.
 Finally, the geometric interpretations of hierarchical forecast reconciliation facilitates an extension into a probabilistic framework.
@@
 \clearpage
+
 \section{Appendix}
-	%\thisfloatpagestyle{empty}
-	\subsection{Proof $\bm{S}\bm{G}\bm{S}=\bm{S}$ implies $\bm{S}\bm{G}$ is a projection} \label{app:projection-proof}
+
+\subsection{Proof $\bm{S}\bm{G}\bm{S}=\bm{S}$ implies $\bm{S}\bm{G}$ is a projection}\label{app:projection-proof}
+
 Here we establish that if $\bm{S}\bm{G}$ is a projection onto the linear subspace spanned by $\bm{S}$ then $\bm{S}\bm{G}\bm{S}=\bm{S}$.
@@
 \begin{align*}
-	\bm{S}\bm{G}\bm{S}&=\begin{pmatrix}
+\bm{S}\bm{G}\bm{S}
+  & = \begin{pmatrix}
         \bm{S}\bm{G}\bm{s}_1, & \bm{S}\bm{G}\bm{s}_2, & \cdots & \bm{S}\bm{G}\bm{s}_m
-	\end{pmatrix}\\
-	&=\begin{pmatrix}
+      \end{pmatrix} \\
+  & = \begin{pmatrix}
         \bm{s}_1, & \bm{s}_2, & \cdots & \bm{s}_m
       \end{pmatrix}\\
-	&=\bm{S}
+  & = \bm{S}.
 \end{align*}

### 2019-09-05 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Updated appendices

@@
 Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{S}\bm{G}\bm{S}=\bm{S}$ or alternatively that $\bm{G}\bm{S}=\bm{I}$.
-Both of these conditions are equivalent to assuming that $\bm{S}\bm{G}$ is a projection matrix (see Section~\ref{app:projection-proof} in the Appendix for a proof).
+Both of these conditions are equivalent to assuming that $\bm{S}\bm{G}$ is a projection matrix (see Section~\ref{app:projection-proof} in Appendix A for a proof).
 However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{G}\bm{S}=\bm{I}$.
@@
 Hence, there are $110$ series across the hierarchy with $75$ bottom-level series.
-More information about the series and the geographical hierarchy is presented in Table~\ref{table:A1} in the Appendix.
+More information about the series and the geographical hierarchy is presented in Table~\ref{table:A1} in Appendix B\@.
 The data span the period January 1998 to December 2017, which gives a total of $240$ observations per series.
@@
 \clearpage
+\appendix
 
@@
 
-To establish the first statement let $\bm{s}_j$ be the $j^{th}$ column of $\bm{S}$.
+To establish the first statement, let $\bm{s}_j$ be the $j$th column of $\bm{S}$.
 Since by definition, $\bm{s}_j$ lies in $\mathfrak{s}$, it must hold that $\bm{S}\bm{G}\bm{s}_j=\bm{s}_j$.
@@
 To establish the converse it suffices to postmultiply the condition $\bm{S}\bm{G}\bm{S}=\bm{S}$ by $\bm{G}$.
-This yields $\bm{S}\bm{G}\bm{S}\bm{G}=\bm{S}\bm{G}$ which in turn implies idempotence since $(\bm{S}\bm{G})^2=\bm{S}\bm{G}$.
+This yields $\bm{S}\bm{G}\bm{S}\bm{G}=\bm{S}\bm{G}$, which in turn implies idempotence since $(\bm{S}\bm{G})^2=\bm{S}\bm{G}$.
 

### 2019-09-14 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Changed the hierarchical structure in figure 1
made mervyns changes

@@
 As such, this paper is in part a review of existing results cast in a new light.
-In addition, we also propose three major and novel results.
+In addition, we also derive three major and novel results.
 
@@
 We believe that this link is lacking in previous work that attempts to establish similar results, in particular \citet{VanErven2015a} and \citet{WicEtAl2019}.
-Futhermore, unlike \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity.
-Third, we revisit the issue of bias.
-We prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased.
+Futhermore, unlike \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general.
+Third, we prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased.
 A natural question that arises is what to do in the case of biased reconciled forecasts.
@@
 The remainder of this paper is structured as follows.
-Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines so called hierarchical time series in a way that does not depend on any notion of bottom-level series.
+Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines hierarchical time series in a way that does not depend on any notion of bottom-level series.
 Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projections and includes a proof that reconciled forecasts dominate base forecasts with respect to a specific loss function.
 In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose methods for bias correction.
-In Section \ref{sec:EmpStudy} we conduct an extensive empirical application to domestic tourism flow in Australia with two objectives; first to demonstrate the theorems discussed in~\ref{sec:Reconciliation}, second to evaluate the methods for bias correction discussed in~\ref{sec:BiasInRecon}.
-Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the future of research in forecast reconciliation.
+In Section \ref{sec:EmpStudy} we conduct an extensive empirical application to domestic tourism flow in Australia with two objectives; first to demonstrate the theorems discussed in Section~\ref{sec:Reconciliation}, second to evaluate the methods for bias correction discussed in Section~\ref{sec:BiasInRecon}.
+Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the future research directions forf forecast reconciliation.
 
@@
 
-\begin{figure}[!hbt]
+\begin{figure}[H]
 	\begin{center}
-    \leaf{AA} \leaf{AB}
-    \branch{2}{A}
+		\leaf{AA} \leaf{AB} \leaf{AC}
+		\branch{3}{A}
 		\leaf{BA} \leaf{BB}
 		\branch{2}{B}
-    \branch{2}{Tot}
+		\leaf{CA} \leaf{CB}
+		\branch{2}{C}
+		\branch{3}{Tot}
 		\qobitree
@@
 To clarify these concepts, consider the example of the hierarchy in Figure~\ref{fig:basichier}.
-For this hierarchy, $n=7$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$ and
+For this hierarchy, $n=11$, $\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}, y_{CA,t}, y_{CB,t}]'$, $m=7$, $\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{AC,t}, y_{BA,t}, y_{BB,t}, y_{CA,t}, y_{CB,t}]'$ and
 \[
   \bm{S} = \begin{pmatrix}
-    1 & 1 & 1 & 1 \\
-    1 & 1 & 0 & 0 \\
-    0 & 0 & 1 & 1 \\
-    & \multicolumn{2}{c}{\bm{I}_4} &
+    1 & 1 & 1 & 1 & 1 & 1 & 1 \\
+    1 & 1 & 1 & 0 & 0 & 0 & 0 \\
+    0 & 0 & 0 & 1 & 1 & 0 & 0 \\
+    0 & 0 & 0 & 0 & 0 & 1 & 1 \\
+    & \multicolumn{5}{c}{\bm{I}_7} &
   \end{pmatrix},
 \]
-where $\bm{I}_4$ is the $4\times 4$ identity matrix.
+where $\bm{I}_7$ is the $7 \times 7$ identity matrix.
 
 While such a definition is completely serviceable, it obscures the full generality of the literature on so-called hierarchical time series.
-In fact, concepts such as coherence and reconciliation, defined in full below, only require the data to have two important characteristics: the first is that they are multivariate, the second is that they adhere to linear constraints.
+In fact, concepts such as coherence and reconciliation, defined in full below, require the data to have only two important characteristics: the first is that they are multivariate, the second is that they adhere to linear constraints.
 
@@
 \begin{definition}[Coherent subspace]\label{def:cohspace}
-   The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which a set of linear constraints holds for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
+   The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which a some linear constraints hold for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
 \end{definition}
 
-To further illustrate, Figure~\ref{fig:3D_hierarchy} depicts the most simple three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.
+To further illustrate, Figure~\ref{fig:3D_hierarchy} depicts the simplest three variable hierarchy where $y_{Tot,t}=y_{A,t}+y_{B,t}$.
 The coherent subspace is depicted as a grey $2$-dimensional plane within $3$-dimensional space; i.e.
@@
 $(\bm{S}\bm{G})^2=\bm{S}\bm{G}$.
-However a much more important property of projection matrices, used in multiple instances below, is that any vector lying in the image of the projection will be mapped to itself by that projection \citep[see Lemma 2.4 in][for a proof]{rao1974}.
+However we also rely on another property of projection matrices, namely that any vector lying in the image of a projection is mapped to itself by that projection \citep[see Lemma 2.4 in][for a proof]{rao1974}.
 In our context this implies that for any $\bm{v}\in\mathfrak{s}$, $\bm{S}\bm{G}\bm{v}=\bm{v}$.
@@
 Consider the Euclidean distance between the target and a forecast.
-This is equivalent to the root of the sum of squared forecast errors over the entire hierarchy.
+This is equivalent to the square root of the sum of squared forecast errors over the entire hierarchy.
 Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$.
-The following theorem shows that reconciliation never increases, and in most cases reduces, the sum of squared errors of point forecasts.
+The following theorem shows that reconciliation never increases, the sum of squared errors of point forecasts.
 
@@
 First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.
-In particular, this measure is the root of the sum of squared forecast errors of \emph{all} variables in the hierarchy.
+In particular, this measure is the square root of the sum of squared forecast errors of \emph{all} variables in the hierarchy.
 Consequently, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to less accurate forecasts for individual series.
@@
 
-One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the root of the sum of squared errors of \emph{all} variables in the hierarchy.
+One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the square root of the sum of squared errors of \emph{all} variables in the hierarchy.
 A clear shortcoming of this measure of forecast accuracy is that forecast errors in all series should not necessarily be treated equally.
@@
 The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.
-As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is only true with respect to a loss function that depends on $\bm{W}$.
-If Euclidean distance (or mean squared error) is used, there will be cases where the MinT estimator does not improve upon base forecasts.
+As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is true only with respect to a loss function that depends on $\bm{W}$.
+If Euclidean distance (or mean squared error) is used, there will be realisations where the MinT estimator does not improve forecast accuracy relative to base forecasts.
 This will be demonstrated using a real data set in the empirical study in Section~\ref{sec:comparebase}.
@@
   \end{subfigure}
-  \caption{A schematic representing orthogonal and oblique reconciliations.
-The orange points in (a) represent in-sample errors.
-$\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$.
+  \caption{A schematic represention of orthogonal and oblique reconciliations.
+The orange points in (a) represent in-sample errors and $\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$.
 Grey points in (b) indicate potential base forecasts while the blue dot ${\hat{\bm y}}$ represents one such realisation.
@@
 
-Before turning our attention to the issue of bias itself it is important to state a sensible property that any reconciliation method should have.
+Before turning our attention to the issue of bias itself it is important to state a desirable property that any reconciliation method should have.
 That is if base forecasts are already coherent then reconciliation should not change the forecasts.
@@
 Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$, $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$.
-This is depicted in Figure~\ref{fig:Schematic_3D} where $\bm{\mu}_{t+h|t}$ is projected to a point $\bar{\bm{\mu}}$ in $\mathfrak{L}$.
-In this case, the expectation of reconciled forecast will be $\bar{\bm{\mu}}$ rather than $\bm{\mu}_{t+h|t}$ and hence biased.
+This is depicted in Figure~\ref{fig:Schematic_3D} where $\bm{\mu}$ is projected to a point ${\bm{\mu}^*}$ in $\mathfrak{L}$.
+In this case, the expectation of reconciled forecast will be ${\bm{\mu}^*}$ rather than $\bm{\mu}$ and hence biased.
 
@@
 Both of these conditions are equivalent to assuming that $\bm{S}\bm{G}$ is a projection matrix (see Section~\ref{app:projection-proof} in Appendix A for a proof).
-However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{G}\bm{S}=\bm{I}$.
+However, problems arise when viewing the preservation of unbiasedness through the prism of imposing the constraint $\bm{G}\bm{S}=\bm{I}$.
 This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.

### 2019-09-14 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
made mervyns changes

@@
 Our main contribution is to propose a geometric interpretation of the entire hierarchical forecasting problem.
-In this setting, we show that reconciled forecasts will have a number of attractive properties when they are obtained via projections.
-We believe that this is clearer and more intuitive than explanations based on regression modelling, notwithstanding the fact that regression based-methods themselves are indeed projections.
-As such, this paper is in part a review of existing results cast in a new light.
-In addition, we also derive three major and novel results.
+In this setting, we show that reconciled forecasts have a number of attractive properties when they are obtained via projections.
+We believe that this is clearer and more intuitive than explanations based on regression modelling.
+In addition to casting existing results in a new light, the geometric interpretation also allows us to derive three new important results.
 

### 2019-09-16 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Working Paper

@@
 \begin{definition}[Coherent subspace]\label{def:cohspace}
-   The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which a some linear constraints hold for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
+   The $m$-dimensional linear subspace $\mathfrak{s}\subset \mathbb{R}^n$ for which some linear constraints hold for all $\bm{y}\in\mathfrak{s}$ is defined as the \emph{coherent subspace}.
 \end{definition}
@@
 
-Defining concepts such as coherence and reconciliation in geometric terms provides new insights into forecast reconciliation methods.
+Defining concepts such as coherence and reconciliation in geometric terms provides new insights into hierarchical forecasting methods.
 We have also provided evidence that bias correction before reconciliation improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation.

### 2020-01-14 R1/Response.tex
added template for response

\documentclass[a4paper,11pt]{article}
\newif\ifblind
\blindfalse %Change this to \blindtrue or \blindfalse depending on whether paper should be blind.
\usepackage{dcolumn}
\newcolumntype{d}[1]{D{.}{.}{-1}}

\usepackage{xcolor,colortbl}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{caption} %captionsf
\usepackage{subcaption} %subcaptions
\usepackage{bbm} % more maths symbols
\usepackage{enumitem} % a b c itemize
\usepackage{pdfpages} % pdf as graphic
\makeatletter % so @ can be used
\setlength{\@fptop}{0pt} % Start graphic at top
\makeatother % turn off @
\usepackage{multirow} % Multirow in table
\usepackage{booktabs,caption,fixltx2e} % table caption with notes
\usepackage[flushleft]{threeparttable} % table caption with notes
\usepackage{setspace} % This is used in the title page
\usepackage{graphicx} % This is used to load the crest in the title page
\usepackage{geometry}
\usepackage{bm}
\usepackage{sectsty}
\usepackage{amssymb} % leqslant
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}

\begin{document}

	%\section{GENERAL COMMENTS TO THE REVIEWERS AND EDITOR}

	\section*{Detailed Response to Referee 1: Summary}

	\textit{The authors provide a geometric interpretation for reconciliation of hierarchical forecasts. They show why and how reconciliation via projection is guaranteed to improve squared forecast errors. They explore a couple of different ways for dealing with biased base forecasts in an application to Australian tourism flows. Overall the paper is well written and the geometric interpretations are an important contribution to the growing literature on forecast reconciliation. The	authors do a very good job explaining the geometric aspects, which lead to new insights. That being said, the contribution of the paper in its current form is mainly theoretical, as the empirical evaluation is not much of a contribution.  I do not think the paper meets the high standard set by the IJF in terms of empirical evaluation. I recommend that the authors revise their paper with a particular focus on strengthening its empirical contribution to more clearly	show the practical value of the geometric insights they derive. I hope that the authors will find my comments useful for improving their paper.}\\	
	Response.\\

	\section*{Detailed Response to Referee 1: Major comments}

	\begin{enumerate}

		\item \textit{When the empirical evaluation is focused on bias, then it would make sense to include an error that measures bias in addition to the squared error. Moreover, simply showing the MSE without any confidence intervals or measures of significance is not sufficient for the reader to assess the results. It would also be useful to show the MSE relative to the base forecasts or	the percentage improvement that is obtained. The best performing reconciliation method is MinT with shrinkage, but the authors never state	the value of the shrinkage parameter or how it was chosen. Similarly, they compare with variance scaling without explaining what they mean by variance scaling. In addition to the above mentioned shortcomings, I think the authors should reconsider their empirical evaluation. Maybe a second case study or a simulation study is needed to show the value of the geometric insights provided. We already know that MinT is better than OLS and WLS. What is the new and better reconciliation approach that has come from the geometric insights?}\\	
		Response.\\

		\item \textit{Improvement guarantees: The boxplot in Figure 8 shows that OLS
		always improves MSE, while this is not the case for the other reconcili-
		ation approaches. To gain a better understanding of the implications of
		Theorem 3.2, it would be useful to show that the other approaches always
		improve accuracy in their transformed spaces. What is the interpreta-
		tion of the transformed spaces and can the authors make the connection
		between these spaces and the choice of reconciliation approach and error
		measure more clear? For example, Hyndman et al. (2011); van Erven and
		Cugliari (2015) argued for selecting OLS to increase the importance of
		forecasting the aggregate. What is the argument for WLS or MinT and
		what is the corresponding consistent error measure?}\\
	    Response.\\

	    \end{enumerate}

	    \section*{Detailed Response to Referee 1:Minor Comments}

	    \begin{enumerate}

	    \item \textit{In the first half of the paper it feels like every other sentence includes a however. I suggest reducing the use of however.}\\
	    Response.\\

	    \item \textit{P. 2, l. 11: In several places the authors talk about adjusting forecasts ex-post. Although I understand what is meant, it gives the impression that forecasts are adjusted after observing the realized values.}\\
	    Response.\\

	    \item \textit{P. 2, l. 12: The authors discuss the regression formulation of forecast reconciliation. It would be useful to also make the connection to the optimization formulation considered by, e.g., van Erven and Cugliari (2015); Nystrup et al. (2020). This could also be useful for clarifying the connection between reconciliation approaches and error measures.}\\
	    Response.\\

	    \item \textit{P. 4, l. 22: forf}\\
	    Response.\\

	    \item \textit{P. 10, l. 12: the comma should not be there.}\\
	    Response.\\

	    \item \textit{P. 11, Figure 3: usually a small square is drawn in the corner of the triangle to show orthogonality.}\\
	    Response.\\

	    \item \textit{P. 17, l. 18: i,e.}\\
	    Response.\\

	    \item \textit{P. 26, l. 14: the authors mention that the full results are available upon request. I suggest including them in an online supplementary appendix.}\\
	    Response.\\

	    \item \textit{P. 27, Conclusions: The authors should comment on the implications of the non-uniqueness of the S matrix for future work on cross-temporal reconciliation (Kourentzes and Athanasopoulos, 2019).}\\
	    Response.\\

    \end{enumerate}

    \section*{Detailed Response to Referee 2}

	\begin{enumerate}

	\item \textit{This type of paper makes me regret not investing more time into geometric interpretation because as shown here, it offers an elegant and intuitive way to showcase results related to data integration and reconciliation. The paper is extremely well written, with a great flow and thoughtful considerations. Figure 4 and its description are exemplary successful in their simplicity and effectiveness. The discussion of theorem 3.1 on page 11 is another example of thoroughness and clever insight.}\\
	Response.\\

    \item\textit{I found only one statement in the paper that could be better supported by evidence on page 8 lines 14 when the author(s) refer to multivariate modeling. State-space approaches have also been shown to be theoretically successful is solving these problems although maybe not to the large scale needed for very detailed and complex hierarchical systems. A comment or comparative discussion to the multivariate modeling may be useful.}\\
    Response.\\

    \item\textit{In the context of real-life application and either for small discussion here or future work, I am wondering if and how the author(s) coherent subspace that would be defined with hard boundaries. For example, the set of Australian tourism flow data and any forecasts that would be considered useful should be non-negative and likely upper bounded (if only by the size of the global population or other more realistic subject matter expert opinion). In many other reconciliation problems, these boundary constraints affect the feasible space. In the context here, could a convoluted case lead to an orthogonal projection be coherent but outside the desired constrained subspace?}\\
    Response.\\

    \item\textit{Please correct the minor typo just before section 2 (forf).}\\
    Response.\\

    \end{enumerate}

\end{document}

### 2020-01-14 R1/Letter.tex
added template for response

\documentclass[11pt,a4paper]{letter}
\addtolength{\topmargin}{-2.5cm}
\addtolength{\textheight}{5cm}
\signature{George Athanasopoulos}
\date{}

\makeatletter
\def\@texttop{}
\makeatother

%\makelabels
\begin{document}
 \begin{letter}{To: Pierre Pinson\\
 	Editor, International Journal of Forecasting\\
 	DTU Elektro\\
 	348, {\O}rsteds Pl., \\
 	2800 Kongens Lyngby, Denmark}
    From: George Athanasopoulos\\
    Department of Econometrics and Business Statistics\\
    Monash University\\
    Melbourne, VIC, 3800, Australia

 \opening{ March 12, 2018\\ \\Dear Professor Pinson,}
%\textbf{RE: Revision for Computational and Graphical Statistics by Tan Ban Kheng, Anastasios
%	Panagiotelis and George Athanasopoulos}
 \medskip

Please find attached a revised manuscript for ``Forecast reconciliation: a geometric view with new insights on bias correction" by Anastasios Panagiotelis, Puwasala Gamakumara, George Athanasopoulos and Rob Hyndman for your consideration for publication in International Journal of Forecasting. We are very excited to have been given the opportunity to revise and resubmit. We carefully considered the comments offered by the two reviewers. Herein, we briefly summarize the major changes in the revision:
\begin{enumerate}
	\item blah
\end{enumerate}

The comments made by the referees warrant a detailed response which is appended to this letter. Overall, we believe we have now addressed all the concerns raised. We thank the referees for their comments as addressing these has significantly improved our manuscript. We look forward to hearing from you.

 \closing{With kind regards and best wishes,}

 \end{letter}
\end{document}

### 2020-01-14 R1/Response.tex
simple corrections made to paper and response

@@
 Although I understand what is meant, it gives the impression that forecasts are adjusted after observing the realized values.}\\
-	    Response.\\
+	    We have either removed all use of the term `ex post' or stated `ex post of base forecasting' to avoid the potential for confusion.\\
 
@@
 	    \item \textit{P. 4, l. 22: forf}\\
-	    Response.\\
+	    This has been corrected.\\
 
 	    \item \textit{P. 10, l. 12: the comma should not be there.}\\
-	    Response.\\
+	    The comma has been removed.\\
 
@@
 	    \item \textit{P. 17, l. 18: i,e.}\\
-	    Response.\\
+	    We believe that you are asking that we include a comma after this instance of `i.e' and we have made this correction.\\
 
@@
     \item\textit{Please correct the minor typo just before section 2 (forf).}\\
-    Response.\\
+    We have made this correction.\\
 

### 2020-01-14 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Submission docs
simple corrections made to paper and response

@@
   \begin{center}
-    {\LARGE\bf Hierarchical Forecasts Reconciliation}
+    {\LARGE\bf Forecast reconciliation: A geometric view with new insights on bias correction}
   \end{center}
@@
 The past decade has seen rapid development in methodologies for forecasting time series that follow a hierarchical aggregation structure.
-Of particular prominence have been \emph{forecast reconciliation} methods involving two steps: first separate forecasts are produced for all series, then these are adjusted ex~post to ensure coherence with aggregation constraints.
+Of particular prominence have been \emph{forecast reconciliation} methods involving two steps: first separate forecasts are produced for all series, then these are adjusted to ensure coherence with aggregation constraints.
 Forecast reconciliation has mostly been formulated using a regression model, see \citet{Hyndman2011} and \citet{WicEtAl2019} for examples.
@@
 In Section \ref{sec:EmpStudy} we conduct an extensive empirical application to domestic tourism flow in Australia with two objectives; first to demonstrate the theorems discussed in Section~\ref{sec:Reconciliation}, second to evaluate the methods for bias correction discussed in Section~\ref{sec:BiasInRecon}.
-Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the future research directions forf forecast reconciliation.
+Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the future research directions for forecast reconciliation.
 
@@
 However, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.\footnote{There are some special cases of using simple approaches such as na\"{i}ve, which extrapolate the coherent nature of the data to the forecasts.} This problem of incoherent forecasts cannot in general be solved by multivariate modelling either.
-Instead, the solution is to make an ex post adjustment that ensures coherence, a process known as \emph{forecast reconciliation}
+Instead, the solution is to make an adjustment, ex post of base forecasting, that ensures coherence, a process known as \emph{forecast reconciliation}
 
@@
 We refrain from any discussion of regression models focusing instead on geometric interpretations.
-However the connection between OLS and orthogonal projection should be clear, in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection of the response onto the span of the regressors.
+However the connection between OLS and orthogonal projection should be clear in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection of the response onto the span of the regressors.
 
@@
 The above result holds when the projection $\bm{S}\bm{G}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general.
-To describe this more explicitly suppose $\bm{S}\bm{G}$ has as its image $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e.
-$\mathfrak{L}\subset\mathfrak{s}$.
+To describe this more explicitly suppose $\bm{S}\bm{G}$ has as its image $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e., $\mathfrak{L}\subset\mathfrak{s}$.
 Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$, $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$.

### 2020-01-15 R1/Response.tex
easy comments from referees addressed

@@
 I hope that the authors will find my comments useful for improving their paper.}\\
-	Response.\\
+
+	We thank the referee for their comments acknowledging the theoretical contributions of the paper.
+While we believe that more theory focused papers lie within the scope of the International Journal of Forecasting, we also agree with the referee that the empirical section could be greatly improved.
+We have endeavoured to do this in ways outlined in our responses below.\\
 
@@
 
-		\item \textit{When the empirical evaluation is focused on bias, then it would make sense to include an error that measures bias in addition to the squared error.
-Moreover, simply showing the MSE without any confidence intervals or measures of significance is not sufficient for the reader to assess the results.
-It would also be useful to show the MSE relative to the base forecasts or	the percentage improvement that is obtained.
-The best performing reconciliation method is MinT with shrinkage, but the authors never state	the value of the shrinkage parameter or how it was chosen.
-Similarly, they compare with variance scaling without explaining what they mean by variance scaling.
-In addition to the above mentioned shortcomings, I think the authors should reconsider their empirical evaluation.
+		\item \textit{When the empirical evaluation is focused on bias, then it would make sense to include an error that measures bias in addition to the squared error.}\\
+
+		We now also report the mean error for all methods to highlight bias. TO DO (GEORGE)\\
+
+		\textit{Moreover, simply showing the MSE without any confidence intervals or measures of significance is not sufficient for the reader to assess the results.
+It would also be useful to show the MSE relative to the base forecasts or the percentage improvement that is obtained.} \\
+
+		We now include a Nemenyi comparison of the methods and report results in terms of percentage improvement over base forecasts. TO DO (GEORGE)\\
+
+	    \textit{The best performing reconciliation method is MinT with shrinkage, but the authors never state	the value of the shrinkage parameter or how it was chosen.
+Similarly, they compare with variance scaling without explaining what they mean by variance scaling.}\\
+
+	    The shrinkage estimator is that of Sch\"afer and Strimmer~(2005).
+Details on this method (including the choice of shrinkage parameter) are now provided.
+Similarly, we now provide more detail on variance scaling, which simply refers to using the variance of one step ahead in-sample forecast errors.\\
+
+	    \textit{In addition to the above mentioned shortcomings, I think the authors should reconsider their empirical evaluation.
 Maybe a second case study or a simulation study is needed to show the value of the geometric insights provided.
@@
 What is the new and better reconciliation approach that has come from the geometric insights?}\\
-		Response.\\
+
+		Propose a generalised MinT.
+TO DO (TAS).
+Demonstrating these additional contributions in the context of our existing empirical example has lengthened the paper considerably.
+Therefore, we prefer to refrain from including a second empirical demonstration.\\
 
@@
 		between these spaces and the choice of reconciliation approach and error
-		measure more clear? For example, Hyndman et al. (2011); van Erven and
+		measure more clear?}\\
+
+	    We now report results for an MSE in the transformed space and show blah blah blah TO DO.
+
+		\textit{For example, Hyndman et al. (2011); van Erven and
 		Cugliari (2015) argued for selecting OLS to increase the importance of
@@
 		what is the corresponding consistent error measure?}\\
-	    Response.\\
+
+	    We would like to point out that any argument made by Hyndman et al.
+(2011) or van Erven and Cugliari (2015) that OLS reconciliation somehow targets and improves the aggregate series is based on empirical rather than theoretical evidence.
+Address this misconception, which appears to be common, has in fact been a major motivation behind us writing the paper.
+We hope that with the revision to the paper these distinctions are clearer.\\
 
@@
 	    \item \textit{In the first half of the paper it feels like every other sentence includes a however. I suggest reducing the use of however.}\\
-	    Response.\\
+
+	    We have reduced the usage of the word however substantially, from over 12 instances to just 3.\\
 
@@
 Although I understand what is meant, it gives the impression that forecasts are adjusted after observing the realized values.}\\
+
 	    We have either removed all use of the term `ex post' or stated `ex post of base forecasting' to avoid the potential for confusion.\\
@@
 This could also be useful for clarifying the connection between reconciliation approaches and error measures.}\\
-	    Response.\\
+
+	    Must reread these papers and comment.  TO DO (TAS)\\
 
@@
 	    \item \textit{P. 11, Figure 3: usually a small square is drawn in the corner of the triangle to show orthogonality.}\\
-	    Response.\\
+	    We have made this change to all Figures. TO DO (George)\\
 
@@
 	    \item \textit{P. 26, l. 14: the authors mention that the full results are available upon request. I suggest including them in an online supplementary appendix.}\\
-	    Response.\\
+	    We now include these an an online supplement. TO DO\\
 
@@
 27, Conclusions: The authors should comment on the implications of the non-uniqueness of the S matrix for future work on cross-temporal reconciliation (Kourentzes and Athanasopoulos, 2019).}\\
-	    Response.\\
+	    TO DO (GEORGE).\\
 
@@
 The discussion of theorem 3.1 on page 11 is another example of thoroughness and clever insight.}\\
-	Response.\\
+
+	We thank the referee for these kind comments.\\
 
@@
 A comment or comparative discussion to the multivariate modeling may be useful.}\\
-    Response.\\
+
+    We have rewritten this sentence and now explicitly include the case of state space models in our discussion.\\
 
@@
 In the context here, could a convoluted case lead to an orthogonal projection be coherent but outside the desired constrained subspace?}\\
-    Response.\\
+    It is indeed possible for an orthogonal projection to reconcile a set of positive base forecasts into a vector that includes some negative values.
+This is a fairly pathological case and does not arise in the application that we consider (and many other applications that we have considered in other work).
+We do agree that this problem may arise in other contexts so we now include some discussion of this issue and cite some recent work that addresses this problem.
+TO DO (TAS)\\
 

### 2020-01-15 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
easy comments from referees addressed

@@
 In Section \ref{sec:EmpStudy} we conduct an extensive empirical application to domestic tourism flow in Australia with two objectives; first to demonstrate the theorems discussed in Section~\ref{sec:Reconciliation}, second to evaluate the methods for bias correction discussed in Section~\ref{sec:BiasInRecon}.
-Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the future research directions for forecast reconciliation.
+Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the future research directions {\color{blue}for} forecast reconciliation.
 
@@
 In Figure~\ref{fig:3D_hierarchy}, these columns are $\vec{s}_1=(1,1,0)'$ and $\vec{s}_2=(1,0,1)'$.
-However, it is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom-level series, $y_{A,t}$ and $y_{B,t}$.
+It is equally important to recognise that the hierarchy could also have been defined in terms of $y_{Tot,t}$ and $y_{A,t}$ rather than the bottom-level series, $y_{A,t}$ and $y_{B,t}$.
 In this case the corresponding `$\bm{S}$ matrix' would have columns $(1,0,1)'$ and $(0,1,-1)'$.
@@
 
-Forecasting a single level of the hierarchy did not, however echo common practice within many industries.
+Forecasting a single level of the hierarchy did not echo common practice within many industries.
 In many organisations different departments or `silos' each produced their own forecasts, often with their own information sets and judgemental adjustments.
@@
 Second, modelling higher level series often identifies features such as trend and seasonality that cannot be detected in noisy disaggregate data.
-However, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.\footnote{There are some special cases of using simple approaches such as na\"{i}ve, which extrapolate the coherent nature of the data to the forecasts.} This problem of incoherent forecasts cannot in general be solved by multivariate modelling either.
-Instead, the solution is to make an adjustment, ex post of base forecasting, that ensures coherence, a process known as \emph{forecast reconciliation}
+However, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.\footnote{There are some special cases of using simple approaches such as na\"{i}ve, which extrapolate the coherent nature of the data to the forecasts.} {\color{blue}While the problem of incoherent forecasts can be addressed by some multivariate approaches, including state space models, these can not always be generalised to models with more complicated features or scaled up to high-dimensional problems.}  Instead, the solution is to make an adjustment, {\color{blue}ex post of base forecasting,} that ensures coherence, a process known as \emph{forecast reconciliation}
 
@@
 $(\bm{S}\bm{G})^2=\bm{S}\bm{G}$.
-However we also rely on another property of projection matrices, namely that any vector lying in the image of a projection is mapped to itself by that projection \citep[see Lemma 2.4 in][for a proof]{rao1974}.
+We also rely on another property of projection matrices, namely that any vector lying in the image of a projection is mapped to itself by that projection \citep[see Lemma 2.4 in][for a proof]{rao1974}.
 In our context this implies that for any $\bm{v}\in\mathfrak{s}$, $\bm{S}\bm{G}\bm{v}=\bm{v}$.
@@
 We refrain from any discussion of regression models focusing instead on geometric interpretations.
-However the connection between OLS and orthogonal projection should be clear in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection of the response onto the span of the regressors.
+{\color{blue} Nonetheless,} the connection between OLS and orthogonal projection should be clear in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection of the response onto the span of the regressors.
 
@@
 
-However, in other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood.
+In other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood.
 First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.
@@
 It should be noted that $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix in the usual Euclidean geometry.
-However this matrix can be considered to be an orthogonal projection for a different geometry defined by the norm\break $||\bm{v}||_{\bm{W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
+{\color{blue}Alternatively,} this matrix can be considered to be an orthogonal projection for a different geometry defined by the norm\break $||\bm{v}||_{\bm{W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
 One way to understand this geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$.
@@
 The above result holds when the projection $\bm{S}\bm{G}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general.
-To describe this more explicitly suppose $\bm{S}\bm{G}$ has as its image $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e., $\mathfrak{L}\subset\mathfrak{s}$.
+To describe this more explicitly suppose $\bm{S}\bm{G}$ has as its image $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, {\color{blue}i.e.,} $\mathfrak{L}\subset\mathfrak{s}$.
 Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$, $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$.
@@
 $\bm{S}\bm{G}\bm{S}\bm{G}=\bm{S}\bm{G}$ and therefore $\bm{S}\bm{G}$ is a projection matrix.
-However the image of this projection is not an $m$-dimensional subspace but a $1$-dimensional subspace.
+However, the image of this projection is not an $m$-dimensional subspace but a $1$-dimensional subspace.
 As such, top-down reconciliation produces biased forecasts even when the base forecasts are unbiased.
@@
 Both of these conditions are equivalent to assuming that $\bm{S}\bm{G}$ is a projection matrix (see Section~\ref{app:projection-proof} in Appendix A for a proof).
-However, problems arise when viewing the preservation of unbiasedness through the prism of imposing the constraint $\bm{G}\bm{S}=\bm{I}$.
+{\color{blue}{Despite this connection,}} problems arise when viewing the preservation of unbiasedness through the prism of imposing the constraint $\bm{G}\bm{S}=\bm{I}$.
 This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.
-However, equipped with a geometric understanding of the problem, we would advise against this approach.
+Equipped with a geometric understanding of the problem, we would advise against this approach.
 The constraint $\bm{G}\bm{S}=\bm{I}$ is not just about bias.
@@
 Previous studies have found that reconciliation improves point forecast accuracy in domestic tourism flows for Australia \citep[see for example][]{Athanasopoulos2009, Hyndman2011,WicEtAl2019}.
-However, our motivation in this study is twofold.
+Our motivation in this study is twofold.
 First, we demonstrate the implications of Theorem~\ref{th:distred} by comparing reconciled and base forecasts.
@@
 
-After obtaining the base forecasts these are reconciled using three different projection methods: OLS reconciliation, MinT using a shrinkage estimator for $\bm{W}$ and WLS reconciliation using variance scaling.
-Squared forecast errors are computed for each series and aggregated across the entire hierarchy; i.e., we compute the loss function described in Section~\ref{sec:orthogonal}.
+After obtaining the base forecasts these are reconciled using three different projection methods: OLS, MinT and WLS.
+{\color{blue}For MinT, the shrinkage estimator of \cite{Schafer2005} is used, i.e., $\bm{W}^{\text{MinT}} = \tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
+\begin{equation*}
+\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{\sigma}_{ij})}{\sum_{i \neq j}{\hat{\sigma}}^2_{ij}}\,,
+\end{equation*}
+where $\sigma_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}^{\text{sam}}$.
+For WLS, variance scaling is used, i.e., $\bm{W}^{\text{WLS}}=\text{diag}(\hat{\bm{\Sigma}})$.} Squared forecast errors are computed for each series and aggregated across the entire hierarchy; i.e., we compute the loss function described in Section~\ref{sec:orthogonal}.
 We then compute the difference in this loss function between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate.

### 2020-01-15 R1/Response.tex
a few more minor changes

@@
 
-		\item \textit{Improvement guarantees: The boxplot in Figure 8 shows that OLS
-		always improves MSE, while this is not the case for the other reconcili-
-		ation approaches. To gain a better understanding of the implications of
-		Theorem 3.2, it would be useful to show that the other approaches always
-		improve accuracy in their transformed spaces. What is the interpreta-
-		tion of the transformed spaces and can the authors make the connection
-		between these spaces and the choice of reconciliation approach and error
-		measure more clear?}\\
+		\item \textit{Improvement guarantees: The boxplot in Figure 8 shows that OLS always improves MSE, while this is not the case for the other reconciliation approaches.
+To gain a better understanding of the implications of Theorem 3.2, it would be useful to show that the other approaches always
+		improve accuracy in their transformed spaces.}\\
 
-	    We now report results for an MSE in the transformed space and show blah blah blah TO DO.
+	    Report results for two different error metrics and include this. TO DO\\
+
+		\textit{What is the interpretation of the transformed spaces and can the authors make the connection	between these spaces and the choice of reconciliation approach and error measure more clear?}\\
+
+	    Discussion to go in here TO DO (TAS).\\
 
@@
 (2011) or van Erven and Cugliari (2015) that OLS reconciliation somehow targets and improves the aggregate series is based on empirical rather than theoretical evidence.
-Address this misconception, which appears to be common, has in fact been a major motivation behind us writing the paper.
+Addressing this misconception, which appears to be common, has in fact been a major motivation behind us writing the paper.
 We hope that with the revision to the paper these distinctions are clearer.\\
@@
 
-	    We have reduced the usage of the word however substantially, from over 12 instances to just 3.\\
+	    We have reduced the usage of the word ``however'' substantially, from twelve instances to just three.\\
 
@@
 	    \item \textit{P. 11, Figure 3: usually a small square is drawn in the corner of the triangle to show orthogonality.}\\
-	    We have made this change to all Figures. TO DO (George)\\
+	    We have made this change to all Figures. TO DO (GEORGE)\\
 
 	    \item \textit{P. 17, l. 18: i,e.}\\
-	    We believe that you are asking that we include a comma after this instance of `i.e' and we have made this correction.\\
+	    We have made this correction.\\
 
@@
 
-	\begin{enumerate}
-
-	\item \textit{This type of paper makes me regret not investing more time into geometric interpretation because as shown here, it offers an elegant and intuitive way to showcase results related to data integration and reconciliation.
+	\noindent \textit{This type of paper makes me regret not investing more time into geometric interpretation because as shown here, it offers an elegant and intuitive way to showcase results related to data integration and reconciliation.
 The paper is extremely well written, with a great flow and thoughtful considerations.
@@
 
-	We thank the referee for these kind comments.\\
+	\noindent We thank the referee for these kind comments.\\
 
-    \item\textit{I found only one statement in the paper that could be better supported by evidence on page 8 lines 14 when the author(s) refer to multivariate modeling.
+    \noindent\textit{I found only one statement in the paper that could be better supported by evidence on page 8 lines 14 when the author(s) refer to multivariate modeling.
 State-space approaches have also been shown to be theoretically successful is solving these problems although maybe not to the large scale needed for very detailed and complex hierarchical systems.
@@
 
-    We have rewritten this sentence and now explicitly include the case of state space models in our discussion.\\
+    \noindent We have rewritten this sentence and now explicitly include the case of state space models in our discussion.\\
 
-    \item\textit{In the context of real-life application and either for small discussion here or future work, I am wondering if and how the author(s) coherent subspace that would be defined with hard boundaries.
+    \noindent\textit{In the context of real-life application and either for small discussion here or future work, I am wondering if and how the author(s) coherent subspace that would be defined with hard boundaries.
 For example, the set of Australian tourism flow data and any forecasts that would be considered useful should be non-negative and likely upper bounded (if only by the size of the global population or other more realistic subject matter expert opinion).
@@
 In the context here, could a convoluted case lead to an orthogonal projection be coherent but outside the desired constrained subspace?}\\
-    It is indeed possible for an orthogonal projection to reconcile a set of positive base forecasts into a vector that includes some negative values.
+
+    \noindent It is indeed possible for an orthogonal projection to reconcile a set of positive base forecasts into a vector that includes some negative values.
 This is a fairly pathological case and does not arise in the application that we consider (and many other applications that we have considered in other work).
@@
 
-    \item\textit{Please correct the minor typo just before section 2 (forf).}\\
+    \noindent\textit{Please correct the minor typo just before section 2 (forf).}\\
     We have made this correction.\\
 
-    \end{enumerate}
-
 \end{document}

### 2020-01-15 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
a few more minor changes

@@
 Let $\bm{y}_{t+h}$ be the realisation of the data generating process at time $t+h$.
-The following theorem shows that reconciliation never increases, the sum of squared errors of point forecasts.
+The following theorem shows that reconciliation never increases the sum of squared errors of point forecasts.
 
@@
 The above result holds when the projection $\bm{S}\bm{G}$ has the coherent subspace $\mathfrak{s}$ as its image and not for all projection matrices in general.
-To describe this more explicitly suppose $\bm{S}\bm{G}$ has as its image $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, {\color{blue}i.e.,} $\mathfrak{L}\subset\mathfrak{s}$.
+To describe this more explicitly suppose $\bm{S}\bm{G}$ has as its image $\mathfrak{L}$ which is itself a lower dimensional linear subspace of $\mathfrak{s}$, i.e., $\mathfrak{L}\subset\mathfrak{s}$.
 Then for $\left\{\bm{\mu}_{t+h|t}:\bm{\mu}_{t+h|t}\in\mathfrak{s},\bm{\mu}_{t+h|t}\notin\mathfrak{L}\right\}$, $\bm{S}\bm{G}\bm{\mu}_{t+h|t} \ne \bm{\mu}_{t+h|t}$.
@@
 where $\bm{p} = (p_1,\dots,p_m)'$ is an $m$-dimensional vector consisting a set of proportions used to disaggregate the top-level forecast.
-In this case it can be verified that $\bm{S}\bm{G}$ is idempotent, i,e.
-$\bm{S}\bm{G}\bm{S}\bm{G}=\bm{S}\bm{G}$ and therefore $\bm{S}\bm{G}$ is a projection matrix.
+In this case it can be verified that $\bm{S}\bm{G}$ is idempotent, {\color{blue} i.e.,} $\bm{S}\bm{G}\bm{S}\bm{G}=\bm{S}\bm{G}$ and therefore $\bm{S}\bm{G}$ is a projection matrix.
 However, the image of this projection is not an $m$-dimensional subspace but a $1$-dimensional subspace.

### 2020-01-16 R1/Response.tex
minor changes

@@
 
-		Propose a generalised MinT.
+		We now propose a generalised version of MinT, to be used with a loss function where $\bm{W}$ is defined by the context of the problem.
+In our empirical study we provide one such example of a loss function.
+We show that blah blah blah.
 TO DO (TAS).
@@
 
-	    Discussion to go in here TO DO (TAS).\\
+	    Reflecting on this issue has led us towards the development of a generalised version of MinT which we now include in the paper.
+Briefly, the geometric insight allows us to decouple the issue of choice of loss function (which may be influenced by the context of the forecasting problem) from the issue of the properties of a given reconciliation method (which is a statistical question).
+TO DO (TAS).\\
 

### 2020-01-16 R1/Letter.tex
minor changes

@@
 \begin{enumerate}
-	\item blah
+	\item We introduce a modification of MinT that can be used with a user defined loss function.  We demonstrate in the empirical example that...
+	\item We have greatly expanded the empirical study including more measures of forecast accuracy (including those specifically measuring bias), a Nemenyi evaluation to highlight where differences in forecast accuracy are significant.
+	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negativity, 
 \end{enumerate}

### 2020-01-16 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
minor changes
GMinT written up

@@
 While the properties discussed so far hold for any projection matrix, the MinT method of \citet{WicEtAl2019} has an additional optimality property.
-\citet{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by an oblique projection with a particular choice of $\bm{W}$.
-Their choice is that $\bm{W}$ should be the forecast error covariance matrix where errors come from using the base forecasts.
+\citet{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by the oblique projection $\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}$.
+Here, $\bm{\Sigma}$ is the forecast error covariance matrix with errors come from using the base forecasts.
 Although the base forecast error covariance matrix is unknown, it can be estimated using in-sample errors.
@@
 
+{\color{blue}
+
+\subsection{Generalised MinT}
+
+Consider a loss function given by $\|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|_{\bm{W}^{-1}}$.
+Rather than choosing $\bm{W}$ by statistical considerations (as is the case with the MinT method), in some cases an alternative choice of $\bm{W}$ may be more appropriate in the forecasting problem.
+For instance, in our empirical example on the number of tourists visiting different regions in Australia, a sensible loss function may be weighted by the average spend of each tourist in that region.
+By theorem~\ref{th:gdistred} we can obtain a reconciliation method guaranteed to improve upon base forecasts according to this loss function.
+This method is an orthogonal projection in the transformed space.
+
+Since MinT has been shown to outperform OLS in a number of contexts there may be some merit to generalising MinT to account for user-defined loss functions.
+That is rather than aiming to minimising the trace of the variance covariance matrix of forecast errors, the aim can be to minimise the trace of the variance covariance matrix of the forecast errors \textit{after} transformation to a generalised Euclidean space defined by ${\bm W}$.
+The projection that minimises the trace of variance covariance matrix of ${\bm W}^{-1/2}{y-\hat{\bm y}}$ can be shown to be
+\begin{equation*}
+\bm{S}\left(\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\bm{S}\right)^{-1}\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\,,
+\end{equation*} 
+where $\bm{W}^{-1/2}$ is any matrix such that $\bm{W}^{-1/2}\bm{W}^{-1/2}$.
+To the best of our knowledge, this method, which we call generalised MinT has not been proposed so far in the literature.
+Generalised MinT allows the choice of loss function to be decoupled from the choice of an oblique projection with attractive statistical properties.
+In these past, these issues have often been conflated, since MinT is often defined as the oblique projection where ${\bm W}$ is set to be $\hat{{\bm \Sigma}}$.
+
+}
 \section{Bias in forecast reconciliation}\label{sec:BiasInRecon}

### 2020-01-16 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
GMinT tidied up

--- 2020-01-15 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
@@
 
+{\color{blue}
+
+\subsection{Generalised MinT}
+
+As discussed in the previous section, the MinT method has a motivation that is quite separate from the considerations of Theorem~\ref{th:gdistred}.
+In spite of this, it is also true that Theorem~\ref{th:gdistred} guarantees that MinT will always improve upon base forecasts when the loss function is based on the norm $\|.\|_{\bm{\Sigma}^{-1}}$.
+This will be verified in our empirical example in Section~\ref{sec:EmpStudy}.
+For this reason there is the potential to conflate the choice of loss function, with the desire to attain the attractive statistical properties of trace minimisation.
+We not propose a generalisation of the MinT method that uncouples these two ideas.
+
+Consider a loss function given based on $\|.\|_{\bm{W}^{-1}}$ where the choice of $\bm{W}$ is determined by the context of the forecasting problem rather than by statistical considerations.
+For instance, our empirical example in Section~\ref{sec:EmpStudy} considers the number of tourists visiting different regions in Australia.
+Here, a sensible loss function may weight tourist numbers by the average spend of tourists in each region.
+Theorem~\ref{th:gdistred} suggests a reconciliation that is guaranteed to improve base forecasts with respect to the loss function based on $\bm{W}$.
+This is an orthogonal projection in the space transformed by pre-multiplication by $W^{-1/2}$.
+
+In the case where $\bm{W}=\bm{I}$, it has been established that MinT often outperform OLS.
+Therefore we propose a generalisation of MinT that accounts for user-defined loss functions.
+Rather than minimising the trace of the variance covariance matrix of forecast errors, the aim is to minimise the trace of the variance covariance matrix of the \textit{transformed} forecast errors.
+The projection that minimises the trace of variance covariance matrix of ${\bm W}^{-1/2}{y-\hat{\bm y}}$ is $\bm{S}\bm{G}^{\text{GMinT}}$, where
+\begin{equation*}
+\bm{G}^{\text{GMinT}}=\left(\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\bm{S}\right)^{-1}\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\,.
+\end{equation*} 
+To the best of our knowledge, this method, which we call generalised MinT has not been proposed so far in the literature.
+The key advantage of Generalised MinT allows the choice of loss function to be decoupled from the choice of an oblique projection with attractive statistical properties.
+
+}
 \section{Bias in forecast reconciliation}\label{sec:BiasInRecon}

### 2020-01-16 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added discussion of degenerate loss functions and a few other minor things

--- 2020-01-15 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
@@
 While the properties discussed so far hold for any projection matrix, the MinT method of \citet{WicEtAl2019} has an additional optimality property.
-\citet{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by an oblique projection with a particular choice of $\bm{W}$.
-Their choice is that $\bm{W}$ should be the forecast error covariance matrix where errors come from using the base forecasts.
+\citet{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by the oblique projection {\color{blue} $\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}$}.
+Here, {\color{blue}$\bm{\Sigma}$} is the forecast error covariance matrix with errors come from using the base forecasts.
 Although the base forecast error covariance matrix is unknown, it can be estimated using in-sample errors.
@@
 
+{\color{blue}
+
+\subsection{Generalised MinT}
+
+As discussed in the previous section, the MinT method has a motivation that is quite separate from the considerations of Theorem~\ref{th:gdistred}.
+In spite of this, it is also true that Theorem~\ref{th:gdistred} guarantees that MinT will always improve upon base forecasts when the loss function is based on the norm $\|.\|_{\bm{\Sigma}^{-1}}$.
+This will be verified in our empirical example in Section~\ref{sec:EmpStudy}.
+For this reason there is the potential to conflate the choice of loss function, with the desire to attain the attractive statistical properties of trace minimisation.
+We now propose a generalisation of the MinT method that uncouples these two ideas.
+
+Consider a loss function based on $\|.\|_{\bm{W}^{-1}}$ where the choice of $\bm{W}$ is determined by the context of the forecasting problem, rather than by statistical considerations.
+For instance, our empirical example in Section~\ref{sec:EmpStudy} considers the number of tourists visiting different regions in Australia.
+Here, a sensible loss function may weight tourist numbers by the average spend of tourists in each region.
+Theorem~\ref{th:gdistred} provides a guarantee to improve upon base forecasts with respect to the loss function based on $\bm{W}$.
+This is an orthogonal projection in the space transformed after pre-multiplying by ${\bm W}^{-1/2}$.
+
+In the case where $\bm{W}=\bm{I}$, it has been established that MinT reconciliation often outperform OLS reconciliation in a statistical sense.
+Therefore we propose a generalisation of MinT that maintains trace minimising properties but also accounts for user-defined loss functions.
+The aim is to minimise the trace of the variance covariance matrix of the \textit{transformed} forecast errors rather than the original errors.
+The projection achieves this is $\bm{S}\bm{G}^{\text{GMinT}}$, where
+\begin{equation*}
+\bm{G}^{\text{GMinT}}=\left(\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\bm{S}\right)^{-1}\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\,.
+\end{equation*} 
+To the best of our knowledge, this method, which we call Generalised MinT has not been proposed so far in the literature.
+The key advantage of Generalised MinT allows the choice of loss function to be decoupled from the choice of an oblique projection with attractive statistical properties.
+
+As an important caveat, it should be noted that rank deficient choices of $\bm{W}$ will in most cases lead to no solution.
+For instance, it is not uncommon in the hierarchical forecasting literature that the overall aggregate is of greatest interest.
+This may suggest a loss function that places a weight of one on forecast errors of the overall aggregate and a weight of zero on errors in all other series.
+In this case, $\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\bm{S}$ is rank deficient and cannot be inverted.
+To be able to accrue the benefits of reconciliation by `borrowing strength' from other series, the loss function must penalise errors in those series.
+
+}
 \section{Bias in forecast reconciliation}\label{sec:BiasInRecon}

### 2020-01-17 Application-R/Application-TourismData/Final-results/TourismData-Final-resultsR1.Rmd
Calculating ME

--- 2019-09-02 Application-R/Application-TourismData/Final-results/TourismData-Final-results.Rmd
@@
   html_document: default
-date: "31 July 2019"
+date: "Jan 2020"
 ---
@@
 
-# Log Transformation with 100 observations of training window (Average MSE calculated over 140 replications)
+# Log Transformation with 100 observations of training window (ME and MSE calculated over 140 replications)
 
@@
 
+DF_LogTrans_WL100 <- DF_LogTrans_WL100 %>% 
+  mutate(F.method=recode(F.method, `Bias` = 'Biased')) 
+# so that we don't confuse Biased forecasts with ME
+
 DF_LogTrans_WL100 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_WL100
+DF_LogTrans_WL100 %>% mutate(ME = `Actual` - `Forecasts`) -> DF_LogTrans_WL100
 
+# ME
+DF_LogTrans_WL100 %>% 
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
+  filter(Forecast_Horizon == 1) %>% 
+  ungroup() %>% 
+  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_ME_h1
+
+Avg_Log_WL100_ME_h1 %>% 
+  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
+                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
+  spread(key = F.method, value = ME) %>% 
+  kable(format = "latex",)
+
+#MSE
 DF_LogTrans_WL100 %>% 
@@
 
-# Log Transformation with 180 observations of training window (Average MSE calculated over 60 replications)
+# Log Transformation with 180 observations of training window (ME and MSE calculated over 60 replications)
 
@@
 
+DF_LogTrans_WL180 <- DF_LogTrans_WL180 %>% 
+  mutate(F.method=recode(F.method, `Bias` = 'Biased')) 
+# so that we don't confuse Biased forecasts with ME
+
 DF_LogTrans_WL180 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_WL180
+DF_LogTrans_WL180 %>% mutate(ME = `Actual` - `Forecasts`) -> DF_LogTrans_WL180
 
+# ME
+DF_LogTrans_WL180 %>% 
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
+  filter(Forecast_Horizon == 1) %>% 
+  ungroup() %>% 
+  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL180_ME_h1
+
+Avg_Log_WL180_ME_h1 %>% 
+  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
+                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
+  spread(key = F.method, value = ME) %>% 
+  kable(format = "latex",)
+
+#MSE
 DF_LogTrans_WL180 %>% 
@@
 
-# BoxCox Transformation for $\lambda \in (-0.5,2)$ with 100 observations of training window (Average MSE calculated over 140 replications)
+# BoxCox Transformation for $\lambda \in (-0.5,2)$ with 100 observations of training window (ME and MSE calculated over 140 replications)
 
@@
 
+DF_BoxCoxTrans_WL100 <- DF_BoxCoxTrans_WL100 %>% 
+  mutate(F.method=recode(F.method, `Bias` = 'Biased')) 
+# so that we don't confuse Biased forecasts with ME
+
 DF_BoxCoxTrans_WL100 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_WL100
+DF_BoxCoxTrans_WL100 %>% mutate(ME = `Actual` - `Forecasts`) -> DF_BoxCoxTrans_WL100
 
+# ME
+DF_BoxCoxTrans_WL100 %>% 
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
+  filter(Forecast_Horizon == 1) %>% 
+  ungroup() %>% 
+  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_ME_h1
+
+Avg_Log_WL100_ME_h1 %>% 
+  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
+                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
+  spread(key = F.method, value = ME) %>% 
+  kable(format = "latex",)
+
+#MSE
 DF_BoxCoxTrans_WL100 %>% 
@@
   ungroup() %>% 
-  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_WL100_MSE_h1
+  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_MSE_h1
 
-Avg_BoxCox_WL100_MSE_h1 %>%
+Avg_Log_WL100_MSE_h1 %>% 
   mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
@@
 
-# BoxCox Transformation for $\lambda \in (-0.5,2)$ with 180 observations of training window (Average MSE calculated over 60 replications)
+# BoxCox Transformation for $\lambda \in (-0.5,2)$ with 180 observations of training window (ME and MSE calculated over 60 replications)
 
@@
 
+DF_BoxCoxTrans_WL180 <- DF_BoxCoxTrans_WL180 %>% 
+  mutate(F.method=recode(F.method, `Bias` = 'Biased')) 
+# so that we don't confuse Biased forecasts with ME
+
 DF_BoxCoxTrans_WL180 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_WL180
+DF_BoxCoxTrans_WL180 %>% mutate(ME = `Actual` - `Forecasts`) -> DF_BoxCoxTrans_WL180
 
+# ME
+DF_BoxCoxTrans_WL180 %>% 
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
+  filter(Forecast_Horizon == 1) %>% 
+  ungroup() %>% 
+  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_ME_h1
+
+Avg_Log_WL100_ME_h1 %>% 
+  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
+                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
+  spread(key = F.method, value = ME) %>% 
+  kable(format = "latex",)
+
+#MSE
 DF_BoxCoxTrans_WL180 %>% 
@@
   ungroup() %>% 
-  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_WL180_MSE_h1
+  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_MSE_h1
 
-Avg_BoxCox_WL180_MSE_h1 %>%
+Avg_Log_WL100_MSE_h1 %>% 
   mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 

### 2020-01-17 Application-R/Application-TourismData/Final-results/TourismData-Final-resultsR1.tex
Calculating ME

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Tourism Data Analysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

\title{Tourism Data Analysis}
\author{}
\date{\vspace{-2.5em}Jan 2020}

\begin{document}
\maketitle

\hypertarget{log-transformation-with-100-observations-of-training-window-me-and-mse-calculated-over-140-replications}{%
\section{Log Transformation with 100 observations of training window (ME
and MSE calculated over 140
replications)}\label{log-transformation-with-100-observations-of-training-window-me-and-mse-calculated-over-140-replications}}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 99.98 & 52.70 & 140.46\\
\hline
Bottom-up & 176.31 & 64.42 & 271.73\\
\hline
MinT(Shrink) & 74.31 & 50.50 & 109.89\\
\hline
OLS & 50.73 & 38.64 & 65.82\\
\hline
WLS & 121.11 & 57.50 & 174.35\\
\hline
\end{tabular}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 4.47 & 4.43 & 4.51\\
\hline
Bottom-up & 6.36 & 5.26 & 8.06\\
\hline
MinT(Shrink) & 4.32 & 4.16 & 4.61\\
\hline
OLS & 4.34 & 4.31 & 4.36\\
\hline
WLS & 4.82 & 4.38 & 5.43\\
\hline
\end{tabular}

\hypertarget{log-transformation-with-180-observations-of-training-window-me-and-mse-calculated-over-60-replications}{%
\section{Log Transformation with 180 observations of training window (ME
and MSE calculated over 60
replications)}\label{log-transformation-with-180-observations-of-training-window-me-and-mse-calculated-over-60-replications}}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 90.45 & 67.34 & 109.95\\
\hline
Bottom-up & 152.69 & 98.06 & 197.11\\
\hline
MinT(Shrink) & 64.64 & 59.36 & 85.54\\
\hline
OLS & 41.62 & 35.92 & 47.51\\
\hline
WLS & 110.65 & 79.64 & 136.58\\
\hline
\end{tabular}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 4.89 & 4.78 & 5.08\\
\hline
Bottom-up & 9.71 & 6.97 & 12.70\\
\hline
MinT(Shrink) & 4.75 & 4.63 & 5.35\\
\hline
OLS & 4.67 & 4.60 & 4.81\\
\hline
WLS & 6.33 & 5.22 & 7.58\\
\hline
\end{tabular}

\hypertarget{boxcox-transformation-for-lambda-in--0.52-with-100-observations-of-training-window-me-and-mse-calculated-over-140-replications}{%
\section{\texorpdfstring{BoxCox Transformation for
\(\lambda \in (-0.5,2)\) with 100 observations of training window (ME
and MSE calculated over 140
replications)}{BoxCox Transformation for \textbackslash lambda \textbackslash in (-0.5,2) with 100 observations of training window (ME and MSE calculated over 140 replications)}}\label{boxcox-transformation-for-lambda-in--0.52-with-100-observations-of-training-window-me-and-mse-calculated-over-140-replications}}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 94.38 & 59.71 & 129.50\\
\hline
Bottom-up & 163.07 & 71.22 & 242.39\\
\hline
MinT(Shrink) & 71.10 & 57.94 & 96.92\\
\hline
OLS & 50.70 & 43.13 & 70.16\\
\hline
WLS & 113.67 & 65.49 & 157.17\\
\hline
\end{tabular}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 4.59 & 4.52 & 4.78\\
\hline
Bottom-up & 6.21 & 5.31 & 7.46\\
\hline
MinT(Shrink) & 4.29 & 4.17 & 4.54\\
\hline
OLS & 4.46 & 4.40 & 4.63\\
\hline
WLS & 4.77 & 4.42 & 5.23\\
\hline
\end{tabular}

\hypertarget{boxcox-transformation-for-lambda-in--0.52-with-180-observations-of-training-window-me-and-mse-calculated-over-60-replications}{%
\section{\texorpdfstring{BoxCox Transformation for
\(\lambda \in (-0.5,2)\) with 180 observations of training window (ME
and MSE calculated over 60
replications)}{BoxCox Transformation for \textbackslash lambda \textbackslash in (-0.5,2) with 180 observations of training window (ME and MSE calculated over 60 replications)}}\label{boxcox-transformation-for-lambda-in--0.52-with-180-observations-of-training-window-me-and-mse-calculated-over-60-replications}}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 88.91 & 73.25 & 103.24\\
\hline
Bottom-up & 142.37 & 98.60 & 178.09\\
\hline
MinT(Shrink) & 63.30 & 62.84 & 75.61\\
\hline
OLS & 47.03 & 44.71 & 51.25\\
\hline
WLS & 105.78 & 83.93 & 124.99\\
\hline
\end{tabular}

\begin{tabular}{l|r|r|r}
\hline
R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
\hline
Base & 4.61 & 4.58 & 4.72\\
\hline
Bottom-up & 9.17 & 7.00 & 11.43\\
\hline
MinT(Shrink) & 4.50 & 4.53 & 4.82\\
\hline
OLS & 4.43 & 4.43 & 4.52\\
\hline
WLS & 6.24 & 5.45 & 7.11\\
\hline
\end{tabular}

\end{document}

### 2020-01-19 R1/Response.tex
material from R1 added to response

@@
 
-		\item \textit{When the empirical evaluation is focused on bias, then it would make sense to include an error that measures bias in addition to the squared error.}\\
+		\item \textit{Lack of empirical contribution: The authors apply a couple of different transformations to the tourism data before constructing base forecasts.
+Failing to correctly transform the base forecasts back before they are reconciled introduces a bias.
+That the highest accuracy is obtained when applying the correct back-transformation is a very small contribution.}\\
+
+		While agree that if our empirical results only showed that applying the correct back-transformation improves accuracy, that this would be a very marginal contribution.
+However, we would like to emphasise that the extent to which it does this, also depend on the reconciliation method.
+TO DO (ELABORATE).\\
+
+        \textit{When the authors introduce the log-transformation and in the graphs in Figures 6 and 7, they do not clarify the interplay between the transformation and the reconciliation constraints.
+If A + B = C then clearly $\log A + \log B = \log C$.
+In other words, a log-transformation affects the	reconciliation constraints.
+This needs to be explained more clearly; e.g., is the reconciliation constraint imposed on the transformed or the raw data?}\\
+
+		TODO
+
+		\textit{When the empirical evaluation is focused on bias, then it would make sense to include an error that measures bias in addition to the squared error.}\\
 

### 2020-01-19 R1/Response.tex
extra exposition on linear constraints and log scale

@@
         \textit{When the authors introduce the log-transformation and in the graphs in Figures 6 and 7, they do not clarify the interplay between the transformation and the reconciliation constraints.
-If A + B = C then clearly $\log A + \log B = \log C$.
+If A + B = C then clearly $\log A + \log B \neq \log C$.
 In other words, a log-transformation affects the	reconciliation constraints.
@@
 
-		TODO
+		The observation regarding the constraints not holding on the log scale is correct.
+When series are transformed to the log scale, forecasts are first produced on the log scale and these are back transformed to the original scale (possibly with bias correction) prior to carrying out reconciliation.
+Therefore while all modelling is done on the log scale, all reconciliation is carried out on the original scale.
+The fact that the constraints do not hold on the log scale is therefore not relevant.\\
+
+		On re-reading the paper we do agree with the referee that there is scope for confusion here.
+Therefore we have added some additional exposition to the beginning of section 4.1.
+The aim here is to make it clear that after producing forecasting on some tranformed scale, the correct sequence of steps is to 1) back-transform to the original scale, 2) bias correct and 3) reconcile.
+\\
 

### 2020-01-19 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
extra exposition on linear constraints and log scale

@@
 In many cases the method for bias correction will be context specific.
-For instance, in our empirical study in Section~\ref{sec:EmpStudy} we consider a scenario where bias is induced via taking either a log transformation or a Box-Cox transformation before modelling.
-In this well-known case a number of bias correction methods exist based on Taylor expansions.
+For instance, in our empirical study in Section~\ref{sec:EmpStudy} we consider a scenario where {\color{blue} data are modelled after} taking either a log transformation or a Box-Cox transformation.
+{\color{blue} Since linear constraints that hold on the original scale do not hold for the transformed series, back-transforming to the original scale is necessary.
+Since this step induces a bias we propose to bias correct after this back-transformation step, and ultimately to reconcile the back-transformed, bias-corrected forecasts.}  In the well-known case {\color{blue} of the Box-Cox transformation} a number of bias correction methods exist based on Taylor expansions.
 

### 2020-01-19 R1/Response.tex
Added discussion of non-negative forecasts and cite paper

@@
 This is a fairly pathological case and does not arise in the application that we consider (and many other applications that we have considered in other work).
-We do agree that this problem may arise in other contexts so we now include some discussion of this issue and cite some recent work that addresses this problem.
-TO DO (TAS)\\
+We do agree that this problem may arise in other contexts so we now include some discussion of this issue in the conclusion and cite some recent work that addresses this problem.\\
 

### 2020-01-19 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Added discussion of non-negative forecasts and cite paper

@@
 
-First, it should be possible to extend the concept of coherence to non-linear constraints.
-In these cases the coherent space may need to be defined by a manifold.
+First, it should be possible to extend the concept of coherence {\color{blue}to examples where the coherent space is not a linear plane in $\mathbb{R}^n$.
+This includes the case where in addition to aggregation constraints, forecasts are also constrained to be non-negative.
+We note the work of \cite{wickramasuriya2019optimal} as an attempt to address this issue.
+Another possibility is} non-linear constraints where the coherent space may need to be defined by a manifold.
 Although much more challenging, it is still possible to define reconciled forecasts in terms of projections onto a manifold.

### 2020-01-19 R1/Response.tex
added some discussion of van Erven and nystrup stuff

@@
 
-		While agree that if our empirical results only showed that applying the correct back-transformation improves accuracy, that this would be a very marginal contribution.
+		We agree that if our empirical results only showed that applying the correct back-transformation improves accuracy, that this would be a very marginal contribution.
 However, we would like to emphasise that the extent to which it does this, also depend on the reconciliation method.
@@
 	    Reflecting on this issue has led us towards the development of a generalised version of MinT which we now include in the paper.
-Briefly, the geometric insight allows us to decouple the issue of choice of loss function (which may be influenced by the context of the forecasting problem) from the issue of the properties of a given reconciliation method (which is a statistical question).
-TO DO (TAS).\\
+Briefly, the geometric insight allows us to decouple the issue of choice of loss function (which may be influenced by the context of the forecasting problem) from the issue of the properties of a given reconciliation method (which is a statistical question).\\
 
@@
 
-	    Must reread these papers and comment.  TO DO (TAS)\\
+	    We now discuss the connection to the optimisation formulation considered by these two papers on page 2 line 12 as requested.
+We believe that some of the other revisions we have made, particularly the new discussion in 3.4 further clarify the connection between reconciliation approaches and error measures.\\
 
 	    \item \textit{P. 4, l. 22: forf}\\
+
 	    This has been corrected.\\
@@
 	    \item \textit{P. 10, l. 12: the comma should not be there.}\\
+
 	    The comma has been removed.\\
@@
 	    \item \textit{P. 11, Figure 3: usually a small square is drawn in the corner of the triangle to show orthogonality.}\\
+
 	    We have made this change to all Figures. TO DO (GEORGE)\\
@@
 	    \item \textit{P. 17, l. 18: i,e.}\\
+
 	    We have made this correction.\\
@@
 	    \item \textit{P. 26, l. 14: the authors mention that the full results are available upon request. I suggest including them in an online supplementary appendix.}\\
+
 	    We now include these an an online supplement. TO DO\\
@@
 27, Conclusions: The authors should comment on the implications of the non-uniqueness of the S matrix for future work on cross-temporal reconciliation (Kourentzes and Athanasopoulos, 2019).}\\
+
 	    TO DO (GEORGE).\\
@@
     \noindent\textit{Please correct the minor typo just before section 2 (forf).}\\
-    We have made this correction.\\
+
+    \noindent We have made this correction.\\
 

### 2020-01-19 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added some discussion of van Erven and nystrup stuff

@@
 Of particular prominence have been \emph{forecast reconciliation} methods involving two steps: first separate forecasts are produced for all series, then these are adjusted to ensure coherence with aggregation constraints.
-Forecast reconciliation has mostly been formulated using a regression model, see \citet{Hyndman2011} and \citet{WicEtAl2019} for examples.
-This setup can be counter-intuitive since a vector comprised of forecasts from different time series models is also assumed to be the dependent variable in a regression model.
+Forecast reconciliation has mostly been formulated using a regression model {\color{blue} that admits a generalised least squares (GLS) solution}, see \citet{Hyndman2011} and \citet{WicEtAl2019} for examples.
+{\color{blue} Alternatively, \cite{VanErven2015a} and \cite{NysEtAl2019} arrive at a GLS solution by formulating the problem as as an optimisation problem to minimises weighted squared errors between coherent and incoherent forecasts}.
+The regression setup can be counter-intuitive since a vector comprised of forecasts from different time series models is also assumed to be the dependent variable in a regression model.
 In this paper, we eschew a regression interpretation in favour of a novel, geometric understanding of forecast reconciliation.
@@
 \begin{itemize}
-\item The first is that reconciliation should adjust the base forecasts as little as possible; i.e. the base and reconciled forecasts should be `close'.
+\item The first is that reconciliation should adjust the base forecasts as little as possible; i.e.
+the base and reconciled forecasts should be `close'.
+{\color{blue} This property is particularly emphasised by \cite{VanErven2015a} and \cite{NysEtAl2019}}
 \item The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value targeted by the forecast.
+{\color{blue} This property is particularly emphasised by \cite{WicEtAl2019}.}
 \end{itemize}
@@
 In spite of this, it is also true that Theorem~\ref{th:gdistred} guarantees that MinT will always improve upon base forecasts when the loss function is based on the norm $\|.\|_{\bm{\Sigma}^{-1}}$.
-This will be verified in our empirical example in Section~\ref{sec:EmpStudy}.
+A similar insight has already been made by \cite{VanErven2015a} and will be verified in our empirical example in Section~\ref{sec:EmpStudy}.
 For this reason there is the potential to conflate the choice of loss function, with the desire to attain the attractive statistical properties of trace minimisation.
 We now propose a generalisation of the MinT method that uncouples these two ideas.
+Our proposed method targets more general loss functions than the sum of squared errors (in a similar vein to \cite{VanErven2015a} and \cite{NysEtAl2019}), while exploiting the correlation structure of forecast errors (in a similar vein to \cite{WicEtAl2019}).
 
@@
 \end{equation*} 
-To the best of our knowledge, this method, which we call Generalised MinT has not been proposed so far in the literature.
-The key advantage of Generalised MinT allows the choice of loss function to be decoupled from the choice of an oblique projection with attractive statistical properties.
+We note that some of solutions to the reconciliation problem proposed by \cite{NysEtAl2019}, for example \textit{series GLASSO scaling} and \textit{series shrinkage scaling} are special cases of this method where $\bm{W}$ is diagonal.
+What we seek to make clear here is the connection between $\bm{W}^{-1/2}$ (which need not be diagonal) and the loss function.
+In particular, Generalised MinT allows the choice of loss function to be decoupled from the choice of an oblique projection with attractive statistical properties.
 

### 2020-01-21 Application-R/Application-TourismData/Final-results/TourismData-Final-resultsR1.Rmd
Calculating Nemenyi tests

--- 2019-08-29 Application-R/Application-TourismData/Final-results/TourismData-Final-results.Rmd
@@
 library(kableExtra)
+library(tsutils)
 # library(reshape2)
@@
 
-# Box and whisker plots for orthogonal and oblique projections from better models
+# Log Transformation with 100 observations of training window (ME and MSE calculated over 140 replications)
 
 ```{r, echo=FALSE}
-OvernightTrips_OriginalScale_Fc <- read.csv("OvernightTrips_OriginalScale_Fc.csv")[,-1]
+DF_LogTrans_WL100 <- read.csv("DF_LogTrans_WL100.csv")[,-1]
 
-OvernightTrips_OriginalScale_Fc %>%
-  mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2,
-         Fc_horizon = recode(Fc_horizon, "1" = "h=1", "2" = "h=2",
-                             "3" = "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6")) %>%
-  group_by(`R.method`, Fc_horizon, Replication) %>%
-  summarise(MSE = mean(SquaredE)) -> OvernightTrips_OriginalScale_MSE
+DF_LogTrans_WL100 <- DF_LogTrans_WL100 %>% 
+  mutate(F.method=recode(F.method, `Bias` = 'Biased')) 
+# so that we don't confuse Biased forecasts with ME
 
-OvernightTrips_OriginalScale_MSE %>%
-  filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>%
-  spread(key = `R.method`, value = MSE) %>%
-  mutate("Base-OLS" = Base - OLS,
-         "Base-MinT" = Base - `MinT(Shrink)`,
-         "Base-WLS" = Base - WLS) %>%
-  dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
-  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>%
-  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>%
-  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>%
-  ggplot(aes(x = Method, y = MSE)) +
-  geom_boxplot() + facet_wrap(~ Fc_horizon) +
-  ylab("MSE") + xlab("Reconciliation Method")
+DF_LogTrans_WL100 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_WL100
+DF_LogTrans_WL100 %>% mutate(ME = `Actual` - `Forecasts`) -> DF_LogTrans_WL100
 
-```
+# ME
+DF_LogTrans_WL100 %>%  
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
+  filter(Forecast_Horizon == 1) %>% 
+  ungroup() %>% 
+  dplyr::select(-Forecast_Horizon) -> Avg_Log_WL100_ME_h1
 
-# Box and whisker plots for orthogonal and oblique projections from misspecified models
+# Make everything percentage improvement
+Avg_Log_WL100_ME_h1 <- Avg_Log_WL100_ME_h1 %>% 
+  mutate(ME=ME/Avg_Log_WL100_ME_h1[1,]$ME)
 
-```{r, echo=FALSE}
-OvernightTrips_OriginalScaleMisspecified_Fc <- read.csv("OvernightTrips_OriginalScaleMisspecified_Fc.csv")[,-1]
+Avg_Log_WL100_ME_h1 %>% 
+  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
+                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
+  spread(key = F.method, value = ME) %>% 
+  kable(format = "latex",digits = 2)
 
-OvernightTrips_OriginalScaleMisspecified_Fc %>%
-  mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2,
-         Fc_horizon = recode(Fc_horizon, "1" = "h=1", "2" = "h=2",
-                             "3" = "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6")) %>%
-  group_by(`R.method`, Fc_horizon, Replication) %>%
-  summarise(MSE = mean(SquaredE)) -> OvernightTrips_OriginalScaleMisspecified_MSE
-
-OvernightTrips_OriginalScaleMisspecified_MSE %>%
-  filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>%
-  spread(key = `R.method`, value = MSE) %>%
-  mutate("Base-OLS" = Base - OLS,
-         "Base-MinT" = Base - `MinT(Shrink)`,
-         "Base-WLS" = Base - WLS) %>%
-  dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
-  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>%
-  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>%
-  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>%
-  ggplot(aes(x = Method, y = MSE)) +
-  geom_boxplot() + facet_wrap(~ Fc_horizon) +
-  ylab("MSE") + xlab("Reconciliation Method")
-
-```
-
-# Log Transformation
-
-```{r, echo=FALSE}
-DF_LogTrans <- read.csv("OvernightTrips_LogTrans_Fc.csv")[,-1]
-
-DF_LogTrans %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans
-
-DF_LogTrans %>% 
+#MSE
+DF_LogTrans_WL100 %>% 
   group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
@@
   ungroup() %>% 
-  dplyr::select(-Forecast_Horizon)-> Avg_Log_MSE_h1
+  dplyr::select(-Forecast_Horizon)-> Avg_Log_WL100_MSE_h1
 
-Avg_Log_MSE_h1 %>% 
+# Make everything percentage improvement
+Avg_Log_WL100_MSE_h1 <- Avg_Log_WL100_MSE_h1 %>% 
+  mutate(MSE=MSE/Avg_Log_WL100_MSE_h1[1,]$MSE)
+
+Avg_Log_WL100_MSE_h1 %>% 
   mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
@@
   spread(key = F.method, value = MSE) %>% 
-  kable(format = "latex")
+  kable(format = "latex", digits = 2)
 
@@
 
-# BoxCox Transformation for $\lambda \in (0,1)$
+# BoxCox Transformation for $\lambda \in (-0.5,2)$ with 100 observations of training window (ME and MSE calculated over 140 replications)
 
 ```{r, echo=FALSE}
-DF_BoxCoxTrans_set1 <- read.csv("OvernightTrips_BoxCoxTrans_set1_Fc.csv")[,-1]
+DF_BoxCoxTrans_WL100 <- read.csv("DF_BoxCoxTrans_WL100.csv")[,-1]
 
-DF_BoxCoxTrans_set1 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_set1
+DF_BoxCoxTrans_WL100 <- DF_BoxCoxTrans_WL100 %>% 
+  mutate(F.method=recode(F.method, `Bias` = 'Biased')) 
+# so that we don't confuse Biased forecasts with ME
 
-DF_BoxCoxTrans_set1 %>%
+DF_BoxCoxTrans_WL100 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_WL100
+DF_BoxCoxTrans_WL100 %>% mutate(ME = `Actual` - `Forecasts`) -> DF_BoxCoxTrans_WL100
+
+# ME
+DF_BoxCoxTrans_WL100 %>% 
+  group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
+  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
+  filter(Forecast_Horizon == 1) %>% 
+  ungroup() %>% 
+  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_WL100_ME_h1
+
+# Make everything percentage improvement
+Avg_BoxCox_WL100_ME_h1 <- Avg_BoxCox_WL100_ME_h1 %>% 
+  mutate(ME=ME/Avg_BoxCox_WL100_ME_h1[1,]$ME)
+
+Avg_BoxCox_WL100_ME_h1 %>% 
+  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
+                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
+  spread(key = F.method, value = ME) %>% 
+  kable(format = "latex",digits = 2)
+
+#MSE
+DF_BoxCoxTrans_WL100 %>% 
   group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
@@
   ungroup() %>% 
-  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_set1_MSE_h1
+  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_WL100_MSE_h1
 
-Avg_BoxCox_set1_MSE_h1 %>%
+Avg_BoxCox_WL100_MSE_h1 <- Avg_BoxCox_WL100_MSE_h1 %>%
+  mutate(MSE=MSE/Avg_BoxCox_WL100_MSE_h1[1,]$MSE)
+
+Avg_BoxCox_WL100_MSE_h1 %>% 
   mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
@@
   spread(key = F.method, value = MSE) %>% 
-  kable(format = "latex")
+  kable(format = "latex", digits = 2)
 
 ```
-
-# BoxCox Transformation for $\lambda \in (-0.5,2)$
-
-```{r, echo=FALSE}
-DF_BoxCoxTrans_set2 <- read.csv("OvernightTrips_BoxCoxTrans_set2_Fc.csv")[,-1]
-
-DF_BoxCoxTrans_set2 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_BoxCoxTrans_set2
-
-DF_BoxCoxTrans_set2 %>%
-  group_by(`F.method`, `R.method`, Forecast_Horizon) %>%
-  summarise(MSE = round(mean(SquaredE)/1e3, digits = 2)) %>%
-  filter(Forecast_Horizon == 1) %>%
-  ungroup() %>%
-  dplyr::select(-Forecast_Horizon)-> Avg_BoxCox_set2_MSE_h1
-
-Avg_BoxCox_set2_MSE_h1 %>%
-  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)",
-                           Unbiased_M2 = "Unbiased (Method 2)")) %>%
-  spread(key = F.method, value = MSE) %>%
-  kable(format = "latex")
-
-```

### 2020-01-21 Application-R/Application-TourismData/Final-results/TourismData-Final-resultsR1.tex
Calculating Nemenyi tests

@@
 \hline
-Base & 99.98 & 52.70 & 140.46\\
+Base & 1.00 & 0.53 & 1.40\\
 \hline
-Bottom-up & 176.31 & 64.42 & 271.73\\
+Bottom-up & 1.76 & 0.64 & 2.72\\
 \hline
-MinT(Shrink) & 74.31 & 50.50 & 109.89\\
+MinT(Shrink) & 0.74 & 0.51 & 1.10\\
 \hline
-OLS & 50.73 & 38.64 & 65.82\\
+OLS & 0.51 & 0.39 & 0.66\\
 \hline
-WLS & 121.11 & 57.50 & 174.35\\
+WLS & 1.21 & 0.58 & 1.74\\
 \hline
@@
 \hline
-Base & 4.47 & 4.43 & 4.51\\
+Base & 1.00 & 0.99 & 1.01\\
 \hline
-Bottom-up & 6.36 & 5.26 & 8.06\\
+Bottom-up & 1.42 & 1.18 & 1.80\\
 \hline
-MinT(Shrink) & 4.32 & 4.16 & 4.61\\
+MinT(Shrink) & 0.97 & 0.93 & 1.03\\
 \hline
-OLS & 4.34 & 4.31 & 4.36\\
+OLS & 0.97 & 0.96 & 0.98\\
 \hline
-WLS & 4.82 & 4.38 & 5.43\\
-\hline
-\end{tabular}
-
-\hypertarget{log-transformation-with-180-observations-of-training-window-me-and-mse-calculated-over-60-replications}{%
-\section{Log Transformation with 180 observations of training window (ME
-and MSE calculated over 60
-replications)}\label{log-transformation-with-180-observations-of-training-window-me-and-mse-calculated-over-60-replications}}
-
-\begin{tabular}{l|r|r|r}
-\hline
-R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
-\hline
-Base & 90.45 & 67.34 & 109.95\\
-\hline
-Bottom-up & 152.69 & 98.06 & 197.11\\
-\hline
-MinT(Shrink) & 64.64 & 59.36 & 85.54\\
-\hline
-OLS & 41.62 & 35.92 & 47.51\\
-\hline
-WLS & 110.65 & 79.64 & 136.58\\
-\hline
-\end{tabular}
-
-\begin{tabular}{l|r|r|r}
-\hline
-R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
-\hline
-Base & 4.89 & 4.78 & 5.08\\
-\hline
-Bottom-up & 9.71 & 6.97 & 12.70\\
-\hline
-MinT(Shrink) & 4.75 & 4.63 & 5.35\\
-\hline
-OLS & 4.67 & 4.60 & 4.81\\
-\hline
-WLS & 6.33 & 5.22 & 7.58\\
+WLS & 1.08 & 0.98 & 1.21\\
 \hline
@@
 \hline
-Base & 94.38 & 59.71 & 129.50\\
+Base & 1.00 & 0.63 & 1.37\\
 \hline
-Bottom-up & 163.07 & 71.22 & 242.39\\
+Bottom-up & 1.73 & 0.75 & 2.57\\
 \hline
-MinT(Shrink) & 71.10 & 57.94 & 96.92\\
+MinT(Shrink) & 0.75 & 0.61 & 1.03\\
 \hline
-OLS & 50.70 & 43.13 & 70.16\\
+OLS & 0.54 & 0.46 & 0.74\\
 \hline
-WLS & 113.67 & 65.49 & 157.17\\
+WLS & 1.20 & 0.69 & 1.67\\
 \hline
@@
 \hline
-Base & 4.59 & 4.52 & 4.78\\
+Base & 1.00 & 0.98 & 1.04\\
 \hline
-Bottom-up & 6.21 & 5.31 & 7.46\\
+Bottom-up & 1.35 & 1.16 & 1.63\\
 \hline
-MinT(Shrink) & 4.29 & 4.17 & 4.54\\
+MinT(Shrink) & 0.93 & 0.91 & 0.99\\
 \hline
-OLS & 4.46 & 4.40 & 4.63\\
+OLS & 0.97 & 0.96 & 1.01\\
 \hline
-WLS & 4.77 & 4.42 & 5.23\\
-\hline
-\end{tabular}
-
-\hypertarget{boxcox-transformation-for-lambda-in--0.52-with-180-observations-of-training-window-me-and-mse-calculated-over-60-replications}{%
-\section{\texorpdfstring{BoxCox Transformation for
-\(\lambda \in (-0.5,2)\) with 180 observations of training window (ME
-and MSE calculated over 60
-replications)}{BoxCox Transformation for \textbackslash lambda \textbackslash in (-0.5,2) with 180 observations of training window (ME and MSE calculated over 60 replications)}}\label{boxcox-transformation-for-lambda-in--0.52-with-180-observations-of-training-window-me-and-mse-calculated-over-60-replications}}
-
-\begin{tabular}{l|r|r|r}
-\hline
-R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
-\hline
-Base & 88.91 & 73.25 & 103.24\\
-\hline
-Bottom-up & 142.37 & 98.60 & 178.09\\
-\hline
-MinT(Shrink) & 63.30 & 62.84 & 75.61\\
-\hline
-OLS & 47.03 & 44.71 & 51.25\\
-\hline
-WLS & 105.78 & 83.93 & 124.99\\
-\hline
-\end{tabular}
-
-\begin{tabular}{l|r|r|r}
-\hline
-R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
-\hline
-Base & 4.61 & 4.58 & 4.72\\
-\hline
-Bottom-up & 9.17 & 7.00 & 11.43\\
-\hline
-MinT(Shrink) & 4.50 & 4.53 & 4.82\\
-\hline
-OLS & 4.43 & 4.43 & 4.52\\
-\hline
-WLS & 6.24 & 5.45 & 7.11\\
+WLS & 1.04 & 0.96 & 1.14\\
 \hline

### 2020-01-21 Application-R/Application-TourismData/Final-results/Nemenyi.R

@@ -1,0 +1,140 @@
+library(tidyverse)
+library(tsutils)
+library(tidyr)
+library(Matrix)
+library(readr)
+library(tibble)
+library(kableExtra)
+
+DF_LogTrans_WL100 <- read.csv("DF_LogTrans_WL100.csv")[,-1]
+
+DF_LogTrans_WL100 <- DF_LogTrans_WL100 %>% 
+  mutate(F.method=recode(F.method, `Bias` = 'Biased')) 
+# so that we don't confuse Biased forecasts with ME/bias
+
+DF_LogTrans_WL100 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_WL100
+DF_LogTrans_WL100 %>% mutate(ME = `Actual` - `Forecasts`) -> DF_LogTrans_WL100
+
+
+# # ME calculations
+# DF_LogTrans_WL100 %>%
+#   filter(Forecast_Horizon == 1) %>% 
+#   group_by(`F.method`, `R.method`) %>% 
+#   summarise(ME = sum(ME)/1e3) %>% 
+#   arrange(ME)
+
+# Nemenyi for ME
+DF_LogTrans_WL100 %>% 
+  filter(Forecast_Horizon == 1) %>% 
+  group_by(Replication, F.method, R.method) %>% 
+  summarise(ME = sum(ME)/1e3) %>%
+  mutate(method=paste(F.method,R.method, sep='_')) %>% 
+  ungroup() %>% 
+  select(Replication, ME ,method) %>% 
+  spread(method,ME) %>% as.matrix() -> m
+
+  m <- m[,-1] 
+  class(m) <- "numeric"
+
+  nemenyi(m,conf.level=0.95,plottype="matrix")
+
+# dm.test(e1,e2, alternative = "two.sided", h = 1, power = 2)
+
+# colSums(m) %>% as.matrix() -> ME
+# ME <-  ME[order(ME[,1]),, drop=F]  %>% as.matrix()
+# ME # ME
+
+
+# # Verifying MSE calculations 
+# DF_LogTrans_WL100 %>%
+#   filter(Forecast_Horizon == 1) %>%
+#   group_by(`F.method`, `R.method`) %>%
+#   summarise(MSE = round(mean(SquaredE)/1e3, digits = 6)) %>%
+#   arrange(MSE)
+
+# Nemenyi for MSE
+DF_LogTrans_WL100 %>%
[…]

### 2020-01-21 Application-R/Application-TourismData/Final-results/TourismData-Final-resultsR1.tex
Adding New Table

@@
 \hline
-R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
-\hline
-Base & 1.00 & 0.53 & 1.40\\
-\hline
-Bottom-up & 1.76 & 0.64 & 2.72\\
-\hline
-MinT(Shrink) & 0.74 & 0.51 & 1.10\\
-\hline
-OLS & 0.51 & 0.39 & 0.66\\
-\hline
+R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\\hline
+Base & 1.00 & 0.53 & 1.40\\ \hline
+Bottom-up & 1.76 & 0.64 & 2.72\\ \hline
+MinT(Shrink) & 0.74 & 0.51 & 1.10\\\hline
+OLS & 0.51 & 0.39 & 0.66\\\hline
 WLS & 1.21 & 0.58 & 1.74\\
@@
 \hline
-R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
-\hline
-Base & 1.00 & 0.99 & 1.01\\
-\hline
-Bottom-up & 1.42 & 1.18 & 1.80\\
-\hline
-MinT(Shrink) & 0.97 & 0.93 & 1.03\\
-\hline
-OLS & 0.97 & 0.96 & 0.98\\
-\hline
-WLS & 1.08 & 0.98 & 1.21\\
-\hline
+R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\\hline
+Base & 1.00 & 0.99 & 1.01\\\hline
+Bottom-up & 1.42 & 1.18 & 1.80\\\hline
+MinT(Shrink) & 0.97 & 0.93 & 1.03\\\hline
+OLS & 0.97 & 0.96 & 0.98\\\hline
+WLS & 1.08 & 0.98 & 1.21\\\hline
 \end{tabular}
@@
 \hline
-R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\
-\hline
-Base & 1.00 & 0.63 & 1.37\\
-\hline
-Bottom-up & 1.73 & 0.75 & 2.57\\
-\hline
-MinT(Shrink) & 0.75 & 0.61 & 1.03\\
-\hline
-OLS & 0.54 & 0.46 & 0.74\\
-\hline
-WLS & 1.20 & 0.69 & 1.67\\
-\hline
+R.method & Biased & Unbiased (Method 1) & Unbiased (Method 2)\\\hline
+Base & 1.00 & 0.63 & 1.37\\\hline
+Bottom-up & 1.73 & 0.75 & 2.57\\\hline
+MinT(Shrink) & 0.75 & 0.61 & 1.03\\\hline
+OLS & 0.54 & 0.46 & 0.74\\\hline
+WLS & 1.20 & 0.69 & 1.67\\\hline
 \end{tabular}
@@
 \hline
-Base & 1.00 & 0.98 & 1.04\\
-\hline
-Bottom-up & 1.35 & 1.16 & 1.63\\
-\hline
-MinT(Shrink) & 0.93 & 0.91 & 0.99\\
-\hline
-OLS & 0.97 & 0.96 & 1.01\\
-\hline
-WLS & 1.04 & 0.96 & 1.14\\
-\hline
+Base & 1.00 & 0.98 & 1.04\\\hline
+Bottom-up & 1.35 & 1.16 & 1.63\\\hline
+MinT(Shrink) & 0.93 & 0.91 & 0.99\\\hline
+OLS & 0.97 & 0.96 & 1.01\\\hline
+WLS & 1.04 & 0.96 & 1.14\\\hline
 \end{tabular}

### 2020-01-21 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Adding New Table

@@
 \usepackage[section]{placeins}
+
+\usepackage{dcolumn}
+\newcolumntype{d}[1]{D{.}{.}{#1}}
 
@@
 
+\begin{table}[!b]
+\caption {Average {MSE($\times 10^3$)} of $1$-step-ahead point forecasts from log and Box-Cox transformed series.
+Biased denotes forecasts from simply reversing the transformation via Eq.~\eqref{eq:BoxCox_back-transformation}.
+Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in Eq.~\eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
+\label{tab:Results_MSE}
+\setlength{\tabcolsep}{7pt}
+\centering
+  \begin{tabular}{ld{3.2}d{3.2}d{3.2}d{3.2}d{3.2}d{3.2}}
+    \toprule
+    \multicolumn{1}{c}{ } & \multicolumn{3}{c}{Log Transformation} &
+    \multicolumn{3}{c}{Box-Cox Transformation}\\
+    \cmidrule(lr){2-4} \cmidrule(lr){5-7}
+    Method & \multicolumn{1}{c}{Biased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Biased} & \multicolumn{1}{c}{Unbiased} & \multicolumn{1}{c}{Unbiased} \\
+    & & \multicolumn{1}{c}{(Method-1)} & \multicolumn{1}{c}{(Method-2)} && \multicolumn{1}{c}{(Method-1)} &\multicolumn{1}{c}{(Method-2)}\\ \midrule
+              & \multicolumn{6}{c}{ME}\\\cmidrule(lr){2-7}
+    Base      & 1.00 & 0.53^{\ast\dag} & 1.40^{\ast\dag} & 1.00 & 0.63^{\ast\dag} & 1.37^{\ast\dag}\\
+    OLS       & 0.51^{\ast} & 0.39^{\ast} & 0.66 & 0.54^{\ast} & 0.46^{\ast} & 0.74\\
+    MinT      & 0.74 & 0.51^{\ast\dag} & 1.10^{\dag} & 0.75 & 0.61^{\ast} & 1.03^{\dag}\\
+    WLS       & 1.21 & 0.58^{\ast\dag} & 1.74^{\ast\dag} & 1.20 & 0.69^{\ast\dag} & 1.67^{\ast\dag}\\
+    Bottom-up & 1.76^{\ast} & 0.64^{\ast\dag} & 2.72^{\ast\dag} & 1.73 & 0.75^{\ast\dag} & 2.57^{\ast\dag}\\
+              & \multicolumn{6}{c}{MSE}\\\cmidrule(lr){2-7}
+    Base      & 1.00 & 0.99 & 1.01 & 1.00 & 0.98 & 1.04\\
+    OLS       & 0.97^{\ast} & 0.96^{\ast} & 0.98^{\ast} & 0.97^{\ast} & 0.96^{\ast} & 1.01\\
+    MinT      & 0.97^{\ast} & 0.93^{\ast} & 1.03 & 0.93^{\ast} & 0.91^{\ast} & 0.99\\
+    WLS       & 1.08 & 0.98 & 1.21 & 1.04 & 0.96 & 1.14\\
+    Bottom-up & 1.42 & 1.18 & 1.80 & 1.35 & 1.16 & 1.63\\
+    \bottomrule
+  \end{tabular}
+\end{table}
+
 Recall that reconciliation approaches via projections preserve unbiasedness in the reconciled forecasts iff the base forecasts are unbiased.

### 2020-01-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
changed table color to blue and added text

@@
 Using the three sets of base forecasts from each of the two transformations, we generate coherent forecasts implementing OLS, MinT and WLS reconciliation projections, and also the bottom-up approach and compare the results for when the base forecasts are biased and bias-adjusted, i.e., unbiased.
-Table~\ref{tab:Results_MSE} presents the results over the $140$ rolling window replications for $1$-step-ahead forecasts.
-As was the case with Section~\ref{sec:comparebase}, the conclusions that follow extend almost identically to longer forecast horizons.
-We do not present these here to save space but they are available upon request.
+{\color{blue} For each replication and for method $q$, the total error (TE) and total squared error (TSE), are computed as
+\begin{equation*}
+\textrm{TE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})\quad \textrm {and}\quad \textrm{TSE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,,
+\end{equation*}
+where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
+The total error gives an indication of bias, while the total squared error is connected with Euclidean distance.
+Table~\ref{tab:Results_MSE} reports the relative mean total error (RMTE) and relative mean total error (RMTSE) defined as
+\begin{equation*}
+\textrm{RMTE}^{q}=\frac{\sum\limits_{t=1}^{140}\textrm{TE}^{q}_t}{\sum\limits_{t=1}^{140}\textrm{TE}^{\textrm{Base}}_t}\quad \textrm {and}\quad \textrm{RMTSE}^{q}=\frac{\sum\limits_{t=1}^{140}\textrm{TSE}^{q}_t}{\sum\limits_{t=1}^{140}\textrm{TSE}^{\textrm{Base}}_t}\,,
+\end{equation*}
+where $\textrm{TE}^{\textrm{Base}}_t$ and $\textrm{TSE}^{\textrm{Base}}_t$ are the total error and total squared error of the biased base forecasts at replication $t$.
+Stars indicate that the results are significantly different from the biased base forecasts using a DETAILS OF TEST HERE.
+Results are shown for $1$-step-ahead forecasts and} as was the case with Section~\ref{sec:comparebase}, the conclusions that follow extend almost identically to longer forecast horizons.
+{\color{blue} These are provided in an online supplement}.
+
+%\begin{table}[!b]
+%\caption {Average {MSE($\times 10^3$)} of $1$-step-ahead point forecasts from log and Box-Cox transformed series.
+Biased denotes forecasts from simply reversing the transformation via Eq.~\eqref{eq:BoxCox_back-transformation}.
+Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in Eq.~\eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
+%\label{tab:Results_MSE}
+%\centering
+%  \begin{tabular}{lcccccc}
+%    \toprule
+%    \multicolumn{1}{c}{ } & \multicolumn{3}{c}{Log Transformation} &
+%    \multicolumn{3}{c}{Box-Cox Transformation}\\
+%    \cmidrule(lr){2-4} \cmidrule(lr){5-7}
+%    Method & Biased & Unbiased & Unbiased & Biased & Unbiased & Unbiased \\
+%    & & (Method-1) & (Method-2) && (Method-1) &(Method-2)\\ \midrule
+%    Base      & 4.47 & 4.43 & 4.51 & 4.59 & 4.52 & 4.78\\
+%    OLS       & 4.34 & 4.31 & 4.36 & 4.46 & 4.40 & 4.63\\
+%    MinT      & 4.32 & \textbf{4.16} & 4.61 & 4.29 & \textbf{4.17} & 4.54\\
+%    WLS       & 4.82 & 4.38 & 5.43 & 4.77 & 4.42 & 5.23\\
+%    Bottom-up & 6.36 & 5.26 & 8.06 & 6.21 & 5.31 & 7.46\\
+%    \bottomrule
+%  \end{tabular}
+%\end{table}
 
 \begin{table}[!b]
-\caption {Average {MSE($\times 10^3$)} of $1$-step-ahead point forecasts from log and Box-Cox transformed series.
+{\color{blue}
+\caption {Average {\color{blue} RMTE and RMTSE} of $1$-step-ahead point forecasts from log and Box-Cox transformed series.
 Biased denotes forecasts from simply reversing the transformation via Eq.~\eqref{eq:BoxCox_back-transformation}.
-Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in Eq.~\eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
-\label{tab:Results_MSE}
-\centering
-  \begin{tabular}{lcccccc}
-    \toprule
-    \multicolumn{1}{c}{ } & \multicolumn{3}{c}{Log Transformation} &
-    \multicolumn{3}{c}{Box-Cox Transformation}\\
-    \cmidrule(lr){2-4} \cmidrule(lr){5-7}
-    Method & Biased & Unbiased & Unbiased & Biased & Unbiased & Unbiased \\
-    & & (Method-1) & (Method-2) && (Method-1) &(Method-2)\\ \midrule
-    Base      & 4.47 & 4.43 & 4.51 & 4.59 & 4.52 & 4.78\\
-    OLS       & 4.34 & 4.31 & 4.36 & 4.46 & 4.40 & 4.63\\
-    MinT      & 4.32 & \textbf{4.16} & 4.61 & 4.29 & \textbf{4.17} & 4.54\\
-    WLS       & 4.82 & 4.38 & 5.43 & 4.77 & 4.42 & 5.23\\
-    Bottom-up & 6.36 & 5.26 & 8.06 & 6.21 & 5.31 & 7.46\\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\begin{table}[!b]
-\caption {Average {MSE($\times 10^3$)} of $1$-step-ahead point forecasts from log and Box-Cox transformed series.
-Biased denotes forecasts from simply reversing the transformation via Eq.~\eqref{eq:BoxCox_back-transformation}.
-Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in Eq.~\eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
+Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in Eq.~\eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.
+{\color{blue}Stars indicate significant difference from biased base forecast according to a TEST DETAILS HERE.}}
 \label{tab:Results_MSE}
@@
   \end{tabular}
+}
 \end{table}

### 2020-01-22 R1/Response.tex
changes made to response documents

@@
 		We agree that if our empirical results only showed that applying the correct back-transformation improves accuracy, that this would be a very marginal contribution.
-However, we would like to emphasise that the extent to which it does this, also depend on the reconciliation method.
-TO DO (ELABORATE).\\
+The referee's suggestions have allowed us to make additional insights that we believe have greatly improved the paper.
+We discuss these in detail below.\\
 
@@
 
-		We now also report the mean error for all methods to highlight bias. TO DO (GEORGE)\\
+		We now also report the total error for all methods to highlight bias.
+Here we see that bias correction method 1 removes bias, while bias correction method 2 in fact worsens bias.
+A new insight that we are able to make is to recognise that reconciliation without bias correction can mitigate bias.
+For example, even if bias correction is not used at all, OLS reconciliation significantly reduces bias for both the log transformation and Box Cox transformation.
+This is likely to occur since bias lies in a direction that is almost orthogonal to the coherent subspace.\\
 
@@
 
-		We now include a Nemenyi comparison of the methods and report results in terms of percentage improvement over base forecasts. TO DO (GEORGE)\\
+		We now include report all results relative to the base forecasts. We also have added starts to the tables that report our results to indicate when a method significantly upon base forecasts.\\
 

### 2020-01-22 R1/Letter.tex
changes made to response documents

--- 2020-01-14 R1/Letter.tex
@@
 \begin{enumerate}
-	\item blah
+	\item We introduce a modification of MinT that should be implemented in contexts where some user defined loss function is sensible.
+Using the empirical example, we demonstrate that this generalised version of MinT takes both the nature of the loss function and dependence between forecast errors into account and outperforms a standard implementation of MinT and WLS.
+	\item We have greatly expanded the empirical study including more measures of forecast accuracy (including those specifically measuring bias).
+This has led to the insight that reconciliation alone can in fact reduce the bias of an estimator.
+Where differences in forecast accuracy are significant.
+	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negativity, 
 \end{enumerate}

### 2020-01-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
rewriting first empirical part

@@
 
-After obtaining the base forecasts these are reconciled using three different projection methods: OLS, MinT and WLS.
-{\color{blue}For MinT, the shrinkage estimator of \cite{Schafer2005} is used, i.e., $\bm{W}^{\text{MinT}} = \tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
+{\color{blue} For each replication and for method $q$, the total squared error (TSE), is computed as
+	\begin{equation*}
+	\textrm{TSE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,,
+	\end{equation*}
+	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
+This corresponds to the loss function described in Section~\ref{sec:orthogonal}. We also consider a loss function based on a generalised Euclidean distance of the form
+\begin{equation*}
+	\textrm{WSE}^{q}_t=\sum\limits_{i=1}^n w_i (y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,,
+	\end{equation*}
+	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
+}
+
+After obtaining the base forecasts these are reconciled using four different projection methods: OLS,{\color{blue} WLS, MinT and GMinT.
+For MinT and GMinT, the shrinkage estimator of \cite{Schafer2005} is used to estimate to covariance matrix of one step ahead forecast errors.
+That is $\bm{\Sigma} = \tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
 	\begin{equation*}
@@
 	where $\sigma_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}^{\text{sam}}$.
-For WLS, variance scaling is used, i.e., $\bm{W}^{\text{WLS}}=\text{diag}(\hat{\bm{\Sigma}})$.} Squared forecast errors are computed for each series and aggregated across the entire hierarchy; i.e., we compute the loss function described in Section~\ref{sec:orthogonal}.
-We then compute the difference in this loss function between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate.
-We also include bottom-up forecasts in this comparison for completeness.
+For WLS and GMinT, variance scaling is used, i.e., $\bm{W}^{\text{WLS}}=\text{diag}(\hat{\bm{\Sigma}})$ CHANGE DEPENDING ON FINAL CHOICE OF W.
+For both loss function} we compute the difference between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate.
 

### 2020-01-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
remove duplication of TSE definition

@@
 {\color{blue} For each replication and for method $q$, the total squared error (TSE), is computed as
-	\begin{equation*}
+	\begin{equation}
+	\label{eq:tse}
 	\textrm{TSE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,,
-	\end{equation*}
+	\end{equation}
 	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
@@
 We only present the results for $h=1$, but the results and conclusions that follow are almost identical for the other longer forecast horizons.
-We do not present these here to save space but they are available upon request.
+We do not present these here to save space but they are available {\color{blue} in an online supplement.}
 
@@
 Using the three sets of base forecasts from each of the two transformations, we generate coherent forecasts implementing OLS, MinT and WLS reconciliation projections, and also the bottom-up approach and compare the results for when the base forecasts are biased and bias-adjusted, i.e., unbiased.
-{\color{blue} For each replication and for method $q$, the total error (TE) and total squared error (TSE), are computed as
+{\color{blue} In addition to the total squared error defined in Equation~\ref{eq:tse}, the total error (TE) is used to measure bias and is computed as
 \begin{equation*}
-\textrm{TE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})\quad \textrm {and}\quad \textrm{TSE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,,
+\textrm{TE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})\quad \textrm {and}\quad \textrm{TSE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,.
 \end{equation*}
-where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
-The total error gives an indication of bias, while the total squared error is connected with Euclidean distance.
 Table~\ref{tab:Results_MSE} reports the relative mean total error (RMTE) and relative mean total error (RMTSE) defined as  

### 2020-01-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added gmint to intro

@@
 Futhermore, unlike \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general.
-Third, we prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased.
+{\color{blue} Third, we propose a generalised version of MinT that can be tailored to different loss functions.
+Recent work by \cite{NysEtAl2019} have proposed special cases of this method, but here we make the distinction  between the role of the loss function and dependence between forecast errors clear, decoupling two concepts that have previously been confounded with one another in the literature.
+Fourth}, we prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased.
 A natural question that arises is what to do in the case of biased reconciled forecasts.

### 2020-01-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added gmint to abstract

@@
 The geometric interpretation is further used to provide a new proof that forecast reconciliation results in unbiased forecasts provided the initial \emph{base} forecasts are also unbiased.
-Approaches for dealing with biased base forecasts are proposed and explored in an extensive empirical study on Australian tourism flows.
-Overall, the method of bias-correcting before carrying out reconciliation is shown to outperform alternatives that only bias-correct or only reconcile forecasts.
+{\color{blue} A generalised version of the MinT method (GMinT) and }approaches for dealing with biased base forecasts are proposed and {\color{blue}are both} explored in an extensive empirical study on Australian tourism flows.
+{\color{blue} Generalised MinT is shown to be effective in taking the loss function into account.} The method of bias-correcting before carrying out reconciliation is shown to outperform alternatives that only bias-correct or only reconcile forecasts.
 

### 2020-01-24 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
rewritten theory section to emphasise new ideas.

--- 2020-01-22 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
@@
 This interpretation facilitates the derivation of novel results that explain why and how reconciliation via projection is guaranteed to improve forecast accuracy with respect to a specific class of loss functions.
-The result is also demonstrated empirically.
-The geometric interpretation is further used to provide a new proof that forecast reconciliation results in unbiased forecasts provided the initial \emph{base} forecasts are also unbiased.
-Approaches for dealing with biased base forecasts are proposed and explored in an extensive empirical study on Australian tourism flows.
-Overall, the method of bias-correcting before carrying out reconciliation is shown to outperform alternatives that only bias-correct or only reconcile forecasts.
+The geometric interpretation is further used to provide a new proof that forecast reconciliation results in unbiased forecasts provided the initial Approaches for dealing with biased base forecasts are proposed.
+The implications of all theoretical results are demonstrated in an extensive empirical study on Australian tourism flows.
+The method of bias-correcting before carrying out reconciliation is shown to outperform alternatives that only bias-correct or only reconcile forecasts.
 
@@
 As a result forecast reconciliation can be applied in contexts where there are no clear candidates of \emph{bottom level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling.
-Second, we provide a new proof that reconciled forecasts dominate unreconciled forecasts which makes explicit the link between a reconciliation method and a loss function.
-We believe that this link is lacking in previous work that attempts to establish similar results, in particular \citet{VanErven2015a} and \citet{WicEtAl2019}.
+Second, {\color{blue} we provide a new proof that for a given class of loss functions, reconciled forecasts can be found that dominate unreconciled forecasts.
+The projection that achieves this only depends on the loss function and not on the dependence in forecast errors.
+We believe that the link between a reconciliation method and loss function has not always been made clear in previous work that has dealt with this issue, for example \citet{VanErven2015a} and \citet{WicEtAl2019}}.
 Futhermore, unlike \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general.
-Third, we prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased.
+{\color{blue} Third, we show that when it comes to minimising the expected value of the same class of loss functions, the optimal projection depends only on the covariance of the forecast errors, something that is targeted by the MinT method as well as newer methods found in \cite{NysEtAl2019}.
+Fourth}, we prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased.
 A natural question that arises is what to do in the case of biased reconciled forecasts.
@@
 A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ is minimal over any possible $\tilde{\bm{y}}\in\mathfrak{s}$.
-In this sense reconciliation via orthogonal projection leads to the smallest possible adjustments of the base forecasts.
+{\color{blue} For Euclidean distance this can be expressed as minimising $\|\bm{S}\bm{G}\hat{\bm{y}}-\hat{\bm{y}}\|$ with respect to $\bm{G}$ where $\|.\|$ denotes the $L_2$ norm.}  In this sense reconciliation via orthogonal projection {\color{blue} $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$} leads to the smallest possible adjustments of the base forecasts.
 
-The property that reconciliation should improve forecasts was touched upon in Section 2.3 of \citet{WicEtAl2019}.
+The {\color{blue} second} property, that reconciliation should improve forecasts was touched upon in Section 2.3 of \citet{WicEtAl2019}.
 The discussion in that paper focuses on the case of MinT\@.
@@
 For example, in hierarchies, top-level series tend to have a much larger scale than bottom-level series.
-Even when two series are on a similar scale, series that are more predictable or less variable will tend to be downweighted by simply aggregating squared errors.
+Even when two series are on a similar scale, series that are more predictable or less variable will tend to be down-weighted by simply aggregating squared errors.
 An even more sophisticated understanding may take the correlation between series into account.
-All of these considerations lead towards reconciliation of the form $\tilde{\bm{y}}=\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, where $\bm{W}$ is a symmetric matrix.
-Generally, it is assumed that $\bm{W}$ is invertible, otherwise a pseudo inverse can be used.
+All of these considerations lead towards {\color{blue} thinking of distance and loss functions based on $||\bm{v}||_{\bm{W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, where $\bm{W}$ is a symmetric matrix assumed to be invertible.
+In the geometry defined by the norm $||.||_{\bm{W}^{-1}}$, referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$, an orthogonal projection has the form $\tilde{\bm{y}}=\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$.}
 
-It should be noted that $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is an oblique, rather than an orthogonal projection matrix in the usual Euclidean geometry.
-{\color{blue}Alternatively,} this matrix can be considered to be an orthogonal projection for a different geometry defined by the norm\break $||\bm{v}||_{\bm{W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
-One way to understand this geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$.
+One way to understand the generalied Euclidean geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$.
 This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{-1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{-1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{-1/2}\tilde{\bm{y}}$.
@@
 
-The implication of Theorem~\ref{th:gdistred} is that if the objective function is some weighted sum of squared errors, or a Mahalanobis distance, then the projection matrix $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts, for an appropriately selected $\bm{W}$.
+The implication of Theorem~\ref{th:gdistred} is that if the objective function is {\color{blue} a priori as} some weighted sum of squared errors, or a Mahalanobis distance, then the projection matrix $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts, for an appropriately selected $\bm{W}$.
+{\color{blue}  This result does not depend on the covariance of forecast errors except in the special case where $\bm{W}$ is set to this covariance matrix.}
 
@@
 In contrast, \citet{WicEtAl2019} follow \citet{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.
-The proof of \citet{WicEtAl2019} requires an assumption about convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.
+The proof of \citet{WicEtAl2019} requires an assumption of convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.
 The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.
-As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is true only with respect to a loss function that depends on $\bm{W}$.
-If Euclidean distance (or mean squared error) is used, there will be realisations where the MinT estimator does not improve forecast accuracy relative to base forecasts.
+As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is true only with respect to a loss function that depends on {\color{blue} $||.||_{\bm{W}^{-1}}$ and only when $\bm{W}$ is the covariance matrix estimate used by MinT}.
+If Euclidean distance (or mean squared error) is used {\color{blue} as a loss function}, there will be realisations where the MinT estimator does not improve forecast accuracy relative to base forecasts.
 This will be demonstrated using a real data set in the empirical study in Section~\ref{sec:comparebase}.
@@
 
-While the properties discussed so far hold for any projection matrix, the MinT method of \citet{WicEtAl2019} has an additional optimality property.
-\citet{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts is minimised by the oblique projection {\color{blue} $\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}$}.
-Here, {\color{blue}$\bm{\Sigma}$} is the forecast error covariance matrix with errors come from using the base forecasts.
+{\color{blue}The discussion so far provides a roadmap, such that for a given choice of $\bm{W}$, a projection method with distance-reducing properties can be derived}.
+While the MinT method of \citet{WicEtAl2019} {\color{blue} is a special case of such a projection, it was in fact motivated by a different} optimality property.
+\citet{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts{\color{blue}, i.e, $\textrm{tr}(E(y_t-\tilde{y}_t)(y_t-\tilde{y}_t)')$,} is minimised by the oblique projection {\color{blue} $\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}$}.
+Here, {\color{blue}$\bm{\Sigma}$} is the forecast error covariance matrix where errors come from using the base forecasts.
 Although the base forecast error covariance matrix is unknown, it can be estimated using in-sample errors.
+{\color{blue} In the subsequent discussion MinT will refer to any method that attempts to estimate $\bm{\Sigma}$, specific estimators can be found in \cite{WicEtAl2019} and also \cite{NysEtAl2019}.}
 
@@
 
-\subsection{Generalised MinT}
+\subsection{MinT with General Loss Functions}
 
-As discussed in the previous section, the MinT method has a motivation that is quite separate from the considerations of Theorem~\ref{th:gdistred}.
+%\subsection{Generalised MinT}
+%
+%As discussed in the previous section, the MinT method has a motivation that is quite separate from the considerations of Theorem~\ref{th:gdistred}.
 In spite of this, it is also true that Theorem~\ref{th:gdistred} guarantees that MinT will always improve upon base forecasts when the loss function is based on the norm $\|.\|_{\bm{\Sigma}^{-1}}$.
@@
 Our proposed method targets more general loss functions than the sum of squared errors (in a similar vein to \cite{VanErven2015a} and \cite{NysEtAl2019}), while exploiting the correlation structure of forecast errors (in a similar vein to \cite{WicEtAl2019}).
-
-Consider a loss function based on $\|.\|_{\bm{W}^{-1}}$ where the choice of $\bm{W}$ is determined by the context of the forecasting problem, rather than by statistical considerations.
+%
+%Consider a loss function based on $\|.\|_{\bm{W}^{-1}}$ where the choice of $\bm{W}$ is determined by the context of the forecasting problem, rather than by statistical considerations.
 For instance, our empirical example in Section~\ref{sec:EmpStudy} considers the number of tourists visiting different regions in Australia.
@@
 This is an orthogonal projection in the space transformed after pre-multiplying by ${\bm W}^{-1/2}$.
-
-In the case where $\bm{W}=\bm{I}$, it has been established that MinT reconciliation often outperform OLS reconciliation in a statistical sense.
+%
+%In the case where $\bm{W}=\bm{I}$, it has been established that MinT reconciliation often outperform OLS reconciliation in a statistical sense.
 Therefore we propose a generalisation of MinT that maintains trace minimising properties but also accounts for user-defined loss functions.
@@
 The projection achieves this is $\bm{S}\bm{G}^{\text{GMinT}}$, where
-\begin{equation*}
-\bm{G}^{\text{GMinT}}=\left(\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\bm{S}\right)^{-1}\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\,.
-\end{equation*}
-We note that some of solutions to the reconciliation problem proposed by \cite{NysEtAl2019}, for example \textit{series GLASSO scaling} and \textit{series shrinkage scaling} are special cases of this method where $\bm{W}$ is diagonal.
+%\begin{equation*}
+%\bm{G}^{\text{GMinT}}=\left(\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\bm{S}\right)^{-1}\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\,.
+%\end{equation*}
+%We note that some of solutions to the reconciliation problem proposed by \cite{NysEtAl2019}, for example \textit{series GLASSO scaling} and \textit{series shrinkage scaling} are special cases of this method where $\bm{W}$ is diagonal.
 What we seek to make clear here is the connection between $\bm{W}^{-1/2}$ (which need not be diagonal) and the loss function.
 In particular, Generalised MinT allows the choice of loss function to be decoupled from the choice of an oblique projection with attractive statistical properties.
-
-As an important caveat, it should be noted that rank deficient choices of $\bm{W}$ will in most cases lead to no solution.
+%
+%As an important caveat, it should be noted that rank deficient choices of $\bm{W}$ will in most cases lead to no solution.
 For instance, it is not uncommon in the hierarchical forecasting literature that the overall aggregate is of greatest interest.

### 2020-01-24 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
more rewriting

@@
 Forecast reconciliation has mostly been formulated using a regression model {\color{blue} that admits a generalised least squares (GLS) solution}, see \citet{Hyndman2011} and \citet{WicEtAl2019} for examples.
-{\color{blue} Alternatively, \cite{VanErven2015a} and \cite{NysEtAl2019} arrive at a GLS solution by formulating the problem as as an optimisation problem to minimises weighted squared errors between coherent and incoherent forecasts}.
+{\color{blue} Alternatively, \cite{VanErven2015a} and \cite{NysEtAl2019} arrive at a GLS solution by formulating reconciliation as an optimisation problem to minimise weighted squared errors between coherent and incoherent forecasts}.
 The regression setup can be counter-intuitive since a vector comprised of forecasts from different time series models is also assumed to be the dependent variable in a regression model.
@@
 The latter paper also proposes a particular version of reconciliation known as the Minimum Trace (MinT) method.
-This is optimal in the sense of minimising the trace of the reconciled forecast error covariance matrix under the assumption that the base forecasts are unbiased.
+This is optimal in a {\color{blue} different} sense of minimising the trace of the reconciled forecast error covariance matrix under the assumption that the base forecasts are unbiased.
 
@@
 We believe that this is clearer and more intuitive than explanations based on regression modelling.
-In addition to casting existing results in a new light, the geometric interpretation also allows us to derive three new important results.
+In addition to casting existing results in a new light, the geometric interpretation also allows us to derive {\color{blue}four} new important results.
 
@@
 As a result forecast reconciliation can be applied in contexts where there are no clear candidates of \emph{bottom level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling.
-Second, {\color{blue} we provide a new proof that for a given class of loss functions, reconciled forecasts can be found that dominate unreconciled forecasts.
-The projection that achieves this only depends on the loss function and not on the dependence in forecast errors.
-We believe that the link between a reconciliation method and loss function has not always been made clear in previous work that has dealt with this issue, for example \citet{VanErven2015a} and \citet{WicEtAl2019}}.
-Futhermore, unlike \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general.
-{\color{blue} Third, we show that when it comes to minimising the expected value of the same class of loss functions, the optimal projection depends only on the covariance of the forecast errors, something that is targeted by the MinT method as well as newer methods found in \cite{NysEtAl2019}.
+Second, {\color{blue} we provide a new proof of the results that reconciled forecasts dominate unreconciled forecasts, for a certain class of loss functions.
+The projection that achieves this need only depend on the loss function and not on the dependence in forecast errors.}  Futhermore, unlike {\color{blue} proofs of similar results by} \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general.
+{\color{blue} Third, we show that when it comes to minimising the expected value of the same class of loss functions, the optimal projection depends only on the covariance of the forecast errors.
+While this is a direct consequence of the trace minimising property already established by \cite{WicEtAl2019}, we provide new intuition and also establish that the result applies to a more general class of loss functions.
 Fourth}, we prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased.
@@
 Section~\ref{sec:CoheForecasts} deals with the concept of coherence and defines hierarchical time series in a way that does not depend on any notion of bottom-level series.
-Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projections and includes a proof that reconciled forecasts dominate base forecasts with respect to a specific loss function.
+Section~\ref{sec:Reconciliation} defines forecast reconciliation in terms of projections and includes proofs that make the optimality properties of different reconciliation methods clear.
 In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose methods for bias correction.
@@
 the base and reconciled forecasts should be `close'.
-{\color{blue} This property is particularly emphasised by \cite{VanErven2015a} and \cite{NysEtAl2019}}
+{\color{blue} This property is particularly emphasised by \cite{NysEtAl2019}}
 \item The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value targeted by the forecast.
@@
 
-To address the first of these properties we make the concept of closeness more concrete, by considering the Euclidean distance between the base forecast $\hat{\bm{y}}$ and the reconciled forecast $\tilde{\bm{y}}$.
-A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ is minimal over any possible $\tilde{\bm{y}}\in\mathfrak{s}$.
-{\color{blue} For Euclidean distance this can be expressed as minimising $\|\bm{S}\bm{G}\hat{\bm{y}}-\hat{\bm{y}}\|$ with respect to $\bm{G}$ where $\|.\|$ denotes the $L_2$ norm.}  In this sense reconciliation via orthogonal projection {\color{blue} $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$} leads to the smallest possible adjustments of the base forecasts.
+To address the first of these properties we make the concept of closeness more concrete by considering the Euclidean distance between the base forecast $\hat{\bm{y}}_{t+h|t}$ and the reconciled forecast $\tilde{\bm{y}}_{t+h|t}$.
+A property of an orthogonal projection is that the distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$ is minimal over any possible $\tilde{\bm{y}}\in\mathfrak{s}$.
+{\color{blue} For Euclidean distance this can be expressed as minimising $\|\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}\|$ with respect to $\bm{G}$ where $\|.\|$ denotes the $L_2$ norm.}  In this sense reconciliation via orthogonal projection {\color{blue} $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$} leads to the smallest possible adjustments of the base forecasts.
 
-The {\color{blue} second} property, that reconciliation should improve forecasts was touched upon in Section 2.3 of \citet{WicEtAl2019}.
-The discussion in that paper focuses on the case of MinT\@.
+The {\color{blue} second property is concerned with $\|{\bm{y}}_{t+h}-\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}\|$ relative to $\|{\bm{y}}_{t+h}-\hat{\bm{y}}_{t+h|t}\|$.
+The idea is} that reconciled forecasts should always be closer to the target than base forecasts and was touched upon in Section 2.3 of \citet{WicEtAl2019}.
+The discussion in that paper focuses on the {\color{blue} special} case of MinT\@.
 Here we provide a new explicit proof of that result.
@@
 In particular, this measure is the square root of the sum of squared forecast errors of \emph{all} variables in the hierarchy.
-Consequently, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to less accurate forecasts for individual series.
+Consequently, while forecast improvement is guaranteed for the hierarchy overall, {\color{blue} forecast errors are treated equally across all series} and reconciliation can {\color{blue} still} lead to less accurate forecasts for individual series.
 Second, although orthogonal projections are guaranteed to improve on base forecasts, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.
 Therefore, referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT\@.
-It is to oblique projections that we now turn our attention.
+{\color{blue} We now turn our attention to the way oblique projections can address both of these shortcomings} .
 
@@
 An even more sophisticated understanding may take the correlation between series into account.
+{\color{blue} Finally, the context of the forecast problem itself may suggest a loss function, for instance in our tourism example an appropriate loss function may weight forecast errors by average tourism expenditure in each reason}.
 All of these considerations lead towards {\color{blue} thinking of distance and loss functions based on $||\bm{v}||_{\bm{W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, where $\bm{W}$ is a symmetric matrix assumed to be invertible.
-In the geometry defined by the norm $||.||_{\bm{W}^{-1}}$, referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$, an orthogonal projection has the form $\tilde{\bm{y}}=\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$.}
+In the geometry defined by the norm $||.||_{\bm{W}^{-1}}$, referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
+}
 
@@
 This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{-1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{-1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{-1/2}\tilde{\bm{y}}$.
-The transformed reconciled forecast results from an orthogonal projection in the transformed space since
+{\color{blue} An orthogonal projection of the form $\tilde{\bm{y}}=\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, is an} orthogonal projection in the transformed space since
 \begin{align*}
@@
 
-The implication of Theorem~\ref{th:gdistred} is that if the objective function is {\color{blue} a priori as} some weighted sum of squared errors, or a Mahalanobis distance, then the projection matrix $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts, for an appropriately selected $\bm{W}$.
+The implication of Theorem~\ref{th:gdistred} is that if the loss function is {\color{blue} given a priori as total sum of squared errors in some linearly transformed space,} then the projection matrix $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts.
 {\color{blue}  This result does not depend on the covariance of forecast errors except in the special case where $\bm{W}$ is set to this covariance matrix.}
@@
 While the MinT method of \citet{WicEtAl2019} {\color{blue} is a special case of such a projection, it was in fact motivated by a different} optimality property.
-\citet{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts{\color{blue}, i.e, $\textrm{tr}(E(y_t-\tilde{y}_t)(y_t-\tilde{y}_t)')$,} is minimised by the oblique projection {\color{blue} $\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}$}.
+\citet{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts{\color{blue}, i.e, $\textrm{tr}(E(\bm{y}_t-\tilde{\bm{y}}_t)(\bm{y}_t-\tilde{\bm{y}}_t)')$,} is minimised by the oblique projection {\color{blue} $\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}$}.
 Here, {\color{blue}$\bm{\Sigma}$} is the forecast error covariance matrix where errors come from using the base forecasts.
@@
 
-After obtaining the base forecasts these are reconciled using four different projection methods: OLS,{\color{blue} WLS, MinT and GMinT.
-For MinT and GMinT, the shrinkage estimator of \cite{Schafer2005} is used to estimate to covariance matrix of one step ahead forecast errors.
+After obtaining the base forecasts these are reconciled using four different projection methods: OLS,{\color{blue} WLS and MinT.
+For MinT, the shrinkage estimator of \cite{Schafer2005} is used to estimate to covariance matrix of one step ahead forecast errors.
 That is $\bm{\Sigma} = \tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
@@
 	where $\sigma_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}^{\text{sam}}$.
-For WLS and GMinT, variance scaling is used, i.e., $\bm{W}^{\text{WLS}}=\text{diag}(\hat{\bm{\Sigma}})$ CHANGE DEPENDING ON FINAL CHOICE OF W.
+For WLS, variance scaling is used, i.e., $\bm{W}^{\text{WLS}}=\text{diag}(\hat{\bm{\Sigma}})$ CHANGE DEPENDING ON FINAL CHOICE OF W.
 For both loss function} we compute the difference between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate.
@@
 \begin{equation*}
-\textrm{TE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})\quad \textrm {and}\quad \textrm{TSE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,.
+\textrm{TE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})\,.
 \end{equation*}

### 2020-01-25 R1/Response.tex
changes made to response and letter in light of the fact that GMinT doesnt work

@@
 
-		We now propose a generalised version of MinT, to be used with a loss function where $\bm{W}$ is defined by the context of the problem.
-In our empirical study we provide one such example of a loss function.
-We show that blah blah blah.
-TO DO (TAS).
-Demonstrating these additional contributions in the context of our existing empirical example has lengthened the paper considerably.
+		The objective of this paper is not to propose a new and better reconciliation approach but to establish new results that lead to clearer understanding of the properties of existing methods.
+Therefore, while the paper does not include a new method, it does provide insights into how new methods should (or should not) be developed.
+For examples of this, see the discussion on page 19 just before Section 4.1 and comments in the conclusion.\\
+
+		In this paper, the purpose of the empirical evaluation is to provide a demonstration of the theoretical results that we have established.
+We agree that this could be improved.
+We have greatly expanded Section 5.2 to more clearly investigate two different loss functions and demonstrate two different understandings of optimality.\\
+
+		Improving the existing empirical application in the ways suggested by the referee has lengthened the paper considerably.
 Therefore, we prefer to refrain from including a second empirical demonstration.\\
@@
 
-	    Report results for two different error metrics and include this. TO DO\\
+	    We now expand section 5.2 to report results for two different error metrics.
+Furthermore we have added additional insights in Section 3.4 that are now also demonstrated in this section.
+In particular we show that while the distance reducing property of Theorem 3.2 depends entirely on the choice of loss function, minimising the expected loss function can always be achieved by a MinT approach.
+TO DO.\\
 
@@
 
-	    Reflecting on this issue has led us towards the development of a generalised version of MinT which we now include in the paper.
-Briefly, the geometric insight allows us to decouple the issue of choice of loss function (which may be influenced by the context of the forecasting problem) from the issue of the properties of a given reconciliation method (which is a statistical question).\\
+	    Reflecting on this issue has led us towards making a number of changes.
+To reiterate, we may define a loss function based on the notion of Euclidean distance.
+In this case an orthogonal projection is guaranteed to lead to reconciled forecasts that are better than base forecasts.
+Alternatively we may define a more general loss function, for instance by taking weights into account.
+In this case, it is an orthogonal projection in the \textit{transformed} space that has the same optimality properties.\\
+
+	    Now consider the property of minimising expected loss when the loss is function based on Euclidean distance.
+This can be achieved by the MinT estimator.
+We now provide a new result proving that minimising the expected loss in a transformed space in fact leads to the same MinT estimator.\\
+
+	    To make the transformed space more interpretable we consider a new loss function that is driven by the example used in our empirical evaluation.  This is a loss function weighted by ... TO DO
 

### 2020-01-25 R1/Letter.tex
changes made to response and letter in light of the fact that GMinT doesnt work

@@
 \begin{enumerate}
-	\item We introduce a modification of MinT that should be implemented in contexts where some user defined loss function is sensible.
-Using the empirical example, we demonstrate that this generalised version of MinT takes both the nature of the loss function and dependence between forecast errors into account and outperforms a standard implementation of MinT and WLS.
 	\item We have greatly expanded the empirical study including more measures of forecast accuracy (including those specifically measuring bias).
@@
 Where differences in forecast accuracy are significant.
+	\item We introduce some new results about MinT that make it clear that MinT minimises expected loss for a wider range of loss functions than previously thought.
 	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negativity, 

### 2020-01-26 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added some of the connection between MinT and loss functions

@@
 A property of an orthogonal projection is that the distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$ is minimal over any possible $\tilde{\bm{y}}\in\mathfrak{s}$.
-{\color{blue} For Euclidean distance this can be expressed as minimising $\|\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}\|$ with respect to $\bm{G}$ where $\|.\|$ denotes the $L_2$ norm.}  In this sense reconciliation via orthogonal projection {\color{blue} $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$} leads to the smallest possible adjustments of the base forecasts.
+{\color{blue} For Euclidean distance this can be expressed as minimising a loss function $\|\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}\|$ with respect to $\bm{G}$ where $\|.\|$ denotes the $L_2$ norm.}  In this sense reconciliation via orthogonal projection {\color{blue} $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$} leads to the smallest possible adjustments of the base forecasts.
 
-The {\color{blue} second property is concerned with $\|{\bm{y}}_{t+h}-\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}\|$ relative to $\|{\bm{y}}_{t+h}-\hat{\bm{y}}_{t+h|t}\|$.
-The idea is} that reconciled forecasts should always be closer to the target than base forecasts and was touched upon in Section 2.3 of \citet{WicEtAl2019}.
-The discussion in that paper focuses on the {\color{blue} special} case of MinT\@.
-Here we provide a new explicit proof of that result.
-We do so first in the case of an orthogonal projection where the geometric intuition of the proof is clear and then generalise the result to reconciliation using any projection matrix in Section~\ref{sec:oblique}.
+The {\color{blue} second property is concerned with a loss function $L({\bm{y}}_{t+h},\breve{\bm{y}}_{t+h})=\|{\bm{y}}_{t+h}-\bm{S}\bm{G}\breve{\bm{y}}_{t+h|t}\|$ where $\breve{\bm{y}}_{t+h|t}$ is either a base or reconciled forecast.
+More specifically, the aim is to reconcile so that $L({\bm{y}}_{t+h},\hat{\bm{y}}_{t+h})-L({\bm{y}}_{t+h},\tilde{\bm{y}}_{t+h})$ is guaranteed to be positive.\, that is} reconciled forecasts should always be closer to the target than base forecasts.
+{\color{blue} This idea was} touched upon in Section 2.3 of \citet{WicEtAl2019} for the {\color{blue} special} case of MinT\@ {\color{blue} which has a slightly different loss function}.
+Here we provide a new explicit {\color{blue} and general} proof of that result.
+We do so first in the case {\color{blue} of a loss function based on Euclidean distance} where the geometric intuition of the proof is clear and then generalise the result to reconciliation using any projection matrix in Section~\ref{sec:oblique}
 
@@
 {\color{blue} Finally, the context of the forecast problem itself may suggest a loss function, for instance in our tourism example an appropriate loss function may weight forecast errors by average tourism expenditure in each reason}.
-All of these considerations lead towards {\color{blue} thinking of distance and loss functions based on $||\bm{v}||_{\bm{W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, where $\bm{W}$ is a symmetric matrix assumed to be invertible.
-In the geometry defined by the norm $||.||_{\bm{W}^{-1}}$, referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
+All of these considerations lead towards {\color{blue} a loss function $L_{\bm W}(\bm{y}_{t+h},\breve{\bm{y}}_{t+h|t})=||{\bm{y}_{t+h}-\breve{\bm{y}}_{t+h|t}}||_{\bm{W}^{-1}}$ where $||\bm{v}||_{\bm{W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, and $\bm{W}$ is a symmetric matrix assumed to be invertible.
+The geometry defined by the norm $||.||_{\bm{W}^{-1}}$, will be referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
 }
@@
 This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{-1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{-1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{-1/2}\tilde{\bm{y}}$.
-{\color{blue} An orthogonal projection of the form $\tilde{\bm{y}}=\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, is an} orthogonal projection in the transformed space since
+{\color{blue} An projection of the form $\tilde{\bm{y}}=\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, is an} orthogonal projection in the transformed space since
 \begin{align*}
@@
 
-Thinking of the problem in terms of a geometry defined by the norm $\bm{v}'\bm{W}^{-1}\bm{v}$ is also quite instructive when it comes to thinking about the connection between distances and loss functions.
+%Thinking of the problem in terms of a geometry defined by the norm $\bm{v}'\bm{W}^{-1}\bm{v}$ is also quite instructive when it comes to thinking about the connection between distances and loss functions.
 In the generalised Euclidean geometry, the distance between the reconciled forecast and the realisation is given by $(\bm{y}-\hat{\bm{y}})'\bm{W}^{-1}(\bm{y}-\hat{\bm{y}})$.
@@
 Therefore Theorem~\ref{th:distred} can easily be generalised as follows.
+
+Thinking of the generalised Euclidean space as a transformed version of Euclidean space also allows the distance reducing property of Theorem~\ref{th:distred} to be generalised to any loss function $L_{\bm{W}}$
 
@@
 {\color{blue}The discussion so far provides a roadmap, such that for a given choice of $\bm{W}$, a projection method with distance-reducing properties can be derived}.
-While the MinT method of \citet{WicEtAl2019} {\color{blue} is a special case of such a projection, it was in fact motivated by a different} optimality property.
-\citet{WicEtAl2019} show that for unbiased base forecasts, the trace of the forecast error covariance matrix of reconciled forecasts{\color{blue}, i.e, $\textrm{tr}(E(\bm{y}_t-\tilde{\bm{y}}_t)(\bm{y}_t-\tilde{\bm{y}}_t)')$,} is minimised by the oblique projection {\color{blue} $\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}$}.
-Here, {\color{blue}$\bm{\Sigma}$} is the forecast error covariance matrix where errors come from using the base forecasts.
+While the MinT method of \citet{WicEtAl2019} {\color{blue} is a special case of such a projection, it was in fact motivated by a different optimality property of minimising the} trace of the forecast error covariance matrix of reconciled forecasts
+
+{\color{blue}
+\begin{equation}
+\label{eq:MinTObj}
+\underset{\bm{G}}{\min}\,\textrm{tr}(E\left[(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'\right])\,.
+\end{equation}
+}
+
+The solution is the oblique projection {\color{blue} $\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}$}.
+Here, {\color{blue}$\bm{\Sigma}=E(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'$} is the forecast error covariance matrix where errors come from using the base forecasts.
 Although the base forecast error covariance matrix is unknown, it can be estimated using in-sample errors.
@@
 
-\subsection{MinT with General Loss Functions}
+\subsection{MinT and Loss Functions}
+
+We now make explicit the connection betwenn the MinT and a loss function based on the Euclidean distance $L(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|$.
+By the properties of the trace operator, the objective function in Equation~\ref{eq:MinTObj} can be rearranged as
+
+\begin{align*}
+\label{eq:MinTObj}
+\textrm{tr}(E\left[(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'\right])&=\textrm{tr}(E\left[(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})\right])\\
+%&=E\left[(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})\right]\\
+&=E\left[\|\bm{y}-{\bm S}{\bm G}\hat{\bm{y}}\|\right]\\
+&=E\left[L(\bm{y},\tilde{\bm{y}})\right]
+\end{align*}
+
+Note that although the loss function used here is the same as in Section~\ref{sec:orthogonal}, the sense in which reconciliation is optimal is different.
+Theorem~\ref{th:distred} implies optimality in the sense that reconcilied forecasts always improve on base forecasts.
+For MinT, optimality refers to minimising the expected loss function \textit{in expectation}.
+
+A natural question may be to derive a reconciliation method that minimises expected loss where the loss function is the generalised Euclidean distance between the realisation and reconciled forecast.
+That is to solve the optimisation problem
+
+{\color{blue}
+	\begin{equation}
+	\label{eq:GMinTObj}
+	\underset{\bm{G}}{\min}\,\textrm{tr}(E\left[(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'\bm{W}^{-1}(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})\right])\,.
+	\end{equation}
+}
+
+The following theorem proves that the solution to this optimisation problem does not depend of the choice of $\bm{W}$ used in the loss function.
+
+\begin{theo}[MinT minimises expected loss]\label{th:gdistred}
+    The usual MinT reconciliation method $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}$ solves the optimisation problem in Equation~\ref{eq:GMinTObj} for any $\bm{W}$.
+\end{theo}
+\begin{proof}
+	To be completed.
+\end{proof}
 

### 2020-01-27 R1/Response.tex
minor changes to letter

@@
 
-		We now include report all results relative to the base forecasts. We also have added starts to the tables that report our results to indicate when a method significantly upon base forecasts.\\
+		We now report all results relative to the base forecasts. We also have added stars to the tables that report our results to indicate when a method significantly upon base forecasts.\\
 
@@
 
-		The objective of this paper is not to propose a new and better reconciliation approach but to establish new results that lead to clearer understanding of the properties of existing methods.
+		The objective of this paper is not to propose a new and better reconciliation approach but to establish new results that lead to clearer understanding of the properties of existing methods that in turn motivate research into new methods.
 Therefore, while the paper does not include a new method, it does provide insights into how new methods should (or should not) be developed.
@@
 Furthermore we have added additional insights in Section 3.4 that are now also demonstrated in this section.
-In particular we show that while the distance reducing property of Theorem 3.2 depends entirely on the choice of loss function, minimising the expected loss function can always be achieved by a MinT approach.
-TO DO.\\
+In particular we show that while the distance reducing property of Theorem 3.2 depends entirely on the choice of loss function, minimising the expected loss function can always be achieved by a MinT approach.\\
 

### 2020-01-27 R1/Letter.tex
minor changes to letter

@@
 This has led to the insight that reconciliation alone can in fact reduce the bias of an estimator.
-Where differences in forecast accuracy are significant.
-	\item We introduce some new results about MinT that make it clear that MinT minimises expected loss for a wider range of loss functions than previously thought.
-	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negativity, 
+We also now also report where differences in forecast accuracy are statistically significant.
+	\item We introduce some new results about MinT that explicitly makes the connection between trace minimisation and minimises a loss function based on Euclidean distance.
+We also prove a new result that MinT minimises expected loss for loss functions based on generalised Euclidean distance.
+This result is demonstrated in an expanded empirical application in section 5.2 that includes a wider range of loss functions.
+	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negative forecasts, and state-space models. 
 \end{enumerate}

### 2020-01-28 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
started proof for MinT

@@
 \begin{proof}
-	To be completed.
+	The loss function in Equation~\ref{eq:GMinTObj} is equivalent to Euclidean distance in the transformed space and can therefore be minimised by using the MinT method in this space.
+The MinT method in the transformed space is give by
+	\begin{equation}
+	\label{eq:MinTtran}
+	\tilde{\bm{y}}^{*}=\bm{S}^{*}\left(\bm{S}^{*'}\bm{\Sigma}^{*-1}\bm{S}^{*}\right)^{-1}\bm{S}^{*'}\bm{\Sigma}^{*-1}\hat{\bm{y}}^{*}\,,
+	\end{equation}
+	where  $\bm{y}^{*}=\bm{W}^{-1/2}\bm{y}$, $\bm{S}^{*}=\bm{W}^{-1/2}\bm{S}$, $\hat{\bm{y}}^{*}=\bm{W}^{-1/2}\hat{\bm{y}}$ and
+	\begin{align*}
+	\bm{\Sigma}^*&=E\left[(\bm{y}^{*}-\hat{\bm{y}}^{*})(\bm{y}^{*}-\hat{\bm{y}}^{*})'\right]\\
+	&=E\left[\bm{W}^{-1/2}(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'\bm{W}^{-1/2'}\right]\\
+	&=\bm{W}^{-1/2}E\left[(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'\right]\bm{W}^{-1/2'}\\
+	&=\bm{W}^{-1/2}\bm{\Sigma}\bm{W}^{-1/2'}
+	\end{align*}
+	Substituting the expressions for $\bm{\Sigma}^*$, $\bm{y}^{*}$ and $\hat{\bm{y}}^{*}$ into Equation~\ref{eq:MinTtran} yields, 
+	\begin{eqnarray*}
+	\bm{W}^{-1/2}\bm{y}=&\bm{W}^{-1/2}\bm{S}\left((\bm{W}^{-1/2}\bm{S})'(\bm{W}^{-1/2}\bm{\Sigma}\bm{W}^{-1/2'})^{*-1}\bm{W}^{-1/2}\bm{S}\right)^{-1}\\
+	&(\bm{W}^{-1/2}\bm{S})'(\bm{W}^{-1/2}\bm{\Sigma}\bm{W}^{-1/2'})^{*-1}\bm{W}^{-1/2}\hat{\bm{y}}\\
+	\end{eqnarray*}
 \end{proof}

### 2020-01-28 R1/Response.tex
minor changes to response and letter to reflect third loss function

@@
 Here we see that bias correction method 1 removes bias, while bias correction method 2 in fact worsens bias.
-A new insight that we are able to make is to recognise that reconciliation without bias correction can mitigate bias.
+A new insight that we are able to make is to recognise that reconciliation without bias correction can still mitigate bias.
 For example, even if bias correction is not used at all, OLS reconciliation significantly reduces bias for both the log transformation and Box Cox transformation.
@@
 
-		The objective of this paper is not to propose a new and better reconciliation approach but to establish new results that lead to clearer understanding of the properties of existing methods that in turn motivate research into new methods.
+		The objective of this paper is not to propose a new and better reconciliation approach.
+Rather it is to establish new results that lead to clearer understanding of the properties of existing methods that in turn motivate research into new methods.
 Therefore, while the paper does not include a new method, it does provide insights into how new methods should (or should not) be developed.
@@
 We agree that this could be improved.
-We have greatly expanded Section 5.2 to more clearly investigate two different loss functions and demonstrate two different understandings of optimality.\\
+We have greatly expanded Section 5.2 to more clearly investigate three different loss functions and demonstrate the different ways in which reconciliation methods can be considered optimal.\\
 
@@
 
-	    We now expand section 5.2 to report results for two different error metrics.
+	    We now expand section 5.2 to report results for three different error metrics.
 Furthermore we have added additional insights in Section 3.4 that are now also demonstrated in this section.
-In particular we show that while the distance reducing property of Theorem 3.2 depends entirely on the choice of loss function, minimising the expected loss function can always be achieved by a MinT approach.\\
+In particular we show that while the distance reducing property of Theorem 3.2 depends entirely on the choice of loss function, minimising the expected loss function can always be achieved by a MinT approach and does not depend on the weights used in a loss function.\\
 
@@
 Alternatively we may define a more general loss function, for instance by taking weights into account.
-In this case, it is an orthogonal projection in the \textit{transformed} space that has the same optimality properties.\\
+We now consider two such loss functions, one based on the structure of the hierarchy (so-called `structural scaling') and another based on average spend in each region.
+The latter of these can be interpreted in terms of tourism revenue rather than tourism numbers.
+In this case, it is an orthogonal projection in the \textit{transformed} space that is guaranteed to improve upon base forecasts with respect to this loss function.\\
 
-	    Now consider the property of minimising expected loss when the loss is function based on Euclidean distance.
+	    We also consider the property of minimising expected loss when the loss is function based on Euclidean distance.
 This can be achieved by the MinT estimator.
 We now provide a new result proving that minimising the expected loss in a transformed space in fact leads to the same MinT estimator.\\
-
-	    To make the transformed space more interpretable we consider a new loss function that is driven by the example used in our empirical evaluation.  This is a loss function weighted by ... TO DO
 

### 2020-01-28 R1/Letter.tex
minor changes to response and letter to reflect third loss function

@@
 We also now also report where differences in forecast accuracy are statistically significant.
-	\item We introduce some new results about MinT that explicitly makes the connection between trace minimisation and minimises a loss function based on Euclidean distance.
+	\item We introduce some new results about MinT that explicitly make the connection between trace minimisation and minimising a loss function based on Euclidean distance.
 We also prove a new result that MinT minimises expected loss for loss functions based on generalised Euclidean distance.

### 2020-01-29 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
finished MinT proof
changes to discussion of loss functions and reconciliation

@@
 \begin{itemize}
-\item The first is that reconciliation should adjust the base forecasts as little as possible; i.e.
-the base and reconciled forecasts should be `close'.
-{\color{blue} This property is particularly emphasised by \cite{NysEtAl2019}}
+\item The first is that reconciliation should adjust the base forecasts as little as possible; i.e. the base and reconciled forecasts should be `close'. 
 \item The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value targeted by the forecast.
-{\color{blue} This property is particularly emphasised by \cite{WicEtAl2019}.}
 \end{itemize}
@@
 A property of an orthogonal projection is that the distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$ is minimal over any possible $\tilde{\bm{y}}\in\mathfrak{s}$.
-{\color{blue} For Euclidean distance this can be expressed as minimising a loss function $\|\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}\|$ with respect to $\bm{G}$ where $\|.\|$ denotes the $L_2$ norm.}  In this sense reconciliation via orthogonal projection {\color{blue} $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$} leads to the smallest possible adjustments of the base forecasts.
+In this sense reconciliation via orthogonal projection {\color{blue} $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$} leads to the smallest possible adjustments of the base forecasts.
+{\color{blue} If the Euclidean distance is interpreted as a loss function $L(\bm{u},\bm{v})=\|\bm{u}-\bm{v}\|$ and $\|.\|$, an orthogonal projection solves the optimisation problem $\underset{\bm{G}}{\min}\,L(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t},\hat{\bm{y}}_{t+h|t})$.
+This is a special case of the optimisation problem considered by \cite{NysEtAl2019}, the more general case will be covered in the next section.}
 
-The {\color{blue} second property is concerned with a loss function $L({\bm{y}}_{t+h},\breve{\bm{y}}_{t+h})=\|{\bm{y}}_{t+h}-\bm{S}\bm{G}\breve{\bm{y}}_{t+h|t}\|$ where $\breve{\bm{y}}_{t+h|t}$ is either a base or reconciled forecast.
-More specifically, the aim is to reconcile so that $L({\bm{y}}_{t+h},\hat{\bm{y}}_{t+h})-L({\bm{y}}_{t+h},\tilde{\bm{y}}_{t+h})$ is guaranteed to be positive.\, that is} reconciled forecasts should always be closer to the target than base forecasts.
-{\color{blue} This idea was} touched upon in Section 2.3 of \citet{WicEtAl2019} for the {\color{blue} special} case of MinT\@ {\color{blue} which has a slightly different loss function}.
-Here we provide a new explicit {\color{blue} and general} proof of that result.
-We do so first in the case {\color{blue} of a loss function based on Euclidean distance} where the geometric intuition of the proof is clear and then generalise the result to reconciliation using any projection matrix in Section~\ref{sec:oblique}
+The {\color{blue} second property is concerned with the loss function $L({\bm{y}}_{t+h},\bar{\bm{y}}_{t+h|t})$ where $\bar{\bm{y}}_{t+h|t}$ is either a base or reconciled forecast.
+More specifically, the aim is to reconcile so that $L({\bm{y}}_{t+h|t},\hat{\bm{y}}_{t+h})-L({\bm{y}}_{t+h},\tilde{\bm{y}}_{t+h|t})$ is guaranteed to be positive, that is} reconciled forecasts should always be closer to the target than base forecasts.
+{\color{blue} This is expressed as a minimax optimisation property by \cite{VanErven2015a} and was also} touched upon in Section 2.3 of \citet{WicEtAl2019}{\color{blue}, in both cases for a slightly different loss function}.
+Here we provide a new explicit proof of {\color{blue} the distance reducing property}.
+We do so first in the case {\color{blue} of the loss function defined here in terms of Euclidean distance} where the geometric intuition of the proof is clear and then generalise the result to {\color{blue} more general loss functions} Section~\ref{sec:oblique}
 
@@
 In particular, this measure is the square root of the sum of squared forecast errors of \emph{all} variables in the hierarchy.
-Consequently, while forecast improvement is guaranteed for the hierarchy overall, {\color{blue} forecast errors are treated equally across all series} and reconciliation can {\color{blue} still} lead to less accurate forecasts for individual series.
+Consequently, while forecast improvement is guaranteed for the hierarchy overall, {\color{blue} forecast errors are treated equally across all series}.
 Second, although orthogonal projections are guaranteed to improve on base forecasts, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.
-Therefore, referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT\@.
+Therefore, referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections.
 {\color{blue} We now turn our attention to the way oblique projections can address both of these shortcomings} .
@@
 For example, in hierarchies, top-level series tend to have a much larger scale than bottom-level series.
-Even when two series are on a similar scale, series that are more predictable or less variable will tend to be down-weighted by simply aggregating squared errors.
-An even more sophisticated understanding may take the correlation between series into account.
-{\color{blue} Finally, the context of the forecast problem itself may suggest a loss function, for instance in our tourism example an appropriate loss function may weight forecast errors by average tourism expenditure in each reason}.
-All of these considerations lead towards {\color{blue} a loss function $L_{\bm W}(\bm{y}_{t+h},\breve{\bm{y}}_{t+h|t})=||{\bm{y}_{t+h}-\breve{\bm{y}}_{t+h|t}}||_{\bm{W}^{-1}}$ where $||\bm{v}||_{\bm{W}^{-1}}=\bm{v}'\bm{W}^{-1}\bm{v}$, and $\bm{W}$ is a symmetric matrix assumed to be invertible.
-The geometry defined by the norm $||.||_{\bm{W}^{-1}}$, will be referred to as the generalised Euclidean geometry with respect to $\bm{W}^{-1}$.
+{\color{blue} The context of the forecast problem itself may suggest a loss function that weights series differently, for instance in our tourism example in Section~\ref{sec:EmpStudy} we will consider weighting forecast errors by average tourism expenditure in each region}.
+An even more sophisticated understanding may take linear combinations of series into account.
+All of these considerations lead towards {\color{blue} a loss function $L_{\bm W}(\bm{y}_{t+h},\bar{\bm{y}}_{t+h|t})=||{\bm{y}_{t+h}-\breve{\bm{y}}_{t+h|t}}||_{\bm{W}}$ where $||\bm{v}||_{\bm{W}}=\bm{v}'\bm{W}\bm{v}$, and $\bm{W}$ is a symmetric matrix assumed to be invertible.
+The geometry defined by the norm $||.||_{\bm{W}}$, will be referred to as the generalised Euclidean geometry with respect to $\bm{W}$.
 }
 
-One way to understand the generalied Euclidean geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{-1/2}$.
-This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{-1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{-1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{-1/2}\tilde{\bm{y}}$.
-{\color{blue} An projection of the form $\tilde{\bm{y}}=\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}}$, is an} orthogonal projection in the transformed space since
+One way to understand the generalied Euclidean geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{1/2}$, {\color{blue} where $\bm{W}=(\bm{W}^{1/2})'\bm{W}^{1/2}$}.
+This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{1/2}\tilde{\bm{y}}$.
+{\color{blue} A projection of the form $\tilde{\bm{y}}=\bm{S}(\bm{S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}\hat{\bm{y}}$, is an} orthogonal projection in the transformed space since
 \begin{align*}
   \tilde{\bm{y}}^*
-    & = \bm{W}^{-1/2}\tilde{\bm{y}} \\
-    & = \bm{W}^{-1/2}\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}\hat{\bm{y}} \\
+    & = \bm{W}^{1/2}\tilde{\bm{y}} \\
+    & = \bm{W}^{1/2}\bm{S}(\bm{S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}\hat{\bm{y}} \\
+    &{\color{blue} = \bm{W}^{1/2}\bm{S}((\bm{W}^{1/2}\bm{S})'\bm{W}^{1/2}\bm{S})^{-1}(\bm{W}^{1/2}\bm{S})'\bm{W}^{1/2}\hat{\bm{y}}}\\
     & = \bm{S}^*(\bm{S}^{*'}\bm{S}^*)^{-1}\bm{S}^{*'}\hat{\bm{y}^*}.
@@
   \begin{equation*}
-    \|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|_{\bm{W}^{-1}}
+    \|(\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t})\|_{\bm{W}}
       \le\
-    |(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|_{\bm{W}^{-1}}.
+    \|(\bm{y}_{t+h}-\hat{\bm{y}}_{t+h|t})\|_{\bm{W}}.
   \end{equation*}
@@
 
-The implication of Theorem~\ref{th:gdistred} is that if the loss function is {\color{blue} given a priori as total sum of squared errors in some linearly transformed space,} then the projection matrix $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts.
-{\color{blue}  This result does not depend on the covariance of forecast errors except in the special case where $\bm{W}$ is set to this covariance matrix.}
+The implication of Theorem~\ref{th:gdistred} is that if the loss function is of the form $L_{\bm{W}}$ {\color{blue} with some $\bm{W}$ given a priori} then the projection matrix $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts.
+{\color{blue}  This result does not depend on the covariance of forecast errors except in general, although we note that MinT is a special case where $\bm{W}$ is set to this inverse of this covariance matrix.}
 
@@
 	Substituting the expressions for $\bm{\Sigma}^*$, $\bm{y}^{*}$ and $\hat{\bm{y}}^{*}$ into Equation~\ref{eq:MinTtran} yields, 
-	\begin{eqnarray*}
-	\bm{W}^{-1/2}\bm{y}=&\bm{W}^{-1/2}\bm{S}\left((\bm{W}^{-1/2}\bm{S})'(\bm{W}^{-1/2}\bm{\Sigma}\bm{W}^{-1/2'})^{*-1}\bm{W}^{-1/2}\bm{S}\right)^{-1}\\
-	&(\bm{W}^{-1/2}\bm{S})'(\bm{W}^{-1/2}\bm{\Sigma}\bm{W}^{-1/2'})^{*-1}\bm{W}^{-1/2}\hat{\bm{y}}\\
-	\end{eqnarray*}
+	\begin{align*}
+	\bm{W}^{-1/2}\tilde{\bm{y}}=\bm{W}^{-1/2}\bm{S}&\left((\bm{W}^{-1/2}\bm{S})'(\bm{W}^{-1/2}\bm{\Sigma}\bm{W}^{-1/2'})^{*-1}\bm{W}^{-1/2}\bm{S}\right)^{-1}\\
+	&(\bm{W}^{-1/2}\bm{S})'(\bm{W}^{-1/2}\bm{\Sigma}\bm{W}^{-1/2'})^{*-1}\bm{W}^{-1/2}\hat{\bm{y}}
+	\end{align*}
+	Rearranging and cancelling gives
+	\begin{align*}
+    \tilde{\bm{y}}&=\bm{S}\left((\bm{S})'(\bm{W}^{-1/2})'(\bm{W}^{1/2})'\bm{\Sigma}^{-1}\bm{W}^{1/2}\bm{W}^{-1/2}\bm{S}\right)^{-1}\bm{S}'(\bm{W}^{-1/2})'(\bm{W}^{1/2})'\bm{\Sigma}^{-1}\bm{W}^{1/2}\bm{W}^{-1/2}\hat{\bm{y}}\\
+	&=\bm{S}\left((\bm{S})'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}\\
+	\end{align*}
+	which corresponds to the usual MinT method.
 \end{proof}

### 2020-01-29 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
rewrite of section 3 including improvement to MinT section

@@
 
+\citet{WicEtAl2019} and \citet{VanErven2015a} both prove special cases of this result, the former in the case where $\bm{W}$ is the inverse of the forecast error covariance and \citet{VanErven2015a} in the case where $\bm{W}$ is diagonal.
 Note here that we rely here on the Generalised Pythagorean Theorem (which involves an equality).
 In contrast, \citet{WicEtAl2019} follow \citet{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.
-The proof of \citet{WicEtAl2019} requires an assumption of convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.
+These proofs require an assumption of convexity so that the angle between the base forecast and coherent subspace must be greater than 90 degrees.
 The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.
-As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is true only with respect to a loss function that depends on {\color{blue} $||.||_{\bm{W}^{-1}}$ and only when $\bm{W}$ is the covariance matrix estimate used by MinT}.
+As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is true only with respect to a loss function that depends on {\color{blue} $||.||_{\bm{W}}$ and only when $\bm{W}^{-1}$ is the covariance matrix estimate used by MinT}.
 If Euclidean distance (or mean squared error) is used {\color{blue} as a loss function}, there will be realisations where the MinT estimator does not improve forecast accuracy relative to base forecasts.
@@
 {\color{blue}The discussion so far provides a roadmap, such that for a given choice of $\bm{W}$, a projection method with distance-reducing properties can be derived}.
-While the MinT method of \citet{WicEtAl2019} {\color{blue} is a special case of such a projection, it was in fact motivated by a different optimality property of minimising the} trace of the forecast error covariance matrix of reconciled forecasts
+While the MinT method of \citet{WicEtAl2019} {\color{blue} is a special case of such a projection, it was in fact motivated by a different optimality property.
+This was to minimise the} trace of the forecast error covariance matrix of reconciled forecasts
 
@@
 
-\subsection{MinT and Loss Functions}
+\subsection{Expected loss minimisation and MinT}
 
-We now make explicit the connection betwenn the MinT and a loss function based on the Euclidean distance $L(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|$.
+We now make explicit the connection betwenn the MinT and a loss function based on the Euclidean distance $L(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|$ before generalising to $L_{\bm W}(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|_{\bm W}$.
 By the properties of the trace operator, the objective function in Equation~\ref{eq:MinTObj} can be rearranged as
@@
 Theorem~\ref{th:distred} implies optimality in the sense that reconcilied forecasts always improve on base forecasts.
-For MinT, optimality refers to minimising the expected loss function \textit{in expectation}.
+For MinT, optimality refers to minimising the loss function \textit{in expectation}.
 
-A natural question may be to derive a reconciliation method that minimises expected loss where the loss function is the generalised Euclidean distance between the realisation and reconciled forecast.
-That is to solve the optimisation problem
+Suppose the optimisation problem is generalised to a loss function based on some ${\bm W}$
 
@@
 	\label{eq:GMinTObj}
-	\underset{\bm{G}}{\min}\,\textrm{tr}(E\left[(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'\bm{W}^{-1}(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})\right])\,.
+	\underset{\bm{G}}{\min}\,(E\left[(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'\bm{W}(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})\right])\,.
 	\end{equation}
@@
 
-\begin{theo}[MinT minimises expected loss]\label{th:gdistred}
-    The usual MinT reconciliation method $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}$ solves the optimisation problem in Equation~\ref{eq:GMinTObj} for any $\bm{W}$.
+\begin{theo}[Expected loss minimisation and MinT]\label{th:gdistred}
+    The usual MinT reconciliation method $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}$ solves the optimisation problem in Equation~\ref{eq:GMinTObj} for any choice of $\bm{W}$.
 \end{theo}
@@
 	The loss function in Equation~\ref{eq:GMinTObj} is equivalent to Euclidean distance in the transformed space and can therefore be minimised by using the MinT method in this space.
-The MinT method in the transformed space is give by
+The MinT method in the transformed space is given by
 	\begin{equation}
@@
 	\end{equation}
-	where  $\bm{y}^{*}=\bm{W}^{-1/2}\bm{y}$, $\bm{S}^{*}=\bm{W}^{-1/2}\bm{S}$, $\hat{\bm{y}}^{*}=\bm{W}^{-1/2}\hat{\bm{y}}$ and
+	where  $\bm{y}^{*}=\bm{W}^{1/2}\bm{y}$, $\bm{S}^{*}=\bm{W}^{1/2}\bm{S}$, $\hat{\bm{y}}^{*}=\bm{W}^{1/2}\hat{\bm{y}}$ and
 	\begin{align*}
 	\bm{\Sigma}^*&=E\left[(\bm{y}^{*}-\hat{\bm{y}}^{*})(\bm{y}^{*}-\hat{\bm{y}}^{*})'\right]\\
-	&=E\left[\bm{W}^{-1/2}(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'\bm{W}^{-1/2'}\right]\\
-	&=\bm{W}^{-1/2}E\left[(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'\right]\bm{W}^{-1/2'}\\
-	&=\bm{W}^{-1/2}\bm{\Sigma}\bm{W}^{-1/2'}
+	&=E\left[\bm{W}^{1/2}(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'(\bm{W}^{1/2})'\right]\\
+	&=\bm{W}^{1/2}E\left[(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'\right](\bm{W}^{1/2})'\\
+	&=\bm{W}^{1/2}\bm{\Sigma}(\bm{W}^{1/2})'
 	\end{align*}
-	Substituting the expressions for $\bm{\Sigma}^*$, $\bm{y}^{*}$ and $\hat{\bm{y}}^{*}$ into Equation~\ref{eq:MinTtran} yields, 
+	Noting that
 	\begin{align*}
-	\bm{W}^{-1/2}\tilde{\bm{y}}=\bm{W}^{-1/2}\bm{S}&\left((\bm{W}^{-1/2}\bm{S})'(\bm{W}^{-1/2}\bm{\Sigma}\bm{W}^{-1/2'})^{*-1}\bm{W}^{-1/2}\bm{S}\right)^{-1}\\
-	&(\bm{W}^{-1/2}\bm{S})'(\bm{W}^{-1/2}\bm{\Sigma}\bm{W}^{-1/2'})^{*-1}\bm{W}^{-1/2}\hat{\bm{y}}
+	(\bm{\Sigma}^{*})^{-1}&=\left(\bm{W}^{1/2}\bm{\Sigma}(\bm{W}^{1/2})'\right)^{-1}\\
+	&=(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\\
+	\end{align*}
+	and substituting the expressions for $\bm{\Sigma}^*$,${\bm{S}^*}$, $\bm{y}^{*}$ and $\hat{\bm{y}}^{*}$ into Equation~\ref{eq:MinTtran} yields, 
+	\begin{align*}
+	\bm{W}^{1/2}\tilde{\bm{y}}=\bm{W}^{1/2}\bm{S}&\left((\bm{W}^{1/2}\bm{S})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}(\bm{W}^{1/2}\bm{S})\right)^{-1}\\
+	&(\bm{W}^{1/2}\bm{S})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\hat{\bm{y}}
 	\end{align*}
@@
 	\begin{align*}
-    \tilde{\bm{y}}&=\bm{S}\left((\bm{S})'(\bm{W}^{-1/2})'(\bm{W}^{1/2})'\bm{\Sigma}^{-1}\bm{W}^{1/2}\bm{W}^{-1/2}\bm{S}\right)^{-1}\bm{S}'(\bm{W}^{-1/2})'(\bm{W}^{1/2})'\bm{\Sigma}^{-1}\bm{W}^{1/2}\bm{W}^{-1/2}\hat{\bm{y}}\\
-	&=\bm{S}\left((\bm{S})'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}\\
+    \tilde{\bm{y}}&=\bm{S}\left(\bm{S}'(\bm{W}^{-1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{1/2}\bm{W}^{-1/2}\bm{S}\right)^{-1}\\
+    &\qquad\qquad\bm{S}'(\bm{W}^{-1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{1/2}\bm{W}^{-1/2}\hat{\bm{y}}\\
+	&=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}\\
 	\end{align*}
@@
 \end{proof}
+
+The implication of this result is that irrespective of the ${\bm W}$ used in the loss function, an oblique projection based on the forecast error covariance will always minimise {\em expected} loss (for the class of loss functions considered here).
+From the point of view of minimising expected loss, considerations about sensible weights for an error metric will only work in so far as they can estimate the forecast error covariance matrix.
+This will be empirically demonstrated in Section~\ref{sec:EmpStudy}.
 

### 2020-01-29 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
further changes to manuscript and response letter

@@
 	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
-This corresponds to the loss function described in Section~\ref{sec:orthogonal}. We also consider a loss function based on a generalised Euclidean distance of the form
+This corresponds to the loss function described in Section~\ref{sec:orthogonal}. We also consider loss functions based on a generalised Euclidean distance of the form
 \begin{equation*}
-	\textrm{WSE}^{q}_t=\sum\limits_{i=1}^n w_i (y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,,
+	\textrm{WSE}^{q}_t=\sum\limits_{i=1}^n \left(w_i (y_{i,t}-\tilde{y}^{(q)}_{i,t})\right)^2\,,
 	\end{equation*}
 	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
+We consider two choices of weights.
+The first is the inverse of the number of bottom level series that are aggregated to form a series.
+For example, for all bottom level series this weight is 1, whereas for the top level series this is 1/75.
+The idea is to not ensure top level series - which due to aggregation are on a much larger scale -  do not dominate the forecast evaluation metric.
+Using this weights in WLS reconciliation is equivalent to what \cite{AthEtAl2017} refer to as \textit{structural scaling}.
+As such we refer to WLS based on these weights as `Structural-WLS' and the loss function based on these weights as `Structural-WSE'.
+
+	The second choice of weights is motivated by our empirical example.
+In addition to visitor numbers per region, we also have access to data on average spend per region.
+In some settings, it may be desirable to have greater forecast accuracy in regions where tourists spend more.
+By using average spend per region as weights, the error metric (and transformed space associated with this metric) can be interpreted in terms of revenue measured in dollars rather than raw tourist numbers.
+We refer to WLS based on these weights as `Spend-WLS' and the loss function based on these weights as `Spend-WSE'.
 }
 
-After obtaining the base forecasts these are reconciled using four different projection methods: OLS,{\color{blue} WLS and MinT.
+After obtaining the base forecasts these are reconciled using four different projection methods: OLS,{\color{blue} Structural-WLS, Spend-WLS  and MinT.
 For MinT, the shrinkage estimator of \cite{Schafer2005} is used to estimate to covariance matrix of one step ahead forecast errors.
@@
 	where $\sigma_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}^{\text{sam}}$.
-For WLS, variance scaling is used, i.e., $\bm{W}^{\text{WLS}}=\text{diag}(\hat{\bm{\Sigma}})$ CHANGE DEPENDING ON FINAL CHOICE OF W.
-For both loss function} we compute the difference between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate.
+For each loss function} we compute the difference between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate.
 

### 2020-01-29 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
tidied intro

@@
 In particular, a general framework is established nesting many existing popular reconciliation methods within the class of \emph{projections}.
-This interpretation facilitates the derivation of novel results that explain why and how reconciliation via projection is guaranteed to improve forecast accuracy with respect to a specific class of loss functions.
-The geometric interpretation is further used to provide a new proof that forecast reconciliation results in unbiased forecasts provided the initial Approaches for dealing with biased base forecasts are proposed.
-The implications of all theoretical results are demonstrated in an extensive empirical study on Australian tourism flows.
+This interpretation facilitates the derivation of novel theoretical results.
+First, reconciliation via projection is guaranteed to improve forecast accuracy with respect to a class of loss functions based on a generalised distance metric.
+Second, the MinT method minimises expected loss for this same class of loss functions.
+The geometric interpretation is further used to provide a new proof that forecast reconciliation using projections results in unbiased forecasts provided the initial base forecasts are also unbiased.
+Approaches for dealing with biased base forecasts are proposed and evaluated in an extensive empirical study on Australian tourism flows.
 The method of bias-correcting before carrying out reconciliation is shown to outperform alternatives that only bias-correct or only reconcile forecasts.
+The empirical study also sheds light on the theoretical results of the paper.
 

### 2020-01-29 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
tidied intro (last time was abstract)

@@
 Forecast reconciliation has mostly been formulated using a regression model {\color{blue} that admits a generalised least squares (GLS) solution}, see \citet{Hyndman2011} and \citet{WicEtAl2019} for examples.
-{\color{blue} Alternatively, \cite{VanErven2015a} and \cite{NysEtAl2019} arrive at a GLS solution by formulating reconciliation as an optimisation problem to minimise weighted squared errors between coherent and incoherent forecasts}.
+{\color{blue} Alternatively, \cite{VanErven2015a} and \cite{NysEtAl2019} arrive at a GLS solution by formulating reconciliation as an optimisation problem}.
 The regression setup can be counter-intuitive since a vector comprised of forecasts from different time series models is also assumed to be the dependent variable in a regression model.
@@
 As a result forecast reconciliation can be applied in contexts where there are no clear candidates of \emph{bottom level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling.
-Second, {\color{blue} we provide a new proof of the results that reconciled forecasts dominate unreconciled forecasts, for a certain class of loss functions.
-The projection that achieves this need only depend on the loss function and not on the dependence in forecast errors.}  Futhermore, unlike {\color{blue} proofs of similar results by} \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general.
-{\color{blue} Third, we show that when it comes to minimising the expected value of the same class of loss functions, the optimal projection depends only on the covariance of the forecast errors.
-While this is a direct consequence of the trace minimising property already established by \cite{WicEtAl2019}, we provide new intuition and also establish that the result applies to a more general class of loss functions.
+Second, {\color{blue} we provide a new proof that reconciled forecasts dominate unreconciled forecasts, for a certain class of loss functions.
+The projection that achieves this depends on the weights used in the loss function but not on the dependence in forecast errors.}  Futhermore, unlike {\color{blue} proofs of similar results by} \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general.
+{\color{blue} Third, we show that when it comes to minimising the expected value of the same class of loss functions, the optimal projection depends only on the covariance of the forecast errors, and not the weights used in the loss function.
+In this case of equal weights, this property is a direct consequence of the trace minimising property already established by \cite{WicEtAl2019}, we now prove that this result also applies to a more general class of loss functions.
 Fourth}, we prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased.

### 2020-01-29 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
tidied coherence

@@
 Rather than addressing this issue by considering matrices that are not projections, we propose to bias-correct before reconciliation.
-This is evaluated in an extensive empirical study where we find that even when bias correction fails, the extent of the problem is mitigated by reconciling forecasts.
+This is evaluated in an extensive empirical study where we find that even when bias correction fails, the extent of the problem is mitigated by reconciling forecasts.\todo{Re-check after results}
 
@@
 The gray coloured two dimensional plane depicts the coherent subspace $\mathfrak{s}$ where $\vec{s}_1 = (1,1,0)'$ and $\vec{s}_2 = (1, 0, 1)'$ are basis vectors that span $\mathfrak{s}$.
-The red points in $\mathfrak{s}$ represent realisations or coherent forecasts}\label{fig:3D_hierarchy}
+The red points in $\mathfrak{s}$ represent realisations or coherent forecasts.}\label{fig:3D_hierarchy}
 \end{figure}
@@
 Much of the early literature that dealt with the problem of forecasting hierarchical time series \citep[see][and references therein]{Gross1990} produced forecasts at a single level of the hierarchy in the first stage.
-Subsequently forecasts for all series were recovered through aggregation, disaggregation according to historical or forecast proportions, or some combination of both.
+Subsequently forecasts for all series were recovered through {\color{blue} either} aggregation, disaggregation according to historical or forecast proportions, or some combination of both.
 Consequently, incoherent forecasts were not a problem in these earlier papers.
@@
 Forecasting a single level of the hierarchy did not echo common practice within many industries.
-In many organisations different departments or `silos' each produced their own forecasts, often with their own information sets and judgemental adjustments.
-\footnote{\citet{Cha2013} discusses silos and the importance of information and data sharing across an organisation.} This approach does have several advantages over only forecasting a single level.
+In many organisations different departments or `silos' each produced their own forecasts, often with their own information sets and judgemental adjustments.\footnote{\citet{Cha2013} discusses silos and the importance of information and data sharing across an organisation.} This approach does have several advantages over only forecasting a single level.
 First, there is no loss of information since all levels and series are modelled.

### 2020-01-29 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
tidied reconciliation

@@
 In this sense reconciliation via orthogonal projection {\color{blue} $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$} leads to the smallest possible adjustments of the base forecasts.
-{\color{blue} If the Euclidean distance is interpreted as a loss function $L(\bm{u},\bm{v})=\|\bm{u}-\bm{v}\|$ and $\|.\|$, an orthogonal projection solves the optimisation problem $\underset{\bm{G}}{\min}\,L(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t},\hat{\bm{y}}_{t+h|t})$.
+{\color{blue} Euclidean distance can be interpreted as a loss function $L(\bm{u},\bm{v})=\|\bm{u}-\bm{v}\|$ where $\|.\|$ is the L2 norm, in which case an orthogonal projection solves the optimisation problem $\underset{\bm{G}}{\min}\,L(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t},\hat{\bm{y}}_{t+h|t})$.
 This is a special case of the optimisation problem considered by \cite{NysEtAl2019}, the more general case will be covered in the next section.}
 
-The {\color{blue} second property is concerned with the loss function $L({\bm{y}}_{t+h},\bar{\bm{y}}_{t+h|t})$ where $\bar{\bm{y}}_{t+h|t}$ is either a base or reconciled forecast.
-More specifically, the aim is to reconcile so that $L({\bm{y}}_{t+h|t},\hat{\bm{y}}_{t+h})-L({\bm{y}}_{t+h},\tilde{\bm{y}}_{t+h|t})$ is guaranteed to be positive, that is} reconciled forecasts should always be closer to the target than base forecasts.
-{\color{blue} This is expressed as a minimax optimisation property by \cite{VanErven2015a} and was also} touched upon in Section 2.3 of \citet{WicEtAl2019}{\color{blue}, in both cases for a slightly different loss function}.
-Here we provide a new explicit proof of {\color{blue} the distance reducing property}.
+The {\color{blue} aim of the second property is to guarantee that} reconciled forecasts should always be closer to the target than base forecasts {\color{blue} and is related with the difference in loss functions $L({\bm{y}}_{t+h},\hat{\bm{y}}_{t+h|t})-L({\bm{y}}_{t+h},\tilde{\bm{y}}_{t+h|t})$.
+This is expressed as a minimax optimisation by \cite{VanErven2015a} and was also} touched upon in Section 2.3 of \citet{WicEtAl2019}{\color{blue}, albeit in both cases for a slightly different loss function}.
+Here we provide a new explicit proof of {\color{blue} this distance reducing property}.
 We do so first in the case {\color{blue} of the loss function defined here in terms of Euclidean distance} where the geometric intuition of the proof is clear and then generalise the result to {\color{blue} more general loss functions} Section~\ref{sec:oblique}
@@
 \begin{theo}[Distance reducing property]\label{th:distred}
-  If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection (in the Euclidean sense) onto $\mathfrak{s}$ and let $\|\bm{v}\|$ be the $L_2$ norm (in the Euclidean sense) of vector $\bm{v}$ then:
+  If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection (in the Euclidean sense) onto $\mathfrak{s}$ then:
   \begin{equation*}
@@
 In this schematic, the coherent subspace is depicted as a black arrow, and the base forecast $\hat{\bm{y}}$ is shown as a blue dot.
-Since $\hat{\bm{y}}$ is incoherent, $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$ and in this case the inequality is strict.
+Since $\hat{\bm{y}}$ is incoherent, $\hat{\bm{y}}\notin\mathfrak{s}$ and in this case the inequality is strict.
 Reconciliation is an orthogonal projection from $\hat{\bm{y}}$ to the coherent subspace yielding the reconciled forecast $\tilde{\bm{y}}$ shown in red.
@@
 In this triangle the line between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.
-Therefore reconciliation is guaranteed to reduce the squared error of the forecast.
+Therefore reconciliation is guaranteed to reduce {\color{blue} a loss function based on distance, or indeed any monotonic function of distance.}
 
@@
 Therefore, referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections.
-{\color{blue} We now turn our attention to the way oblique projections can address both of these shortcomings} .
+{\color{blue} We now turn our attention to the way oblique projections can address both of these shortcomings.}
 
@@
 
-One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of the square root of the sum of squared errors of \emph{all} variables in the hierarchy.
-A clear shortcoming of this measure of forecast accuracy is that forecast errors in all series should not necessarily be treated equally.
+One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of {\color{blue} a loss function based on Euclidean distance that involves \emph{all} variables in the hierarchy.} A clear shortcoming of this measure of forecast accuracy is that forecast errors in all series should not necessarily be treated equally.
 For example, in hierarchies, top-level series tend to have a much larger scale than bottom-level series.
-{\color{blue} The context of the forecast problem itself may suggest a loss function that weights series differently, for instance in our tourism example in Section~\ref{sec:EmpStudy} we will consider weighting forecast errors by average tourism expenditure in each region}.
-An even more sophisticated understanding may take linear combinations of series into account.
-All of these considerations lead towards {\color{blue} a loss function $L_{\bm W}(\bm{y}_{t+h},\bar{\bm{y}}_{t+h|t})=||{\bm{y}_{t+h}-\breve{\bm{y}}_{t+h|t}}||_{\bm{W}}$ where $||\bm{v}||_{\bm{W}}=\bm{v}'\bm{W}\bm{v}$, and $\bm{W}$ is a symmetric matrix assumed to be invertible.
+{\color{blue} Alternatively, the context of the forecast problem itself may suggest a loss function that weights series differently.
+For example in our tourism application in Section~\ref{sec:EmpStudy} we will consider weighting forecast errors by average tourism expenditure in each region.}\footnote{Similar consideration are taken into account for the loss function used in the M5 forecasting competition, see M5 REF HERE for more details.}  An even more sophisticated understanding may take {\color{blue}linear combinations} of series into account.
+All of these considerations lead towards {\color{blue} a loss function $L_{\bm W}(\bm{y}_{t+h},\tilde{\bm{y}}_{t+h|t})=||{\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t}}||_{\bm{W}}$ where $||\bm{v}||_{\bm{W}}=\bm{v}'\bm{W}\bm{v}$, and $\bm{W}$ is a symmetric matrix assumed to be invertible.
 The geometry defined by the norm $||.||_{\bm{W}}$, will be referred to as the generalised Euclidean geometry with respect to $\bm{W}$.
@@
 The implication of Theorem~\ref{th:gdistred} is that if the loss function is of the form $L_{\bm{W}}$ {\color{blue} with some $\bm{W}$ given a priori} then the projection matrix $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts.
-{\color{blue}  This result does not depend on the covariance of forecast errors except in general, although we note that MinT is a special case where $\bm{W}$ is set to this inverse of this covariance matrix.}
-
-\citet{WicEtAl2019} and \citet{VanErven2015a} both prove special cases of this result, the former in the case where $\bm{W}$ is the inverse of the forecast error covariance and \citet{VanErven2015a} in the case where $\bm{W}$ is diagonal.
+{\color{blue}  This result does not necessarily involve the covariance of forecast errors unless $\bm{W}$ is explicitly chosen to depend on these covariances.}
+
+\citet{WicEtAl2019} and \citet{VanErven2015a} both prove special cases of this result, the former in the case where $\bm{W}$ is the inverse of the forecast error covariance and the latter in the case where $\bm{W}$ is diagonal.
 Note here that we rely here on the Generalised Pythagorean Theorem (which involves an equality).
@@
 The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.
-As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is true only with respect to a loss function that depends on {\color{blue} $||.||_{\bm{W}}$ and only when $\bm{W}^{-1}$ is the covariance matrix estimate used by MinT}.
+As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is true only with respect to a loss function that depends on {\color{blue} $||.||_{\bm{\Sigma}^{-1}}$, where $\bm{\Sigma}=E(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'$}.
 If Euclidean distance (or mean squared error) is used {\color{blue} as a loss function}, there will be realisations where the MinT estimator does not improve forecast accuracy relative to base forecasts.
@@
 
-{\color{blue}The discussion so far provides a roadmap, such that for a given choice of $\bm{W}$, a projection method with distance-reducing properties can be derived}.
+{\color{blue}The discussion so far provides a roadmap, such that for a given choice of $\bm{W}$, a projection with distance-reducing properties can be derived}.
 While the MinT method of \citet{WicEtAl2019} {\color{blue} is a special case of such a projection, it was in fact motivated by a different optimality property.
-This was to minimise the} trace of the forecast error covariance matrix of reconciled forecasts
+This was to minimise the} trace of the forecast error covariance matrix of reconciled forecasts, i.e,
 
@@
 The solution is the oblique projection {\color{blue} $\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}$}.
-Here, {\color{blue}$\bm{\Sigma}=E(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'$} is the forecast error covariance matrix where errors come from using the base forecasts.
-Although the base forecast error covariance matrix is unknown, it can be estimated using in-sample errors.
-{\color{blue} In the subsequent discussion MinT will refer to any method that attempts to estimate $\bm{\Sigma}$, specific estimators can be found in \cite{WicEtAl2019} and also \cite{NysEtAl2019}.}
+{\color{blue} While MinT is used here to refer to the case where $\bm{\Sigma}$ is known, in practice,} it is unknown.
+It can be estimated using in-sample errors, {\color{blue} with some specific estimators found in \cite{WicEtAl2019} and also \cite{NysEtAl2019}.}
 
@@
 
-We now make explicit the connection betwenn the MinT and a loss function based on the Euclidean distance $L(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|$ before generalising to $L_{\bm W}(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|_{\bm W}$.
+We now make explicit the connection betwenn the MinT and a loss function based on the squared Euclidean distance $L(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|^2$ before generalising to $L_{\bm W}(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|^2_{\bm W}$.
 By the properties of the trace operator, the objective function in Equation~\ref{eq:MinTObj} can be rearranged as
@@
 %&=E\left[(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})\right]\\
-&=E\left[\|\bm{y}-{\bm S}{\bm G}\hat{\bm{y}}\|\right]\\
+&=E\left[\|\bm{y}-{\bm S}{\bm G}\hat{\bm{y}}\|^2\right]\\
 &=E\left[L(\bm{y},\tilde{\bm{y}})\right]
@@
 
-Note that although the loss function used here is the same as in Section~\ref{sec:orthogonal}, the sense in which reconciliation is optimal is different.
+Note that trace minimisation implies a different optimality property to the distance reducing property described in Section~\ref{sec:orthogonal}.
 Theorem~\ref{th:distred} implies optimality in the sense that reconcilied forecasts always improve on base forecasts.
@@
 	\end{align*}
-	and substituting the expressions for $\bm{\Sigma}^*$,${\bm{S}^*}$, $\bm{y}^{*}$ and $\hat{\bm{y}}^{*}$ into Equation~\ref{eq:MinTtran} yields, 
+	and substituting the expressions for $\bm{\Sigma}^*$, ${\bm{S}^*}$, $\bm{y}^{*}$ and $\hat{\bm{y}}^{*}$ into Equation~\ref{eq:MinTtran} yields, 
 	\begin{align*}
@@
 	\begin{align*}
-    \tilde{\bm{y}}&=\bm{S}\left(\bm{S}'(\bm{W}^{-1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{1/2}\bm{W}^{-1/2}\bm{S}\right)^{-1}\\
-    &\qquad\qquad\bm{S}'(\bm{W}^{-1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{1/2}\bm{W}^{-1/2}\hat{\bm{y}}\\
+    \tilde{\bm{y}}&=\bm{S}\left(\bm{S}'(\bm{W}^{-1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\bm{S}\right)^{-1}\\
+    &\qquad\qquad\bm{S}'(\bm{W}^{-1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\hat{\bm{y}}\\
 	&=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}\\
@@
 
-The implication of this result is that irrespective of the ${\bm W}$ used in the loss function, an oblique projection based on the forecast error covariance will always minimise {\em expected} loss (for the class of loss functions considered here).
-From the point of view of minimising expected loss, considerations about sensible weights for an error metric will only work in so far as they can estimate the forecast error covariance matrix.
+The implication of this result is that irrespective of the ${\bm W}$ used in the loss function, an oblique projection based on the forecast error covariance will always minimise {\em expected} loss (where loss is based on squared generalised Euclidean distance).
+From the point of view of minimising expected loss, considerations about sensible weights for an error metric are only relevant in so far as they can estimate the forecast error covariance matrix.
 This will be empirically demonstrated in Section~\ref{sec:EmpStudy}.

### 2020-01-29 Application-R/Application-TourismData/OrthVsOblq_projections/Original-scale_betterModels/Results/lossvmethods_h_1.tex
rewrote code to process results for example in 5.2

% latex table generated in R 3.6.2 by xtable 1.8-4 package
% Thu Jan 30 00:24:35 2020
\begin{table}[ht]
\centering
\begin{tabular}{lrrrrrr}
  \hline
Loss Function & Base & Bottom-up & OLS & Structural-WLS & Spend-WLS & MinT \\ 
  \hline
TSE & 1.00 & 1.22 & 0.97 & 1.13 & 0.98 & 0.96 \\ 
  Structural WSE & 1.00 & 1.01 & 0.96 & 0.98 & 1.00 & 0.93 \\ 
  Spend WSE & 1.00 & 1.20 & 0.97 & 1.12 & 0.98 & 0.96 \\ 
   \hline
\end{tabular}
\caption{Means of different loss functions for 1-step ahead forecasts using different reconciliation methods in the tourism application.  All figures are reported relative to base forecasts.} 
\end{table}

### 2020-01-29 Application-R/Application-TourismData/OrthVsOblq_projections/Original-scale_betterModels/Results/Analysis.R

@@ -1,7 +1,7 @@
 
 library(tidyverse)
 
-
+library(xtable)
 
 
 # OvernightTrips_OriginalScale_Fc_1_50 <- read.csv("DF_OriginalScale_1-50.csv")[,-1]
@@ -24,6 +24,7 @@ OvernightTrips_OriginalScale_Fc %>%
 # OvernightTrips_OriginalScale_Fc %>% 
 #   group_by(`R.method`, Fc_horizon) %>% 
 #   summarise(MSE = mean(SquaredE)) %>% 
+#  summarise(MTSE=mean(TSE,na.rm = T),MWSE=mean(WSE,na.rm = T),MSpWSE=mean(SpWSE,na.rm = T))%>%View
 #   spread(key = Fc_horizon, value = MSE)
 # 
 # 
@@ -42,72 +43,121 @@ OvernightTrips_OriginalScale_FcW %>%
          Fc_horizon = recode(Fc_horizon, "1" = "h=1", "2" = "h=2",
                              "3" = "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6")) %>%
   group_by(`R.method`, Fc_horizon, Replication) %>%
-  summarise(TSE = sum(SquaredE),WSE = sum(WeightedSquaredE),SpWSE = sum(SpWeightedSquaredE)) -> OvernightTrips_OriginalScale_MSE
+  summarise(TSE = sum(SquaredE),`Structural-WSE` = sum(WeightedSquaredE),`Spend-WSE` = sum(SpWeightedSquaredE)) -> OvernightTrips_OriginalScale_MSE
 
 
-OvernightTrips_OriginalScale_MSE%>%
-  filter(Fc_horizon=='h=1')%>%
+#OvernightTrips_OriginalScale_MSE%>%
+#  filter(Fc_horizon=='h=1')%>%
+#  group_by(R.method)%>%
+
+
+############Create Table (Messy)
+
+for (j in 1:6){
+
+hor<-paste0('h=',j)
+
+OvernightTrips_OriginalScale_MSE %>%
+  ungroup()%>%
+  filter(Fc_horizon==hor)%>%
+  select(-Fc_horizon)%>%
   group_by(R.method)%>%
-  summarise(MTSE=mean(TSE,na.rm = T),MWSE=mean(WSE,na.rm = T),MSpWSE=mean(SpWSE,na.rm = T))%>%View
[…]

### 2020-01-29 R1/Response.tex

@@
 We now consider two such loss functions, one based on the structure of the hierarchy (so-called `structural scaling') and another based on average spend in each region.
-The latter of these can be interpreted in terms of tourism revenue rather than tourism numbers.
-In this case, it is an orthogonal projection in the \textit{transformed} space that is guaranteed to improve upon base forecasts with respect to this loss function.\\
+To highlight how the transformed space can be interpreted in some contexts we have added the following sentence to the manuscript: ``By using average spend per region as weights, the error metric (and transformed space associated with this metric) can be interpreted in terms of revenue measured in dollars rather than raw tourist numbers.''
 
-	    We also consider the property of minimising expected loss when the loss is function based on Euclidean distance.
-This can be achieved by the MinT estimator.
-We now provide a new result proving that minimising the expected loss in a transformed space in fact leads to the same MinT estimator.\\
+	    In cases where the transformed space cannot be easily be interpreted in terms of the empirical example, it is nevertheless it is an important construction in our proofs.
+This includes a new proof that MinT minimises expected loss even for loss functions based on generalised Euclidean distance.
+\\
 

### 2020-01-29 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex

@@
 
-\begin{theo}[Expected loss minimisation and MinT]\label{th:gdistred}
+\begin{theo}[Expected loss minimisation and MinT]\label{th:gmint}
     The usual MinT reconciliation method $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}$ solves the optimisation problem in Equation~\ref{eq:GMinTObj} for any choice of $\bm{W}$.
@@
 Our motivation in this study is twofold.
-First, we demonstrate the implications of Theorem~\ref{th:distred} by comparing reconciled and base forecasts.
-In contrast to previous studies, we consider individual periods rather than computing averages over a rolling window.
+First, we demonstrate the implications of Theorem~\ref{th:distred} {\color{blue} and Theorem~\ref{th:gmint}} by comparing reconciled and base forecasts.
+In contrast to previous studies, we consider individual periods {\color{blue} as well as} compute averages over a rolling window.
 Second, we demonstrate how the bias correction methods discussed in the previous section along with the projection-based reconciliation help to improve forecast accuracy.
@@
 
-To demonstrate the implications of Theorem~\ref{th:distred} we consider the improvement of different reconciliation methods over base forecasts.
+To demonstrate the implications of Theorem~\ref{th:distred} we consider the improvement of different reconciliation methods over base forecasts {\color{blue} using different loss functions}.
 For each series the ARIMA model minimising AICc is chosen using the \verb|auto.arima()| function in the \verb|forecast| package.
-Using these fitted models, base forecasts are produced for $h=1$ to $12$-steps ahead for each series in the hierarchy.
+Using these fitted models, base forecasts are produced for $h=1$ to $6$-steps ahead for each series in the hierarchy.
 This is first carried out with a training sample of $100$ observations, i.e., Jan-$1998$ to Apr-$2006$.
 The training window is then rolled forward one observation at a time until the end of the sample.
-This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $129~12$-steps-ahead forecasts available for forecast evaluation.
-
-{\color{blue} For each replication and for method $q$, the total squared error (TSE), is computed as
+This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $135~6$-steps-ahead forecasts available for forecast evaluation.
+
+{\color{blue} For each replication and for method $q$, we compute three loss functions.  The first is the total squared error (TSE), computed as
 	\begin{equation}
@@
 	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
-This corresponds to the loss function described in Section~\ref{sec:orthogonal}. We also consider loss functions based on a generalised Euclidean distance of the form
+This corresponds to the loss function described in Section~\ref{sec:orthogonal}. We also consider loss functions based on a squared generalised Euclidean distance of the form
 \begin{equation*}
@@
 	\end{equation*}
-	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
 	We consider two choices of weights.
-The first is the inverse of the number of bottom level series that are aggregated to form a series.
+The first is the inverse of the number of bottom level series included in forming a specific aggregate.
 For example, for all bottom level series this weight is 1, whereas for the top level series this is 1/75.
-The idea is to not ensure top level series - which due to aggregation are on a much larger scale -  do not dominate the forecast evaluation metric.
-Using this weights in WLS reconciliation is equivalent to what \cite{AthEtAl2017} refer to as \textit{structural scaling}.
+The idea is to ensure top level series - which are on a much larger scale -  do not dominate the forecast evaluation metric.
+Using these weights in WLS reconciliation is equivalent to what \cite{AthEtAl2017} refer to as \textit{structural scaling}.
 As such we refer to WLS based on these weights as `Structural-WLS' and the loss function based on these weights as `Structural-WSE'.
@@
 
-After obtaining the base forecasts these are reconciled using four different projection methods: OLS,{\color{blue} Structural-WLS, Spend-WLS  and MinT.
-For MinT, the shrinkage estimator of \cite{Schafer2005} is used to estimate to covariance matrix of one step ahead forecast errors.
-That is $\bm{\Sigma} = \tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
+After obtaining the base forecasts these are reconciled using four different projection methods: OLS, {\color{blue} Structural-WLS, Spend-WLS  and MinT.
+For MinT, the shrinkage estimator of \cite{Schafer2005} is used to estimate  $\bm{\Sigma}$.
+The estimate is $\tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
 	\begin{equation*}
@@
 	\end{equation*}
-	where $\sigma_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}^{\text{sam}}$.
+	where $\hat{\sigma}_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}$.
 For each loss function} we compute the difference between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate.
 
-The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of this measure over each rolling window.
+The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of this difference over each rolling window.
 We only present the results for $h=1$, but the results and conclusions that follow are almost identical for the other longer forecast horizons.

### 2020-01-29 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added new table and figure to manuscript

@@
     \small
-    \includegraphics[width = \textwidth]{Figs/BoxPlot.pdf}
-    \caption{MSE differences between base forecasts and reconciled forecasts using OLS, MinT and WLS, and also the bottom-up approach for $h = 1$.
+    \includegraphics[width = \textwidth]{Figs/lossboxplots_1.pdf}
+    \caption{Differences between base forecasts and reconciled forecasts for different loss functions using different reconciliation methods for $h = 1$.
 A positive value indicates that the coherent forecasts are an improvement over the base forecasts.}\label{fig:BaseVSRecon_Fc}
@@
 
-\begin{table}[!hbt]
-\caption {Average {MSE($\times 10^3$)} over all 140 rolling window replications for $h=1$.}\label{tab:AveraveDifferences}
-  \centering \tabcolsep=0.4cm
-  \begin{tabular}{lccccc}
-  \toprule
-          & Base & OLS & MinT & WLS & Bottom-up \\
-   MSE    & 4.31 & 4.20 & \textbf{4.16} & 4.48 & 5.28 \\
-  \bottomrule
-  \end{tabular}
-\end{table}
+%\begin{table}[!hbt]
+%\caption {Average {MSE($\times 10^3$)} over all 140 rolling window replications for $h=1$.}\label{tab:AveraveDifferences}
+%  \centering \tabcolsep=0.4cm
+%  \begin{tabular}{lccccc}
+%  \toprule
+%          & Base & OLS & MinT & WLS & Bottom-up \\
+%   MSE    & 4.31 & 4.20 & \textbf{4.16} & 4.48 & 5.28 \\
+%  \bottomrule
+%  \end{tabular}
+%\end{table}
+\input{Tables/lossvmethods_h_1.tex}
 

### 2020-01-30 Application-R/Application-TourismData/Final-results/TourismData-Final-resultsR1.Rmd
Nemenyi Results in paper

@@
   group_by(`F.method`, `R.method`, Forecast_Horizon) %>% 
-  summarise(ME = round(sum(ME)/1e3, digits = 2)) %>% 
+  summarise(ME = sum(ME)/1e3) %>% 
   filter(Forecast_Horizon == 1) %>% 
@@
   dplyr::select(-Forecast_Horizon) -> Avg_Log_WL100_ME_h1
+
+# New ME
+DF_LogTrans_WL100 %>% 
+  group_by(F.method, R.method, Series, Forecast_Horizon) %>% 
+  summarise(ME = sum(ME)/1e3) %>%
+  filter(Forecast_Horizon == 1) %>% 
+  group_by(F.method,R.method) %>% 
+  summarise(AME=sum(abs(ME))) %>% 
+  ungroup() -> Avg_Log_WL100_ME_h1_new
 
@@
 
+Avg_Log_WL100_ME_h1_new <- Avg_Log_WL100_ME_h1_new %>%
+  mutate(AME=AME/Avg_Log_WL100_ME_h1_new[1,]$AME)
+
+print("ME")
 Avg_Log_WL100_ME_h1 %>% 
@@
 
-#MSE
+print("New ME")
+Avg_Log_WL100_ME_h1_new %>% 
+  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
+                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
+  spread(key = F.method, value = AME) %>% 
+  kable(format = "latex",digits = 2)
+
+print("MSE")
 DF_LogTrans_WL100 %>% 
@@
 
+\newpage
 # BoxCox Transformation for $\lambda \in (-0.5,2)$ with 100 observations of training window (ME and MSE calculated over 140 replications)
@@
 
+# New ME
+DF_BoxCoxTrans_WL100 %>% 
+  group_by(F.method, R.method, Series, Forecast_Horizon) %>% 
+  summarise(ME = sum(ME)/1e3) %>%
+  filter(Forecast_Horizon == 1) %>% 
+  group_by(F.method,R.method) %>% 
+  summarise(AME=sum(abs(ME))) %>% 
+  ungroup() -> Avg_BoxCox_WL100_ME_h1_new
+
 # Make everything percentage improvement
@@
   mutate(ME=ME/Avg_BoxCox_WL100_ME_h1[1,]$ME)
+
+Avg_BoxCox_WL100_ME_h1_new <- Avg_BoxCox_WL100_ME_h1_new %>%
+  mutate(AME=AME/Avg_BoxCox_WL100_ME_h1_new[1,]$AME)
 
@@
 
-#MSE
+print("New ME")
+Avg_BoxCox_WL100_ME_h1_new %>% 
+  mutate(F.method = recode(F.method, Unbiased_M1 = "Unbiased (Method 1)", 
+                           Unbiased_M2 = "Unbiased (Method 2)")) %>% 
+  spread(key = F.method, value = AME) %>% 
+  kable(format = "latex",digits = 2)
+
+print("MSE")
 DF_BoxCoxTrans_WL100 %>% 

### 2020-01-30 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Nemenyi Results in paper

@@
               & \multicolumn{6}{c}{ME}\\\cmidrule(lr){2-7}
-    Base      & 1.00 & 0.53^{\ast\dag} & 1.40^{\ast\dag} & 1.00 & 0.63^{\ast\dag} & 1.37^{\ast\dag}\\
-    OLS       & 0.51^{\ast} & 0.39^{\ast} & 0.66 & 0.54^{\ast} & 0.46^{\ast} & 0.74\\
-    MinT      & 0.74 & 0.51^{\ast\dag} & 1.10^{\dag} & 0.75 & 0.61^{\ast} & 1.03^{\dag}\\
-    WLS       & 1.21 & 0.58^{\ast\dag} & 1.74^{\ast\dag} & 1.20 & 0.69^{\ast\dag} & 1.67^{\ast\dag}\\
-    Bottom-up & 1.76^{\ast} & 0.64^{\ast\dag} & 2.72^{\ast\dag} & 1.73 & 0.75^{\ast\dag} & 2.57^{\ast\dag}\\
+    Base      & 1.00        & 0.58^{\ast\dag} & 1.40^{\ast\dag} & 1.00        & 0.73^{\ast\dag} & 1.38^{\ast\dag}\\
+    OLS       & 0.63^{\ast} & 0.54^{\ast}     & 0.76^{\dag}     & 0.65^{\ast} & 0.67^{\ast}     & 0.86 \\
+    MinT      & 0.77^{\ast} & 0.57^{\ast\dag} & 1.15^{\dag}     & 0.77^{\ast} & 0.70^{\ast}     & 1.09^{\dag}\\
+    WLS       & 1.22        & 0.63^{\ast\dag} & 1.75^{\ast}     & 1.22        & 0.79^{\ast\dag} & 1.68^{\ast\dag}\\
+    Bottom-up & 1.76^{\ast} & 0.69^{\ast\dag} & 2.72^{\ast\dag} & 1.73        & 0.84^{\ast\dag} & 2.57^{\ast\dag}\\
               & \multicolumn{6}{c}{MSE}\\\cmidrule(lr){2-7}

### 2020-01-30 Application-R/Application-TourismData/Final-results/Nemenyi.R

@@ -23,6 +23,8 @@ DF_LogTrans_WL100 %>% mutate(ME = `Actual` - `Forecasts`) -> DF_LogTrans_WL100
 #   summarise(ME = sum(ME)/1e3) %>% 
 #   arrange(ME)
 
+DF_LogTrans_WL100 %>%  head()
+
 # Nemenyi for ME
 DF_LogTrans_WL100 %>% 
   filter(Forecast_Horizon == 1) %>% 
@@ -33,11 +35,31 @@ DF_LogTrans_WL100 %>%
   select(Replication, ME ,method) %>% 
   spread(method,ME) %>% as.matrix() -> m
 
+  m %>%  head()
+
   m <- m[,-1] 
   class(m) <- "numeric"
 
   nemenyi(m,conf.level=0.95,plottype="matrix")
 
+  
+# New Nemenyi for ME
+  DF_LogTrans_WL100 %>% 
+    filter(Forecast_Horizon == 1) %>% 
+    group_by(Series, F.method, R.method) %>% 
+    summarise(ME = sum(ME)/1e3) %>%
+    mutate(AME=abs(ME)) %>% 
+    mutate(method=paste(F.method,R.method, sep='_')) %>% 
+    ungroup() %>% 
+    select(Series, AME ,method) %>% 
+    spread(method,AME) %>% as.matrix() -> m
+  
+  m <- m[,-1] 
+  class(m) <- "numeric"
+  
+  nemenyi(m,conf.level=0.95,plottype="matrix")
+  
+  
 # dm.test(e1,e2, alternative = "two.sided", h = 1, power = 2)
 
 # colSums(m) %>% as.matrix() -> ME
@@ -53,6 +75,7 @@ DF_LogTrans_WL100 %>%
 #   arrange(MSE)
 
 # Nemenyi for MSE
+
 DF_LogTrans_WL100 %>%
   filter(Forecast_Horizon == 1) %>% 
   group_by(Replication, F.method, R.method) %>% 

### 2020-01-30 Application-R/Application-TourismData/OrthVsOblq_projections/Original-scale_betterModels/Results/Analysis.R
changed boxplots to relative

@@ -95,18 +95,18 @@ OvernightTrips_OriginalScale_MSE %>%
   filter(Fc_horizon==hor)%>%
   select(-Fc_horizon)%>%
   pivot_wider(id_cols = Replication,names_from = `R.method`,values_from = c('TSE',`Structural-WSE`,`Spend-WSE`))%>%
-    mutate("TSE_OLS" = TSE_Base - TSE_OLS,
-         "TSE_MinT" = TSE_Base - `TSE_MinT(Shrink)`,
-         "TSE_Structural-WLS" = TSE_Base - TSE_WLS1,
-         "TSE_Spend-WLS" = TSE_Base - TSE_WLS2,
-         "Structural-WSE_OLS" = `Structural-WSE_Base` - `Structural-WSE_OLS`,
-         "Structural-WSE_MinT" = `Structural-WSE_Base` - `Structural-WSE_MinT(Shrink)`,
-         "Structural-WSE_Structural-WLS" = `Structural-WSE_Base` - `Structural-WSE_WLS1`,
-         "Structural-WSE_Spend-WLS" = `Structural-WSE_Base` - `Structural-WSE_WLS2`,
-         "Spend-WSE_OLS" = `Spend-WSE_Base` - `Spend-WSE_OLS`,
-         "Spend-WSE_MinT" = `Spend-WSE_Base` - `Spend-WSE_MinT(Shrink)`,
-         "Spend-WSE_Structural-WLS" = `Spend-WSE_Base` - `Spend-WSE_WLS1`,
-         "Spend-WSE_Spend-WLS" = `Spend-WSE_Base` - `Spend-WSE_WLS2`) %>%
+    mutate("TSE_OLS" = 1/(TSE_Base / TSE_OLS),
+         "TSE_MinT" = 1/(TSE_Base/  `TSE_MinT(Shrink)`),
+         "TSE_Structural-WLS" = 1/(TSE_Base / TSE_WLS1),
+         "TSE_Spend-WLS" = 1/(TSE_Base / TSE_WLS2),
+         "Structural-WSE_OLS" = 1/(`Structural-WSE_Base` / `Structural-WSE_OLS`),
+         "Structural-WSE_MinT" = 1/(`Structural-WSE_Base` / `Structural-WSE_MinT(Shrink)`),
[…]

### 2020-01-30 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
write up of 5.2

--- 2020-01-29 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
@@
 {\color{blue} Alternatively, the context of the forecast problem itself may suggest a loss function that weights series differently.
-For example in our tourism application in Section~\ref{sec:EmpStudy} we will consider weighting forecast errors by average tourism expenditure in each region.}\footnote{Similar consideration are taken into account for the loss function used in the M5 forecasting competition, see M5 REF HERE for more details.}  An even more sophisticated understanding may take {\color{blue}linear combinations} of series into account.
+For example in our tourism application in Section~\ref{sec:EmpStudy} we will consider weighting forecast errors by average tourism expenditure in each region.}\footnote{Similar consideration are taken into account for the loss function used in the M5 forecasting competition, see M5 REF HERE for more details.
+Add Athanasopoulos and Kourentzes (2020) discussion paper}  An even more sophisticated understanding may take {\color{blue}linear combinations} of series into account.
 All of these considerations lead towards {\color{blue} a loss function $L_{\bm W}(\bm{y}_{t+h},\tilde{\bm{y}}_{t+h|t})=||{\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t}}||_{\bm{W}}$ where $||\bm{v}||_{\bm{W}}=\bm{v}'\bm{W}\bm{v}$, and $\bm{W}$ is a symmetric matrix assumed to be invertible.
@@
 
-One way to understand the generalied Euclidean geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{1/2}$, {\color{blue} where $\bm{W}=(\bm{W}^{1/2})'\bm{W}^{1/2}$}.
+One way to understand the generalised Euclidean geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{1/2}$, {\color{blue} where $\bm{W}=(\bm{W}^{1/2})'\bm{W}^{1/2}$}.
 This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{1/2}\tilde{\bm{y}}$.
@@
 
-We now make explicit the connection betwenn the MinT and a loss function based on the squared Euclidean distance $L(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|^2$ before generalising to $L_{\bm W}(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|^2_{\bm W}$.
-By the properties of the trace operator, the objective function in Equation~\ref{eq:MinTObj} can be rearranged as
+We now make explicit the connection between the MinT and a loss function based on the squared Euclidean distance $L(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|^2$ before generalising to $L_{\bm W}(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|^2_{\bm W}$.
+By the properties of the trace operator, the objective function in Eq.~\eqref{eq:MinTObj} can be rearranged as
 
@@
 \begin{theo}[Expected loss minimisation and MinT]\label{th:gmint}
-    The usual MinT reconciliation method $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}$ solves the optimisation problem in Equation~\ref{eq:GMinTObj} for any choice of $\bm{W}$.
+    The usual MinT reconciliation method $\tilde{\bm{y}}=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}$ solves the optimisation problem in Eq.~\eqref{eq:GMinTObj} for any choice of $\bm{W}$.
 \end{theo}
 \begin{proof}
-	The loss function in Equation~\ref{eq:GMinTObj} is equivalent to Euclidean distance in the transformed space and can therefore be minimised by using the MinT method in this space.
+	The loss function in Eq.~\eqref{eq:GMinTObj} is equivalent to Euclidean distance in the transformed space and can therefore be minimised by using the MinT method in this space.
 The MinT method in the transformed space is given by
@@
 	\end{align*}
-	and substituting the expressions for $\bm{\Sigma}^*$, ${\bm{S}^*}$, $\bm{y}^{*}$ and $\hat{\bm{y}}^{*}$ into Equation~\ref{eq:MinTtran} yields, 
+	and substituting the expressions for $\bm{\Sigma}^*$, ${\bm{S}^*}$, $\bm{y}^{*}$ and $\hat{\bm{y}}^{*}$ into Eq.~\ref{eq:MinTtran} yields,
 	\begin{align*}
@@
 	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
-This corresponds to the loss function described in Section~\ref{sec:orthogonal}. We also consider loss functions based on a squared generalised Euclidean distance of the form
+This loss function is the square of the usual Euclidean distance described in Section~\ref{sec:orthogonal}.
+We also consider loss functions based on a squared generalised Euclidean distance of the form
 \begin{equation*}
@@
 	\end{equation*}
-	where $\hat{\sigma}_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}$.
-For each loss function} we compute the difference between base forecasts and reconciled forecasts, where positive values indicate that reconciled forecasts are more accurate.
-
-The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of this difference over each rolling window.
+	where $\hat{\sigma}_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}$. }
+
+{\color{blue} For each replication we compute the ratio of the value of the loss function corresponding to each alternative reconciliation method relative to the loss function corresponding to base forecsats.
+A value less than 1 indicates that a reconciliation method has a lower relative error than the base forecast for that replication, while a value greater than 1 indicates the opposite.
+The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of these ratios over each rolling window.
 We only present the results for $h=1$, but the results and conclusions that follow are almost identical for the other longer forecast horizons.
-We do not present these here to save space but they are available {\color{blue} in an online supplement.}
-
-As the theory predicts, OLS reconciliation always leads to an improvement relative to base forecasts.
+We do not present these here to save space but they are available {\color{red} in an online supplement.}
+
+For TSE, relative loss is always less than 1 only for OLS reconciliation, for Structural-WSE the same is only true for Structural-WLS and for Spend-WSE the same is only true for Spend-WLS.
+Therefore, Figure~\ref{fig:BaseVSRecon_Fc} demonstrates that a reconciliation method is guaranteed to improve upon base forecasts only when the $\bm{W}$ used in the loss function and reconciliation coincide.
+This is precisely what Theorem~\ref{th:distred} and Theorem~\ref{th:gdistred} would predict.
+On the other hand, for every loss function, MinT will perform worse than base for some realisations.
+For Theorem~\ref{th:gdistred} to hold for MinT, the loss function would need to set $\bm{W}=\bm{\Sigma}^{-1}$ and since the estimate of $\Sigma$ will change with each realisation we do not believe this is a sensible loss function to use.
+
+}
+
+%As the theory predicts, OLS reconciliation always leads to an improvement relative to base forecasts.
 The entire boxplot for OLS reconciliation is above zero.
@@
     \small
-    \includegraphics[width = \textwidth]{Figs/lossboxplots_1.pdf}
+    \includegraphics[width = \textwidth, height=14cm]{Figs/lossboxplots_1.pdf}
     \caption{Differences between base forecasts and reconciled forecasts for different loss functions using different reconciliation methods for $h = 1$.
-A positive value indicates that the coherent forecasts are an improvement over the base forecasts.}\label{fig:BaseVSRecon_Fc}
+A value less than 1 indicates that the coherent forecasts improvement upon base forecasts.
+}\label{fig:BaseVSRecon_Fc}
 \end{figure}
@@
 %\end{table}
+
+{\color{blue}
+
+The advantage of MinT however is clearly seen when loss functions are averaged.
+Table~\ref{tab:lossVmethods} reports the relative total error for each loss function.
+For example, for TSE the relative total squared error (RMTSE) is defined as
+\begin{equation}
+\textrm{RMTSE}^{q}=\frac{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{q}_t}{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{\textrm{Base}}_t}\,\label{eq:RTSE}
+\end{equation} 
+where $\textrm{TSE}^{\textrm{Base}}_t$ is the total squared error of the base forecasts at replication $t$.
+In contrast with what is displayed in the boxplots, here the average is taken over the replications before taking a ratio.
+Table~\ref{tab:lossVmethods} shows that the average loss for MinT is lower than for all other reconciliation methods, irrespective of the loss function used.
+This is precisely what would be expected from Theorem~\ref{th:gmint}.
+}
+
 \input{Tables/lossvmethods_h_1.tex}
@@
 Using the three sets of base forecasts from each of the two transformations, we generate coherent forecasts implementing OLS, MinT and WLS reconciliation projections, and also the bottom-up approach and compare the results for when the base forecasts are biased and bias-adjusted, i.e., unbiased.
-{\color{blue} In addition to the total squared error defined in Equation~\ref{eq:tse}, the total error (TE) is used to measure bias and is computed as
+{\color{blue} In addition to the relative total squared error (RTSE) defined in Eq.~\eqref{eq:RTSE}, the relative absolute total error (RATE) is used to measure bias.
+Total error (TE) is first calculated for each series $i$,
 \begin{equation*}
-\textrm{TE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})\,.
+\textrm{TE}^{q}_i=\sum\limits_{t=1}^{140}(y_{i,t}-\tilde{y}^{(q)}_{i,t})\,
 \end{equation*}
-Table~\ref{tab:Results_MSE} reports the relative mean total error (RMTE) and relative mean total error (RMTSE) defined as  
+and RATE is defined as,
 \begin{equation*}
-\textrm{RMTE}^{q}=\frac{\sum\limits_{t=1}^{140}\textrm{TE}^{q}_t}{\sum\limits_{t=1}^{140}\textrm{TE}^{\textrm{Base}}_t}\quad \textrm {and}\quad \textrm{RMTSE}^{q}=\frac{\sum\limits_{t=1}^{140}\textrm{TSE}^{q}_t}{\sum\limits_{t=1}^{140}\textrm{TSE}^{\textrm{Base}}_t}\,,
-\end{equation*}
-where $\textrm{TE}^{\textrm{Base}}_t$ and $\textrm{TSE}^{\textrm{Base}}_t$ are the total error and total squared error of the biased base forecasts at replication $t$.
-Stars indicate that the results are significantly different from the biased base forecasts using a DETAILS OF TEST HERE.
-Results are shown for $1$-step-ahead forecasts and} as was the case with Section~\ref{sec:comparebase}, the conclusions that follow extend almost identically to longer forecast horizons.
-{\color{blue} These are provided in an online supplement}.
+\textrm{RATE}^{q}=\frac{\sum\limits_{i=1}^{110}|\textrm{TE}^{q}_i|}{\sum\limits_{i=1}^{110}|\textrm{TE}^{\textrm{Base}}_i|} \end{equation*}
+
+Table~\ref{tab:Results_MSE} reports both RTSE and RATE.
+A star indicates that forecasts are significantly different from the biased base forecasts, while a dagger indicates that the unbiased forecasts are significantly different from the biased base forecasts from the same reconciliation method.
+Statistical significance of the differences in the forecast errors is based on the non-parametric Friedman and post-hoc Nemenyi tests, at a 5\% level of significance \citep{HolEtAl2013}.
+The Friedman test first establishes whether at least one of the forecasts is significantly different from the rest.
+If this is the case, we use the Nemenyi test to identify groups of forecasts for which there is no evidence of statistically significant differences.
+This testing approach does not impose any distributional assumptions and does not require multiple pairwise testing between forecasts, which would distort the outcome of the tests.We use the implementation of the tests available in the tsutils \citep{tsutils} package for R.}
 
@@
 {\color{blue}
-\caption {Average {\color{blue} RMTE and RMTSE} of $1$-step-ahead point forecasts from log and Box-Cox transformed series.
+\caption {{\color{blue} RATE and RTSE} of $1$-step-ahead point forecasts from log and Box-Cox transformed series.
 Biased denotes forecasts from simply reversing the transformation via Eq.~\eqref{eq:BoxCox_back-transformation}.
 Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in Eq.~\eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.
-{\color{blue}Stars indicate significant difference from biased base forecast according to a TEST DETAILS HERE.}}
+{\color{blue} A star indicates a statistically significant difference from the biased base forecasts, while a dagger indicates a statistically significant difference from the biased base forecasts from the same reconciliation approach.}}
 \label{tab:Results_MSE}
@@
               & \multicolumn{6}{c}{ME}\\\cmidrule(lr){2-7}
-    Base      & 1.00 & 0.53^{\ast\dag} & 1.40^{\ast\dag} & 1.00 & 0.63^{\ast\dag} & 1.37^{\ast\dag}\\
-    OLS       & 0.51^{\ast} & 0.39^{\ast} & 0.66 & 0.54^{\ast} & 0.46^{\ast} & 0.74\\
-    MinT      & 0.74 & 0.51^{\ast\dag} & 1.10^{\dag} & 0.75 & 0.61^{\ast} & 1.03^{\dag}\\
-    WLS       & 1.21 & 0.58^{\ast\dag} & 1.74^{\ast\dag} & 1.20 & 0.69^{\ast\dag} & 1.67^{\ast\dag}\\
-    Bottom-up & 1.76^{\ast} & 0.64^{\ast\dag} & 2.72^{\ast\dag} & 1.73 & 0.75^{\ast\dag} & 2.57^{\ast\dag}\\
+    Base      & 1.00        & 0.58^{\ast\dag} & 1.40^{\ast\dag} & 1.00        & 0.73^{\ast\dag} & 1.38^{\ast\dag}\\
+    OLS       & 0.63^{\ast} & 0.54^{\ast}     & 0.76^{\dag}     & 0.65^{\ast} & 0.67^{\ast}     & 0.86 \\
+    MinT      & 0.77^{\ast} & 0.57^{\ast\dag} & 1.15^{\dag}     & 0.77^{\ast} & 0.70^{\ast}     & 1.09^{\dag}\\
+    Bottom-up & 1.76^{\ast} & 0.69^{\ast\dag} & 2.72^{\ast\dag} & 1.73        & 0.84^{\ast\dag} & 2.57^{\ast\dag}\\
               & \multicolumn{6}{c}{MSE}\\\cmidrule(lr){2-7}
@@
     MinT      & 0.97^{\ast} & 0.93^{\ast} & 1.03 & 0.93^{\ast} & 0.91^{\ast} & 0.99\\
-    WLS       & 1.08 & 0.98 & 1.21 & 1.04 & 0.96 & 1.14\\
     Bottom-up & 1.42 & 1.18 & 1.80 & 1.35 & 1.16 & 1.63\\

### 2020-01-30 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex

@@
 	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
-This loss function is the square of the usual Euclidean distance described in Section~\ref{sec:orthogonal}.
-We also consider loss functions based on a squared generalised Euclidean distance of the form
+This corresponds to the loss function described in Section~\ref{sec:orthogonal}. We also consider loss functions based on a squared generalised Euclidean distance of the form
 \begin{equation*}
@@
 
-{\color{blue} For each replication we compute the ratio of the value of the loss function corresponding to each alternative reconciliation method relative to the loss function corresponding to base forecsats.
-A value less than 1 indicates that a reconciliation method has a lower relative error than the base forecast for that replication, while a value greater than 1 indicates the opposite.
+{\color{blue} For each loss function we compute the relative ratio of each alternative reconciliation method to base.
+A value ($<1$) shows a lower relative error compared to base, while a value $(>1)$ shows a relative error greater than base.
 The boxplots in Figure~\ref{fig:BaseVSRecon_Fc} summarise the distribution of these ratios over each rolling window.
 We only present the results for $h=1$, but the results and conclusions that follow are almost identical for the other longer forecast horizons.
-We do not present these here to save space but they are available {\color{red} in an online supplement.}
-
-For TSE, relative loss is always less than 1 only for OLS reconciliation, for Structural-WSE the same is only true for Structural-WLS and for Spend-WSE the same is only true for Spend-WLS.
-Therefore, Figure~\ref{fig:BaseVSRecon_Fc} demonstrates that a reconciliation method is guaranteed to improve upon base forecasts only when the $\bm{W}$ used in the loss function and reconciliation coincide.
-This is precisely what Theorem~\ref{th:distred} and Theorem~\ref{th:gdistred} would predict.
-On the other hand, for every loss function, MinT will perform worse than base for some realisations.
-For Theorem~\ref{th:gdistred} to hold for MinT, the loss function would need to set $\bm{W}=\bm{\Sigma}^{-1}$ and since the estimate of $\Sigma$ will change with each realisation we do not believe this is a sensible loss function to use.
-
-}
-
-%As the theory predicts, OLS reconciliation always leads to an improvement relative to base forecasts.
+We do not present these here to save space but they are available {\color{red} in an online supplement.}}
+
+As the theory predicts, OLS reconciliation always leads to an improvement relative to base forecasts.
 The entire boxplot for OLS reconciliation is above zero.
@@
     \caption{Differences between base forecasts and reconciled forecasts for different loss functions using different reconciliation methods for $h = 1$.
-A value less than 1 indicates that the coherent forecasts improvement upon base forecasts.
-}\label{fig:BaseVSRecon_Fc}
+A positive value indicates that the coherent forecasts are an improvement over the base forecasts.}\label{fig:BaseVSRecon_Fc}
 \end{figure}
@@
 {\color{blue}
-
-The advantage of MinT however is clearly seen when loss functions are averaged.
-Table~\ref{tab:lossVmethods} reports the relative total error for each loss function.
-For example, for TSE the relative total squared error (RMTSE) is defined as
+Table~\ref{tab:lossVmethods} reports the relative total error for each loss function. For example, for TSE the relative total squared error (RTSE) is defined as
 \begin{equation}
-\textrm{RMTSE}^{q}=\frac{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{q}_t}{\frac{1}{140}\sum\limits_{t=1}^{140}\textrm{TSE}^{\textrm{Base}}_t}\,\label{eq:RTSE}
+\textrm{RTSE}^{q}=\frac{\sum\limits_{t=1}^{140}\textrm{TSE}^{q}_t}{\sum\limits_{t=1}^{140}\textrm{TSE}^{\textrm{Base}}_t}\,\label{eq:RTSE}
 \end{equation} 
 where $\textrm{TSE}^{\textrm{Base}}_t$ is the total squared error of the base forecasts at replication $t$. 
-In contrast with what is displayed in the boxplots, here the average is taken over the replications before taking a ratio.
-Table~\ref{tab:lossVmethods} shows that the average loss for MinT is lower than for all other reconciliation methods, irrespective of the loss function used.
-This is precisely what would be expected from Theorem~\ref{th:gmint}.
 }

### 2020-01-30 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
small changes made to figure captions

--- 2020-01-30 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
@@
 A value less than 1 indicates that the coherent forecasts improvement upon base forecasts.
-}\label{fig:BaseVSRecon_Fc}
+Although it is not clearly apparent in the plot, for OLS there are some values in the Spend-WSE that are slightly greater than 1.}\label{fig:BaseVSRecon_Fc}
 \end{figure}
@@
 
-\input{Tables/lossvmethods_h_1.tex}
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{lrrrrrr}
+		\hline
+		Loss Function & Base & Bottom-up & OLS & Structural-WLS & Spend-WLS & MinT \\ 
+		\hline
+		TSE & 1.00 & 1.22 & 0.97 & 1.13 & 0.98 & 0.96 \\ 
+		Structural WSE & 1.00 & 1.01 & 0.96 & 0.98 & 1.00 & 0.93 \\ 
+		Spend WSE & 1.00 & 1.20 & 0.97 & 1.12 & 0.98 & 0.96 \\ 
+		\hline
+	\end{tabular}
+
+	\caption{Means of different loss functions for 1-step ahead forecasts using different reconciliation methods in the tourism application.  All figures are reported relative to base forecasts.}
+	\label{tab:lossVmethods} 
+\end{table}
 

### 2020-01-30 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
changes to captions

@@
     \includegraphics[width = \textwidth, height=14cm]{Figs/lossboxplots_1.pdf}
-    \caption{Differences between base forecasts and reconciled forecasts for different loss functions using different reconciliation methods for $h = 1$.
-A value less than 1 indicates that the coherent forecasts improvement upon base forecasts.
-Although it is not clearly apparent in the plot, for OLS there are some values in the Spend-WSE that are slightly greater than 1.}\label{fig:BaseVSRecon_Fc}
+    \caption{{\color{blue} Ratio of loss of reconciled forecast to loss of base forecast for $h = 1$.
+A value less than 1 indicates that the reconciled forecasts improve upon base forecasts.
+A log scale is used for the y axis.}}\label{fig:BaseVSRecon_Fc}
 \end{figure}
@@
 	\centering
+{\color{blue}	
 	\begin{tabular}{lrrrrrr}
@@
     \end{tabular}
-
-	\caption{Means of different loss functions for 1-step ahead forecasts using different reconciliation methods in the tourism application.  All figures are reported relative to base forecasts.}
+}
+	\caption{{\color{blue}Means of different loss functions for 1-step ahead forecasts using different reconciliation methods in the tourism application.
+All figures are reported relative to base forecasts.
+The lowest mean is always provided by MinT, for structural-WSE, the average loss for MinT is significantly than every other method.}}
 	\label{tab:lossVmethods} 

### 2020-01-30 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
log scale figure in manuscript

@@
 
-{\color{blue} For each replication we compute the ratio of the value of the loss function corresponding to each alternative reconciliation method relative to the loss function corresponding to base forecsats.
+{\color{blue} For each replication we compute the ratio of the loss of each alternative reconciliation method to the loss of base forecasts.
 A value less than 1 indicates that a reconciliation method has a lower relative error than the base forecast for that replication, while a value greater than 1 indicates the opposite.
@@
 On the other hand, for every loss function, MinT will perform worse than base for some realisations.
-For Theorem~\ref{th:gdistred} to hold for MinT, the loss function would need to set $\bm{W}=\bm{\Sigma}^{-1}$ and since the estimate of $\Sigma$ will change with each realisation we do not believe this is a sensible loss function to use.
+For Theorem~\ref{th:gdistred} to hold for MinT, the loss function would need to set $\bm{W}=\bm{\Sigma}^{-1}$.
+Since the estimate of ${\bm\Sigma}$ will change with each replication we do not believe this is a sensible loss function to use.
 
@@
 
-The advantage of MinT however is clearly seen when loss functions are averaged.
+The advantage of MinT however is clearly seen when loss functions are averaged (an estimate of expected loss).
 Table~\ref{tab:lossVmethods} reports the relative total error for each loss function.

### 2020-01-30 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Updated text for Bias correction. See also adjustments in loss functions

@@
 Table~\ref{tab:lossVmethods} reports the relative total error for each loss function.
-For example, for TSE the relative total squared error (RMTSE) is defined as
+For example, for TSE the relative mean total squared error (RMTSE) is defined as
 \begin{equation}
@@
 This is precisely what would be expected from Theorem~\ref{th:gmint}.
+{\color{red}Should we add a comment about significance?}
 }
@@
 All figures are reported relative to base forecasts.
-The lowest mean is always provided by MinT, for structural-WSE, the average loss for MinT is significantly than every other method.}}
+The lowest mean is always provided by MinT, for structural-WSE, the average loss for MinT is significantly than every other method.}{\color{red} I wonder what the Nemenyi matrix tests will look like here.
+Maybe these will show some stat significances worth reporting.}}
 	\label{tab:lossVmethods}
@@
 Using the three sets of base forecasts from each of the two transformations, we generate coherent forecasts implementing OLS, MinT and WLS reconciliation projections, and also the bottom-up approach and compare the results for when the base forecasts are biased and bias-adjusted, i.e., unbiased.
-{\color{blue} In addition to the relative total squared error (RTSE) defined in Eq.~\eqref{eq:RTSE}, the relative absolute total error (RATE) is used to measure bias.
-Total error (TE) is first calculated for each series $i$,
+{\color{blue} In addition to the relative mean total squared error (RMTSE) defined in Eq.~\eqref{eq:RTSE}, the relative mean absolute total error (RMATE) is used to measure bias.
+Total error (TE) is first calculated
 \begin{equation*}
@@
 \end{equation*}
-and RATE is defined as,
+reflecting the total bias of method $q$ across the 140 iterations for each series $i$.
+Taking the absolute value of each of these, so that positive and negative biases do not cancel across series, and then averaging over the 110 series, RMATE is defined as,
 \begin{equation*}
-\textrm{RATE}^{q}=\frac{\sum\limits_{i=1}^{110}|\textrm{TE}^{q}_i|}{\sum\limits_{i=1}^{110}|\textrm{TE}^{\textrm{Base}}_i|} \end{equation*}
-
-Table~\ref{tab:Results_MSE} reports both RTSE and RATE.
-A star indicates that forecasts are significantly different from the biased base forecasts, while a dagger indicates that the unbiased forecasts are significantly different from the biased base forecasts from the same reconciliation method.
+\textrm{RMATE}^{q}=\frac{\frac{1}{110}\sum\limits_{i=1}^{110}|\textrm{TE}^{q}_i|}{\frac{1}{110}\sum\limits_{i=1}^{110}|\textrm{TE}^{\textrm{Base}}_i|} \end{equation*}
+{\color{red} I have added M mean to both RTSE and RATE. Does this help or should it be dropped for simplicity}.
+
+Table~\ref{tab:Results_MSE} reports both RMTSE and RMATE for 1-step-ahead forecasts.
+\footnote{{\color{blue} Results and conclusions that follow are almost identical for the other longer forecast horizons I HOPE.
+Doing those today.
+We do not present these here to save space but they are available in an online supplement.}}
+
+An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased base forecasts from the same reconciliation method $q$.
 Statistical significance of the differences in the forecast errors is based on the non-parametric Friedman and post-hoc Nemenyi tests, at a 5\% level of significance \citep{HolEtAl2013}.
@@
 If this is the case, we use the Nemenyi test to identify groups of forecasts for which there is no evidence of statistically significant differences.
-This testing approach does not impose any distributional assumptions and does not require multiple pairwise testing between forecasts, which would distort the outcome of the tests.We use the implementation of the tests available in the tsutils \citep{tsutils} package for R.}
-
-%\begin{table}[!b]
-%\caption {Average {MSE($\times 10^3$)} of $1$-step-ahead point forecasts from log and Box-Cox transformed series.
+This testing approach does not impose any distributional assumptions and does not require multiple pairwise testing between forecasts, which would distort the outcome of the tests.
+We use the implementation of the tests available in the \verb"tsutils " \citep{tsutils} package for R.}
+
+\begin{table}[!b]
+{\color{blue}
+\caption {{\color{blue} RMATE and RMTSE} of $1$-step-ahead forecasts from log and Box-Cox transformed series.
 Biased denotes forecasts from simply reversing the transformation via Eq.~\eqref{eq:BoxCox_back-transformation}.
 Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in Eq.~\eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.}
-%\label{tab:Results_MSE}
-%\centering
-%  \begin{tabular}{lcccccc}
-%    \toprule
-%    \multicolumn{1}{c}{ } & \multicolumn{3}{c}{Log Transformation} &
-%    \multicolumn{3}{c}{Box-Cox Transformation}\\
-%    \cmidrule(lr){2-4} \cmidrule(lr){5-7}
-%    Method & Biased & Unbiased & Unbiased & Biased & Unbiased & Unbiased \\
-%    & & (Method-1) & (Method-2) && (Method-1) &(Method-2)\\ \midrule
-%    Base      & 4.47 & 4.43 & 4.51 & 4.59 & 4.52 & 4.78\\
-%    OLS       & 4.34 & 4.31 & 4.36 & 4.46 & 4.40 & 4.63\\
-%    MinT      & 4.32 & \textbf{4.16} & 4.61 & 4.29 & \textbf{4.17} & 4.54\\
-%    WLS       & 4.82 & 4.38 & 5.43 & 4.77 & 4.42 & 5.23\\
-%    Bottom-up & 6.36 & 5.26 & 8.06 & 6.21 & 5.31 & 7.46\\
-%    \bottomrule
-%  \end{tabular}
-%\end{table}
-
-\begin{table}[!b]
-{\color{blue}
-\caption {{\color{blue} RATE and RTSE} of $1$-step-ahead point forecasts from log and Box-Cox transformed series.
-Biased denotes forecasts from simply reversing the transformation via Eq.~\eqref{eq:BoxCox_back-transformation}.
-Unbiased(Method-1) performs bias adjustment via a Taylor series expansion as shown in Eq.~\eqref{eq:BoxCox_BT_biasadj} whereas Unbiased(Method-2) bias adjusts by subtracting the in-sample forecast error mean.
-{\color{blue} A star indicates a statistically significant difference from the biased base forecasts, while a dagger indicates a statistically significant difference from the biased base forecasts from the same reconciliation approach.}}
 \label{tab:Results_MSE}
@@
     & & \multicolumn{1}{c}{(Method-1)} & \multicolumn{1}{c}{(Method-2)} && \multicolumn{1}{c}{(Method-1)} &\multicolumn{1}{c}{(Method-2)}\\ \midrule
-              & \multicolumn{6}{c}{ME}\\\cmidrule(lr){2-7}
+              & \multicolumn{6}{c}{RMATE}\\\cmidrule(lr){2-7}
     Base      & 1.00        & 0.58^{\ast\dag} & 1.40^{\ast\dag} & 1.00        & 0.73^{\ast\dag} & 1.38^{\ast\dag}\\
@@
     Bottom-up & 1.76^{\ast} & 0.69^{\ast\dag} & 2.72^{\ast\dag} & 1.73        & 0.84^{\ast\dag} & 2.57^{\ast\dag}\\
-              & \multicolumn{6}{c}{MSE}\\\cmidrule(lr){2-7}
+              & \multicolumn{6}{c}{RMTSE}\\\cmidrule(lr){2-7}
     Base      & 1.00 & 0.99 & 1.01 & 1.00 & 0.98 & 1.04\\
@@
   \end{tabular}
-}
+}    {\color{blue} $^\ast$ indicates a statistically significant difference from the biased base forecasts.$^\dag$ indicates a statistically significant difference from the biased base forecasts from the same reconciliation method.}
+
 \end{table}
 
+Messages:
+\begin{itemize}
+  \item Bias correcting correctly using Method-1 and then reconciling returns the best results for both RMATE and RMTSE.
+The improvements over the biased base forecasts are statistically significant for both RMATE and RMTSE.
+OLS returns the best results for RMATE while MinT returns the best results for RMTSE.
+  \item Reconciliation helps with accounting for some of the bias.
+The improvements in the reconciled biased base forecasts are statistically significant compared to the base biased forecasts for both RMATE and RMTSE.
+  \item Bias correcting incorrectly has dier consequences as shown by Method-2.
+\end{itemize}
 Recall that reconciliation approaches via projections preserve unbiasedness in the reconciled forecasts iff the base forecasts are unbiased.

### 2020-01-31 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
write up of results in 5.2

@@
 
-Using the three sets of base forecasts from each of the two transformations, we generate coherent forecasts implementing OLS, MinT and WLS reconciliation projections, and also the bottom-up approach and compare the results for when the base forecasts are biased and bias-adjusted, i.e., unbiased.
+Using the three sets of base forecasts from each of the two transformations, we generate coherent forecasts implementing OLS and MinT reconciliation projections, and also the bottom-up approach and compare the results for when the base forecasts are biased and bias-adjusted, i.e., unbiased.
 {\color{blue} In addition to the relative mean total squared error (RMTSE) defined in Eq.~\eqref{eq:RTSE}, the relative mean absolute total error (RMATE) is used to measure bias.
@@
 \textrm{RMATE}^{q}=\frac{\frac{1}{110}\sum\limits_{i=1}^{110}|\textrm{TE}^{q}_i|}{\frac{1}{110}\sum\limits_{i=1}^{110}|\textrm{TE}^{\textrm{Base}}_i|} \end{equation*}
-{\color{red} I have added M mean to both RTSE and RATE. Does this help or should it be dropped for simplicity}.
 
@@
 Doing those today.
-We do not present these here to save space but they are available in an online supplement.}}
-
-An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased base forecasts from the same reconciliation method $q$.
+We do not present these here to save space but they are available in an online supplement.}}  An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased base forecasts from the same reconciliation method $q$.
 Statistical significance of the differences in the forecast errors is based on the non-parametric Friedman and post-hoc Nemenyi tests, at a 5\% level of significance \citep{HolEtAl2013}.
@@
 
-Messages:
-\begin{itemize}
-  \item Bias correcting correctly using Method-1 and then reconciling returns the best results for both RMATE and RMTSE.
-The improvements over the biased base forecasts are statistically significant for both RMATE and RMTSE.
-OLS returns the best results for RMATE while MinT returns the best results for RMTSE.
-  \item Reconciliation helps with accounting for some of the bias.
-The improvements in the reconciled biased base forecasts are statistically significant compared to the base biased forecasts for both RMATE and RMTSE.
-  \item Bias correcting incorrectly has dier consequences as shown by Method-2.
-\end{itemize}
 Recall that reconciliation approaches via projections preserve unbiasedness in the reconciled forecasts iff the base forecasts are unbiased.
 Hence, the two columns labelled ``Biased'' contain results for biased base but also reconciled forecasts.
-Using Method-1 for first bias adjusting the base forecasts and then reconciling, results in forecast improvements for all methods for both the log and the Box-Cox transformation induced bias.
-In this case MinT returns the lowest MSE across all forecasts.
-Notice that the ``Box-Cox biased'' base forecasts carry a higher bias compared to the ``log biased'' base forecasts.
+Using Method-1 for first bias adjusting the base forecasts and then reconciling, results in forecast improvements for all methods {\color{blue} for both RMATE and RMTSE and} both the log and the Box-Cox transformations.
+{\color{blue}The improvements over the biased base forecasts are statistically significant and OLS returns the best results for RMATE while MinT returns the best results for RMTSE.} %Notice that the ``Box-Cox biased'' base forecasts carry a higher bias compared to the ``log biased'' base forecasts.
 Even for these MinT reconciliation of bias adjusted base forecasts generates very accurate forecasts, almost as accurate as the forecasts that come from the less biased log transformation.
@@
 In contrast to the results from using Method-1 for bias adjusting before reconciliation, using Method-2 has an adverse effect on the forecast accuracy of the reconciled forecasts.
-In this case the reconciled unbiased forecasts are less accurate than the biased reconciled forecasts.
-This reflects the fact and sends the warning that implementing inappropriate bias adjustment, in this case using an additive rather than a multiplicative factor, will hinder forecast accuracy and extra care must be taken in this bias adjustment procedure.
+In this case the reconciled unbiased forecasts {\color{blue}leads to a significantly worse RMATE and RMTSE compared to base forecasts.}.
+This sends the warning that implementing inappropriate bias adjustment, in this case using an additive rather than a multiplicative factor, will hinder forecast accuracy and extra care must be taken in this bias adjustment procedure.
+
+{\color{blue} Also  of interest is the fact that reconciliation can to some extent mitigate bias even without bias correction.
+In particular, using OLS reconciliation without bias correction leads to a statistically significant reduction in bias relative to base forecasts.
+This is likely to occur since the direction of bias lies in a direction that is close to orthogonal to the coherent subspace.
+Projection therefore eliminates this bias to some extent.}
 

### 2020-01-31 Hierarchical-forecast-reconciliation/Supplement/supplement.tex
started supplementary appendix

\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage[margin=2cm]{geometry}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}

\title{\bf Supplementary Results for ``Forecast reconciliation: A geometric view with new insights on bias correction''}
\begin{document}
  \maketitle
  \section{Results for $h=2$ to $h=6$ for Section~5.2}

  	Figures~\ref{fig:BaseVSRecon_Fch2} through to~\ref{fig:BaseVSRecon_Fch6} show results for $h=2$ to $h=6$ corresponding to the application studied in Section~5.2.  These demonstrate the distance reducing properties of Theorem 3.1 and Theorem 3.2. The loss function TSE refers to total squared error (squared Euclidean distance).  The other two loss functions are weighted squared errors (squared generalised Euclidean distance) with the weights either determined by the structure of the hierarchy (Structural-WSE) or the average spend per region (Spend-WSE).  The reconciliation methods used are Base, bottom up, OLS, MinT WLS with the weights corresponding to either the `structural' or `spend weights.'

  	\begin{figure}[!hbt]
  		\centering
  		\small
  		\includegraphics[width = \textwidth, height=14cm]{lossboxplots_2.pdf}
  		\caption{ Ratio of loss of reconciled forecast to loss of base forecast for $h = 1$. A value less than 1 indicates that the reconciled forecasts improve upon base forecasts.  A log scale is used for the y axis.}
  		\label{fig:BaseVSRecon_Fch2}
  	\end{figure}
    	\begin{figure}[!hbt]
  	\centering
  	\small
  	\includegraphics[width = \textwidth, height=14cm]{lossboxplots_3.pdf}
  	\caption{Ratio of loss of reconciled forecast to loss of base forecast for $h = 1$. A value less than 1 indicates that the reconciled forecasts improve upon base forecasts.  A log scale is used for the y axis.}
  	\label{fig:BaseVSRecon_Fch3}
  \end{figure}
  	\begin{figure}[!hbt]
	\centering
	\small
	\includegraphics[width = \textwidth, height=14cm]{lossboxplots_4.pdf}
	\caption{Ratio of loss of reconciled forecast to loss of base forecast for $h = 1$. A value less than 1 indicates that the reconciled forecasts improve upon base forecasts.  A log scale is used for the y axis.}
	\label{fig:BaseVSRecon_Fch4}
\end{figure}
  	\begin{figure}[!hbt]
	\centering
	\small
	\includegraphics[width = \textwidth, height=14cm]{lossboxplots_5.pdf}
	\caption{Ratio of loss of reconciled forecast to loss of base forecast for $h = 1$. A value less than 1 indicates that the reconciled forecasts improve upon base forecasts.  A log scale is used for the y axis.}
	\label{fig:BaseVSRecon_Fch5}
\end{figure}
  	\begin{figure}[!hbt]
	\centering
	\small
	\includegraphics[width = \textwidth, height=14cm]{lossboxplots_6.pdf}
	\caption{ Ratio of loss of reconciled forecast to loss of base forecast for $h = 1$. A value less than 1 indicates that the reconciled forecasts improve upon base forecasts.  A log scale is used for the y axis.}
	\label{fig:BaseVSRecon_Fch6}
\end{figure}

  	Tables ~\ref{tab:sec52h2} through to~\ref{tab:sec52h6} demonstrate Theorem 3.3; namely that MinT minimises expected loss irrespective of the choice of the weighting matrix.  For these results, an average loss is taken over all replications.  These averages are all expressed relative to base.

  	\begin{table}[ht]
  		\centering
  		\begin{tabular}{lrrrrrr}
  			\hline
  			Loss Function & Base & Bottom-up & OLS & Structural-WLS & Spend-WLS & MinT \\ 
  			\hline
  			TSE & 1.00 & 1.27 & 0.97 & 1.17 & 0.98 & 0.97 \\ 
  			Structural WSE & 1.00 & 1.01 & 0.96 & 0.98 & 0.99 & 0.93 \\ 
  			Spend WSE & 1.00 & 1.25 & 0.97 & 1.16 & 0.98 & 0.96 \\ 
  			\hline
  		\end{tabular}
  		\caption{Means of different loss functions for 2-step ahead forecasts using different reconciliation methods in the tourism application.  All figures are reported relative to base forecasts.}
  		\label{tab:sec52h2} 
  	\end{table}

  	\begin{table}[ht]
  		\centering
  		\begin{tabular}{lrrrrrr}
  			\hline
  			Loss Function & Base & Bottom-up & OLS & Structural-WLS & Spend-WLS & MinT \\ 
  			\hline
  			TSE & 1.00 & 1.25 & 0.97 & 1.16 & 0.98 & 0.97 \\ 
  			Structural WSE & 1.00 & 1.00 & 0.96 & 0.98 & 1.00 & 0.93 \\ 
  			Spend WSE & 1.00 & 1.23 & 0.97 & 1.15 & 0.98 & 0.96 \\ 
  			\hline
  		\end{tabular}
  		\caption{Means of different loss functions for 3-step ahead forecasts using different reconciliation methods in the tourism application.  All figures are reported relative to base forecasts.} 
  	\end{table}

  	\begin{table}[ht]
  		\centering
  		\begin{tabular}{lrrrrrr}
  			\hline
  			Loss Function & Base & Bottom-up & OLS & Structural-WLS & Spend-WLS & MinT \\ 
  			\hline
  			TSE & 1.00 & 1.27 & 0.98 & 1.17 & 0.98 & 0.97 \\ 
  			Structural WSE & 1.00 & 1.01 & 0.96 & 0.98 & 0.99 & 0.92 \\ 
  			Spend WSE & 1.00 & 1.26 & 0.97 & 1.16 & 0.98 & 0.97 \\ 
  			\hline
  		\end{tabular}
  		\caption{Means of different loss functions for 4-step ahead forecasts using different reconciliation methods in the tourism application.  All figures are reported relative to base forecasts.} 
  	\end{table}

  \begin{table}[ht]
  	\centering
  	\begin{tabular}{lrrrrrr}
  		\hline
  		Loss Function & Base & Bottom-up & OLS & Structural-WLS & Spend-WLS & MinT \\ 
  		\hline
  		TSE & 1.00 & 1.28 & 0.98 & 1.18 & 0.98 & 0.97 \\ 
  		Structural WSE & 1.00 & 1.01 & 0.96 & 0.98 & 0.99 & 0.92 \\ 
  		Spend WSE & 1.00 & 1.26 & 0.97 & 1.17 & 0.98 & 0.96 \\ 
  		\hline
  	\end{tabular}
  	\caption{Means of different loss functions for 5-step ahead forecasts using different reconciliation methods in the tourism application.  All figures are reported relative to base forecasts.} 
  \end{table}

  \begin{table}[ht]
    \centering
	\begin{tabular}{lrrrrrr}
		\hline
		Loss Function & Base & Bottom-up & OLS & Structural-WLS & Spend-WLS & MinT \\ 
		\hline
		TSE & 1.00 & 1.21 & 0.98 & 1.13 & 0.99 & 0.97 \\ 
		Structural WSE & 1.00 & 1.00 & 0.97 & 0.98 & 1.00 & 0.93 \\ 
		Spend WSE & 1.00 & 1.20 & 0.98 & 1.12 & 0.98 & 0.97 \\ 
		\hline
	\end{tabular}
	\caption{Means of different loss functions for 6-step ahead forecasts using different reconciliation methods in the tourism application.  All figures are reported relative to base forecasts.}
	\label{tab:sec52h6} 
  \end{table}

  \section{Results for $h=2$ to $h=6$ for Section~5.3}

  George to include

\end{document}

### 2020-01-31 Application-R/Application-TourismData/Final-results/ModifiedNemenyiForLongerHorizons.R
O theos voithos

@@ -1,0 +1,103 @@
+library(tidyverse)
+library(tsutils)
+library(tidyr)
+library(Matrix)
+library(readr)
+library(tibble)
+library(kableExtra)
+
+DF_LogTrans_WL100 <- read.csv("DF_LogTrans_WL100.csv")[,-1]
+
+DF_LogTrans_WL100 <- DF_LogTrans_WL100 %>% 
+  mutate(F.method=recode(F.method, `Bias` = 'Biased')) 
+# so that we don't confuse Biased forecasts with ME/bias
+
+DF_LogTrans_WL100 %>% mutate(SquaredE = (`Actual` - `Forecasts`)^2) -> DF_LogTrans_WL100 
+DF_LogTrans_WL100 %>% mutate(ME = `Actual` - `Forecasts`)  -> DF_LogTrans_WL100
+
+
+# # ME calculations
+# DF_LogTrans_WL100 %>%
+#   filter(Forecast_Horizon == 1) %>% 
+#   group_by(`F.method`, `R.method`) %>% 
+#   summarise(ME = sum(ME)/1e3) %>% 
+#   arrange(ME)
+
+DF_LogTrans_WL100 %>%  head()
+DF_LogTrans_WL100 %>% select(F.method) %>% unique()
+
+# Being quick about this and not spending time to generalise
+
+# We drop Unbiased (Method 2 and WLS)
+DF_LogTrans_WL100 <- DF_LogTrans_WL100 %>% 
+  filter(F.method!="Unbiased_M2", R.method!="WLS") 
+
+# New ME calculations
+DF_LogTrans_WL100%>% 
+  group_by(F.method, R.method, Series, Forecast_Horizon) %>% 
+  summarise(ME = sum(ME)/1e3) %>%
+  group_by(F.method,R.method, Forecast_Horizon) %>% 
+  summarise(AME=sum(abs(ME))) %>% 
+  ungroup() %>% 
+  pivot_wider(names_from = c('F.method','R.method'),values_from =AME) %>%
+  mutate_at(vars(`Biased_Bottom-up`:Unbiased_M1_OLS),funs(./Biased_Base)) %>% 
+  mutate(Biased_Base=1) %>% 
+  pivot_longer(cols = -Forecast_Horizon) %>% 
+  pivot_wider(names_from = 'Forecast_Horizon')
+
+
+# Nemenyi for MSE
[…]

### 2020-01-31 Hierarchical-forecast-reconciliation/Supplement/supplement.tex
Supplement George

@@
 \usepackage[margin=2cm]{geometry}
-\usepackage{graphicx,psfrag,epsf}
+\usepackage{graphicx,psfrag,epsf,siunitx, multirow,booktabs}
 \usepackage{enumerate}
@@
 
+% Table generated by Excel2LaTeX from sheet 'Sheet1'
+\begin{table}[htbp]
+  \centering\footnotesize
+  \caption{Add caption}
+    \begin{tabular}{lrrrrrrrrrrrrr}
+    \toprule
+    & \multicolumn{6}{c}{Log Transformation}         &       & \multicolumn{6}{c}{Box-Cox Transformation} \\\cmidrule(lr){2-7}\cmidrule(lr){9-14}
+    Forecast horizon  & 1     & 2     & 3     & 4     & 5     & 6     &       & 1     & 2     & 3     & 4     & 5     & 6 \\\midrule
+          & \multicolumn{13}{c}{RMATE} \\ \cmidrule(lr){2-14}
+    Biased Base             & 1.00  & 1.00  & 1.00  & 1.00  & 1.00  & 1.00  &       & 1.00  & 1.00  & 1.00  & 1.00  & 1.00  & 1.00 \\
+    Biased Bottom-up        & 1.76  & 1.69  & 1.73  & 1.72  & 1.64  & 1.60  &       & 1.73  & 1.69  & 1.67  & 1.66  & 1.59  & 1.55 \\
+    Biased MinT             & 0.77  & 0.81  & 0.79  & 0.78  & 0.80  & 0.81  &       & 0.77  & 0.78  & 0.77  & 0.75  & 0.79  & 0.80 \\
+    Biased OLS              & 0.63  & 0.65  & 0.65  & 0.65  & 0.68  & 0.70  &       & 0.65  & 0.67  & 0.67  & 0.68  & 0.70  & 0.72 \\
+    Unbiased Base           & 0.58  & 0.62  & 0.64  & 0.65  & 0.68  & 0.69  &       & 0.73  & 0.75  & 0.76  & 0.77  & 0.78  & 0.79 \\
+    Unbiased Bottom-up      & 0.69  & 0.73  & 0.79  & 0.82  & 0.81  & 0.81  &       & 0.84  & 0.86  & 0.88  & 0.90  & 0.88  & 0.87 \\
+    Unbiased MinT           & 0.57  & 0.62  & 0.61  & 0.61  & 0.65  & 0.66  &       & 0.70  & 0.71  & 0.71  & 0.70  & 0.74  & 0.75 \\
+    Unbiased OLS            & 0.54  & 0.56  & 0.56  & 0.58  & 0.61  & 0.63  &       & 0.67  & 0.69  & 0.69  & 0.70  & 0.71  & 0.72 \\
+          & \multicolumn{13}{c}{RMTSE} \\\cmidrule(lr){2-14}
+    Biased Base             & 1.00  & 1.00  & 1.00  & 1.00  & 1.00  & 1.00  &       & 1.00  & 1.00  & 1.00  & 1.00  & 1.00  & 1.00 \\
+    Biased Bottom-up        & 1.42  & 1.48  & 1.56  & 1.53  & 1.52  & 1.50  &       & 1.35  & 1.37  & 1.39  & 1.39  & 1.37  & 1.32 \\
+    Biased MinT             & 0.97  & 0.98  & 1.02  & 0.98  & 0.98  & 0.98  &       & 0.93  & 0.95  & 0.96  & 0.96  & 0.96  & 0.94 \\
+    Biased OLS              & 0.97  & 0.97  & 0.97  & 0.97  & 0.97  & 0.97  &       & 0.97  & 0.97  & 0.97  & 0.97  & 0.97  & 0.97 \\
+    Unbiased Base           & 0.99  & 0.99  & 0.99  & 0.99  & 0.99  & 0.99  &       & 0.99  & 0.99  & 0.99  & 0.99  & 0.99  & 0.99 \\
+    Unbiased Bottom-up      & 1.18  & 1.21  & 1.27  & 1.24  & 1.23  & 1.20  &       & 1.16  & 1.15  & 1.17  & 1.17  & 1.14  & 1.11 \\
+    Unbiased MinT           & 0.93  & 0.94  & 0.97  & 0.94  & 0.94  & 0.93  &       & 0.91  & 0.92  & 0.93  & 0.93  & 0.93  & 0.91 \\
+    Unbiased OLS            & 0.96  & 0.96  & 0.96  & 0.96  & 0.96  & 0.96  &       & 0.96  & 0.96  & 0.96  & 0.96  & 0.96  & 0.96 \\\bottomrule
+    \end{tabular}
+  \label{tab:addlabel}%
+\end{table}%
+
 \end{document}

### 2020-01-31 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
O theos voithos
Having a go at 5.2 and 5.3

@@
 First, our approach makes it clear that the defining characteristic of so-called \emph{hierarchical time series} is not aggregation but linear constraints.
-As a result forecast reconciliation can be applied in contexts where there are no clear candidates of \emph{bottom level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling.
+As a result forecast reconciliation can be applied in contexts where there are no clear candidates of \emph{bottom-level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling.
 Second, {\color{blue} we provide a new proof that reconciled forecasts dominate unreconciled forecasts, for a certain class of loss functions.
@@
 
+\clearpage
+
+{\color{red} I've done a clear page here so we can see the flow better. We will remove this}
+
 \subsection{Comparison to Base Forecasts}\label{sec:comparebase}
@@
 
-{\color{blue} For each replication and for method $q$, we compute three loss functions.  The first is the total squared error (TSE), computed as
+{\color{red} I think the flow here is a bit confusing.
+I see that we need to talk about the loss functions before the reconciliation methods because of Spend-WLS.
+I suggest the following.
+We first introduce the three typical reconciliation methods - OLS, Structural-WLS and MinT and move the paragraph that introduces these above.
+Then when we introduce the loss functions we introduce in the second paragraph, starting ``The second choice'' Spend-WLS.
+I've re-written 5.2 based on this thought and called it -George in the end.
+See what do you think?
+Please delete appropriately.}
+
+{\color{blue} For each replication {\color{red} and for method $q$,- I don't think we need this here - $q$ is defined over the page} we compute three loss functions.
+The first is the total squared error (TSE), computed as
 	\begin{equation}
@@
 	We consider two choices of weights.
-The first is the inverse of the number of bottom level series included in forming a specific aggregate.
-For example, for all bottom level series this weight is 1, whereas for the top level series this is 1/75.
-The idea is to ensure top level series - which are on a much larger scale -  do not dominate the forecast evaluation metric.
+The first is the inverse of the number of bottom-level series included in forming a specific aggregate.
+For example, for all bottom-level series this weight is 1, whereas for the top-level series this is 1/75.
+The idea is to ensure top-level series, which are on a much larger scale, do not dominate the forecast evaluation metric.
 Using these weights in WLS reconciliation is equivalent to what \cite{AthEtAl2017} refer to as \textit{structural scaling}.
@@
 	where $\hat{\sigma}_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}$. }
+
+\clearpage
+\subsection*{Comparison to Base Forecasts - George}\label{sec:comparebase}
+
+To demonstrate the implications of Theorem~\ref{th:distred} we consider the improvement of different reconciliation methods over base forecasts {\color{blue} using different loss functions}.
+For each series the ARIMA model minimising AICc is chosen using the \verb|auto.arima()| function in the \verb|forecast| package.
+Using these fitted models, base forecasts are produced for $h=1$ to $6$-steps ahead for each series in the hierarchy.
+This is first carried out with a training sample of $100$ observations, i.e., Jan-$1998$ to Apr-$2006$.
+The training window is then rolled forward one observation at a time until the end of the sample.
+This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $135~6$-steps-ahead forecasts available for forecast evaluation.
+
+After obtaining the base forecasts these are reconciled using various projection methods.
+In particular: OLS reconciliation; WLS reconciliation using structural scaling introduced by \cite{AthEtAl2017} which we refer to as Structural-WLS; and MinT using the shrinkage estimator of \cite{Schafer2005} to estimate  $\bm{\Sigma}$.
+The estimate is $\tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
+	\begin{equation*}
+	\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{\sigma}_{ij})}{\sum_{i \neq j}{\hat{\sigma}}^2_{ij}}\,,
+	\end{equation*}
+	where $\hat{\sigma}_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}$.
+
+{\color{blue} For each method we compute three loss functions.  The first is the total squared error (TSE), computed as
+	\begin{equation}
+	\label{eq:tse}
+	\textrm{TSE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,,
+	\end{equation}
+	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
+This loss function is the square of the usual Euclidean distance described in Section~\ref{sec:orthogonal}.
+We also consider loss functions based on a squared generalised Euclidean distance of the form
+\begin{equation*}
+	\textrm{WSE}^{q}_t=\sum\limits_{i=1}^n \left(w_i (y_{i,t}-\tilde{y}^{(q)}_{i,t})\right)^2\,,
+	\end{equation*}
+	We consider two choices of weights.
+The first is the inverse of the number of bottom-level series included in forming a specific aggregate.
+For example, for all bottom-level series this weight is 1, whereas for the top-level series this is 1/75.
+The idea is to ensure top-level series, which are on a much larger scale, do not dominate the forecast evaluation metric.
+These are the weights used in the Structural-WLS reconciliation approach introduced in the previous paragraph.
+As such we refer to the loss function based on these weights as `Structural-WSE'.
+
+	The second choice of weights is motivated by our empirical example.
+In addition to visitor numbers per region, we also have access to data on average spend per region.
+In some settings, it may be desirable to have greater forecast accuracy in regions where tourists spend more.
+By using average spend per region as weights, the error metric (and transformed space associated with this metric) can be interpreted in terms of revenue measured in dollars rather than raw tourist numbers.
+Using these weights we introduce an alternative WLS reconciliation approach which we refer to as `Spend-WLS'.
+Correspondingly we refer to the loss function based on these weights as `Spend-WSE'.
+}
+
+{\color{red} My rewrite of 5.2 ends here}
 
@@
 This is precisely what would be expected from Theorem~\ref{th:gmint}.
-{\color{red}Should we add a comment about significance?}
+{\color{red} You said you commented on statistical significance but I cannot see it.
+I wonder what the Nemenyi matrix tests will look like here.
+Maybe these will show some stat significances worth reporting.
+--- Ok I see it is in the caption but the sentence needs fixing.
+Maybe it is best to have in the text rather than the caption.}
 }
@@
 		TSE & 1.00 & 1.22 & 0.97 & 1.13 & 0.98 & 0.96 \\
-		Structural WSE & 1.00 & 1.01 & 0.96 & 0.98 & 1.00 & 0.93 \\
-		Spend WSE & 1.00 & 1.20 & 0.97 & 1.12 & 0.98 & 0.96 \\
+		Structural-WSE & 1.00 & 1.01 & 0.96 & 0.98 & 1.00 & 0.93 \\
+		Spend-WSE & 1.00 & 1.20 & 0.97 & 1.12 & 0.98 & 0.96 \\
 		\hline
@@
 All figures are reported relative to base forecasts.
-The lowest mean is always provided by MinT, for structural-WSE, the average loss for MinT is significantly than every other method.}{\color{red} I wonder what the Nemenyi matrix tests will look like here.
-Maybe these will show some stat significances worth reporting.}}
+The lowest mean is always provided by MinT, for Structural-WSE, the average loss for MinT is significantly than every other method.}}
 	\label{tab:lossVmethods}
@@
 This is likely to occur since the direction of bias lies in a direction that is close to orthogonal to the coherent subspace.
-Projection therefore eliminates this bias to some extent.}
+Projection therefore eliminates this bias to some extent.}{\color{red} I now see that maybe the daggers should go since we are not talking about them.
+Please feel free to remove.}.
 

### 2020-02-01 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
editing writing up to empirical section

@@
 First, reconciliation via projection is guaranteed to improve forecast accuracy with respect to a class of loss functions based on a generalised distance metric.
-Second, the MinT method minimises expected loss for this same class of loss functions.
-The geometric interpretation is further used to provide a new proof that forecast reconciliation using projections results in unbiased forecasts provided the initial base forecasts are also unbiased.
-Approaches for dealing with biased base forecasts are proposed and evaluated in an extensive empirical study on Australian tourism flows.
-The method of bias-correcting before carrying out reconciliation is shown to outperform alternatives that only bias-correct or only reconcile forecasts.
-The empirical study also sheds light on the theoretical results of the paper.
+{\color{blue} Second, the MinT method minimises expected loss for this same class of loss functions.}  Third, the geometric interpretation provides a new proof that forecast reconciliation using projections results in unbiased forecasts provided the initial base forecasts are also unbiased.
+Approaches for dealing with biased base forecasts are proposed.
+An extensive empirical study on Australian tourism flows {\color{blue} demonstrates the theoretical results of the paper and shows that bias correction prior to reconciliation} outperforms alternatives that only bias-correct or only reconcile forecasts.
 
@@
 In this paper, we eschew a regression interpretation in favour of a novel, geometric understanding of forecast reconciliation.
-This allows us to develop novel proofs and a clearer understanding of the interplay between forecast bias and reconciliation methods.
+This allows us to develop novel proofs and a clearer understanding of the interplay between {\color{blue} objective functions, loss functions, }forecast bias and reconciliation methods.
 
@@
 As a result forecast reconciliation can be applied in contexts where there are no clear candidates of \emph{bottom-level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling.
-Second, {\color{blue} we provide a new proof that reconciled forecasts dominate unreconciled forecasts, for a certain class of loss functions.
+Second, {\color{blue} we provide a new proof that reconciled forecasts dominate base forecasts, for a certain class of loss functions.
 The projection that achieves this depends on the weights used in the loss function but not on the dependence in forecast errors.}  Futhermore, unlike {\color{blue} proofs of similar results by} \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general.
-{\color{blue} Third, we show that when it comes to minimising the expected value of the same class of loss functions, the optimal projection depends only on the covariance of the forecast errors, and not the weights used in the loss function.
-In this case of equal weights, this property is a direct consequence of the trace minimising property already established by \cite{WicEtAl2019}, we now prove that this result also applies to a more general class of loss functions.
-Fourth}, we prove that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased.
+{\color{blue} Third, we show that when it comes a different objective, namely minimising the expected loss, the optimal projection depends only on the covariance of the forecast errors, and not the weights used in the loss function.
+In this case of equal weights, this property is a direct consequence of the trace minimising property already established by \cite{WicEtAl2019}.
+We now prove that this result also applies to a more general class of loss functions.
+Fourth}, we prove a new proof that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased.
 A natural question that arises is what to do in the case of biased reconciled forecasts.
 Rather than addressing this issue by considering matrices that are not projections, we propose to bias-correct before reconciliation.
-This is evaluated in an extensive empirical study where we find that even when bias correction fails, the extent of the problem is mitigated by reconciling forecasts.\todo{Re-check after results}
+This is evaluated in an extensive empirical study where we find that even when bias correction fails, the extent of the problem is mitigated by reconciling forecasts.
 
@@
 
-The property that data adhere to some linear constraints is referred to as \emph{coherence}. We now provide definitions aimed at providing geometric intuition of hierarchical time series.
+The property that data adhere to some linear constraints is referred to as \emph{coherence}. We now provide definitions aimed at providing geometric intuition for hierarchical time series.
 
@@
 In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.
-\begin{itemize}
+\begin{enumerate}
 \item The first is that reconciliation should adjust the base forecasts as little as possible; i.e. the base and reconciled forecasts should be `close'.
 \item The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value targeted by the forecast.
-\end{itemize}
+\end{enumerate}
 
 To address the first of these properties we make the concept of closeness more concrete by considering the Euclidean distance between the base forecast $\hat{\bm{y}}_{t+h|t}$ and the reconciled forecast $\tilde{\bm{y}}_{t+h|t}$.
-A property of an orthogonal projection is that the distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$ is minimal over any possible $\tilde{\bm{y}}\in\mathfrak{s}$.
+A property of an orthogonal projection is that the distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$ is minimal over any possible $\tilde{\bm{y}}_{t+h|t}\in\mathfrak{s}$.
 In this sense reconciliation via orthogonal projection {\color{blue} $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$} leads to the smallest possible adjustments of the base forecasts.
-{\color{blue} Euclidean distance can be interpreted as a loss function $L(\bm{u},\bm{v})=\|\bm{u}-\bm{v}\|$ where $\|.\|$ is the L2 norm, in which case an orthogonal projection solves the optimisation problem $\underset{\bm{G}}{\min}\,L(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t},\hat{\bm{y}}_{t+h|t})$.
+{\color{blue} ALternatively, Euclidean distance can be interpreted as a loss function $L(\bm{u},\bm{v})=\|\bm{u}-\bm{v}\|$ where $\|.\|$ denotes the L2 norm, in which case an orthogonal projection solves the optimisation problem $\underset{\bm{G}}{\min}\,L(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t},\hat{\bm{y}}_{t+h|t})$.
 This is a special case of the optimisation problem considered by \cite{NysEtAl2019}, the more general case will be covered in the next section.}
 
-The {\color{blue} aim of the second property is to guarantee that} reconciled forecasts should always be closer to the target than base forecasts {\color{blue} and is related with the difference in loss functions $L({\bm{y}}_{t+h},\hat{\bm{y}}_{t+h|t})-L({\bm{y}}_{t+h},\tilde{\bm{y}}_{t+h|t})$.
+The {\color{blue} aim of the second property is to guarantee that} reconciled forecasts should always be closer to the target than base forecasts {\color{blue} and is related to the difference in loss functions $L({\bm{y}}_{t+h},\hat{\bm{y}}_{t+h|t})-L({\bm{y}}_{t+h},\tilde{\bm{y}}_{t+h|t})$.
 This is expressed as a minimax optimisation by \cite{VanErven2015a} and was also} touched upon in Section 2.3 of \citet{WicEtAl2019}{\color{blue}, albeit in both cases for a slightly different loss function}.
@@
 Figure~\ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle with $\tilde{\bm{y}}$ at the right-angled vertex.
-In this triangle the line between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.
+In this triangle, the line between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.
 Therefore reconciliation is guaranteed to reduce {\color{blue} a loss function based on distance, or indeed any monotonic function of distance.}
@@
 First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.
-In particular, this measure is the square root of the sum of squared forecast errors of \emph{all} variables in the hierarchy.
-Consequently, while forecast improvement is guaranteed for the hierarchy overall, {\color{blue} forecast errors are treated equally across all series}.
-Second, although orthogonal projections are guaranteed to improve on base forecasts, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.
-Therefore, referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections.
+In particular, this measure is the sum of squared forecast errors of \emph{all} variables in the hierarchy {\color{blue}(or any monotonic function thereof)}.
+Second, although an orthogonal projection is guaranteed to improve on base forecasts, it is not necessarily the projection that leads to the greatest improvement in forecast accuracy in expectation.
+Therefore, referring to OLS reconciliation as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections.
 {\color{blue} We now turn our attention to the way oblique projections can address both of these shortcomings.}
@@
 
-The implication of Theorem~\ref{th:gdistred} is that if the loss function is of the form $L_{\bm{W}}$ {\color{blue} with some $\bm{W}$ given a priori} then the projection matrix $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts.
+The implication of Theorem~\ref{th:gdistred} is that if the loss function is a monotonic function of $L_{\bm{W}}$ {\color{blue} with some $\bm{W}$ given a priori} then the projection matrix $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts.
 {\color{blue}  This result does not necessarily involve the covariance of forecast errors unless $\bm{W}$ is explicitly chosen to depend on these covariances.}
@@
 The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.
-As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is true only with respect to a loss function that depends on {\color{blue} $||.||_{\bm{\Sigma}^{-1}}$, where $\bm{\Sigma}=E(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'$}.
+As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is true only for loss {\color{blue}that is a monotonic function of $L_{\bm{\Sigma}^{-1}}$, where $\bm{\Sigma}=E(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'$}.
 If Euclidean distance (or mean squared error) is used {\color{blue} as a loss function}, there will be realisations where the MinT estimator does not improve forecast accuracy relative to base forecasts.
@@
 
-We now make explicit the connection between the MinT and a loss function based on the squared Euclidean distance $L(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|^2$ before generalising to $L_{\bm W}(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|^2_{\bm W}$.
-By the properties of the trace operator, the objective function in Eq.~\eqref{eq:MinTObj} can be rearranged as
+We now make explicit the connection between MinT and a loss function based on the squared Euclidean distance $L^2(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|^2$ before generalising to $L^2_{\bm W}(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|^2_{\bm W}$.
+\footnote{Since taking the square is monotonic over the range of $L$ and $L_{\bm W}$, the properties in Theorem~\ref{th:distred} and Theorem~\ref{th:gdistred} also apply to $L^2$ and $L^2_{\bm W}$.}  By the properties of the trace operator, the objective function in Eq.~\eqref{eq:MinTObj} can be rearranged as
 
@@
 &=E\left[\|\bm{y}-{\bm S}{\bm G}\hat{\bm{y}}\|^2\right]\\
-&=E\left[L(\bm{y},\tilde{\bm{y}})\right]
+&=E\left[L^2(\bm{y},\tilde{\bm{y}})\right]
 \end{align*}
@@
 	\begin{align*}
-	\bm{W}^{1/2}\tilde{\bm{y}}=\bm{W}^{1/2}\bm{S}&\left((\bm{W}^{1/2}\bm{S})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}(\bm{W}^{1/2}\bm{S})\right)^{-1}\\
+	\bm{W}^{1/2}\tilde{\bm{y}}=\bm{W}^{1/2}\bm{S}&\left((\bm{W}^{1/2}\bm{S})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\bm{S}\right)^{-1}\\
 	&(\bm{W}^{1/2}\bm{S})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\hat{\bm{y}}
@@
 	\begin{align*}
-    \tilde{\bm{y}}&=\bm{S}\left(\bm{S}'(\bm{W}^{-1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\bm{S}\right)^{-1}\\
-    &\qquad\qquad\bm{S}'(\bm{W}^{-1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\hat{\bm{y}}\\
+    \tilde{\bm{y}}&=\bm{S}\left(\bm{S}'(\bm{W}^{1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\bm{S}\right)^{-1}\\
+    &\qquad\qquad\bm{S}'(\bm{W}^{1/2})'(\bm{W}^{1/2'})^{-1}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{W}^{1/2}\hat{\bm{y}}\\
 	&=\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}\hat{\bm{y}}\\
@@
 The implication of this result is that irrespective of the ${\bm W}$ used in the loss function, an oblique projection based on the forecast error covariance will always minimise {\em expected} loss (where loss is based on squared generalised Euclidean distance).
-From the point of view of minimising expected loss, considerations about sensible weights for an error metric are only relevant in so far as they can estimate the forecast error covariance matrix.
+From the point of view of minimising expected loss, for loss defined in Equation~\ref{eq:GMinTObj}, considerations about sensible weights for an error metric are not relevant.
 This will be empirically demonstrated in Section~\ref{sec:EmpStudy}.
@@
 
-The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation of \citet{WicEtAl2019}.
+The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of \citet{WicEtAl2019}.
 Before restating this proof using a clear geometric interpretation, we discuss in a precise fashion what is meant by unbiasedness.
@@
 {\color{blue} Since linear constraints that hold on the original scale do not hold for the transformed series, back-transforming to the original scale is necessary.
-Since this step induces a bias we propose to bias correct after this back-transformation step, and ultimately to reconcile the back-transformed, bias-corrected forecasts.}  In the well-known case {\color{blue} of the Box-Cox transformation} a number of bias correction methods exist based on Taylor expansions.
+Since this step induces a bias we propose to bias correct after this back-transformation step, but before reconciliation.}  In the well-known case {\color{blue} of the Box-Cox transformation} a number of bias correction methods exist based on Taylor expansions.
 

### 2020-02-01 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
rewrit of section 5

@@
 Our motivation in this study is twofold.
-First, we demonstrate the implications of Theorem~\ref{th:distred} {\color{blue} and Theorem~\ref{th:gmint}} by comparing reconciled and base forecasts.
+First, we demonstrate the implications of Theorems~\ref{th:distred}{\color{blue},~\ref{th:gdistred} and~\ref{th:gmint}} by comparing reconciled and base forecasts.
 In contrast to previous studies, we consider individual periods {\color{blue} as well as} compute averages over a rolling window.
@@
 
-The top panel of Figure~\ref{fig:States_Zones_Regs_TSplots} shows time plots for the seven states, hence the first level of the geographical hierarchy.
+The top panel of Figure~\ref{fig:States_Zones_Regs_TSplots} shows time plots for the six states and Northern Territory, hence the first level of the geographical hierarchy.
 The panels below show some selected series from the second-level zones and the bottom-level regions.
 The plots display the diversity of time series features, within but also between levels.
-For example, noticeable at the first level is the asynchronous seasonal pattern between the Northern Territory and the other states.
+For example, noticeable at the first level is the asynchronous seasonal pattern between the Northern Territory and the states.
 For the Northern Territory the high tourist season occurs during June-August with July being the peak, while the low season is during December-February.
-This reflects the tropical climate of the Northern Territory, with Australians mostly visiting the North during its dry winter-season rather than the wet summer season.
+This reflects the tropical climate of the Northern Territory, with Australians mostly visiting the north during its dry winter-season rather than the wet summer season.
 Noticeable as we move to the lower levels is the variation in the signal-to-noise ratio, with the regional bottom-level series being much noisier compared to the series from levels above.
@@
 
-\subsection{Comparison to Base Forecasts}\label{sec:comparebase}
+\subsection*{Comparison to Base Forecasts}\label{sec:comparebase}
 
@@
 
-{\color{red} I think the flow here is a bit confusing.
-I see that we need to talk about the loss functions before the reconciliation methods because of Spend-WLS.
-I suggest the following.
-We first introduce the three typical reconciliation methods - OLS, Structural-WLS and MinT and move the paragraph that introduces these above.
-Then when we introduce the loss functions we introduce in the second paragraph, starting ``The second choice'' Spend-WLS.
-I've re-written 5.2 based on this thought and called it -George in the end.
-See what do you think?
-Please delete appropriately.}
-
-{\color{blue} For each replication {\color{red} and for method $q$,- I don't think we need this here - $q$ is defined over the page} we compute three loss functions.
-The first is the total squared error (TSE), computed as
-	\begin{equation}
-	\label{eq:tse}
-	\textrm{TSE}^{q}_t=\sum\limits_{i=1}^n(y_{i,t}-\tilde{y}^{(q)}_{i,t})^2\,,
-	\end{equation}
-	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
-This loss function is the square of the usual Euclidean distance described in Section~\ref{sec:orthogonal}.
-We also consider loss functions based on a squared generalised Euclidean distance of the form
-\begin{equation*}
-	\textrm{WSE}^{q}_t=\sum\limits_{i=1}^n \left(w_i (y_{i,t}-\tilde{y}^{(q)}_{i,t})\right)^2\,,
-	\end{equation*}
-	We consider two choices of weights.
-The first is the inverse of the number of bottom-level series included in forming a specific aggregate.
-For example, for all bottom-level series this weight is 1, whereas for the top-level series this is 1/75.
-The idea is to ensure top-level series, which are on a much larger scale, do not dominate the forecast evaluation metric.
-Using these weights in WLS reconciliation is equivalent to what \cite{AthEtAl2017} refer to as \textit{structural scaling}.
-As such we refer to WLS based on these weights as `Structural-WLS' and the loss function based on these weights as `Structural-WSE'.
-
-	The second choice of weights is motivated by our empirical example.
-In addition to visitor numbers per region, we also have access to data on average spend per region.
-In some settings, it may be desirable to have greater forecast accuracy in regions where tourists spend more.
-By using average spend per region as weights, the error metric (and transformed space associated with this metric) can be interpreted in terms of revenue measured in dollars rather than raw tourist numbers.
-We refer to WLS based on these weights as `Spend-WLS' and the loss function based on these weights as `Spend-WSE'.
-}
-
-After obtaining the base forecasts these are reconciled using four different projection methods: OLS, {\color{blue} Structural-WLS, Spend-WLS  and MinT.
-For MinT, the shrinkage estimator of \cite{Schafer2005} is used to estimate  $\bm{\Sigma}$.
-The estimate is $\tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
-	\begin{equation*}
-	\tau = \frac{\sum_{i \neq j}\hat{\var}(\hat{\sigma}_{ij})}{\sum_{i \neq j}{\hat{\sigma}}^2_{ij}}\,,
-	\end{equation*}
-	where $\hat{\sigma}_{ij}$ denotes the $(i,j)$th element of $\hat{\bm{\Sigma}}$. }
-
-\clearpage
-\subsection*{Comparison to Base Forecasts - George}\label{sec:comparebase}
-
-To demonstrate the implications of Theorem~\ref{th:distred} we consider the improvement of different reconciliation methods over base forecasts {\color{blue} using different loss functions}.
-For each series the ARIMA model minimising AICc is chosen using the \verb|auto.arima()| function in the \verb|forecast| package.
-Using these fitted models, base forecasts are produced for $h=1$ to $6$-steps ahead for each series in the hierarchy.
-This is first carried out with a training sample of $100$ observations, i.e., Jan-$1998$ to Apr-$2006$.
-The training window is then rolled forward one observation at a time until the end of the sample.
-This generates $140~1$-step-ahead, $139~2$-steps-ahead through to $135~6$-steps-ahead forecasts available for forecast evaluation.
-
 After obtaining the base forecasts these are reconciled using various projection methods.
-In particular: OLS reconciliation; WLS reconciliation using structural scaling introduced by \cite{AthEtAl2017} which we refer to as Structural-WLS; and MinT using the shrinkage estimator of \cite{Schafer2005} to estimate  $\bm{\Sigma}$.
-The estimate is $\tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
+In particular: OLS reconciliation, MinT and WLS reconciliation with two different choices of weights that are defined below.
+For MinT the shrinkage estimator of \cite{Schafer2005} is used to estimate  $\bm{\Sigma}$.
+It is given by $\tau\text{diag}(\hat{\bm{\Sigma}}) + (1-\tau)\hat{\bm{\Sigma}}$  where $\hat{\bm{\Sigma}}$ is the sample estimate of the variance covariance matrix of the in-sample, one-step ahead forecast errors and,
 	\begin{equation*}
@@
 	where $\tilde{y}^{(q)}$ is the reconciled forecast using method $q$ for series $i$ and replication $t$.
-This loss function is the square of the usual Euclidean distance described in Section~\ref{sec:orthogonal}.
-We also consider loss functions based on a squared generalised Euclidean distance of the form
+This loss function is $L^2$, the square of the usual Euclidean distance described in Section~\ref{sec:Reconciliation}. We also consider weighted squared error
 \begin{equation*}
-	\textrm{WSE}^{q}_t=\sum\limits_{i=1}^n \left(w_i (y_{i,t}-\tilde{y}^{(q)}_{i,t})\right)^2\,,
+	\textrm{WSE}^{q}_t=\sum\limits_{i=1}^n w_i\left( (y_{i,t}-\tilde{y}^{(q)}_{i,t})\right)^2\,,
 	\end{equation*}
+	which is a loss functions based on a squared generalised Euclidean distance $L_{\bm{W}}^2$, with diagonal $\bm{W}$.
 We consider two choices of weights.
-The first is the inverse of the number of bottom-level series included in forming a specific aggregate.
+The first is the squared inverse of the number of bottom-level series included in forming a specific aggregate.
 For example, for all bottom-level series this weight is 1, whereas for the top-level series this is 1/75.
 The idea is to ensure top-level series, which are on a much larger scale, do not dominate the forecast evaluation metric.
-These are the weights used in the Structural-WLS reconciliation approach introduced in the previous paragraph.
-As such we refer to the loss function based on these weights as `Structural-WSE'.
+Using these weights in WLS reconciliation is equivalent to what \cite{AthEtAl2017} refer to as \textit{structural scaling}.
+As such we refer to the reconciliation method that uses these weights as `Stuctural-WLS' and the loss function based on these weights as `Structural-WSE'.
 
@@
 In some settings, it may be desirable to have greater forecast accuracy in regions where tourists spend more.
-By using average spend per region as weights, the error metric (and transformed space associated with this metric) can be interpreted in terms of revenue measured in dollars rather than raw tourist numbers.
-Using these weights we introduce an alternative WLS reconciliation approach which we refer to as `Spend-WLS'.
-Correspondingly we refer to the loss function based on these weights as `Spend-WSE'.
+By using average spend per region as weights, the error metric (and transformed space associated with this metric) can be interpreted in terms of revenue, measured in dollars, rather than raw tourist numbers.
+We refer to the reconciliation method that uses these weights as `Stuctural-WLS' and the loss function based on these weights as `Structural-WSE'.
 }
-
-{\color{red} My rewrite of 5.2 ends here}
 
@@
 This is precisely what would be expected from Theorem~\ref{th:gmint}.
-{\color{red} You said you commented on statistical significance but I cannot see it.
-I wonder what the Nemenyi matrix tests will look like here.
-Maybe these will show some stat significances worth reporting.
---- Ok I see it is in the caption but the sentence needs fixing.
-Maybe it is best to have in the text rather than the caption.}
-}
+For Structural-WSE, a Diebold Mariano test confirms that the average loss for MinT is significantly lower when tested against every other method\footnote{{\color{blue} While differences are not significant for the other loss functions, the scale of the aggregate series leads to a large variance in loss, reducing the power of the test.
+Strutural-WSE stablises this effect.}}.
 
@@
 	\caption{{\color{blue}Means of different loss functions for 1-step ahead forecasts using different reconciliation methods in the tourism application.
-All figures are reported relative to base forecasts.
-The lowest mean is always provided by MinT, for Structural-WSE, the average loss for MinT is significantly than every other method.}}
+All figures are reported relative to base forecasts.}}
 	\label{tab:lossVmethods}
@@
 
-Table~\ref{tab:Results_MSE} reports both RMTSE and RMATE for 1-step-ahead forecasts.
-\footnote{{\color{blue} Results and conclusions that follow are almost identical for the other longer forecast horizons I HOPE.
-Doing those today.
-We do not present these here to save space but they are available in an online supplement.}}  An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased base forecasts from the same reconciliation method $q$.
+Table~\ref{tab:Results_MSE} reports both RMTSE and RMATE for 1-step-ahead forecasts.\footnote{{\color{blue} Results and conclusions that follow are almost identical for the other longer forecast horizons.
+We do not present these here to save space but they are available in an online supplement.}}  An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased forecasts from the same reconciliation method $q$.
 Statistical significance of the differences in the forecast errors is based on the non-parametric Friedman and post-hoc Nemenyi tests, at a 5\% level of significance \citep{HolEtAl2013}.
@@
   \end{tabular}
-}    {\color{blue} $^\ast$ indicates a statistically significant difference from the biased base forecasts.$^\dag$ indicates a statistically significant difference from the biased base forecasts from the same reconciliation method.}
+}    {\color{blue} $^\ast$ indicates a statistically significant difference from the biased base forecasts.$^\dag$ indicates a statistically significant difference from the biased forecasts from the same reconciliation method (same row).}
 

### 2020-02-01 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
new recommendations in conclusions

@@
 
-The implication of Theorem~\ref{th:gdistred} is that if the loss function is a monotonic function of $L_{\bm{W}}$ {\color{blue} with some $\bm{W}$ given a priori} then the projection matrix $\bm{S}(\bm{S}'\bm{W}^{-1}\bm{S})^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts.
+The implication of Theorem~\ref{th:gdistred} is that if the loss function is a monotonic function of $L_{\bm{W}}$ {\color{blue} with some $\bm{W}$ given a priori} then the projection matrix $\bm{S}(\bm{S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}$ is guaranteed to improve forecast accuracy over base forecasts.
 {\color{blue}  This result does not necessarily involve the covariance of forecast errors unless $\bm{W}$ is explicitly chosen to depend on these covariances.}
@@
 From the point of view of minimising expected loss, for loss defined in Equation~\ref{eq:GMinTObj}, considerations about sensible weights for an error metric are not relevant.
-This will be empirically demonstrated in Section~\ref{sec:EmpStudy}.
+This is an important caveat to the statement by \cite{VanErven2015a} that \textit{``one should not assume that the choice ${\bm\Sigma}^{-1}=\bm{W}$ will adequately take care of sharing information between hierarchical levels!''}.
+While this statement is correct in the context of Theorem~\ref{th:gdistred}, which is the case considered by \cite{VanErven2015a}, it is not true for the objective described in Equation~\ref{eq:GMinTObj}.
+This will be empirically demonstrated in Section~\ref{sec:EmpStudy}.}
 
@@
 
-}
 \section{Bias in forecast reconciliation}\label{sec:BiasInRecon}
@@
 
-\clearpage
-
-{\color{red} I've done a clear page here so we can see the flow better. We will remove this}
-
-\subsection*{Comparison to Base Forecasts}\label{sec:comparebase}
+\subsection{Comparison to Base Forecasts}\label{sec:comparebase}
 
@@
 Strutural-WSE stablises this effect.}}.
+}
 
@@
 
-Defining concepts such as coherence and reconciliation in geometric terms provides new insights into hierarchical forecasting methods.
-We have also provided evidence that bias correction before reconciliation improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation.
+Defining concepts such as coherence and reconciliation in geometric terms provides new insights into hierarchical forecasting methods. {\color{blue} We recommend the following steps for practitioners
+\begin{enumerate}
+	\item Choose an objective, either
+	\begin{enumerate}
+		\item To guarantee that reconciled forecasts improve upon base forecasts.
+		\item To find the reconciliation method that is best on average.
+	\end{enumerate}
+    \item Select a ${\bm W}$ to use in loss function $L^2_{\bm W}$ that is well suited to the empirical problem.  For objective (a) our results also apply to any monotonic function of $L^2_{\bm W}$.
+    \item Select a reconciliation method.  For objective:
+    \begin{enumerate}
+    	\item This should be ${\bm G}=({\bm S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}$. The dependence in forecast errors is not relevant.
+    	\item This should be ${\bm G}=({\bm S}'\bm{\Sigma}^{-1}\bm{S})^{-1}\bm{S}'\bm{\Sigma}^{-1}$. The choice of ${\bm W}$ is not relevant.
+    \end{enumerate}
+\end{enumerate}}
+{\color{blue} Furthermore, for the second objective, base forecasts must be unbiased.
+We recommend carrying out} bias correction before reconciliation {\color{blue} and provide evidence that this} improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation.
+
 Our intention in proposing a geometric interpretation is also to provoke research into new areas.
 We now discuss three such possibilities.
-
 First, it should be possible to extend the concept of coherence {\color{blue}to examples where the coherent space is not a linear plane in $\mathbb{R}^n$.

### 2020-02-01 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
removed daggers

@@
 Table~\ref{tab:Results_MSE} reports both RMTSE and RMATE for 1-step-ahead forecasts.\footnote{{\color{blue} Results and conclusions that follow are almost identical for the other longer forecast horizons.
-We do not present these here to save space but they are available in an online supplement.}}  An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased forecasts from the same reconciliation method $q$.
+We do not present these here to save space but they are available in an online supplement.}}  An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts.%, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased forecasts from the same reconciliation method $q$.
 Statistical significance of the differences in the forecast errors is based on the non-parametric Friedman and post-hoc Nemenyi tests, at a 5\% level of significance \citep{HolEtAl2013}.
@@
               & \multicolumn{6}{c}{RMATE}\\\cmidrule(lr){2-7}
-    Base      & 1.00        & 0.58^{\ast\dag} & 1.40^{\ast\dag} & 1.00        & 0.73^{\ast\dag} & 1.38^{\ast\dag}\\
-    OLS       & 0.63^{\ast} & 0.54^{\ast}     & 0.76^{\dag}     & 0.65^{\ast} & 0.67^{\ast}     & 0.86 \\
-    MinT      & 0.77^{\ast} & 0.57^{\ast\dag} & 1.15^{\dag}     & 0.77^{\ast} & 0.70^{\ast}     & 1.09^{\dag}\\
-    Bottom-up & 1.76^{\ast} & 0.69^{\ast\dag} & 2.72^{\ast\dag} & 1.73        & 0.84^{\ast\dag} & 2.57^{\ast\dag}\\
+    Base      & 1.00        & 0.58^{\ast} & 1.40^{\ast} & 1.00        & 0.73^{\ast} & 1.38^{\ast}\\
+    OLS       & 0.63^{\ast} & 0.54^{\ast}     & 0.76     & 0.65^{\ast} & 0.67^{\ast}     & 0.86 \\
+    MinT      & 0.77^{\ast} & 0.57^{\ast} & 1.15^{\dag}     & 0.77^{\ast} & 0.70^{\ast}     & 1.09\\
+    Bottom-up & 1.76^{\ast} & 0.69^{\ast} & 2.72^{\ast} & 1.73        & 0.84^{\ast} & 2.57^{\ast}\\
               & \multicolumn{6}{c}{RMTSE}\\\cmidrule(lr){2-7}
@@
   \end{tabular}
-}    {\color{blue} $^\ast$ indicates a statistically significant difference from the biased base forecasts.$^\dag$ indicates a statistically significant difference from the biased forecasts from the same reconciliation method (same row).}
+}    {\color{blue} $^\ast$ indicates a statistically significant difference from the biased base forecasts.}
 
@@
 This is likely to occur since the direction of bias lies in a direction that is close to orthogonal to the coherent subspace.
-Projection therefore eliminates this bias to some extent.}{\color{red} I now see that maybe the daggers should go since we are not talking about them.
-Please feel free to remove.}.
+Projection therefore eliminates this bias to some extent.}
 

### 2020-02-01 R1/Response.tex
changes to response and added square for orthogonality to figure

@@
 The referee's suggestions have allowed us to make additional insights that we believe have greatly improved the paper.
-We discuss these in detail below.\\
+We discuss these in detail at the relevant points below.\\
 
@@
 
-		We now also report the total error for all methods to highlight bias.
+		We now also report a measure of bias, defined in section 5.2.
 Here we see that bias correction method 1 removes bias, while bias correction method 2 in fact worsens bias.
@@
 Details on this method (including the choice of shrinkage parameter) are now provided.
-Similarly, we now provide more detail on variance scaling, which simply refers to using the variance of one step ahead in-sample forecast errors.\\
+Due to other changes in the paper we no longer consider variance scaling, we do however consider two alternative WLS reconciliation methods.
+The weights for these are explained in Section 5.2.\\
 
@@
 
+		We introduce a new form of WLS (Spend-WLS) that is admittedly somewhat context specific.
 The objective of this paper is not to propose a new and better reconciliation approach.
-Rather it is to establish new results that lead to clearer understanding of the properties of existing methods that in turn motivate research into new methods.
-Therefore, while the paper does not include a new method, it does provide insights into how new methods should (or should not) be developed.
-For examples of this, see the discussion on page 19 just before Section 4.1 and comments in the conclusion.\\
+Rather it is to establish new results that lead to clearer understanding of the properties of existing methods that can assist practitioners and in turn motivate research into new methods.
+Our recommendations to practitioners are now summarised in an expanded conclusion.
+Some insights into how new methods should (or should not) be developed by researchers are also provided in the conclusion and also in the just before Section 4.1.\\
 
@@
 
-		Improving the existing empirical application in the ways suggested by the referee has lengthened the paper considerably.
+		Improving the existing empirical application in the ways suggested by the referee, as well as some new material, has lengthened the paper considerably.
 Therefore, we prefer to refrain from including a second empirical demonstration.\\
@@
 	    We now expand section 5.2 to report results for three different error metrics.
-Furthermore we have added additional insights in Section 3.4 that are now also demonstrated in this section.
-In particular we show that while the distance reducing property of Theorem 3.2 depends entirely on the choice of loss function, minimising the expected loss function can always be achieved by a MinT approach and does not depend on the weights used in a loss function.\\
+In each case we show that the improvement guarantee only holds if the reconciliation method is aligned with the choice of error metric / loss function (we use error metric and loss function synonymously here).
+
+	    This result holds in a special case for MinT, when the loss function depends on the error covariance matrix, but since this matrix has to be reestimated for each replication, we do not believe this is a sensible loss function.
+Instead we now highlight that MinT has a rather different optimality property.
+While we briefly discussed this in the previous submission, we have now greatly expanded this discussion (mostly in Section 3.4).
+In particular we now show that MinT minimises expected loss for any loss function that is a squared generalised Euclidean distance.
+The choice of $\bm{W}$ is irrelevant in this setting.\\
 
@@
 We now consider two such loss functions, one based on the structure of the hierarchy (so-called `structural scaling') and another based on average spend in each region.
-To highlight how the transformed space can be interpreted in some contexts we have added the following sentence to the manuscript: ``By using average spend per region as weights, the error metric (and transformed space associated with this metric) can be interpreted in terms of revenue measured in dollars rather than raw tourist numbers.''
+To highlight how the transformed space can be interpreted in the latter context, we have added the following sentence to the manuscript: ``By using average spend per region as weights, the error metric (and transformed space associated with this metric) can be interpreted in terms of revenue measured in dollars rather than raw tourist numbers.''
 
 	    In cases where the transformed space cannot be easily be interpreted in terms of the empirical example, it is nevertheless it is an important construction in our proofs.
-This includes a new proof that MinT minimises expected loss even for loss functions based on generalised Euclidean distance.
-\\
+This includes the new proof that MinT minimises expected loss even for loss functions that is squared generalised Euclidean distance.
+In the revision we believe that we have more clearly decoupled the notion of optimality, loss functions and reconciliation methods that should be used in each case.
+The transformed space is critical to this understanding.\\
 
@@
 
-	    We have reduced the usage of the word ``however'' substantially, from twelve instances to just three.\\
+	    We have reduced the usage of the word ``however'' substantially, from twelve instances to just four.\\
 
@@
 
-	    We have made this change to all Figures. TO DO (GEORGE)\\
+	    We have made this change.\\
 
@@
 
-	    We now include these an an online supplement. TO DO\\
+	    We now include these an an online supplement. {\color{red} Eventually add link}\\
 
@@
 
-	    TO DO (GEORGE).\\
+	    It is not clear to us how the implications for the non-uniqueness of the S matrix for cross-temporal reconciliation are substantial (or at least more substantial than for any other paper in the literature).
+To reiterate, while S is not unique, the span of the columns of S is unique.
+While the S matrix used to construct a projection onto this linear subspace is non-unique, the final reconciled forecast will be the same.\\
 

### 2020-02-01 R1/Letter.tex
changes to response and added square for orthogonality to figure

@@
 \begin{enumerate}
-	\item We have greatly expanded the empirical study including more measures of forecast accuracy (including those specifically measuring bias).
+	\item We introduce a new result about MinT that explicitly makes the connection between trace minimisation and minimising a loss function based on squared Euclidean distance.
+We also prove a new result that MinT minimises expected loss for loss functions based on squared generalised Euclidean distance.
+This result is demonstrated in an expanded empirical application in section 5.2 that includes a wider range of loss functions.
+	\item We have greatly expanded the empirical study of Section 5.3 including more measures of forecast accuracy (including one specifically measuring bias).
 This has led to the insight that reconciliation alone can in fact reduce the bias of an estimator.
 We also now also report where differences in forecast accuracy are statistically significant.
-	\item We introduce some new results about MinT that explicitly make the connection between trace minimisation and minimising a loss function based on Euclidean distance.
-We also prove a new result that MinT minimises expected loss for loss functions based on generalised Euclidean distance.
-This result is demonstrated in an expanded empirical application in section 5.2 that includes a wider range of loss functions.
 	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negative forecasts, and state-space models. 

### 2020-02-01 Hierarchical-forecast-reconciliation/Supplement/supplement.tex
changed supplement

@@
 
-  \section{Results for $h=2$ to $h=6$ for Section~5.3}
+  \section{Results for all forecast horizons for Section~5.3}
 
-  George to include
+  Table~\ref{tab:bias} shows results for $h=2$ to $h=6$ corresponding to the study in Section~5.3.
+For conciseness results for Method 2 which were shown to not adequately address the bias issue are omitted.
 
@@
   \centering\footnotesize
-  \caption{Add caption}
+  \caption{Summary of results for all forecast horizons.
+All unbiased methods bias-correct the back-transformed forecasts before reconciling using Method 1 as described in the paper.
+The reconciliation methods used are Bottom-up, MinT and OLS.
+RMATE refers to relative mean absolute total error and RMTSE refers to relative mean total squared error.}
     \begin{tabular}{lrrrrrrrrrrrrr}
@@
     \end{tabular}
-  \label{tab:addlabel}%
+  \label{tab:bias}%
 \end{table}%

### 2020-02-01 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
added link to online supplement

@@
 We only present the results for $h=1$, but the results and conclusions that follow are almost identical for the other longer forecast horizons.
-We do not present these here to save space but they are available {\color{red} in an online supplement.}
+We do not present these here to save space but they are available in an online supplement\footnote{Available at \url{https://anastasiospanagiotelis.netlify.com/papers/GeomRecoSupplement.pdf}}.
 
@@
 Table~\ref{tab:Results_MSE} reports both RMTSE and RMATE for 1-step-ahead forecasts.\footnote{{\color{blue} Results and conclusions that follow are almost identical for the other longer forecast horizons.
-We do not present these here to save space but they are available in an online supplement.}}  An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts.%, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased forecasts from the same reconciliation method $q$.
+We do not present these here to save space but they are available at \url{https://anastasiospanagiotelis.netlify.com/papers/GeomRecoSupplement.pdf}.}}  An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts.%, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased forecasts from the same reconciliation method $q$.
 Statistical significance of the differences in the forecast errors is based on the non-parametric Friedman and post-hoc Nemenyi tests, at a 5\% level of significance \citep{HolEtAl2013}.

### 2020-02-04 R1/Response.tex
added link to online supplement
Final version

@@
 \usepackage{geometry}
+\usepackage{hyperref}
 \usepackage{bm}
@@
 
-		We introduce a new form of WLS (Spend-WLS) that is admittedly somewhat context specific.
         The objective of this paper is not to propose a new and better reconciliation approach.
@@
 Our recommendations to practitioners are now summarised in an expanded conclusion.
-Some insights into how new methods should (or should not) be developed by researchers are also provided in the conclusion and also in the just before Section 4.1.\\
+Some insights into how new methods should (or should not) be developed by researchers are also provided in the conclusion and also in the just before Section 4.1.
+Furthermore, we note that Spend-WLS is a new reconciliation method (albeit somewhat context specific).
+\\
 
 		In this paper, the purpose of the empirical evaluation is to provide a demonstration of the theoretical results that we have established.
-We agree that this could be improved.
+We have now improved the empirical evaluation.
 We have greatly expanded Section 5.2 to more clearly investigate three different loss functions and demonstrate the different ways in which reconciliation methods can be considered optimal.\\
-
-		Improving the existing empirical application in the ways suggested by the referee, as well as some new material, has lengthened the paper considerably.
-Therefore, we prefer to refrain from including a second empirical demonstration.\\
 
@@
 
-	    We now expand section 5.2 to report results for three different error metrics.
+	    We now expand Section 5.2 to report results for three different error metrics.
 In each case we show that the improvement guarantee only holds if the reconciliation method is aligned with the choice of error metric / loss function (we use error metric and loss function synonymously here).
@@
 
-	    In cases where the transformed space cannot be easily be interpreted in terms of the empirical example, it is nevertheless it is an important construction in our proofs.
-This includes the new proof that MinT minimises expected loss even for loss functions that is squared generalised Euclidean distance.
+	    In cases where the transformed space cannot be easily interpreted in terms of the empirical example, it is nevertheless an important construction in our proofs.
+This includes the new proof that MinT minimises expected loss for loss functions based on squared generalised Euclidean distance.
 In the revision we believe that we have more clearly decoupled the notion of optimality, loss functions and reconciliation methods that should be used in each case.
@@
 
-	    We have either removed all use of the term `ex post' or stated `ex post of base forecasting' to avoid the potential for confusion.\\
+	    We have either removed all use of the term `ex post' to avoid the potential for confusion.\\
 
@@
 
-	    We now include these an an online supplement. {\color{red} Eventually add link}\\
+	    We now include these an an online supplement available at\\ \href{https://anastasiospanagiotelis.netlify.com/papers/GeomRecoSupplement.pdf}{https://anastasiospanagiotelis.netlify.com/papers/GeomRecoSupplement.pdf}\\
 

### 2020-02-04 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Final version

@@
 
-Multivariate time series following an aggregation structure arise in many sectors such as retail, energy, insurance, health and welfare and economics \citep[see for example][]{KarMal2019, Taieb2017, NysEtAl2019, AlmVan2016, JeoEtAl2019, Mahkya2017, LiTan2019, Shang2017, AthEtAl2019_MacroBook}.
+Multivariate time series following an aggregation structure arise in many sectors such as retail, energy, insurance, health and welfare and economics \citep[see for example][]{KarMal2019, Taieb2017, NysEtAl2020, AlmVan2016, JeoEtAl2019, Mahkya2017, LiTan2019, Shang2017, AthEtAl2019_MacroBook}.
 Forecasts of these series should adhere to aggregation constraints to ensure aligned decision making.
 Earlier studies achieved this by only forecasting a single level of the hierarchy and then either aggregating in a bottom-up fashion \citep{Dunn1976} or disaggregating in a top-down fashion \citep{Gross1990, Athanasopoulos2009}.
-For reviews of these approaches, including a discussion of their advantages and disadvantages, see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001}.
+For reviews of these approaches, including a discussion of their advantages and disadvantages, see \citet{Schwarzkopf1988, Kahn1998, Lapide1998, Fliedner2001, Athanasopoulos2009}.
 
@@
 The latter paper also proposes a particular version of reconciliation known as the Minimum Trace (MinT) method.
-This is optimal in a {\color{blue} different} sense of minimising the trace of the reconciled forecast error covariance matrix under the assumption that the base forecasts are unbiased.
+This is optimal in a sense of minimising the trace of the reconciled forecast error covariance matrix under the assumption that the base forecasts are unbiased.
 
@@
 The projection that achieves this depends on the weights used in the loss function but not on the dependence in forecast errors.}  Futhermore, unlike {\color{blue} proofs of similar results by} \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general.
-{\color{blue} Third, we show that when it comes a different objective, namely minimising the expected loss, the optimal projection depends only on the covariance of the forecast errors, and not the weights used in the loss function.
+{\color{blue} Third, we show that when it comes to a different objective, namely minimising the expected loss, the optimal projection depends only on the covariance of the forecast errors, and not the weights used in the loss function.
 In this case of equal weights, this property is a direct consequence of the trace minimising property already established by \cite{WicEtAl2019}.
 We now prove that this result also applies to a more general class of loss functions.
-Fourth}, we prove a new proof that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased.
+Fourth}, we provide a new proof that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased.
 A natural question that arises is what to do in the case of biased reconciled forecasts.
@@
 In Section~\ref{sec:BiasInRecon} we prove the unbiasedness preserving property of reconciliation via certain projection matrices and propose methods for bias correction.
-In Section \ref{sec:EmpStudy} we conduct an extensive empirical application to domestic tourism flow in Australia with two objectives; first to demonstrate the theorems discussed in Section~\ref{sec:Reconciliation}, second to evaluate the methods for bias correction discussed in Section~\ref{sec:BiasInRecon}.
-Section~\ref{sec:conclusions} concludes with some discussion and thoughts on the future research directions {\color{blue}for} forecast reconciliation.
+In Section \ref{sec:EmpStudy} we conduct an extensive empirical application to domestic tourism flows in Australia with two objectives; first to demonstrate the theorems discussed in Section~\ref{sec:Reconciliation}, and second to evaluate the methods for bias correction discussed in Section~\ref{sec:BiasInRecon}.
+Section~\ref{sec:conclusions} concludes with some discussion, {\color{blue} practical recommendations} and thoughts on the future research directions {\color{blue}for} forecast reconciliation.
 
@@
 Subsequently forecasts for all series were recovered through {\color{blue} either} aggregation, disaggregation according to historical or forecast proportions, or some combination of both.
-Consequently, incoherent forecasts were not a problem in these earlier papers.
+Consequently, incoherent forecasts were not a challenge in these earlier papers.
 
@@
 Second, modelling higher level series often identifies features such as trend and seasonality that cannot be detected in noisy disaggregate data.
-However, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.\footnote{There are some special cases of using simple approaches such as na\"{i}ve, which extrapolate the coherent nature of the data to the forecasts.} {\color{blue}While the problem of incoherent forecasts can be addressed by some multivariate approaches, including state space models, these can not always be generalised to models with more complicated features or scaled up to high-dimensional problems.}  Instead, the solution is to make an adjustment, {\color{blue}ex post of base forecasting,} that ensures coherence, a process known as \emph{forecast reconciliation}
+However, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.\footnote{There are some special cases of using simple approaches such as na\"{i}ve, which extrapolate the coherent nature of the data to the forecasts.} {\color{blue}While the problem of incoherent forecasts can be addressed by some multivariate approaches, including state space models, these can not always be generalised to models with more complicated features or scaled up to high-dimensional problems.}  Instead, the solution is to make an adjustment that ensures coherence, a process known as \emph{forecast reconciliation}
 
@@
 We refrain from any discussion of regression models focusing instead on geometric interpretations.
-{\color{blue} Nonetheless,} the connection between OLS and orthogonal projection should be clear in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection of the response onto the span of the regressors.
+{\color{blue} Nonetheless,} the connection between OLS and orthogonal projection should be clear; in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection onto the span of the regressors.
 
@@
 \begin{enumerate}
-\item The first is that reconciliation should adjust the base forecasts as little as possible; i.e. the base and reconciled forecasts should be `close'.
+\item The first is that reconciliation should adjust the base forecasts as little as possible; i.e., the base and reconciled forecasts should be `close'.
 \item The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value targeted by the forecast.
@@
 In this sense reconciliation via orthogonal projection {\color{blue} $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$} leads to the smallest possible adjustments of the base forecasts.
-{\color{blue} ALternatively, Euclidean distance can be interpreted as a loss function $L(\bm{u},\bm{v})=\|\bm{u}-\bm{v}\|$ where $\|.\|$ denotes the L2 norm, in which case an orthogonal projection solves the optimisation problem $\underset{\bm{G}}{\min}\,L(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t},\hat{\bm{y}}_{t+h|t})$.
-This is a special case of the optimisation problem considered by \cite{NysEtAl2019}, the more general case will be covered in the next section.}
+{\color{blue} Alternatively, Euclidean distance can be interpreted as a loss function $L(\bm{u},\bm{v})=\|\bm{u}-\bm{v}\|$ where $\|.\|$ denotes the L2 norm, in which case an orthogonal projection solves the optimisation problem $\underset{\bm{G}}{\min}\,L(\hat{\bm{y}}_{t+h|t},\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t})$.
+This is a special case of the optimisation problem considered by \cite{NysEtAl2020}, the more general case will be covered in the next section.}
 
@@
 {\color{blue} Alternatively, the context of the forecast problem itself may suggest a loss function that weights series differently.
-For example in our tourism application in Section~\ref{sec:EmpStudy} we will consider weighting forecast errors by average tourism expenditure in each region.}\footnote{Similar consideration are taken into account for the loss function used in the M5 forecasting competition, see M5 REF HERE for more details.
-Add Athanasopoulos and Kourentzes (2020) discussion paper}  An even more sophisticated understanding may take {\color{blue}linear combinations} of series into account.
+For example in our tourism application in Section~\ref{sec:EmpStudy} we will consider weighting forecast errors by average tourism expenditure in each region.}\footnote{Similar consideration are made in the \cite{KouAth2019_Intermittent} discussion paper, and also are taken into account for the loss functions used in the M5 forecasting competition (see https://mofc.unic.ac.cy/m5-competition).}  An even more sophisticated understanding may take {\color{blue}linear combinations} of series into account.
 All of these considerations lead towards {\color{blue} a loss function $L_{\bm W}(\bm{y}_{t+h},\tilde{\bm{y}}_{t+h|t})=||{\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t}}||_{\bm{W}}$ where $||\bm{v}||_{\bm{W}}=\bm{v}'\bm{W}\bm{v}$, and $\bm{W}$ is a symmetric matrix assumed to be invertible.
@@
 {\color{blue} While MinT is used here to refer to the case where $\bm{\Sigma}$ is known, in practice,} it is unknown.
-It can be estimated using in-sample errors, {\color{blue} with some specific estimators found in \cite{WicEtAl2019} and also \cite{NysEtAl2019}.}
+It can be estimated using in-sample errors, {\color{blue} with some specific estimators found in \cite{WicEtAl2019} and also \cite{NysEtAl2020}.}
 
@@
 	\end{align*}
-	and substituting the expressions for $\bm{\Sigma}^*$, ${\bm{S}^*}$, $\bm{y}^{*}$ and $\hat{\bm{y}}^{*}$ into Eq.~\ref{eq:MinTtran} yields,
+	and substituting the expressions for $\bm{\Sigma}^*$, ${\bm{S}^*}$, $\bm{y}^{*}$ and $\hat{\bm{y}}^{*}$ into Eq.~\eqref{eq:MinTtran} yields,
 	\begin{align*}
@@
 The implication of this result is that irrespective of the ${\bm W}$ used in the loss function, an oblique projection based on the forecast error covariance will always minimise {\em expected} loss (where loss is based on squared generalised Euclidean distance).
-From the point of view of minimising expected loss, for loss defined in Equation~\ref{eq:GMinTObj}, considerations about sensible weights for an error metric are not relevant.
+From the point of view of minimising expected loss, for loss defined in Eq.~\eqref{eq:GMinTObj}, considerations about sensible weights for an error metric are not relevant.
 This is an important caveat to the statement by \cite{VanErven2015a} that \textit{``one should not assume that the choice ${\bm\Sigma}^{-1}=\bm{W}$ will adequately take care of sharing information between hierarchical levels!''}.
-While this statement is correct in the context of Theorem~\ref{th:gdistred}, which is the case considered by \cite{VanErven2015a}, it is not true for the objective described in Equation~\ref{eq:GMinTObj}.
+While this statement is correct in the context of Theorem~\ref{th:gdistred}, which is the case considered by \cite{VanErven2015a}, it is not true for the objective described in Eq.~\eqref{eq:GMinTObj}.
 This will be empirically demonstrated in Section~\ref{sec:EmpStudy}.}
@@
 We now propose a generalisation of the MinT method that uncouples these two ideas.
-Our proposed method targets more general loss functions than the sum of squared errors (in a similar vein to \cite{VanErven2015a} and \cite{NysEtAl2019}), while exploiting the correlation structure of forecast errors (in a similar vein to \cite{WicEtAl2019}).
+Our proposed method targets more general loss functions than the sum of squared errors (in a similar vein to \cite{VanErven2015a} and \cite{NysEtAl2020}), while exploiting the correlation structure of forecast errors (in a similar vein to \cite{WicEtAl2019}).
 %
@@
 %\end{equation*}
-%We note that some of solutions to the reconciliation problem proposed by \cite{NysEtAl2019}, for example \textit{series GLASSO scaling} and \textit{series shrinkage scaling} are special cases of this method where $\bm{W}$ is diagonal.
+%We note that some of solutions to the reconciliation problem proposed by \cite{NysEtAl2020}, for example \textit{series GLASSO scaling} and \textit{series shrinkage scaling} are special cases of this method where $\bm{W}$ is diagonal.
 What we seek to make clear here is the connection between $\bm{W}^{-1/2}$ (which need not be diagonal) and the loss function.
@@
 	\end{equation*}
-	which is a loss functions based on a squared generalised Euclidean distance $L_{\bm{W}}^2$, with diagonal $\bm{W}$.
+	which is a loss function based on a squared generalised Euclidean distance $L_{\bm{W}}^2$, with diagonal $\bm{W}$.
 We consider two choices of weights.
@@
 By using average spend per region as weights, the error metric (and transformed space associated with this metric) can be interpreted in terms of revenue, measured in dollars, rather than raw tourist numbers.
-We refer to the reconciliation method that uses these weights as `Stuctural-WLS' and the loss function based on these weights as `Structural-WSE'.
+We refer to the reconciliation method that uses these weights as `Spend-WLS' and the loss function based on these weights as `Spend-WSE'.
 }
@@
 {\color{blue}
-
 The advantage of MinT however is clearly seen when loss functions are averaged (an estimate of expected loss).
@@
 This is precisely what would be expected from Theorem~\ref{th:gmint}.
-For Structural-WSE, a Diebold Mariano test confirms that the average loss for MinT is significantly lower when tested against every other method\footnote{{\color{blue} While differences are not significant for the other loss functions, the scale of the aggregate series leads to a large variance in loss, reducing the power of the test.
+For Structural-WSE, a Friedman test confirms that the average loss for MinT is significantly lower when tested against every other method\footnote{{\color{blue} While differences are not significant for the other loss functions, the scale of the aggregate series leads to a large variance in loss, reducing the power of the test.
 Strutural-WSE stablises this effect.}}.
@@
 \begin{equation*}
-\textrm{RMATE}^{q}=\frac{\frac{1}{110}\sum\limits_{i=1}^{110}|\textrm{TE}^{q}_i|}{\frac{1}{110}\sum\limits_{i=1}^{110}|\textrm{TE}^{\textrm{Base}}_i|} \end{equation*}
+\textrm{RMATE}^{q}=\frac{\frac{1}{110}\sum\limits_{i=1}^{110}|\textrm{TE}^{q}_i|}{\frac{1}{110}\sum\limits_{i=1}^{110}|\textrm{TE}^{\textrm{Base}}_i|} . \end{equation*}
 
 Table~\ref{tab:Results_MSE} reports both RMTSE and RMATE for 1-step-ahead forecasts.\footnote{{\color{blue} Results and conclusions that follow are almost identical for the other longer forecast horizons.
-We do not present these here to save space but they are available at \url{https://anastasiospanagiotelis.netlify.com/papers/GeomRecoSupplement.pdf}.}}  An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts.%, while a dagger ($^\dag$) indicates that the unbiased forecasts are significantly different from the biased forecasts from the same reconciliation method $q$.
+We do not present these here to save space but they are available at \url{https://anastasiospanagiotelis.netlify.com/papers/GeomRecoSupplement.pdf}.}}  An asterisk ($^\ast$) indicates that forecasts are significantly different from the biased base forecasts.
 Statistical significance of the differences in the forecast errors is based on the non-parametric Friedman and post-hoc Nemenyi tests, at a 5\% level of significance \citep{HolEtAl2013}.
@@
     OLS       & 0.63^{\ast} & 0.54^{\ast}     & 0.76     & 0.65^{\ast} & 0.67^{\ast}     & 0.86 \\
-    MinT      & 0.77^{\ast} & 0.57^{\ast} & 1.15^{\dag}     & 0.77^{\ast} & 0.70^{\ast}     & 1.09\\
+    MinT      & 0.77^{\ast} & 0.57^{\ast} & 1.15     & 0.77^{\ast} & 0.70^{\ast}     & 1.09\\
     Bottom-up & 1.76^{\ast} & 0.69^{\ast} & 2.72^{\ast} & 1.73        & 0.84^{\ast} & 2.57^{\ast}\\
@@
 Using Method-1 for first bias adjusting the base forecasts and then reconciling, results in forecast improvements for all methods {\color{blue} for both RMATE and RMTSE and} both the log and the Box-Cox transformations.
-{\color{blue}The improvements over the biased base forecasts are statistically significant and OLS returns the best results for RMATE while MinT returns the best results for RMTSE.} %Notice that the ``Box-Cox biased'' base forecasts carry a higher bias compared to the ``log biased'' base forecasts.
-Even for these MinT reconciliation of bias adjusted base forecasts generates very accurate forecasts, almost as accurate as the forecasts that come from the less biased log transformation.
-
-In contrast to the results from using Method-1 for bias adjusting before reconciliation, using Method-2 has an adverse effect on the forecast accuracy of the reconciled forecasts.
-In this case the reconciled unbiased forecasts {\color{blue}leads to a significantly worse RMATE and RMTSE compared to base forecasts.}.
-This sends the warning that implementing inappropriate bias adjustment, in this case using an additive rather than a multiplicative factor, will hinder forecast accuracy and extra care must be taken in this bias adjustment procedure.
+{\color{blue}There are improvements over the biased base forecasts OLS returns the best results for RMATE while MinT returns the best results for RMTSE.} In contrast to the results from using Method-1 for bias adjusting before reconciliation, using Method-2 has an adverse effect on the forecast accuracy of the reconciled forecasts.
+In this case the reconciled unbiased forecasts {\color{blue}leads to a significantly worse RMATE and RMTSE compared to base forecasts.} This sends the warning that implementing inappropriate bias adjustment, in this case using an additive rather than a multiplicative factor, will hinder forecast accuracy and extra care must be taken in this bias adjustment procedure.
 
@@
 	\item Choose an objective, either
-	\begin{enumerate}
+	\begin{enumerate}[a.]
 		\item To guarantee that reconciled forecasts improve upon base forecasts.
@@
     \item Select a ${\bm W}$ to use in loss function $L^2_{\bm W}$ that is well suited to the empirical problem.  For objective (a) our results also apply to any monotonic function of $L^2_{\bm W}$.
-    \item Select a reconciliation method.  For objective:
-    \begin{enumerate}
-    	\item This should be ${\bm G}=({\bm S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}$. The dependence in forecast errors is not relevant.
-    	\item This should be ${\bm G}=({\bm S}'\bm{\Sigma}^{-1}\bm{S})^{-1}\bm{S}'\bm{\Sigma}^{-1}$. The choice of ${\bm W}$ is not relevant.
-    \end{enumerate}
+    \item Select a reconciliation method.  
+    \begin{itemize}
+    	\item For objective (a) this should be ${\bm G}=({\bm S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}$. The dependence in forecast errors is not relevant.
+    	\item For objective (a) this should be ${\bm G}=({\bm S}'\bm{\Sigma}^{-1}\bm{S})^{-1}\bm{S}'\bm{\Sigma}^{-1}$. The choice of ${\bm W}$ is not relevant.
+    \end{itemize}
 \end{enumerate}}

### 2020-02-04 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
NystrupEtAl2020 corrected

@@
 Forecast reconciliation has mostly been formulated using a regression model {\color{blue} that admits a generalised least squares (GLS) solution}, see \citet{Hyndman2011} and \citet{WicEtAl2019} for examples.
-{\color{blue} Alternatively, \cite{VanErven2015a} and \cite{NysEtAl2019} arrive at a GLS solution by formulating reconciliation as an optimisation problem}.
+{\color{blue} Alternatively, \cite{VanErven2015a} and \cite{NysEtAl2020} arrive at a GLS solution by formulating reconciliation as an optimisation problem}.
 The regression setup can be counter-intuitive since a vector comprised of forecasts from different time series models is also assumed to be the dependent variable in a regression model.

### 2020-02-06 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Minor wording improvements

@@
 Second, {\color{blue} we provide a new proof that reconciled forecasts dominate base forecasts, for a certain class of loss functions.
-The projection that achieves this depends on the weights used in the loss function but not on the dependence in forecast errors.}  Futhermore, unlike {\color{blue} proofs of similar results by} \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general.
+The projection that achieves this depends on the weights used in the loss function but not on the dependence in forecast errors.}  Furthermore, unlike {\color{blue} proofs of similar results by} \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general.
 {\color{blue} Third, we show that when it comes to a different objective, namely minimising the expected loss, the optimal projection depends only on the covariance of the forecast errors, and not the weights used in the loss function.
@@
 We call these \emph{base forecasts} and denote them as $\hat{\bm{y}}_{t+h|t}$.
-In the sequel, this subscript will be dropped at times for ease of exposition.
+We will sometimes drop this subscript for ease of exposition.
 In the most general terms, reconciliation can be defined as follows.
@@
 All reconciliation methods that we are aware of consider a linear mapping for $\psi$, which involves pre-multiplying base forecasts by an $n\times n$ matrix that has $\mathfrak{s}$ as its image.
-One way to achieve this is with a matrix $\bm{S}\bm{G}$, where $\bm{G}$ is an $m\times n$ matrix (some authors use $\bm{P}$ in place of $\bm{G}$).
+One way to achieve this is with a matrix $\bm{S}\bm{G}$, where $\bm{G}$ is an $m\times n$ matrix (in some papers, $\bm{P}$ is used in place of $\bm{G}$).
 This facilitates an interpretation of reconciliation as a two-step process.
@@
 We begin by considering the special case of an orthogonal projection whereby $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$.
-This is equivalent to so called OLS reconciliation as introduced by \citet{Hyndman2011}.
+This is equivalent to so-called OLS reconciliation as introduced by \citet{Hyndman2011}.
 We refrain from any discussion of regression models focusing instead on geometric interpretations.
@@
 For example in our tourism application in Section~\ref{sec:EmpStudy} we will consider weighting forecast errors by average tourism expenditure in each region.}\footnote{Similar consideration are made in the \cite{KouAth2019_Intermittent} discussion paper, and also are taken into account for the loss functions used in the M5 forecasting competition (see https://mofc.unic.ac.cy/m5-competition).}  An even more sophisticated understanding may take {\color{blue}linear combinations} of series into account.
-All of these considerations lead towards {\color{blue} a loss function $L_{\bm W}(\bm{y}_{t+h},\tilde{\bm{y}}_{t+h|t})=||{\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t}}||_{\bm{W}}$ where $||\bm{v}||_{\bm{W}}=\bm{v}'\bm{W}\bm{v}$, and $\bm{W}$ is a symmetric matrix assumed to be invertible.
+All of these considerations lead towards {\color{blue} a loss function $L_{\bm{W}}(\bm{y}_{t+h},\tilde{\bm{y}}_{t+h|t})=||{\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t}}||_{\bm{W}}$ where $||\bm{v}||_{\bm{W}}=\bm{v}'\bm{W}\bm{v}$, and $\bm{W}$ is a symmetric matrix assumed to be invertible.
 The geometry defined by the norm $||.||_{\bm{W}}$, will be referred to as the generalised Euclidean geometry with respect to $\bm{W}$.
@@
 \citet{WicEtAl2019} and \citet{VanErven2015a} both prove special cases of this result, the former in the case where $\bm{W}$ is the inverse of the forecast error covariance and the latter in the case where $\bm{W}$ is diagonal.
-Note here that we rely here on the Generalised Pythagorean Theorem (which involves an equality).
+Note that we rely here on the Generalised Pythagorean Theorem (which involves an equality).
 In contrast, \citet{WicEtAl2019} follow \citet{VanErven2015a} in stating their result in terms of the Generalised Pythagorean Inequality.
@@
 This was to minimise the} trace of the forecast error covariance matrix of reconciled forecasts, i.e,
-
 {\color{blue}
@@
 \label{eq:MinTObj}
-\underset{\bm{G}}{\min}\,\textrm{tr}(E\left[(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'\right])\,.
+\underset{\bm{G}}{\min}\,\textrm{tr}(E\left[(\bm{y}-\bm{S}\bm{G}\hat{\bm{y}})(\bm{y}-\bm{S}\bm{G}\hat{\bm{y}})'\right])\,.
 \end{equation}
@@
 The solution is the oblique projection {\color{blue} $\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}$}.
-{\color{blue} While MinT is used here to refer to the case where $\bm{\Sigma}$ is known, in practice,} it is unknown.
+{\color{blue} While MinT is used here to refer to the case where $\bm{\Sigma}$ is known, in practice} it is unknown.
 It can be estimated using in-sample errors, {\color{blue} with some specific estimators found in \cite{WicEtAl2019} and also \cite{NysEtAl2020}.}
@@
   \end{subfigure}
-  \caption{A schematic represention of orthogonal and oblique reconciliations.
+  \caption{A schematic representation of orthogonal and oblique reconciliations.
 The orange points in (a) represent in-sample errors and $\bm{R}$ shows the most likely direction of deviations from the coherent subspace $\mathfrak{s}$.
@@
 
-We now make explicit the connection between MinT and a loss function based on the squared Euclidean distance $L^2(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|^2$ before generalising to $L^2_{\bm W}(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|^2_{\bm W}$.
-\footnote{Since taking the square is monotonic over the range of $L$ and $L_{\bm W}$, the properties in Theorem~\ref{th:distred} and Theorem~\ref{th:gdistred} also apply to $L^2$ and $L^2_{\bm W}$.}  By the properties of the trace operator, the objective function in Eq.~\eqref{eq:MinTObj} can be rearranged as
-
+We now make explicit the connection between MinT and a loss function based on the squared Euclidean distance $L^2(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|^2$ before generalising to $L^2_{\bm{W}}(\bm{y},\tilde{\bm{y}})=\|\bm{y}-\tilde{\bm{y}}\|^2_{\bm{W}}$.
+\footnote{Since taking the square is monotonic over the range of $L$ and $L_{\bm{W}}$, the properties in Theorem~\ref{th:distred} and Theorem~\ref{th:gdistred} also apply to $L^2$ and $L^2_{\bm{W}}$.}  By the properties of the trace operator, the objective function in Eq.~\eqref{eq:MinTObj} can be rearranged as
 \begin{align*}
 \label{eq:MinTObj}
-\textrm{tr}(E\left[(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'\right])&=\textrm{tr}(E\left[(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})\right])\\
-%&=E\left[(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})\right]\\
-&=E\left[\|\bm{y}-{\bm S}{\bm G}\hat{\bm{y}}\|^2\right]\\
+\textrm{tr}(E\left[(\bm{y}-\bm{S}\bm{G}\hat{\bm{y}})(\bm{y}-\bm{S}\bm{G}\hat{\bm{y}})'\right])&=\textrm{tr}(E\left[(\bm{y}-\bm{S}\bm{G}\hat{\bm{y}})'(\bm{y}-\bm{S}\bm{G}\hat{\bm{y}})\right])\\
+%&=E\left[(\bm{y}-\bm{S}\bm{G}\hat{\bm{y}})'(\bm{y}-\bm{S}\bm{G}\hat{\bm{y}})\right]\\
+&=E\left[\|\bm{y}-\bm{S}\bm{G}\hat{\bm{y}}\|^2\right]\\
 &=E\left[L^2(\bm{y},\tilde{\bm{y}})\right]
@@
 Note that trace minimisation implies a different optimality property to the distance reducing property described in Section~\ref{sec:orthogonal}.
-Theorem~\ref{th:distred} implies optimality in the sense that reconcilied forecasts always improve on base forecasts.
+Theorem~\ref{th:distred} implies optimality in the sense that reconciled forecasts always improve on base forecasts.
 For MinT, optimality refers to minimising the loss function \textit{in expectation}.
 
-Suppose the optimisation problem is generalised to a loss function based on some ${\bm W}$
-
+Suppose the optimisation problem is generalised to a loss function based on some $\bm{W}$:
 {\color{blue}
@@
 	\label{eq:GMinTObj}
-	\underset{\bm{G}}{\min}\,(E\left[(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})'\bm{W}(\bm{y}-{\bm S}{\bm G}\hat{\bm{y}})\right])\,.
+	\underset{\bm{G}}{\min}\,(E\left[(\bm{y}-\bm{S}\bm{G}\hat{\bm{y}})'\bm{W}(\bm{y}-\bm{S}\bm{G}\hat{\bm{y}})\right])\,.
 	\end{equation}
@@
 The following theorem proves that the solution to this optimisation problem does not depend of the choice of $\bm{W}$ used in the loss function.
-
 \begin{theo}[Expected loss minimisation and MinT]\label{th:gmint}
@@
 
-The implication of this result is that irrespective of the ${\bm W}$ used in the loss function, an oblique projection based on the forecast error covariance will always minimise {\em expected} loss (where loss is based on squared generalised Euclidean distance).
+The implication of this result is that irrespective of the $\bm{W}$ used in the loss function, an oblique projection based on the forecast error covariance will always minimise {\em expected} loss (where loss is based on squared generalised Euclidean distance).
 From the point of view of minimising expected loss, for loss defined in Eq.~\eqref{eq:GMinTObj}, considerations about sensible weights for an error metric are not relevant.
@@
 Theorem~\ref{th:gdistred} provides a guarantee to improve upon base forecasts with respect to the loss function based on $\bm{W}$.
-This is an orthogonal projection in the space transformed after pre-multiplying by ${\bm W}^{-1/2}$.
+This is an orthogonal projection in the space transformed after pre-multiplying by $\bm{W}^{-1/2}$.
 %
@@
 %\begin{equation*}
-%\bm{G}^{\text{GMinT}}=\left(\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\bm{S}\right)^{-1}\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\,.
+%\bm{G}^{\text{GMinT}}=\left(\bm{S}'\bm{W}^{-1/2}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1/2}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\,.
 %\end{equation*}
@@
 This may suggest a loss function that places a weight of one on forecast errors of the overall aggregate and a weight of zero on errors in all other series.
-In this case, $\bm{S}'{\bm W}^{-1/2}\bm{\Sigma}^{-1}{\bm W}^{-1/2}\bm{S}$ is rank deficient and cannot be inverted.
+In this case, $\bm{S}'\bm{W}^{-1/2}\bm{\Sigma}^{-1}\bm{W}^{-1/2}\bm{S}$ is rank deficient and cannot be inverted.
 To be able to accrue the benefits of reconciliation by `borrowing strength' from other series, the loss function must penalise errors in those series.
@@
 By using average spend per region as weights, the error metric (and transformed space associated with this metric) can be interpreted in terms of revenue, measured in dollars, rather than raw tourist numbers.
-We refer to the reconciliation method that uses these weights as `Spend-WLS' and the loss function based on these weights as `Spend-WSE'.
+We refer to the reconciliation method that uses these weights as `Spend-WLS' and the loss function based on these weights as `Spend-WSE'.%
 }
@@
 For Structural-WSE, a Friedman test confirms that the average loss for MinT is significantly lower when tested against every other method\footnote{{\color{blue} While differences are not significant for the other loss functions, the scale of the aggregate series leads to a large variance in loss, reducing the power of the test.
-Strutural-WSE stablises this effect.}}.
+Strutural-WSE stabilises this effect.}}.
 }
@@
 In order to avoid extreme and volatile transformations we restrict $\lambda \in (-0.5,2)$.
-As zero observations exist in some of the bottom-level series, before transforming we add a constant (more specifically $1$) to each series.
+As zero observations exist in some of the bottom-level series, before transforming we add a constant (specifically $1$) to each series.
 This overcomes the challenge of undefined transformed values for zero observations when we specifically implement the log transformation or when $\lambda$ is selected to be zero by the ``Guerrero'' method.
@@
 This testing approach does not impose any distributional assumptions and does not require multiple pairwise testing between forecasts, which would distort the outcome of the tests.
-We use the implementation of the tests available in the \verb"tsutils " \citep{tsutils} package for R.}
+We use the implementation of the tests available in the \verb"tsutils" \citep{tsutils} package for R.}
 
@@
 
-Defining concepts such as coherence and reconciliation in geometric terms provides new insights into hierarchical forecasting methods. {\color{blue} We recommend the following steps for practitioners
+Defining concepts such as coherence and reconciliation in geometric terms provides new insights into hierarchical forecasting methods. {\color{blue} We recommend the following steps for practitioners.
 \begin{enumerate}
@@
 	\end{enumerate}
-    \item Select a ${\bm W}$ to use in loss function $L^2_{\bm W}$ that is well suited to the empirical problem.  For objective (a) our results also apply to any monotonic function of $L^2_{\bm W}$.
+    \item Select a $\bm{W}$ to use in loss function $L^2_{\bm{W}}$ that is well suited to the empirical problem.  For objective (a) our results also apply to any monotonic function of $L^2_{\bm{W}}$.
     \item Select a reconciliation method.
     \begin{itemize}
-    	\item For objective (a) this should be ${\bm G}=({\bm S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}$. The dependence in forecast errors is not relevant.
-    	\item For objective (a) this should be ${\bm G}=({\bm S}'\bm{\Sigma}^{-1}\bm{S})^{-1}\bm{S}'\bm{\Sigma}^{-1}$. The choice of ${\bm W}$ is not relevant.
+    	\item For objective (a) this should be $\bm{G}=(\bm{S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}$. The dependencies between forecast errors is not relevant.
+    	\item For objective (a) this should be $\bm{G}=(\bm{S}'\bm{\Sigma}^{-1}\bm{S})^{-1}\bm{S}'\bm{\Sigma}^{-1}$. The choice of $\bm{W}$ is not relevant.
     \end{itemize}

### 2020-02-07 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
Conclusion correction
Minor Puwasala changes
Blind and submission

@@
 % NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{1}
+\newcommand{\blind}{0}
 
@@
   \title{\bf Forecast reconciliation: A geometric view with new insights on bias correction}
-  \author{Anastasios Panagiotelis\\
+  \author{Anastasios Panagiotelis\thanks{Corresponding Author.
+The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.
+We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
     Department of Econometrics and Business Statistics,\\
@@
     Email: Anastasios.Panagiotelis@monash.edu \\[0.6cm]
+    George Athanasopoulos\\
+    Department of Econometrics and Business Statistics,\\
+    Monash University, VIC 3145, Australia.\\
+    Email: George.Athanasopoulos@monash.edu \\[0.6cm]
     Puwasala Gamakumara\\
@@
     Email: Puwasala.Gamakumara@monash.edu \\[0.6cm]
-    George Athanasopoulos\thanks{Corresponding Author.
-The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.
-We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
-    Department of Econometrics and Business Statistics,\\
-    Monash University, VIC 3145, Australia.\\
-    Email: George.Athanasopoulos@monash.edu \\[0.6cm]
     Rob J Hyndman\\
@@
 
-The following theorem proves that the solution to this optimisation problem does not depend of the choice of $\bm{W}$ used in the loss function.
+The following theorem proves that the solution to this optimisation problem does not depend on the choice of $\bm{W}$ used in the loss function.
 \begin{theo}[Expected loss minimisation and MinT]\label{th:gmint}
@@
     	\item For objective (a) this should be $\bm{G}=(\bm{S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}$. The dependencies between forecast errors is not relevant.
-    	\item For objective (a) this should be $\bm{G}=(\bm{S}'\bm{\Sigma}^{-1}\bm{S})^{-1}\bm{S}'\bm{\Sigma}^{-1}$. The choice of $\bm{W}$ is not relevant.
+    	\item For objective (b) this should be $\bm{G}=(\bm{S}'\bm{\Sigma}^{-1}\bm{S})^{-1}\bm{S}'\bm{\Sigma}^{-1}$. The choice of $\bm{W}$ is not relevant.
     \end{itemize}

### 2020-02-07 R1/Letter.tex
Changed date
Blind and submission

@@
 \begin{document}
- \begin{letter}{To: Pierre Pinson\\
- 	Editor, International Journal of Forecasting\\
- 	DTU Elektro\\
- 	348, {\O}rsteds Pl., \\
- 	2800 Kongens Lyngby, Denmark}
+ \begin{letter}{To: Michael McCracken\\
+ 	Handling Editor, International Journal of Forecasting
+    }
     From: George Athanasopoulos\\
@@
 
- \opening{ March 12, 2018\\ \\Dear Professor Pinson,}
+ \opening{\today\ \\Dear Mike,}
 %\textbf{RE: Revision for Computational and Graphical Statistics by Tan Ban Kheng, Anastasios
@@
 
-Please find attached a revised manuscript for ``Forecast reconciliation: a geometric view with new insights on bias correction" by Anastasios Panagiotelis, Puwasala Gamakumara, George Athanasopoulos and Rob Hyndman for your consideration for publication in International Journal of Forecasting.
+Please find attached a revised manuscript for ``Forecast reconciliation: a geometric view with new insights on bias correction" by Anastasios Panagiotelis, George Athanasopoulos, Puwasala Gamakumara, and Rob Hyndman for your consideration for publication in International Journal of Forecasting.
 We are very excited to have been given the opportunity to revise and resubmit.
@@
 We also prove a new result that MinT minimises expected loss for loss functions based on squared generalised Euclidean distance.
-This result is demonstrated in an expanded empirical application in section 5.2 that includes a wider range of loss functions.
+This result is demonstrated in an expanded empirical application in Section 5.2 that includes a wider range of loss functions.
 	\item We have greatly expanded the empirical study of Section 5.3 including more measures of forecast accuracy (including one specifically measuring bias).

### 2020-02-11 R1/Response.tex
Re submission completed

@@
 Our recommendations to practitioners are now summarised in an expanded conclusion.
-Some insights into how new methods should (or should not) be developed by researchers are also provided in the conclusion and also in the just before Section 4.1.
+Some insights into how new methods should (or should not) be developed by researchers are also provided in the conclusion and also just before Section 4.1.
 Furthermore, we note that Spend-WLS is a new reconciliation method (albeit somewhat context specific).

### 2020-08-13 SourceFiles/Figs/Schem_3D.tex
SourceFilesFor IJF

--- 2019-04-26 Hierarchical-forecast-reconciliation/Figs/Schem_3D.tex
@@
-% Created by tikzDevice version 0.12 on 2019-04-26 11:42:01
+% Created by tikzDevice version 0.12.3 on 2019-09-02 13:04:58
 % !TEX encoding = UTF-8 Unicode
@@
 
-\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at (277.57,258.86) {{$\bar{\mu}$}};
-
-\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (227.47,309.94) {{\Huge ${\color{blue} s\circ g}$}};
+\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  2.00] at (277.57,258.86) {{$\mu^{*}$}};
 

### 2020-08-13 SourceFiles/HierarchicalForecastReconciliation.tex
SourceFilesFor IJF

--- 2020-02-07 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex
@@
 \title{\bf Forecast reconciliation: A geometric view with new insights on bias correction}
-  \author{Anastasios Panagiotelis\thanks{Corresponding Author.
-The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.
-We also thank Professor Mervyn Silvapulle for valuable comments.}\hspace{.2cm}\\
+  \author{Anastasios Panagiotelis\\
     Department of Econometrics and Business Statistics,\\
@@
     Email: Anastasios.Panagiotelis@monash.edu \\[0.6cm]
-    George Athanasopoulos\\
+    George Athanasopoulos\thanks{Corresponding Author.
+The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.
+We also thank Professor Mervyn Silvapulle for valuable
     Department of Econometrics and Business Statistics,\\
@@
 First, reconciliation via projection is guaranteed to improve forecast accuracy with respect to a class of loss functions based on a generalised distance metric.
-{\color{blue} Second, the MinT method minimises expected loss for this same class of loss functions.}  Third, the geometric interpretation provides a new proof that forecast reconciliation using projections results in unbiased forecasts provided the initial base forecasts are also unbiased.
+Second, the MinT method minimises expected loss for this same class of loss functions.
+Third, the geometric interpretation provides a new proof that forecast reconciliation using projections results in unbiased forecasts provided the initial base forecasts are also unbiased.
 Approaches for dealing with biased base forecasts are proposed.
-An extensive empirical study on Australian tourism flows {\color{blue} demonstrates the theoretical results of the paper and shows that bias correction prior to reconciliation} outperforms alternatives that only bias-correct or only reconcile forecasts.
+An extensive empirical study on Australian tourism flows demonstrates the theoretical results of the paper and shows that bias correction prior to reconciliation outperforms alternatives that only bias-correct or only reconcile forecasts.
 
@@
 
-%  \noindent%
-%  {\it Keywords:} Forecast Reconciliation, Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
-%  \vfill
+\noindent%
+  {\it Keywords:} Forecast Reconciliation, Projections, Elliptical Distributions, Scoring Rules, High-dimensional Time Series.
+  \vfill
 
@@
 Of particular prominence have been \emph{forecast reconciliation} methods involving two steps: first separate forecasts are produced for all series, then these are adjusted to ensure coherence with aggregation constraints.
-Forecast reconciliation has mostly been formulated using a regression model {\color{blue} that admits a generalised least squares (GLS) solution}, see \citet{Hyndman2011} and \citet{WicEtAl2019} for examples.
-{\color{blue} Alternatively, \cite{VanErven2015a} and \cite{NysEtAl2020} arrive at a GLS solution by formulating reconciliation as an optimisation problem}.
+Forecast reconciliation has mostly been formulated using a regression model that admits a generalised least squares (GLS) solution, see \citet{Hyndman2011} and \citet{WicEtAl2019} for examples.
+Alternatively, \cite{VanErven2015a} and \cite{NysEtAl2020} arrive at a GLS solution by formulating reconciliation as an optimisation problem.
 The regression setup can be counter-intuitive since a vector comprised of forecasts from different time series models is also assumed to be the dependent variable in a regression model.
 In this paper, we eschew a regression interpretation in favour of a novel, geometric understanding of forecast reconciliation.
-This allows us to develop novel proofs and a clearer understanding of the interplay between {\color{blue} objective functions, loss functions, }forecast bias and reconciliation methods.
+This allows us to develop novel proofs and a clearer understanding of the interplay between objective functions, loss functions, forecast bias and reconciliation methods.
 
@@
 We believe that this is clearer and more intuitive than explanations based on regression modelling.
-In addition to casting existing results in a new light, the geometric interpretation also allows us to derive {\color{blue}four} new important results.
+In addition to casting existing results in a new light, the geometric interpretation also allows us to derive four new important results.
 
@@
 As a result forecast reconciliation can be applied in contexts where there are no clear candidates of \emph{bottom-level} series, an insight that is not apparent when the problem is viewed through the lens of regression modelling.
-Second, {\color{blue} we provide a new proof that reconciled forecasts dominate base forecasts, for a certain class of loss functions.
-The projection that achieves this depends on the weights used in the loss function but not on the dependence in forecast errors.}  Furthermore, unlike {\color{blue} proofs of similar results by} \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general.
-{\color{blue} Third, we show that when it comes to a different objective, namely minimising the expected loss, the optimal projection depends only on the covariance of the forecast errors, and not the weights used in the loss function.
+Second, we provide a new proof that reconciled forecasts dominate base forecasts, for a certain class of loss functions.
+The projection that achieves this depends on the weights used in the loss function but not on the dependence in forecast errors.
+Furthermore, unlike proofs of similar results by \citet{VanErven2015a} and \citet{WicEtAl2019}, our proof does not require an assumption about convexity that may not hold in general.
+Third, we show that when it comes to a different objective, namely minimising the expected loss, the optimal projection depends only on the covariance of the forecast errors, and not the weights used in the loss function.
 In this case of equal weights, this property is a direct consequence of the trace minimising property already established by \cite{WicEtAl2019}.
 We now prove that this result also applies to a more general class of loss functions.
-Fourth}, we provide a new proof that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased.
+Fourth, we provide a new proof that reconciliation using certain projection matrices guarantees unbiased reconciled forecasts provided the base forecasts are also unbiased.
 A natural question that arises is what to do in the case of biased reconciled forecasts.
@@
 In Section \ref{sec:EmpStudy} we conduct an extensive empirical application to domestic tourism flows in Australia with two objectives; first to demonstrate the theorems discussed in Section~\ref{sec:Reconciliation}, and second to evaluate the methods for bias correction discussed in Section~\ref{sec:BiasInRecon}.
-Section~\ref{sec:conclusions} concludes with some discussion, {\color{blue} practical recommendations} and thoughts on the future research directions {\color{blue}for} forecast reconciliation.
+Section~\ref{sec:conclusions} concludes with some discussion, practical recommendations and thoughts on the future research directions for forecast reconciliation.
 
@@
 Much of the early literature that dealt with the problem of forecasting hierarchical time series \citep[see][and references therein]{Gross1990} produced forecasts at a single level of the hierarchy in the first stage.
-Subsequently forecasts for all series were recovered through {\color{blue} either} aggregation, disaggregation according to historical or forecast proportions, or some combination of both.
+Subsequently forecasts for all series were recovered through either aggregation, disaggregation according to historical or forecast proportions, or some combination of both.
 Consequently, incoherent forecasts were not a challenge in these earlier papers.
@@
 Second, modelling higher level series often identifies features such as trend and seasonality that cannot be detected in noisy disaggregate data.
-However, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.\footnote{There are some special cases of using simple approaches such as na\"{i}ve, which extrapolate the coherent nature of the data to the forecasts.} {\color{blue}While the problem of incoherent forecasts can be addressed by some multivariate approaches, including state space models, these can not always be generalised to models with more complicated features or scaled up to high-dimensional problems.}  Instead, the solution is to make an adjustment that ensures coherence, a process known as \emph{forecast reconciliation}
+However, when forecasts are produced independently at all levels, forecasts are likely to be incoherent.\footnote{There are some special cases of using simple approaches such as na\"{i}ve, which extrapolate the coherent nature of the data to the forecasts.} While the problem of incoherent forecasts can be addressed by some multivariate approaches, including state space models, these can not always be generalised to models with more complicated features or scaled up to high-dimensional problems.
+Instead, the solution is to make an adjustment that ensures coherence, a process known as \emph{forecast reconciliation}
 
@@
 We refrain from any discussion of regression models focusing instead on geometric interpretations.
-{\color{blue} Nonetheless,} the connection between OLS and orthogonal projection should be clear; in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection onto the span of the regressors.
+Nonetheless, the connection between OLS and orthogonal projection should be clear; in the context of regression modelling predicted values from OLS are obtained via an orthogonal projection onto the span of the regressors.
 
@@
 A property of an orthogonal projection is that the distance between $\hat{\bm{y}}_{t+h|t}$ and $\tilde{\bm{y}}_{t+h|t}$ is minimal over any possible $\tilde{\bm{y}}_{t+h|t}\in\mathfrak{s}$.
-In this sense reconciliation via orthogonal projection {\color{blue} $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$} leads to the smallest possible adjustments of the base forecasts.
-{\color{blue} Alternatively, Euclidean distance can be interpreted as a loss function $L(\bm{u},\bm{v})=\|\bm{u}-\bm{v}\|$ where $\|.\|$ denotes the L2 norm, in which case an orthogonal projection solves the optimisation problem $\underset{\bm{G}}{\min}\,L(\hat{\bm{y}}_{t+h|t},\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t})$.
-This is a special case of the optimisation problem considered by \cite{NysEtAl2020}, the more general case will be covered in the next section.}
-
-The {\color{blue} aim of the second property is to guarantee that} reconciled forecasts should always be closer to the target than base forecasts {\color{blue} and is related to the difference in loss functions $L({\bm{y}}_{t+h},\hat{\bm{y}}_{t+h|t})-L({\bm{y}}_{t+h},\tilde{\bm{y}}_{t+h|t})$.
-This is expressed as a minimax optimisation by \cite{VanErven2015a} and was also} touched upon in Section 2.3 of \citet{WicEtAl2019}{\color{blue}, albeit in both cases for a slightly different loss function}.
-Here we provide a new explicit proof of {\color{blue} this distance reducing property}.
-We do so first in the case {\color{blue} of the loss function defined here in terms of Euclidean distance} where the geometric intuition of the proof is clear and then generalise the result to {\color{blue} more general loss functions} Section~\ref{sec:oblique}
+In this sense reconciliation via orthogonal projection $\bm{G}=(\bm{S}'\bm{S})^{-1}\bm{S}'$ leads to the smallest possible adjustments of the base forecasts.
+Alternatively, Euclidean distance can be interpreted as a loss function $L(\bm{u},\bm{v})=\|\bm{u}-\bm{v}\|$ where $\|.\|$ denotes the L2 norm, in which case an orthogonal projection solves the optimisation problem $\underset{\bm{G}}{\min}\,L(\hat{\bm{y}}_{t+h|t},\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t})$.
+This is a special case of the optimisation problem considered by \cite{NysEtAl2020}, the more general case will be covered in the next section.
+
+The aim of the second property is to guarantee that reconciled forecasts should always be closer to the target than base forecasts and is related to the difference in loss functions $L({\bm{y}}_{t+h},\hat{\bm{y}}_{t+h|t})-L({\bm{y}}_{t+h},\tilde{\bm{y}}_{t+h|t})$.
+This is expressed as a minimax optimisation by \cite{VanErven2015a} and was also touched upon in Section 2.3 of \citet{WicEtAl2019}, albeit in both cases for a slightly different loss function.
+Here we provide a new explicit proof of this distance reducing property.
+We do so first in the case of the loss function defined here in terms of Euclidean distance where the geometric intuition of the proof is clear and then generalise the result to more general loss functions Section~\ref{sec:oblique}
 
@@
 In this triangle, the line between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.
-Therefore reconciliation is guaranteed to reduce {\color{blue} a loss function based on distance, or indeed any monotonic function of distance.}
+Therefore reconciliation is guaranteed to reduce a loss function based on distance, or indeed any monotonic function of distance.
 
@@
 First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.
-In particular, this measure is the sum of squared forecast errors of \emph{all} variables in the hierarchy {\color{blue}(or any monotonic function thereof)}.
+In particular, this measure is the sum of squared forecast errors of \emph{all} variables in the hierarchy (or any monotonic function thereof).
 Second, although an orthogonal projection is guaranteed to improve on base forecasts, it is not necessarily the projection that leads to the greatest improvement in forecast accuracy in expectation.
 Therefore, referring to OLS reconciliation as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections.
-{\color{blue} We now turn our attention to the way oblique projections can address both of these shortcomings.}
+We now turn our attention to the way oblique projections can address both of these shortcomings.
 
@@
 
-One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of {\color{blue} a loss function based on Euclidean distance that involves \emph{all} variables in the hierarchy.} A clear shortcoming of this measure of forecast accuracy is that forecast errors in all series should not necessarily be treated equally.
+One justification for using an orthogonal projection is that it leads to improved forecast accuracy in terms of a loss function based on Euclidean distance that involves \emph{all} variables in the hierarchy.
+A clear shortcoming of this measure of forecast accuracy is that forecast errors in all series should not necessarily be treated equally.
 For example, in hierarchies, top-level series tend to have a much larger scale than bottom-level series.
-{\color{blue} Alternatively, the context of the forecast problem itself may suggest a loss function that weights series differently.
-For example in our tourism application in Section~\ref{sec:EmpStudy} we will consider weighting forecast errors by average tourism expenditure in each region.}\footnote{Similar consideration are made in the \cite{KouAth2019_Intermittent} discussion paper, and also are taken into account for the loss functions used in the M5 forecasting competition (see https://mofc.unic.ac.cy/m5-competition).}  An even more sophisticated understanding may take {\color{blue}linear combinations} of series into account.
-All of these considerations lead towards {\color{blue} a loss function $L_{\bm{W}}(\bm{y}_{t+h},\tilde{\bm{y}}_{t+h|t})=||{\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t}}||_{\bm{W}}$ where $||\bm{v}||_{\bm{W}}=\bm{v}'\bm{W}\bm{v}$, and $\bm{W}$ is a symmetric matrix assumed to be invertible.
+Alternatively, the context of the forecast problem itself may suggest a loss function that weights series differently.
+For example in our tourism application in Section~\ref{sec:EmpStudy} we will consider weighting forecast errors by average tourism expenditure in each region.\footnote{Similar consideration are made in the \cite{AthKou2020} discussion paper, and also are taken into account for the loss functions used in the M5 forecasting competition (see https://mofc.unic.ac.cy/m5-competition).}  An even more sophisticated understanding may take linear combinations of series into account.
+All of these considerations lead towards a loss function $L_{\bm{W}}(\bm{y}_{t+h},\tilde{\bm{y}}_{t+h|t})=||{\bm{y}_{t+h}-\tilde{\bm{y}}_{t+h|t}}||_{\bm{W}}$ where $||\bm{v}||_{\bm{W}}=\bm{v}'\bm{W}\bm{v}$, and $\bm{W}$ is a symmetric matrix assumed to be invertible.
 The geometry defined by the norm $||.||_{\bm{W}}$, will be referred to as the generalised Euclidean geometry with respect to $\bm{W}$.
-}
-
-One way to understand the generalised Euclidean geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{1/2}$, {\color{blue} where $\bm{W}=(\bm{W}^{1/2})'\bm{W}^{1/2}$}.
+
+One way to understand the generalised Euclidean geometry is that it is the same as Euclidean geometry when all vectors are first transformed by pre-multiplying by $\bm{W}^{1/2}$, where $\bm{W}=(\bm{W}^{1/2})'\bm{W}^{1/2}$.
 This leads to a transformed $\bm{S}$ matrix $\bm{S}^*=\bm{W}^{1/2}\bm{S}$ and transformed $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ vectors $\hat{\bm{y}}^*=\bm{W}^{1/2}\hat{\bm{y}}$ and $\tilde{\bm{y}}^*=\bm{W}^{1/2}\tilde{\bm{y}}$.
-{\color{blue} A projection of the form $\tilde{\bm{y}}=\bm{S}(\bm{S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}\hat{\bm{y}}$, is an} orthogonal projection in the transformed space since
+A projection of the form $\tilde{\bm{y}}=\bm{S}(\bm{S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}\hat{\bm{y}}$, is an orthogonal projection in the transformed space since
 \begin{align*}
@@
     & = \bm{W}^{1/2}\bm{S}(\bm{S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}\hat{\bm{y}} \\
-    &{\color{blue} = \bm{W}^{1/2}\bm{S}((\bm{W}^{1/2}\bm{S})'\bm{W}^{1/2}\bm{S})^{-1}(\bm{W}^{1/2}\bm{S})'\bm{W}^{1/2}\hat{\bm{y}}}\\
+    & = \bm{W}^{1/2}\bm{S}((\bm{W}^{1/2}\bm{S})'\bm{W}^{1/2}\bm{S})^{-1}(\bm{W}^{1/2}\bm{S})'\bm{W}^{1/2}\hat{\bm{y}}\\
     & = \bm{S}^*(\bm{S}^{*'}\bm{S}^*)^{-1}\bm{S}^{*'}\hat{\bm{y}^*}.
@@
 
-The implication of Theorem~\ref{th:gdistred} is that if the loss function is a monotonic function of $L_{\bm{W}}$ {\color{blue} with some $\bm{W}$ given a priori} then the projection matrix $\bm{S}(\bm{S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}$ is guaranteed to improve forecast accuracy over base forecasts.
-{\color{blue}  This result does not necessarily involve the covariance of forecast errors unless $\bm{W}$ is explicitly chosen to depend on these covariances.}
+The implication of Theorem~\ref{th:gdistred} is that if the loss function is a monotonic function of $L_{\bm{W}}$ with some $\bm{W}$ given a priori then the projection matrix $\bm{S}(\bm{S}'\bm{W}\bm{S})^{-1}\bm{S}'\bm{W}$ is guaranteed to improve forecast accuracy over base forecasts.
+This result does not necessarily involve the covariance of forecast errors unless $\bm{W}$ is explicitly chosen to depend on these covariances.
 
@@
 The proof we have provided here requires no such assumption, since this may not hold for an arbitrary $\bm{W}$.
-As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is true only for loss {\color{blue}that is a monotonic function of $L_{\bm{\Sigma}^{-1}}$, where $\bm{\Sigma}=E(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'$}.
-If Euclidean distance (or mean squared error) is used {\color{blue} as a loss function}, there will be realisations where the MinT estimator does not improve forecast accuracy relative to base forecasts.
+As such the statement from \citet{WicEtAl2019} that \emph{``MinT reconciled forecasts are at least as good as the incoherent forecasts''} should be qualified --- this is true only for loss that is a monotonic function of $L_{\bm{\Sigma}^{-1}}$, where $\bm{\Sigma}=E(\bm{y}-\hat{\bm{y}})(\bm{y}-\hat{\bm{y}})'$.
+If Euclidean distance (or mean squared error) is used as a loss function, there will be realisations where the MinT estimator does not improve forecast accuracy relative to base forecasts.
 This will be demonstrated using a real data set in the empirical study in Section~\ref{sec:comparebase}.
@@
 
-{\color{blue}The discussion so far provides a roadmap, such that for a given choice of $\bm{W}$, a projection with distance-reducing properties can be derived}.
-While the MinT method of \citet{WicEtAl2019} {\color{blue} is a special case of such a projection, it was in fact motivated by a different optimality property.
-This was to minimise the} trace of the forecast error covariance matrix of reconciled forecasts, i.e,
-{\color{blue}
+The discussion so far provides a roadmap, such that for a given choice of $\bm{W}$, a projection with distance-reducing properties can be derived.
+While the MinT method of \citet{WicEtAl2019} is a special case of such a projection, it was in fact motivated by a different optimality property.
+This was to minimise the trace of the forecast error covariance matrix of reconciled forecasts, i.e,
+
 \begin{equation}
@@
 \end{equation}
-}
-
-The solution is the oblique projection {\color{blue} $\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}$}.
-{\color{blue} While MinT is used here to refer to the case where $\bm{\Sigma}$ is known, in practice} it is unknown.
-It can be estimated using in-sample errors, {\color{blue} with some specific estimators found in \cite{WicEtAl2019} and also \cite{NysEtAl2020}.}
+
+The solution is the oblique projection $\bm{S}\left(\bm{S}'\bm{\Sigma}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{\Sigma}^{-1}$.
+While MinT is used here to refer to the case where $\bm{\Sigma}$ is known, in practice it is unknown.
+It can be estimated using in-sample errors, with some specific estimators found in \cite{WicEtAl2019} and also \cite{NysEtAl2020}.
 
@@
 
-{\color{blue}
-
 \subsection{Expected loss minimisation and MinT}
@@
 Suppose the optimisation problem is generalised to a loss function based on some $\bm{W}$:
-{\color{blue}
+
 	\begin{equation}
@@
 	\end{equation}
-}
 
@@
 While this statement is correct in the context of Theorem~\ref{th:gdistred}, which is the case considered by \cite{VanErven2015a}, it is not true for the objective described in Eq.~\eqref{eq:GMinTObj}.
-This will be empirically demonstrated in Section~\ref{sec:EmpStudy}.}
+This will be empirically demonstrated in Section~\ref{sec:EmpStudy}.
 
@@
 where $\bm{p} = (p_1,\dots,p_m)'$ is an $m$-dimensional vector consisting a set of proportions used to disaggregate the top-level forecast.
-In this case it can be verified that $\bm{S}\bm{G}$ is idempotent, {\color{blue} i.e.,} $\bm{S}\bm{G}\bm{S}\bm{G}=\bm{S}\bm{G}$ and therefore $\bm{S}\bm{G}$ is a projection matrix.
+In this case it can be verified that $\bm{S}\bm{G}$ is idempotent, i.e., $\bm{S}\bm{G}\bm{S}\bm{G}=\bm{S}\bm{G}$ and therefore $\bm{S}\bm{G}$ is a projection matrix.
 However, the image of this projection is not an $m$-dimensional subspace but a $1$-dimensional subspace.
@@
 Both of these conditions are equivalent to assuming that $\bm{S}\bm{G}$ is a projection matrix (see Section~\ref{app:projection-proof} in Appendix A for a proof).
-{\color{blue}{Despite this connection,}} problems arise when viewing the preservation of unbiasedness through the prism of imposing the constraint $\bm{G}\bm{S}=\bm{I}$.
+Despite this connection, problems arise when viewing the preservation of unbiasedness through the prism of imposing the constraint $\bm{G}\bm{S}=\bm{I}$.
 This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.
@@
 In many cases the method for bias correction will be context specific.
-For instance, in our empirical study in Section~\ref{sec:EmpStudy} we consider a scenario where {\color{blue} data are modelled after} taking either a log transformation or a Box-Cox transformation.
-{\color{blue} Since linear constraints that hold on the original scale do not hold for the transformed series, back-transforming to the original scale is necessary.
-Since this step induces a bias we propose to bias correct after this back-transformation step, but before reconciliation.}  In the well-known case {\color{blue} of the Box-Cox transformation} a number of bias correction methods exist based on Taylor expansions.
+For instance, in our empirical study in Section~\ref{sec:EmpStudy} we consider a scenario where data are modelled after taking either a log transformation or a Box-Cox transformation.
+Since linear constraints that hold on the original scale do not hold for the transformed series, back-transforming to the original scale is necessary.
+Since this step induces a bias we propose to bias correct after this back-transformation step, but before reconciliation.
+In the well-known case of the Box-Cox transformation a number of bias correction methods exist based on Taylor expansions.
 
@@
 Our motivation in this study is twofold.
-First, we demonstrate the implications of Theorems~\ref{th:distred}{\color{blue},~\ref{th:gdistred} and~\ref{th:gmint}} by comparing reconciled and base forecasts.
-In contrast to previous studies, we consider individual periods {\color{blue} as well as} compute averages over a rolling window.
+First, we demonstrate the implications of Theorems~\ref{th:distred},~\ref{th:gdistred} and~\ref{th:gmint} by comparing reconciled and base forecasts.
+In contrast to previous studies, we consider individual periods as well as compute averages over a rolling window.
 Second, we demonstrate how the bias correction methods discussed in the previous section along with the projection-based reconciliation help to improve forecast accuracy.
@@
   \small
-  \includegraphics[width = \textwidth]{Empirical-results/TS-plots/Total_TSplots.pdf}
+  \includegraphics[width = \textwidth]{Figs/Total_TSplots.pdf}
   \caption{Total domestic overnight trips (in logs) for Australia from January 1998 to December 2017.
@@
   \small
-  \includegraphics[width= .95\textwidth]{Empirical-results/TS-plots/States_Zones_Regs_TSplots1.pdf}
+  \includegraphics[width= .95\textwidth]{Figs/States_Zones_Regs_TSplots1.pdf}
   \caption{Time plot of overnight trips for some selected series from different disaggregate levels of the hierarchy.
@@
 
-To demonstrate the implications of Theorem~\ref{th:distred} we consider the improvement of different reconciliation methods over base forecasts {\color{blue} using different loss functions}.
+To demonstrate the implications of Theorem~\ref{th:distred} we consider the improvement of different reconciliation methods over base forecasts using different loss functions.
 For each series the ARIMA model minimising AICc is chosen using the \verb|auto.arima()| function in the \verb|forecast| package.
@@
 
-{\color{blue} For each method we compute three loss functions.  The first is the total squared error (TSE), computed as
+For each method we compute three loss functions.  The first is the total squared error (TSE), computed as
 	\begin{equation}
@@
 We refer to the reconciliation method that uses these weights as `Spend-WLS' and the loss function based on these weights as `Spend-WSE'.%
-}
-
-{\color{blue} For each replication we compute the ratio of the loss of each alternative reconciliation method to the loss of base forecasts.
+
+For each replication we compute the ratio of the loss of each alternative reconciliation method to the loss of base forecasts.
 A value less than 1 indicates that a reconciliation method has a lower relative error than the base forecast for that replication, while a value greater than 1 indicates the opposite.
@@
 
-}
-
 %As the theory predicts, OLS reconciliation always leads to an improvement relative to base forecasts.
@@
     \includegraphics[width = \textwidth, height=14cm]{Figs/lossboxplots_1.pdf}
-    \caption{{\color{blue} Ratio of loss of reconciled forecast to loss of base forecast for $h = 1$.
+    \caption{Ratio of loss of reconciled forecast to loss of base forecast for $h = 1$.
 A value less than 1 indicates that the reconciled forecasts improve upon base forecasts.
-A log scale is used for the y axis.}}\label{fig:BaseVSRecon_Fc}
+A log scale is used for the y axis.}\label{fig:BaseVSRecon_Fc}
 \end{figure}
@@
 
-{\color{blue}
 The advantage of MinT however is clearly seen when loss functions are averaged (an estimate of expected loss).
@@
 This is precisely what would be expected from Theorem~\ref{th:gmint}.
-For Structural-WSE, a Friedman test confirms that the average loss for MinT is significantly lower when tested against every other method\footnote{{\color{blue} While differences are not significant for the other loss functions, the scale of the aggregate series leads to a large variance in loss, reducing the power of the test.
-Strutural-WSE stabilises this effect.}}.
-}
+For Structural-WSE, a Friedman test confirms that the average loss for MinT is significantly lower when tested against every other method\footnote{While differences are not significant for the other loss functions, the scale of the aggregate series leads to a large variance in loss, reducing the power of the test.
+Strutural-WSE stabilises this effect.}.
 
@@
 	\centering
-{\color{blue}
 	\begin{tabular}{lrrrrrr}
@@
     \end{tabular}
-}
-	\caption{{\color{blue}Means of different loss functions for 1-step ahead forecasts using different reconciliation methods in the tourism application.
-All figures are reported relative to base forecasts.}}
+
+	\caption{Means of different loss functions for 1-step ahead forecasts using different reconciliation methods in the tourism application.  All figures are reported relative to base forecasts.}
 	\label{tab:lossVmethods}
@@
 Using the three sets of base forecasts from each of the two transformations, we generate coherent forecasts implementing OLS and MinT reconciliation projections, and also the bottom-up approach and compare the results for when the base forecasts are biased and bias-adjusted, i.e., unbiased.
-{\color{blue} In addition to the relative mean total squared error (RMTSE) defined in Eq.~\eqref{eq:RTSE}, the relative mean absolute total error (RMATE) is used to measure bias.
+In addition to the relative mean total squared error (RMTSE) defined in Eq.~\eqref{eq:RTSE}, the relative mean absolute total error (RMATE) is used to measure bias.
 Total error (TE) is first calculated
@@
 This testing approach does not impose any distributional assumptions and does not require multiple pairwise testing between forecasts, which would distort the outcome of the tests.
-We use the implementation of the tests available in the \verb"tsutils" \citep{tsutils} package for R.}
+We use the implementation of the tests available in the \verb"tsutils" \citep{tsutils} package for R.
 
 \begin{table}[!b]
-{\color{blue}
 \caption {{\color{blue} RMATE and RMTSE} of $1$-step-ahead forecasts from log and Box-Cox transformed series.
@@
   \end{tabular}
-}    {\color{blue} $^\ast$ indicates a statistically significant difference from the biased base forecasts.}
+$^\ast$ indicates a statistically significant difference from the biased base forecasts.
 
@@
 Hence, the two columns labelled ``Biased'' contain results for biased base but also reconciled forecasts.
-Using Method-1 for first bias adjusting the base forecasts and then reconciling, results in forecast improvements for all methods {\color{blue} for both RMATE and RMTSE and} both the log and the Box-Cox transformations.
-{\color{blue}There are improvements over the biased base forecasts OLS returns the best results for RMATE while MinT returns the best results for RMTSE.} In contrast to the results from using Method-1 for bias adjusting before reconciliation, using Method-2 has an adverse effect on the forecast accuracy of the reconciled forecasts.
-In this case the reconciled unbiased forecasts {\color{blue}leads to a significantly worse RMATE and RMTSE compared to base forecasts.} This sends the warning that implementing inappropriate bias adjustment, in this case using an additive rather than a multiplicative factor, will hinder forecast accuracy and extra care must be taken in this bias adjustment procedure.
-
-{\color{blue} Also  of interest is the fact that reconciliation can to some extent mitigate bias even without bias correction.
+Using Method-1 for first bias adjusting the base forecasts and then reconciling, results in forecast improvements for all methods for both RMATE and RMTSE and both the log and the Box-Cox transformations.
+There are improvements over the biased base forecasts OLS returns the best results for RMATE while MinT returns the best results for RMTSE.
+In contrast to the results from using Method-1 for bias adjusting before reconciliation, using Method-2 has an adverse effect on the forecast accuracy of the reconciled forecasts.
+In this case the reconciled unbiased forecasts leads to a significantly worse RMATE and RMTSE compared to base forecasts.
+This sends the warning that implementing inappropriate bias adjustment, in this case using an additive rather than a multiplicative factor, will hinder forecast accuracy and extra care must be taken in this bias adjustment procedure.
+
+Also  of interest is the fact that reconciliation can to some extent mitigate bias even without bias correction.
 In particular, using OLS reconciliation without bias correction leads to a statistically significant reduction in bias relative to base forecasts.
 This is likely to occur since the direction of bias lies in a direction that is close to orthogonal to the coherent subspace.
-Projection therefore eliminates this bias to some extent.}
+Projection therefore eliminates this bias to some extent.
 
@@
 
-Defining concepts such as coherence and reconciliation in geometric terms provides new insights into hierarchical forecasting methods. {\color{blue} We recommend the following steps for practitioners.
+Defining concepts such as coherence and reconciliation in geometric terms provides new insights into hierarchical forecasting methods. We recommend the following steps for practitioners.
 \begin{enumerate}
@@
     \end{itemize}
-\end{enumerate}}
-{\color{blue} Furthermore, for the second objective, base forecasts must be unbiased.
-We recommend carrying out} bias correction before reconciliation {\color{blue} and provide evidence that this} improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation.
+\end{enumerate}
+Furthermore, for the second objective, base forecasts must be unbiased.
+We recommend carrying out bias correction before reconciliation and provide evidence that this improves forecast accuracy compared to approaches that do not bias correct and/or do not use reconciliation.
 
@@
 We now discuss three such possibilities.
-First, it should be possible to extend the concept of coherence {\color{blue}to examples where the coherent space is not a linear plane in $\mathbb{R}^n$.
+First, it should be possible to extend the concept of coherence to examples where the coherent space is not a linear plane in $\mathbb{R}^n$.
 This includes the case where in addition to aggregation constraints, forecasts are also constrained to be non-negative.
-We note the work of \cite{wickramasuriya2019optimal} as an attempt to address this issue.
-Another possibility is} non-linear constraints where the coherent space may need to be defined by a manifold.
+We note the work of \cite{wickramasuriya2019optimal} and \cite{KouAth2020} as attempts to address this issue.
+Another possibility is non-linear constraints where the coherent space may need to be defined by a manifold.
 Although much more challenging, it is still possible to define reconciled forecasts in terms of projections onto a manifold.

### 2020-08-13 SourceFiles/HierarchicalForecastReconciliation.tex
Fixed blinding on titlepage

@@
 
-%\pdfminorversion=4
-% NOTE: To produce blinded version, replace "0" with "1" below.
-\newcommand{\blind}{1}
-
 % DON'T change margins - should be 1 inch all around.
@@
 
-\begin{document}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\if1\blind
-{
-\title{\bf Forecast reconciliation: A geometric view with new insights on bias correction}
+% NOTE: To produce blinded version
+\makeatletter
+\newif\if@blind
+\@blindtrue %uncomment to hide author names
+%\@blindfalse %uncomment to show author names
+
+\if@blind
+  \author{}
+  \def\titlepage{\maketitle}
+\else
   \author{Anastasios Panagiotelis\\
@@
 The authors gratefully acknowledge the support of Australian Research Council Grant DP140103220.
-We also thank Professor Mervyn Silvapulle for valuable
+We also thank Professor Mervyn Silvapulle for valuable comments.}\\
     Department of Econometrics and Business Statistics,\\
@@
     Monash University, VIC 3800, Australia.\\
-    Email: Rob.Hyndman@monash.edu\\[1.5cm]}
-  \maketitle
-} \fi
-
-\if0\blind
-{
-  \bigskip
-  \bigskip
-  \bigskip
-  \begin{center}
-    {\LARGE\bf Forecast reconciliation: A geometric view with new insights on bias correction}
-  \end{center}
-  \medskip
-} \fi
-
-\newpage
+    Email: Rob.Hyndman@monash.edu\\[1.5cm]
+  }
+  \def\titlepage{\maketitle\newpage}
+\fi
+\makeatother
+
+\title{\bf Forecast reconciliation: A geometric view with new insights on bias correction}
+
+\begin{document}
+\titlepage
 
